### 2019-11-15 Code/analysis.Rmd
Code for importing, processing and plotting gaze data.

---
title: "Statistical analysis"
author: "Gonzalo García-Castro, Serene Siow, Nuria-Sebastian-Galles, and Kim Plunkett"
date: "10/28/2019"
output: pdf_document
bibliography: "../Bibliography/CognatePriming.bib"
csl: "../Bibliography/apa.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

sample.rate <- 120

```

We will use **Logistic Growth Curve Analysis** to analyse our data [e.g. @vonholzen2012; @chow2018]. Growth Curve Analysis [GCA; @mirman2008] allows us to model the probability of target fixation across the time course of trials. Traditional analyses of the Visual World Paradigm involve aggregating the number/proportion of fixation of each trial to  single value to be predicted by certain variables of interest. By using GCA, we will we will minimise the need to aggregate data across trials, thus increasing the power of our analysis. GCA is a generalised case of regression models where multiple polynomials of the time course of the trial are included as predictors. This means that our model will be able to accomodate non-linear patterns of target fixations within a given trial. Since our response variable is binary (i.e. follows a binomial distribution), we use logistic regression, following @barr2008 guidelines. We will include three predictors of interest to model the probability of target fixation at each time point: prime-target relatedness (related/unrelated, $Relatedness$), prime cognateness (cognate/non-cognate, $Cognateness$), linguistic profile (Spanish-English, Spanish-Catalan, $Profile$). We will include participants ($ID$), and items ($Item$) as random effects to account for variability caused by individual differences across participants or intrinsic properties of the stimuli involved in each trial.

# Response variable

We want to predict whether a given participant is fixating the target in each time point within a given trial. This response variable follows a binomial distribution: at each time point within the trial, a participant is either fixating the target or not. This technique requires the transformation of the in-principle binary outcome to either the log odds scale or the logit scale. We will transform our response variable to the empirical logit scale, given that the first tends to be problematic for near-zero values [@agresti2000; @mccullagh1989; both cited by @barr2013].

The presence of a target fixation in each time point will be coded as 1, and its absence will be coded as 0. We create time bins of 50 ms duration (`r sample.rate*0.05` samples, given `r sample.rate` Hz sampling rate). At each time bin within the trial, we will aggregate fixations for each participant, item, and condition using the empirical logit transformation suggested by @barr2008:

$$
elogit(Y, N) = \log \left(\frac{Y+0.5}{N-Y+0.51}\right)
$$

Where $elogit(Y, N)$ is the resulting empirical logit of target fixation for $Y$ number of fixations across trials and $N$ number of trials. This formula includes a 0.5 adjustment factor that avoids unreliable logit scores near endpoints. This empirical logic, from now on named $elog$ indicates the probability of target fixation at each time bin within the trial.

## Missing data

We will use multilevel multiple imputation [@vanbuuren2013].

# Model

To predict the probablity of target fixation, we will include several terms in our model. Some terms will correspond to variables of intrinsic interest, others will be included to account for individual differences across participants and items.

## Fixed effects

### Effects of interest

We expect three variables to exert an effect on the probability of target fixation across the time course of each trial: prime-target phonological relatedess ($Relatedness$), prime cognateness ($Cognateness$), and linguistic profile ($LangProfile$). We will implement these predictors by including the following terms in our model as fixed effects:

* Overall intercept ($\beta_{0}$)
* Time ($ot1$): time within trial, specified in seconds to avoid coefficients being too small [@barr2008]. Following @barr2008 guidelines, we will time-lock the time domain at the time point at which the grand mean of the probability of fixations shows the first tendency to rise. This will be taken as an indicator of signal-driven looking behaviour.
* Time2 ($ot2$): second-order (quadratic) polynomial of the time domain.
* Time3 ($ot3$): third-order (cubic) polynomial of the time domain.
* Prime-target relatedness ($Relatedness$): do prime and target words hare phonological onset (related/unrelated)
* Prime cognateness ($Cognateness$): is the prime word a cognate between the languages the two toddler is learning?
* Interaction effect of prime-target relatedness and prime cognateness ($Relatedness \times Cognateness$).

### Individual differences

The expect other variables not directly related to out hypothesis to also determine the probability of target fixation. Some of these variables will influence the outcome via individual differences across participants, while others will do so via intrinsic properties of the stimuli included in each trial. Regarding participant-level differences, we expect the effects of interest to be influenced by participants' receptive vocabulary size in their dominant language ($VocabSizeL1$), participants' receptive vocabulary in their non-dominant language ($VocabSizeL2$), and sex ($Sex$). Regarding stimulus-level differences, we expect our the effects of interest to be influenced by prime frequency, ($PrimeFreq$), and target frequency ($TargetFreq$). We will account for such differences among participants and items by including the following terms in our model as fixed effects:

* Receptive vocabulary size in dominant language ($VocabSizeL1$): number of words participants are able to understand in their dominant language (i.e. the language in which they were tested). Continous variable.
* Receptive vocabulary size in non-dominant language ($VocabSizeL2$): number of words participants are able to understand in their non-dominant language (i.e. the language in which they were not tested). Continuous variable.
* Sex ($Sex$): Sex of the participant. Categorical variable (female/male).
* Prime word frequency ($PrimeFreq$): Frequency of the label associated to the prime image, operationalised by the Zipf score of such word in SUBTLEX corpora. Continuous variable.
* Target word frequency ($PrimeFreq$): Frequency of the label associated to the target image, operationalised by the Zipf score of such word in SUBTLEX corpora. Continuous variable.

## Random effects

We will include participant ($ID$) and item ($Item$) as crossed random effects [@barr2008]:

* Random intercept by participant: The overall target fixation probability will be allowed to vary across participants.
* Random slope for main effect of prime-target relatedness by participant: The effect of prime-target relatedness will be allowed to vary across participants.
* Random slope for main effect of prime cognateness by participant: The effect of prime cognateness will be allowed to vary across participants.
* Random slope for interaction effect of prime-target relatedness and prime cognatess by participant: The effect of the interaction effect of prime-target relatedness and prime cognateness will be allowed to vary across participants.
* Random intercept by item: The overall target fixation probability will be allowed to vary across items (target-distractor pairs).
* Random slope for main effect of prime-target relatedness by item: The effect of prime-target relatedness will be allowed to vary across items.
* Random slope for main effect of prime cognateness by item: The effect of prime cognateness will be allowed to vary across items.
* Random slope for interaction effect of prime-target relatedness and prime-cognateness by item: The interaction effect between prime-target relateddness and prime cognateness will be allowed to very across items.
* Random slope for the main effect of Time, Time2 and Time3 by participant: The intercept of the target fixation probability will be allowed to vary across time points for each participant.
* Random slope for all combinations of interactions between the three time terms by participant.
* Random slope for the main effect of Time, Time2, and Time3 by item: The intercept of the target fixation probability will be allowed to vary across time points for each item.
* Random slope for all combinations of interactions between the three time terms by item.

## Formal model

The maximal-random structure of our multilevel model can be summarised in the following set of formulas:

### Level 1

The likelihood of target fixation, expressed as the epirical logic transformation of the originally binary outcome, is predicted for each participant, item and a linear, a quadratic, and a cubic transformation of the time domain, parsed into time bins of 50 ms.

$$
\begin{aligned}
elog_{fip} = &\pi_{0} + \pi_{1}Time_{fip} + \pi_{2}Time2_{fip} + \pi_{3}Time3_{fip} + \dots \\
&\pi_{4}(Time1 \times Time2)_{fip} + \dots \\
&\pi_{5}(Time1 \times Time3)_{fip} + \dots \\
&\pi_{6}(Time2 \times Time3)_{fip} + \dots \\
&\pi_{7}(Time1 \times Time2 \times Time3)_{fip}
&\end{aligned}
$$

Where:

* $elog$ is the empirical logit of target fixation
* $t$ is the time bin
* $f$ indexes time bins 
* $i$ indexes items
* $p$ indexes participants
* $\pi_0$ is the overal intercept for participant $p$, in item $i$, at time bin $f$ 
* $\pi_1$ is the regression coefficient (slope) of the linear time term ($Time$)
* $\pi_2$ is the regression coefficient (slope) of the quadratic time term ($Time2$)
* $\pi_3$ is the regression coefficient (slope) of the cubic time term ($Time3$)
* $\pi_4$ is the regression coefficient (slope) of the interaction between the linear and the quadratic time terms ($Time1 \times Time2$)
* $\pi_5$ is the regression coefficient (slope) of the interaction between the linear and the cubic time terms ($Time1 \times Time3$)
* $\pi_6$ is the regression coefficient (slope) of the interaction between the cuadratic and the cubic time terms ($Time2 \times Time3$)
* $\pi_7$ is the regression coefficient (slope) of the interaction between the linear, the quadratic, and the cubic time terms ($Time1 \times Time2 \times Time3$)

### Level 2

The regression coefficients previously used to predict the likelihood of target fixation are a function of the predictors of interest (i.e. fixed effects). They are computed for each participant in each item. fixed effects include prime-target relatedness, prime-cognateness, and their interaction.

$$\pi_0 =  \beta_{00} + \beta_{01} Relatedness_{ip} + \beta_{02} Cognateness_{ip} + \beta_{03} (Relatedness \times Cognateness)_{ip} + r_{0} + u0$$

Where:

* $\beta_{00}$ is the grand mean of the intercept.
* $\beta_{01}$ is the slope of the main effect of Relatedness on the overall intercept.
* $\beta_{02}$ is the slope of the main effect of Cognateness on the overall intercept.
* $\beta_{03}$ is the slope of the interaction effect between Relatedness and Cognateness on the overall intercept.
* $r_0$:

$$\pi_1 =  \beta_{10} + \beta_{11} Relatedness_{ip} + \beta_{12} Cognateness_{ip} + \beta_{13} (Relatedness \times Cognateness)_{ip} + r_{1} + u1$$

Where:

* $\beta_{10}$ is the grand mean of the slope of the meain effect of the linear time term.
* $\beta_{11}$ is the slope of the main effect of Relatedness on the overall slope of the main effect of the linear time term.
* $\beta_{12}$ is the slope of the main effect of Cognateness on the overall slope of the main effect of the linear time term.
* $\beta_{13}$ is the slope of the interaction effect of Relatedness and Cognateness on the overall slope of the main effect of the linear time term.
* $r_1$:

$$\pi_2 =  \beta_{20} + \beta_{21} Relatedness_{ip} + \beta_{22} Cognateness_{ip} + \beta_{23} (Relatedness \times Cognateness)_{ip} + r_{2} + u2$$

Where:

* $\beta_{20}$ is the grand mean of the slope of the main effect of the quadratic time term.
* $\beta_{21}$ is the slope of the main effect of Relatedness on overall slope of the main effect of the quadratic time term.
* $\beta_{22}$ is the slope of the main effect of Cognateness on overall slope of the main effect of the quadratic time term.
* $\beta_{23}$ is the slope of the interaction effect of Relatedness and Cognateness on overall slope of the main effect of the quadratic time term.
* $r_2$:

$$\pi_3 =  \beta_{30} + \beta_{31} Relatedness_{ip} + \beta_{32} Cognateness_{ip} + \beta_{33} (Relatedness \times Cognateness)_{ip} + r_{3} + u3$$

Where:

* $\beta_{30}$ is the grand mean of the slope of the main effect of the cubic time term.
* $\beta_{31}$ is the slope of the main effect of Relatedness on overall slope of the main effect of the cubic time term.
* $\beta_{32}$ is the slope of the main effect of Cognateness on overall slope of the main effect of the cubic time term.
* $\beta_{33}$ is the slope of the interaction effect of Relatedness and Cognateness on overall slope of the main effect of the cubic time term.
* $r_3$:

$$\pi_4 =  \beta_{40} + \beta_{41} Relatedness_{ip} + \beta_{42} Cognateness_{ip} + \beta_{43} (Relatedness \times Cognateness)_{ip} + r_{4} + u4$$

Where:

* $\beta_{40}$ is the grand mean of the slope of the interaction effect of the linear and the quadratic time terms.
* $\beta_{41}$ is the slope of the main effect of Relatedness on overall slope of the interaction effect of the linear and the quadratic time terms.
* $\beta_{42}$ is the slope of the main effect of Cognateness on overall slope of the interaction effect of the linear and the quadratic time terms.
* $\beta_{43}$ is the slope of the interaction effect of Relatedness and Cognateness on overall slope of the interaction effect of the linear and the quadratic time terms.
* $r_4$:

$$\pi_5 =  \beta_{50} + \beta_{51} Relatedness_{ip} + \beta_{52} Cognateness_{ip} + \beta_{53} (Relatedness \times Cognateness)_{ip} + r_{5} + u5$$

Where:

* $\beta_{50}$ is the grand mean of the slope of the interaction effect of the linear and the cubic time terms.
* $\beta_{51}$ is the slope of the main effect of Relatedness on overall slope of the interaction effect of the linear and the cubic time terms.
* $\beta_{52}$ is the slope of the main effect of Cognateness on overall slope of the interaction effect of the linear and the cubic time terms.
* $\beta_{53}$ is the slope of the interaction effect of Relatedness and Cognateness on overall slope of the interaction effect of the linear and the cubic time terms.
* $r_5$:

$$\pi_6 =  \beta_{60} + \beta_{61} Relatedness_{ip} + \beta_{62} Cognateness_{ip} + \beta_{63} (Relatedness \times Cognateness)_{ip} + r_{6}  + u6$$

Where:

* $\beta_{60}$ is the grand mean of the slope of the interaction effect of the quadratic and the cubic time terms.
* $\beta_{61}$ is the slope of the main effect of Relatedness on overall slope of the interaction effect of the quadratic and the cubic time terms.
* $\beta_{62}$ is the slope of the main effect of Cognateness on overall slope of the interaction effect of the quadratic and the cubic time terms.
* $\beta_{63}$ is the slope of the interaction effect of Relatedness and Cognateness on overall slope of the interaction effect of the quadratic and the cubic time terms.
* $r_6$:

$$\pi_7 =  \beta_{70} + \beta_{71} Relatedness_{ip} + \beta_{72} Cognateness_{ip} + \beta_{73} (Relatedness \times Cognateness)_{ip} + r_{7} + u7$$

Where:

* $\beta_{70}$ is the grand mean of the slope of the interaction effect of the linear, the quadratic and the cubic time terms.
* $\beta_{71}$ is the slope of the main effect of Relatedness on overall slope of the interaction effect of the linear, the quadratic and the cubic time terms.
* $\beta_{72}$ is the slope of the main effect of Cognateness on overall slope of the interaction effect of the quadratic and the cubic time terms.
* $\beta_{73}$ is the slope of the interaction effect of Relatedness and Cognateness on overall slope of the interaction effect of the linear, the quadratic and the cubic time terms.
* $r_7$:

## Model implementation

We will use the `lme4` R package [@bates2015] to fit the model. We will use population-average parameter estimation [@fitzmaurice2004; cited by @barr2008] with Restricted Maximum Likelihood criterion (REML). We will use the "bobyqa" optimiser from the `minqa` R package [@bates2014], and will set the maximum number of iterations at 1000 [@field2013].

Following @mirman2016, we will adjust the importance of observations based on their reliability. We want more reliable observations to be more determining on how coefficients are estimated to fit the model to the data. Empirical logit scores resulting from aggregating fixations across a higher amount of trials will be weighted higher that those resulting from aggregating less trials. Weights will be calculated using the following formula:

$$
w(Y, N) = \frac{1}{Y+0.5} + \frac{1}{N-Y+0.5}
$$

The model will be implemented in R using the following code:

```{r model, eval=FALSE, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=FALSE}

lme4::lmer(
  # response variable
  elog ~                                          # empirical logic of target fixation
    # fixed effects
    (ot1+ot2+ot3) +                               # f eff of time, time^2 and time^3
    Relatedness +                                 # f eff of prime-target relatedness
    Cognateness +                                 # f eff of prime cognateness (C)
    LangProfile +                                 # f eff of language profile (LP)
    Relatedness*Cognateness +                     # f int of R and C
    Relatedness*LangProfile +                     # f int of R and LP
    Cognateness*LangProfile +                     # f int of C and LP
    Relatedness*Cognateness*LangProfile +         # f int of C and LP
    VocabSizeL1 +                                 # f eff of receptive L1 vocab
    VocabSizeL2 +                                 # f eff of receptive L2 vocab
    PrimeFreq +                                   # f eff of prime label freq
    TargetFreq +                                  # f eff of target label freq

    # random effects
    (1|ID) +                                      # r int by ID
    (1+ot1+ot+ot3|ID) +                           # r int and slope of time by ID
    (1+Relatedness|ID) +                          # r int and slope of R by ID
    (1+Cognatedness|ID) +                         # r int of of of C by ID
    (1+LangProfile|ID) +                          # r int of of of LP by ID
    (1+Relatedness*Cognatedness|ID) +             # r int and slope of RxC by ID
    (1+Relatedness*LangProfile|ID) +              # r int and slope of RxLP by ID
    (1+Cognateness*LangProfile|ID) +              # r int and slope of CxLP by ID
    (1+Relatedness*Cognateness*LangProfile|ID) +  # r int and slope of RxCxLP by ID
    (1|Item) +                                    # r int by item
    (1+ot1+ot+ot3|Item) +                         # r int and slope of time by item
    (1+Relatedness|Item) +                        # r int and slope of of R by item
    (1+Cognateness|Item) +                        # r int and slope of of C by item
    (1+LangProfile|Item) +                        # r int and slope of of R by item
    (1+Relatedness*Cognateness|Item) +            # r int and slope of RxC by item
    (1+Relatedness*LangProfile|Item) +            # r int and slope of RxLP by item
    (1+Cognateness*LangProfile|Item) +            # r int and slope of CxLP by item
    (1+Relatedness*Cognateness*LangProfile|Item), # r int and slope of RxCxLP by item

  # other settings
  data = CognatePriming,                          # data set
  REML = TRUE,                                    # use Restricted Maximum Likelihood
  control = lmerControl(
    maxit = 1000,                                 # number of max iterations to 1000
    optimizer = "bobyqa"                          # define optimiser
  ), 
  verbose = TRUE,                                 # for more information during fitting
  weights = 1/weights                             # weight of each observation
)

```

### Dealing with convergence issues

Due to the large number of parameters to be estimated in our model, and the limited amount of data we can collect, it is posible that we run into convergence issues. Logistic regression models are more likely than linear regression models to be subject of convergence issues as the random effects structure gets more complex. Lack of convergence means that some of the estimated coefficients are unreliable, as other values of the same coefficients could provide a similar fit to the data. We will handle this issue as follows:

 1. We will change the optimiser until we reach convergence: first to "optimx" from the `optimx` R package [@nash2014], second to "nloptwrap" from the `nloptr` R package [@johnson2018]. If lack of convergence persist we will skip to step 2.
 2. We will start a pruning process to simplify our model. Terms will be dropped from the model according to their scientific interest of for theoretical reasons. The order of pruning will be as follows:
    1) Random slopes of the interaction effect between `Relatedness` and `Cognateness` by item.
    2) Random slopes of main effect of `Relatedness` and `Cognateness` by item.
    3) Random slopes of the interaction effect between `Relatedness` and `Cognateness` by participant.
    4) Random slopes of the main effects of `Relatedness` and `Cognateness` by participant.
    5) Main (fixed) effect of the 3rd order (cubic) polynomial of time (`ot3`), exluding this term from the random by-participant and by-item effect.

If after taking the previous steps, convergence issues persist, we consider that dropping more terms would lead to the oversimplification of the model. This model would no longer capture the sources of variation that we consider intrincis to our hypotheses. For this reason, at this point we will change the approach and will perform Bayesian modelling.

## Inference criteria

We will use a frequentist approach toward statistical inference. Extracting *p*-values in mixed-effect models is not straightforawrd due to the difficulty to estimate the degrees of freedom of the distributions from which parameters are drawn. We will use the Satterthwaite's approximation to degrees of freedom [@satterthwaite1948] to extract *p*-values using the `lmerTest` R package [@kuznetsova2017]. If we run into convergence issues that persist even after model simplification, we will shift to a fully Bayesian approach toward statistical inference (see previous section).

## Data exclusion

How will you determine which data points or samples if any to exclude from your analyses? How will outliers be handled? Will you use any awareness check?

## References

### 2019-11-15 Code/check_aoi.R

@@ -1,0 +1,18 @@
+# check_aoi: Evaluate whether gaze is in AOI
+# Gonzalo García-Castro, gonzalo.garciadecastro@upf.edu
+# Based on Kret & Sjak-Shie (2019)
+# https://link.springer.com/article/10.3758/s13428-018-1075-y
+# Center for Brain and Cognition, Pompeu Fabra University
+
+check_aoi <- function(
+  data,
+  aoi = c(1140, 1640, 290, 790),
+  gazeX, gazeY
+){
+  require(rlang)
+  data %>%
+    {{ gazeX }}>=aoi[1] &
+    {{ gazeX }}<=aoi[2] &
+    {{ gazeY }}>=aoi[3] &
+    {{ gazeY }}<aoi[4]
+}

### 2019-11-15 Code/get_dilation_speed.R

@@ -1,0 +1,23 @@
+# get_dilation_speed: Calculate dilation speed
+# Gonzalo García-Castro, gonzalo.garciadecastro@upf.edu
+# Based on Kret & Sjak-Shie (2019)
+# https://link.springer.com/article/10.3758/s13428-018-1075-y
+# Center for Brain and Cognition, Pompeu Fabra University
+
+get_dilation_speed <- function(data, pupil, time){
+  
+  require(rlang)
+
+  data %>%
+    mutate(
+      diff_pre       = abs({{ pupil }} - lag({{ pupil }})),
+      diff_time_pre  = abs({{ time }}  - lag({{ time }})),
+      diff_post      = abs({{ pupil }} - lead({{ pupil }})),
+      diff_time_post = abs({{ time }}  - lead({{ time }})),
+      pot_pre        = diff_pre/diff_time_pre,
+      pot_post       = diff_post/diff_time_post
+    )
+  }
+    
+
+

### 2019-11-15 Code/stimuli_duration.R

@@ -1,0 +1,111 @@
+# stimuli_duration: Calculate duration of audio files
+# Gonzalo García-Castro, gonzalo.garciadecastro@upf.edu
+# Center for Brain and Cognition, Pompeu Fabra University
+
+#### set up #############################################
+
+# load packages
+library(audio)     # for acoustic analysis
+library(tibble)    # for tidy data presentation
+library(magrittr)  # for using pipes ('%>%')
+library(dplyr)     # for manipulating data
+library(tidyr)     # for manipulating datasets
+library(purrr)     # for working with lists
+library(readxl)    # for importing Excel spreadsheets
+library(forcats)   # for working with categorical variables
+library(stringr)   # for working with character strings
+library(stringi)   # for working with character strings
+library(ggplot2)   # for visualising data
+library(ggalt)     # for plotting lollipops
+library(patchwork) # for arranging plots
+
+# specify paths
+file.names <- list.files('/Volumes/GONZALOGC/BiPrime/stimuli/sounds/04_denoised')                      # locate .wav files
+file.paths <- list.files('/Volumes/GONZALOGC/BiPrime/stimuli/sounds/04_denoised', full.names = TRUE)   # build path for each file
+words      <- str_replace_all(file.names, '04_|.wav', '') # word id
+
+#### get stimuli lists #######################################
+
+# make long version of stimuli lists
+trials.long <-
+  # import stimuli lists
+  as.list(c('/Volumes/GONZALOGC/biprime/stimuli/stimuli_stats_catalan.xlsx',
+            '/Volumes/GONZALOGC/biprime/stimuli/stimuli_stats_spanish.xlsx')) %>%
+  map(~read_xlsx(.)) %>%
+  map(~mutate(., trialID = as.factor(trialID))) %>%
+  set_names(c('catalan', 'spanish')) %T>%
+  assign('trials.wide', ., envir = .GlobalEnv) %>% # save intermediate wide version
+  bind_rows(., .id = 'language') %>%
+  gather(role, 'word', -c(language, trialID, trialType)) %>%
+  select(word, language, trialID, role, trialType)
+
+trials.long$word <- stri_trans_general(trials.long$word, "latin-ascii")
+
+#### get durations ###########################################
+amplitude   <- map(file.paths, load.wave) %>% set_names(words) # extract amplitude from each audio
[…]

### 2019-11-15 Code/stimuli_ipa.R

@@ -1,0 +1,17 @@
+trials.long <-
+  # import stimuli lists
+  as.list(c('/Volumes/GONZALOGC/biprime/stimuli/stimuli_stats_catalan.xlsx',
+            '/Volumes/GONZALOGC/biprime/stimuli/stimuli_stats_spanish.xlsx')) %>%
+  map(~read_xlsx(.)) %>%
+  map(~mutate(., trialID = as.factor(trialID))) %>%
+  set_names(c('catalan', 'spanish')) %T>%
+  assign('trials.wide', ., envir = .GlobalEnv) %>% # save intermediate wide version
+  bind_rows(., .id = 'language') %>%
+  gather(role, 'word', -c(language, trialID, trialType)) %>%
+  select(word, language, trialID, role, trialType)
+
+  read_xlsx('/Volumes/GONZALOGC/biprime/stimuli/stimuli_main.xlsx', sheet = 'IPA') %>%
+  left.join(.,   read_xlsx('/Volumes/GONZALOGC/biprime/stimuli/stimuli_main.xlsx', sheet = 'IPA') %>%
+)
+  gather(role, 'word', -c(language, trialID, trialType)) %>%
+  select(word, language, trialID, role, trialType)

### 2020-01-30 Rmd/power.Rmd
Big time screwed up
I overwrote the folder with an empty one and lost almost everything I had done for the last month. "Sh*t, here we go again".

---
title: "Power analysis"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
bibliography: "../Bibliography/CognatePriming.bib"
csl: "../Bibliography/apa.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Justification

We plan to analyse our data using Growth Curve Analysis [GCA; @mirman2016] fitting a mixed-effects model that predicts the probability of fixation to the target at each time point within a given trial. Following @barr2013, we will specify a maximal random-effects structure. Our model will include, at least, polynomial transformations of the time domain (first, second, and third order, initially), prime-target phonological relatedness, and prime cognateness, as fixed effects. We will include random intercepts for participants and stimuli, and all combinations of random slopes for fixed effects by participants and items. In case of convergence issues due to model complexity, we will prune terms of the model following a pre-specified order.

There are limitations regarding the calculation of statistical power of mixed-effects models like ours, mainly due to the lack of consensus on how to estimate degrees of freedom. For this reason, we opted for calculating the power for a two-way repeated-measures ANOVA that only includes prime-target relatedness and prime cognateness as within-participant factors. Such analysis would neglect two important sources of variability, making it underspowered compared to the GCA we plan to perform.

The lack of random effect involving stimuli makes the ANOVA neglect two main sources of variability. First, the across-stimuli variability: some prime-target pairs may elicity larger priming effects. Second, this model neglects the temporal unfolding of fixations to the target across trials: the probability of fixation to the target must be summarised for each trial. This means tha radically divergent patterns of looking behaviour within trials can lead to the same average probability of fixation to the target [@barr2008]. The neglect of these two sources of variation makes this analysis underpowered when compared with the GCA we plan to perform.

For this reason our GCA will achieve a higher power that that resulting from a power analysis of the ANOVA, given identical parameters. Thus, we will perform a power analysis based on an underpowered ANOVA to calculate the under which parameters our GCA will achieve an appropriate power.

Due to contraints related to sample collection, we expect the maximum sample size we will be able to reach to be around 200 toddlers, including those tested in Barcelona and Oxford. Given this fixed sample size, we calculated the smallest effect size of interest we would be able to detect with that sample size ($N$ = 200), given a desired 80% statistical power, and a 5% significance criterion.

# Power analysis

We used the `pwr` R package [@champely2018] to calculate the smallest effect size we would be able to detect with a repeated measures ANOVA the only included prime-target relatedness and prime-cognateness as within-participant factors. This effect size would be an indicator of the sensitivity of our design. We used the following code:

```{r power, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}

n       <- 100     # sample size (by group)
power   <- 0.80    # desired power
alpha   <- 0.05    # significance criterion
es.eta2 <- 0.06 # effect size (eta-squared)
f       <- sqrt(es.eta2/(1-es.eta2)) # effect size (Cohen's f)

pwr <- pwr::pwr.anova.test(
  k         = 8,     # number of groups (2W x 2W x 2B)
  n         = n,     # maximum sample size per condition (1 by participant x 100 participants)
  sig.level = alpha, # significance criterion
  power     = power
  )
```

The smallest effect size our design would detect is a Cohen's $f$ = `r round(pwr$f, 3)`, small according to @cohen1969 standards. This effect size is equivalent to $\eta_p^2$ = `r round((pwr$f/(1-pwr$f))^2, 3)`. Put in others words our effect would be able to detect an effect that explains `r round((((pwr$f/(1-pwr$f)))^2)*100, 3)`% of the variance. Given that our planned GCA would yield a higher power, our power to detect the same effect size will be higher than 80%. Figure 1 depicts the increase in power associated with each possible sample size, given our parameters.

```{r power_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align="c", fig.cap="Statistical power as a function of sample size. Given the repeated measures nature of the ANOVA, the number of observations in each condition of the 2x2 design will be equal to the total sample size."}

pwr::plot.power.htest(pwr)

```

# References

### 2020-01-30 Code/analyse_power.R

@@ -1,41 +1,0 @@
-# Power analysis (based on DeBruine & Barr, 2019)
-# Gonzalo García-Castro, gonzalo.garciadecastro@upf.edu
-# Center for Brain and Congition, Pompeu Fabra University
-
-#### set up #############################################
-
-# load packages
-library(dplyr)       # for manipulating data
-library(magrittr)    # for using pipes
-library(tidyr)       # for reshaping datasets
-library(lmer)        # for Linear Mixed-Effects Models
-library(pwr)         # for power analysis
-library(ANOVApower)  # for power analysis
-library(broom.mixed) # for tidy lmer output
-
-#### analyse ANOVA power ################################
-cells <- expand.grid(
-  TrialType = c("unrelated", "non-cognate", "cognate"),
-  LP        = c("Spanish-English", "Spanish-Catalan"),
-  Age       = c(24, 30)
-  ) %>%
-  select(Age, LP, TrialType)
-
-labelnames <- cells %>%
-  unite("label", c(Age, LP, TrialType), sep = "_") %>%
-  pull(label)
-
-comparisons <- ((2*2*2)^2)-((2*2*2)/2)
-
-ANOVApower::ANOVA_design(
-  design = "2b*2b*2w",
-  n = 20,
-  mu = c(65, 60, 55,
-         65, 60, 50,
-         70, 65, 60,
-         70, 65, 55),
-  sd = 5,
-  r = rep(0.95, comparisons),
-  labelnames = labelnames,
-  plot = TRUE
-)

### 2020-02-13 Rmd/report.Rmd
First commit for report

---
title: "Report"
output: pdf_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# load packages
library(papaja)
library(knitr)
library(data.table)
library(dplyr)
library(magrittr)
library(readxl)
library(tidyr)
library(tibble)
library(ggplot2)
library(lubridate)
library(patchwork)
library(here)

# load data
data.sample <- read_xlsx(here("Data", "Participant data", "data_participants.xlsx"))
data.fixations <- fread(here("Data", "03_fixations.txt"))
trackloss <- fread(here("Data", "02_filtered-trackloss.txt"))

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "\\textwidth"
)
options(knitr.kable.NA = '-')

```

# Procedure

# Stimuli

# Sample

We tested `r data.sample %>% filter(!Pilot, DateTest<now()) %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` participants, of which `r data.sample %>% filter(!Pilot, DateTest<now(), !Valid) %>% pull(ID) %>% length() %>% printnum(digits = 0)` we excluded. The final sample included `r data.sample %>% filter(!Pilot, DateTest<now(), Valid, LangProfile=="Monolingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` monolinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan monolinguals, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish monolinguals) and `r data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` bilinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan-dominant, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish-dominant).

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

data.sample %>%
	filter(!Pilot, Valid, DateTest<now()) %>%
	select(ID, LangProfile, AgeGroup, Language, List, Sex) %>%
	group_by(LangProfile, AgeGroup, Language, List) %>%
	summarise(n = n()) %>%
	pivot_wider(id_cols = c("LangProfile", "AgeGroup", "Language"), names_from = "List", values_from = "n") %>%
	kable(digits = 0,
		  col.names = c("***LP***", "**Age group**", "**Language**", "**List 1**", "**List 2**", "**List 3**"), 
		  align = "c",
		  caption = "Sample size by age group, testing language, and list. Only participants that made it in the final sample are included.")

```

# Results

## Trackloss

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

trackloss %>%
	group_by(ParticipantID) %>%
	summarise(
		TracklossForParticipant = first(TracklossForParticipant),
		TracklossForParticipantSD = sd(TracklossForTrial, na.rm = TRUE)

		) %>%
	mutate(TracklossForParticipant = paste(printnum(TracklossForParticipant), "%"),
		   TracklossForParticipantSD = printnum(TracklossForParticipantSD)) %>%
	kable(digits = 3,
		  row.names = FALSE,
		  align = "c",
		  col.names = c("**Participant ID**", "**Mean**", "***SD***"),
		  caption = "Mean proportion of samples lost by trial.")

```

# Appendix

## Participants

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

data.sample %>%
	filter(!Pilot, DateTest<now()) %>%
	select(ID, LangProfile, AgeGroup, Language, List, DateTest, Age, Sex, Valid) %>%
	arrange(desc(Valid), LangProfile, AgeGroup, Language, List, DateTest) %>%
	kable(digits = 2,
		  row.names = FALSE,
		  align = "c",
		  col.names = c("**Participant ID**", "***LP***", "**Age group**", "**Lang.**", "**List**", "**Date**", "**Age**", "**Sex**", "**Valid?**"),
		  caption = "Complete list of participants. *LP* = Language profile.")

```

### 2020-03-02 Rmd/report.Rmd
Filter data

@@
 # load data
+stimuli.duration  <- fread(here("Data", "Stimuli", "stimuli_duration-aggregated.txt"))
 data.sample       <- read_xlsx(here("Data", "Participant data", "data_participants.xlsx"))
@@
 trackloss         <- fread(here("Data", "02_filtered-trackloss.txt"))
-
+results           <- fread(here("Data", "05_gca-results.txt"))
+predictions       <- fread(here("Data", "05_gca-predictions.txt"))
+multicollinearity <- fread(here("Data", "05_gca-multicollinearity.txt"))
 ```
@@
 	cache.extra = knitr::rand_seed,
-	out.width = "\\textwidth"
+	out.width = "100%",
+	results = "asis"
 )
@@
 # Stimuli
+
+## Duration
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+stimuli.duration %>%
+	select(Location, Language, Version, TrialType, m_duration, sd_duration, mean_overlap) %>%
+	kable(
+		digits = 2,
+		row.names = FALSE,
+		col.names = c("**Location**", "**Language**", "**Version**", "**Trial type**", "***M* duration (s)**", "***SD***", "***M* overlap (s)***"),
+		align = "c"
+	)
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Audio duration.
+A) Distribution of audio durations by trial type, split by testing language and location.
+Boxplots indicate median duration, 25\\% and 75\\% percentiles, and maximum and minimum.
+B) Distribution of overlap between audio and target-distractor presentation, split by testing language and location.
+C) Individual audio duration by word, split by trial type, testing language, and location.
+The dashed lines indicate the onset of target and distractor pictures presentation."}
+
+include_graphics(here("Figures", "Stimuli", "duration-overlap.png"))
+
+```
 
@@
 		TracklossForParticipantSD = sd(TracklossForTrial, na.rm = TRUE)
-
 		) %>%
@@
 		   TracklossForParticipantSD = printnum(TracklossForParticipantSD)) %>%
+	arrange(ParticipantID) %>%
 	kable(digits = 3,
@@
 
+```
+
+## Growth Curve Analysis
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+results %>%
+	select(Term, Estimate, SEM, Chisq, Df, p, ci1, ci2) %>%
+	mutate(CI = paste0("[", printnum(ci1, digits=2), ",", printnum(ci2, digits=2), "]"),
+		   p = printp(p)) %>%
+	select(-c(ci1, ci2)) %>%
+	kable(
+		digits = 2,
+		row.names = FALSE,
+		col.names = c("**Term**", "**$\\beta$**", "***SEM***", "**$\\chi^2$**", "***Df***", "***p***", "**95\\%*CI***"),
+		align = "c",
+		caption = "Results of the Growth Curve Analysis, reporting the estimated coefficients of the fixed effects included in the model. *p*-values were extracted using Wald's $\\chi^2$ approximation."
+	)
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Coefficients of the fixed effects included in the Growth Curve Analysis.
+Black dots and whiskers represent the estimated coefficient and standard error of the mean, respectively.
+Grey boxes represent two-sided 95\\% confidence intervals, calculated using the Wald $\\chi^2$ approximation to degrees of freedom."}
+
+include_graphics(here("Figures", "05_gca-coefficients.png"))
+
+```
+
+## Predictions
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Predicted unfolding of target fixations across the time course of the trial for each participant, split by trial type, language profile, and testing language."}
+
+include_graphics(here("Figures", "05_gca-predictions-participant.png"))
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Predicted unfolding of target fixations across the time course of the trial for each trial, split by trial type, language profile, and testing language."}
+
+include_graphics(here("Figures", "05_gca-predictions-trial.png"))
+
+```
+
+## Variance-covariance parameters
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Variance-covariance matrix."}
+
+include_graphics(here("Figures", "05_gca-vcov.png"))
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Correlations between random effects split by fixed effect."}
+
+include_graphics(here("Figures", "05_gca-correlation.png"))
+
+```
+
+## Checking assumptions
+
+### Normality
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Distribution of the observed studentised residuals, compared with the theoretical normal distribution."}
+
+include_graphics(here("Figures", "05_gca-residuals.png"))
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Distribution of the observed studentised residuals, compared with the theoretical normal distribution."}
+
+results %>%
+	select(Term, VIF) %>%
+	kable(digits = 2,
+		  row.names = FALSE,
+		  col.names = c("***Term***", "***VIF***"),
+		  align = "c",
+		  caption = "Multicollinearity" 
+		  )
 ```
@@
 	select(ID, LangProfile, AgeGroup, Language, List, DateTest, Age, Sex, Valid) %>%
-	arrange(desc(Valid), LangProfile, AgeGroup, Language, List, DateTest) %>%
+	arrange(desc(Valid), LangProfile, AgeGroup, Language, List, ID) %>%
 	kable(digits = 2,

### 2020-03-02 R/00_import.R

@@ -28,7 +28,10 @@ screenY       <- 1080 # height of the screen in pixels
 participants <- read_xlsx(here("Data", "Participant data", "data_participants.xlsx")) %>%
 	filter(!Pilot) %>%
 	drop_na(Version) 
-
+# import trial-level data
+trials <- read_xlsx(here("Stimuli", "stimuli.xlsx"))  %>%
+	mutate(TrialID = as.character(TrialID))
+	
 # import eye-tracking data
 data <- paste0(here("Data", "Gaze data", "Barcelona/"), participants$Filename) %>% # locate files with gaze data
 	map(., ~fread(., sep = ",", dec = '.', header = TRUE, stringsAsFactors = FALSE, na.strings = c("NaN", "NA", "Na", "-", ""))) %>%  # import files in the folder
@@ -47,24 +50,43 @@ data <- paste0(here("Data", "Gaze data", "Barcelona/"), participants$Filename) %
 	as_tibble() %>%
 	rename(
 		ParticipantID = Participant,
-		TrialID = Trial
-		) %>%
+		TrialID = Trial,
+		lDistance = lUserCoordZ,
+		rDistance = rUserCoordZ
+	) %>%
 	mutate(
 		TrialID       = as.character(TrialID),
-		meanX         = rowMeans(cbind(lX, rX), na.rm = TRUE)*screenX,  # change relative coords to screen coords
-		meanY         = rowMeans(cbind(lY, rY), na.rm = TRUE)*screenY,  # change relative coords to screen coords
-		meanDistance  = rowMeans(cbind(lUserCoordZ, rUserCoordZ), na.rm = TRUE)/1000, # change distance from screen to centimeters
+		lX            = lX*screenX, # change relative coords to screen coords
+		rX            = rX*screenX, # change relative coords to screen coords
+		lY            = lY*screenY, # change relative coords to screen coords
+		rY            = rY*screenY, # change relative coords to screen coords
+		meanX         = rowMeans(cbind(lX, rX), na.rm = TRUE),  
+		meanY         = rowMeans(cbind(lY, rY), na.rm = TRUE),
+		lDistance     = lDistance/1000,
+		rDistance     = rDistance/1000,
+		meanDistance  = rowMeans(cbind(lDistance, rDistance), na.rm = TRUE), # change distance from screen to centimeters
[…]

### 2020-03-02 R/01_process.R

@@ -1,4 +1,4 @@
-# 01_process: Analyse gaze in Cognate Priming task
+# 01_process: process data 
 # Gonzalo García-Castro, gonzalo.garciadecastro@upf.edu
 # Center for Brain and Cognition, Pompeu Fabra University
 
@@ -14,9 +14,9 @@ library(purrr)        # for working with lists
 library(here)         # for locating files
 
 # load functions
-source(here("R", "Functions", "prime_coords.R"))
-source(here("R", "Functions", "target_coords.R"))
-source(here("R", "Functions", "distractor_coords.R"))
+source(here("R", "Functions", "eval_prime.R"))
+source(here("R", "Functions", "eval_target.R"))
+source(here("R", "Functions", "eval_distractor.R"))
 "%!in%" <- function(x, y) !(x %in% y)
 
 # set experimental parameters
@@ -45,23 +45,23 @@ trials <- read_xlsx(here("Stimuli", "stimuli.xlsx"))
 data.merged <- left_join(data.raw, participants, by = "ParticipantID") %>%
 	left_join(., trials, by = c("TrialID", "Language", "Version", "List")) %>%
 	as_tibble() %>%
-	select(ParticipantID, TrialID, Phase, TimeStamp, meanX, meanY, meanDistance, Trackloss, TargetLocation, TrialType, Language, List, Version, DateTest, DateBirth, Age, Sex, LangProfile, ValidParticipant, ValidTrial, Pilot)
+	select(ParticipantID, TrialID, Phase, TimeStamp, lX, rX, meanX, lY, rY, meanY, lDistance, rDistance, meanDistance, Trackloss, TargetLocation, TrialType)
 
 #### process data ###########################################################
 data <- data.merged %>%
 	mutate(
 		TrialID = as.character(TrialID),
 		# evaluate if gaze is in prime AOI
-		GazePrime = prime_coords(data = .,
+		GazePrime = eval_prime(data = .,
 							 x_gaze = meanX,
 							 y_gaze = meanY),
 		# evaluate if gaze is in target AOI
-		GazeTarget = target_coords(data = .,
+		GazeTarget = eval_target(data = .,
 							  x_gaze = meanX,
 							  y_gaze = meanY,
 							  target_location = TargetLocation),
 		# evaluate if gaze is in distractor AOI
-		GazeDistractor = distractor_coords(data = .,
+		GazeDistractor = eval_distractor(data = .,
 								  x_gaze = meanX,
 								  y_gaze = meanY,
 								  target_location = TargetLocation),

### 2020-03-02 R/02_filter.R

@@ -17,7 +17,9 @@ library(eyetrackingR) # for processing eye-tracking data
 library(here)         # for locating files
 
 # set parameters
-sampling_rate <- 120
+sampling_rate  <- 120   # samples per second
+prime_duration <- 1500  # prime presentation duration (ms)
+target_duration <- 2000 # target-distractor presentation duration (ms)
 
 #### import data #########################################################
 
@@ -29,13 +31,15 @@ data.processed <- fread(here("Data", "01_processed.txt"), sep = "\t", header = T
 # import participants
 participants <- read_xlsx(here("Data", "Participant data", "data_participants.xlsx")) %>%
 	rename(ParticipantID    = ID,
-		   ValidParticipant = Valid)
+		   ValidParticipant = Valid) %>%
+	filter(!Pilot)
 
 # import trials
-trials <- read_xlsx(here("Stimuli", "stimuli.xlsx")) %>% select(-c(TargetLocation, ValidTrial, TrialType))
+trials <- read_xlsx(here("Stimuli", "stimuli.xlsx")) %>%
+	select(-c(TargetLocation, TrialType))
 
 # import vocabulary data
-#vocab <- fread("~/projects/BiLexicon/Data/02_merged.txt") %>% select(ID, Item, Response, LanguageItem = Language, Dominance)
+vocab <- fread("~/projects/BiLexicon/Data/02_merged.txt") %>% select(ID, Item, Response, LanguageItem = Language, Dominance)
 
 trial.familiarity <- left_join(participants, trials, by = c("Language", "Version", "List", "Location")) %>%
 	pivot_longer(c("PrimeCDI", "TargetCDI", "DistractorCDI"), names_to = "Role", values_to = "Item") %>%
@@ -48,46 +52,150 @@ trial.familiarity <- left_join(participants, trials, by = c("Language", "Version
 								Language=="Catalan" ~ PrimeCDI_Catalan & PrimeCDI_Spanish & TargetCDI_Catalan & DistractorCDI_Catalan,
 								TRUE                ~ NA)) %>%
 	select(ParticipantID, TrialID, AllKnown, Pilot)
+
+#### identify trials to remove #############################################
+
+# trials that are not valid because of how the words involved (constant across participants)
+exclude_list_trials <- trials %>%
+	filter(!ValidTrial) %>%
[…]

### 2020-03-02 R/Functions/filter_trials.R

@@ -1,0 +1,70 @@
+#### filter_trials_aoi: Filter trials according by time in AOI
+# Gonzalo García-Castro, gonzalo.garciadecastro@upf.edu
+# Center for Brain and Cognition, Universitat Pompeu Fabra
+
+################################################################
+
+filter_trials <- function(
+	
+	data,                                          # dataset
+	participant_cols,                              # column indexing participants
+	aoi_cols,                                      # column(s) evaluating whether gaze is in AOIs
+	trial_cols,                                    # column indexing trials
+	condition_cols,                                # column indexing gruping variables
+	trackloss_cols,                                # column indicating trackloss
+	trial_phase_col,                               # column indicating trial phase
+	trial_phase                            = NULL, # trial phase(es) of interest; if NULL include all
+	trial_aoi                              = NULL, # AOI; if NULL include all
+	max_trackloss_trial                    = 0.75, # max number of invalid samples by trial
+	max_trackloss_trial_by_phase           = TRUE, # should max_trackloss_trial be applied phase-wise?
+	max_trackloss_participant              = 0.50, # max number of invalid trials by participant
+	max_trackloss_participant_by_condition = TRUE, # should max_trackloss_participant by applied condition-wise? 
+	min_samples_aoi                        = 0.10, # min n samples to consider participant has looked at AOI
+	min_samples_aoi_each                   = TRUE  # should min_samples_aoi be applied AOI-wise?
+	
+	
+){
+	
+	# load packages
+	require(rlang, warn.conflicts = FALSE, quietly = TRUE)
+	require(dplyr, warn.conflicts = FALSE, quietly = TRUE)
+	require(tidyr, warn.conflicts = FALSE, quietly = TRUE)
+	
+	# filter by phase
+	data.phase <-
+		if(!is.null({{ trial_phase }}))
+			filter({{ data }}, {{ trial_phase_col }}=={{ trial_phase }})
+	else {{ data }}
+	
+	# print log
+	message(
+		paste0("Observations not correponding to the ",
+			   {{ trial_phase }},
+			   " trial phase were removed: ",
+			   nrow({{ data }})-nrow(data.phase),
+			   " out of ",
+			   nrow({{ data }}),
[…]

### 2020-03-02 R/stimuli_duration.R

@@ -46,8 +46,8 @@ durations <- tibble(
 			TRUE                    ~ "English"
 		),
 		Duration = unlist(
-			map2(.x = map(map(file.paths, load.wave) %>% set_names(file.names), length), # get time domain of each audio from sample rate and number of measurements
-				 .y = map(map(file.paths, load.wave) %>% set_names(file.names), get_rate),
+			map2(.x = map(map(Path, load.wave) %>% set_names(Filename), length), # get time domain of each audio from sample rate and number of measurements
+				 .y = map(map(Path, load.wave) %>% set_names(Filename), get_rate),
 				 .f = function(x = .x, y = .y) x*(1/y)*0.5
 			)  
 		)

### 2020-06-25 Rmd/report.Rmd
Restore workflow and prepare poster for ICIS

@@
 data.fixations    <- fread(here("Data", "03_fixations.txt"))
-trackloss         <- fread(here("Data", "02_filtered-trackloss.txt"))
+attrition         <- fread(here("Data", "02_filtered-excluded-trials.txt"))
 results           <- fread(here("Data", "05_gca-results.txt"))
@@
 	pivot_wider(id_cols = c("LangProfile", "AgeGroup", "Language"), names_from = "List", values_from = "n") %>%
+	mutate(Total = sum(`1`, `2`, `3`, na.rm = TRUE)) %>%
+
 	kable(digits = 0,
-		  col.names = c("***LP***", "**Age group**", "**Language**", "**List 1**", "**List 2**", "**List 3**"), 
+		  col.names = c("***LP***", "**Age group**", "**Language**", "**List 1**", "**List 2**", "**List 3**", "**Total**"), 
 		  align = "c",
@@
 
-trackloss %>%
-	group_by(ParticipantID) %>%
+attrition %>%
+	left_join(data.sample, by = c("ParticipantID" = "ID")) %>%
 	summarise(

### 2020-06-25 R/03_fixations.R

@@ -1,112 +1,0 @@
-# 03_fixations: Analyse gaze in Cognate Priming task
-# Gonzalo García-Castro, gonzalo.garciadecastro@upf.edu
-# Center for Brain and Cognition, Pompeu Fabra University
-
-#### set up ############################################
-
-# load packages
-library(magrittr)     # for using pipes
-library(readxl)       # for importing Excel files
-library(tibble)       # for tidy data presentation
-library(dplyr)        # for manipulating data
-library(purrr)        # for working with lists
-library(data.table)   # for importing data
-library(janitor)      # for cleaning variable names
-library(gazepath)     # for identiying fixations
-library(ggplot2)
-library(here)         # for locating files
-
-# set parameters
-time_bin_duration <- 100  # how long should time bins be in ms?
-sampling_rate     <- 120  # how many samples are takien per second?
-screen_x          <- 1920 # screen width in pixels
-screen_y          <- 1080 # screen heigh in pixels
-resolution        <- 23   # screen size in inches
-
-# load functions
-source(here("R", "functions.R")) 
-
-#### import data ###########################################################
-# import participant-level data
-participants <- read_xlsx(here("Data", "Participant data", "data_participants.xlsx")) %>%
-	clean_names() %>%
-	rename(participant_id = id,
-		   valid_participant = valid) %>%
-	filter(!pilot)
-
-# import trial-leve data
-trials <- read_xlsx(here("Stimuli", "stimuli.xlsx")) %>%
-	clean_names() %>%
-	select(-c(target_location, trial_type)) %>%
-	mutate(trial_id = as.character(trial_id))
-
-# import filtered data
-dat <- fread(here("Data", "02_filtered.csv"), sep = ",", header = TRUE, stringsAsFactors = FALSE) %>%
-	select(-c(phase, gaze_prime)) %>%
-	mutate(trial_id = as.character(trial_id),
-		   participant_id = as.character(participant_id)) %>%
-	as.data.frame()
-
-#### identify fixations ####################################################
-fixation_info <- split(dat, f = dat$participant_id) %>% # separate each participant's dataset
-	# get fixations in each dataset
-	map(., ~gazepath(data       = .,
-					 x1         = "l_x",             # horizontal position
-					 y1         = "l_y",             # vertical position
-					 d1         = "l_dist",          # distance
-					 x2         = "r_x",
[…]

### 2020-06-25 R/06_gca.R

@@ -1,98 +1,0 @@
-# 04_gca: Growth Curve Analysis
-# Gonzalo García-Castro, gonzalo.garciadecastro@upf.edu
-# Center for Brain and Congition, Pompeu Fabra University
-
-#### set up ################################################
-
-# load packages
-library(tibble)      # for more informative data sets
-library(dplyr)       # for manipulating data
-library(tidyr)       # for reshaping datasets
-library(magrittr)
-library(data.table)  # for importing data
-library(ggplot2)     # for visualising data
-library(janitor)
-library(stringr)     # for manipulating character strings
-library(lme4)        # for fitting frequentist mixed effect models
-library(ggeffects)   # for predicting means
-library(lmerTest)         # for Wald test
-library(purrr)       # for extracting elements from lists
-library(forcats)     # for dealing with categorical variables
-library(patchwork)   # for arranging plots
-library(here)        # for locating files
-
-# set params
-time_bin_duration <- 100
-
-#### import data ###########################################
-dat <- fread(here("Data", "04_prepared.csv"), sep = ",", header = TRUE, stringsAsFactors = FALSE) %>%
-	as_tibble() %>%
-	distinct(participant_id, trial_id, timebin, .keep_all = TRUE)
-
-#### fit model #############################################
-
-# maximal model with crossed-random effeto for participant and trial
-fit0 <- glmer(cbind(target, distractor) ~
-			  	(timebin1 + timebin2 + timebin3) * lang_profile  +
-			  	(timebin1 + timebin2 + timebin3 | participant_id),
-			  na.action = na.exclude,
-			  family = binomial(link = "logit"),
-			  data = dat)
-fit1 <- glmer(cbind(target, distractor) ~
-				(timebin1 + timebin2 + timebin3) * trial_type * lang_profile  +
-				(timebin1 + timebin2 + timebin3 | participant_id:trial_type),
-			na.action = na.exclude,
-			family = binomial(link = "logit"),
-			data = dat)
-
-summary(fit0)               # extract summary of model
-summary(fit1)
-
-#### coefficients ##########################################
-coefs <- summary(fit) %$% 
-	coefficients %>%
-	as.data.frame() %>%
[…]

### 2021-03-03 Rmd/report.Rmd
Process data and merge old data'

@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(
+	echo = FALSE,
+	message = TRUE,
+	warning = TRUE, 
+	cache.extra = knitr::rand_seed,
+	out.width = "100%",
+	results = "asis"
+)
+options(knitr.kable.NA = '-')
+
+```
+
+```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 
@@
 # load data
-stimuli.duration  <- fread(here("Data", "Stimuli", "stimuli_duration-aggregated.txt"))
-data.sample       <- read_xlsx(here("Data", "Participant data", "data_participants.xlsx"))
-data.fixations    <- fread(here("Data", "03_fixations.txt"))
-attrition         <- fread(here("Data", "02_filtered-excluded-trials.txt"))
-results           <- fread(here("Data", "05_gca-results.txt"))
-predictions       <- fread(here("Data", "05_gca-predictions.txt"))
-multicollinearity <- fread(here("Data", "05_gca-multicollinearity.txt"))
-```
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = FALSE,
-	message = TRUE,
-	warning = TRUE, 
-	cache.extra = knitr::rand_seed,
-	out.width = "100%",
-	results = "asis"
-)
-options(knitr.kable.NA = '-')
-
+stimuli <- readRDS(here("Results", "stimuli.rds"))
+participants <- readRDS(here("Results", "participants.rds"))
+gaze_trial <- readRDS(here("Results", "gaze_trial.rds"))
+gaze_time <- readRDS(here("Results", "gaze_time.rds"))
+attrition <- readRDS(here("Results", "attrition.rds"))
+fit <- readRDS(here("Results", "fit_trials.rds"))
 ```
@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+## Intensity
 
-stimuli.duration %>%
-	select(Location, Language, Version, TrialType, m_duration, sd_duration, mean_overlap) %>%
-	kable(
-		digits = 2,
-		row.names = FALSE,
-		col.names = c("**Location**", "**Language**", "**Version**", "**Trial type**", "***M* duration (s)**", "***SD***", "***M* overlap (s)***"),
-		align = "c"
-	)
+## Pitch/F0
 
-```
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Audio duration.
-A) Distribution of audio durations by trial type, split by testing language and location.
-Boxplots indicate median duration, 25\\% and 75\\% percentiles, and maximum and minimum.
-B) Distribution of overlap between audio and target-distractor presentation, split by testing language and location.
-C) Individual audio duration by word, split by trial type, testing language, and location.
-The dashed lines indicate the onset of target and distractor pictures presentation."}
-
-include_graphics(here("Figures", "Stimuli", "duration-overlap.png"))
-
-```
+## Lexical frequency
 
@@
 
-We tested `r data.sample %>% filter(!Pilot, DateTest<now()) %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` participants, of which `r data.sample %>% filter(!Pilot, DateTest<now(), !Valid) %>% pull(ID) %>% length() %>% printnum(digits = 0)` we excluded.
+We tested `r distinct(participants, participant) %>% nrow()` participants, of which `r data.sample %>% filter(!Pilot, DateTest<now(), !Valid) %>% pull(ID) %>% length() %>% printnum(digits = 0)` were excluded.
 The final sample included `r data.sample %>% filter(!Pilot, DateTest<now(), Valid, LangProfile=="Monolingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` monolinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan monolinguals, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish monolinguals) and `r data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` bilinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan-dominant, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish-dominant).

### 2021-03-03 R/participants.R

@@ -1,41 +1,0 @@
-#### participants: analyse samples----------------------------------------------
-
-#### set up --------------------------------------------------------------------
-
-# load packages
-library(tidyverse)
-library(readxl)
-library(lubridate)
-library(here)
-
-#### import data ---------------------------------------------------------------
-
-d <- read_xlsx(here("Data", "participants.xlsx")) %>% 
-	filter(location=="Barcelona",
-		   !pilot,
-		   valid_participant
-	) %>% 
-	mutate_at(vars(age_group, list), as.factor) %>%
-	group_by(age_group, test_language, lp, list, .drop = FALSE) %>% 
-	summarise(n = n(), .groups = "drop") %>% 
-	right_join(
-		expand(age_group, test_language, lp, list),
-		by = c("age_group", "test_language", "lp", "list")
-	) %>% 
-	mutate(
-		n = ifelse(is.na(n), 0, n),
-		age_group = paste0(age_group, " months")
-	) %>% 
-	arrange(age_group, test_language, lp, list)
-
-ggplot(d, aes(age_group, n, fill = list, label = n)) +
-	facet_grid(test_language~lp, drop = FALSE) +
-	geom_col() +
-	geom_label(position = position_stack()) +
-	labs(x = "Age group", y = "N", fill = "List") +
-	theme_bw() +
-	theme(axis.title= element_blank(),
-		  axis.text = element_text(colour = "black"),
-		  panel.grid.major.x = element_blank(),
-		  legend.position = "top") +
-	ggsave(here("Figures", "participants.png"))

### 2021-03-08 Rmd/report.Rmd
Add report

@@
 title: "Report"
-output: pdf_document
+output:
+  html_document:
+    df_print: paged
 ---
@@
 	out.width = "100%",
-	results = "asis"
+	results = "asis",
+	dev.args = list(png = list(type = "cairo"))
 )
@@
 library(knitr)
-library(data.table)
-library(dplyr)
-library(magrittr)
+library(tidyverse)
 library(readxl)
-library(tidyr)
-library(tibble)
-library(ggplot2)
 library(lubridate)
+library(scales)
 library(patchwork)
 library(here)
+
+# load functions
+source(here("R", "utils.R"))
 
@@
 
-# Procedure
+# Participants
 
-# Stimuli
-
-## Duration
-
-## Intensity
-
-## Pitch/F0
-
-## Lexical frequency
-
-# Sample
-
-We tested `r distinct(participants, participant) %>% nrow()` participants, of which `r data.sample %>% filter(!Pilot, DateTest<now(), !Valid) %>% pull(ID) %>% length() %>% printnum(digits = 0)` were excluded.
-The final sample included `r data.sample %>% filter(!Pilot, DateTest<now(), Valid, LangProfile=="Monolingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` monolinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan monolinguals, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish monolinguals) and `r data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` bilinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan-dominant, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish-dominant).
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-data.sample %>%
-	filter(!Pilot, Valid, DateTest<now()) %>%
-	select(ID, LangProfile, AgeGroup, Language, List, Sex) %>%
-	group_by(LangProfile, AgeGroup, Language, List) %>%
-	summarise(n = n()) %>%
-	pivot_wider(id_cols = c("LangProfile", "AgeGroup", "Language"), names_from = "List", values_from = "n") %>%
-	mutate(Total = sum(`1`, `2`, `3`, na.rm = TRUE)) %>%
-
-	kable(digits = 0,
-		  col.names = c("***LP***", "**Age group**", "**Language**", "**List 1**", "**List 2**", "**List 3**", "**Total**"), 
-		  align = "c",
-		  caption = "Sample size by age group, testing language, and list. Only participants that made it in the final sample are included.")
-
+```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+# plot participants
+participants %>% 
+	drop_na() %>% 
+	ggplot(aes(lp, fill = valid_participant)) +
+	facet_grid(~age_group) +
+	geom_bar() +
+	geom_hline(yintercept = 24, linetype = "dashed") +
+	labs(x = "Group", y = "N", fill = "Valid?") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_custom() +
+	theme(axis.title.x = element_blank()) +
+	ggsave(here("Figures", "sample.png"))
 ```
@@
 
-## Trackloss
+## Attrition rate
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
+
+col <- ifelse(distinct(attrition, participant, valid_participant)$valid_participant, "#377EB8", "#E41A1C")
 
 attrition %>% 
-	left_join(data.sample, by = c("ParticipantID" = "ID")) %>%
-	summarise(
-		TracklossForParticipant = first(TracklossForParticipant),
-		TracklossForParticipantSD = sd(TracklossForTrial, na.rm = TRUE)
-		) %>%
-	mutate(TracklossForParticipant = paste(printnum(TracklossForParticipant), "%"),
-		   TracklossForParticipantSD = printnum(TracklossForParticipantSD)) %>%
-	arrange(ParticipantID) %>%
-	kable(digits = 3,
-		  row.names = FALSE,
-		  align = "c",
-		  col.names = c("**Participant ID**", "**Mean**", "***SD***"),
-		  caption = "Mean proportion of samples lost by trial.")
+	mutate(valid_trial = ifelse(valid_trial, "Valid", "Invalid"),
+		   participant = paste0(participant, " (", missing_n, ", ", percent(missing_prop), ")")) %>% 
+	ggplot(aes(missing, participant, colour = valid_trial)) +
+	geom_point(alpha = 0.5) +
+	geom_vline(xintercept = 0.25, linetype = "dashed") +
+	labs(x = "Proportion of missing trials (out of 32)", y = "Participant") +
+	scale_color_brewer(palette = "Set1") +
+	theme_custom() +
+	theme(axis.text.y = element_text(colour = col, size = 8),
+		  axis.title.y = element_blank(),
+		  axis.text.x = element_text(colour = "black"),
+		  legend.title = element_blank(),
+		  legend.position = "top",
+		  text = element_text(size = 15)) +
+	ggsave(here("Figures", "missing.png"), height = 9)
 
@@
 
-## Growth Curve Analysis
+## Vocabulary
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-results %>%
-	select(Term, Estimate, SEM, Chisq, Df, p, ci1, ci2) %>%
-	mutate(CI = paste0("[", printnum(ci1, digits=2), ",", printnum(ci2, digits=2), "]"),
-		   p = printp(p)) %>%
-	select(-c(ci1, ci2)) %>%
-	kable(
-		digits = 2,
-		row.names = FALSE,
-		col.names = c("**Term**", "**$\\beta$**", "***SEM***", "**$\\chi^2$**", "***Df***", "***p***", "**95\\%*CI***"),
-		align = "c",
-		caption = "Results of the Growth Curve Analysis, reporting the estimated coefficients of the fixed effects included in the model. *p*-values were extracted using Wald's $\\chi^2$ approximation."
-	)
+```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+# vocabulary
+participants %>% 
+	mutate(age_group = as.factor(age_group)) %>% 
+	drop_na(lp) %>% 
+	ggplot(aes(as.factor(age_group), vocab_size, colour = lp, fill = lp)) +
+	geom_point(shape = 1, size = 3, stroke = 1, position = position_jitter(width = 0.1, seed = 888)) +
+	geom_boxplot(width = 0.1, colour = "black", outlier.colour = NA, position = position_dodge(width = 0.75)) +
+	labs(x = "Age group (months)", y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_custom() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "vocabulary.png"))
 
@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Coefficients of the fixed effects included in the Growth Curve Analysis.
-Black dots and whiskers represent the estimated coefficient and standard error of the mean, respectively.
-Grey boxes represent two-sided 95\\% confidence intervals, calculated using the Wald $\\chi^2$ approximation to degrees of freedom."}
+## Target fixations
 
-include_graphics(here("Figures", "05_gca-coefficients.png"))
+### Aggregated by trial
+
+```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze_trial %>% 
+	filter(valid_participant, valid_trial) %>% 
+	group_by(participant, lp, trial_type, age_group) %>% 
+	summarise(prop = mean(prop), .groups = "drop") %>% 
+	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
+	#stat_slab(position = position_nudge(x = 0.25)) +
+	geom_boxplot(width = 0.1, colour = "black", fill = "white", position = position_nudge(x = 0.2), outlier.colour = NA) +
+	geom_point(size = 2, shape = 1, stroke = 1) +
+	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
+	scale_colour_brewer(palette = "Set1") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	theme_custom() +
+	theme(legend.position = "none",
+		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "gaze_trial.png"))
 
@@
 
-## Predictions
+```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze_trial %>% 
+	filter(valid_participant, valid_trial) %>% 
+	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
+	summarise(prop = mean(prop), .groups = "drop") %>% 
+	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
+	#stat_slab(position = position_nudge(x = 0.25)) +
+	geom_point(size = 2, shape = 1, stroke = 1) +
+	geom_smooth(se = FALSE, method = "lm") +
+	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
+	scale_colour_brewer(palette = "Set1") +
+	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	theme_custom() +
+	theme(legend.position = "none",
+		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
+```
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Predicted unfolding of target fixations across the time course of the trial for each participant, split by trial type, language profile, and testing language."}
+### Aggregated by time bin
 
-include_graphics(here("Figures", "05_gca-predictions-participant.png"))
+```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze_time %>% 
+	filter(valid_participant, valid_trial) %>% 
+	group_by(time_bin, trial_type, lp, age_group) %>% 
+	summarise(
+		prop = mean(prop, na.rm = TRUE),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	ungroup() %>% 
+	mutate(
+		se = sqrt((prop*(1-prop))/(n+4)),
+		lower = prop-se,
+		upper = prop+se
+	) %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	geom_point(shape = 1, stroke = 1, size = 1) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_custom() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "gaze_time.png"))
 
@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Predicted unfolding of target fixations across the time course of the trial for each trial, split by trial type, language profile, and testing language."}
-
-include_graphics(here("Figures", "05_gca-predictions-trial.png"))
-
-```
-
-## Variance-covariance parameters
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Variance-covariance matrix."}
-
-include_graphics(here("Figures", "05_gca-vcov.png"))
-
-```
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Correlations between random effects split by fixed effect."}
-
-include_graphics(here("Figures", "05_gca-correlation.png"))
-
-```
-
-## Checking assumptions
-
-### Normality
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Distribution of the observed studentised residuals, compared with the theoretical normal distribution."}
-
-include_graphics(here("Figures", "05_gca-residuals.png"))
-
-```
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Distribution of the observed studentised residuals, compared with the theoretical normal distribution."}
-
-results %>%
-	select(Term, VIF) %>%
-	kable(digits = 2,
-		  row.names = FALSE,
-		  col.names = c("***Term***", "***VIF***"),
-		  align = "c",
-		  caption = "Multicollinearity" 
-		  )
+```{r gaze_time_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
+gaze_time %>% 
+	filter(valid_participant, valid_trial) %>% 
+	group_by(participant, time_bin, trial_type, lp, age_group) %>% 
+	summarise(
+		prop = mean(prop, na.rm = TRUE),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	ungroup() %>% 
+	mutate(
+		se = sqrt((prop*(1-prop))/(n+4)),
+		lower = prop-se,
+		upper = prop+se
+	) %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
+	facet_wrap(age_group~participant~lp) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	geom_point(shape = 1, stroke = 1, size = 0.5) +
+	geom_text(aes(x = 0, y = 1, label =
+				  	paste0(str_remove_all(participant, pattern = "[a-zA-Z]"),
+				  		   "/", age_group, "mo/", lp)),
+			  size = 2, colour = "black", hjust = 0) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_custom() +
+	theme(
+		axis.text = element_text(size = 7),
+		legend.title = element_blank(),
+		legend.position = "top",
+		strip.background = element_blank(),
+		strip.text.x = element_blank()
+	) +
+	ggsave(here("Figures", "gaze_time_participant.png"), height = 12, width = 12)
 ```
@@
 # Appendix
-
-## Participants
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-data.sample %>%
-	filter(!Pilot, DateTest<now()) %>%
-	select(ID, LangProfile, AgeGroup, Language, List, DateTest, Age, Sex, Valid) %>%
-	arrange(desc(Valid), LangProfile, AgeGroup, Language, List, ID) %>%
-	kable(digits = 2,
-		  row.names = FALSE,
-		  align = "c",
-		  col.names = c("**Participant ID**", "***LP***", "**Age group**", "**Lang.**", "**List**", "**Date**", "**Age**", "**Sex**", "**Valid?**"),
-		  caption = "Complete list of participants. *LP* = Language profile.")
-
-```

### 2021-03-08 Rmd/report.Rmd
First attempt to merge Barcelona and Oxford data (with mild success)

@@
 # load functions
-source(here("R", "utils.R"))
+source(here("R", "utils-others.R"))
+source(here("R", "utils-vocabulary.R"))
+source(here("R", "utils-participants.R"))
+source(here("R", "utils-gaze.R"))
 
@@
 fit <- readRDS(here("Results", "fit_trials.rds"))
+
 ```
@@
 participants %>% 
-	drop_na() %>% 
+	drop_na(valid_participant) %>% 
 	ggplot(aes(lp, fill = valid_participant)) +
-	facet_grid(~age_group) +
+	facet_grid(location~age_group, scales = "free") +
 	geom_bar() +
@@
 		  text = element_text(size = 15)) +
-	ggsave(here("Figures", "missing.png"), height = 9)
+	ggsave(here("Figures", "missing.png"), height = 15)
 
@@
 	filter(valid_participant, valid_trial) %>% 
-	group_by(participant, lp, trial_type, age_group) %>% 
+	group_by(participant, lp, trial_type, age_group, location) %>% 
 	summarise(prop = mean(prop), .groups = "drop") %>% 
 	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~age_group) +
+	facet_grid(location~age_group) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
@@
 	theme(legend.position = "none",
+		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
 		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
@@
 	filter(valid_participant, valid_trial) %>% 
-	group_by(time_bin, trial_type, lp, age_group) %>% 
+	group_by(time_bin, trial_type, lp, age_group,location) %>% 
 	summarise(
@@
 	geom_smooth() +
-	geom_line() +
+	#geom_line() +
 	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 

### 2021-03-08 R/utils-others.R

@@ -1,0 +1,27 @@
+# utils: helper functions
+
+# evaluate if x is NOT an element of y -----------------------------------------
+"%!in%" <- function(x, y){!(x %in% y)}
+
+# replace NaNs with NAs --------------------------------------------------------
+nan_to_na <- function(x) ifelse(is.nan(x), NA_real_, x)
+
+# find first/last non-missing value in vector ----------------------------------
+first_non_na <- function(x) ifelse(is.logical(first(x[!is.na(x)])), NA, first(x[!is.na(x)]))
+last_non_na <- function(x) ifelse(is.logical(last(x[!is.na(x)])), NA, last(x[!is.na(x)]))
+
+# big mark format
+add_big_mark <- function(x) format(x, big.mark = ",", scientific = FALSE)
+
+# custom ggplot theme ----------------------------------------------------------
+theme_custom <- function(){
+	theme(
+		panel.background = element_rect(fill = "transparent"),
+		panel.grid = element_blank(),
+		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
+		panel.border = element_rect(fill = "transparent", colour = "black"),
+		text = element_text(colour = "black", size = 15),
+		axis.text = element_text(colour = "black")
+	)
+}
+

### 2021-03-08 R/utils-vocabulary.R

@@ -1,0 +1,62 @@
+# utils vocabulary
+
+import_vocabulary <- function(location = c("oxf", "bcn")){
+	
+	if ("bcn" %in% location){
+		# vocabulary Barcelona
+		ml_connect("gonzalo.garciadecastro@upf.edu")
+		p <- ml_participants() 
+		r <- ml_responses(p, update = TRUE)
+		vocab_responses <- r %>% 
+			mutate(
+				understands = response > 1, # participant understands the item
+				age_group = case_when(
+					between(age, 20, 24) ~ 21,
+					between(age, 24, 28) ~ 25,
+					between(age, 28, 33) ~ 30
+				)
+			) %>% 
+			filter(understands, study %in% "CognatePriming") %>% 
+			select(id_exp, time, age_group, item, response) %>% 
+			group_by(id_exp, time, age_group) %>% 
+			summarise(understands = list(unique(item)), .groups = "drop")
+		
+		vocab_bcn <- ml_vocabulary(p, r, scale = "prop", by = c("id_exp")) %>% 
+			right_join(select(p, id_db, time, id_exp)) %>% 
+			filter(type=="understands") %>% 
+			right_join(vocab_responses) %>% 
+			select(
+				id_db,
+				vocab_size = vocab_prop_total,
+				age_group
+			) 
+	}
+	
+	# vocabulary Oxford
+	if("oxf" %in% location) {
+		vocab_oxf <- read_xlsx(here("Data", "vocabulary_oxf.xlsx"), na = c("", "NA", "?")) %>% 
+			mutate_at(vars(everything(), -item), as.integer) %>% 
+			pivot_longer(-item, names_to = "id_db", values_to = "response") %>% 
+			separate(item, c("category", "item"), sep = " - ") %>% 
+			mutate(
+				understands = response %in% c(1, 2),
+				says = response %in% 2,
+				age_group = case_when(
+					substr(id_db, start = 1, stop = 2) %in% c(21) ~ 21,
+					substr(id_db, start = 1, stop = 2) %in% c(24, 25) ~ 25,
+					substr(id_db, start = 1, stop = 2) %in% c(27, 30) ~ 30
+				)
+			) %>% 
+			group_by(id_db, age_group) %>% 
+			summarise(
+				vocab_size = mean(understands),
+				.groups = "drop"
+			)
+	}
+	
+	# merge both
+	x <- list(OXF = vocab_oxf, BCN = vocab_bcn) %>% 
+		bind_rows(.id = "location")
+	
+	return(x)
+}

### 2021-03-11 Rmd/report.Rmd
Add bilingualr to the workflow

@@
 library(tidyverse)
-library(readxl)
+library(bilingualr)
 library(lubridate)
@@
 library(here)
-
-# load functions
-source(here("R", "utils-others.R"))
-source(here("R", "utils-vocabulary.R"))
-source(here("R", "utils-participants.R"))
-source(here("R", "utils-gaze.R"))
 
@@
 	scale_fill_brewer(palette = "Set1") +
-	theme_custom() +
+	theme_bilingual() +
 	theme(axis.title.x = element_blank()) +
@@
 	scale_color_brewer(palette = "Set1") +
-	theme_custom() +
+	theme_bilingual() +
 	theme(axis.text.y = element_text(colour = col, size = 8),
@@
 	scale_fill_brewer(palette = "Set1") +
-	theme_custom() +
+	theme_bilingual() +
 	theme(legend.title = element_blank(),
@@
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme_custom() +
+	theme_bilingual() +
 	theme(legend.position = "none",
@@
 	scale_fill_brewer(palette = "Set1") +
-	theme_custom() +
+	theme_bilingual() +
 	theme(

### 2021-04-29 Rmd/report.Rmd
Generate new report

--- 2021-03-08 Rmd/report.Rmd
@@
 library(tidyverse)
-library(readxl)
+library(bilingualr)
 library(lubridate)
 library(scales)
+library(janitor)
+library(gt)
 library(patchwork)
@@
 
-# load functions
-source(here("R", "utils.R"))
-
 # load data
-stimuli <- readRDS(here("Results", "stimuli.rds"))
 participants <- readRDS(here("Results", "participants.rds"))
@@
 attrition <- readRDS(here("Results", "attrition.rds"))
-fit <- readRDS(here("Results", "fit_trials.rds"))
+
 ```
@@
 
-```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
 # plot participants
 participants %>% 
-	drop_na() %>% 
+	drop_na(valid_participant) %>% 
 	ggplot(aes(lp, fill = valid_participant)) +
-	facet_grid(~age_group) +
+	facet_grid(location~age_group, scales = "free") +
 	geom_bar() +
@@
 	scale_fill_brewer(palette = "Set1") +
-	theme_custom() +
-	theme(axis.title.x = element_blank()) +
+	theme_bilingual() +
+	theme(
+		legend.position = "top",
+		axis.title.x = element_blank(),
+		axis.title.y = element_text(angle = 90)
+	) +
 	ggsave(here("Figures", "sample.png"))
@@
 
+This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
+
 ```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
 
-col <- ifelse(distinct(attrition, participant, valid_participant)$valid_participant, "#377EB8", "#E41A1C")
-
 attrition %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Invalid"),
-		   participant = paste0(participant, " (", missing_n, ", ", percent(missing_prop), ")")) %>% 
-	ggplot(aes(missing, participant, colour = valid_trial)) +
-	geom_point(alpha = 0.5) +
-	geom_vline(xintercept = 0.25, linetype = "dashed") +
-	labs(x = "Proportion of missing trials (out of 32)", y = "Participant") +
-	scale_color_brewer(palette = "Set1") +
-	theme_custom() +
-	theme(axis.text.y = element_text(colour = col, size = 8),
-		  axis.title.y = element_blank(),
-		  axis.text.x = element_text(colour = "black"),
-		  legend.title = element_blank(),
-		  legend.position = "top",
-		  text = element_text(size = 15)) +
-	ggsave(here("Figures", "missing.png"), height = 9)
+	left_join(select(participants, location, lp, participant, date_test)) %>% 
+	drop_na(trial_type) %>% 
+	group_by(participant, lp, location, date_test, age_group, trial_type, valid_participant, valid_other) %>% 
+	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
+			  .groups = "drop") %>% 
+	pivot_wider(
+		names_from = trial_type,
+		values_from = valid_trial_count
+	) %>% 
+	clean_names() %>% 
+	group_by(lp, location, age_group) %>% 
+	summarise(
+		cognate = mean(cognate, na.rm = TRUE),
+		non_cognate = mean(non_cognate, na.rm = TRUE),
+		unrelated = mean(unrelated, na.rm = TRUE),
+		sum_n = sum(valid_participant, na.rm = TRUE),
+		prop_n = mean(valid_participant, na.rm = TRUE),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	arrange(age_group, lp, location) %>% 
+	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
+	gt() %>% 
+	tab_spanner(
+		"Mean valid trials",
+		c("cognate", "non_cognate", "unrelated")
+	) %>% 
+	tab_spanner(
+		"N participants",
+		c("sum_n", "n", "prop_n")
+	) %>% 
+	cols_label(
+		age_group = "Age",
+		lp = "Group",
+		sum_n = "Valid",
+		location = "Laboratory",
+		n = "Tested",
+		prop_n = "Valid (%)",
+		cognate = "Cognate (8)",
+		non_cognate = "Non-cognate (8)",
+		unrelated = "Unrelated (16)"
+	) %>% 
+	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
+	fmt_percent(c("prop_n")) %>% 
+	fmt_number(c("n", "sum_n"), decimals = 0)
 
@@
 
+### vocabualry in the dominant language (L1)
+
+This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
+Results are presented separately for each age group.
+The shape of the violins, represents the distribution of the vocabulary sizes.
+The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
+vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
+for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
+
 ```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
@@
 participants %>% 
-	mutate(age_group = as.factor(age_group)) %>% 
+	mutate(age_group = as.factor(paste0(age_group, " mo"))) %>% 
 	drop_na(lp) %>% 
-	ggplot(aes(as.factor(age_group), vocab_size, colour = lp, fill = lp)) +
-	geom_point(shape = 1, size = 3, stroke = 1, position = position_jitter(width = 0.1, seed = 888)) +
-	geom_boxplot(width = 0.1, colour = "black", outlier.colour = NA, position = position_dodge(width = 0.75)) +
-	labs(x = "Age group (months)", y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
+	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
+	facet_wrap(~age_group) +
+	geom_violin(position = position_dodge(width = 0.75)) + 
+	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
+	# 		   position = position_jitter(width = 0.1, seed = 888)) +
+	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
+				 position = position_dodge(width = 0.75)) +
+	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
 	scale_colour_brewer(palette = "Set1") +
 	scale_fill_brewer(palette = "Set1") +
-	theme_custom() +
+	theme_bilingual() +
 	theme(legend.title = element_blank(),
-		  legend.position = "top",
+		  legend.position = "none",
+		  axis.title.x = element_blank(),
 		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
@@
 
+For each participant and trial, the proportion of fixations to the target object were calculated from the total of fixations to the target, the distractor, and the rest of the screen.
+Then proportions for the same participant were aggregated within conditions, so that for each participant three data points were obtained: one in each trial type (cognate, non-cognate, and unrelated).
+Some participants were longitudinal.
+Scores form longitudinal participant  are indicated by gray lines linking data points from the same participant.
+
 ```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 gaze_trial %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
 	filter(valid_participant, valid_trial) %>% 
-	group_by(participant, lp, trial_type, age_group) %>% 
+	group_by(participant, lp, trial_type, age_group, location) %>% 
 	summarise(prop = mean(prop), .groups = "drop") %>% 
+	drop_na() %>% 
 	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
 	facet_grid(lp~age_group) +
+	geom_violin() +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
@@
 	#stat_slab(position = position_nudge(x = 0.25)) +
-	geom_boxplot(width = 0.1, colour = "black", fill = "white", position = position_nudge(x = 0.2), outlier.colour = NA) +
-	geom_point(size = 2, shape = 1, stroke = 1) +
+	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
+	#geom_point(size = 2, shape = 1, stroke = 1) +
 	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
 	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme_custom() +
+	theme_bilingual() +
 	theme(legend.position = "none",
+		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
 		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
@@
 
+## By age group
+
+```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze_trial %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
+	filter(valid_participant, valid_trial) %>% 
+	group_by(participant, lp, trial_type, age_group, location) %>% 
+	summarise(prop = mean(prop), .groups = "drop") %>% 
+	drop_na() %>% 
+	ggplot(aes(age_group, prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(~lp) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_line(aes(group = interaction(participant, trial_type)), alpha = 0.5) +
+	geom_violin(position = position_dodge(width = 0.5)) +
+	#stat_slab(position = position_nudge(x = 0.25)) +
+	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
+	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
+				 position = position_dodge(width = 0.5), colour = "black", fill = "white") +
+	labs(x = "Age (months)", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	theme_bilingual() +
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "gaze_trial_age.png"))
+
+```
+
+## Effect of vocabulary
+
 ```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 gaze_trial %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
 	filter(valid_participant, valid_trial) %>% 
@@
 	summarise(prop = mean(prop), .groups = "drop") %>% 
+	drop_na() %>% 
 	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
@@
 	#stat_slab(position = position_nudge(x = 0.25)) +
-	geom_point(size = 2, shape = 1, stroke = 1) +
+	geom_point(alpha = 0.5) +
 	geom_smooth(se = FALSE, method = "lm") +
@@
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme_custom() +
-	theme(legend.position = "none",
-		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
+	theme_bilingual() +
+	theme(panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		  legend.position = "top",
+		  axis.text.x = element_text(size = 10)) +
 	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
@@
 gaze_time %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
 	filter(valid_participant, valid_trial) %>% 
-	group_by(time_bin, trial_type, lp, age_group) %>% 
+	group_by(time_bin, trial_type, lp, age_group,location) %>% 
 	summarise(
@@
 	) %>% 
+	drop_na() %>% 
 	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
@@
 	geom_smooth() +
-	geom_line() +
+	#geom_line() +
 	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	geom_point(shape = 1, stroke = 1, size = 1) +
+	geom_point(alpha = 0.5) +
 	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
@@
 ```
+
+```{r gaze_time_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
+gaze_time %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
+	left_join(select(participants, participant, age_group, vocab_size)) %>% 
+	filter(valid_participant, valid_trial) %>% 
+	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
+	summarise(
+		prop = mean(prop, na.rm = TRUE),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	ungroup() %>% 
+	mutate(
+		se = sqrt((prop*(1-prop))/(n+4)),
+		lower = prop-se,
+		upper = prop+se,
+		vocab_cat = ifelse(
+			vocab_size < median(.$vocab_size, na.rm = TRUE),
+			"Below the median",
+			"Above the median"
+		)
+	) %>% 
+	drop_na() %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
+	facet_wrap(age_group~lp~vocab_cat) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "gaze_time_vocab.png"))
+
+```
+
+# Appendix
+
+## Appendix 1: Individual attrition rates
+
+```{r attrition_individual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
+
+attrition %>%
+	left_join(select(participants, location, lp, participant, date_test)) %>% 
+	drop_na(trial_type) %>% 
+	group_by(participant, lp, location, date_test, age_group, trial_type, valid_participant, valid_other) %>% 
+	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
+			  .groups = "drop") %>% 
+	pivot_wider(names_from = trial_type, values_from = valid_trial_count) %>% 
+	clean_names() %>% 
+	mutate(
+		participant = str_remove(participant, "cognatepriming"),
+		cognate = paste0(cognate, " (", round(cognate/8, 2), "%)"),
+		non_cognate = paste0(non_cognate, " (", round(non_cognate/8, 2), "%)"),
+		unrelated = paste0(unrelated, " (", round(unrelated/8, 2), "%)"),
+	) %>% 
+	arrange(location, date_test) %>% 
+	relocate(
+		participant, location, date_test,
+		age_group, lp, cognate, non_cognate,
+		unrelated, valid_other, valid_participant) %>% 
+	gt() %>% 
+	gt::tab_spanner(
+		"Valid trials (%) by trial type",
+		c("cognate", "non_cognate", "unrelated")
+	) %>% 
+	cols_label(
+		participant = "Participant",
+		location = "Location",
+		date_test = "Date",
+		lp = "Group",
+		age_group = "Age",
+		valid_participant = "Valid trials",
+		valid_other = "Valid (other)?",
+		cognate = "Cognate",
+		non_cognate = "Non-cognate",
+		unrelated = "Unrelated"
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#00FA9A")
+		),
+		locations = cells_body(
+			columns = c("valid_participant"),
+			rows = valid_participant
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#00FA9A")
+		),
+		locations = cells_body(
+			columns = c("valid_other"),
+			rows = valid_other
+		)
+	)
+
+```
+
+## Appendix 2: Individual target looking times
 
@@
 	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	geom_point(shape = 1, stroke = 1, size = 0.5) +
+	# geom_point(shape = 1, stroke = 1, size = 0.5) +
 	geom_text(aes(x = 0, y = 1, label =

### 2021-04-29 R/processing.R

@@ -5,6 +5,7 @@
 # load packages
 library(tidyverse)
 library(multilex)
+library(lubridate)
 library(bilingualr)
 library(here)
 
@@ -13,10 +14,9 @@ sampling_rate <- 120  # how many samples does the eye-tracker take per second?
 left_coords <- c(xmin = 280, xmax = 780, ymin = 290, ymax = 790)
 right_coords <- c(xmin = 1140, xmax = 1640, ymin = 290, ymax = 790)
 email <- "gonzalo.garciadecastro@upf.edu"
-
+ml_connect(email)
 
 # participants -----------------------------------------------------------------
-
 # get vocabulary data
 vocabulary <- import_vocabulary(
 	location = c("barcelona", "oxford"),
@@ -30,10 +30,11 @@ participants <- get_participants(google_email = email) %>%
 	rename(valid_other = valid_participant) %>% 
 	left_join(vocabulary) %>% 
 	filter(!pilot) %>% 
-	select(participant, id_db, location, age_group, test_language, list, version, lp, vocab_size, valid_other, test_language, list, version, filename)
+	mutate(date_test = as_date(date_test)) %>% 
+	select(participant, id_db, date_test, location, age_group, test_language, list, version, lp, vocab_size, valid_other, test_language, list, version, filename)
 
 # trials -----------------------------------------------------------------------
-trials <- stimuli %>%
+trials <- bilingualr::trials %>%
 	rename(trial = trial_id) %>% 
 	mutate(trial = as.numeric(trial)) %>% 
 	select(location, test_language, list, version, trial, trial_type, target_location,
@@ -47,7 +48,10 @@ items_to_know <- trials %>%
 	unique()
 
 # get gaze data
-gaze <- import_gaze(location = c("oxford", "barcelona"), participants = participants) %>% 
+gaze <- import_gaze(
+	path = "Data", location = c("oxford", "barcelona"),
+	participants = participants
+) %>% 
 	mutate(
 		gaze_in_l_aoi = gaze_in_aoi(x, y, left_coords),
 		gaze_in_r_aoi = gaze_in_aoi(x, y, right_coords),
@@ -57,7 +61,7 @@ gaze <- import_gaze(location = c("oxford", "barcelona"), participants = particip
 	mutate_at(vars(age_group, lp, trial_type), as.factor) %>% 
 	arrange(id_db, trial_num, time) %>% 
[…]

### 2021-05-03 Rmd/report.Rmd
Add longitudinal language profile plot

@@
     df_print: paged
+    toc: true
+    toc_depth: 2
 ---
@@
 
+## Sample sizes
+
 ```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
@@
 	drop_na(valid_participant) %>% 
+	mutate(valid_participant = ifelse(valid_participant, "Valid", "Not valid")) %>% 
 	ggplot(aes(lp, fill = valid_participant)) +
@@
 	geom_hline(yintercept = 24, linetype = "dashed") +
-	labs(x = "Group", y = "N", fill = "Valid?") +
+	labs(x = "Group", y = "Sample size", fill = "Valid?") +
 	scale_fill_brewer(palette = "Set1") +
@@
 		legend.position = "top",
+		legend.title = element_blank(),
 		axis.title.x = element_blank(),
+		axis.text.x = element_text(size = 10),
 		axis.title.y = element_text(angle = 90)
@@
 	ggsave(here("Figures", "sample.png"))
+```
+
+## Language profiles
+
+Only valid participants.
+
+```{r lps, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+participants %>% 
+	filter(valid_participant) %>% 
+	ggplot(aes(age, doe_2, colour = lp)) +
+	facet_grid(test_language~location) +
+	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
+	geom_point(size = 3, alpha = 0.5) +
+	geom_hline(yintercept = 0.2, linetype = "dashed") +
+	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
+			 xmin = 20, xmax = 22, ymin = -Inf, ymax = Inf) +
+	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
+			 xmin = 24, xmax = 26, ymin = -Inf, ymax = Inf) +
+	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
+			 xmin = 28, xmax = 32, ymin = -Inf, ymax = Inf) +
+	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Group") +
+	scale_colour_brewer(palette = "Set1") +
+	scale_y_continuous(labels = percent) +
+	theme_bilingual() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.y = element_line(linetype = "dotted", colour = "grey"),
+		axis.text.x = element_text(size = 10),
+		axis.title.y = element_text(angle = 90),
+		axis.text.y = element_text(size = 10)
+	) +
+	ggsave(here("Figures", "lps.png"))
 ```
@@
 
-### vocabualry in the dominant language (L1)
+### Vocabulary in the dominant language (L1)
 
@@
 
-### Aggregated by trial
+### Target fixations: Age group and language profile {.tabset .tabset-pills}
+
+#### Cross-sectional
 
@@
 
-## By age group
+#### Longitudinal
+
+Each trial was divided into 100 ms time bins.
+for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
+Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
+This figure shows the fitted line of a General Additive Model (GAM) generated using the `geom_smooth()` function from the `ggplot` R package, with default settings.
 
@@
 
-## Effect of vocabulary
+### {-}
 
-```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-gaze_trial %>% 
-	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
-	filter(valid_participant, valid_trial) %>% 
-	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	drop_na() %>% 
-	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
-	#stat_slab(position = position_nudge(x = 0.25)) +
-	geom_point(alpha = 0.5) +
-	geom_smooth(se = FALSE, method = "lm") +
-	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
-	scale_colour_brewer(palette = "Set1") +
-	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme_bilingual() +
-	theme(panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		  legend.position = "top",
-		  axis.text.x = element_text(size = 10)) +
-	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
-```
-
-### Aggregated by time bin
+### Target fixations: Time course analysis
 
@@
 
+### Target fixations: Vocabulary size
+
+```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze_trial %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
+	filter(valid_participant, valid_trial) %>% 
+	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
+	summarise(prop = mean(prop), .groups = "drop") %>% 
+	drop_na() %>% 
+	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
+	#stat_slab(position = position_nudge(x = 0.25)) +
+	geom_point(alpha = 0.5) +
+	geom_smooth(se = FALSE, method = "lm") +
+	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
+	scale_colour_brewer(palette = "Set1") +
+	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	theme_bilingual() +
+	theme(panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		  legend.position = "top",
+		  axis.text.x = element_text(size = 10)) +
+	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
+```
+
+### Target fixations: High vocabulary vs. low vocabulary {.tabset .tabset-pills}
+
 ```{r gaze_time_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
-gaze_time %>% 
+gaze_time_vocab_d <- gaze_time %>% 
 	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
@@
 			"Above the median"
-		)
+		),
+		age_group = paste0(age_group, " months")
 	) %>% 
-	drop_na() %>% 
+	drop_na()
+
+```
+
+#### Age group: 21 months
+
+```{r gaze_time_vocab_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "21 months") %>% 
 	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_wrap(age_group~lp~vocab_cat) +
+	facet_grid(lp~vocab_cat) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
 	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
 	#geom_line() +
@@
 		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "gaze_time_vocab.png"))
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
 
 ```
+
+#### Age group: 25 months
+
+```{r gaze_time_vocab_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "25 months") %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~vocab_cat) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+
+```
+
+#### Age group: 30 months
+
+```{r gaze_time_vocab_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "30 months") %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~vocab_cat) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+
+```
+### {-}
 
@@
 
-# Appendix
+# References

### 2021-05-03 R/processing.R

@@ -30,8 +30,11 @@ participants <- get_participants(google_email = email) %>%
 	rename(valid_other = valid_participant) %>% 
 	left_join(vocabulary) %>% 
 	filter(!pilot) %>% 
-	mutate(date_test = as_date(date_test)) %>% 
-	select(participant, id_db, date_test, location, age_group, test_language, list, version, lp, vocab_size, valid_other, test_language, list, version, filename)
+	mutate(
+		date_test = as_date(date_test),
+		doe_2 = ifelse(test_language=="Spanish", doe_catalan, doe_spanish)
+		) %>% 
+	select(participant, id_db, date_test, location, age_group, age, test_language, list, version, lp, doe_2, vocab_size, valid_other, test_language, list, version, filename)
 
 # trials -----------------------------------------------------------------------
 trials <- bilingualr::trials %>%

### 2021-05-04 Rmd/report.Rmd
No idea of what I changed

--- 2021-03-11 Rmd/report.Rmd
@@
 
+We collected data from `r length(unique(participants$participant))` participants, of which `r length(unique(participants$participant[participants$valid_participant]))` met the inclusion criteria and were included in data analyses.
+`r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+
 ```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+
 # plot participants
@@
 	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = valid_participant)) +
+	mutate(lp = ifelse(lp=="Monolingual", "Mon.", "Bil.")) %>% 
+	ggplot(aes(lp, fill = valid_participant, colour = valid_participant)) +
 	facet_grid(location~age_group, scales = "free") +
-	geom_bar() +
+	geom_bar(colour = NA) +
 	geom_hline(yintercept = 24, linetype = "dashed") +
-	labs(x = "Group", y = "N", fill = "Valid?") +
+	labs(x = "Group", y = "N", fill = "Valid?", colour = "Valid?") +
+	scale_colour_brewer(palette = "Set1") +
 	scale_fill_brewer(palette = "Set1") +
@@
 	ggsave(here("Figures", "sample.png"))
+```
+
+We collected data from `r sum(duplicated(participant$participant)` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
+Of those, `r sum(duplicated(participant$participant[participants$location=="Oxford"])` were tested in Oxford, and `r `sum(duplicated(participants$participant[participants$location=="Barcelona"])` were tested in Barcelona.
+
+```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+
+# plot participants
+participants %>% 
+	drop_na(valid_participant) %>% 
+	ggplot(aes(age_group, participant, fill = valid_participant, colour = valid_participant)) +
+	facet_grid(lp~location, scales = "free") +
+	geom_point(size = 3, shape = 4) +
+	geom_line(aes(group = participant)) +
+	labs(x = "Age (months)", y = "Language profile", fill = "Valid?", colour = "Valid?") +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(axis.title.y = element_blank(),
+		  axis.text.y = element_blank(),
+		  axis.ticks.y = element_blank(),
+		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "sample_cohort.png"))
 ```
@@
 
-attrition %>% 
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Invalid"),
-		   participant = paste0(participant, " (", missing_n, ", ", percent(missing_prop), ")")) %>% 
-	ggplot(aes(missing, participant, colour = valid_trial)) +
-	geom_point(alpha = 0.5) +
+attrition_summary %>% 
+	mutate(valid_trial = ifelse(valid_participant, "Valid", "Invalid"),
+		   participant = paste0(participant, " (", percent(missing_prop), ")")) %>% 
+	ggplot(aes(missing_prop, participant, colour = valid_participant, fill = valid_participant)) +
+	geom_col() +
 	geom_vline(xintercept = 0.25, linetype = "dashed") +
@@
 	scale_color_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
 	theme_bilingual() +
@@
 ```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+lp_labels <- c("Monolingual", "Bilingual")
+names(lp_labels) <- lp_labels
+age_group_labels <- c("21 months", "25 months")
+names(age_group_labels) <- c("21", "25")
+
 gaze_time %>% 
-	filter(valid_participant, valid_trial) %>% 
+	filter(valid_participant, valid_trial, age_group %in% c(21, 25),
+		   location == "Barcelona") %>% 
 	group_by(time_bin, trial_type, lp, age_group,location) %>% 
@@
 		lower = prop-se,
-		upper = prop+se
+		upper = prop+se,
+		time_bin = time_bin*100
 	) %>% 
 	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~age_group) +
+	facet_grid(lp~age_group, labeller = labeller(lp = lp_labels, age_group = age_group_labels)) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
@@
 	geom_point(shape = 1, stroke = 1, size = 1) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	labs(x = "Time (ms)", y = "Pr(Target fixation)", colour = "Condition", fill = "Condition") +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
@@
 		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "gaze_time.png"))
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"),
+		  panel.grid.minor = element_blank()) +
+	ggsave(here("Figures", "gaze_time.png"), height = 5, width = 7)
 

### 2021-05-04 Rmd/report.Rmd
Add data processing workflows to report

--- 2021-05-03 Rmd/report.Rmd
@@
     toc_depth: 2
+    toc_float: true
 ---
@@
 library(scales)
+library(DiagrammeR)
 library(janitor)
@@
 
-## Sample sizes
+We collected data from `r length(unique(participants$participant))` participants, of which `r length(unique(participants$participant[participants$valid_participant]))` met the inclusion criteria and were included in data analyses.
+`r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
 
@@
 	facet_grid(location~age_group, scales = "free") +
-	geom_bar() +
+	geom_bar(colour = NA) +
 	geom_hline(yintercept = 24, linetype = "dashed") +
+	scale_colour_brewer(palette = "Set1") +
 	labs(x = "Group", y = "Sample size", fill = "Valid?") +
@@
 	ggsave(here("Figures", "sample.png"))
+```
+
+We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
+Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+
+```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+
+# plot participants
+participants %>% 
+	drop_na(valid_participant) %>% 
+	ggplot(aes(age_group, participant, fill = valid_participant, colour = valid_participant)) +
+	facet_grid(lp~location, scales = "free") +
+	geom_point(size = 3, shape = 4) +
+	geom_line(aes(group = participant)) +
+	labs(x = "Age (months)", y = "Language profile", fill = "Valid?", colour = "Valid?") +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(axis.title.y = element_blank(),
+		  axis.text.y = element_blank(),
+		  axis.ticks.y = element_blank(),
+		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "sample_cohort.png"))
 ```
@@
 ```
+
+# Methods
+
+## Preprocessing participant data
+
+## Preprocessing vocabulary data
+
+We collected vocabulary data from participants.
+In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
+In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
+In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
+In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
+All checklists included the words involved in the trial lists.
+When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
+Each response to either checklist was aggregated to produce several vocabulary measures:
+
+* **Total vocabulary**: total number of words the child knows, summing up both languages.
+For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
+* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
+For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
+* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
+For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
+
+Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$1 month) and language profile (similar exposure to a second language, $\pm$10%) that completed the same vocabulary checklist previously.
+
+## Preprocessing gaze data {.tabset .tabset-pills}
+
+### Workflow
+
+```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+DiagrammeR::grViz("digraph {
+  graph [layout = dot, rankdir = TB]
+
+  node [shape = rectangle, fontname = 'Arial']        
+  rec1 [label = 'Merge Barcelona and Oxford data']
+  rec2 [label = 'Impute missing/invalid samples (pending)']
+  rec2 [label = 'Extract fixations (pending)']
+  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
+  rec4 [label = 'Divide each trial into 100 ms time bins']
+  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
+  rec6 [label = 'Exclude time bins 1-3 (pending)']
+  rec7 [label = 'Apply trial-level inclusion criteria']
+  rec8 [label = 'Apply participant-level inclusion criteria']
+
+  # edge definitions with the node IDs
+  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
+  }", 
+  height = 500)
+```
+
+### Trial-level inclusion criteria
+
+* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
+* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
+* At least one sample in target and one sample in distractor
+* Participant understands prime word in both languages
+* Participant knows the target word in the test language
+* Participant knows the distractor word in the test language
+
+### Participant-level inclusion criteria
+
+* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
+* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
+* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
+* $\geq$ 36 gestational weeks
+* $\geq$ 2,800g birth weight
+* No diagnosed developmental, hearing, or visual disorders
+* Not exposed to more than 10% to a 3rd language
+
+## {-}
 
@@
 ```{r gaze_time_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
+
 gaze_time_vocab_d <- gaze_time %>% 
@@
 		upper = prop+se,
+		time_bin = time_bin*100,
 		vocab_cat = ifelse(
@@
 	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	labs(x = "Time (ms)", y = "Pr(Target fixation)", colour = "Condition", fill = "Condition") +
 	#geom_point(alpha = 0.5) +
@@
 		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"),
+		  panel.grid.minor = element_blank()) +
+	ggsave(here("Figures", "gaze_time.png"), height = 5, width = 7)
 
@@
 ```
+
 ### {-}

### 2021-05-12 Rmd/report.Rmd
Add prime filter

@@
 
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$1 month) and language profile (similar exposure to a second language, $\pm$10%) that completed the same vocabulary checklist previously.
+Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
 
@@
 
+### Target fixations: Oxford vs. Barcelona {.tabset .tabset-pills}
+
+#### Age group: 21 months
+
+```{r gaze_time_location_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "21 months") %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~location) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+
+```
+
+#### Age group: 25 months
+
+```{r gaze_time_location_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "25 months") %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~location) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+
+```
+
+#### Age group: 30 months
+
+```{r gaze_time_location_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "30 months") %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~location) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+
+```
+
+#### {-}
+
+# Data analysis {.tabset .tab-pills}
+
+## Model
+
+$$
+\log(\frac{p}{n - q}) &=& (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
+(\beta_{1} + \beta_{1p} + \beta_{1i})\times Condition_{pi} + ... \\
+(\beta_{2} + \beta_{2i}) \times Group_{pi} + ... \\
+(\beta_{3} + \beta_{3i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
+(\beta_{4} + \beta_{4p}) \times Vocabulary_{p} + \varepsilon_{pi}
+$$
+
+## {-}
+
 # Appendix
@@
 gaze_time %>% 
-	filter(valid_participant, valid_trial) %>% 
 	group_by(participant, time_bin, trial_type, lp, age_group) %>% 

### 2021-05-12 R/processing.R

@@ -13,6 +13,8 @@ library(here)
 sampling_rate <- 120  # how many samples does the eye-tracker take per second?
 left_coords <- c(xmin = 280, xmax = 780, ymin = 290, ymax = 790)
 right_coords <- c(xmin = 1140, xmax = 1640, ymin = 290, ymax = 790)
+center_coords <- c(xmin = 480, xmax = 1160, ymin = 290, ymax = 790)
+
 email <- "gonzalo.garciadecastro@upf.edu"
 ml_connect(email)
 
@@ -21,7 +23,7 @@ ml_connect(email)
 vocabulary <- import_vocabulary(
 	location = c("barcelona", "oxford"),
 	path_oxford = here("Data", "vocabulary_oxford.xlsx"),
-	google_email = email
+	google_email = email, update = FALSE
 ) %>% 
 	distinct(id_db, age_group, .keep_all = TRUE) 
 
@@ -33,11 +35,11 @@ participants <- get_participants(google_email = email) %>%
 	mutate(
 		date_test = as_date(date_test),
 		doe_2 = ifelse(test_language=="Spanish", doe_catalan, doe_spanish)
-		) %>% 
+	) %>% 
 	select(participant, id_db, date_test, location, age_group, age, test_language, list, version, lp, doe_2, vocab_size, valid_other, test_language, list, version, filename)
 
 # trials -----------------------------------------------------------------------
-trials <- bilingualr::trials %>%
+trials <- bilingualr::trials$cp %>%
 	rename(trial = trial_id) %>% 
 	mutate(trial = as.numeric(trial)) %>% 
 	select(location, test_language, list, version, trial, trial_type, target_location,
@@ -58,36 +60,48 @@ gaze <- import_gaze(
 	mutate(
 		gaze_in_l_aoi = gaze_in_aoi(x, y, left_coords),
 		gaze_in_r_aoi = gaze_in_aoi(x, y, right_coords),
+		gaze_in_c_aoi = gaze_in_aoi(x, y, center_coords),
 		fix_target = (target_location=="r" & gaze_in_r_aoi) | (target_location=="l" & gaze_in_l_aoi),
 		fix_distractor = (target_location=="r" & gaze_in_l_aoi) | (target_location=="l" & gaze_in_r_aoi),
+		fix_prime = gaze_in_c_aoi
 	) %>% 
[…]

### 2021-05-13 Rmd/report.Rmd
Separate target and distractor fixations

--- 2021-05-04 Rmd/report.Rmd
@@
 	drop_na(valid_participant) %>% 
-	mutate(valid_participant = ifelse(valid_participant, "Valid", "Not valid")) %>% 
-	ggplot(aes(lp, fill = valid_participant)) +
+	mutate(
+		valid_status = case_when(
+			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
+			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
+			!valid_participant ~ "No valid"
+		)
+	) %>% 
+	ggplot(aes(lp, fill = valid_status)) +
 	facet_grid(location~age_group, scales = "free") +
@@
 	drop_na(valid_participant) %>% 
-	ggplot(aes(age_group, participant, fill = valid_participant, colour = valid_participant)) +
+	mutate(
+		valid_status = case_when(
+			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
+			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
+			!valid_participant ~ "No valid"
+		)
+	) %>% 
+	ggplot(aes(age_group, participant, fill = valid_status, colour = valid_status)) +
 	facet_grid(lp~location, scales = "free") +
@@
 	ggplot(aes(age, doe_2, colour = lp)) +
-	facet_grid(test_language~location) +
+	facet_wrap(location~test_language) +
 	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
@@
 
-## Preprocessing participant data
-
 ## Preprocessing vocabulary data
@@
 	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
-	facet_wrap(~age_group) +
+	facet_wrap(location~age_group) +
 	geom_violin(position = position_dodge(width = 0.75)) + 
@@
 
-#### Cross-sectional
+#### Cross-sectional {.tab-set .tab-pills}
 
@@
 
-```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+##### Age group: 21 months
+
+```{r gaze_trial_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 gaze_trial %>% 
 	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
-	filter(valid_participant, valid_trial) %>% 
+	mutate(age_group = paste0(age_group, " months")) %>% 
+	filter(valid_participant, valid_trial, age_group == "21 months") %>% 
 	group_by(participant, lp, trial_type, age_group, location) %>% 
-	summarise(prop = mean(prop), .groups = "drop") %>% 
+	summarise(prop_target = mean(prop_target),
+			  prop_distractor = mean(prop_distractor),
+			  .groups = "drop") %>% 
+	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
+	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
 	drop_na() %>% 
-	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~age_group) +
+	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
+	facet_grid(trial_type~lp) +
 	geom_violin() +
@@
 	#stat_slab(position = position_nudge(x = 0.25)) +
-	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
+	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
 	#geom_point(size = 2, shape = 1, stroke = 1) +
-	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
+	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
 	scale_colour_brewer(palette = "Set1") +
@@
 	theme_bilingual() +
-	theme(legend.position = "none",
-		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
-		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "gaze_trial.png"))
+	theme(
+		legend.position = "none",
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	) +
+	ggsave(here("Figures", "gaze_trial_21.png"))
 
 ```
+
+##### Age group: 25 months
+
+```{r gaze_trial_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze_trial %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
+	mutate(age_group = paste0(age_group, " months")) %>% 
+	filter(valid_participant, valid_trial, age_group == "25 months") %>% 
+	group_by(participant, lp, trial_type, age_group, location) %>% 
+	summarise(prop_target = mean(prop_target),
+			  prop_distractor = mean(prop_distractor),
+			  .groups = "drop") %>% 
+	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
+	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
+	drop_na() %>% 
+	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
+	facet_grid(trial_type~lp) +
+	geom_violin() +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
+	#stat_slab(position = position_nudge(x = 0.25)) +
+	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
+	#geom_point(size = 2, shape = 1, stroke = 1) +
+	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	theme_bilingual() +
+	theme(
+		legend.position = "none",
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	) +
+	ggsave(here("Figures", "gaze_trial_25.png"))
+```
+
+##### Age group: 30 months
+
+```{r gaze_trial_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze_trial %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
+	mutate(age_group = paste0(age_group, " months")) %>% 
+	filter(valid_participant, valid_trial, age_group == "30 months") %>% 
+	group_by(participant, lp, trial_type, age_group, location) %>% 
+	summarise(prop_target = mean(prop_target),
+			  prop_distractor = mean(prop_distractor),
+			  .groups = "drop") %>% 
+	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
+	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
+	drop_na() %>% 
+	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
+	facet_grid(trial_type~lp) +
+	geom_violin() +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
+	#stat_slab(position = position_nudge(x = 0.25)) +
+	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
+	#geom_point(size = 2, shape = 1, stroke = 1) +
+	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	theme_bilingual() +
+	theme(
+		legend.position = "none",
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	) +
+	ggsave(here("Figures", "gaze_trial_30.png"))
+
+```
+
+##### {-}
 
@@
 	group_by(participant, lp, trial_type, age_group, location) %>% 
-	summarise(prop = mean(prop), .groups = "drop") %>% 
+	summarise(
+		prop_target = mean(prop_target),
+		prop_distractor = mean(prop_distractor),
+		.groups = "drop"
+	) %>% 
 	drop_na() %>% 
-	ggplot(aes(age_group, prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(~lp) +
+	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
+	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
+	ggplot(aes(age_group, prop, colour = aoi, fill = aoi)) +
+	facet_grid(trial_type~lp) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
@@
 	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
-	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
+	geom_boxplot(aes(group = interaction(age_group, aoi)), width = 0.1, outlier.colour = NA,
 				 position = position_dodge(width = 0.5), colour = "black", fill = "white") +
@@
 
-### Target fixations: Time course analysis
+### Target fixations: Time course analysis {.tabset .tab-pills}
 
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+#### Age group: 21 months
+
+```{r gaze_time_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 gaze_time %>% 
 	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>%
-	filter(valid_participant, valid_trial) %>% 
-	group_by(time_bin, trial_type, lp, age_group,location) %>% 
+	mutate(age_group = paste0(age_group, " months")) %>% 
+	filter(valid_participant, valid_trial, age_group=="21 months") %>% 
+	group_by(time_bin, trial_type, lp, age_group, location) %>% 
 	summarise(
-		prop = mean(prop, na.rm = TRUE),
+		prop_target = mean(prop_target, na.rm = TRUE),
+		prop_distractor = mean(prop_distractor, na.rm = TRUE),
 		n = n(),
@@
 	) %>% 
+	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
+	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
 	ungroup() %>% 
@@
 	drop_na() %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~age_group) +
+	ggplot(aes(x = time_bin, y = prop, colour = aoi, fill = aoi, shape = aoi)) +
+	facet_grid(lp~trial_type) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
 	geom_smooth() +
+	stat_summary(fun.data = "mean_se", geom = "pointrange", size = 0.5, alpha = 0.5) +
 	#geom_line() +
 	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
@@
 		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "gaze_time.png"))
+	ggsave(here("Figures", "gaze_time_21.png"))
 
 ```
+
+#### Age group: 25 months
+
+```{r gaze_time_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze_time %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>%
+	mutate(age_group = paste0(age_group, " months")) %>% 
+	filter(valid_participant, valid_trial, age_group=="25 months") %>% 
+	group_by(time_bin, trial_type, lp, age_group, location) %>% 
+	summarise(
+		prop_target = mean(prop_target, na.rm = TRUE),
+		prop_distractor = mean(prop_distractor, na.rm = TRUE),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
+	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
+	ungroup() %>% 
+	mutate(
+		se = sqrt((prop*(1-prop))/(n+4)),
+		lower = prop-se,
+		upper = prop+se
+	) %>% 
+	drop_na() %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = aoi, fill = aoi, shape = aoi)) +
+	facet_grid(lp~trial_type) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = "mean_se", geom = "pointrange", size = 0.5, alpha = 0.5) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "gaze_time_25.png"))
+
+```
+
+#### Age group: 30 months
+
+```{r gaze_time_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze_time %>% 
+	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>%
+	mutate(age_group = paste0(age_group, " months")) %>% 
+	filter(valid_participant, valid_trial, age_group=="30 months") %>% 
+	group_by(time_bin, trial_type, lp, age_group, location) %>% 
+	summarise(
+		prop_target = mean(prop_target, na.rm = TRUE),
+		prop_distractor = mean(prop_distractor, na.rm = TRUE),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
+	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
+	ungroup() %>% 
+	mutate(
+		se = sqrt((prop*(1-prop))/(n+4)),
+		lower = prop-se,
+		upper = prop+se
+	) %>% 
+	drop_na() %>% 
+	ggplot(aes(x = time_bin, y = prop, colour = aoi, fill = aoi, shape = aoi)) +
+	facet_grid(lp~trial_type) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = "mean_se", geom = "pointrange", size = 0.5, alpha = 0.5) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.title = element_blank(),
+		  legend.position = "top",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "gaze_time_30.png"))
+
+```
+
+#### {-}
 
@@
 	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
-	summarise(prop = mean(prop), .groups = "drop") %>% 
+	summarise(prop = mean(prop_target), .groups = "drop") %>% 
 	drop_na() %>% 
@@
 	geom_smooth(se = FALSE, method = "lm") +
-	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
+	labs(
+		x = "L1 vocabulary size",
+		y = "Target looking / Total looking",
+		colour = "Condition",
+		fill = "Condition"
+	) + 
 	scale_colour_brewer(palette = "Set1") +
@@
 	summarise(
-		prop = mean(prop, na.rm = TRUE),
+		prop_target = mean(prop_target, na.rm = TRUE),
+		prop_distractor = mean(prop_distractor, na.rm = TRUE),
 		n = n(),
@@
 	) %>% 
+	pivot_longer(c(prop_target, prop_distractor), names_to = "aoi", values_to = "prop") %>% 
 	ungroup() %>% 
@@
 		),
-		age_group = paste0(age_group, " months")
+		age_group = paste0(age_group, " months"),
+		aoi = str_to_sentence(str_remove(aoi, "prop_"))
 	) %>% 
@@
 
-#### Age group: 21 months
+#### Target fixations: 21 months
 
-```{r gaze_time_vocab_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r gaze_time_vocab_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%"}
 
@@
 	filter(age_group == "21 months") %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~vocab_cat) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_smooth() +
-	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	#geom_line() +
-	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	labs(x = "Time (ms)", y = "Pr(Target fixation)", colour = "Condition", fill = "Condition") +
-	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(legend.title = element_blank(),
-		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		  panel.grid.minor = element_blank()) +
-	ggsave(here("Figures", "gaze_time.png"), height = 5, width = 7)
-
-```
-
-#### Age group: 25 months
-
-```{r gaze_time_vocab_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-gaze_time_vocab_d %>% 
-	filter(age_group == "25 months") %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~vocab_cat) +
+	ggplot(aes(
+		x = time_bin, y = prop,
+		colour = interaction(vocab_cat, aoi, sep = " - "),
+		fill = interaction(vocab_cat, aoi, sep = " - "),
+		shape = interaction(vocab_cat, aoi, sep = " - ")
+	)
+	) +
+	facet_grid(lp~trial_type) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
@@
 	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Vocab-AOI",
+		 fill = "Vocab-AOI", shape = "Vocab-AOI") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.position = "right",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+```
+
+#### Target fixations: 25 months
+
+```{r gaze_time_vocab_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%"}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "25 months") %>% 
+	ggplot(aes(
+		x = time_bin, y = prop,
+		colour = interaction(vocab_cat, aoi, sep = " - "),
+		fill = interaction(vocab_cat, aoi, sep = " - "),
+		shape = interaction(vocab_cat, aoi, sep = " - ")
+	)
+	) +
+	facet_grid(lp~trial_type) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Vocab-AOI",
+		 fill = "Vocab-AOI", shape = "Vocab-AOI") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.position = "right",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+```
+
+#### Target fixations: 30 months
+
+```{r gaze_time_vocab_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%"}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "30 months") %>% 
+	ggplot(aes(
+		x = time_bin, y = prop,
+		colour = interaction(vocab_cat, aoi, sep = " - "),
+		fill = interaction(vocab_cat, aoi, sep = " - "),
+		shape = interaction(vocab_cat, aoi, sep = " - ")
+	)
+	) +
+	facet_grid(lp~trial_type) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Vocab-AOI",
+		 fill = "Vocab-AOI", shape = "Vocab-AOI") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.position = "right",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+```
+
+### {-}
+
+### Target fixations: Oxford vs. Barcelona {.tabset .tabset-pills}
+
+#### Age group: 21 months
+
+```{r gaze_time_location_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "21 months") %>% 
+	ggplot(aes(
+		x = time_bin, y = prop,
+		colour = interaction(location, aoi, sep = "-"),
+		fill = interaction(location, aoi, sep = "-"),
+		shape = interaction(location, aoi, sep = "-")
+	)) +
+	facet_grid(lp~trial_type) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
@@
 	theme(legend.title = element_blank(),
-		  legend.position = "top",
+		  legend.position = "right",
+		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
+```
+
+#### Age group: 25 months
+
+```{r gaze_time_location_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%"}
+
+gaze_time_vocab_d %>% 
+	filter(age_group == "25 months") %>% 
+	ggplot(aes(
+		x = time_bin, y = prop,
+		colour = interaction(location, aoi, sep = "-"),
+		fill = interaction(location, aoi, sep = "-"),
+		shape = interaction(location, aoi, sep = "-")
+	)) +
+	facet_grid(lp~trial_type) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	geom_smooth() +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	#geom_line() +
+	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
+	#geom_point(alpha = 0.5) +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Location-AOI",
+		 fill = "Location-AOI", shape = "Location-AOI") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_colour_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(legend.position = "right",
 		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
@@
 
-```{r gaze_time_vocab_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r gaze_time_location_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%"}
 
@@
 	filter(age_group == "30 months") %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~vocab_cat) +
+	ggplot(aes(
+		x = time_bin, y = prop,
+		colour = interaction(location, aoi, sep = "-"),
+		fill = interaction(location, aoi, sep = "-"),
+		shape = interaction(location, aoi, sep = "-")
+	)) +
+	facet_grid(lp~trial_type) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
@@
 	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
+	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Location-AOI",
+		 fill = "Location-AOI", shape = "Location-AOI") +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
@@
 	theme_bilingual() +
-	theme(legend.title = element_blank(),
-		  legend.position = "top",
+	theme(legend.position = "right",
 		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
@@
 
-### {-}
+#### {-}
+
+# Data analysis {.tabset .tab-pills}
+
+## Model
+
+$$
+\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
+(\beta_{1} + \beta_{1p} + \beta_{1i})\times Condition_{pi} + ... \\
+(\beta_{2} + \beta_{2i}) \times Group_{pi} + ... \\
+(\beta_{3} + \beta_{3i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
+(\beta_{4} + \beta_{4p}) \times Vocabulary_{p} + \varepsilon_{pi}
+$$
+
+## {-}
 
@@
 	gt() %>% 
-	gt::tab_spanner(
+	tab_spanner(
 		"Valid trials (%) by trial type",
@@
 gaze_time %>% 
-	filter(valid_participant, valid_trial) %>% 
 	group_by(participant, time_bin, trial_type, lp, age_group) %>% 
 	summarise(
-		prop = mean(prop, na.rm = TRUE),
+		prop = mean(prop_target, na.rm = TRUE),
 		n = n(),

### 2021-05-13 Rmd/report.Rmd
Simplify report code.

@@
 
-##### Age group: 21 months
-
-```{r gaze_trial_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-gaze_trial %>% 
+```{r gaze_trial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+gaze_trial_age <- gaze_trial %>% 
 	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
 	mutate(age_group = paste0(age_group, " months")) %>% 
-	filter(valid_participant, valid_trial, age_group == "21 months") %>% 
+	filter(valid_participant, valid_trial) %>% 
 	group_by(participant, lp, trial_type, age_group, location) %>% 
@@
 	drop_na() %>% 
-	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
-	facet_grid(trial_type~lp) +
+	split(f = .$age_group) %>% 
+	set_names(c("21", "25", "30"))
+```
+
+##### Age group: 21 months
+
+```{r gaze_trial_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+ggplot(gaze_trial_age[["21"]], aes(aoi, prop, colour = aoi, fill = aoi)) +
+	facet_grid(lp~trial_type) +
 	geom_violin() +
@@
 		legend.position = "none",
+		axis.title.x = element_blank(),
 		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
@@
 ```{r gaze_trial_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-gaze_trial %>% 
-	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
-	mutate(age_group = paste0(age_group, " months")) %>% 
-	filter(valid_participant, valid_trial, age_group == "25 months") %>% 
-	group_by(participant, lp, trial_type, age_group, location) %>% 
-	summarise(prop_target = mean(prop_target),
-			  prop_distractor = mean(prop_distractor),
-			  .groups = "drop") %>% 
-	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
-	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
-	drop_na() %>% 
-	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
-	facet_grid(trial_type~lp) +
+ggplot(gaze_trial_age[["25"]], aes(aoi, prop, colour = aoi, fill = aoi)) +
+	facet_grid(lp~trial_type) +
 	geom_violin() +
@@
 ```{r gaze_trial_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-gaze_trial %>% 
-	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
-	mutate(age_group = paste0(age_group, " months")) %>% 
-	filter(valid_participant, valid_trial, age_group == "30 months") %>% 
-	group_by(participant, lp, trial_type, age_group, location) %>% 
-	summarise(prop_target = mean(prop_target),
-			  prop_distractor = mean(prop_distractor),
-			  .groups = "drop") %>% 
-	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
-	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
-	drop_na() %>% 
-	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
-	facet_grid(trial_type~lp) +
+ggplot(gaze_trial_age[["30"]], aes(aoi, prop, colour = aoi, fill = aoi)) +
+	facet_grid(lp~trial_type) +
 	geom_violin() +
@@
 	) %>% 
-	drop_na()
+	drop_na() %>% 
+	split(f = .$age_group) %>% 
+	set_names(c("21", "25", "30"))
 
@@
 
-gaze_time_vocab_d %>% 
-	filter(age_group == "21 months") %>% 
-	ggplot(aes(
+ggplot(
+	gaze_time_vocab_d[["21"]],
+	aes(
 		x = time_bin, y = prop,
@@
 	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Vocab-AOI",
-		 fill = "Vocab-AOI", shape = "Vocab-AOI") +
+	labs(x = "Time (ms)", y = "Fixations", colour = "Vocabulary-AOI",
+		 fill = "Vocabulary-AOI", shape = "Vocabulary-AOI") +
+	guides(
+		fill = guide_legend(ncol = 2),
+		colour = guide_legend(ncol = 2),
+		shape = guide_legend(ncol = 2)
+	) +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
@@
 	theme_bilingual() +
-	theme(legend.position = "right",
+	theme(legend.position = "top",
 		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
@@
 
-gaze_time_vocab_d %>% 
-	filter(age_group == "25 months") %>% 
-	ggplot(aes(
+ggplot(
+	gaze_time_vocab_d[["25"]],
+	aes(
 		x = time_bin, y = prop,
@@
 
-gaze_time_vocab_d %>% 
-	filter(age_group == "30 months") %>% 
-	ggplot(aes(
+ggplot(
+	gaze_time_vocab_d[["21"]],
+	aes(
 		x = time_bin, y = prop,
@@
 	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
+	labs(x = "Time (ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
@@
 	theme(legend.title = element_blank(),
-		  legend.position = "right",
+		  legend.position = "top",
 		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
@@
 	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Location-AOI",
+	labs(x = "Time (ms)", y = "Fixations", colour = "Location-AOI",
 		 fill = "Location-AOI", shape = "Location-AOI") +
@@
 
-gaze_time_vocab_d %>% 
-	filter(age_group == "30 months") %>% 
-	ggplot(aes(
+ggplot(
+	gaze_time_vocab_d[["30"]],
+	aes(
 		x = time_bin, y = prop,

### 2021-05-20 Rmd/CP_eyetrackingR.Rmd
EyetrackingR script
Script for visualisation and analysis using eyetrackingR package

---
title: "CognatePriming_EyetrackingR"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library("Matrix")
library("eyetrackingR")
library("tidyverse")
library("lme4")
library("ggplot2")

```

```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# load data
processed_oxford <- readRDS(here("Results", "processed_oxford.rds")) %>%
  mutate(sample = "oxford")

processed <- bind_rows(processed_oxford)

```

## PREPARING DATA FOR ANALYSIS

```{r eyetrackingR, eval=TRUE, echo = FALSE}

processed_clean <- processed %>%
  filter(valid_trial == TRUE) %>%
  filter(valid_participant == TRUE) %>%
  mutate(trackloss_col = ifelse(valid_sample == TRUE, FALSE, TRUE)) # needed for eyetrackingR - TRUE means trackloss, FALSE means valid gaze

data <- make_eyetrackingr_data(processed_clean, 
                                      participant_column = "participant",
                                      trial_column = "trial_num",
                                      time_column = "time",
                                      trackloss_column = "trackloss_col",
                                      item_columns = c("prime", "target"),
                                      aoi_columns = c('aoi_target','aoi_distractor'), 
                                      treat_non_aoi_looks_as_missing = FALSE)

```

#### Aggregrate timebins + specify Target as AOI

```{r time_sequence, eval=TRUE, echo = FALSE}

# aggregate across trials within subjects in time analysis
response_time <- make_time_sequence_data(data, time_bin_size = 0.1, 
                                                predictor_columns = c("test_language", "sample", "trial_type", "age_group", "lp"),
                                                aois = "aoi_target")
#summary(response_time)

```

### Descriptives

```{r descriptive, eval=TRUE, echo = FALSE}

# Number of participants after cleaning
print("Final participants after data cleaning")

response_time %>%
  dplyr::select(participant, sample, age_group, lp) %>%
  unique() %>%
  group_by(sample, age_group, lp) %>%
  summarise(N = n())

```

## ANALYSIS
### Growth curve

```{r visualise only, eval=TRUE, echo = FALSE}

response_time_mono_21 <- response_time %>%
  filter(lp == "Monolingual" & age_group == "21 months")
response_time_mono_25 <- response_time %>%
  filter(lp == "Monolingual" & age_group == "25 months")
response_time_mono_30 <- response_time %>%
  filter(lp == "Monolingual" & age_group == "30 months")

# Visualise data from each group
# Monolingual

print("21 month monolingual data")

plot(response_time_mono_21, predictor_column = "trial_type", dv = "Prop") +
  theme_light() +
  xlab("Time from target & distractor image onset (s)") +
  ylab("Proportion of time looking at target") +
  ylim(c(0:1))

print("21 month monolingual data with model fit curve")

# Plot monolingual data with model fit curve
model_time_sequence_plot_mono_21 <- lmer(Prop ~ trial_type*(ot1 + ot2 + ot3) + 
                                               (1 | participant), 
                                             data = response_time_mono_21, REML = FALSE)

plot(response_time_mono_21, predictor_column = "trial_type", dv = "Prop", model = model_time_sequence_plot_mono_21) +
  theme_light() +
  xlab("Time from target & distractor image onset (s)") +
  ylab("Proportion of time looking at target") +
  ylim(c(0:1))

print("25 month monolingual data")

plot(response_time_mono_25, predictor_column = "trial_type", dv = "Prop") +
  theme_light() +
  xlab("Time from target & distractor image onset (s)") +
  ylab("Proportion of time looking at target") +
  ylim(c(0:1))

print("30 month monolingual data")

plot(response_time_mono_30, predictor_column = "trial_type", dv = "Prop") +
  theme_light() +
  xlab("Time from target & distractor image onset (s)") +
  ylab("Proportion of time looking at target") +
  ylim(c(0:1))

```

### 2021-05-21 Rmd/CP_eyetrackingR.Rmd
Added analysis section
Code for analysing model fit (growth curve) and bonferroni tests for specific comparisons of interest

@@
 library("ggplot2")
+library("multcomp") # bonferroni
 
@@
 
+############ 21 months ##################
+
 print("21 month monolingual data")
@@
 
-# Plot monolingual data with model fit curve
-model_time_sequence_plot_mono_21 <- lmer(Prop ~ trial_type*(ot1 + ot2 + ot3) + 
-                                               (1 | participant), 
-                                             data = response_time_mono_21, REML = FALSE)
-
-plot(response_time_mono_21, predictor_column = "trial_type", dv = "Prop", model = model_time_sequence_plot_mono_21) +
-  theme_light() +
-  xlab("Time from target & distractor image onset (s)") +
-  ylab("Proportion of time looking at target") +
-  ylim(c(0:1))
+############ 25 months ##################
 
@@
   ylim(c(0:1))
+
+############ 30 months ##################
 
@@
 ```
+
+```{r analysis, eval=TRUE, echo = FALSE}
+
+# Plot 21 month monolingual data with model fit curve
+model_time_sequence_mono_21 <- lmer(Prop ~ trial_type*(ot1 + ot2 + ot3) + 
+                                               (1 | participant), 
+                                             data = response_time_mono_21, REML = FALSE)
+
+plot(response_time_mono_21, predictor_column = "trial_type", dv = "Prop", model = model_time_sequence_mono_21) +
+  theme_light() +
+  xlab("Time from target & distractor image onset (s)") +
+  ylab("Proportion of time looking at target") +
+  ylim(c(0:1))
+
+summary(model_time_sequence_mono_21)
+
+# Post-hoc tests - only analyse significant predictors / interactions
+#library(multcomp)
+# To construct matrix, refer to summary()
+contrast.matrix = rbind(
+  "CP-NP" = c(0,-1,0, 0,0,0, 0,0,0,0,0,0), # ConditionCognate Prime(REFERENCE) - ConditionNon-Cognate Prime (Is there a significant difference between CP and NP?)
+  "NP-UN" = c(0,1,-1, 0,0,0, 0,0, 0,0, 0,0), # ConditionNon-Cognate Prime - ConditionUnrelated Prime (Is there a significant difference between NP and UN?)
+  "CP-NP_OT1" = c(0,0,0, 0,0,0, -1,0, 0,0, 0,0), # ConditionCognate Prime(REFERENCE) - ConditionNon-Cognate Prime (OT1, linear)
+  "NP-UN_OT1" = c(0,0,0, 0,0,0, -1,1, 0,0, 0,0) # ConditionNon-Cognate Prime - ConditionUnrelated Prime (OT1, linear)
+)
+comps <- glht(model_time_sequence_mono_21, contrast.matrix )
+summary(comps, test= adjusted("bonferroni"))
+
+```

### 2021-05-27 Rmd/report.Rmd
Update Rmd

--- 2021-05-12 Rmd/report.Rmd
@@
     toc: true
-    toc_depth: 2
+    toc_depth: 4
     toc_float: true
@@
 library(janitor)
+library(lme4)
+library(broom.mixed)
 library(gt)
 library(patchwork)
+library(htmltools)
 library(here)
 
+# create functions
+logit_to_prob <- function(x) exp(x) / (1 + exp(x))
+
 # load data
-participants <- readRDS(here("Results", "participants.rds"))
-gaze_trial <- readRDS(here("Results", "gaze_trial.rds"))
-gaze_time <- readRDS(here("Results", "gaze_time.rds"))
+gaze <- readRDS(here("Data", "Gaze", "processed.rds"))
 attrition <- readRDS(here("Results", "attrition.rds"))
+participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
+	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+	drop_na(participant)
+fit <- readRDS(here("Results", "fit.rds"))
 
@@
 
-# Participants
+# Methods
 
-We collected data from `r length(unique(participants$participant))` participants, of which `r length(unique(participants$participant[participants$valid_participant]))` met the inclusion criteria and were included in data analyses.
-`r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+## Participants {.tabset .tabpills}
 
-```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
+* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
+`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
+* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
+
+### Summary
+
+```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants %>% 
+	left_join(distinct(attrition, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	ggplot(aes(lp, fill = as.factor(test_language))) +
+	facet_grid(location~age_group, scales = "free") +
+	geom_bar(colour = NA) +
+	geom_hline(yintercept = 24, linetype = "dashed") +
+	scale_colour_brewer(palette = "Set1") +
+	labs(x = "Group", y = "Sample size", fill = "Test language") +
+	scale_fill_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(
+		legend.position = "top",
+		axis.title.x = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.title.y = element_text(angle = 90)
+	) +
+	ggsave(here("Figures", "sample.png"))
+
+```
+
+### Longitudinal
+
+We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
+Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+
+```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
 # plot participants
 participants %>% 
+	left_join(distinct(attrition, participant, valid_participant)) %>% 
+	mutate(
+		valid_status = case_when(
+			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
+			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
+			!valid_participant ~ "Not valid"
+		),
+		age_group = str_remove(age_group, " months")
+	) %>%
+	drop_na(valid_status) %>% 
+	ggplot(aes(age_group, participant, colour = valid_status)) +
+	facet_grid(location~lp, scales = "free") +
+	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
+	geom_point(size = 2, alpha = 0.5) +
+	geom_hline(yintercept = 0.2, linetype = "dashed") +
+	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
+	scale_colour_brewer(palette = "Set1") +
+	theme_bilingual() +
+	theme(
+		legend.position = "right",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.title.y = element_blank(),
+		axis.text.y = element_blank(),
+		axis.ticks.y = element_blank()
+	) +
+	ggsave(here("Figures", "cohort.png"))
+```
+
+### Attrition (overall)
+
+```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+participants %>% 
+	left_join(distinct(attrition, participant, valid_participant)) %>% 
 	drop_na(valid_participant) %>% 
-	mutate(valid_participant = ifelse(valid_participant, "Valid", "Not valid")) %>% 
-	ggplot(aes(lp, fill = valid_participant)) +
+	mutate(
+		valid_status = case_when(
+			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
+			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
+			!valid_participant ~ "Not valid"
+		)
+	) %>% 
+	ggplot(aes(lp, fill = valid_status)) +
 	facet_grid(location~age_group, scales = "free") +
@@
 	) +
-	ggsave(here("Figures", "sample.png"))
+	ggsave(here("Figures", "participants_attrition.png"))
 ```
 
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-
-# plot participants
-participants %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(age_group, participant, fill = valid_participant, colour = valid_participant)) +
-	facet_grid(lp~location, scales = "free") +
-	geom_point(size = 3, shape = 4) +
-	geom_line(aes(group = participant)) +
-	labs(x = "Age (months)", y = "Language profile", fill = "Valid?", colour = "Valid?") +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(axis.title.y = element_blank(),
-		  axis.text.y = element_blank(),
-		  axis.ticks.y = element_blank(),
-		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "sample_cohort.png"))
-```
-
-## Language profiles
-
-Only valid participants.
-
-```{r lps, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	filter(valid_participant) %>% 
-	ggplot(aes(age, doe_2, colour = lp)) +
-	facet_grid(test_language~location) +
-	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
-	geom_point(size = 3, alpha = 0.5) +
-	geom_hline(yintercept = 0.2, linetype = "dashed") +
-	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
-			 xmin = 20, xmax = 22, ymin = -Inf, ymax = Inf) +
-	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
-			 xmin = 24, xmax = 26, ymin = -Inf, ymax = Inf) +
-	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
-			 xmin = 28, xmax = 32, ymin = -Inf, ymax = Inf) +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Group") +
-	scale_colour_brewer(palette = "Set1") +
-	scale_y_continuous(labels = percent) +
-	theme_bilingual() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.y = element_line(linetype = "dotted", colour = "grey"),
-		axis.text.x = element_text(size = 10),
-		axis.title.y = element_text(angle = 90),
-		axis.text.y = element_text(size = 10)
-	) +
-	ggsave(here("Figures", "lps.png"))
-```
-
-# Methods
-
-## Preprocessing participant data
-
-## Preprocessing vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Preprocessing gaze data {.tabset .tabset-pills}
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-## {-}
-
-# Results
-
-## Attrition rate
+### Attrition (by group)
 
@@
 
-attrition %>%
-	left_join(select(participants, location, lp, participant, date_test)) %>% 
-	drop_na(trial_type) %>% 
-	group_by(participant, lp, location, date_test, age_group, trial_type, valid_participant, valid_other) %>% 
+left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
+	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant, valid_other) %>% 
 	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
@@
 
+### Attrition (by participant)
+
+```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(select(participants, participant, location)) %>% 
+	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
+	group_by(location, participant, lp, age_group, valid_participant) %>% 
+	summarise(
+		valid = mean(valid_trial),
+		invalid_gaze = mean(!valid_gaze),
+		invalid_other = mean(!valid_other),
+		invalid_vocab = mean(!valid_vocab),
+		.groups = "drop"
+	) %>% 
+	relocate(participant) %>% 
+	relocate(invalid_other, .after = invalid_vocab) %>% 
+	gt() %>% 
+	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
+	cols_label(
+		participant = "Participant",
+		location = "Location",
+		lp = "Lang. Profile",
+		age_group = "Age",
+		valid_participant = "Valid participant",
+		valid = "Valid trials (%)",
+		invalid_gaze = "Gaze (%)",
+		invalid_vocab = "Vocabulary (%)",
+		invalid_other = "Other (%)"
+	) %>% 
+	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab", "invalid_other")) %>% 
+	div(style='height:600px; overflow-y: scroll', .)
+```
+
+### Attrition (by trials)
+
+```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(select(participants, participant, location)) %>% 
+	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
+	count() %>% 
+	ungroup() %>%
+	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
+	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
+	clean_names() %>% 
+	gt(groupname_col = c("location", "lp")) %>% 
+	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
+	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
+	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
+	cols_label(
+		location = "Location",
+		lp = "Group",
+		trial_type = "Trial type",
+		x21_months_not_valid = "Not valid",
+		x21_months_valid = "Valid",
+		x25_months_not_valid = "Not valid",
+		x25_months_valid = "Valid",
+		x30_months_not_valid = "Not valid",
+		x30_months_valid = "Valid"
+	)
+
+```
+
+```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(select(participants, participant, location)) %>% 
+	mutate(valid_status = case_when(
+		!valid_vocab ~ "Invalid vocabulary",
+		!valid_gaze ~ "Invalid gaze",
+		!valid_other ~ "Other",
+		!valid_participant ~ "Invalid participant",
+		TRUE ~ "Valid"
+	)) %>% 
+	count(location, lp, age_group, trial_type, valid_status) %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_col(position = position_fill()) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	scale_color_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	scale_y_continuous(labels = scales::percent) +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	theme_bilingual() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(angle = 20, hjust = 1),
+		axis.text.y = element_text(size = 8),
+		axis.title.y = element_blank()
+	)
+```
+
+### {-}
+
+## Materials
+
+## Procedure
+
+## Data analysis
+
+### Vocabulary data
+
+We collected vocabulary data from participants.
+In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
+In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
+In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
+In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
+All checklists included the words involved in the trial lists.
+When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
+Each response to either checklist was aggregated to produce several vocabulary measures:
+
+* **Total vocabulary**: total number of words the child knows, summing up both languages.
+For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
+* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
+For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
+* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
+For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
+
+Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
+
+## Gaze data {.tabset .tabset-pills}
+
+Each trial was divided into 100 ms time bins.
+for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
+Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
+
+### Workflow
+
+```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+DiagrammeR::grViz("digraph {
+  graph [layout = dot, rankdir = TB]
+
+  node [shape = rectangle, fontname = 'Arial']        
+  rec1 [label = 'Merge Barcelona and Oxford data']
+  rec2 [label = 'Impute missing/invalid samples (pending)']
+  rec2 [label = 'Extract fixations (pending)']
+  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
+  rec4 [label = 'Divide each trial into 100 ms time bins']
+  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
+  rec6 [label = 'Exclude time bins 1-3 (pending)']
+  rec7 [label = 'Apply trial-level inclusion criteria']
+  rec8 [label = 'Apply participant-level inclusion criteria']
+
+  # edge definitions with the node IDs
+  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
+  }", 
+  height = 500)
+```
+
+### Trial-level inclusion criteria
+
+* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
+* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
+* At least one sample in target and one sample in distractor
+* Participant understands prime word in both languages
+* Participant knows the target word in the test language
+* Participant knows the distractor word in the test language
+
+### Participant-level inclusion criteria
+
+* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
+* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
+* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
+* $\geq$ 36 gestational weeks
+* $\geq$ 2,800g birth weight
+* No diagnosed developmental, hearing, or visual disorders
+* Not exposed to more than 10% to a 3rd language
+
+### {-}
+
+# Results
+
 ## Vocabulary
-
-### Vocabulary in the dominant language (L1)
 
@@
 participants %>% 
-	mutate(age_group = as.factor(paste0(age_group, " mo"))) %>% 
+	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
 	drop_na(lp) %>%
+	filter(valid_participant) %>% 
 	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
-	facet_wrap(~age_group) +
+	facet_wrap(location~age_group) +
 	geom_violin(position = position_dodge(width = 0.75)) + 
@@
 
-## Target fixations
+## Target fixations {.tabset .tab-pills}
 
-### Target fixations: Age group and language profile {.tabset .tabset-pills}
-
-#### Cross-sectional
+### Aggregated by trial
 
@@
 Some participants were longitudinal.
-Scores form longitudinal participant  are indicated by gray lines linking data points from the same participant.
+Scores form longitudinal participant  are indicated by grey lines linking data points from the same participant.
 
-```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-gaze_trial %>% 
+```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+gaze %>% 
 	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
+	left_join(select(participants, participant, age_group, location)) %>% 
 	filter(valid_participant, valid_trial) %>% 
 	group_by(participant, lp, trial_type, age_group, location) %>% 
-	summarise(prop = mean(prop), .groups = "drop") %>% 
+	summarise(
+		prop = mean(prop, na.rm = TRUE),
+		.groups = "drop"
+	) %>% 
 	drop_na() %>% 
@@
 	facet_grid(lp~age_group) +
-	geom_violin() +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
+	geom_violin(position = position_dodge(width = 0.75)) +
 	#stat_slab(position = position_nudge(x = 0.25)) +
-	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
-	#geom_point(size = 2, shape = 1, stroke = 1) +
-	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
+	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
+	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
+				 position = position_dodge(width = 0.75), colour = "black", fill = "white") +
+	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
 	scale_colour_brewer(palette = "Set1") +
@@
 	theme(legend.position = "none",
+		  axis.title.x = element_blank(),
 		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
-		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "gaze_trial.png"))
-
-```
-
-#### Longitudinal
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-This figure shows the fitted line of a General Additive Model (GAM) generated using the `geom_smooth()` function from the `ggplot` R package, with default settings.
-
-```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-gaze_trial %>% 
-	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
-	filter(valid_participant, valid_trial) %>% 
-	group_by(participant, lp, trial_type, age_group, location) %>% 
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	drop_na() %>% 
-	ggplot(aes(age_group, prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(~lp) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_line(aes(group = interaction(participant, trial_type)), alpha = 0.5) +
-	geom_violin(position = position_dodge(width = 0.5)) +
-	#stat_slab(position = position_nudge(x = 0.25)) +
-	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
-	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
-				 position = position_dodge(width = 0.5), colour = "black", fill = "white") +
-	labs(x = "Age (months)", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme_bilingual() +
-	theme(legend.position = "top",
 		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
@@
 
-### {-}
+### Growth curve analysis {.tabset .tab-pills}
 
-### Target fixations: Time course analysis
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-gaze_time %>% 
-	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
-	filter(valid_participant, valid_trial) %>% 
-	group_by(time_bin, trial_type, lp, age_group,location) %>% 
-	summarise(
-		prop = mean(prop, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	ungroup() %>% 
-	mutate(
-		se = sqrt((prop*(1-prop))/(n+4)),
-		lower = prop-se,
-		upper = prop+se
-	) %>% 
-	drop_na() %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_smooth() +
-	#geom_line() +
-	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(legend.title = element_blank(),
-		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "gaze_time.png"))
+We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
 
 ```
-
-### Target fixations: Vocabulary size
-
-```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-gaze_trial %>% 
-	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
-	filter(valid_participant, valid_trial) %>% 
-	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	drop_na() %>% 
-	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
-	#stat_slab(position = position_nudge(x = 0.25)) +
-	geom_point(alpha = 0.5) +
-	geom_smooth(se = FALSE, method = "lm") +
-	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
-	scale_colour_brewer(palette = "Set1") +
-	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme_bilingual() +
-	theme(panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		  legend.position = "top",
-		  axis.text.x = element_text(size = 10)) +
-	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
+elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
+	(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant) +
+	(1 + ot1 + ot2 + ot3 + trial_type + age_group + lp | target)
 ```
 
-### Target fixations: High vocabulary vs. low vocabulary {.tabset .tabset-pills}
-
-```{r gaze_time_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
-
-gaze_time_vocab_d <- gaze_time %>% 
-	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
-	left_join(select(participants, participant, age_group, vocab_size)) %>% 
-	filter(valid_participant, valid_trial) %>% 
-	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
-	summarise(
-		prop = mean(prop, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	ungroup() %>% 
-	mutate(
-		se = sqrt((prop*(1-prop))/(n+4)),
-		lower = prop-se,
-		upper = prop+se,
-		time_bin = time_bin*100,
-		vocab_cat = ifelse(
-			vocab_size < median(.$vocab_size, na.rm = TRUE),
-			"Below the median",
-			"Above the median"
-		),
-		age_group = paste0(age_group, " months")
-	) %>% 
-	drop_na()
-
-```
-
-#### Age group: 21 months
-
-```{r gaze_time_vocab_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-gaze_time_vocab_d %>% 
-	filter(age_group == "21 months") %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~vocab_cat) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_smooth() +
-	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	#geom_line() +
-	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	labs(x = "Time (ms)", y = "Pr(Target fixation)", colour = "Condition", fill = "Condition") +
-	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(legend.title = element_blank(),
-		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		  panel.grid.minor = element_blank()) +
-	ggsave(here("Figures", "gaze_time.png"), height = 5, width = 7)
-
-```
-
-#### Age group: 25 months
-
-```{r gaze_time_vocab_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-gaze_time_vocab_d %>% 
-	filter(age_group == "25 months") %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~vocab_cat) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_smooth() +
-	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	#geom_line() +
-	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(legend.title = element_blank(),
-		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
-
-```
-
-#### Age group: 30 months
-
-```{r gaze_time_vocab_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-gaze_time_vocab_d %>% 
-	filter(age_group == "30 months") %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~vocab_cat) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_smooth() +
-	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	#geom_line() +
-	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(legend.title = element_blank(),
-		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
-
-```
-
-### {-}
-
-### Target fixations: Oxford vs. Barcelona {.tabset .tabset-pills}
-
-#### Age group: 21 months
-
-```{r gaze_time_location_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-gaze_time_vocab_d %>% 
-	filter(age_group == "21 months") %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~location) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_smooth() +
-	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	#geom_line() +
-	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(legend.title = element_blank(),
-		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
-
-```
-
-#### Age group: 25 months
-
-```{r gaze_time_location_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-gaze_time_vocab_d %>% 
-	filter(age_group == "25 months") %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~location) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_smooth() +
-	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	#geom_line() +
-	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(legend.title = element_blank(),
-		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
-
-```
-
-#### Age group: 30 months
-
-```{r gaze_time_location_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-gaze_time_vocab_d %>% 
-	filter(age_group == "30 months") %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~location) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_smooth() +
-	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	#geom_line() +
-	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	#geom_point(alpha = 0.5) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(legend.title = element_blank(),
-		  legend.position = "top",
-		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
-
-```
-
-#### {-}
-
-# Data analysis {.tabset .tab-pills}
-
-## Model
+The formal implementation of this model is:
 
 $$
-\log(\frac{p}{n - q}) &=& (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
+\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
 (\beta_{1} + \beta_{1p} + \beta_{1i})\times Condition_{pi} + ... \\
@@
 
-## {-}
+#### Fixed effects
+
+```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+confint.merMod(fit, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	  tab_style(
+    style = list(
+      cell_fill(color = "#F9E3D6")
+      ),
+    locations = cells_body(
+      columns = everything(),
+      rows = p_value < 0.05
+    )
+  )
+```
+
+#### Random effects {.tabset .tab-pills}
+
+##### By participant
+
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+VarCorr(fit)$participant %>% 
+	as.data.frame() %>% 
+	rownames_to_column("term1") %>% 
+	pivot_longer(-term1, names_to = "term2", values_to = "value") %>% 
+	ggplot(aes(term1, term2, fill = value)) +
+	geom_tile() +
+	coord_fixed() +
+	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
+	scale_fill_distiller(palette = "Oranges") +
+	theme_bilingual() +
+	theme(
+		axis.title = element_blank(),
+		axis.text.x = element_text(angle = 90)
+	)
+
+```
+
+##### By target word
+
+```{r random_effects_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+VarCorr(fit)$target %>% 
+	as.data.frame() %>% 
+	rownames_to_column("term1") %>% 
+	pivot_longer(-term1, names_to = "term2", values_to = "value") %>% 
+	ggplot(aes(term1, term2, fill = value)) +
+	geom_tile() +
+	coord_fixed() +
+	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
+	scale_fill_distiller(palette = "Oranges") +
+	theme_bilingual() +
+	theme(
+		axis.title = element_blank(),
+		axis.text.x = element_text(angle = 90)
+	)
+
+```
+
+##### {-}
+
+#### {-}
+
+#### Marginal means
+
+```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+y_pred <- logit_to_prob(predict(fit))
+
+gaze %>% 
+	drop_na() %>% 
+	ggplot(aes(x = ot1, y = prop, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(fun.data = mean_se, aes(y = y_pred), geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(fun = mean, aes(y = y_pred), geom = "line", size = 1) +
+	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_color_brewer(palette = "Set1") +
+	scale_fill_brewer(palette = "Set1") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme_bw() +
+	theme(
+		legend.position = "top",
+		panel.background = element_rect(fill = "white", colour = NA),
+		strip.background = element_rect(colour = "grey"),
+		panel.border = element_rect(colour = "grey"),
+		panel.grid = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		axis.text.x = element_text(size = 7)
+	)
+```
+
+#### {-}
 
@@
 
-## Appendix 2: Individual target looking times
-
-```{r gaze_time_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
-gaze_time %>% 
-	group_by(participant, time_bin, trial_type, lp, age_group) %>% 
-	summarise(
-		prop = mean(prop, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	ungroup() %>% 
-	mutate(
-		se = sqrt((prop*(1-prop))/(n+4)),
-		lower = prop-se,
-		upper = prop+se
-	) %>% 
-	drop_na() %>% 
-	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
-	facet_wrap(age_group~participant~lp) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_smooth() +
-	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
-	# geom_point(shape = 1, stroke = 1, size = 0.5) +
-	geom_text(aes(x = 0, y = 1, label =
-				  	paste0(str_remove_all(participant, pattern = "[a-zA-Z]"),
-				  		   "/", age_group, "mo/", lp)),
-			  size = 2, colour = "black", hjust = 0) +
-	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
-	theme(
-		axis.text = element_text(size = 7),
-		legend.title = element_blank(),
-		legend.position = "top",
-		strip.background = element_blank(),
-		strip.text.x = element_blank()
-	) +
-	ggsave(here("Figures", "gaze_time_participant.png"), height = 12, width = 12)
-```
-
 # References

### 2021-05-27 R/participants.R

@@ -1,0 +1,131 @@
+# participants
+
+# set up ----
+library(tidyverse)
+library(janitor)
+library(multilex)
+library(googlesheets4)
+library(readxl)
+library(multilex)
+library(lubridate)
+library(here)
+
+# set params
+ml_connect("gonzalo.garciadecastro@upf.edu") # log into MultiLex
+cdi_replacements <- c("boots" = "boot", "boot(s)" = "boot", "fire engine" = "fireengine",
+					  "teddy bear" = "teddy", "bunny / rabbit" = "bunny",
+					  "lorry / truck" = "truck", "bicycle / bike" = "bike")
+
+# Barcelona data ----
+p <- ml_participants()
+r <- ml_responses(p, update = FALSE)
+vocab_raw_barcelona <- r %>% 
+	mutate(
+		understands = response > 1,
+		age_group =  as.factor(
+			case_when(
+				between(age, 20, 24) ~ 21,
+				between(age, 24, 28) ~ 25,
+				between(age, 28, 33) ~ 30
+			)),
+		age_group = paste0(age_group, " months")
+		) %>%
+	filter(
+		study=="CognatePriming",
+		understands
+	) %>%
+	select("id_exp", "time", "age_group", "item", "response") %>%
+	group_by(id_exp, time, age_group) %>%
+	summarise(vocab_words = list(unique(item)), .groups = "drop")
+
+vocabulary_barcelona <- ml_vocabulary(p, r, scale = "prop", by = c("id_exp")) %>%
+	right_join(select(p, id_db, time, id_exp)) %>%
+	filter(type=="understands") %>%
+	right_join(vocab_raw_barcelona) %>%
+	select(id_db, age_group, vocab_size = vocab_prop_total, vocab_words)
+
+vocab_norms_barcelona <- r %>%
+	filter(language==dominance, between(age, 19, 22)) %>% 
+	mutate(understands = response > 1) %>% 
+	group_by(item) %>% 
+	summarise(prop = mean(understands, na.rm = TRUE), .groups = "drop") %>% 
+	filter(prop > 0.5) %>% 
+	pull(item)
+
+# participants
+participants_barcelona <- range_read(ss = "1JkhN4iBh3bi6PSReGGk9jSrVgDhZNOUmve6vNS2eEqE", sheet = "barcelona", na = "") %>%
+	mutate_if(is.logical, ~ifelse(is.na(.), FALSE, .)) %>%
+	mutate(
+		age_group = as.factor(paste0(age_group, " months")),
[…]

### 2021-05-28 Rmd/report.Rmd
Try to fix (finally)

@@
 
-#### Random effects {.tabset .tab-pills}
-
-##### By participant
+#### Random effects
 
@@
 VarCorr(fit)$participant %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = "value") %>% 
-	ggplot(aes(term1, term2, fill = value)) +
-	geom_tile() +
-	coord_fixed() +
-	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
-	scale_fill_distiller(palette = "Oranges") +
-	theme_bilingual() +
-	theme(
-		axis.title = element_blank(),
-		axis.text.x = element_text(angle = 90)
-	)
-
-```
-
-##### By target word
-
-```{r random_effects_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-VarCorr(fit)$target %>% 
 	as.data.frame() %>% 

### 2021-05-28 Rmd/report.Rmd
Merge report.Rmd from both branches

@@
 )
-options(knitr.kable.NA = '-')
+options(knitr.kable.NA = '-',
+		ggplot2.discrete.fill = RColorBrewer::brewer.pal(6, name = "Dark2"),
+		ggplot2.discrete.colour = RColorBrewer::brewer.pal(6, name = "Dark2"),
+		ggplot2.continuous.fill = RColorBrewer::brewer.pal(6, name = "Dark2"),
+		ggplot2.continuous.colour = RColorBrewer::brewer.pal(6, name = "Dark2")
+)
 
@@
 logit_to_prob <- function(x) exp(x) / (1 + exp(x))
+
+theme_custom <- function(){
+	theme(
+		panel.background = element_rect(fill = "transparent"),
+		panel.grid = element_blank(),
+		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
+		panel.border = element_rect(fill = "transparent", colour = "black"),
+		text = element_text(colour = "black", size = 15),
+		axis.text = element_text(colour = "black")
+	)
+}
+theme_set(theme_custom())
 
@@
 	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
 	theme(
@@
 	facet_grid(location~lp, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
-	geom_point(size = 2, alpha = 0.5) +
+	geom_line(aes(group = interaction(lp, participant))) +
+	geom_point(size = 2) +
 	geom_hline(yintercept = 0.2, linetype = "dashed") +
 	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
-	scale_colour_brewer(palette = "Set1") +
-	theme_bilingual() +
 	theme(
@@
 	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
 	theme(
@@
 	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_color_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
 	scale_y_continuous(labels = scales::percent) +
 	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	theme_bilingual() +
 	theme(
@@
 ```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants %>% 
+	count(age_group, location)
+
 # vocabulary
@@
 				 position = position_dodge(width = 0.75)) +
+		geom_text(data = sample_size,
+			  aes(x = 1.5, y = 0.95, label = paste0("n = ", n),
+			  	colour = "black", fill = "black"), show.legend = FALSE) +
 	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	theme_bilingual() +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
 	theme(legend.title = element_blank(),
@@
 ```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	count(age_group, lp)
+
 gaze %>% 
@@
 				 position = position_dodge(width = 0.75), colour = "black", fill = "white") +
+	geom_text(data = sample_size,
+			  aes(x = 1, y = 0.95, label = paste0("n = ", n),
+			  	colour = "black", fill = "black"), show.legend = FALSE) +
 	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
-	scale_colour_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme_bilingual() +
 	theme(legend.position = "none",
@@
 
+#### Model details
+
 We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
@@
 elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-	(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant) +
-	(1 + ot1 + ot2 + ot3 + trial_type + age_group + lp | target)
+(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
 ```
@@
 	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
-	scale_fill_distiller(palette = "Oranges") +
-	theme_bilingual() +
+	scale_fill_viridis_c() +
 	theme(
@@
 
-#### Marginal means
+#### Marginal means {.tabset .tab-pills}
+
+##### Overall
 
@@
 y_pred <- logit_to_prob(predict(fit))
+sample_size <- participants %>% 
+	filter(valid_participant) %>%
+	count(age_group, lp)
 
@@
 	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
+			  	colour = "black", fill = "black"), show.legend = FALSE) +
 	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
 		 colour = "Trial type", fill = "Trial type") +
-	scale_color_brewer(palette = "Set1") +
-	scale_fill_brewer(palette = "Set1") +
-	scale_y_continuous(limits = c(0, 1)) + 
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
 	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme_bw() +
+	theme_custom() +
 	theme(
 		legend.position = "top",
-		panel.background = element_rect(fill = "white", colour = NA),
-		strip.background = element_rect(colour = "grey"),
-		panel.border = element_rect(colour = "grey"),
-		panel.grid = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		axis.text.x = element_text(size = 7)
+		axis.text = element_text(size = 7)
 	)
@@
 
+##### By vocabulary size
+
+```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(vocab_size <= median(.$vocab_size, na.rm = TRUE), valid_participant) %>% 
+	count(age_group, lp)
+
+augment(fit) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(vocab_size <= median(.$vocab_size)) %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
+			  	colour = "black", fill = "black"), show.legend = FALSE) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Vocabulary size <= median") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(vocab_size > median(.$vocab_size, na.rm = TRUE), valid_participant) %>% 
+	count(age_group, lp)
+
+augment(fit) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(vocab_size > median(.$vocab_size)) %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
+			  	colour = "black", fill = "black"), show.legend = FALSE) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Vocabulary size > median") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+##### By location
+
+```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(location=="Barcelona", valid_participant) %>% 
+	count(age_group, lp)
+
+augment(fit) %>% 
+	left_join(distinct(participants, participant, location)) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(location=="Barcelona") %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
+			  	colour = "black", fill = "black"), show.legend = FALSE) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Barcelona") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(location=="Oxford") %>% 
+	count(age_group, lp)
+
+augment(fit) %>% 
+	left_join(distinct(participants, participant, location)) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(location=="Oxford") %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
+			  	colour = "black", fill = "black"), show.legend = FALSE) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Oxford") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+##### {-}
+
 #### {-}
 
-# Appendix
+# Appendix {.tabset .tab-pills}
 
@@
 
+## {-}
+
 # References

### 2021-05-28 Rmd/report.Rmd
Fix bug in line 583

@@
 ```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-y_pred <- logit_to_prob(predict(fit))
 sample_size <- participants %>% 
@@
 
-gaze %>% 
-	drop_na() %>% 
-	ggplot(aes(x = ot1, y = prop, colour = trial_type, fill = trial_type)) +
+augment(fit) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
 	facet_grid(lp~age_group) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(fun.data = mean_se, aes(y = y_pred), geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(fun = mean, aes(y = y_pred), geom = "line", size = 1) +
-	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	stat_summary(fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
 	geom_text(data = sample_size,

### 2021-05-31 Rmd/report.Rmd
Add sample sizes to plots

@@
 	filter(valid_participant) %>% 
-	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
+	ggplot() +
 	facet_wrap(location~age_group) +
-	geom_violin(position = position_dodge(width = 0.75)) + 
+	geom_violin(position = position_dodge(width = 0.75),
+				aes(lp, vocab_size, colour = lp, fill = lp)) + 
 	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
 	# 		   position = position_jitter(width = 0.1, seed = 888)) +
-	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
+	geom_boxplot(aes(lp, vocab_size, colour = lp, fill = lp),
+				 width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
 				 position = position_dodge(width = 0.75)) +
 	geom_text(data = sample_size,
-			  aes(x = 1.5, y = 0.95, label = paste0("n = ", n),
-			  	colour = "black", fill = "black"), show.legend = FALSE) +
+			  aes(x = 1, y = 0.95, label = paste0("n = ", n)),
+			  colour = "black", fill = "black", show.legend = FALSE) +
 	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
@@
 	drop_na() %>% 
-	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
+	ggplot() +
 	facet_grid(lp~age_group) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_violin(position = position_dodge(width = 0.75)) +
+	geom_violin(aes(trial_type, prop, colour = trial_type, fill = trial_type),
+				position = position_dodge(width = 0.75)) +
 	#stat_slab(position = position_nudge(x = 0.25)) +
 	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
-	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
-				 position = position_dodge(width = 0.75), colour = "black", fill = "white") +
+	geom_boxplot(aes(trial_type, prop, colour = trial_type, fill = trial_type,
+					 group = interaction(age_group, trial_type)),
+				 width = 0.1, outlier.colour = NA,
+				 position = position_dodge(width = 0.75),
+				 colour = "black", fill = "white") +
 	geom_text(data = sample_size,
-			  aes(x = 1, y = 0.95, label = paste0("n = ", n),
-			  	colour = "black", fill = "black"), show.legend = FALSE) +
+			  aes(x = 1, y = 0.95, label = paste0("n = ", n)),
+			  colour = "black", fill = "black", show.legend = FALSE) +
 	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
@@
 ```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-confint.merMod(fit, method = "Wald") %>% 
+main_effects <- confint.merMod(fit, method = "Wald") %>% 
 	as.data.frame() %>% 
@@
 	)
+gtsave(data = main_effects, filename = "main_effects.png", path = here("Figures"))
+main_effects
 ```
@@
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
+	ggplot() +
 	facet_grid(lp~age_group) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(fun = mean, geom = "line", size = 1) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
 	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
 	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
-			  	colour = "black", fill = "black"), show.legend = FALSE) +
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
 	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type") +
+		 colour = "Trial type", fill = "Trial type",
+		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
+Sample sizes are indicated at the upper left corner in each panel.
+The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
@@
 		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
+		axis.text = element_text(size = 7),
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	) +
+	ggsave(here("Figures", "emmeans.png"), height = 6)
 ```

### 2021-06-10 Rmd/report.Rmd
Add 21 mo monolinguals analysis

@@
 fit <- readRDS(here("Results", "fit.rds"))
+fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
 
@@
 
-# Results
-
-## Vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_wrap(location~age_group) +
-	geom_violin(position = position_dodge(width = 0.75),
-				aes(lp, vocab_size, colour = lp, fill = lp)) + 
-	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
-	# 		   position = position_jitter(width = 0.1, seed = 888)) +
-	geom_boxplot(aes(lp, vocab_size, colour = lp, fill = lp),
-				 width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
-				 position = position_dodge(width = 0.75)) +
-	geom_text(data = sample_size,
-			  aes(x = 1, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme(legend.title = element_blank(),
-		  legend.position = "none",
-		  axis.title.x = element_blank(),
-		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "vocabulary.png"))
-
-```
+# Results {.tabset .tab-pills}
 
@@
 	)
+
 gtsave(data = main_effects, filename = "main_effects.png", path = here("Figures"))
@@
 
-#### {-}
+#### 21 month-old monolinguals
 
-# Appendix {.tabset .tab-pills}
-
-## Appendix 1: Individual attrition rates
-
-```{r attrition_individual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-attrition %>%
-	left_join(select(participants, location, lp, participant, date_test)) %>% 
-	drop_na(trial_type) %>% 
-	group_by(participant, lp, location, date_test, age_group, trial_type, valid_participant, valid_other) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(names_from = trial_type, values_from = valid_trial_count) %>% 
+```{r fixef_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
+	as.data.frame() %>% 
 	clean_names() %>% 
-	mutate(
-		participant = str_remove(participant, "cognatepriming"),
-		cognate = paste0(cognate, " (", round(cognate/8, 2), "%)"),
-		non_cognate = paste0(non_cognate, " (", round(non_cognate/8, 2), "%)"),
-		unrelated = paste0(unrelated, " (", round(unrelated/8, 2), "%)"),
-	) %>% 
-	arrange(location, date_test) %>% 
-	relocate(
-		participant, location, date_test,
-		age_group, lp, cognate, non_cognate,
-		unrelated, valid_other, valid_participant) %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
 	gt() %>% 
-	tab_spanner(
-		"Valid trials (%) by trial type",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
 	cols_label(
-		participant = "Participant",
-		location = "Location",
-		date_test = "Date",
-		lp = "Group",
-		age_group = "Age",
-		valid_participant = "Valid trials",
-		valid_other = "Valid (other)?",
-		cognate = "Cognate",
-		non_cognate = "Non-cognate",
-		unrelated = "Unrelated"
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
 	) %>% 
@@
 		style = list(
-			cell_fill(color = "#00FA9A")
+			cell_fill(color = "#F9E3D6")
 		),
 		locations = cells_body(
-			columns = c("valid_participant"),
-			rows = valid_participant
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#00FA9A")
-		),
-		locations = cells_body(
-			columns = c("valid_other"),
-			rows = valid_other
+			columns = everything(),
+			rows = p_value < 0.05
 		)
 	)
+
+gtsave(data = main_effects, filename = "main_effects_21_mon.png", path = here("Figures"))
+main_effects
+
+```
+
+```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
+	count(age_group, lp)
+
+augment(fit_21_mon) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
+	plot_annotation(
+		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
+Sample sizes are indicated at the upper left corner in each panel.
+The first and last 300 ms in each trial\nwere trimmed before the analysis.
+B: mean observed probability of target looking, aggregated by participant.",
+		tag_levels = "A") &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	) &
+	ggsave(here("Figures", "emmeans_21_mon.png"))
+```
+
+#### {-}
+
+## Vocabulary
+
+This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
+Results are presented separately for each age group.
+The shape of the violins, represents the distribution of the vocabulary sizes.
+The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
+vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
+for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
+
+```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants %>% 
+	count(age_group, location)
+
+# vocabulary
+participants %>% 
+	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+	drop_na(lp) %>%
+	filter(valid_participant) %>% 
+	ggplot() +
+	facet_wrap(location~age_group) +
+	geom_violin(position = position_dodge(width = 0.75),
+				aes(lp, vocab_size, colour = lp, fill = lp)) + 
+	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
+	# 		   position = position_jitter(width = 0.1, seed = 888)) +
+	geom_boxplot(aes(lp, vocab_size, colour = lp, fill = lp),
+				 width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
+				 position = position_dodge(width = 0.75)) +
+	geom_text(data = sample_size,
+			  aes(x = 1, y = 0.95, label = paste0("n = ", n)),
+			  colour = "black", fill = "black", show.legend = FALSE) +
+	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	theme(legend.title = element_blank(),
+		  legend.position = "none",
+		  axis.title.x = element_blank(),
+		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
+	ggsave(here("Figures", "vocabulary.png"))
 
@@
 
+# Appendix {.tabset .tab-pills}
+
+## {-}
+
 # References

### 2021-06-14 Rmd/report.Rmd
Add more sanity checks.

@@
 options(knitr.kable.NA = '-',
-		ggplot2.discrete.fill = RColorBrewer::brewer.pal(6, name = "Dark2"),
-		ggplot2.discrete.colour = RColorBrewer::brewer.pal(6, name = "Dark2"),
-		ggplot2.continuous.fill = RColorBrewer::brewer.pal(6, name = "Dark2"),
-		ggplot2.continuous.colour = RColorBrewer::brewer.pal(6, name = "Dark2")
+		ggplot2.discrete.fill = ggthemes::colorblind_pal()(8),
+		ggplot2.discrete.colour = ggthemes::colorblind_pal()(8),
+		ggplot2.continuous.fill = ggthemes::colorblind_pal()(8),
+		ggplot2.continuous.colour = ggthemes::colorblind_pal()(8)
 )
@@
 fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
+fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
+fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
+fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))
 
@@
 	count(location, lp, age_group, trial_type, valid_status) %>% 
+	drop_na(trial_type) %>% 
 	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
@@
 		legend.title = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1),
 		axis.text.y = element_text(size = 8),
-		axis.title.y = element_blank()
+		axis.title = element_blank()
 	)
@@
 
-## Target fixations {.tabset .tab-pills}
+## Growth curve analysis {.tabset .tab-pills}
 
-### Aggregated by trial
-
-For each participant and trial, the proportion of fixations to the target object were calculated from the total of fixations to the target, the distractor, and the rest of the screen.
-Then proportions for the same participant were aggregated within conditions, so that for each participant three data points were obtained: one in each trial type (cognate, non-cognate, and unrelated).
-Some participants were longitudinal.
-Scores form longitudinal participant  are indicated by grey lines linking data points from the same participant.
-
-```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	count(age_group, lp)
-
-gaze %>% 
-	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
-	left_join(select(participants, participant, age_group, location)) %>% 
-	filter(valid_participant, valid_trial) %>% 
-	group_by(participant, lp, trial_type, age_group, location) %>% 
-	summarise(
-		prop = mean(prop, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na() %>% 
-	ggplot() +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	geom_violin(aes(trial_type, prop, colour = trial_type, fill = trial_type),
-				position = position_dodge(width = 0.75)) +
-	#stat_slab(position = position_nudge(x = 0.25)) +
-	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
-	geom_boxplot(aes(trial_type, prop, colour = trial_type, fill = trial_type,
-					 group = interaction(age_group, trial_type)),
-				 width = 0.1, outlier.colour = NA,
-				 position = position_dodge(width = 0.75),
-				 colour = "black", fill = "white") +
-	geom_text(data = sample_size,
-			  aes(x = 1, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme(legend.position = "none",
-		  axis.title.x = element_blank(),
-		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
-		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "gaze_trial_age.png"))
-
-```
-
-### Growth curve analysis {.tabset .tab-pills}
-
-#### Model details
+### Model details
 
@@
 
-#### Fixed effects
+### Fixed effects
 
@@
 
-gtsave(data = main_effects, filename = "main_effects.png", path = here("Figures"))
 main_effects
@@
 
-#### Random effects
+### Random effects
 
@@
 
-##### {-}
-
 #### {-}
 
-#### Marginal means {.tabset .tab-pills}
+### {-}
 
-##### Overall
+### Marginal means {.tabset .tab-pills}
+
+#### Overall
 
@@
 
-##### By vocabulary size
+#### By vocabulary size
 
@@
 sample_size <- participants %>% 
-	filter(vocab_size <= median(.$vocab_size, na.rm = TRUE), valid_participant) %>% 
+	filter(vocab_size_center <= median(.$vocab_size_center, na.rm = TRUE), valid_participant) %>% 
 	count(age_group, lp)
@@
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size <= median(.$vocab_size)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
+	filter(vocab_size_center <= median(.$vocab_size_center)) %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
 	facet_grid(lp~age_group) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
 	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
-			  	colour = "black", fill = "black"), show.legend = FALSE) +
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
 	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
@@
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size > median(.$vocab_size)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
+	filter(vocab_size_center > median(.$vocab_size_center)) %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
 	facet_grid(lp~age_group) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
 	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
-			  	colour = "black", fill = "black"), show.legend = FALSE) +
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
 	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
@@
 
-##### By location
+#### By location
 
@@
 	filter(location=="Barcelona") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
 	facet_grid(lp~age_group) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
 	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
-			  	colour = "black", fill = "black"), show.legend = FALSE) +
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
 	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
@@
 	filter(location=="Oxford") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
 	facet_grid(lp~age_group) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
 	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
-			  	colour = "black", fill = "black"), show.legend = FALSE) +
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
 	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
@@
 
-##### {-}
+#### {-}
 
-#### 21 month-old monolinguals
+### 21 month-old monolinguals {.tabset .tab-pills}
+
+#### All data
 
@@
 
-gtsave(data = main_effects, filename = "main_effects_21_mon.png", path = here("Figures"))
 main_effects
@@
 
+#### Location
+
+```{r fixef_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#F9E3D6")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+
+main_effects
+
+```
+
+```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
+	count(age_group, location)
+
+augment(fit_21_mon_location) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	facet_wrap(~location, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(
+		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  	colour = "black", fill = "black", show.legend = FALSE) +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon_location) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, location, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
+	facet_wrap(~location, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	) &
+	ggsave(here("Figures", "emmeans_21_mon_location.png"))
+```
+
+#### Vocabulary (median split)
+
+```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#F9E3D6")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+main_effects
+
+```
+
+```{r gaze_time_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+sample_size <- participants %>% 
+	drop_na(vocab_size_center) %>% 
+	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
+	mutate(vocab_cat = ifelse(vocab_size_center > median(participants$vocab_size_center, na.rm = TRUE), "Above median", "Below median")) %>% 
+	count(age_group, vocab_cat, lp)
+
+augment(fit_21_mon_vocab) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	facet_wrap(~vocab_cat, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+		geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon_vocab) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, vocab_cat, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob)) +
+	facet_wrap(~vocab_cat, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	) &
+	ggsave(here("Figures", "emmeans_21_mon_vocab.png"))
+```
+
+#### Vocabulary (balanced)
+
+```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#F9E3D6")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+main_effects
+
+```
+
+```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+# by vocab (balanced)
+sample_size <- participants %>%
+	drop_na(vocab_size) %>% 
+	filter(age_group=="21 months", lp=="Monolingual") %>% 
+	arrange(location, desc(vocab_size)) %>% 
+	group_by(location) %>% 
+	mutate(vocab_index = row_number()) %>% 
+	ungroup() %>% 
+	filter(
+		((location=="Barcelona") & (vocab_index %in% 1:15)) |
+			((location=="Oxford")) & (vocab_index %in% seq(
+				max(vocab_index[location=="Oxford"])-15,
+				max(vocab_index[location=="Oxford"])))
+	) %>% 
+	count(location)
+
+augment(fit_21_mon_vocab_pct) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	facet_wrap(~location, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(
+		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  	colour = "black", fill = "black", show.legend = FALSE) +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon_vocab_pct) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, location, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob)) +
+	facet_wrap(~location, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA) +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	) &
+	ggsave(here("Figures", "emmeans_21_mon_vocab_pct.png"))
+```
+
 #### {-}
+
+### {-}
 
@@
 
-# Appendix {.tabset .tab-pills}
-
-## {-}
+# Appendix
 

### 2021-06-14 R/stimuli.R

@@ -5,13 +5,17 @@
 # load packages
 library(tidyverse)
 library(readxl)
+library(multilex)
 library(here)
 
 # set parameters
 individual_plots <- FALSE
 
 # process stimuli
-stimuli <- read_xlsx(here("Stimuli", "stimuli.xlsx"))
+stimuli <- read_xlsx(here("Stimuli", "stimuli.xlsx")) %>% 
+	mutate(version) %>% 
+	left_join(select(multilex::pool, item, language, frequency_zipf),
+			  by = c("target_cdi" = "item", "test_language" = "language"))
 
 # export
 saveRDS(stimuli, here("Data", "Stimuli", "stimuli.rds"))

### 2021-06-29 Rmd/report.Rmd
Reorganise code, include job, add English lexical frequencies, embedd add in report, fix some item CDI labels.

@@
     toc: true
-    toc_depth: 4
+    toc_depth: 5
     toc_float: true
+runtime: shiny
 ---
@@
 options(knitr.kable.NA = '-',
-		ggplot2.discrete.fill = ggthemes::colorblind_pal()(8),
-		ggplot2.discrete.colour = ggthemes::colorblind_pal()(8),
-		ggplot2.continuous.fill = ggthemes::colorblind_pal()(8),
-		ggplot2.continuous.colour = ggthemes::colorblind_pal()(8)
+		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
+		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
 )
@@
 library(htmltools)
+library(shiny)
 library(here)
@@
 # load data
-gaze <- readRDS(here("Data", "Gaze", "processed.rds"))
-attrition <- readRDS(here("Results", "attrition.rds"))
+gaze <- readRDS(here("Data", "Gaze", "d.rds"))
+stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
+attrition <- readRDS(here("Results", "attrition.rds")) %>% 
+	mutate(
+		valid_gaze = valid_gaze_prime & valid_gaze_target,
+		valid_status = case_when(
+			!valid_vocab ~ "Invalid vocabulary",
+			!valid_gaze ~ "Invalid gaze",
+			!valid_participant ~ "Invalid participant",
+			TRUE ~ "Valid"
+		))
+vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
 participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
 	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant)
+	drop_na(participant) %>% 
+	left_join(vocab) %>% 
+	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
 fit <- readRDS(here("Results", "fit.rds"))
@@
 	geom_hline(yintercept = 24, linetype = "dashed") +
-	scale_colour_brewer(palette = "Set1") +
 	labs(x = "Group", y = "Sample size", fill = "Test language") +
@@
 		axis.title.x = element_blank(),
-		axis.text.x = element_text(size = 10),
+		axis.text = element_text(size = 10),
 		axis.title.y = element_text(angle = 90)
@@
 		valid_status = case_when(
-			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
+			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
+			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
 			!valid_participant ~ "Not valid"
@@
 		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
+		axis.text = element_text(size = 10),
 		axis.title.y = element_blank(),
@@
 
-### Attrition (overall)
+### {-}
+
+## Stimuli {.tabset .tab-pills}
+
+### Frequency {.tabset .tab-pills}
+
+#### Prime
+
+```{r stimuli_frequency_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	ggplot(aes(trial_type, frequency_prime, colour = trial_type, fill = trial_type)) +
+	facet_wrap(location~test_language) +
+	geom_violin() +
+	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
+	geom_jitter(colour = "black", size = 1, shape = 1,
+				width = 0.1, alpha = 0.5, stroke = 1) +
+	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
+		 colour = "Trial type", fill = "Trial type") +
+	theme(
+		legend.position = "none",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 9),
+		axis.title.x = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
+```
+
+#### Target
+
+```{r stimuli_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	ggplot(aes(trial_type, frequency_target, colour = trial_type, fill = trial_type)) +
+	facet_wrap(location~test_language) +
+	geom_violin() +
+	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
+	geom_jitter(colour = "black", size = 1, shape = 1,
+				width = 0.1, alpha = 0.5, stroke = 1) +
+	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
+		 colour = "Trial type", fill = "Trial type") +
+	theme(
+		legend.position = "none",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 9),
+		axis.title.x = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+```
+
+#### {-}
+
+### Familiarity {.tabset .tab-pills}
+
+#### Prime
+
+```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="100%"}
+means <- stimuli %>% 
+	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
+	filter(location=="Barcelona") %>% 
+	group_by(test_language, location, trial_type) %>% 
+	summarise(familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
+			  .groups = "drop") %>% 
+	drop_na()
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	drop_na() %>% 
+	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
+	facet_wrap(~test_language, scales = "free_y") +
+	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
+	geom_errorbar() +
+	geom_point() +
+	labs(x = "% of infants that understand", y = "Prime word",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_x_continuous(labels = scales::percent) +
+	theme_custom() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 10),
+		axis.title.y = element_blank(),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
+```
+
+#### Target
+
+```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
+means <- stimuli %>% 
+	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
+	filter(location=="Barcelona") %>% 
+	group_by(test_language, location, trial_type) %>% 
+	summarise(familiarity_target = mean(familiarity_target, na.rm = TRUE),
+			  .groups = "drop") %>% 
+	drop_na()
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	drop_na() %>% 
+	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
+	facet_wrap(~test_language, scales = "free_y") +
+	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
+	geom_errorbar() +
+	geom_point() +
+	labs(x = "% of infants that understand", y = "Target word",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_x_continuous(labels = scales::percent) +
+	theme_custom() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 10),
+		axis.title.y = element_blank(),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
+```
+
+#### {-}
+
+### Animacy
+
+```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
+
+animacy <- stimuli %>%
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
+	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
+	count(location, test_language, trial_type, role, is_animate) %>% 
+	drop_na(is_animate) %>% 
+	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
+
+animacy %>% 
+	filter(role=="Prime") %>% 
+	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
+	facet_wrap(role~location~test_language, ncol = 4) +
+	geom_col(position = position_fill(), colour = "white") +
+	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() + 
+	theme(
+		axis.title.x = element_blank()
+	) +
+
+	animacy %>% 
+	filter(role=="Target") %>% 
+	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
+	facet_wrap(role~location~test_language, ncol = 4) +
+	geom_col(position = position_fill(), colour = "white") +
+	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() +
+
+	plot_layout(guides = "collect", ncol = 1) &
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 10),
+		strip.text = element_text(size = 11)
+	)
+
+```
+
+### Semantic category
+
+```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
+	mutate(role = str_to_sentence(str_remove(role, "_category"))) %>% 
+	drop_na() %>% 
+	count(trial_type, test_language, location, role, category) %>% 
+	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
+	facet_grid(role~location~test_language) +
+	geom_col(position = position_fill()) +
+	labs(x = "% of trials", y = "Trial type",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_fill_manual(values = wesanderson::wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
+	scale_colour_manual(values = wesanderson::wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
+	scale_x_continuous(labels = scales::percent) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 9),
+		axis.title.y = element_blank(),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
+```
+
+### {-}
+
+## Procedure
+
+## Data analysis
+
+### Vocabulary data
+
+We collected vocabulary data from participants.
+In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
+In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
+In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
+In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
+All checklists included the words involved in the trial lists.
+When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
+Each response to either checklist was aggregated to produce several vocabulary measures:
+
+* **Total vocabulary**: total number of words the child knows, summing up both languages.
+For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
+* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
+For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
+* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
+For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
+
+Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
+
+## Gaze data {.tabset .tabset-pills}
+
+Each trial was divided into 100 ms time bins.
+for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
+Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
+
+### Workflow
+
+```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+DiagrammeR::grViz("digraph {
+  graph [layout = dot, rankdir = TB]
+
+  node [shape = rectangle, fontname = 'Arial']        
+  rec1 [label = 'Merge Barcelona and Oxford data']
+  rec2 [label = 'Impute missing/invalid samples (pending)']
+  rec2 [label = 'Extract fixations (pending)']
+  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
+  rec4 [label = 'Divide each trial into 100 ms time bins']
+  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
+  rec6 [label = 'Exclude time bins 1-3 (pending)']
+  rec7 [label = 'Apply trial-level inclusion criteria']
+  rec8 [label = 'Apply participant-level inclusion criteria']
+
+  # edge definitions with the node IDs
+  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
+  }", 
+  height = 500)
+```
+
+### Trial-level inclusion criteria
+
+* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
+* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
+* At least one sample in target and one sample in distractor
+* Participant understands prime word in both languages
+* Participant knows the target word in the test language
+* Participant knows the distractor word in the test language
+
+### Participant-level inclusion criteria
+
+* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
+* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
+* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
+* $\geq$ 36 gestational weeks
+* $\geq$ 2,800g birth weight
+* No diagnosed developmental, hearing, or visual disorders
+* Not exposed to more than 10% to a 3rd language
+
+### {-}
+
+## {-}
+
+# Results {.tabset .tab-pills}
+
+## Raw data
+
+```{r, echo = FALSE}
+shinyAppFile(
+	here("R", "gaze_app", "app.R"), 
+	options = list(width = "100%", height = 700)
+)
+```
+
+## Growth curve analysis {.tabset .tab-pills}
+
+### Model details
+
+We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
+
+```
+elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
+(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
+```
+
+The formal implementation of this model is:
+
+$$
+\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
+(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
+(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
+(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
+(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
+(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
+(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
+(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
+(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
+$$
+
+### Fixed effects
+
+```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#ffc7a1")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+
+main_effects
+```
+
+### Random effects
+
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+VarCorr(fit)$participant %>% 
+	cov2cor() %>% 
+	as.data.frame() %>% 
+	rownames_to_column("term1") %>% 
+	gt(rowname_col = "term1") %>% 
+	fmt_number(columns = 2:9) %>% 
+	data_color(
+		columns = 2:9,
+		colors = scales::col_numeric(
+			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
+			domain = c(-1, 1), alpha = 0.5
+		)
+	)
+
+```
+
+### Marginal means {.tabset .tab-pills}
+
+#### Overall
+
+```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant) %>% 
+	count(age_group, lp)
+
+augment(fit) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
+Sample sizes are indicated at the upper left corner in each panel.
+The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme_custom() +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7),
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	) +
+	ggsave(here("Figures", "emmeans.png"), height = 6)
+```
+
+#### By vocabulary size
+
+```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	count(age_group, lp)
+
+augment(fit) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Vocabulary size <= median") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
+	count(age_group, lp)
+
+augment(fit) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Vocabulary size > median") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+#### By location
+
+```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(location=="Barcelona", valid_participant) %>% 
+	count(age_group, lp)
+
+augment(fit) %>% 
+	left_join(distinct(participants, participant, location)) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(location=="Barcelona") %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Barcelona") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(location=="Oxford") %>% 
+	count(age_group, lp)
+
+augment(fit) %>% 
+	left_join(distinct(participants, participant, location)) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(location=="Oxford") %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Oxford") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+#### {-}
+
+### {-}
+
+## Attrition {.tabset .tab-pills}
+
+### Summary
 
@@
 	left_join(distinct(attrition, participant, valid_participant)) %>%
+	left_join(vocab) %>% 
 	drop_na(valid_participant) %>% 
@@
 
-### Attrition (by group)
+### By group
 
@@
 left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant, valid_other) %>% 
+	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
 	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
@@
 
-### Attrition (by participant)
+### By participant
 
@@
 		invalid_gaze = mean(!valid_gaze),
-		invalid_other = mean(!valid_other),
 		invalid_vocab = mean(!valid_vocab),
@@
 	relocate(participant) %>% 
-	relocate(invalid_other, .after = invalid_vocab) %>% 
 	gt() %>% 
@@
 		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)",
-		invalid_other = "Other (%)"
+		invalid_vocab = "Vocabulary (%)"
 	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab", "invalid_other")) %>% 
+	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
 	div(style='height:600px; overflow-y: scroll', .)
@@
 
-### Attrition (by trials)
+### By trial
 
@@
 	left_join(select(participants, participant, location)) %>% 
-	mutate(valid_status = case_when(
-		!valid_vocab ~ "Invalid vocabulary",
-		!valid_gaze ~ "Invalid gaze",
-		!valid_other ~ "Other",
-		!valid_participant ~ "Invalid participant",
-		TRUE ~ "Valid"
-	)) %>% 
 	count(location, lp, age_group, trial_type, valid_status) %>% 
@@
 		legend.title = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
 		axis.text.y = element_text(size = 8),
@@
 
+### By lexical frequency {.tabset .tab-pills}
+
+#### Prime frequency
+
+```{r attirion_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime)) %>% 
+	drop_na(trial_type, frequency_prime) %>% 
+	mutate(frequency_prime = round(frequency_prime)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, frequency_prime) %>% 
+	ggplot(aes(as.factor(frequency_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+#### Target frequency
+
+```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target)) %>% 
+	drop_na(trial_type, frequency_target) %>% 
+	mutate(frequency_target = round(frequency_target)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, frequency_target) %>% 
+	ggplot(aes(as.factor(frequency_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+#### {-}
+
+### By familiarity {.tabset .tab-pills}
+
+#### Prime familiarity
+
+```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
+	drop_na(trial_type, familiarity_prime) %>% 
+	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
+	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+#### Target familiarity
+
+```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
+	drop_na(trial_type, familiarity_target) %>% 
+	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
+	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+#### {-}
+
+### By animacy {.tabset .tab-pills}
+
+#### Prime
+
+```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
+	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
+	drop_na(trial_type, is_animate_prime) %>% 
+	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
+	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+
+```
+
+#### Target
+
+```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
+	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
+	drop_na(trial_type, is_animate_target) %>% 
+	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
+	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+
+```
+
+#### {-}
+
+### By category {.tabset .tab-pills}
+
+#### Prime
+
+```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
+	drop_na(trial_type, category_prime) %>% 
+	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
+	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+#### Target
+
+```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
+	drop_na(trial_type, category_target) %>% 
+	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
+	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
 ### {-}
 
-## Materials
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### {-}
-
-# Results {.tabset .tab-pills}
-
-## Growth curve analysis {.tabset .tab-pills}
-
-### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-$$
-\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i})\times Condition_{pi} + ... \\
-(\beta_{2} + \beta_{2i}) \times Group_{pi} + ... \\
-(\beta_{3} + \beta_{3i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{4} + \beta_{4p}) \times Vocabulary_{p} + \varepsilon_{pi}
-$$
-
-### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#F9E3D6")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-```
-
-### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-VarCorr(fit)$participant %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = "value") %>% 
-	ggplot(aes(term1, term2, fill = value)) +
-	geom_tile() +
-	coord_fixed() +
-	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
-	scale_fill_viridis_c() +
-	theme(
-		axis.title = element_blank(),
-		axis.text.x = element_text(angle = 90)
-	)
-
-```
-
-#### {-}
-
-### {-}
-
-### Marginal means {.tabset .tab-pills}
-
-#### Overall
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7),
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	) +
-	ggsave(here("Figures", "emmeans.png"), height = 6)
-```
-
-#### By vocabulary size
-
-```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(vocab_size_center <= median(.$vocab_size_center, na.rm = TRUE), valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_center <= median(.$vocab_size_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size <= median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(vocab_size > median(.$vocab_size, na.rm = TRUE), valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_center > median(.$vocab_size_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size > median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### By location
-
-```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Barcelona", valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Barcelona") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Oxford") %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Oxford") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### {-}
-
-### 21 month-old monolinguals {.tabset .tab-pills}
-
-#### All data
+## 21 month-old monolinguals {.tabset .tab-pills}
+
+### All data
 
@@
 		style = list(
-			cell_fill(color = "#F9E3D6")
+			cell_fill(color = "#ffc7a1")
 		),
@@
 
-#### Location
+### Location
 
@@
 
-#### Vocabulary (median split)
+### Vocabulary (median split)
 
@@
 sample_size <- participants %>% 
-	drop_na(vocab_size_center) %>% 
+	drop_na(vocab_size_l1_center) %>% 
 	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	mutate(vocab_cat = ifelse(vocab_size_center > median(participants$vocab_size_center, na.rm = TRUE), "Above median", "Below median")) %>% 
+	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
 	count(age_group, vocab_cat, lp)
@@
 
-#### Vocabulary (balanced)
+### Vocabulary (balanced)
 
@@
 sample_size <- participants %>%
-	drop_na(vocab_size) %>% 
+	drop_na(vocab_size_l1_center) %>% 
 	filter(age_group=="21 months", lp=="Monolingual") %>% 
-	arrange(location, desc(vocab_size)) %>% 
+	arrange(location, desc(vocab_size_l1_center)) %>% 
 	group_by(location) %>% 
@@
 	) %>% 
-	count(location)
+	nrow() %>% 
+	data.frame(n = .)
 
@@
 	ggplot() +
-	facet_wrap(~location, ncol = 1) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
@@
 	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, location, trial_type) %>% 
+	group_by(participant, trial_type) %>% 
 	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
 	ggplot(aes(trial_type, elog_prob)) +
-	facet_wrap(~location, ncol = 1) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
@@
 	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
 	theme_custom() &
@@
 
-#### {-}
-
 ### {-}
 
-## Vocabulary
+## Vocabulary {.tabset .tab-pills}
+
+### L1 vocabulary
 
@@
 
-```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
 sample_size <- participants %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
 	count(age_group, location)
@@
 	ggplot() +
-	facet_wrap(location~age_group) +
-	geom_violin(position = position_dodge(width = 0.75),
-				aes(lp, vocab_size, colour = lp, fill = lp)) + 
-	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
-	# 		   position = position_jitter(width = 0.1, seed = 888)) +
-	geom_boxplot(aes(lp, vocab_size, colour = lp, fill = lp),
-				 width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
-				 position = position_dodge(width = 0.75)) +
-	geom_text(data = sample_size,
-			  aes(x = 1, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
+	facet_grid(location~age_group) +
+	# geom_violin(
+	# 	position = position_dodge(width = 0.75),
+	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
+	# ) + 
+	geom_hline(yintercept = 0.5, colour = "grey") +
+	geom_point(
+		aes(lp, vocab_size_l1),
+		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
+		position = position_jitter(width = 0.1, seed = 888)
+	) +
+	geom_boxplot(
+		aes(lp, vocab_size_l1, colour = lp, fill = lp),
+		width = 0.25, colour = "black", outlier.colour = NA,
+		position = position_dodge(width = 0.75)
+	) +
+	geom_text(
+		data = sample_size,
+		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
+		colour = "black", fill = "black", show.legend = FALSE
+	) +
+	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
 	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
-	theme(legend.title = element_blank(),
+	theme(
+		legend.title = element_blank(),
 		legend.position = "none",
 		axis.title.x = element_blank(),
-		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
-	ggsave(here("Figures", "vocabulary.png"))
-
-```
+		axis.text = element_text(size = 9),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	) +
+	ggsave(here("Figures", "vocabulary_l1.png"))
+
+```
+
+### Total vocabulary
+
+```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	count(age_group, location)
+
+# vocabulary
+participants %>% 
+	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+	drop_na(lp) %>%
+	filter(valid_participant) %>% 
+	ggplot() +
+	facet_grid(location~age_group) +
+	# geom_violin(
+	# 	position = position_dodge(width = 0.75),
+	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
+	# ) + 
+	geom_hline(yintercept = 0.5, colour = "grey") +
+	geom_point(
+		aes(lp, vocab_size_total),
+		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
+		position = position_jitter(width = 0.1, seed = 888)
+	) +
+	geom_boxplot(
+		aes(lp, vocab_size_total, colour = lp, fill = lp),
+		width = 0.25, colour = "black", outlier.colour = NA,
+		position = position_dodge(width = 0.75)
+	) +
+	geom_text(
+		data = sample_size,
+		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
+		colour = "black", fill = "black", show.legend = FALSE
+	) +
+	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	theme(
+		legend.title = element_blank(),
+		legend.position = "none",
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 9),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	) +
+	ggsave(here("Figures", "vocabulary_total.png"))
+
+```
+
+### Conceptual vocabulary
+
+```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	count(age_group, location)
+
+# vocabulary
+participants %>% 
+	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+	drop_na(lp) %>%
+	filter(valid_participant) %>% 
+	ggplot() +
+	facet_grid(location~age_group) +
+	# geom_violin(
+	# 	position = position_dodge(width = 0.75),
+	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
+	# ) + 
+	geom_hline(yintercept = 0.5, colour = "grey") +
+	geom_point(
+		aes(lp, vocab_size_conceptual),
+		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
+		position = position_jitter(width = 0.1, seed = 888)
+	) +
+	geom_boxplot(
+		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
+		width = 0.25, colour = "black", outlier.colour = NA,
+		position = position_dodge(width = 0.75)
+	) +
+	geom_text(
+		data = sample_size,
+		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
+		colour = "black", fill = "black", show.legend = FALSE
+	) +
+	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
+	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	theme(
+		legend.title = element_blank(),
+		legend.position = "none",
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 9),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	) +
+	ggsave(here("Figures", "vocabulary_conceptual.png"))
+
+```
+
+### {-}
 
@@
 
+# {-}
+
 # Appendix

### 2021-06-29 R/00_stimuli.R

@@ -1,0 +1,114 @@
+# stimuli
+
+# set up ----
+
+# load packages
+library(tidyverse)
+library(readxl)
+library(multilex)
+library(janitor)
+library(here)
+
+# set params
+ml_connect("gonzalo.garciadecastro@upf.edu")
+
+# import data ----
+trials <- read_xlsx(here("Stimuli", "stimuli.xlsx"))
+
+# semantic category ----
+pool <- select(multilex::pool, item, language, category) %>%
+	rename(test_language = language)
+
+# animacy ----
+animacy <- read.csv(here("Data", "Stimuli", "animacy.csv")) %>% 
+	as_tibble() %>% 
+	mutate(is_animate = as.logical(is_animate))
+
+# lexical frequency norms ----
+# UK SUBTLEX: http://crr.ugent.be/papers/SUBTLEX-UK.xlsx
+subtlex_eng <- read_xlsx(here("Data", "Stimuli", "SUBTLEX-UK.xlsx")) %>% 
+	clean_names() %>% 
+	rename(word = spelling, frequency = log_freq_zipf) %>% 
+	select(word, frequency)
+
+# Catalan SUBTLEX: https://psico.fcep.urv.cat/projectes/gip/papers/SUBTLEX-CAT.xlsx
+subtlex_cat <- read_xlsx(here("Data", "Stimuli", "SUBTLEX-CAT.xlsx")) %>% 
+	clean_names() %>% 
+	rename(word = words, frequency = zipf) %>% 
+	select(word, frequency)
+
+# Spanish SUBTLEX: http://crr.ugent.be/papers/SUBTLEX-ESP.zip
+subtlex_spa <- read_xlsx(here("Data", "Stimuli", "SUBTLEX-ESP.xlsx"), .name_repair = "minimal") %>% 
+	clean_names() %>% 
+	select(-starts_with("x"))
+subtlex_spa <- tibble(
+	word = unlist(subtlex_spa[, c(1, 5, 9)]),
+	freq_count = unlist(subtlex_spa[, c(2, 6, 10)]),
+	freq_per_million = unlist(subtlex_spa[, c(3, 7, 11)]),
+	log_freq = unlist(subtlex_spa[, c(4, 8, 12)])
+) %>% 
+	mutate(frequency = log10(freq_per_million)+3) %>% 
+	select(word, frequency)
+
+# merge
+subtlex <- bind_rows(
[…]

### 2021-06-29 R/02_vocabulary.R

@@ -1,0 +1,185 @@
+# vocabulary size
+
+# set up ----
+
+# load packages
+library(tidyverse)
+library(mice) # for multiple imputation
+library(multilex) # for extracting Barcelona vocabulary data
+library(readxl) # for importing Excel spradsheets
+library(here) # for reproducible file paths
+
+# set params
+ml_connect("gonzalo.garciadecastro@upf.edu") # log into MultiLex
+cdi_replacements <- c("boots" = "boot", "boot(s)" = "boot", "fire engine" = "fireengine",
+					  "teddy bear" = "teddy", "bunny / rabbit" = "bunny",
+					  "lorry / truck" = "truck", "bicycle / bike" = "bike")
+
+participants <- readRDS(here("Data", "Participants", "participants.rds"))
+
+# Barcelona vocabulary ----
+p <- ml_participants()
+r <- ml_responses(p, update = FALSE)
+l <- ml_logs(p, r) %>% 
+	rename(participant = id_exp) %>% 
+	mutate(
+		age_group =  as.factor(
+			case_when(
+				between(age, 19, 24) ~ 21,
+				between(age, 24, 28) ~ 25,
+				between(age, 28, 34) ~ 30
+			)),
+		age_group = paste0(age_group, " months")
+	) %>% 
+	filter(age_group != "NA months") %>% 
+	select(participant, time, age_group, lp)
+v <- ml_vocabulary(p, r, scale = "prop", by = "id_exp") %>% 
+	filter(type=="understands")
+
+# norms (by item)
+vocab_items_barcelona <- r %>% 
+	rename(participant = id_exp) %>% 
+	mutate(
+		understands = response > 1,
+		age_group =  as.factor(
+			case_when(
+				between(age, 19, 24) ~ 21,
+				between(age, 24, 28) ~ 25,
+				between(age, 28, 34) ~ 30
+			)),
+		age_group = paste0(age_group, " months")
+	) %>%
+	filter(study=="CognatePriming", age_group != "NA months", understands) %>%
+	select(participant, time, age_group, item, response) %>%
+	group_by(participant, age_group) %>%
+	summarise(vocab_words = list(unique(item)), .groups = "drop")
+
+# norms (by participant)
+vocab_size_barcelona <- v %>%
+	rename(participant = id_exp) %>% 
[…]

### 2021-06-29 R/04_attrition.R

@@ -1,0 +1,112 @@
+# attrition
+
+# set up ----
+
+# load packages
+library(tidyverse)
+library(janitor) # for cleaning column names
+library(here) # for locating files
+
+# set params
+looking_threshold <- c(prime = 500, target = 500) # minimum looking time
+missing_trials_threshold <- c(cognate = 2, noncognate = 2, unrelated = 2) # minimum n trials in each condition
+
+# import data ----
+participants <- readRDS(here("Data", "Participants", "participants.rds"))
+vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
+gaze <- list(
+	Barcelona = readRDS(here("Data", "Gaze", "processed_barcelona.rds")),
+	Oxford = readRDS(here("Data", "Gaze", "processed_oxford.rds"))
+) %>% 
+	bind_rows(.id = "location") %>% 
+	# to avoid issues with column names
+	rename(time_stamp = time)
+
+processed <- reduce(list(participants, vocab, gaze), left_join)
+
+
+# evaluate inclusion criteria ----
+# valid gaze
+valid_gaze <- processed %>% 
+	group_by(participant, age_group, trial_type, trial) %>% 
+	summarise(
+		# proportion of prime looking time during prime phase
+		valid_looking_prime = sum(aoi_prime[phase=="Prime"], na.rm = TRUE)*(1000/120),
+		# proportion of target looking time during target-distractor phase
+		valid_looking_target = sum(aoi_target[phase=="Target-Distractor"], na.rm = TRUE)*(1000/120), 
+		.groups = "drop"
+	) %>% 
+	mutate(
+		# prime looking proportion during prime phase is higher or equal than minimum
+		valid_gaze_prime = valid_looking_prime >= looking_threshold["prime"],
+		# participant has looked at least once to target AND distractor and higher or equal than minimum to both
+		valid_gaze_target = valid_looking_target>0 &
+			(valid_looking_target >= looking_threshold["target"]),
+		# trial meets all gaze criteria
+		valid_gaze = valid_gaze_prime & valid_gaze_target 
+	)
+
+# evaluate vocabulary
+valid_vocabulary <- processed %>%
+	distinct(participant, age_group, trial, prime, target, vocab_words) %>% 
+	rowwise() %>% 
+	# evaluate if word in in participant's vocabulary or is understood by 50% or more of 19-22 aged children
+	mutate(
+		valid_vocab_prime = prime %in% vocab_words,
[…]

### 2021-06-29 R/gaze_oxford.R

@@ -1,169 +1,0 @@
-# process Oxford gaze data
-
-# set up ----
-library(tidyverse)
-library(janitor) # for cleaning colnames
-library(lubridate) # for dealing with dates
-library(readxl) # for importing Excel files
-library(data.table) # for importing CSV files
-library(here) # for locating files
-
-# set params
-screen_resolution <- c(x = 1920, y = 1080)
-center_coords <- c(xmin = 710, xmax = 1210, ymin = 290, ymax = 790)
-left_coords <- c(xmin = 180, xmax = 680, ymin = 290, ymax = 790)
-right_coords <- c(xmin = 1240, xmax = 1640, ymin = 290, ymax = 790)
-looking_threshold <- c(prime = 500, target = 500) # minimum looking time
-missing_trials_threshold <- c(cognate = 2, noncognate = 2, unrelated = 2) # minimum n trials in each condition
-
-# import participant data
-participants <- readRDS(here("Data", "Participants", "participants.rds"))
-
-# import gaze data ----
-raw <- list.files(here("Data", "Gaze", "Oxford"), full.names = TRUE) %>% 
-	# import and merge all files
-	map(fread, na = c("", "NA")) %>% 
-	bind_rows() %>% 
-	as_tibble() %>%
-	clean_names() %>% # colnames to snake case
-  mutate(trial = ifelse(block == 2, trial+16, trial)) %>% # because of block format, trial number for 17th trial is recorded as block 2 trial 1
-  rename(
-		id_db = id, trial_num = trial, time = timestamp,
-		l_x = gaze_raw_left_x, l_y = gaze_raw_left_y,
-		r_x = gaze_raw_right_x, r_y = gaze_raw_right_y,
-		l_v = gaze_left_validity, r_v = gaze_right_validity,
-		target_location = vis_target_stm_pos,
-		prime_unrelated = vis_un_stm, prime_cognate = vis_cp_stm, prime_noncognate = vis_np_stm,
-		target = vis_target_stm, distractor = vis_distr_stm
-	) %>%
-	mutate_at(vars(matches("_v")), as.logical) %>%
-	mutate(
-		id_db = as.character(id_db),
-		trial_type = case_when(
-			!is.na(prime_unrelated) ~ "Unrelated",
-			!is.na(prime_cognate) ~ "Cognate",
-			!is.na(prime_noncognate) ~ "Non-cognate"
-		),
-		phase = case_when(
[…]

### 2021-07-05 Rmd/report.Rmd
Add contrasts

@@
 
-### Trial-level inclusion criteria
+### Inclusion criteria
+
+#### Trial-level inclusion criteria
 
@@
 
-### Participant-level inclusion criteria
+#### Participant-level inclusion criteria
 
@@
 * Not exposed to more than 10% to a 3rd language
+
+### Input variables
+
+* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
+* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
+* Trial type (`trial_type1` and `trial_type2`).
+Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
+We coded two contrasts: `trial_type1`, comparing related trials vs.
+unrelated trials (*Cognate* + *Non-cognate* vs.
+*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
+*Non-cognate* trials.
+These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
+
+```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+contrasts(gaze$trial_type) %>% 
+  as.data.frame() %>% 
+  set_names(paste0("trial_type", 1:2)) %>% 
+  rownames_to_column("level") %>% 
+  gt(rowname_col = "level")
+
+```
 

### 2021-07-05 Rmd/report.Rmd
Better comments, compare CHILDES vs. SUBTLEX frequencies.

@@
 library(tidyverse)
-library(bilingualr)
 library(lubridate)
@@
 library(htmltools)
+library(wesanderson)
 library(shiny)
@@
 		axis.title.y = element_text(angle = 90)
-	) +
-	ggsave(here("Figures", "sample.png"))
-
+	) 
 ```
@@
 		axis.ticks.y = element_blank()
-	) +
-	ggsave(here("Figures", "cohort.png"))
+	)
 ```
@@
 
-#### Prime
-
-```{r stimuli_frequency_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
+#### CHILDES vs. SUBTLEX
+
+```{r frequencies_compare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+frequency_compare_data <- bind_rows(
+	stimuli %>%
+		distinct(test_language, prime, .keep_all = TRUE) %>%
+		select(prime, test_language, matches("frequency_prime")) %>% 
+		rename(word = prime, frequency_subtlex = frequency_prime_subtlex,
+			   frequency_childes = frequency_prime_childes),
+	stimuli %>%
+		distinct(test_language, target, .keep_all = TRUE) %>%
+		select(target, test_language, matches("frequency_target")) %>% 
+		rename(word = target, frequency_subtlex = frequency_target_subtlex,
+			   frequency_childes = frequency_target_childes),
+) %>% 
+	group_by(test_language) %>% 
+	mutate_at(vars(starts_with("frequency")), function(x) scale(x)[,1])
+
+frequency_compare_test <- group_split(frequency_compare_data) %>% 
+	set_names(c("Catalan", "English", "Spanish")) %>% 
+	map(function(x) {
+		a <- pull(x, frequency_subtlex)
+		b <- pull(x, frequency_childes)
+		tidy(cor.test(a, b), use = "complete.obs")
+	}) %>% 
+	bind_rows(.id = "test_language") %>% 
+	clean_names()
+
+```
+
+We tested the correlation between the (standardised) lexical frequencies of the stimuli extract from SUBTLEX (adult norms based on subtitles) and CHILDES (child norms based on audio transcriptions) within each test language using a Pearson's product-moment correlation at .05 confidence level (two-sided):
+
+```{r stimuli_frequency_compare_test, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+frequency_compare_test %>% 
+	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
+	mutate(p_value = printp(p_value)) %>% 
+	gt(rowname_col = "test_language") %>% 
+	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
+	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
+	cols_label(
+		estimate = md("**Correlation**"),
+		statistic = md("***t***"),
+		parameter = md("***df***"),
+		p_value = md("***p***"),
+		conf_low = md("**CI<sub>95%<sub/>**")
+	)
+
+```
+
+```{r stimuli_frequency_compare_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
+
+frequency_compare_data %>% 
+	ggplot(aes(frequency_subtlex, frequency_childes, colour = test_language, fill = test_language)) +
+	facet_wrap(~test_language) +
+	geom_point(alpha = 0.5, stroke = 1, shape = 1) +
+	geom_smooth(method = "lm") +
+	labs(x = "SUBTLEX (adult norms)", y = "CHILDES (child norms)",
+		 colour = "Language", fill = "Language") +
+	coord_fixed() +
+	theme(
+		legend.position = "none",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 9),
+		axis.title.x = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
+```
+
+#### CHILDES {.tabset .tab-pills}
+
+##### Prime
+
+```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
 
@@
 	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime, colour = trial_type, fill = trial_type)) +
+	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
 	facet_wrap(location~test_language) +
@@
 
-#### Target
-
-```{r stimuli_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
+##### Target
+
+```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
 
@@
 	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target, colour = trial_type, fill = trial_type)) +
+	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
 	facet_wrap(location~test_language) +
@@
 ```
+
+##### {-}
+
+#### SUBTLEX {.tabset .tab-pills}
+
+##### Prime
+
+```{r stimuli_frequency_subtlex_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
+	facet_wrap(location~test_language) +
+	geom_violin() +
+	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
+	geom_jitter(colour = "black", size = 1, shape = 1,
+				width = 0.1, alpha = 0.5, stroke = 1) +
+	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
+		 colour = "Trial type", fill = "Trial type") +
+	theme(
+		legend.position = "none",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 9),
+		axis.title.x = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
+```
+
+##### Target
+
+```{r stimuli_frequency_subtlex_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
+	facet_wrap(location~test_language) +
+	geom_violin() +
+	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
+	geom_jitter(colour = "black", size = 1, shape = 1,
+				width = 0.1, alpha = 0.5, stroke = 1) +
+	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
+		 colour = "Trial type", fill = "Trial type") +
+	theme(
+		legend.position = "none",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 9),
+		axis.title.x = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+```
+
+##### {-}
 
@@
 		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = scales::percent) +
+	scale_x_continuous(labels = percent) +
 	theme_custom() +
@@
 	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = scales::percent) +
+	scale_y_continuous(labels = percent) +
 	coord_flip() + 
@@
 	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = scales::percent) +
+	scale_y_continuous(labels = percent) +
 	coord_flip() +
@@
 		 colour = "Trial type", fill = "Trial type") +
-	scale_fill_manual(values = wesanderson::wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_colour_manual(values = wesanderson::wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_x_continuous(labels = scales::percent) +
+	scale_fill_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
+	scale_colour_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
+	scale_x_continuous(labels = percent) +
 	theme(
@@
 		columns = 2:9,
-		colors = scales::col_numeric(
+		colors = col_numeric(
 			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
@@
 The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
 	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
@@
 		plot.caption.position = "plot"
-	) +
-	ggsave(here("Figures", "emmeans.png"), height = 6)
+	) 
 ```
@@
 		axis.title.y = element_text(angle = 90)
-	) +
-	ggsave(here("Figures", "participants_attrition.png"))
+	) 
 ```
@@
 	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = scales::percent) +
+	scale_y_continuous(labels = percent) +
 	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
@@
 attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime)) %>% 
-	drop_na(trial_type, frequency_prime) %>% 
-	mutate(frequency_prime = round(frequency_prime)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_prime) %>% 
-	ggplot(aes(as.factor(frequency_prime), n, fill = valid_status, colour = valid_status)) +
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
+	drop_na(trial_type, frequency_prime_childes) %>% 
+	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
+	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
 	facet_grid(trial_type~age_group) +
@@
 	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = scales::percent) +
+	scale_y_continuous(labels = percent) +
 	coord_flip() +
@@
 attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target)) %>% 
-	drop_na(trial_type, frequency_target) %>% 
-	mutate(frequency_target = round(frequency_target)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target) %>% 
-	ggplot(aes(as.factor(frequency_target), n, fill = valid_status, colour = valid_status)) +
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
+	drop_na(trial_type, frequency_target_childes) %>% 
+	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
+	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
 	facet_grid(trial_type~age_group) +
@@
 	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = scales::percent) +
+	scale_y_continuous(labels = percent) +
 	coord_flip() +
@@
 		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
 	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
@@
 		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
 	theme(
@@
 		plot.caption.position = "plot"
-	) &
-	ggsave(here("Figures", "emmeans_21_mon.png"))
+	)
 ```
@@
 		plot.caption.position = "plot"
-	) &
-	ggsave(here("Figures", "emmeans_21_mon_location.png"))
+	)
 ```
@@
 		plot.caption.position = "plot"
-	) &
-	ggsave(here("Figures", "emmeans_21_mon_vocab.png"))
+	)
 ```
@@
 		plot.caption.position = "plot"
-	) &
-	ggsave(here("Figures", "emmeans_21_mon_vocab_pct.png"))
+	)
 ```
@@
 	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_y_continuous(limits = c(0, 1), labels = percent) +
 	theme(
@@
 		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	) +
-	ggsave(here("Figures", "vocabulary_l1.png"))
+	)
 
@@
 	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_y_continuous(limits = c(0, 1), labels = percent) +
 	theme(
@@
 		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	) +
-	ggsave(here("Figures", "vocabulary_total.png"))
+	)
 
@@
 	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
+	scale_y_continuous(limits = c(0, 1), labels = percent) +
 	theme(
@@
 		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	) +
-	ggsave(here("Figures", "vocabulary_conceptual.png"))
+	)
 

### 2021-07-07 Rmd/report.Rmd
CHILDES frequencies in Barcelona and Oxford (the latter provided by @SiowSerene)

@@
 	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(role~location~test_language, ncol = 4) +
+	facet_wrap(location~test_language, ncol = 4) +
 	geom_col(position = position_fill(), colour = "white") +
@@
 		axis.title.y = element_text(angle = 90)
+	) 
+```
+
+### By location
+
+```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
+# plot participants
+attrition_location <- attrition %>% 
+	left_join(select(participants, participant, location)) %>% 
+	count(location, lp, age_group, trial_type, valid_status) %>% 
+	drop_na(trial_type)
+
+attrition_location %>% 
+	filter(location=="Barcelona") %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
+
+	attrition_location %>% 
+	filter(location=="Oxford") %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
+
+	plot_layout(guides = "collect", ncol = 1) &
+	scale_y_continuous(labels = percent) &
+	coord_flip() &
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 10),
+		axis.title = element_blank()
 	)

### 2021-07-07 R/01_participants.R

@@ -3,7 +3,6 @@
 # set up ----
 library(tidyverse)
 library(janitor) # for cleaining column names
-library(multilex) # for vocabulary data
 library(googlesheets4) # for participant data
 library(readxl) # for importing Excel spreadsheets
 library(lubridate) # for working with dates
@@ -22,8 +21,6 @@ participants_barcelona <- range_read(ss = "1JkhN4iBh3bi6PSReGGk9jSrVgDhZNOUmve6v
 
 # Oxford data ----
 # import vocabulary data
-
-
 participants_oxford <- read_xlsx(here("Data", "Participants", "participant_oxford_Apr2021.xlsx")) %>% 
 	clean_names() %>% 
 	rename(participant = id, lp = lang_group) %>% 

### 2021-07-07 R/02_vocabulary.R

@@ -10,10 +10,15 @@ library(readxl) # for importing Excel spreadsheets
 library(here) # for reproducible file paths
 
 # set params
-ml_connect("gonzalo.garciadecastro@upf.edu") # log into MultiLex
-cdi_replacements <- c("boots" = "boot", "boot(s)" = "boot", "fire engine" = "fireengine",
-					  "teddy bear" = "teddy", "bunny / rabbit" = "bunny",
-					  "lorry / truck" = "truck", "bicycle / bike" = "bike")
+ml_connect(
+	google_email = "gonzalo.garciadecastro@upf.edu",
+	formr_password = key_get("formr", "gonzalo.garciadecastro@upf.edu")
+)
+cdi_replacements <- c(
+	"boots" = "boot", "boot(s)" = "boot", "fire engine" = "fireengine",
+	"teddy bear" = "teddy", "bunny / rabbit" = "bunny",
+	"lorry / truck" = "truck", "bicycle / bike" = "bike"
+)
 
 participants <- readRDS(here("Data", "Participants", "participants.rds"))
 
@@ -123,7 +128,7 @@ vocab_barcelona[[2]] <- vocab_barcelona[[2]] %>%
 	left_join(vocab_norms_item_barcelona)
 vocab_barcelona <- bind_rows(vocab_barcelona) %>% 
 	select(-c(lp, is_imputed_vocab_words))
-	
+
 # Oxford vocabulary ----
 vocab_raw_oxford <- excel_sheets(here("Data", "Vocabulary", "vocabulary_oxford_Apr2021.xlsx")) %>%
 	map(function(x){

### 2021-07-13 Rmd/report.Rmd
Add targets to workflow

@@
 
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="100%"}
+```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
 means <- stimuli %>% 
 	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	filter(location=="Barcelona") %>% 
 	group_by(test_language, location, trial_type) %>% 
-	summarise(familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-			  .groups = "drop") %>% 
+	summarise(
+		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
+		.groups = "drop"
+	) %>% 
 	drop_na()
@@
 	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	drop_na() %>% 
 	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
-	facet_wrap(~test_language, scales = "free_y") +
+	facet_wrap(location~test_language, scales = "free_y") +
 	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
@@
 	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	filter(location=="Barcelona") %>% 
 	group_by(test_language, location, trial_type) %>% 
-	summarise(familiarity_target = mean(familiarity_target, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	drop_na()
+	summarise(
+		familiarity_target = mean(familiarity_target, na.rm = TRUE),
+		.groups = "drop"
+	)
 
@@
 	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	drop_na() %>% 
 	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
-	facet_wrap(~test_language, scales = "free_y") +
+	facet_wrap(location~test_language, scales = "free_y") +
 	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +

### 2021-07-14 Rmd/report.Rmd
Add Rmd to workflow and relaxed_criteria branch

@@
 
-```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 
 # load packages
+library(targets)
 library(papaja)
@@
 
-# create functions
-logit_to_prob <- function(x) exp(x) / (1 + exp(x))
-
-theme_custom <- function(){
-	theme(
-		panel.background = element_rect(fill = "transparent"),
-		panel.grid = element_blank(),
-		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		panel.border = element_rect(fill = "transparent", colour = "black"),
-		text = element_text(colour = "black", size = 15),
-		axis.text = element_text(colour = "black")
-	)
-}
-theme_set(theme_custom())
-
-# load data
-gaze <- readRDS(here("Data", "Gaze", "d.rds"))
-stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
-attrition <- readRDS(here("Results", "attrition.rds")) %>% 
+# load objects
+tar_load(participants)
+tar_load(stimuli)
+tar_load(vocabulary)
+
+# stringent version
+tar_load(gaze)
+tar_load(attrition)
+tar_load(fit)
+tar_load(fit_21_mon)
+tar_load(fit_21_mon_vocab_split)
+tar_load(fit_21_mon_vocab_balanced)
+tar_load(fit_21_mon_location)
+
+# relaxed version
+tar_load(gaze_relaxed)
+tar_load(attrition_relaxed)
+tar_load(fit_relaxed)
+tar_load(fit_21_mon_relaxed)
+tar_load(fit_21_mon_vocab_split_relaxed)
+tar_load(fit_21_mon_vocab_balanced_relaxed)
+tar_load(fit_21_mon_location_relaxed)
+
+theme_set(theme_custom()) # in utils.R
+```
+
+```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+attrition <- attrition %>% 
 	mutate(
@@
 		))
-vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
-participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
+
+attrition_relaxed <- attrition_relaxed %>% 
+	mutate(
+		valid_gaze = valid_gaze_prime & valid_gaze_target,
+		valid_status = case_when(
+			!valid_vocab ~ "Invalid vocabulary",
+			!valid_gaze ~ "Invalid gaze",
+			!valid_participant ~ "Invalid participant",
+			TRUE ~ "Valid"
+		))
+
+participants <- participants %>% 
 	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
 	drop_na(participant) %>% 
-	left_join(vocab) %>% 
+	left_join(vocabulary) %>% 
 	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-fit <- readRDS(here("Results", "fit.rds"))
-fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
-fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
-fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
-fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))
 
@@
 
-## Raw data
-
-```{r, echo = FALSE}
-shinyAppFile(
-	here("R", "gaze_app", "app.R"), 
-	options = list(width = "100%", height = 700)
-)
-```
-
-## Growth curve analysis {.tabset .tab-pills}
-
-### Model details
+## Stringent criteria  {.tabset .tab-pills}
+
+### Growth curve analysis {.tabset .tab-pills}
+
+#### Model details
 
@@
 
-### Fixed effects
+#### Fixed effects
 
@@
 
-### Random effects
+##### Random effects
 
@@
 
-### Marginal means {.tabset .tab-pills}
-
-#### Overall
+#### Marginal means {.tabset .tab-pills}
+
+##### Overall
 
@@
 
-#### By vocabulary size
+##### By vocabulary size
 
@@
 
-#### By location
+##### By location
 
@@
 
+##### {-}
+
 #### {-}
 
-### {-}
-
-## Attrition {.tabset .tab-pills}
-
-### Summary
+### Attrition {.tabset .tab-pills}
+
+#### Summary
 
@@
 	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocab) %>% 
+	left_join(vocabulary) %>% 
 	drop_na(valid_participant) %>% 
@@
 
-### By location
+#### By location
 
@@
 
-### By group
+#### By group
 
@@
 
-### By participant
+#### By participant
 
@@
 
-### By trial
+#### By trial
 
@@
 
-### By lexical frequency {.tabset .tab-pills}
-
-#### Prime frequency
+#### By lexical frequency {.tabset .tab-pills}
+
+##### Prime frequency
 
@@
 
-#### Target frequency
+##### Target frequency
 
@@
 
-#### {-}
-
-### By familiarity {.tabset .tab-pills}
-
-#### Prime familiarity
+##### {-}
+
+#### By familiarity {.tabset .tab-pills}
+
+##### Prime familiarity
 
@@
 
-#### Target familiarity
+##### Target familiarity
 
@@
 
-#### {-}
-
-### By animacy {.tabset .tab-pills}
-
-#### Prime
+##### {-}
+
+#### By animacy {.tabset .tab-pills}
+
+##### Prime
 
@@
 
-#### Target
+##### Target
 
@@
 
-#### {-}
-
-### By category {.tabset .tab-pills}
-
-#### Prime
+##### {-}
+
+#### By category {.tabset .tab-pills}
+
+##### Prime
 
@@
 
-### {-}
-
-## 21 month-old monolinguals {.tabset .tab-pills}
-
-### All data
+#### {-}
+
+### Raw data
+
+```{r, echo = FALSE}
+shinyAppFile(
+	here("R", "gaze_app", "app.R"), 
+	options = list(width = "100%", height = 700)
+)
+```
+
+### 21 month-old monolinguals {.tabset .tab-pills}
+
+#### All data
 
@@
 
-### Location
+#### Location
 
@@
 
-### Vocabulary (median split)
-
-```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
+#### Vocabulary (median split)
+
+```{r fixef_21_mon_vocab_split, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_21_mon_vocab_split, method = "Wald") %>% 
 	as.data.frame() %>% 
@@
 	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
+	right_join(clean_names(tidy(fit_21_mon_vocab_split, effects = "fixed"))) %>% 
 	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
@@
 
-augment(fit_21_mon_vocab) %>% 
+augment(fit_21_mon_vocab_split) %>% 
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
@@
 
-	augment(fit_21_mon_vocab) %>% 
+	augment(fit_21_mon_vocab_split) %>% 
 	mutate(elog_prob = logit_to_prob(elog)) %>% 
@@
 
-### Vocabulary (balanced)
-
-```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
+#### Vocabulary (balanced)
+
+```{r fixef_21_mon_vocab_balanced, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+main_effects <- confint.merMod(fit_21_mon_vocab_balanced, method = "Wald") %>% 
 	as.data.frame() %>% 
@@
 	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
+	right_join(clean_names(tidy(fit_21_mon_vocab_balanced, effects = "fixed"))) %>% 
 	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
@@
 
-```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-# by vocab (balanced)
+```{r gaze_time_21_mon_vocab_balanced, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+# by vocabulary (balanced)
 sample_size <- participants %>%
@@
 
-augment(fit_21_mon_vocab_pct) %>% 
+augment(fit_21_mon_vocab_balanced) %>% 
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
@@
 
-	augment(fit_21_mon_vocab_pct) %>% 
+	augment(fit_21_mon_vocab_balanced) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob)) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA) +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	)
+```
+
+#### {-}
+
+## Relaxed criteria  {.tabset .tab-pills}
+
+### Growth curve analysis {.tabset .tab-pills}
+
+#### Model details
+
+We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
+
+```
+elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
+(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
+```
+
+The formal implementation of this model is:
+
+$$
+\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
+(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
+(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
+(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
+(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
+(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
+(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
+(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
+(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
+$$
+
+#### Fixed effects
+
+```{r fixed_effects_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_relaxed, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_relaxed, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#ffc7a1")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+
+main_effects
+```
+
+##### Random effects
+
+```{r random_effects_participant_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+VarCorr(fit_relaxed)$participant %>% 
+	cov2cor() %>% 
+	as.data.frame() %>% 
+	rownames_to_column("term1") %>% 
+	gt(rowname_col = "term1") %>% 
+	fmt_number(columns = 2:9) %>% 
+	data_color(
+		columns = 2:9,
+		colors = col_numeric(
+			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
+			domain = c(-1, 1), alpha = 0.5
+		)
+	)
+
+```
+
+#### Marginal means {.tabset .tab-pills}
+
+##### Overall
+
+```{r gaze_time_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant) %>% 
+	count(age_group, lp)
+
+augment(fit_relaxed) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
+Sample sizes are indicated at the upper left corner in each panel.
+The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme_custom() +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7),
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	) 
+```
+
+##### By vocabulary size
+
+```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	count(age_group, lp)
+
+augment(fit_relaxed) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Vocabulary size <= median") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
+	count(age_group, lp)
+
+augment(fit_relaxed) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Vocabulary size > median") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+##### By location
+
+```{r gaze_time_location_barcelona_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(location=="Barcelona", valid_participant) %>% 
+	count(age_group, lp)
+
+augment(fit_relaxed) %>% 
+	left_join(distinct(participants, participant, location)) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(location=="Barcelona") %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Barcelona") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+```{r gaze_time_location_oxford_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(location=="Oxford") %>% 
+	count(age_group, lp)
+
+augment(fit_relaxed) %>% 
+	left_join(distinct(participants, participant, location)) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	filter(location=="Oxford") %>% 
+	ggplot(aes(x = ot1, y = .fitted_prob)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
+		 colour = "Trial type", fill = "Trial type",
+		 title = "Oxford") +
+	scale_y_continuous(limits = c(0, 1)) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		legend.position = "top",
+		axis.text = element_text(size = 7)
+	)
+```
+
+##### {-}
+
+#### {-}
+
+### Attrition {.tabset .tab-pills}
+
+#### Summary
+
+```{r participants_cdi_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+participants %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>%
+	left_join(vocabulary) %>% 
+	drop_na(valid_participant) %>% 
+	mutate(
+		valid_status = case_when(
+			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
+			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
+			!valid_participant ~ "Not valid"
+		)
+	) %>% 
+	ggplot(aes(lp, fill = valid_status)) +
+	facet_grid(location~age_group, scales = "free") +
+	geom_bar(colour = NA) +
+	geom_hline(yintercept = 24, linetype = "dashed") +
+	scale_colour_brewer(palette = "Set1") +
+	labs(x = "Group", y = "Sample size", fill = "Valid?") +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 10),
+		axis.title.y = element_text(angle = 90)
+	) 
+```
+
+#### By location
+
+```{r trials_attrition_location_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
+# plot participants
+attrition_location <- attrition_relaxed %>% 
+	left_join(select(participants, participant, location)) %>% 
+	count(location, lp, age_group, trial_type, valid_status) %>% 
+	drop_na(trial_type)
+
+attrition_location %>% 
+	filter(location=="Barcelona") %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
+
+	attrition_location %>% 
+	filter(location=="Oxford") %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
+
+	plot_layout(guides = "collect", ncol = 1) &
+	scale_y_continuous(labels = percent) &
+	coord_flip() &
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 10),
+		axis.title = element_blank()
+	)
+```
+
+#### By group
+
+This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
+
+```{r attrition_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
+
+left_join(attrition_relaxed, select(participants, age_group, location, lp, participant, date_test)) %>% 
+	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
+	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
+			  .groups = "drop") %>% 
+	pivot_wider(
+		names_from = trial_type,
+		values_from = valid_trial_count
+	) %>% 
+	clean_names() %>% 
+	group_by(lp, location, age_group) %>% 
+	summarise(
+		cognate = mean(cognate, na.rm = TRUE),
+		non_cognate = mean(non_cognate, na.rm = TRUE),
+		unrelated = mean(unrelated, na.rm = TRUE),
+		sum_n = sum(valid_participant, na.rm = TRUE),
+		prop_n = mean(valid_participant, na.rm = TRUE),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	arrange(age_group, lp, location) %>% 
+	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
+	gt() %>% 
+	tab_spanner(
+		"Mean valid trials",
+		c("cognate", "non_cognate", "unrelated")
+	) %>% 
+	tab_spanner(
+		"N participants",
+		c("sum_n", "n", "prop_n")
+	) %>% 
+	cols_label(
+		age_group = "Age",
+		lp = "Group",
+		sum_n = "Valid",
+		location = "Laboratory",
+		n = "Tested",
+		prop_n = "Valid (%)",
+		cognate = "Cognate (8)",
+		non_cognate = "Non-cognate (8)",
+		unrelated = "Unrelated (16)"
+	) %>% 
+	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
+	fmt_percent(c("prop_n")) %>% 
+	fmt_number(c("n", "sum_n"), decimals = 0)
+
+```
+
+#### By participant
+
+```{r participants_attrition_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition_relaxed %>% 
+	left_join(select(participants, participant, location)) %>% 
+	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
+	group_by(location, participant, lp, age_group, valid_participant) %>% 
+	summarise(
+		valid = mean(valid_trial),
+		invalid_gaze = mean(!valid_gaze),
+		invalid_vocab = mean(!valid_vocab),
+		.groups = "drop"
+	) %>% 
+	relocate(participant) %>% 
+	gt() %>% 
+	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
+	cols_label(
+		participant = "Participant",
+		location = "Location",
+		lp = "Lang. Profile",
+		age_group = "Age",
+		valid_participant = "Valid participant",
+		valid = "Valid trials (%)",
+		invalid_gaze = "Gaze (%)",
+		invalid_vocab = "Vocabulary (%)"
+	) %>% 
+	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
+	div(style='height:600px; overflow-y: scroll', .)
+```
+
+#### By trial
+
+```{r trials_attrition_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition_relaxed %>% 
+	left_join(select(participants, participant, location)) %>% 
+	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
+	count() %>% 
+	ungroup() %>%
+	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
+	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
+	clean_names() %>% 
+	gt(groupname_col = c("location", "lp")) %>% 
+	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
+	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
+	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
+	cols_label(
+		location = "Location",
+		lp = "Group",
+		trial_type = "Trial type",
+		x21_months_not_valid = "Not valid",
+		x21_months_valid = "Valid",
+		x25_months_not_valid = "Not valid",
+		x25_months_valid = "Valid",
+		x30_months_not_valid = "Not valid",
+		x30_months_valid = "Valid"
+	)
+
+```
+
+```{r trials_attrition_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition_relaxed %>% 
+	left_join(select(participants, participant, location)) %>% 
+	count(location, lp, age_group, trial_type, valid_status) %>% 
+	drop_na(trial_type) %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_col(position = position_fill()) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	scale_y_continuous(labels = percent) +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+#### By lexical frequency {.tabset .tab-pills}
+
+##### Prime frequency
+
+```{r attirion_summary_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
+	drop_na(trial_type, frequency_prime_childes) %>% 
+	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
+	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### Target frequency
+
+```{r attrition_frequency_target_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
+	drop_na(trial_type, frequency_target_childes) %>% 
+	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
+	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### {-}
+
+#### By familiarity {.tabset .tab-pills}
+
+##### Prime familiarity
+
+```{r attrition_familiarity_prime_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
+	drop_na(trial_type, familiarity_prime) %>% 
+	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
+	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### Target familiarity
+
+```{r attrition_familiarity_target_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
+	drop_na(trial_type, familiarity_target) %>% 
+	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
+	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### {-}
+
+#### By animacy {.tabset .tab-pills}
+
+##### Prime
+
+```{r attrition_animacy_prime_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
+	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
+	drop_na(trial_type, is_animate_prime) %>% 
+	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
+	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+
+```
+
+##### Target
+
+```{r attrition_animacy_target_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
+	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
+	drop_na(trial_type, is_animate_target) %>% 
+	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
+	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+
+```
+
+##### {-}
+
+#### By category {.tabset .tab-pills}
+
+##### Prime
+
+```{r attrition_category_prime_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
+	drop_na(trial_type, category_prime) %>% 
+	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
+	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### Target
+
+```{r attrition_category_target_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
+	drop_na(trial_type, category_target) %>% 
+	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
+	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "white") +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+#### {-}
+
+### Raw data
+
+```{r, echo = FALSE}
+shinyAppFile(
+	here("R", "gaze_app", "app.R"), 
+	options = list(width = "100%", height = 700)
+)
+```
+
+### 21 month-old monolinguals {.tabset .tab-pills}
+
+#### All data
+
+```{r fixef_21_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_21_mon_relaxed, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon_relaxed, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#ffc7a1")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+
+main_effects
+
+```
+
+```{r gaze_time_21_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
+	count(age_group, lp)
+
+augment(fit_21_mon_relaxed) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon_relaxed) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
+	plot_annotation(
+		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
+Sample sizes are indicated at the upper left corner in each panel.
+The first and last 300 ms in each trial\nwere trimmed before the analysis.
+B: mean observed probability of target looking, aggregated by participant.",
+		tag_levels = "A") &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	)
+```
+
+#### Location
+
+```{r fixef_21_mon_location_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_21_mon_location_relaxed, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon_location_relaxed, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#ffc7a1")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+
+main_effects
+
+```
+
+```{r gaze_time_21_mon_location_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
+	count(age_group, location)
+
+augment(fit_21_mon_location_relaxed) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	facet_wrap(~location, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(
+		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  colour = "black", fill = "black", show.legend = FALSE) +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon_location_relaxed) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, location, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
+	facet_wrap(~location, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	)
+```
+
+#### Vocabulary (median split)
+
+```{r fixef_21_mon_vocab_split_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_21_mon_vocab_split_relaxed, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon_vocab_split_relaxed, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#ffc7a1")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+main_effects
+
+```
+
+```{r gaze_time_21_mon_vocab_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+sample_size <- participants %>% 
+	drop_na(vocab_size_l1_center) %>% 
+	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
+	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
+	count(age_group, vocab_cat, lp)
+
+augment(fit_21_mon_vocab_split_relaxed) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	facet_wrap(~vocab_cat, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
+			  show.legend = FALSE,
+			  colour = "black", fill = "black") +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon_vocab_split_relaxed) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, vocab_cat, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob)) +
+	facet_wrap(~vocab_cat, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	)
+```
+
+#### Vocabulary (balanced)
+
+```{r fixef_21_mon_vocab_balanced_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+main_effects <- confint.merMod(fit_21_mon_vocab_balanced_relaxed, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon_vocab_balanced_relaxed, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#ffc7a1")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+main_effects
+
+```
+
+```{r gaze_time_21_mon_vocab_balanced_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+# by vocabulary (balanced)
+sample_size <- participants %>%
+	drop_na(vocab_size_l1_center) %>% 
+	filter(age_group=="21 months", lp=="Monolingual") %>% 
+	arrange(location, desc(vocab_size_l1_center)) %>% 
+	group_by(location) %>% 
+	mutate(vocab_index = row_number()) %>% 
+	ungroup() %>% 
+	filter(
+		((location=="Barcelona") & (vocab_index %in% 1:15)) |
+			((location=="Oxford")) & (vocab_index %in% seq(
+				max(vocab_index[location=="Oxford"])-15,
+				max(vocab_index[location=="Oxford"])))
+	) %>% 
+	nrow() %>% 
+	data.frame(n = .)
+
+augment(fit_21_mon_vocab_balanced_relaxed) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(
+		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  colour = "black", fill = "black", show.legend = FALSE) +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon_vocab_balanced_relaxed) %>% 
 	mutate(elog_prob = logit_to_prob(elog)) %>% 

### 2021-07-14 R/utils.R

@@ -1,5 +1,16 @@
 # utils
 
+# custom ggplot theme
+theme_custom <- function(){
+	theme(
+		panel.background = element_rect(fill = "transparent"),
+		panel.grid = element_blank(),
+		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
+		panel.border = element_rect(fill = "transparent", colour = "black"),
+		text = element_text(colour = "black", size = 15),
+		axis.text = element_text(colour = "black")
+	)
+}
 
 # get multilex data ----
 get_credentials <- function(

### 2021-07-19 Rmd/report.Rmd

@@
 
-participants <- participants %>% 
+participants_stringent <- participants %>% 
 	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
@@
 
+participants_relaxed <- participants %>% 
+	left_join(distinct(attrition_relaxed, participant, age_group, valid_participant)) %>% 
+	drop_na(participant) %>% 
+	left_join(vocabulary) %>% 
+	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
+
 ```
@@
 
-## Participants {.tabset .tabpills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-### Summary
-
-```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
+## Participants {.tabset .tabset-pills}
+
+### Stringent criteria {.tabset}
+
+* We collected data from `r length(unique(participants_stringent$participant))` participants `r length(unique(participants_stringent$participant[participants_stringent$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants_stringent$participant[participants_stringent$location=="Barcelona"]))` were tested in Barcelona.
+* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants_stringent$participant[participants_stringent$valid_participant]))` (`r length(unique(participants_stringent$participant[participants_stringent$valid_participant & participants_stringent$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants_stringent$participant[participants_stringent$valid_participant & participants_stringent$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
+* `r length(participants_stringent$participant[duplicated(participants_stringent$participant) & participants_stringent$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
+`r length(participants_stringent$participant[duplicated(participants_stringent$participant) & participants_stringent$location=="Oxford" & participants_stringent$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants_stringent$participant[duplicated(participants_stringent$participant) & participants_stringent$location=="Barcelona" & participants_stringent$valid_participant])` were tested in Barcelona.
+* From the longitudinal participants, `r length(participants_stringent$participant[(as.data.frame(table(participants_stringent$participant))$Freq>2) & participants_stringent$valid_participant])` were tested at two age groups, and `r length(participants_stringent$participant[(as.data.frame(table(participants_stringent$participant))$Freq>2) & participants_stringent$valid_participant])`were tested at three age groups.
+
+#### Summary
+
+```{r participants_summary_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_stringent %>% 
 	left_join(distinct(attrition, participant, valid_participant)) %>% 
@@
 
-### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
+#### Longitudinal
+
+We collected data from `r sum(duplicated(participants_stringent$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
+Of those, `r sum(duplicated(participants_stringent$participant[participants_stringent$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants_stringent$participant[participants_stringent$location=="Barcelona"]))` were tested in Barcelona.
+
+```{r participants_cohort_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
 # plot participants
-participants %>% 
+participants_stringent %>% 
 	left_join(distinct(attrition, participant, valid_participant)) %>%
@@
 
+#### {-}
+
+### Relaxed criteria {.tabset}
+
+* We collected data from `r length(unique(participants_relaxed$participant))` participants `r length(unique(participants_relaxed$participant[participants_relaxed$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants_relaxed$participant[participants_relaxed$location=="Barcelona"]))` were tested in Barcelona.
+* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants_relaxed$participant[participants_relaxed$valid_participant]))` (`r length(unique(participants_relaxed$participant[participants_relaxed$valid_participant & participants_relaxed$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants_relaxed$participant[participants_relaxed$valid_participant & participants_relaxed$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
+* `r length(participants_relaxed$participant[duplicated(participants_relaxed$participant) & participants_relaxed$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
+`r length(participants_relaxed$participant[duplicated(participants_relaxed$participant) & participants_relaxed$location=="Oxford" & participants_relaxed$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants_relaxed$participant[duplicated(participants_relaxed$participant) & participants_relaxed$location=="Barcelona" & participants_relaxed$valid_participant])` were tested in Barcelona.
+* From the longitudinal participants, `r length(participants_relaxed$participant[(as.data.frame(table(participants_relaxed$participant))$Freq>2) & participants_relaxed$valid_participant])` were tested at two age groups, and `r length(participants_relaxed$participant[(as.data.frame(table(participants_relaxed$participant))$Freq>2) & participants_relaxed$valid_participant])`were tested at three age groups.
+
+#### Summary
+
+```{r participants_summary_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	ggplot(aes(lp, fill = as.factor(test_language))) +
+	facet_grid(location~age_group, scales = "free") +
+	geom_bar(colour = NA) +
+	geom_hline(yintercept = 24, linetype = "dashed") +
+	labs(x = "Group", y = "Sample size", fill = "Test language") +
+	theme(
+		legend.position = "top",
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 10),
+		axis.title.y = element_text(angle = 90)
+	) 
+```
+
+#### Longitudinal
+
+We collected data from `r sum(duplicated(participants_relaxed$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
+Of those, `r sum(duplicated(participants_relaxed$participant[participants_relaxed$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants_relaxed$participant[participants_relaxed$location=="Barcelona"]))` were tested in Barcelona.
+
+```{r participants_cohort_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
+# plot participants
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>%
+	mutate(
+		valid_status = case_when(
+			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
+			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
+			!valid_participant ~ "Not valid"
+		),
+		age_group = str_remove(age_group, " months")
+	) %>%
+	drop_na(valid_status) %>% 
+	ggplot(aes(age_group, participant, colour = valid_status)) +
+	facet_grid(location~lp, scales = "free") +
+	geom_line(aes(group = interaction(lp, participant))) +
+	geom_point(size = 2) +
+	geom_hline(yintercept = 0.2, linetype = "dashed") +
+	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
+	theme(
+		legend.position = "right",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 10),
+		axis.title.y = element_blank(),
+		axis.text.y = element_blank(),
+		axis.ticks.y = element_blank()
+	)
+```
+
+#### {-}
+
 ### {-}
 
-## Stimuli {.tabset .tab-pills}
-
-### Frequency {.tabset .tab-pills}
+## Stimuli {.tabset }
+
+### Frequency {.tabset }
 
@@
 
-#### CHILDES {.tabset .tab-pills}
+#### CHILDES {.tabset }
 
@@
 
-#### SUBTLEX {.tabset .tab-pills}
+#### SUBTLEX {.tabset }
 
@@
 
-### Familiarity {.tabset .tab-pills}
+### Familiarity {.tabset }
 
@@
 
-# Results {.tabset .tab-pills}
-
-## Stringent criteria  {.tabset .tab-pills}
-
-### Growth curve analysis {.tabset .tab-pills}
+# Results {.tabset .tabset-pills}
+
+## Stringent criteria  {.tabset }
+
+### Growth curve analysis {.tabset }
 
@@
 
-##### Random effects
+#### Random effects
 
@@
 
-#### Marginal means {.tabset .tab-pills}
+#### Marginal means {.tabset }
 
@@
 ```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_stringent %>% 
 	filter(valid_participant) %>% 
@@
 ```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_stringent %>% 
 	count(age_group, lp)
@@
 ```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_stringent %>% 
 	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
@@
 ```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_stringent %>% 
 	filter(location=="Barcelona", valid_participant) %>% 
@@
 ```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_stringent %>% 
 	filter(location=="Oxford") %>% 
@@
 
-### Attrition {.tabset .tab-pills}
+### Attrition {.tabset }
 
@@
 # plot participants
-participants %>% 
+participants_stringent %>% 
 	left_join(distinct(attrition, participant, valid_participant)) %>%
@@
 attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+	left_join(select(participants_stringent, participant, location)) %>% 
 	count(location, lp, age_group, trial_type, valid_status) %>% 
@@
 
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
+left_join(attrition, select(participants_stringent, age_group, location, lp, participant, date_test)) %>% 
 	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
@@
 attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+	left_join(select(participants_stringent, participant, location)) %>% 
 	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
@@
 attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+	left_join(select(participants_stringent, participant, location)) %>% 
 	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
@@
 attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+	left_join(select(participants_stringent, participant, location)) %>% 
 	count(location, lp, age_group, trial_type, valid_status) %>% 
@@
 
-#### By lexical frequency {.tabset .tab-pills}
+#### By lexical frequency {.tabset }
 
@@
 
-#### By familiarity {.tabset .tab-pills}
+#### By familiarity {.tabset }
 
@@
 
-#### By animacy {.tabset .tab-pills}
+#### By animacy {.tabset }
 
@@
 
-#### By category {.tabset .tab-pills}
+#### By category {.tabset }
 
@@
 
-### 21 month-old monolinguals {.tabset .tab-pills}
+### 21 month-old monolinguals {.tabset }
 
@@
 ```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_stringent %>% 
 	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
@@
 ```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_stringent %>% 
 	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
@@
 
-sample_size <- participants %>% 
+sample_size <- participants_stringent %>% 
 	drop_na(vocab_size_l1_center) %>% 
 	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
+	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants_stringent$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
 	count(age_group, vocab_cat, lp)
@@
 # by vocabulary (balanced)
-sample_size <- participants %>%
+sample_size <- participants_stringent %>%
 	drop_na(vocab_size_l1_center) %>% 
@@
 
-## Relaxed criteria  {.tabset .tab-pills}
-
-### Growth curve analysis {.tabset .tab-pills}
+## Relaxed criteria  {.tabset }
+
+### Growth curve analysis {.tabset}
 
@@
 ```{r gaze_time_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_relaxed %>% 
 	filter(valid_participant) %>% 
@@
 ```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_relaxed %>% 
 	count(age_group, lp)
@@
 ```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_relaxed %>% 
 	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
@@
 ```{r gaze_time_location_barcelona_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_relaxed %>% 
 	filter(location=="Barcelona", valid_participant) %>% 
@@
 ```{r gaze_time_location_oxford_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_relaxed %>% 
 	filter(location=="Oxford") %>% 
@@
 # plot participants
-participants %>% 
+participants_relaxed %>% 
 	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>%
@@
 attrition_location <- attrition_relaxed %>% 
-	left_join(select(participants, participant, location)) %>% 
+	left_join(select(participants_relaxed, participant, location)) %>% 
 	count(location, lp, age_group, trial_type, valid_status) %>% 
@@
 
-left_join(attrition_relaxed, select(participants, age_group, location, lp, participant, date_test)) %>% 
+left_join(attrition_relaxed, select(participants_relaxed, age_group, location, lp, participant, date_test)) %>% 
 	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
@@
 attrition_relaxed %>% 
-	left_join(select(participants, participant, location)) %>% 
+	left_join(select(participants_relaxed, participant, location)) %>% 
 	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
@@
 attrition_relaxed %>% 
-	left_join(select(participants, participant, location)) %>% 
+	left_join(select(participants_relaxed, participant, location)) %>% 
 	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
@@
 attrition_relaxed %>% 
-	left_join(select(participants, participant, location)) %>% 
+	left_join(select(participants_relaxed, participant, location)) %>% 
 	count(location, lp, age_group, trial_type, valid_status) %>% 
@@
 
-#### By familiarity {.tabset .tab-pills}
+#### By familiarity {.tabset}
 
@@
 
-#### By category {.tabset .tab-pills}
+#### By category {.tabset}
 
@@
 ```{r gaze_time_21_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_relaxed %>% 
 	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
@@
 ```{r gaze_time_21_mon_location_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+sample_size <- participants_relaxed %>% 
 	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
@@
 
-sample_size <- participants %>% 
+sample_size <- participants_relaxed %>% 
 	drop_na(vocab_size_l1_center) %>% 
 	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
+	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants_relaxed$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
 	count(age_group, vocab_cat, lp)
@@
 # by vocabulary (balanced)
-sample_size <- participants %>%
+sample_size <- participants_relaxed %>%
 	drop_na(vocab_size_l1_center) %>% 
@@
 
-## Vocabulary {.tabset .tab-pills}
-
-### L1 vocabulary
+## Vocabulary {.tabset .tabset-pills}
+
+### Stringent criteria {.tabset}
+
+#### L1 vocabulary
 
@@
 
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
+```{r vocabulary_l1_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants_stringent %>% 
 	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
@@
 # vocabulary
-participants %>% 
+participants_stringent %>% 
 	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
@@
 
-### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
+#### Total vocabulary
+
+```{r vocabulary_total_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants_stringent %>% 
 	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
@@
 
-### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
+#### Conceptual vocabulary
+
+```{r vocabulary_conceptual_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants_stringent %>% 
 	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
@@
 
+#### {-}
+
+### Relaxed criteria {.tabset}
+
+#### L1 vocabulary
+
+This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
+Results are presented separately for each age group.
+The shape of the violins, represents the distribution of the vocabulary sizes.
+The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
+vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
+for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
+
+```{r vocabulary_l1_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants_relaxed %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	count(age_group, location)
+
+# vocabulary
+participants_relaxed %>% 
+	drop_na(lp) %>%
+	filter(valid_participant) %>% 
+	ggplot() +
+	facet_grid(location~age_group) +
+	# geom_violin(
+	# 	position = position_dodge(width = 0.75),
+	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
+	# ) + 
+	geom_hline(yintercept = 0.5, colour = "grey") +
+	geom_point(
+		aes(lp, vocab_size_l1),
+		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
+		position = position_jitter(width = 0.1, seed = 888)
+	) +
+	geom_boxplot(
+		aes(lp, vocab_size_l1, colour = lp, fill = lp),
+		width = 0.25, colour = "black", outlier.colour = NA,
+		position = position_dodge(width = 0.75)
+	) +
+	geom_text(
+		data = sample_size,
+		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
+		colour = "black", fill = "black", show.legend = FALSE
+	) +
+	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) +
+	theme(
+		legend.title = element_blank(),
+		legend.position = "none",
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 9),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	)
+
+```
+
+#### Total vocabulary
+
+```{r vocabulary_total_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants_relaxed %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	count(age_group, location)
+
+# vocabulary
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, age_group, valid_participant)) %>% 
+	drop_na(lp) %>%
+	filter(valid_participant) %>% 
+	ggplot() +
+	facet_grid(location~age_group) +
+	# geom_violin(
+	# 	position = position_dodge(width = 0.75),
+	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
+	# ) + 
+	geom_hline(yintercept = 0.5, colour = "grey") +
+	geom_point(
+		aes(lp, vocab_size_total),
+		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
+		position = position_jitter(width = 0.1, seed = 888)
+	) +
+	geom_boxplot(
+		aes(lp, vocab_size_total, colour = lp, fill = lp),
+		width = 0.25, colour = "black", outlier.colour = NA,
+		position = position_dodge(width = 0.75)
+	) +
+	geom_text(
+		data = sample_size,
+		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
+		colour = "black", fill = "black", show.legend = FALSE
+	) +
+	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) +
+	theme(
+		legend.title = element_blank(),
+		legend.position = "none",
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 9),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	)
+
+```
+
+#### Conceptual vocabulary
+
+```{r vocabulary_conceptual_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants_relaxed %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	count(age_group, location)
+
+# vocabulary
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, age_group, valid_participant)) %>% 
+	drop_na(lp) %>%
+	filter(valid_participant) %>% 
+	ggplot() +
+	facet_grid(location~age_group) +
+	# geom_violin(
+	# 	position = position_dodge(width = 0.75),
+	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
+	# ) + 
+	geom_hline(yintercept = 0.5, colour = "grey") +
+	geom_point(
+		aes(lp, vocab_size_conceptual),
+		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
+		position = position_jitter(width = 0.1, seed = 888)
+	) +
+	geom_boxplot(
+		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
+		width = 0.25, colour = "black", outlier.colour = NA,
+		position = position_dodge(width = 0.75)
+	) +
+	geom_text(
+		data = sample_size,
+		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
+		colour = "black", fill = "black", show.legend = FALSE
+	) +
+	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) +
+	theme(
+		legend.title = element_blank(),
+		legend.position = "none",
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 9),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	)
+
+```
+
+#### {-}
+
 ### {-}

### 2021-07-19 Rmd/report_00_participants_relaxed.Rmd
Separate report.Rmd into chunks

--- 2021-07-13 Rmd/report.Rmd
@@
 ---
-title: "Report"
-output:
-  html_document:
-    df_print: paged
-    toc: true
-    toc_depth: 5
-    toc_float: true
-runtime: shiny
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = FALSE,
-	message = TRUE,
-	warning = TRUE, 
-	cache.extra = knitr::rand_seed,
-	out.width = "100%",
-	results = "asis",
-	dev.args = list(png = list(type = "cairo"))
-)
-options(knitr.kable.NA = '-',
-		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
-		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
-)
+* We collected data from `r length(unique(participants_relaxed$participant))` participants `r length(unique(participants_relaxed$participant[participants_relaxed$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants_relaxed$participant[participants_relaxed$location=="Barcelona"]))` were tested in Barcelona.
+* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants_relaxed$participant[participants_relaxed$valid_participant]))` (`r length(unique(participants_relaxed$participant[participants_relaxed$valid_participant & participants_relaxed$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants_relaxed$participant[participants_relaxed$valid_participant & participants_relaxed$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
+* `r length(participants_relaxed$participant[duplicated(participants_relaxed$participant) & participants_relaxed$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
+`r length(participants_relaxed$participant[duplicated(participants_relaxed$participant) & participants_relaxed$location=="Oxford" & participants_relaxed$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants_relaxed$participant[duplicated(participants_relaxed$participant) & participants_relaxed$location=="Barcelona" & participants_relaxed$valid_participant])` were tested in Barcelona.
+* From the longitudinal participants, `r length(participants_relaxed$participant[(as.data.frame(table(participants_relaxed$participant))$Freq>2) & participants_relaxed$valid_participant])` were tested at two age groups, and `r length(participants_relaxed$participant[(as.data.frame(table(participants_relaxed$participant))$Freq>2) & participants_relaxed$valid_participant])`were tested at three age groups.
 
-```
+#### Summary
 
-```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# load packages
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(lme4)
-library(broom.mixed)
-library(gt)
-library(patchwork)
-library(htmltools)
-library(wesanderson)
-library(shiny)
-library(here)
-
-# create functions
-logit_to_prob <- function(x) exp(x) / (1 + exp(x))
-
-theme_custom <- function(){
-	theme(
-		panel.background = element_rect(fill = "transparent"),
-		panel.grid = element_blank(),
-		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		panel.border = element_rect(fill = "transparent", colour = "black"),
-		text = element_text(colour = "black", size = 15),
-		axis.text = element_text(colour = "black")
-	)
-}
-theme_set(theme_custom())
-
-# load data
-gaze <- readRDS(here("Data", "Gaze", "d.rds"))
-stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
-attrition <- readRDS(here("Results", "attrition.rds")) %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
-participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocab) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-fit <- readRDS(here("Results", "fit.rds"))
-fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
-fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
-fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
-fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))
-
-```
-
-# Methods
-
-## Participants {.tabset .tabpills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-### Summary
-
-```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
+```{r participants_summary_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
 	filter(valid_participant) %>% 
@@
 
-### Longitudinal
+#### Longitudinal
 
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+We collected data from `r sum(duplicated(participants_relaxed$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
+Of those, `r sum(duplicated(participants_relaxed$participant[participants_relaxed$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants_relaxed$participant[participants_relaxed$location=="Barcelona"]))` were tested in Barcelona.
 
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
+```{r participants_cohort_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
 # plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>%
 	mutate(
@@
 
-### {-}
-
-## Stimuli {.tabset .tab-pills}
-
-### Frequency {.tabset .tab-pills}
-
-#### CHILDES vs. SUBTLEX
-
-```{r frequencies_compare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_data <- bind_rows(
-	stimuli %>%
-		distinct(test_language, prime, .keep_all = TRUE) %>%
-		select(prime, test_language, matches("frequency_prime")) %>% 
-		rename(word = prime, frequency_subtlex = frequency_prime_subtlex,
-			   frequency_childes = frequency_prime_childes),
-	stimuli %>%
-		distinct(test_language, target, .keep_all = TRUE) %>%
-		select(target, test_language, matches("frequency_target")) %>% 
-		rename(word = target, frequency_subtlex = frequency_target_subtlex,
-			   frequency_childes = frequency_target_childes),
-) %>% 
-	group_by(test_language) %>% 
-	mutate_at(vars(starts_with("frequency")), function(x) scale(x)[,1])
-
-frequency_compare_test <- group_split(frequency_compare_data) %>% 
-	set_names(c("Catalan", "English", "Spanish")) %>% 
-	map(function(x) {
-		a <- pull(x, frequency_subtlex)
-		b <- pull(x, frequency_childes)
-		tidy(cor.test(a, b), use = "complete.obs")
-	}) %>% 
-	bind_rows(.id = "test_language") %>% 
-	clean_names()
-
-```
-
-We tested the correlation between the (standardised) lexical frequencies of the stimuli extract from SUBTLEX (adult norms based on subtitles) and CHILDES (child norms based on audio transcriptions) within each test language using a Pearson's product-moment correlation at .05 confidence level (two-sided):
-
-```{r stimuli_frequency_compare_test, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_test %>% 
-	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
-	mutate(p_value = printp(p_value)) %>% 
-	gt(rowname_col = "test_language") %>% 
-	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
-	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
-	cols_label(
-		estimate = md("**Correlation**"),
-		statistic = md("***t***"),
-		parameter = md("***df***"),
-		p_value = md("***p***"),
-		conf_low = md("**CI<sub>95%<sub/>**")
-	)
-
-```
-
-```{r stimuli_frequency_compare_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
-
-frequency_compare_data %>% 
-	ggplot(aes(frequency_subtlex, frequency_childes, colour = test_language, fill = test_language)) +
-	facet_wrap(~test_language) +
-	geom_point(alpha = 0.5, stroke = 1, shape = 1) +
-	geom_smooth(method = "lm") +
-	labs(x = "SUBTLEX (adult norms)", y = "CHILDES (child norms)",
-		 colour = "Language", fill = "Language") +
-	coord_fixed() +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### CHILDES {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### SUBTLEX {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_subtlex_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_subtlex_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
 #### {-}
-
-### Familiarity {.tabset .tab-pills}
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 10),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "_category"))) %>% 
-	drop_na() %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_grid(role~location~test_language) +
-	geom_col(position = position_fill()) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_fill_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_colour_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level")
-
-```
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tab-pills}
-
-## Raw data
-
-```{r, echo = FALSE}
-shinyAppFile(
-	here("R", "gaze_app", "app.R"), 
-	options = list(width = "100%", height = 700)
-)
-```
-
-## Growth curve analysis {.tabset .tab-pills}
-
-### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-$$
-\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
-(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
-(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
-(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
-(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
-(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
-(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
-$$
-
-### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-```
-
-### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-VarCorr(fit)$participant %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	gt(rowname_col = "term1") %>% 
-	fmt_number(columns = 2:9) %>% 
-	data_color(
-		columns = 2:9,
-		colors = col_numeric(
-			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
-			domain = c(-1, 1), alpha = 0.5
-		)
-	)
-
-```
-
-### Marginal means {.tabset .tab-pills}
-
-#### Overall
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7),
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	) 
-```
-
-#### By vocabulary size
-
-```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size <= median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size > median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### By location
-
-```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Barcelona", valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Barcelona") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Oxford") %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Oxford") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### {-}
-
-### {-}
-
-## Attrition {.tabset .tab-pills}
-
-### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocab) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0)
-
-```
-
-### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	div(style='height:600px; overflow-y: scroll', .)
-```
-
-### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	)
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill()) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-### By lexical frequency {.tabset .tab-pills}
-
-#### Prime frequency
-
-```{r attirion_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
-	drop_na(trial_type, frequency_prime_childes) %>% 
-	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
-	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target frequency
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### {-}
-
-### By familiarity {.tabset .tab-pills}
-
-#### Prime familiarity
-
-```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
-	drop_na(trial_type, familiarity_prime) %>% 
-	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
-	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target familiarity
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### {-}
-
-### By animacy {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
-	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_prime) %>% 
-	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
-	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### Target
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### {-}
-
-### By category {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
-	drop_na(trial_type, category_prime) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
-	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-### {-}
-
-## 21 month-old monolinguals {.tabset .tab-pills}
-
-### All data
-
-```{r fixef_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, lp)
-
-augment(fit_21_mon) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	plot_annotation(
-		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.
-B: mean observed probability of target looking, aggregated by participant.",
-		tag_levels = "A") &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Location
-
-```{r fixef_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, location)
-
-augment(fit_21_mon_location) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_location) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, location, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (median split)
-
-```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-sample_size <- participants %>% 
-	drop_na(vocab_size_l1_center) %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
-	count(age_group, vocab_cat, lp)
-
-augment(fit_21_mon_vocab) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, vocab_cat, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (balanced)
-
-```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-# by vocab (balanced)
-sample_size <- participants %>%
-	drop_na(vocab_size_l1_center) %>% 
-	filter(age_group=="21 months", lp=="Monolingual") %>% 
-	arrange(location, desc(vocab_size_l1_center)) %>% 
-	group_by(location) %>% 
-	mutate(vocab_index = row_number()) %>% 
-	ungroup() %>% 
-	filter(
-		((location=="Barcelona") & (vocab_index %in% 1:15)) |
-			((location=="Oxford")) & (vocab_index %in% seq(
-				max(vocab_index[location=="Oxford"])-15,
-				max(vocab_index[location=="Oxford"])))
-	) %>% 
-	nrow() %>% 
-	data.frame(n = .)
-
-augment(fit_21_mon_vocab_pct) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab_pct) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### {-}
-
-## Vocabulary {.tabset .tab-pills}
-
-### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### {-}
-
-## {-}
-
-# {-}
-
-# Appendix
-
-# References

### 2021-07-19 Rmd/report_00_participants_stringent.Rmd
Separate report.Rmd into chunks

--- 2021-07-13 Rmd/report.Rmd
@@
 ---
-title: "Report"
-output:
-  html_document:
-    df_print: paged
-    toc: true
-    toc_depth: 5
-    toc_float: true
-runtime: shiny
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = FALSE,
-	message = TRUE,
-	warning = TRUE, 
-	cache.extra = knitr::rand_seed,
-	out.width = "100%",
-	results = "asis",
-	dev.args = list(png = list(type = "cairo"))
-)
-options(knitr.kable.NA = '-',
-		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
-		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
-)
+* We collected data from `r length(unique(participants_stringent$participant))` participants `r length(unique(participants_stringent$participant[participants_stringent$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants_stringent$participant[participants_stringent$location=="Barcelona"]))` were tested in Barcelona.
+* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants_stringent$participant[participants_stringent$valid_participant]))` (`r length(unique(participants_stringent$participant[participants_stringent$valid_participant & participants_stringent$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants_stringent$participant[participants_stringent$valid_participant & participants_stringent$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
+* `r length(participants_stringent$participant[duplicated(participants_stringent$participant) & participants_stringent$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
+`r length(participants_stringent$participant[duplicated(participants_stringent$participant) & participants_stringent$location=="Oxford" & participants_stringent$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants_stringent$participant[duplicated(participants_stringent$participant) & participants_stringent$location=="Barcelona" & participants_stringent$valid_participant])` were tested in Barcelona.
+* From the longitudinal participants, `r length(participants_stringent$participant[(as.data.frame(table(participants_stringent$participant))$Freq>2) & participants_stringent$valid_participant])` were tested at two age groups, and `r length(participants_stringent$participant[(as.data.frame(table(participants_stringent$participant))$Freq>2) & participants_stringent$valid_participant])`were tested at three age groups.
 
-```
+#### Summary
 
-```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# load packages
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(lme4)
-library(broom.mixed)
-library(gt)
-library(patchwork)
-library(htmltools)
-library(wesanderson)
-library(shiny)
-library(here)
-
-# create functions
-logit_to_prob <- function(x) exp(x) / (1 + exp(x))
-
-theme_custom <- function(){
-	theme(
-		panel.background = element_rect(fill = "transparent"),
-		panel.grid = element_blank(),
-		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		panel.border = element_rect(fill = "transparent", colour = "black"),
-		text = element_text(colour = "black", size = 15),
-		axis.text = element_text(colour = "black")
-	)
-}
-theme_set(theme_custom())
-
-# load data
-gaze <- readRDS(here("Data", "Gaze", "d.rds"))
-stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
-attrition <- readRDS(here("Results", "attrition.rds")) %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
-participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocab) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-fit <- readRDS(here("Results", "fit.rds"))
-fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
-fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
-fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
-fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))
-
-```
-
-# Methods
-
-## Participants {.tabset .tabpills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-### Summary
-
-```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
+```{r participants_summary_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_stringent %>% 
 	left_join(distinct(attrition, participant, valid_participant)) %>% 
@@
 
-### Longitudinal
+#### Longitudinal
 
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+We collected data from `r sum(duplicated(participants_stringent$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
+Of those, `r sum(duplicated(participants_stringent$participant[participants_stringent$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants_stringent$participant[participants_stringent$location=="Barcelona"]))` were tested in Barcelona.
 
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
+```{r participants_cohort_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
 # plot participants
-participants %>% 
+participants_stringent %>% 
 	left_join(distinct(attrition, participant, valid_participant)) %>%

### 2021-07-19 Rmd/report_01_stimuli.Rmd
Separate report.Rmd into chunks

--- 2021-07-13 Rmd/report.Rmd
@@
 ---
-title: "Report"
-output:
-  html_document:
-    df_print: paged
-    toc: true
-    toc_depth: 5
-    toc_float: true
-runtime: shiny
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = FALSE,
-	message = TRUE,
-	warning = TRUE, 
-	cache.extra = knitr::rand_seed,
-	out.width = "100%",
-	results = "asis",
-	dev.args = list(png = list(type = "cairo"))
-)
-options(knitr.kable.NA = '-',
-		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
-		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
-)
+## Stimuli {.tabset }
 
-```
-
-```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# load packages
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(lme4)
-library(broom.mixed)
-library(gt)
-library(patchwork)
-library(htmltools)
-library(wesanderson)
-library(shiny)
-library(here)
-
-# create functions
-logit_to_prob <- function(x) exp(x) / (1 + exp(x))
-
-theme_custom <- function(){
-	theme(
-		panel.background = element_rect(fill = "transparent"),
-		panel.grid = element_blank(),
-		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		panel.border = element_rect(fill = "transparent", colour = "black"),
-		text = element_text(colour = "black", size = 15),
-		axis.text = element_text(colour = "black")
-	)
-}
-theme_set(theme_custom())
-
-# load data
-gaze <- readRDS(here("Data", "Gaze", "d.rds"))
-stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
-attrition <- readRDS(here("Results", "attrition.rds")) %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
-participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocab) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-fit <- readRDS(here("Results", "fit.rds"))
-fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
-fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
-fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
-fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))
-
-```
-
-# Methods
-
-## Participants {.tabset .tabpills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-### Summary
-
-```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		),
-		age_group = str_remove(age_group, " months")
-	) %>%
-	drop_na(valid_status) %>% 
-	ggplot(aes(age_group, participant, colour = valid_status)) +
-	facet_grid(location~lp, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	geom_hline(yintercept = 0.2, linetype = "dashed") +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
-	theme(
-		legend.position = "right",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
-```
-
-### {-}
-
-## Stimuli {.tabset .tab-pills}
-
-### Frequency {.tabset .tab-pills}
+### Frequency {.tabset }
 
@@
 	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
+	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
+	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), colour = trial_type, fill = trial_type)) +
 	facet_wrap(location~test_language, scales = "free_y") +
@@
 	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	geom_errorbar() +
+	# geom_errorbar() +
 	geom_point() +
@@
 	scale_x_continuous(labels = percent) +
+	# scale_y_reordered() +
 	theme_custom() +
@@
 	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
+	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
 	facet_wrap(location~test_language, scales = "free_y") +
@@
 	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	geom_errorbar() +
+	# geom_errorbar() +
 	geom_point() +
@@
 	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "_category"))) %>% 
-	drop_na() %>% 
+	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
+	drop_na(trial_type, category) %>% 
 	count(trial_type, test_language, location, role, category) %>% 
 	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_grid(role~location~test_language) +
+	facet_wrap(role~location~test_language) +
 	geom_col(position = position_fill()) +
@@
 		 colour = "Trial type", fill = "Trial type") +
-	scale_fill_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_colour_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
 	scale_x_continuous(labels = percent) +
@@
 ### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level")
-
-```
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tab-pills}
-
-## Raw data
-
-```{r, echo = FALSE}
-shinyAppFile(
-	here("R", "gaze_app", "app.R"), 
-	options = list(width = "100%", height = 700)
-)
-```
-
-## Growth curve analysis {.tabset .tab-pills}
-
-### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-$$
-\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
-(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
-(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
-(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
-(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
-(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
-(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
-$$
-
-### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-```
-
-### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-VarCorr(fit)$participant %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	gt(rowname_col = "term1") %>% 
-	fmt_number(columns = 2:9) %>% 
-	data_color(
-		columns = 2:9,
-		colors = col_numeric(
-			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
-			domain = c(-1, 1), alpha = 0.5
-		)
-	)
-
-```
-
-### Marginal means {.tabset .tab-pills}
-
-#### Overall
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7),
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	) 
-```
-
-#### By vocabulary size
-
-```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size <= median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size > median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### By location
-
-```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Barcelona", valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Barcelona") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Oxford") %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Oxford") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### {-}
-
-### {-}
-
-## Attrition {.tabset .tab-pills}
-
-### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocab) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0)
-
-```
-
-### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	div(style='height:600px; overflow-y: scroll', .)
-```
-
-### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	)
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill()) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-### By lexical frequency {.tabset .tab-pills}
-
-#### Prime frequency
-
-```{r attirion_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
-	drop_na(trial_type, frequency_prime_childes) %>% 
-	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
-	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target frequency
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### {-}
-
-### By familiarity {.tabset .tab-pills}
-
-#### Prime familiarity
-
-```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
-	drop_na(trial_type, familiarity_prime) %>% 
-	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
-	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target familiarity
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### {-}
-
-### By animacy {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
-	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_prime) %>% 
-	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
-	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### Target
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### {-}
-
-### By category {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
-	drop_na(trial_type, category_prime) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
-	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-### {-}
-
-## 21 month-old monolinguals {.tabset .tab-pills}
-
-### All data
-
-```{r fixef_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, lp)
-
-augment(fit_21_mon) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	plot_annotation(
-		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.
-B: mean observed probability of target looking, aggregated by participant.",
-		tag_levels = "A") &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Location
-
-```{r fixef_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, location)
-
-augment(fit_21_mon_location) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_location) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, location, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (median split)
-
-```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-sample_size <- participants %>% 
-	drop_na(vocab_size_l1_center) %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
-	count(age_group, vocab_cat, lp)
-
-augment(fit_21_mon_vocab) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, vocab_cat, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (balanced)
-
-```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-# by vocab (balanced)
-sample_size <- participants %>%
-	drop_na(vocab_size_l1_center) %>% 
-	filter(age_group=="21 months", lp=="Monolingual") %>% 
-	arrange(location, desc(vocab_size_l1_center)) %>% 
-	group_by(location) %>% 
-	mutate(vocab_index = row_number()) %>% 
-	ungroup() %>% 
-	filter(
-		((location=="Barcelona") & (vocab_index %in% 1:15)) |
-			((location=="Oxford")) & (vocab_index %in% seq(
-				max(vocab_index[location=="Oxford"])-15,
-				max(vocab_index[location=="Oxford"])))
-	) %>% 
-	nrow() %>% 
-	data.frame(n = .)
-
-augment(fit_21_mon_vocab_pct) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab_pct) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### {-}
-
-## Vocabulary {.tabset .tab-pills}
-
-### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### {-}
-
-## {-}
-
-# {-}
-
-# Appendix
-
-# References

### 2021-07-19 Rmd/report_04_gca_relaxed.Rmd
Separate report.Rmd into chunks

--- 2021-07-13 Rmd/report.Rmd
@@
 ---
-title: "Report"
-output:
-  html_document:
-    df_print: paged
-    toc: true
-    toc_depth: 5
-    toc_float: true
-runtime: shiny
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = FALSE,
-	message = TRUE,
-	warning = TRUE, 
-	cache.extra = knitr::rand_seed,
-	out.width = "100%",
-	results = "asis",
-	dev.args = list(png = list(type = "cairo"))
-)
-options(knitr.kable.NA = '-',
-		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
-		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
-)
+### Growth curve analysis {.tabset}
 
-```
-
-```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# load packages
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(lme4)
-library(broom.mixed)
-library(gt)
-library(patchwork)
-library(htmltools)
-library(wesanderson)
-library(shiny)
-library(here)
-
-# create functions
-logit_to_prob <- function(x) exp(x) / (1 + exp(x))
-
-theme_custom <- function(){
-	theme(
-		panel.background = element_rect(fill = "transparent"),
-		panel.grid = element_blank(),
-		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		panel.border = element_rect(fill = "transparent", colour = "black"),
-		text = element_text(colour = "black", size = 15),
-		axis.text = element_text(colour = "black")
-	)
-}
-theme_set(theme_custom())
-
-# load data
-gaze <- readRDS(here("Data", "Gaze", "d.rds"))
-stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
-attrition <- readRDS(here("Results", "attrition.rds")) %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
-participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocab) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-fit <- readRDS(here("Results", "fit.rds"))
-fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
-fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
-fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
-fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))
-
-```
-
-# Methods
-
-## Participants {.tabset .tabpills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-### Summary
-
-```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		),
-		age_group = str_remove(age_group, " months")
-	) %>%
-	drop_na(valid_status) %>% 
-	ggplot(aes(age_group, participant, colour = valid_status)) +
-	facet_grid(location~lp, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	geom_hline(yintercept = 0.2, linetype = "dashed") +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
-	theme(
-		legend.position = "right",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
-```
-
-### {-}
-
-## Stimuli {.tabset .tab-pills}
-
-### Frequency {.tabset .tab-pills}
-
-#### CHILDES vs. SUBTLEX
-
-```{r frequencies_compare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_data <- bind_rows(
-	stimuli %>%
-		distinct(test_language, prime, .keep_all = TRUE) %>%
-		select(prime, test_language, matches("frequency_prime")) %>% 
-		rename(word = prime, frequency_subtlex = frequency_prime_subtlex,
-			   frequency_childes = frequency_prime_childes),
-	stimuli %>%
-		distinct(test_language, target, .keep_all = TRUE) %>%
-		select(target, test_language, matches("frequency_target")) %>% 
-		rename(word = target, frequency_subtlex = frequency_target_subtlex,
-			   frequency_childes = frequency_target_childes),
-) %>% 
-	group_by(test_language) %>% 
-	mutate_at(vars(starts_with("frequency")), function(x) scale(x)[,1])
-
-frequency_compare_test <- group_split(frequency_compare_data) %>% 
-	set_names(c("Catalan", "English", "Spanish")) %>% 
-	map(function(x) {
-		a <- pull(x, frequency_subtlex)
-		b <- pull(x, frequency_childes)
-		tidy(cor.test(a, b), use = "complete.obs")
-	}) %>% 
-	bind_rows(.id = "test_language") %>% 
-	clean_names()
-
-```
-
-We tested the correlation between the (standardised) lexical frequencies of the stimuli extract from SUBTLEX (adult norms based on subtitles) and CHILDES (child norms based on audio transcriptions) within each test language using a Pearson's product-moment correlation at .05 confidence level (two-sided):
-
-```{r stimuli_frequency_compare_test, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_test %>% 
-	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
-	mutate(p_value = printp(p_value)) %>% 
-	gt(rowname_col = "test_language") %>% 
-	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
-	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
-	cols_label(
-		estimate = md("**Correlation**"),
-		statistic = md("***t***"),
-		parameter = md("***df***"),
-		p_value = md("***p***"),
-		conf_low = md("**CI<sub>95%<sub/>**")
-	)
-
-```
-
-```{r stimuli_frequency_compare_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
-
-frequency_compare_data %>% 
-	ggplot(aes(frequency_subtlex, frequency_childes, colour = test_language, fill = test_language)) +
-	facet_wrap(~test_language) +
-	geom_point(alpha = 0.5, stroke = 1, shape = 1) +
-	geom_smooth(method = "lm") +
-	labs(x = "SUBTLEX (adult norms)", y = "CHILDES (child norms)",
-		 colour = "Language", fill = "Language") +
-	coord_fixed() +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### CHILDES {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### SUBTLEX {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_subtlex_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_subtlex_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### {-}
-
-### Familiarity {.tabset .tab-pills}
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 10),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "_category"))) %>% 
-	drop_na() %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_grid(role~location~test_language) +
-	geom_col(position = position_fill()) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_fill_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_colour_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level")
-
-```
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tab-pills}
-
-## Raw data
-
-```{r, echo = FALSE}
-shinyAppFile(
-	here("R", "gaze_app", "app.R"), 
-	options = list(width = "100%", height = 700)
-)
-```
-
-## Growth curve analysis {.tabset .tab-pills}
-
-### Model details
+#### Model details
 
@@
 
-### Fixed effects
+#### Fixed effects
 
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit, method = "Wald") %>% 
+```{r fixed_effects_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_relaxed, method = "Wald") %>% 
 	as.data.frame() %>% 
@@
 	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
+	right_join(clean_names(tidy(fit_relaxed, effects = "fixed"))) %>% 
 	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
@@
 
-### Random effects
+#### Random effects
 
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r random_effects_participant_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 
-VarCorr(fit)$participant %>% 
+VarCorr(fit_relaxed)$participant %>% 
 	cov2cor() %>% 
@@
 
-### Marginal means {.tabset .tab-pills}
+#### Marginal means {.tabset }
 
-#### Overall
+##### Overall
 
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+```{r gaze_time_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants_relaxed %>% 
 	filter(valid_participant) %>% 
@@
 
-augment(fit) %>% 
+augment(fit_relaxed) %>% 
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
@@
 	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
 	theme_custom() +
@@
 
-#### By vocabulary size
+##### By vocabulary size
 
-```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants_relaxed %>% 
 	count(age_group, lp)
 
-augment(fit) %>% 
+augment(fit_relaxed) %>% 
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
@@
 	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
 	theme(
@@
 
-```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants_relaxed %>% 
 	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
@@
 
-#### By location
+##### By location
 
-```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+```{r gaze_time_location_barcelona_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants_relaxed %>% 
 	filter(location=="Barcelona", valid_participant) %>% 
@@
 
-augment(fit) %>% 
+augment(fit_relaxed) %>% 
 	left_join(distinct(participants, participant, location)) %>% 
@@
 
-```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
+```{r gaze_time_location_oxford_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants_relaxed %>% 
 	filter(location=="Oxford") %>% 
@@
 
-#### {-}
-
-### {-}
-
-## Attrition {.tabset .tab-pills}
-
-### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocab) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0)
-
-```
-
-### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	div(style='height:600px; overflow-y: scroll', .)
-```
-
-### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	)
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill()) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-### By lexical frequency {.tabset .tab-pills}
-
-#### Prime frequency
-
-```{r attirion_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
-	drop_na(trial_type, frequency_prime_childes) %>% 
-	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
-	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target frequency
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
+##### {-}
 
 #### {-}
-
-### By familiarity {.tabset .tab-pills}
-
-#### Prime familiarity
-
-```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
-	drop_na(trial_type, familiarity_prime) %>% 
-	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
-	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target familiarity
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### {-}
-
-### By animacy {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
-	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_prime) %>% 
-	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
-	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### Target
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### {-}
-
-### By category {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
-	drop_na(trial_type, category_prime) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
-	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-### {-}
-
-## 21 month-old monolinguals {.tabset .tab-pills}
-
-### All data
-
-```{r fixef_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, lp)
-
-augment(fit_21_mon) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	plot_annotation(
-		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.
-B: mean observed probability of target looking, aggregated by participant.",
-		tag_levels = "A") &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Location
-
-```{r fixef_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, location)
-
-augment(fit_21_mon_location) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_location) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, location, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (median split)
-
-```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-sample_size <- participants %>% 
-	drop_na(vocab_size_l1_center) %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
-	count(age_group, vocab_cat, lp)
-
-augment(fit_21_mon_vocab) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, vocab_cat, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (balanced)
-
-```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-# by vocab (balanced)
-sample_size <- participants %>%
-	drop_na(vocab_size_l1_center) %>% 
-	filter(age_group=="21 months", lp=="Monolingual") %>% 
-	arrange(location, desc(vocab_size_l1_center)) %>% 
-	group_by(location) %>% 
-	mutate(vocab_index = row_number()) %>% 
-	ungroup() %>% 
-	filter(
-		((location=="Barcelona") & (vocab_index %in% 1:15)) |
-			((location=="Oxford")) & (vocab_index %in% seq(
-				max(vocab_index[location=="Oxford"])-15,
-				max(vocab_index[location=="Oxford"])))
-	) %>% 
-	nrow() %>% 
-	data.frame(n = .)
-
-augment(fit_21_mon_vocab_pct) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab_pct) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### {-}
-
-## Vocabulary {.tabset .tab-pills}
-
-### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### {-}
-
-## {-}
-
-# {-}
-
-# Appendix
-
-# References

### 2021-07-19 Rmd/report_05_attrition_relaxed.Rmd
Separate report.Rmd into chunks

--- 2021-07-13 Rmd/report.Rmd
@@
 ---
-title: "Report"
-output:
-  html_document:
-    df_print: paged
-    toc: true
-    toc_depth: 5
-    toc_float: true
-runtime: shiny
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = FALSE,
-	message = TRUE,
-	warning = TRUE, 
-	cache.extra = knitr::rand_seed,
-	out.width = "100%",
-	results = "asis",
-	dev.args = list(png = list(type = "cairo"))
-)
-options(knitr.kable.NA = '-',
-		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
-		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
-)
+### Attrition {.tabset}
 
-```
+#### Summary
 
-```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# load packages
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(lme4)
-library(broom.mixed)
-library(gt)
-library(patchwork)
-library(htmltools)
-library(wesanderson)
-library(shiny)
-library(here)
-
-# create functions
-logit_to_prob <- function(x) exp(x) / (1 + exp(x))
-
-theme_custom <- function(){
-	theme(
-		panel.background = element_rect(fill = "transparent"),
-		panel.grid = element_blank(),
-		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		panel.border = element_rect(fill = "transparent", colour = "black"),
-		text = element_text(colour = "black", size = 15),
-		axis.text = element_text(colour = "black")
-	)
-}
-theme_set(theme_custom())
-
-# load data
-gaze <- readRDS(here("Data", "Gaze", "d.rds"))
-stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
-attrition <- readRDS(here("Results", "attrition.rds")) %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
-participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocab) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-fit <- readRDS(here("Results", "fit.rds"))
-fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
-fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
-fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
-fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))
-
-```
-
-# Methods
-
-## Participants {.tabset .tabpills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-### Summary
-
-```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
+```{r participants_cdi_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
 # plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		),
-		age_group = str_remove(age_group, " months")
-	) %>%
-	drop_na(valid_status) %>% 
-	ggplot(aes(age_group, participant, colour = valid_status)) +
-	facet_grid(location~lp, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	geom_hline(yintercept = 0.2, linetype = "dashed") +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
-	theme(
-		legend.position = "right",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
-```
-
-### {-}
-
-## Stimuli {.tabset .tab-pills}
-
-### Frequency {.tabset .tab-pills}
-
-#### CHILDES vs. SUBTLEX
-
-```{r frequencies_compare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_data <- bind_rows(
-	stimuli %>%
-		distinct(test_language, prime, .keep_all = TRUE) %>%
-		select(prime, test_language, matches("frequency_prime")) %>% 
-		rename(word = prime, frequency_subtlex = frequency_prime_subtlex,
-			   frequency_childes = frequency_prime_childes),
-	stimuli %>%
-		distinct(test_language, target, .keep_all = TRUE) %>%
-		select(target, test_language, matches("frequency_target")) %>% 
-		rename(word = target, frequency_subtlex = frequency_target_subtlex,
-			   frequency_childes = frequency_target_childes),
-) %>% 
-	group_by(test_language) %>% 
-	mutate_at(vars(starts_with("frequency")), function(x) scale(x)[,1])
-
-frequency_compare_test <- group_split(frequency_compare_data) %>% 
-	set_names(c("Catalan", "English", "Spanish")) %>% 
-	map(function(x) {
-		a <- pull(x, frequency_subtlex)
-		b <- pull(x, frequency_childes)
-		tidy(cor.test(a, b), use = "complete.obs")
-	}) %>% 
-	bind_rows(.id = "test_language") %>% 
-	clean_names()
-
-```
-
-We tested the correlation between the (standardised) lexical frequencies of the stimuli extract from SUBTLEX (adult norms based on subtitles) and CHILDES (child norms based on audio transcriptions) within each test language using a Pearson's product-moment correlation at .05 confidence level (two-sided):
-
-```{r stimuli_frequency_compare_test, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_test %>% 
-	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
-	mutate(p_value = printp(p_value)) %>% 
-	gt(rowname_col = "test_language") %>% 
-	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
-	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
-	cols_label(
-		estimate = md("**Correlation**"),
-		statistic = md("***t***"),
-		parameter = md("***df***"),
-		p_value = md("***p***"),
-		conf_low = md("**CI<sub>95%<sub/>**")
-	)
-
-```
-
-```{r stimuli_frequency_compare_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
-
-frequency_compare_data %>% 
-	ggplot(aes(frequency_subtlex, frequency_childes, colour = test_language, fill = test_language)) +
-	facet_wrap(~test_language) +
-	geom_point(alpha = 0.5, stroke = 1, shape = 1) +
-	geom_smooth(method = "lm") +
-	labs(x = "SUBTLEX (adult norms)", y = "CHILDES (child norms)",
-		 colour = "Language", fill = "Language") +
-	coord_fixed() +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### CHILDES {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### SUBTLEX {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_subtlex_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_subtlex_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### {-}
-
-### Familiarity {.tabset .tab-pills}
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 10),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "_category"))) %>% 
-	drop_na() %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_grid(role~location~test_language) +
-	geom_col(position = position_fill()) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_fill_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_colour_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level")
-
-```
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tab-pills}
-
-## Raw data
-
-```{r, echo = FALSE}
-shinyAppFile(
-	here("R", "gaze_app", "app.R"), 
-	options = list(width = "100%", height = 700)
-)
-```
-
-## Growth curve analysis {.tabset .tab-pills}
-
-### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-$$
-\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
-(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
-(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
-(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
-(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
-(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
-(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
-$$
-
-### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-```
-
-### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-VarCorr(fit)$participant %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	gt(rowname_col = "term1") %>% 
-	fmt_number(columns = 2:9) %>% 
-	data_color(
-		columns = 2:9,
-		colors = col_numeric(
-			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
-			domain = c(-1, 1), alpha = 0.5
-		)
-	)
-
-```
-
-### Marginal means {.tabset .tab-pills}
-
-#### Overall
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7),
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	) 
-```
-
-#### By vocabulary size
-
-```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size <= median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size > median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### By location
-
-```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Barcelona", valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Barcelona") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Oxford") %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Oxford") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### {-}
-
-### {-}
-
-## Attrition {.tabset .tab-pills}
-
-### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocab) %>% 
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>%
+	left_join(vocabulary) %>% 
 	drop_na(valid_participant) %>% 
@@
 
-### By location
+#### By location
 
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
+```{r trials_attrition_location_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
 # plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+attrition_location <- attrition_relaxed %>% 
+	left_join(select(participants_relaxed, participant, location)) %>% 
 	count(location, lp, age_group, trial_type, valid_status) %>% 
@@
 
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
+```{r attrition_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
 
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
+left_join(attrition_relaxed, select(participants_relaxed, age_group, location, lp, participant, date_test)) %>% 
 	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
@@
 
-### By participant
+#### By participant
 
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+```{r participants_attrition_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
 # plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+attrition_relaxed %>% 
+	left_join(select(participants_relaxed, participant, location)) %>% 
 	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
@@
 
-### By trial
+#### By trial
 
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+```{r trials_attrition_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
 # plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+attrition_relaxed %>% 
+	left_join(select(participants_relaxed, participant, location)) %>% 
 	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
@@
 
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+```{r trials_attrition_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
 # plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+attrition_relaxed %>% 
+	left_join(select(participants_relaxed, participant, location)) %>% 
 	count(location, lp, age_group, trial_type, valid_status) %>% 
@@
 
-### By lexical frequency {.tabset .tab-pills}
+#### By lexical frequency {.tabset }
 
-#### Prime frequency
+##### Prime frequency
 
-```{r attirion_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+```{r attrition_frequency_prime_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+sample_size <- attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, frequency_prime_childes) %>% 
+	count(trial_type, lp, age_group, valid_status)
+
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, frequency_prime_childes) %>% 
+	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_boxplot(fill = "white", width = 0.25,
+				 position =  position_dodge(width = 0.5),
+				 size = 1, outlier.colour = NA) +
+	geom_label(data = sample_size, aes(y = 2, label = n),
+			   position = position_dodge(width = 0.7), colour = "white") +
+	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
+	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		axis.text.x = element_text(size = 10),
+		axis.title = element_blank()
+	)
+```
+
+```{r attrition_frequency_prime_causes_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
 # plot participants
-attrition %>% 
+attrition_relaxed %>% 
 	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
@@
 
-#### Target frequency
+##### Target frequency
 
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
+```{r attrition_frequency_target_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+sample_size <- attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, frequency_target_childes) %>% 
+	count(trial_type, lp, age_group, valid_status)
+
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, frequency_target_childes) %>% 
+	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_boxplot(fill = "white", width = 0.25,
+				 position =  position_dodge(width = 0.5),
+				 size = 1, outlier.colour = NA) +
+	geom_label(data = sample_size, aes(y = 2, label = n),
+			   position = position_dodge(width = 0.7), colour = "white") +
+	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
+	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		axis.text.x = element_text(size = 10),
+		axis.title = element_blank()
+	)
+```
+
+```{r attrition_frequency_target_causes_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+attrition_relaxed %>% 
 	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
@@
 
-#### {-}
+##### {-}
 
-### By familiarity {.tabset .tab-pills}
+#### By familiarity {.tabset}
 
-#### Prime familiarity
+##### Prime familiarity
 
-```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+```{r attrition_familiarity_prime_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+sample_size <- attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, familiarity_prime) %>% 
+	count(trial_type, lp, age_group, valid_status)
+
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, familiarity_prime) %>% 
+	ggplot(aes(trial_type, familiarity_prime, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_boxplot(fill = "white", width = 0.25,
+				 position =  position_dodge(width = 0.5),
+				 size = 1, outlier.colour = NA) +
+	geom_label(data = sample_size, aes(y = 0.1, label = n),
+			   position = position_dodge(width = 0.7), colour = "white") +
+	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent, limits = c(0, 1)) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+```{r attrition_familiarity_prime_causes_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
 # plot participants
-attrition %>% 
+attrition_relaxed %>% 
 	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
@@
 
-#### Target familiarity
+##### Target familiarity
 
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+```{r attrition_familiarity_target_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+sample_size <- attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, familiarity_target) %>% 
+	count(trial_type, lp, age_group, valid_status)
+
+attrition_relaxed %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, familiarity_target) %>% 
+	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_boxplot(fill = "white", width = 0.25,
+				 position =  position_dodge(width = 0.5),
+				 size = 1, outlier.colour = NA) +
+	geom_label(data = sample_size, aes(y = 0.1, label = n),
+			   position = position_dodge(width = 0.7), colour = "white") +
+	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent, limits = c(0, 1)) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+```{r attrition_familiarity_target_causes_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
 # plot participants
-attrition %>% 
+attrition_relaxed %>% 
 	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
@@
 
-#### {-}
+##### {-}
 
-### By animacy {.tabset .tab-pills}
+#### By animacy {.tabset }
 
-#### Prime
+##### Prime
 
-```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
+```{r attrition_animacy_prime_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition_relaxed %>% 
 	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
@@
 
-#### Target
+##### Target
 
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
+```{r attrition_animacy_target_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition_relaxed %>% 
 	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
@@
 
-#### {-}
+##### {-}
 
-### By category {.tabset .tab-pills}
+#### By category {.tabset}
 
-#### Prime
+##### Prime
 
-```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
+```{r attrition_category_prime_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition_relaxed %>% 
 	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
@@
 
-#### Target
+##### Target
 
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
+```{r attrition_category_target_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition_relaxed %>% 
 	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
@@
 
-### {-}
-
-## 21 month-old monolinguals {.tabset .tab-pills}
-
-### All data
-
-```{r fixef_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, lp)
-
-augment(fit_21_mon) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	plot_annotation(
-		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.
-B: mean observed probability of target looking, aggregated by participant.",
-		tag_levels = "A") &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Location
-
-```{r fixef_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, location)
-
-augment(fit_21_mon_location) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_location) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, location, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (median split)
-
-```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-sample_size <- participants %>% 
-	drop_na(vocab_size_l1_center) %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
-	count(age_group, vocab_cat, lp)
-
-augment(fit_21_mon_vocab) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, vocab_cat, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (balanced)
-
-```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-# by vocab (balanced)
-sample_size <- participants %>%
-	drop_na(vocab_size_l1_center) %>% 
-	filter(age_group=="21 months", lp=="Monolingual") %>% 
-	arrange(location, desc(vocab_size_l1_center)) %>% 
-	group_by(location) %>% 
-	mutate(vocab_index = row_number()) %>% 
-	ungroup() %>% 
-	filter(
-		((location=="Barcelona") & (vocab_index %in% 1:15)) |
-			((location=="Oxford")) & (vocab_index %in% seq(
-				max(vocab_index[location=="Oxford"])-15,
-				max(vocab_index[location=="Oxford"])))
-	) %>% 
-	nrow() %>% 
-	data.frame(n = .)
-
-augment(fit_21_mon_vocab_pct) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab_pct) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### {-}
-
-## Vocabulary {.tabset .tab-pills}
-
-### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### {-}
-
-## {-}
-
-# {-}
-
-# Appendix
-
-# References
+#### {-}

### 2021-07-19 Rmd/report_08_vocabulary_relaxed.Rmd
Separate report.Rmd into chunks

--- 2021-07-13 Rmd/report.Rmd
@@
 ---
-title: "Report"
-output:
-  html_document:
-    df_print: paged
-    toc: true
-    toc_depth: 5
-    toc_float: true
-runtime: shiny
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = FALSE,
-	message = TRUE,
-	warning = TRUE, 
-	cache.extra = knitr::rand_seed,
-	out.width = "100%",
-	results = "asis",
-	dev.args = list(png = list(type = "cairo"))
-)
-options(knitr.kable.NA = '-',
-		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
-		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
-)
-
-```
-
-```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# load packages
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(lme4)
-library(broom.mixed)
-library(gt)
-library(patchwork)
-library(htmltools)
-library(wesanderson)
-library(shiny)
-library(here)
-
-# create functions
-logit_to_prob <- function(x) exp(x) / (1 + exp(x))
-
-theme_custom <- function(){
-	theme(
-		panel.background = element_rect(fill = "transparent"),
-		panel.grid = element_blank(),
-		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		panel.border = element_rect(fill = "transparent", colour = "black"),
-		text = element_text(colour = "black", size = 15),
-		axis.text = element_text(colour = "black")
-	)
-}
-theme_set(theme_custom())
-
-# load data
-gaze <- readRDS(here("Data", "Gaze", "d.rds"))
-stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
-attrition <- readRDS(here("Results", "attrition.rds")) %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
-participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocab) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-fit <- readRDS(here("Results", "fit.rds"))
-fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
-fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
-fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
-fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))
-
-```
-
-# Methods
-
-## Participants {.tabset .tabpills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-### Summary
-
-```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		),
-		age_group = str_remove(age_group, " months")
-	) %>%
-	drop_na(valid_status) %>% 
-	ggplot(aes(age_group, participant, colour = valid_status)) +
-	facet_grid(location~lp, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	geom_hline(yintercept = 0.2, linetype = "dashed") +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
-	theme(
-		legend.position = "right",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
-```
-
-### {-}
-
-## Stimuli {.tabset .tab-pills}
-
-### Frequency {.tabset .tab-pills}
-
-#### CHILDES vs. SUBTLEX
-
-```{r frequencies_compare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_data <- bind_rows(
-	stimuli %>%
-		distinct(test_language, prime, .keep_all = TRUE) %>%
-		select(prime, test_language, matches("frequency_prime")) %>% 
-		rename(word = prime, frequency_subtlex = frequency_prime_subtlex,
-			   frequency_childes = frequency_prime_childes),
-	stimuli %>%
-		distinct(test_language, target, .keep_all = TRUE) %>%
-		select(target, test_language, matches("frequency_target")) %>% 
-		rename(word = target, frequency_subtlex = frequency_target_subtlex,
-			   frequency_childes = frequency_target_childes),
-) %>% 
-	group_by(test_language) %>% 
-	mutate_at(vars(starts_with("frequency")), function(x) scale(x)[,1])
-
-frequency_compare_test <- group_split(frequency_compare_data) %>% 
-	set_names(c("Catalan", "English", "Spanish")) %>% 
-	map(function(x) {
-		a <- pull(x, frequency_subtlex)
-		b <- pull(x, frequency_childes)
-		tidy(cor.test(a, b), use = "complete.obs")
-	}) %>% 
-	bind_rows(.id = "test_language") %>% 
-	clean_names()
-
-```
-
-We tested the correlation between the (standardised) lexical frequencies of the stimuli extract from SUBTLEX (adult norms based on subtitles) and CHILDES (child norms based on audio transcriptions) within each test language using a Pearson's product-moment correlation at .05 confidence level (two-sided):
-
-```{r stimuli_frequency_compare_test, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_test %>% 
-	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
-	mutate(p_value = printp(p_value)) %>% 
-	gt(rowname_col = "test_language") %>% 
-	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
-	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
-	cols_label(
-		estimate = md("**Correlation**"),
-		statistic = md("***t***"),
-		parameter = md("***df***"),
-		p_value = md("***p***"),
-		conf_low = md("**CI<sub>95%<sub/>**")
-	)
-
-```
-
-```{r stimuli_frequency_compare_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
-
-frequency_compare_data %>% 
-	ggplot(aes(frequency_subtlex, frequency_childes, colour = test_language, fill = test_language)) +
-	facet_wrap(~test_language) +
-	geom_point(alpha = 0.5, stroke = 1, shape = 1) +
-	geom_smooth(method = "lm") +
-	labs(x = "SUBTLEX (adult norms)", y = "CHILDES (child norms)",
-		 colour = "Language", fill = "Language") +
-	coord_fixed() +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### CHILDES {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### SUBTLEX {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_subtlex_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_subtlex_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### {-}
-
-### Familiarity {.tabset .tab-pills}
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 10),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "_category"))) %>% 
-	drop_na() %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_grid(role~location~test_language) +
-	geom_col(position = position_fill()) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_fill_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_colour_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level")
-
-```
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tab-pills}
-
-## Raw data
-
-```{r, echo = FALSE}
-shinyAppFile(
-	here("R", "gaze_app", "app.R"), 
-	options = list(width = "100%", height = 700)
-)
-```
-
-## Growth curve analysis {.tabset .tab-pills}
-
-### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-$$
-\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
-(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
-(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
-(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
-(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
-(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
-(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
-$$
-
-### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-```
-
-### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-VarCorr(fit)$participant %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	gt(rowname_col = "term1") %>% 
-	fmt_number(columns = 2:9) %>% 
-	data_color(
-		columns = 2:9,
-		colors = col_numeric(
-			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
-			domain = c(-1, 1), alpha = 0.5
-		)
-	)
-
-```
-
-### Marginal means {.tabset .tab-pills}
-
-#### Overall
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7),
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	) 
-```
-
-#### By vocabulary size
-
-```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size <= median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size > median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### By location
-
-```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Barcelona", valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Barcelona") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Oxford") %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Oxford") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### {-}
-
-### {-}
-
-## Attrition {.tabset .tab-pills}
-
-### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocab) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0)
-
-```
-
-### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	div(style='height:600px; overflow-y: scroll', .)
-```
-
-### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	)
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill()) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-### By lexical frequency {.tabset .tab-pills}
-
-#### Prime frequency
-
-```{r attirion_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
-	drop_na(trial_type, frequency_prime_childes) %>% 
-	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
-	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target frequency
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### {-}
-
-### By familiarity {.tabset .tab-pills}
-
-#### Prime familiarity
-
-```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
-	drop_na(trial_type, familiarity_prime) %>% 
-	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
-	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target familiarity
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### {-}
-
-### By animacy {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
-	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_prime) %>% 
-	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
-	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### Target
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### {-}
-
-### By category {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
-	drop_na(trial_type, category_prime) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
-	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-### {-}
-
-## 21 month-old monolinguals {.tabset .tab-pills}
-
-### All data
-
-```{r fixef_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, lp)
-
-augment(fit_21_mon) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	plot_annotation(
-		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.
-B: mean observed probability of target looking, aggregated by participant.",
-		tag_levels = "A") &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Location
-
-```{r fixef_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, location)
-
-augment(fit_21_mon_location) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_location) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, location, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (median split)
-
-```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-sample_size <- participants %>% 
-	drop_na(vocab_size_l1_center) %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
-	count(age_group, vocab_cat, lp)
-
-augment(fit_21_mon_vocab) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, vocab_cat, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (balanced)
-
-```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-# by vocab (balanced)
-sample_size <- participants %>%
-	drop_na(vocab_size_l1_center) %>% 
-	filter(age_group=="21 months", lp=="Monolingual") %>% 
-	arrange(location, desc(vocab_size_l1_center)) %>% 
-	group_by(location) %>% 
-	mutate(vocab_index = row_number()) %>% 
-	ungroup() %>% 
-	filter(
-		((location=="Barcelona") & (vocab_index %in% 1:15)) |
-			((location=="Oxford")) & (vocab_index %in% seq(
-				max(vocab_index[location=="Oxford"])-15,
-				max(vocab_index[location=="Oxford"])))
-	) %>% 
-	nrow() %>% 
-	data.frame(n = .)
-
-augment(fit_21_mon_vocab_pct) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab_pct) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### {-}
-
-## Vocabulary {.tabset .tab-pills}
-
-### L1 vocabulary
+#### L1 vocabulary
 
@@
 
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
+```{r vocabulary_l1_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants_relaxed %>% 
 	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
@@
 # vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+participants_relaxed %>% 
 	drop_na(lp) %>%
@@
 
-### Total vocabulary
+#### Total vocabulary
 
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
+```{r vocabulary_total_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants_relaxed %>% 
 	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
@@
 # vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, age_group, valid_participant)) %>% 
 	drop_na(lp) %>%
@@
 
-### Conceptual vocabulary
+#### Conceptual vocabulary
 
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
+```{r vocabulary_conceptual_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants_relaxed %>% 
 	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
@@
 
+#### {-}
+
 ### {-}
-
-## {-}
-
-# {-}
-
-# Appendix
-
-# References

### 2021-07-19 Rmd/report.Rmd

--- 2021-07-13 Rmd/report.Rmd
@@
 library(shiny)
+library(tidytext)
 library(here)
 
-# create functions
-logit_to_prob <- function(x) exp(x) / (1 + exp(x))
+# load objects
+tar_load(participants)
+tar_load(stimuli)
+tar_load(vocabulary)
 
-theme_custom <- function(){
-	theme(
-		panel.background = element_rect(fill = "transparent"),
-		panel.grid = element_blank(),
-		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
-		panel.border = element_rect(fill = "transparent", colour = "black"),
-		text = element_text(colour = "black", size = 15),
-		axis.text = element_text(colour = "black")
-	)
-}
-theme_set(theme_custom())
+# stringent version
+tar_load(gaze)
+tar_load(attrition)
+tar_load(fit)
+tar_load(fit_21_mon)
+tar_load(fit_21_mon_vocab_split)
+tar_load(fit_21_mon_vocab_balanced)
+tar_load(fit_21_mon_location)
 
-# load data
-gaze <- readRDS(here("Data", "Gaze", "d.rds"))
-stimuli <- readRDS(here("Data", "Stimuli", "stimuli.rds"))
-attrition <- readRDS(here("Results", "attrition.rds")) %>% 
+# relaxed version
+tar_load(gaze_relaxed)
+tar_load(attrition_relaxed)
+tar_load(fit_relaxed)
+tar_load(fit_21_mon_relaxed)
+tar_load(fit_21_mon_vocab_split_relaxed)
+tar_load(fit_21_mon_vocab_balanced_relaxed)
+tar_load(fit_21_mon_location_relaxed)
+
+theme_set(theme_custom()) # in utils.R
+```
+
+```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+attrition <- attrition %>% 
 	mutate(
@@
 		))
-vocab <- readRDS(here("Data", "Vocabulary", "vocabulary.rds"))
-participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
+
+attrition_relaxed <- attrition_relaxed %>% 
+	mutate(
+		valid_gaze = valid_gaze_prime & valid_gaze_target,
+		valid_status = case_when(
+			!valid_vocab ~ "Invalid vocabulary",
+			!valid_gaze ~ "Invalid gaze",
+			!valid_participant ~ "Invalid participant",
+			TRUE ~ "Valid"
+		))
+
+participants_stringent <- participants %>% 
 	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
 	drop_na(participant) %>% 
-	left_join(vocab) %>% 
+	left_join(vocabulary) %>% 
 	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-fit <- readRDS(here("Results", "fit.rds"))
-fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))
-fit_21_mon_vocab <- readRDS(here("Results", "fit_21_mon_vocab.rds"))
-fit_21_mon_vocab_pct <- readRDS(here("Results", "fit_21_mon_vocab_pct.rds"))
-fit_21_mon_location <- readRDS(here("Results", "fit_21_mon_location.rds"))
+
+participants_relaxed <- participants %>% 
+	left_join(distinct(attrition_relaxed, participant, age_group, valid_participant)) %>% 
+	drop_na(participant) %>% 
+	left_join(vocabulary) %>% 
+	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
 
@@
 
-## Participants {.tabset .tabpills}
+## Participants {.tabset .tabset-pills}
 
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
+### Stringent criteria {.tabset}
 
-### Summary
-
-```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
+```{r child="report_00_participants_stringent.Rmd"}
 ```
 
-### Longitudinal
+### Relaxed criteria {.tabset}
 
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		),
-		age_group = str_remove(age_group, " months")
-	) %>%
-	drop_na(valid_status) %>% 
-	ggplot(aes(age_group, participant, colour = valid_status)) +
-	facet_grid(location~lp, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	geom_hline(yintercept = 0.2, linetype = "dashed") +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
-	theme(
-		legend.position = "right",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
+```{r child="report_00_participants_relaxed.Rmd"}
 ```
 
-### {-}
+## Stimuli
 
-## Stimuli {.tabset .tab-pills}
-
-### Frequency {.tabset .tab-pills}
-
-#### CHILDES vs. SUBTLEX
-
-```{r frequencies_compare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_data <- bind_rows(
-	stimuli %>%
-		distinct(test_language, prime, .keep_all = TRUE) %>%
-		select(prime, test_language, matches("frequency_prime")) %>% 
-		rename(word = prime, frequency_subtlex = frequency_prime_subtlex,
-			   frequency_childes = frequency_prime_childes),
-	stimuli %>%
-		distinct(test_language, target, .keep_all = TRUE) %>%
-		select(target, test_language, matches("frequency_target")) %>% 
-		rename(word = target, frequency_subtlex = frequency_target_subtlex,
-			   frequency_childes = frequency_target_childes),
-) %>% 
-	group_by(test_language) %>% 
-	mutate_at(vars(starts_with("frequency")), function(x) scale(x)[,1])
-
-frequency_compare_test <- group_split(frequency_compare_data) %>% 
-	set_names(c("Catalan", "English", "Spanish")) %>% 
-	map(function(x) {
-		a <- pull(x, frequency_subtlex)
-		b <- pull(x, frequency_childes)
-		tidy(cor.test(a, b), use = "complete.obs")
-	}) %>% 
-	bind_rows(.id = "test_language") %>% 
-	clean_names()
-
+```{r child="report_01_stimuli.Rmd"}
 ```
-
-We tested the correlation between the (standardised) lexical frequencies of the stimuli extract from SUBTLEX (adult norms based on subtitles) and CHILDES (child norms based on audio transcriptions) within each test language using a Pearson's product-moment correlation at .05 confidence level (two-sided):
-
-```{r stimuli_frequency_compare_test, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_test %>% 
-	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
-	mutate(p_value = printp(p_value)) %>% 
-	gt(rowname_col = "test_language") %>% 
-	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
-	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
-	cols_label(
-		estimate = md("**Correlation**"),
-		statistic = md("***t***"),
-		parameter = md("***df***"),
-		p_value = md("***p***"),
-		conf_low = md("**CI<sub>95%<sub/>**")
-	)
-
-```
-
-```{r stimuli_frequency_compare_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
-
-frequency_compare_data %>% 
-	ggplot(aes(frequency_subtlex, frequency_childes, colour = test_language, fill = test_language)) +
-	facet_wrap(~test_language) +
-	geom_point(alpha = 0.5, stroke = 1, shape = 1) +
-	geom_smooth(method = "lm") +
-	labs(x = "SUBTLEX (adult norms)", y = "CHILDES (child norms)",
-		 colour = "Language", fill = "Language") +
-	coord_fixed() +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### CHILDES {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### SUBTLEX {.tabset .tab-pills}
-
-##### Prime
-
-```{r stimuli_frequency_subtlex_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_subtlex_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### {-}
-
-### Familiarity {.tabset .tab-pills}
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), xmin = familiarity_ci_lower_prime, xmax = familiarity_ci_upper_prime, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), xmin = familiarity_ci_lower_target, xmax = familiarity_ci_upper_target, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 10),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "_category"))) %>% 
-	drop_na() %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_grid(role~location~test_language) +
-	geom_col(position = position_fill()) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_fill_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_colour_manual(values = wes_palette(name = "Zissou1", n = 9, type = "continuous")) +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-### {-}
 
@@
 
+```{r child="report_02_procedure.Rmd"}
+```
+
 ## Data analysis
 
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level")
-
+```{r child="report_03_data-analysis.Rmd"}
 ```
@@
 
-# Results {.tabset .tab-pills}
+# Results {.tabset .tabset-pills}
 
-## Raw data
+## Gaze {.tabset .tabset-pills}
 
-```{r, echo = FALSE}
-shinyAppFile(
-	here("R", "gaze_app", "app.R"), 
-	options = list(width = "100%", height = 700)
-)
+### Stringent criteria {.tabset}
+
+```{r child="report_04_gca_stringent.Rmd"}
 ```
 
-## Growth curve analysis {.tabset .tab-pills}
-
-### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
+```{r child="report_05_attrition_stringent.Rmd"}
 ```
 
-The formal implementation of this model is:
-
-$$
-\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
-(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
-(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
-(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
-(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
-(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
-(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
-$$
-
-### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
+```{r child="report_06_21-mon_stringent.Rmd"}
 ```
 
-### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-VarCorr(fit)$participant %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	gt(rowname_col = "term1") %>% 
-	fmt_number(columns = 2:9) %>% 
-	data_color(
-		columns = 2:9,
-		colors = col_numeric(
-			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
-			domain = c(-1, 1), alpha = 0.5
-		)
-	)
-
+```{r child="report_07_raw_relaxed.Rmd"}
 ```
 
-### Marginal means {.tabset .tab-pills}
+### Relaxed criteria {.tabset}
 
-#### Overall
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme_custom() +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7),
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	) 
+```{r child="report_04_gca_relaxed.Rmd"}
 ```
 
-#### By vocabulary size
-
-```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size <= median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
+```{r child="report_05_attrition_relaxed.Rmd"}
 ```
 
-```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size > median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
+```{r child="report_06_21-mon_relaxed.Rmd"}
 ```
 
-#### By location
-
-```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Barcelona", valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Barcelona") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(location=="Oxford") %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Oxford") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-#### {-}
-
-### {-}
-
-## Attrition {.tabset .tab-pills}
-
-### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocab) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0)
-
-```
-
-### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	div(style='height:600px; overflow-y: scroll', .)
-```
-
-### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	)
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill()) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-### By lexical frequency {.tabset .tab-pills}
-
-#### Prime frequency
-
-```{r attirion_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
-	drop_na(trial_type, frequency_prime_childes) %>% 
-	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
-	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target frequency
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### {-}
-
-### By familiarity {.tabset .tab-pills}
-
-#### Prime familiarity
-
-```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
-	drop_na(trial_type, familiarity_prime) %>% 
-	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
-	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target familiarity
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### {-}
-
-### By animacy {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
-	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_prime) %>% 
-	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
-	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### Target
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-#### {-}
-
-### By category {.tabset .tab-pills}
-
-#### Prime
-
-```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
-	drop_na(trial_type, category_prime) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
-	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### Target
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
+```{r child="report_07_raw_relaxed.Rmd"}
 ```
@@
 
-## 21 month-old monolinguals {.tabset .tab-pills}
+## Vocabulary {.tabset .tabset-pills}
 
-### All data
+### Stringent criteria {.tabset}
 
-```{r fixef_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
+```{r child="report_08_vocabulary_stringent.Rmd"}
 ```
 
-```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, lp)
+### Relaxed criteria {.tabset}
 
-augment(fit_21_mon) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	plot_annotation(
-		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.
-B: mean observed probability of target looking, aggregated by participant.",
-		tag_levels = "A") &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Location
-
-```{r fixef_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-
-main_effects
-
-```
-
-```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	count(age_group, location)
-
-augment(fit_21_mon_location) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_location) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, location, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
-	facet_wrap(~location, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (median split)
-
-```{r fixef_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_vocab, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-sample_size <- participants %>% 
-	drop_na(vocab_size_l1_center) %>% 
-	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
-	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
-	count(age_group, vocab_cat, lp)
-
-augment(fit_21_mon_vocab) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, vocab_cat, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	facet_wrap(~vocab_cat, ncol = 1) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### Vocabulary (balanced)
-
-```{r fixef_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-main_effects <- confint.merMod(fit_21_mon_vocab_pct, method = "Wald") %>% 
-	as.data.frame() %>% 
-	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab_pct, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#ffc7a1")
-		),
-		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
-		)
-	)
-main_effects
-
-```
-
-```{r gaze_time_21_mon_vocab_pct, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-# by vocab (balanced)
-sample_size <- participants %>%
-	drop_na(vocab_size_l1_center) %>% 
-	filter(age_group=="21 months", lp=="Monolingual") %>% 
-	arrange(location, desc(vocab_size_l1_center)) %>% 
-	group_by(location) %>% 
-	mutate(vocab_index = row_number()) %>% 
-	ungroup() %>% 
-	filter(
-		((location=="Barcelona") & (vocab_index %in% 1:15)) |
-			((location=="Oxford")) & (vocab_index %in% seq(
-				max(vocab_index[location=="Oxford"])-15,
-				max(vocab_index[location=="Oxford"])))
-	) %>% 
-	nrow() %>% 
-	data.frame(n = .)
-
-augment(fit_21_mon_vocab_pct) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  colour = "black", fill = "black", show.legend = FALSE) +
-	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		legend.position = "left"
-	) +
-
-	augment(fit_21_mon_vocab_pct) %>% 
-	mutate(elog_prob = logit_to_prob(elog)) %>% 
-	group_by(participant, trial_type) %>% 
-	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
-	ggplot(aes(trial_type, elog_prob)) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
-	geom_boxplot(width = 0.1, outlier.colour = NA) +
-	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		axis.title = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_blank(),
-		axis.text.y = element_blank()
-	) +
-	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
-	theme_custom() &
-	theme(
-		legend.position = "right",
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	)
-```
-
-### {-}
-
-## Vocabulary {.tabset .tab-pills}
-
-### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, colour = "black", outlier.colour = NA,
-		position = position_dodge(width = 0.75)
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "black", fill = "black", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
+```{r child="report_08_vocabulary_relaxed.Rmd"}
 ```
@@
 
-# {-}
-
 # Appendix

### 2021-07-19 Rmd/report_03_data-analysis.Rmd

---
---

## Data analysis

### Vocabulary data

We collected vocabulary data from participants. In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment. In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it. In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language. In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists. All checklists included the words involved in the trial lists. When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*. Each response to either checklist was aggregated to produce several vocabulary measures:

* **Total vocabulary**: total number of words the child knows, summing up both languages. For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language). For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages. For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.

Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.

## Gaze data {.tabset .tabset-pills}

Each trial was divided into 100 ms time bins. for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin. Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).

### Workflow

```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
DiagrammeR::grViz("digraph {
  graph [layout = dot, rankdir = TB]

  node [shape = rectangle, fontname = 'Arial']        
  rec1 [label = 'Merge Barcelona and Oxford data']
  rec2 [label = 'Impute missing/invalid samples (pending)']
  rec2 [label = 'Extract fixations (pending)']
  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
  rec4 [label = 'Divide each trial into 100 ms time bins']
  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
  rec6 [label = 'Exclude time bins 1-3 (pending)']
  rec7 [label = 'Apply trial-level inclusion criteria']
  rec8 [label = 'Apply participant-level inclusion criteria']

  # edge definitions with the node IDs
  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
  }", 
  height = 500)
```

### Inclusion criteria

#### Trial-level inclusion criteria

* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
* At least one sample in target and one sample in distractor
* Participant understands prime word in both languages
* Participant knows the target word in the test language
* Participant knows the distractor word in the test language

#### Participant-level inclusion criteria

* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
* $\geq$ 36 gestational weeks
* $\geq$ 2,800g birth weight
* No diagnosed developmental, hearing, or visual disorders
* Not exposed to more than 10% to a 3rd language

### Input variables

* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
* Trial type (`trial_type1` and `trial_type2`). Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*. We coded two contrasts: `trial_type1`, comparing related trials vs. unrelated trials (*Cognate* + *Non-cognate* vs. *Unrelated*), and `trial_type2`, comparing *Cognate* vs. *Non-cognate* trials. These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].

```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

contrasts(gaze$trial_type) %>% 
	as.data.frame() %>% 
	set_names(paste0("trial_type", 1:2)) %>% 
	rownames_to_column("level") %>% 
	gt(rowname_col = "level")

```

### {-}

## {-}

### 2021-07-19 Rmd/report_04_gca_stringent.Rmd

---
---

### Growth curve analysis {.tabset }

#### Model details

We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:

```
elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
```

The formal implementation of this model is:

$$
\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
$$

#### Fixed effects

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects
```

#### Random effects

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

VarCorr(fit)$participant %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	gt(rowname_col = "term1") %>% 
	fmt_number(columns = 2:9) %>% 
	data_color(
		columns = 2:9,
		colors = col_numeric(
			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
			domain = c(-1, 1), alpha = 0.5
		)
	)

```

#### Marginal means {.tabset }

##### Overall

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(valid_participant) %>% 
	count(age_group, lp)

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7),
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) 
```

##### By vocabulary size

```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	count(age_group, lp)

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size <= median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size > median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

##### By location

```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	count(age_group, lp)

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Barcelona") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(location=="Oxford") %>% 
	count(age_group, lp)

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Oxford") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

##### {-}

#### {-}

### 2021-07-19 Rmd/report_05_attrition_stringent.Rmd

---
---

### Attrition {.tabset }

#### Summary

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants_stringent %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

#### By location

```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
# plot participants
attrition_location <- attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type)

attrition_location %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +

	attrition_location %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +

	plot_layout(guides = "collect", ncol = 1) &
	scale_y_continuous(labels = percent) &
	coord_flip() &
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 10),
		axis.title = element_blank()
	)
```

#### By group

This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).

```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}

left_join(attrition, select(participants_stringent, age_group, location, lp, participant, date_test)) %>% 
	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0)

```

#### By participant

```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
	div(style='height:600px; overflow-y: scroll', .)
```

#### By trial

```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
	count() %>% 
	ungroup() %>%
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
	clean_names() %>% 
	gt(groupname_col = c("location", "lp")) %>% 
	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
	cols_label(
		location = "Location",
		lp = "Group",
		trial_type = "Trial type",
		x21_months_not_valid = "Not valid",
		x21_months_valid = "Valid",
		x25_months_not_valid = "Not valid",
		x25_months_valid = "Valid",
		x30_months_not_valid = "Not valid",
		x30_months_valid = "Valid"
	)

```

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

#### By lexical frequency {.tabset}

##### Prime frequency

```{r attrition_frequency_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n),
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(size = 10),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### Target frequency

```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n),
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(size = 10),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### {-}

#### By familiarity {.tabset}

##### Prime familiarity

```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	ggplot(aes(trial_type, familiarity_prime, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n),
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### Target familiarity

```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n),
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### {-}

#### By animacy {.tabset }

##### Prime

```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_prime) %>% 
	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

```

##### Target

```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

```

##### {-}

#### By category {.tabset }

##### Prime

```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
	drop_na(trial_type, category_prime) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### Target

```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
	drop_na(trial_type, category_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

#### {-}

### Raw data

```{r, echo = FALSE}
shinyAppFile(
	here("R", "gaze_app", "app.R"), 
	options = list(width = "100%", height = 700)
)
```

### 2021-07-19 Rmd/report_06_21-mon_relaxed.Rmd

---
---

### 21 month-old monolinguals {.tabset }

#### All data

```{r fixef_21_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_relaxed, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_relaxed, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects

```

```{r gaze_time_21_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, lp)

augment(fit_21_mon_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_relaxed) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	plot_annotation(
		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis. B: mean observed probability of target looking, aggregated by participant.",
		tag_levels = "A") &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

#### Location

```{r fixef_21_mon_location_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_location_relaxed, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_location_relaxed, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects

```

```{r gaze_time_21_mon_location_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, location)

augment(fit_21_mon_location_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~location, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(
		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_location_relaxed) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, location, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~location, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

#### Vocabulary (median split)

```{r fixef_21_mon_vocab_split_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_vocab_split_relaxed, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab_split_relaxed, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

```

```{r gaze_time_21_mon_vocab_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

sample_size <- participants_relaxed %>% 
	drop_na(vocab_size_l1_center) %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants_relaxed$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
	count(age_group, vocab_cat, lp)

augment(fit_21_mon_vocab_split_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab_split_relaxed) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, vocab_cat, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

#### Vocabulary (balanced)

```{r fixef_21_mon_vocab_balanced_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

main_effects <- confint.merMod(fit_21_mon_vocab_balanced_relaxed, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab_balanced_relaxed, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

```

```{r gaze_time_21_mon_vocab_balanced_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# by vocabulary (balanced)
sample_size <- participants_relaxed %>%
	drop_na(vocab_size_l1_center) %>% 
	filter(age_group=="21 months", lp=="Monolingual") %>% 
	arrange(location, desc(vocab_size_l1_center)) %>% 
	group_by(location) %>% 
	mutate(vocab_index = row_number()) %>% 
	ungroup() %>% 
	filter(
		((location=="Barcelona") & (vocab_index %in% 1:15)) |
			((location=="Oxford")) & (vocab_index %in% seq(
				max(vocab_index[location=="Oxford"])-15,
				max(vocab_index[location=="Oxford"])))
	) %>% 
	nrow() %>% 
	data.frame(n = .)

augment(fit_21_mon_vocab_balanced_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(
		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab_balanced_relaxed) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

### {-}

### 2021-07-19 Rmd/report_06_21-mon_stringent.Rmd

---
---

### 21 month-old monolinguals {.tabset }

#### All data

```{r fixef_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects

```

```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, lp)

augment(fit_21_mon) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	plot_annotation(
		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis. B: mean observed probability of target looking, aggregated by participant.",
		tag_levels = "A") &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

#### Location

```{r fixef_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects

```

```{r gaze_time_21_mon_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, location)

augment(fit_21_mon_location) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~location, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(
		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_location) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, location, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~location, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

#### Vocabulary (median split)

```{r fixef_21_mon_vocab_split, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_vocab_split, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab_split, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

```

```{r gaze_time_21_mon_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

sample_size <- participants_stringent %>% 
	drop_na(vocab_size_l1_center) %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	mutate(vocab_cat = ifelse(vocab_size_l1_center > median(participants_stringent$vocab_size_l1_center, na.rm = TRUE), "Above median", "Below median")) %>% 
	count(age_group, vocab_cat, lp)

augment(fit_21_mon_vocab_split) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab_split) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, vocab_cat, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	facet_wrap(~vocab_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes( fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

#### Vocabulary (balanced)

```{r fixef_21_mon_vocab_balanced, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

main_effects <- confint.merMod(fit_21_mon_vocab_balanced, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_vocab_balanced, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
main_effects

```

```{r gaze_time_21_mon_vocab_balanced, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# by vocabulary (balanced)
sample_size <- participants_stringent %>%
	drop_na(vocab_size_l1_center) %>% 
	filter(age_group=="21 months", lp=="Monolingual") %>% 
	arrange(location, desc(vocab_size_l1_center)) %>% 
	group_by(location) %>% 
	mutate(vocab_index = row_number()) %>% 
	ungroup() %>% 
	filter(
		((location=="Barcelona") & (vocab_index %in% 1:15)) |
			((location=="Oxford")) & (vocab_index %in% seq(
				max(vocab_index[location=="Oxford"])-15,
				max(vocab_index[location=="Oxford"])))
	) %>% 
	nrow() %>% 
	data.frame(n = .)

augment(fit_21_mon_vocab_balanced) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(
		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
		fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_vocab_balanced) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob)) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(aes(fill = trial_type, colour = trial_type), show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA) +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

#### {-}

### 2021-07-19 Rmd/report_08_vocabulary_stringent.Rmd

---
---

#### L1 vocabulary

This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis. Results are presented separately for each age group. The shape of the violins, represents the distribution of the vocabulary sizes. The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values. vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure. for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.

```{r vocabulary_l1_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants_stringent %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, location)

# vocabulary
participants_stringent %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_grid(location~age_group) +
	# geom_violin(
	# 	position = position_dodge(width = 0.75),
	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
	# ) + 
	geom_hline(yintercept = 0.5, colour = "grey") +
	geom_point(
		aes(lp, vocab_size_l1),
		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_boxplot(
		aes(lp, vocab_size_l1, colour = lp, fill = lp),
		width = 0.25, colour = "black", outlier.colour = NA,
		position = position_dodge(width = 0.75)
	) +
	geom_text(
		data = sample_size,
		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
		colour = "black", fill = "black", show.legend = FALSE
	) +
	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	)

```

#### Total vocabulary

```{r vocabulary_total_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants_stringent %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, location)

# vocabulary
participants_stringent %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_grid(location~age_group) +
	# geom_violin(
	# 	position = position_dodge(width = 0.75),
	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
	# ) + 
	geom_hline(yintercept = 0.5, colour = "grey") +
	geom_point(
		aes(lp, vocab_size_total),
		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_boxplot(
		aes(lp, vocab_size_total, colour = lp, fill = lp),
		width = 0.25, colour = "black", outlier.colour = NA,
		position = position_dodge(width = 0.75)
	) +
	geom_text(
		data = sample_size,
		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
		colour = "black", fill = "black", show.legend = FALSE
	) +
	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	)

```

#### Conceptual vocabulary

```{r vocabulary_conceptual_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants_stringent %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, location)

# vocabulary
participants_stringent %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_grid(location~age_group) +
	# geom_violin(
	# 	position = position_dodge(width = 0.75),
	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
	# ) + 
	geom_hline(yintercept = 0.5, colour = "grey") +
	geom_point(
		aes(lp, vocab_size_conceptual),
		shape = 1, colour = "black", alpha = 0.5, size = 1, stroke = 1,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_boxplot(
		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
		width = 0.25, colour = "black", outlier.colour = NA,
		position = position_dodge(width = 0.75)
	) +
	geom_text(
		data = sample_size,
		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
		colour = "black", fill = "black", show.legend = FALSE
	) +
	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	)

```

#### {-}

### 2021-07-23 Rmd/report.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

@@
 tar_load(vocabulary)
-
-# stringent version
 tar_load(gaze)
+tar_load(gaze_relaxed)
 tar_load(attrition)
-tar_load(fit)
-tar_load(fit_21_mon)
-tar_load(fit_21_mon_vocab_split)
-tar_load(fit_21_mon_vocab_balanced)
-tar_load(fit_21_mon_location)
-
-# relaxed version
-tar_load(gaze_relaxed)
 tar_load(attrition_relaxed)
-tar_load(fit_relaxed)
-tar_load(fit_21_mon_relaxed)
-tar_load(fit_21_mon_vocab_split_relaxed)
-tar_load(fit_21_mon_vocab_balanced_relaxed)
-tar_load(fit_21_mon_location_relaxed)
+tar_load(attrition_counter)
+tar_load(attrition_relaxed_counter)
+tar_load(model_fits)
+tar_load(model_fits_relaxed)
 
@@
 
+attrition_counter <- attrition_counter %>% 
+	mutate(
+		valid_gaze = valid_gaze_prime & valid_gaze_target,
+		valid_status = case_when(
+			!valid_vocab ~ "Invalid vocabulary",
+			!valid_gaze ~ "Invalid gaze",
+			!valid_participant ~ "Invalid participant",
+			!valid_counter ~ "Invalid counter",
+			TRUE ~ "Valid"
+		))
+
+attrition_relaxed_counter <- attrition_relaxed_counter %>% 
+	mutate(
+		valid_gaze = valid_gaze_prime & valid_gaze_target,
+		valid_status = case_when(
+			!valid_vocab ~ "Invalid vocabulary",
+			!valid_gaze ~ "Invalid gaze",
+			!valid_participant ~ "Invalid participant",
+			!valid_counter ~ "Invalid counter",
+			TRUE ~ "Valid"
+		))
+
 participants_stringent <- participants %>% 
@@
 	left_join(distinct(attrition_relaxed, participant, age_group, valid_participant)) %>% 
+	drop_na(participant) %>% 
+	left_join(vocabulary) %>% 
+	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
+
+participants_counter <- participants %>% 
+	left_join(distinct(attrition_counter, participant, age_group, valid_participant)) %>% 
+	drop_na(participant) %>% 
+	left_join(vocabulary) %>% 
+	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
+
+participants_relaxed_counter <- participants %>% 
+	left_join(distinct(attrition_relaxed_counter, participant, age_group, valid_participant)) %>% 
 	drop_na(participant) %>% 
@@
 
-```{r child="report_05_attrition_stringent.Rmd"}
-```
-
-```{r child="report_06_21-mon_stringent.Rmd"}
-```
-
-```{r child="report_07_raw_relaxed.Rmd"}
-```
-
 ### Relaxed criteria {.tabset}
@@
 
+### {-}
+
+## Attrition {.tabset}
+
+### Stringent criteria {.tabset}
+
+```{r child="report_05_attrition_stringent.Rmd"}
+```
+
+### Relaxed criteria {.tabset}
+
 ```{r child="report_05_attrition_relaxed.Rmd"}
@@
 
-```{r child="report_06_21-mon_relaxed.Rmd"}
+### Counterbalancing {.tabset}
+
+#### Stringent criteria {.tabset}
+
+```{r child="report_05_attrition_counter_stringent.Rmd"}
 ```
 
-```{r child="report_07_raw_relaxed.Rmd"}
+#### Relaxed criteria {.tabset}
+
+```{r child="report_05_attrition_counter_relaxed.Rmd"}
+```
+
+#### {-}
+
+### {-}
+
+## 21 months-old monolinguals {.tabset}
+
+### Stringent criteria {.tabset}
+
+```{r child="report_06_21-mon_stringent.Rmd"}
+```
+
+### Relaxed criteria {.tabset}
+
+```{r child="report_06_21-mon_relaxed.Rmd"}
 ```

### 2021-07-23 Rmd/report_00_participants_relaxed.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

@@
 #### Summary
+
+```{r participants_summary_relaxed_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	count(location, age_group, lp) %>% 
+	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
+	gt(groupname_col = "location") %>% 
+	cols_label(
+		lp = md("**Language profile**"),
+		`21 months` = md("**21 months**"),
+		`25 months` = md("**25 months**"),
+		`30 months` = md("**30 months**")
+	)
+
+```
 

### 2021-07-23 Rmd/report_00_participants_stringent.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

@@
 #### Summary
+
+```{r participants_summary_stringent_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	count(location, age_group, lp) %>% 
+	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
+	gt(groupname_col = "location") %>% 
+	cols_label(
+		lp = md("**Language profile**"),
+		`21 months` = md("**21 months**"),
+		`25 months` = md("**25 months**"),
+		`30 months` = md("**30 months**")
+	)
+
+```
 

### 2021-07-23 Rmd/report_01_stimuli.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

@@
 ---
-
-## Stimuli {.tabset }
 
@@
 		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
+		axis.text = element_text(size = 7),
 		axis.title.x = element_blank(),
@@
 		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	# scale_y_reordered() +
-	theme_custom() +
+	scale_x_continuous(labels = percent, limits = c(0, 1)) +
 	theme(
@@
 		legend.title = element_blank(),
-		axis.text = element_text(size = 10),
+		axis.text = element_text(size = 7),
 		axis.title.y = element_blank(),
@@
 		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme_custom() +
+	scale_x_continuous(labels = percent, limits = c(0, 1)) +
+	# scale_y_reordered() +
 	theme(
@@
 		axis.title.y = element_blank(),
-		axis.text = element_text(size = 10),
+		axis.text = element_text(size = 7),
 		strip.text = element_text(size = 11)

### 2021-07-23 Rmd/report_04_gca_relaxed.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

@@
 
-### Growth curve analysis {.tabset}
+```{r define_model_relaxed, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+fit <- model_fits_relaxed$fit
+fit_21_mon <- model_fits_relaxed$fit_21_mon
+fit_21_mon_location <- model_fits_relaxed$fit_21_mon_location
+fit_21_mon_vocab_split<- model_fits_relaxed$fit_21_mon_vocab_split
+fit_21_mon_vocab_balanced <- model_fits_relaxed$fit_21_mon_vocab_balanced
+```
 
@@
 ```{r fixed_effects_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_relaxed, method = "Wald") %>% 
+main_effects <- confint.merMod(fit, method = "Wald") %>% 
 	as.data.frame() %>% 
@@
 	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_relaxed, effects = "fixed"))) %>% 
+	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
 	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
@@
 
-VarCorr(fit_relaxed)$participant %>% 
+VarCorr(fit)$participant %>% 
 	cov2cor() %>% 
@@
 
-augment(fit_relaxed) %>% 
+augment(fit) %>% 
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
@@
 				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob,
+					 group = interaction(participant, trial_type),
+					 colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
 	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
 				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
 	geom_text(data = sample_size,
@@
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	stat_summary(aes(x = ot1, y = .fitted_prob,
+					 group = interaction(participant, trial_type),
+					 colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
 	geom_text(data = sample_size,
@@
 
-augment(fit_relaxed) %>% 
+augment(fit) %>% 
 	left_join(distinct(participants, participant, location)) %>% 

### 2021-07-23 Rmd/report_04_gca_stringent.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

@@
 
-### Growth curve analysis {.tabset }
+```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+fit <- model_fits$fit
+fit_21_mon <- model_fits$fit_21_mon
+fit_21_mon_location <- model_fits$fit_21_mon_location
+fit_21_mon_vocab_split<- model_fits$fit_21_mon_vocab_split
+fit_21_mon_vocab_balanced <- model_fits$fit_21_mon_vocab_balanced
+```
 
@@
 ```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit, method = "Wald") %>% 
+main_effects <- confint.merMod(model_fits$fit, method = "Wald") %>% 
 	as.data.frame() %>% 

### 2021-07-23 Rmd/report_05_attrition_counter_relaxed.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

---
---

##### Summary

```{r participants_cdi_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants_relaxed_counter %>% 
	left_join(distinct(attrition_relaxed_counter, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

##### By location

```{r trials_attrition_location_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
# plot participants
attrition_location <- attrition_relaxed_counter %>% 
	left_join(select(participants_relaxed_counter, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type)

attrition_location %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +

	attrition_location %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +

	plot_layout(guides = "collect", ncol = 1) &
	scale_y_continuous(labels = percent) &
	coord_flip() &
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 10),
		axis.title = element_blank()
	)
```

##### By group

This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).

```{r attrition_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}

left_join(
	attrition_relaxed_counter,
	select(
		participants_relaxed_counter, age_group, location, lp, participant, date_test)
) %>% 
	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0)

```

##### By participant

```{r participants_attrition_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_relaxed_counter %>% 
	left_join(select(participants_relaxed_counter, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
	div(style='height:600px; overflow-y: scroll', .)
```

##### By trial

```{r trials_attrition_table_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_relaxed_counter %>% 
	left_join(select(participants_relaxed_counter, participant, location)) %>% 
	drop_na(trial_type) %>% 
	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
	count() %>% 
	ungroup() %>%
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
	clean_names() %>% 
	gt(groupname_col = c("location", "lp")) %>% 
	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
	cols_label(
		location = "Location",
		lp = "Group",
		trial_type = "Trial type",
		x21_months_not_valid = "Not valid",
		x21_months_valid = "Valid",
		x25_months_not_valid = "Not valid",
		x25_months_valid = "Valid",
		x30_months_not_valid = "Not valid",
		x30_months_valid = "Valid"
	)

```

```{r trials_attrition_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_relaxed_counter %>% 
	left_join(select(participants_relaxed_counter, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### By lexical frequency {.tabset }

###### Prime frequency

```{r attrition_frequency_prime_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_prime_causes_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### Target frequency

```{r attrition_frequency_target_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_target_causes_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### {-}

##### By familiarity {.tabset}

###### Prime familiarity

```{r attrition_familiarity_prime_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	ggplot(aes(trial_type, familiarity_prime, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_prime_causes_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### Target familiarity

```{r attrition_familiarity_target_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_target_causes_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### {-}

##### By animacy {.tabset }

###### Prime

```{r attrition_animacy_prime_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_prime) %>% 
	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

```

###### Target

```{r attrition_animacy_target_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

```

###### {-}

##### By category {.tabset}

###### Prime

```{r attrition_category_prime_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
	drop_na(trial_type, category_prime) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### Target

```{r attrition_category_target_relaxed_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition_relaxed_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
	drop_na(trial_type, category_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### {-}

### 2021-07-23 Rmd/report_05_attrition_counter_stringent.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

---
---

##### Summary

```{r participants_cdi_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants_counter %>% 
	left_join(distinct(attrition_counter, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

##### By location

```{r trials_attrition_location_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
# plot participants
attrition_location <- attrition_counter %>% 
	left_join(select(participants_counter, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type)

attrition_location %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +

	attrition_location %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +

	plot_layout(guides = "collect", ncol = 1) &
	scale_y_continuous(labels = percent) &
	coord_flip() &
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 10),
		axis.title = element_blank()
	)
```

##### By group

This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).

```{r attrition_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}

left_join(
	attrition_counter,
	select(
		participants_counter, age_group, location, lp, participant, date_test)
) %>% 
	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0)

```

##### By participant

```{r participants_attrition_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_counter %>% 
	left_join(select(participants_counter, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
	div(style='height:600px; overflow-y: scroll', .)
```

##### By trial

```{r trials_attrition_table_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_counter %>% 
	left_join(select(participants_counter, participant, location)) %>% 
	drop_na(trial_type) %>% 
	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
	count() %>% 
	ungroup() %>%
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
	clean_names() %>% 
	gt(groupname_col = c("location", "lp")) %>% 
	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
	cols_label(
		location = "Location",
		lp = "Group",
		trial_type = "Trial type",
		x21_months_not_valid = "Not valid",
		x21_months_valid = "Valid",
		x25_months_not_valid = "Not valid",
		x25_months_valid = "Valid",
		x30_months_not_valid = "Not valid",
		x30_months_valid = "Valid"
	)

```

```{r trials_attrition_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_counter %>% 
	left_join(select(participants_counter, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### By lexical frequency {.tabset }

###### Prime frequency

```{r attrition_frequency_prime_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_prime_causes_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### Target frequency

```{r attrition_frequency_target_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_target_causes_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### {-}

##### By familiarity {.tabset}

###### Prime familiarity

```{r attrition_familiarity_prime_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	ggplot(aes(trial_type, familiarity_prime, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_prime_causes_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### Target familiarity

```{r attrition_familiarity_target_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_target_causes_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### {-}

##### By animacy {.tabset }

###### Prime

```{r attrition_animacy_prime_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_prime) %>% 
	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

```

###### Target

```{r attrition_animacy_target_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

```

###### {-}

##### By category {.tabset}

###### Prime

```{r attrition_category_prime_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
	drop_na(trial_type, category_prime) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### Target

```{r attrition_category_target_stringent_counter, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition_counter %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
	drop_na(trial_type, category_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

###### {-}

### 2021-07-23 Rmd/report_05_attrition_relaxed.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

@@
 ---
-
-### Attrition {.tabset}
 
@@
 	left_join(select(participants_relaxed, participant, location)) %>% 
+	drop_na(trial_type) %>% 
 	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
@@
 				 size = 1, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 2, label = n),
+	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
 			   position = position_dodge(width = 0.7), colour = "white") +
@@
 		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		axis.text.x = element_text(size = 10),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
+		axis.text.y = element_text(size = 8),
 		axis.title = element_blank()
@@
 				 size = 1, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 0.1, label = n),
+	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
 			   position = position_dodge(width = 0.7), colour = "white") +
@@
 		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		axis.text.x = element_text(size = 10),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
 		axis.text.y = element_text(size = 8),
@@
 
-#### {-}
+##### {-}

### 2021-07-23 Rmd/report_06_21-mon_relaxed.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

@@
 
-### 21 month-old monolinguals {.tabset }
+```{r define_model_21_mon_relaxed, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+fit_21_mon <- model_fits_relaxed$fit_21_mon
+fit_21_mon_location <- model_fits_relaxed$fit_21_mon_location
+fit_21_mon_vocab_split<- model_fits_relaxed$fit_21_mon_vocab_split
+fit_21_mon_vocab_balanced <- model_fits_relaxed$fit_21_mon_vocab_balanced
+```
 
@@
 ```{r fixef_21_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_relaxed, method = "Wald") %>% 
+main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
 	as.data.frame() %>% 
@@
 	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_relaxed, effects = "fixed"))) %>% 
+	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
 	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
@@
 
-augment(fit_21_mon_relaxed) %>% 
+augment(fit_21_mon) %>% 
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
@@
 
-	augment(fit_21_mon_relaxed) %>% 
+	augment(fit_21_mon) %>% 
 	mutate(elog_prob = logit_to_prob(elog)) %>% 
@@
 ```{r fixef_21_mon_location_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_location_relaxed, method = "Wald") %>% 
+main_effects <- confint.merMod(fit_21_mon_location, method = "Wald") %>% 
 	as.data.frame() %>% 
@@
 	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_location_relaxed, effects = "fixed"))) %>% 
+	right_join(clean_names(tidy(fit_21_mon_location, effects = "fixed"))) %>% 
 	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
@@
 
-augment(fit_21_mon_location_relaxed) %>% 
+augment(fit_21_mon_location) %>% 
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
@@
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(
-		aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
 				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	stat_summary(aes(x = ot1, y = .fitted_prob,
+					 group = interaction(participant, trial_type),
+					 colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
 	geom_text(data = sample_size,
@@
 
-	augment(fit_21_mon_location_relaxed) %>% 
+	augment(fit_21_mon_location) %>% 
 	mutate(elog_prob = logit_to_prob(elog)) %>% 
@@
 ```{r fixef_21_mon_vocab_split_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_21_mon_vocab_split_relaxed, method = "Wald") %>% 
+main_effects <- confint.merMod(fit_21_mon_vocab_split, method = "Wald") %>% 
 	as.data.frame() %>% 
@@
 	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab_split_relaxed, effects = "fixed"))) %>% 
+	right_join(clean_names(tidy(fit_21_mon_vocab_split, effects = "fixed"))) %>% 
 	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
@@
 
-augment(fit_21_mon_vocab_split_relaxed) %>% 
+augment(fit_21_mon_vocab_split) %>% 
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
@@
 
-	augment(fit_21_mon_vocab_split_relaxed) %>% 
+	augment(fit_21_mon_vocab_split) %>% 
 	mutate(elog_prob = logit_to_prob(elog)) %>% 
@@
 
-main_effects <- confint.merMod(fit_21_mon_vocab_balanced_relaxed, method = "Wald") %>% 
+main_effects <- confint.merMod(fit_21_mon_vocab_balanced, method = "Wald") %>% 
 	as.data.frame() %>% 
@@
 	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_21_mon_vocab_balanced_relaxed, effects = "fixed"))) %>% 
+	right_join(clean_names(tidy(fit_21_mon_vocab_balanced, effects = "fixed"))) %>% 
 	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
@@
 
-augment(fit_21_mon_vocab_balanced_relaxed) %>% 
+augment(fit_21_mon_vocab_balanced) %>% 
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
@@
 
-	augment(fit_21_mon_vocab_balanced_relaxed) %>% 
+	augment(fit_21_mon_vocab_balanced) %>% 
 	mutate(elog_prob = logit_to_prob(elog)) %>% 

### 2021-07-23 Rmd/report_06_21-mon_stringent.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

@@
 
-### 21 month-old monolinguals {.tabset }
+```{r define_model_21_mon, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+fit_21_mon <- model_fits$fit_21_mon
+fit_21_mon_location <- model_fits$fit_21_mon_location
+fit_21_mon_vocab_split<- model_fits$fit_21_mon_vocab_split
+fit_21_mon_vocab_balanced <- model_fits$fit_21_mon_vocab_balanced
+```
 

### 2021-07-23 R/04_attrition.R

@@ -6,7 +6,8 @@ get_attrition <- function(
 	stimuli, # stimuli dataset, get_stimuli output
 	vocabulary, # vocabulary dataset, get_vocabulary output
 	filter_vocabulary = c("prime", "target"), # should the trial be excluded if no comprehension in any of these words? (prime, target, distractor)
-	looking_threshold = c(prime = 250, target = 250), # minimum looking time
+	filter_counterbalancing = TRUE, # should trials from same counterbalancing pair be excluded together?
+	looking_threshold = c(prime = 0, target = 0, distractor = 0), # minimum looking time
 	missing_trials_threshold = c(cognate = 0, noncognate = 0, unrelated = 0) # minimum n trials in each condition
 ){
 	suppressWarnings({
@@ -33,18 +34,28 @@ get_attrition <- function(
 			) %>% 
 			mutate(
 				# prime looking proportion during prime phase is higher or equal than minimum
-				valid_gaze_prime = valid_looking_prime >= looking_threshold["prime"],
+				valid_gaze_prime = case_when(
+					looking_threshold["prime"]>0 ~ (valid_looking_prime > looking_threshold["prime"]),
+					TRUE ~ TRUE
+				),					
 				# participant has looked at least once to target AND distractor and higher or equal than minimum to both
-				valid_gaze_target = valid_looking_target>0 & (valid_looking_target >= looking_threshold["target"]),
+				valid_gaze_target = case_when(
+					looking_threshold["target"]>0 ~ (valid_looking_target > looking_threshold["target"]),
+					TRUE ~ TRUE
+				),				
 				# participant has looked at least once to target AND distractor and higher or equal than minimum to both
-				valid_gaze_distractor = valid_looking_distractor>0 & (valid_looking_distractor >= looking_threshold["distractor"]),
+				valid_gaze_distractor = case_when(
+					looking_threshold["distractor"]>0 ~ (valid_looking_distractor > looking_threshold["distractor"]),
+					TRUE ~ TRUE
+				),
 				# trial meets all gaze criteria
-				valid_gaze = valid_gaze_prime & valid_gaze_target 
-			)
+				valid_gaze = (valid_gaze_prime & valid_gaze_target & valid_gaze_distractor)
+			) %>% 
+			mutate_at(vars(starts_with("valid_")), function(x) ifelse(is.na(x), FALSE, x))
 		
[…]

### 2021-07-23 R/05_prepare.R

@@ -45,7 +45,11 @@ prepare_data <- function(
 				aoi_columns = c("aoi_target","aoi_distractor"), 
 				treat_non_aoi_looks_as_missing = FALSE
 			) %>% 
-			subset_by_window(rezero = TRUE, window_start_time = 0.3, window_end_time = 1.8) %>% 
+			subset_by_window(
+				rezero = TRUE,
+				window_start_time = 0.3,
+				window_end_time = 1.8
+			) %>% 
 			make_time_sequence_data(
 				time_bin_size = 0.1, 
 				predictor_columns = c("test_language", "location", "trial_type", "age_group", "lp"),
@@ -54,19 +58,22 @@ prepare_data <- function(
 			as_tibble() %>% 
 			# add previous ID to link longitudinal participants
 			left_join(distinct(participants, participant, participant_unique)) %>% 
-			left_join(vocabulary) %>% 
+			left_join(vocabulary) %>%  
 			clean_names() %>% 
-			select(participant, location, age_group, lp,
-				   vocab_size_total_center, vocab_size_l1_center, vocab_size_conceptual_center,
-				   prime, target, trial, trial_type,
-				   time_bin, ot1, ot2, ot3, prop, weights, elog, logit_adjusted) %>%
+			select(
+				participant, location, age_group, lp,
+				vocab_size_total_center, vocab_size_l1_center, vocab_size_conceptual_center,
+				prime, target, trial, trial_type,
+				time_bin, ot1, ot2, ot3, prop, weights, elog, logit_adjusted
+			) %>%
 			mutate_at(vars(age_group, lp, location, prime, target, trial, trial_type), as.factor)
 		
 		# set a prior contrasts and orthogonal polynomials
 		contrasts(gaze$lp) <- c(-0.5, 0.5)
 		contrasts(gaze$trial_type) <- cbind(c(-0.25, -0.25, 0.5), c(0.5, -0.5, 0))
 		contrasts(gaze$age_group) <- contr.poly(3, contrasts = TRUE)
-		
-		return(gaze)
+		contrasts(gaze$location) <- c(0.5, -0.5)
 	})
+	return(gaze)
+	
 }

### 2021-07-27 Rmd/report_04_gca_relaxed.Rmd
Add 25 months analysis

@@
 
-```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r gaze_time_vocab_lower_relaxed, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 sample_size <- participants_relaxed %>% 
@@
 
-```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r gaze_time_vocab_upper_relaxed, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 sample_size <- participants_relaxed %>% 

### 2021-07-27 Rmd/report_04_gca_stringent.Rmd
Add 25 months analysis

@@
 
-```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r gaze_time_vocab_lower, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 sample_size <- participants_stringent %>% 
@@
 
-```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r gaze_time_vocab_upper, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 sample_size <- participants_stringent %>% 

### 2021-07-27 Rmd/report_07_2125-mon_relaxed.Rmd
Add 25 months analysis

---
---

```{r define_model_2125_mon_relaxed, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit_2125_mon <- model_fits_relaxed$fit_2125_mon
```

```{r fixef_2125_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_2125_mon, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_2125_mon, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects

```

```{r gaze_time_2125_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- augment(fit_2125_mon) %>% 
	distinct(participant, age_group) %>% 
	count(age_group)

augment(fit_2125_mon) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob,
					 group = interaction(participant, trial_type),
					 colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0.25, 0.75), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_2125_mon) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, age_group, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~age_group, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0.25, 0.75), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	plot_annotation(
		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis. B: mean observed probability of target looking, aggregated by participant.",
		tag_levels = "A") &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

### 2021-07-27 Rmd/report_07_2125-mon_stringent.Rmd
Add 25 months analysis

---
---

```{r define_model_2125_mon_stringent, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit_2125_mon <- model_fits$fit_2125_mon
```

```{r fixef_2125_mon_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_2125_mon, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_2125_mon, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects

```

```{r gaze_time_2125_mon_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- augment(fit_2125_mon) %>%
	distinct(participant, age_group) %>% 
	count(age_group)

augment(fit_2125_mon) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~age_group, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	# stat_summary(aes(x = ot1, y = .fitted_prob,
	# 				 group = interaction(participant, trial_type),
	# 				 colour = trial_type, fill = trial_type),
	# 			 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_2125_mon) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, age_group, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~age_group, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	plot_annotation(
		caption = "A: Marginal means of the multilevel model, plotted in separate panels for 21- and 25-month olds.\nSample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis. B: mean observed probability of target looking, aggregated by participant\nfirst and by prime type second.",
		tag_levels = "A") &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

### 2021-07-27 Rmd/report_08_mon_relaxed.Rmd
Add 25 months analysis

---
---

```{r define_model_mon_relaxed, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit_mon <- model_fits_relaxed$fit_mon
```

```{r fixef_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_mon, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_mon, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

main_effects

```

```{r gaze_time_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- augment(fit_mon) %>%
	distinct(participant, age_group) %>% 
	count(age_group)

augment(fit_mon) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~age_group, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob,
					 group = interaction(participant, trial_type),
					 colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_mon) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, age_group, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~age_group, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	plot_annotation(
		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis. B: mean observed probability of target looking, aggregated by participant.",
		tag_levels = "A") &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

### 2021-07-27 Rmd/report_08_mon_stringent.Rmd
Add 25 months analysis

--- 2021-07-27 Rmd/report_08_mon_relaxed.Rmd
@@
 
-```{r define_model_mon_relaxed, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-fit_mon <- model_fits_relaxed$fit_mon
+```{r define_model_mon_stringent, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+fit_mon <- model_fits$fit_mon
 ```
 
-```{r fixef_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r fixef_mon_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 main_effects <- confint.merMod(fit_mon, method = "Wald") %>% 
@@
 
-```{r gaze_time_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r gaze_time_mon_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 sample_size <- augment(fit_mon) %>%

### 2021-07-29 Rmd/report_07_2125-mon_stringent.Rmd
Update .Rprofile to include the run function

@@
 
-```{r gaze_time_2125_mon_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r gaze_time_2125_mon_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.dim = c(6.5, 5)}
 sample_size <- augment(fit_2125_mon) %>%
@@
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
+	ggplot(shape = trial_type, linetype = trial_type) +
 	facet_wrap(~age_group, ncol = 1) +
@@
 	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
+		 colour = "Prime type", fill = "Prime type",
+		 shape = "Prime type", linetype = "Prime type") +
 	scale_y_continuous(limits = c(0, 1), labels = percent) + 
@@
 	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
+		 colour = "Trial type", fill = "Prime type") +
 	scale_y_continuous(limits = c(0, 1), labels = percent) + 
@@
 	plot_annotation(
-		caption = "A: Marginal means of the multilevel model, plotted in separate panels for 21- and 25-month olds.\nSample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.
-B: mean observed probability of target looking, aggregated by participant\nfirst and by prime type second.",
-		tag_levels = "A") &
+		caption = "(A) Marginal means of the Growth Curve analysis model (100 ms time bins), plotted in separate\npanels for 21- and 25-month olds.
+Sample sizes are indicated at the upper left corner in each panel.\n(B) Mean observed probability of target looking, aggregated across time bins.",
+		tag_levels = "A"
+	) &
 	theme_custom() &

### 2021-10-07 Rmd/report.Rmd
Add 25 months analysis
Update .Rprofile to include the run function
Bayesian analysis

@@
 output:
-  html_document:
-    df_print: paged
-    toc: true
-    toc_depth: 5
-    toc_float: true
-runtime: shiny
+  github_document:
+    pandoc_args: --webtex
+always_allow_html: true
 ---
@@
 options(knitr.kable.NA = '-',
+		knitr.duplicate.label = "allow",
 		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
@@
 library(janitor)
-library(lme4)
-library(broom.mixed)
 library(gt)
 library(patchwork)
-library(htmltools)
 library(wesanderson)
@@
 library(tidytext)
+library(brms)
+library(tidyverse)
 library(here)
@@
 
-theme_set(theme_custom()) # in utils.R
+theme_set(theme_github()) # in utils.R
 ```
@@
 
-### Counterbalancing {.tabset}
-
-#### Stringent criteria {.tabset}
-
-```{r child="report_05_attrition_counter_stringent.Rmd"}
-```
-
-#### Relaxed criteria {.tabset}
-
-```{r child="report_05_attrition_counter_relaxed.Rmd"}
-```
-
-#### {-}
-
-### {-}
-
-## 21 months-old monolinguals {.tabset}
-
-### Stringent criteria {.tabset}
-
-```{r child="report_06_21-mon_stringent.Rmd"}
-```
-
-### Relaxed criteria {.tabset}
-
-```{r child="report_06_21-mon_relaxed.Rmd"}
-```
-
 ### {-}
@@
 
-```{r child="report_08_vocabulary_stringent.Rmd"}
+```{r child="report_06_vocabulary_stringent.Rmd"}
 ```
@@
 
-```{r child="report_08_vocabulary_relaxed.Rmd"}
+```{r child="report_06_vocabulary_relaxed.Rmd"}
 ```

### 2021-10-07 Rmd/report_00_participants_relaxed.Rmd
Bayesian analysis

--- 2021-07-19 Rmd/report_00_participants_relaxed.Rmd
@@
 #### Summary
+
+```{r participants_summary_relaxed_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	count(location, age_group, lp) %>% 
+	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
+	gt(groupname_col = "location") %>% 
+	cols_label(
+		lp = md("**Language profile**"),
+		`21 months` = md("**21 months**"),
+		`25 months` = md("**25 months**"),
+		`30 months` = md("**30 months**")
+	) %>% 
+	as_raw_html()
+
+```
 

### 2021-10-07 Rmd/report_01_stimuli.Rmd
Bayesian analysis

@@
 		conf_low = md("**CI<sub>95%<sub/>**")
-	)
+	) %>% 
+	as_raw_html()
 

### 2021-10-07 Rmd/report_04_gca_relaxed.Rmd
Bayesian analysis

--- 2021-07-19 Rmd/report_04_gca_relaxed.Rmd
@@
 
-### Growth curve analysis {.tabset}
+```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+fit <- model_fits_relaxed$fit
+```
 
@@
 
-```{r fixed_effects_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit_relaxed, method = "Wald") %>% 
-	as.data.frame() %>% 
+```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
+
+draws %>% 
+	mean_qi(.width = c(0.95, 0.50)) %>% 
+	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
 	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit_relaxed, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	select(-c(point, interval, value_0_5)) %>% 
+	gt(rowname_col = "variable") %>% 
+	fmt_number(2:6) %>% 
+	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
+	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
 	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
+		variable = md("**Predictor**"),
+		value_0_95 = md("**Mean**"),
+		lower_0_95 = md("**95% CrI**"),
+		lower_0_5 = md("**50% CrI**")
 	) %>% 
@@
 		style = list(
-			cell_fill(color = "#ffc7a1")
+			cell_fill(color = "#b9fac4")
 		),
 		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
+			columns = lower_0_95,
+			rows = lower_0_95 > 0
 		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#b9fac4")
+		),
+		locations = cells_body(
+			columns = lower_0_5,
+			rows = lower_0_5 > 0
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#fabfb9")
+		),
+		locations = cells_body(
+			columns = lower_0_95,
+			rows = upper_0_95 < 0
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#fabfb9")
+		),
+		locations = cells_body(
+			columns = lower_0_5,
+			rows = upper_0_5 < 0
+		)
+	) %>% 
+	as_raw_html()
+```
+
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+draws %>% 
+	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
+	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95, 1))))) +
+	geom_vline(xintercept = 0) +
+	stat_halfeye() +
+	labs(x = "Value", y = "Variable", fill = "CrI") +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	theme(
+		axis.title = element_blank(),
+		legend.position = "top"
 	)
 
-main_effects
 ```
@@
 
-```{r random_effects_participant_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 
-VarCorr(fit_relaxed)$participant %>% 
+vcov(fit) %>% 
 	cov2cor() %>% 
@@
 	rownames_to_column("term1") %>% 
-	gt(rowname_col = "term1") %>% 
-	fmt_number(columns = 2:9) %>% 
-	data_color(
-		columns = 2:9,
-		colors = col_numeric(
-			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
-			domain = c(-1, 1), alpha = 0.5
-		)
+	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
+	geom_tile() +
+	labs(x = "Term 1", y = "Term 2", fill = "Mean post. correlation") +
+	scale_fill_distiller(limits = c(-1, 1)) +
+	coord_equal() +
+	theme(
+		legend.position = "top",
+		legend.text = element_text(size = 8),
+		axis.title = element_blank(),
+		axis.text = element_text(hjust = 1, size = 8),
+		axis.text.x = element_text(angle = 90, hjust = 1, size = 8)
 	)
@@
 
-```{r gaze_time_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants_relaxed %>% 
+```{r gaze_relaxed_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants_stringent %>% 
 	filter(valid_participant) %>% 
-	count(age_group, lp)
+	count(lp)
 
-augment(fit_relaxed) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
+n <- expand_grid(
+	lp = c("Monolingual", "Bilingual"),
+	age_group = c("25 months"),
+	trial_type = unique(gaze_relaxed$trial_type),
+	time_bin_center = seq(min(gaze_relaxed$time_bin_center), max(gaze_relaxed$time_bin_center), 0.5)
+)
+
+m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
+	mutate(.value = logit_to_prob(.epred))
+
+ggplot(m, aes(time_bin_center, .value)) +
+	facet_wrap(~fct_rev(lp)) +
+	geom_hline(yintercept = 0.5) +
+	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
+				  colour = trial_type),
+			  alpha = 0.15, size = 0.75) +
+	stat_summary(aes(group = trial_type, colour = trial_type),
+				 fun = mean, geom = "line", size = 1.25) +
+	stat_summary(data = gaze_relaxed, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
+							   colour = trial_type),
+				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
+				 position = position_dodge(width = 0.3)) +
+	geom_text(data = sample_size, aes(x = min(gaze_relaxed$time_bin_center), y = 1, label = paste0("N = ", n)),
+			  colour = "white", hjust = 0, size = 5) +
+	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
+		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
+	scale_color_brewer(palette = "Set1") +
+	scale_x_continuous(breaks = min(gaze_relaxed$time_bin_center):max(gaze_relaxed$time_bin_center), labels = unique(gaze_relaxed$time_bin)) +
 	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
-	theme_custom() +
 	theme(
 		legend.position = "top",
-		axis.text = element_text(size = 7),
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	) 
-```
-
-##### By vocabulary size
-
-```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants_relaxed %>% 
-	count(age_group, lp)
-
-augment(fit_relaxed) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size <= median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants_relaxed %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit_relaxed) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size > median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-##### By location
-
-```{r gaze_time_location_barcelona_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants_relaxed %>% 
-	filter(location=="Barcelona", valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit_relaxed) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Barcelona") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_location_oxford_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants_relaxed %>% 
-	filter(location=="Oxford") %>% 
-	count(age_group, lp)
-
-augment(fit_relaxed) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Oxford") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 9)
 	)

### 2021-10-07 Rmd/report_04_gca_stringent.Rmd
Bayesian analysis

--- 2021-07-19 Rmd/report_04_gca_stringent.Rmd
@@
 
-### Growth curve analysis {.tabset }
+```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+fit <- model_fits$fit
+```
 
@@
 ```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-main_effects <- confint.merMod(fit, method = "Wald") %>% 
-	as.data.frame() %>% 
+draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
+
+draws %>% 
+	mean_qi(.width = c(0.95, 0.50)) %>% 
+	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
 	clean_names() %>% 
-	drop_na(x2_5_percent) %>%
-	rownames_to_column("term") %>% 
-	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
-	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
-		   statistic, df, p_value) %>% 
-	gt() %>% 
-	fmt_number(2:7) %>% 
-	fmt_number(8, decimals = 3) %>% 
-	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	select(-c(point, interval, value_0_5)) %>% 
+	gt(rowname_col = "variable") %>% 
+	fmt_number(2:6) %>% 
+	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
+	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
 	cols_label(
-		term = md("**Predictor**"),
-		estimate = md("**Estimate**"),
-		std_error = md("**SE**"),
-		conf_lower = md("**CI<sub>95%</sub>**"),
-		statistic = md("***t***"),
-		df = md("**df**"),
-		p_value = md("***p***")
+		variable = md("**Predictor**"),
+		value_0_95 = md("**Mean**"),
+		lower_0_95 = md("**95% CrI**"),
+		lower_0_5 = md("**50% CrI**")
 	) %>% 
@@
 		style = list(
-			cell_fill(color = "#ffc7a1")
+			cell_fill(color = "#b9fac4")
 		),
 		locations = cells_body(
-			columns = everything(),
-			rows = p_value < 0.05
+			columns = lower_0_95,
+			rows = lower_0_95 > 0
 		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#b9fac4")
+		),
+		locations = cells_body(
+			columns = lower_0_5,
+			rows = lower_0_5 > 0
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#fabfb9")
+		),
+		locations = cells_body(
+			columns = lower_0_95,
+			rows = upper_0_95 < 0
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#fabfb9")
+		),
+		locations = cells_body(
+			columns = lower_0_5,
+			rows = upper_0_5 < 0
+		)
+	) %>% 
+	as_raw_html()
+```
+
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+draws %>% 
+	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
+	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95, 1))))) +
+	geom_vline(xintercept = 0) +
+	stat_halfeye() +
+	labs(x = "Value", y = "Variable", fill = "CrI") +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	theme_github() +
+	theme(
+		axis.title = element_blank(),
+		legend.position = "top"
 	)
 
-main_effects
 ```
@@
 
-VarCorr(fit)$participant %>% 
+vcov(fit) %>% 
 	cov2cor() %>% 
@@
 	rownames_to_column("term1") %>% 
-	gt(rowname_col = "term1") %>% 
-	fmt_number(columns = 2:9) %>% 
-	data_color(
-		columns = 2:9,
-		colors = col_numeric(
-			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
-			domain = c(-1, 1), alpha = 0.5
-		)
+	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
+	geom_tile() +
+	labs(x = "Term 1", y = "Term 2", fill = "Mean post. correlation") +
+	scale_fill_distiller(limits = c(-1, 1)) +
+	coord_equal() +
+	theme_github() +
+	theme(
+		legend.position = "top",
+		legend.text = element_text(size = 8),
+		axis.title = element_blank(),
+		axis.text = element_text(hjust = 1, size = 8),
+		axis.text.x = element_text(angle = 90, hjust = 1, size = 8)
 	)
@@
 	filter(valid_participant) %>% 
-	count(age_group, lp)
+	count(lp)
 
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", size = 1) +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
+n <- expand_grid(
+	lp = c("Monolingual", "Bilingual"),
+	age_group = c("25 months"),
+	trial_type = unique(gaze$trial_type),
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
+)
+
+m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
+	mutate(.value = logit_to_prob(.epred))
+
+ggplot(m, aes(time_bin_center, .value)) +
+	facet_wrap(~fct_rev(lp)) +
+	geom_hline(yintercept = 0.5) +
+	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
+				  colour = trial_type),
+			  alpha = 0.15, size = 0.75) +
+	stat_summary(aes(group = trial_type, colour = trial_type),
+				 fun = mean, geom = "line", size = 1.25) +
+	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
+							   colour = trial_type),
+				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
+				 position = position_dodge(width = 0.3)) +
+	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 1, label = paste0("N = ", n)),
+			  colour = "black", hjust = 0, size = 5) +
+	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
+		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
+	scale_color_brewer(palette = "Set1") +
+	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
 	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme_custom() +
+	theme_github() +
 	theme(
 		legend.position = "top",
-		axis.text = element_text(size = 7),
-		plot.caption = element_text(size = 10, hjust = 0),
-		plot.caption.position = "plot"
-	) 
-```
-
-##### By vocabulary size
-
-```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants_stringent %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size <= median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants_stringent %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Vocabulary size > median") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-##### By location
-
-```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants_stringent %>% 
-	filter(location=="Barcelona", valid_participant) %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Barcelona") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
-	)
-```
-
-```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants_stringent %>% 
-	filter(location=="Oxford") %>% 
-	count(age_group, lp)
-
-augment(fit) %>% 
-	left_join(distinct(participants, participant, location)) %>% 
-	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(x = ot1, y = .fitted_prob)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
-	geom_text(data = sample_size,
-			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
-			  show.legend = FALSE,
-			  colour = "black", fill = "black") +
-	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
-	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
-		 colour = "Trial type", fill = "Trial type",
-		 title = "Oxford") +
-	scale_y_continuous(limits = c(0, 1)) + 
-	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
-	theme(
-		legend.position = "top",
-		axis.text = element_text(size = 7)
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 9)
 	)

### 2021-10-07 Rmd/report_05_attrition_relaxed.Rmd
Bayesian analysis

@@
 	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0)
+	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
+	as_raw_html()
 
@@
 	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	div(style='height:600px; overflow-y: scroll', .)
+	as_raw_html()
 ```
@@
 		x30_months_valid = "Valid"
-	)
+	) %>% 
+	as_raw_html()
 

### 2021-10-07 _targets_packages.R

@@ -1,4 +1,5 @@
 # Generated by targets::tar_renv(): do not edit by hand
+library(brms)
 library(bs4Dash)
 library(childesr)
 library(clustermq)
@@ -13,20 +14,21 @@ library(httr)
 library(janitor)
 library(keyring)
 library(knitr)
-library(lme4)
-library(lmerTest)
 library(lubridate)
 library(markdown)
 library(mice)
 library(multilex)
+library(patchwork)
 library(pingr)
 library(purrr)
 library(readxl)
 library(rmarkdown)
 library(rstudioapi)
+library(scales)
 library(shiny)
 library(shinybusy)
 library(shinyWidgets)
 library(stringr)
+library(tidybayes)
 library(tidyr)
 library(visNetwork)

### 2021-10-07 Rmd/report_04_gca_relaxed.Rmd
Render report with figures

@@
 	facet_wrap(~fct_rev(lp)) +
-	geom_hline(yintercept = 0.5) +
+	geom_hline(yintercept = 0.5, colour = "white") +
 	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
 				  colour = trial_type),
-			  alpha = 0.15, size = 0.75) +
+			  alpha = 0.15, size = 0.65) +
 	stat_summary(aes(group = trial_type, colour = trial_type),
@@
 		legend.title = element_blank(),
-		axis.text.x = element_text(size = 9)
+		axis.text.x = element_text(size = 9),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.x = element_blank()
 	)

### 2021-10-07 _targets_packages.R

@@ -6,7 +6,9 @@ library(clustermq)
 library(data.table)
 library(dplyr)
 library(eyetrackingR)
+library(forcats)
 library(future)
+library(ggplot2)
 library(googlesheets4)
 library(gt)
 library(here)
@@ -29,6 +31,7 @@ library(shiny)
 library(shinybusy)
 library(shinyWidgets)
 library(stringr)
+library(tibble)
 library(tidybayes)
 library(tidyr)
 library(visNetwork)

### 2021-10-07 Rmd/report.Rmd
Render report with figures
Render report

@@
 ---
-title: "Report"
+title: "Cognate Priming: Report"
 output:
@@
     pandoc_args: --webtex
-always_allow_html: true
 ---
@@
 	results = "asis",
+	dpi = 250,
 	dev.args = list(png = list(type = "cairo"))

### 2021-10-07 Rmd/report.Rmd
Render report

@@
 	results = "asis",
-	dpi = 250,
+	dpi = 150,
 	dev.args = list(png = list(type = "cairo"))

### 2021-10-07 Rmd/report_03_data-analysis.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets
Render report

@@
 ---
-
-## Data analysis
 
@@
 	rownames_to_column("level") %>% 
-	gt(rowname_col = "level")
+	gt(rowname_col = "level") %>%
+	as_raw_html()
 

### 2021-10-07 Rmd/report_04_gca_relaxed.Rmd
Render report

--- 2021-10-07 Rmd/report_04_gca_relaxed.Rmd
@@
 $$
-\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
+
+\color{white}{
+\log \Bigg( \frac{p}{n - q} \Bigg) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
 (\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
@@
 (\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
+}
 $$
@@
 	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
-	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95, 1))))) +
-	geom_vline(xintercept = 0) +
-	stat_halfeye() +
+	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
+	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
+	geom_vline(xintercept = 0, colour = "white") +
+	stat_halfeye(point_color = "white", interval_color = "white") +
 	labs(x = "Value", y = "Variable", fill = "CrI") +
@@
 	geom_tile() +
-	labs(x = "Term 1", y = "Term 2", fill = "Mean post. correlation") +
+	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
 	scale_fill_distiller(limits = c(-1, 1)) +
@@
 		axis.title = element_blank(),
-		axis.text = element_text(hjust = 1, size = 8),
-		axis.text.x = element_text(angle = 90, hjust = 1, size = 8)
+		axis.text.y = element_text(hjust = 1, size = 7),
+		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
 	)
@@
 				 position = position_dodge(width = 0.3)) +
-	geom_text(data = sample_size, aes(x = min(gaze_relaxed$time_bin_center), y = 1, label = paste0("N = ", n)),
+	geom_text(data = sample_size, aes(x = min(gaze_relaxed$time_bin_center), y = 0.95, label = paste0("N = ", n)),
 			  colour = "white", hjust = 0, size = 5) +

### 2021-10-15 Rmd/report.Rmd
Render report
Disaggregate participant counts

@@
 library(shiny)
+library(tidybayes)
+library(brms)
 library(tidytext)
@@
 
-### Stringent criteria {.tabset}
-
-```{r child="report_00_participants_stringent.Rmd"}
-```
-
-### Relaxed criteria {.tabset}
-
 ```{r child="report_00_participants_relaxed.Rmd"}
@@
 
-### Stringent criteria {.tabset}
-
-```{r child="report_04_gca_stringent.Rmd"}
-```
-
-### Relaxed criteria {.tabset}
-
 ```{r child="report_04_gca_relaxed.Rmd"}
@@
 
-### {-}
-
 ## Attrition {.tabset}
-
-### Stringent criteria {.tabset}
-
-```{r child="report_05_attrition_stringent.Rmd"}
-```
-
-### Relaxed criteria {.tabset}
 
@@
 
-### {-}
-
 ## Vocabulary {.tabset .tabset-pills}
-
-### Stringent criteria {.tabset}
-
-```{r child="report_06_vocabulary_stringent.Rmd"}
-```
-
-### Relaxed criteria {.tabset}
 
@@
 ```
-
-### {-}
 

### 2021-10-15 Rmd/report_00_participants_relaxed.Rmd
Disaggregate participant counts

--- 2021-07-19 Rmd/report_00_participants_relaxed.Rmd
@@
 
+```{r participants_summary_relaxed_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	count(location, age_group, lp) %>% 
+	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
+	gt(groupname_col = "location") %>% 
+	cols_label(
+		lp = md("**Language profile**"),
+		`21 months` = md("**21 months**"),
+		`25 months` = md("**25 months**"),
+		`30 months` = md("**30 months**")
+	) %>% 
+	as_raw_html()
+```
+
+```{r participants_summary_relaxed_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	count(location, age_group, lp, test_language) %>% 
+	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
+	gt(groupname_col = "location") %>% 
+	cols_label(
+		lp = md("**Language profile**"),
+		test_language = md("**Language**"),
+		`21 months` = md("**21 months**"),
+		`25 months` = md("**25 months**"),
+		`30 months` = md("**30 months**")
+	) 
+	as_raw_html()
+```
+
 ```{r participants_summary_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
@@
 	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed") +
+	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
 	labs(x = "Group", y = "Sample size", fill = "Test language") +

### 2021-10-21 Rmd/report.Rmd

--- 2021-10-07 Rmd/report.Rmd
@@
 ---
-title: "Cognate Priming: Report"
+title: "Report"
 output:
-  github_document:
-    pandoc_args: --webtex
+  html_document:
+    df_print: paged
+    toc: true
+    toc_depth: 5
+    toc_float: true
 ---
@@
 	results = "asis",
-	dpi = 150,
 	dev.args = list(png = list(type = "cairo"))
@@
 options(knitr.kable.NA = '-',
-		knitr.duplicate.label = "allow",
 		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
@@
 library(janitor)
+library(lme4)
+library(broom.mixed)
 library(gt)
 library(patchwork)
+library(htmltools)
 library(wesanderson)
@@
 library(tidytext)
-library(brms)
-library(tidyverse)
 library(here)
@@
 
-theme_set(theme_github()) # in utils.R
+theme_set(theme_custom()) # in utils.R
 ```
@@
 
+### Counterbalancing {.tabset}
+
+#### Stringent criteria {.tabset}
+
+```{r child="report_05_attrition_counter_stringent.Rmd"}
+```
+
+#### Relaxed criteria {.tabset}
+
+```{r child="report_05_attrition_counter_relaxed.Rmd"}
+```
+
+#### {-}
+
+### {-}
+
+## 21 months-old monolinguals {.tabset}
+
+### Stringent criteria {.tabset}
+
+```{r child="report_06_21-mon_stringent.Rmd"}
+```
+
+### Relaxed criteria {.tabset}
+
+```{r child="report_06_21-mon_relaxed.Rmd"}
+```
+
+### {-}
+
+## 21 and 25 months-old monolinguals {.tabset}
+
+### Stringent criteria {.tabset}
+
+```{r child="report_07_2125-mon_stringent.Rmd"}
+```
+
+### Relaxed criteria {.tabset}
+
+```{r child="report_07_2125-mon_relaxed.Rmd"}
+```
+
+### {-}
+
+## 21, 25, and 30 months-old monolinguals {.tabset}
+
+### Stringent criteria {.tabset}
+
+```{r child="report_08_mon_stringent.Rmd"}
+```
+
+### Relax
+
+```{r child="report_08_mon_relaxed.Rmd"}
+```
+
 ### {-}
@@
 
-```{r child="report_06_vocabulary_stringent.Rmd"}
+```{r child="report_09_vocabulary_stringent.Rmd"}
 ```
@@
 
-```{r child="report_06_vocabulary_relaxed.Rmd"}
+```{r child="report_09_vocabulary_relaxed.Rmd"}
 ```

### 2021-10-21 Rmd/report_06_21-mon_relaxed.Rmd

@@
 fit_21_mon_location <- model_fits_relaxed$fit_21_mon_location
+fit_21_mon_frequency <- model_fits_relaxed$fit_21_mon_frequency
 fit_21_mon_vocab_split<- model_fits_relaxed$fit_21_mon_vocab_split
 fit_21_mon_vocab_balanced <- model_fits_relaxed$fit_21_mon_vocab_balanced
+
 ```
@@
 	facet_wrap(~location, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	)
+```
+
+#### Frequency
+
+```{r fixef_21_mon_frequency_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_21_mon_frequency, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon_frequency, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#ffc7a1")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+
+main_effects
+
+```
+
+```{r gaze_time_21_mon_frequency_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants_relaxed %>% 
+	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
+	count()
+
+augment(fit_21_mon_frequency) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	facet_wrap(~frequency_target_childes_cat, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	# stat_summary(aes(x = ot1, y = .fitted_prob,
+	# 				 group = interaction(participant, trial_type),
+	# 				 colour = trial_type, fill = trial_type),
+	# 			 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  colour = "black", fill = "black", show.legend = FALSE) +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon_frequency) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, frequency_target_childes_cat, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
+	facet_wrap(~frequency_target_childes_cat, ncol = 1) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +

### 2021-10-21 Rmd/report_06_21-mon_stringent.Rmd

@@
 fit_21_mon_location <- model_fits$fit_21_mon_location
+fit_21_mon_frequency <- model_fits$fit_21_mon_frequency
 fit_21_mon_vocab_split<- model_fits$fit_21_mon_vocab_split
@@
 	facet_wrap(~location, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_violin(show.legend = FALSE) +
+	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
+	labs(x = "Trial type", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme(
+		axis.title = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_blank(),
+		axis.text.y = element_blank()
+	) +
+	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
+	theme_custom() &
+	theme(
+		legend.position = "right",
+		plot.caption = element_text(size = 10, hjust = 0),
+		plot.caption.position = "plot"
+	)
+```
+
+#### Frequency
+
+```{r fixef_21_mon_frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+main_effects <- confint.merMod(fit_21_mon_frequency, method = "Wald") %>% 
+	as.data.frame() %>% 
+	clean_names() %>% 
+	drop_na(x2_5_percent) %>%
+	rownames_to_column("term") %>% 
+	right_join(clean_names(tidy(fit_21_mon_frequency, effects = "fixed"))) %>% 
+	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
+		   statistic, df, p_value) %>% 
+	gt() %>% 
+	fmt_number(2:7) %>% 
+	fmt_number(8, decimals = 3) %>% 
+	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		term = md("**Predictor**"),
+		estimate = md("**Estimate**"),
+		std_error = md("**SE**"),
+		conf_lower = md("**CI<sub>95%</sub>**"),
+		statistic = md("***t***"),
+		df = md("**df**"),
+		p_value = md("***p***")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#ffc7a1")
+		),
+		locations = cells_body(
+			columns = everything(),
+			rows = p_value < 0.05
+		)
+	)
+
+main_effects
+
+```
+
+```{r gaze_time_21_mon_frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants_stringent %>% 
+	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
+	count()
+
+augment(fit_21_mon_frequency) %>% 
+	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
+	ggplot() +
+	facet_wrap(~frequency_target_childes_cat, ncol = 1) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
+	# stat_summary(aes(x = ot1, y = .fitted_prob,
+	# 				 group = interaction(participant, trial_type),
+	# 				 colour = trial_type, fill = trial_type),
+	# 			 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
+	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
+				 fun = mean, geom = "line", size = 1) +
+	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
+	geom_text(data = sample_size,
+			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
+			  colour = "black", fill = "black", show.legend = FALSE) +
+	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+	theme(
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		legend.position = "left"
+	) +
+
+	augment(fit_21_mon_frequency) %>% 
+	mutate(elog_prob = logit_to_prob(elog)) %>% 
+	group_by(participant, frequency_target_childes_cat, trial_type) %>% 
+	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
+	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
+	facet_wrap(~frequency_target_childes_cat, ncol = 1) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +

### 2021-10-21 Rmd/report_07_2125-mon_relaxed.Rmd

@@
 	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
-	ggplot() +
-	facet_wrap(~age_group) +
+	ggplot(shape = trial_type, linetype = trial_type) +
+	facet_wrap(~age_group, ncol = 1) +
 	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
@@
 				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
-	stat_summary(aes(x = ot1, y = .fitted_prob,
-					 group = interaction(participant, trial_type),
-					 colour = trial_type, fill = trial_type),
-				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
+	# stat_summary(aes(x = ot1, y = .fitted_prob,
+	# 				 group = interaction(participant, trial_type),
+	# 				 colour = trial_type, fill = trial_type),
+	# 			 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
 	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
@@
 	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0.25, 0.75), labels = percent) + 
-	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
+		 colour = "Prime type", fill = "Prime type",
+		 shape = "Prime type", linetype = "Prime type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
 	theme(
@@
 	labs(x = "Trial type", y = "Pr(Target fixation)",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(limits = c(0.25, 0.75), labels = percent) + 
+		 colour = "Trial type", fill = "Prime type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
 	theme(
@@
 	plot_annotation(
-		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups.
-Sample sizes are indicated at the upper left corner in each panel.
-The first and last 300 ms in each trial\nwere trimmed before the analysis.
-B: mean observed probability of target looking, aggregated by participant.",
-		tag_levels = "A") &
+		caption = "(A) Marginal means of the Growth Curve analysis model (100 ms time bins), plotted in separate\npanels for 21- and 25-month olds.
+Sample sizes are indicated at the upper left corner in each panel.\n(B) Mean observed probability of target looking, aggregated across time bins.",
+		tag_levels = "A"
+	) &
 	theme_custom() &

### 2021-10-21 Rmd/report.Rmd
Fix renv

--- 2021-10-15 Rmd/report.Rmd
@@
     pandoc_args: --webtex
+always_allow_html: true
+date: "`r paste0('Updated: ', format(Sys.Date(), '%d/%m/%Y'))`"
 ---
@@
 )
-options(knitr.kable.NA = '-',
+options(
+	knitr.kable.NA = '-',
 		knitr.duplicate.label = "allow",

### 2021-10-21 Rmd/report_00_participants_relaxed.Rmd

@@
 		`30 months` = md("**30 months**")
-	) 
+	) %>% 
 	as_raw_html()
@@
 	geom_point(size = 2) +
-	geom_hline(yintercept = 0.2, linetype = "dashed") +
+	geom_hline(yintercept = 0.2, linetype = "dashed", colour = "white") +
 	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +

### 2021-10-21 Rmd/report_00_participants_stringent.Rmd

--- 2021-07-19 Rmd/report_00_participants_stringent.Rmd
@@
 #### Summary
+
+```{r participants_summary_stringent_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants_relaxed %>% 
+	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	count(location, age_group, lp) %>% 
+	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
+	gt(groupname_col = "location") %>% 
+	cols_label(
+		lp = md("**Language profile**"),
+		`21 months` = md("**21 months**"),
+		`25 months` = md("**25 months**"),
+		`30 months` = md("**30 months**")
+	) %>% 
+	as_raw_html()
+
+```
 

### 2021-10-21 Rmd/report_01_stimuli.Rmd

--- 2021-07-23 Rmd/report_01_stimuli.Rmd
@@
 ### Frequency {.tabset }
-
-#### CHILDES vs. SUBTLEX
-
-```{r frequencies_compare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_data <- bind_rows(
-	stimuli %>%
-		distinct(test_language, prime, .keep_all = TRUE) %>%
-		select(prime, test_language, matches("frequency_prime")) %>% 
-		rename(word = prime, frequency_subtlex = frequency_prime_subtlex,
-			   frequency_childes = frequency_prime_childes),
-	stimuli %>%
-		distinct(test_language, target, .keep_all = TRUE) %>%
-		select(target, test_language, matches("frequency_target")) %>% 
-		rename(word = target, frequency_subtlex = frequency_target_subtlex,
-			   frequency_childes = frequency_target_childes),
-) %>% 
-	group_by(test_language) %>% 
-	mutate_at(vars(starts_with("frequency")), function(x) scale(x)[,1])
-
-frequency_compare_test <- group_split(frequency_compare_data) %>% 
-	set_names(c("Catalan", "English", "Spanish")) %>% 
-	map(function(x) {
-		a <- pull(x, frequency_subtlex)
-		b <- pull(x, frequency_childes)
-		tidy(cor.test(a, b), use = "complete.obs")
-	}) %>% 
-	bind_rows(.id = "test_language") %>% 
-	clean_names()
-
-```
-
-We tested the correlation between the (standardised) lexical frequencies of the stimuli extract from SUBTLEX (adult norms based on subtitles) and CHILDES (child norms based on audio transcriptions) within each test language using a Pearson's product-moment correlation at .05 confidence level (two-sided):
-
-```{r stimuli_frequency_compare_test, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-frequency_compare_test %>% 
-	select(test_language, estimate, statistic, parameter, p_value, conf_low, conf_high) %>% 
-	mutate(p_value = printp(p_value)) %>% 
-	gt(rowname_col = "test_language") %>% 
-	fmt_number(c(2, 3, 6, 7), decimals = 2) %>% 
-	cols_merge(c("conf_low", "conf_high"), pattern = "{1}, {2}") %>% 
-	cols_label(
-		estimate = md("**Correlation**"),
-		statistic = md("***t***"),
-		parameter = md("***df***"),
-		p_value = md("***p***"),
-		conf_low = md("**CI<sub>95%<sub/>**")
-	)
-
-```
-
-```{r stimuli_frequency_compare_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
-
-frequency_compare_data %>% 
-	ggplot(aes(frequency_subtlex, frequency_childes, colour = test_language, fill = test_language)) +
-	facet_wrap(~test_language) +
-	geom_point(alpha = 0.5, stroke = 1, shape = 1) +
-	geom_smooth(method = "lm") +
-	labs(x = "SUBTLEX (adult norms)", y = "CHILDES (child norms)",
-		 colour = "Language", fill = "Language") +
-	coord_fixed() +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
 
@@
 		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-```
-
-##### {-}
-
-#### SUBTLEX {.tabset }
-
-##### Prime
-
-```{r stimuli_frequency_subtlex_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_subtlex_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
 		axis.title.x = element_blank(),

### 2021-10-21 Rmd/report_04_gca_relaxed.Rmd

@@
 	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
 	ggplot(aes(fct_rev(term1), term2, fill = .value)) +

### 2021-10-21 Rmd/report_05_attrition_stringent.Rmd

@@
 ---
-
-### Attrition {.tabset }
 
@@
 #### By trial
+
+```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(select(participants_stringent, participant, location)) %>% 
+	count(location, lp, age_group, trial_type, valid_status) %>% 
+	drop_na(trial_type) %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_col(position = position_fill()) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	scale_y_continuous(labels = percent) +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
 
@@
 		x30_months_valid = "Valid"
-	)
+	) %>% 
+	as_raw_html()
 
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants_stringent, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill()) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
 ```
@@
 		legend.title = element_blank(),
-		axis.text.x = element_text(size = 10),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
 		axis.text.y = element_text(size = 8),
@@
 
+##### {-}
+
 #### {-}
-
-### Raw data
-
-```{r, echo = FALSE}
-shinyAppFile(
-	here("R", "gaze_app", "app.R"), 
-	options = list(width = "100%", height = 700)
-)
-```

### 2021-10-21 Rmd/report.Rmd
Use only relaxed criteria

@@
 # load objects
+tar_load_globals()
 tar_load(participants)
@@
 tar_load(gaze)
-tar_load(gaze_relaxed)
+tar_load(gaze)
 tar_load(attrition)
-tar_load(attrition_relaxed)
+tar_load(attrition)
 tar_load(attrition_counter)
-tar_load(attrition_relaxed_counter)
+tar_load(attrition_counter)
 tar_load(model_fits)
-tar_load(model_fits_relaxed)
+tar_load(model_fits)
 
@@
 attrition <- attrition %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-
-attrition_relaxed <- attrition_relaxed %>% 
 	mutate(
@@
 
-attrition_relaxed_counter <- attrition_relaxed_counter %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			!valid_counter ~ "Invalid counter",
-			TRUE ~ "Valid"
-		))
-
-participants_stringent <- participants %>% 
+participants <- participants %>% 
 	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
-participants_relaxed <- participants %>% 
-	left_join(distinct(attrition_relaxed, participant, age_group, valid_participant)) %>% 
 	drop_na(participant) %>% 
@@
 
-participants_relaxed_counter <- participants %>% 
-	left_join(distinct(attrition_relaxed_counter, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
 ```
@@
 
-```{r child="report_00_participants_relaxed.Rmd"}
+```{r child="report_00_participants.Rmd"}
 ```
@@
 
-```{r child="report_04_gca_relaxed.Rmd"}
+```{r child="report_04_gca.Rmd"}
 ```
@@
 
-```{r child="report_05_attrition_relaxed.Rmd"}
+```{r child="report_05_attrition.Rmd"}
 ```
@@
 
-```{r child="report_06_vocabulary_relaxed.Rmd"}
+```{r child="report_06_vocabulary.Rmd"}
 ```

### 2021-10-21 Rmd/report_00_participants.Rmd
Use only relaxed criteria

---
---

* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group). `r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.

#### Summary

```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	as_raw_html()
```

```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp, test_language) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		test_language = md("**Language**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	as_raw_html()
```

```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

#### Longitudinal

We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30). Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	filter(valid_participant) %>% 
	mutate(age_group = str_remove(age_group, " months")) %>%
	ggplot(aes(age_group, participant, colour = lp)) +
	facet_grid(~location, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Lang. Pofile") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	)
```

#### {-}

### 2021-10-21 Rmd/report_01_stimuli.Rmd
Use only relaxed criteria

@@
 	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
+	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
+	# geom_jitter(colour = "white", size = 1, shape = 1,
+	# 			width = 0.1, alpha = 0.5, stroke = 1) +
 	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
@@
 		axis.title.x = element_blank(),
+		panel.grid.major.x = element_blank(),
 		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
@@
 ```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
 stimuli %>% 
@@
 	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
-	geom_jitter(colour = "black", size = 1, shape = 1,
-				width = 0.1, alpha = 0.5, stroke = 1) +
+	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
+	# geom_jitter(colour = "black", size = 1, shape = 1,
+	# 			width = 0.1, alpha = 0.5, stroke = 1) +
 	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
@@
 	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type)) +
+	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type,
+			   xmin = familiarity_prime-familiarity_se_prime, xmax = familiarity_prime-familiarity_se_prime)) +
 	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
 	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
@@
 		axis.title.y = element_blank(),
+		panel.grid.major.y = element_blank(),
 		plot.caption = element_text(size = 10, hjust = 0),
@@
 
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
+```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6.5, out.width="100%"}
 means <- stimuli %>% 
@@
 	facet_wrap(location~test_language, scales = "free_y") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
 	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
@@
 	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "white") +
+	geom_col(position = position_fill(), colour = "#0D1117") +
 	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
@@
 		legend.title = element_blank(),
+		panel.grid = element_blank(),
 		axis.title.y = element_blank(),
@@
 	facet_wrap(role~location~test_language) +
-	geom_col(position = position_fill()) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
 	labs(x = "% of trials", y = "Trial type",

### 2021-10-21 Rmd/report_05_attrition.Rmd
Use only relaxed criteria

---
---

#### Summary

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = "#0D1117", size = 1) +
	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

#### By location

```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
# plot participants
attrition_location <- attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type)

attrition_location %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +

	attrition_location %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +

	plot_layout(guides = "collect", ncol = 1) &
	scale_y_continuous(labels = percent) &
	coord_flip() &
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 10),
		axis.title = element_blank()
	)
```

#### By group

This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).

```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}

left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
	as_raw_html()

```

#### By participant

```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
	as_raw_html()
```

#### By trial

```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	drop_na(trial_type) %>% 
	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
	count() %>% 
	ungroup() %>%
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
	clean_names() %>% 
	gt(groupname_col = c("location", "lp")) %>% 
	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
	cols_label(
		location = "Location",
		lp = "Group",
		trial_type = "Trial type",
		x21_months_not_valid = "Not valid",
		x21_months_valid = "Valid",
		x25_months_not_valid = "Not valid",
		x25_months_valid = "Valid",
		x30_months_not_valid = "Not valid",
		x30_months_valid = "Valid"
	) %>% 
	as_raw_html()

```

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	count(location, age_group, trial_type, valid_status) %>% 
	drop_na(trial_type) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(location~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

#### By lexical frequency {.tabset }

##### Prime frequency

```{r attrition_frequency_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### Target frequency

```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "#0D1117", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "#0D1117") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### {-}

#### By familiarity {.tabset}

##### Prime familiarity

```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	ggplot(aes(trial_type, familiarity_prime, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "#0D1117", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "#0D1117") +
	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### Target familiarity

```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
sample_size <- attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	count(trial_type, lp, age_group, valid_status)

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "#0D1117", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "#0D1117") +
	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### {-}

#### By animacy {.tabset }

##### Prime

```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_prime) %>% 
	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

```

##### Target

```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

```

##### {-}

#### By category {.tabset}

##### Prime

```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
	drop_na(trial_type, category_prime) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### Target

```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
	drop_na(trial_type, category_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

##### {-}

### 2021-10-21 Rmd/report_06_vocabulary.Rmd
Use only relaxed criteria

---
---

#### L1 vocabulary

This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis. Results are presented separately for each age group. The shape of the violins, represents the distribution of the vocabulary sizes. The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values. vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure. for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.

```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, location)

# vocabulary
participants %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_grid(location~age_group) +
	# geom_violin(
	# 	position = position_dodge(width = 0.75),
	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
	# ) + 
	geom_hline(yintercept = 0.5, colour = "white") +
	geom_point(
		aes(lp, vocab_size_l1),
		shape = 1, colour = "white", size = 1, stroke = 1,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_boxplot(
		aes(lp, vocab_size_l1, colour = lp, fill = lp),
		width = 0.25, outlier.colour = NA, fill = "#0D1117",
		position = position_dodge(width = 0.75), size = 1
	) +
	geom_text(
		data = sample_size,
		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
		colour = "white", fill = "white", show.legend = FALSE
	) +
	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		panel.grid.major.y = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

```

#### Total vocabulary

```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, location)

# vocabulary
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_grid(location~age_group) +
	# geom_violin(
	# 	position = position_dodge(width = 0.75),
	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
	# ) + 
	geom_hline(yintercept = 0.5, colour = "grey") +
	geom_point(
		aes(lp, vocab_size_total),
		shape = 1, colour = "white", size = 1, stroke = 1,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_boxplot(
		aes(lp, vocab_size_total, colour = lp, fill = lp),
		width = 0.25, fill = "#0D1117", outlier.colour = NA,
		position = position_dodge(width = 0.75), size = 1
	) +
	geom_text(
		data = sample_size,
		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
		colour = "white", fill = "white", show.legend = FALSE
	) +
	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	)

```

#### Conceptual vocabulary

```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, location)

# vocabulary
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_grid(location~age_group) +
	# geom_violin(
	# 	position = position_dodge(width = 0.75),
	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
	# ) + 
	geom_hline(yintercept = 0.5, colour = "grey") +
	geom_point(
		aes(lp, vocab_size_conceptual),
		shape = 1, colour = "white", size = 1, stroke = 1,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_boxplot(
		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
		width = 0.25, fill = "#0D1117", outlier.colour = NA,
		position = position_dodge(width = 0.75), size = 1
	) +
	geom_text(
		data = sample_size,
		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
		colour = "white", fill = "white", show.legend = FALSE
	) +
	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9),
		panel.grid.major.x = element_blank()
	)

```

#### {-}

### {-}

### 2021-10-22 Rmd/report.Rmd
Use only one Rmd for report

@@
 tar_load(gaze)
-tar_load(gaze)
-tar_load(attrition)
 tar_load(attrition)
 tar_load(attrition_counter)
-tar_load(attrition_counter)
-tar_load(model_fits)
 tar_load(model_fits)
@@
 
-```{r child="report_00_participants.Rmd"}
+* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
+* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
+`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
+* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
+
+#### Summary
+
+```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants %>% 
+	left_join(distinct(attrition, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	count(location, age_group, lp) %>% 
+	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
+	gt(groupname_col = "location") %>% 
+	cols_label(
+		lp = md("**Language profile**"),
+		`21 months` = md("**21 months**"),
+		`25 months` = md("**25 months**"),
+		`30 months` = md("**30 months**")
+	) %>% 
+	as_raw_html()
 ```
+
+```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants %>% 
+	left_join(distinct(attrition, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	count(location, age_group, lp, test_language) %>% 
+	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
+	gt(groupname_col = "location") %>% 
+	cols_label(
+		lp = md("**Language profile**"),
+		test_language = md("**Language**"),
+		`21 months` = md("**21 months**"),
+		`25 months` = md("**25 months**"),
+		`30 months` = md("**30 months**")
+	) %>% 
+	as_raw_html()
+```
+
+```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+participants %>% 
+	left_join(distinct(attrition, participant, valid_participant)) %>% 
+	filter(valid_participant) %>% 
+	drop_na(valid_participant) %>% 
+	ggplot(aes(lp, fill = as.factor(test_language))) +
+	facet_grid(location~age_group, scales = "free") +
+	geom_bar(colour = NA) +
+	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
+	labs(x = "Group", y = "Sample size", fill = "Test language") +
+	theme(
+		legend.position = "top",
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 10),
+		axis.title.y = element_text(angle = 90)
+	) 
+```
+
+#### Longitudinal
+
+We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
+Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+
+```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+participants %>% 
+	left_join(distinct(attrition, participant, valid_participant)) %>%
+	filter(valid_participant) %>% 
+	mutate(age_group = str_remove(age_group, " months")) %>%
+	ggplot(aes(age_group, participant, colour = lp)) +
+	facet_grid(~location, scales = "free") +
+	geom_line(aes(group = interaction(lp, participant))) +
+	geom_point(size = 2) +
+	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Lang. Pofile") +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text = element_text(size = 10),
+		axis.title.y = element_blank(),
+		axis.text.y = element_blank(),
+		axis.ticks.y = element_blank()
+	)
+```
+
+#### {-}
 
@@
 
-```{r child="report_01_stimuli.Rmd"}
+### Frequency {.tabset }
+
+#### CHILDES {.tabset }
+
+##### Prime
+
+```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
+	facet_wrap(location~test_language) +
+	geom_violin() +
+	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
+	# geom_jitter(colour = "white", size = 1, shape = 1,
+	# 			width = 0.1, alpha = 0.5, stroke = 1) +
+	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
+		 colour = "Trial type", fill = "Trial type") +
+	theme(
+		legend.position = "none",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 9),
+		axis.title.x = element_blank(),
+		panel.grid.major.x = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
 ```
+
+##### Target
+
+```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
+	facet_wrap(location~test_language) +
+	geom_violin() +
+	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
+	# geom_jitter(colour = "black", size = 1, shape = 1,
+	# 			width = 0.1, alpha = 0.5, stroke = 1) +
+	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
+		 colour = "Trial type", fill = "Trial type") +
+	theme(
+		legend.position = "none",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 9),
+		axis.title.x = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+```
+
+##### {-}
+
+#### {-}
+
+### Familiarity {.tabset }
+
+#### Prime
+
+```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
+means <- stimuli %>% 
+	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
+	group_by(test_language, location, trial_type) %>% 
+	summarise(
+		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
+		.groups = "drop"
+	) %>% 
+	drop_na()
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
+	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type,
+			   xmin = familiarity_prime-familiarity_se_prime, xmax = familiarity_prime-familiarity_se_prime)) +
+	facet_wrap(location~test_language, scales = "free_y") +
+	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
+	# geom_errorbar() +
+	geom_point() +
+	labs(x = "% of infants that understand", y = "Prime word",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_x_continuous(labels = percent, limits = c(0, 1)) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 7),
+		axis.title.y = element_blank(),
+		panel.grid.major.y = element_blank(),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
+```
+
+#### Target
+
+```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6.5, out.width="100%"}
+means <- stimuli %>% 
+	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
+	group_by(test_language, location, trial_type) %>% 
+	summarise(
+		familiarity_target = mean(familiarity_target, na.rm = TRUE),
+		.groups = "drop"
+	)
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
+	facet_wrap(location~test_language, scales = "free_y") +
+	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
+	# geom_errorbar() +
+	geom_point() +
+	labs(x = "% of infants that understand", y = "Target word",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_x_continuous(labels = percent, limits = c(0, 1)) +
+	# scale_y_reordered() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 7),
+		axis.title.y = element_blank(),
+		panel.grid.major.y = element_blank(),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
+```
+
+#### {-}
+
+### Animacy
+
+```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
+
+animacy <- stimuli %>%
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
+	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
+	count(location, test_language, trial_type, role, is_animate) %>% 
+	drop_na(is_animate) %>% 
+	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
+
+animacy %>% 
+	filter(role=="Prime") %>% 
+	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
+	facet_wrap(location~test_language, ncol = 4) +
+	geom_col(position = position_fill(), colour = "#0D1117") +
+	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
+	scale_y_continuous(labels = percent) +
+	coord_flip() + 
+	theme(
+		axis.title.x = element_blank()
+	) +
+
+	animacy %>% 
+	filter(role=="Target") %>% 
+	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
+	facet_wrap(location~test_language, ncol = 4) +
+	geom_col(position = position_fill(), colour = "#0D1117") +
+	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+
+	plot_layout(guides = "collect", ncol = 1) &
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.title.y = element_blank(),
+		axis.text = element_text(size = 7),
+		strip.text = element_text(size = 11)
+	)
+
+```
+
+### Semantic category
+
+```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
+
+stimuli %>% 
+	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
+	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
+	drop_na(trial_type, category) %>% 
+	count(trial_type, test_language, location, role, category) %>% 
+	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
+	facet_wrap(role~location~test_language) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "% of trials", y = "Trial type",
+		 colour = "Trial type", fill = "Trial type") +
+	scale_x_continuous(labels = percent) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text = element_text(size = 9),
+		axis.title.y = element_blank(),
+		plot.caption = element_text(size = 10, hjust = 0),
+	)
+
+```
+
+### {-}
 
@@
 
-```{r child="report_02_procedure.Rmd"}
+## Data analysis
+
+### Vocabulary data
+
+We collected vocabulary data from participants.
+In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
+In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
+In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
+In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
+All checklists included the words involved in the trial lists.
+When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
+Each response to either checklist was aggregated to produce several vocabulary measures:
+
+* **Total vocabulary**: total number of words the child knows, summing up both languages.
+For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
+* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
+For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
+* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
+For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
+
+Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
+
+## Gaze data {.tabset .tabset-pills}
+
+Each trial was divided into 100 ms time bins.
+for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
+Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
+
+### Workflow
+
+```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+DiagrammeR::grViz("digraph {
+  graph [layout = dot, rankdir = TB]
+
+  node [shape = rectangle, fontname = 'Arial']        
+  rec1 [label = 'Merge Barcelona and Oxford data']
+  rec2 [label = 'Impute missing/invalid samples (pending)']
+  rec2 [label = 'Extract fixations (pending)']
+  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
+  rec4 [label = 'Divide each trial into 100 ms time bins']
+  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
+  rec6 [label = 'Exclude time bins 1-3 (pending)']
+  rec7 [label = 'Apply trial-level inclusion criteria']
+  rec8 [label = 'Apply participant-level inclusion criteria']
+
+  # edge definitions with the node IDs
+  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
+  }", 
+  height = 500)
 ```
 
-## Data analysis
+### Inclusion criteria
 
-```{r child="report_03_data-analysis.Rmd"}
+#### Trial-level inclusion criteria
+
+* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
+* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
+* At least one sample in target and one sample in distractor
+* Participant understands prime word in both languages
+* Participant knows the target word in the test language
+* Participant knows the distractor word in the test language
+
+#### Participant-level inclusion criteria
+
+* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
+* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
+* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
+* $\geq$ 36 gestational weeks
+* $\geq$ 2,800g birth weight
+* No diagnosed developmental, hearing, or visual disorders
+* Not exposed to more than 10% to a 3rd language
+
+### Input variables
+
+* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
+* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
+* Trial type (`trial_type1` and `trial_type2`).
+Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
+We coded two contrasts: `trial_type1`, comparing related trials vs.
+unrelated trials (*Cognate* + *Non-cognate* vs.
+*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
+*Non-cognate* trials.
+These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
+
+```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+contrasts(gaze$trial_type) %>% 
+	as.data.frame() %>% 
+	set_names(paste0("trial_type", 1:2)) %>% 
+	rownames_to_column("level") %>% 
+	gt(rowname_col = "level") %>%
+	as_raw_html()
+
 ```
+
+### {-}
+
+## {-}
 
@@
 
-```{r child="report_04_gca.Rmd"}
+```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+fit <- model_fits$fit
 ```
+
+#### Model details
+
+We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
+
+```
+elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
+(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
+```
+
+The formal implementation of this model is:
+
+$$
+
+\color{white}{
+\log \Bigg( \frac{p}{n - q} \Bigg) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
+(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
+(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
+(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
+(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
+(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
+(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
+(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
+(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
+}
+$$
+
+#### Fixed effects
+
+```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
+
+draws %>% 
+	mean_qi(.width = c(0.95, 0.50)) %>% 
+	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
+	clean_names() %>% 
+	select(-c(point, interval, value_0_5)) %>% 
+	gt(rowname_col = "variable") %>% 
+	fmt_number(2:6) %>% 
+	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
+	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		variable = md("**Predictor**"),
+		value_0_95 = md("**Mean**"),
+		lower_0_95 = md("**95% CrI**"),
+		lower_0_5 = md("**50% CrI**")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#b9fac4")
+		),
+		locations = cells_body(
+			columns = lower_0_95,
+			rows = lower_0_95 > 0
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#b9fac4")
+		),
+		locations = cells_body(
+			columns = lower_0_5,
+			rows = lower_0_5 > 0
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#fabfb9")
+		),
+		locations = cells_body(
+			columns = lower_0_95,
+			rows = upper_0_95 < 0
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_fill(color = "#fabfb9")
+		),
+		locations = cells_body(
+			columns = lower_0_5,
+			rows = upper_0_5 < 0
+		)
+	) %>% 
+	as_raw_html()
+```
+
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
+
+draws %>% 
+	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
+	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
+	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
+	geom_vline(xintercept = 0, colour = "white") +
+	stat_halfeye(point_color = "white", interval_color = "white") +
+	labs(x = "Value", y = "Variable", fill = "CrI") +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	theme(
+		axis.title = element_blank(),
+		legend.position = "top"
+	)
+
+```
+
+#### Random effects
+
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+vcov(fit) %>% 
+	cov2cor() %>% 
+	as.data.frame() %>% 
+	rownames_to_column("term1") %>% 
+	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
+	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
+	geom_tile() +
+	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
+	scale_fill_distiller(limits = c(-1, 1)) +
+	coord_equal() +
+	theme(
+		legend.position = "top",
+		legend.text = element_text(size = 8),
+		axis.title = element_blank(),
+		axis.text.y = element_text(hjust = 1, size = 7),
+		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
+	)
+
+```
+
+#### Marginal means {.tabset }
+
+##### Overall
+
+```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant) %>% 
+	count(lp)
+
+n <- expand_grid(
+	lp = c("Monolingual", "Bilingual"),
+	age_group = c("25 months"),
+	trial_type = unique(gaze$trial_type),
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
+)
+
+m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
+	mutate(.value = logit_to_prob(.epred))
+
+ggplot(m, aes(time_bin_center, .value)) +
+	facet_wrap(~fct_rev(lp)) +
+	geom_hline(yintercept = 0.5, colour = "white") +
+	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
+				  colour = trial_type),
+			  alpha = 0.15, size = 0.65) +
+	stat_summary(aes(group = trial_type, colour = trial_type),
+				 fun = mean, geom = "line", size = 1.25) +
+	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
+										  colour = trial_type),
+				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
+				 position = position_dodge(width = 0.3)) +
+	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
+			  colour = "white", hjust = 0, size = 5) +
+	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
+		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
+	scale_color_brewer(palette = "Set1") +
+	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 9),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.x = element_blank()
+	)
+```
+
+##### {-}
+
+#### {-}
 
@@
 
-```{r child="report_05_attrition.Rmd"}
+#### Summary
+
+```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+participants %>% 
+	left_join(distinct(attrition, participant, valid_participant)) %>%
+	left_join(vocabulary) %>% 
+	drop_na(valid_participant) %>% 
+	mutate(
+		valid_status = case_when(
+			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
+			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
+			!valid_participant ~ "Not valid"
+		)
+	) %>% 
+	ggplot(aes(lp, fill = valid_status)) +
+	facet_grid(location~age_group, scales = "free") +
+	geom_bar(colour = "#0D1117", size = 1) +
+	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
+	scale_colour_brewer(palette = "Set1") +
+	labs(x = "Group", y = "Sample size", fill = "Valid?") +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.y = element_blank(),
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 10),
+		axis.title.y = element_text(angle = 90)
+	) 
 ```
+
+#### By location
+
+```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
+# plot participants
+attrition_location <- attrition %>% 
+	left_join(select(participants, participant, location)) %>% 
+	count(location, lp, age_group, trial_type, valid_status) %>% 
+	drop_na(trial_type)
+
+attrition_location %>% 
+	filter(location=="Barcelona") %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
+
+	attrition_location %>% 
+	filter(location=="Oxford") %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
+
+	plot_layout(guides = "collect", ncol = 1) &
+	scale_y_continuous(labels = percent) &
+	coord_flip() &
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 10),
+		axis.title = element_blank()
+	)
+```
+
+#### By group
+
+This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
+
+```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
+
+left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
+	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
+	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
+			  .groups = "drop") %>% 
+	pivot_wider(
+		names_from = trial_type,
+		values_from = valid_trial_count
+	) %>% 
+	clean_names() %>% 
+	group_by(lp, location, age_group) %>% 
+	summarise(
+		cognate = mean(cognate, na.rm = TRUE),
+		non_cognate = mean(non_cognate, na.rm = TRUE),
+		unrelated = mean(unrelated, na.rm = TRUE),
+		sum_n = sum(valid_participant, na.rm = TRUE),
+		prop_n = mean(valid_participant, na.rm = TRUE),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	arrange(age_group, lp, location) %>% 
+	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
+	gt() %>% 
+	tab_spanner(
+		"Mean valid trials",
+		c("cognate", "non_cognate", "unrelated")
+	) %>% 
+	tab_spanner(
+		"N participants",
+		c("sum_n", "n", "prop_n")
+	) %>% 
+	cols_label(
+		age_group = "Age",
+		lp = "Group",
+		sum_n = "Valid",
+		location = "Laboratory",
+		n = "Tested",
+		prop_n = "Valid (%)",
+		cognate = "Cognate (8)",
+		non_cognate = "Non-cognate (8)",
+		unrelated = "Unrelated (16)"
+	) %>% 
+	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
+	fmt_percent(c("prop_n")) %>% 
+	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
+	as_raw_html()
+
+```
+
+#### By participant
+
+```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(select(participants, participant, location)) %>% 
+	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
+	group_by(location, participant, lp, age_group, valid_participant) %>% 
+	summarise(
+		valid = mean(valid_trial),
+		invalid_gaze = mean(!valid_gaze),
+		invalid_vocab = mean(!valid_vocab),
+		.groups = "drop"
+	) %>% 
+	relocate(participant) %>% 
+	gt() %>% 
+	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
+	cols_label(
+		participant = "Participant",
+		location = "Location",
+		lp = "Lang. Profile",
+		age_group = "Age",
+		valid_participant = "Valid participant",
+		valid = "Valid trials (%)",
+		invalid_gaze = "Gaze (%)",
+		invalid_vocab = "Vocabulary (%)"
+	) %>% 
+	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
+	as_raw_html()
+```
+
+#### By trial
+
+```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(select(participants, participant, location)) %>% 
+	drop_na(trial_type) %>% 
+	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
+	count() %>% 
+	ungroup() %>%
+	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
+	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
+	clean_names() %>% 
+	gt(groupname_col = c("location", "lp")) %>% 
+	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
+	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
+	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
+	cols_label(
+		location = "Location",
+		lp = "Group",
+		trial_type = "Trial type",
+		x21_months_not_valid = "Not valid",
+		x21_months_valid = "Valid",
+		x25_months_not_valid = "Not valid",
+		x25_months_valid = "Valid",
+		x30_months_not_valid = "Not valid",
+		x30_months_valid = "Valid"
+	) %>% 
+	as_raw_html()
+
+```
+
+```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(select(participants, participant, location)) %>% 
+	count(location, age_group, trial_type, valid_status) %>% 
+	drop_na(trial_type) %>% 
+	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	facet_grid(location~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	scale_y_continuous(labels = percent) +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+#### By lexical frequency {.tabset }
+
+##### Prime frequency
+
+```{r attrition_frequency_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+sample_size <- attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, frequency_prime_childes) %>% 
+	count(trial_type, lp, age_group, valid_status)
+
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, frequency_prime_childes) %>% 
+	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_boxplot(fill = "white", width = 0.25,
+				 position =  position_dodge(width = 0.5),
+				 size = 0.75, outlier.colour = NA) +
+	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
+			   position = position_dodge(width = 0.7), colour = "white") +
+	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
+	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.y = element_blank(),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+```{r attrition_frequency_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
+	drop_na(trial_type, frequency_prime_childes) %>% 
+	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
+	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### Target frequency
+
+```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+sample_size <- attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, frequency_target_childes) %>% 
+	count(trial_type, lp, age_group, valid_status)
+
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, frequency_target_childes) %>% 
+	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_boxplot(fill = "#0D1117", width = 0.25,
+				 position =  position_dodge(width = 0.5),
+				 size = 0.75, outlier.colour = NA) +
+	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
+			   position = position_dodge(width = 0.7), colour = "#0D1117") +
+	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
+	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.y = element_blank(),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
+	drop_na(trial_type, frequency_target_childes) %>% 
+	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
+	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### {-}
+
+#### By familiarity {.tabset}
+
+##### Prime familiarity
+
+```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+sample_size <- attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, familiarity_prime) %>% 
+	count(trial_type, lp, age_group, valid_status)
+
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, familiarity_prime) %>% 
+	ggplot(aes(trial_type, familiarity_prime, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_boxplot(fill = "#0D1117", width = 0.25,
+				 position =  position_dodge(width = 0.5),
+				 size = 0.75, outlier.colour = NA) +
+	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
+			   position = position_dodge(width = 0.7), colour = "#0D1117") +
+	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent, limits = c(0, 1)) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.y = element_blank(),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+```{r attrition_familiarity_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
+	drop_na(trial_type, familiarity_prime) %>% 
+	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
+	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### Target familiarity
+
+```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+sample_size <- attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, familiarity_target) %>% 
+	count(trial_type, lp, age_group, valid_status)
+
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
+	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	drop_na(trial_type, familiarity_target) %>% 
+	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
+	facet_grid(lp~age_group) +
+	geom_boxplot(fill = "#0D1117", width = 0.25,
+				 position =  position_dodge(width = 0.5),
+				 size = 0.75, outlier.colour = NA) +
+	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
+			   position = position_dodge(width = 0.7), colour = "#0D1117") +
+	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent, limits = c(0, 1)) +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid.major.y = element_blank(),
+		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
+# plot participants
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
+	drop_na(trial_type, familiarity_target) %>% 
+	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
+	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
+	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### {-}
+
+#### By animacy {.tabset }
+
+##### Prime
+
+```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
+	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
+	drop_na(trial_type, is_animate_prime) %>% 
+	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
+	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+
+```
+
+##### Target
+
+```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
+	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
+	drop_na(trial_type, is_animate_target) %>% 
+	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
+	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+
+```
+
+##### {-}
+
+#### By category {.tabset}
+
+##### Prime
+
+```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
+	drop_na(trial_type, category_prime) %>% 
+	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
+	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### Target
+
+```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+attrition %>% 
+	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
+	drop_na(trial_type, category_target) %>% 
+	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
+	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
+	facet_grid(trial_type~age_group) +
+	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
+	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	scale_y_continuous(labels = percent) +
+	coord_flip() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		panel.grid = element_blank(),
+		axis.text.x = element_text(size = 10),
+		axis.text.y = element_text(size = 8),
+		axis.title = element_blank()
+	)
+```
+
+##### {-}
 
@@
 
-```{r child="report_06_vocabulary.Rmd"}
+#### L1 vocabulary
+
+This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
+Results are presented separately for each age group.
+The shape of the violins, represents the distribution of the vocabulary sizes.
+The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
+vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
+for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
+
+```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	count(age_group, location)
+
+# vocabulary
+participants %>% 
+	drop_na(lp) %>%
+	filter(valid_participant) %>% 
+	ggplot() +
+	facet_grid(location~age_group) +
+	# geom_violin(
+	# 	position = position_dodge(width = 0.75),
+	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
+	# ) + 
+	geom_hline(yintercept = 0.5, colour = "white") +
+	geom_point(
+		aes(lp, vocab_size_l1),
+		shape = 1, colour = "white", size = 1, stroke = 1,
+		position = position_jitter(width = 0.1, seed = 888)
+	) +
+	geom_boxplot(
+		aes(lp, vocab_size_l1, colour = lp, fill = lp),
+		width = 0.25, outlier.colour = NA, fill = "#0D1117",
+		position = position_dodge(width = 0.75), size = 1
+	) +
+	geom_text(
+		data = sample_size,
+		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
+		colour = "white", fill = "white", show.legend = FALSE
+	) +
+	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) +
+	theme(
+		legend.title = element_blank(),
+		legend.position = "none",
+		panel.grid.major.y = element_blank(),
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 9)
+	)
+
 ```
+
+#### Total vocabulary
+
+```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	count(age_group, location)
+
+# vocabulary
+participants %>% 
+	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+	drop_na(lp) %>%
+	filter(valid_participant) %>% 
+	ggplot() +
+	facet_grid(location~age_group) +
+	# geom_violin(
+	# 	position = position_dodge(width = 0.75),
+	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
+	# ) + 
+	geom_hline(yintercept = 0.5, colour = "grey") +
+	geom_point(
+		aes(lp, vocab_size_total),
+		shape = 1, colour = "white", size = 1, stroke = 1,
+		position = position_jitter(width = 0.1, seed = 888)
+	) +
+	geom_boxplot(
+		aes(lp, vocab_size_total, colour = lp, fill = lp),
+		width = 0.25, fill = "#0D1117", outlier.colour = NA,
+		position = position_dodge(width = 0.75), size = 1
+	) +
+	geom_text(
+		data = sample_size,
+		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
+		colour = "white", fill = "white", show.legend = FALSE
+	) +
+	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) +
+	theme(
+		legend.title = element_blank(),
+		legend.position = "none",
+		panel.grid.major.x = element_blank(),
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 9),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+	)
+
+```
+
+#### Conceptual vocabulary
+
+```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
+sample_size <- participants %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	count(age_group, location)
+
+# vocabulary
+participants %>% 
+	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+	drop_na(lp) %>%
+	filter(valid_participant) %>% 
+	ggplot() +
+	facet_grid(location~age_group) +
+	# geom_violin(
+	# 	position = position_dodge(width = 0.75),
+	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
+	# ) + 
+	geom_hline(yintercept = 0.5, colour = "grey") +
+	geom_point(
+		aes(lp, vocab_size_conceptual),
+		shape = 1, colour = "white", size = 1, stroke = 1,
+		position = position_jitter(width = 0.1, seed = 888)
+	) +
+	geom_boxplot(
+		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
+		width = 0.25, fill = "#0D1117", outlier.colour = NA,
+		position = position_dodge(width = 0.75), size = 1
+	) +
+	geom_text(
+		data = sample_size,
+		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
+		colour = "white", fill = "white", show.legend = FALSE
+	) +
+	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
+	scale_y_continuous(limits = c(0, 1), labels = percent) +
+	theme(
+		legend.title = element_blank(),
+		legend.position = "none",
+		axis.title.x = element_blank(),
+		axis.text = element_text(size = 9),
+		panel.grid.major.x = element_blank()
+	)
+
+```
+
+#### {-}
+
+### {-}
 

### 2021-10-22 Rmd/report.Rmd
Fix plots

@@
 		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
+		axis.title.y = element_text(angle = 90),
+		panel.grid.major.x = element_blank()
 	) 
@@
 		axis.title.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
 		plot.caption = element_text(size = 10, hjust = 0),
+		panel.grid.major.x = element_blank()
+
 	)
@@
 		plot.caption = element_text(size = 10, hjust = 0),
+		panel.grid = element_blank()
+
 	)
@@
 	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "white", width = 0.25,
+	geom_boxplot(fill = "#0D1117", width = 0.25,
 				 position =  position_dodge(width = 0.5),
@@
 	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "white") +
+			   position = position_dodge(width = 0.7), colour = "#0D1117") +
 	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +

### 2021-10-22 Rmd/report.Rmd
Fix plots

@@
 	results = "asis",
-	dpi = 150,
+	dpi = 100,
 	dev.args = list(png = list(type = "cairo"))

### 2021-10-22 Rmd/report.Rmd
Reduce dpi

@@
 
-##### Prime frequency
-
-```{r attrition_frequency_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_prime_childes) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_prime_childes) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_frequency_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
-	drop_na(trial_type, frequency_prime_childes) %>% 
-	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
-	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### Target frequency
-
 ```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
@@
 #### By familiarity {.tabset}
-
-##### Prime familiarity
-
-```{r attrition_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_prime) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_prime) %>% 
-	ggplot(aes(trial_type, familiarity_prime, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_familiarity_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
-	drop_na(trial_type, familiarity_prime) %>% 
-	mutate(familiarity_prime = round(familiarity_prime, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_prime) %>% 
-	ggplot(aes(as.factor(familiarity_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### Target familiarity
 
@@
 
-##### Prime
-
-```{r attrition_animacy_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_prime)) %>%
-	mutate(is_animate_prime = ifelse(is_animate_prime, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_prime) %>% 
-	count(trial_type, location, age_group, valid_status, trial_type, is_animate_prime) %>% 
-	ggplot(aes(as.factor(is_animate_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-##### Target
-
 ```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
@@
 #### By category {.tabset}
-
-##### Prime
-
-```{r attrition_category_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_prime)) %>%
-	drop_na(trial_type, category_prime) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_prime) %>% 
-	ggplot(aes(fct_rev(category_prime), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### Target
 

### 2021-10-22 Rmd/report.Rmd
Reduce dpi

@@
 	cache.extra = knitr::rand_seed,
-	out.width = "100%",
+	out.width = "80%",
 	results = "asis",

### 2021-11-08 Rmd/report.Rmd

@@
 	results = "asis",
-	dpi = 100,
+	dpi = 25,
 	dev.args = list(png = list(type = "cairo"))

### 2021-11-12 Shiny/posterior/app.R
Add Shiny app and item-level random effects to the model

@@ -1,0 +1,227 @@
+library(here)
+library(dplyr)
+library(shiny)
+library(tidybayes)
+library(ggplot2)
+library(purrr)
+library(brms)
+library(scales)
+
+fit <- readRDS(here("Results", "fit.rds"))
+d <- fit$data
+
+source(here("R", "utils.R"))
+
+# population-level effects
+message("Generating population-level effects...")
+
+coefs <- gather_draws(fit, `b_.*`, regex = TRUE)
+
+nd <- expand.grid(
+    age_group = paste0(c(21, 25, 30), " months"),
+    lp = c("Monolingual", "Bilingual"),
+    trial_type = unique(d$trial_type),
+    time_bin_center = seq(min(d$time_bin_center), max(d$time_bin_center), 0.25)
+)
+
+preds <- add_epred_draws(nd, fit, ndraws = 25, re_formula = NA) %>% 
+    mutate(.epred = inv_logit_scaled(.epred))
+
+
+# conditional means by participant
+message("Generating participant-level effects...")
+
+nd_participant <- expand.grid(
+    participant = unique(d$participant),
+    trial_type = unique(d$trial_type),
+    time_bin_center = seq(min(d$time_bin_center), max(d$time_bin_center), 0.25)
+) %>% 
+    left_join(distinct(d, participant, age_group, lp))
+
+preds_participant <- add_epred_draws(
+    nd_participant, fit, ndraws = 25,
+    re_formula = ~ (1 + time_bin_center*trial_type + age_group) | participant
+) %>% 
+    mutate(.epred = inv_logit_scaled(.epred)) %>% 
+    ungroup() %>% 
+    group_split(participant) %>% 
+    set_names(unique(d$participant))
+
+coefs_participant <- gather_draws(fit, r_participant[participant, param]) %>% 
+    ungroup() %>% 
+    group_split(participant) %>% 
+    set_names(unique(d$participant))
+
+# conditional means by target
+message("Generating target-level effects...")
+
+nd_target <- expand.grid(
+    target = unique(d$target),
+    age_group = paste0(c(21, 25, 30), " months"),
+    lp = c("Monolingual", "Bilingual"),
+    trial_type = unique(d$trial_type),
+    time_bin_center = seq(min(d$time_bin_center), max(d$time_bin_center), 0.25)
+)
+
+preds_target <- add_epred_draws(
+    nd_target, fit, ndraws = 25,
[…]

### 2021-12-06 Communications/2022-01-25_lacre/2021-01-25_lacre.tex
Add new communications for ICIS and LACRE

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={2021-01-25\_lacre},
  pdfauthor={Gonzalo García-Castro},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{2021-01-25\_lacre}
\author{Gonzalo García-Castro}
\date{10/11/2021}

\begin{document}
\maketitle

\hypertarget{background}{%
\subsection{Background}\label{background}}

Infants learning two languages face the challenge of having to learn two
distinct sets of words. Some of the words across both languages refer to
similar concepts: for instance, \emph{chair} and \emph{silla} (in
Spanish). These pairs of words are called \emph{translation
equivalents}. Sometimes, translation equivalents also overlap in form,
frequently due to their shared etymological origin. These form-similar
translation equivalents, such as \emph{boot} and \emph{bota} (in
Spanish), are referred to as \emph{cognates}.

There is extensive literature on how cognateness impacts the dynamics of
lexical access during words comprehension and production. One of its
main findings is that bilinguals process cognates (such as \emph{boot}
and \emph{bota}) more differently than non-cognates (such as
\emph{chair} and \emph{silla}). For instance, Costa, Caramazza, and
Sebastian-Galles (2000) asked Spanish-Catalan bilinguals to name a
series of familiar pictures in Spanish. Part of the pictures referred to
objects whose labels in Spanish and Catalan were cognates, whereas the
other pictures referred to non-cognates. On average, participants named
cognate pictures faster than non-cognate pictures. This effect was
independent of lexical frequency and, critically, was not observed when
Spanish monolinguals performed the same task. This suggests that
bilinguals activated labels in both languages, and that their phonology
interacted to facilitate naming.

Later studies provided evidence that the locus of this facilitation
effect was at the lexical level, and not just at the articulatory level
{[}reference needed here{]}: this effect has also been reported during
comprehension, at both the visual-orthographic and the
auditory-phonology modalities) (e.g., Thierry and Wu 2007). Overall,
these findings have led researchers to hypothesise that lexical access
is language-non selective, that is, bilinguals activate lexical
representations in both languages in parallel during comprehension and
production, based on their semantic and phonological overlap.

This cross-talk between languages has also been suggested to be present
in children's and toddlers' lexicon (Von Holzen and Mani 2012; Bosma and
Nota 2020), but it is still unclear how it impacts the trajectories of
language acquisition at these early ages. In this study we sought to
investigate the developmental trajectories of lexical access in a cohort
of Catalan-Spanish and English-Spanish bilinguals.

To do this, we used an adaptation of Mani and Plunkett (2010)'s priming
paradigm. This paradigm consists of a spoken word recognition task in
which participants are first presented with a picture in silence in the
centre of the screen for 1.5 seconds. Then, two other pictures are
presented side-by-side during 2 seconds, and one of them is named. The
other is not. Looking times to the target picture are recorded from name
onset. From now on, I will refer to the silent picture presented first
as the \emph{prime}, to the named picture as the \emph{target}, and to
the non-named picture presented next to the target as \emph{distractor}.

In their experiment, Mani and Plunkett manipulated the phonological
overlap between the prime label and the target label: in some trials,
both labels shared phonological onset (\emph{bee}-\emph{ball}), whereas
in other trials they did not share phonological onset
(\emph{cow}-\emph{book}). In all trials, the distractor label did not
share onset with either of the prime or target labels (e.g.,
\emph{teeth}). The authors registered 18 month-old participants' looking
preference for the target object after name onset, as a proxy of word
recognition, and found that target preference was stronger after a
phonologically related prime than after a phonologically unrelated
prime. There results have three main implications:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Phonologically related prime pictures facilitated target recognition
\item
  This is only possible if participants lexicalised the prime pictures,
  even though this picture was presented in silence
\item
  The label participants generated upon prime picture presentation was
  phonologically detailed, and this phonological form interacted with
  the auditory recognition of a subsequently presented word
\end{enumerate}

In a subsequent study, the authors found the inverse effect in 24
month-old toddlers: target looking preference was weaker after a
phonologically related prime picture compared to after an unrelated one
(Mani and Plunkett 2011). The authors suggested that the change in the
direction of the effect observed between 18 and 24 month-old
participants was due to the increment in vocabulary size and the
establishment of (inhibitory) links between phonologically related
lexical entries that might have occurred between both ages. Supporting
this account, the inhibition effect they reported was stronger as the
number of phonological neighbours of the target increased: the
recognition of words surrounded by more phonologically related
neighbours suffered the most from the priming effect.

We adapted this paradigm to test the language-non selectivity account in
bilingual toddlers. Following Mani \& Plunkett's original
implementation, In our task half of the prime-target pairs in the trial
lists shared phonological onset, and the other half did not share
phonological onset. We added a novel manipulation: half of the primes in
the phonologically related condition were cognates and the other half
were non-cognates. We classified two translation equivalents as cognates
if they shared phonological onset. Here is an illustration of each trial
type:

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{llll}
\toprule
Prime type & Prime & Target & Distractor \\ 
\midrule
Cognate (N = 8) & flower (flor) & fork & balloon \\ 
Non-cognate (N = 8) & tree (árbol) & truck & phone \\ 
Unrelated (N = 16) & penguin (pingüino) & table & shoe \\ 
\bottomrule
\end{longtable}

This is what a trial looks like {[}see figure below{]}:

\includegraphics{img/task.png}

\hypertarget{hypotheses}{%
\subsection{Hypotheses}\label{hypotheses}}

If participants lexicalise the prime pictures in a language-non
selective way, they should generate two labels upon prime picture
presentation: one in each language. Therefore, if lexical access is
language non-selective, in cognate trials two prime labels should
interfere with target recognition (since both prime labels share onset
with the target). In non-cognate trials, only one prime label should
interfere with the target. Finally, in unrelated trials no prime labels
should interfere with the target. As a result, we expect bilingual
participants' target looking preference to be weaker in cognate trials
than in non-cognate trials, and in cognate and non-cognate trials than
in unrelated trials.

\includegraphics{img/diagram.png}

We also collected data from same-aged monolingual participants as a
control group: in this group we also expect to find weaker target
looking in cognate and non-cognate trials, compared to unrelated trials,
but no differences between cognate and non-cognate trials (these
participants should be insensitive to the cognate status of the primes).

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

We planned to collect data from participants learning English and/or
Spanish in Oxford, and from participants learning Catalan and/or Spanish
in Barcelona. Due to limitations imposed by the pandemic and lockdown,
data collection in Oxford was severely interrupted, so I will present
preliminary data from participants tested in Barcelona exclusively.

We tested participants at three age points: 21, 25, and 30 months, to
explore their trajectories of lexical access through these sensitive
ages in which participants' vocabulary size is growing a full speed
{[}Reference here.{]}

We classified participants as monolinguals or bilinguals by estimating
their overall exposure to each of their languages using Bosch and
Sebastián-Gallés (2001). Following the consensus reached by the
ManyBabies consortium (Byers-Heinlein et al. 2021), participants exposed
to any languages more than 80\% of the time were classified as
monolinguals. Otherwise, participants were classified as bilinguals.
Participants exposed more than 10\% to a third language or a language
other than Catalan and Spanish (in Barcelona) or English and Spanish (in
Oxford) were excluded from data analysis.

This is how testing sessions are distributed across ages and language
profiles:

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{llrrrr}
\toprule
 & Testing language & 21 months & 25 months & 30 months & N \\ 
\midrule
\multicolumn{1}{l}{Bilingual} \\ 
\midrule
 & Catalan & 13 & 7 & 8 & 28 \\ 
 & Spanish & 12 & 7 & 11 & 30 \\ 
\midrule
\multicolumn{1}{l}{Monolingual} \\ 
\midrule
 & Catalan & 26 & 20 & 13 & 59 \\ 
 & Spanish & 18 & 9 & 12 & 39 \\ 
\bottomrule
\end{longtable}

These 156 testing sessions correspond to 106 distinct participants. Of
these participants, 1, 64 only participated once (I will refer top these
participants as cross-sectional participants), 2, 34 participated twice,
and 3, 8 participated three times.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{n\_obs }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(fit}\SpecialCharTok{$}\NormalTok{data)}

\NormalTok{n\_trials\_total }\OtherTok{\textless{}{-}} \FunctionTok{distinct}\NormalTok{(fit}\SpecialCharTok{$}\NormalTok{data, participant, target, trial\_type) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{count}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{pull}\NormalTok{(n)}

\NormalTok{n\_trials }\OtherTok{\textless{}{-}} \FunctionTok{distinct}\NormalTok{(gaze, participant, trial, trial\_type) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{count}\NormalTok{(trial\_type) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{pull}\NormalTok{(n, }\AttributeTok{name =}\NormalTok{ trial\_type)}
\end{Highlighting}
\end{Shaded}

In each testing session, participants were presented with 32 trials (8
cognate, 8 non-cognate and 16 unrelated). In each trial, we used an
eye-tracker to register participants' looking time to the target
picture. We delimited a time window of interest between 250 ms after the
target onset and 150 ms before the target offset. This resulted in a
1,500 ms long time window. We divided this time window into 15 time bins
of 100 ms each, and calculated the adjusted logit of the samples in
which participants' gaze was located in the target coordinates, out of
the total of valid samples in that time bin. This resulted in 15
observations per participant, per age group, and per trial. Our final
dataset comprised 75078 data points from 4224 distinct trials: 1039,
cognate trials, 1033 trials, and 2088 trials.

To model these data we used Growth Curve Analysis (Mirman 2017). First,
we included \texttt{time\_bin} as a fixed effect in our model to account
for the correlation between the data points collected within each trial.
We included this variable as a third degree polynomial, in order to
account for the possibly non-linearity of the target fixations across
the same trial (target fixations might increase rapidly at the beginning
of the trial and decrease at the end of it. We then included our
predictors of interest: age group (\texttt{age\_group}), language
profile (\texttt{lp}), trial type (\texttt{trial\_type}), and the
two-way interaction between language profile and trial type. Finally, we
added random intercepts and slopes by participant and by target picture,
to account for the possible correlation between time series from the
same participant or trial (more details of the model at the end).

We estimated our model using the Bayesian framework, under which we
estimate the probability of each value of the sampling space of each
parameter, given the data we have observed. to do this, we used the brms
R package (Bürkner 2017).

\hypertarget{results}{%
\subsection{Results}\label{results}}

\includegraphics{2021-01-25_lacre_files/figure-latex/unnamed-chunk-2-1.pdf}

\includegraphics{2021-01-25_lacre_files/figure-latex/gaze_time-1.pdf}

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bosch2001evidence}{}}%
Bosch, Laura, and Núria Sebastián-Gallés. 2001. {``Evidence of Early
Language Discrimination Abilities in Infants from Bilingual
Environments.''} \emph{Infancy} 2 (1): 29--49.

\leavevmode\vadjust pre{\hypertarget{ref-bosma2020cognate}{}}%
Bosma, Evelyn, and Naomi Nota. 2020. {``Cognate Facilitation in
Frisian--Dutch Bilingual Children's Sentence Reading: An Eye-Tracking
Study.''} \emph{Journal of Experimental Child Psychology} 189: 104699.

\leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
Bürkner, Paul-Christian. 2017. {``Brms: An r Package for Bayesian
Multilevel Models Using Stan.''} \emph{Journal of Statistical Software}
80 (1): 1--28.

\leavevmode\vadjust pre{\hypertarget{ref-byers2021multilab}{}}%
Byers-Heinlein, Krista, Angeline Sin Mei Tsui, Christina Bergmann,
Alexis K Black, Anna Brown, Maria Julia Carbajal, Samantha Durrant, et
al. 2021. {``A Multilab Study of Bilingual Infants: Exploring the
Preference for Infant-Directed Speech.''} \emph{Advances in Methods and
Practices in Psychological Science} 4 (1): 2515245920974622.

\leavevmode\vadjust pre{\hypertarget{ref-costa2000cognate}{}}%
Costa, Albert, Alfonso Caramazza, and Nuria Sebastian-Galles. 2000.
{``The Cognate Facilitation Effect: Implications for Models of Lexical
Access.''} \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition} 26 (5): 1283.

\leavevmode\vadjust pre{\hypertarget{ref-mani2010infant}{}}%
Mani, Nivedita, and Kim Plunkett. 2010. {``In the Infant's Mind's Ear:
Evidence for Implicit Naming in 18-Month-Olds.''} \emph{Psychological
Science} 21 (7): 908--13.

\leavevmode\vadjust pre{\hypertarget{ref-mani2011phonological}{}}%
---------. 2011. {``Phonological Priming and Cohort Effects in
Toddlers.''} \emph{Cognition} 121 (2): 196--206.

\leavevmode\vadjust pre{\hypertarget{ref-mirman2017growth}{}}%
Mirman, Daniel. 2017. \emph{Growth Curve Analysis and Visualization
Using r}. Chapman; Hall/CRC.

\leavevmode\vadjust pre{\hypertarget{ref-thierry2007brain}{}}%
Thierry, Guillaume, and Yan Jing Wu. 2007. {``Brain Potentials Reveal
Unconscious Translation During Foreign-Language Comprehension.''}
\emph{Proceedings of the National Academy of Sciences} 104 (30):
12530--35.

\leavevmode\vadjust pre{\hypertarget{ref-von2012language}{}}%
Von Holzen, Katie, and Nivedita Mani. 2012. {``Language Nonselective
Lexical Access in Bilingual Toddlers.''} \emph{Journal of Experimental
Child Psychology} 113 (4): 569--86.

\end{CSLReferences}

\end{document}

### 2021-12-06 Rmd/report.Rmd
Add Shiny app and item-level random effects to the model
Fit Bayesian model using brms

@@
 title: "Cognate Priming: Report"
-output:
-  github_document:
-    pandoc_args: --webtex
+output: html_document
 always_allow_html: true
@@
 	results = "asis",
-	dpi = 25,
+	dpi = 300,
 	dev.args = list(png = list(type = "cairo"))
@@
 ```{r params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# load packages
-library(targets)
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(gt)
-library(patchwork)
-library(wesanderson)
-library(shiny)
-library(tidybayes)
-library(brms)
-library(tidytext)
-library(brms)
-library(tidyverse)
-library(here)
 
@@
 
-theme_set(theme_github()) # in utils.R
+theme_set(theme_minimal()) # in utils.R
 ```
@@
 	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
+	geom_hline(yintercept = 24, linetype = "dashed", colour = "black") +
 	labs(x = "Group", y = "Sample size", fill = "Test language") +
@@
 
+**Likelihoods**:
+
 $$
-
-\color{white}{
-\log \Bigg( \frac{p}{n - q} \Bigg) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
-(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
-(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
-(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
-(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
-(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
-(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
-}
+\Bigg( \frac{p}{n - q} \Bigg) \sim \mathcal{N}(y_{ij}, ~ \sigma^2_m)
+$$
+
+**Parameters**:
+
+$$
+\begin{align}
+y_{ij} =&~ (\beta_{0} + \beta_{0p} + \beta_{0i}) ~+~ ... \\ 
+& (\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} ~+~ ... \\
+& (\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} ~ + ~ ... \\
+& (\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} ~ + ~ ... \\
+& (\beta_{4} + \beta_{4i}) \times Group_{pi} ~+~ ... \\
+& (\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) ~+~ ... \\
+& (\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) ~+~ ... \\
+& (\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) ~+~ ... \\
+& (\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) ~+~ \\ & \sigma^2_{e}
+\end{align}
+$$
+
+**Priors**:
+
+$$
+\begin{align}
+\beta_0 \sim~ & \mathcal{N}(0, 1) \\
+\beta_{1-8} \sim~ &\mathcal{N}(0, 1) \\
+\sigma_m, ~\sigma^2,~ \sigma^2_p,~ \sigma^2_i \sim~ & exp(2) \\
+\rho \sim ~&  LKJ(2)
+\end{align}
 $$
@@
 	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
-	geom_vline(xintercept = 0, colour = "white") +
-	stat_halfeye(point_color = "white", interval_color = "white") +
+	geom_vline(xintercept = 0, colour = "black") +
+	stat_halfeye(point_color = "black", interval_color = "black") +
 	labs(x = "Value", y = "Variable", fill = "CrI") +
@@
 
-##### Overall
+##### Marginal to time course
+
+```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+m <- emmeans(fit, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
+	as_tibble() %>% 
+	clean_names() %>% 
+	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x < 0, 0, x)) %>% 
+	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x > 1, 1, x))
+
+ggplot(m, aes(age_group, emmean, ymin = lower_hpd, ymax = upper_hpd, colour = trial_type)) +
+	facet_wrap(~lp, ncol = 1) +
+	# geom_line(aes(group = trial_type), size = 1, position = position_dodge(width = 0.25)) +
+	geom_errorbar(size = 1, width = 0, position = position_dodge(width = 0.25)) +
+	geom_point(size = 4, position = position_dodge(width = 0.25)) +
+	labs(x = "Age (months))", y = "P(target)", colour = "Trial type") +
+	scale_y_continuous(limits = c(0, 1), labels = percent)  +
+	theme(
+		legend.title = element_blank(),
+		legend.position = "top"
+	)
+
+```
+
+##### Time course
 
@@
 	filter(valid_participant) %>% 
-	count(lp)
+	count(lp, age_group)
 
@@
 	lp = c("Monolingual", "Bilingual"),
-	age_group = c("25 months"),
+	age_group = paste(c(21, 25, 30), "months"),
 	trial_type = unique(gaze$trial_type),
@@
 
-m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
+m <- epred_draws(object = fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
 	mutate(.value = logit_to_prob(.epred))
@@
 ggplot(m, aes(time_bin_center, .value)) +
-	facet_wrap(~fct_rev(lp)) +
-	geom_hline(yintercept = 0.5, colour = "white") +
+	facet_grid(fct_rev(lp)~age_group) +
+	geom_hline(yintercept = 0.5, colour = "black") +
 	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),

### 2021-12-06 Communications/2022-01-25_lacre/2021-01-25_lacre.Rmd

---
author: "Gonzalo García-Castro"
date: "25/01/2021"
output: word_document
bibliography: "../../references.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(gt)
library(tibble)
library(ggplot2)
library(tidyr)
library(dplyr)
library(tidybayes)
library(stringr)
library(forcats)
library(targets)
library(scales)
library(here)

source(here::here("R", "utils.R"))

tar_load(participants)
tar_load(attrition)
tar_load(gaze)
tar_load(model_fits)

# withr::with_dir("../..", tar_load(participants))
# withr::with_dir("../..", tar_load(attrition))
# withr::with_dir("../..", tar_load(gaze))
# withr::with_dir("../..", tar_load(model_fits))

fit <- model_fits$fit

```

## Background

Infants learning two languages face the challenge of having to learn two distinct sets of words. Some of the words across both languages refer to similar concepts: for instance, *chair* and *silla* (in Spanish). These pairs of words are called *translation equivalents*. Sometimes, translation equivalents also overlap in form, frequently due to their shared etymological origin. These form-similar translation equivalents, such as *boot* and *bota* (in Spanish), are referred to as *cognates*.

There is extensive literature on how cognateness impacts the dynamics of lexical access during words comprehension and production. One of its main findings is that bilinguals process cognates (such as *boot* and *bota*) more differently than non-cognates (such as *chair* and *silla*). For instance, @costa2000cognate asked Spanish-Catalan bilinguals to name a series of familiar pictures in Spanish. Part of the pictures referred to objects whose labels in Spanish and Catalan were cognates, whereas the other pictures referred to non-cognates. On average, participants named cognate pictures faster than non-cognate pictures. This effect was independent of lexical frequency and, critically, was not observed when Spanish monolinguals performed the same task. This suggests that bilinguals activated labels in both languages, and that their phonology interacted to facilitate naming.

Later studies provided evidence that the locus of this facilitation effect was at the lexical level, and not just at the articulatory level [reference needed here]: this effect has also been reported during comprehension, at both the visual-orthographic and the auditory-phonology modalities) [e.g., @thierry2007brain]. Overall, these findings have led researchers to hypothesise that lexical access is language-non selective, that is, bilinguals activate lexical representations in both languages in parallel during comprehension and production, based on their semantic and phonological overlap.

This cross-talk between languages has also been suggested to be present in children's and toddlers' lexicon [@von2012language; @bosma2020cognate], but it is still unclear how it impacts the trajectories of language acquisition at these early ages. In this study we sought to investigate the developmental trajectories of lexical access in a cohort of Catalan-Spanish and English-Spanish bilinguals.

To do this, we used an adaptation of @mani2010infant's priming paradigm. This paradigm consists of a spoken word recognition task in which participants are first presented with a picture in silence in the centre of the screen for 1.5 seconds. Then, two other pictures are presented side-by-side during 2 seconds, and one of them is named. The other is not. Looking times to the target picture are recorded from name onset. From now on, I will refer to the silent picture presented first as the *prime*, to the named picture as the *target*, and to the non-named picture presented next to the target as *distractor*.

In their experiment, Mani and Plunkett manipulated the phonological overlap between the prime label and the target label: in some trials, both labels shared phonological onset (*bee*-*ball*), whereas in other trials they did not share phonological onset (*cow*-*book*). In all trials, the distractor label did not share onset with either of the prime or target labels (e.g., *teeth*). The authors registered 18 month-old participants' looking preference for the target object after name onset, as a proxy of word recognition, and found that target preference was stronger after a phonologically related prime than after a phonologically unrelated prime. There results have three main implications:

1) Phonologically related prime pictures facilitated target recognition
2) This is only possible if participants lexicalised the prime pictures, even though this picture was presented in silence
3) The label participants generated upon prime picture presentation was phonologically detailed, and this phonological form interacted with the auditory recognition of a subsequently presented word

In a subsequent study, the authors found the inverse effect in 24 month-old toddlers: target looking preference was weaker after a phonologically related prime picture compared to after an unrelated one [@mani2011phonological]. The authors suggested that the change in the direction of the effect observed between 18 and 24 month-old participants was due to the increment in vocabulary size and the establishment of (inhibitory) links between phonologically related lexical entries that might have occurred between both ages. Supporting this account, the inhibition effect they reported was stronger as the number of phonological neighbours of the target increased: the recognition of words surrounded by more phonologically related neighbours suffered the most from the priming effect.

We adapted this paradigm to test the language-non selectivity account in bilingual toddlers. Following Mani & Plunkett's original implementation, In our task half of the prime-target pairs in the trial lists shared phonological onset, and the other half did not share phonological onset. We added a novel manipulation: half of the primes in the phonologically related condition were cognates and the other half were non-cognates. We classified two translation equivalents as cognates if they shared phonological onset. Here is an illustration of each trial type:

```{r trials, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

tribble(
	~trial_type, ~prime, ~target, ~distractor,
	"Cognate (N = 8)", "flower (flor)", "fork", "balloon",
	"Non-cognate (N = 8)", "tree (árbol)", "truck", "phone",
	"Unrelated (N = 16)", "penguin (pingüino)", "table", "shoe"
) %>% 
	gt() %>% 
	cols_label(
		trial_type = "Prime type",
		prime = "Prime",
		target = "Target",
		distractor = "Distractor"

	)
```

This is what a trial looks like [see figure below]:

![](img/task.png)

## Hypotheses

If participants lexicalise the prime pictures in a language-non selective way, they should generate two labels upon prime picture presentation: one in each language. Therefore, if lexical access is language non-selective, in cognate trials two prime labels should interfere with target recognition (since both prime labels share onset with the target). In non-cognate trials, only one prime label should interfere with the target. Finally, in unrelated trials no prime labels should interfere with the target. As a result, we expect bilingual participants' target looking preference to be weaker in cognate trials than in non-cognate trials, and in cognate and non-cognate trials than in unrelated trials.

![](img/diagram.png)

We also collected data from same-aged monolingual participants as a control group: in this group we also expect to find weaker target looking in cognate and non-cognate trials, compared to unrelated trials, but no differences between cognate and non-cognate trials (these participants should be insensitive to the cognate status of the primes).

## Participants

We planned to collect data from participants learning English and/or Spanish in Oxford, and from participants learning Catalan and/or Spanish in Barcelona. Due to limitations imposed by the pandemic and lockdown, data collection in Oxford was severely interrupted, so I will present preliminary data from participants tested in Barcelona exclusively.

We tested participants at three age points: 21, 25, and 30 months, to explore their trajectories of lexical access through these sensitive ages in which participants' vocabulary size is growing a full speed [Reference here.]

We classified participants as monolinguals or bilinguals by estimating their overall exposure to each of their languages using @bosch2001evidence. Following the consensus reached by the ManyBabies consortium [@byers2021multilab], participants exposed to any languages more than 80% of the time were classified as monolinguals. Otherwise, participants were classified as bilinguals. Participants exposed more than 10% to a third language or a language other than Catalan and Spanish (in Barcelona) or English and Spanish (in Oxford) were excluded from data analysis.

This is how testing sessions are distributed across ages and language profiles:

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	count(test_language, age_group, lp) %>% 
	drop_na() %>% 
	pivot_wider(names_from = age_group, values_from = n) %>% 
	rowwise() %>% 
	mutate(N = sum(`21 months`, `25 months`, `30 months`)) %>% 
	ungroup() %>% 
	relocate(lp) %>% 
	gt(groupname_col = "lp") %>% 
	cols_label(test_language = "Testing language", lp = "Group") %>% 
	summary_rows(columns = 3:6, fns = list(N = "sum"), decimals = 0)

n_total <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	distinct(participant) %>% 
	count()

n_total_cohort <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	distinct(participant, age_group) %>%
	count(participant) %>% 
	count(n, name = "n_cohort") %>% 
	group_split(n)

```

These 156 testing sessions correspond to `r n_total$n` distinct participants. Of these participants, `r n_total_cohort[[1]]` only participated once (I will refer top these participants as cross-sectional participants), `r n_total_cohort[[2]]` participated twice, and `r n_total_cohort[[3]]` participated three times.

## Data analysis

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
n_obs <- nrow(fit$data)

n_trials_total <- distinct(fit$data, participant, target, trial_type) %>% 
	count() %>% 
	pull(n)

n_trials <- distinct(gaze, participant, trial, trial_type) %>% 
	count(trial_type) %>% 
	pull(n, name = trial_type)
```

In each testing session, participants were presented with 32 trials (8 cognate, 8 non-cognate and 16 unrelated). In each trial, we used an eye-tracker to register participants' looking time to the target picture. We delimited a time window of interest between 250 ms after the target onset and 150 ms before the target offset. This resulted in a 1,500 ms long time window. We divided this time window into 15 time bins of 100 ms each, and calculated the adjusted logit of the samples in which participants' gaze was located in the target coordinates, out of the total of valid samples in that time bin. This resulted in 15 observations per participant, per age group, and per trial. Our final dataset comprised `r n_obs` data points from `r n_trials_total` distinct trials: `r n_trials["Cognate"]`, cognate trials, `r n_trials["Non-cognate"]` trials, and `r n_trials["Unrelated"]` trials.

To model these data we used Growth Curve Analysis [@mirman2017growth]. First, we included `time_bin` as a fixed effect in our model to account for the correlation between the data points collected within each trial. We included this variable as a third degree polynomial, in order to account for the possibly non-linearity of the target fixations across the same trial (target fixations might increase rapidly at the beginning of the trial and decrease at the end of it. We then included our predictors of interest: age group (`age_group`), language profile (`lp`), trial type (`trial_type`), and the two-way interaction between language profile and trial type. Finally, we added random intercepts and slopes by participant and by target picture, to account for the possible correlation between time series from the same participant or trial (more details of the model at the end).

We estimated our model using the Bayesian framework, under which we estimate the probability of each value of the sampling space of each parameter, given the data we have observed. to do this, we used the brms R package [@burkner2017brms].

## Results

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)

draws %>% 
	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit(.value), .value/4)) %>% 
	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
	geom_vline(xintercept = 0, colour = "grey", size = 1) +
	stat_halfeye(point_color = "black", interval_color = "black") +
	labs(x = "Value", y = "Variable", fill = "CrI") +
	theme_ggdist() +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	theme(
		panel.grid.major.y = element_line(colour = "grey"),
		axis.title.y = element_blank(),
		axis.title.x = element_blank(),
		legend.position = "top"
	)

```

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	filter(valid_participant) %>% 
	count(lp)

n <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	age_group = c("25 months"),
	trial_type = unique(gaze$trial_type),
	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
)

m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
	mutate(.value = logit_to_prob(.epred))

ggplot(m, aes(time_bin_center, .value)) +
	facet_wrap(~fct_rev(lp)) +
	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
				  colour = trial_type),
			  alpha = 0.15, size = 0.65) +
	stat_summary(aes(group = trial_type, colour = trial_type),
				 fun = mean, geom = "line", size = 1.25) +
	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
								  colour = trial_type),
				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
				 position = position_dodge(width = 0.3)) +
	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
			  colour = "white", hjust = 0, size = 5) +
	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_brewer(palette = "Set1") +
	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme_ggdist() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", size = 0.5, linetype = "dotted"),
		axis.text.x = element_text(size = 9),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank()
	)
```

## References

### 2021-12-06 Communications/2022-01-25_lacre/2022-01-25_lacre-abstract.Rmd

---
title: "LACRE 2022: abstract"
author: "Gonzalo García-Castro"
date: "25/01/2022"
output: 
  word_document: 
    reference_docx: "manuscript_template.docx"
bibliography: "../../references.bib"
---

Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language [e.g., @costa2000cognate; @thierry2007brain]. It has been suggested that this parallel activation is already present during toddlerhood [e.g., @von2012language; @jardak2019labels], but it is unclear how this parallel activation impacts the developing lexicon. We tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task. Participants were tested exclusively in their language of most exposure. two pictures were presented side-by-side, one of them was named, and participants' visual preference for the named (target) picture was taken as a proxy of word recognition. Each pair of pictures was preceded by the presentation of a silent image (prime). We manipulated two variables regarding to the relationship between the label associated to the prime image and the target word: their phonological overlap in the testing language and the cognate status of the prime label. This resulted in three types of trials: trials in which prime and target labels shared phonological onset and the prime label was a cognate (cognate trials; e.g., *flower*/*flor*-*bird*, for an English-Spanish participant), trials where prime and target labels shared phonological onset but the prime label was a non-cognate (non-cognate trials; e.g., *chair*/*silla*-*bird*), and trials where prime and target labels did not share phonological onset (unrelated trials; *car*/*coche*-*bird*).

In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset [e.g.; @mani2010infant]. Under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we further predicted  that interference over target word recognition would be stronger after cognate primes (labels from both languages interfere with target word recognition) than after non-cognate primes (only the label in the target language interferes with target word recognition). We tested bilinguals (and same-aged monolingual controls) at three age points (21, 25, and 30 months) to investigate how any cross-language priming effect emerged or changed across these ages, capitalising on the potential role of vocabulary size. Preliminary data suggest that bilinguals were almost insensitive to the phonological similarity between the prime and the spoken target word, or to the cognate status of the prime label. Surprisingly, monolinguals' preference for the target picture at 25 was stronger after non-cognate primes, compared to cognate primes or unrelated primes, and also after cognate and non-cognate primes compared to unrelated primes. We present this preliminary data along with exploratory analyses addressing the puzzling pattern of results we observed.

![](img/gca.png)

### 2021-12-06 Communications/2022-07-07_icis/2022-07-07_icis-abstract.Rmd

---
title: "ICIS 2022: abstract"
author: "Gonzalo Garcia-Castro"
date: "07/07/2022"
output: 
  word_document: 
    reference_docx: "manuscript_template.docx"
bibliography: "../../references.bib"
csl: "../../apa7.csl"
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE, 
	dpi = 800
)

tar_load_globals()
tar_load(participants)
tar_load(gaze)
tar_load(attrition)
tar_load(vocabulary)
tar_load(model_fits)

theme_set(theme_custom())

participants <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])

coefs <- fixef(model_fits$fit) %>%
	as.data.frame() %>% 
	clean_names()

emmean <- emmeans(
	model_fits$fit,
	~trial_type, 
	by = "lp",
	epred = TRUE
) %>% 
	as_tibble() %>% 
	mutate_if(is.numeric, inv_logit_scaled)

```

Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language [e.g., @costa2000cognate; @thierry2007brain]. It has been suggested that this parallel activation is already present during toddlerhood [@von2012language; @jardak2019labels], but it is unclear how it impacts the developing lexicon. In the present study, we tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task, in which they were presented with words in their dominant language exclusively. In each trial, two pictures were presented side-by-side and one of them was named (target picture). Participants' visual preference for the named picture was taken as an indicator of word recognition. Each pair of pictures was preceded by the presentation of a silent image (prime picture). We designed three types of trials: trials in which prime and target labels shared phonological onset and the prime label was a cognate (cognate trials; e.g., *flower*-*flor* / *bird*, for an English-Spanish participant), trials where prime and target labels shared phonological onset but the prime label was a non-cognate (non-cognate trials; e.g., *chair*-*silla* / *bird*), and trials where prime and target labels did not share phonological onset (unrelated trials; *car*-*coche* / *bird*).

In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset [e.g., @mani2010infant]. Additionally, under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we predicted that interference would be stronger after cognate primes (labels from both languages share phonological overlap with target word recognition) than after non-cognate primes (only the label in the target language share phonological overlap with target word recognition). We tested bilinguals (*n* = `r length(unique(model_fits$fit$data[model_fits$fit$data$lp=="Bilingual",]$participant))`) and same-aged monolingual controls, *n* = `r length(unique(model_fits$fit$data[model_fits$fit$data$lp=="Monolingual",]$participant))`) at three age points (21, 25, and 30 months) to investigate how any cross-language priming effect emerged or changed across these ages.

Preliminary results (data collection is ongoing) from a Bayesian Growth Curve Analysis suggest that bilinguals' proportion target looking (PTL) did not differ across the cognate (`r percent(emmean$emmean[1], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[1]*100)`, `r printnum(emmean$upper.HPD[1]*100)`]), non-cognate (`r percent(emmean$emmean[2], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[2]*100)`, `r printnum(emmean$upper.HPD[2]*100)`]), or unrelated (`r percent(emmean$emmean[3], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[3]*100)`, `r printnum(emmean$upper.HPD[3]*100)`]) priming conditions. Surprisingly, monolinguals' preference for the target picture was stronger after non-cognate primes (`r percent(emmean$emmean[5], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[5]*100)`, `r printnum(emmean$upper.HPD[5]*100)`]) and unrelated primes (`r percent(emmean$emmean[6], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[6]*100)`, `r printnum(emmean$upper.HPD[6]*100)`]) compared to cognate primes (`r percent(emmean$emmean[4], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[1]*100)`, `r printnum(emmean$upper.HPD[1]*100)`]). This suggests that contrary to our predictions, monolinguals were sensitive to both phonological priming and cognateness. This effect survived after adjusting for potential confounders such as lexical frequency, age of acquisition or object animacy. We present these results along with exploratory analyses addressing the puzzling pattern of results we observed.

```{r results, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%", fig.height=4, fig.width=8}
sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(lp, age_group)

n <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	age_group = paste(c(21, 25, 30), "months"),
	trial_type = unique(gaze$trial_type),
	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
)

m <- epred_draws(object = model_fits$fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(.value = logit_to_prob(.epred))

ggplot(m, aes(time_bin_center, .value)) +
	facet_grid(fct_rev(lp)~age_group) +
	geom_hline(yintercept = 0.5, colour = "black") +
	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
				  colour = trial_type),
			  alpha = 0.1, size = 0.45) +
	stat_summary(aes(group = trial_type),
				 fun = mean, geom = "line", size = 1.1, colour = "white") +
	stat_summary(aes(group = trial_type, colour = trial_type),
				 fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
			  colour = "white", hjust = 0, size = 5) +
	labs(x = "Time (ms)", y = "Expected posterior PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
	scale_x_continuous(breaks = seq(-7, 7, 3.5), labels = seq(0, 1400, 350)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		legend.key = element_rect(fill = "white", colour = NA),
		axis.text.x = element_text(size = 9),
		axis.text.y = element_text(size = 9),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank()
	)
```

### 2021-12-06 Rmd/report.Rmd

@@
 title: "Cognate Priming: Report"
-output: html_document
+output:
+  html_document:
+    df_print: paged
+    toc: true
+    toc_depth: 5
+    toc_float: true
 always_allow_html: true

### 2021-12-29 docs/00_participants.Rmd
Add participants

--- 2021-12-06 Rmd/report.Rmd
@@
 ---
-title: "Cognate Priming: Report"
-output: html_document
+title: "Participants"
+output: github_document
 always_allow_html: true
@@
 tar_load(participants)
-tar_load(stimuli)
 tar_load(vocabulary)
-tar_load(gaze)
 tar_load(attrition)
-tar_load(attrition_counter)
-tar_load(model_fits)
 
@@
 
-attrition_counter <- attrition_counter %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			!valid_counter ~ "Invalid counter",
-			TRUE ~ "Valid"
-		))
-
 participants <- participants %>% 
@@
 
-participants_counter <- participants %>% 
-	left_join(distinct(attrition_counter, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
 ```
-
-# Methods
-
-## Participants {.tabset .tabset-pills}
 
@@
 
-#### Summary
+# Summary
 
@@
 
-#### Longitudinal
+# Longitudinal
 
@@
 ```
-
-#### {-}
-
-## Stimuli
-
-### Frequency {.tabset }
-
-#### CHILDES {.tabset }
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "white", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "black", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid.major.x = element_blank()
-
-	)
-```
-
-##### {-}
-
-#### {-}
-
-### Familiarity {.tabset }
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type,
-			   xmin = familiarity_prime-familiarity_se_prime, xmax = familiarity_prime-familiarity_se_prime)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6.5, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	# scale_y_reordered() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
-	drop_na(trial_type, category) %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_wrap(role~location~test_language) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid = element_blank()
-
-	)
-
-```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level") %>%
-	as_raw_html()
-
-```
-
-### {-}
-
-## {-}
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tabset-pills}
-
-## Gaze {.tabset .tabset-pills}
-
-```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-fit <- model_fits$fit
-```
-
-#### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-**Likelihoods**:
-
-$$
-\Bigg( \frac{p}{n - q} \Bigg) \sim \mathcal{N}(y_{ij}, ~ \sigma^2_m)
-$$
-
-**Parameters**:
-
-$$
-\begin{align}
-y_{ij} =&~ (\beta_{0} + \beta_{0p} + \beta_{0i}) ~+~ ... \\ 
-& (\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} ~+~ ... \\
-& (\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} ~ + ~ ... \\
-& (\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} ~ + ~ ... \\
-& (\beta_{4} + \beta_{4i}) \times Group_{pi} ~+~ ... \\
-& (\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) ~+~ ... \\
-& (\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) ~+~ ... \\
-& (\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) ~+~ ... \\
-& (\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) ~+~ \\ & \sigma^2_{e}
-\end{align}
-$$
-
-**Priors**:
-
-$$
-\begin{align}
-\beta_0 \sim~ & \mathcal{N}(0, 1) \\
-\beta_{1-8} \sim~ &\mathcal{N}(0, 1) \\
-\sigma_m, ~\sigma^2,~ \sigma^2_p,~ \sigma^2_i \sim~ & exp(2) \\
-\rho \sim ~&  LKJ(2)
-\end{align}
-$$
-
-#### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
-
-draws %>% 
-	mean_qi(.width = c(0.95, 0.50)) %>% 
-	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
-	clean_names() %>% 
-	select(-c(point, interval, value_0_5)) %>% 
-	gt(rowname_col = "variable") %>% 
-	fmt_number(2:6) %>% 
-	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		variable = md("**Predictor**"),
-		value_0_95 = md("**Mean**"),
-		lower_0_95 = md("**95% CrI**"),
-		lower_0_5 = md("**50% CrI**")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = lower_0_95 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = lower_0_5 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = upper_0_95 < 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = upper_0_5 < 0
-		)
-	) %>% 
-	as_raw_html()
-```
-
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
-
-draws %>% 
-	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
-	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
-	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
-	geom_vline(xintercept = 0, colour = "black") +
-	stat_halfeye(point_color = "black", interval_color = "black") +
-	labs(x = "Value", y = "Variable", fill = "CrI") +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	theme(
-		axis.title = element_blank(),
-		legend.position = "top"
-	)
-
-```
-
-#### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-vcov(fit) %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
-	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
-	geom_tile() +
-	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
-	scale_fill_distiller(limits = c(-1, 1)) +
-	coord_equal() +
-	theme(
-		legend.position = "top",
-		legend.text = element_text(size = 8),
-		axis.title = element_blank(),
-		axis.text.y = element_text(hjust = 1, size = 7),
-		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
-	)
-
-```
-
-#### Marginal means {.tabset }
-
-##### Marginal to time course
-
-```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-m <- emmeans(fit, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
-	as_tibble() %>% 
-	clean_names() %>% 
-	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x < 0, 0, x)) %>% 
-	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x > 1, 1, x))
-
-ggplot(m, aes(age_group, emmean, ymin = lower_hpd, ymax = upper_hpd, colour = trial_type)) +
-	facet_wrap(~lp, ncol = 1) +
-	# geom_line(aes(group = trial_type), size = 1, position = position_dodge(width = 0.25)) +
-	geom_errorbar(size = 1, width = 0, position = position_dodge(width = 0.25)) +
-	geom_point(size = 4, position = position_dodge(width = 0.25)) +
-	labs(x = "Age (months))", y = "P(target)", colour = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent)  +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "top"
-	)
-
-```
-
-##### Time course
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(lp, age_group)
-
-n <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	age_group = paste(c(21, 25, 30), "months"),
-	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
-)
-
-m <- epred_draws(object = fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
-	mutate(.value = logit_to_prob(.epred))
-
-ggplot(m, aes(time_bin_center, .value)) +
-	facet_grid(fct_rev(lp)~age_group) +
-	geom_hline(yintercept = 0.5, colour = "black") +
-	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
-				  colour = trial_type),
-			  alpha = 0.15, size = 0.65) +
-	stat_summary(aes(group = trial_type, colour = trial_type),
-				 fun = mean, geom = "line", size = 1.25) +
-	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
-								  colour = trial_type),
-				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
-				 position = position_dodge(width = 0.3)) +
-	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
-			  colour = "white", hjust = 0, size = 5) +
-	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
-		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_brewer(palette = "Set1") +
-	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 9),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank()
-	)
-```
-
-##### {-}
-
-#### {-}
-
-## Attrition {.tabset}
-
-#### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = "#0D1117", size = 1) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-#### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-#### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
-	as_raw_html()
-
-```
-
-#### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	as_raw_html()
-```
-
-#### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	drop_na(trial_type) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	) %>% 
-	as_raw_html()
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(location~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### By lexical frequency {.tabset }
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By familiarity {.tabset}
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By animacy {.tabset }
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-##### {-}
-
-#### By category {.tabset}
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-## Vocabulary {.tabset .tabset-pills}
-
-#### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "white") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, outlier.colour = NA, fill = "#0D1117",
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9)
-	)
-
-```
-
-#### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.x = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-#### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.x = element_blank()
-	)
-
-```
-
-#### {-}
-
-### {-}
-
-## {-}
-
-# Appendix
-
-# References

### 2021-12-29 docs/01_stimuli.Rmd
Add participants

--- 2021-11-08 Rmd/report.Rmd
@@
 ---
-title: "Cognate Priming: Report"
-output:
-  github_document:
-    pandoc_args: --webtex
+title: "Stimuli"
+output: github_document
 always_allow_html: true
@@
 
-# load packages
-library(targets)
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(gt)
-library(patchwork)
-library(wesanderson)
-library(shiny)
-library(tidybayes)
-library(brms)
-library(tidytext)
-library(brms)
-library(tidyverse)
-library(here)
-
 # load objects
 tar_load_globals()
-tar_load(participants)
 tar_load(stimuli)
-tar_load(vocabulary)
-tar_load(gaze)
-tar_load(attrition)
-tar_load(attrition_counter)
-tar_load(model_fits)
 
-theme_set(theme_github()) # in utils.R
+theme_set(theme_minimal()) # in utils.R
 ```
 
-```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+# Frequency {.tabset }
 
-attrition <- attrition %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
+## CHILDES {.tabset }
 
-attrition_counter <- attrition_counter %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			!valid_counter ~ "Invalid counter",
-			TRUE ~ "Valid"
-		))
-
-participants <- participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
-participants_counter <- participants %>% 
-	left_join(distinct(attrition_counter, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
-```
-
-# Methods
-
-## Participants {.tabset .tabset-pills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-#### Summary
-
-```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp, test_language) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		test_language = md("**Language**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90),
-		panel.grid.major.x = element_blank()
-	) 
-```
-
-#### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	filter(valid_participant) %>% 
-	mutate(age_group = str_remove(age_group, " months")) %>%
-	ggplot(aes(age_group, participant, colour = lp)) +
-	facet_grid(~location, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Lang. Pofile") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
-```
-
-#### {-}
-
-## Stimuli
-
-### Frequency {.tabset }
-
-#### CHILDES {.tabset }
-
-##### Prime
+### Prime
 
@@
 
-##### Target
+### Target
 
@@
 
-##### {-}
+# Familiarity {.tabset }
 
-#### {-}
-
-### Familiarity {.tabset }
-
-#### Prime
+## Prime
 
@@
 
-#### Target
+## Target
 
@@
 
-#### {-}
-
-### Animacy
+# Animacy
 
@@
 
-### Semantic category
+# Semantic category
 
@@
 ```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level") %>%
-	as_raw_html()
-
-```
-
-### {-}
-
-## {-}
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tabset-pills}
-
-## Gaze {.tabset .tabset-pills}
-
-```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-fit <- model_fits$fit
-```
-
-#### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-$$
-
-\color{white}{
-\log \Bigg( \frac{p}{n - q} \Bigg) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
-(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
-(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
-(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
-(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
-(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
-(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
-}
-$$
-
-#### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
-
-draws %>% 
-	mean_qi(.width = c(0.95, 0.50)) %>% 
-	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
-	clean_names() %>% 
-	select(-c(point, interval, value_0_5)) %>% 
-	gt(rowname_col = "variable") %>% 
-	fmt_number(2:6) %>% 
-	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		variable = md("**Predictor**"),
-		value_0_95 = md("**Mean**"),
-		lower_0_95 = md("**95% CrI**"),
-		lower_0_5 = md("**50% CrI**")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = lower_0_95 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = lower_0_5 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = upper_0_95 < 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = upper_0_5 < 0
-		)
-	) %>% 
-	as_raw_html()
-```
-
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
-
-draws %>% 
-	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
-	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
-	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
-	geom_vline(xintercept = 0, colour = "white") +
-	stat_halfeye(point_color = "white", interval_color = "white") +
-	labs(x = "Value", y = "Variable", fill = "CrI") +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	theme(
-		axis.title = element_blank(),
-		legend.position = "top"
-	)
-
-```
-
-#### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-vcov(fit) %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
-	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
-	geom_tile() +
-	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
-	scale_fill_distiller(limits = c(-1, 1)) +
-	coord_equal() +
-	theme(
-		legend.position = "top",
-		legend.text = element_text(size = 8),
-		axis.title = element_blank(),
-		axis.text.y = element_text(hjust = 1, size = 7),
-		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
-	)
-
-```
-
-#### Marginal means {.tabset }
-
-##### Overall
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(lp)
-
-n <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	age_group = c("25 months"),
-	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
-)
-
-m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
-	mutate(.value = logit_to_prob(.epred))
-
-ggplot(m, aes(time_bin_center, .value)) +
-	facet_wrap(~fct_rev(lp)) +
-	geom_hline(yintercept = 0.5, colour = "white") +
-	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
-				  colour = trial_type),
-			  alpha = 0.15, size = 0.65) +
-	stat_summary(aes(group = trial_type, colour = trial_type),
-				 fun = mean, geom = "line", size = 1.25) +
-	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
-								  colour = trial_type),
-				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
-				 position = position_dodge(width = 0.3)) +
-	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
-			  colour = "white", hjust = 0, size = 5) +
-	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
-		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_brewer(palette = "Set1") +
-	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 9),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank()
-	)
-```
-
-##### {-}
-
-#### {-}
-
-## Attrition {.tabset}
-
-#### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = "#0D1117", size = 1) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-#### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-#### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
-	as_raw_html()
-
-```
-
-#### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	as_raw_html()
-```
-
-#### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	drop_na(trial_type) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	) %>% 
-	as_raw_html()
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(location~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### By lexical frequency {.tabset }
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By familiarity {.tabset}
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By animacy {.tabset }
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-##### {-}
-
-#### By category {.tabset}
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-## Vocabulary {.tabset .tabset-pills}
-
-#### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "white") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, outlier.colour = NA, fill = "#0D1117",
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9)
-	)
-
-```
-
-#### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.x = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-#### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.x = element_blank()
-	)
-
-```
-
-#### {-}
-
-### {-}
-
-## {-}
-
-# Appendix
-
-# References

### 2021-12-29 docs/02_vocabulary.Rmd
Add participants

--- 2021-11-08 Rmd/report.Rmd
@@
 ---
-title: "Cognate Priming: Report"
-output:
-  github_document:
-    pandoc_args: --webtex
+title: "Vocabulary"
+output: github_document
 always_allow_html: true
@@
 
-# load packages
-library(targets)
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(gt)
-library(patchwork)
-library(wesanderson)
-library(shiny)
-library(tidybayes)
-library(brms)
-library(tidytext)
-library(brms)
-library(tidyverse)
-library(here)
-
 # load objects
 tar_load_globals()
+tar_load(vocabulary)
+tar_load(attrition)
 tar_load(participants)
-tar_load(stimuli)
-tar_load(vocabulary)
-tar_load(gaze)
-tar_load(attrition)
-tar_load(attrition_counter)
-tar_load(model_fits)
 
-theme_set(theme_github()) # in utils.R
-```
-
-```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+theme_set(theme_minimal()) # in utils.R
 
@@
 	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
-participants_counter <- participants %>% 
-	left_join(distinct(attrition_counter, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
 ```
-
-# Methods
-
-## Participants {.tabset .tabset-pills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-#### Summary
-
-```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp, test_language) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		test_language = md("**Language**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90),
-		panel.grid.major.x = element_blank()
-	) 
-```
-
-#### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	filter(valid_participant) %>% 
-	mutate(age_group = str_remove(age_group, " months")) %>%
-	ggplot(aes(age_group, participant, colour = lp)) +
-	facet_grid(~location, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Lang. Pofile") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
-```
-
-#### {-}
-
-## Stimuli
-
-### Frequency {.tabset }
-
-#### CHILDES {.tabset }
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "white", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "black", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid.major.x = element_blank()
-
-	)
-```
-
-##### {-}
-
-#### {-}
-
-### Familiarity {.tabset }
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type,
-			   xmin = familiarity_prime-familiarity_se_prime, xmax = familiarity_prime-familiarity_se_prime)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6.5, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	# scale_y_reordered() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
-	drop_na(trial_type, category) %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_wrap(role~location~test_language) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid = element_blank()
-
-	)
-
-```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
 
@@
 
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level") %>%
-	as_raw_html()
-
-```
-
-### {-}
-
-## {-}
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tabset-pills}
-
-## Gaze {.tabset .tabset-pills}
-
-```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-fit <- model_fits$fit
-```
-
-#### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-$$
-
-\color{white}{
-\log \Bigg( \frac{p}{n - q} \Bigg) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
-(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
-(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
-(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
-(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
-(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
-(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
-}
-$$
-
-#### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
-
-draws %>% 
-	mean_qi(.width = c(0.95, 0.50)) %>% 
-	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
-	clean_names() %>% 
-	select(-c(point, interval, value_0_5)) %>% 
-	gt(rowname_col = "variable") %>% 
-	fmt_number(2:6) %>% 
-	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		variable = md("**Predictor**"),
-		value_0_95 = md("**Mean**"),
-		lower_0_95 = md("**95% CrI**"),
-		lower_0_5 = md("**50% CrI**")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = lower_0_95 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = lower_0_5 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = upper_0_95 < 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = upper_0_5 < 0
-		)
-	) %>% 
-	as_raw_html()
-```
-
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
-
-draws %>% 
-	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
-	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
-	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
-	geom_vline(xintercept = 0, colour = "white") +
-	stat_halfeye(point_color = "white", interval_color = "white") +
-	labs(x = "Value", y = "Variable", fill = "CrI") +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	theme(
-		axis.title = element_blank(),
-		legend.position = "top"
-	)
-
-```
-
-#### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-vcov(fit) %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
-	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
-	geom_tile() +
-	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
-	scale_fill_distiller(limits = c(-1, 1)) +
-	coord_equal() +
-	theme(
-		legend.position = "top",
-		legend.text = element_text(size = 8),
-		axis.title = element_blank(),
-		axis.text.y = element_text(hjust = 1, size = 7),
-		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
-	)
-
-```
-
-#### Marginal means {.tabset }
-
-##### Overall
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(lp)
-
-n <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	age_group = c("25 months"),
-	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
-)
-
-m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
-	mutate(.value = logit_to_prob(.epred))
-
-ggplot(m, aes(time_bin_center, .value)) +
-	facet_wrap(~fct_rev(lp)) +
-	geom_hline(yintercept = 0.5, colour = "white") +
-	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
-				  colour = trial_type),
-			  alpha = 0.15, size = 0.65) +
-	stat_summary(aes(group = trial_type, colour = trial_type),
-				 fun = mean, geom = "line", size = 1.25) +
-	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
-								  colour = trial_type),
-				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
-				 position = position_dodge(width = 0.3)) +
-	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
-			  colour = "white", hjust = 0, size = 5) +
-	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
-		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_brewer(palette = "Set1") +
-	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 9),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank()
-	)
-```
-
-##### {-}
-
-#### {-}
-
-## Attrition {.tabset}
-
-#### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = "#0D1117", size = 1) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-#### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-#### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
-	as_raw_html()
-
-```
-
-#### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	as_raw_html()
-```
-
-#### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	drop_na(trial_type) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	) %>% 
-	as_raw_html()
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(location~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### By lexical frequency {.tabset }
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By familiarity {.tabset}
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By animacy {.tabset }
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-##### {-}
-
-#### By category {.tabset}
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-## Vocabulary {.tabset .tabset-pills}
-
-#### L1 vocabulary
+# L1 vocabulary
 
@@
 
-#### Total vocabulary
+# Total vocabulary
 
@@
 
-#### Conceptual vocabulary
+# Conceptual vocabulary
 
@@
 ```
-
-#### {-}
-
-### {-}
-
-## {-}
-
-# Appendix
-
-# References

### 2021-12-29 docs/03_design.Rmd
Add participants

--- 2021-12-29 docs/02_vocabulary.Rmd
@@
 ---
-title: "Vocabulary"
+title: "Design"
 output: github_document
@@
 ```
-
-```{r params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# load objects
-tar_load_globals()
-tar_load(vocabulary)
-tar_load(attrition)
-tar_load(participants)
-
-theme_set(theme_minimal()) # in utils.R
-
-attrition <- attrition %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-
-participants <- participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-```
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-# L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "white") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, outlier.colour = NA, fill = "#0D1117",
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9)
-	)
-
-```
-
-# Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.x = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-# Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.x = element_blank()
-	)
-
-```

### 2021-12-29 docs/04_analysis.Rmd
Add participants

--- 2021-12-06 Rmd/report.Rmd
@@
 ---
-title: "Cognate Priming: Report"
-output: html_document
+title: "Analysis"
+output: github_document
 always_allow_html: true
@@
 tar_load_globals()
-tar_load(participants)
-tar_load(stimuli)
-tar_load(vocabulary)
 tar_load(gaze)
-tar_load(attrition)
-tar_load(attrition_counter)
-tar_load(model_fits)
 
@@
 
-```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-attrition <- attrition %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-
-attrition_counter <- attrition_counter %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			!valid_counter ~ "Invalid counter",
-			TRUE ~ "Valid"
-		))
-
-participants <- participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
-participants_counter <- participants %>% 
-	left_join(distinct(attrition_counter, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
-```
-
-# Methods
-
-## Participants {.tabset .tabset-pills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-#### Summary
-
-```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp, test_language) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		test_language = md("**Language**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "black") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90),
-		panel.grid.major.x = element_blank()
-	) 
-```
-
-#### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	filter(valid_participant) %>% 
-	mutate(age_group = str_remove(age_group, " months")) %>%
-	ggplot(aes(age_group, participant, colour = lp)) +
-	facet_grid(~location, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Lang. Pofile") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
-```
-
-#### {-}
-
-## Stimuli
-
-### Frequency {.tabset }
-
-#### CHILDES {.tabset }
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "white", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "black", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid.major.x = element_blank()
-
-	)
-```
-
-##### {-}
-
-#### {-}
-
-### Familiarity {.tabset }
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type,
-			   xmin = familiarity_prime-familiarity_se_prime, xmax = familiarity_prime-familiarity_se_prime)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6.5, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	# scale_y_reordered() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
-	drop_na(trial_type, category) %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_wrap(role~location~test_language) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid = element_blank()
-
-	)
-
-```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
+# Gaze data {.tabset .tabset-pills}
 
@@
 
-### Workflow
+## Workflow
 
@@
 
-### Inclusion criteria
+## Inclusion criteria
 
-#### Trial-level inclusion criteria
+### Trial-level inclusion criteria
 
@@
 
-#### Participant-level inclusion criteria
+### Participant-level inclusion criteria
 
@@
 
-### {-}
-
-## {-}
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tabset-pills}
-
-## Gaze {.tabset .tabset-pills}
-
-```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-fit <- model_fits$fit
-```
-
-#### Model details
+# Model
 
@@
 $$
-
-#### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
-
-draws %>% 
-	mean_qi(.width = c(0.95, 0.50)) %>% 
-	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
-	clean_names() %>% 
-	select(-c(point, interval, value_0_5)) %>% 
-	gt(rowname_col = "variable") %>% 
-	fmt_number(2:6) %>% 
-	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		variable = md("**Predictor**"),
-		value_0_95 = md("**Mean**"),
-		lower_0_95 = md("**95% CrI**"),
-		lower_0_5 = md("**50% CrI**")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = lower_0_95 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = lower_0_5 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = upper_0_95 < 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = upper_0_5 < 0
-		)
-	) %>% 
-	as_raw_html()
-```
-
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
-
-draws %>% 
-	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
-	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
-	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
-	geom_vline(xintercept = 0, colour = "black") +
-	stat_halfeye(point_color = "black", interval_color = "black") +
-	labs(x = "Value", y = "Variable", fill = "CrI") +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	theme(
-		axis.title = element_blank(),
-		legend.position = "top"
-	)
-
-```
-
-#### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-vcov(fit) %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
-	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
-	geom_tile() +
-	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
-	scale_fill_distiller(limits = c(-1, 1)) +
-	coord_equal() +
-	theme(
-		legend.position = "top",
-		legend.text = element_text(size = 8),
-		axis.title = element_blank(),
-		axis.text.y = element_text(hjust = 1, size = 7),
-		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
-	)
-
-```
-
-#### Marginal means {.tabset }
-
-##### Marginal to time course
-
-```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-m <- emmeans(fit, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
-	as_tibble() %>% 
-	clean_names() %>% 
-	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x < 0, 0, x)) %>% 
-	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x > 1, 1, x))
-
-ggplot(m, aes(age_group, emmean, ymin = lower_hpd, ymax = upper_hpd, colour = trial_type)) +
-	facet_wrap(~lp, ncol = 1) +
-	# geom_line(aes(group = trial_type), size = 1, position = position_dodge(width = 0.25)) +
-	geom_errorbar(size = 1, width = 0, position = position_dodge(width = 0.25)) +
-	geom_point(size = 4, position = position_dodge(width = 0.25)) +
-	labs(x = "Age (months))", y = "P(target)", colour = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent)  +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "top"
-	)
-
-```
-
-##### Time course
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(lp, age_group)
-
-n <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	age_group = paste(c(21, 25, 30), "months"),
-	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
-)
-
-m <- epred_draws(object = fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
-	mutate(.value = logit_to_prob(.epred))
-
-ggplot(m, aes(time_bin_center, .value)) +
-	facet_grid(fct_rev(lp)~age_group) +
-	geom_hline(yintercept = 0.5, colour = "black") +
-	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
-				  colour = trial_type),
-			  alpha = 0.15, size = 0.65) +
-	stat_summary(aes(group = trial_type, colour = trial_type),
-				 fun = mean, geom = "line", size = 1.25) +
-	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
-								  colour = trial_type),
-				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
-				 position = position_dodge(width = 0.3)) +
-	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
-			  colour = "white", hjust = 0, size = 5) +
-	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
-		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_brewer(palette = "Set1") +
-	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 9),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank()
-	)
-```
-
-##### {-}
-
-#### {-}
-
-## Attrition {.tabset}
-
-#### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = "#0D1117", size = 1) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-#### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-#### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
-	as_raw_html()
-
-```
-
-#### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	as_raw_html()
-```
-
-#### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	drop_na(trial_type) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	) %>% 
-	as_raw_html()
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(location~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### By lexical frequency {.tabset }
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By familiarity {.tabset}
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By animacy {.tabset }
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-##### {-}
-
-#### By category {.tabset}
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-## Vocabulary {.tabset .tabset-pills}
-
-#### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "white") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, outlier.colour = NA, fill = "#0D1117",
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9)
-	)
-
-```
-
-#### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.x = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-#### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.x = element_blank()
-	)
-
-```
-
-#### {-}
-
-### {-}
-
-## {-}
-
-# Appendix
-
-# References

### 2021-12-29 docs/05_attrition.Rmd
Add participants

--- 2021-11-08 Rmd/report.Rmd
@@
 ---
-title: "Cognate Priming: Report"
-output:
-  github_document:
-    pandoc_args: --webtex
+title: "Attrition"
+output: github_document
 always_allow_html: true
@@
 
-# load packages
-library(targets)
-library(papaja)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(scales)
-library(DiagrammeR)
-library(janitor)
-library(gt)
-library(patchwork)
-library(wesanderson)
-library(shiny)
-library(tidybayes)
-library(brms)
-library(tidytext)
-library(brms)
-library(tidyverse)
-library(here)
-
 # load objects
@@
 tar_load(participants)
+tar_load(vocabulary)
 tar_load(stimuli)
-tar_load(vocabulary)
-tar_load(gaze)
 tar_load(attrition)
-tar_load(attrition_counter)
-tar_load(model_fits)
 
-theme_set(theme_github()) # in utils.R
-```
-
-```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+theme_set(theme_minimal()) # in utils.R
 
@@
 		))
-
-attrition_counter <- attrition_counter %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			!valid_counter ~ "Invalid counter",
-			TRUE ~ "Valid"
-		))
-
-participants <- participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
-participants_counter <- participants %>% 
-	left_join(distinct(attrition_counter, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
 ```
 
-# Methods
-
-## Participants {.tabset .tabset-pills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-#### Summary
-
-```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp, test_language) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		test_language = md("**Language**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90),
-		panel.grid.major.x = element_blank()
-	) 
-```
-
-#### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	filter(valid_participant) %>% 
-	mutate(age_group = str_remove(age_group, " months")) %>%
-	ggplot(aes(age_group, participant, colour = lp)) +
-	facet_grid(~location, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Lang. Pofile") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
-```
-
-#### {-}
-
-## Stimuli
-
-### Frequency {.tabset }
-
-#### CHILDES {.tabset }
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "white", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "black", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid.major.x = element_blank()
-
-	)
-```
-
-##### {-}
-
-#### {-}
-
-### Familiarity {.tabset }
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type,
-			   xmin = familiarity_prime-familiarity_se_prime, xmax = familiarity_prime-familiarity_se_prime)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6.5, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	# scale_y_reordered() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
-	drop_na(trial_type, category) %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_wrap(role~location~test_language) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid = element_blank()
-
-	)
-
-```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level") %>%
-	as_raw_html()
-
-```
-
-### {-}
-
-## {-}
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tabset-pills}
-
-## Gaze {.tabset .tabset-pills}
-
-```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-fit <- model_fits$fit
-```
-
-#### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-$$
-
-\color{white}{
-\log \Bigg( \frac{p}{n - q} \Bigg) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
-(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
-(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
-(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
-(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
-(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
-(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
-(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
-(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
-}
-$$
-
-#### Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
-
-draws %>% 
-	mean_qi(.width = c(0.95, 0.50)) %>% 
-	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
-	clean_names() %>% 
-	select(-c(point, interval, value_0_5)) %>% 
-	gt(rowname_col = "variable") %>% 
-	fmt_number(2:6) %>% 
-	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		variable = md("**Predictor**"),
-		value_0_95 = md("**Mean**"),
-		lower_0_95 = md("**95% CrI**"),
-		lower_0_5 = md("**50% CrI**")
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = lower_0_95 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#b9fac4")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = lower_0_5 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = upper_0_95 < 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = upper_0_5 < 0
-		)
-	) %>% 
-	as_raw_html()
-```
-
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
-
-draws %>% 
-	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
-	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
-	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
-	geom_vline(xintercept = 0, colour = "white") +
-	stat_halfeye(point_color = "white", interval_color = "white") +
-	labs(x = "Value", y = "Variable", fill = "CrI") +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	theme(
-		axis.title = element_blank(),
-		legend.position = "top"
-	)
-
-```
-
-#### Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-vcov(fit) %>% 
-	cov2cor() %>% 
-	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
-	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
-	geom_tile() +
-	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
-	scale_fill_distiller(limits = c(-1, 1)) +
-	coord_equal() +
-	theme(
-		legend.position = "top",
-		legend.text = element_text(size = 8),
-		axis.title = element_blank(),
-		axis.text.y = element_text(hjust = 1, size = 7),
-		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
-	)
-
-```
-
-#### Marginal means {.tabset }
-
-##### Overall
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(lp)
-
-n <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	age_group = c("25 months"),
-	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
-)
-
-m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
-	mutate(.value = logit_to_prob(.epred))
-
-ggplot(m, aes(time_bin_center, .value)) +
-	facet_wrap(~fct_rev(lp)) +
-	geom_hline(yintercept = 0.5, colour = "white") +
-	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
-				  colour = trial_type),
-			  alpha = 0.15, size = 0.65) +
-	stat_summary(aes(group = trial_type, colour = trial_type),
-				 fun = mean, geom = "line", size = 1.25) +
-	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
-								  colour = trial_type),
-				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
-				 position = position_dodge(width = 0.3)) +
-	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
-			  colour = "white", hjust = 0, size = 5) +
-	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
-		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_brewer(palette = "Set1") +
-	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 9),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank()
-	)
-```
-
-##### {-}
-
-#### {-}
-
-## Attrition {.tabset}
-
-#### Summary
+# Summary
 
@@
 
-#### By location
+# By location
 
@@
 
-#### By group
+# By group
 
@@
 
-#### By participant
+# By participant
 
@@
 
-#### By trial
+# By trial
 
@@
 
-#### By lexical frequency {.tabset }
+## By lexical frequency {.tabset }
 
@@
 
-##### {-}
-
-#### By familiarity {.tabset}
+## By familiarity {.tabset}
 
@@
 
-##### {-}
-
-#### By animacy {.tabset }
+## By animacy {.tabset }
 
@@
 
-##### {-}
-
-#### By category {.tabset}
+## By category {.tabset}
 
@@
 ```
-
-##### {-}
-
-## Vocabulary {.tabset .tabset-pills}
-
-#### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "white") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, outlier.colour = NA, fill = "#0D1117",
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9)
-	)
-
-```
-
-#### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.x = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-#### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.x = element_blank()
-	)
-
-```
-
-#### {-}
-
-### {-}
-
-## {-}
-
-# Appendix
-
-# References

### 2021-12-29 docs/06_results.Rmd
Add participants

--- 2021-12-06 Rmd/report.Rmd
@@
 ---
-title: "Cognate Priming: Report"
-output: html_document
+title: "Results"
+output: github_document
 always_allow_html: true
@@
 tar_load(participants)
-tar_load(stimuli)
+tar_load(attrition)
 tar_load(vocabulary)
 tar_load(gaze)
-tar_load(attrition)
-tar_load(attrition_counter)
 tar_load(model_fits)
@@
 theme_set(theme_minimal()) # in utils.R
-```
-
-```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
@@
 
-participants_counter <- participants %>% 
-	left_join(distinct(attrition_counter, participant, age_group, valid_participant)) %>% 
-	drop_na(participant) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
-
 ```
-
-# Methods
-
-## Participants {.tabset .tabset-pills}
-
-* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
-* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group).
-`r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
-* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
-
-#### Summary
-
-```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	count(location, age_group, lp, test_language) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
-	cols_label(
-		lp = md("**Language profile**"),
-		test_language = md("**Language**"),
-		`21 months` = md("**21 months**"),
-		`25 months` = md("**25 months**"),
-		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
-```
-
-```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "black") +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(
-		legend.position = "top",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90),
-		panel.grid.major.x = element_blank()
-	) 
-```
-
-#### Longitudinal
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	filter(valid_participant) %>% 
-	mutate(age_group = str_remove(age_group, " months")) %>%
-	ggplot(aes(age_group, participant, colour = lp)) +
-	facet_grid(~location, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Lang. Pofile") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
-		axis.ticks.y = element_blank()
-	)
-```
-
-#### {-}
-
-## Stimuli
-
-### Frequency {.tabset }
-
-#### CHILDES {.tabset }
-
-##### Prime
-
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "white", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-##### Target
-
-```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "black", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
-	theme(
-		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.x = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid.major.x = element_blank()
-
-	)
-```
-
-##### {-}
-
-#### {-}
-
-### Familiarity {.tabset }
-
-#### Prime
-
-```{r stimuli_familiarity_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=7, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-		.groups = "drop"
-	) %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type,
-			   xmin = familiarity_prime-familiarity_se_prime, xmax = familiarity_prime-familiarity_se_prime)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### Target
-
-```{r stimuli_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6.5, out.width="100%"}
-means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
-	summarise(
-		familiarity_target = mean(familiarity_target, na.rm = TRUE),
-		.groups = "drop"
-	)
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	# scale_y_reordered() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
-		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-	)
-
-```
-
-#### {-}
-
-### Animacy
-
-```{r stimuli_animacy, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(
-		axis.title.x = element_blank()
-	) +
-
-	animacy %>% 
-	filter(role=="Target") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.title.y = element_blank(),
-		axis.text = element_text(size = 7),
-		strip.text = element_text(size = 11)
-	)
-
-```
-
-### Semantic category
-
-```{r stimuli_category, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=6, out.width="100%"}
-
-stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
-	drop_na(trial_type, category) %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_wrap(role~location~test_language) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
-		axis.title.y = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid = element_blank()
-
-	)
-
-```
-
-### {-}
-
-## Procedure
-
-## Data analysis
-
-### Vocabulary data
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [MultiLex](https://github.com/gongcastro/multilex) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.
-
-## Gaze data {.tabset .tabset-pills}
-
-Each trial was divided into 100 ms time bins.
-for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin.
-Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).
-
-### Workflow
-
-```{r workflow_preprocessing, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-DiagrammeR::grViz("digraph {
-  graph [layout = dot, rankdir = TB]
-
-  node [shape = rectangle, fontname = 'Arial']        
-  rec1 [label = 'Merge Barcelona and Oxford data']
-  rec2 [label = 'Impute missing/invalid samples (pending)']
-  rec2 [label = 'Extract fixations (pending)']
-  rec3 [label = 'For each sample, evaluate if gaze is in target or distractor']
-  rec4 [label = 'Divide each trial into 100 ms time bins']
-  rec5 [label = 'Aggregate samples from the same time bin and calculate\nthe number of valid samples in target, distractor, or none']
-  rec6 [label = 'Exclude time bins 1-3 (pending)']
-  rec7 [label = 'Apply trial-level inclusion criteria']
-  rec8 [label = 'Apply participant-level inclusion criteria']
-
-  # edge definitions with the node IDs
-  rec1 -> rec2 -> rec3 -> rec4 -> rec5 -> rec6 -> rec7 -> rec8
-  }", 
-  height = 500)
-```
-
-### Inclusion criteria
-
-#### Trial-level inclusion criteria
-
-* $\geq$ 50% or more valid samples during prime phase (1,500 ms)
-* $\geq$ 50% or more valid samples during target-distractor phase (2,000 ms)
-* At least one sample in target and one sample in distractor
-* Participant understands prime word in both languages
-* Participant knows the target word in the test language
-* Participant knows the distractor word in the test language
-
-#### Participant-level inclusion criteria
-
-* $\geq$ 4 trials in *Cognate* condition (50%, from a total of 8)
-* $\geq$ 4 trials in *Non-cognate* condition (50%, from a total of 8)
-* $\geq$ 8 trials in *Unrelated* condition (50%, from a total of 16)
-* $\geq$ 36 gestational weeks
-* $\geq$ 2,800g birth weight
-* No diagnosed developmental, hearing, or visual disorders
-* Not exposed to more than 10% to a 3rd language
-
-### Input variables
-
-* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
-* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
-* Trial type (`trial_type1` and `trial_type2`).
-Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*.
-We coded two contrasts: `trial_type1`, comparing related trials vs.
-unrelated trials (*Cognate* + *Non-cognate* vs.
-*Unrelated*), and `trial_type2`, comparing *Cognate* vs.
-*Non-cognate* trials.
-These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].
-
-```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-contrasts(gaze$trial_type) %>% 
-	as.data.frame() %>% 
-	set_names(paste0("trial_type", 1:2)) %>% 
-	rownames_to_column("level") %>% 
-	gt(rowname_col = "level") %>%
-	as_raw_html()
-
-```
-
-### {-}
-
-## {-}
-
-### {-}
-
-## {-}
-
-# Results {.tabset .tabset-pills}
-
-## Gaze {.tabset .tabset-pills}
-
-```{r define_model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-fit <- model_fits$fit
-```
-
-#### Model details
-
-We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:
-
-```
-elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
-(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
-```
-
-The formal implementation of this model is:
-
-**Likelihoods**:
-
-$$
-\Bigg( \frac{p}{n - q} \Bigg) \sim \mathcal{N}(y_{ij}, ~ \sigma^2_m)
-$$
-
-**Parameters**:
-
-$$
-\begin{align}
-y_{ij} =&~ (\beta_{0} + \beta_{0p} + \beta_{0i}) ~+~ ... \\ 
-& (\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} ~+~ ... \\
-& (\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} ~ + ~ ... \\
-& (\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} ~ + ~ ... \\
-& (\beta_{4} + \beta_{4i}) \times Group_{pi} ~+~ ... \\
-& (\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) ~+~ ... \\
-& (\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) ~+~ ... \\
-& (\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) ~+~ ... \\
-& (\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) ~+~ \\ & \sigma^2_{e}
-\end{align}
-$$
-
-**Priors**:
-
-$$
-\begin{align}
-\beta_0 \sim~ & \mathcal{N}(0, 1) \\
-\beta_{1-8} \sim~ &\mathcal{N}(0, 1) \\
-\sigma_m, ~\sigma^2,~ \sigma^2_p,~ \sigma^2_i \sim~ & exp(2) \\
-\rho \sim ~&  LKJ(2)
-\end{align}
-$$
 
@@
 ```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
+draws <- gather_draws(model_fits$fit, `b_.*`, `sigma`, regex = TRUE)
 
@@
 
-vcov(fit) %>% 
+vcov(model_fits$fit) %>% 
 	cov2cor() %>% 
@@
 
-m <- emmeans(fit, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
+m <- emmeans(model_fits$fit, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
 	as_tibble() %>% 
@@
 
-m <- epred_draws(object = fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
+m <- epred_draws(object = model_fits$fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
 	mutate(.value = logit_to_prob(.epred))
@@
 ```
-
-##### {-}
-
-#### {-}
-
-## Attrition {.tabset}
-
-#### Summary
-
-```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-participants %>% 
-	left_join(distinct(attrition, participant, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
-			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
-			!valid_participant ~ "Not valid"
-		)
-	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = "#0D1117", size = 1) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
-	scale_colour_brewer(palette = "Set1") +
-	labs(x = "Group", y = "Sample size", fill = "Valid?") +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 10),
-		axis.title.y = element_text(angle = 90)
-	) 
-```
-
-#### By location
-
-```{r trials_attrition_location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, out.width="100%"}
-# plot participants
-attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type)
-
-attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
-	)
-```
-
-#### By group
-
-This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).
-
-```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}
-
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(
-		names_from = trial_type,
-		values_from = valid_trial_count
-	) %>% 
-	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
-	summarise(
-		cognate = mean(cognate, na.rm = TRUE),
-		non_cognate = mean(non_cognate, na.rm = TRUE),
-		unrelated = mean(unrelated, na.rm = TRUE),
-		sum_n = sum(valid_participant, na.rm = TRUE),
-		prop_n = mean(valid_participant, na.rm = TRUE),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
-	tab_spanner(
-		"Mean valid trials",
-		c("cognate", "non_cognate", "unrelated")
-	) %>% 
-	tab_spanner(
-		"N participants",
-		c("sum_n", "n", "prop_n")
-	) %>% 
-	cols_label(
-		age_group = "Age",
-		lp = "Group",
-		sum_n = "Valid",
-		location = "Laboratory",
-		n = "Tested",
-		prop_n = "Valid (%)",
-		cognate = "Cognate (8)",
-		non_cognate = "Non-cognate (8)",
-		unrelated = "Unrelated (16)"
-	) %>% 
-	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
-	fmt_percent(c("prop_n")) %>% 
-	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
-	as_raw_html()
-
-```
-
-#### By participant
-
-```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
-	summarise(
-		valid = mean(valid_trial),
-		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
-		.groups = "drop"
-	) %>% 
-	relocate(participant) %>% 
-	gt() %>% 
-	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
-	cols_label(
-		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
-		age_group = "Age",
-		valid_participant = "Valid participant",
-		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
-	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
-	as_raw_html()
-```
-
-#### By trial
-
-```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	drop_na(trial_type) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
-	count() %>% 
-	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
-	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
-	cols_label(
-		location = "Location",
-		lp = "Group",
-		trial_type = "Trial type",
-		x21_months_not_valid = "Not valid",
-		x21_months_valid = "Valid",
-		x25_months_not_valid = "Not valid",
-		x25_months_valid = "Valid",
-		x30_months_not_valid = "Not valid",
-		x30_months_valid = "Valid"
-	) %>% 
-	as_raw_html()
-
-```
-
-```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, age_group, trial_type, valid_status) %>% 
-	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(location~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(labels = percent) +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-#### By lexical frequency {.tabset }
-
-```{r attrition_frequency_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_frequency_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
-	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By familiarity {.tabset}
-
-```{r attrition_familiarity_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	count(trial_type, lp, age_group, valid_status)
-
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
-	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-# plot participants
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
-	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-#### By animacy {.tabset }
-
-```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
-	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
-	drop_na(trial_type, is_animate_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
-	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-
-```
-
-##### {-}
-
-#### By category {.tabset}
-
-```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent) +
-	coord_flip() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
-	)
-```
-
-##### {-}
-
-## Vocabulary {.tabset .tabset-pills}
-
-#### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "white") +
-	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, outlier.colour = NA, fill = "#0D1117",
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.y = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9)
-	)
-
-```
-
-#### Total vocabulary
-
-```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.x = element_blank(),
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
-	)
-
-```
-
-#### Conceptual vocabulary
-
-```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
-	count(age_group, location)
-
-# vocabulary
-participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
-	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "white", size = 1, stroke = 1,
-		position = position_jitter(width = 0.1, seed = 888)
-	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
-	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
-	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(
-		legend.title = element_blank(),
-		legend.position = "none",
-		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.x = element_blank()
-	)
-
-```
-
-#### {-}
-
-### {-}
-
-## {-}
-
-# Appendix
-
-# References

### 2021-12-29 _targets.R

@@ -2,15 +2,15 @@ library(targets)
 library(tarchetypes)
 
 # load functions
-source("R/utils.R")
-source("R/00_stimuli.R")
-source("R/01_participants.R")
-source("R/02_vocabulary.R")
-source("R/03_gaze_bcn.R")
-source("R/03_gaze_oxf.R")
-source("R/04_attrition.R")
-source("R/05_prepare.R")
-source("R/06_analysis.R")
+source("src/R/utils.R")
+source("src/R/00_stimuli.R")
+source("src/R/01_participants.R")
+source("src/R/02_vocabulary.R")
+source("src/R/03_gaze_bcn.R")
+source("src/R/03_gaze_oxf.R")
+source("src/R/04_attrition.R")
+source("src/R/05_prepare.R")
+source("src/R/06_analysis.R")
 
 # load packages ----
 tar_option_set(
@@ -27,7 +27,9 @@ tar_option_set(
 		# data visualisation
 		"ggplot2", "shiny", "patchwork", "shiny",
 		# data reporting
-		"rmarkdown", "knitr", "papaja", "scales", "DiagrammeR", "gt"
+		"rmarkdown", "knitr", "papaja", "scales", "DiagrammeR", "gt",
+		# unit testing
+		"testthat"
 	)
 )
 
@@ -55,9 +57,9 @@ list(
 	
 	# stimuli ----
 	# define file paths
-	tar_target(trials_path, here("Stimuli", "stimuli.xlsx"), format = "file"), # trial list,
-	tar_target(stimuli_english_path, here("Data", "Stimuli", "stimuli_english.xlsx"), format = "file"), # stimuli info for English version
-	tar_target(animacy_path, here("Data", "Stimuli", "animacy.csv"), format = "file"), # animacy of stimuli (hand coded)
+	tar_target(trials_path, here("stimuli", "stimuli.xlsx"), format = "file"), # trial list,
+	tar_target(stimuli_english_path, here("data", "stimuli", "stimuli_english.xlsx"), format = "file"), # stimuli info for English version
+	tar_target(animacy_path, here("data", "stimuli", "animacy.csv"), format = "file"), # animacy of stimuli (hand coded)
 	
 	# import data
 	tar_target(trials, read_xlsx(trials_path)),
@@ -78,41 +80,18 @@ list(
 	
 	# participants ----
 	# define Oxford file paths
-	tar_target(
[…]

### 2021-12-29 src/R/00_stimuli.R

@@ -1,0 +1,111 @@
+# stimuli
+
+get_stimuli <- function(
+	trials, # trials dataset
+	familiarity_age = c(17, 19), # age range for familiarity norms (min-max)
+	familiarity_type = c("understands"), # vocabulary type (understands or produces)
+	impute = TRUE, # impute missing data?
+	update = FALSE, # update vocabulary data? (multilex may take a while to update)
+	conf = 0.95, # confidence level for familiarity estimates
+	multilex_data, # output of get_multilex()
+	oxford_data,
+	animacy_data
+){
+	suppressMessages({
+		
+		get_credentials()
+		
+		# familiarity norms ----
+		# see utils.R for details on the get_familiarity() function
+		familiarity <- get_familiarity(
+			# words to compute familiarity norms for (primes and targets)
+			tokens =  trials %>% # defined in arguments
+				distinct(prime_cdi, target_cdi) %>%
+				unlist() %>%
+				unique(),
+			oxford_data = oxford_data,
+			type = familiarity_type, # defined in arguments
+			update = update, # defined in arguments
+			multilex_data = multilex_data # defined in arguments
+		)
+		
+		
+		# lexical frequency norms (CHILDES) ----
+		# see utils.R for details on the get_frequency_childes() function
+		frequency_childes <- get_frequency_childes(
+			# words to compute CHILDES frequency norms for (primes and targets)
+			token = trials %>% # defined in arguments
+				distinct(prime, target) %>%
+				unlist() %>%
+				unique()
+		) %>% 
+			# to avoid issues with other column names
+			rename(frequency_childes = frequency) 
+		
+		
+		# lexical frequency norms (SUBTLEX) ----
+		# see utils.R for details on the get_frequency_subtlex() function
+		frequency_subtlex <- get_frequency_subtlex(
+			# words to compute SUBTLEX frequency norms for (primes and targets)
+			token = trials %>% # defined in arguments
+				distinct(prime, target) %>%
+				unlist() %>%
+				unique()
+		) %>% 
+			rename(frequency_subtlex = frequency) 
+		
+		# semantic category ----
+		# only available for Barcelona for now (pending: include Oxford categories)
+		semantic_category <- multilex_data$pool %>% # defined in arguments
+			select(word = item, language, category) %>%
+			rename(test_language = language)
+		
+		# animacy ----
[…]

### 2021-12-29 src/R/04_attrition.R

@@ -1,0 +1,156 @@
+# attrition
+get_attrition <- function(
+	gaze_bcn, # Barcelona gaze data, get_gaze_bcn output
+	gaze_oxf, # Barcelona gaze data, get_gaze_bcn output
+	participants, # participants dataset, get_participants output
+	stimuli, # stimuli dataset, get_stimuli output
+	vocabulary, # vocabulary dataset, get_vocabulary output
+	filter_vocabulary = c("prime", "target"), # should the trial be excluded if no comprehension in any of these words? (prime, target, distractor)
+	filter_counterbalancing = TRUE, # should trials from same counterbalancing pair be excluded together?
+	looking_threshold = c(prime = 0, target = 0, distractor = 0), # minimum looking time
+	missing_trials_threshold = c(cognate = 0, noncognate = 0, unrelated = 0) # minimum n trials in each condition
+){
+	suppressWarnings({
+		# merge Barcelona and Oxford gaze data
+		gaze <- list(Barcelona = gaze_bcn, Oxford = gaze_oxf) %>% 
+			bind_rows(.id = "location") %>% 
+			# to avoid issues with column names
+			rename(time_stamp = time)
+		
+		processed <- reduce(list(participants, vocabulary, gaze), left_join)
+		
+		# evaluate inclusion criteria ----
+		# valid gaze
+		valid_gaze <- processed %>% 
+			group_by(participant, age_group, trial_type, trial) %>% 
+			summarise(
+				# proportion of prime looking time during prime phase
+				valid_looking_prime = sum(aoi_prime[phase=="Prime"], na.rm = TRUE)*(1000/120),
+				# proportion of target looking time during target-distractor phase
+				valid_looking_target = sum(aoi_target[phase=="Target-Distractor"], na.rm = TRUE)*(1000/120), 
+				# proportion of distractor looking time during target-distractor phase
+				valid_looking_distractor = sum(aoi_distractor[phase=="Target-Distractor"], na.rm = TRUE)*(1000/120), 
+				.groups = "drop"
+			) %>% 
+			mutate(
+				# prime looking proportion during prime phase is higher or equal than minimum
+				valid_gaze_prime = case_when(
+					looking_threshold["prime"]>0 ~ (valid_looking_prime > looking_threshold["prime"]),
+					TRUE ~ TRUE
+				),					
+				# participant has looked at least once to target AND distractor and higher or equal than minimum to both
[…]

### 2021-12-29 presentations/2022-07-07_icis/2022-07-07_icis-abstract.Rmd

--- 2021-12-06 Communications/2022-07-07_icis/2022-07-07_icis-abstract.Rmd
@@
 tar_load(model_fits)
+tar_load(epreds)
+tar_load(emmeans_lp)
 
@@
 
-emmean <- emmeans(
-	model_fits$fit,
-	~trial_type, 
-	by = "lp",
-	epred = TRUE
-) %>% 
-	as_tibble() %>% 
-	mutate_if(is.numeric, inv_logit_scaled)
-
 ```
@@
 Each pair of pictures was preceded by the presentation of a silent image (prime picture).
-We designed three types of trials: trials in which prime and target labels shared phonological onset and the prime label was a cognate (cognate trials; e.g., *flower*-*flor* / *bird*, for an English-Spanish participant), trials where prime and target labels shared phonological onset but the prime label was a non-cognate (non-cognate trials; e.g., *chair*-*silla* / *bird*), and trials where prime and target labels did not share phonological onset (unrelated trials; *car*-*coche* / *bird*).
+We designed three types of trials: (1) *cognate trials* in which prime and target labels shared phonological onset and the prime label was a cognate (e.g., *flower*-*flor* / *bird*), (2) *non-cognate trials*, in which prime and target labels shared phonological onset but the prime label was a non-cognate (e.g., *chair*-*silla* / *bird*), and (3) *unrelated trials*, in which prime and target labels did not share phonological onset (unrelated trials; *car*-*coche* / *bird*).
 
-In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset [e.g., @mani2010infant].
+In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset [e.g., @mani2011phonological].
 Additionally, under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we predicted that interference would be stronger after cognate primes (labels from both languages share phonological overlap with target word recognition) than after non-cognate primes (only the label in the target language share phonological overlap with target word recognition).
@@
 
-Preliminary results (data collection is ongoing) from a Bayesian Growth Curve Analysis suggest that bilinguals' proportion target looking (PTL) did not differ across the cognate (`r percent(emmean$emmean[1], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[1]*100)`, `r printnum(emmean$upper.HPD[1]*100)`]), non-cognate (`r percent(emmean$emmean[2], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[2]*100)`, `r printnum(emmean$upper.HPD[2]*100)`]), or unrelated (`r percent(emmean$emmean[3], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[3]*100)`, `r printnum(emmean$upper.HPD[3]*100)`]) priming conditions.
-Surprisingly, monolinguals' preference for the target picture was stronger after non-cognate primes (`r percent(emmean$emmean[5], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[5]*100)`, `r printnum(emmean$upper.HPD[5]*100)`]) and unrelated primes (`r percent(emmean$emmean[6], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[6]*100)`, `r printnum(emmean$upper.HPD[6]*100)`]) compared to cognate primes (`r percent(emmean$emmean[4], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmean$lower.HPD[1]*100)`, `r printnum(emmean$upper.HPD[1]*100)`]).
+Preliminary results (data collection is ongoing) from a Bayesian Growth Curve Analysis suggest that bilinguals' proportion target looking (PTL) did not differ across the cognate (`r percent(emmeans_lp$emmean[1], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmeans_lp$lower.HPD[1]*100)`, `r printnum(emmeans_lp$upper.HPD[1]*100)`]), non-cognate (`r percent(emmeans_lp$emmean[2], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmeans_lp$lower.HPD[2]*100)`, `r printnum(emmeans_lp$upper.HPD[2]*100)`]), or unrelated (`r percent(emmeans_lp$emmean[3], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmeans_lp$lower.HPD[3]*100)`, `r printnum(emmeans_lp$upper.HPD[3]*100)`]) priming conditions.
+Surprisingly, monolinguals' preference for the target picture was stronger after non-cognate primes (`r percent(emmeans_lp$emmean[5], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmeans_lp$lower.HPD[5]*100)`, `r printnum(emmeans_lp$upper.HPD[5]*100)`]) and unrelated primes (`r percent(emmeans_lp$emmean[6], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmeans_lp$lower.HPD[6]*100)`, `r printnum(emmeans_lp$upper.HPD[6]*100)`]) compared to cognate primes (`r percent(emmeans_lp$emmean[4], accuracy = 0.01)`, 95% *HPD* = [`r printnum(emmeans_lp$lower.HPD[1]*100)`, `r printnum(emmeans_lp$upper.HPD[1]*100)`]).
 This suggests that contrary to our predictions, monolinguals were sensitive to both phonological priming and cognateness.
@@
 
-n <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	age_group = paste(c(21, 25, 30), "months"),
-	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
-)
-
-m <- epred_draws(object = model_fits$fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
-	mutate(.value = logit_to_prob(.epred))
-
-ggplot(m, aes(time_bin_center, .value)) +
+ggplot(epreds, aes(time_bin_center, .epred)) +
 	facet_grid(fct_rev(lp)~age_group) +

### 2022-01-03 docs/06_results-bcn.Rmd
Only Barcelona data

--- 2021-12-29 docs/06_results.Rmd
@@
 ---
-title: "Results"
+title: "Results (Barcelona)"
 output: github_document
@@
 ```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(model_fits$fit, `b_.*`, `sigma`, regex = TRUE)
+draws <- gather_draws(model_fits$fit_bcn, `b_.*`, `sigma`, regex = TRUE)
 
@@
 
-vcov(model_fits$fit) %>% 
+vcov(model_fits$fit_bcn) %>% 
 	cov2cor() %>% 
@@
 
-m <- emmeans(model_fits$fit, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
+m <- emmeans(model_fits$fit_bcn, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
 	as_tibble() %>% 
@@
 
-m <- epred_draws(object = model_fits$fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
+m <- epred_draws(object = model_fits$fit_bcn, newdata = n, ndraws = 50, re_formula = NA) %>% 
 	mutate(.value = logit_to_prob(.epred))

### 2022-01-04 presentations/2022-01-25_lacre/2022-01-25_lacre-abstract.Rmd
Update participants

--- 2021-12-06 Communications/2022-01-25_lacre/2022-01-25_lacre-abstract.Rmd
@@
 
-Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language [e.g., @costa2000cognate; @thierry2007brain].
-It has been suggested that this parallel activation is already present during toddlerhood [e.g., @von2012language; @jardak2019labels], but it is unclear how this parallel activation impacts the developing lexicon.
-We tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task.
-Participants were tested exclusively in their language of most exposure.
-two pictures were presented side-by-side, one of them was named, and participants' visual preference for the named (target) picture was taken as a proxy of word recognition.
-Each pair of pictures was preceded by the presentation of a silent image (prime).
-We manipulated two variables regarding to the relationship between the label associated to the prime image and the target word: their phonological overlap in the testing language and the cognate status of the prime label.
+Previous studies have provided evidence that bilingual lexical access is language non-selective: recognising and producing words in one language activates lexical representations of words in the other language [e.g., @costa2000cognate; @thierry2007brain].
+It has been suggested that this parallel activation is already present during toddlerhood [e.g., @von2012language; @jardak2019labels], but it is unclear how this it impacts the developing lexicon.
+We tested Catalan-Spanish bilinguals in a primed word recognition task, in which the auditory stimuli presented during the task were exclusively in participants' dominant language.
+We registered participants' looking preference for named (target) pictures as an indicator of word recognition.
+In primed trials, target pictures were preceded by the presentation of a silent picture whose label shared phonological onset with the target label.
+In non-primed trials, both labels had different onsets.
+We also manipulated the cognate status of the prime labels: some prime labels also shared phonological onset with their translation in participants' other language, while others did not.
 This resulted in three types of trials: trials in which prime and target labels shared phonological onset and the prime label was a cognate (cognate trials; e.g., *flower*/*flor*-*bird*, for an English-Spanish participant), trials where prime and target labels shared phonological onset but the prime label was a non-cognate (non-cognate trials; e.g., *chair*/*silla*-*bird*), and trials where prime and target labels did not share phonological onset (unrelated trials; *car*/*coche*-*bird*).

### 2022-01-13 docs/02_vocabulary.Rmd
Sample posterior

@@
 	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = lp, fill = lp),
-		width = 0.25, outlier.colour = NA, fill = "#0D1117",
+		aes(lp, vocab_size_l1, fill = lp),
+		width = 0.25, outlier.colour = NA,
 		position = position_dodge(width = 0.75), size = 1

### 2022-01-13 docs/06_results-bcn.Rmd
Sample posterior

@@
 tar_load(gaze)
-tar_load(model_fits)
+tar_load(fit)
 
@@
 participants <- participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+	left_join(distinct(attrition, participant, valid_participant)) %>% 
 	drop_na(participant) %>% 
 	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
+	mutate(
+		vocab_size_l1_center = scale(vocab_size_l1)[,1],
+		vocab_size_total_center = scale(vocab_size_total)[,1]
+	)
 
@@
 ```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(model_fits$fit_bcn, `b_.*`, `sigma`, regex = TRUE)
+draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
 
@@
 	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
-	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
-	geom_vline(xintercept = 0, colour = "black") +
-	stat_halfeye(point_color = "black", interval_color = "black") +
+	ggplot(aes(.value, .variable)) +
+	geom_vline(xintercept = 0, colour = "red", size = 1) +
+	# stat_halfeye(point_color = "black", interval_color = "black") +
+	stat_pointinterval() +
 	labs(x = "Value", y = "Variable", fill = "CrI") +
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent) +
 	theme(
@@
 
-vcov(model_fits$fit_bcn) %>% 
+vcov(fit) %>% 
 	cov2cor() %>% 
@@
 
-m <- emmeans(model_fits$fit_bcn, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
+m <- emmeans(fit, ~trial_type:lp, by = "vocab_size_total_center", epred = TRUE) %>% 
 	as_tibble() %>% 
@@
 
-ggplot(m, aes(age_group, emmean, ymin = lower_hpd, ymax = upper_hpd, colour = trial_type)) +
+ggplot(m, aes(vocab_size_total_center, emmean, ymin = lower_hpd, ymax = upper_hpd, colour = trial_type)) +
 	facet_wrap(~lp, ncol = 1) +
@@
 	filter(valid_participant) %>% 
-	count(lp, age_group)
+	count(lp, vocab_size_total_center)
 
@@
 	lp = c("Monolingual", "Bilingual"),
-	age_group = paste(c(21, 25, 30), "months"),
+	vocab_size_total_center = c(-1, 1),
 	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
 )
 
-m <- epred_draws(object = model_fits$fit_bcn, newdata = n, ndraws = 50, re_formula = NA) %>% 
-	mutate(.value = logit_to_prob(.epred))
+m <- epred_draws(object = fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
+	mutate(
+		.value = logit_to_prob(.epred),
+		vocab_size_total_center = ifelse(
+			vocab_size_total_center==-1, 
+			"Low vocabulary size (-1 SD)",
+			"High vocabulary size (+1 SD)"
+		)
+	)
 
+# stat_summary(
+# 	aes(group = trial_type, colour = trial_type),
+# 	fun = mean, geom = "line", size = 1.25
+# ) +
+# stat_summary(
+# 	data = gaze, aes(
+# 		x = as.factor(time_bin_center), y = logit_to_prob(logit_adjusted), 
+# 		group = trial_type,
+# 		colour = trial_type
+# 	),
+# 	fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
+# 	position = position_dodge(width = 0.3), inherit.aes = FALSE
+# ) 
 ggplot(m, aes(time_bin_center, .value)) +
-	facet_grid(fct_rev(lp)~age_group) +
+	facet_grid(fct_rev(lp)~vocab_size_total_center) +
 	geom_hline(yintercept = 0.5, colour = "black") +
-	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
+	geom_line(
+		aes(group = interaction(vocab_size_total_center, trial_type, lp, .draw),
 			colour = trial_type),
-			  alpha = 0.15, size = 0.65) +
-	stat_summary(aes(group = trial_type, colour = trial_type),
-				 fun = mean, geom = "line", size = 1.25) +
-	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
-								  colour = trial_type),
-				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
-				 position = position_dodge(width = 0.3)) +
-	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
-			  colour = "white", hjust = 0, size = 5) +
+		alpha = 0.5, size = 0.65
+	) +
+
 	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
 		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_brewer(palette = "Set1") +
-	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
+	ggsci::scale_color_futurama() +
+	scale_x_continuous(
+		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
+		labels = 1:20
+	) +
 	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme_minimal() +
 	theme(
@@
 		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank()
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(fill = "white", colour = NA),
+		plot.background = element_rect(fill = "white", colour = NA)
 	)
+
 ```

### 2022-01-13 presentations/2022-01-25_lacre/2022-01-25_lacre-abstract.Rmd
Sample posterior

--- 2021-12-06 Communications/2022-01-25_lacre/2022-01-25_lacre-abstract.Rmd
@@
 
-Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language [e.g., @costa2000cognate; @thierry2007brain].
-It has been suggested that this parallel activation is already present during toddlerhood [e.g., @von2012language; @jardak2019labels], but it is unclear how this parallel activation impacts the developing lexicon.
-We tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task.
-Participants were tested exclusively in their language of most exposure.
-two pictures were presented side-by-side, one of them was named, and participants' visual preference for the named (target) picture was taken as a proxy of word recognition.
-Each pair of pictures was preceded by the presentation of a silent image (prime).
-We manipulated two variables regarding to the relationship between the label associated to the prime image and the target word: their phonological overlap in the testing language and the cognate status of the prime label.
-This resulted in three types of trials: trials in which prime and target labels shared phonological onset and the prime label was a cognate (cognate trials; e.g., *flower*/*flor*-*bird*, for an English-Spanish participant), trials where prime and target labels shared phonological onset but the prime label was a non-cognate (non-cognate trials; e.g., *chair*/*silla*-*bird*), and trials where prime and target labels did not share phonological onset (unrelated trials; *car*/*coche*-*bird*).
-
-In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset [e.g.; @mani2010infant].
-Under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we further predicted  that interference over target word recognition would be stronger after cognate primes (labels from both languages interfere with target word recognition) than after non-cognate primes (only the label in the target language interferes with target word recognition).
-We tested bilinguals (and same-aged monolingual controls) at three age points (21, 25, and 30 months) to investigate how any cross-language priming effect emerged or changed across these ages, capitalising on the potential role of vocabulary size.
-Preliminary data suggest that bilinguals were almost insensitive to the phonological similarity between the prime and the spoken target word, or to the cognate status of the prime label.
-Surprisingly, monolinguals' preference for the target picture at 25 was stronger after non-cognate primes, compared to cognate primes or unrelated primes, and also after cognate and non-cognate primes compared to unrelated primes.
-We present this preliminary data along with exploratory analyses addressing the puzzling pattern of results we observed.
-
-![](img/gca.png)
+Previous studies suggest that bilinguals access their lexicon in a language non-selective way: recognising and producing words in one language activates word representations in the other [e.g., @costa2000cognate; @thierry2007brain].
+This parallel activation of both languages seems to be already present during toddlerhood [e.g., @von2012language], but its impact on the developing lexicon remains unclear.
+We investigated this issue by testing bilingual toddlers in a primed word recognition task adapted from @mani2010infant.
+In each trial, participants were first presented with a prime picture in silence.
+Then, two more pictures were presented side by side, and one of them (target picture) was named in participants' dominant language.
+We registered participants' looking preference for the target picture as an indicator of word recognition.
+We designed three types of trials by manipulating the phonological overlap between the prime and the target labels (at word onset), and the cognate status of the prime label.
+Following @mani2010infant's findings, we expected participants to generate an implicit label for the prime picture, which should interfere with the recognition of the subsequent recognition of the target word if both labels share phonological overlap.
+Under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we further predicted that interference would be stronger after cognate primes (labels from both languages overlap with the target word) than after non-cognate primes (only the label in the language of test overlaps with the target word).
+We tested bilingual toddlers (and same-aged monolingual controls) at three age points (21, 25, and 30 months) to investigate how parallel activation of both languages emerged or changed across these ages, capitalising on the potential role of vocabulary size.
+We present preliminary data from this ongoing study, and discuss the potential implications of the current collected data on out hypotheses.

### 2022-01-13 docs/02_vocabulary.Rmd
Add both models

@@
 	knitr.duplicate.label = "allow",
-	ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
-	ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
+	ggplot2.discrete.fill = ggsci::pal_futurama()(7),
+	ggplot2.discrete.slab_color = ggsci::pal_futurama()(7),
+	ggplot2.discrete.colour = ggsci::pal_futurama()(7)
 )
@@
 	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
+	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1]) %>% 
+	filter(location=="Barcelona")
 ```
@@
 
+sample_size_lp <- participants %>% 
+	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	count(age_group, lp, location) %>% 
+	mutate(
+		age_group = case_when(
+			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
+			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
+			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
+		)
+	)
+
 # vocabulary
 participants %>% 
+	mutate(
+		age_group = case_when(
+			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
+			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
+			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
+		)
+	) %>% 
 	drop_na(lp) %>%
@@
 	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "white") +
+	facet_wrap(~age_group, scales = "free_x") +
+	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
+	stat_pointinterval(
+		aes(lp, vocab_size_l1, group = lp),
+		position = position_nudge(x = 0.2),
+		.width = c(0.95, 0.89, 0.50),
+		point_size = 3
+	) +
 	geom_point(
-		aes(lp, vocab_size_l1),
-		shape = 1, colour = "white", size = 1, stroke = 1,
+		aes(lp, vocab_size_l1, color = lp),
+		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
 		position = position_jitter(width = 0.1, seed = 888)
 	) +
-	geom_boxplot(
-		aes(lp, vocab_size_l1, fill = lp),
-		width = 0.25, outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
+	geom_text(
+		data = sample_size_lp,
+		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
+		show.legend = FALSE, position = position_dodge(width = 2)
 	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
+	labs(
+		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
+		title = "Total vocabulary size",
+		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
 	) +
-	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
+	guides(colour = "none") +
+	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
 	scale_y_continuous(limits = c(0, 1), labels = percent) +
@@
 		legend.title = element_blank(),
-		legend.position = "none",
-		panel.grid.major.y = element_blank(),
+		legend.position = "top",
+		panel.grid.major.x = element_blank(),
 		axis.title.x = element_blank(),
@@
 sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	filter(valid_participant, !is.na(vocab_size_total)) %>% 
 	count(age_group, location)
+
+sample_size_lp <- participants %>% 
+	filter(valid_participant, !is.na(vocab_size_total)) %>% 
+	count(age_group, lp, location) %>% 
+	mutate(
+		age_group = case_when(
+			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
+			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
+			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
+		)
+	)
 
@@
 participants %>% 
-	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
+	mutate(
+		age_group = case_when(
+			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
+			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
+			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
+		)
+	) %>% 
 	drop_na(lp) %>%
@@
 	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
+	facet_wrap(~age_group, scales = "free_x") +
+	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
+	stat_pointinterval(
+		aes(lp, vocab_size_total, group = lp),
+		position = position_nudge(x = 0.2),
+		.width = c(0.95, 0.89, 0.50),
+		point_size = 3
+	) +
 	geom_point(
-		aes(lp, vocab_size_total),
-		shape = 1, colour = "white", size = 1, stroke = 1,
+		aes(lp, vocab_size_total, color = lp),
+		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
 		position = position_jitter(width = 0.1, seed = 888)
 	) +
-	geom_boxplot(
-		aes(lp, vocab_size_total, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
+	geom_text(
+		data = sample_size_lp,
+		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
+		show.legend = FALSE, position = position_dodge(width = 2)
 	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
+	labs(
+		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
+		title = "L1 vocabulary size",
+		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
 	) +
-	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
+	guides(colour = "none") +
+	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
 	scale_y_continuous(limits = c(0, 1), labels = percent) +
@@
 		legend.title = element_blank(),
-		legend.position = "none",
+		legend.position = "top",
 		panel.grid.major.x = element_blank(),
 		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
+		axis.text = element_text(size = 9)
 	)
@@
 sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	filter(valid_participant, !is.na(vocab_size_conceptual)) %>% 
 	count(age_group, location)
+
+sample_size_lp <- participants %>% 
+	filter(valid_participant, !is.na(vocab_size_total)) %>% 
+	count(age_group, lp, location) %>% 
+	mutate(
+		age_group = case_when(
+			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
+			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
+			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
+		)
+	)
 
@@
 	ggplot() +
-	facet_grid(location~age_group) +
-	# geom_violin(
-	# 	position = position_dodge(width = 0.75),
-	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
-	# ) + 
-	geom_hline(yintercept = 0.5, colour = "grey") +
+	facet_wrap(~age_group, scales = "free_x") +
+	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
+	stat_pointinterval(
+		aes(lp, vocab_size_conceptual, group = lp),
+		position = position_nudge(x = 0.2),
+		.width = c(0.95, 0.89, 0.50),
+		point_size = 3
+	) +
 	geom_point(
-		aes(lp, vocab_size_conceptual),
-		shape = 1, colour = "white", size = 1, stroke = 1,
+		aes(lp, vocab_size_conceptual, color = lp),
+		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
 		position = position_jitter(width = 0.1, seed = 888)
 	) +
-	geom_boxplot(
-		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
-		width = 0.25, fill = "#0D1117", outlier.colour = NA,
-		position = position_dodge(width = 0.75), size = 1
+	geom_text(
+		data = sample_size_lp,
+		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
+		show.legend = FALSE, position = position_dodge(width = 2)
 	) +
-	geom_text(
-		data = sample_size,
-		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
-		colour = "white", fill = "white", show.legend = FALSE
+	labs(
+		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
+		title = "Conceptual vocabulary size",
+		subtitle = "Percentage of lexicalised concepts reported to be understood from the vocabulary checklist"
 	) +
-	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
+	guides(colour = "none") +
+	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
 	scale_y_continuous(limits = c(0, 1), labels = percent) +
@@
 		legend.title = element_blank(),
-		legend.position = "none",
+		legend.position = "top",
+		panel.grid.major.x = element_blank(),
 		axis.title.x = element_blank(),
-		axis.text = element_text(size = 9),
-		panel.grid.major.x = element_blank()
+		axis.text = element_text(size = 9)
 	)

### 2022-01-13 docs/06_results-bcn.Rmd
Add both models

@@
 	knitr.duplicate.label = "allow",
-	ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
-	ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
+	ggplot2.discrete.fill = ggsci::pal_futurama()(7),
+	ggplot2.discrete.colour = ggsci::pal_futurama()(7)
 )
@@
 tar_load(gaze)
-tar_load(fit)
+tar_load(fit_total)
 
@@
 ```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
+str_repl <- c(
+
+	# 3-way interactions
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
+
+	# 2-way interactions
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" =
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" =
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_time_bin_center:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil" =
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Group \u00d7 Vocab (total)",
+
+	# main effects (linear)
+	"b_time_bin_center:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_time_bin_center:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+
+	"b_time_bin_center:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	"b_time_bin_center:vocab_size_total_center" = 
+		"Vocab. (total, +1 SD)",
+	"b_Itime_bin_centerE2:vocab_size_total_center" = 
+		"Vocab. (total, +1 SD)",
+	"b_Itime_bin_centerE3:vocab_size_total_center" = 
+		"Vocab. (total, +1 SD)",
+
+	# 3-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",
+
+	# 2-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab. (total, +1 SD)",
+	"b_trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab. (total, +1 SD)",
+
+	"b_lpLPMonvs.Bil:vocab_size_total_center" =
+		"Group \u00d7 Vocab. (total, +1 SD)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" =
+		"Trial type (C vs. NC)",
+
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	# main linear effects
+	"b_Intercept" = "Intercept",
+	"b_Itime_bin_centerE2" = "Time bin 2",
+	"b_Itime_bin_centerE3" = "Time bin 3",
+	"b_time_bin_center" = "Time bin",
+	"b_vocab_size_total_center" = "Vocab. (total, +1 SD)",
+
+	"b_trial_typePrimeUvs.CPNC" = "Trial type (U vs. C+NC)",
+	"b_trial_typePrimeNCvs.C" = "Trial type (C vs. NC)",
+	"b_lpLPMonvs.Bil" = "Group (Mon. vs. Bil.)",
+
+	# sigma
+	"sigma" = "Sigma"
+)
+
+draws <- gather_draws(fit_total, `b_.*`, `sigma`, regex = TRUE) %>% 
+	mutate(
+		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
+		.variable_name = str_replace_all(.variable, str_repl),
+		type = case_when(
+			str_detect(.variable, "E2") ~ "Quadratic time",
+			str_detect(.variable, "E3") ~ "Cubic time",
+			str_detect(.variable, "time_bin") ~ "Linear time",
+			str_detect(.variable, "sigma") ~ "Error",
+			TRUE ~ "Main effects"
+		) %>% 
+			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
+	)
 
 draws %>% 
-	mean_qi(.width = c(0.95, 0.50)) %>% 
-	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
-	clean_names() %>% 
-	select(-c(point, interval, value_0_5)) %>% 
-	gt(rowname_col = "variable") %>% 
-	fmt_number(2:6) %>% 
-	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
+	group_by(.variable, .variable_name, type) %>% 
+	mean_qi() %>% 
+	select(type, .variable_name, .value, .lower, .upper) %>% 
+	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
+	fmt_percent(3) %>%
+	fmt_number(4:5, scale_by = 100) %>% 
+	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
 	cols_label(
-		variable = md("**Predictor**"),
-		value_0_95 = md("**Mean**"),
-		lower_0_95 = md("**95% CrI**"),
-		lower_0_5 = md("**50% CrI**")
+		.variable_name = md("**Predictor**"),
+		.value = md("**Mean**"),
+		.lower = md("**95% CrI**")
 	) %>% 
@@
 		style = list(
-			cell_fill(color = "#b9fac4")
+			cell_text(weight = "bold", style = "italic")
 		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = lower_0_95 > 0
+		locations = list(
+			cells_row_groups()
 		)
@@
 		style = list(
-			cell_fill(color = "#b9fac4")
+			cell_text(weight = "bold")
 		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = lower_0_5 > 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_95,
-			rows = upper_0_95 < 0
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_fill(color = "#fabfb9")
-		),
-		locations = cells_body(
-			columns = lower_0_5,
-			rows = upper_0_5 < 0
+		locations = list(
+			cells_column_labels()
 		)
@@
 
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=5}
 
-draws %>% 
-	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
-	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
-	ggplot(aes(.value, .variable)) +
-	geom_vline(xintercept = 0, colour = "red", size = 1) +
-	# stat_halfeye(point_color = "black", interval_color = "black") +
-	stat_pointinterval() +
-	labs(x = "Value", y = "Variable", fill = "CrI") +
+draws_intercept <- draws %>% 
+	filter(str_detect(.variable, "Intercept")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5,
+		color = "#FF6F00FF",
+		fill = "#FF6F00FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		title = "Intercept",
+		alpha = "CrI"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent) +
+	scale_x_continuous(labels = percent, limits = c(0, 1))
+
+draws_predictors <- draws %>% 
+	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#C71000FF", 
+		fill = "#C71000FF") +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Main effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2))
+
+draws_time <- draws %>%
+	filter(str_detect(.variable, "time_bin")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	facet_wrap(~type, scales = "free_x") +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#008EA0FF", 
+		fill = "#008EA0FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Polynomial effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent)
+
+draws_sigma <- draws %>% 
+	filter(str_detect(.variable, "sigma")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#8A4198FF", 
+		fill = "#8A4198FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		alpha = "CrI",
+		fill = "CrI", 
+		title = "Error"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(0.92, 0.97))
+
+((draws_intercept / draws_sigma / guide_area()) | draws_predictors) /
+	draws_time + 
+	plot_layout(heights = c(0.5, 0.5)) &
+	guides(fill = "none", color = "none") &
 	theme(
+		panel.background = element_rect(fill = NA, colour = "grey"),
+		axis.text.y = element_text(size = 7),
+		axis.text.x = element_text(size = 7),
 		axis.title = element_blank(),
-		legend.position = "top"
+		legend.position = c(1, 1.2),
+		legend.direction = "horizontal",
+		legend.justification = "right",
+		legend.key.size = unit(0.35, "cm"),
+		legend.text = element_text(size = 7),
+		legend.title = element_text(size = 7),
+		panel.grid.major.y = element_blank()
 	)
@@
 
-vcov(fit) %>% 
-	cov2cor() %>% 
+corr_mat <- VarCorr(fit_total, summary = TRUE)$participant$cor 
+corr_names <- rownames(VarCorr(fit_total, summary = TRUE)$participant$cor)
+
+corr_mat <- corr_mat %>% 
+	as_tibble() %>% 
+	select(matches("Estimate")) %>% 
+	rename_all(str_remove, "Estimate.") %>% 
+	mutate(term1 = corr_names)
+
+corr_mat[lower.tri(corr_mat)] <- NA
+
+corr_data <- corr_mat %>% 
 	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
 	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
-	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
-	geom_tile() +
-	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
-	scale_fill_distiller(limits = c(-1, 1)) +
+	drop_na(.value)
+
+post_cors_participant <- corr_data %>% 
+	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
+	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
+	mutate(
+		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
+		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
+	) %>% 
+	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
+	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
+	geom_tile(na.rm = TRUE) +
+	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
+	labs(
+		x = "Term 1", 
+		y = "Term 2", 
+		fill = "Posterior\ncorrelation",
+		title = "By participant"
+	) +
+	scale_fill_gradient2(
+		low = "#04bf78", mid = "white", high = "#FFC20A", 
+		na.value = "white", limits = c(-0.4, 0.4)
+	) +
+	scale_x_discrete() +
 	coord_equal() +
 	theme(
+		panel.grid = element_blank(),
+		legend.position = c(1, 1),
+		legend.direction = "horizontal",
+		legend.key.height = unit(0.1, "cm"),
+		legend.key.width = unit(0.3, "cm"),
+		legend.justification = c(1, 1),
+		legend.title = element_blank(),
+		legend.text = element_text(size = 5),
+		axis.title.x = element_blank(),
+		axis.title.y = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_text(size = 6, angle = 90, hjust = 0, vjust = 1),
+		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
+	)
+
+# correlations by item
+corr_mat <- VarCorr(fit_total, summary = TRUE)$target$cor 
+corr_names <- rownames(VarCorr(fit_total, summary = TRUE)$target$cor)
+
+corr_mat <- corr_mat %>% 
+	as_tibble() %>% 
+	select(matches("Estimate")) %>% 
+	rename_all(str_remove, "Estimate.") %>% 
+	mutate(term1 = corr_names)
+
+corr_mat[lower.tri(corr_mat)] <- NA
+
+corr_data <- corr_mat %>% 
+	as.data.frame() %>% 
+	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	drop_na(.value)
+
+post_cors_item <- corr_data %>% 
+	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
+	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
+	mutate(
+		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
+		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
+	) %>% 
+	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
+	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
+	geom_tile(na.rm = TRUE) +
+	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
+	labs(
+		x = "Term 1", y = "Term 2", fill = "Posterior\ncorrelation",
+		title = "By item"
+	) +
+	scale_fill_gradient2(
+		low = "#04bf78", mid = "white", high = "#FFC20A", 
+		na.value = "white", limits = c(-0.4, 0.4)
+	) +
+	scale_x_discrete() +
+	coord_equal()
+
+(post_cors_participant | post_cors_item) &
+	plot_layout(guides = "collect") &
+	theme(
+		panel.grid = element_blank(),
 		legend.position = "top",
-		legend.text = element_text(size = 8),
-		axis.title = element_blank(),
-		axis.text.y = element_text(hjust = 1, size = 7),
-		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
+		legend.direction = "horizontal",
+		legend.key.height = unit(0.1, "cm"),
+		legend.key.width = unit(0.3, "cm"),
+		legend.justification = c(1, 1),
+		legend.title = element_blank(),
+		legend.text = element_text(size = 5),
+		axis.title.x = element_blank(),
+		axis.title.y = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1),
+		axis.text.y = element_text(size = 7, vjust = 0, hjust = 0)
 	)
@@
 
-m <- emmeans(fit, ~trial_type:lp, by = "vocab_size_total_center", epred = TRUE) %>% 
+m <- emmeans(fit_total, ~trial_type | lp, epred = TRUE)
+
+m_draws <- gather_emmeans_draws(m) %>% 
 	as_tibble() %>% 
-	clean_names() %>% 
-	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x < 0, 0, x)) %>% 
-	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x > 1, 1, x))
+	mutate_at(vars(.value), function(x) ifelse(x < 0, 0, x)) %>% 
+	mutate_at(vars(.value), function(x) ifelse(x > 1, 1, x))
 
-ggplot(m, aes(vocab_size_total_center, emmean, ymin = lower_hpd, ymax = upper_hpd, colour = trial_type)) +
-	facet_wrap(~lp, ncol = 1) +
-	# geom_line(aes(group = trial_type), size = 1, position = position_dodge(width = 0.25)) +
-	geom_errorbar(size = 1, width = 0, position = position_dodge(width = 0.25)) +
-	geom_point(size = 4, position = position_dodge(width = 0.25)) +
-	labs(x = "Age (months))", y = "P(target)", colour = "Trial type") +
-	scale_y_continuous(limits = c(0, 1), labels = percent)  +
+ggplot(m_draws, aes(.value, trial_type, colour = trial_type, fill = trial_type)) +
+	facet_wrap(~lp) +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		position = position_nudge(y = 0.05)
+	) +
+	stat_pointinterval(
+		color = "black",
+	) +
+	labs(
+		x = "Expected posterior mean PTLT", y = "Trial type",
+		colour = "Trial type", fill = "Trial type",
+		alpha = "CrI"
+	) +
+	guides(color = "none", fill = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_x_continuous(limits = c(0.5, 1), labels = percent)  +
 	theme(
-		legend.title = element_blank(),
-		legend.position = "top"
+		axis.title.y = element_blank(),
+		legend.position = "right",
+		panel.grid.major.y = element_blank(),
+		panel.grid.minor.y = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(fill = NA, colour = "grey")
 	)
@@
 
-m <- epred_draws(object = fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
+m <- epred_draws(object = fit_total, newdata = n, ndraws = 50, re_formula = NA) %>% 
 	mutate(
@@
 		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	ggsci::scale_color_futurama() +
+	scale_color_futurama() +
 	scale_x_continuous(

### 2022-01-13 _targets_packages.R

@@ -11,6 +11,7 @@ library(eyetrackingR)
 library(forcats)
 library(future)
 library(ggplot2)
+library(ggsci)
 library(googlesheets4)
 library(gt)
 library(here)
@@ -36,6 +37,7 @@ library(shinyWidgets)
 library(stringr)
 library(tarchetypes)
 library(targets)
+library(testthat)
 library(tibble)
 library(tidybayes)
 library(tidyr)

### 2022-01-17 docs/02_vocabulary.Rmd
Add L1 model

@@
 tar_load_globals()
-tar_load(vocabulary)
-tar_load(attrition)
-tar_load(participants)
+tar_load_all()
 
@@
 ```
+
+# Results
+
+## Model comparison
+
+## Model outputs
+
+```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+str_repl <- c(
+
+	# 3-way interactions
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
+
+	# 2-way interactions
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" =
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" =
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_time_bin_center:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil" =
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Group \u00d7 Vocab (total)",
+
+	# main effects (linear)
+	"b_time_bin_center:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_time_bin_center:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+
+	"b_time_bin_center:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	"b_time_bin_center:vocab_size_total_center" = 
+		"Vocab. (total, +1 SD)",
+	"b_Itime_bin_centerE2:vocab_size_total_center" = 
+		"Vocab. (total, +1 SD)",
+	"b_Itime_bin_centerE3:vocab_size_total_center" = 
+		"Vocab. (total, +1 SD)",
+
+	# 3-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",
+
+	# 2-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab. (total, +1 SD)",
+	"b_trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab. (total, +1 SD)",
+
+	"b_lpLPMonvs.Bil:vocab_size_total_center" =
+		"Group \u00d7 Vocab. (total, +1 SD)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" =
+		"Trial type (C vs. NC)",
+
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	# main linear effects
+	"b_Intercept" = "Intercept",
+	"b_Itime_bin_centerE2" = "Time bin 2",
+	"b_Itime_bin_centerE3" = "Time bin 3",
+	"b_time_bin_center" = "Time bin",
+	"b_vocab_size_total_center" = "Vocab. (total, +1 SD)",
+
+	"b_trial_typePrimeUvs.CPNC" = "Trial type (U vs. C+NC)",
+	"b_trial_typePrimeNCvs.C" = "Trial type (C vs. NC)",
+	"b_lpLPMonvs.Bil" = "Group (Mon. vs. Bil.)",
+
+	# sigma
+	"sigma" = "Sigma"
+)
+
+draws <- gather_draws(fit_total, `b_.*`, `sigma`, regex = TRUE) %>% 
+	mutate(
+		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
+		.variable_name = str_replace_all(.variable, str_repl),
+		type = case_when(
+			str_detect(.variable, "E2") ~ "Quadratic time",
+			str_detect(.variable, "E3") ~ "Cubic time",
+			str_detect(.variable, "time_bin") ~ "Linear time",
+			str_detect(.variable, "sigma") ~ "Error",
+			TRUE ~ "Main effects"
+		) %>% 
+			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
+	)
+
+draws %>% 
+	group_by(.variable, .variable_name, type) %>% 
+	mean_qi() %>% 
+	select(type, .variable_name, .value, .lower, .upper) %>% 
+	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
+	fmt_percent(3) %>%
+	fmt_number(4:5, scale_by = 100) %>% 
+	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		.variable_name = md("**Predictor**"),
+		.value = md("**Mean**"),
+		.lower = md("**95% CrI**")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_text(weight = "bold", style = "italic")
+		),
+		locations = list(
+			cells_row_groups()
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_text(weight = "bold")
+		),
+		locations = list(
+			cells_column_labels()
+		)
+	) %>% 
+	as_raw_html()
+```
+
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=5}
+
+draws_intercept <- draws %>% 
+	filter(str_detect(.variable, "Intercept")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5,
+		color = "#FF6F00FF",
+		fill = "#FF6F00FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		title = "Intercept",
+		alpha = "CrI"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(0, 1))
+
+draws_predictors <- draws %>% 
+	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#C71000FF", 
+		fill = "#C71000FF") +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Main effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2))
+
+draws_time <- draws %>%
+	filter(str_detect(.variable, "time_bin")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	facet_wrap(~type, scales = "free_x") +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#008EA0FF", 
+		fill = "#008EA0FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Polynomial effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent)
+
+draws_sigma <- draws %>% 
+	filter(str_detect(.variable, "sigma")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#8A4198FF", 
+		fill = "#8A4198FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		alpha = "CrI",
+		fill = "CrI", 
+		title = "Error"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(0.92, 0.97))
+
+((draws_intercept / draws_sigma / guide_area()) | draws_predictors) /
+	draws_time + 
+	plot_layout(heights = c(0.5, 0.5)) &
+	guides(fill = "none", color = "none") &
+	theme(
+		panel.background = element_rect(fill = NA, colour = "grey"),
+		axis.text.y = element_text(size = 7),
+		axis.text.x = element_text(size = 7),
+		axis.title = element_blank(),
+		legend.position = c(1, 1.2),
+		legend.direction = "horizontal",
+		legend.justification = "right",
+		legend.key.size = unit(0.35, "cm"),
+		legend.text = element_text(size = 7),
+		legend.title = element_text(size = 7),
+		panel.grid.major.y = element_blank()
+	)
+
+```

### 2022-01-17 docs/06_results-bcn.Rmd
Add L1 model

@@
 tar_load_globals()
-tar_load(participants)
-tar_load(attrition)
-tar_load(vocabulary)
-tar_load(gaze)
-tar_load(fit_total)
+tar_load_all()
 
@@
 
-#### Fixed effects
+# Model comparison
+
+```{model-comparison}
+
+waics %>% 
+	map("estimates") %>% 
+	map(function(x) as.data.frame(x) %>% rownames_to_column("variable")) %>% 
+	bind_rows(.id = "model") %>%
+	clean_names() %>% 
+	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
+	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
+	gt() %>% 
+	fmt_number(-model) %>% 
+	tab_spanner("WAIC", matches("waic")) %>% 
+	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
+	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
+	cols_label(
+		model = "Model",
+		estimate_elpd_waic = "Estimate",
+		estimate_waic = "Estimate",
+		estimate_p_waic = "Estimate",
+		se_elpd_waic = md("*SE*"),
+		se_waic = md("*SE*"),
+		se_p_waic = md("*SE*"),
+	)
+
+```
+
+# Model with total vocabulary
+
+## Fixed effects
 
@@
 	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
-	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
-		size = 0.5, 
+	# stat_slab(
+	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+	# 	size = 0.5, 
+	# 	color = "#008EA0FF", 
+	# 	fill = "#008EA0FF"
+	# ) +
+	stat_pointinterval(
 		color = "#008EA0FF",
-		fill = "#008EA0FF"
+		fill = "#008EA0FF",
+		point_size = 1.5
 	) +
@@
 
-#### Random effects
+## Random effects
 
@@
 
-#### Marginal means {.tabset }
+## Margin means
 
-##### Marginal to time course
+### Prior predictions (before seeing the data)
+
+```{r gaze_time_prior, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant) %>% 
+	count(lp, vocab_size_total_center)
+
+n <- expand_grid(
+	lp = c("Monolingual", "Bilingual"),
+	vocab_size_total_center = c(-1, 1),
+	trial_type = unique(gaze$trial_type),
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
+)
+
+m <- epred_draws(object = fit_prior, newdata = n, ndraws = 50, re_formula = NA) %>% 
+	mutate(
+		.value = logit_to_prob(.epred),
+		vocab_size_total_center = ifelse(
+			vocab_size_total_center==-1, 
+			"Low vocabulary size (-1 SD)",
+			"High vocabulary size (+1 SD)"
+		)
+	)
+
+ggplot(m, aes(time_bin_center, .value)) +
+	facet_grid(fct_rev(lp)~vocab_size_total_center) +
+	geom_hline(yintercept = 0.5, colour = "black") +
+	geom_line(
+		aes(group = interaction(vocab_size_total_center, trial_type, lp, .draw),
+			colour = trial_type),
+		alpha = 0.5, size = 0.65
+	) +
+
+	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
+		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
+	scale_color_futurama() +
+	scale_x_continuous(
+		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
+		labels = 1:20
+	) +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme_minimal() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 7),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(fill = "white", colour = NA),
+		plot.background = element_rect(fill = "white", colour = NA)
+	)
+
+```
+
+### Posterior predictions (after seeing the data)
+
+```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant) %>% 
+	count(lp, vocab_size_total_center)
+
+n <- expand_grid(
+	lp = c("Monolingual", "Bilingual"),
+	vocab_size_total_center = c(-1, 1),
+	trial_type = unique(gaze$trial_type),
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
+)
+
+m <- epred_draws(object = fit_total, newdata = n, ndraws = 50, re_formula = NA) %>% 
+	mutate(
+		.value = logit_to_prob(.epred),
+		vocab_size_total_center = ifelse(
+			vocab_size_total_center==-1, 
+			"Low vocabulary size (-1 SD)",
+			"High vocabulary size (+1 SD)"
+		)
+	)
+
+ggplot(m, aes(time_bin_center, .value)) +
+	facet_grid(fct_rev(lp)~vocab_size_total_center) +
+	geom_hline(yintercept = 0.5, colour = "black") +
+	geom_line(
+		aes(group = interaction(vocab_size_total_center, trial_type, lp, .draw),
+			colour = trial_type),
+		alpha = 0.5, size = 0.65
+	) +
+	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
+		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
+	scale_color_futurama() +
+	scale_x_continuous(
+		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
+		labels = 1:20
+	) +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme_minimal() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 7),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(fill = "white", colour = NA),
+		plot.background = element_rect(fill = "white", colour = NA)
+	)
+
+```
+
+## Marginal means {.tabset }
 
@@
 
-##### Time course
+# Model with L1 vocabulary
+
+## Fixed effects
+
+```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+str_repl <- c(
+
+	# 3-way interactions
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",
+
+	# 2-way interactions
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_l1_center" =
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" =
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_time_bin_center:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Group \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil" =
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Group \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Group \u00d7 Vocab (L1)",
+
+	# main effects (linear)
+	"b_time_bin_center:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_time_bin_center:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+
+	"b_time_bin_center:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	"b_time_bin_center:vocab_size_l1_center" = 
+		"Vocab. (L1, +1 SD)",
+	"b_Itime_bin_centerE2:vocab_size_l1_center" = 
+		"Vocab. (L1, +1 SD)",
+	"b_Itime_bin_centerE3:vocab_size_l1_center" = 
+		"Vocab. (L1, +1 SD)",
+
+	# 3-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab. (L1, +1 SD)",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab. (L1, +1 SD)",
+
+	# 2-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab. (L1, +1 SD)",
+	"b_trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab. (L1, +1 SD)",
+
+	"b_lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Group \u00d7 Vocab. (L1, +1 SD)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" =
+		"Trial type (C vs. NC)",
+
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	# main linear effects
+	"b_Intercept" = "Intercept",
+	"b_Itime_bin_centerE2" = "Time bin 2",
+	"b_Itime_bin_centerE3" = "Time bin 3",
+	"b_time_bin_center" = "Time bin",
+	"b_vocab_size_l1_center" = "Vocab. (L1, +1 SD)",
+
+	"b_trial_typePrimeUvs.CPNC" = "Trial type (U vs. C+NC)",
+	"b_trial_typePrimeNCvs.C" = "Trial type (C vs. NC)",
+	"b_lpLPMonvs.Bil" = "Group (Mon. vs. Bil.)",
+
+	# sigma
+	"sigma" = "Sigma"
+)
+
+draws <- gather_draws(fit_l1, `b_.*`, `sigma`, regex = TRUE) %>% 
+	mutate(
+		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
+		.variable_name = str_replace_all(.variable, str_repl),
+		type = case_when(
+			str_detect(.variable, "E2") ~ "Quadratic time",
+			str_detect(.variable, "E3") ~ "Cubic time",
+			str_detect(.variable, "time_bin") ~ "Linear time",
+			str_detect(.variable, "sigma") ~ "Error",
+			TRUE ~ "Main effects"
+		) %>% 
+			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
+	)
+
+draws %>% 
+	group_by(.variable, .variable_name, type) %>% 
+	mean_qi() %>% 
+	select(type, .variable_name, .value, .lower, .upper) %>% 
+	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
+	fmt_percent(3) %>%
+	fmt_number(4:5, scale_by = 100) %>% 
+	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		.variable_name = md("**Predictor**"),
+		.value = md("**Mean**"),
+		.lower = md("**95% CrI**")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_text(weight = "bold", style = "italic")
+		),
+		locations = list(
+			cells_row_groups()
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_text(weight = "bold")
+		),
+		locations = list(
+			cells_column_labels()
+		)
+	) %>% 
+	as_raw_html()
+```
+
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=5}
+
+draws_intercept <- draws %>% 
+	filter(str_detect(.variable, "Intercept")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5,
+		color = "#FF6F00FF",
+		fill = "#FF6F00FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		title = "Intercept",
+		alpha = "CrI"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(0, 1))
+
+draws_predictors <- draws %>% 
+	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#C71000FF", 
+		fill = "#C71000FF") +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Main effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2))
+
+draws_time <- draws %>%
+	filter(str_detect(.variable, "time_bin")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	facet_wrap(~type, scales = "free_x") +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	# stat_slab(
+	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+	# 	size = 0.5, 
+	# 	color = "#008EA0FF", 
+	# 	fill = "#008EA0FF"
+	# ) +
+	stat_pointinterval(
+		color = "#008EA0FF",
+		fill = "#008EA0FF",
+		point_size = 1.5
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Polynomial effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent)
+
+draws_sigma <- draws %>% 
+	filter(str_detect(.variable, "sigma")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#8A4198FF", 
+		fill = "#8A4198FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		alpha = "CrI",
+		fill = "CrI", 
+		title = "Error"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(0.92, 0.97))
+
+((draws_intercept / draws_sigma / guide_area()) | draws_predictors) /
+	draws_time + 
+	plot_layout(heights = c(0.5, 0.5)) &
+	guides(fill = "none", color = "none") &
+	theme(
+		panel.background = element_rect(fill = NA, colour = "grey"),
+		axis.text.y = element_text(size = 7),
+		axis.text.x = element_text(size = 7),
+		axis.title = element_blank(),
+		legend.position = c(1, 1.2),
+		legend.direction = "horizontal",
+		legend.justification = "right",
+		legend.key.size = unit(0.35, "cm"),
+		legend.text = element_text(size = 7),
+		legend.title = element_text(size = 7),
+		panel.grid.major.y = element_blank()
+	)
+
+```
+
+## Random effects
+
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+corr_mat <- VarCorr(fit_l1, summary = TRUE)$participant$cor 
+corr_names <- rownames(VarCorr(fit_l1, summary = TRUE)$participant$cor)
+
+corr_mat <- corr_mat %>% 
+	as_tibble() %>% 
+	select(matches("Estimate")) %>% 
+	rename_all(str_remove, "Estimate.") %>% 
+	mutate(term1 = corr_names)
+
+corr_mat[lower.tri(corr_mat)] <- NA
+
+corr_data <- corr_mat %>% 
+	as.data.frame() %>% 
+	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	drop_na(.value)
+
+post_cors_participant <- corr_data %>% 
+	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
+	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
+	mutate(
+		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
+		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
+	) %>% 
+	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
+	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
+	geom_tile(na.rm = TRUE) +
+	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
+	labs(
+		x = "Term 1", 
+		y = "Term 2", 
+		fill = "Posterior\ncorrelation",
+		title = "By participant"
+	) +
+	scale_fill_gradient2(
+		low = "#04bf78", mid = "white", high = "#FFC20A", 
+		na.value = "white", limits = c(-0.4, 0.4)
+	) +
+	scale_x_discrete() +
+	coord_equal() +
+	theme(
+		panel.grid = element_blank(),
+		legend.position = c(1, 1),
+		legend.direction = "horizontal",
+		legend.key.height = unit(0.1, "cm"),
+		legend.key.width = unit(0.3, "cm"),
+		legend.justification = c(1, 1),
+		legend.title = element_blank(),
+		legend.text = element_text(size = 5),
+		axis.title.x = element_blank(),
+		axis.title.y = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_text(size = 6, angle = 90, hjust = 0, vjust = 1),
+		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
+	)
+
+# correlations by item
+corr_mat <- VarCorr(fit_l1, summary = TRUE)$target$cor 
+corr_names <- rownames(VarCorr(fit_l1, summary = TRUE)$target$cor)
+
+corr_mat <- corr_mat %>% 
+	as_tibble() %>% 
+	select(matches("Estimate")) %>% 
+	rename_all(str_remove, "Estimate.") %>% 
+	mutate(term1 = corr_names)
+
+corr_mat[lower.tri(corr_mat)] <- NA
+
+corr_data <- corr_mat %>% 
+	as.data.frame() %>% 
+	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	drop_na(.value)
+
+post_cors_item <- corr_data %>% 
+	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
+	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
+	mutate(
+		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
+		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
+	) %>% 
+	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
+	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
+	geom_tile(na.rm = TRUE) +
+	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
+	labs(
+		x = "Term 1", y = "Term 2", fill = "Posterior\ncorrelation",
+		title = "By item"
+	) +
+	scale_fill_gradient2(
+		low = "#04bf78", mid = "white", high = "#FFC20A", 
+		na.value = "white", limits = c(-0.4, 0.4)
+	) +
+	scale_x_discrete() +
+	coord_equal()
+
+(post_cors_participant | post_cors_item) &
+	plot_layout(guides = "collect") &
+	theme(
+		panel.grid = element_blank(),
+		legend.position = "top",
+		legend.direction = "horizontal",
+		legend.key.height = unit(0.1, "cm"),
+		legend.key.width = unit(0.3, "cm"),
+		legend.justification = c(1, 1),
+		legend.title = element_blank(),
+		legend.text = element_text(size = 5),
+		axis.title.x = element_blank(),
+		axis.title.y = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1),
+		axis.text.y = element_text(size = 7, vjust = 0, hjust = 0)
+	)
+
+```
+
+## Margin means
+
+### Posterior predictions (after seeing the data)
 
@@
 	filter(valid_participant) %>% 
-	count(lp, vocab_size_total_center)
+	count(lp, vocab_size_l1_center)
 
@@
 	lp = c("Monolingual", "Bilingual"),
-	vocab_size_total_center = c(-1, 1),
+	vocab_size_l1_center = c(-1, 1),
 	trial_type = unique(gaze$trial_type),
@@
 
-m <- epred_draws(object = fit_total, newdata = n, ndraws = 50, re_formula = NA) %>% 
+m <- epred_draws(object = fit_l1, newdata = n, ndraws = 50, re_formula = NA) %>% 
 	mutate(
 		.value = logit_to_prob(.epred),
-		vocab_size_total_center = ifelse(
-			vocab_size_total_center==-1, 
+		vocab_size_l1_center = ifelse(
+			vocab_size_l1_center==-1, 
 			"Low vocabulary size (-1 SD)",
@@
 
-# stat_summary(
-# 	aes(group = trial_type, colour = trial_type),
-# 	fun = mean, geom = "line", size = 1.25
-# ) +
-# stat_summary(
-# 	data = gaze, aes(
-# 		x = as.factor(time_bin_center), y = logit_to_prob(logit_adjusted), 
-# 		group = trial_type,
-# 		colour = trial_type
-# 	),
-# 	fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
-# 	position = position_dodge(width = 0.3), inherit.aes = FALSE
-# ) 
 ggplot(m, aes(time_bin_center, .value)) +
-	facet_grid(fct_rev(lp)~vocab_size_total_center) +
+	facet_grid(fct_rev(lp)~vocab_size_l1_center) +
 	geom_hline(yintercept = 0.5, colour = "black") +
 	geom_line(
-		aes(group = interaction(vocab_size_total_center, trial_type, lp, .draw),
+		aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
 			colour = trial_type),
@@
 	) +
-
 	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
@@
 		legend.title = element_blank(),
-		axis.text.x = element_text(size = 9),
+		axis.text.x = element_text(size = 7),
 		panel.grid.major.x = element_blank(),
@@
 ```
+
+## Marginal means {.tabset }
+
+```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+m <- emmeans(fit_l1, ~trial_type | lp, epred = TRUE)
+
+m_draws <- gather_emmeans_draws(m) %>% 
+	as_tibble() %>% 
+	mutate_at(vars(.value), function(x) ifelse(x < 0, 0, x)) %>% 
+	mutate_at(vars(.value), function(x) ifelse(x > 1, 1, x))
+
+ggplot(m_draws, aes(.value, trial_type, colour = trial_type, fill = trial_type)) +
+	facet_wrap(~lp) +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		position = position_nudge(y = 0.05)
+	) +
+	stat_pointinterval(
+		color = "black",
+	) +
+	labs(
+		x = "Expected posterior mean PTLT", y = "Trial type",
+		colour = "Trial type", fill = "Trial type",
+		alpha = "CrI"
+	) +
+	guides(color = "none", fill = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_x_continuous(limits = c(0.5, 1), labels = percent)  +
+	theme(
+		axis.title.y = element_blank(),
+		legend.position = "right",
+		panel.grid.major.y = element_blank(),
+		panel.grid.minor.y = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(fill = NA, colour = "grey")
+	)
+
+```

### 2022-01-17 presentations/2022-01-25_lacre/2021-01-25_lacre.Rmd
Add L1 model

--- 2021-12-06 Communications/2022-01-25_lacre/2021-01-25_lacre.Rmd
@@
 ```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-library(gt)
-library(tibble)
-library(ggplot2)
-library(tidyr)
-library(dplyr)
-library(tidybayes)
-library(stringr)
-library(forcats)
-library(targets)
-library(scales)
-library(here)
 
-source(here::here("R", "utils.R"))
-
-tar_load(participants)
-tar_load(attrition)
-tar_load(gaze)
-tar_load(model_fits)
-
-# withr::with_dir("../..", tar_load(participants))
-# withr::with_dir("../..", tar_load(attrition))
-# withr::with_dir("../..", tar_load(gaze))
-# withr::with_dir("../..", tar_load(model_fits))
-
-fit <- model_fits$fit
+tar_load_globals()
+tar_load_all()
 
@@
 
+### Total vocabulary model
+
 ```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(fit, `b_.*`, `sigma`, regex = TRUE)
+draws <- gather_draws(fit_total, `b_.*`, `sigma`, regex = TRUE)
 
@@
 	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5),
+	vocab_size_total_center = c(-1, 0, 1)
 )
 
-m <- epred_draws(object = fit, newdata = n, ndraws = 20, re_formula = NA) %>% 
+m <- epred_draws(object = fit_total, newdata = n, ndraws = 20, re_formula = NA) %>% 
 	mutate(.value = logit_to_prob(.epred))
@@
 ggplot(m, aes(time_bin_center, .value)) +
-	facet_wrap(~fct_rev(lp)) +
+	facet_wrap(vocab_size_total_center ~ fct_rev(lp)) +
 	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
@@
 			  alpha = 0.15, size = 0.65) +
-	stat_summary(aes(group = trial_type, colour = trial_type),
-				 fun = mean, geom = "line", size = 1.25) +
-	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
-								  colour = trial_type),
-				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
-				 position = position_dodge(width = 0.3)) +
+	# stat_summary(aes(group = trial_type, colour = trial_type),
+	# 			 fun = mean, geom = "line", size = 1.25) +
+	# stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
+	# 							  colour = trial_type),
+	# 			 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
+	# 			 position = position_dodge(width = 0.3)) +
 	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),

### 2022-01-17 presentations/2022-01-25_lacre/2022-01-25_lacre-abstract.Rmd
Add L1 model

@@
 ---
-title: "LACRE 2022: abstract"
+title: "Parallel activation and the developing bilingual lexicon: a longitudinal study on word recognition"
 author: "Gonzalo García-Castro"
@@
 output:
-  word_document: 
-    reference_docx: "manuscript_template.docx"
+  pdf_document:
+    latex_engine: xelatex
 bibliography: "../../references.bib"
@@
 In each trial, participants were first presented with a prime picture in silence.
-Then, two more pictures were presented side by side, and one of them (target picture) was named in participants' dominant language.
-We registered participants' looking preference for the target picture as an indicator of word recognition.
-We designed three types of trials by manipulating the phonological overlap between the prime and the target labels (at word onset), and the cognate status of the prime label.
-Following @mani2010infant's findings, we expected participants to generate an implicit label for the prime picture, which should interfere with the recognition of the subsequent recognition of the target word if both labels share phonological overlap.
+Then, two more pictures were presented side by side, and one of them (target picture) was named in participants’ dominant language.
+We registered participants’ looking preference for the target picture as an indicator of word recognition.
+We manipulated the phonological overlap between the prime and the target labels, and the cognate status of the prime label.
+This allowed us to test whether bilingual toddlers generated an implicit label for the prime picture (presented in silence), and whether they did so in only the language of test, or in both languages.
+Following Mani and Plunkett’s findings, we expected participants to generate an implicit label for the prime picture, which should interfere with the subsequent recognition of the target word when both labels share phonological overlap.
 Under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we further predicted that interference would be stronger after cognate primes (labels from both languages overlap with the target word) than after non-cognate primes (only the label in the language of test overlaps with the target word).
-We tested bilingual toddlers (and same-aged monolingual controls) at three age points (21, 25, and 30 months) to investigate how parallel activation of both languages emerged or changed across these ages, capitalising on the potential role of vocabulary size.
-We present preliminary data from this ongoing study, and discuss the potential implications of the current collected data on out hypotheses.
+We tested bilingual toddlers and same-aged monolingual controls at three age points: 21, 25, and 30 months to investigate if and how parallel activation of both languages emerged or changed across these ages.
+We present preliminary data from this ongoing study and discuss the potential theoretical implications of the data collected so far.
+
+## References

### 2022-01-17 docs/06_results-bcn.Rmd
Add L1 model

@@
 
-```{model-comparison}
+```{r model-comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 
@@
 		se_p_waic = md("*SE*"),
-	)
+	) %>% 
+	as_raw_html()
 
@@
 
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=5}
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}
 

### 2022-01-17 docs/06_results-bcn.Rmd
Change fig size"

@@
 
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, fig.width=8}
 
@@
 
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=5,fig.height=5}
 

### 2022-01-17 docs/06_results-bcn.Rmd
Change fig size"

--- 2022-01-17 docs/06_results-bcn.Rmd
@@
 
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, fig.width=5}
 
@@
 	scale_x_discrete() +
-	coord_equal()
+	coord_equal()  +
+	theme(
+		axis.text.y = element_blank()
+	)
 
@@
 
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4,fig.height=5}
 
@@
 	scale_x_discrete() +
-	coord_equal()
+	coord_equal() +
+	theme(
+		axis.text.y = element_blank()
+	)
 

### 2022-01-17 docs/06_results-bcn.Rmd
Change fig size"

@@
 
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, fig.width=5}
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, fig.height=4}
 
@@
 	theme(
-		panel.grid = element_blank(),
-		legend.position = c(1, 1),
-		legend.direction = "horizontal",
-		legend.key.height = unit(0.1, "cm"),
-		legend.key.width = unit(0.3, "cm"),
-		legend.justification = c(1, 1),
-		legend.title = element_blank(),
-		legend.text = element_text(size = 5),
-		axis.title.x = element_blank(),
-		axis.title.y = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_text(size = 6, angle = 90, hjust = 0, vjust = 1),
 		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
@@
 		axis.ticks = element_blank(),
-		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1),
-		axis.text.y = element_text(size = 7, vjust = 0, hjust = 0)
+		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)
 	)
@@
 
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4,fig.height=5}
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8,fig.height=4}
 
@@
 	theme(
-		panel.grid = element_blank(),
-		legend.position = c(1, 1),
-		legend.direction = "horizontal",
-		legend.key.height = unit(0.1, "cm"),
-		legend.key.width = unit(0.3, "cm"),
-		legend.justification = c(1, 1),
-		legend.title = element_blank(),
-		legend.text = element_text(size = 5),
-		axis.title.x = element_blank(),
-		axis.title.y = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_text(size = 6, angle = 90, hjust = 0, vjust = 1),
-		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
+		axis.text.y = element_text(size = 7)
 	)
@@
 		axis.ticks = element_blank(),
-		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1),
-		axis.text.y = element_text(size = 7, vjust = 0, hjust = 0)
+		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)
+
 	)

### 2022-01-20 docs/00_participants.Rmd
Model comparisons with simpler models

@@
 ```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
+participants_tab <- participants %>% 
 	left_join(distinct(attrition, participant, valid_participant)) %>% 
@@
 		`30 months` = md("**30 months**")
-	) %>% 
-	as_raw_html()
+	)
+
+gtsave(participants_tab, here("img", "participants_tab.png"))
+as_raw_html(participants_tab)
 ```

### 2022-01-20 docs/02_vocabulary.Rmd
Model comparisons with simpler models

@@
 sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	filter(
+		participant %in% fit_l1_4$data$participant
+	) %>% 
 	count(age_group, location)
@@
 sample_size_lp <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
+	filter(
+		participant %in% fit_l1_4$data$participant
+	) %>% 
 	count(age_group, lp, location) %>% 
@@
 		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
-		title = "Total vocabulary size",
-		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
+		title = "L1 vocabulary size",
+		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
 	) +
@@
 
+ggsave(here("img", "vocab_l1.png"))
+
 ```
@@
 sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_total)) %>% 
+	filter(participant %in% fit_total_4$data$participant) %>% 
 	count(age_group, location)
@@
 sample_size_lp <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_total)) %>% 
+	filter(participant %in% fit_total_4$data$participant) %>% 
 	count(age_group, lp, location) %>% 
@@
 	labs(
-		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
-		title = "L1 vocabulary size",
-		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
+		y = "Receptive vocabulary (total)", colour = "Group", fill = "Group",
+		title = "Total vocabulary size",
+		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
 	) +
@@
 
+ggsave(here("img", "vocab_total.png"))
 ```
@@
 
-draws <- gather_draws(fit_total, `b_.*`, `sigma`, regex = TRUE) %>% 
+draws <- gather_draws(fit_total_4, `b_.*`, `sigma`, regex = TRUE) %>% 
 	mutate(

### 2022-01-20 docs/06_results-bcn.Rmd
Model comparisons with simpler models

@@
 
-waics %>% 
+model_comparison <- waics_l1 %>% 
 	map("estimates") %>% 
@@
 	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
+	mutate(model = str_replace_all(model, c("fit_l1_4" = "L1 vocab.", "fit_total_4" = "Total vocab."))) %>% 
 	gt() %>% 
@@
 	) %>% 
-	as_raw_html()
+	tab_style(
+		cell_text(weight = "bold"),
+		cells_column_spanners()
+	) %>% 
+	tab_style(
+		cell_text(style = "italic"),
+		cells_column_labels()
+	)
+
+gtsave(model_comparison, here("img", "model_comparison.png"))
+
+as_raw_html(model_comparison)
 
@@
 	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(0.95, 0.8, 0.5), labels = percent_format()))),
 		size = 0.5,
@@
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(0, 1))
+	scale_x_continuous(labels = percent, limits = c(0, 1)) +
+	theme(
+		axis.title.y = element_blank()
+	)
 
@@
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2))
+	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2)) +
+	theme(
+		axis.title.y = element_blank()
+	)
 
@@
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent)
+	scale_x_continuous(labels = percent) +
+	theme(
+		axis.title.y = element_blank()
+	)
 
@@
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(0.92, 0.97))
+	scale_x_continuous(labels = percent, limits = c(0.92, 0.97)) +
+	theme(
+		axis.title.y = element_blank()
+	)
 
@@
 
-corr_mat <- VarCorr(fit_total, summary = TRUE)$participant$cor 
-corr_names <- rownames(VarCorr(fit_total, summary = TRUE)$participant$cor)
+corr_mat <- VarCorr(fit_total_4, summary = TRUE)$participant$cor 
+corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$participant$cor)
 
@@
 # correlations by item
-corr_mat <- VarCorr(fit_total, summary = TRUE)$target$cor 
-corr_names <- rownames(VarCorr(fit_total, summary = TRUE)$target$cor)
+corr_mat <- VarCorr(fit_total_4, summary = TRUE)$target$cor 
+corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$target$cor)
 
@@
 
-m <- epred_draws(object = fit_prior, newdata = n, ndraws = 50, re_formula = NA) %>% 
+m <- epred_draws(object = fit_prior_l1_prior, newdata = n, ndraws = 50, re_formula = NA) %>% 
 	mutate(
@@
 
-m <- epred_draws(object = fit_total, newdata = n, ndraws = 50, re_formula = NA) %>% 
+m <- epred_draws(object = fit_total_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
 	mutate(
@@
 
-m <- emmeans(fit_total, ~trial_type | lp, epred = TRUE)
+m <- emmeans(fit_total_4, ~trial_type | lp, epred = TRUE)
 
@@
 
-draws <- gather_draws(fit_l1, `b_.*`, `sigma`, regex = TRUE) %>% 
+draws <- gather_draws(fit_l1_4, `b_.*`, `sigma`, regex = TRUE) %>% 
 	mutate(
@@
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(0, 1))
+	scale_x_continuous(labels = percent, limits = c(0, 1)) +
+	theme(
+		panel.grid.major.y = element_blank()
+	)
+
+ggsave(here("img", "posterior_intercept_l1.png"), draws_intercept, height = 2, width = 7)
 
@@
 		color = "#C71000FF", 
-		fill = "#C71000FF") +
+		fill = "#C71000FF"
+	) +
 	labs(
@@
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2))
+	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2)) +
+	theme(
+		panel.grid.major.y = element_blank()
+	)
+
+ggsave(here("img", "posterior_predictors_l1.png"), draws_predictors, height = 7, width = 7)
 
@@
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent)
+	scale_x_continuous(labels = percent) +
+	theme(
+		panel.grid.major.y = element_blank(),
+		panel.border = element_rect(fill = NA, colour = "grey"),
+		axis.title = element_blank()
+	)
+
+ggsave(here("img", "posterior_poly_l1.png"), draws_time, height = 7, width = 9)
 
@@
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(0.92, 0.97))
+	scale_x_continuous(labels = percent, limits = c(0.92, 0.96)) +
+	theme(
+		panel.grid.major.y = element_blank()
+	)
+
+ggsave(here("img", "posterior_sigma_l1.png"), draws_sigma, height = 2, width = 7)
 
@@
 
-corr_mat <- VarCorr(fit_l1, summary = TRUE)$participant$cor 
-corr_names <- rownames(VarCorr(fit_l1, summary = TRUE)$participant$cor)
+corr_mat <- VarCorr(fit_l1_4, summary = TRUE)$participant$cor 
+corr_names <- rownames(VarCorr(fit_l1_4, summary = TRUE)$participant$cor)
 
@@
 # correlations by item
-corr_mat <- VarCorr(fit_l1, summary = TRUE)$target$cor 
-corr_names <- rownames(VarCorr(fit_l1, summary = TRUE)$target$cor)
+corr_mat <- VarCorr(fit_l1_4, summary = TRUE)$target$cor 
+corr_names <- rownames(VarCorr(fit_l1_4, summary = TRUE)$target$cor)
 
@@
 
-m <- epred_draws(object = fit_l1, newdata = n, ndraws = 50, re_formula = NA) %>% 
+m <- epred_draws(object = fit_l1_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
 	mutate(
@@
 
+ggsave(here("img", "epreds_l1.pdf"), dpi = 1000)
+
 ```
@@
 
-m <- emmeans(fit_l1, ~trial_type | lp, epred = TRUE)
+m <- emmeans(fit_l1_4, ~trial_type | lp, epred = TRUE)
 

### 2022-01-20 presentations/2022-01-25_lacre/2022-01-25_lacre.Rmd
Model comparisons with simpler models

---
author: "Gonzalo García-Castro"
date: "25/01/2021"
output: html_document
bibliography: "../../references.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_futurama()(7),
	ggplot2.discrete.colour = ggsci::pal_futurama()(7)
)

```

```{r params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# load objects
tar_load_globals()
tar_load_all()

theme_set(theme_minimal()) # in utils.R

attrition <- attrition %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_vocab ~ "Invalid vocabulary",
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))

participants <- participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(
		vocab_size_l1_center = scale(vocab_size_l1)[,1],
		vocab_size_total_center = scale(vocab_size_total)[,1]
	)

```

## Background

Infants learning two languages face the challenge of having to learn two distinct sets of words. Some of the words across both languages refer to similar concepts: for instance, *chair* and *silla* (in Spanish). These pairs of words are called *translation equivalents*. Sometimes, translation equivalents also overlap in form, frequently due to their shared etymological origin. These form-similar translation equivalents, such as *boot* and *bota* (in Spanish), are referred to as *cognates*.

There is extensive literature on how cognateness impacts the dynamics of lexical access during words comprehension and production. One of its main findings is that bilinguals process cognates (such as *boot* and *bota*) more differently than non-cognates (such as *chair* and *silla*). For instance, @costa2000cognate asked Spanish-Catalan bilinguals to name a series of familiar pictures in Spanish. Part of the pictures referred to objects whose labels in Spanish and Catalan were cognates, whereas the other pictures referred to non-cognates. On average, participants named cognate pictures faster than non-cognate pictures. This effect was independent of lexical frequency and, critically, was not observed when Spanish monolinguals performed the same task. This suggests that bilinguals activated labels in both languages, and that their phonology interacted to facilitate naming.

Later studies provided evidence that the locus of this facilitation effect was at the lexical level, and not just at the articulatory level [reference needed here]: this effect has also been reported during comprehension, at both the visual-orthographic and the auditory-phonology modalities) [e.g., @thierry2007brain]. Overall, these findings have led researchers to hypothesise that lexical access is language-non selective, that is, bilinguals activate lexical representations in both languages in parallel during comprehension and production, based on their semantic and phonological overlap.

This cross-talk between languages has also been suggested to be present in children's and toddlers' lexicon [@von2012language; @bosma2020cognate], but it is still unclear how it impacts the trajectories of language acquisition at these early ages. In this study we sought to investigate the developmental trajectories of lexical access in a cohort of Catalan-Spanish and English-Spanish bilinguals.

To do this, we used an adaptation of @mani2010infant's priming paradigm. This paradigm consists of a spoken word recognition task in which participants are first presented with a picture in silence in the centre of the screen for 1.5 seconds. Then, two other pictures are presented side-by-side during 2 seconds, and one of them is named. The other is not. Looking times to the target picture are recorded from name onset. From now on, I will refer to the silent picture presented first as the *prime*, to the named picture as the *target*, and to the non-named picture presented next to the target as *distractor*.

In their experiment, Mani and Plunkett manipulated the phonological overlap between the prime label and the target label: in some trials, both labels shared phonological onset (*bee*-*ball*), whereas in other trials they did not share phonological onset (*cow*-*book*). In all trials, the distractor label did not share onset with either of the prime or target labels (e.g., *teeth*). The authors registered 18 month-old participants' looking preference for the target object after name onset, as a proxy of word recognition, and found that target preference was stronger after a phonologically related prime than after a phonologically unrelated prime. There results have three main implications:

1) Phonologically related prime pictures facilitated target recognition
2) This is only possible if participants lexicalised the prime pictures, even though this picture was presented in silence
3) The label participants generated upon prime picture presentation was phonologically detailed, and this phonological form interacted with the auditory recognition of a subsequently presented word

In a subsequent study, the authors found the inverse effect in 24 month-old toddlers: target looking preference was weaker after a phonologically related prime picture compared to after an unrelated one [@mani2011phonological]. The authors suggested that the change in the direction of the effect observed between 18 and 24 month-old participants was due to the increment in vocabulary size and the establishment of (inhibitory) links between phonologically related lexical entries that might have occurred between both ages. Supporting this account, the inhibition effect they reported was stronger as the number of phonological neighbours of the target increased: the recognition of words surrounded by more phonologically related neighbours suffered the most from the priming effect.

We adapted this paradigm to test the language-non selectivity account in bilingual toddlers. Following Mani & Plunkett's original implementation, In our task half of the prime-target pairs in the trial lists shared phonological onset, and the other half did not share phonological onset. We added a novel manipulation: half of the primes in the phonologically related condition were cognates and the other half were non-cognates. We classified two translation equivalents as cognates if they shared phonological onset. Here is an illustration of each trial type:

```{r trials, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

design <- tribble(
	~trial_type, ~prime, ~target, ~distractor,
	"Cognate (N = 8)", "flower (flor)", "fork", "balloon",
	"Non-cognate (N = 8)", "tree (árbol)", "truck", "phone",
	"Unrelated (N = 16)", "penguin (pingüino)", "table", "shoe"
) %>% 
	gt() %>% 
	cols_label(
		trial_type = "Prime type",
		prime = "Prime",
		target = "Target",
		distractor = "Distractor"

	)

gtsave(design, here("presentations", "2022-01-25_lacre", "img", "design.png"))
```

This is what a trial looks like [see figure below]:

![](img/task.png)

## Hypotheses

If participants lexicalise the prime pictures in a language-non selective way, they should generate two labels upon prime picture presentation: one in each language. Therefore, if lexical access is language non-selective, in cognate trials two prime labels should interfere with target recognition (since both prime labels share onset with the target). In non-cognate trials, only one prime label should interfere with the target. Finally, in unrelated trials no prime labels should interfere with the target. As a result, we expect bilingual participants' target looking preference to be weaker in cognate trials than in non-cognate trials, and in cognate and non-cognate trials than in unrelated trials.

![](img/diagram.png)

We also collected data from same-aged monolingual participants as a control group: in this group we also expect to find weaker target looking in cognate and non-cognate trials, compared to unrelated trials, but no differences between cognate and non-cognate trials (these participants should be insensitive to the cognate status of the primes).

## Participants

We planned to collect data from participants learning English and/or Spanish in Oxford, and from participants learning Catalan and/or Spanish in Barcelona. Due to limitations imposed by the pandemic and lockdown, data collection in Oxford was severely interrupted, so I will present preliminary data from participants tested in Barcelona exclusively.

We tested participants at three age points: 21, 25, and 30 months, to explore their trajectories of lexical access through these sensitive ages in which participants' vocabulary size is growing a full speed [Reference here.]

We classified participants as monolinguals or bilinguals by estimating their overall exposure to each of their languages using @bosch2001evidence. Following the consensus reached by the ManyBabies consortium [@byers2021multilab], participants exposed to any languages more than 80% of the time were classified as monolinguals. Otherwise, participants were classified as bilinguals. Participants exposed more than 10% to a third language or a language other than Catalan and Spanish (in Barcelona) or English and Spanish (in Oxford) were excluded from data analysis.

This is how testing sessions are distributed across ages and language profiles:

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants_data <- fit_l1$data %>% 
	distinct(participant, lp) %>% 
	left_join(select(participants, participant, age_group, lp, test_language, vocab_size_total, vocab_size_l1))

participants_design <- participants_data %>% 
	count(participant, lp, name = "n_sessions") %>% 
	mutate(is_longitudinal = n_sessions > 1) %>% 
	left_join(select(participants_data, participant, age_group, lp)) %>% 
	count(age_group, lp, is_longitudinal, name ="n_longitudinal") %>% 
	filter(is_longitudinal)

participants_tab <- participants_data %>% 
	count(age_group, lp) %>%
	left_join(participants_design) %>% 
	filter(is_longitudinal) %>% 
	mutate(n_label = paste0(n, " (", n_longitudinal, ")")) %>% 
	select(age_group, lp, n_label) %>% 
	pivot_wider(names_from = age_group, values_from = n_label) %>% 
	rowwise() %>% 
	# mutate(N = sum(`n_21 months`, `n_25 months`, `n_30 months`)) %>% 
	ungroup() %>% 
	relocate(lp) %>% 
	gt() %>% 
	cols_label(lp = "Group") %>% 
	# summary_rows(columns = 2:4, fns = list(N = "sum"), decimals = 0)
	tab_source_note(md("(*) The number of longitudinal participants in each <br>group is indicated between parentheses.")) %>% 
	tab_style(
		cell_text(weight = "bold"),
		cells_column_labels()
	)

gtsave(participants_tab, here("presentations", "2022-01-25_lacre", "img", "participants_tab.png"))

n_total <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	distinct(participant) %>% 
	count()

n_total_cohort <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	distinct(participant, age_group) %>%
	count(participant) %>% 
	count(n, name = "n_cohort") %>% 
	group_split(n)

```

These 156 testing sessions correspond to `r n_total$n` distinct participants. Of these participants, `r n_total_cohort[[1]]` only participated once (I will refer top these participants as cross-sectional participants), `r n_total_cohort[[2]]` participated twice, and `r n_total_cohort[[3]]` participated three times.

## Vocabulary

```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(participant %in% fit_total$data$participant) %>% 
	count(age_group, location)

sample_size_lp <- participants %>% 
	filter(participant %in% fit_total$data$participant) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		lp_label = paste0(lp, " (N = ", n, ")"),
		age_group_label = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	select(participant, lp, age_group, vocab_size_l1, vocab_size_total) %>% 
	pivot_longer(c(vocab_size_l1, vocab_size_total), names_to = "measure", values_to = "value") %>% 
	left_join(sample_size_lp) %>% 
	mutate(
		measure = str_replace_all(measure, c("vocab_size_l1" = "L1", "vocab_size_total" = "Total"))
	) %>% 
	ggplot() +
	aes(lp, value, color = lp, fill = lp) +
	facet_grid(measure~age_group) +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(position = position_dodge(width = 0.75), slab_color = "white", slab_size = 1) +
	# geom_violin(position = position_dodge(width = 1)) +
	stat_pointinterval(
		position = position_dodge(width = 0.75),
		.width = c(0.95, 0.89, 0.50),
		point_size = 2,
		color = "black"
	) +
	# geom_point(
	# 	size = 1,
	# 	alpha = 0.5
	# ) +
	# geom_text(
	# 	data = sample_size_lp,
	# 	aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
	# 	show.legend = FALSE, position = position_dodge(width = 2),
	# 	inherit.aes = FALSE
	# ) +
	labs(
		y = "Receptive vocabulary", colour = "Group", fill = "Group",
		title = "Vocabulary size",
		subtitle = "Percentage of words reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = c(0.5, 0.6),
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9),
		panel.border = element_rect(fill = NA, color = "grey")
	)

ggsave(here("presentations", "2022-01-25_lacre", "img", "vocab_all.png"), dpi = 600)
```

## Data analysis

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
n_obs <- nrow(fit_l1$data)

n_trials_total <- distinct(fit_l1$data, participant, target, trial_type) %>% 
	count() %>% 
	pull(n)

n_trials <- distinct(gaze, participant, trial, trial_type) %>% 
	count(trial_type) %>% 
	pull(n, name = trial_type)
```

```{r participants_lp, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

participants_data

```

In each testing session, participants were presented with 32 trials (8 cognate, 8 non-cognate and 16 unrelated). In each trial, we used an eye-tracker to register participants' looking time to the target picture. We delimited a time window of interest between 250 ms after the target onset and 150 ms before the target offset. This resulted in a 1,500 ms long time window. We divided this time window into 15 time bins of 100 ms each, and calculated the adjusted logit of the samples in which participants' gaze was located in the target coordinates, out of the total of valid samples in that time bin. This resulted in 15 observations per participant, per age group, and per trial. Our final dataset comprised `r n_obs` data points from `r n_trials_total` distinct trials: `r n_trials["Cognate"]`, cognate trials, `r n_trials["Non-cognate"]` trials, and `r n_trials["Unrelated"]` trials.

To model these data we used Growth Curve Analysis [@mirman2017growth]. First, we included `time_bin` as a fixed effect in our model to account for the correlation between the data points collected within each trial. We included this variable as a third degree polynomial, in order to account for the possibly non-linearity of the target fixations across the same trial (target fixations might increase rapidly at the beginning of the trial and decrease at the end of it. We then included our predictors of interest: age group (`age_group`), language profile (`lp`), trial type (`trial_type`), and the two-way interaction between language profile and trial type. Finally, we added random intercepts and slopes by participant and by target picture, to account for the possible correlation between time series from the same participant or trial (more details of the model at the end).

We estimated our model using the Bayesian framework, under which we estimate the probability of each value of the sampling space of each parameter, given the data we have observed. to do this, we used the brms R package [@burkner2017brms].

# Results

## Model comparison

```{r model-comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

waics %>% 
	map("estimates") %>% 
	map(function(x) as.data.frame(x) %>% rownames_to_column("variable")) %>% 
	bind_rows(.id = "model") %>%
	clean_names() %>% 
	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
	gt() %>% 
	fmt_number(-model) %>% 
	tab_spanner("WAIC", matches("waic")) %>% 
	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
	cols_label(
		model = "Model",
		estimate_elpd_waic = "Estimate",
		estimate_waic = "Estimate",
		estimate_p_waic = "Estimate",
		se_elpd_waic = md("*SE*"),
		se_waic = md("*SE*"),
		se_p_waic = md("*SE*"),
	) %>% 
	as_raw_html()

```

## Fixed effects

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
str_repl <- c(

	# 3-way interactions
	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",

	# 2-way interactions
	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (L1)",

	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",
	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_l1_center" =
		"Trial type (C vs. NC) \u00d7 Vocab (L1)",

	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" =
		"Trial type (U vs. C+NC) \u00d7 Group",  
	"b_time_bin_center:lpLPMonvs.Bil:vocab_size_l1_center" =
		"Group \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",
	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil" =
		"Trial type (C vs. NC) \u00d7 Group",

	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",  
	"b_Itime_bin_centerE2:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Group \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",  
	"b_Itime_bin_centerE3:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Group \u00d7 Vocab (L1)",

	# main effects (linear)
	"b_time_bin_center:trial_typePrimeUvs.CPNC" =
		"Trial type (U vs. C+NC)",
	"b_time_bin_center:trial_typePrimeNCvs.C" = 
		"Trial type (C vs. NC)",
	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC" = 
		"Trial type (U vs. C+NC)",
	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C" = 
		"Trial type (C vs. NC)",
	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" = 
		"Trial type (U vs. C+NC)",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" = 
		"Trial type (C vs. NC)",

	"b_time_bin_center:lpLPMonvs.Bil" = 
		"Group (Mon. vs. Bil.)",
	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
		"Group (Mon. vs. Bil.)",
	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
		"Group (Mon. vs. Bil.)",

	"b_time_bin_center:vocab_size_l1_center" = 
		"Vocab. (L1, +1 SD)",
	"b_Itime_bin_centerE2:vocab_size_l1_center" = 
		"Vocab. (L1, +1 SD)",
	"b_Itime_bin_centerE3:vocab_size_l1_center" = 
		"Vocab. (L1, +1 SD)",

	# 3-way interaction linear effects
	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab. (L1, +1 SD)",
	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" =
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab. (L1, +1 SD)",

	# 2-way interaction linear effects
	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",
	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

	"b_trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab. (L1, +1 SD)",
	"b_trial_typePrimeNCvs.C:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab. (L1, +1 SD)",

	"b_lpLPMonvs.Bil:vocab_size_l1_center" =
		"Group \u00d7 Vocab. (L1, +1 SD)",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" =
		"Trial type (U vs. C+NC)",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" =
		"Trial type (C vs. NC)",

	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
		"Group (Mon. vs. Bil.)",

	# main linear effects
	"b_Intercept" = "Intercept",
	"b_Itime_bin_centerE2" = "Time bin 2",
	"b_Itime_bin_centerE3" = "Time bin 3",
	"b_time_bin_center" = "Time bin",
	"b_vocab_size_l1_center" = "Vocab. (L1, +1 SD)",

	"b_trial_typePrimeUvs.CPNC" = "Trial type (U vs. C+NC)",
	"b_trial_typePrimeNCvs.C" = "Trial type (C vs. NC)",
	"b_lpLPMonvs.Bil" = "Group (Mon. vs. Bil.)",

	# sigma
	"sigma" = "Sigma"
)

draws <- gather_draws(fit_l1, `b_.*`, `sigma`, regex = TRUE) %>% 
	mutate(
		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
		.variable_name = str_replace_all(.variable, str_repl),
		type = case_when(
			str_detect(.variable, "E2") ~ "Quadratic time",
			str_detect(.variable, "E3") ~ "Cubic time",
			str_detect(.variable, "time_bin") ~ "Linear time",
			str_detect(.variable, "sigma") ~ "Error",
			TRUE ~ "Main effects"
		) %>% 
			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
	)

```

```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}

draws_intercept <- draws %>% 
	filter(str_detect(.variable, "Intercept")) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, slab_size = 1,
		color = "white",
		fill = "#FF6F00FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		title = "Intercept",
		alpha = "CrI"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		axis.title.y = element_blank(),
		panel.grid.major.y = element_blank()
	)

ggsave(
	here("presentations", "2022-01-25_lacre", "img", "post_intercept.png"), 
	draws_intercept, 
	height = 2,
	width = 7,
	dpi = 600
)

predictors_order <- c(
	"Trial type (U vs. C+NC)",
	"Trial type (C vs. NC)",
	"Group (Mon. vs. Bil.)",
	"Vocab. (total, +1 SD)",
	"Trial type (U vs. C+NC) × Group",
	"Trial type (C vs. NC) × Group",
	"Trial type (U vs. C+NC) × Vocab. (total, +1 SD)",
	"Trial type (C vs. NC) × Vocab. (total, +1 SD)",
	"Group × Vocab. (total, +1 SD)",
	"Trial type (U vs. C+NC) × Group × Vocab. (total, +1 SD)",
	"Trial type (C vs. NC) × Group × Vocab. (total, +1 SD)"
)

draws_predictors <- draws %>% 
	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
	mutate(.variable_name = factor(.variable_name, levels = predictors_order, ordered = TRUE)) %>% 
	ggplot(aes(.value, fct_rev(.variable_name))) +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(0.95, 0.8, 0.5), labels = percent_format()))),
		size = 0.5, 
		color = "white", 
		fill = "#C71000FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Main effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(-0.4, 0.4)) +
	theme(
		axis.title.y = element_blank(),
		panel.grid.major.y = element_blank()
	)

ggsave(
	here("presentations", "2022-01-25_lacre", "img", "post_predictors.png"), 
	draws_predictors, 
	height = 7,
	width = 7,
	dpi = 600
)

predictors_order <- c(
	"Time bin",
	"Time bin 2",
	"Time bin 3",
	"Trial type (U vs. C+NC)",
	"Trial type (C vs. NC)",
	"Group (Mon. vs. Bil.)",
	"Vocab. (total, +1 SD)",
	"Trial type (U vs. C+NC) × Group",
	"Trial type (C vs. NC) × Group",
	"Trial type (U vs. C+NC) × Vocab (total)",
	"Trial type (C vs. NC) × Vocab (total)",
	"Group × Vocab (total)",
	"Trial type (U vs. C+NC) × Group × Vocab (total)",
	"Trial type (C vs. NC) × Group × Vocab (total)"
)

draws_time <- draws %>%
	filter(str_detect(.variable, "time_bin")) %>% 
	mutate(.variable_name = factor(.variable_name, levels = predictors_order, ordered = TRUE)) %>%
	ggplot(aes(.value, fct_rev(.variable_name))) +
	facet_wrap(~type, scales = "free_x") +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	stat_interval(size = 3, labels = percent_format()) +
	# stat_pointinterval(
	# 	color = "#008EA0FF",
	# 	fill = "#008EA0FF",
	# 	point_size = 1.5
	# ) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		color = "CrI",
		alpha = "CrI",
		title = "Polynomial effects"
	) +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_color_manual(values = c("#b7eded", "#4cb0b0", "#007373"), ) +
	scale_x_continuous(labels = percent) +
	theme(
		axis.title.y = element_blank(),
		panel.grid.major.y = element_blank(),
		panel.border = element_rect(fill = NA, color = "grey")
	)

ggsave(
	here("presentations", "2022-01-25_lacre", "img", "post_poly.png"), 
	draws_time, 
	height = 5,
	width = 9,
	dpi = 600
)

draws_sigma <- draws %>% 
	filter(str_detect(.variable, "sigma")) %>% 
	ggplot(aes(.value, .variable_name)) +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#8A4198FF", 
		fill = "#8A4198FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		alpha = "CrI",
		fill = "CrI", 
		title = "Error"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0.92, 0.97)) +
	theme(
		axis.title.y = element_blank(),
		panel.grid.major.y = element_blank()

	)

ggsave(
	here("presentations", "2022-01-25_lacre", "img", "post_sigma.png"), 
	draws_sigma, 
	height = 2,
	width = 7,
	dpi = 600
)

((draws_intercept / draws_sigma / guide_area()) | draws_predictors) /
	draws_time + 
	plot_layout(heights = c(0.5, 0.5)) &
	guides(fill = "none", color = "none") &
	theme(
		panel.background = element_rect(fill = NA, colour = "grey"),
		axis.text.y = element_text(size = 7),
		axis.text.x = element_text(size = 7),
		axis.title = element_blank(),
		legend.position = c(1, 1.2),
		legend.direction = "horizontal",
		legend.justification = "right",
		legend.key.size = unit(0.35, "cm"),
		legend.text = element_text(size = 7),
		legend.title = element_text(size = 7),
		panel.grid.major.y = element_blank()
	)

```

## Margin means

### Posterior predictions (after seeing the data)

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, fig.width=11}
sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(lp, vocab_size_l1_center)

n <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	vocab_size_l1_center = c(-1, 0, 1),
	trial_type = unique(gaze$trial_type),
	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
)

m <- epred_draws(object = fit_l1, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_l1_center = case_when(
			vocab_size_l1_center==-1 ~ "Low vocabulary size (-1 SD)",
			vocab_size_l1_center==1 ~ "High vocabulary size (+1 SD)",
			vocab_size_l1_center==0 ~ "Mean vocabulary size (0 SD)"
		) %>% 
			factor(levels = c(
				"Low vocabulary size (-1 SD)",
				"Mean vocabulary size (0 SD)",
				"High vocabulary size (+1 SD)"
			), ordered = TRUE)
	)

ggplot(m, aes(time_bin_center, .value)) +
	facet_grid(fct_rev(lp)~vocab_size_l1_center) +
	geom_hline(yintercept = 0.5, colour = "black") +
	geom_line(
		aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
			colour = trial_type),
		alpha = 0.5, size = 0.65
	) +
	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_futurama() +
	scale_x_continuous(
		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
		labels = 1:20
	) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme_minimal() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 7),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = "white", colour = NA),
		plot.background = element_rect(fill = "white", colour = NA)
	)

```

## Marginal means {.tabset }

```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, fig.width=9}

m <- emmeans(fit_l1, ~trial_type | lp, epred = TRUE)

m_draws <- gather_emmeans_draws(m) %>% 
	mutate(.value = logit_to_prob(.value)) %>% 
	as_tibble() %>% 
	mutate_at(vars(.value), function(x) ifelse(x < 0, 0, x)) %>% 
	mutate_at(vars(.value), function(x) ifelse(x > 1, 1, x))

ggplot(m_draws, aes(.value, trial_type, colour = trial_type, fill = trial_type)) +
	facet_wrap(~fct_rev(lp)) +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		color = "white"
	) +
	stat_pointinterval(
		color = "black", 
		position = position_dodge(width = 0.5)
	) +
	labs(
		x = "Expected posterior mean PTLT", y = "Trial type",
		colour = "Trial type", fill = "Trial type",
		alpha = "CrI"
	) +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_x_continuous(limits = c(0.6, 0.8), labels = percent)  +
	theme(
		axis.title.y = element_blank(),
		legend.position = "right",
		panel.grid.major.y = element_blank(),
		panel.grid.minor.y = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = NA, colour = "grey")
	)

```

### 2022-02-11 docs/06_results.Rmd
Relocate files

@@
 tar_load_globals()
-tar_load(participants)
-tar_load(attrition)
-tar_load(vocabulary)
-tar_load(gaze)
-tar_load(model_fits)
+tar_load_all()
 
@@
 
-#### Fixed effects
+# Model comparison
+
+```{r model-comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+model_comparison <- waics_l1 %>% 
+	map("estimates") %>% 
+	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
+	bind_rows(.id = "model") %>%
+	clean_names() %>% 
+	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
+	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
+	mutate(
+		model = c(
+			"Intercept",
+			"... + Trial type",
+			"... + Group \u00d7Trial type\u00d7Group",
+			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
+			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
+		)
+	) %>% 
+	gt() %>% 
+	fmt_number(-model) %>% 
+	tab_spanner("WAIC", matches("waic")) %>% 
+	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
+	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
+	cols_label(
+		model = "Model",
+		estimate_elpd_waic = "Estimate",
+		estimate_waic = "Estimate",
+		estimate_p_waic = "Estimate",
+		se_elpd_waic = md("*SE*"),
+		se_waic = md("*SE*"),
+		se_p_waic = md("*SE*"),
+	) %>% 
+	cols_align("right", "model") %>% 
+	tab_style(
+		cell_text(weight = "bold"),
+		cells_column_spanners()
+	) %>% 
+	tab_style(
+		cell_text(style = "italic"),
+		cells_column_labels()
+	)
+
+gtsave(model_comparison, here("img", "model_comparison.png"))
+
+as_raw_html(model_comparison)
+
+```
+
+# Model with total vocabulary
+
+## Fixed effects
 
 ```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-draws <- gather_draws(model_fits$fit, `b_.*`, `sigma`, regex = TRUE)
+str_repl <- c(
+
+	# 3-way interactions
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
+
+	# 2-way interactions
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" =
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" =
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_time_bin_center:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil" =
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Group \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (total)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil:vocab_size_total_center" = 
+		"Group \u00d7 Vocab (total)",
+
+	# main effects (linear)
+	"b_time_bin_center:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_time_bin_center:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+
+	"b_time_bin_center:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	"b_time_bin_center:vocab_size_total_center" = 
+		"Vocab. (total, +1 SD)",
+	"b_Itime_bin_centerE2:vocab_size_total_center" = 
+		"Vocab. (total, +1 SD)",
+	"b_Itime_bin_centerE3:vocab_size_total_center" = 
+		"Vocab. (total, +1 SD)",
+
+	# 3-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" =
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",
+
+	# 2-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab. (total, +1 SD)",
+	"b_trial_typePrimeNCvs.C:vocab_size_total_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab. (total, +1 SD)",
+
+	"b_lpLPMonvs.Bil:vocab_size_total_center" =
+		"Group \u00d7 Vocab. (total, +1 SD)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" =
+		"Trial type (C vs. NC)",
+
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	# main linear effects
+	"b_Intercept" = "Intercept",
+	"b_Itime_bin_centerE2" = "Time bin 2",
+	"b_Itime_bin_centerE3" = "Time bin 3",
+	"b_time_bin_center" = "Time bin",
+	"b_vocab_size_total_center" = "Vocab. (total, +1 SD)",
+
+	"b_trial_typePrimeUvs.CPNC" = "Trial type (U vs. C+NC)",
+	"b_trial_typePrimeNCvs.C" = "Trial type (C vs. NC)",
+	"b_lpLPMonvs.Bil" = "Group (Mon. vs. Bil.)",
+
+	# sigma
+	"sigma" = "Sigma"
+)
+
+draws <- gather_draws(fit_total_4, `b_.*`, `sigma`, regex = TRUE) %>% 
+	mutate(
+		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
+		.variable_name = str_replace_all(.variable, str_repl),
+		type = case_when(
+			str_detect(.variable, "E2") ~ "Quadratic time",
+			str_detect(.variable, "E3") ~ "Cubic time",
+			str_detect(.variable, "time_bin") ~ "Linear time",
+			str_detect(.variable, "sigma") ~ "Error",
+			TRUE ~ "Main effects"
+		) %>% 
+			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
+	)
 
 draws %>% 
-	mean_qi(.width = c(0.95, 0.50)) %>% 
-	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
-	clean_names() %>% 
-	select(-c(point, interval, value_0_5)) %>% 
-	gt(rowname_col = "variable") %>% 
-	fmt_number(2:6) %>% 
-	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
+	group_by(.variable, .variable_name, type) %>% 
+	mean_qi() %>% 
+	select(type, .variable_name, .value, .lower, .upper) %>% 
+	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
+	fmt_percent(3) %>%
+	fmt_number(4:5, scale_by = 100) %>% 
+	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
 	cols_label(
-		variable = md("**Predictor**"),
-		value_0_95 = md("**Mean**"),
-		lower_0_95 = md("**95% CrI**"),
-		lower_0_5 = md("**50% CrI**")
+		.variable_name = md("**Predictor**"),
+		.value = md("**Mean**"),
+		.lower = md("**95% CrI**")
 	) %>% 
@@
 
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}
 
-draws %>% 
-	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
-	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
-	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
-	geom_vline(xintercept = 0, colour = "black") +
-	stat_halfeye(point_color = "black", interval_color = "black") +
-	labs(x = "Value", y = "Variable", fill = "CrI") +
+draws_intercept <- draws %>% 
+	filter(str_detect(.variable, "Intercept")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(0.95, 0.8, 0.5), labels = percent_format()))),
+		size = 0.5,
+		color = "#FF6F00FF",
+		fill = "#FF6F00FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		title = "Intercept",
+		alpha = "CrI"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(0, 1)) +
 	theme(
+		axis.title.y = element_blank()
+	)
+
+draws_predictors <- draws %>% 
+	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#C71000FF", 
+		fill = "#C71000FF") +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Main effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2)) +
+	theme(
+		axis.title.y = element_blank()
+	)
+
+draws_time <- draws %>%
+	filter(str_detect(.variable, "time_bin")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	facet_wrap(~type, scales = "free_x") +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	# stat_slab(
+	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+	# 	size = 0.5, 
+	# 	color = "#008EA0FF", 
+	# 	fill = "#008EA0FF"
+	# ) +
+	stat_pointinterval(
+		color = "#008EA0FF",
+		fill = "#008EA0FF",
+		point_size = 1.5
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Polynomial effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent) +
+	theme(
+		axis.title.y = element_blank()
+	)
+
+draws_sigma <- draws %>% 
+	filter(str_detect(.variable, "sigma")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#8A4198FF", 
+		fill = "#8A4198FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		alpha = "CrI",
+		fill = "CrI", 
+		title = "Error"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(0.92, 0.97)) +
+	theme(
+		axis.title.y = element_blank()
+	)
+
+((draws_intercept / draws_sigma / guide_area()) | draws_predictors) /
+	draws_time + 
+	plot_layout(heights = c(0.5, 0.5)) &
+	guides(fill = "none", color = "none") &
+	theme(
+		panel.background = element_rect(fill = NA, colour = "grey"),
+		axis.text.y = element_text(size = 7),
+		axis.text.x = element_text(size = 7),
 		axis.title = element_blank(),
-		legend.position = "top"
+		legend.position = c(1, 1.2),
+		legend.direction = "horizontal",
+		legend.justification = "right",
+		legend.key.size = unit(0.35, "cm"),
+		legend.text = element_text(size = 7),
+		legend.title = element_text(size = 7),
+		panel.grid.major.y = element_blank()
 	)
@@
 
-#### Random effects
+## Random effects
 
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, fig.height=4}
 
-vcov(model_fits$fit) %>% 
-	cov2cor() %>% 
+corr_mat <- VarCorr(fit_total_4, summary = TRUE)$participant$cor 
+corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$participant$cor)
+
+corr_mat <- corr_mat %>% 
+	as_tibble() %>% 
+	select(matches("Estimate")) %>% 
+	rename_all(str_remove, "Estimate.") %>% 
+	mutate(term1 = corr_names)
+
+corr_mat[lower.tri(corr_mat)] <- NA
+
+corr_data <- corr_mat %>% 
 	as.data.frame() %>% 
-	rownames_to_column("term1") %>% 
 	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
-	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
-	geom_tile() +
-	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
-	scale_fill_distiller(limits = c(-1, 1)) +
+	drop_na(.value)
+
+post_cors_participant <- corr_data %>% 
+	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
+	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
+	mutate(
+		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
+		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
+	) %>% 
+	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
+	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
+	geom_tile(na.rm = TRUE) +
+	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
+	labs(
+		x = "Term 1", 
+		y = "Term 2", 
+		fill = "Posterior\ncorrelation",
+		title = "By participant"
+	) +
+	scale_fill_gradient2(
+		low = "#04bf78", mid = "white", high = "#FFC20A", 
+		na.value = "white", limits = c(-0.4, 0.4)
+	) +
+	scale_x_discrete() +
 	coord_equal() +
 	theme(
+		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
+	)
+
+# correlations by item
+corr_mat <- VarCorr(fit_total_4, summary = TRUE)$target$cor 
+corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$target$cor)
+
+corr_mat <- corr_mat %>% 
+	as_tibble() %>% 
+	select(matches("Estimate")) %>% 
+	rename_all(str_remove, "Estimate.") %>% 
+	mutate(term1 = corr_names)
+
+corr_mat[lower.tri(corr_mat)] <- NA
+
+corr_data <- corr_mat %>% 
+	as.data.frame() %>% 
+	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	drop_na(.value)
+
+post_cors_item <- corr_data %>% 
+	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
+	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
+	mutate(
+		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
+		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
+	) %>% 
+	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
+	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
+	geom_tile(na.rm = TRUE) +
+	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
+	labs(
+		x = "Term 1", y = "Term 2", fill = "Posterior\ncorrelation",
+		title = "By item"
+	) +
+	scale_fill_gradient2(
+		low = "#04bf78", mid = "white", high = "#FFC20A", 
+		na.value = "white", limits = c(-0.4, 0.4)
+	) +
+	scale_x_discrete() +
+	coord_equal()  +
+	theme(
+		axis.text.y = element_blank()
+	)
+
+(post_cors_participant | post_cors_item) &
+	plot_layout(guides = "collect") &
+	theme(
+		panel.grid = element_blank(),
 		legend.position = "top",
-		legend.text = element_text(size = 8),
-		axis.title = element_blank(),
-		axis.text.y = element_text(hjust = 1, size = 7),
-		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
+		legend.direction = "horizontal",
+		legend.key.height = unit(0.1, "cm"),
+		legend.key.width = unit(0.3, "cm"),
+		legend.justification = c(1, 1),
+		legend.title = element_blank(),
+		legend.text = element_text(size = 5),
+		axis.title.x = element_blank(),
+		axis.title.y = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)
 	)
@@
 
-#### Marginal means {.tabset }
+## Marginal means
 
-##### Marginal to time course
+### Prior predictions (before seeing the data)
 
-```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r gaze_time_prior, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant) %>% 
+	count(lp, vocab_size_total_center)
 
-m <- emmeans(model_fits$fit, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
-	as_tibble() %>% 
-	clean_names() %>% 
-	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x < 0, 0, x)) %>% 
-	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x > 1, 1, x))
+n <- expand_grid(
+	lp = c("Monolingual", "Bilingual"),
+	vocab_size_l1_center = c(-1, 1),
+	trial_type = unique(gaze$trial_type),
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
+)
 
-ggplot(m, aes(age_group, emmean, ymin = lower_hpd, ymax = upper_hpd, colour = trial_type)) +
-	facet_wrap(~lp, ncol = 1) +
-	# geom_line(aes(group = trial_type), size = 1, position = position_dodge(width = 0.25)) +
-	geom_errorbar(size = 1, width = 0, position = position_dodge(width = 0.25)) +
-	geom_point(size = 4, position = position_dodge(width = 0.25)) +
-	labs(x = "Age (months))", y = "P(target)", colour = "Trial type") +
+m <- epred_draws(fit_l1_prior, newdata = n, ndraws = 50, re_formula = NA) %>% 
+	mutate(
+		.value = logit_to_prob(.epred),
+		vocab_size_l1_center = ifelse(
+			vocab_size_l1_center==-1, 
+			"Low vocabulary size (-1 SD)",
+			"High vocabulary size (+1 SD)"
+		)
+	)
+
+ggplot(m, aes(time_bin_center, .value)) +
+	facet_grid(fct_rev(lp)~vocab_size_l1_center) +
+	geom_hline(yintercept = 0.5, colour = "black") +
+	geom_line(
+		aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
+			colour = trial_type),
+		alpha = 0.5, size = 0.65
+	) +
+
+	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
+		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
+	scale_color_futurama() +
+	scale_x_continuous(
+		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
+		labels = 1:20
+	) +
 	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme_minimal() +
 	theme(
+		legend.position = "top",
 		legend.title = element_blank(),
-		legend.position = "top"
+		axis.text.x = element_text(size = 7),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(fill = "white", colour = NA),
+		plot.background = element_rect(fill = "white", colour = NA)
 	)
@@
 
-##### Time course
+### Posterior predictions (after seeing the data)
 
@@
 	lp = c("Monolingual", "Bilingual"),
-	age_group = paste(c(21, 25, 30), "months"),
+	vocab_size_total_center = c(-1, 1),
 	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
 )
 
-m <- epred_draws(object = model_fits$fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
-	mutate(.value = logit_to_prob(.epred))
+m <- epred_draws(object = fit_total_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
+	mutate(
+		.value = logit_to_prob(.epred),
+		vocab_size_total_center = ifelse(
+			vocab_size_total_center==-1, 
+			"Low vocabulary size (-1 SD)",
+			"High vocabulary size (+1 SD)"
+		)
+	)
 
 ggplot(m, aes(time_bin_center, .value)) +
-	facet_grid(fct_rev(lp)~age_group) +
+	facet_grid(fct_rev(lp)~vocab_size_total_center) +
 	geom_hline(yintercept = 0.5, colour = "black") +
-	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
+	geom_line(
+		aes(group = interaction(vocab_size_total_center, trial_type, lp, .draw),
 			colour = trial_type),
-			  alpha = 0.15, size = 0.65) +
-	stat_summary(aes(group = trial_type, colour = trial_type),
-				 fun = mean, geom = "line", size = 1.25) +
-	stat_summary(data = gaze, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
-								  colour = trial_type),
-				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
-				 position = position_dodge(width = 0.3)) +
-	geom_text(data = sample_size, aes(x = min(gaze$time_bin_center), y = 0.95, label = paste0("N = ", n)),
-			  colour = "white", hjust = 0, size = 5) +
+		alpha = 0.5, size = 0.65
+	) +
 	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
 		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_brewer(palette = "Set1") +
-	scale_x_continuous(breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), labels = unique(gaze$time_bin)) +
+	scale_color_futurama() +
+	scale_x_continuous(
+		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
+		labels = 1:20
+	) +
 	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme_minimal() +
 	theme(
@@
 		legend.title = element_blank(),
-		axis.text.x = element_text(size = 9),
+		axis.text.x = element_text(size = 7),
 		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank()
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(fill = "white", colour = NA),
+		plot.background = element_rect(fill = "white", colour = NA)
 	)
+
 ```
+
+## Marginal means {.tabset }
+
+```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+m <- emmeans(fit_total_4, ~trial_type | lp, epred = TRUE)
+
+m_draws <- gather_emmeans_draws(m) %>% 
+	as_tibble() %>% 
+	mutate_at(vars(.value), function(x) ifelse(x < 0, 0, x)) %>% 
+	mutate_at(vars(.value), function(x) ifelse(x > 1, 1, x))
+
+ggplot(m_draws, aes(.value, trial_type, fill = trial_type)) +
+	facet_wrap(~lp) +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		position = position_nudge(y = 0.05),
+		color = "white"
+	) +
+	stat_pointinterval(
+		color = "black"
+	) +
+	labs(
+		x = "Expected posterior mean PTLT", y = "Trial type",
+		colour = "Trial type", fill = "Trial type",
+		alpha = "CrI"
+	) +
+	guides(color = "none", fill = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_x_continuous(limits = c(0.5, 1), labels = percent)  +
+	theme(
+		axis.title.y = element_blank(),
+		legend.position = "right",
+		panel.grid.major.y = element_blank(),
+		panel.grid.minor.y = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(fill = NA, colour = "grey")
+	)
+
+```
+
+# Model with L1 vocabulary
+
+## Fixed effects
+
+```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+str_repl <- c(
+
+	# 3-way interactions
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",
+
+	# 2-way interactions
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_l1_center" =
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" =
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_time_bin_center:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Group \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil" =
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Group \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",  
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil:vocab_size_l1_center" = 
+		"Group \u00d7 Vocab (L1)",
+
+	# main effects (linear)
+	"b_time_bin_center:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_time_bin_center:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" = 
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" = 
+		"Trial type (C vs. NC)",
+
+	"b_time_bin_center:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	"b_time_bin_center:vocab_size_l1_center" = 
+		"Vocab. (L1, +1 SD)",
+	"b_Itime_bin_centerE2:vocab_size_l1_center" = 
+		"Vocab. (L1, +1 SD)",
+	"b_Itime_bin_centerE3:vocab_size_l1_center" = 
+		"Vocab. (L1, +1 SD)",
+
+	# 3-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab. (L1, +1 SD)",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab. (L1, +1 SD)",
+
+	# 2-way interaction linear effects
+	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
+		"Trial type (U vs. C+NC) \u00d7 Vocab. (L1, +1 SD)",
+	"b_trial_typePrimeNCvs.C:vocab_size_l1_center" = 
+		"Trial type (C vs. NC) \u00d7 Vocab. (L1, +1 SD)",
+
+	"b_lpLPMonvs.Bil:vocab_size_l1_center" =
+		"Group \u00d7 Vocab. (L1, +1 SD)",
+
+	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" =
+		"Trial type (U vs. C+NC)",
+	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" =
+		"Trial type (C vs. NC)",
+
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
+		"Group (Mon. vs. Bil.)",
+
+	# main linear effects
+	"b_Intercept" = "Intercept",
+	"b_Itime_bin_centerE2" = "Time bin 2",
+	"b_Itime_bin_centerE3" = "Time bin 3",
+	"b_time_bin_center" = "Time bin",
+	"b_vocab_size_l1_center" = "Vocab. (L1, +1 SD)",
+
+	"b_trial_typePrimeUvs.CPNC" = "Trial type (U vs. C+NC)",
+	"b_trial_typePrimeNCvs.C" = "Trial type (C vs. NC)",
+	"b_lpLPMonvs.Bil" = "Group (Mon. vs. Bil.)",
+
+	# sigma
+	"sigma" = "Sigma"
+)
+
+draws <- gather_draws(fit_l1_4, `b_.*`, `sigma`, regex = TRUE) %>% 
+	mutate(
+		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
+		.variable_name = str_replace_all(.variable, str_repl),
+		type = case_when(
+			str_detect(.variable, "E2") ~ "Quadratic time",
+			str_detect(.variable, "E3") ~ "Cubic time",
+			str_detect(.variable, "time_bin") ~ "Linear time",
+			str_detect(.variable, "sigma") ~ "Error",
+			TRUE ~ "Main effects"
+		) %>% 
+			factor(
+				levels = c(
+					"Main effects",
+					"Linear time", 
+					"Quadratic time",
+					"Cubic time", 
+					"Error"
+				), 
+				ordered = TRUE
+			)
+	)
+
+draws %>% 
+	group_by(.variable, .variable_name, type) %>% 
+	mean_qi() %>% 
+	select(type, .variable_name, .value, .lower, .upper) %>% 
+	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
+	fmt_percent(3) %>%
+	fmt_number(4:5, scale_by = 100) %>% 
+	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
+	cols_label(
+		.variable_name = md("**Predictor**"),
+		.value = md("**Mean**"),
+		.lower = md("**95% CrI**")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_text(weight = "bold", style = "italic")
+		),
+		locations = list(
+			cells_row_groups()
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_text(weight = "bold")
+		),
+		locations = list(
+			cells_column_labels()
+		)
+	) %>% 
+	as_raw_html()
+```
+
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}
+
+draws_intercept <- draws %>% 
+	filter(str_detect(.variable, "Intercept")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5,
+		color = "#FF6F00FF",
+		fill = "#FF6F00FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		title = "Intercept",
+		alpha = "CrI"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(0, 1)) +
+	theme(
+		panel.grid.major.y = element_blank()
+	)
+
+ggsave(here("img", "posterior_intercept_l1.png"), draws_intercept, height = 2, width = 7)
+
+draws_predictors <- draws %>% 
+	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#C71000FF", 
+		fill = "#C71000FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Main effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2)) +
+	theme(
+		panel.grid.major.y = element_blank()
+	)
+
+ggsave(here("img", "posterior_predictors_l1.png"), draws_predictors, height = 7, width = 7)
+
+draws_time <- draws %>%
+	filter(str_detect(.variable, "time_bin")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	facet_wrap(~type, scales = "free_x") +
+	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
+	# stat_slab(
+	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+	# 	size = 0.5, 
+	# 	color = "#008EA0FF", 
+	# 	fill = "#008EA0FF"
+	# ) +
+	stat_pointinterval(
+		color = "#008EA0FF",
+		fill = "#008EA0FF",
+		point_size = 1.5
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		fill = "CrI", 
+		alpha = "CrI",
+		title = "Polynomial effects"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent) +
+	theme(
+		panel.grid.major.y = element_blank(),
+		panel.border = element_rect(fill = NA, colour = "grey"),
+		axis.title = element_blank()
+	)
+
+ggsave(here("img", "posterior_poly_l1.png"), draws_time, height = 7, width = 9)
+
+draws_sigma <- draws %>% 
+	filter(str_detect(.variable, "sigma")) %>% 
+	ggplot(aes(.value, .variable_name)) +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		size = 0.5, 
+		color = "#8A4198FF", 
+		fill = "#8A4198FF"
+	) +
+	labs(
+		x = "Value", 
+		y = "Variable", 
+		alpha = "CrI",
+		fill = "CrI", 
+		title = "Error"
+	) +
+	guides(fill = "none", color = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_fill_brewer(direction = -1, na.translate = FALSE) +
+	scale_x_continuous(labels = percent, limits = c(0.92, 0.96)) +
+	theme(
+		panel.grid.major.y = element_blank()
+	)
+
+ggsave(here("img", "posterior_sigma_l1.png"), draws_sigma, height = 2, width = 7)
+
+((draws_intercept / draws_sigma / guide_area()) | draws_predictors) /
+	draws_time + 
+	plot_layout(heights = c(0.5, 0.5)) &
+	guides(fill = "none", color = "none") &
+	theme(
+		panel.background = element_rect(fill = NA, colour = "grey"),
+		axis.text.y = element_text(size = 7),
+		axis.text.x = element_text(size = 7),
+		axis.title = element_blank(),
+		legend.position = c(1, 1.2),
+		legend.direction = "horizontal",
+		legend.justification = "right",
+		legend.key.size = unit(0.35, "cm"),
+		legend.text = element_text(size = 7),
+		legend.title = element_text(size = 7),
+		panel.grid.major.y = element_blank()
+	)
+
+```
+
+## Random effects
+
+```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8,fig.height=4}
+
+corr_mat <- VarCorr(fit_l1_4, summary = TRUE)$participant$cor 
+corr_names <- rownames(VarCorr(fit_l1_4, summary = TRUE)$participant$cor)
+
+corr_mat <- corr_mat %>% 
+	as_tibble() %>% 
+	select(matches("Estimate")) %>% 
+	rename_all(str_remove, "Estimate.") %>% 
+	mutate(term1 = corr_names)
+
+corr_mat[lower.tri(corr_mat)] <- NA
+
+corr_data <- corr_mat %>% 
+	as.data.frame() %>% 
+	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	drop_na(.value)
+
+post_cors_participant <- corr_data %>% 
+	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
+	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
+	mutate(
+		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
+		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
+	) %>% 
+	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
+	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
+	geom_tile(na.rm = TRUE) +
+	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
+	labs(
+		x = "Term 1", 
+		y = "Term 2", 
+		fill = "Posterior\ncorrelation",
+		title = "By participant"
+	) +
+	scale_fill_gradient2(
+		low = "#04bf78", mid = "white", high = "#FFC20A", 
+		na.value = "white", limits = c(-0.4, 0.4)
+	) +
+	scale_x_discrete() +
+	coord_equal()  +
+	theme(
+		axis.text.y = element_text(size = 7)
+	)
+
+# correlations by item
+corr_mat <- VarCorr(fit_l1_4, summary = TRUE)$target$cor 
+corr_names <- rownames(VarCorr(fit_l1_4, summary = TRUE)$target$cor)
+
+corr_mat <- corr_mat %>% 
+	as_tibble() %>% 
+	select(matches("Estimate")) %>% 
+	rename_all(str_remove, "Estimate.") %>% 
+	mutate(term1 = corr_names)
+
+corr_mat[lower.tri(corr_mat)] <- NA
+
+corr_data <- corr_mat %>% 
+	as.data.frame() %>% 
+	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	drop_na(.value)
+
+post_cors_item <- corr_data %>% 
+	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
+	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
+	mutate(
+		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
+		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
+	) %>% 
+	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
+	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
+	geom_tile(na.rm = TRUE) +
+	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
+	labs(
+		x = "Term 1", y = "Term 2", fill = "Posterior\ncorrelation",
+		title = "By item"
+	) +
+	scale_fill_gradient2(
+		low = "#04bf78", mid = "white", high = "#FFC20A", 
+		na.value = "white", limits = c(-0.4, 0.4)
+	) +
+	scale_x_discrete() +
+	coord_equal() +
+	theme(
+		axis.text.y = element_blank()
+	)
+
+(post_cors_participant | post_cors_item) &
+	plot_layout(guides = "collect") &
+	theme(
+		panel.grid = element_blank(),
+		legend.position = "top",
+		legend.direction = "horizontal",
+		legend.key.height = unit(0.1, "cm"),
+		legend.key.width = unit(0.3, "cm"),
+		legend.justification = c(1, 1),
+		legend.title = element_blank(),
+		legend.text = element_text(size = 5),
+		axis.title.x = element_blank(),
+		axis.title.y = element_blank(),
+		axis.ticks = element_blank(),
+		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)
+
+	)
+
+```
+
+## Posterior predictions (after seeing the data)
+
+```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant) %>% 
+	count(lp, vocab_size_l1_center)
+
+n <- expand_grid(
+	lp = c("Monolingual", "Bilingual"),
+	vocab_size_l1_center = c(-1, 1),
+	trial_type = unique(gaze$trial_type),
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
+)
+
+m <- epred_draws(object = fit_l1_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
+	mutate(
+		.value = logit_to_prob(.epred),
+		vocab_size_l1_center = ifelse(
+			vocab_size_l1_center==-1, 
+			"Low vocabulary size (-1 SD)",
+			"High vocabulary size (+1 SD)"
+		) %>% 
+			factor(levels = c(
+				"Low vocabulary size (-1 SD)",
+				"High vocabulary size (+1 SD)"
+			),
+			ordered = TRUE)
+	)
+
+ggplot(m, aes(time_bin_center, .value, fill = trial_type, colour = trial_type)) +
+	facet_grid(fct_rev(lp)~vocab_size_l1_center) +
+	geom_hline(yintercept = 0.5, colour = "black") +
+	# geom_line(
+	# 	aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
+	# 		colour = trial_type),
+	# 	alpha = 0.5, size = 0.65
+	# ) +
+	stat_lineribbon(.width = 0.95, alpha = 0.5, color = NA) +
+	stat_lineribbon(.width = 0.95, fill = NA) +
+	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
+		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
+	scale_color_futurama() +
+	scale_fill_futurama() +
+	scale_x_continuous(
+		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
+		labels = 1:20
+	) +
+	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	theme_minimal() +
+	theme(
+		text = element_text(size = 15),
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(size = 7),
+		axis.text.y = element_text(size = 9),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.grid.minor.y = element_blank(),
+		panel.grid.major.y = element_blank(),
+		panel.background = element_rect(fill = "white", colour = NA),
+		panel.border = element_rect(fill = NA, colour = "grey"),
+		plot.background = element_rect(fill = "white", colour = NA)
+	)
+
+ggsave(here("img", "epreds_l1.jpeg"), dpi = 1000)
+
+```
+
+```{r gaze_matrix, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+sample_size <- participants %>% 
+	filter(valid_participant) %>% 
+	count(lp, vocab_size_l1_center)
+
+n <- expand_grid(
+	lp = c("Monolingual", "Bilingual"),
+	vocab_size_l1_center = seq(-2, 2, 0.25),
+	trial_type = unique(gaze$trial_type),
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.25)
+)
+
+m <- epred_draws(object = fit_l1_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
+	median_qi() %>%  
+	mutate(.value = logit_to_prob(.epred))
+
+ggplot(m, aes(time_bin_center, vocab_size_l1_center, fill = .value)) +
+	facet_grid(fct_rev(lp)~trial_type) +
+	# geom_line(
+	# 	aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
+	# 		colour = trial_type),
+	# 	alpha = 0.5, size = 0.65
+	# ) +
+	geom_raster(interpolate = TRUE) +
+	labs(
+		x = "Time bin (100 ms)", 
+		y = "Vocabulary size (SD)", 
+		colour = "Expected posterior mean PTLT",
+		fill = "Expected posterior mean PTLT",
+		shape = "Expected posterior mean PTLT",
+		linetype = "Expected posterior mean PTLT"
+	) +
+	scale_fill_viridis_c(labels = percent, option = "plasma") +
+	scale_x_continuous(
+		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
+		labels = 1:20
+	) +
+	theme_minimal() +
+	theme(
+		text = element_text(size = 15),
+		legend.position = "top",
+		legend.text = element_text(size = 9),
+		legend.key.width = unit(1, "cm"),
+		axis.text.x = element_text(size = 7),
+		axis.text.y = element_text(size = 9),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.grid.minor.y = element_blank(),
+		panel.grid.major.y = element_blank(),
+		panel.background = element_rect(fill = "white", colour = NA),
+		plot.background = element_rect(fill = "white", colour = NA)
+	)
+
+ggsave(here("img", "epreds_l1_3d.jpeg"), dpi = 1000)
+
+```
+
+## Marginal means {.tabset }
+
+```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+m <- emmeans(fit_l1_4, ~trial_type | lp, epred = TRUE)
+
+m_draws <- gather_emmeans_draws(m) %>% 
+	as_tibble() %>% 
+	mutate_at(vars(.value), function(x) ifelse(x < 0, 0, x)) %>% 
+	mutate_at(vars(.value), function(x) ifelse(x > 1, 1, x))
+
+ggplot(m_draws, aes(.value, trial_type, colour = trial_type, fill = trial_type)) +
+	facet_wrap(~lp) +
+	stat_slab(
+		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		position = position_nudge(y = 0.05)
+	) +
+	stat_pointinterval(
+		color = "black",
+	) +
+	labs(
+		x = "Expected posterior mean PTLT", y = "Trial type",
+		colour = "Trial type", fill = "Trial type",
+		alpha = "CrI"
+	) +
+	guides(color = "none", fill = "none") +
+	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
+	scale_x_continuous(limits = c(0.5, 1), labels = percent)  +
+	theme(
+		axis.title.y = element_blank(),
+		legend.position = "right",
+		panel.grid.major.y = element_blank(),
+		panel.grid.minor.y = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(fill = NA, colour = "grey")
+	)
+
+ggsave(here("img", "emmeans_l1.jpeg"), dpi = 1000)
+
+```

### 2022-02-11 presentations/2022-01-25_lacre/2022-01-25_lacre.Rmd
Relocate files

@@
 
-waics %>% 
+waics_l1 %>% 
 	map("estimates") %>% 

### 2022-02-11 scripts/R/01_participants.R

@@ -1,0 +1,58 @@
+# participants
+
+get_participants <- function(
+	participants_bcn, # participants dataset in Barcelona
+	participants_oxf # participants dataset in Oxford
+){
+	
+	suppressMessages({
+		# participants
+		participants_bcn <- participants_bcn %>% # defined in arguments
+			# NA -> FALSE
+			mutate_if(is.logical, ~ifelse(is.na(.), FALSE, .)) %>%
+			mutate(
+				age_group = as.factor(paste0(age_group, " months")),
+				date_test = as_date(date_test)
+			) %>% 
+			# remove pilot participants
+			filter(!pilot) %>% 
+			# remove participants with no gaze data
+			drop_na(filename) %>% 
+			select(
+				participant, id_db, sex, date_test, age_group, lp,
+				test_language, list, version, filename
+			)
+		
+		# Oxford data ----
+		# import vocabulary data
+		participants_oxf <- participants_oxf %>% # defined in arguments
+			clean_names() %>% # all column names to snake case
+			rename(
+				participant = id,
+				lp = lang_group
+			) %>% 
+			# in Oxford, participant ID and DB id are the same
+			mutate(
+				id_db = participant,
+				test_language = "English"
+			) %>% 
+			# move column
+			relocate(id_db, .after = participant)
+		
+		# merge data ----
+		participants <- list(
+			Barcelona = participants_bcn,
+			Oxford = participants_oxf
+		) %>% 
+			bind_rows(.id = "location") %>% 
+			select(
+				participant, id_db, date_test, location, lp, age_group,
+				test_language, list, version, filename
+			) %>% 
+			drop_na(participant)
+		
+	})
+	
+	return(participants)
+	
+}

### 2022-02-11 scripts/R/05_prepare.R

@@ -1,0 +1,90 @@
+# prepare
+
+prepare_data <- function(
+	gaze_bcn, # Barcelona gaze data, get_gaze_bcn output
+	gaze_oxf, # Oxford gaze data, get_gaze_oxf output
+	participants, # participants dataset, get_participants output
+	stimuli, # stimuli dataset, get_stimuli output
+	vocabulary, # vocabulary dataset, get_vocabulary output
+	attrition # attrition dataset , get_attrition output
+){
+	suppressMessages({
+		participants <- mutate(participants, participant_unique = as.character(row_number()))
+		
+		vocabulary <- mutate(
+			vocabulary,
+			vocab_size_total_center = scale(vocab_size_total)[,1],
+			vocab_size_l1_center = scale(vocab_size_l1)[,1],
+			vocab_size_conceptual_center = scale(vocab_size_conceptual)[,1]
+		) 
+		
+		clean <- list(Barcelona = gaze_bcn, Oxford = gaze_oxf) %>% 
+			bind_rows(.id = "location") %>% 
+			# to avoid issues with column names
+			rename(time_stamp = time) %>% 
+			left_join(attrition) %>% 
+			left_join(vocabulary) %>% 
+			filter(phase=="Target-Distractor", valid_trial, valid_participant) %>% 
+			select(
+				participant, date_test, lp, location, list, age_group, trial, test_language, phase,
+				time_stamp, x, y, valid_sample, trial_type, target_location, aoi_target, aoi_distractor, prime, target,
+				vocab_size_total, vocab_size_l1, vocab_size_conceptual
+			) %>% 
+			drop_na(trial) %>% 
+			left_join(participants)
+		
+		# to eyetrackingR format
+		gaze <- clean %>% 
+			mutate(trackloss_col = !valid_sample) %>% # eyetracking R
+			make_eyetrackingr_data(
+				participant_column = "participant_unique",
+				trial_column = "trial",
+				time_column = "time_stamp",
+				trackloss_column = "trackloss_col",
+				item_columns = c("prime", "target"),
+				aoi_columns = c("aoi_target","aoi_distractor"), 
+				treat_non_aoi_looks_as_missing = FALSE
+			) %>% 
+			subset_by_window(
+				rezero = TRUE,
+				window_start_time = 0,
+				window_end_time = 2
+			) %>% 
[…]

### 2022-02-11 scripts/matlab/Functions/phase_test_.m

@@ -1,0 +1,224 @@
+function [full_gaze_data, variableNames, calculated] = test_phase(eyetracker, window, monitorWindow, pAudioHandle, condition)
+%familiarization
+%   test process of Generalization2 study
+
+global STIM_PATH;
+global STEEP_SOUND_LEVEL_UP;
+global STEEP_SOUND_LEVEL_DOWN;
+global LIMIT_ROTATION;
+global STEEP_ROTATION;
+global TEXT_COLOR;
+global BACKGROUND_COLOR;
+global SCREEN_MONITOR_PROPORTION;
+global EYE_DOT_COLOR;
+global DRAW_CUES;   %for DEBUG allow to dray AOI rectangle ans gazePoint
+global Y_KEY;
+global N_KEY;
+global E_KEY;
+
+TEST_STIM_DURATION = 12;
+
+variableNames={'SystemTimeStamp','meanX','meanY','meanValidity','lX','lY','lV','lPupil','lPupilV','rX','rY','rV','rPupil','rPupilV','process', 'extra'};
+[screenXpixels, screenYpixels] = Screen('WindowSize', window);
+
+%% Select & prepare Stim pairs Image(1) Sound(2)
+IMAGE_L_INDEX = 1;
+IMAGE_R_INDEX = 2;
+SOUND_INDEX = 3;
+IMAGE_TARGET = 4;
+
+stim_list1 = {"green_dino.png" "red_car.png"   "kegike.wav" "R"; ...
+            "yellow_car.png" "blue_dino.png" "kekegi.wav" "L"; ...
+            "green_dino.png" "red_car.png" "gikegi.wav" "R"; ...
+            "yellow_car.png" "green_dino.png" "gigike.wav" "L"};
+
+stim_list2 = {"green_dino.png" "red_car.png"   "kekegi.wav" "R"; ...
+            "yellow_car.png" "blue_dino.png" "kegike.wav" "L"; ...
+            "green_dino.png" "red_car.png" "gigike.wav" "R"; ...
+            "yellow_car.png" "green_dino.png" "gikegi.wav" "L"};
+
+if condition==1
+    stim_list=stim_list1;
+else    
+    stim_list=stim_list2;
+end
+
+% load stim images
+% Import image and and convert it, stored in
+% MATLAB matrix, into a Psychtoolbox OpenGL texture using 'MakeTexture';
+for stimIndex = 1:size(stim_list,1)
[…]

### 2022-02-11 src/R/01_participants.R

@@ -1,58 +1,0 @@
-# participants
-
-get_participants <- function(
-	participants_bcn, # participants dataset in Barcelona
-	participants_oxf # participants dataset in Oxford
-){
-	
-	suppressMessages({
-		# participants
-		participants_bcn <- participants_bcn %>% # defined in arguments
-			# NA -> FALSE
-			mutate_if(is.logical, ~ifelse(is.na(.), FALSE, .)) %>%
-			mutate(
-				age_group = as.factor(paste0(age_group, " months")),
-				date_test = as_date(date_test)
-			) %>% 
-			# remove pilot participants
-			filter(!pilot) %>% 
-			# remove participants with no gaze data
-			drop_na(filename) %>% 
-			select(
-				participant, id_db, sex, date_test, age_group, lp,
-				test_language, list, version, filename
-			)
-		
-		# Oxford data ----
-		# import vocabulary data
-		participants_oxf <- participants_oxf %>% # defined in arguments
-			clean_names() %>% # all column names to snake case
-			rename(
-				participant = id,
-				lp = lang_group
-			) %>% 
-			# in Oxford, participant ID and DB id are the same
-			mutate(
-				id_db = participant,
-				test_language = "English"
-			) %>% 
-			# move column
-			relocate(id_db, .after = participant)
-		
-		# merge data ----
-		participants <- list(
-			Barcelona = participants_bcn,
-			Oxford = participants_oxf
-		) %>% 
-			bind_rows(.id = "location") %>% 
-			select(
-				participant, id_db, date_test, location, lp, age_group,
-				test_language, list, version, filename
-			) %>% 
-			drop_na(participant)
-		
-	})
-	
-	return(participants)
-	
-}

### 2022-02-11 src/R/06_analysis.R

@@ -1,68 +1,0 @@
-# analysis
-
-fit_models <- function(
-	formulas,
-	datasets,
-	prior,
-	model_paths,
-	refit = TRUE
-){
-	
-	fit_path <- here("results", "model_fits.rds")
-	fit_exists <- file.exists(fit_path)
-	
-	if (!fit_exists){
-		formulas <- map(formulas, as.formula)
-		
-		fits <- map2(
-			.x = formulas, .y = datasets,
-			~brm(
-				formula = .x, data = .y, prior = prior, backend = "cmdstanr", 
-				init = 0, iter = 2000, chains = 4, seed = 888, cores = 4
-			) 
-		)
-		
-		names(fits) <- names(formulas)
-		
-		# save file
-		saveRDS(fits, fit_path)
-		
-		# save Stan code
-		stan_code <- map(fits, stancode)
-		map2(.x = stan_code, .y = model_paths, ~save(.x, .y))
-		
-	} else {
-		fit <- readRDS(fit_path)
-	}
-	
-	return(fit)
-}
-
-# get posterior draws for population-level effects
-get_posterior_draws <- function(fit){
-	gather_draws(fit, `b_.*`, regex = TRUE)
-}
-
-# get expected predictions
-get_epreds <- function(fit, gaze, transform = TRUE){
-	n <- expand_grid(
-		lp = c("Monolingual", "Bilingual"),
-		vocab_size_total_center = c(-1, 1),
-		trial_type = unique(gaze$trial_type),
-		time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
-	)
-	
-	m <- epred_draws(fit, newdata = n, ndraws = 50, re_formula = NA)
-	if (transform) m$.epred <- logit_to_prob(m$.epred)
-	return(m)
-}
-
-
-# get marginal means
-get_emmeans <- function(fit, ...){
-	
-	emmean <- emmeans(fit, ~trial_type, epred = TRUE, ...) %>% 
-		as_tibble() %>% 
-		mutate_if(is.numeric, inv_logit_scaled)
-	return(emmean)
-}

### 2022-02-11 src/matlab/CognatePriming.m

@@ -1,879 +1,0 @@
-% Basic Sample to use Tobii Eye Trackers with TobiiPro.SDK.Matlab_1.6.1.21
-% Code following Guide: http://developer.tobiipro.com/matlab/matlab-sdk-reference-guide.html
-%
-%qq
-% 20190516 ... by xMayoral + sBlanch
-%qq
-% INITIALIZATIONq, vars...
-%  SETUP Tobiiqqq
-
-%   setup path
-%   look for eyetraqqckers
-%  SETUP PsychToolBox
-%   graphics
-%   audio
-% Possitioning subjent in front eyeTracker
-% Calibrate eyeTracker for subject eyes
-% START Study
-%  Show an image and get eye dataq
-% FINALIZATION
-%
-% PRESS 'e' to exit at any moment
-
-%% [INI] Initialization
-
-% % Clear and basic scripte Set-Up
-% sca;
-% close all;
-
-% clear the workspace and the screen
-% --------------------------------------
-sca
-clc
-clearvars;
-close all;
-delete(instrfind);
-warning('off') %if you do not want to see warnings in command window
-
-
-ME = [];    % To keep track of possible failures
-fullGazeData = []; %SIL2020
-full_extra_cols = [];   
-
-
-try         % and enable a possible "clean" exit
-    
-    folder = strcat(pwd, filesep, 'MATLAB', filesep, 'Functions');
-    addpath(genpath(folder));
-    % Add access to all the Tobii SDK functions
-    folder = strcat(pwd, filesep, 'MATLAB', filesep, 'TobiiPro.SDK.Matlab_1.6.1.21');
-    addpath(genpath(folder));
-    
-    % set paths GONZALO ------------------------------------------------------------
-    mainDirectory = 'C:\Users\cbclab\Documents\gGarciaCastro\cognate-priming';
-    cd(mainDirectory);
-    
-    %gettersImagePath = [mainDirectory '\getterImage.jpg']; % provisional
-    listsPath      = [mainDirectory '\Stimuli\Lists\'];
-    gettersPath    = [mainDirectory '\Stimuli\Getters\'];
-    allImagesPath  = [mainDirectory '\Stimuli\Images\'];
-    audiosPath     = [mainDirectory '\Stimuli\Sounds\'];
-    
-    % Global variables used acros funtions
-    % % %%
-    % global DRAW_CUES;   %for DEBUG allow to dray AOI rectangle ans gazePoint
[…]

### 2022-02-11 src/matlab/Functions/calibrate/calibrateBB.m

@@ -1,196 +1,0 @@
-function calibrateBB(eyetracker, window, monitorWindow, pAudioHandle, filenamecalibration)
-%     global SCREEN_MONITOR_PROPORTION;
-%     global SCREEN_WIDTH;
-%     global SCREEN_HEIGHT;
-%     global TEXT_COLOR;
-%     global BACKGROUND_COLOR; %20200203 SIL as chiara
-    
-    TEXT_COLOR = [255, 255, 255]; %20200203 SIL as chiara
-    
-    [SCREEN_WIDTH, SCREEN_HEIGHT] = Screen('WindowSize', window); %20200203 SIL as chiara
-    [mScreenXpixels, mScreenYpixels] = Screen('WindowSize', monitorWindow); %20200203 SIL as chiara
-    SCREEN_MONITOR_PROPORTION = SCREEN_WIDTH / mScreenXpixels; %20200203 SIL as chiara
-
-    spaceKey = KbName('Space');
-    RKey = KbName('R');
-        
-    % image to attract atention
-    % Import image and and convert it, stored in
-    % MATLAB matrix, into a Psychtoolbox OpenGL texture using 'MakeTexture';
-    imageFileName = ["spiral0.png","spiral0.png","spiral0.png","spiral0.png"];
-    audioFileName = ["Ring01.wav","Ring02.wav","Ring03.wav","Ring04.wav"];
-
-    % Import image and and convert it, stored in
-    % MATLAB matrix, into a Psychtoolbox OpenGL texture using 'MakeTexture';
-    for stimIndex = 1:size(imageFileName,2)
-        [img, ~, alpha]=imread(imageFileName(stimIndex), 'png');
-        [iy, ix, ~] = size(img);
-        img(:, :, 4) = alpha;
-        STIM(stimIndex).texture = Screen('MakeTexture', window, img);
-        STIM(stimIndex).iRect = [0 0 ix iy];
-        STIM(stimIndex).x = 100;
-        STIM(stimIndex).y = 100;
-        STIM(stimIndex).AOI = CenterRectOnPoint(STIM(stimIndex).iRect/2, STIM(stimIndex).x, STIM(stimIndex).y); % stimolous Area Of Interest (AOI)
-        STIM(stimIndex).steepX = 10;
-        STIM(stimIndex).steepY = 10;
-        STIM(stimIndex).rotation = 5;
-        STIM(stimIndex).rotationSteep = 5;
-        STIM(stimIndex).zoom = 1;
-        
[…]

### 2022-02-11 src/utils.R

@@ -1,0 +1,305 @@
+# utils
+
+# custom ggplot theme
+theme_custom <- function(){
+	theme(
+		panel.background = element_rect(fill = "transparent"),
+		panel.grid = element_blank(),
+		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
+		panel.border = element_rect(fill = "transparent", colour = "black"),
+		text = element_text(colour = "black", size = 15),
+		axis.text = element_text(colour = "black")
+	)
+}
+
+# dark GitHub theme
+theme_github <- function(){
+	theme_dark() +
+		theme(
+			text = element_text(colour = "white", size = 12),
+			axis.text = element_text(colour = "white", size = 8),
+			legend.title = element_text(colour = "white", size = 10),
+			legend.text = element_text(colour = "white", size = 10),
+			legend.background = element_rect(fill = "#0D1117"),
+			strip.text = element_text(size = 10),
+			legend.key = element_rect(fill = "#0D1117", colour = "#0D1117"),
+			strip.background = element_rect(fill = "#161B22"),
+			plot.background = element_rect(fill = "#0D1117"),
+			panel.background = element_rect(fill = "#0D1117"),
+			panel.border = element_rect(fill = "transparent", colour = "#0D1117")
+		)
+}
+
+# get multilex data ----
+get_credentials <- function(){
+	ml_connect()
+}
+
+get_multilex <- function(
+	update = FALSE,
+	type = "understands"
+){
+	get_credentials()
+	
+	p <- ml_participants()
+	r <- ml_responses(p, update = update)
+	l <- ml_logs(p, r) %>% 
+		rename(participant = id_exp) %>% 
+		mutate(
+			age_group =  as.factor(
+				case_when(
+					between(age, 19, 24) ~ 21,
+					between(age, 24, 28) ~ 25,
+					between(age, 28, 34) ~ 30
+				)),
+			age_group = paste0(age_group, " months")
+		) %>% 
+		filter(age_group != "NA months") %>% 
+		select(participant, time, age_group, lp)
+	
+	v <- ml_vocabulary(p, r, scale = "prop", by = "id_exp") %>% 
+		filter(type==type)
+	
+	m <- list(
+		participants = p, responses = r, logs = l,
[…]

### 2022-02-14 docs/01_stimuli.Rmd
Render Rmds

@@
 	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	geom_col(position = position_fill()) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
 	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
@@
 	facet_wrap(location~test_language, ncol = 4) +
-	geom_col(position = position_fill(), colour = "#0D1117") +
-	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
+	geom_col(position = position_fill()) +
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
 	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
@@
 	facet_wrap(role~location~test_language) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	geom_col(position = position_fill(), colour = "white") +
 	labs(x = "% of trials", y = "Trial type",

### 2022-02-14 docs/05_attrition.Rmd
Render Rmds

@@
 	facet_grid(location~age_group, scales = "free") +
-	geom_bar(colour = "#0D1117", size = 1) +
+	geom_bar(size = 1) +
 	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
@@
 	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	geom_col(position = position_fill(), colour = "white") +
 	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
@@
 	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	geom_col(position = position_fill(), colour = "white") +
 	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
@@
 	facet_grid(location~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	geom_col(position = position_fill(), colour = "white") +
 	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
@@
 	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "#0D1117", width = 0.25,
+	geom_boxplot(fill = "white", width = 0.25,
 				 position =  position_dodge(width = 0.5),
@@
 	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
+			   position = position_dodge(width = 0.7), colour = "white") +
 	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
@@
 	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
+	geom_col(position = position_fill(), colour = "white") +
 	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
@@
 	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "#0D1117") +
+			   position = position_dodge(width = 0.7), colour = "white") +
 	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +

### 2022-02-14 docs/06_results.Rmd
Render Rmds

@@
 
-model_comparison <- waics_l1 %>% 
-	map("estimates") %>% 
-	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
-	bind_rows(.id = "model") %>%
-	clean_names() %>% 
-	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
-	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
-	mutate(
-		model = c(
-			"Intercept",
-			"... + Trial type",
-			"... + Group \u00d7Trial type\u00d7Group",
-			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
-			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
-		)
-	) %>% 
-	gt() %>% 
-	fmt_number(-model) %>% 
-	tab_spanner("WAIC", matches("waic")) %>% 
-	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
-	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
-	cols_label(
-		model = "Model",
-		estimate_elpd_waic = "Estimate",
-		estimate_waic = "Estimate",
-		estimate_p_waic = "Estimate",
-		se_elpd_waic = md("*SE*"),
-		se_waic = md("*SE*"),
-		se_p_waic = md("*SE*"),
-	) %>% 
-	cols_align("right", "model") %>% 
-	tab_style(
-		cell_text(weight = "bold"),
-		cells_column_spanners()
-	) %>% 
-	tab_style(
-		cell_text(style = "italic"),
-		cells_column_labels()
-	)
-
-gtsave(model_comparison, here("img", "model_comparison.png"))
-
-as_raw_html(model_comparison)
+# model_comparison <- waics_l1 %>% 
+# 	map("estimates") %>% 
+# 	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
+# 	bind_rows(.id = "model") %>%
+# 	clean_names() 
+# 	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
+# 	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
+# 	mutate(
+# 		model = c(
+# 			"Intercept",
+# 			"... + Trial type",
+# 			"... + Group \u00d7Trial type\u00d7Group",
+# 			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
+# 			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
+# 		)
+# 	) %>% 
+# 	gt() %>% 
+# 	fmt_number(-model) %>% 
+# 	tab_spanner("WAIC", matches("waic")) %>% 
+# 	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
+# 	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
+# 	cols_label(
+# 		model = "Model",
+# 		estimate_elpd_waic = "Estimate",
+# 		estimate_waic = "Estimate",
+# 		estimate_p_waic = "Estimate",
+# 		se_elpd_waic = md("*SE*"),
+# 		se_waic = md("*SE*"),
+# 		se_p_waic = md("*SE*"),
+# 	) %>% 
+# 	cols_align("right", "model") %>% 
+# 	tab_style(
+# 		cell_text(weight = "bold"),
+# 		cells_column_spanners()
+# 	) %>% 
+# 	tab_style(
+# 		cell_text(style = "italic"),
+# 		cells_column_labels()
+# 	)
+# 
+# gtsave(model_comparison, here("img", "model_comparison.png"))
+# 
+# 
+# as_raw_html(model_comparison)
 
@@
 	tab_style(
-		style = list(
-			cell_text(weight = "bold", style = "italic")
-		),
-		locations = list(
+		cell_text(weight = "bold", style = "italic"),
 		cells_row_groups()
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_text(weight = "bold")
-		),
-		locations = list(
-			cells_column_labels()
-		)
 	) %>% 
@@
 	tab_style(
-		style = list(
-			cell_text(weight = "bold", style = "italic")
-		),
-		locations = list(
+		cell_text(weight = "bold", style = "italic"),
 		cells_row_groups()
-		)
-	) %>% 
-	tab_style(
-		style = list(
-			cell_text(weight = "bold")
-		),
-		locations = list(
-			cells_column_labels()
-		)
 	) %>%

### 2022-02-14 _targets.R

@@ -499,16 +499,16 @@ list(
 	tar_target(loos_l1, map(model_fits_l1, loo) %>% saveRDS("results/loos_l1.rds")),
 	
 	tar_target(waics_total, map(model_fits_total, waic) %>% saveRDS("results/waics_total.rds")),
-	tar_target(loos_total, map(model_fits_total, loo) %>% saveRDS("results/loos_total.rds"))
+	tar_target(loos_total, map(model_fits_total, loo) %>% saveRDS("results/loos_total.rds")),
 	
 	# # render docs
-	# tar_render(docs_participants, "docs/00_participants.Rmd", priority = 0),
-	# tar_render(docs_stimuli, "docs/01_stimuli.Rmd", priority = 0),
-	# tar_render(docs_vocabulary, "docs/02_vocabulary.Rmd", priority = 0),
-	# tar_render(docs_design, "docs/03_design.Rmd", priority = 0),
-	# tar_render(docs_analysis, "docs/04_analysis.Rmd", priority = 0),
-	# tar_render(docs_attrition, "docs/05_attrition.Rmd", priority = 0),
-	# tar_render(docs_results, "docs/06_results.Rmd")
+	tar_render(docs_participants, "docs/00_participants.Rmd", priority = 0),
+	tar_render(docs_stimuli, "docs/01_stimuli.Rmd", priority = 0),
+	tar_render(docs_vocabulary, "docs/02_vocabulary.Rmd", priority = 0),
+	tar_render(docs_design, "docs/03_design.Rmd", priority = 0),
+	tar_render(docs_analysis, "docs/04_analysis.Rmd", priority = 0),
+	tar_render(docs_attrition, "docs/05_attrition.Rmd", priority = 0),
+	tar_render(docs_results, "docs/06_results.Rmd")
 	#
 	# # render presentations
 	# tar_render(communications_lacre_abstract, "presentations/2022-01-25_lacre/2022-01-25_lacre-abstract.Rmd", priority = 0),

### 2022-02-18 docs/00_participants.Rmd
Render README as target

@@
 		valid_status = case_when(
-			!valid_vocab ~ "Invalid vocabulary",
 			!valid_gaze ~ "Invalid gaze",

### 2022-02-18 docs/02_vocabulary.Rmd
Render README as target

@@
 	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1]) %>% 
+	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed")) %>% 
 	filter(location=="Barcelona")
@@
 sample_size <- participants %>% 
-	filter(
-		participant %in% fit_l1_4$data$participant
-	) %>% 
+	filter(participant %in% fit_l1_4$data$participant) %>% 
 	count(age_group, location)
@@
 	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_pointinterval(
-		aes(lp, vocab_size_l1, group = lp),
-		position = position_nudge(x = 0.2),
-		.width = c(0.95, 0.89, 0.50),
-		point_size = 3
+	geom_boxplot(
+		aes(lp, vocab_size_l1, colour = is_imputed),
+		position = position_dodge(width = 1),
+		width = 0.25,
+		size = 1
 	) +
 	geom_point(
-		aes(lp, vocab_size_l1, color = lp),
-		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
+		aes(lp, vocab_size_l1, color = is_imputed),
+		size = 1,
+		alpha = 0.75,
 		position = position_jitter(width = 0.1, seed = 888)
@@
 		data = sample_size_lp,
-		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
-		show.legend = FALSE, position = position_dodge(width = 2)
+		aes(
+			x = 1.5,
+			y = 0, 
+			label = paste0("N = ", n),
+			group = lp
+		),
+		colour = "black",
+		show.legend = FALSE, 
+		position = position_dodge(width = 2)
 	) +
 	labs(
-		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
+		y = "Receptive vocabulary (L1)", 
+		colour = "Imputed", 
+		fill = "Imputed",
 		title = "L1 vocabulary size",
@@
 	) +
-	guides(colour = "none") +
 	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
@@
 		legend.position = "top",
+		panel.border = element_rect(fill = NA, colour = "grey", size = 1),
 		panel.grid.major.x = element_blank(),
@@
 	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_pointinterval(
-		aes(lp, vocab_size_total, group = lp),
-		position = position_nudge(x = 0.2),
-		.width = c(0.95, 0.89, 0.50),
-		point_size = 3
+	geom_boxplot(
+		aes(lp, vocab_size_l1, colour = is_imputed),
+		position = position_dodge(width = 1),
+		width = 0.25,
+		size = 1
 	) +
 	geom_point(
-		aes(lp, vocab_size_total, color = lp),
-		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
+		aes(lp, vocab_size_l1, color = is_imputed),
+		size = 1,
+		alpha = 0.75,
 		position = position_jitter(width = 0.1, seed = 888)
@@
 		data = sample_size_lp,
-		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
-		show.legend = FALSE, position = position_dodge(width = 2)
+		aes(
+			x = 1.5,
+			y = 0, 
+			label = paste0("N = ", n),
+			group = lp
+		),
+		colour = "black",
+		show.legend = FALSE, 
+		position = position_dodge(width = 2)
 	) +
@@
 	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_pointinterval(
-		aes(lp, vocab_size_conceptual, group = lp),
-		position = position_nudge(x = 0.2),
-		.width = c(0.95, 0.89, 0.50),
-		point_size = 3
+		geom_boxplot(
+		aes(lp, vocab_size_l1, colour = is_imputed),
+		position = position_dodge(width = 1),
+		width = 0.25,
+		size = 1
 	) +
 	geom_point(
-		aes(lp, vocab_size_conceptual, color = lp),
-		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
+		aes(lp, vocab_size_l1, color = is_imputed),
+		size = 1,
+		alpha = 0.75,
 		position = position_jitter(width = 0.1, seed = 888)

### 2022-02-18 docs/05_attrition.Rmd
Render README as target

@@
 		invalid_gaze = mean(!valid_gaze),
-		invalid_vocab = mean(!valid_vocab),
 		.groups = "drop"
@@
 		valid = "Valid trials (%)",
-		invalid_gaze = "Gaze (%)",
-		invalid_vocab = "Vocabulary (%)"
+		invalid_gaze = "Gaze (%)"
 	) %>% 
-	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
+	fmt_percent(c("valid", "invalid_gaze")) %>% 
 	as_raw_html()

### 2022-02-18 cognate-priming-app/R/modelUI.R

@@ -1,0 +1,17 @@
+modelUI <- function(){
+	
+	tagList(
+		# title
+		titlePanel("Model outputs"),
+		
+		# tabs
+		tabsetPanel(
+			tabPanel("Population-level effects"),
+			tabPanel("Group-level effects"),
+			tabPanel("Population-level predictions"),
+			tabPanel("Group-level predictions"),
+			tabPanel("Model diagnostics")
+		)
+	)
+	
+}

### 2022-02-18 cognate-priming-app/R/summaryUI.R

@@ -1,0 +1,17 @@
+summaryUI <- function(){
+	
+	tagList(
+		titlePanel("Summary"),
+		
+		column(
+			width = 2,
+			tableOutput("summary_table")
+		),
+		
+		column(
+			width = 10,
+			plotOutput("summary_plot")
+		)
+	)
+	
+}

### 2022-02-18 scripts/R/02_vocabulary.R

@@ -6,43 +6,22 @@ get_vocabulary <- function(
 	participants, # participants dataset (get_participants output)
 	update = FALSE, # update vocabulary data?
 	type = "understands", # vocabulary type (understands or produces)
-	impute = TRUE, # impute missing data?
 	vocabulary_oxf, # Oxford vocabulary data
 	multilex_data
 ){
 	suppressMessages({
 		
-		cdi_replacements <- c(
-			"boots" = "boot", "boot(s)" = "boot", "fire engine" = "fireengine",
-			"teddy bear" = "teddy", "bunny / rabbit" = "bunny",
-			"lorry / truck" = "truck", "bicycle / bike" = "bike"
-		)
+		
 		
 		# Barcelona vocabulary ----
-		# norms (by item)
-		vocab_items_bcn <- multilex_data$responses %>% 
-			rename(participant = id_exp) %>% 
-			mutate(
-				understands = response > 1,
-				age_group =  as.factor(
-					case_when(
-						between(age, 19, 24) ~ 21,
-						between(age, 24, 28) ~ 25,
-						between(age, 28, 34) ~ 30
-					)),
-				age_group = paste0(age_group, " months")
-			) %>%
-			filter(study=="CognatePriming", age_group != "NA months", understands) %>%
-			select(participant, time, age_group, item, response) %>%
-			group_by(participant, age_group) %>%
-			summarise(vocab_words = list(unique(item)), .groups = "drop")
+		participants_bcn <- participants %>% 
+			filter(location=="Barcelona") %>% 
+			select(participant, age_group, lp)
 		
-		# norms (by participant)
-		vocab_size_bcn <- multilex_data$vocabulary %>%
-			rename(participant = id_exp) %>% 
-			right_join(select(multilex_data$logs, participant, time)) %>% 
+		# vocabulary sizes multilex database and cognatepriming
+		to_impute <- multilex_data$vocabulary %>%
 			mutate(
-				age_group =  as.factor(
+				age_group = as.factor(
 					case_when(
 						between(age, 19, 24) ~ 21,
 						between(age, 24, 28) ~ 25,
@@ -50,75 +29,37 @@ get_vocabulary <- function(
 					)),
 				age_group = paste0(age_group, " months")
 			) %>%
-			filter(
-				age_group != "NA months",
[…]

### 2022-06-28 docs/00_participants.Rmd
Add tests

@@
 	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
 	drop_na(valid_participant) %>% 
-	count(location, age_group, lp) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
+	count(age_group, lp, valid_participant) %>% 
+	pivot_wider(
+		names_from = c("age_group", "valid_participant"),
+		values_from = c("n"), 
+		values_fill = 0
+	) %>% 
+	mutate(
+		`21 months` = paste0(`21 months_TRUE`, " (", `21 months_FALSE`, ")"),
+		`25 months` = paste0(`25 months_TRUE`, " (", `25 months_FALSE`, ")"),
+		`30 months` = paste0(`30 months_TRUE`, " (", `30 months_FALSE`, ")")
+
+	) %>% 
+	select(-c(ends_with("TRUE"), ends_with("FALSE"))) %>% 
+	gt() %>% 
+	tab_header(
+		title = "Testing sessions",
+		subtitle = "Invalid testing sessions are shown between parentheses"
+	) %>%
 	cols_label(
-		lp = md("**Language profile**"),
+		lp = "",
 		`21 months` = md("**21 months**"),
@@
 		`30 months` = md("**30 months**")
+	) %>% 
+	tab_style(
+		style = list(
+			cell_text(weight = "bold"),
+			cell_fill("grey82")
+		),
+		locations = list(
+			cells_row_groups()
+		)
 	)
@@
 ```{r participants_summary_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
-participants %>% 
+participants_tab <- participants %>% 
 	left_join(distinct(attrition, participant, valid_participant)) %>% 
-	filter(valid_participant) %>% 
 	drop_na(valid_participant) %>% 
-	count(location, age_group, lp, test_language) %>% 
-	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
-	gt(groupname_col = "location") %>% 
+	count(age_group, lp, test_language, valid_participant) %>% 
+	pivot_wider(
+		names_from = c("age_group", "valid_participant"),
+		values_from = c("n"), 
+		values_fill = 0
+	) %>% 
+	mutate(
+		`21 months` = paste0(`21 months_TRUE`, " (", `21 months_FALSE`, ")"),
+		`25 months` = paste0(`25 months_TRUE`, " (", `25 months_FALSE`, ")"),
+		`30 months` = paste0(`30 months_TRUE`, " (", `30 months_FALSE`, ")")
+
+	) %>% 
+	select(-c(ends_with("TRUE"), ends_with("FALSE"))) %>% 
+	gt(groupname_col = "lp") %>% 
 	cols_label(
 		lp = md("**Language profile**"),
-		test_language = md("**Language**"),
+		test_language = "",
 		`21 months` = md("**21 months**"),
@@
 	) %>% 
-	as_raw_html()
+	tab_style(
+		style = list(
+			cell_text(weight = "bold"),
+			cell_fill("grey82")
+		),
+		locations = list(
+			cells_row_groups()
+		)
+	)
+
+gtsave(participants_tab, here("img", "participants_tab.png"))
+as_raw_html(participants_tab)
 ```
@@
 	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = as.factor(test_language))) +
-	facet_grid(location~age_group, scales = "free") +
+	ggplot(aes(lp, fill = as.factor(lp))) +
+	facet_grid(~age_group, scales = "free") +
 	geom_bar(colour = NA) +
@@
 	theme(
-		legend.position = "top",
+		legend.position = "none",
 		axis.title.x = element_blank(),
@@
 	filter(valid_participant) %>% 
-	mutate(age_group = str_remove(age_group, " months")) %>%
-	ggplot(aes(age_group, participant, colour = lp)) +
-	facet_grid(~location, scales = "free") +
-	geom_line(aes(group = interaction(lp, participant))) +
-	geom_point(size = 2) +
-	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Lang. Pofile") +
+	count(participant, age_group) %>% 
+	pivot_wider(
+		id_cols = participant,
+		names_from = age_group,
+		values_from = n,
+		values_fill = 0
+	) %>% 
+	pivot_longer(
+		2:4,
+		names_to = "age_group",
+		values_to = "n"
+	) %>% 
+	ggplot() +
+	aes(
+		age_group,
+		participant,
+		fill = as.factor(n)
+	) + 
+	geom_tile(
+		colour = "white"
+	) +
+	labs(
+		x = "Age (months)", 
+		y = "Exposure to 2nd language", 
+		fill = "Lang. Pofile"
+	) +
+	scale_fill_manual(values = c("white", pal_d3()(2)[2])) +
 	theme(
@@
 		axis.title.y = element_blank(),
-		axis.text.y = element_blank(),
+		axis.text.y = element_text(size = 7),
 		axis.ticks.y = element_blank()
 	)
+
+ggsave(
+	here("img", "participants_longitudinal.png"),
+	height = 15,
+	width = 1.5
+)
+
 ```

### 2022-06-28 docs/01_stimuli.Rmd
Add tests

@@
 	knitr.duplicate.label = "allow",
-	ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
-	ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
+	ggplot2.discrete.fill = pal_d3()(4),
+	ggplot2.discrete.colour = pal_d3()(4)
 )
@@
 
-theme_set(theme_minimal()) # in utils.R
+theme_set(theme_custom()) # in utils.R
 ```
@@
 
-```{r stimuli_frequency_childes_prime, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
+```{r stimuli_frequency_childes_prime, echo=FALSE, fig.height=5, message=FALSE, warning=FALSE, out.width="80%", paged.print=TRUE}
 
 stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_prime_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "white", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
+	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
+	ggplot() +
+	aes(
+		x = trial_type, 
+		y = frequency_prime_childes, 
+		colour = trial_type, 
+		fill = trial_type
+	) +
+	facet_wrap(~test_language) +
+	geom_boxplot(
+		colour = "black",
+		fill = "white", 
+		size = 1, 
+		outlier.colour = NA,
+		width = 0.1
+	) + 
+	geom_point(
+		shape = 1, 
+		stroke = 1.25,
+		size = 3,
+		position = position_jitter(
+			width = 0.1,
+			seed = 888
+		)
+	) +
+	labs(
+		x = "Trial type", 
+		y = "Lexical frequency (Zipf score)",
+		colour = "Trial type", 
+		fill = "Trial type"
+	) +
 	theme(
 		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
 		axis.title.x = element_blank(),
-		panel.grid.major.x = element_blank(),
 		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
-		plot.caption = element_text(size = 10, hjust = 0),
 	)
+
+ggsave(here("img", "stimuli_frequency_prime_childes.png"))
 
@@
 stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language) +
-	geom_violin() +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
-	# geom_jitter(colour = "black", size = 1, shape = 1,
-	# 			width = 0.1, alpha = 0.5, stroke = 1) +
-	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", fill = "Trial type") +
+	distinct(
+		test_language, 
+		target,
+		prime,
+		.keep_all = TRUE
+	) %>% 
+	ggplot() +
+	aes(
+		x = trial_type, 
+		y = frequency_target_childes, 
+		colour = trial_type,
+		fill = trial_type
+	) + 
+	facet_wrap(~test_language) +
+	geom_boxplot(
+		colour = "black", 
+		fill = "white",
+		size = 1,
+		outlier.colour = NA, 
+		width = 0.1
+	) +
+	geom_point(
+		shape = 1, 
+		stroke = 1.25,
+		size = 3,
+		position = position_jitter(
+			width = 0.1,
+			seed = 888
+		)
+	) +
+	labs(
+		x = "Trial type",
+		y = "Lexical frequency (Zipf score)",
+		colour = "Trial type",
+		fill = "Trial type"
+	) +
 	theme(
 		legend.position = "none",
-		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
 		axis.title.x = element_blank(),
-		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid.major.x = element_blank()
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
+	)
 
-	)
+ggsave(here("img", "stimuli_frequency_target_childes.png"))
+
 ```
@@
 means <- stimuli %>% 
-	distinct(location, test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, location, trial_type) %>% 
+	distinct(test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
+	group_by(test_language, trial_type) %>% 
 	summarise(
@@
 stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
+	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
 	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
-	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type,
-			   xmin = familiarity_prime-familiarity_se_prime, xmax = familiarity_prime-familiarity_se_prime)) +
-	facet_wrap(location~test_language, scales = "free_y") +
-	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
-	# geom_errorbar() +
+	ggplot() +
+	aes(
+		familiarity_prime, 
+		reorder(prime, familiarity_prime),
+		colour = trial_type, 
+		fill = trial_type,
+		xmin = familiarity_prime-familiarity_se_prime,
+		xmax = familiarity_prime+familiarity_se_prime
+	) +
+	facet_wrap(~test_language, scales = "free_y") +
+	geom_vline(
+		data = means, 
+		aes(
+			xintercept = familiarity_prime, 
+			colour = trial_type
+		),
+		size = 1
+	) +
+	geom_errorbar(width = 0) +
 	geom_point() +
-	labs(x = "% of infants that understand", y = "Prime word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
+	labs(
+		x = "% of infants that understand",
+		y = "Prime word",
+		colour = "Trial type", 
+		fill = "Trial type"
+	) +
+	scale_x_continuous(
+		labels = percent,
+		limits = c(0, 1)
+	) +
+	theme_custom() +
 	theme(
@@
 		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
+		axis.text.y = element_text(size = 7),
 		axis.title.y = element_blank(),
-		panel.grid.major.y = element_blank(),
+		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
 		plot.caption = element_text(size = 10, hjust = 0),
 	)
+
+ggsave(here("img", "stimuli_familiarity_prime.png"))
 
@@
 stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
-	facet_wrap(location~test_language, scales = "free_y") +
+	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
+	ggplot() +
+	aes(
+		x = familiarity_target, 
+		y = reorder(target, familiarity_target), 
+		colour = trial_type,
+		fill = trial_type,
+		xmin = familiarity_target-familiarity_se_target,
+		xmax = familiarity_target+familiarity_se_target
+	) +
+	facet_wrap(
+		~test_language, 
+		scales = "free_y"
+	) +
 	# geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
-	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
-	# geom_errorbar() +
-	geom_point() +
-	labs(x = "% of infants that understand", y = "Target word",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
+	geom_vline(
+		data = means,
+		aes(
+			xintercept = familiarity_target,
+			colour = trial_type
+		), 
+		size = 1
+	) +
+	geom_errorbar(width = 0) +
+	geom_point(
+		shape = 1,
+		size = 0.5,
+		stroke = 1
+	) +
+	labs(
+		x = "% of infants that understand",
+		y = "Target word",
+		colour = "Trial type",
+		fill = "Trial type"
+	) +
+	scale_x_continuous(
+		labels = percent,
+		limits = c(0, 1)
+	) +
 	# scale_y_reordered() +
+	theme_custom() +
 	theme(
@@
 		legend.title = element_blank(),
-		axis.text = element_text(size = 7),
+		axis.text.y = element_text(size = 7),
 		axis.title.y = element_blank(),
@@
 	)
+ggsave(here("img", "stimuli_familiarity_target.png"))
 
@@
 animacy <- stimuli %>%
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), names_to = "role", values_to = "is_animate") %>% 
+	distinct(
+		test_language, 
+		target, 
+		prime, 
+		.keep_all = TRUE
+	) %>% 
+	pivot_longer(
+		c(is_animate_prime, is_animate_target), 
+		names_to = "role",
+		values_to = "is_animate"
+	) %>% 
 	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(location, test_language, trial_type, role, is_animate) %>% 
+	count(
+		test_language, 
+		trial_type,
+		role,
+		is_animate
+	) %>% 
 	drop_na(is_animate) %>% 
@@
 	filter(role=="Prime") %>% 
-	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
+	ggplot() +
+	aes(
+		x = trial_type, 
+		y = n, 
+		fill = is_animate,
+		colour = is_animate
+	) + 
+	facet_wrap(~test_language, ncol = 4) +
 	geom_col(position = position_fill()) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	labs(title = "Prime", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
+	geom_hline(
+		yintercept = 0.5, 
+		size = 1,
+		colour = "grey"
+	) +
+	labs(
+		title = "Prime", 
+		x = "Trial type", 
+		y = "# trials",
+		colour = "Animacy", 
+		fill = "Animacy"
+	) +
 	scale_y_continuous(labels = percent) +
@@
 	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
-	facet_wrap(location~test_language, ncol = 4) +
+	facet_wrap(~test_language, ncol = 4) +
 	geom_col(position = position_fill()) +
@@
 
+ggsave(here("img", "stimuli_animacy.png"))
+
 ```
@@
 stimuli %>% 
-	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
+	distinct(
+		test_language, 
+		target, 
+		prime,
+		.keep_all = TRUE
+	) %>% 
+	pivot_longer(
+		c(category_prime, category_target),
+		names_to = "role",
+		values_to = "category"
+	) %>% 
 	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
-	drop_na(trial_type, category) %>% 
-	count(trial_type, test_language, location, role, category) %>% 
-	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
-	facet_wrap(role~location~test_language) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "% of trials", y = "Trial type",
-		 colour = "Trial type", fill = "Trial type") +
-	scale_x_continuous(labels = percent) +
+	drop_na(
+		trial_type,
+		category
+	) %>% 
+	count(
+		trial_type, 
+		test_language, 
+		role, 
+		category,
+		name = "sum"
+	) %>% 
+	right_join(
+		expand(
+			.,
+			trial_type, 
+			test_language, 
+			role, 
+			category
+		)
+	) %>%
+	replace_na(list(sum = 0)) %>% 
+	group_by(trial_type, test_language, role) %>% 
+	mutate(
+		n =  sum(sum),
+		prop = sum/n
+	) %>% 
+	ungroup() %>% 
+	ggplot() +
+	aes(
+		x = prop,
+		y = reorder_within(category, desc(prop), list(trial_type, role, test_language)),
+		fill = test_language,
+		order = prop
+	) + 
+	facet_wrap(
+		trial_type~role~test_language,
+		scales = "free_y", labeller = label_wrap_gen(multi_line = FALSE)
+	) +
+	geom_col(
+		colour = "white",
+		position = position_dodge(),
+		width = 1
+	) +
+	labs(
+		x = "% of trials",
+		y = "Trial type",
+		colour = "Trial type",
+		fill = "Trial type"
+	) +
+	scale_fill_d3(palette = "category10") +
+	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
+	scale_y_reordered() +
 	theme(
-		legend.position = "top",
+		legend.position = "none",
 		legend.title = element_blank(),
-		axis.text = element_text(size = 9),
+		axis.text.y = element_text(size = 9, hjust = 1),
+		axis.text.x = element_text(size = 8, hjust = 1),
 		axis.title.y = element_blank(),
+		axis.ticks.y = element_blank(),
 		plot.caption = element_text(size = 10, hjust = 0),
-		panel.grid = element_blank()
-
+		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
+		strip.text = element_text(size = 10)
 	)
 
+ggsave(here("img", "stimuli_animacy.png"), width = 15)
+
 ```

### 2022-06-28 docs/02_vocabulary.Rmd
Add tests

@@
 	knitr.duplicate.label = "allow",
-	ggplot2.discrete.fill = ggsci::pal_futurama()(7),
-	ggplot2.discrete.slab_color = ggsci::pal_futurama()(7),
-	ggplot2.discrete.colour = ggsci::pal_futurama()(7)
+	ggplot2.discrete.fill = ggsci::pal_d3()(4),
+	ggplot2.discrete.slab_color = ggsci::pal_d3()(4),
+	ggplot2.discrete.colour = ggsci::pal_d3()(4)
 )
@@
 	left_join(vocabulary) %>% 
-	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed")) %>% 
-	filter(location=="Barcelona")
+	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"))
+
 ```
@@
 sample_size <- participants %>% 
-	filter(participant %in% fit_l1_4$data$participant) %>% 
-	count(age_group, location)
+	filter(participant %in% fit_3$data$participant) %>% 
+	count(age_group)
 
@@
 	filter(
-		participant %in% fit_l1_4$data$participant
+		participant %in% fit_3$data$participant
 	) %>% 
-	count(age_group, lp, location) %>% 
+	count(age_group, lp) %>% 
 	mutate(
@@
 	ggplot() +
+	aes(
+		lp, 
+		vocab_size_l1,
+		colour = lp,
+		fill = lp
+	) +
 	facet_wrap(~age_group, scales = "free_x") +
 	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
+	stat_slab(
+		aes(side = ifelse(lp=="Monolingual", "left", "right")),
+		colour = "white",
+		alpha = 0.5
+	) +
 	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = is_imputed),
 		position = position_dodge(width = 1),
-		width = 0.25,
-		size = 1
+		width = 0.15,
+		size = 1,
+		colour = "black",
+		fill = "white",
+		outlier.colour = NA
 	) +
 	geom_point(
-		aes(lp, vocab_size_l1, color = is_imputed),
-		size = 1,
+		aes(lp, vocab_size_l1),
+		size = 2,
+		shape = 1,
+		stroke = 1,
 		alpha = 0.75,
-		position = position_jitter(width = 0.1, seed = 888)
+		position = position_jitterdodge(
+			jitter.width = 0.8, 
+			seed = 888, 
+			dodge.width = 0.5
+		)
 	) +
@@
 		show.legend = FALSE, 
-		position = position_dodge(width = 2)
+		position = position_dodge(width = 2),
+		inherit.aes = FALSE
 	) +
@@
 	) +
-	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
+	scale_y_continuous(
+		limits = c(0, 1),
+		labels = percent
+	) +
+	theme_custom() +
 	theme(
 		legend.title = element_blank(),
-		legend.position = "top",
-		panel.border = element_rect(fill = NA, colour = "grey", size = 1),
+		legend.position = "none",
 		panel.grid.major.x = element_blank(),
@@
 ```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(participant %in% fit_total_4$data$participant) %>% 
-	count(age_group, location)
-
-sample_size_lp <- participants %>% 
-	filter(participant %in% fit_total_4$data$participant) %>% 
-	count(age_group, lp, location) %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		)
-	)
 
@@
 	ggplot() +
+	aes(
+		lp, 
+		vocab_size_total,
+		colour = lp,
+		fill = lp
+	) +
 	facet_wrap(~age_group, scales = "free_x") +
 	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
+	stat_slab(
+		aes(side = ifelse(lp=="Monolingual", "left", "right")),
+		colour = "white",
+		alpha = 0.5
+	) +
 	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = is_imputed),
 		position = position_dodge(width = 1),
-		width = 0.25,
-		size = 1
+		width = 0.15,
+		size = 1,
+		colour = "black",
+		fill = "white",
+		outlier.colour = NA
 	) +
 	geom_point(
-		aes(lp, vocab_size_l1, color = is_imputed),
-		size = 1,
+		aes(lp, vocab_size_total),
+		size = 2,
+		shape = 1,
+		stroke = 1,
 		alpha = 0.75,
-		position = position_jitter(width = 0.1, seed = 888)
+		position = position_jitterdodge(
+			jitter.width = 0.8, 
+			seed = 888, 
+			dodge.width = 0.5
+		)
 	) +
@@
 	scale_y_continuous(limits = c(0, 1), labels = percent) +
+	theme_custom() +
 	theme(
 		legend.title = element_blank(),
-		legend.position = "top",
+		legend.position = "none",
 		panel.grid.major.x = element_blank(),
@@
 ```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
-sample_size <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_conceptual)) %>% 
-	count(age_group, location)
-
-sample_size_lp <- participants %>% 
-	filter(valid_participant, !is.na(vocab_size_total)) %>% 
-	count(age_group, lp, location) %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		)
-	)
 
@@
 	ggplot() +
+	aes(
+		lp, 
+		vocab_size_conceptual,
+		colour = lp,
+		fill = lp
+	) +
 	facet_wrap(~age_group, scales = "free_x") +
 	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
+	stat_slab(
+		aes(side = ifelse(lp=="Monolingual", "left", "right")),
+		colour = "white",
+		alpha = 0.5
+	) +
 	geom_boxplot(
-		aes(lp, vocab_size_l1, colour = is_imputed),
 		position = position_dodge(width = 1),
-		width = 0.25,
-		size = 1
+		width = 0.15,
+		size = 1,
+		colour = "black",
+		fill = "white",
+		outlier.colour = NA
 	) +
 	geom_point(
-		aes(lp, vocab_size_l1, color = is_imputed),
-		size = 1,
+		aes(lp, vocab_size_conceptual),
+		size = 2,
+		shape = 1,
+		stroke = 1,
 		alpha = 0.75,
-		position = position_jitter(width = 0.1, seed = 888)
+		position = position_jitterdodge(
+			jitter.width = 0.8, 
+			seed = 888, 
+			dodge.width = 0.5
+		)
 	) +
@@
 		show.legend = FALSE, 
-		position = position_dodge(width = 2)
+		position = position_dodge(width = 2),
+		inherit.aes = FALSE
 	) +
 	labs(
-		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
+		y = "Conceptual vocabulary", 
+		x = "Group",
+		fill = "Group",
+		colour = "Group",
 		title = "Conceptual vocabulary size",
@@
 	) +
-	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
+
+	scale_y_continuous(
+		limits = c(0, 1), 
+		labels = percent
+	) +
+	theme_custom() +
 	theme(
 		legend.title = element_blank(),
-		legend.position = "top",
+		legend.position = "none",
 		panel.grid.major.x = element_blank(),
@@
 
+ggsave(here("img", "vocab_conceptual.png"))
+
 ```

### 2022-06-28 docs/05_attrition.Rmd
Add tests

@@
 
-theme_set(theme_minimal()) # in utils.R
+theme_set(theme_custom()) # in utils.R
 
@@
 	) %>% 
-	ggplot(aes(lp, fill = valid_status)) +
-	facet_grid(location~age_group, scales = "free") +
+	ggplot() +
+	aes(lp, fill = valid_status) +
+	facet_grid(~age_group, scales = "free") +
 	geom_bar(size = 1) +
-	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
+	geom_hline(
+		yintercept = 24,
+		linetype = "dashed",
+		colour = "white"
+	) +
 	scale_colour_brewer(palette = "Set1") +
@@
 attrition_location <- attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, lp, age_group, trial_type, valid_status) %>% 
+	left_join(select(participants, participant, lp)) %>% 
+	count(lp, age_group, trial_type, valid_status) %>% 
 	drop_na(trial_type)
@@
 attrition_location %>% 
-	filter(location=="Barcelona") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
+	ggplot() +
+	aes(
+		trial_type, 
+		n,
+		fill = valid_status, 
+		colour = valid_status
+	) +
 	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Barcelona") +
-
-	attrition_location %>% 
-	filter(location=="Oxford") %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(lp~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity", title = "Oxford") +
-
-	plot_layout(guides = "collect", ncol = 1) &
-	scale_y_continuous(labels = percent) &
-	coord_flip() &
+	geom_col(
+		position = position_fill(), 
+		colour = "white"
+	) +
+	labs(
+		x = "Trial type", 
+		y = "Trials",
+		colour = "Validity", 
+		fill = "Validity"
+	) +
+	scale_y_continuous(labels = percent) +
 	theme(
 		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid = element_blank(),
-		axis.text.x = element_text(size = 10),
-		axis.text.y = element_text(size = 10),
-		axis.title = element_blank()
+		axis.title.x = element_blank()
 	)
+
+ggsave(here("img", "attrition_participants.png"))
+
 ```
@@
 
-left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
-	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
+attrition %>% 
+	left_join(select(participants, age_group, lp, participant, date_test)) %>% 
+	group_by(participant, lp, trial_type, date_test, age_group, valid_participant) %>% 
+	summarise(
+		valid_trial_count = sum(valid_trial, na.rm = TRUE),
+		.groups = "drop"
+	) %>% 
 	pivot_wider(
@@
 	clean_names() %>% 
-	group_by(lp, location, age_group) %>% 
+	group_by(lp, age_group) %>% 
 	summarise(
@@
 	) %>% 
-	arrange(age_group, lp, location) %>% 
-	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
-	gt() %>% 
+	arrange(age_group, lp) %>% 
+	relocate(age_group, lp, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
+	gt(groupname_col = "age_group") %>% 
 	tab_spanner(
@@
 		age_group = "Age",
-		lp = "Group",
+		lp = "",
 		sum_n = "Valid",
-		location = "Laboratory",
 		n = "Tested",
@@
 	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
+	tab_style(
+		style = cell_text(weight = "bold"),
+		locations = list(
+			cells_row_groups(),
+			cells_column_spanners()
+		)
+	)
 as_raw_html()
@@
 # plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+tab_participant_attrition <- attrition %>% 
+	left_join(select(participants, participant, lp)) %>% 
 	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
-	group_by(location, participant, lp, age_group, valid_participant) %>% 
+	group_by(participant, lp, age_group, valid_participant) %>% 
 	summarise(
@@
 	relocate(participant) %>% 
-	gt() %>% 
+	gt(groupname_col = "participant") %>% 
 	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
@@
 		participant = "Participant",
-		location = "Location",
-		lp = "Lang. Profile",
+		lp = "Group",
 		age_group = "Age",
@@
 	fmt_percent(c("valid", "invalid_gaze")) %>% 
-	as_raw_html()
+	tab_style(
+		style = cell_text(weight = "bold"),
+		locations = list(
+			cells_column_labels()
+		)
+	) %>% 
+	tab_style(
+		style = cell_text(style = "italic"),
+		locations = list(
+			cells_row_groups()
+		)
+	)
+
+gtsave(tab_participant_attrition, here("img", "participants_attrition_table.png"))
+as_raw_html(tab_participant_attrition)
 ```
@@
 # plot participants
-attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
+tab_n_trials <- attrition %>% 
+	left_join(select(participants, participant, lp)) %>% 
 	drop_na(trial_type) %>% 
-	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
+	group_by(lp, age_group, trial_type, valid_trial) %>% 
 	count() %>% 
 	ungroup() %>%
-	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
-	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
+	mutate(
+		valid_trial = ifelse(
+			valid_trial,
+			"Valid",
+			"Not valid"
+		)
+	) %>% 
+	pivot_wider(
+		names_from = c(age_group, valid_trial), 
+		values_from = n,
+		values_fill = 0
+	) %>% 
 	clean_names() %>% 
-	gt(groupname_col = c("location", "lp")) %>% 
-	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
-	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
-	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
+	gt(groupname_col = "lp") %>% 
+	tab_spanner(
+		label = "21 months", 
+		columns = contains("21_")
+	) %>% 
+	tab_spanner(
+		label = "25 months", 
+		columns = contains("25_")
+	) %>% 
+	tab_spanner(
+		label = "30 months", 
+		columns = contains("30_")
+	) %>% 
 	cols_label(
-		location = "Location",
 		lp = "Group",
@@
 	) %>% 
-	as_raw_html()
+	tab_style(
+		style = list(
+			cell_text(weight = "bold")
+		),
+		locations = list(
+			cells_column_spanners()
+		)
+	) %>% 
+	tab_style(
+		style = list(
+			cell_text(style = "italic")
+		),
+		locations = list(
+			cells_row_groups()
+		)
+	)
+
+gtsave(tab_n_trials, here("img", "attrition_trials.png"))
+
+as_raw_html(tab_n_trials)
 
@@
 attrition %>% 
-	left_join(select(participants, participant, location)) %>% 
-	count(location, age_group, trial_type, valid_status) %>% 
+	left_join(select(participants, participant)) %>% 
+	count(age_group, trial_type, valid_status) %>% 
 	drop_na(trial_type) %>% 
-	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
-	facet_grid(location~age_group) +
+	ggplot() +
+	aes(
+		trial_type,
+		n,
+		fill = valid_status, 
+		colour = valid_status
+	) +
+	facet_grid(~age_group) +
 	geom_col(position = position_fill(), colour = "white") +
@@
 sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
+	left_join(distinct(participants, participant, age_group, lp)) %>% 
+	left_join(distinct(stimuli, test_language, list, trial, trial_type, frequency_target_childes)) %>% 
 	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
@@
 attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	left_join(distinct(stimuli, test_language, list, trial, trial_type, frequency_target_childes)) %>% 
+	mutate(
+		valid_status = ifelse(
+			valid_status != "Valid", 
+			"Invalid", 
+			valid_status
+		)
+	) %>% 
 	drop_na(trial_type, frequency_target_childes) %>% 
-	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
+	ggplot() +
+	aes(
+		trial_type,
+		frequency_target_childes,
+		fill = valid_status,
+		colour = valid_status
+	) +
 	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "white", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "white") +
-	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
-	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
+	geom_boxplot(
+		fill = "white", 
+		width = 0.25,
+		position =  position_dodge(width = 1),
+		size = 0.75, 
+		outlier.colour = NA
+	) +
+	geom_label(
+		data = sample_size, 
+		aes(
+			y = 2,
+			label = format(n, big.mark = ",", scientific = FALSE)
+		), 
+		size = 3,
+		position = position_dodge(width = 1), 
+		colour = "white"
+	) +
+	labs(
+		x = "Trial type",
+		y = "Frequency (CHILDES)", 
+		colour = "Validity", 
+		fill = "Validity"
+	) +
+	scale_y_continuous(
+		breaks = 0:7, 
+		limits = c(0, 7)
+	) +
 	theme(
@@
 		legend.title = element_blank(),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
 		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
+		axis.title.x = element_blank()
 	)
+
+ggsave(here("img", "attrition_frequency_childes.png"))
+
 ```
@@
 attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
-	drop_na(trial_type, frequency_target_childes) %>% 
+	left_join(
+		distinct(
+			stimuli, 
+			test_language,
+			list, 
+			trial, 
+			trial_type,
+			frequency_target_childes
+		)
+	) %>% 
+	drop_na(
+		trial_type,
+		frequency_target_childes
+	) %>% 
 	mutate(frequency_target_childes = round(frequency_target_childes)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, frequency_target_childes) %>% 
-	ggplot(aes(as.factor(frequency_target_childes), n, fill = valid_status, colour = valid_status)) +
+	count(
+		trial_type,
+		age_group, 
+		valid_status, 
+		trial_type,
+		frequency_target_childes
+	) %>% 
+	ggplot() +
+	aes(
+		as.factor(frequency_target_childes),
+		n, 
+		fill = valid_status, 
+		colour = valid_status
+	) + 
 	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	geom_col(
+		position = position_fill(), 
+		colour = "white"
+	) +
+	labs(
+		x = "Trial type",
+		y = "Trials", 
+		colour = "Validity",
+		fill = "Validity"
+	) +
+	guides(
+		fill = guide_legend(ncol = 2), 
+		colour = guide_legend(ncol = 2)
+	)	+
 	scale_y_continuous(labels = percent) +
@@
 		axis.text.y = element_text(size = 8),
-		axis.title = element_blank()
 	)
+
+ggsave(here("img", "attrition_frequency_target_childes.png"))
 ```
@@
 sample_size <- attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
+	left_join(distinct(participants, participant, age_group, lp)) %>% 
+	left_join(distinct(stimuli, test_language, list, trial, trial_type, familiarity_target)) %>% 
 	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
@@
 attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
+	left_join(distinct(stimuli, test_language, list, trial, trial_type, familiarity_target)) %>% 
+	mutate(
+		valid_status = ifelse(
+			valid_status!="Valid",
+			"Invalid",
+			valid_status
+		)
+	) %>% 
 	drop_na(trial_type, familiarity_target) %>% 
-	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
+	ggplot() +
+	aes(
+		trial_type,
+		familiarity_target,
+		fill = valid_status, 
+		colour = valid_status
+	) +
 	facet_grid(lp~age_group) +
-	geom_boxplot(fill = "white", width = 0.25,
-				 position =  position_dodge(width = 0.5),
-				 size = 0.75, outlier.colour = NA) +
-	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
-			   position = position_dodge(width = 0.7), colour = "white") +
-	labs(x = "Trial type", y = "Familiarity", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_y_continuous(labels = percent, limits = c(0, 1)) +
+	geom_boxplot(
+		colour = "black",
+		width = 0.25,
+		position = position_dodge(width = 0.9),
+		size = 0.75, 
+		outlier.colour = NA
+	) +
+	geom_label(
+		data = sample_size, 
+		aes(
+			y = 0.1,
+			label = format(n, big.mark = ",")
+		),
+		size = 3,
+		position = position_dodge(width = 0.9),
+		colour = "white"
+	) +
+	labs(
+		x = "Trial type",
+		y = "Familiarity", 
+		colour = "Validity", 
+		fill = "Validity"
+	) +
+	guides(
+		fill = guide_legend(ncol = 2), 
+		colour = guide_legend(ncol = 2)
+	)	+
+	scale_y_continuous(
+		labels = percent, 
+		limits = c(0, 1)
+	) +
 	theme(
@@
 	)
+
+ggsave(here("attrition_familiarity.png"))
 ```

### 2022-06-28 docs/06_results.Rmd
Add tests

@@
 
-	# 3-way interactions
-	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
-		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
-
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
-		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
-		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
-		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
-		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",
-
-	# 2-way interactions
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
-	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (total)",
-
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+	# cubic terms ----
+	"b_Itime_bin_centerE3:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_Itime_bin_centerE3:trial_typerelated_unrelated:lpLPMonvs.Bil" = 
 		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
+
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil" =
+		"Group (ML vs. BL)",
+
+	"b_Itime_bin_centerE3:trial_typecognate_noncognate" = 
+		"Trial type (C vs. NC)",
+
+	"b_Itime_bin_centerE3:trial_typerelated_unrelated" = 
+		"Trial type (U vs. C+NC)",
+
+	"b_Itime_bin_centerE3" = 
+		"Main effect",
+
+	# quadratic terms ----
+	"b_Itime_bin_centerE2:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
 		"Trial type (C vs. NC) \u00d7 Group",
 
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
-	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" =
-		"Trial type (C vs. NC) \u00d7 Vocab (total)",
-
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" =
+	"b_Itime_bin_centerE2:trial_typerelated_unrelated:lpLPMonvs.Bil" = 
 		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_time_bin_center:lpLPMonvs.Bil:vocab_size_total_center" =
-		"Group \u00d7 Vocab (total)",
-
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (total)",
-
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil" =
+		"Group (ML vs. BL)",
+
+	"b_Itime_bin_centerE2:trial_typecognate_noncognate" = 
+		"Trial type (C vs. NC)",
+
+	"b_Itime_bin_centerE2:trial_typerelated_unrelated" = 
+		"Trial type (U vs. C+NC)",
+
+	"b_Itime_bin_centerE2" = 
+		"Main effect",
+
+	# linear terms ----
+	"b_time_bin_center:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+
+	"b_time_bin_center:trial_typerelated_unrelated:lpLPMonvs.Bil" = 
 		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil" =
+
+	"b_time_bin_center:lpLPMonvs.Bil" =
+		"Group (ML vs. BL)",
+
+	"b_time_bin_center:trial_typecognate_noncognate" = 
+		"Trial type (C vs. NC)",
+
+	"b_time_bin_center:trial_typerelated_unrelated" = 
+		"Trial type (U vs. C+NC)",
+
+	"b_time_bin_center" = 
+		"Main effect",
+
+	# marginal terms ----
+	"b_trial_typecognate_noncognate:lpLPMonvs.Bil" = 
 		"Trial type (C vs. NC) \u00d7 Group",
 
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (total)",
-
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
+	"b_trial_typerelated_unrelated:lpLPMonvs.Bil" = 
 		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_Itime_bin_centerE2:lpLPMonvs.Bil:vocab_size_total_center" = 
-		"Group \u00d7 Vocab (total)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (total)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
-		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
-		"Trial type (C vs. NC) \u00d7 Group",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (total)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
-		"Trial type (U vs. C+NC) \u00d7 Group",  
-	"b_Itime_bin_centerE3:lpLPMonvs.Bil:vocab_size_total_center" = 
-		"Group \u00d7 Vocab (total)",
-
-	# main effects (linear)
-	"b_time_bin_center:trial_typePrimeUvs.CPNC" =
+
+	"b_lpLPMonvs.Bil" = 
+		"Group (ML vs. BL)",
+
+	"b_trial_typecognate_noncognate" =
+		"Trial type (C vs. NC)",
+
+	"b_trial_typerelated_unrelated" =
 		"Trial type (U vs. C+NC)",
-	"b_time_bin_center:trial_typePrimeNCvs.C" = 
-		"Trial type (C vs. NC)",
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC" = 
-		"Trial type (U vs. C+NC)",
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C" = 
-		"Trial type (C vs. NC)",
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" = 
-		"Trial type (U vs. C+NC)",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" = 
-		"Trial type (C vs. NC)",
-
-	"b_time_bin_center:lpLPMonvs.Bil" = 
-		"Group (Mon. vs. Bil.)",
-	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
-		"Group (Mon. vs. Bil.)",
-	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
-		"Group (Mon. vs. Bil.)",
-
-	"b_time_bin_center:vocab_size_total_center" = 
-		"Vocab. (total, +1 SD)",
-	"b_Itime_bin_centerE2:vocab_size_total_center" = 
-		"Vocab. (total, +1 SD)",
-	"b_Itime_bin_centerE3:vocab_size_total_center" = 
-		"Vocab. (total, +1 SD)",
-
-	# 3-way interaction linear effects
-	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
-		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",
-	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" =
-		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",
-
-	# 2-way interaction linear effects
-	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
-		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
-		"Trial type (C vs. NC) \u00d7 Group",
-
-	"b_trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab. (total, +1 SD)",
-	"b_trial_typePrimeNCvs.C:vocab_size_total_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab. (total, +1 SD)",
-
-	"b_lpLPMonvs.Bil:vocab_size_total_center" =
-		"Group \u00d7 Vocab. (total, +1 SD)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" =
-		"Trial type (U vs. C+NC)",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" =
-		"Trial type (C vs. NC)",
-
-	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
-		"Group (Mon. vs. Bil.)",
-
-	# main linear effects
+
 	"b_Intercept" = "Intercept",
-	"b_Itime_bin_centerE2" = "Time bin 2",
-	"b_Itime_bin_centerE3" = "Time bin 3",
-	"b_time_bin_center" = "Time bin",
-	"b_vocab_size_total_center" = "Vocab. (total, +1 SD)",
-
-	"b_trial_typePrimeUvs.CPNC" = "Trial type (U vs. C+NC)",
-	"b_trial_typePrimeNCvs.C" = "Trial type (C vs. NC)",
-	"b_lpLPMonvs.Bil" = "Group (Mon. vs. Bil.)",
 
@@
 
-draws <- gather_draws(fit_total_4, `b_.*`, `sigma`, regex = TRUE) %>% 
+draws <- gather_draws(fit_2, `b_.*`, `sigma`, regex = TRUE) %>% 
 	mutate(
@@
 		cells_row_groups()
-	) %>% 
+	) 
 as_raw_html()
@@
 
-draws_intercept <- draws %>% 
+draws %>% 
 	filter(str_detect(.variable, "Intercept")) %>% 
@@
 	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
-	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(0.95, 0.8, 0.5), labels = percent_format()))),
-		size = 0.5,
-		color = "#FF6F00FF",
-		fill = "#FF6F00FF"
-	) +
+	stat_pointinterval() +
 	labs(
@@
 	guides(fill = "none", color = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
 	scale_fill_brewer(direction = -1, na.translate = FALSE) +
@@
 
-draws_predictors <- draws %>% 
-	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
-	ggplot(aes(.value, .variable_name)) +
-	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
-	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
-		size = 0.5, 
-		color = "#C71000FF", 
-		fill = "#C71000FF") +
+draws %>% 
+	filter(
+		str_detect(
+			.variable, 
+			"sigma|sd|time_bin", 
+			negate = TRUE
+		)
+	) %>% 
+	ggplot() +
+	aes(
+		x = .value, 
+		y = .variable_name,
+		colour = .variable_name
+	) +
+	geom_vline(
+		xintercept = 0,
+		colour = "black", 
+		linetype = "dashed"
+	) +
+	stat_pointinterval() +
 	labs(
@@
 	) +
-	guides(fill = "none", color = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2)) +
+	guides(
+		fill = "none", 
+		color = "none"
+	) +
+	scale_color_d3() +
+	scale_x_continuous(
+		labels = percent,
+		limits = c(-0.45, 1)
+	) +
 	theme(
@@
 
-draws_time <- draws %>%
+```
+
+```{r main_effects_plot_time, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}
+
+draws %>%
 	filter(str_detect(.variable, "time_bin")) %>% 
-	ggplot(aes(.value, .variable_name)) +
-	facet_wrap(~type, scales = "free_x") +
-	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
-	# stat_slab(
-	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
-	# 	size = 0.5, 
-	# 	color = "#008EA0FF", 
-	# 	fill = "#008EA0FF"
-	# ) +
+	ggplot() +
+	aes(
+		x = .value, 
+		y = .variable_name,
+		colour = type
+	) +
+	facet_wrap(
+		~type, 
+		scales = "free_x"
+	) +
+	geom_vline(
+		xintercept = 0,
+		colour = "black",
+		linetype = "dashed"
+	) +
 	stat_pointinterval(
-		color = "#008EA0FF",
-		fill = "#008EA0FF",
 		point_size = 1.5
@@
 	) +
+	scale_color_d3() +
 	guides(fill = "none", color = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent) +
-	theme(
-		axis.title.y = element_blank()
-	)
-
-draws_sigma <- draws %>% 
+	scale_x_continuous(labels = ~percent(., accuracy = 0.1)) +
+	theme(
+		axis.title.y = element_blank(),
+		panel.border = element_rect(fill = NA, colour = "grey", size = 0.75),
+		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
+	)
+
+```
+
+```{r main_effects_plot_sigma, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}
+
+draws %>% 
 	filter(str_detect(.variable, "sigma")) %>% 
-	ggplot(aes(.value, .variable_name)) +
-	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
-		size = 0.5, 
-		color = "#8A4198FF", 
-		fill = "#8A4198FF"
-	) +
+	ggplot(
+		aes(.value, 
+			.variable_name
+		)
+	) +
+	stat_pointinterval() +
 	labs(
@@
 	guides(fill = "none", color = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(0.92, 0.97)) +
+	scale_x_continuous(labels = percent, limits = c(0.7, 0.72)) +
 	theme(
@@
 
-((draws_intercept / draws_sigma / guide_area()) | draws_predictors) /
-	draws_time + 
-	plot_layout(heights = c(0.5, 0.5)) &
-	guides(fill = "none", color = "none") &
-	theme(
-		panel.background = element_rect(fill = NA, colour = "grey"),
-		axis.text.y = element_text(size = 7),
-		axis.text.x = element_text(size = 7),
-		axis.title = element_blank(),
-		legend.position = c(1, 1.2),
-		legend.direction = "horizontal",
-		legend.justification = "right",
-		legend.key.size = unit(0.35, "cm"),
-		legend.text = element_text(size = 7),
-		legend.title = element_text(size = 7),
-		panel.grid.major.y = element_blank()
-	)
-
 ```
@@
 
-corr_mat <- VarCorr(fit_total_4, summary = TRUE)$participant$cor 
-corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$participant$cor)
+corr_mat <- VarCorr(fit_2, summary = TRUE)$participant$cor 
+corr_names <- rownames(VarCorr(fit_2, summary = TRUE)$participant$cor)
 
@@
 	as.data.frame() %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
+	pivot_longer(
+		-term1, 
+		names_to = "term2",
+		values_to = ".value"
+	) %>% 
 	drop_na(.value)
 
-post_cors_participant <- corr_data %>% 
+corr_data %>% 
 	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
@@
 	coord_equal() +
-	theme(
-		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
-	)
-
-# correlations by item
-corr_mat <- VarCorr(fit_total_4, summary = TRUE)$target$cor 
-corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$target$cor)
-
-corr_mat <- corr_mat %>% 
-	as_tibble() %>% 
-	select(matches("Estimate")) %>% 
-	rename_all(str_remove, "Estimate.") %>% 
-	mutate(term1 = corr_names)
-
-corr_mat[lower.tri(corr_mat)] <- NA
-
-corr_data <- corr_mat %>% 
-	as.data.frame() %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	drop_na(.value)
-
-post_cors_item <- corr_data %>% 
-	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
-	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
-	mutate(
-		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
-		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
-	) %>% 
-	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
-	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
-	geom_tile(na.rm = TRUE) +
-	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
-	labs(
-		x = "Term 1", y = "Term 2", fill = "Posterior\ncorrelation",
-		title = "By item"
-	) +
-	scale_fill_gradient2(
-		low = "#04bf78", mid = "white", high = "#FFC20A", 
-		na.value = "white", limits = c(-0.4, 0.4)
-	) +
-	scale_x_discrete() +
-	coord_equal()  +
-	theme(
-		axis.text.y = element_blank()
-	)
-
-(post_cors_participant | post_cors_item) &
-	plot_layout(guides = "collect") &
 	theme(
@@
 ```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
 sample_size <- participants %>% 
 	filter(valid_participant) %>% 
-	count(lp, vocab_size_total_center)
-
-n <- expand_grid(
+	count(lp, age_group, vocab_size_total_center)
+
+nd <- expand_grid(
 	lp = c("Monolingual", "Bilingual"),
-	vocab_size_total_center = c(-1, 1),
 	trial_type = unique(gaze$trial_type),
+	age_group = unique(gaze$age_group),
 	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
@@
 
-m <- epred_draws(object = fit_total_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
+m <- epred_draws(
+	object = fit_3, 
+	newdata = nd, 
+	ndraws = NULL,
+	re_formula = NA
+) %>% 
 	mutate(
-		.value = logit_to_prob(.epred),
-		vocab_size_total_center = ifelse(
-			vocab_size_total_center==-1, 
-			"Low vocabulary size (-1 SD)",
-			"High vocabulary size (+1 SD)"
-		)
-	)
-
-ggplot(m, aes(time_bin_center, .value)) +
-	facet_grid(fct_rev(lp)~vocab_size_total_center) +
+		.value = logit_to_prob(.epred)
+	)
+
+m %>% 
+	ggplot() +
+	aes(
+		x = time_bin_center, 
+		y = .value,
+		colour = trial_type,
+		fill = trial_type,
+		linetype = trial_type
+	) +
+	facet_grid(age_group~lp) +
 	geom_hline(yintercept = 0.5, colour = "black") +
-	geom_line(
-		aes(group = interaction(vocab_size_total_center, trial_type, lp, .draw),
-			colour = trial_type),
-		alpha = 0.5, size = 0.65
-	) +
-	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
-		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_futurama() +
+	# geom_line(
+	# 	aes(group = interaction(trial_type, lp, .draw),
+	# 		colour = trial_type),
+	# 	alpha = 0.5, size = 0.65
+	# ) +
+	stat_summary(
+		fun.data = mean_qi,
+		geom = "ribbon",
+		colour = NA,
+		alpha = 0.1
+	) +
+	stat_summary(
+		fun = mean,
+		geom = "line",
+		size = 1
+	) +
+	labs(
+		x = "Time bin (100 ms)", 
+		y = "Expected posterior mean PTLT",
+		colour = "Trial type",
+		fill = "Trial type", 
+		shape = "Trial type",
+		linetype = "Trial type"
+	) +
+	scale_color_d3() +
+	scale_fill_d3() +
 	scale_x_continuous(
-		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
-		labels = 1:20
-	) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme_minimal() +
+		breaks = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), len = 5),
+		labels = format(100*(seq(0, 20, 5)), big.mark = ",")
+	) +
+	scale_y_continuous(
+		limits = c(0, 1),
+		labels = percent
+	) + 
 	theme(
@@
 		legend.title = element_blank(),
-		axis.text.x = element_text(size = 7),
 		panel.grid.major.x = element_blank(),
@@
 
+ggsave(here("img", "predictions.png"))
+
 ```
@@
 
-m <- emmeans(fit_total_4, ~trial_type | lp, epred = TRUE)
+m <- emmeans(fit_2, ~trial_type | lp, epred = TRUE)
 
@@
 
-ggplot(m_draws, aes(.value, trial_type, fill = trial_type)) +
+m_draws %>% 
+	ggplot() +
+	aes(
+		x = .value, 
+		y = trial_type, 
+		fill = trial_type
+	) +
 	facet_wrap(~lp) +
 	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
+		aes(
+			alpha = stat(
+				cut_cdf_qi(
+					cdf, 
+					.width = c(.95, .8, .5), 
+					labels = percent_format()
+				)
+			)
+		),
 		position = position_nudge(y = 0.05),
@@
 	labs(
-		x = "Expected posterior mean PTLT", y = "Trial type",
-		colour = "Trial type", fill = "Trial type",
+		x = "Expected posterior mean PTLT",
+		y = "Trial type",
+		colour = "Trial type", 
+		fill = "Trial type",
 		alpha = "CrI"
 	) +
-	guides(color = "none", fill = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
-	scale_x_continuous(limits = c(0.5, 1), labels = percent)  +
+	guides(
+		color = "none",
+		fill = "none"
+	) +
+	scale_alpha_discrete(
+		range = c(0.8, 0.2),
+		na.translate = FALSE
+	) +
+	scale_x_continuous(
+		limits = c(0, 1),
+		labels = percent
+	)  +
 	theme(

### 2022-06-28 R/01_participants.R

@@ -1,0 +1,48 @@
+# participants ----
+get_participants <- function(){
+	
+	suppressMessages({
+		# participants
+		
+		participants <- range_read(
+			ss = "1JkhN4iBh3bi6PSReGGk9jSrVgDhZNOUmve6vNS2eEqE",
+			sheet = "barcelona", 
+			na = ""
+		) %>% # defined in arguments
+			# NA -> FALSE
+			mutate_if(is.logical, ~ifelse(is.na(.), FALSE, .)) %>%
+			mutate(
+				age_group = factor(
+					paste0(age_group, " months"),
+					levels = paste0(c(21, 25, 30), " months")
+				),
+				date_test = as_date(date_test),
+				lp = factor(lp, levels = c("Monolingual", "Bilingual")),
+				test_language = factor(test_language, levels = c("Catalan", "Spanish")),
+				list = as.integer(list)
+			) %>% 
+			# remove pilot participants
+			filter(!pilot) %>% 
+			# remove participants with no gaze data
+			drop_na(
+				participant,
+				filename
+			) %>% 
+			select(
+				participant,
+				id_db,
+				date_test, 
+				lp, 
+				age_group,
+				test_language,
+				list, 
+				version,
+				filename
+			)
+	})
+	
+	write_csv_arrow(participants, "data/participants.csv")
+	
+	return(participants)
+	
+}

### 2022-06-28 R/04_attrition.R

@@ -1,0 +1,207 @@
+# attrition
+get_attrition <- function(
+		gaze_imputed, # Barcelona gaze data, get_gaze_bcn output
+		participants, # participants dataset, get_participants output
+		stimuli, # stimuli dataset, get_stimuli output
+		vocabulary, # vocabulary dataset, get_vocabulary output
+		aoi_coords = aoi_coords,
+		filter_vocabulary = c("prime", "target"), # should the trial be excluded if no comprehension in any of these words? (prime, target, distractor)
+		filter_counterbalancing = FALSE, # should trials from same counterbalancing pair be excluded together?
+		looking_threshold = c(prime = 0.25, target = 0.25, distractor = 0), # minimum looking time
+		missing_trials_threshold = c(cognate = 2, non_cognate = 2, unrelated = 2) # minimum n trials in each condition
+){
+	suppressWarnings({
+		
+
+		processed <- list(
+			select(participants, -filename),
+			stimuli,
+			gaze_imputed
+			) %>% 
+			reduce(full_join) %>%  
+			drop_na(filename) %>% 
+			select(
+				participant, age_group, trial, phase, time, x, y, 
+				target_location,
+				valid_sample,
+				trial_type, prime_cdi, target_cdi, distractor_cdi,
+				filename
+			) 
+		
+		# evaluate inclusion criteria ----
+		# valid gaze
+		valid_gaze <- processed %>% 
+			# evaluate if gaze coordinates are inside any AOI, and which
+			mutate(
+				aoi_prime = gaze_in_prime(x, y, aoi_coords = aoi_coords),
+				aoi_target = gaze_in_target(x, y, target_location, aoi_coords),
+				aoi_distractor = gaze_in_distractor(x, y, target_location, aoi_coords)
+			) %>%  
+			rename_all(function(x) str_remove(x, "_cdi")) %>% 
+			group_by(
+				participant, 
+				age_group,
+				trial_type,
+				filename,
+				trial
+			) %>% 
+			summarise(
+				# proportion of prime looking time during prime phase
+				valid_looking_prime = sum(aoi_prime[phase=="Prime"], na.rm = TRUE)*(1/120),
+				# proportion of target looking time during target-distractor phase
+				valid_looking_target = sum(aoi_target[phase=="Target-Distractor"], na.rm = TRUE)*(1/120), 
[…]

### 2022-06-28 scripts/R/03_gaze_bcn.R

@@ -1,72 +1,0 @@
-# process Barcelona gaze data
-get_gaze_bcn <- function(
-	file_paths, # gaze data file paths
-	participants, # participants dataset, get_participants output
-	stimuli, # stimuli dataset, get_stimuli output
-	screen_resolution = c(x = 1920, y = 1080), # screen size in pixels
-	center_coords = c(xmin = 710, xmax = 1210, ymin = 290, ymax = 790), # coordinates of centre picture
-	left_coords = c(xmin = 180, xmax = 680, ymin = 290, ymax = 790), # coordinates of left picture
-	right_coords = c(xmin = 1240, xmax = 1640, ymin = 290, ymax = 790) # coordinates of right picture
-){
-	suppressMessages({
-		# trial data ----
-		stimuli <- stimuli %>%
-			filter(location=="Barcelona") %>% 
-			select(-c("prime2", "target2", "prime2_cdi", "target2_cdi", "valid_trial"))
-		
-		# import gaze data ----
-		raw <- map(file_paths, get_gaze_raw) %>% 
-			# merge all data sets assigning them their file name
-			set_names(list.files(here("data", "gaze", "barcelona")))  %>% 
-			bind_rows(.id = "filename") %>% 
-			as_tibble() %>%
-			# restart timestamps at each trial phase change, and express in seconds
-			group_by(participant, trial, phase, filename) %>%
-			mutate(time = as.double(time-min(time, na.rm = TRUE))/1000) %>%
-			ungroup() %>%
-			# trim timestamps outside the 2 seconds range
-			filter(
-				between(time, 0, 2),
-				participant %in% participants$participant # get only valid participants
-			) %>%
-			mutate(
-				# more detailed evaluation of sample validity
-				valid_sample = l_v & !is.na(l_x) & !is.na(l_y) & between(l_x, 0, 1) & between(l_y, 0, 1),
-				# if sample is not valid, change value to NA
-				x = ifelse(valid_sample, l_x, NA),
-				y = ifelse(valid_sample, l_y, NA),
-				# change gaze coodinates from 0-1 scale to screen resolution scale [1920x1080]
-				x = x*screen_resolution["x"],
-				y = y*screen_resolution["y"]
-			) %>% 
-			# add paticipant and trial info
-			left_join(participants) %>% 
-			left_join(stimuli) %>% 
-			# evaluate if gaze coordinates are inside any AOI, and which
-			mutate(
[…]

### 2022-06-28 scripts/R/03_gaze_oxf.R

@@ -1,96 +1,0 @@
-# process Oxford gaze data
-
-get_gaze_oxf <- function(
-	file_paths, # gaze data file paths
-	participants, # participants dataset, get_participants output
-	stimuli, # stimuli dataset, get_stimuli output
-	screen_resolution = c(x = 1920, y = 1080),
-	center_coords = c(xmin = 710, xmax = 1210, ymin = 290, ymax = 790),
-	left_coords = c(xmin = 180, xmax = 680, ymin = 290, ymax = 790),
-	right_coords = c(xmin = 1240, xmax = 1640, ymin = 290, ymax = 790)
-){
-	
-	suppressWarnings({
-		# import gaze data ----
-		raw <- map(file_paths, fread, na = c("", "NA")) %>% 
-			bind_rows() %>% 
-			as_tibble() %>%
-			clean_names() %>% # colnames to snake case
-			mutate(trial = ifelse(block==2, trial+16, trial)) %>% # because of block format, trial number for 17th trial is recorded as block 2 trial 1
-			rename(
-				id_db = id, trial_num = trial, time = timestamp,
-				l_x = gaze_raw_left_x, l_y = gaze_raw_left_y,
-				r_x = gaze_raw_right_x, r_y = gaze_raw_right_y,
-				l_v = gaze_left_validity, r_v = gaze_right_validity,
-				target_location = vis_target_stm_pos,
-				prime_unrelated = vis_un_stm, prime_cognate = vis_cp_stm, prime_noncognate = vis_np_stm,
-				target = vis_target_stm, distractor = vis_distr_stm
-			) %>%
-			mutate_at(vars(matches("_v")), as.logical) %>%
-			mutate(
-				id_db = as.character(id_db),
-				trial_type = case_when(
-					!is.na(prime_unrelated) ~ "Unrelated",
-					!is.na(prime_cognate) ~ "Cognate",
-					!is.na(prime_noncognate) ~ "Non-cognate"
-				),
-				phase = case_when(
-					between(time, 0, 2500) ~ "Getter", # attention getter lasts shorter than in Barcelona (3s)
-					between(time, 2500, 4000) ~ "Prime",
-					between(time, 4000, 4050) ~ "Blank",
-					between(time, 4050, 4750) ~ "Audio",
-					between(time, 4750, 6750) ~ "Target-Distractor"
-				),
-				target_location = ifelse(target_location==2, "L", "R"),
-				prime = coalesce(prime_unrelated, prime_cognate, prime_noncognate), # get prime picture
[…]

### 2022-06-28 scripts/R/05_prepare.R

@@ -1,156 +1,0 @@
-# prepare
-
-prepare_data <- function(
-	gaze_bcn, # Barcelona gaze data, get_gaze_bcn output
-	gaze_oxf, # Oxford gaze data, get_gaze_oxf output
-	participants, # participants dataset, get_participants output
-	stimuli, # stimuli dataset, get_stimuli output
-	vocabulary, # vocabulary dataset, get_vocabulary output
-	attrition # attrition dataset , get_attrition output
-){
-	suppressMessages({
-		participants <- participants %>% 
-			mutate(participant_unique = as.character(row_number())
-			)
-		
-		vocabulary <- vocabulary %>% 
-			mutate(
-				vocab_size_total_center = scale(vocab_size_total)[,1],
-				vocab_size_l1_center = scale(vocab_size_l1)[,1],
-				vocab_size_conceptual_center = scale(vocab_size_conceptual)[,1]
-			) 
-		
-		clean <- list(
-			Barcelona = gaze_bcn,
-			Oxford = gaze_oxf
-		) %>% 
-			bind_rows(.id = "location") %>% 
-			# to avoid issues with column names
-			rename(time_stamp = time) %>% 
-			left_join(attrition) %>% 
-			left_join(vocabulary) %>% 
-			filter(
-				phase=="Target-Distractor",
-				valid_trial,
-				valid_participant
-			) %>% 
-			select(
-				participant,
-				date_test, 
-				lp, 
-				location, 
-				list, 
-				age_group,
-				trial, 
-				test_language, 
-				phase,
-				time_stamp, 
-				x,
-				y, 
-				valid_sample,
-				trial_type, 
-				target_location, 
-				aoi_target, 
-				aoi_distractor, 
-				prime, 
-				target,
-				vocab_size_total,
-				vocab_size_l1,
-				vocab_size_conceptual
-			) %>% 
-			drop_na(trial) %>% 
-			left_join(participants)
-		
-		# to eyetrackingR format
-		gaze <- clean %>% 
-			mutate(trackloss_col = !valid_sample) %>% # eyetracking R
-			make_eyetrackingr_data(
-				participant_column = "participant_unique",
-				trial_column = "trial",
-				time_column = "time_stamp",
-				trackloss_column = "trackloss_col",
-				item_columns = c("prime", "target"),
[…]

### 2022-06-28 tests/testthat/test-participants.R

@@ -1,0 +1,61 @@
+test_participants <- function(participants){
+	
+	test_that("participants has the right columns", {
+		expect_equal(
+			colnames(participants),
+			c(
+				"participant",
+				"id_db",
+				"date_test",
+				"lp",
+				"age_group",
+				"test_language",
+				"list",
+				"version",
+				"filename"
+			)
+		)
+	})
+	
+	test_that("participants variables are the right types", {
+		expect_type(participants$participant, "character")
+		expect_type(participants$id_db, "character")
+		expect_equal(class(participants$date_test), "Date")
+		expect_type(participants$lp, "integer")
+		expect_type(participants$age_group, "integer")
+		expect_type(participants$test_language, "integer")
+		expect_type(participants$list, "integer")
+		expect_type(participants$version, "character")
+		expect_type(participants$filename, "character")
+	})
+	
+	test_that("participants has no missing data", {
+		expect_false(any(is.na(participants$participant)))
+		expect_false(any(is.na(participants$id_db)))
+		expect_false(any(is.na(participants$date_test)))
+		expect_false(any(is.na(participants$lp)))
+		expect_false(any(is.na(participants$age_group)))
+		expect_false(any(is.na(participants$test_language)))
+		expect_false(any(is.na(participants$list)))
+		expect_false(any(is.na(participants$version)))
+		expect_false(any(is.na(participants$filename)))
+		
+	})
+	
+	test_that("participants and age groups combinations are not duplicated", {
+		expect_true(
+			participants %>%
+				get_dupes(participant, age_group) %>% 
+				nrow() < 1
+		)
+	})
+	
+	test_that("filenames are not duplicated", {
+		expect_true(!any(duplicated(participants$filename)))
+	})
+	
+	test_that("all filenames correspond to a file in data/gaze/00_raw", {
+		expect_true(all(participants$filename %in% list.files("data/gaze/00_raw", pattern = ".csv")))
+	})
+}
+

### 2022-06-28 tests/testthat/test-stimuli.R

@@ -1,0 +1,123 @@
+test_stimuli <- function(stimuli){
+	
+	test_that("stimuli has the right columns", {
+		expect_equal(
+			colnames(stimuli),
+			c(
+				"trial",
+				"test_language",
+				"version",
+				"list",
+				"trial_type",
+				"prime",
+				"target",
+				"distractor",
+				"audio",
+				"target_location",
+				"prime_cdi",
+				"target_cdi",
+				"distractor_cdi",
+				"valid_trial",
+				"familiarity_prime",
+				"familiarity_target",
+				"familiarity_se_prime",
+				"familiarity_se_target",
+				"frequency_prime_childes",
+				"frequency_target_childes",
+				"category_prime",
+				"category_target",
+				"is_animate_prime",
+				"is_animate_target",
+				"frequency_prime_subtlex",
+				"frequency_target_subtlex"
+			)
+		)
+	})
+	
+	test_that("stimuli has the variable classes", {
+		expect_type(stimuli$trial, "integer")
+		expect_type(stimuli$test_language, "character")
+		expect_type(stimuli$version, "character")
+		expect_type(stimuli$list, "integer")
+		expect_type(stimuli$trial_type, "character")
+		expect_type(stimuli$prime, "character")
+		expect_type(stimuli$target, "character")
+		expect_type(stimuli$distractor, "character")
+		expect_type(stimuli$prime_cdi, "character")
+		expect_type(stimuli$target_cdi, "character")
+		expect_type(stimuli$distractor_cdi, "character")
+		expect_type(stimuli$audio, "character")
+		expect_type(stimuli$target_location, "character")
+		expect_type(stimuli$valid_trial, "logical")
+		expect_type(stimuli$familiarity_prime, "double")
+		expect_type(stimuli$familiarity_target, "double")
+		expect_type(stimuli$familiarity_se_prime, "double")
+		expect_type(stimuli$familiarity_se_target, "double")
+		expect_type(stimuli$frequency_prime_childes, "double")
+		expect_type(stimuli$frequency_target_childes, "double")
+		expect_type(stimuli$category_prime, "character")
+		expect_type(stimuli$category_target, "character")
+		expect_type(stimuli$is_animate_prime, "logical")
[…]

### 2022-07-05 docs/00_participants.Rmd
Prepare ICIS presentation

@@
 )
+
 options(
@@
 ```
+
+# Language profile
+
+```{r participants-lp, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+participants %>% 
+	select(participant, age_group, lp, starts_with("doe_"), test_language) %>% 
+	mutate(participant = paste0(participant, "(", age_group, ")")) %>% 
+	pivot_longer(
+		starts_with("doe_"),
+		names_to = "language",
+		values_to = "doe"
+	) %>% 
+	mutate(
+		language = str_remove_all(language, "doe_") %>% 
+			str_to_sentence(),
+	) %>% 
+	ggplot() +
+	aes(
+		x = doe,
+		y = reorder(participant, lp),
+		fill = language
+	) +
+	facet_wrap(
+		lp~test_language,
+		scales = "free_y",
+		labeller = label_wrap_gen(multi_line = FALSE)
+	) +
+	geom_col(
+		position = position_fill(),
+		size = 0.1,
+		colour = "white"
+	) +
+	geom_vline(
+		xintercept = 0.5
+	) +
+	labs(
+		x = "Degree of exposure",
+		y = "Participant",
+		fill = "Language"
+	) +
+	scale_x_continuous(
+		labels = percent
+	) +
+	theme(
+		axis.text.y = element_blank(),
+		panel.grid = element_blank(),
+		axis.title.y = element_blank(),
+		plot.background = element_rect(fill = "white")
+
+	)
+
+ggsave(here("img", "participants_lp.png"))
+
+```

### 2022-07-05 docs/01_stimuli.Rmd
Prepare ICIS presentation

@@
 	) +
+	scale_fill_d3() +
+	scale_colour_d3() +
 	scale_y_continuous(labels = percent) +
@@
 	coord_flip() +
+	scale_fill_d3() +
+		scale_colour_d3() +
 
@@
 
-ggsave(here("img", "stimuli_animacy.png"), width = 15)
+ggsave(here("img", "stimuli_semantic-category.png"), width = 15, dpi = 2000)
 

### 2022-07-05 docs/05_attrition.Rmd
Prepare ICIS presentation

@@
 	)
+
+ggsave(here("img", "participant_attrition.png"))
 ```
@@
 attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
-	drop_na(trial_type, familiarity_target) %>% 
+	left_join(distinct(stimuli, test_language, list, trial, trial_type, familiarity_target)) %>% 
+	drop_na(
+		trial_type, 
+		familiarity_target
+	) %>% 
 	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
-	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
-	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
+	count(
+		trial_type,
+		age_group,
+		valid_status, 
+		trial_type, 
+		familiarity_target
+	) %>% 
+	ggplot() +
+	aes(
+		as.factor(familiarity_target), 
+		n, 
+		fill = valid_status,
+		colour = valid_status
+	) +
 	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
-	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
+	geom_col(
+		position = position_fill(),
+		colour = "white"
+	) +
+	labs(
+		x = "Trial type",
+		y = "Trials",
+		colour = "Validity", 
+		fill = "Validity"
+	) +
+	guides(
+		fill = guide_legend(ncol = 2), 
+		colour = guide_legend(ncol = 2)
+	)	+
+	scale_x_discrete(
+		labels = function(x) paste0(as.numeric(x)*100, "%"),
+	) +
 	scale_y_continuous(labels = percent) +
+	scale_fill_d3() +
 	coord_flip() +
@@
 	)
+
+ggsave(here("img", "attrition_familiarity.png"))
 ```
@@
 attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
+	left_join(distinct(stimuli, test_language, list, trial, trial_type, is_animate_target)) %>%
 	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
@@
 attrition %>% 
-	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
-	drop_na(trial_type, category_target) %>% 
-	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
-	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
-	facet_grid(trial_type~age_group) +
-	geom_col(position = position_fill(), colour = "white") +
-	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
-	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
+	left_join(distinct(stimuli, test_language, list, trial, trial_type, category_target)) %>%
+	drop_na(
+		trial_type, 
+		category_target
+	) %>% 
+	count(
+		trial_type,
+		age_group,
+		valid_status,
+		trial_type, 
+		category_target
+	) %>% 
+	ggplot() +
+	aes(
+		fct_rev(category_target),
+		n, 
+		fill = valid_status,
+		colour = valid_status
+	) +
+	facet_wrap(
+		trial_type~age_group, 
+		labeller = label_wrap_gen(multi_line = FALSE),
+		scales = "free_y"
+	) +
+	geom_col(
+		position = position_fill(),
+		colour = "white"
+	) +
+	labs(
+		x = "Trial type", 
+		y = "Trials",
+		colour = "Validity",
+		fill = "Validity"
+	) +
+	guides(
+		fill = guide_legend(ncol = 2),
+		colour = guide_legend(ncol = 2)
+	)	+
 	scale_y_continuous(labels = percent) +

### 2022-07-05 docs/06_results.Rmd
Prepare ICIS presentation

@@
 ---
-title: "Results (Barcelona)"
+title: "Results"
 output: github_document
@@
 	knitr.duplicate.label = "allow",
-	ggplot2.discrete.fill = ggsci::pal_futurama()(7),
-	ggplot2.discrete.colour = ggsci::pal_futurama()(7)
+	ggplot2.discrete.fill = pal_d3()(4),
+	ggplot2.discrete.colour = pal_d3()(4)
 )
@@
 	filter(str_detect(.variable, "time_bin")) %>% 
+	mutate(
+		.variable_name = factor(
+			.variable_name,
+			levels = c(
+				"Main effect",
+				"Group (ML vs. BL)",
+				"Trial type (U vs. C+NC)",
+				"Trial type (C vs. NC)",
+				"Trial type (U vs. C+NC) \u00d7 Group",
+				"Trial type (C vs. NC) \u00d7 Group"
+			)
+		)
+	) %>% 
 	ggplot() +
@@
 		x = .value, 
-		y = .variable_name,
+		y = fct_rev(.variable_name),
 		colour = type
@@
 		axis.title.y = element_blank(),
+		axis.text.y = element_text(hjust = 1),
 		panel.border = element_rect(fill = NA, colour = "grey", size = 0.75),
@@
 
+ggsave(here("img", "results_polynomial_terms.png"))
 ```
@@
 
-corr_mat <- VarCorr(fit_2, summary = TRUE)$participant$cor 
-corr_names <- rownames(VarCorr(fit_2, summary = TRUE)$participant$cor)
+corr_mat <- VarCorr(fit_3, summary = TRUE)$participant$cor 
+corr_names <- rownames(VarCorr(fit_3, summary = TRUE)$participant$cor)
 
@@
 	) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
+	scale_y_continuous(
+		limits = c(0, 1), 
+		labels = percent
+	) + 
 	theme_minimal() +
@@
 
+observed <- fit_3$data %>% 
+	group_by(time_bin_center, trial_type, lp, age_group) %>% 
+	summarise(
+		.value = logit_to_prob(mean(logit, na.rm = TRUE)),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	mutate(.value_se = sd(.value, na.rm = TRUE) / sqrt(n))
+
 nd <- expand_grid(
@@
 	age_group = unique(gaze$age_group),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
+	time_bin_center = seq(
+		min(gaze$time_bin_center), 
+		max(gaze$time_bin_center), 
+		0.1
+	)
 )
@@
 	newdata = nd, 
-	ndraws = NULL,
+	# ndraws = 20,
 	re_formula = NA
@@
 		fill = trial_type,
-		linetype = trial_type
-	) +
-	facet_grid(age_group~lp) +
-	geom_hline(yintercept = 0.5, colour = "black") +
+		linetype = trial_type,
+		shape = trial_type
+	) +
+	facet_wrap(
+		fct_rev(lp)~age_group,
+		scales = "free",
+		labeller = label_wrap_gen(multi_line = FALSE)
+	) +
+	geom_hline(
+		yintercept = 0.5,
+		colour = "black"
+	) +
 	# geom_line(
@@
 		colour = NA,
-		alpha = 0.1
+		alpha = 0.25
 	) +
@@
 		geom = "line",
-		size = 1
+		size = 0.75
+	) +
+	geom_text(
+		data = sample_size,
+		aes(
+			x = min(gaze$time_bin_center),
+			y = 1,
+			label = paste0("N = ", n)
+		),
+		colour = "black",
+		hjust = 0,
+		vjust = 1,
+		inherit.aes = FALSE
+	) +
+	geom_point(
+		data = observed,
+		size = 1.5
+	) +
+	labs(
+		x = "Time from target-distractor onset (ms)", 
+		y = "Posterior mean PTLT",
+		colour = "Trial type",
+		fill = "Trial type", 
+		shape = "Trial type",
+		linetype = "Trial type"
+	) +
+	scale_color_d3() +
+	scale_fill_d3() +
+	scale_x_continuous(
+		breaks = seq(
+			min(gaze$time_bin_center),
+			max(gaze$time_bin_center),
+			len = 7
+		),
+		labels = format(
+			100*(seq(3, 18, 3)), 
+			big.mark = ",", trim = TRUE
+		)
+	) +
+	scale_y_continuous(
+		limits = c(0, 1),
+		labels = percent
+	) + 
+	theme_custom() +
+	theme(
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(face = "plain"),
+		axis.text.y = element_text(face = "plain"),
+		panel.grid.major.x = element_blank(),
+		panel.grid.minor.x = element_blank(),
+		panel.background = element_rect(
+			fill = NA, 
+			colour = NA
+		),
+		plot.background = element_rect(
+			fill = "white",
+			colour = NA
+		)
+	)
+
+ggsave(
+	here("img", "predictions.png"),
+	dpi = 2000,
+	height = 7,
+	width = 12
+)
+
+```
+
+```{r gaze_time_observed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+sample_size <- participants %>% 
+	filter(valid_participant) %>% 
+	count(lp, age_group)
+
+observed <- fit_3$data %>% 
+	group_by(time_bin_center, trial_type, lp, age_group) %>% 
+	summarise(
+		.value = logit_to_prob(mean(logit, na.rm = TRUE)),
+		n = n(),
+		.groups = "drop"
+	) %>% 
+	mutate(.value_se = sd(.value, na.rm = TRUE) / sqrt(n))
+
+nd <- expand_grid(
+	lp = c("Monolingual", "Bilingual"),
+	trial_type = unique(gaze$trial_type),
+	age_group = unique(gaze$age_group),
+	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
+)
+
+m <- epred_draws(
+	object = fit_3, 
+	newdata = nd, 
+	# ndraws = 20,
+	re_formula = NA
+) %>% 
+	mutate(
+		.value = logit_to_prob(.epred)
+	)
+
+m %>% 
+	ggplot() +
+	aes(
+		x = time_bin_center, 
+		y = .value,
+		colour = trial_type,
+		fill = trial_type,
+		linetype = trial_type,
+		shape = trial_type
+	) +
+	facet_grid(lp~age_group) +
+	geom_hline(
+		yintercept = 0.5,
+		colour = "black"
+	) +
+	geom_line(
+		data = observed
+	) +
+	geom_point(
+		data = observed,
+		size = 3
+	) +
+	geom_text(
+		data = sample_size,
+		aes(
+			x = min(gaze$time_bin_center),
+			y = 1,
+			label = paste0("N = ", n)
+		),
+		colour = "black",
+		hjust = 0,
+		vjust = 1,
+		inherit.aes = FALSE
 	) +
@@
 	scale_x_continuous(
-		breaks = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), len = 5),
-		labels = format(100*(seq(0, 20, 5)), big.mark = ",")
+		breaks = seq(
+			min(gaze$time_bin_center),
+			max(gaze$time_bin_center),
+			len = 5
+		),
+		labels = format(
+			100*(seq(0, 20, 5)), 
+			big.mark = ","
+		)
 	) +
@@
 
-ggsave(here("img", "predictions.png"))
+ggsave(here("img", "predictions_observed.png"))
 
@@
 
-m <- emmeans(fit_2, ~trial_type | lp, epred = TRUE)
+m <- emmeans(fit_3, ~trial_type | age_group, by = "lp", epred = TRUE)
 
@@
 	) +
-	facet_wrap(~lp) +
+	facet_grid(lp~age_group) +
 	stat_slab(
@@
 		legend.position = "right",
-		panel.grid.major.y = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		panel.grid.minor.x = element_blank(),
+		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
 		panel.background = element_rect(fill = NA, colour = "grey")

### 2022-07-05 _targets.R

@@ -26,57 +26,46 @@ tar_option_set(
 	packages = c(
 		# project utils
 		"arrow",
-		"clustermq",
-		"DiagrammeR",
-		
-	 
-		"here",
-		"conflicted",
-		"usethis",
-		"testthat",
-		"lazyeval",
-		# data manipulation
-		"dplyr",
-		"tidyr",
-		"purrr", 
-		"stringr",
-		"tibble",
-		"forcats", 
-		"lubridate", 
-		# data retrieval
-		"janitor",
-		"childesr",
-		"multilex", 
-		"keyring",
-		"googlesheets4",
-		"httr",
-		# modelling
-		"eyetrackingR",
 		"brms",
-		"tidybayes", 
+		"childesr",
+		"clustermq",
+		"conflicted",
+		"DiagrammeR",
+		"dplyr",
+		"eyetrackingR",
 		"emmeans",
-		"mice",
-		# data visualisation
+		"forcats", 
 		"ggplot2", 
-		"shiny", 
-		"patchwork",
-		"shiny",
 		"ggsci",
-		# data reporting
-		"knitr", 
-		"papaja",
+		"googlesheets4",
 		"gt",
-		# unit testing
+		"here",
+		"httr",
+		"janitor",
+		"keyring",
+		"knitr",
+		"lazyeval",
+		"lubridate", 
+		"mice",
+		"multilex", 
+		"papaja",
+		"patchwork",
+		"purrr", 
 		"readxl", 
 		"rmarkdown", 
 		"scales", 
 		"shiny",
+		"stringr",
 		"testthat",
 		"targets",
 		"tarchetypes",
+		"testthat",
+		"tibble",
+		"tidybayes", 
 		"tidytext",
+		"tidyr",
+		"usethis",
 		"zoo"
-		
 	)
 )
 
@@ -329,11 +318,9 @@ list(
 			stimuli = stimuli, 
 			vocabulary = vocabulary,
 			attrition = attrition,
-			aoi_coords = aoi_coords
-		) %>% 
-			filter(
-				participant %in% unique(.$participant)[1:20]
-			)
+			aoi_coords = aoi_coords, 
+			time_subset = c(0.3, 2)
+		) 
 	),
 	tar_target(
 		gaze_test,
@@ -373,7 +360,8 @@ list(
 				prior = model_prior_agg[-c(2, 5),],
 				data = gaze_aggregated,
 				iter = 2000, chains = 2, seed = 888,
[…]

### 2022-07-05 tests/testthat/test-participants.R

@@ -8,6 +8,9 @@ test_participants <- function(participants){
 				"id_db",
 				"date_test",
 				"lp",
+				"doe_catalan",
+				"doe_spanish",
+				"doe_others",
 				"age_group",
 				"test_language",
 				"list",

### 2022-07-07 docs/06_results.Rmd
Figures for presentationns

@@
 	# cubic terms ----
+	"b_Itime_bin_centerE3:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE3:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+
+	"b_Itime_bin_centerE3:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE3:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+
 	"b_Itime_bin_centerE3:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
@@
 
+	"b_Itime_bin_centerE3:trial_typerelated_unrelated:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE3:trial_typerelated_unrelated:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",
+
+	"b_Itime_bin_centerE3:trial_typecognate_noncognate:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE3:trial_typecognate_noncognate:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",
+
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil:age_group21_25" =
+		"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE3:lpLPMonvs.Bil:age_group25_30" =
+		"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",
+
 	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
@@
 
+	"b_Itime_bin_centerE3:age_group21_25" = 
+		"Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE3:age_group25_30" = 
+		"Age (25 vs. 30 mo)",
+
 	"b_Itime_bin_centerE3:trial_typecognate_noncognate" =
@@
 	"b_Itime_bin_centerE3" = 
-		"Main effect",
+		"Intercept",
 
 	# quadratic terms ----
+	"b_Itime_bin_centerE2:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE2:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+
+	"b_Itime_bin_centerE2:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE2:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+
 	"b_Itime_bin_centerE2:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
@@
 
+	"b_Itime_bin_centerE2:trial_typerelated_unrelated:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE2:trial_typerelated_unrelated:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",
+
+	"b_Itime_bin_centerE2:trial_typecognate_noncognate:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE2:trial_typecognate_noncognate:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",
+
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil:age_group21_25" =
+		"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE2:lpLPMonvs.Bil:age_group25_30" =
+		"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",
+
 	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
@@
 
+	"b_Itime_bin_centerE2:age_group21_25" = 
+		"Age (21 vs. 25 mo)",
+
+	"b_Itime_bin_centerE2:age_group25_30" = 
+		"Age (25 vs. 30 mo)",
+
 	"b_Itime_bin_centerE2:trial_typecognate_noncognate" =
@@
 	"b_Itime_bin_centerE2" = 
-		"Main effect",
+		"Intercept",
 
 	# linear terms ----
+	"b_time_bin_center:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+
+	"b_time_bin_center:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+
+	"b_time_bin_center:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+
+	"b_time_bin_center:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+
 	"b_time_bin_center:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
@@
 
+	"b_time_bin_center:trial_typerelated_unrelated:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_time_bin_center:trial_typerelated_unrelated:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",
+
+	"b_time_bin_center:trial_typecognate_noncognate:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_time_bin_center:trial_typecognate_noncognate:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",
+
+	"b_time_bin_center:lpLPMonvs.Bil:age_group21_25" =
+		"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_time_bin_center:lpLPMonvs.Bil:age_group25_30" =
+		"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",
+
 	"b_time_bin_center:lpLPMonvs.Bil" = 
@@
 
+	"b_time_bin_center:age_group21_25" = 
+		"Age (21 vs. 25 mo)",
+
+	"b_time_bin_center:age_group25_30" = 
+		"Age (25 vs. 30 mo)",
+
 	"b_time_bin_center:trial_typecognate_noncognate" =
@@
 	"b_time_bin_center" = 
-		"Main effect",
+		"Intercept",
 
 	# marginal terms ----
+	"b_trial_typerelated_unrelated:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+
+	"b_trial_typerelated_unrelated:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+
+	"b_trial_typecognate_noncognate:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+
+	"b_trial_typecognate_noncognate:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+
 	"b_trial_typecognate_noncognate:lpLPMonvs.Bil" = 
@@
 
+	"b_trial_typerelated_unrelated:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_trial_typerelated_unrelated:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",
+
+	"b_trial_typecognate_noncognate:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_trial_typecognate_noncognate:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",
+
+	"b_lpLPMonvs.Bil:age_group21_25" =
+		"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",
+
+	"b_lpLPMonvs.Bil:age_group25_30" =
+		"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",
+
 	"b_lpLPMonvs.Bil" = 
@@
 
+	"b_age_group21_25" = 
+		"Age (21 vs. 25 mo)",
+
+	"b_age_group25_30" = 
+		"Age (25 vs. 30 mo)",
+
 	"b_trial_typecognate_noncognate" =
@@
 	# sigma
-	"sigma" = "Sigma"
-)
-
-draws <- gather_draws(fit_2, `b_.*`, `sigma`, regex = TRUE) %>% 
+	"sigma" = "Standard deviation"
+)
+
+# cubic terms ----
+levels <- c(
+	"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+	"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+	"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+	"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+	"Trial type (C vs. NC) \u00d7 Group",
+	"Trial type (U vs. C+NC) \u00d7 Group",
+	"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",
+	"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",
+	"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",
+	"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",
+	"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",
+	"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",
+	"Group (ML vs. BL)",
+	"Age (21 vs. 25 mo)",
+	"Age (25 vs. 30 mo)",
+	"Trial type (C vs. NC)",
+	"Trial type (U vs. C+NC)",
+	"Standard deviation",
+	"Intercept"
+)
+
+draws <- gather_draws(
+	fit_3, 
+	`b_.*`, 
+	`sigma`,
+	regex = TRUE
+) %>% 
 	mutate(
-		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
-		.variable_name = str_replace_all(.variable, str_repl),
+		.variable_name = str_replace_all(.variable, str_repl) %>% 
+			factor(levels = levels),
 		type = case_when(
-			str_detect(.variable, "E2") ~ "Quadratic time",
-			str_detect(.variable, "E3") ~ "Cubic time",
-			str_detect(.variable, "time_bin") ~ "Linear time",
-			str_detect(.variable, "sigma") ~ "Error",
-			TRUE ~ "Main effects"
-		) %>% 
-			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
-	)
-
-draws %>% 
-	group_by(.variable, .variable_name, type) %>% 
-	mean_qi() %>% 
+			str_detect(.variable, "Itime_bin_centerE2") ~ "Quadratic time",
+			str_detect(.variable, "Itime_bin_centerE3") ~ "Cubic time",
+			str_detect(.variable, "time_bin_center") & 
+				str_detect(.variable, "E2|E3", negate = TRUE) ~ "Linear time",
+			str_detect(.variable, "sigma") ~ "Distributional",
+			.variable=="b_Intercept" ~ "Distributional",
+			TRUE ~ "Main effects",
+		) %>% 
+			factor(
+				levels = c(
+					"Main effects", 
+					"Linear time", 
+					"Quadratic time", 
+					"Cubic time",
+					"Distributional"
+				), 
+				ordered = TRUE
+			),
+		.value = ifelse(
+			(.variable %in% c("sigma", "b_Intercept")) & (type=="Main effects"),
+			inv_logit(.value),
+			.value/4
+		),
+	)
+
+coefs_tab <- draws %>% 
+	group_by(.variable_name, type) %>% 
+	mean_qi(
+		.exclude = c(
+			".chain",
+			".iteration",
+			".variable",
+			".draw",
+			".row",
+			".variable_name", 
+			"type"
+		)
+	) %>%  
+	mutate(.variable_name = factor(.variable_name, levels = rev(levels))) %>% 
+	arrange(type, .variable_name) %>% 
 	select(type, .variable_name, .value, .lower, .upper) %>% 
-	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
+	gt(
+		rowname_col = ".variable", 
+		groupname_col = "type"
+	)  %>% 
+	row_group_order(
+		groups = c(
+			"Main effects", 
+			"Linear time", 
+			"Quadratic time", 
+			"Cubic time",
+			"Distributional"
+		)
+	) %>% 
 	fmt_percent(3) %>%
 	fmt_number(4:5, scale_by = 100) %>% 
-	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
+	cols_merge(
+		c(".lower", ".upper"), 
+		pattern = "[{1}, {2}]"
+	) %>% 
 	cols_label(
@@
 		cells_row_groups()
-	) 
-as_raw_html()
+	) %>% 
+	tab_style(
+		cell_text(align = "left"),
+		cells_body()
+	) %>% 
+	tab_style(
+		style = cell_fill(color = pal_d3()(2)[1]),
+		locations = cells_body(
+			columns = everything(),
+			rows = .lower > 0
+		)
+	) %>% 
+	tab_style(
+		style = cell_fill(color = pal_d3()(2)[2]),
+		locations = cells_body(
+			columns = everything(),
+			rows = .upper < 0
+		)
+	)
+
+gtsave(coefs_tab, here("img", "coefs_tab.png"))
+as_raw_html(coefs_tab)
 ```
 
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}
+```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=15}
 
 draws %>% 
-	filter(str_detect(.variable, "Intercept")) %>% 
-	ggplot(aes(.value, .variable_name)) +
-	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
-	stat_pointinterval() +
-	labs(
-		x = "Value", 
-		y = "Variable", 
-		fill = "CrI", 
-		title = "Intercept",
-		alpha = "CrI"
-	) +
-	guides(fill = "none", color = "none") +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		axis.title.y = element_blank()
-	)
-
-draws %>% 
-	filter(
-		str_detect(
-			.variable, 
-			"sigma|sd|time_bin", 
-			negate = TRUE
-		)
+	filter(!(type %in% c("Standard deviation", "Intercept"))) %>% 
+	group_by(type, .variable, .variable_name) %>% 
+	summarise(
+		.lower = quantile(.value, 0.025),
+		.upper = quantile(.value, 0.975),
+		.value = mean(.value),
+		.groups = "drop"
+	) %>% 
+	mutate(
+		excludes_zero = (.lower > 0) | (.upper < 0),
+		excludes_zero = ifelse(excludes_zero, "Yes", "No") %>% 
+			factor(levels = c("Yes", "No"))
 	) %>% 
@@
 		y = .variable_name,
-		colour = .variable_name
+		xmin = .lower,
+		xmax = .upper,
+		colour = excludes_zero
+	) +
+	facet_wrap(
+		~type, 
+		nrow = 1, 
+		scales = "free_x"
 	) +
@@
 	) +
-	stat_pointinterval() +
+	geom_pointinterval(
+		size = 5,
+		point_size = 3
+	) +
 	labs(
@@
 		alpha = "CrI",
-		title = "Main effects"
-	) +
-	guides(
-		fill = "none", 
-		color = "none"
-	) +
-	scale_color_d3() +
+		title = "Main effects",
+		subtitle = "Mean and 95% credible interval of posterior distribution",
+		colour = "Interval excludes zero?"
+	) +
+	scale_color_manual(values = rev(pal_d3()(2))) +
 	scale_x_continuous(
-		labels = percent,
-		limits = c(-0.45, 1)
+		labels = percent
 	) +
 	theme(
-		axis.title.y = element_blank()
-	)
-
-```
-
-```{r main_effects_plot_time, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}
-
-draws %>%
-	filter(str_detect(.variable, "time_bin")) %>% 
-	mutate(
-		.variable_name = factor(
-			.variable_name,
-			levels = c(
-				"Main effect",
-				"Group (ML vs. BL)",
-				"Trial type (U vs. C+NC)",
-				"Trial type (C vs. NC)",
-				"Trial type (U vs. C+NC) \u00d7 Group",
-				"Trial type (C vs. NC) \u00d7 Group"
-			)
-		)
-	) %>% 
-	ggplot() +
-	aes(
-		x = .value, 
-		y = fct_rev(.variable_name),
-		colour = type
-	) +
-	facet_wrap(
-		~type, 
-		scales = "free_x"
-	) +
-	geom_vline(
-		xintercept = 0,
-		colour = "black",
-		linetype = "dashed"
-	) +
-	stat_pointinterval(
-		point_size = 1.5
-	) +
-	labs(
-		x = "Value", 
-		y = "Variable", 
-		fill = "CrI", 
-		alpha = "CrI",
-		title = "Polynomial effects"
-	) +
-	scale_color_d3() +
-	guides(fill = "none", color = "none") +
-	scale_x_continuous(labels = ~percent(., accuracy = 0.1)) +
-	theme(
+		legend.position = "top",
 		axis.title.y = element_blank(),
 		axis.text.y = element_text(hjust = 1),
-		panel.border = element_rect(fill = NA, colour = "grey", size = 0.75),
-		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
-	)
-
-ggsave(here("img", "results_polynomial_terms.png"))
+		panel.border = element_rect(colour = "black", fill = NA)
+	)
+
+ggsave(here("img", "coefficients.png"), height = 10, width = 16)
 ```
 
-```{r main_effects_plot_sigma, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}
-
-draws %>% 
-	filter(str_detect(.variable, "sigma")) %>% 
-	ggplot(
-		aes(.value, 
-			.variable_name
-		)
-	) +
-	stat_pointinterval() +
-	labs(
-		x = "Value", 
-		y = "Variable", 
-		alpha = "CrI",
-		fill = "CrI", 
-		title = "Error"
-	) +
-	guides(fill = "none", color = "none") +
-	scale_x_continuous(labels = percent, limits = c(0.7, 0.72)) +
-	theme(
-		axis.title.y = element_blank()
-	)
-
-```
-
-## Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, fig.height=4}
-
-corr_mat <- VarCorr(fit_3, summary = TRUE)$participant$cor 
-corr_names <- rownames(VarCorr(fit_3, summary = TRUE)$participant$cor)
-
-corr_mat <- corr_mat %>% 
-	as_tibble() %>% 
-	select(matches("Estimate")) %>% 
-	rename_all(str_remove, "Estimate.") %>% 
-	mutate(term1 = corr_names)
-
-corr_mat[lower.tri(corr_mat)] <- NA
-
-corr_data <- corr_mat %>% 
-	as.data.frame() %>% 
-	pivot_longer(
-		-term1, 
-		names_to = "term2",
-		values_to = ".value"
-	) %>% 
-	drop_na(.value)
-
-corr_data %>% 
-	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
-	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
-	mutate(
-		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
-		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
-	) %>% 
-	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
-	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
-	geom_tile(na.rm = TRUE) +
-	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
-	labs(
-		x = "Term 1", 
-		y = "Term 2", 
-		fill = "Posterior\ncorrelation",
-		title = "By participant"
-	) +
-	scale_fill_gradient2(
-		low = "#04bf78", mid = "white", high = "#FFC20A", 
-		na.value = "white", limits = c(-0.4, 0.4)
-	) +
-	scale_x_discrete() +
-	coord_equal() +
-	theme(
-		panel.grid = element_blank(),
-		legend.position = "top",
-		legend.direction = "horizontal",
-		legend.key.height = unit(0.1, "cm"),
-		legend.key.width = unit(0.3, "cm"),
-		legend.justification = c(1, 1),
-		legend.title = element_blank(),
-		legend.text = element_text(size = 5),
-		axis.title.x = element_blank(),
-		axis.title.y = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)
-	)
-
-```
-
 ## Marginal means
 
-### Prior predictions (before seeing the data)
-
-```{r gaze_time_prior, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+### Posterior predictions (after seeing the data)
+
+```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
 sample_size <- participants %>% 
 	filter(valid_participant) %>% 
-	count(lp, vocab_size_total_center)
-
-n <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	vocab_size_l1_center = c(-1, 1),
-	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
-)
-
-m <- epred_draws(fit_l1_prior, newdata = n, ndraws = 50, re_formula = NA) %>% 
-	mutate(
-		.value = logit_to_prob(.epred),
-		vocab_size_l1_center = ifelse(
-			vocab_size_l1_center==-1, 
-			"Low vocabulary size (-1 SD)",
-			"High vocabulary size (+1 SD)"
-		)
-	)
-
-ggplot(m, aes(time_bin_center, .value)) +
-	facet_grid(fct_rev(lp)~vocab_size_l1_center) +
-	geom_hline(yintercept = 0.5, colour = "black") +
-	geom_line(
-		aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
-			colour = trial_type),
-		alpha = 0.5, size = 0.65
-	) +
-
-	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
-		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_futurama() +
-	scale_x_continuous(
-		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
-		labels = 1:20
-	) +
-	scale_y_continuous(
-		limits = c(0, 1), 
-		labels = percent
-	) + 
-	theme_minimal() +
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 7),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank(),
-		panel.background = element_rect(fill = "white", colour = NA),
-		plot.background = element_rect(fill = "white", colour = NA)
-	)
-
-```
-
-### Posterior predictions (after seeing the data)
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(lp, age_group, vocab_size_total_center)
+	count(lp, age_group)
 
@@
 			max(gaze$time_bin_center),
-			len = 7
+			len = 6
 		),
@@
 
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(lp, age_group)
-
-observed <- fit_3$data %>% 
-	group_by(time_bin_center, trial_type, lp, age_group) %>% 
-	summarise(
-		.value = logit_to_prob(mean(logit, na.rm = TRUE)),
-		n = n(),
-		.groups = "drop"
-	) %>% 
-	mutate(.value_se = sd(.value, na.rm = TRUE) / sqrt(n))
-
-nd <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	trial_type = unique(gaze$trial_type),
-	age_group = unique(gaze$age_group),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
-)
-
-m <- epred_draws(
-	object = fit_3, 
-	newdata = nd, 
-	# ndraws = 20,
-	re_formula = NA
-) %>% 
-	mutate(
-		.value = logit_to_prob(.epred)
-	)
-
-m %>% 
+observed %>% 
 	ggplot() +
@@
 	) +
-	facet_grid(lp~age_group) +
+	facet_wrap(
+		fct_rev(lp)~age_group,
+		scales = "free",
+		labeller = label_wrap_gen(multi_line = FALSE)
+	) +
 	geom_hline(
@@
 	) +
-	geom_line(
-		data = observed
-	) +
+	geom_line() +
 	geom_point(
-		data = observed,
-		size = 3
+		size = 2
 	) +
@@
 	labs(
-		x = "Time bin (100 ms)", 
-		y = "Expected posterior mean PTLT",
+		x = "Time from target-distractor onset (ms)", 
+		y = "Observed PTLT",
 		colour = "Trial type",
@@
 			max(gaze$time_bin_center),
-			len = 5
+			len = 6
 		),
 		labels = format(
-			100*(seq(0, 20, 5)), 
-			big.mark = ","
+			100*(seq(3, 18, 3)), 
+			big.mark = ",", trim = TRUE
 		)
@@
 		legend.title = element_blank(),
+		axis.text.x = element_text(face = "plain"),
+		axis.text.y = element_text(face = "plain"),
 		panel.grid.major.x = element_blank(),
 		panel.grid.minor.x = element_blank(),
-		panel.background = element_rect(fill = "white", colour = NA),
-		plot.background = element_rect(fill = "white", colour = NA)
-	)
-
-ggsave(here("img", "predictions_observed.png"))
-
+		panel.background = element_rect(
+			fill = NA, 
+			colour = NA
+		),
+		plot.background = element_rect(
+			fill = "white",
+			colour = NA
+		)
+	)
+
+ggsave(
+	here("img", "predictions_observed.png"),
+	dpi = 2000,
+	height = 7,
+	width = 12
+)
 ```
@@
 
-```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-m <- emmeans(fit_3, ~trial_type | age_group, by = "lp", epred = TRUE)
-
-m_draws <- gather_emmeans_draws(m) %>% 
-	as_tibble() %>% 
-	mutate_at(vars(.value), function(x) ifelse(x < 0, 0, x)) %>% 
-	mutate_at(vars(.value), function(x) ifelse(x > 1, 1, x))
-
-m_draws %>% 
+```{r coefs-aggregated, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+str_repl_agg <- c(
+
+	# marginal terms ----
+	"b_trial_typerelated_unrelated:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+	"b_trial_typerelated_unrelated:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+	"b_trial_typecognate_noncognate:lpLPMonvs.Bil:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+	"b_trial_typecognate_noncognate:lpLPMonvs.Bil:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+	"b_trial_typecognate_noncognate:lpLPMonvs.Bil" = 
+		"Trial type (C vs. NC) \u00d7 Group",
+	"b_trial_typerelated_unrelated:lpLPMonvs.Bil" = 
+		"Trial type (U vs. C+NC) \u00d7 Group",
+	"b_trial_typerelated_unrelated:age_group21_25" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",
+	"b_trial_typerelated_unrelated:age_group25_30" = 
+		"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",
+	"b_trial_typecognate_noncognate:age_group21_25" = 
+		"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",
+	"b_trial_typecognate_noncognate:age_group25_30" = 
+		"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",
+	"b_lpLPMonvs.Bil:age_group21_25" =
+		"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",
+	"b_lpLPMonvs.Bil:age_group25_30" =
+		"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",
+	"b_lpLPMonvs.Bil" = 
+		"Group (ML vs. BL)",
+	"b_age_group21_25" = 
+		"Age (21 vs. 25 mo)",
+	"b_age_group25_30" = 
+		"Age (25 vs. 30 mo)",
+	"b_trial_typecognate_noncognate" =
+		"Trial type (C vs. NC)",
+	"b_trial_typerelated_unrelated" =
+		"Trial type (U vs. C+NC)",
+	"b_Intercept" = "Intercept",
+	"sigma" = "Standard deviation"
+)
+
+levels_agg <- c(
+	"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+	"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+	"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
+	"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
+	"Trial type (C vs. NC) \u00d7 Group",
+	"Trial type (U vs. C+NC) \u00d7 Group",
+	"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",
+	"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",
+	"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",
+	"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",
+	"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",
+	"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",
+	"Group (ML vs. BL)",
+	"Age (21 vs. 25 mo)",
+	"Age (25 vs. 30 mo)",
+	"Trial type (C vs. NC)",
+	"Trial type (U vs. C+NC)",
+	"Standard deviation",
+	"Intercept"
+)
+
+draws_agg <- gather_draws(
+	fit_agg_3, 
+	`b_.*`, 
+	`sigma`,
+	regex = TRUE
+) %>% 
+	mutate(
+		.value = ifelse(
+			.variable %in% c("sigma", "b_Intercept"),
+			inv_logit_scaled(.value),
+			.value/4
+		),
+		.variable_name = str_replace_all(.variable, str_repl_agg) %>% 
+			factor(levels = levels_agg, ordered = TRUE)
+	)
+
+a <- draws_agg %>% 
+	# filter(!(type %in% c("Sigma", "Intercept"))) %>% 
+	group_by(.variable, .variable_name) %>% 
+	summarise(
+		.lower = quantile(.value, 0.025),
+		.upper = quantile(.value, 0.975),
+		.value = mean(.value),
+		.groups = "drop"
+	) %>% 
+	mutate(
+		excludes_zero = (.lower > 0) | (.upper < 0),
+		excludes_zero = ifelse(excludes_zero, "Yes", "No") %>% 
+			factor(levels = c("Yes", "No"))
+	) %>% 
 	ggplot() +
@@
 		x = .value, 
-		y = trial_type, 
-		fill = trial_type
-	) +
-	facet_grid(lp~age_group) +
-	stat_slab(
-		aes(
-			alpha = stat(
-				cut_cdf_qi(
-					cdf, 
-					.width = c(.95, .8, .5), 
-					labels = percent_format()
-				)
-			)
-		),
-		position = position_nudge(y = 0.05),
-		color = "white"
-	) +
-	stat_pointinterval(
-		color = "black"
-	) +
-	labs(
-		x = "Expected posterior mean PTLT",
-		y = "Trial type",
-		colour = "Trial type", 
-		fill = "Trial type",
-		alpha = "CrI"
-	) +
-	guides(
-		color = "none",
-		fill = "none"
-	) +
-	scale_alpha_discrete(
-		range = c(0.8, 0.2),
-		na.translate = FALSE
-	) +
-	scale_x_continuous(
-		limits = c(0, 1),
-		labels = percent
-	)  +
-	theme(
-		axis.title.y = element_blank(),
-		legend.position = "right",
-		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-		panel.background = element_rect(fill = NA, colour = "grey")
-	)
-
-```
-
-# Model with L1 vocabulary
-
-## Fixed effects
-
-```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-str_repl <- c(
-
-	# 3-way interactions
-	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
-		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",
-
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
-		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
-		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
-		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
-		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",
-
-	# 2-way interactions
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
-	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
-
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
-		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
-		"Trial type (C vs. NC) \u00d7 Group",
-
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
-	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_l1_center" =
-		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
-
-	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" =
-		"Trial type (U vs. C+NC) \u00d7 Group",  
-	"b_time_bin_center:lpLPMonvs.Bil:vocab_size_l1_center" =
-		"Group \u00d7 Vocab (L1)",
-
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
-
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
-		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil" =
-		"Trial type (C vs. NC) \u00d7 Group",
-
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
-
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
-		"Trial type (U vs. C+NC) \u00d7 Group",  
-	"b_Itime_bin_centerE2:lpLPMonvs.Bil:vocab_size_l1_center" = 
-		"Group \u00d7 Vocab (L1)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
-		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
-		"Trial type (C vs. NC) \u00d7 Group",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
-		"Trial type (U vs. C+NC) \u00d7 Group",  
-	"b_Itime_bin_centerE3:lpLPMonvs.Bil:vocab_size_l1_center" = 
-		"Group \u00d7 Vocab (L1)",
-
-	# main effects (linear)
-	"b_time_bin_center:trial_typePrimeUvs.CPNC" =
-		"Trial type (U vs. C+NC)",
-	"b_time_bin_center:trial_typePrimeNCvs.C" = 
-		"Trial type (C vs. NC)",
-	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC" = 
-		"Trial type (U vs. C+NC)",
-	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C" = 
-		"Trial type (C vs. NC)",
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" = 
-		"Trial type (U vs. C+NC)",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" = 
-		"Trial type (C vs. NC)",
-
-	"b_time_bin_center:lpLPMonvs.Bil" = 
-		"Group (Mon. vs. Bil.)",
-	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
-		"Group (Mon. vs. Bil.)",
-	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
-		"Group (Mon. vs. Bil.)",
-
-	"b_time_bin_center:vocab_size_l1_center" = 
-		"Vocab. (L1, +1 SD)",
-	"b_Itime_bin_centerE2:vocab_size_l1_center" = 
-		"Vocab. (L1, +1 SD)",
-	"b_Itime_bin_centerE3:vocab_size_l1_center" = 
-		"Vocab. (L1, +1 SD)",
-
-	# 3-way interaction linear effects
-	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
-		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab. (L1, +1 SD)",
-	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" =
-		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab. (L1, +1 SD)",
-
-	# 2-way interaction linear effects
-	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
-		"Trial type (U vs. C+NC) \u00d7 Group",
-	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
-		"Trial type (C vs. NC) \u00d7 Group",
-
-	"b_trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
-		"Trial type (U vs. C+NC) \u00d7 Vocab. (L1, +1 SD)",
-	"b_trial_typePrimeNCvs.C:vocab_size_l1_center" = 
-		"Trial type (C vs. NC) \u00d7 Vocab. (L1, +1 SD)",
-
-	"b_lpLPMonvs.Bil:vocab_size_l1_center" =
-		"Group \u00d7 Vocab. (L1, +1 SD)",
-
-	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" =
-		"Trial type (U vs. C+NC)",
-	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" =
-		"Trial type (C vs. NC)",
-
-	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
-		"Group (Mon. vs. Bil.)",
-
-	# main linear effects
-	"b_Intercept" = "Intercept",
-	"b_Itime_bin_centerE2" = "Time bin 2",
-	"b_Itime_bin_centerE3" = "Time bin 3",
-	"b_time_bin_center" = "Time bin",
-	"b_vocab_size_l1_center" = "Vocab. (L1, +1 SD)",
-
-	"b_trial_typePrimeUvs.CPNC" = "Trial type (U vs. C+NC)",
-	"b_trial_typePrimeNCvs.C" = "Trial type (C vs. NC)",
-	"b_lpLPMonvs.Bil" = "Group (Mon. vs. Bil.)",
-
-	# sigma
-	"sigma" = "Sigma"
-)
-
-draws <- gather_draws(fit_l1_4, `b_.*`, `sigma`, regex = TRUE) %>% 
-	mutate(
-		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
-		.variable_name = str_replace_all(.variable, str_repl),
-		type = case_when(
-			str_detect(.variable, "E2") ~ "Quadratic time",
-			str_detect(.variable, "E3") ~ "Cubic time",
-			str_detect(.variable, "time_bin") ~ "Linear time",
-			str_detect(.variable, "sigma") ~ "Error",
-			TRUE ~ "Main effects"
-		) %>% 
-			factor(
-				levels = c(
-					"Main effects",
-					"Linear time", 
-					"Quadratic time",
-					"Cubic time", 
-					"Error"
-				), 
-				ordered = TRUE
-			)
-	)
-
-draws %>% 
-	group_by(.variable, .variable_name, type) %>% 
-	mean_qi() %>% 
-	select(type, .variable_name, .value, .lower, .upper) %>% 
-	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
-	fmt_percent(3) %>%
-	fmt_number(4:5, scale_by = 100) %>% 
-	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
-	cols_label(
-		.variable_name = md("**Predictor**"),
-		.value = md("**Mean**"),
-		.lower = md("**95% CrI**")
-	) %>% 
-	tab_style(
-		cell_text(weight = "bold", style = "italic"),
-		cells_row_groups()
-	) %>%
-	as_raw_html()
-```
-
-```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}
-
-draws_intercept <- draws %>% 
-	filter(str_detect(.variable, "Intercept")) %>% 
-	ggplot(aes(.value, .variable_name)) +
-	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
-	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
-		size = 0.5,
-		color = "#FF6F00FF",
-		fill = "#FF6F00FF"
-	) +
-	labs(
-		x = "Value", 
-		y = "Variable", 
-		fill = "CrI", 
-		title = "Intercept",
-		alpha = "CrI"
-	) +
-	guides(fill = "none", color = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	theme(
-		panel.grid.major.y = element_blank()
-	)
-
-ggsave(here("img", "posterior_intercept_l1.png"), draws_intercept, height = 2, width = 7)
-
-draws_predictors <- draws %>% 
-	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
-	ggplot(aes(.value, .variable_name)) +
-	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
-	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
-		size = 0.5, 
-		color = "#C71000FF", 
-		fill = "#C71000FF"
+		y = .variable_name,
+		xmin = .lower,
+		xmax = .upper,
+		colour = excludes_zero
+	) +
+	geom_vline(
+		xintercept = 0,
+		colour = "black", 
+		linetype = "dashed"
+	) +
+	geom_pointinterval(
+		size = 5,
+		point_size = 3
 	) +
@@
 		alpha = "CrI",
-		title = "Main effects"
-	) +
-	guides(fill = "none", color = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2)) +
+		title = "Main effects",
+		subtitle = "Mean and 95% credible interval of posterior distribution",
+		colour = "Interval excludes zero?"
+	) +
+	scale_color_manual(values = rev(pal_d3()(2))) +
+	scale_x_continuous(
+		labels = percent
+	) +
 	theme(
-		panel.grid.major.y = element_blank()
-	)
-
-ggsave(here("img", "posterior_predictors_l1.png"), draws_predictors, height = 7, width = 7)
-
-draws_time <- draws %>%
-	filter(str_detect(.variable, "time_bin")) %>% 
-	ggplot(aes(.value, .variable_name)) +
-	facet_wrap(~type, scales = "free_x") +
-	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
-	# stat_slab(
-	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
-	# 	size = 0.5, 
-	# 	color = "#008EA0FF", 
-	# 	fill = "#008EA0FF"
-	# ) +
-	stat_pointinterval(
-		color = "#008EA0FF",
-		fill = "#008EA0FF",
-		point_size = 1.5
-	) +
-	labs(
-		x = "Value", 
-		y = "Variable", 
-		fill = "CrI", 
-		alpha = "CrI",
-		title = "Polynomial effects"
-	) +
-	guides(fill = "none", color = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent) +
-	theme(
-		panel.grid.major.y = element_blank(),
-		panel.border = element_rect(fill = NA, colour = "grey"),
-		axis.title = element_blank()
-	)
-
-ggsave(here("img", "posterior_poly_l1.png"), draws_time, height = 7, width = 9)
-
-draws_sigma <- draws %>% 
-	filter(str_detect(.variable, "sigma")) %>% 
-	ggplot(aes(.value, .variable_name)) +
-	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
-		size = 0.5, 
-		color = "#8A4198FF", 
-		fill = "#8A4198FF"
-	) +
-	labs(
-		x = "Value", 
-		y = "Variable", 
-		alpha = "CrI",
-		fill = "CrI", 
-		title = "Error"
-	) +
-	guides(fill = "none", color = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
-	scale_fill_brewer(direction = -1, na.translate = FALSE) +
-	scale_x_continuous(labels = percent, limits = c(0.92, 0.96)) +
-	theme(
-		panel.grid.major.y = element_blank()
-	)
-
-ggsave(here("img", "posterior_sigma_l1.png"), draws_sigma, height = 2, width = 7)
-
-((draws_intercept / draws_sigma / guide_area()) | draws_predictors) /
-	draws_time + 
-	plot_layout(heights = c(0.5, 0.5)) &
-	guides(fill = "none", color = "none") &
-	theme(
-		panel.background = element_rect(fill = NA, colour = "grey"),
-		axis.text.y = element_text(size = 7),
-		axis.text.x = element_text(size = 7),
-		axis.title = element_blank(),
-		legend.position = c(1, 1.2),
-		legend.direction = "horizontal",
-		legend.justification = "right",
-		legend.key.size = unit(0.35, "cm"),
-		legend.text = element_text(size = 7),
-		legend.title = element_text(size = 7),
-		panel.grid.major.y = element_blank()
-	)
+		legend.position = "top",
+		axis.title.y = element_blank(),
+		axis.text.y = element_text(hjust = 1),
+		panel.border = element_rect(colour = "black", fill = NA)
+	)
+
+ggsave(here("img", "coefficients_agg.png"), height = 10, width = 13)
 
@@
 
-## Random effects
-
-```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8,fig.height=4}
-
-corr_mat <- VarCorr(fit_l1_4, summary = TRUE)$participant$cor 
-corr_names <- rownames(VarCorr(fit_l1_4, summary = TRUE)$participant$cor)
-
-corr_mat <- corr_mat %>% 
-	as_tibble() %>% 
-	select(matches("Estimate")) %>% 
-	rename_all(str_remove, "Estimate.") %>% 
-	mutate(term1 = corr_names)
-
-corr_mat[lower.tri(corr_mat)] <- NA
-
-corr_data <- corr_mat %>% 
-	as.data.frame() %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	drop_na(.value)
-
-post_cors_participant <- corr_data %>% 
-	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
-	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
-	mutate(
-		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
-		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
-	) %>% 
-	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
-	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
-	geom_tile(na.rm = TRUE) +
-	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
-	labs(
-		x = "Term 1", 
-		y = "Term 2", 
-		fill = "Posterior\ncorrelation",
-		title = "By participant"
-	) +
-	scale_fill_gradient2(
-		low = "#04bf78", mid = "white", high = "#FFC20A", 
-		na.value = "white", limits = c(-0.4, 0.4)
-	) +
-	scale_x_discrete() +
-	coord_equal()  +
-	theme(
-		axis.text.y = element_text(size = 7)
-	)
-
-# correlations by item
-corr_mat <- VarCorr(fit_l1_4, summary = TRUE)$target$cor 
-corr_names <- rownames(VarCorr(fit_l1_4, summary = TRUE)$target$cor)
-
-corr_mat <- corr_mat %>% 
-	as_tibble() %>% 
-	select(matches("Estimate")) %>% 
-	rename_all(str_remove, "Estimate.") %>% 
-	mutate(term1 = corr_names)
-
-corr_mat[lower.tri(corr_mat)] <- NA
-
-corr_data <- corr_mat %>% 
-	as.data.frame() %>% 
-	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
-	drop_na(.value)
-
-post_cors_item <- corr_data %>% 
-	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
-	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
-	mutate(
-		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
-		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
-	) %>% 
-	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
-	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
-	geom_tile(na.rm = TRUE) +
-	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
-	labs(
-		x = "Term 1", y = "Term 2", fill = "Posterior\ncorrelation",
-		title = "By item"
-	) +
-	scale_fill_gradient2(
-		low = "#04bf78", mid = "white", high = "#FFC20A", 
-		na.value = "white", limits = c(-0.4, 0.4)
-	) +
-	scale_x_discrete() +
-	coord_equal() +
-	theme(
-		axis.text.y = element_blank()
-	)
-
-(post_cors_participant | post_cors_item) &
-	plot_layout(guides = "collect") &
-	theme(
-		panel.grid = element_blank(),
-		legend.position = "top",
-		legend.direction = "horizontal",
-		legend.key.height = unit(0.1, "cm"),
-		legend.key.width = unit(0.3, "cm"),
-		legend.justification = c(1, 1),
-		legend.title = element_blank(),
-		legend.text = element_text(size = 5),
-		axis.title.x = element_blank(),
-		axis.title.y = element_blank(),
-		axis.ticks = element_blank(),
-		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)
-
-	)
-
-```
-
-## Posterior predictions (after seeing the data)
-
-```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(lp, vocab_size_l1_center)
-
-n <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	vocab_size_l1_center = c(-1, 1),
-	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
-)
-
-m <- epred_draws(object = fit_l1_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
-	mutate(
-		.value = logit_to_prob(.epred),
-		vocab_size_l1_center = ifelse(
-			vocab_size_l1_center==-1, 
-			"Low vocabulary size (-1 SD)",
-			"High vocabulary size (+1 SD)"
-		) %>% 
-			factor(levels = c(
-				"Low vocabulary size (-1 SD)",
-				"High vocabulary size (+1 SD)"
-			),
-			ordered = TRUE)
-	)
-
-ggplot(m, aes(time_bin_center, .value, fill = trial_type, colour = trial_type)) +
-	facet_grid(fct_rev(lp)~vocab_size_l1_center) +
-	geom_hline(yintercept = 0.5, colour = "black") +
-	# geom_line(
-	# 	aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
-	# 		colour = trial_type),
-	# 	alpha = 0.5, size = 0.65
-	# ) +
-	stat_lineribbon(.width = 0.95, alpha = 0.5, color = NA) +
-	stat_lineribbon(.width = 0.95, fill = NA) +
-	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
-		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
-	scale_color_futurama() +
-	scale_fill_futurama() +
-	scale_x_continuous(
-		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
-		labels = 1:20
-	) +
-	scale_y_continuous(limits = c(0, 1), labels = percent) + 
-	theme_minimal() +
-	theme(
-		text = element_text(size = 15),
-		legend.position = "top",
-		legend.title = element_blank(),
-		axis.text.x = element_text(size = 7),
-		axis.text.y = element_text(size = 9),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		panel.background = element_rect(fill = "white", colour = NA),
-		panel.border = element_rect(fill = NA, colour = "grey"),
-		plot.background = element_rect(fill = "white", colour = NA)
-	)
-
-ggsave(here("img", "epreds_l1.jpeg"), dpi = 1000)
-
-```
-
-```{r gaze_matrix, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-sample_size <- participants %>% 
-	filter(valid_participant) %>% 
-	count(lp, vocab_size_l1_center)
-
-n <- expand_grid(
-	lp = c("Monolingual", "Bilingual"),
-	vocab_size_l1_center = seq(-2, 2, 0.25),
-	trial_type = unique(gaze$trial_type),
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.25)
-)
-
-m <- epred_draws(object = fit_l1_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
-	median_qi() %>%  
-	mutate(.value = logit_to_prob(.epred))
-
-ggplot(m, aes(time_bin_center, vocab_size_l1_center, fill = .value)) +
-	facet_grid(fct_rev(lp)~trial_type) +
-	# geom_line(
-	# 	aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
-	# 		colour = trial_type),
-	# 	alpha = 0.5, size = 0.65
-	# ) +
-	geom_raster(interpolate = TRUE) +
-	labs(
-		x = "Time bin (100 ms)", 
-		y = "Vocabulary size (SD)", 
-		colour = "Expected posterior mean PTLT",
-		fill = "Expected posterior mean PTLT",
-		shape = "Expected posterior mean PTLT",
-		linetype = "Expected posterior mean PTLT"
-	) +
-	scale_fill_viridis_c(labels = percent, option = "plasma") +
-	scale_x_continuous(
-		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
-		labels = 1:20
-	) +
-	theme_minimal() +
-	theme(
-		text = element_text(size = 15),
-		legend.position = "top",
-		legend.text = element_text(size = 9),
-		legend.key.width = unit(1, "cm"),
-		axis.text.x = element_text(size = 7),
-		axis.text.y = element_text(size = 9),
-		panel.grid.major.x = element_blank(),
-		panel.grid.minor.x = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		panel.grid.major.y = element_blank(),
-		panel.background = element_rect(fill = "white", colour = NA),
-		plot.background = element_rect(fill = "white", colour = NA)
-	)
-
-ggsave(here("img", "epreds_l1_3d.jpeg"), dpi = 1000)
-
-```
-
-## Marginal means {.tabset }
-
-```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-m <- emmeans(fit_l1_4, ~trial_type | lp, epred = TRUE)
+```{r gaze_marginal, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=7, fig.height=7}
+
+m <- emmeans(
+	fit_agg_3, 
+	~trial_type | age_group, 
+	by = "lp",
+	epred = TRUE
+)
 
@@
 	mutate_at(vars(.value), function(x) ifelse(x < 0, 0, x)) %>% 
-	mutate_at(vars(.value), function(x) ifelse(x > 1, 1, x))
-
-ggplot(m_draws, aes(.value, trial_type, colour = trial_type, fill = trial_type)) +
-	facet_wrap(~lp) +
-	stat_slab(
-		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
-		position = position_nudge(y = 0.05)
+	mutate_at(vars(.value), function(x) ifelse(x > 1, 1, x)) %>% 
+	mutate(.value = inv_logit_scaled(.value))
+
+observed <- fit_agg_3$data %>% 
+	mutate(.value = inv_logit_scaled(logit))
+
+m_draws %>% 
+	ggplot() +
+	aes(
+		x = trial_type, 
+		y = .value, 
+		fill = trial_type,
+		colour = trial_type
+	) +
+	facet_grid(lp~age_group) +
+	geom_hline(
+		yintercept = 0.5,
+		linetype = "dotted"
+	) +
+	geom_text(
+		data = sample_size,
+		aes(
+			x = "Cognate",
+			y = 1,
+			label = paste0("N = ", n)
+		),
+		colour = "black",
+		hjust = 0,
+		vjust = 1,
+		inherit.aes = FALSE,
+		position = position_nudge(x = -0.75)
+	) +
+	stat_pointinterval(
+		data = observed,
+		position = position_nudge(x = -0.4),
+		.width = 0.95,
+		size = 4,
+		point_size = 3
+	) +
+	geom_point(
+		data = observed,
+		position = position_jitter(width = 0.05),
+		shape = 1,
+		stroke = 1,
+		size = 2,
+		alpha = 0.25
 	) +
@@
 		color = "black",
+		position = position_nudge(x = -0.2),
+		point_size = 3,
+		.width = 0,
+		shape = 4,
+		show.legend = FALSE
 	) +
 	labs(
-		x = "Expected posterior mean PTLT", y = "Trial type",
-		colour = "Trial type", fill = "Trial type",
-		alpha = "CrI"
-	) +
-	guides(color = "none", fill = "none") +
-	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
-	scale_x_continuous(limits = c(0.5, 1), labels = percent)  +
+		x = "Trial type",
+		y = "PTLT",
+		colour = "Trial type", 
+		fill = "Trial type",
+		alpha = "CrI",
+		title = "PTLT aggregated for time windows of interest",
+		subtitle = "Black crosses indicate the mean of the posterior predictions of the model.\nPoints and whiskers indicate observed PTLTS."
+	) +
+	scale_y_continuous(
+		limits = c(0, 1),
+		labels = percent
+	)  +
+	scale_fill_d3() +
+	scale_color_d3() +
 	theme(
-		axis.title.y = element_blank(),
-		legend.position = "right",
-		panel.grid.major.y = element_blank(),
-		panel.grid.minor.y = element_blank(),
-		panel.grid.minor.x = element_blank(),
+		legend.position = "top",
+		legend.title = element_blank(),
+		axis.text.x = element_text(colour = "black", hjust = 0.5),
+		axis.title.x = element_blank(),
+		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
 		panel.background = element_rect(fill = NA, colour = "grey")
@@
 
-ggsave(here("img", "emmeans_l1.jpeg"), dpi = 1000)
+ggsave(here("img", "predictions_aggregated.png"), height = 8, width = 15)
 

### 2022-12-15 index.qmd
Restore workflow

---
title: "Cognate Priming"
subtitle: "Lab notes"
date: "Updated: `r format(Sys.Date(), '%Y/%m/%d')`"
authors:
  - name: Gonzalo Garcia-Castro
    orcid: 0000-0002-8553-4209
    email: gonzalo.garciadecastro@upf.edu
    corresponding: true
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
        address: Ramon Trias fargas 25-27
        city: Barcelona
        state: Spain
        postal-code: 08005
abstract: "Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language (e.g., Costa et al., 2000; Thierry & Wu, 2007). It has been suggested that this parallel activation is already present during toddlerhood (Jardak & Byers-Heinlein, 2019; Von Holzen & Mani, 2012), but it is unclear how it impacts the developing lexicon. In the present study, we tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task, in which they were presented with words in their dominant language exclusively. In each trial, two pictures were presented side-by-side and one of them was named (target picture). Participants' visual preference for the named picture was taken as an indicator of word recognition. Each pair of pictures was preceded by the presentation of a silent image (prime picture). We designed three types of trials: (1) cognate trials in which prime and target labels shared phonological onset and the prime label was a cognate (e.g., flower-flor / fork), (2) non-cognate trials, in which prime and target labels shared phonological onset but the prime label was a non-cognate (e.g., frog-rana / fork), and (3) unrelated trials, in which prime and target labels did not share onset (unrelated trials; car-coche / fork). In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset (e.g., Mani & Plunkett, 2011). Additionally, under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we predicted that interference would be stronger after cognate primes (labels from both languages share phonological overlap with target word recognition) than after non-cognate primes (only the label in the target language share phonological overlap with target word recognition). We tested bilinguals (n = 46) and same-aged monolingual controls, n = 123) at three age points (21, 25, and 30 months) to investigate how any cross-language priming effect emerged or changed across these ages."
format:
    html:
        link-external-newwindow: true
        number-offset: 0
        code-fold: true
        code-overflow: scroll
        code-line-numbers: true
        code-copy: hover
        reference-location: margin
        execute-dir: "C:/Users/U155880/Documents/trajectories/"
    pdf: default
    docx:
        reference-doc: reference.docx
fig-dpi: 1000
warning: false
echo: false
toc: true
colorlinks: true
number-sections: true
bibliography: "references.bib"
csl: "apa7.csl"
---

```{r}
#| label: setup
tar_load_globals()
tar_load_everything()

# set ggplot theme and colour palette
theme_set(theme_custom()) # set custom ggplot theme
clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")

options(
	ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
	ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
	ggplot2.discrete.fill = clrs[c(1, 4, 5)],
	ggplot2.discrete.colour = clrs[c(1, 4, 5)],
	ggplot2.continuous.fill = ggplot2::scale_color_gradient,
	ggplot2.continuous.colour = ggplot2::scale_color_gradient
)

# prepare data
attrition <- attrition %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))

participants <- participants %>% 
	left_join(distinct(attrition, id, age_group, valid_participant)) %>% 
	drop_na(id) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])

```

# Methods

## Participants

We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.

After applying trial- and participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.

From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.

```{r}
#| label: tbl-participants-summary
#| tbl-cap: "Testing sessions"
participants %>% 
	left_join(distinct(attrition, id, valid_participant)) %>% 
	drop_na(valid_participant) %>% 
	count(age_group, lp, test_language) %>% 
	pivot_wider(names_from = age_group,
				values_from = n, 
				values_fill = 0) %>% 
	clean_names() %>% 
	gt(rowname_col = "test_language", groupname_col = "lp") %>% 
	cols_label(x21_months = "21 months",
			   x25_months = "25 months",
			   x30_months = "30 months") %>% 
	summary_rows(group = TRUE,
				 columns = where(is.numeric),
				 fns = list("n" = ~sum(.)),
				 formatter = fmt_number,
				 decimals = 0) %>% 
	grand_summary_rows(columns = where(is.numeric),
					   fns = list("N" = ~sum(.)),
					   formatter = fmt_number,
					   decimals = 0) %>% 
	tab_style(style = cell_fill("grey82"),
			  locations = list(cells_row_groups())) %>% 
	tab_style(cell_text(weight = "bold"), cells_column_labels())
```

```{r}
#|  label: fig-participants-summary
participants %>% 
	left_join(distinct(attrition, id, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = test_language)) +
	facet_grid(~age_group, scales = "free") +
	geom_bar(colour = NA) +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(legend.position = "top",
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 10),
		  axis.title.y = element_text(angle = 90),
		  panel.grid.major.x = element_blank()) 
```

### Longitudinal participants

We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30). Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.

```{r}
#| label: fig-participants-longitudinal
#| fig-height: 10
#| fig-width: 4
participants %>% 
	left_join(distinct(attrition, id, valid_participant)) %>%
	filter(valid_participant) %>% 
	add_count(id, lp, name = "n_total") %>% 
	count(id, age_group, test_language, lp, n_total) %>% 
	pivot_wider(id_cols = c(id, lp, test_language, n_total),
				names_from = age_group,
				values_from = n,
				values_fill = 0) %>% 
	pivot_longer(5:7,
				 names_to = "age_group",
				 values_to = "n") %>% 
	mutate(id_reordered = reorder_within(id, by = n_total, within = list(test_language, lp))) %>% 
	ggplot(aes(age_group, id_reordered, fill = as.factor(n))) + 
	facet_wrap(test_language~lp, scales = "free_y") +
	geom_tile(colour = "white") +
	labs(x = "Age (months)", 
		 y = "Exposure to 2nd language", 
		 fill = "Lang. Profile") +
	scale_fill_manual(values = c("white", clrs[4], "white")) +
	theme(legend.position = "none",
		  legend.title = element_blank(),
		  panel.grid = element_blank(),
		  axis.text = element_text(size = 10),
		  axis.title.y = element_blank(),
		  axis.text.y = element_blank(),
		  axis.ticks.y = element_blank())

```

### Sample description

```{r}
#| label: fig-participants-lp
#| fig-height: 7
participants %>% 
	select(id, age_group, age, lp, starts_with("doe_"), test_language) %>% 
	mutate(id = paste0(id, " (", age_group, ")"),) %>% 
	pivot_longer(starts_with("doe_"), names_to = "language", values_to = "doe") %>%
	mutate(language = str_remove_all(language, "doe_") %>% 
		   	str_to_sentence(),
		   test_language = paste0("Tested in ", test_language)) %>% 
	group_by(age_group, lp, test_language, language) %>% 
	summarise(n = n(), 
			  across(c(age, doe), lst(mean, sd, min, max)),
			  .groups = "drop") %>% 
	pivot_wider(names_from = c(language),
				values_from = matches("doe")) %>% 
	clean_names() %>% 
	relocate(age_group, lp, test_language, n,
			 matches("age"), matches("catalan"),
			 matches("spanish"), matches("other")) %>% 
	gt(rowname_col = "test_language", groupname_col = c("age_group", "lp")) %>% 
	tab_spanner("Age (months)", c(matches("age"), -age_group)) %>% 
	tab_spanner("Catalan DoE", matches("catalan")) %>% 
	tab_spanner("Spanish DoE", matches("spanish")) %>% 
	tab_spanner("Others DoE", matches("others")) %>% 
	fmt_number(c(starts_with("age"), -age_group)) %>% 
	fmt_percent(matches("doe"), decimals = 1) %>% 
	cols_merge_uncert(col_val = age_mean, col_uncert = age_sd) %>% 
	cols_merge_uncert(col_val = doe_mean_catalan, col_uncert = doe_sd_catalan) %>% 
	cols_merge_uncert(col_val = doe_mean_spanish, col_uncert = doe_sd_spanish) %>% 
	cols_merge_uncert(col_val = doe_mean_others, col_uncert = doe_sd_others) %>% 
	cols_merge_range(col_begin = age_min, col_end = age_max) %>% 
	cols_merge_range(col_begin = doe_min_catalan, col_end = doe_max_catalan) %>% 
	cols_merge_range(col_begin = doe_min_spanish, col_end = doe_max_spanish) %>% 
	cols_merge_range(col_begin = doe_min_others, col_end = doe_max_others) %>% 
	cols_label(n = "N",
			   age_mean = "Mean",
			   age_min = "Range",
			   doe_mean_catalan = "Mean ± SD",
			   doe_min_catalan = "Range",
			   doe_mean_spanish = "Mean ± SD",
			   doe_min_spanish = "Range",
			   doe_mean_others = "Mean ± SD",
			   doe_min_others = "Range") %>% 
	summary_rows(group = TRUE,
				 columns = c(where(is.numeric), -n),
				 fns = list("Mean" = ~mean(.)),
				 formatter = fmt_number,
				 decimals = 1) %>% 
	summary_rows(group = TRUE,
				 columns = c(where(is.numeric), -n, -matches("age")),
				 fns = list("Mean" = ~mean(.)),
				 formatter = fmt_percent,
				 decimals = 1) %>% 
	grand_summary_rows(columns = c(where(is.numeric), -n),
					   fns = list("Grand mean" = ~mean(.)),
					   formatter = fmt_number,
					   decimals = 1) %>% 
	grand_summary_rows(columns = c(where(is.numeric), -n, -matches("age")),
					   fns = list("Grand mean" = ~mean(.)),
					   formatter = fmt_percent,
					   decimals = 1) %>% 
	tab_style(style = cell_fill("grey82"),
			  locations = list(cells_row_groups())) %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners(),
			  	 cells_grand_summary(),
			  	 cells_row_groups(),
			  	 cells_stub_grand_summary(),
			  	 cells_stub_summary()))
```

## Stimuli

### Lexical frequency

::: {.tabset-panel}

#### Prime

```{r}
#| label: fig-stimuli-frequency-prime
#| fig-height: 5
stimuli %>% 
	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot() +
	aes(x = trial_type, 
		y = freq_prime, 
		colour = trial_type, 
		fill = trial_type) +
	facet_wrap(~test_language) +
	stat_slab(fill = "grey", colour = "white", scale = 0.5, adjust = 2,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(colour = "black", fill = "white", size = 0.75, 
				 outlier.colour = NA, width = 0.1,
				 position = position_nudge(x = 0.3)) + 
	geom_point(shape = 1, stroke = 1.25, size = 3,
			   position = position_jitter(width = 0.15, seed = 888)) +
	labs(x = "Trial type", 
		 y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", 
		 fill = "Trial type") +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted"))
```

#### Target

```{r}
#| label: fig-stimuli-frequency-target,
#| fig-height: 5
stimuli %>% 
	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot() +
	aes(x = trial_type, y = freq_target, 
		colour = trial_type, fill = trial_type) + 
	facet_wrap(~test_language) +
	stat_slab(fill = "grey", colour = "white", scale = 0.5, adjust = 2,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(colour = "black", fill = "white", size = 0.75, 
				 outlier.colour = NA, width = 0.1,
				 position = position_nudge(x = 0.3)) + 
	geom_point(shape = 1, stroke = 1.25, size = 3,
			   position = position_jitter(width = 0.15, seed = 888)) +
	labs(x = "Trial type",
		 y = "Lexical frequency (Zipf score)",
		 colour = "Trial type",
		 fill = "Trial type") +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted"))
```

:::

### Familiarity

::: {.tabset-panel}

#### Prime

```{r}
#| label: fig-stimuli-familiarity-prime
#| fig-height: 7
means <- stimuli %>% 
	distinct(test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	group_by(test_language, trial_type) %>% 
	summarise(familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
			  .groups = "drop") %>% 
	drop_na()

stimuli %>% 
	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
	mutate(prime = reorder_within(prime, familiarity_prime, list(test_language))) %>% 
	ggplot() +
	aes(familiarity_prime, 
		reorder(prime, familiarity_prime),
		colour = trial_type, 
		fill = trial_type,
		xmin = familiarity_prime-familiarity_se_prime,
		xmax = familiarity_prime+familiarity_se_prime) +
	facet_wrap(~test_language, scales = "free_y") +
	# geom_vline(data = means, 
	# 		   aes(xintercept = familiarity_prime, 
	# 		   	colour = trial_type),
	# 		   size = 1) +
	geom_errorbar(width = 0.5) +
	geom_point() +
	labs(x = "% of infants that understand",
		 y = "Prime word",
		 colour = "Trial type", 
		 fill = "Trial type") +
	scale_y_reordered() +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	theme(legend.position = "top",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 7, hjust = 1),
		  axis.title.y = element_blank(),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  plot.caption = element_text(size = 10, hjust = 0))
```

#### Target

```{r}
#| label: stimuli-familiarity-target
#| fig-height: 6.5
means <- stimuli %>% 
	distinct(test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
	group_by(test_language, trial_type) %>% 
	summarise(familiarity_target = mean(familiarity_target, na.rm = TRUE),
			  .groups = "drop")

stimuli %>% 
	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
	mutate(target = reorder_within(target, familiarity_target, list(test_language))) %>% 
	ggplot(aes(x = familiarity_target, 
			   y = target, 
			   colour = trial_type,
			   fill = trial_type,
			   xmin = familiarity_target-familiarity_se_target,
			   xmax = familiarity_target+familiarity_se_target)) +
	facet_wrap(~test_language,  scales = "free_y") +
	# geom_vline(data = means,
	# 		   aes(xintercept = familiarity_target,
	# 		   	colour = trial_type), 
	# 		   size = 1) +
	geom_errorbar(width = 0.5) +
	geom_point(shape = 1, size = 0.5, stroke = 1) +
	labs(x = "% of infants that understand",
		 y = "Target word",
		 colour = "Trial type",
		 fill = "Trial type") +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	scale_y_reordered() +
	theme(legend.position = "top",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 7, hjust = 1),
		  axis.title.y = element_blank(),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  plot.caption = element_text(size = 10, hjust = 0))
```

:::

### Animacy

```{r}
#| label: fig-stimuli-animacy
#| fig-height: 6
animacy <- stimuli %>%
	distinct(test_language, 
			 target, 
			 prime, 
			 .keep_all = TRUE) %>% 
	pivot_longer(c(is_animate_prime, is_animate_target), 
				 names_to = "role",
				 values_to = "is_animate") %>% 
	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
	count(test_language,  trial_type, role, is_animate) %>% 
	drop_na(is_animate) %>% 
	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))

animacy %>% 
	# filter(role=="Prime") %>% 
	ggplot() +
	aes(x = trial_type, 
		y = n, 
		fill = is_animate,
		colour = is_animate) + 
	facet_grid(test_language~role) +
	geom_col(position = position_fill(), colour = "white", size = 0.75) +
	geom_hline(yintercept = 0.5,  size = 1, colour = "grey") +
	labs(title = "Prime", 
		 x = "Trial type", 
		 y = "# trials",
		 colour = "Animacy", 
		 fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(legend.position = "top",
		  legend.title = element_blank(),
		  panel.grid = element_blank(),
		  axis.title.y = element_blank(),
		  axis.text = element_text(size = 7),
		  axis.text.y = element_text(hjust = 1),
		  strip.text = element_text(size = 11))
```

### Semantic category

```{r}
#| label: fig-stimuli-category 
#| fig-height: 7
#| fig-width: 12
stimuli %>% 
	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
	pivot_longer(c(semantic_category_prime, semantic_category_target),
				 names_to = "role",
				 values_to = "semantic_category") %>% 
	mutate(role = str_to_sentence(str_remove(role, "semantic_category_"))) %>% 
	drop_na(trial_type, semantic_category) %>% 
	count(trial_type, test_language, role, semantic_category, name = "sum") %>% 
	right_join(expand(., trial_type,  test_language,  role,  semantic_category)) %>%
	replace_na(list(sum = 0)) %>% 
	group_by(trial_type, test_language, role) %>% 
	mutate(n =  sum(sum), prop = sum/n) %>% 
	ungroup() %>% 
	ggplot() +
	aes(x = prop,
		y = reorder_within(semantic_category, 
						   desc(prop), 
						   list(trial_type, role, test_language)),
		fill = test_language,
		order = prop) + 
	facet_wrap(trial_type~role~test_language,
			   scales = "free_y",
			   labeller = label_wrap_gen(multi_line = FALSE)) +
	geom_col(colour = "white",
			 position = position_dodge(),
			 width = 1) +
	labs(x = "% of trials",
		 y = "Trial type",
		 colour = "Trial type",
		 fill = "Trial type") +
	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
	scale_y_reordered() +
	theme(legend.position = "none",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 9, hjust = 1),
		  axis.text.x = element_text(size = 8, hjust = 1),
		  axis.title.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  plot.caption = element_text(size = 10, hjust = 0),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  strip.text = element_text(size = 10))
```

## Vocabulary

We collected vocabulary data from participants. In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment. In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvqdev) immediately after the appointment, and were given two weeks to fill it. In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language. In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists. All checklists included the words involved in the trial lists. When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*. Each response to either checklist was aggregated to produce several vocabulary measures:

* **Total vocabulary**: total number of words the child knows, summing up both languages. For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language). For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages. For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.

Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm 1$ month) and language profile (similar exposure to a second language, $\pm 10%$) that completed the same vocabulary checklist previously.

### L1 vocabulary

This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis. Results are presented separately for each age group. The shape of the violins, represents the distribution of the vocabulary sizes. The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values. vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure. for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.

```{r}
#| label: fig-vocabulary-l1
#| fig-cap: "L1 vocabulary. Percentage of words in L1 reported to be understood from the vocabulary checklist."
#| fig-height: 4
sample_size <- participants %>% 
	filter(id %in% fit_0$data$id) %>% 
	count(age_group)

sample_size_lp <- participants %>% 
	filter(id %in% fit_0$data$id) %>% 
	count(age_group, lp) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_l1, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

### Total vocabulary

```{r}
#| label: fig-vocabulary-total
#| fig-cap: "Total vocabulary"
#| fig-height: 4
# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_total, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

### Conceptual vocabulary

```{r}
#| label: fig-vocabulary-conceptual
#| fig-height: 4
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_conceptual, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

## Design

## Data analysis

**Parameters**:

$$
\begin{align}
y_{ij} =&~ (\beta_{0} + \beta_{0p} + \beta_{0i}) ~+~ ... \\ 
& (\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} ~+~ ... \\
& (\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} ~ + ~ ... \\
& (\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} ~ + ~ ... \\
& (\beta_{4} + \beta_{4i}) \times Group_{pi} ~+~ ... \\
& (\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) ~+~ ... \\
& (\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) ~+~ ... \\
& (\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) ~+~ ... \\
& (\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) ~+~ \\ & \sigma^2_{e}
\end{align}
$$

**Priors**:

$$
\begin{align}
\beta_0 \sim~ & \mathcal{N}(0, 1) \\
\beta_{1-8} \sim~ &\mathcal{N}(0, 1) \\
\sigma_m, ~\sigma^2,~ \sigma^2_p,~ \sigma^2_i \sim~ & exp(2) \\
\rho \sim ~&  LKJ(2)
\end{align}
$$

### Prior expected predicted mean

```{r}
#| label: fig-prior-epred
nd <- tibble(time_bin = seq(0, 20, 0.1)) %>% 
	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)

m <- add_epred_draws(nd, fit_prior, ndraws = 50, re_formula = NA) %>% 
	mutate(.epred = plogis(.epred))

ggplot(m, aes(time_bin, .epred)) +
	geom_hline(yintercept = 0.5, colour = "grey", size = 1) +
	geom_line(aes(group = .draw), colour = clrs[4], size = 1, alpha = 0.5) +
	labs(x = "Time (ms)",
		 y = "Proportion of target looking time") +
	scale_y_continuous(labels = percent) +
	scale_x_continuous(labels = function(x) format(x*100, big.mark = ","))
```

# Results

## Attrition

::: {.tabset-panel}

### By participants

```{r}
#| label: fig-attrition-vocab
#| fig-height: 4
n_text <- participants %>% 
	left_join(distinct(attrition, id, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is_imputed ~ "Valid (observed CDI)",
			valid_participant & is_imputed ~ "Valid (imputed CDI)",
			!valid_participant ~ "Excluded"
		)
	) %>% 
	filter(valid_status != "Excluded") %>% 
	count(lp, age_group) %>% 
	mutate(n_label = paste0(n, " valid"),
		   valid_status = "Valid (observed CDI)")

participants %>% 
	left_join(distinct(attrition, id, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(valid_status = case_when(
		valid_participant & !is_imputed ~ "valid_cdi_observed",
		valid_participant & is_imputed ~ "valid_cdi_imputed",
		!valid_participant ~ "excluded")) %>% 
	add_count(age_group, lp, name = "n_total") %>% 
	count(age_group, lp, n_total, valid_status) %>% 
	pivot_wider(names_from = valid_status, values_from = n, values_fill = 0) %>% 
	relocate(age_group, lp, n_total, valid_cdi_observed, valid_cdi_imputed, excluded) %>% 
	mutate(across(matches("valid_|excluded"), ~./n_total, .names = "{.col}_prop")) %>% 
	gt(rowname_col = "lp", groupname_col = "age_group") %>% 
	fmt_percent(matches("prop"), decimals = 1) %>% 
	cols_merge_n_pct(col_n = valid_cdi_observed, col_pct = valid_cdi_observed_prop) %>% 
	cols_merge_n_pct(col_n = valid_cdi_imputed, col_pct = valid_cdi_imputed_prop) %>% 
	cols_merge_n_pct(col_n = excluded, col_pct = excluded_prop) %>% 
	tab_spanner("Included participants", matches("valid")) %>% 
	tab_spanner("Excluded participants", matches("excluded")) %>% 
	cols_label(n_total = "N",
			   valid_cdi_observed = "Collected CDI",
			   valid_cdi_imputed = "Missing CDI",
			   excluded = "") %>% 
	summary_rows(groups = TRUE, columns = where(is.integer), 
				 fns = list("N" = ~sum(.)),
				 formatter = fmt_number,
				 decimals = 0) %>% 
	grand_summary_rows(columns = where(is.integer), 
					   fns = list("N" = ~sum(.)),
					   formatter = fmt_number,
					   decimals = 0) %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners(),
			  	 cells_grand_summary(),
			  	 cells_row_groups(),
			  	 cells_stub_grand_summary(),
			  	 cells_stub_summary()))
```

### By trials

```{r} 
#| label: tbl-attrition-group
#| tbl-cap: "Summary of the dataset."
attrition %>% 
	left_join(select(participants, age_group, lp, id, date_test)) %>% 
	add_count(age_group, lp, name = "n_trials") %>% 
	group_by(id, lp, trial_type, date_test, age_group, valid_participant, n_trials) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(names_from = trial_type, values_from = valid_trial_count, values_fill = 0) %>% 
	clean_names() %>% 
	add_count(lp, age_group) %>%
	group_by(lp, age_group, n, n_trials) %>% 
	summarise(across(cognate:unrelated, lst(sum, mean, sd)),
			  n_valid = sum(valid_participant),
			  .groups = "drop") %>%
	relocate(n_valid, .after = n) %>% 
	mutate(n_prop = n_valid/n) %>% 
	arrange(age_group, lp) %>% 
	relocate(age_group, lp, n_valid, n_prop, matches("cognate"), matches("non_cognate"), matches("unrelated")) %>% 
	gt(groupname_col = "age_group", rowname_col = "lp")  %>%
	cols_hide(c(n, n_trials)) %>% 
	fmt_number(matches("_mean|_sd"), decimals = 1) %>%
	fmt_percent(matches("_prop"), decimals = 1) %>% 
	cols_merge_n_pct(col_n = n_valid, col_pct = n_prop, autohide = TRUE)  %>% 
	tab_spanner("Cognate", matches("cognate")) %>%
	tab_spanner("Non-cognate", matches("non_cognate")) %>%
	tab_spanner("Unrelated", matches("unrelated")) %>%
	cols_merge_uncert(col_val = cognate_mean, col_uncert = cognate_sd) %>% 
	cols_merge_uncert(col_val = non_cognate_mean, col_uncert = non_cognate_sd) %>% 
	cols_merge_uncert(col_val = unrelated_mean, col_uncert = unrelated_sd) %>% 
	cols_label(age_group = "Age",
			   n_valid = "Participants (included)",
			   cognate_sum = "Trials",
			   cognate_mean = "Mean ± SD",
			   non_cognate_sum = "Trials",
			   non_cognate_mean = "Mean ± SD",
			   unrelated_sum = "Trials",
			   unrelated_mean = "Mean ± SD") %>% 
	summary_rows(groups = TRUE,
				 columns = where(is.integer), 
				 fns = list("Sum" = ~sum(.)), 
				 formatter = fmt_number,
				 decimals = 0) %>% 
	summary_rows(groups = TRUE,
				 columns = c(where(is.numeric), -n_valid), 
				 fns = list("Mean" = ~mean(.)),
				 formatter = fmt_number,
				 decimals = 1) %>% 
	grand_summary_rows(columns = where(is.integer),
					   fns = list("N" = ~sum(.)),
					   formatter = fmt_number,
					   decimals = 0) %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners(),
			  	 cells_grand_summary(),
			  	 cells_row_groups(),
			  	 cells_stub_grand_summary(),
			  	 cells_stub_summary())) 
```

### By stimuli properties

```{r}
#| label: tbl-attrition-predictors

attrition %>% 
	left_join(distinct(stimuli, test_language, list, trial, trial_type,
					   freq_target, freq_prime, familiarity_prime, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status != "Valid",  "Excluded", valid_status)) %>% 
	drop_na() %>% 
	group_by(trial_type, valid_status, age_group) %>% 
	summarise(n = n(),
			  across(matches("freq_|familiarity_"),
			  	   lst(mean, sd)),
			  .groups = "drop") %>% 
	pivot_wider(names_from = valid_status,
				values_from = c(n, matches("freq_|familiarity_")),
				values_fill = 0) %>%
	clean_names() %>% 
	relocate(age_group, trial_type, n_valid, n_excluded, 
			 matches("_valid")) %>%

	gt(rowname_col = "trial_type", groupname_col = "age_group") %>% 
	fmt_number(matches("n_"), decimals = 0) %>% 
	fmt_number(matches("freq_"), decimals = 1) %>% 
	fmt_percent(matches("familiarity"), decimals = 1) %>% 
	tab_spanner("N", matches("n_")) %>% 
	tab_spanner("Prime familiarity", matches("familiarity_?prime_")) %>%
	tab_spanner("Target familiarity", matches("familiarity_?target_")) %>% 
	tab_spanner("Prime frequency", matches("freq_?prime_")) %>% 
	tab_spanner("Target frequency", matches("freq_?target_")) %>%

	cols_merge_uncert(col_val = freq_prime_mean_valid, col_uncert = freq_prime_sd_valid) %>% 
	cols_merge_uncert(col_val = freq_prime_mean_excluded, col_uncert = freq_prime_sd_excluded) %>% 
	cols_merge_uncert(col_val = freq_target_mean_valid, col_uncert = freq_target_sd_valid) %>% 
	cols_merge_uncert(col_val = freq_target_mean_excluded, col_uncert = freq_target_sd_excluded) %>%

	cols_merge_uncert(col_val = familiarity_prime_mean_valid, col_uncert = familiarity_prime_sd_valid) %>% 
	cols_merge_uncert(col_val = familiarity_prime_mean_excluded, col_uncert = familiarity_prime_sd_excluded) %>% 
	cols_merge_uncert(col_val = familiarity_target_mean_valid, col_uncert = familiarity_target_sd_valid) %>% 
	cols_merge_uncert(col_val = familiarity_target_mean_excluded, col_uncert = familiarity_target_sd_excluded) %>%

	cols_label(n_excluded = "⨯",
			   n_valid = "✓",
			   freq_prime_mean_valid = "✓",
			   freq_prime_mean_excluded = "⨯",
			   freq_target_mean_valid = "✓",
			   freq_target_mean_excluded = "⨯",
			   familiarity_prime_mean_valid = "✓",
			   familiarity_prime_mean_excluded = "⨯",
			   familiarity_target_mean_valid = "✓",
			   familiarity_target_mean_excluded = "⨯") %>% 
	summary_rows(groups = TRUE,
				 columns = matches("freq_") ,
				 fns = list("Mean" = ~mean(.)), 
				 formatter = fmt_number,
				 decimals = 0) %>% 
	summary_rows(groups = TRUE,
				 columns = matches("familiarity_"), 
				 fns = list("Mean" = ~mean(.)),
				 formatter = fmt_percent,
				 decimals = 1) %>% 
	grand_summary_rows(columns = matches("n_"),
					   fns = list("N" = ~sum(.)),
					   formatter = fmt_number,
					   decimals = 0) %>% 
	tab_style(cell_text(align = "center"),
			  cells_column_labels()) %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners(),
			  	 cells_grand_summary(),
			  	 cells_row_groups(),
			  	 cells_stub_grand_summary(),
			  	 cells_stub_summary()))

```

:::

## Descriptive statistics

### Aggregated target looking

```{r}
#| label: fig-descriptives-aggregated
df %>% 
	group_by(id, lp, trial_type, age_group) %>%
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_line(aes(group = id), alpha = 0.25) +
	stat_slab(side = "right", scale = 0.5) +
	geom_boxplot(width = 0.1, size = 0.75, fill = "white", colour = "black", outlier.colour = NA) +
	labs(x = "Trial type", y = "Proportion of target looking", colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
	theme(legend.position = "none")
```

### Time-course target looking

```{r}
#| label: fig-descriptives-time-course
df %>% 
	group_by(id, time_bin, lp, trial_type, age_group) %>%
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(time_bin, prop, colour = trial_type, fill = trial_type, shape = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
	stat_summary(fun = mean, geom = "point", size = 2) +
	stat_summary(fun = mean, geom = "line", size = 0.75) +
	labs(x = "Time bin (100 ms)", y = "Proportion of target looking",
		 colour = "Trial type", fill = "Trial type", shape = "Trial type") +
	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
	scale_x_continuous(labels = function(x) format(x*100, big.mark = ",")) +
	theme(legend.position = "top",
		  panel.grid.major = element_line(colour = "grey", linetype = "dotted"))
```

## Model outputs

### Model comparison

```{r model-comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# model_comparison <- waics_l1 %>% 
# 	map("estimates") %>% 
# 	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
# 	bind_rows(.id = "model") %>%
# 	clean_names() 
# 	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
# 	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
# 	mutate(
# 		model = c(
# 			"Intercept",
# 			"... + Trial type",
# 			"... + Group \u00d7Trial type\u00d7Group",
# 			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
# 			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
# 		)
# 	) %>% 
# 	gt() %>% 
# 	fmt_number(-model) %>% 
# 	tab_spanner("WAIC", matches("waic")) %>% 
# 	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
# 	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
# 	cols_label(
# 		model = "Model",
# 		estimate_elpd_waic = "Estimate",
# 		estimate_waic = "Estimate",
# 		estimate_p_waic = "Estimate",
# 		se_elpd_waic = md("*SE*"),
# 		se_waic = md("*SE*"),
# 		se_p_waic = md("*SE*"),
# 	) %>% 
# 	cols_align("right", "model") %>% 
# 	tab_style(
# 		cell_text(weight = "bold"),
# 		cells_column_spanners()
# 	) %>% 
# 	tab_style(
# 		cell_text(style = "italic"),
# 		cells_column_labels()
# 	)
# 
# gtsave(model_comparison, here("img", "model_comparison.png"))
# 
# 
# as_raw_html(model_comparison)

```

### Fixed effects

```{r}
#| label: fixed-effects
#| fig-height: 10
#| fig-width: 12
post_draws <- gather_draws(fit_3, `b_.*`, regex = TRUE)

post_draws %>% 
	median_hdi() %>% 
	mutate(excludes_zero = (.lower > 0) | (.upper < 0),
		excludes_zero = ifelse(excludes_zero, "Yes", "No") %>% 
			factor(levels = c("Yes", "No")),
		poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
						 str_detect(.variable, "ot2") ~ "Quadratic",
						 str_detect(.variable, "ot3") ~ "Qubic",
						 TRUE ~ "Main"),
		.variable_name = str_remove(.variable, "b_ot1:|b_ot2:|b_ot3:|b_")) %>% 
	ggplot(aes(x = .value, y = .variable_name, 
			   xmin = .lower, xmax = .upper, 
			   colour = excludes_zero)) +
	facet_wrap(~poly, scales = "free_x") +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	geom_pointinterval(size = 5, point_size = 3) +
	labs(x = "Estimate (Logit scale)", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Main effects",
		subtitle = "Mean and 95% credible interval of posterior distribution",
		colour = "Interval excludes zero?") +
	theme(legend.position = "top",
		  axis.title.y = element_blank(),
		  axis.text.y = element_text(hjust = 1),
		  panel.border = element_rect(colour = "black", fill = NA))
```

### Marginal means

```{r}
#| label: fig-posterior-epred
nd <- expand_grid(time_bin = seq(0, 20, 0.1),
				  age_group = levels(fit_1$data$age_group),
				  lp = levels(fit_2$data$lp),
				  trial_type = levels(fit_4$data$trial_type)) %>% 
	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)

m <- add_epred_draws(nd, fit_3, ndraws = 25, re_formula = NA) %>% 
	mutate(.epred = plogis(.epred))

m %>% 
	ggplot(aes(ot1, .epred, colour = trial_type)) +
	facet_grid(lp~age_group) +
	geom_line(aes(group = interaction(.draw, trial_type)), alpha = 0.15, size = 1) +
	stat_summary(fun = median, geom = "line", size = 1) +
	theme(legend.position = "top")

```

### 2022-12-15 R/00_stimuli.R

@@ -1,6 +1,6 @@
-# get familiarity ----
+# get familiarity
 get_familiarity <- function(
-		multilex_data,
+		bvq_data,
 		tokens, # words to retrieve familiarity for
 		type = "understands", # understands or produces
 		update = TRUE, # should vocabulary data be updated
@@ -8,26 +8,20 @@ get_familiarity <- function(
 		.width = 0.95 # confidence level of the estimates
 ){
 	
-	familiarity <- ml_norms(
-		multilex_data$participants,
-		multilex_data$responses, 
-		type = type,
-		age = age,
-		.width = .width
-	) %>% 
+	familiarity <- bvq_norms(bvq_data$participants,
+							 bvq_data$responses, 
+							 type = type,
+							 age = age,
+							 .width = .width) %>% 
 		filter(item_dominance=="L1") %>% 
 		group_by(item) %>% 
-		summarise(
-			yes = sum(yes, na.rm = TRUE),
-			n = sum(n, na.rm = TRUE),
-			.groups = "drop"
-		) 
+		summarise(yes = sum(yes, na.rm = TRUE),
+				  n = sum(n, na.rm = TRUE),
+				  .groups = "drop") 
 	
 	familiarity <- familiarity %>% 
-		mutate(
-			familiarity = prop_adj(yes, n),
-			familiarity_se = prop_adj_se(yes, n)
-		) %>% 
+		mutate(familiarity = prop_adj(yes, n),
+			   familiarity_se = prop_adj_se(yes, n)) %>% 
 		select(item, starts_with("familiarity")) %>% 
 		rename(word = item) %>% 
 		mutate(
@@ -43,26 +37,18 @@ get_familiarity <- function(
 }
 
 
-# get frequencies from CHILDES ----
-get_childes_corpora <- function(
-		token,
-		languages = c("cat", "spa")
-){
+# get frequencies from CHILDES
+get_childes_corpora <- function(token, languages = c("cat", "spa")) {
 	
 	if (file.exists("data/stimuli/childes.csv")){
-		
 		childes <- read_csv_arrow("data/stimuli/childes.csv")
-		
-		ui_done("Previous versions of childes loaded")
-		
+		cli::cli_alert_success("Previous versions of childes loaded")
 	} else {
 		
 		# absolute frequency (raw counts)
-		childes <- get_tokens(
-			role = "target_child", 
-			token =  token,
-			language = languages
-		) %>%
+		childes <- get_tokens(role = "target_child", 
+							  token =  token,
+							  language = languages) %>%
[…]

### 2022-12-15 R/02_vocabulary.R

@@ -1,69 +1,51 @@
 # vocabulary size
-
-# set up ----
-
-get_vocabulary <- function(
-		participants, # participants dataset (get_participants output)
-		update = FALSE, # update vocabulary data?
-		type = "understands", # vocabulary type (understands or produces)
-		multilex_data
+get_vocabulary <- function(participants, # participants dataset (get_participants output)
+						   update = FALSE, # update vocabulary data?
+						   type = "understands", # vocabulary type (understands or produces)
+						   bvq_data
 ){
 	suppressMessages({
 		
-		participants <- select(participants, participant, age_group, lp)
+		participants <- select(participants, id, age_group, lp)
 		
-		# vocabulary sizes multilex database and cognatepriming
-		to_impute <- multilex_data$vocabulary %>%
-			mutate(
-				age_group = as.factor(
-					case_when(
-						between(age, 19, 24) ~ 21,
-						between(age, 24, 28) ~ 25,
-						between(age, 28, 34) ~ 30
-					)
-				),
-				age_group = paste0(age_group, " months")
-			) %>%
+		# vocabulary sizes BVQ database and Cognate Priming
+		to_impute <- bvq_data$vocabulary %>%
+			mutate(age_group = as.factor(case_when(between(age, 19, 24) ~ 21,
+												   between(age, 24, 28) ~ 25,
+												   between(age, 28, 34) ~ 30)),
+				   age_group = paste0(age_group, " months")) %>%
 			filter(type=="understands") %>% 
-			rename(participant = id_exp) %>% 
-			right_join(select(multilex_data$logs, participant, age_group)) %>% 
+			right_join(select(bvq_data$logs, id, age_group)) %>% 
 			filter(age_group != "NA months") %>% 
-			select(
-				participant, age_group,
-				vocab_size_total = vocab_prop_total,
-				vocab_size_l1 = vocab_prop_dominance_l1,
-				vocab_size_conceptual = vocab_prop_conceptual
-			) %>% 
+			select(id, age_group,
+				   vocab_size_total = vocab_prop_total,
+				   vocab_size_l1 = vocab_prop_dominance_l1,
+				   vocab_size_conceptual = vocab_prop_conceptual) %>% 
 			full_join(select(participants, -lp)) %>% 
[…]

### 2022-12-15 R/03_gaze.R

@@ -1,98 +1,107 @@
-get_gaze_files <- function(){
+# pass eye-tracking files to Arrow
+gaze_csv_to_arrow <- function() {
 	
-	file_paths <- list.files(here("data", "gaze", "00_raw"), full.names = TRUE)
-	file_names <- list.files(here("data", "gaze", "00_raw"))
+	# set directories
+	path <- "data/gaze/00_raw"
+	new_path <- "data/gaze/01_arrow"
+	
+	# validate paths
+	stopifnot(dir.exists(path))
+	stopifnot(dir.exists(new_path))
+	
+	# get file names and paths
+	file_paths <- list.files(path, full.names = TRUE)
+	file_names <- gsub(".csv", "", list.files(path))
+	
+	# prepare progress bar
+	i <- 1
 	n_files <- length(file_paths)
+	pb_text <- "{pb_spin} Reading file {pb_current}/{pb_total} [{pb_percent}]"
+	cli_progress_bar("Processing", total = n_files, format = pb_text)
 	
-	relevant_variables <- c("participant", "trial_num", "trial", "phase", "time", "l_x", "l_y", "l_v", "r_x", "r_y", "r_v")
-	
-	col_name_changes <- c(
-		"system_time_stamp" = "time",
-		"l_1" = "l_x",
-		"l_2" = "l_y",
-		"process" = "phase",
-		"r_1" = "r_x",
-		"r_2" = "r_y",
-		"l_user_coord_3" = "l_user_coord_z",
-		"r_user_coord_3" = "r_user_coord_z",
-		"suje_num" = "participant"
-	)
-	
-	phase_name_changes <- c(
-		"GETTER" = "Getter",
-		"PRIMEIMAGE" = "Prime",
-		"TARGET_DISTRACTOR" = "Target-Distractor",
-		"prime" = "Prime",
-		"primeimage" = "Prime",
-		"target_distractor" = "Target-Distractor"
-	)
-	
-	
-	i <- 0
-	cli_progress_bar("Processing", total = n_files, format = "{pb_spin} Reading file {pb_current}/{pb_total} [{pb_percent}]")
-	
+	# read CSV and write Feather
 	for (i in 1:n_files){
-		raw_data <- read_csv_arrow(file_paths[i], na = c("", "NaN", "NA", "<NA>"))
-		
-		sampling_rate <- ifelse(nrow(raw_data) > 20e3, 120, 60)
-		
-		raw <- raw_data %>% 
-			# rename all variables to snake case
[…]

### 2022-12-15 R/model_test.R

@@ -1,136 +1,0 @@
-
-fit <- brm(
-	prop ~ 1 + time_bin_center + 
-		s(time_bin_center, bs = "cs", by = trial_type),
-	family = Beta(),
-	data = gaze,
-	# prior = c(
-	# 	prior(normal(0, 0.1), class = "Intercept"),
-	# 	prior(normal(0, 0.5), class = "b"),
-	# 	prior(normal(0, 0.5), class = "sds"),
-	# 	prior(normal(5, 0.1), class = "phi")
-	# 	# prior(exponential(7), class = "sd"),
-	# 	# prior(lkj(8), class = "cor")
-	# ),
-	iter = 500,
-	chains = 6,
-	cores = 6
-)
-
-
-post <- gather_draws(
-	fit,
-	`b_.*`,
-	`sds_.*`,
-	regex = TRUE
-) %>% 
-	mutate(
-		.chain = as.factor(.chain),
-		group = case_when(
-			str_detect(.variable, "b_") ~ "b",
-			str_detect(.variable, "sds_") ~ "sds",
-			str_detect(.variable, "sd_|cor_") ~ "sd"
-		)
-	)
-
-post %>% 
-	ggplot() +
-	aes(
-		x = .value,
-		y = .variable
-	) +
-	facet_wrap(~group, scales = "free_y", ncol  =1) + 
-	geom_vline(xintercept = 0, linetype = "dotted") +
-	stat_pointinterval() +
-	theme_custom()
-
-nd <- expand.grid(
-	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1),
-	trial_type = unique(gaze$trial_type)
-)
-
-preds <- add_epred_draws(
-	nd,
-	fit,
-	ndraws = 50,
-	re_formula = NA
-)
-
-preds %>% 
-	ggplot() +
-	aes(
-		x = time_bin_center,
-		y = .epred,
-		colour = trial_type,
-		fill = trial_type
-	) +
-	# geom_line(
-	# 	aes(group = interaction(.draw, trial_type)),
-	# 	alpha = 0.2,
-	# 	size = 0.75
-	# ) +
-	stat_summary(
-		fun = mean,
-		geom = "line",
-		size = 1
-	) +
-	stat_summary(
-		fun.data = mean_qi,
-		geom = "ribbon",
-		colour = NA,
-		alpha = 0.5
-	)
-
-
-nd_re <- expand.grid(
[…]

### 2022-12-15 tests/testthat/test-gaze.R

@@ -1,89 +1,0 @@
-test_gaze <- function(gaze){
-	
-	test_that("gaze has the right columns", {
-		expect_equal(
-			colnames(gaze),
-			c(
-				"participant",
-				"age_group",
-				"trial_type",
-				"time_bin",
-				"time_bin_center",
-				"sum_target",
-				"sum_distractor",
-				"n",
-				"prop",
-				"logit",
-				"lp",
-				"n_trials",
-				"vocab_size_total",
-				"vocab_size_l1",
-				"vocab_size_conceptual",
-				"vocab_size_total_center",
-				"vocab_size_l1_center",
-				"vocab_size_conceptual_center"
-			)
-		)
-	})
-	
-	test_that("gaze has the variable classes", {
-		expect_type(gaze$participant, "character")
-		expect_equal(class(gaze$age_group), "factor")
-		expect_equal(class(gaze$trial_type), "factor")
-		expect_type(gaze$time_bin, "integer")
-		expect_type(gaze$time_bin_center, "double")
-		expect_type(gaze$sum_target, "integer")
-		expect_type(gaze$sum_distractor, "integer")
-		expect_type(gaze$n, "integer")
-		expect_type(gaze$prop, "double")
-		expect_type(gaze$logit, "double")
-		expect_equal(class(gaze$lp), "factor")
-		expect_type(gaze$n_trials, "integer")
-		expect_type(gaze$vocab_size_total, "double")
-		expect_type(gaze$vocab_size_l1, "double")
-		expect_type(gaze$vocab_size_conceptual, "double")
-		expect_type(gaze$vocab_size_total_center, "double")
-		expect_type(gaze$vocab_size_l1_center, "double")
-		expect_type(gaze$vocab_size_conceptual_center, "double")		
-	})
-	
-	test_that("gaze missing data is dealt with", {
-		expect_false(any(is.na(gaze$participant)))
-		expect_false(any(is.na(gaze$age_group)))
-		expect_false(any(is.na(gaze$trial_type)))
-		expect_false(any(is.na(gaze$time_bin)))
-		expect_false(any(is.na(gaze$time_bin_center)))
-		expect_false(any(is.na(gaze$sum_target)))
-		expect_false(any(is.na(gaze$sum_distractor)))
-		expect_false(any(is.na(gaze$n)))
-		expect_false(any(is.na(gaze$prop)))
[…]

### 2022-12-16 index.qmd
Add participant description

@@
 
-We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+```{r}
+#| label: participants-numbers
+n_participants_total <- length(unique(participants$id))
+n_participants_sessions <- count(participants, id, name = "n_sessions") %>% 
+	count(n_sessions) %>% 
+	split(.$n_sessions)
+n_sessions_total <- count(participants)
+n_sessions_age_group <- participants %>% 
+	group_by(age_group) %>% 
+	summarise(across(age, lst(mean, sd, min, max)),
+			  n = n(),
+			  .groups = "drop") %>% 
+	mutate(across(age_mean:age_max, round, 2)) %>% 
+	split(f = .$age_group) %>% 
+	set_names(c("age_21", "age_25", "age_30"))
+n_sessions_dominance <- count(participants, test_language) %>% 
+	split(f = .$test_language) %>% 
+	set_names(c("catalan", "spanish"))
+n_sessions_dominance_age_group <- count(participants, age_group, test_language) %>% 
+	split(f = .$test_language) %>% 
+	set_names(c("catalan", "spanish")) %>% 
+	map(~split(., f = .$age_group) %>% 
+			set_names(c("age_21", "age_25", "age_30")))
+n_sessions_lp <- participants %>% 
+	count(lp) %>% 
+	split(f = .$lp) %>% 
+	set_names(c("monolingual", "bilingual"))
+n_sessions_lp_age_group <- participants %>% 
+	count(lp, age_group) %>% 
+	split(f = .$lp) %>% 
+	set_names(c("monolingual", "bilingual")) %>% 
+	map(~split(., f = .$age_group) %>% 
+			set_names(c("age_21", "age_25", "age_30")))
+```
 
-After applying trial- and participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
+We collected data from `r n_participants_total` monolingual and bilingual participants living in the Metropolitan Area of Barcelona (Spain), who were exposed to at least Catalan and/or Spanish from birth.
+Families were recruited from maternity room in private hospitals in Barcelona, and contacted via phone when the child's age spanned between our age intervals of interest.
+Families were invited to participate at three age points: 21, 25, and 30 months.
+`r n_participants_sessions[[1]]$n` participants were tested at one age point,  `r n_participants_sessions[[2]]$n` at two age points, and `r n_participants_sessions[[3]]$n` at the three age points.
+In total, we gathered data from `r n_sessions_total$n` testing sessions: `r n_sessions_age_group$age_21$n` at 21 months (*Mean* = `r round(n_sessions_age_group$age_21$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_21$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_21$age_min`--`r n_sessions_age_group$age_21$age_max`), `r n_sessions_age_group$age_25$n` at 25 months (*Mean* = `r round(n_sessions_age_group$age_25$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_25$age_min`--`r n_sessions_age_group$age_25$age_max`), and `r n_sessions_age_group$age_30$n` at 30 months (*Mean* = `r round(n_sessions_age_group$age_30$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_30$age_min`--`r n_sessions_age_group$age_30$age_max`).
 
-From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.
+We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
+Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
+The output of this interview is an estimated degree of exposure (DoE) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
+According to this estimate, we classified participants as Catalan- or Spanish-dominant if the language with highest DoE was Catalan or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
+We collected data from `r n_sessions_dominance$catalan$n` Catalan-dominant participants in Catalan (`r n_sessions_dominance_age_group$catalan$age_21$n` at 21 months, `r n_sessions_dominance_age_group$catalan$age_25$n` at 25 months, and `r n_sessions_dominance_age_group$catalan$age_30$n` at 30 months).
+We further classified participants as monolinguals if the DoE to their dominant language exceeded 80% of the total DoE to Catalan and Spanish, and as bilinguals otherwise.
+Participants with DoE to language other than Catalan or Spanish were excluded from analyses.
+This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
+tbl-participants-lp summarises the linguistic profile of our sample.
 
 ```{r}
-#| label: tbl-participants-summary
-#| tbl-cap: "Testing sessions"
+#| label: tbl-participants-lp
+#| tbl-cap: "Description of language profile of participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
 participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>% 
-	drop_na(valid_participant) %>% 
-	count(age_group, lp, test_language) %>% 
-	pivot_wider(names_from = age_group,
-				values_from = n, 
-				values_fill = 0) %>% 
+	select(id, age_group, age, lp, doe_catalan, doe_spanish, test_language) %>% 
+	mutate(id = paste0(id, " (", age_group, ")")) %>%
+	add_count(lp, name = "n_lp") %>% 
+		add_count(age_group, name = "n_age_group") %>%
+
+	pivot_longer(starts_with("doe_"), names_to = "language", values_to = "doe") %>%
+	add_count(age_group, test_language, name = "n_age_test") %>% 
+	mutate(language = str_remove_all(language, "doe_") %>% 
+		   	str_to_sentence(),
+		   age_group = paste0(age_group, " (N = ", n_age_group, ")"),
+		   test_language = paste0("Tested in ", test_language, " (N = ", n_age_test, ")"),
+		   lp = factor(lp, levels = rev(unique(lp))))  %>% 
+	group_by(age_group, lp, test_language, language) %>% 
+	summarise(across(doe, lst(mean, sd)),
+			  .groups = "drop") %>% 
+	pivot_wider(id_cols = c(age_group, test_language),
+				names_from = c(language, lp),
+				values_from = c(matches("doe"))) %>% 
 	clean_names() %>% 
-	gt(rowname_col = "test_language", groupname_col = "lp") %>% 
-	cols_label(x21_months = "21 months",
-			   x25_months = "25 months",
-			   x30_months = "30 months") %>% 
-	summary_rows(group = TRUE,
-				 columns = where(is.numeric),
-				 fns = list("n" = ~sum(.)),
-				 formatter = fmt_number,
-				 decimals = 0) %>% 
-	grand_summary_rows(columns = where(is.numeric),
-					   fns = list("N" = ~sum(.)),
-					   formatter = fmt_number,
-					   decimals = 0) %>% 
-	tab_style(style = cell_fill("grey82"),
-			  locations = list(cells_row_groups())) %>% 
-	tab_style(cell_text(weight = "bold"), cells_column_labels())
+	relocate(age_group, test_language,
+			 matches("catalan"),
+			 matches("spanish")) %>% 
+	gt(rowname_col = "test_language", 
+	   groupname_col = "age_group", row_group.sep = ": ") %>% 
+	tab_spanner(md("Monolingual (*N* = 162)"), matches("monolingual")) %>% 
+	tab_spanner(md("Bilingual (*N* = 133)"), matches("bilingual")) %>%
+	fmt_number(matches("doe"), decimals = 1, scale_by = 100) %>% 
+	cols_merge_uncert(col_val = doe_mean_catalan_monolingual,
+					  col_uncert = doe_sd_catalan_monolingual) %>% 
+	cols_merge_uncert(col_val = doe_mean_catalan_bilingual,
+					  col_uncert = doe_sd_catalan_bilingual) %>% 
+	cols_merge_uncert(col_val = doe_mean_spanish_monolingual, 
+					  col_uncert = doe_sd_spanish_monolingual) %>% 
+	cols_merge_uncert(col_val = doe_mean_spanish_bilingual, 
+					  col_uncert = doe_sd_spanish_bilingual) %>%
+
+	cols_label(doe_mean_catalan_monolingual = "Catalan (%)",
+			   doe_mean_catalan_bilingual = "Catalan (%)",
+			   doe_mean_spanish_monolingual = "Spanish (%)",
+			   doe_mean_spanish_bilingual = "Spanish (%)") %>% 
+	tab_style(cell_text(weight = "bold"),
+			  list(cells_column_spanners())) %>% 
+	tab_style(cell_text(size = "small"),
+			  list(cells_body(),
+			  	 cells_stub()))
 ```
 
-```{r}
-#|  label: fig-participants-summary
-participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>% 
-	filter(valid_participant) %>% 
-	drop_na(valid_participant) %>% 
-	ggplot(aes(lp, fill = test_language)) +
-	facet_grid(~age_group, scales = "free") +
-	geom_bar(colour = NA) +
-	labs(x = "Group", y = "Sample size", fill = "Test language") +
-	theme(legend.position = "top",
-		  axis.title.x = element_blank(),
-		  axis.text = element_text(size = 10),
-		  axis.title.y = element_text(angle = 90),
-		  panel.grid.major.x = element_blank()) 
-```
-
-### Longitudinal participants
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r}
-#| label: fig-participants-longitudinal
-#| fig-height: 10
-#| fig-width: 4
-participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	filter(valid_participant) %>% 
-	add_count(id, lp, name = "n_total") %>% 
-	count(id, age_group, test_language, lp, n_total) %>% 
-	pivot_wider(id_cols = c(id, lp, test_language, n_total),
-				names_from = age_group,
-				values_from = n,
-				values_fill = 0) %>% 
-	pivot_longer(5:7,
-				 names_to = "age_group",
-				 values_to = "n") %>% 
-	mutate(id_reordered = reorder_within(id, by = n_total, within = list(test_language, lp))) %>% 
-	ggplot(aes(age_group, id_reordered, fill = as.factor(n))) + 
-	facet_wrap(test_language~lp, scales = "free_y") +
-	geom_tile(colour = "white") +
-	labs(x = "Age (months)", 
-		 y = "Exposure to 2nd language", 
-		 fill = "Lang. Profile") +
-	scale_fill_manual(values = c("white", clrs[4], "white")) +
-	theme(legend.position = "none",
-		  legend.title = element_blank(),
-		  panel.grid = element_blank(),
-		  axis.text = element_text(size = 10),
-		  axis.title.y = element_blank(),
-		  axis.text.y = element_blank(),
-		  axis.ticks.y = element_blank())
-
-```
-
-### Sample description
-
-```{r}
-#| label: fig-participants-lp
-#| fig-height: 7
-participants %>% 
-	select(id, age_group, age, lp, starts_with("doe_"), test_language) %>% 
-	mutate(id = paste0(id, " (", age_group, ")"),) %>% 
-	pivot_longer(starts_with("doe_"), names_to = "language", values_to = "doe") %>%
-	mutate(language = str_remove_all(language, "doe_") %>% 
-		   	str_to_sentence(),
-		   test_language = paste0("Tested in ", test_language)) %>% 
-	group_by(age_group, lp, test_language, language) %>% 
-	summarise(n = n(), 
-			  across(c(age, doe), lst(mean, sd, min, max)),
-			  .groups = "drop") %>% 
-	pivot_wider(names_from = c(language),
-				values_from = matches("doe")) %>% 
-	clean_names() %>% 
-	relocate(age_group, lp, test_language, n,
-			 matches("age"), matches("catalan"),
-			 matches("spanish"), matches("other")) %>% 
-	gt(rowname_col = "test_language", groupname_col = c("age_group", "lp")) %>% 
-	tab_spanner("Age (months)", c(matches("age"), -age_group)) %>% 
-	tab_spanner("Catalan DoE", matches("catalan")) %>% 
-	tab_spanner("Spanish DoE", matches("spanish")) %>% 
-	tab_spanner("Others DoE", matches("others")) %>% 
-	fmt_number(c(starts_with("age"), -age_group)) %>% 
-	fmt_percent(matches("doe"), decimals = 1) %>% 
-	cols_merge_uncert(col_val = age_mean, col_uncert = age_sd) %>% 
-	cols_merge_uncert(col_val = doe_mean_catalan, col_uncert = doe_sd_catalan) %>% 
-	cols_merge_uncert(col_val = doe_mean_spanish, col_uncert = doe_sd_spanish) %>% 
-	cols_merge_uncert(col_val = doe_mean_others, col_uncert = doe_sd_others) %>% 
-	cols_merge_range(col_begin = age_min, col_end = age_max) %>% 
-	cols_merge_range(col_begin = doe_min_catalan, col_end = doe_max_catalan) %>% 
-	cols_merge_range(col_begin = doe_min_spanish, col_end = doe_max_spanish) %>% 
-	cols_merge_range(col_begin = doe_min_others, col_end = doe_max_others) %>% 
-	cols_label(n = "N",
-			   age_mean = "Mean",
-			   age_min = "Range",
-			   doe_mean_catalan = "Mean ± SD",
-			   doe_min_catalan = "Range",
-			   doe_mean_spanish = "Mean ± SD",
-			   doe_min_spanish = "Range",
-			   doe_mean_others = "Mean ± SD",
-			   doe_min_others = "Range") %>% 
-	summary_rows(group = TRUE,
-				 columns = c(where(is.numeric), -n),
-				 fns = list("Mean" = ~mean(.)),
-				 formatter = fmt_number,
-				 decimals = 1) %>% 
-	summary_rows(group = TRUE,
-				 columns = c(where(is.numeric), -n, -matches("age")),
-				 fns = list("Mean" = ~mean(.)),
-				 formatter = fmt_percent,
-				 decimals = 1) %>% 
-	grand_summary_rows(columns = c(where(is.numeric), -n),
-					   fns = list("Grand mean" = ~mean(.)),
-					   formatter = fmt_number,
-					   decimals = 1) %>% 
-	grand_summary_rows(columns = c(where(is.numeric), -n, -matches("age")),
-					   fns = list("Grand mean" = ~mean(.)),
-					   formatter = fmt_percent,
-					   decimals = 1) %>% 
-	tab_style(style = cell_fill("grey82"),
-			  locations = list(cells_row_groups())) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary()))
-```
+The research reported in this article was conducted in accordance with the principles expressed in the Declaration of Helsinki and approved by the local ethical committee (the clinical research ethical committee of the Parc de la Salut Mar).
+Before every testing session, caretakers were asked to read and sign an informed consent form, and were given a small gift at the end of it.
 
 ## Stimuli
-
-### Lexical frequency
-
-::: {.tabset-panel}
-
-#### Prime
-
-```{r}
-#| label: fig-stimuli-frequency-prime
-#| fig-height: 5
-stimuli %>% 
-	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot() +
-	aes(x = trial_type, 
-		y = freq_prime, 
-		colour = trial_type, 
-		fill = trial_type) +
-	facet_wrap(~test_language) +
-	stat_slab(fill = "grey", colour = "white", scale = 0.5, adjust = 2,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, 
-				 outlier.colour = NA, width = 0.1,
-				 position = position_nudge(x = 0.3)) + 
-	geom_point(shape = 1, stroke = 1.25, size = 3,
-			   position = position_jitter(width = 0.15, seed = 888)) +
-	labs(x = "Trial type", 
-		 y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type", 
-		 fill = "Trial type") +
-	theme(legend.position = "none",
-		  axis.title.x = element_blank(),
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-```
-
-#### Target
-
-```{r}
-#| label: fig-stimuli-frequency-target,
-#| fig-height: 5
-stimuli %>% 
-	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
-	ggplot() +
-	aes(x = trial_type, y = freq_target, 
-		colour = trial_type, fill = trial_type) + 
-	facet_wrap(~test_language) +
-	stat_slab(fill = "grey", colour = "white", scale = 0.5, adjust = 2,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(colour = "black", fill = "white", size = 0.75, 
-				 outlier.colour = NA, width = 0.1,
-				 position = position_nudge(x = 0.3)) + 
-	geom_point(shape = 1, stroke = 1.25, size = 3,
-			   position = position_jitter(width = 0.15, seed = 888)) +
-	labs(x = "Trial type",
-		 y = "Lexical frequency (Zipf score)",
-		 colour = "Trial type",
-		 fill = "Trial type") +
-	theme(legend.position = "none",
-		  axis.title.x = element_blank(),
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-```
-
-:::
-
-### Familiarity
-
-::: {.tabset-panel}
-
-#### Prime
-
-```{r}
-#| label: fig-stimuli-familiarity-prime
-#| fig-height: 7
-means <- stimuli %>% 
-	distinct(test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, trial_type) %>% 
-	summarise(familiarity_prime = mean(familiarity_prime, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	drop_na()
-
-stimuli %>% 
-	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
-	mutate(prime = reorder_within(prime, familiarity_prime, list(test_language))) %>% 
-	ggplot() +
-	aes(familiarity_prime, 
-		reorder(prime, familiarity_prime),
-		colour = trial_type, 
-		fill = trial_type,
-		xmin = familiarity_prime-familiarity_se_prime,
-		xmax = familiarity_prime+familiarity_se_prime) +
-	facet_wrap(~test_language, scales = "free_y") +
-	# geom_vline(data = means, 
-	# 		   aes(xintercept = familiarity_prime, 
-	# 		   	colour = trial_type),
-	# 		   size = 1) +
-	geom_errorbar(width = 0.5) +
-	geom_point() +
-	labs(x = "% of infants that understand",
-		 y = "Prime word",
-		 colour = "Trial type", 
-		 fill = "Trial type") +
-	scale_y_reordered() +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	theme(legend.position = "top",
-		  legend.title = element_blank(),
-		  axis.text.y = element_text(size = 7, hjust = 1),
-		  axis.title.y = element_blank(),
-		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-		  plot.caption = element_text(size = 10, hjust = 0))
-```
-
-#### Target
-
-```{r}
-#| label: stimuli-familiarity-target
-#| fig-height: 6.5
-means <- stimuli %>% 
-	distinct(test_language, target, trial_type, prime, .keep_all = TRUE) %>% 
-	group_by(test_language, trial_type) %>% 
-	summarise(familiarity_target = mean(familiarity_target, na.rm = TRUE),
-			  .groups = "drop")
-
-stimuli %>% 
-	distinct(test_language, target, prime, .keep_all = TRUE) %>% 
-	mutate(target = reorder_within(target, familiarity_target, list(test_language))) %>% 
-	ggplot(aes(x = familiarity_target, 
-			   y = target, 
-			   colour = trial_type,
-			   fill = trial_type,
-			   xmin = familiarity_target-familiarity_se_target,
-			   xmax = familiarity_target+familiarity_se_target)) +
-	facet_wrap(~test_language,  scales = "free_y") +
-	# geom_vline(data = means,
-	# 		   aes(xintercept = familiarity_target,
-	# 		   	colour = trial_type), 
-	# 		   size = 1) +
-	geom_errorbar(width = 0.5) +
-	geom_point(shape = 1, size = 0.5, stroke = 1) +
-	labs(x = "% of infants that understand",
-		 y = "Target word",
-		 colour = "Trial type",
-		 fill = "Trial type") +
-	scale_x_continuous(labels = percent, limits = c(0, 1)) +
-	scale_y_reordered() +
-	theme(legend.position = "top",
-		  legend.title = element_blank(),
-		  axis.text.y = element_text(size = 7, hjust = 1),
-		  axis.title.y = element_blank(),
-		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-		  plot.caption = element_text(size = 10, hjust = 0))
-```
-
-:::
 
@@
 
+```{r} 
+#| label: tbl-attrition-group
+#| tbl-cap: "Summary of the dataset."
+attrition %>% 
+	left_join(select(participants, age_group, lp, id, date_test)) %>% 
+	add_count(age_group, lp, name = "n_trials") %>% 
+	group_by(id, lp, trial_type, date_test, age_group, valid_participant, n_trials) %>% 
+	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
+			  .groups = "drop") %>% 
+	pivot_wider(names_from = trial_type, values_from = valid_trial_count, values_fill = 0) %>% 
+	clean_names() %>% 
+	add_count(lp, age_group) %>%
+	group_by(lp, age_group, n, n_trials) %>% 
+	summarise(across(cognate:unrelated, lst(sum, mean, sd)),
+			  n_valid = sum(valid_participant),
+			  .groups = "drop") %>%
+	relocate(n_valid, .after = n) %>% 
+	mutate(n_prop = n_valid/n) %>% 
+	arrange(age_group, lp) %>% 
+	relocate(age_group, lp, n_valid, n_prop, matches("cognate"), matches("non_cognate"), matches("unrelated")) %>% 
+	gt(groupname_col = "age_group", rowname_col = "lp")  %>%
+	cols_hide(c(n, n_trials)) %>% 
+	fmt_number(matches("_mean|_sd"), decimals = 1) %>%
+	fmt_percent(matches("_prop"), decimals = 1) %>% 
+	cols_merge_n_pct(col_n = n_valid, col_pct = n_prop, autohide = TRUE)  %>% 
+	tab_spanner("Non-cognate", matches("non_cognate")) %>%
+	tab_spanner("Cognate", starts_with("cognate")) %>%
+	tab_spanner("Unrelated", matches("unrelated")) %>%
+	tab_spanner("Related", matches("cognate")) %>%
+
+	cols_merge_uncert(col_val = cognate_mean, col_uncert = cognate_sd) %>% 
+	cols_merge_uncert(col_val = non_cognate_mean, col_uncert = non_cognate_sd) %>% 
+	cols_merge_uncert(col_val = unrelated_mean, col_uncert = unrelated_sd) %>% 
+	cols_label(age_group = "Age",
+			   n_valid = "Participants (included)",
+			   cognate_sum = "Trials",
+			   cognate_mean = "Mean ± SD",
+			   non_cognate_sum = "Trials",
+			   non_cognate_mean = "Mean ± SD",
+			   unrelated_sum = "Trials",
+			   unrelated_mean = "Mean ± SD") %>% 
+	summary_rows(groups = TRUE,
+				 columns = where(is.integer), 
+				 fns = list("Sum" = ~sum(.)), 
+				 formatter = fmt_number,
+				 decimals = 0) %>% 
+	summary_rows(groups = TRUE,
+				 columns = c(where(is.numeric), -n_valid), 
+				 fns = list("Mean" = ~mean(.)),
+				 formatter = fmt_number,
+				 decimals = 1) %>% 
+	grand_summary_rows(columns = where(is.integer),
+					   fns = list("N" = ~sum(.)),
+					   formatter = fmt_number,
+					   decimals = 0) %>% 
+	tab_style(cell_text(weight = "bold"),
+			  list(cells_column_spanners(),
+			  	 cells_grand_summary(),
+			  	 cells_row_groups(),
+			  	 cells_stub_grand_summary(),
+			  	 cells_stub_summary())) 
+```
+
 **Parameters**:
@@
 ```{r}
-#| label: fig-attrition-vocab
+#| label: fig-attrition-participants
 #| fig-height: 4
@@
 				 decimals = 0) %>% 
-	grand_summary_rows(columns = where(is.integer), 
-					   fns = list("N" = ~sum(.)),
-					   formatter = fmt_number,
-					   decimals = 0) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary()))
-```
-
-### By trials
-
-```{r} 
-#| label: tbl-attrition-group
-#| tbl-cap: "Summary of the dataset."
-attrition %>% 
-	left_join(select(participants, age_group, lp, id, date_test)) %>% 
-	add_count(age_group, lp, name = "n_trials") %>% 
-	group_by(id, lp, trial_type, date_test, age_group, valid_participant, n_trials) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(names_from = trial_type, values_from = valid_trial_count, values_fill = 0) %>% 
-	clean_names() %>% 
-	add_count(lp, age_group) %>%
-	group_by(lp, age_group, n, n_trials) %>% 
-	summarise(across(cognate:unrelated, lst(sum, mean, sd)),
-			  n_valid = sum(valid_participant),
-			  .groups = "drop") %>%
-	relocate(n_valid, .after = n) %>% 
-	mutate(n_prop = n_valid/n) %>% 
-	arrange(age_group, lp) %>% 
-	relocate(age_group, lp, n_valid, n_prop, matches("cognate"), matches("non_cognate"), matches("unrelated")) %>% 
-	gt(groupname_col = "age_group", rowname_col = "lp")  %>%
-	cols_hide(c(n, n_trials)) %>% 
-	fmt_number(matches("_mean|_sd"), decimals = 1) %>%
-	fmt_percent(matches("_prop"), decimals = 1) %>% 
-	cols_merge_n_pct(col_n = n_valid, col_pct = n_prop, autohide = TRUE)  %>% 
-	tab_spanner("Cognate", matches("cognate")) %>%
-	tab_spanner("Non-cognate", matches("non_cognate")) %>%
-	tab_spanner("Unrelated", matches("unrelated")) %>%
-	cols_merge_uncert(col_val = cognate_mean, col_uncert = cognate_sd) %>% 
-	cols_merge_uncert(col_val = non_cognate_mean, col_uncert = non_cognate_sd) %>% 
-	cols_merge_uncert(col_val = unrelated_mean, col_uncert = unrelated_sd) %>% 
-	cols_label(age_group = "Age",
-			   n_valid = "Participants (included)",
-			   cognate_sum = "Trials",
-			   cognate_mean = "Mean ± SD",
-			   non_cognate_sum = "Trials",
-			   non_cognate_mean = "Mean ± SD",
-			   unrelated_sum = "Trials",
-			   unrelated_mean = "Mean ± SD") %>% 
-	summary_rows(groups = TRUE,
-				 columns = where(is.integer), 
-				 fns = list("Sum" = ~sum(.)), 
-				 formatter = fmt_number,
-				 decimals = 0) %>% 
-	summary_rows(groups = TRUE,
-				 columns = c(where(is.numeric), -n_valid), 
-				 fns = list("Mean" = ~mean(.)),
-				 formatter = fmt_number,
-				 decimals = 1) %>% 
 	grand_summary_rows(columns = where(is.integer), 
@@
 	theme(legend.position = "top")
+```
+
+# Appendix
+
+## Longitudinal participants
+
+We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
+Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
+
+```{r}
+#| label: fig-participants-longitudinal
+#| fig-height: 10
+#| fig-width: 4
+participants %>% 
+	left_join(distinct(attrition, id, valid_participant)) %>%
+	filter(valid_participant) %>% 
+	add_count(id, lp, name = "n_total") %>% 
+	count(id, age_group, test_language, lp, n_total) %>% 
+	pivot_wider(id_cols = c(id, lp, test_language, n_total),
+				names_from = age_group,
+				values_from = n,
+				values_fill = 0) %>% 
+	pivot_longer(5:7,
+				 names_to = "age_group",
+				 values_to = "n") %>% 
+	mutate(id_reordered = reorder_within(id, by = n_total, within = list(test_language, lp))) %>% 
+	ggplot(aes(age_group, id_reordered, fill = as.factor(n))) + 
+	facet_wrap(test_language~lp, 
+			   scales = "free_y",
+			   labeller = label_wrap_gen(multi_line = FALSE)) +
+	geom_tile(colour = "white") +
+	labs(x = "Age (months)", 
+		 y = "Exposure to 2nd language", 
+		 fill = "Lang. Profile") +
+	scale_fill_manual(values = c("white", clrs[4], "white")) +
+	theme(legend.position = "none",
+		  legend.title = element_blank(),
+		  panel.grid = element_blank(),
+		  axis.text.x = element_text(size = 6),
+		  axis.title.y = element_blank(),
+		  axis.title.x = element_text(size = 6),
+		  axis.text.y = element_blank(),
+		  axis.ticks.y = element_blank(),
+		  strip.text = element_text(size = 6))
 

### 2022-12-21 docs/index.qmd
Render Quarto report in targets workflow

--- 2022-12-16 index.qmd
@@
         reference-location: margin
-        execute-dir: "C:/Users/U155880/Documents/trajectories/"
     pdf: default
@@
 #| label: setup
-tar_load_globals()
-tar_load_everything()
+#| include: false
+
+tar_load_everything() # load target objects
+
+# load packages
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(tibble)
+library(purrr)
+library(lubridate)
+library(ggplot2)
+library(gt)
+library(tidybayes)
+library(brms)
+library(polypoly)
+library(tidytext)
+library(janitor)
+library(forcats)
+library(scales)
+library(patchwork)
+library(bvqdev)
 
@@
 
-options(
-	ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
+options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
 	ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
@@
 	ggplot2.continuous.fill = ggplot2::scale_color_gradient,
-	ggplot2.continuous.colour = ggplot2::scale_color_gradient
-)
+	ggplot2.continuous.colour = ggplot2::scale_color_gradient)
 
@@
 			  list(cells_column_spanners())) %>% 
-	tab_style(cell_text(size = "small"),
+	tab_style(cell_text(size = "medium"),
 			  list(cells_body(),
@@
 
-```{r}
-#| label: fig-stimuli-category 
+::: {.panel-tabset}
+
+#### Prime
+
+```{r}
+#| label: fig-stimuli-category-prime
 #| fig-height: 7
@@
 	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(semantic_category_prime, semantic_category_target),
-				 names_to = "role",
-				 values_to = "semantic_category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "semantic_category_"))) %>% 
-	drop_na(trial_type, semantic_category) %>% 
-	count(trial_type, test_language, role, semantic_category, name = "sum") %>% 
-	right_join(expand(., trial_type,  test_language,  role,  semantic_category)) %>%
+	drop_na(trial_type, semantic_category_prime) %>% 
+	count(trial_type, test_language, semantic_category_prime, name = "sum") %>% 
+	right_join(expand(., trial_type,  test_language,  semantic_category_prime)) %>%
 	replace_na(list(sum = 0)) %>% 
-	group_by(trial_type, test_language, role) %>% 
+	group_by(trial_type, test_language) %>% 
 	mutate(n =  sum(sum), prop = sum/n) %>% 
@@
 	aes(x = prop,
-		y = reorder_within(semantic_category, 
-						   desc(prop), 
-						   list(trial_type, role, test_language)),
+		y = reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
 		fill = test_language,
 		order = prop) + 
-	facet_wrap(trial_type~role~test_language,
+	facet_wrap(test_language~trial_type,
 			   scales = "free_y",
@@
 
+#### Target
+
+```{r}
+#| label: fig-stimuli-category-target
+#| fig-height: 7
+#| fig-width: 12
+stimuli %>% 
+	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
+	drop_na(trial_type, semantic_category_target) %>% 
+	count(trial_type, test_language, semantic_category_target, name = "sum") %>% 
+	right_join(expand(., trial_type,  test_language,  semantic_category_target)) %>%
+	replace_na(list(sum = 0)) %>% 
+	group_by(trial_type, test_language) %>% 
+	mutate(n =  sum(sum), prop = sum/n) %>% 
+	ungroup() %>% 
+	ggplot() +
+	aes(x = prop,
+		y = reorder_within(semantic_category_target, desc(prop), list(trial_type, test_language)),
+		fill = test_language,
+		order = prop) + 
+	facet_wrap(test_language~trial_type,
+			   scales = "free_y",
+			   labeller = label_wrap_gen(multi_line = FALSE)) +
+	geom_col(colour = "white",
+			 position = position_dodge(),
+			 width = 1) +
+	labs(x = "% of trials",
+		 y = "Trial type",
+		 colour = "Trial type",
+		 fill = "Trial type") +
+	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
+	scale_y_reordered() +
+	theme(legend.position = "none",
+		  legend.title = element_blank(),
+		  axis.text.y = element_text(size = 9, hjust = 1),
+		  axis.text.x = element_text(size = 8, hjust = 1),
+		  axis.title.y = element_blank(),
+		  axis.ticks.y = element_blank(),
+		  plot.caption = element_text(size = 10, hjust = 0),
+		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
+		  strip.text = element_text(size = 10))
+```
+
+:::
+
 ## Vocabulary
@@
 We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
+In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI, @hamilton2000infant] two weeks before each appointment.
 In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvqdev) immediately after the appointment, and were given two weeks to fill it.
@@
 
+### Data processing
+
 ```{r} 
@@
 
-**Parameters**:
+### Predictors
+
+### Model
 
 $$
-\begin{align}
-y_{ij} =&~ (\beta_{0} + \beta_{0p} + \beta_{0i}) ~+~ ... \\ 
-& (\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} ~+~ ... \\
-& (\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} ~ + ~ ... \\
-& (\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} ~ + ~ ... \\
-& (\beta_{4} + \beta_{4i}) \times Group_{pi} ~+~ ... \\
-& (\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) ~+~ ... \\
-& (\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) ~+~ ... \\
-& (\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) ~+~ ... \\
-& (\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) ~+~ \\ & \sigma^2_{e}
-\end{align}
+\begin{aligned}
+\textbf{Likelihood:} \\
+y_{ij} &\sim \text{Bernoulli}(p)
+\end{aligned}
+$$ {#eq-likelihood}
+
+where:
+
+- $y$ is an observed response ($y \in \{\text{No, Understands, Understands and Says}\}$)
+- $i$ is the participant index
+- $j$ is the translation equivalent (TE) index
+- $p$ is the probability f target looking ($p \in (0, 1)$)
+
+$p$ is then estimated using a logit regression model as indicated in @eq-linear.
+
 $$
-
-**Priors**:
+\begin{aligned}
+\textbf{Linear model:} \\
+logit(p) = \text{ln} \frac{p}{1-p} &= (\beta_{0} + u_{0_{i}}) + \\
+& (\beta_{1} + u_{1_{i}}) · \text{Age group}_{i} + & \\
+& \beta_{2} · \text{Language Profile}_{i} + & \\
+& (\beta_{3} + u_{2_{i}}) · \text{Trial type}_{i} + & \\
+& \beta_{4} · (\text{Age group}_{i} \times \text{Language Profile}_{i}) & \\
+& (\beta_{5} + u_{3_{i}}) · (\text{Age group}_{i} \times \text{Trial type}_{i}) + & \\
+& \beta_{6} · (\text{Language Profile}_{ij} \times \text{Trial type}_{i}) & \\
+& \beta_{7} · (\text{Age group}_{i} \times \text{Language Profile}_{i} \times \text{Trial type}_{i}) & \\
+\end{aligned}
+$$ {#eq-linear}
+
+where:
+
+- $i$ and $j$ index the participant and translation equivalent (TE)
+- $\beta_{0_k}$ is the fixed coefficient of the regression model for the intercept of threshold $k$
+- $u_{0_{i}}$ and $w_{0_{j}}$ are the by-participant and by-TE adjustments for $\beta_{0_{k}}$ (i.e., random intercepts), respectively
+- $\beta_{1-8}$ are the fixed coefficients of the regression model for the predictors of interest
+- $u_{1-8_{i}}$ and $w_{1-3_{j}}$ are the by-participant and by-TE adjustments for$\beta_{1-8}$ (i.e., random slopes), respectively
 
 $$
-\begin{align}
-\beta_0 \sim~ & \mathcal{N}(0, 1) \\
-\beta_{1-8} \sim~ &\mathcal{N}(0, 1) \\
-\sigma_m, ~\sigma^2,~ \sigma^2_p,~ \sigma^2_i \sim~ & exp(2) \\
-\rho \sim ~&  LKJ(2)
-\end{align}
-$$
-
-### Prior expected predicted mean
+\begin{aligned}
+\\
+\textbf{Prior:} \\
+\beta_{0_{k}} &\sim \mathcal{N}(-0.25, 0.1) & [\mbox{Intercept/response category threshold}] \\
+\beta_{1} &\sim \mathcal{N}(1, 0.1) & [\mbox{Age population-level coefficient}]\\
+\beta_{2-8} &\sim \mathcal{N}(0, 1) & [\mbox{Rest of population-level coefficients}] \\
+u_{0-8_{i}} &\sim \mathcal{N}(0, \sigma_{u_{0-8_{i}}}) & [\mbox{Participant-level coefficient variability}] \\
+w_{0-3_{j}} &\sim \mathcal{N}(0, \sigma_{w_{0-3_{j}}}) & [\mbox{TE-level coefficient variability}] \\\\
+&&\mbox{[Participant-level coefficient variability]} \\ \\
+\Bigg(\begin{smallmatrix}
+u_{k_{0}} \\ 
+u_{1_{i}} \\ 
+\vdots \\ 
+u_{8_{i}} 
+\end{smallmatrix}\Bigg) &\sim \mathcal{N} 
+\Bigg(\Bigg(\begin{smallmatrix}0 \\
+0 \\ 
+\vdots \\
+0\end{smallmatrix}\Bigg), \Sigma_{u}\Bigg) \\
+\Sigma_{u} &= \Bigg(\begin{smallmatrix} \\
+\rho_{u_{0}} & \rho_{u_{0}} \sigma_{u_{0_{k}}} \sigma_{u_{1}} & \dots & \rho_{u_{0}} \sigma_{u_{0}} \sigma_{w_{8}}\\ 
+\rho_{u_{1}} \sigma_{u_{1}} \sigma_{u_{0}} & \rho_{u_{1}} & \dots & \rho_{u_{1}} \sigma_{u_{1}} \sigma_{u_{8}}\\ 
+\vdots & \vdots & \vdots & \vdots \\
+\rho_{8} \sigma_{u_{8}} \sigma_{u_{0_{k}}} & \dots & \dots & \rho_{u_{8}} \end{smallmatrix}\Bigg) \\
+\sigma_{u_{0-8}} &\sim \mathcal{N_{+}}(1, 0.1) \\
+\rho_{u} &\sim LKJcorr(2) \\
+\\
+&&\mbox{[TE-level coefficient variability]} \\ \\
+\Bigg(\begin{smallmatrix}
+w_{k_{0}}\\ 
+w_{1_{j}} \\ 
+\vdots \\ 
+w_{3_{j}} 
+\end{smallmatrix}\Bigg) &\sim \mathcal{N} \Bigg(\Bigg(\begin{smallmatrix}
+0\\ 
+0 \\ 
+\vdots \\
+0 
+\end{smallmatrix}\Bigg), \Sigma_{w}\Bigg) \\
+\Sigma_{w} &= \Bigg(\begin{smallmatrix} \\
+\rho_{w_{0}} & \rho_{w_{0}} \sigma_{w_{0_{k}}} \sigma_{w_{1}} & \dots & \rho_{w_{0}} \sigma_{w_{0}} \sigma_{w_{3}}\\ 
+\rho_{w_{1}} \sigma_{w_{1}} \sigma_{w_{0}} & \rho_{w_{1}} & \dots & \rho_{w_{1}} \sigma_{w_{1}} \sigma_{w_{3}}\\ 
+\vdots & \vdots & \vdots & \vdots \\
+\rho_{3} \sigma_{w_{3}} \sigma_{w_{0_{k}}} & \dots & \dots & \rho_{w_{3}} \end{smallmatrix}\Bigg) \\
+\sigma_{w_{0-3}} &\sim \mathcal{N_{+}}(1, 0.1) \\
+\rho_{w_{0-3}} &\sim LKJcorr(2)
+\end{aligned}
+$$ {#eq-prior}
 
@@
 attrition %>% 
-	left_join(distinct(stimuli, test_language, list, trial, trial_type,
+	left_join(distinct(participants, id, age_group, test_language, list, version, list)) %>% 
+	left_join(distinct(stimuli, test_language, version, list, trial_id, trial_type,
 					   freq_target, freq_prime, familiarity_prime, familiarity_target)) %>% 
@@
 	summarise(n = n(),
-			  across(matches("freq_|familiarity_"),
-			  	   lst(mean, sd)),
+			  across(matches("freq_|familiarity_"), lst(mean, sd)),
 			  .groups = "drop") %>% 
@@
 	fmt_number(matches("freq_"), decimals = 1) %>% 
-	fmt_percent(matches("familiarity"), decimals = 1) %>% 
-	tab_spanner("N", matches("n_")) %>% 
-	tab_spanner("Prime familiarity", matches("familiarity_?prime_")) %>%
-	tab_spanner("Target familiarity", matches("familiarity_?target_")) %>% 
-	tab_spanner("Prime frequency", matches("freq_?prime_")) %>% 
-	tab_spanner("Target frequency", matches("freq_?target_")) %>%
+	fmt_number(matches("familiarity"), scale_by = 100, decimals = 1) %>%
+
+	tab_spanner("N", c(n_valid, n_excluded)) %>%
+
+	tab_spanner("Prime", id = 1, c(freq_prime_mean_valid, freq_prime_mean_excluded)) %>%
+	tab_spanner("Target", id = 2, c(freq_target_mean_valid, freq_target_mean_excluded)) %>% 
+	tab_spanner("Prime", id = 3, c(familiarity_prime_mean_valid, familiarity_prime_mean_excluded)) %>% 
+	tab_spanner("Target", id = 4, c(familiarity_target_mean_valid, familiarity_target_mean_excluded)) %>%
+	tab_spanner("Frequency", starts_with("freq_")) %>% 
+	tab_spanner("Familiarity (%)", starts_with("familiarity_")) %>%
 
@@
 	cols_merge_uncert(col_val = freq_target_mean_excluded, col_uncert = freq_target_sd_excluded) %>% 
-
 	cols_merge_uncert(col_val = familiarity_prime_mean_valid, col_uncert = familiarity_prime_sd_valid) %>% 
@@
 
-	cols_label(n_excluded = "⨯",
-			   n_valid = "✓",
-			   freq_prime_mean_valid = "✓",
-			   freq_prime_mean_excluded = "⨯",
-			   freq_target_mean_valid = "✓",
-			   freq_target_mean_excluded = "⨯",
-			   familiarity_prime_mean_valid = "✓",
-			   familiarity_prime_mean_excluded = "⨯",
-			   familiarity_target_mean_valid = "✓",
-			   familiarity_target_mean_excluded = "⨯") %>% 
+	cols_label(n_excluded = "Excluded",
+			   n_valid = "Included",
+			   freq_prime_mean_valid = "Included",
+			   freq_prime_mean_excluded = "Excluded",
+			   freq_target_mean_valid = "Included",
+			   freq_target_mean_excluded = "Excluded",
+			   familiarity_prime_mean_valid = "Included",
+			   familiarity_prime_mean_excluded = "Excluded",
+			   familiarity_target_mean_valid = "Included",
+			   familiarity_target_mean_excluded = "Excluded") %>% 
 	summary_rows(groups = TRUE,
@@
 				 formatter = fmt_number,
-				 decimals = 0) %>% 
+				 decimals = 1) %>% 
 	summary_rows(groups = TRUE,
@@
 				 fns = list("Mean" = ~mean(.)),
-				 formatter = fmt_percent,
+				 formatter = fmt_number,
+				 scale_by = 100,
 				 decimals = 1) %>% 
-	grand_summary_rows(columns = matches("n_"),
+	grand_summary_rows(columns = c(n_valid, n_excluded),
 					   fns = list("N" = ~sum(.)),
@@
 					   decimals = 0) %>% 
+	grand_summary_rows(columns = matches("familiarity_"),
+					   fns = list("Mean" = ~mean(.)),
+					   formatter = fmt_number,
+					   scale_by = 100,
+					   decimals = 1) %>% 
+	grand_summary_rows(columns = matches("freq_"),
+					   fns = list("Mean" = ~mean(.)),
+					   formatter = fmt_number,
+					   decimals = 1) %>% 
 	tab_style(cell_text(align = "center"),
@@
 
-```{r model-comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# model_comparison <- waics_l1 %>% 
-# 	map("estimates") %>% 
-# 	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
-# 	bind_rows(.id = "model") %>%
-# 	clean_names() 
-# 	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
-# 	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
-# 	mutate(
-# 		model = c(
-# 			"Intercept",
-# 			"... + Trial type",
-# 			"... + Group \u00d7Trial type\u00d7Group",
-# 			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
-# 			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
-# 		)
-# 	) %>% 
-# 	gt() %>% 
-# 	fmt_number(-model) %>% 
-# 	tab_spanner("WAIC", matches("waic")) %>% 
-# 	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
-# 	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
-# 	cols_label(
-# 		model = "Model",
-# 		estimate_elpd_waic = "Estimate",
-# 		estimate_waic = "Estimate",
-# 		estimate_p_waic = "Estimate",
-# 		se_elpd_waic = md("*SE*"),
-# 		se_waic = md("*SE*"),
-# 		se_p_waic = md("*SE*"),
-# 	) %>% 
-# 	cols_align("right", "model") %>% 
-# 	tab_style(
-# 		cell_text(weight = "bold"),
-# 		cells_column_spanners()
-# 	) %>% 
-# 	tab_style(
-# 		cell_text(style = "italic"),
-# 		cells_column_labels()
-# 	)
-# 
-# gtsave(model_comparison, here("img", "model_comparison.png"))
-# 
-# 
-# as_raw_html(model_comparison)
-
+```{r}
+#| label: tab-model-comparison
+loos %>% 
+	as_tibble(.name_repair = make_clean_names) %>% 
+	rownames_to_column("model") %>% 
+	relocate(
+		model, 
+		matches("diff"),
+		matches("elpd_loo"),
+		matches("p_loo"), 
+		matches("looic")
+	) %>%
+	mutate(across(everything(), as.numeric),
+		   model = attr(loos, "dimnames")[[1]]) %>% 
+	select(-matches("subsampling")) %>% 
+	gt(rowname_col = "model") %>%
+	fmt_number(is.numeric, decimals = 1) %>% 
+	cols_merge_uncert(col_val = elpd_diff, col_uncert = se_diff) %>% 
+	cols_merge_uncert(col_val = elpd_loo, col_uncert = se_elpd_loo) %>% 
+	cols_merge_uncert(col_val = p_loo, col_uncert = se_p_loo) %>% 
+	cols_merge_uncert(col_val = looic, col_uncert = se_looic) %>% 
+	cols_label(model = "Model",
+			   elpd_loo = md("*ELPD*"),
+			   p_loo = md("*p*"),
+			   looic = md("*LOO-IC*"),
+			   elpd_diff = md("Difference")) %>% 
+	tab_source_note(md("Pareto-*k* estimates of all models were acceptable (*k* < 0.5)")) %>% 
+	tab_style(cell_text(weight = "bold"),
+			  cells_column_labels()) %>% 
+	tab_style(cell_fill(color = "grey", alpha = 0.5),
+			  cells_body(matches("diff"))) %>% 
+	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
+			  cells_body(everything(), 1))
 ```
@@
 
-```{r}
-#| label: fixed-effects
-#| fig-height: 10
-#| fig-width: 12
+::: {.panel-tabset}
+
+#### Table
+
+```{r}
+#| label: tbl-fixed-effects
+#| tbl-cap: "Summary of the posterior distribution of the Growth Curve Analysis model.
+We report the median and 95% highest density interval (*HDI*) of each fixed coefficient.
+The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability.
+Values are in *logit* scale.
+Coefficients whose 95% HDI excludes zero are highlighted in red.
+Coefficients on the intercept indicate changes in overal proportion of target looking, coefficients in the linear term indicate changes in the overall slope of target looking growth across time, coefficients in the quadratic and cubic terms reflect the steepness of the rise and fall or of the rise, fall and rise, respectivey,  of the curve."
 post_draws <- gather_draws(fit_3, `b_.*`, regex = TRUE)
+
+str_repl <- c(
+	"b_Intercept" = "Base",
+	"b_ot1" = "Base",
+	"b_ot2" = "Base",
+	"b_ot3" = "Base",
+	"b_age_group21_25" = "Age [21-25]",
+	"b_age_group25_30" = "Age [25-30]",
+	"b_lpmon_bil" = "Group",
+	"b_trial_typerelated_unrelated" = "Prime (relatedness)",
+	"b_trial_typecognate_noncognate" = "Prime (cognateness)",
+
+	"b_age_group21_25:lpmon_bil" = "Age [21-25] × Group",
+	"b_age_group25_30:lpmon_bil" = "Age [25-30] × Group",
+	"b_age_group21_25:trial_typerelated_unrelated" = "Age [21-25] × Prime (relatedness)",
+	"b_age_group21_25:trial_typecognate_noncognate" = "Age [21-25] × Prime (cognateness)",
+	"b_age_group25_30:trial_typerelated_unrelated" = "Age [25-30] × Prime (relatedness)",
+	"b_age_group25_30:trial_typecognate_noncognate" = "Age [25-30] × Prime (cognateness)",
+	"b_lpmon_bil:trial_typerelated_unrelated" = "Group × Prime (relatedness)",
+	"b_lpmon_bil:trial_typecognate_noncognate" = "Group × Prime (cognateness)",
+
+	"b_age_group21_25:lpmon_bil:trial_typerelated_unrelated" = "Age [21-25] × Group × Prime (relatedness)",
+	"b_age_group21_25:lpmon_bil:trial_typecognate_noncognate" = "Age [21-25] × Group × Prime (cognateness)",
+	"b_age_group25_30:lpmon_bil:trial_typerelated_unrelated" = "Age [25-30] × Group × Prime (relatedness)",
+	"b_age_group25_30:lpmon_bil:trial_typecognate_noncognate" = "Age [25-30] × Group × Prime (cognateness)"
+)
 
@@
 	median_hdi() %>%
-	mutate(excludes_zero = (.lower > 0) | (.upper < 0),
-		   excludes_zero = ifelse(excludes_zero, "Yes", "No") %>% 
-		   	factor(levels = c("Yes", "No")),
-		   poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
+	mutate(poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
 							str_detect(.variable, "ot2") ~ "Quadratic",
-		   				 str_detect(.variable, "ot3") ~ "Qubic",
-		   				 TRUE ~ "Main"),
-		   .variable_name = str_remove(.variable, "b_ot1:|b_ot2:|b_ot3:|b_")) %>% 
-	ggplot(aes(x = .value, y = .variable_name, 
-			   xmin = .lower, xmax = .upper, 
-			   colour = excludes_zero)) +
-	facet_wrap(~poly, scales = "free_x") +
-	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
-	geom_pointinterval(size = 5, point_size = 3) +
+							str_detect(.variable, "ot3") ~ "Cubic",
+							TRUE ~ "Intercept"),
+		   .variable_name = case_when(.variable %in% paste0("b_ot", 1:3) ~ .variable,
+		   						   TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) %>% 
+		   	factor(levels = names(str_repl),
+		   		   label = str_repl,
+		   		   ordered = TRUE),
+		   type = case_when(.variable_name %in% str_repl[1:9] ~ "Main effect",
+		   				 .variable_name %in% str_repl[10:17] ~ "Two-way interactions",
+		   				 .variable_name %in% str_repl[18:length(str_repl)] ~ "Three-way interactions")) %>%
+	select(.variable_name, type, poly, .value:.upper) %>%
+	arrange(.variable_name) %>% 
+	pivot_wider(names_from = poly, 
+				values_from = is.numeric,
+				id_cols = c(.variable_name, type),
+				values_fill = NA,
+				names_repair = make_clean_names) %>% 
+	relocate(variable_name, starts_with("value_")) %>% 
+	gt(rowname_col = "variable_name",
+	   groupname_col = "type") %>% 
+	fmt_number(is.numeric) %>%
+	tab_spanner("Intercept", matches("intercept")) %>% 
+	sub_missing(everything(), rows = everything(), missing_text = "--") %>% 
+	tab_spanner("Linear", matches("linear")) %>% 
+	tab_spanner("Quadratic", matches("quadratic")) %>% 
+	tab_spanner("Cubic", matches("cubic")) %>% 
+	cols_merge(c(lower_intercept, upper_intercept), pattern = "[{1}, {2}]") %>% 
+	cols_merge(c(lower_linear, upper_linear), pattern = "[{1}, {2}]") %>% 
+	cols_merge(c(lower_quadratic, upper_quadratic), pattern = "[{1}, {2}]") %>% 
+	cols_merge(c(lower_cubic, upper_cubic), pattern = "[{1}, {2}]") %>%
+	cols_label(value_intercept = md("b"),
+			   lower_intercept = md("95% *HDI*"),
+			   value_linear = md("b"),
+			   lower_linear = md("95% *HDI*"),
+			   value_quadratic = md("b"),
+			   lower_quadratic = md("95% *HDI*"),
+			   value_cubic = md("b"),
+			   lower_cubic = md("95% *HDI*")) %>% 
+	tab_style(cell_text(align = "left", indent = px(10)),
+			  cells_stub()) %>% 
+	tab_style(cell_fill(color = "grey90"),
+			  cells_body(matches("value"))) %>% 
+	tab_style(cell_text(weight = "bold"),
+			  cells_column_spanners()) %>% 
+	tab_style(cell_text(weight = "bold"),
+			  cells_row_groups()) %>% 
+	tab_style(cell_text(style = "oblique"),
+			  cells_column_labels(columns = matches("value"))) %>% 
+	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
+			  cells_body(columns = value_intercept, 
+			  		   rows = (upper_intercept < 0) | (lower_intercept > 0))) %>% 
+	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
+			  cells_body(columns = value_linear, 
+			  		   rows = (upper_linear < 0) | (lower_linear > 0))) %>%
+	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
+			  cells_body(columns = value_quadratic, 
+			  		   rows = (upper_quadratic < 0) | (lower_quadratic > 0))) %>%
+	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
+			  cells_body(columns = value_cubic, 
+			  		   rows = (upper_cubic < 0) | (lower_cubic > 0))) %>% 
+	tab_style(cell_text(size = "small"), 
+			  list(cells_body(), cells_stub())) %>% 
+	tab_footnote("Sum-coded contrast between 21 and 25 month old participants.",
+				 cells_stub(rows = 2)) %>% 
+	tab_footnote("Sum-coded contrast between 25 and 30 month old participants.",
+				 cells_stub(rows = 3)) %>% 
+	tab_footnote("Sum-coded contrast between monolingual and bilingual participants.",
+				 cells_stub(rows = 4)) %>% 
+	tab_footnote("Sum-coded contrast between related (cognate and non-cognate) and unrelated trials",
+				 cells_stub(rows = 5)) %>% 
+	tab_footnote("Sum-coded contrast between cognate and non-cognate trials",
+				 cells_stub(rows = 6))
+```
+
+#### Plot
+
+```{r}
+#| label: fig-fixed-effects
+#| fig-height: 7
+#| fig-width: 13
+#| fig-cap: "Summary of the posterior of the Growth Curve Analysis model.
+We report the median and 95% highest density interval (*HDI*) of each fixed coefficient.
+The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability.
+Values are in *logit* scale.
+Coefficients whose 95% HDI excludes zero are highlighted in red.
+Summary of the posterior distribution of the Growth Curve Analysis model.
+We report the median and 95% highest density interval (*HDI*) of each fixed coefficient.
+The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability.
+Values are in *logit* scale.
+Coefficients whose 95% HDI excludes zero are highlighted in red.
+Coefficients on the intercept indicate changes in overal proportion of target looking, coefficients in the linear term indicate changes in the overall slope of target looking growth across time, coefficients in the quadratic and cubic terms reflect the steepness of the rise and fall or of the rise, fall and rise, respectivey,  of the curve."
+post_draws %>% 
+	median_hdi() %>%
+	mutate(poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
+							str_detect(.variable, "ot2") ~ "Quadratic",
+							str_detect(.variable, "ot3") ~ "Cubic",
+							TRUE ~ "Intercept") %>% 
+		   	factor(levels = c("Intercept", "Linear", "Quadratic", "Cubic")),
+		   .variable_name = case_when(.variable %in% paste0("b_ot", 1:3) ~ .variable,
+		   						   TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) %>% 
+		   	factor(levels = names(str_repl),
+		   		   label = str_repl,
+		   		   ordered = TRUE),
+		   type = case_when(.variable_name %in% str_repl[1:9] ~ "Main effect",
+		   				 .variable_name %in% str_repl[10:17] ~ "Two-way interactions",
+		   				 .variable_name %in% str_repl[18:length(str_repl)] ~ "Three-way interactions"),
+		   excludes_zero = ifelse((.lower > 0) | (.upper < 0), "Yes", "No")) %>%
+	select(.variable_name, type, poly, .value:.upper, excludes_zero) %>%
+	arrange(.variable_name) %>% 
+	ggplot(aes(x = .value, y = fct_rev(.variable_name), 
+			   colour = excludes_zero,
+			   xmin = .lower, xmax = .upper)) +
+	facet_wrap(~poly, scales = "free_x", nrow = 1) +
+	geom_vline(xintercept = 0, colour = "grey", size = 1) +
+	geom_errorbar(width = 0.2, size = 0.75) +
+	geom_point(size = 3) +
 	labs(x = "Estimate (Logit scale)", 
@@
 		 alpha = "CrI",
-		 title = "Main effects",
-		 subtitle = "Mean and 95% credible interval of posterior distribution",
 		 colour = "Interval excludes zero?") +
@@
 		  axis.title.y = element_blank(),
-		  axis.text.y = element_text(hjust = 1),
+		  axis.text.y = element_text(face = "plain", hjust = 1),
 		  panel.border = element_rect(colour = "black", fill = NA))
 ```
+
+:::
 
@@
 
+ptlt_means <- df %>% 
+	group_by(id, age_group, lp, trial_type, time_bin) %>% 
+	summarise(prop = mean(prop), .groups = "drop") %>% 
+	group_by(age_group, lp, trial_type, time_bin) %>% 
+	summarise(prop = mean(prop), .groups = "drop")
+
 m %>% 
-	ggplot(aes(ot1, .epred, colour = trial_type)) +
+	ggplot(aes(time_bin, .epred, colour = trial_type, shape = trial_type)) +
 	facet_grid(lp~age_group) +
-	geom_line(aes(group = interaction(.draw, trial_type)), alpha = 0.15, size = 1) +
-	stat_summary(fun = median, geom = "line", size = 1) +
-	theme(legend.position = "top")
+	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
+	geom_line(aes(group = interaction(.draw, trial_type)), alpha = 0.15, size = 0.75) +
+	# stat_summary(fun = median, geom = "line", size = 1) +
+	geom_point(data = ptlt_means, aes(y = prop)) +
+	labs(x = "Time (ms)",
+		 y = "Proportion of target looking time",
+		 colour = "Prime",
+		 fill = "Prime",
+		 shape = "Prime",
+		 linetype = "Trial type") +
+	scale_x_continuous(labels = function(x) format(x*100, big.mark = ",")) +
+	scale_y_continuous(labels = percent) +
+	theme(legend.position = "top",
+		  panel.grid = element_line(linetype = "dotted", colour = "grey"),
+		  panel.grid.minor = element_blank(),
+		  legend.title = element_blank())
 ```

### 2022-12-21 R/04_attrition.R

@@ -1,95 +1,39 @@
 # attrition
 get_attrition <- function(
-		gaze_imputed, # Barcelona gaze data, get_gaze_bcn output
+		gaze_aoi, # Barcelona gaze data, get_gaze_bcn output
 		participants, # participants dataset, get_participants output
 		stimuli, # stimuli dataset, get_stimuli output
 		vocabulary, # vocabulary dataset, get_vocabulary output
 		aoi_coords = aoi_coords,
 		filter_vocabulary = c("prime", "target"), # should the trial be excluded if no comprehension in any of these words? (prime, target, distractor)
-		filter_counterbalancing = FALSE, # should trials from same counterbalancing pair be excluded together?
 		looking_threshold = c(prime = 0.25, target = 0.25, distractor = 0), # minimum looking time
-		missing_trials_threshold = c(cognate = 2, non_cognate = 2, unrelated = 2) # minimum n trials in each condition
+		min_trials = c(cognate = 2, non_cognate = 2, unrelated = 2) # minimum n trials in each condition
 ){
 	suppressWarnings({
 		
-		processed <- list(select(participants, -filename), stimuli, gaze_imputed) %>% 
-			reduce(full_join) %>%  
-			drop_na(filename) %>% 
-			select(id, age_group, trial, phase, time, x, y, 
-				   target_location, valid_sample,
-				   trial_type, prime_cdi, target_cdi, distractor_cdi,
-				   filename) 
-		
-		# evaluate inclusion criteria ----
-		# valid gaze
-		valid_gaze <- processed %>% 
-			# evaluate if gaze coordinates are inside any AOI, and which
-			mutate(aoi_center = gaze_in_center(x, y, aoi_coords = aoi_coords),
-				   aoi_left = gaze_in_left(x, y, aoi_coords),
-				   aoi_right = gaze_in_right(x, y, aoi_coords)) %>% 
-			replace_na(list(aoi_center = FALSE, aoi_right = FALSE, aoi_left = FALSE)) %>% 
-			mutate(aoi_prime = aoi_center,
-				   aoi_target = ifelse(target_location=="r", aoi_right, aoi_left),
-				   aoi_distractor = ifelse(target_location=="l", aoi_right, aoi_left)) %>% 
-			rename_with(~str_remove(., "_cdi"), everything()) %>% 
-			group_by(id, age_group, trial_type, filename, trial) %>% 
[…]

### 2022-12-21 tests/testthat/test-attrition.R

@@ -11,6 +11,7 @@ test_attrition <- function(
 			c("id",
 			  "age_group",
 			  "trial",
+			  "trial_id",
 			  "trial_type",
 			  "valid_gaze_prime",
 			  "valid_gaze_target",
@@ -33,8 +34,9 @@ test_attrition <- function(
 	
 	test_that("attrition has the variable classes", {
 		expect_type(attrition$id, "character")
-		expect_equal(class(attrition$age_group), "factor")
+		expect_equal(class(attrition$age_group), "character")
 		expect_equal(class(attrition$trial), "integer")
+		expect_equal(class(attrition$trial_id), "integer")
 		expect_type(attrition$trial_type, "character")
 		expect_type(attrition$valid_gaze_prime, "logical")
 		expect_type(attrition$valid_gaze_target, "logical")
@@ -52,6 +54,7 @@ test_attrition <- function(
 		expect_false(any(is.na(attrition$id)))
 		expect_false(any(is.na(attrition$age_group)))
 		expect_false(any(is.na(attrition$trial)))
+		expect_false(any(is.na(attrition$trial_id)))
 		expect_false(any(is.na(attrition$trial_type)))
 		expect_false(any(is.na(attrition$valid_gaze_prime)))
 		expect_false(any(is.na(attrition$valid_gaze_target)))
@@ -63,8 +66,9 @@ test_attrition <- function(
 	})
 	
 	test_that("attrition variables have the right values", {
-		expect_equal(levels(attrition$age_group), paste0(c(21, 25, 30), " months"))
+		expect_true(all(unique(attrition$age_group) %in% paste0(c(21, 25, 30), " months")))
 		expect_true(all(between(unique(attrition$trial), 0, 32)))
+		expect_true(all(between(unique(attrition$trial_id), 0, 32)))
 		expect_true(all(unique(attrition$trial_type) %in% c("Cognate", "Non-cognate", "Unrelated")))
 		expect_true(all(unique(attrition$valid_gaze_prime) %in% c(TRUE, FALSE)))
 		expect_true(all(unique(attrition$valid_gaze_target) %in% c(TRUE, FALSE)))

### 2022-12-21 tests/testthat/test-gaze_imputed.R

@@ -6,6 +6,7 @@ test_gaze_imputed <- function(gaze_imputed){
 			c("id",
 			  "age_group",
 			  "trial",
+			  "trial_id",
 			  "phase",
 			  "time",
 			  "x",
@@ -17,7 +18,7 @@ test_gaze_imputed <- function(gaze_imputed){
 	
 	test_that("gaze_imputed has the variable classes", {
 		expect_type(gaze_imputed$id, "character")
-		expect_equal(class(gaze_imputed$age_group), "factor")
+		expect_equal(class(gaze_imputed$age_group), "character")
 		expect_equal(class(gaze_imputed$trial), "integer")
 		expect_type(gaze_imputed$phase, "character")
 		expect_type(gaze_imputed$time, "double")
@@ -39,7 +40,7 @@ test_gaze_imputed <- function(gaze_imputed){
 	})
 	
 	test_that("gaze_imputed variables have the right values", {
-		expect_equal(levels(gaze_imputed$age_group), paste0(c(21, 25, 30), " months"))
+		expect_true(all(unique(gaze_imputed$age_group) %in% paste0(c(21, 25, 30), " months")))
 		expect_true(all(between(unique(gaze_imputed$trial), 0, 32)))
 		expect_true(all(unique(gaze_imputed$phase) %in% c("Prime", "Target-Distractor")))
 		expect_true(all(between(unique(gaze_imputed$time[gaze_imputed$phase=="Prime"]), 0, 1.5)))

### 2022-12-21 docs/index.qmd
Stop ignoring HTMLs in the docs/ folder

@@
 #| label: fig-stimuli-category-prime
-#| fig-height: 7
-#| fig-width: 12
+#| fig-height: 5
+#| fig-width: 10
 stimuli %>% 
@@
 #| label: fig-stimuli-category-target
-#| fig-height: 7
-#| fig-width: 12
+#| fig-height: 5
+#| fig-width: 10
 stimuli %>% 
@@
 #| fig-cap: "L1 vocabulary. Percentage of words in L1 reported to be understood from the vocabulary checklist."
-#| fig-height: 4
+#| fig-height: 5
+#| fig-width: 8
 sample_size <- participants %>% 
@@
 #| fig-cap: "Total vocabulary"
-#| fig-height: 4
-# vocabulary
+#| fig-height: 5
+#| fig-width: 8
 participants %>% 
@@
 #| label: fig-vocabulary-conceptual
-#| fig-height: 4
+#| fig-height: 5
+#| fig-width: 8
 participants %>% 
@@
 #| label: fig-prior-epred
+#| fig-width: 9
+#| fig-height: 6
 nd <- tibble(time_bin = seq(0, 20, 0.1)) %>% 
@@
 
-	cols_label(n_excluded = "Excluded",
-			   n_valid = "Included",
-			   freq_prime_mean_valid = "Included",
-			   freq_prime_mean_excluded = "Excluded",
-			   freq_target_mean_valid = "Included",
-			   freq_target_mean_excluded = "Excluded",
-			   familiarity_prime_mean_valid = "Included",
-			   familiarity_prime_mean_excluded = "Excluded",
-			   familiarity_target_mean_valid = "Included",
-			   familiarity_target_mean_excluded = "Excluded") %>% 
+	cols_label(n_excluded = "Exc.",
+			   n_valid = "Inc.",
+			   freq_prime_mean_valid = "Inc.",
+			   freq_prime_mean_excluded = "Exc.",
+			   freq_target_mean_valid = "Inc.",
+			   freq_target_mean_excluded = "Exc.",
+			   familiarity_prime_mean_valid = "Inc.",
+			   familiarity_prime_mean_excluded = "Exc.",
+			   familiarity_target_mean_valid = "Inc.",
+			   familiarity_target_mean_excluded = "Exc.") %>% 
 	summary_rows(groups = TRUE,
@@
 			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary()))
-
+			  	 cells_stub_summary())) %>% 
+	tab_footnote("Included trials.", cells_column_labels(matches("_valid"))) %>% 
+	tab_footnote("Excluded trials.", cells_column_labels(matches("_excluded")))
 ```
@@
 #| label: fig-descriptives-aggregated
+#| fig-width: 10
+#| fig-height: 6
 df %>% 
@@
 #| label: fig-descriptives-time-course
+#| fig-width: 12
+#| fig-height: 8
 df %>% 
@@
 	theme(legend.position = "top",
+		  legend.title = element_blank(),
+		  panel.grid = element_line(linetype = "dotted", colour = "grey"),
 		  panel.grid.major = element_line(colour = "grey", linetype = "dotted"))
@@
 	"b_lpmon_bil" = "Group",
-	"b_trial_typerelated_unrelated" = "Prime (relatedness)",
-	"b_trial_typecognate_noncognate" = "Prime (cognateness)",
+	"b_trial_typerelated_unrelated" = "Prime (R)",
+	"b_trial_typecognate_noncognate" = "Prime (C)",
 
@@
 	"b_age_group25_30:lpmon_bil" = "Age [25-30] × Group",
-	"b_age_group21_25:trial_typerelated_unrelated" = "Age [21-25] × Prime (relatedness)",
-	"b_age_group21_25:trial_typecognate_noncognate" = "Age [21-25] × Prime (cognateness)",
-	"b_age_group25_30:trial_typerelated_unrelated" = "Age [25-30] × Prime (relatedness)",
-	"b_age_group25_30:trial_typecognate_noncognate" = "Age [25-30] × Prime (cognateness)",
-	"b_lpmon_bil:trial_typerelated_unrelated" = "Group × Prime (relatedness)",
-	"b_lpmon_bil:trial_typecognate_noncognate" = "Group × Prime (cognateness)",
-
-	"b_age_group21_25:lpmon_bil:trial_typerelated_unrelated" = "Age [21-25] × Group × Prime (relatedness)",
-	"b_age_group21_25:lpmon_bil:trial_typecognate_noncognate" = "Age [21-25] × Group × Prime (cognateness)",
-	"b_age_group25_30:lpmon_bil:trial_typerelated_unrelated" = "Age [25-30] × Group × Prime (relatedness)",
-	"b_age_group25_30:lpmon_bil:trial_typecognate_noncognate" = "Age [25-30] × Group × Prime (cognateness)"
+	"b_age_group21_25:trial_typerelated_unrelated" = "Age [21-25] × Prime (R)",
+	"b_age_group21_25:trial_typecognate_noncognate" = "Age [21-25] × Prime (C)",
+	"b_age_group25_30:trial_typerelated_unrelated" = "Age [25-30] × Prime (R)",
+	"b_age_group25_30:trial_typecognate_noncognate" = "Age [25-30] × Prime (C)",
+	"b_lpmon_bil:trial_typerelated_unrelated" = "Group × Prime (R)",
+	"b_lpmon_bil:trial_typecognate_noncognate" = "Group × Prime (C)",
+
+	"b_age_group21_25:lpmon_bil:trial_typerelated_unrelated" = "Age [21-25] × Group × Prime (R)",
+	"b_age_group21_25:lpmon_bil:trial_typecognate_noncognate" = "Age [21-25] × Group × Prime (C)",
+	"b_age_group25_30:lpmon_bil:trial_typerelated_unrelated" = "Age [25-30] × Group × Prime (R)",
+	"b_age_group25_30:lpmon_bil:trial_typecognate_noncognate" = "Age [25-30] × Group × Prime (C)"
 )
@@
 #| label: fig-posterior-epred
+#| fig-width: 12
+#| fig-height: 8
 nd <- expand_grid(time_bin = seq(0, 20, 0.1),

### 2022-12-21 docs/index.qmd
Update report

@@
 
-### Animacy
-
-```{r}
-#| label: fig-stimuli-animacy
-#| fig-height: 6
-animacy <- stimuli %>%
-	distinct(test_language, 
-			 target, 
-			 prime, 
-			 .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), 
-				 names_to = "role",
-				 values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(test_language,  trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	# filter(role=="Prime") %>% 
-	ggplot() +
-	aes(x = trial_type, 
-		y = n, 
-		fill = is_animate,
-		colour = is_animate) + 
-	facet_grid(test_language~role) +
-	geom_col(position = position_fill(), colour = "white", size = 0.75) +
-	geom_hline(yintercept = 0.5,  size = 1, colour = "grey") +
-	labs(title = "Prime", 
-		 x = "Trial type", 
-		 y = "# trials",
-		 colour = "Animacy", 
-		 fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(legend.position = "top",
-		  legend.title = element_blank(),
-		  panel.grid = element_blank(),
-		  axis.title.y = element_blank(),
-		  axis.text = element_text(size = 7),
-		  axis.text.y = element_text(hjust = 1),
-		  strip.text = element_text(size = 11))
-```
-
-### Semantic category
-
-::: {.panel-tabset}
-
-#### Prime
-
-```{r}
-#| label: fig-stimuli-category-prime
-#| fig-height: 5
-#| fig-width: 10
-stimuli %>% 
-	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
-	drop_na(trial_type, semantic_category_prime) %>% 
-	count(trial_type, test_language, semantic_category_prime, name = "sum") %>% 
-	right_join(expand(., trial_type,  test_language,  semantic_category_prime)) %>%
-	replace_na(list(sum = 0)) %>% 
-	group_by(trial_type, test_language) %>% 
-	mutate(n =  sum(sum), prop = sum/n) %>% 
-	ungroup() %>% 
-	ggplot() +
-	aes(x = prop,
-		y = reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
-		fill = test_language,
-		order = prop) + 
-	facet_wrap(test_language~trial_type,
-			   scales = "free_y",
-			   labeller = label_wrap_gen(multi_line = FALSE)) +
-	geom_col(colour = "white",
-			 position = position_dodge(),
-			 width = 1) +
-	labs(x = "% of trials",
-		 y = "Trial type",
-		 colour = "Trial type",
-		 fill = "Trial type") +
-	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
-	scale_y_reordered() +
-	theme(legend.position = "none",
-		  legend.title = element_blank(),
-		  axis.text.y = element_text(size = 9, hjust = 1),
-		  axis.text.x = element_text(size = 8, hjust = 1),
-		  axis.title.y = element_blank(),
-		  axis.ticks.y = element_blank(),
-		  plot.caption = element_text(size = 10, hjust = 0),
-		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-		  strip.text = element_text(size = 10))
-```
-
-#### Target
-
-```{r}
-#| label: fig-stimuli-category-target
-#| fig-height: 5
-#| fig-width: 10
-stimuli %>% 
-	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
-	drop_na(trial_type, semantic_category_target) %>% 
-	count(trial_type, test_language, semantic_category_target, name = "sum") %>% 
-	right_join(expand(., trial_type,  test_language,  semantic_category_target)) %>%
-	replace_na(list(sum = 0)) %>% 
-	group_by(trial_type, test_language) %>% 
-	mutate(n =  sum(sum), prop = sum/n) %>% 
-	ungroup() %>% 
-	ggplot() +
-	aes(x = prop,
-		y = reorder_within(semantic_category_target, desc(prop), list(trial_type, test_language)),
-		fill = test_language,
-		order = prop) + 
-	facet_wrap(test_language~trial_type,
-			   scales = "free_y",
-			   labeller = label_wrap_gen(multi_line = FALSE)) +
-	geom_col(colour = "white",
-			 position = position_dodge(),
-			 width = 1) +
-	labs(x = "% of trials",
-		 y = "Trial type",
-		 colour = "Trial type",
-		 fill = "Trial type") +
-	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
-	scale_y_reordered() +
-	theme(legend.position = "none",
-		  legend.title = element_blank(),
-		  axis.text.y = element_text(size = 9, hjust = 1),
-		  axis.text.x = element_text(size = 8, hjust = 1),
-		  axis.title.y = element_blank(),
-		  axis.ticks.y = element_blank(),
-		  plot.caption = element_text(size = 10, hjust = 0),
-		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-		  strip.text = element_text(size = 10))
-```
-
-:::
-
 ## Vocabulary
@@
 #| fig-height: 5
-#| fig-width: 8
+#| fig-width: 11
 sample_size <- participants %>% 
@@
 #| fig-height: 5
-#| fig-width: 8
+#| fig-width: 11
 participants %>% 
@@
 ```
+
+## Additional stimuli properties
+
+### Animacy
+
+```{r}
+#| label: fig-stimuli-animacy
+#| fig-height: 6
+animacy <- stimuli %>%
+	distinct(test_language, 
+			 target, 
+			 prime, 
+			 .keep_all = TRUE) %>% 
+	pivot_longer(c(is_animate_prime, is_animate_target), 
+				 names_to = "role",
+				 values_to = "is_animate") %>% 
+	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
+	count(test_language,  trial_type, role, is_animate) %>% 
+	drop_na(is_animate) %>% 
+	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
+
+animacy %>% 
+	# filter(role=="Prime") %>% 
+	ggplot() +
+	aes(x = trial_type, 
+		y = n, 
+		fill = is_animate,
+		colour = is_animate) + 
+	facet_grid(test_language~role) +
+	geom_col(position = position_fill(), colour = "white", size = 0.75) +
+	geom_hline(yintercept = 0.5,  size = 1, colour = "grey") +
+	labs(title = "Prime", 
+		 x = "Trial type", 
+		 y = "# trials",
+		 colour = "Animacy", 
+		 fill = "Animacy") +
+	scale_y_continuous(labels = percent) +
+	coord_flip() + 
+	theme(legend.position = "top",
+		  legend.title = element_blank(),
+		  panel.grid = element_blank(),
+		  axis.title.y = element_blank(),
+		  axis.text = element_text(size = 7),
+		  axis.text.y = element_text(hjust = 1),
+		  strip.text = element_text(size = 11))
+```
+
+### Semantic category
+
+::: {.panel-tabset}
+
+#### Prime
+
+```{r}
+#| label: fig-stimuli-category-prime
+#| fig-height: 5
+#| fig-width: 10
+stimuli %>% 
+	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
+	drop_na(trial_type, semantic_category_prime) %>% 
+	count(trial_type, test_language, semantic_category_prime, name = "sum") %>% 
+	right_join(expand(., trial_type,  test_language,  semantic_category_prime)) %>%
+	replace_na(list(sum = 0)) %>% 
+	group_by(trial_type, test_language) %>% 
+	mutate(n =  sum(sum), prop = sum/n) %>% 
+	ungroup() %>% 
+	ggplot() +
+	aes(x = prop,
+		y = reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
+		fill = test_language,
+		order = prop) + 
+	facet_wrap(test_language~trial_type,
+			   scales = "free_y",
+			   labeller = label_wrap_gen(multi_line = FALSE)) +
+	geom_col(colour = "white",
+			 position = position_dodge(),
+			 width = 1) +
+	labs(x = "% of trials",
+		 y = "Trial type",
+		 colour = "Trial type",
+		 fill = "Trial type") +
+	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
+	scale_y_reordered() +
+	theme(legend.position = "none",
+		  legend.title = element_blank(),
+		  axis.text.y = element_text(size = 9, hjust = 1),
+		  axis.text.x = element_text(size = 8, hjust = 1),
+		  axis.title.y = element_blank(),
+		  axis.ticks.y = element_blank(),
+		  plot.caption = element_text(size = 10, hjust = 0),
+		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
+		  strip.text = element_text(size = 10))
+```
+
+#### Target
+
+```{r}
+#| label: fig-stimuli-category-target
+#| fig-height: 5
+#| fig-width: 10
+stimuli %>% 
+	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
+	drop_na(trial_type, semantic_category_target) %>% 
+	count(trial_type, test_language, semantic_category_target, name = "sum") %>% 
+	right_join(expand(., trial_type,  test_language,  semantic_category_target)) %>%
+	replace_na(list(sum = 0)) %>% 
+	group_by(trial_type, test_language) %>% 
+	mutate(n =  sum(sum), prop = sum/n) %>% 
+	ungroup() %>% 
+	ggplot() +
+	aes(x = prop,
+		y = reorder_within(semantic_category_target, desc(prop), list(trial_type, test_language)),
+		fill = test_language,
+		order = prop) + 
+	facet_wrap(test_language~trial_type,
+			   scales = "free_y",
+			   labeller = label_wrap_gen(multi_line = FALSE)) +
+	geom_col(colour = "white",
+			 position = position_dodge(),
+			 width = 1) +
+	labs(x = "% of trials",
+		 y = "Trial type",
+		 colour = "Trial type",
+		 fill = "Trial type") +
+	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
+	scale_y_reordered() +
+	theme(legend.position = "none",
+		  legend.title = element_blank(),
+		  axis.text.y = element_text(size = 9, hjust = 1),
+		  axis.text.x = element_text(size = 8, hjust = 1),
+		  axis.title.y = element_blank(),
+		  axis.ticks.y = element_blank(),
+		  plot.caption = element_text(size = 10, hjust = 0),
+		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
+		  strip.text = element_text(size = 10))
+```
+
+:::

### 2023-05-03 docs/index.qmd
Fix targets workflow

@@
 library(patchwork)
-library(bvqdev)
+library(bvq)
 
@@
 In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI, @hamilton2000infant] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvqdev) immediately after the appointment, and were given two weeks to fill it.
+In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvq) immediately after the appointment, and were given two weeks to fill it.
 In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.

### 2023-05-03 manuscript/manuscript.qmd
Fix targets workflow

--- 2023-05-03 docs/index.qmd
@@
 ---
-title: "Cognate Priming"
-subtitle: "Lab notes"
-date: "Updated: `r format(Sys.Date(), '%Y/%m/%d')`"
-authors:
+title: "Developmental trajectories of word recognition: a priming study in bilinguals"
+editor: source
+author:
   - name: Gonzalo Garcia-Castro
@@
     email: gonzalo.garciadecastro@upf.edu
+    affiliations:
+      - ref: upf
     corresponding: true
+  - name: Serene Siow
     affiliations:
-      - name: Universitat Pompeu Fabra
-        department: Center for Brain and Cognition
-        address: Ramon Trias fargas 25-27
-        city: Barcelona
-        state: Spain
-        postal-code: 08005
+      - ref: oxf
+  - name: Núria Sebastian-Galles
+    affiliations:
+      - ref: upf
+  - name: Kim Plunkett
+    affiliations:
+      - ref: oxf
+affiliations:
+  - id: upf
+    name: Center for Brain and Cognition, Universitat Pompeu Fabra
+  - id: oxf
+    name: Department of Experimental Psychology, University of Oxford
+
+pagetitle: Cross-linguistic similarity and  word acquisition
 abstract: "Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language (e.g., Costa et al., 2000; Thierry & Wu, 2007).
@@
 We tested bilinguals (n = 46) and same-aged monolingual controls, n = 123) at three age points (21, 25, and 30 months) to investigate how any cross-language priming effect emerged or changed across these ages."
+thanks: "This research was supported by grants from the Spanish Ministerio de Ciencia, Innovación y Universidades (PGC2018-101831-B-I00 and PRE2019-088165), and the Catalan Government [ICREA (Catalan Institution for Research and Advanced Studies) Academia 2019 award].
+Gonzalo Garcia-Castro was supported by a fellowship of the Spanish Ministerio de Ciencia, Innovación y Universidades (FPI 2019).
+The authors declare no conflicts of interest with regard to the funding source of this study.
+We thank Xavier Mayoral, Silvia Blanch, Cristina Cuadrado, and Irina Lepadatu for their technical support.
+We also thank Cristina Dominguez, Katia Pistrin, and Nicola Gillen for their efforts in recruiting infants.
+We would like to thank the clinics Quirón and Sagrada Familia that allowed us to recruit participants in their premises.
+We also thank all families and infants who participated in the experiments.
+Data collection was half-way when the COVID-19 pandemic started.
+We would like to pay special tribute to the families that collaborated with us under these difficult circumstances."
+keywords: word recognition, cognate, vocabulary, bilingualism, eye-tracking, growth curve analysis, bayesian
+csl: assets/bibliography/apa7.csl
+bibliography: assets/bibliography/references.bib
 format:
-    html:
-        link-external-newwindow: true
-        number-offset: 0
-        code-fold: true
-        code-overflow: scroll
-        code-line-numbers: true
-        code-copy: hover
-        reference-location: margin
-    pdf: default
+  pdf:
+    pdf-engine: lualatex
+    number-sections: true
+    whitespace: small
   docx:
-        reference-doc: reference.docx
+  	reference-doc: assets/templates/template.docx
+linestretch: 1.5
+toc: false
 fig-dpi: 1000
+echo: false
 warning: false
-echo: false
-toc: true
-colorlinks: true
-number-sections: true
-bibliography: "references.bib"
-csl: "apa7.csl"
 ---
@@
 
+# Introduction
+
 # Methods
+
+All materials, data, and reproducible code can be found at the OSF ([https://osf.io/hy984/](https://osf.io/ckydb/)) and GitHub ([https://github.com/gongcastro/cognate-priming](https://github.com/gongcastro/cognate-priming)) repositories.
+This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I.
 
@@
 
-```{r}
-#| label: tbl-participants-lp
-#| tbl-cap: "Description of language profile of participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
-participants %>% 
-	select(id, age_group, age, lp, doe_catalan, doe_spanish, test_language) %>% 
-	mutate(id = paste0(id, " (", age_group, ")")) %>%
-	add_count(lp, name = "n_lp") %>% 
-	add_count(age_group, name = "n_age_group") %>%
-
-	pivot_longer(starts_with("doe_"), names_to = "language", values_to = "doe") %>%
-	add_count(age_group, test_language, name = "n_age_test") %>% 
-	mutate(language = str_remove_all(language, "doe_") %>% 
-		   	str_to_sentence(),
-		   age_group = paste0(age_group, " (N = ", n_age_group, ")"),
-		   test_language = paste0("Tested in ", test_language, " (N = ", n_age_test, ")"),
-		   lp = factor(lp, levels = rev(unique(lp))))  %>% 
-	group_by(age_group, lp, test_language, language) %>% 
-	summarise(across(doe, lst(mean, sd)),
-			  .groups = "drop") %>% 
-	pivot_wider(id_cols = c(age_group, test_language),
-				names_from = c(language, lp),
-				values_from = c(matches("doe"))) %>% 
-	clean_names() %>% 
-	relocate(age_group, test_language,
-			 matches("catalan"),
-			 matches("spanish")) %>% 
-	gt(rowname_col = "test_language", 
-	   groupname_col = "age_group", row_group.sep = ": ") %>% 
-	tab_spanner(md("Monolingual (*N* = 162)"), matches("monolingual")) %>% 
-	tab_spanner(md("Bilingual (*N* = 133)"), matches("bilingual")) %>%
-	fmt_number(matches("doe"), decimals = 1, scale_by = 100) %>% 
-	cols_merge_uncert(col_val = doe_mean_catalan_monolingual,
-					  col_uncert = doe_sd_catalan_monolingual) %>% 
-	cols_merge_uncert(col_val = doe_mean_catalan_bilingual,
-					  col_uncert = doe_sd_catalan_bilingual) %>% 
-	cols_merge_uncert(col_val = doe_mean_spanish_monolingual, 
-					  col_uncert = doe_sd_spanish_monolingual) %>% 
-	cols_merge_uncert(col_val = doe_mean_spanish_bilingual, 
-					  col_uncert = doe_sd_spanish_bilingual) %>%
-
-	cols_label(doe_mean_catalan_monolingual = "Catalan (%)",
-			   doe_mean_catalan_bilingual = "Catalan (%)",
-			   doe_mean_spanish_monolingual = "Spanish (%)",
-			   doe_mean_spanish_bilingual = "Spanish (%)") %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) %>% 
-	tab_style(cell_text(size = "medium"),
-			  list(cells_body(),
-			  	 cells_stub()))
-```
-
-The research reported in this article was conducted in accordance with the principles expressed in the Declaration of Helsinki and approved by the local ethical committee (the clinical research ethical committee of the Parc de la Salut Mar).
-Before every testing session, caretakers were asked to read and sign an informed consent form, and were given a small gift at the end of it.
-
 ## Stimuli
 
-## Vocabulary
+## Procedure
 
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI, @hamilton2000infant] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvq) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm 1$ month) and language profile (similar exposure to a second language, $\pm 10%$) that completed the same vocabulary checklist previously.
-
-### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r}
-#| label: fig-vocabulary-l1
-#| fig-cap: "L1 vocabulary. Percentage of words in L1 reported to be understood from the vocabulary checklist."
-#| fig-height: 5
-#| fig-width: 11
-sample_size <- participants %>% 
-	filter(id %in% fit_0$data$id) %>% 
-	count(age_group)
-
-sample_size_lp <- participants %>% 
-	filter(id %in% fit_0$data$id) %>% 
-	count(age_group, lp) %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		)
-	)
-
-# vocabulary
-participants %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		),
-		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
-							levels = c("Observed", "Imputed"))
-	) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot(aes(lp,  vocab_size_l1, colour = is_imputed, fill = is_imputed)) +
-	facet_wrap(~age_group, scales = "free_x") +
-	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(width = 0.15, size = 1, colour = "black",
-				 fill = "white", outlier.colour = NA,
-				 position = position_nudge(x = 0.3)) +
-	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
-	geom_text(data = sample_size_lp,
-			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
-			  colour = "black", show.legend = FALSE, 
-			  position = position_dodge(width = 2), inherit.aes = FALSE) +
-	labs(y = "Receptive vocabulary", 
-		 colour = "Imputed", 
-		 fill = "Imputed") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(legend.position = "top", 
-		  legend.title = element_blank(),
-		  panel.grid.major.x = element_blank(),
-		  axis.title.x = element_blank(),
-		  axis.text = element_text(size = 9))
-```
-
-### Total vocabulary
-
-```{r}
-#| label: fig-vocabulary-total
-#| fig-cap: "Total vocabulary"
-#| fig-height: 5
-#| fig-width: 11
-participants %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		),
-		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
-							levels = c("Observed", "Imputed"))
-	) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot(aes(lp,  vocab_size_total, colour = is_imputed, fill = is_imputed)) +
-	facet_wrap(~age_group, scales = "free_x") +
-	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(width = 0.15, size = 1, colour = "black",
-				 fill = "white", outlier.colour = NA,
-				 position = position_nudge(x = 0.3)) +
-	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
-	geom_text(data = sample_size_lp,
-			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
-			  colour = "black", show.legend = FALSE, 
-			  position = position_dodge(width = 2), inherit.aes = FALSE) +
-	labs(y = "Receptive vocabulary", 
-		 colour = "Imputed", 
-		 fill = "Imputed") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(legend.position = "top", 
-		  legend.title = element_blank(),
-		  panel.grid.major.x = element_blank(),
-		  axis.title.x = element_blank(),
-		  axis.text = element_text(size = 9))
-```
-
-### Conceptual vocabulary
-
-```{r}
-#| label: fig-vocabulary-conceptual
-#| fig-height: 5
-#| fig-width: 11
-participants %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		),
-		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
-							levels = c("Observed", "Imputed"))
-	) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot(aes(lp,  vocab_size_conceptual, colour = is_imputed, fill = is_imputed)) +
-	facet_wrap(~age_group, scales = "free_x") +
-	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(width = 0.15, size = 1, colour = "black",
-				 fill = "white", outlier.colour = NA,
-				 position = position_nudge(x = 0.3)) +
-	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
-	geom_text(data = sample_size_lp,
-			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
-			  colour = "black", show.legend = FALSE, 
-			  position = position_dodge(width = 2), inherit.aes = FALSE) +
-	labs(y = "Receptive vocabulary", 
-		 colour = "Imputed", 
-		 fill = "Imputed") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(legend.position = "top", 
-		  legend.title = element_blank(),
-		  panel.grid.major.x = element_blank(),
-		  axis.title.x = element_blank(),
-		  axis.text = element_text(size = 9))
-```
-
-## Design
+## Apparatus
 
@@
 
-### Data processing
-
-```{r} 
-#| label: tbl-attrition-group
-#| tbl-cap: "Summary of the dataset."
-attrition %>% 
-	left_join(select(participants, age_group, lp, id, date_test)) %>% 
-	add_count(age_group, lp, name = "n_trials") %>% 
-	group_by(id, lp, trial_type, date_test, age_group, valid_participant, n_trials) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(names_from = trial_type, values_from = valid_trial_count, values_fill = 0) %>% 
-	clean_names() %>% 
-	add_count(lp, age_group) %>%
-	group_by(lp, age_group, n, n_trials) %>% 
-	summarise(across(cognate:unrelated, lst(sum, mean, sd)),
-			  n_valid = sum(valid_participant),
-			  .groups = "drop") %>%
-	relocate(n_valid, .after = n) %>% 
-	mutate(n_prop = n_valid/n) %>% 
-	arrange(age_group, lp) %>% 
-	relocate(age_group, lp, n_valid, n_prop, matches("cognate"), matches("non_cognate"), matches("unrelated")) %>% 
-	gt(groupname_col = "age_group", rowname_col = "lp")  %>%
-	cols_hide(c(n, n_trials)) %>% 
-	fmt_number(matches("_mean|_sd"), decimals = 1) %>%
-	fmt_percent(matches("_prop"), decimals = 1) %>% 
-	cols_merge_n_pct(col_n = n_valid, col_pct = n_prop, autohide = TRUE)  %>% 
-	tab_spanner("Non-cognate", matches("non_cognate")) %>%
-	tab_spanner("Cognate", starts_with("cognate")) %>%
-	tab_spanner("Unrelated", matches("unrelated")) %>%
-	tab_spanner("Related", matches("cognate")) %>%
-
-	cols_merge_uncert(col_val = cognate_mean, col_uncert = cognate_sd) %>% 
-	cols_merge_uncert(col_val = non_cognate_mean, col_uncert = non_cognate_sd) %>% 
-	cols_merge_uncert(col_val = unrelated_mean, col_uncert = unrelated_sd) %>% 
-	cols_label(age_group = "Age",
-			   n_valid = "Participants (included)",
-			   cognate_sum = "Trials",
-			   cognate_mean = "Mean ± SD",
-			   non_cognate_sum = "Trials",
-			   non_cognate_mean = "Mean ± SD",
-			   unrelated_sum = "Trials",
-			   unrelated_mean = "Mean ± SD") %>% 
-	summary_rows(groups = TRUE,
-				 columns = where(is.integer), 
-				 fns = list("Sum" = ~sum(.)), 
-				 formatter = fmt_number,
-				 decimals = 0) %>% 
-	summary_rows(groups = TRUE,
-				 columns = c(where(is.numeric), -n_valid), 
-				 fns = list("Mean" = ~mean(.)),
-				 formatter = fmt_number,
-				 decimals = 1) %>% 
-	grand_summary_rows(columns = where(is.integer),
-					   fns = list("N" = ~sum(.)),
-					   formatter = fmt_number,
-					   decimals = 0) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary())) 
-```
-
-### Predictors
-
-### Model
-
-$$
-\begin{aligned}
-\textbf{Likelihood:} \\
-y_{ij} &\sim \text{Bernoulli}(p)
-\end{aligned}
-$$ {#eq-likelihood}
-
-where:
-
-- $y$ is an observed response ($y \in \{\text{No, Understands, Understands and Says}\}$)
-- $i$ is the participant index
-- $j$ is the translation equivalent (TE) index
-- $p$ is the probability f target looking ($p \in (0, 1)$)
-
-$p$ is then estimated using a logit regression model as indicated in @eq-linear.
-
-$$
-\begin{aligned}
-\textbf{Linear model:} \\
-logit(p) = \text{ln} \frac{p}{1-p} &= (\beta_{0} + u_{0_{i}}) + \\
-& (\beta_{1} + u_{1_{i}}) · \text{Age group}_{i} + & \\
-& \beta_{2} · \text{Language Profile}_{i} + & \\
-& (\beta_{3} + u_{2_{i}}) · \text{Trial type}_{i} + & \\
-& \beta_{4} · (\text{Age group}_{i} \times \text{Language Profile}_{i}) & \\
-& (\beta_{5} + u_{3_{i}}) · (\text{Age group}_{i} \times \text{Trial type}_{i}) + & \\
-& \beta_{6} · (\text{Language Profile}_{ij} \times \text{Trial type}_{i}) & \\
-& \beta_{7} · (\text{Age group}_{i} \times \text{Language Profile}_{i} \times \text{Trial type}_{i}) & \\
-\end{aligned}
-$$ {#eq-linear}
-
-where:
-
-- $i$ and $j$ index the participant and translation equivalent (TE)
-- $\beta_{0_k}$ is the fixed coefficient of the regression model for the intercept of threshold $k$
-- $u_{0_{i}}$ and $w_{0_{j}}$ are the by-participant and by-TE adjustments for $\beta_{0_{k}}$ (i.e., random intercepts), respectively
-- $\beta_{1-8}$ are the fixed coefficients of the regression model for the predictors of interest
-- $u_{1-8_{i}}$ and $w_{1-3_{j}}$ are the by-participant and by-TE adjustments for$\beta_{1-8}$ (i.e., random slopes), respectively
-
-$$
-\begin{aligned}
-\\
-\textbf{Prior:} \\
-\beta_{0_{k}} &\sim \mathcal{N}(-0.25, 0.1) & [\mbox{Intercept/response category threshold}] \\
-\beta_{1} &\sim \mathcal{N}(1, 0.1) & [\mbox{Age population-level coefficient}]\\
-\beta_{2-8} &\sim \mathcal{N}(0, 1) & [\mbox{Rest of population-level coefficients}] \\
-u_{0-8_{i}} &\sim \mathcal{N}(0, \sigma_{u_{0-8_{i}}}) & [\mbox{Participant-level coefficient variability}] \\
-w_{0-3_{j}} &\sim \mathcal{N}(0, \sigma_{w_{0-3_{j}}}) & [\mbox{TE-level coefficient variability}] \\\\
-&&\mbox{[Participant-level coefficient variability]} \\ \\
-\Bigg(\begin{smallmatrix}
-u_{k_{0}} \\ 
-u_{1_{i}} \\ 
-\vdots \\ 
-u_{8_{i}} 
-\end{smallmatrix}\Bigg) &\sim \mathcal{N} 
-\Bigg(\Bigg(\begin{smallmatrix}0 \\
-0 \\ 
-\vdots \\
-0\end{smallmatrix}\Bigg), \Sigma_{u}\Bigg) \\
-\Sigma_{u} &= \Bigg(\begin{smallmatrix} \\
-\rho_{u_{0}} & \rho_{u_{0}} \sigma_{u_{0_{k}}} \sigma_{u_{1}} & \dots & \rho_{u_{0}} \sigma_{u_{0}} \sigma_{w_{8}}\\ 
-\rho_{u_{1}} \sigma_{u_{1}} \sigma_{u_{0}} & \rho_{u_{1}} & \dots & \rho_{u_{1}} \sigma_{u_{1}} \sigma_{u_{8}}\\ 
-\vdots & \vdots & \vdots & \vdots \\
-\rho_{8} \sigma_{u_{8}} \sigma_{u_{0_{k}}} & \dots & \dots & \rho_{u_{8}} \end{smallmatrix}\Bigg) \\
-\sigma_{u_{0-8}} &\sim \mathcal{N_{+}}(1, 0.1) \\
-\rho_{u} &\sim LKJcorr(2) \\
-\\
-&&\mbox{[TE-level coefficient variability]} \\ \\
-\Bigg(\begin{smallmatrix}
-w_{k_{0}}\\ 
-w_{1_{j}} \\ 
-\vdots \\ 
-w_{3_{j}} 
-\end{smallmatrix}\Bigg) &\sim \mathcal{N} \Bigg(\Bigg(\begin{smallmatrix}
-0\\ 
-0 \\ 
-\vdots \\
-0 
-\end{smallmatrix}\Bigg), \Sigma_{w}\Bigg) \\
-\Sigma_{w} &= \Bigg(\begin{smallmatrix} \\
-\rho_{w_{0}} & \rho_{w_{0}} \sigma_{w_{0_{k}}} \sigma_{w_{1}} & \dots & \rho_{w_{0}} \sigma_{w_{0}} \sigma_{w_{3}}\\ 
-\rho_{w_{1}} \sigma_{w_{1}} \sigma_{w_{0}} & \rho_{w_{1}} & \dots & \rho_{w_{1}} \sigma_{w_{1}} \sigma_{w_{3}}\\ 
-\vdots & \vdots & \vdots & \vdots \\
-\rho_{3} \sigma_{w_{3}} \sigma_{w_{0_{k}}} & \dots & \dots & \rho_{w_{3}} \end{smallmatrix}\Bigg) \\
-\sigma_{w_{0-3}} &\sim \mathcal{N_{+}}(1, 0.1) \\
-\rho_{w_{0-3}} &\sim LKJcorr(2)
-\end{aligned}
-$$ {#eq-prior}
-
-```{r}
-#| label: fig-prior-epred
-#| fig-width: 9
-#| fig-height: 6
-nd <- tibble(time_bin = seq(0, 20, 0.1)) %>% 
-	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)
-
-m <- add_epred_draws(nd, fit_prior, ndraws = 50, re_formula = NA) %>% 
-	mutate(.epred = plogis(.epred))
-
-ggplot(m, aes(time_bin, .epred)) +
-	geom_hline(yintercept = 0.5, colour = "grey", size = 1) +
-	geom_line(aes(group = .draw), colour = clrs[4], size = 1, alpha = 0.5) +
-	labs(x = "Time (ms)",
-		 y = "Proportion of target looking time") +
-	scale_y_continuous(labels = percent) +
-	scale_x_continuous(labels = function(x) format(x*100, big.mark = ","))
-```
-
 # Results
 
-## Attrition
-
-::: {.tabset-panel}
-
-### By participants
-
-```{r}
-#| label: fig-attrition-participants
-#| fig-height: 4
-n_text <- participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is_imputed ~ "Valid (observed CDI)",
-			valid_participant & is_imputed ~ "Valid (imputed CDI)",
-			!valid_participant ~ "Excluded"
-		)
-	) %>% 
-	filter(valid_status != "Excluded") %>% 
-	count(lp, age_group) %>% 
-	mutate(n_label = paste0(n, " valid"),
-		   valid_status = "Valid (observed CDI)")
-
-participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(valid_status = case_when(
-		valid_participant & !is_imputed ~ "valid_cdi_observed",
-		valid_participant & is_imputed ~ "valid_cdi_imputed",
-		!valid_participant ~ "excluded")) %>% 
-	add_count(age_group, lp, name = "n_total") %>% 
-	count(age_group, lp, n_total, valid_status) %>% 
-	pivot_wider(names_from = valid_status, values_from = n, values_fill = 0) %>% 
-	relocate(age_group, lp, n_total, valid_cdi_observed, valid_cdi_imputed, excluded) %>% 
-	mutate(across(matches("valid_|excluded"), ~./n_total, .names = "{.col}_prop")) %>% 
-	gt(rowname_col = "lp", groupname_col = "age_group") %>% 
-	fmt_percent(matches("prop"), decimals = 1) %>% 
-	cols_merge_n_pct(col_n = valid_cdi_observed, col_pct = valid_cdi_observed_prop) %>% 
-	cols_merge_n_pct(col_n = valid_cdi_imputed, col_pct = valid_cdi_imputed_prop) %>% 
-	cols_merge_n_pct(col_n = excluded, col_pct = excluded_prop) %>% 
-	tab_spanner("Included participants", matches("valid")) %>% 
-	tab_spanner("Excluded participants", matches("excluded")) %>% 
-	cols_label(n_total = "N",
-			   valid_cdi_observed = "Collected CDI",
-			   valid_cdi_imputed = "Missing CDI",
-			   excluded = "") %>% 
-	summary_rows(groups = TRUE, columns = where(is.integer), 
-				 fns = list("N" = ~sum(.)),
-				 formatter = fmt_number,
-				 decimals = 0) %>% 
-	grand_summary_rows(columns = where(is.integer), 
-					   fns = list("N" = ~sum(.)),
-					   formatter = fmt_number,
-					   decimals = 0) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary()))
-```
-
-### By stimuli properties
-
-```{r}
-#| label: tbl-attrition-predictors
-
-attrition %>% 
-	left_join(distinct(participants, id, age_group, test_language, list, version, list)) %>% 
-	left_join(distinct(stimuli, test_language, version, list, trial_id, trial_type,
-					   freq_target, freq_prime, familiarity_prime, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status != "Valid",  "Excluded", valid_status)) %>% 
-	drop_na() %>% 
-	group_by(trial_type, valid_status, age_group) %>% 
-	summarise(n = n(),
-			  across(matches("freq_|familiarity_"), lst(mean, sd)),
-			  .groups = "drop") %>% 
-	pivot_wider(names_from = valid_status,
-				values_from = c(n, matches("freq_|familiarity_")),
-				values_fill = 0) %>%
-	clean_names() %>% 
-	relocate(age_group, trial_type, n_valid, n_excluded, 
-			 matches("_valid")) %>%
-
-	gt(rowname_col = "trial_type", groupname_col = "age_group") %>% 
-	fmt_number(matches("n_"), decimals = 0) %>% 
-	fmt_number(matches("freq_"), decimals = 1) %>% 
-	fmt_number(matches("familiarity"), scale_by = 100, decimals = 1) %>%
-
-	tab_spanner("N", c(n_valid, n_excluded)) %>%
-
-	tab_spanner("Prime", id = 1, c(freq_prime_mean_valid, freq_prime_mean_excluded)) %>%
-	tab_spanner("Target", id = 2, c(freq_target_mean_valid, freq_target_mean_excluded)) %>% 
-	tab_spanner("Prime", id = 3, c(familiarity_prime_mean_valid, familiarity_prime_mean_excluded)) %>% 
-	tab_spanner("Target", id = 4, c(familiarity_target_mean_valid, familiarity_target_mean_excluded)) %>%
-	tab_spanner("Frequency", starts_with("freq_")) %>% 
-	tab_spanner("Familiarity (%)", starts_with("familiarity_")) %>%
-
-	cols_merge_uncert(col_val = freq_prime_mean_valid, col_uncert = freq_prime_sd_valid) %>% 
-	cols_merge_uncert(col_val = freq_prime_mean_excluded, col_uncert = freq_prime_sd_excluded) %>% 
-	cols_merge_uncert(col_val = freq_target_mean_valid, col_uncert = freq_target_sd_valid) %>% 
-	cols_merge_uncert(col_val = freq_target_mean_excluded, col_uncert = freq_target_sd_excluded) %>% 
-	cols_merge_uncert(col_val = familiarity_prime_mean_valid, col_uncert = familiarity_prime_sd_valid) %>% 
-	cols_merge_uncert(col_val = familiarity_prime_mean_excluded, col_uncert = familiarity_prime_sd_excluded) %>% 
-	cols_merge_uncert(col_val = familiarity_target_mean_valid, col_uncert = familiarity_target_sd_valid) %>%
-	cols_merge_uncert(col_val = familiarity_target_mean_excluded, col_uncert = familiarity_target_sd_excluded) %>%
-
-	cols_label(n_excluded = "Exc.",
-			   n_valid = "Inc.",
-			   freq_prime_mean_valid = "Inc.",
-			   freq_prime_mean_excluded = "Exc.",
-			   freq_target_mean_valid = "Inc.",
-			   freq_target_mean_excluded = "Exc.",
-			   familiarity_prime_mean_valid = "Inc.",
-			   familiarity_prime_mean_excluded = "Exc.",
-			   familiarity_target_mean_valid = "Inc.",
-			   familiarity_target_mean_excluded = "Exc.") %>% 
-	summary_rows(groups = TRUE,
-				 columns = matches("freq_") ,
-				 fns = list("Mean" = ~mean(.)), 
-				 formatter = fmt_number,
-				 decimals = 1) %>% 
-	summary_rows(groups = TRUE,
-				 columns = matches("familiarity_"), 
-				 fns = list("Mean" = ~mean(.)),
-				 formatter = fmt_number,
-				 scale_by = 100,
-				 decimals = 1) %>% 
-	grand_summary_rows(columns = c(n_valid, n_excluded),
-					   fns = list("N" = ~sum(.)),
-					   formatter = fmt_number,
-					   decimals = 0) %>% 
-	grand_summary_rows(columns = matches("familiarity_"),
-					   fns = list("Mean" = ~mean(.)),
-					   formatter = fmt_number,
-					   scale_by = 100,
-					   decimals = 1) %>% 
-	grand_summary_rows(columns = matches("freq_"),
-					   fns = list("Mean" = ~mean(.)),
-					   formatter = fmt_number,
-					   decimals = 1) %>% 
-	tab_style(cell_text(align = "center"),
-			  cells_column_labels()) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary())) %>% 
-	tab_footnote("Included trials.", cells_column_labels(matches("_valid"))) %>% 
-	tab_footnote("Excluded trials.", cells_column_labels(matches("_excluded")))
-```
-
-:::
-
-## Descriptive statistics
-
-### Aggregated target looking
-
-```{r}
-#| label: fig-descriptives-aggregated
-#| fig-width: 10
-#| fig-height: 6
-df %>% 
-	group_by(id, lp, trial_type, age_group) %>%
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_line(aes(group = id), alpha = 0.25) +
-	stat_slab(side = "right", scale = 0.5) +
-	geom_boxplot(width = 0.1, size = 0.75, fill = "white", colour = "black", outlier.colour = NA) +
-	labs(x = "Trial type", y = "Proportion of target looking", colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
-	theme(legend.position = "none")
-```
-
-### Time-course target looking
-
-```{r}
-#| label: fig-descriptives-time-course
-#| fig-width: 12
-#| fig-height: 8
-df %>% 
-	group_by(id, time_bin, lp, trial_type, age_group) %>%
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	ggplot(aes(time_bin, prop, colour = trial_type, fill = trial_type, shape = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
-	stat_summary(fun = mean, geom = "point", size = 2) +
-	stat_summary(fun = mean, geom = "line", size = 0.75) +
-	labs(x = "Time bin (100 ms)", y = "Proportion of target looking",
-		 colour = "Trial type", fill = "Trial type", shape = "Trial type") +
-	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
-	scale_x_continuous(labels = function(x) format(x*100, big.mark = ",")) +
-	theme(legend.position = "top",
-		  legend.title = element_blank(),
-		  panel.grid = element_line(linetype = "dotted", colour = "grey"),
-		  panel.grid.major = element_line(colour = "grey", linetype = "dotted"))
-```
-
-## Model outputs
-
-### Model comparison
-
-```{r}
-#| label: tab-model-comparison
-loos %>% 
-	as_tibble(.name_repair = make_clean_names) %>% 
-	rownames_to_column("model") %>% 
-	relocate(
-		model, 
-		matches("diff"),
-		matches("elpd_loo"),
-		matches("p_loo"), 
-		matches("looic")
-	) %>%
-	mutate(across(everything(), as.numeric),
-		   model = attr(loos, "dimnames")[[1]]) %>% 
-	select(-matches("subsampling")) %>% 
-	gt(rowname_col = "model") %>%
-	fmt_number(is.numeric, decimals = 1) %>% 
-	cols_merge_uncert(col_val = elpd_diff, col_uncert = se_diff) %>% 
-	cols_merge_uncert(col_val = elpd_loo, col_uncert = se_elpd_loo) %>% 
-	cols_merge_uncert(col_val = p_loo, col_uncert = se_p_loo) %>% 
-	cols_merge_uncert(col_val = looic, col_uncert = se_looic) %>% 
-	cols_label(model = "Model",
-			   elpd_loo = md("*ELPD*"),
-			   p_loo = md("*p*"),
-			   looic = md("*LOO-IC*"),
-			   elpd_diff = md("Difference")) %>% 
-	tab_source_note(md("Pareto-*k* estimates of all models were acceptable (*k* < 0.5)")) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  cells_column_labels()) %>% 
-	tab_style(cell_fill(color = "grey", alpha = 0.5),
-			  cells_body(matches("diff"))) %>% 
-	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-			  cells_body(everything(), 1))
-```
-
-### Fixed effects
-
-::: {.panel-tabset}
-
-#### Table
-
-```{r}
-#| label: tbl-fixed-effects
-#| tbl-cap: "Summary of the posterior distribution of the Growth Curve Analysis model.
-We report the median and 95% highest density interval (*HDI*) of each fixed coefficient.
-The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability.
-Values are in *logit* scale.
-Coefficients whose 95% HDI excludes zero are highlighted in red.
-Coefficients on the intercept indicate changes in overal proportion of target looking, coefficients in the linear term indicate changes in the overall slope of target looking growth across time, coefficients in the quadratic and cubic terms reflect the steepness of the rise and fall or of the rise, fall and rise, respectivey,  of the curve."
-post_draws <- gather_draws(fit_3, `b_.*`, regex = TRUE)
-
-str_repl <- c(
-	"b_Intercept" = "Base",
-	"b_ot1" = "Base",
-	"b_ot2" = "Base",
-	"b_ot3" = "Base",
-	"b_age_group21_25" = "Age [21-25]",
-	"b_age_group25_30" = "Age [25-30]",
-	"b_lpmon_bil" = "Group",
-	"b_trial_typerelated_unrelated" = "Prime (R)",
-	"b_trial_typecognate_noncognate" = "Prime (C)",
-
-	"b_age_group21_25:lpmon_bil" = "Age [21-25] × Group",
-	"b_age_group25_30:lpmon_bil" = "Age [25-30] × Group",
-	"b_age_group21_25:trial_typerelated_unrelated" = "Age [21-25] × Prime (R)",
-	"b_age_group21_25:trial_typecognate_noncognate" = "Age [21-25] × Prime (C)",
-	"b_age_group25_30:trial_typerelated_unrelated" = "Age [25-30] × Prime (R)",
-	"b_age_group25_30:trial_typecognate_noncognate" = "Age [25-30] × Prime (C)",
-	"b_lpmon_bil:trial_typerelated_unrelated" = "Group × Prime (R)",
-	"b_lpmon_bil:trial_typecognate_noncognate" = "Group × Prime (C)",
-
-	"b_age_group21_25:lpmon_bil:trial_typerelated_unrelated" = "Age [21-25] × Group × Prime (R)",
-	"b_age_group21_25:lpmon_bil:trial_typecognate_noncognate" = "Age [21-25] × Group × Prime (C)",
-	"b_age_group25_30:lpmon_bil:trial_typerelated_unrelated" = "Age [25-30] × Group × Prime (R)",
-	"b_age_group25_30:lpmon_bil:trial_typecognate_noncognate" = "Age [25-30] × Group × Prime (C)"
-)
-
-post_draws %>% 
-	median_hdi() %>%
-	mutate(poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
-							str_detect(.variable, "ot2") ~ "Quadratic",
-							str_detect(.variable, "ot3") ~ "Cubic",
-							TRUE ~ "Intercept"),
-		   .variable_name = case_when(.variable %in% paste0("b_ot", 1:3) ~ .variable,
-		   						   TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) %>% 
-		   	factor(levels = names(str_repl),
-		   		   label = str_repl,
-		   		   ordered = TRUE),
-		   type = case_when(.variable_name %in% str_repl[1:9] ~ "Main effect",
-		   				 .variable_name %in% str_repl[10:17] ~ "Two-way interactions",
-		   				 .variable_name %in% str_repl[18:length(str_repl)] ~ "Three-way interactions")) %>%
-	select(.variable_name, type, poly, .value:.upper) %>%
-	arrange(.variable_name) %>% 
-	pivot_wider(names_from = poly, 
-				values_from = is.numeric,
-				id_cols = c(.variable_name, type),
-				values_fill = NA,
-				names_repair = make_clean_names) %>% 
-	relocate(variable_name, starts_with("value_")) %>% 
-	gt(rowname_col = "variable_name",
-	   groupname_col = "type") %>% 
-	fmt_number(is.numeric) %>%
-	tab_spanner("Intercept", matches("intercept")) %>% 
-	sub_missing(everything(), rows = everything(), missing_text = "--") %>% 
-	tab_spanner("Linear", matches("linear")) %>% 
-	tab_spanner("Quadratic", matches("quadratic")) %>% 
-	tab_spanner("Cubic", matches("cubic")) %>% 
-	cols_merge(c(lower_intercept, upper_intercept), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c(lower_linear, upper_linear), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c(lower_quadratic, upper_quadratic), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c(lower_cubic, upper_cubic), pattern = "[{1}, {2}]") %>%
-	cols_label(value_intercept = md("b"),
-			   lower_intercept = md("95% *HDI*"),
-			   value_linear = md("b"),
-			   lower_linear = md("95% *HDI*"),
-			   value_quadratic = md("b"),
-			   lower_quadratic = md("95% *HDI*"),
-			   value_cubic = md("b"),
-			   lower_cubic = md("95% *HDI*")) %>% 
-	tab_style(cell_text(align = "left", indent = px(10)),
-			  cells_stub()) %>% 
-	tab_style(cell_fill(color = "grey90"),
-			  cells_body(matches("value"))) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  cells_column_spanners()) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  cells_row_groups()) %>% 
-	tab_style(cell_text(style = "oblique"),
-			  cells_column_labels(columns = matches("value"))) %>% 
-	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-			  cells_body(columns = value_intercept, 
-			  		   rows = (upper_intercept < 0) | (lower_intercept > 0))) %>% 
-	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-			  cells_body(columns = value_linear, 
-			  		   rows = (upper_linear < 0) | (lower_linear > 0))) %>%
-	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-			  cells_body(columns = value_quadratic, 
-			  		   rows = (upper_quadratic < 0) | (lower_quadratic > 0))) %>%
-	tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-			  cells_body(columns = value_cubic, 
-			  		   rows = (upper_cubic < 0) | (lower_cubic > 0))) %>% 
-	tab_style(cell_text(size = "small"), 
-			  list(cells_body(), cells_stub())) %>% 
-	tab_footnote("Sum-coded contrast between 21 and 25 month old participants.",
-				 cells_stub(rows = 2)) %>% 
-	tab_footnote("Sum-coded contrast between 25 and 30 month old participants.",
-				 cells_stub(rows = 3)) %>% 
-	tab_footnote("Sum-coded contrast between monolingual and bilingual participants.",
-				 cells_stub(rows = 4)) %>% 
-	tab_footnote("Sum-coded contrast between related (cognate and non-cognate) and unrelated trials",
-				 cells_stub(rows = 5)) %>% 
-	tab_footnote("Sum-coded contrast between cognate and non-cognate trials",
-				 cells_stub(rows = 6))
-```
-
-#### Plot
-
-```{r}
-#| label: fig-fixed-effects
-#| fig-height: 7
-#| fig-width: 13
-#| fig-cap: "Summary of the posterior of the Growth Curve Analysis model.
-We report the median and 95% highest density interval (*HDI*) of each fixed coefficient.
-The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability.
-Values are in *logit* scale.
-Coefficients whose 95% HDI excludes zero are highlighted in red.
-Summary of the posterior distribution of the Growth Curve Analysis model.
-We report the median and 95% highest density interval (*HDI*) of each fixed coefficient.
-The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability.
-Values are in *logit* scale.
-Coefficients whose 95% HDI excludes zero are highlighted in red.
-Coefficients on the intercept indicate changes in overal proportion of target looking, coefficients in the linear term indicate changes in the overall slope of target looking growth across time, coefficients in the quadratic and cubic terms reflect the steepness of the rise and fall or of the rise, fall and rise, respectivey,  of the curve."
-post_draws %>% 
-	median_hdi() %>%
-	mutate(poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
-							str_detect(.variable, "ot2") ~ "Quadratic",
-							str_detect(.variable, "ot3") ~ "Cubic",
-							TRUE ~ "Intercept") %>% 
-		   	factor(levels = c("Intercept", "Linear", "Quadratic", "Cubic")),
-		   .variable_name = case_when(.variable %in% paste0("b_ot", 1:3) ~ .variable,
-		   						   TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) %>% 
-		   	factor(levels = names(str_repl),
-		   		   label = str_repl,
-		   		   ordered = TRUE),
-		   type = case_when(.variable_name %in% str_repl[1:9] ~ "Main effect",
-		   				 .variable_name %in% str_repl[10:17] ~ "Two-way interactions",
-		   				 .variable_name %in% str_repl[18:length(str_repl)] ~ "Three-way interactions"),
-		   excludes_zero = ifelse((.lower > 0) | (.upper < 0), "Yes", "No")) %>%
-	select(.variable_name, type, poly, .value:.upper, excludes_zero) %>%
-	arrange(.variable_name) %>% 
-	ggplot(aes(x = .value, y = fct_rev(.variable_name), 
-			   colour = excludes_zero,
-			   xmin = .lower, xmax = .upper)) +
-	facet_wrap(~poly, scales = "free_x", nrow = 1) +
-	geom_vline(xintercept = 0, colour = "grey", size = 1) +
-	geom_errorbar(width = 0.2, size = 0.75) +
-	geom_point(size = 3) +
-	labs(x = "Estimate (Logit scale)", 
-		 y = "Variable", 
-		 fill = "CrI", 
-		 alpha = "CrI",
-		 colour = "Interval excludes zero?") +
-	theme(legend.position = "top",
-		  axis.title.y = element_blank(),
-		  axis.text.y = element_text(face = "plain", hjust = 1),
-		  panel.border = element_rect(colour = "black", fill = NA))
-```
-
-:::
-
-### Marginal means
-
-```{r}
-#| label: fig-posterior-epred
-#| fig-width: 12
-#| fig-height: 8
-nd <- expand_grid(time_bin = seq(0, 20, 0.1),
-				  age_group = levels(fit_1$data$age_group),
-				  lp = levels(fit_2$data$lp),
-				  trial_type = levels(fit_4$data$trial_type)) %>% 
-	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)
-
-m <- add_epred_draws(nd, fit_3, ndraws = 25, re_formula = NA) %>% 
-	mutate(.epred = plogis(.epred))
-
-ptlt_means <- df %>% 
-	group_by(id, age_group, lp, trial_type, time_bin) %>% 
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	group_by(age_group, lp, trial_type, time_bin) %>% 
-	summarise(prop = mean(prop), .groups = "drop")
-
-m %>% 
-	ggplot(aes(time_bin, .epred, colour = trial_type, shape = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_line(aes(group = interaction(.draw, trial_type)), alpha = 0.15, size = 0.75) +
-	# stat_summary(fun = median, geom = "line", size = 1) +
-	geom_point(data = ptlt_means, aes(y = prop)) +
-	labs(x = "Time (ms)",
-		 y = "Proportion of target looking time",
-		 colour = "Prime",
-		 fill = "Prime",
-		 shape = "Prime",
-		 linetype = "Trial type") +
-	scale_x_continuous(labels = function(x) format(x*100, big.mark = ",")) +
-	scale_y_continuous(labels = percent) +
-	theme(legend.position = "top",
-		  panel.grid = element_line(linetype = "dotted", colour = "grey"),
-		  panel.grid.minor = element_blank(),
-		  legend.title = element_blank())
-```
-
-# Appendix
-
-## Longitudinal participants
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r}
-#| label: fig-participants-longitudinal
-#| fig-height: 10
-#| fig-width: 4
-participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	filter(valid_participant) %>% 
-	add_count(id, lp, name = "n_total") %>% 
-	count(id, age_group, test_language, lp, n_total) %>% 
-	pivot_wider(id_cols = c(id, lp, test_language, n_total),
-				names_from = age_group,
-				values_from = n,
-				values_fill = 0) %>% 
-	pivot_longer(5:7,
-				 names_to = "age_group",
-				 values_to = "n") %>% 
-	mutate(id_reordered = reorder_within(id, by = n_total, within = list(test_language, lp))) %>% 
-	ggplot(aes(age_group, id_reordered, fill = as.factor(n))) + 
-	facet_wrap(test_language~lp, 
-			   scales = "free_y",
-			   labeller = label_wrap_gen(multi_line = FALSE)) +
-	geom_tile(colour = "white") +
-	labs(x = "Age (months)", 
-		 y = "Exposure to 2nd language", 
-		 fill = "Lang. Profile") +
-	scale_fill_manual(values = c("white", clrs[4], "white")) +
-	theme(legend.position = "none",
-		  legend.title = element_blank(),
-		  panel.grid = element_blank(),
-		  axis.text.x = element_text(size = 6),
-		  axis.title.y = element_blank(),
-		  axis.title.x = element_text(size = 6),
-		  axis.text.y = element_blank(),
-		  axis.ticks.y = element_blank(),
-		  strip.text = element_text(size = 6))
-
-```
-
-## Additional stimuli properties
-
-### Animacy
-
-```{r}
-#| label: fig-stimuli-animacy
-#| fig-height: 6
-animacy <- stimuli %>%
-	distinct(test_language, 
-			 target, 
-			 prime, 
-			 .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), 
-				 names_to = "role",
-				 values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(test_language,  trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	# filter(role=="Prime") %>% 
-	ggplot() +
-	aes(x = trial_type, 
-		y = n, 
-		fill = is_animate,
-		colour = is_animate) + 
-	facet_grid(test_language~role) +
-	geom_col(position = position_fill(), colour = "white", size = 0.75) +
-	geom_hline(yintercept = 0.5,  size = 1, colour = "grey") +
-	labs(title = "Prime", 
-		 x = "Trial type", 
-		 y = "# trials",
-		 colour = "Animacy", 
-		 fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(legend.position = "top",
-		  legend.title = element_blank(),
-		  panel.grid = element_blank(),
-		  axis.title.y = element_blank(),
-		  axis.text = element_text(size = 7),
-		  axis.text.y = element_text(hjust = 1),
-		  strip.text = element_text(size = 11))
-```
-
-### Semantic category
-
-::: {.panel-tabset}
-
-#### Prime
-
-```{r}
-#| label: fig-stimuli-category-prime
-#| fig-height: 5
-#| fig-width: 10
-stimuli %>% 
-	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
-	drop_na(trial_type, semantic_category_prime) %>% 
-	count(trial_type, test_language, semantic_category_prime, name = "sum") %>% 
-	right_join(expand(., trial_type,  test_language,  semantic_category_prime)) %>%
-	replace_na(list(sum = 0)) %>% 
-	group_by(trial_type, test_language) %>% 
-	mutate(n =  sum(sum), prop = sum/n) %>% 
-	ungroup() %>% 
-	ggplot() +
-	aes(x = prop,
-		y = reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
-		fill = test_language,
-		order = prop) + 
-	facet_wrap(test_language~trial_type,
-			   scales = "free_y",
-			   labeller = label_wrap_gen(multi_line = FALSE)) +
-	geom_col(colour = "white",
-			 position = position_dodge(),
-			 width = 1) +
-	labs(x = "% of trials",
-		 y = "Trial type",
-		 colour = "Trial type",
-		 fill = "Trial type") +
-	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
-	scale_y_reordered() +
-	theme(legend.position = "none",
-		  legend.title = element_blank(),
-		  axis.text.y = element_text(size = 9, hjust = 1),
-		  axis.text.x = element_text(size = 8, hjust = 1),
-		  axis.title.y = element_blank(),
-		  axis.ticks.y = element_blank(),
-		  plot.caption = element_text(size = 10, hjust = 0),
-		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-		  strip.text = element_text(size = 10))
-```
-
-#### Target
-
-```{r}
-#| label: fig-stimuli-category-target
-#| fig-height: 5
-#| fig-width: 10
-stimuli %>% 
-	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
-	drop_na(trial_type, semantic_category_target) %>% 
-	count(trial_type, test_language, semantic_category_target, name = "sum") %>% 
-	right_join(expand(., trial_type,  test_language,  semantic_category_target)) %>%
-	replace_na(list(sum = 0)) %>% 
-	group_by(trial_type, test_language) %>% 
-	mutate(n =  sum(sum), prop = sum/n) %>% 
-	ungroup() %>% 
-	ggplot() +
-	aes(x = prop,
-		y = reorder_within(semantic_category_target, desc(prop), list(trial_type, test_language)),
-		fill = test_language,
-		order = prop) + 
-	facet_wrap(test_language~trial_type,
-			   scales = "free_y",
-			   labeller = label_wrap_gen(multi_line = FALSE)) +
-	geom_col(colour = "white",
-			 position = position_dodge(),
-			 width = 1) +
-	labs(x = "% of trials",
-		 y = "Trial type",
-		 colour = "Trial type",
-		 fill = "Trial type") +
-	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
-	scale_y_reordered() +
-	theme(legend.position = "none",
-		  legend.title = element_blank(),
-		  axis.text.y = element_text(size = 9, hjust = 1),
-		  axis.text.x = element_text(size = 8, hjust = 1),
-		  axis.title.y = element_blank(),
-		  axis.ticks.y = element_blank(),
-		  plot.caption = element_text(size = 10, hjust = 0),
-		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-		  strip.text = element_text(size = 10))
-```
-
-:::
+# Discussion

### 2023-05-03 R/participants.R

@@ -1,0 +1,27 @@
+# get participant information
+get_participants <- function(){
+	
+	suppressMessages({
+		# participants
+		
+		sheet_id <- "1JkhN4iBh3bi6PSReGGk9jSrVgDhZNOUmve6vNS2eEqE"
+		participants <- range_read(ss = sheet_id, sheet = "barcelona", na = "") %>%
+			mutate(
+				across(where(is.logical), ~ifelse(is.na(.), FALSE, .)),
+				age = time_length(interval(date_birth, date_test), unit = "months"),
+				age_group = factor(paste0(age_group, " months"),
+								   levels = paste0(c(21, 25, 30), " months")),
+				date_test = as_date(date_test),
+				lp = factor(lp, levels = c("Monolingual", "Bilingual")),
+				test_language = factor(test_language, levels = c("Catalan", "Spanish")),
+				list = as.integer(list)
+			) %>% 
+			filter(!pilot) %>% # remove pilot participants
+			drop_na(id, filename) %>% # remove participants with no gaze data
+			select(id = id_db, date_test, lp, doe_catalan, doe_spanish, doe_others,
+				   age_group, age, test_language, list, version, filename)
+	})
+	
+	return(participants)
+	
+}

### 2023-05-03 R/stimuli.R

@@ -1,0 +1,162 @@
+# get familiarity
+get_familiarity <- function(
+		bvq_data,
+		tokens, # words to retrieve familiarity for
+		type = "understands", # understands or produces
+		update = TRUE, # should vocabulary data be updated
+		age = c(17, 19), # age range for familiarity norms (min-max)
+		.width = 0.95 # confidence level of the estimates
+){
+	
+	familiarity <- bvq_norms(bvq_data$participants,
+							 bvq_data$responses, 
+							 type = type,
+							 age = age,
+							 .width = .width) %>% 
+		filter(item_dominance=="L1") %>% 
+		summarise(across(c(.sum, .n), sum), .by = "item") 
+	
+	familiarity <- familiarity %>% 
+		mutate(familiarity = prop_adj(.sum, .n),
+			   familiarity_se = prop_adj_se(.sum, .n)) %>% 
+		select(item, starts_with("familiarity")) %>% 
+		rename(word = item) %>% 
+		mutate(
+			test_language = case_when(
+				grepl("eng_", word) ~ "English",
+				grepl("cat_", word) ~ "Catalan",
+				grepl("spa_", word) ~ "Spanish"
+			)
+		) %>% 
+		relocate(test_language, .before = word)
+	
+	return(familiarity)
+}
+
+
+# get frequencies from CHILDES
+get_childes_corpora <- function(token, languages = c("cat", "spa")) {
+	
+	if (file.exists("data/stimuli/childes.csv")){
+		childes <- read_csv_arrow("data/stimuli/childes.csv")
+		cli::cli_alert_success("Previous versions of childes loaded")
+	} else {
+		
+		# absolute frequency (raw counts)
+		childes <- get_tokens(role = "target_child", 
+							  token =  token,
+							  language = languages) %>%
+			mutate(gloss = str_to_lower(gloss)) %>%
+			filter(str_detect(language, paste(languages, collapse = "|"))) %>%
+			count(gloss, language) %>%
+			mutate(language = str_split(language, " ")) %>%
+			unnest(language) %>%
+			group_by(language, gloss) %>%
+			summarise(freq_counts = sum(n), .groups = "drop") %>%
+			filter(freq_counts > 0)
+		
+		write_csv_arrow(childes, "data/stimuli/childes.csv")
+		
+	}
+	
+	return(childes)
+}
+
+# compute lexical frequencies from CHILDES corpora ----
+# WARNING: especial characters are not being handled very well
+get_frequency_childes <- function(childes,
[…]

### 2023-05-03 R/vocabulary.R

@@ -1,0 +1,52 @@
+# vocabulary size
+get_vocabulary <- function(participants, # participants dataset (get_participants output)
+						   bvq_data
+){
+	suppressMessages({
+		
+		# vocabulary sizes BVQ database and Cognate Priming
+		
+		participants_tmp <- select(participants, id, age_group, lp)
+		
+		to_impute <- bvq_data$vocabulary %>%
+			right_join(select(participants_tmp, id, age_group, lp),
+					   by = join_by(id, age_group)) |> 
+			rowwise() |> 
+			mutate(is_imputed = any(is.na(c_across(total_prop:te_prop)))) %>% 
+			ungroup() |> 
+			relocate(id, age_group, is_imputed)
+		
+		impute <- function(x) {
+			# index of missing observations to impute
+			x <- select(x, id, lp, age_group, ends_with("_prop"))
+			impute_index <- is.na(x)
+			impute_index[, 1:3] <- FALSE
+			
+			mice(x, 
+				 m = 5,
+				 where = impute_index,
+				 method = "pmm", 
+				 seed = 888) %>% 
+				complete() %>% 
+				as_tibble()
+		}
+		
+	# multiple imputation
+		imputed <- to_impute %>%
+			filter(age_group != "Other") %>% 
+			impute()
+		
+		# merge both datasets ----
+		vocabulary <- left_join(participants_tmp, imputed,
+								by = join_by(id, age_group, lp)) %>% 
+			left_join(select(to_impute, id, age_group, is_imputed),
+					  by = join_by(id, age_group)) |> 
+			mutate(age_group = factor(age_group,
+									  levels = paste0(c(21, 25, 30), " months")),
+				   lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+	})
+	
+	return(vocabulary)
+}
+
+

### 2023-05-03 tests/testthat/test-participants.R

@@ -4,7 +4,6 @@ test_participants <- function(participants){
 		expect_equal(
 			colnames(participants),
 			c("id",
-			  "id_db",
 			  "date_test",
 			  "lp",
 			  "doe_catalan",
@@ -20,7 +19,6 @@ test_participants <- function(participants){
 	
 	test_that("participants variables are the right types", {
 		expect_type(participants$id, "character")
-		expect_type(participants$id_db, "character")
 		expect_equal(class(participants$date_test), "Date")
 		expect_type(participants$lp, "integer")
 		expect_type(participants$age_group, "integer")
@@ -33,7 +31,6 @@ test_participants <- function(participants){
 	
 	test_that("participants has no missing data", {
 		expect_false(any(is.na(participants$id)))
-		expect_false(any(is.na(participants$id_db)))
 		expect_false(any(is.na(participants$date_test)))
 		expect_false(any(is.na(participants$lp)))
 		expect_false(any(is.na(participants$age_group)))

### 2023-05-03 tests/testthat/test-vocabulary.R

@@ -6,29 +6,38 @@ test_vocabulary <- function(vocabulary){
 			c("id",
 			  "age_group",
 			  "lp",
-			  "is_imputed",
-			  "vocab_size_total",
-			  "vocab_size_l1",
-			  "vocab_size_conceptual"))
+			  "total_prop",
+			  "l1_prop",
+			  "l2_prop",
+			  "concept_prop",
+			  "te_prop",
+			  "is_imputed"
+			))
 	})
 	
 	test_that("vocabulary has the variable classes", {
 		expect_type(vocabulary$id, "character")
 		expect_equal(class(vocabulary$age_group), "factor")
 		expect_equal(class(vocabulary$lp), "factor")
-		expect_type(vocabulary$vocab_size_total, "double")
-		expect_type(vocabulary$vocab_size_l1, "double")
-		expect_type(vocabulary$vocab_size_conceptual, "double")
+		expect_type(vocabulary$total_prop, "double")
+		expect_type(vocabulary$l1_prop, "double")
+		expect_type(vocabulary$l2_prop, "double")
+		expect_type(vocabulary$concept_prop, "double")
+		expect_type(vocabulary$te_prop, "double")
 		expect_type(vocabulary$is_imputed, "logical")
+		
+		
 	})
 	
 	test_that("vocabulary missing data is dealt with", {
 		expect_false(any(is.na(vocabulary$id)))
 		expect_false(any(is.na(vocabulary$age_group)))
 		expect_false(any(is.na(vocabulary$lp)))
-		expect_false(any(is.na(vocabulary$vocab_size_total)))
-		expect_false(any(is.na(vocabulary$vocab_size_l1)))
-		expect_false(any(is.na(vocabulary$vocab_size_conceptual)))
+		expect_false(any(is.na(vocabulary$total_prop)))
+		expect_false(any(is.na(vocabulary$l1_prop)))
+		expect_false(any(is.na(vocabulary$l2_prop)))
+		expect_false(any(is.na(vocabulary$concept_prop)))
+		expect_false(any(is.na(vocabulary$te_prop)))
 		expect_false(any(is.na(vocabulary$is_imputed)))
 		
 	})
@@ -36,10 +45,13 @@ test_vocabulary <- function(vocabulary){
 	test_that("stimuli variables have the right values", {
 		expect_equal(levels(vocabulary$age_group), paste0(c(21, 25, 30), " months"))
[…]

### 2023-05-05 manuscript/manuscript.qmd
Stop tracking data

@@
 # set ggplot theme and colour palette
-theme_set(theme_custom()) # set custom ggplot theme
+theme_set(
+	theme(
+		panel.background = element_rect(fill = "white", colour = NA),
+		panel.border = element_blank(),
+		panel.grid = element_blank(),
+		plot.background = element_rect(fill = "white", color = NA),
+		legend.key = element_rect(fill = "white", colour = NA),
+		text = element_text(colour = "black", size = 15),
+		axis.text.x = element_text(size = 9),
+		axis.text.y = element_text(size = 9),
+		axis.line = element_line(colour = "black", size = 0.75),
+		strip.text = element_text(size = 13, face = "bold"),
+		strip.background = element_rect(fill = "white", colour = NA)
+	)
+)
+
+# set custom ggplot theme
 clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")

### 2023-05-05 R/gaze.R

@@ -17,103 +17,130 @@ get_gaze_normalised <- function() {
 	# prepare for loop and pre-allocate list
 	i <- 1
 	n_files <- length(file_paths)
-	gaze_normalised <- vector(mode = "list", length = n_files)
-	names(gaze_normalised) <- file_names
+	db <- vector(mode = "list", length = n_files)
+	names(db) <- file_names
 	
 	names_dict <- get_name_dictionary() # name changes (see R/utils.R)
 	
 	# prepare progress bar
-	pb_text <- "{pb_spin} Reading file {pb_current}/{pb_total} [{pb_percent}]"
+	pb_text <- "{pb_spin} Reading {pb_current}/{pb_total} | {col_blue(pb_percent)}"
 	cli_progress_bar("Processing", total = n_files, format = pb_text)
 	
 	# read CSV and write Feather
 	for (i in 1:n_files){
 		
-		gaze_normalised[[i]] <- read_csv_arrow(file_paths[i], na = c("", "NaN", "NA", "<NA>")) %>% 
-			clean_names() %>% # rename all variables to snake case
-			rename_with(~str_replace_all(., names_dict$col_name_changes), everything()) %>% # fix some values from outdates files
-			mutate(phase =  str_replace_all(phase, names_dict$phase_name_changes),
-				   across(c(l_x, l_y, r_x, r_y), as.double),
-				   across(c(l_v, r_v), ~as.logical(as.integer(.))),
-				   x = ifelse(is.na(l_x) | !l_v, r_x, l_x) %>% 
-				   	ifelse(!between(., 0, 1), NA_real_, .),
-				   y = ifelse(is.na(l_y) | !l_v, r_y, l_y) %>% 
-				   	ifelse(!between(., 0, 1), NA_real_, .),
-				   valid_sample = (!is.na(x) & !is.na(y) & (l_v | r_v))) %>% 
-			select(one_of(names_dict$relevant_variables), -time)
+		db[[i]] <- x <- read_csv_arrow(file_paths[i], 
+									   na = c("", "NaN", "NA", "<NA>")) |> 
+			clean_names() |>  # rename all variables to snake case
+			rename_with(
+				\(x) str_replace_all(x, names_dict$col_name_changes),
+				everything()
+			) |> 
+			fix_timestamps() |> 
+			fix_validity() |> 
+			mutate(
+				phase =  str_replace_all(phase, names_dict$phase_name_changes),
+				across(c(l_v, r_v), \(x) as.logical(as.integer(x))),
[…]

### 2023-07-07 docs/index.qmd
Fix attrition

@@
     reference-location: margin
-    pdf: default
-    docx:
-        reference-doc: reference.docx
 fig-dpi: 1000
@@
 
-tar_load_everything() # load target objects
-
-# load packages
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(tibble)
-library(purrr)
-library(lubridate)
-library(ggplot2)
-library(gt)
-library(tidybayes)
-library(brms)
-library(polypoly)
-library(tidytext)
-library(janitor)
-library(forcats)
-library(scales)
-library(patchwork)
-library(bvq)
+# load target objects
+tar_load(c(participants, stimuli, 
+		   attrition_trials,
+		   attrition_participants,
+		   gaze_aoi,
+		   data_time, data_summary))
 
 # set ggplot theme and colour palette
-theme_set(theme_custom()) # set custom ggplot theme
+theme_set(theme_ggdist()) # set custom ggplot theme
+
 clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
@@
 # prepare data
-attrition <- attrition %>% 
+attrition_participants <- attrition_participants |> 
 	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
+		is_valid_gaze = is_valid_cognate & is_valid_noncognate & is_valid_unrelated,
 		valid_status = case_when(
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
+			!is_valid_gaze ~ "Invalid gaze",
+			!is_valid_participant ~ "Invalid participant",
 			TRUE ~ "Valid"
@@
 
-participants <- participants %>% 
-	left_join(distinct(attrition, id, age_group, valid_participant)) %>% 
-	drop_na(id) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
+participants <- participants |> 
+	left_join(distinct(attrition_participants, id, age_group,
+					   is_valid_participant),
+			  by = join_by(id, age_group)) |> 
+	drop_na(id) |>
+	left_join(vocabulary,
+			  by = join_by(id_db, lp, age_group)) |> 
+	mutate(l1_prop_c = scale(l1_prop)[, 1])
 
@@
 n_participants_total <- length(unique(participants$id))
-n_participants_sessions <- count(participants, id, name = "n_sessions") %>% 
-	count(n_sessions) %>% 
-	split(.$n_sessions)
+
+n_participants_sessions <- count(participants, id, name = "n_sessions") |> 
+	count(n_sessions) |> 
+	group_split(n_sessions)
+
 n_sessions_total <- count(participants)
-n_sessions_age_group <- participants %>% 
-	group_by(age_group) %>% 
+
+n_sessions_age_group <- participants |> 
 	summarise(across(age, lst(mean, sd, min, max)),
 			  n = n(),
-			  .groups = "drop") %>% 
-	mutate(across(age_mean:age_max, round, 2)) %>% 
-	split(f = .$age_group) %>% 
+			  .by = age_group) |> 
+	mutate(across(age_mean:age_max, round, 2)) |> 
+	group_split(age_group) |> 
 	set_names(c("age_21", "age_25", "age_30"))
-n_sessions_dominance <- count(participants, test_language) %>% 
-	split(f = .$test_language) %>% 
+
+n_sessions_dominance <- count(participants, test_language) |> 
+	group_split(test_language) |> 
 	set_names(c("catalan", "spanish"))
-n_sessions_dominance_age_group <- count(participants, age_group, test_language) %>% 
-	split(f = .$test_language) %>% 
-	set_names(c("catalan", "spanish")) %>% 
-	map(~split(., f = .$age_group) %>% 
+
+n_sessions_dominance_age_group <- count(participants, age_group, test_language) |> 
+	group_split(test_language) |> 
+	set_names(c("catalan", "spanish")) |> 
+	map(\(x) group_split(x, age_group) |> 
 			set_names(c("age_21", "age_25", "age_30")))
-n_sessions_lp <- participants %>% 
-	count(lp) %>% 
-	split(f = .$lp) %>% 
+n_sessions_lp <- participants |> 
+	count(lp) |> 
+	group_split(lp) |> 
 	set_names(c("monolingual", "bilingual"))
-n_sessions_lp_age_group <- participants %>% 
-	count(lp, age_group) %>% 
-	split(f = .$lp) %>% 
-	set_names(c("monolingual", "bilingual")) %>% 
-	map(~split(., f = .$age_group) %>% 
+
+n_sessions_lp_age_group <- participants |> 
+	count(lp, age_group) |> 
+	group_split(lp) |> 
+	set_names(c("monolingual", "bilingual")) |> 
+	map(\(x) group_split(x, age_group) |> 
 			set_names(c("age_21", "age_25", "age_30")))
@@
 Participants with DoE to language other than Catalan or Spanish were excluded from analyses.
-This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
-tbl-participants-lp summarises the linguistic profile of our sample.
+This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21$n` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25$n` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30$n` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21$n` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25$n` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30$n` at 30 months).
+@tbl-participants-lp summarises the linguistic profile of our sample.
 
@@
 #| label: tbl-participants-lp
-#| tbl-cap: "Description of language profile of participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
-participants %>% 
-	select(id, age_group, age, lp, doe_catalan, doe_spanish, test_language) %>% 
-	mutate(id = paste0(id, " (", age_group, ")")) %>%
-	add_count(lp, name = "n_lp") %>% 
-	add_count(age_group, name = "n_age_group") %>%
-
-	pivot_longer(starts_with("doe_"), names_to = "language", values_to = "doe") %>%
-	add_count(age_group, test_language, name = "n_age_test") %>% 
-	mutate(language = str_remove_all(language, "doe_") %>% 
+#| tbl-cap: "Description of language profile of test participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
+participants |> 
+	select(id, age_group, age, lp, doe_catalan, doe_spanish, test_language) |> 
+	mutate(id = paste0(id, " (", age_group, ")")) |>
+	add_count(lp, name = "n_lp") |> 
+	add_count(age_group, name = "n_age_group") |>
+
+	pivot_longer(starts_with("doe_"), names_to = "language", values_to = "doe") |>
+	add_count(age_group, test_language, name = "n_age_test") |> 
+	mutate(language = str_remove_all(language, "doe_") |> 
 		   	str_to_sentence(),
@@
 		   test_language = paste0("Tested in ", test_language, " (N = ", n_age_test, ")"),
-		   lp = factor(lp, levels = rev(unique(lp))))  %>% 
-	group_by(age_group, lp, test_language, language) %>% 
+		   lp = factor(lp, levels = rev(unique(lp))))  |> 
+	group_by(age_group, lp, test_language, language) |> 
 	summarise(across(doe, lst(mean, sd)),
-			  .groups = "drop") %>% 
+			  .groups = "drop") |> 
 	pivot_wider(id_cols = c(age_group, test_language),
 				names_from = c(language, lp),
-				values_from = c(matches("doe"))) %>% 
-	clean_names() %>% 
+				values_from = c(matches("doe")),
+				names_repair = janitor::make_clean_names) |> 
 	relocate(age_group, test_language,
 			 matches("catalan"),
-			 matches("spanish")) %>% 
+			 matches("spanish")) |> 
 	gt(rowname_col = "test_language", 
-	   groupname_col = "age_group", row_group.sep = ": ") %>% 
-	tab_spanner(md("Monolingual (*N* = 162)"), matches("monolingual")) %>% 
-	tab_spanner(md("Bilingual (*N* = 133)"), matches("bilingual")) %>%
-	fmt_number(matches("doe"), decimals = 1, scale_by = 100) %>% 
+	   groupname_col = "age_group", row_group.sep = ": ") |> 
+	tab_spanner(md("Monolingual (*N* = 162)"), matches("monolingual")) |> 
+	tab_spanner(md("Bilingual (*N* = 133)"), matches("bilingual")) |>
+	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
 	cols_merge_uncert(col_val = doe_mean_catalan_monolingual,
-					  col_uncert = doe_sd_catalan_monolingual) %>% 
+					  col_uncert = doe_sd_catalan_monolingual) |> 
 	cols_merge_uncert(col_val = doe_mean_catalan_bilingual,
-					  col_uncert = doe_sd_catalan_bilingual) %>% 
+					  col_uncert = doe_sd_catalan_bilingual) |> 
 	cols_merge_uncert(col_val = doe_mean_spanish_monolingual, 
-					  col_uncert = doe_sd_spanish_monolingual) %>% 
+					  col_uncert = doe_sd_spanish_monolingual) |> 
 	cols_merge_uncert(col_val = doe_mean_spanish_bilingual, 
-					  col_uncert = doe_sd_spanish_bilingual) %>%
+					  col_uncert = doe_sd_spanish_bilingual) |>
 
@@
 			   doe_mean_spanish_monolingual = "Spanish (%)",
-			   doe_mean_spanish_bilingual = "Spanish (%)") %>% 
+			   doe_mean_spanish_bilingual = "Spanish (%)") |> 
 	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) %>% 
+			  list(cells_column_spanners())) |> 
 	tab_style(cell_text(size = "medium"),
@@
 
+::: {.panel-tabset}
+
 ### L1 vocabulary
@@
 #| fig-width: 11
-sample_size <- participants %>% 
-	filter(id %in% fit_0$data$id) %>% 
+sample_size <- distinct(data_summary, id, age_group) |> 
 	count(age_group)
 
-sample_size_lp <- participants %>% 
-	filter(id %in% fit_0$data$id) %>% 
-	count(age_group, lp) %>% 
+sample_size_lp <- data_summary |> 
+	distinct(id, age_group, lp) |> 
+	count(age_group, lp) |> 
 	mutate(
@@
 # vocabulary
-participants %>% 
+participants |> 
 	mutate(
@@
 							levels = c("Observed", "Imputed"))
-	) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot(aes(lp,  vocab_size_l1, colour = is_imputed, fill = is_imputed)) +
+	) |> 
+	drop_na(lp) |>
+	filter(is_valid_participant) |> 
+	ggplot(aes(lp,  l1_prop, 
+			   colour = is_imputed,
+			   fill = is_imputed,
+			   group = NA)) +
 	facet_wrap(~age_group, scales = "free_x") +
 	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(width = 0.15, size = 1, colour = "black",
+	geom_dots(layout = "swarm", side = "left") +
+	geom_boxplot(width = 0.15, size = 3/4,
+				 colour = "black",
+				 aes(group = lp),
 				 fill = "white", outlier.colour = NA,
-				 position = position_nudge(x = 0.3)) +
-	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
+				 position = position_nudge(x = 0.1)) +
 	geom_text(data = sample_size_lp,
@@
 		 fill = "Imputed") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
+	scale_y_continuous(limits = c(0, 1), 
+					   labels = scales::percent) +
 	theme(legend.position = "top", 
@@
 #| fig-width: 11
-participants %>% 
+participants |> 
 	mutate(
@@
 							levels = c("Observed", "Imputed"))
-	) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot(aes(lp,  vocab_size_total, colour = is_imputed, fill = is_imputed)) +
+	) |> 
+	drop_na(lp) |>
+	filter(is_valid_participant) |> 
+	ggplot(aes(lp,  total_prop, 
+			   colour = is_imputed,
+			   fill = is_imputed,
+			   group = NA)) +
 	facet_wrap(~age_group, scales = "free_x") +
 	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(width = 0.15, size = 1, colour = "black",
+	geom_dots(layout = "swarm", side = "left") +
+	geom_boxplot(width = 0.15, size = 3/4,
+				 colour = "black",
+				 aes(group = lp),
 				 fill = "white", outlier.colour = NA,
-				 position = position_nudge(x = 0.3)) +
-	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
+				 position = position_nudge(x = 0.1)) +
 	geom_text(data = sample_size_lp,
@@
 							levels = c("Observed", "Imputed"))
-	) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot(aes(lp,  vocab_size_conceptual, colour = is_imputed, fill = is_imputed)) +
+	) |> 
+	drop_na(lp) |>
+	filter(is_valid_participant) |> 
+	ggplot(aes(lp,  concept_prop, 
+			   colour = is_imputed,
+			   fill = is_imputed,
+			   group = NA)) +
 	facet_wrap(~age_group, scales = "free_x") +
 	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(width = 0.15, size = 1, colour = "black",
+	geom_dots(layout = "swarm", side = "left") +
+	geom_boxplot(width = 0.15, size = 3/4,
+				 colour = "black",
+				 aes(group = lp),
 				 fill = "white", outlier.colour = NA,
-				 position = position_nudge(x = 0.3)) +
-	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
+				 position = position_nudge(x = 0.1)) +
 	geom_text(data = sample_size_lp,
@@
 
+:::
+
 ## Design
@@
 ### Data processing
+
+Trial-level inclusion criteria:
+
+1. Valid prime: $\text{Prime}_{LT} \geq 750 \text{ms}$ (50%)
+2. Valid test: $\text{Target}_{LT} + \text{Distractor}_{LT} \geq 1,000 \text{ms}$ (50%)
+3. Minimum 100ms looking time to target, and minimum 100ms looking time to target (5%)
+
+Participant-level inclusion criteria:
+
+4. At least two valid trial of each type (cognate, non-cognate, unrelated)
 
@@
 #| tbl-cap: "Summary of the dataset."
-attrition %>% 
-	left_join(select(participants, age_group, lp, id, date_test)) %>% 
-	add_count(age_group, lp, name = "n_trials") %>% 
-	group_by(id, lp, trial_type, date_test, age_group, valid_participant, n_trials) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(names_from = trial_type, values_from = valid_trial_count, values_fill = 0) %>% 
-	clean_names() %>% 
-	add_count(lp, age_group) %>%
-	group_by(lp, age_group, n, n_trials) %>% 
-	summarise(across(cognate:unrelated, lst(sum, mean, sd)),
-			  n_valid = sum(valid_participant),
-			  .groups = "drop") %>%
-	relocate(n_valid, .after = n) %>% 
-	mutate(n_prop = n_valid/n) %>% 
-	arrange(age_group, lp) %>% 
-	relocate(age_group, lp, n_valid, n_prop, matches("cognate"), matches("non_cognate"), matches("unrelated")) %>% 
-	gt(groupname_col = "age_group", rowname_col = "lp")  %>%
-	cols_hide(c(n, n_trials)) %>% 
-	fmt_number(matches("_mean|_sd"), decimals = 1) %>%
-	fmt_percent(matches("_prop"), decimals = 1) %>% 
-	cols_merge_n_pct(col_n = n_valid, col_pct = n_prop, autohide = TRUE)  %>% 
-	tab_spanner("Non-cognate", matches("non_cognate")) %>%
-	tab_spanner("Cognate", starts_with("cognate")) %>%
-	tab_spanner("Unrelated", matches("unrelated")) %>%
-	tab_spanner("Related", matches("cognate")) %>%
-
-	cols_merge_uncert(col_val = cognate_mean, col_uncert = cognate_sd) %>% 
-	cols_merge_uncert(col_val = non_cognate_mean, col_uncert = non_cognate_sd) %>% 
-	cols_merge_uncert(col_val = unrelated_mean, col_uncert = unrelated_sd) %>% 
+attrition_trials |> 
+	left_join(select(participants, age_group, lp, id, date_test),
+			  by = join_by(id, age_group)) |> 
+	left_join(attrition_participants,
+			  by = join_by(id, age_group)) |> 
+	add_count(age_group, lp, name = "n_trials") |> 
+	summarise(valid_trial_count = sum(is_valid_trial, na.rm = TRUE),
+			  .by = c(id, lp, trial_type, date_test,
+			  		age_group, is_valid_participant, n_trials)) |> 
+	pivot_wider(names_from = trial_type, 
+				values_from = valid_trial_count, 
+				values_fill = 0,
+				names_repair = janitor::make_clean_names) |> 
+	rename(noncognate = non_cognate) |> 
+	add_count(lp, age_group) |>
+	summarise(across(c(cognate, noncognate, unrelated),
+					 lst(sum, mean, sd)),
+			  n_valid = sum(is_valid_participant),
+			  .by = c(lp, age_group, n, n_trials)) |>
+	relocate(n_valid, .after = n) |> 
+	mutate(n_prop = n_valid/n) |> 
+	arrange(age_group, lp) |> 
+	relocate(age_group, lp, n_valid, n_prop, 
+			 matches("cognate"),
+			 matches("noncognate"),
+			 matches("unrelated")) |> 
+	gt(groupname_col = "age_group",
+	   rowname_col = "lp")  |>
+	cols_hide(c(n, n_trials)) |> 
+	fmt_number(matches("_mean|_sd"), 
+			   decimals = 1) |>
+	fmt_percent(matches("_prop"),
+				decimals = 1) |> 
+	cols_merge_n_pct(col_n = n_valid, 
+					 col_pct = n_prop,
+					 autohide = TRUE)  |> 
+	tab_spanner("Non-cognate", matches("noncognate")) |>
+	tab_spanner("Cognate", starts_with("cognate")) |>
+	tab_spanner("Unrelated", matches("unrelated")) |>
+	tab_spanner("Related", matches("cognate")) |> 
+	cols_merge_uncert(col_val = cognate_mean,
+					  col_uncert = cognate_sd) |> 
+	cols_merge_uncert(col_val = noncognate_mean,
+					  col_uncert = noncognate_sd) |> 
+	cols_merge_uncert(col_val = unrelated_mean, 
+					  col_uncert = unrelated_sd) |> 
 	cols_label(age_group = "Age",
@@
 			   cognate_mean = "Mean ± SD",
-			   non_cognate_sum = "Trials",
-			   non_cognate_mean = "Mean ± SD",
+			   noncognate_sum = "Trials",
+			   noncognate_mean = "Mean ± SD",
 			   unrelated_sum = "Trials",
-			   unrelated_mean = "Mean ± SD") %>% 
+			   unrelated_mean = "Mean ± SD") |> 
 	summary_rows(groups = TRUE,
 				 columns = where(is.integer),
-				 fns = list("Sum" = ~sum(.)), 
-				 formatter = fmt_number,
-				 decimals = 0) %>% 
+				 fns = list("Sum" = "sum"),
+				 fmt = fmt_number,
+				 decimals = 0) |>
 	summary_rows(groups = TRUE,
 				 columns = c(where(is.numeric), -n_valid),
-				 fns = list("Mean" = ~mean(.)),
-				 formatter = fmt_number,
-				 decimals = 1) %>% 
+				 fns = list("Mean" = "mean"),
+				 fmt = fmt_number,
+				 decimals = 1) |>
 	grand_summary_rows(columns = where(is.integer),
-					   fns = list("N" = ~sum(.)),
-					   formatter = fmt_number,
-					   decimals = 0) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary())) 
+					   fns = list("N" = "sum"),
+					   formatter = fmt_integer) 
 ```
@@
 
-### Model
+### Modelling approach
 
@@
 #| fig-height: 6
-nd <- tibble(time_bin = seq(0, 20, 0.1)) %>% 
-	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)
-
-m <- add_epred_draws(nd, fit_prior, ndraws = 50, re_formula = NA) %>% 
+nd <- tibble(time_bin = seq(0, 20, 0.1)) |> 
+polypoly::poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)
+
+m <- add_epred_draws(nd, fit_prior, ndraws = 50, re_formula = NA) |> 
 mutate(.epred = plogis(.epred))
@@
 #| fig-height: 4
-n_text <- participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
+n_text <- participants |> 
+drop_na(is_valid_participant) |> 
 mutate(
 valid_status = case_when(
-			valid_participant & !is_imputed ~ "Valid (observed CDI)",
-			valid_participant & is_imputed ~ "Valid (imputed CDI)",
-			!valid_participant ~ "Excluded"
+is_valid_participant & !is_imputed ~ "Valid (observed CDI)",
+is_valid_participant & is_imputed ~ "Valid (imputed CDI)",
+!is_valid_participant ~ "Excluded"
 )
-	) %>% 
-	filter(valid_status != "Excluded") %>% 
-	count(lp, age_group) %>% 
-	mutate(n_label = paste0(n, " valid"),
-		   valid_status = "Valid (observed CDI)")
-
-participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
+) |> 
+count(lp, age_group, valid_status)
+
+participants |> 
 mutate(valid_status = case_when(
-		valid_participant & !is_imputed ~ "valid_cdi_observed",
-		valid_participant & is_imputed ~ "valid_cdi_imputed",
-		!valid_participant ~ "excluded")) %>% 
-	add_count(age_group, lp, name = "n_total") %>% 
-	count(age_group, lp, n_total, valid_status) %>% 
-	pivot_wider(names_from = valid_status, values_from = n, values_fill = 0) %>% 
-	relocate(age_group, lp, n_total, valid_cdi_observed, valid_cdi_imputed, excluded) %>% 
-	mutate(across(matches("valid_|excluded"), ~./n_total, .names = "{.col}_prop")) %>% 
-	gt(rowname_col = "lp", groupname_col = "age_group") %>% 
-	fmt_percent(matches("prop"), decimals = 1) %>% 
-	cols_merge_n_pct(col_n = valid_cdi_observed, col_pct = valid_cdi_observed_prop) %>% 
-	cols_merge_n_pct(col_n = valid_cdi_imputed, col_pct = valid_cdi_imputed_prop) %>% 
-	cols_merge_n_pct(col_n = excluded, col_pct = excluded_prop) %>% 
-	tab_spanner("Included participants", matches("valid")) %>% 
-	tab_spanner("Excluded participants", matches("excluded")) %>% 
+is_valid_participant & !is_imputed ~ "valid_cdi_observed",
+is_valid_participant & is_imputed ~ "valid_cdi_imputed",
+!is_valid_participant ~ "excluded")) |> 
+add_count(age_group, lp, name = "n_total") |> 
+count(age_group, lp, n_total, valid_status) |> 
+pivot_wider(names_from = valid_status, values_from = n, values_fill = 0) |> 
+relocate(age_group, lp, n_total, valid_cdi_observed, valid_cdi_imputed, excluded) |> 
+mutate(across(matches("valid_|excluded"), ~./n_total, .names = "{.col}_prop")) |> 
+gt(rowname_col = "lp", groupname_col = "age_group") |> 
+fmt_percent(matches("prop"), decimals = 1) |> 
+cols_merge_n_pct(col_n = valid_cdi_observed, col_pct = valid_cdi_observed_prop) |> 
+cols_merge_n_pct(col_n = valid_cdi_imputed, col_pct = valid_cdi_imputed_prop) |> 
+cols_merge_n_pct(col_n = excluded, col_pct = excluded_prop) |> 
+tab_spanner("Included participants", matches("valid")) |> 
+tab_spanner("Excluded participants", matches("excluded")) |> 
 cols_label(n_total = "N",
@@
 valid_cdi_imputed = "Missing CDI",
-			   excluded = "") %>% 
+excluded = "") |> 
 summary_rows(groups = TRUE, columns = where(is.integer), 
@@
 formatter = fmt_number,
-				 decimals = 0) %>% 
+decimals = 0) |> 
 grand_summary_rows(columns = where(is.integer), 
@@
 formatter = fmt_number,
-					   decimals = 0) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary()))
+decimals = 0) 
 ```
@@
 
-attrition %>% 
-	left_join(distinct(participants, id, age_group, test_language, list, version, list)) %>% 
-	left_join(distinct(stimuli, test_language, version, list, trial_id, trial_type,
-					   freq_target, freq_prime, familiarity_prime, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status != "Valid",  "Excluded", valid_status)) %>% 
-	drop_na() %>% 
-	group_by(trial_type, valid_status, age_group) %>% 
+attrition_participants |> 
+left_join(distinct(participants, id, age_group,
+test_language, list, version, list),
+by = join_by(id, age_group)) |> 
+left_join(distinct(stimuli, test_language, version, list,
+trial_id, trial_type,
+freq_target, freq_prime,
+familiarity_prime, familiarity_target),
+relationship = "many-to-many",
+by = join_by(test_language, list, version))|> 
+mutate(valid_status = ifelse(valid_status != "Valid",
+"Excluded", 
+valid_status)) |> 
 summarise(n = n(),
 across(matches("freq_|familiarity_"), lst(mean, sd)),
-			  .groups = "drop") %>% 
+.by = c(trial_type, valid_status, age_group)) |> 
 pivot_wider(names_from = valid_status,
 values_from = c(n, matches("freq_|familiarity_")),
-				values_fill = 0) %>%
-	clean_names() %>% 
-	relocate(age_group, trial_type, n_valid, n_excluded, 
-			 matches("_valid")) %>%
-
-	gt(rowname_col = "trial_type", groupname_col = "age_group") %>% 
-	fmt_number(matches("n_"), decimals = 0) %>% 
-	fmt_number(matches("freq_"), decimals = 1) %>% 
-	fmt_number(matches("familiarity"), scale_by = 100, decimals = 1) %>%
-
-	tab_spanner("N", c(n_valid, n_excluded)) %>%
-
-	tab_spanner("Prime", id = 1, c(freq_prime_mean_valid, freq_prime_mean_excluded)) %>%
-	tab_spanner("Target", id = 2, c(freq_target_mean_valid, freq_target_mean_excluded)) %>% 
-	tab_spanner("Prime", id = 3, c(familiarity_prime_mean_valid, familiarity_prime_mean_excluded)) %>% 
-	tab_spanner("Target", id = 4, c(familiarity_target_mean_valid, familiarity_target_mean_excluded)) %>%
-	tab_spanner("Frequency", starts_with("freq_")) %>% 
-	tab_spanner("Familiarity (%)", starts_with("familiarity_")) %>%
-
-	cols_merge_uncert(col_val = freq_prime_mean_valid, col_uncert = freq_prime_sd_valid) %>% 
-	cols_merge_uncert(col_val = freq_prime_mean_excluded, col_uncert = freq_prime_sd_excluded) %>% 
-	cols_merge_uncert(col_val = freq_target_mean_valid, col_uncert = freq_target_sd_valid) %>% 
-	cols_merge_uncert(col_val = freq_target_mean_excluded, col_uncert = freq_target_sd_excluded) %>% 
-	cols_merge_uncert(col_val = familiarity_prime_mean_valid, col_uncert = familiarity_prime_sd_valid) %>% 
-	cols_merge_uncert(col_val = familiarity_prime_mean_excluded, col_uncert = familiarity_prime_sd_excluded) %>% 
-	cols_merge_uncert(col_val = familiarity_target_mean_valid, col_uncert = familiarity_target_sd_valid) %>%
-	cols_merge_uncert(col_val = familiarity_target_mean_excluded, col_uncert = familiarity_target_sd_excluded) %>%
-
+values_fill = 0,
+names_repair = janitor::make_clean_names) |>
+relocate(age_group, trial_type,
+n_valid, n_excluded, 
+matches("_valid")) |> 
+gt(rowname_col = "trial_type", 
+groupname_col = "age_group") |> 
+fmt_number(matches("n_"),
+decimals = 0) |> 
+fmt_number(matches("freq_"),
+decimals = 1) |> 
+fmt_number(matches("familiarity"),
+scale_by = 100,
+decimals = 1) |> 
+tab_spanner("N", c(n_valid, n_excluded)) |> 
+tab_spanner("Prime", id = 1,
+c(freq_prime_mean_valid,
+freq_prime_mean_excluded)) |>
+tab_spanner("Target", id = 2, 
+c(freq_target_mean_valid, 
+freq_target_mean_excluded)) |> 
+tab_spanner("Prime", id = 3, 
+c(familiarity_prime_mean_valid, 
+familiarity_prime_mean_excluded)) |> 
+tab_spanner("Target", id = 4, 
+c(familiarity_target_mean_valid,
+familiarity_target_mean_excluded)) |>
+tab_spanner("Frequency", starts_with("freq_")) |> 
+tab_spanner("Familiarity (%)", starts_with("familiarity_")) |>
+
+cols_merge_uncert(col_val = freq_prime_mean_valid, 
+col_uncert = freq_prime_sd_valid) |> 
+cols_merge_uncert(col_val = freq_prime_mean_excluded,
+col_uncert = freq_prime_sd_excluded) |> 
+cols_merge_uncert(col_val = freq_target_mean_valid,
+col_uncert = freq_target_sd_valid) |> 
+cols_merge_uncert(col_val = freq_target_mean_excluded,
+col_uncert = freq_target_sd_excluded) |> 
+cols_merge_uncert(col_val = familiarity_prime_mean_valid,
+col_uncert = familiarity_prime_sd_valid) |> 
+cols_merge_uncert(col_val = familiarity_prime_mean_excluded, 
+col_uncert = familiarity_prime_sd_excluded) |> 
+cols_merge_uncert(col_val = familiarity_target_mean_valid,
+col_uncert = familiarity_target_sd_valid) |>
+cols_merge_uncert(col_val = familiarity_target_mean_excluded, 
+col_uncert = familiarity_target_sd_excluded) |> 
 cols_label(n_excluded = "Exc.",
@@
 familiarity_target_mean_valid = "Inc.",
-			   familiarity_target_mean_excluded = "Exc.") %>% 
+familiarity_target_mean_excluded = "Exc.") |> 
 summary_rows(groups = TRUE,
@@
 formatter = fmt_number,
-				 decimals = 1) %>% 
+decimals = 1) |> 
 summary_rows(groups = TRUE,
@@
 scale_by = 100,
-				 decimals = 1) %>% 
+decimals = 1) |> 
 grand_summary_rows(columns = c(n_valid, n_excluded),
@@
 formatter = fmt_number,
-					   decimals = 0) %>% 
+decimals = 0) |> 
 grand_summary_rows(columns = matches("familiarity_"),
@@
 scale_by = 100,
-					   decimals = 1) %>% 
+decimals = 1) |> 
 grand_summary_rows(columns = matches("freq_"),
@@
 formatter = fmt_number,
-					   decimals = 1) %>% 
+decimals = 1) |> 
 tab_style(cell_text(align = "center"),
-			  cells_column_labels()) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary())) %>% 
-	tab_footnote("Included trials.", cells_column_labels(matches("_valid"))) %>% 
+cells_column_labels()) |> 
+# tab_style(cell_text(weight = "bold"),
+# 		  list(cells_column_spanners(),
+# 		  	 cells_grand_summary(),
+# 		  	 cells_row_groups(),
+# 		  	 cells_stub_grand_summary(),
+# 		  	 cells_stub_summary())) |> 
+tab_footnote("Included trials.", cells_column_labels(matches("_valid"))) |> 
 tab_footnote("Excluded trials.", cells_column_labels(matches("_excluded")))
@@
 #| fig-height: 6
-df %>% 
-	group_by(id, lp, trial_type, age_group) %>%
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
+data_summary |> 
+summarise(.prop = mean(.prop),
+.by = c(id, lp, trial_type, age_group)) |> 
+ggplot(aes(trial_type, 
+.prop, 
+colour = trial_type,
+fill = trial_type)) +
 facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_line(aes(group = id), alpha = 0.25) +
-	stat_slab(side = "right", scale = 0.5) +
-	geom_boxplot(width = 0.1, size = 0.75, fill = "white", colour = "black", outlier.colour = NA) +
-	labs(x = "Trial type", y = "Proportion of target looking", colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
+geom_hline(yintercept = 0.5, 
+size = 1, 
+colour = "grey") +
+geom_line(aes(group = id),
+colour = "grey",
+alpha = 0.25) +
+geom_dots(layout = "swarm") +
+geom_boxplot(width = 0.1,
+fill = "white", 
+colour = "black",
+outlier.colour = NA) +
+labs(x = "Trial type",
+y = "Proportion of target looking",
+colour = "Trial type", 
+fill = "Trial type") +
+scale_y_continuous(labels = \(x) scales::percent(x, accuracy = 1)) +
 theme(legend.position = "none")
@@
 #| fig-height: 8
-df %>% 
-	group_by(id, time_bin, lp, trial_type, age_group) %>%
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	ggplot(aes(time_bin, prop, colour = trial_type, fill = trial_type, shape = trial_type)) +
+data_time |> 
+summarise(.logit = mean(.logit),
+.by = c(id, timebin, lp, trial_type, age_group)) |> 
+ggplot(aes(timebin, .logit,
+colour = trial_type, 
+fill = trial_type, 
+shape = trial_type)) +
 facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
-	stat_summary(fun = mean, geom = "point", size = 2) +
-	stat_summary(fun = mean, geom = "line", size = 0.75) +
-	labs(x = "Time bin (100 ms)", y = "Proportion of target looking",
-		 colour = "Trial type", fill = "Trial type", shape = "Trial type") +
-	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
-	scale_x_continuous(labels = function(x) format(x*100, big.mark = ",")) +
+geom_hline(yintercept = 0, 
+size = 1,
+colour = "grey") +
+stat_summary(fun.data = mean_se,
+geom = "ribbon",
+colour = NA,
+alpha = 0.5) +
+stat_summary(fun = mean,
+geom = "point",
+size = 2) +
+stat_summary(fun = mean,
+geom = "line", 
+size = 0.75) +
+labs(x = "Time bin (100 ms)",
+y = "Proportion of target looking",
+colour = "Trial type", 
+fill = "Trial type", 
+shape = "Trial type") +
+scale_y_continuous(labels = \(x) scales::percent(x, accuracy = 1)) +
+scale_x_continuous(labels = \(x) format(x * 100, big.mark = ",")) +
 theme(legend.position = "top",
 legend.title = element_blank(),
-		  panel.grid = element_line(linetype = "dotted", colour = "grey"),
-		  panel.grid.major = element_line(colour = "grey", linetype = "dotted"))
+panel.grid = element_line(linetype = "dotted", 
+colour = "grey"),
+panel.grid.major = element_line(colour = "grey", 
+linetype = "dotted"))
 ```
@@
 #| label: tab-model-comparison
-loos %>% 
-	as_tibble(.name_repair = make_clean_names) %>% 
-	rownames_to_column("model") %>% 
+loos |> 
+as_tibble(.name_repair = make_clean_names) |> 
+rownames_to_column("model") |> 
 relocate(
@@
 matches("looic")
-	) %>%
+) |>
 mutate(across(everything(), as.numeric),
-		   model = attr(loos, "dimnames")[[1]]) %>% 
-	select(-matches("subsampling")) %>% 
-	gt(rowname_col = "model") %>%
-	fmt_number(is.numeric, decimals = 1) %>% 
-	cols_merge_uncert(col_val = elpd_diff, col_uncert = se_diff) %>% 
-	cols_merge_uncert(col_val = elpd_loo, col_uncert = se_elpd_loo) %>% 
-	cols_merge_uncert(col_val = p_loo, col_uncert = se_p_loo) %>% 
-	cols_merge_uncert(col_val = looic, col_uncert = se_looic) %>% 
+model = attr(loos, "dimnames")[[1]]) |> 
+select(-matches("subsampling")) |> 
+gt(rowname_col = "model") |>
+fmt_number(is.numeric, decimals = 1) |> 
+cols_merge_uncert(col_val = elpd_diff, col_uncert = se_diff) |> 
+cols_merge_uncert(col_val = elpd_loo, col_uncert = se_elpd_loo) |> 
+cols_merge_uncert(col_val = p_loo, col_uncert = se_p_loo) |> 
+cols_merge_uncert(col_val = looic, col_uncert = se_looic) |> 
 cols_label(model = "Model",
@@
 looic = md("*LOO-IC*"),
-			   elpd_diff = md("Difference")) %>% 
-	tab_source_note(md("Pareto-*k* estimates of all models were acceptable (*k* < 0.5)")) %>% 
+elpd_diff = md("Difference")) |> 
+tab_source_note(md("Pareto-*k* estimates of all models were acceptable (*k* < 0.5)")) |> 
 tab_style(cell_text(weight = "bold"),
-			  cells_column_labels()) %>% 
+cells_column_labels()) |> 
 tab_style(cell_fill(color = "grey", alpha = 0.5),
-			  cells_body(matches("diff"))) %>% 
+cells_body(matches("diff"))) |> 
 tab_style(cell_fill(color = clrs[4], alpha = 0.75),
@@
 
-post_draws %>% 
-	median_hdi() %>%
+post_draws |> 
+median_hdi() |>
 mutate(poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
@@
 .variable_name = case_when(.variable %in% paste0("b_ot", 1:3) ~ .variable,
-		   						   TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) %>% 
+TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) |> 
 factor(levels = names(str_repl),
@@
 .variable_name %in% str_repl[10:17] ~ "Two-way interactions",
-		   				 .variable_name %in% str_repl[18:length(str_repl)] ~ "Three-way interactions")) %>%
-	select(.variable_name, type, poly, .value:.upper) %>%
-	arrange(.variable_name) %>% 
+.variable_name %in% str_repl[18:length(str_repl)] ~ "Three-way interactions")) |>
+select(.variable_name, type, poly, .value:.upper) |>
+arrange(.variable_name) |> 
 pivot_wider(names_from = poly, 
@@
 values_fill = NA,
-				names_repair = make_clean_names) %>% 
-	relocate(variable_name, starts_with("value_")) %>% 
+names_repair = make_clean_names) |> 
+relocate(variable_name, starts_with("value_")) |> 
 gt(rowname_col = "variable_name",
-	   groupname_col = "type") %>% 
-	fmt_number(is.numeric) %>%
-	tab_spanner("Intercept", matches("intercept")) %>% 
-	sub_missing(everything(), rows = everything(), missing_text = "--") %>% 
-	tab_spanner("Linear", matches("linear")) %>% 
-	tab_spanner("Quadratic", matches("quadratic")) %>% 
-	tab_spanner("Cubic", matches("cubic")) %>% 
-	cols_merge(c(lower_intercept, upper_intercept), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c(lower_linear, upper_linear), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c(lower_quadratic, upper_quadratic), pattern = "[{1}, {2}]") %>% 
-	cols_merge(c(lower_cubic, upper_cubic), pattern = "[{1}, {2}]") %>%
+groupname_col = "type") |> 
+fmt_number(is.numeric) |>
+tab_spanner("Intercept", matches("intercept")) |> 
+sub_missing(everything(), rows = everything(), missing_text = "--") |> 
+tab_spanner("Linear", matches("linear")) |> 
+tab_spanner("Quadratic", matches("quadratic")) |> 
+tab_spanner("Cubic", matches("cubic")) |> 
+cols_merge(c(lower_intercept, upper_intercept), pattern = "[{1}, {2}]") |> 
+cols_merge(c(lower_linear, upper_linear), pattern = "[{1}, {2}]") |> 
+cols_merge(c(lower_quadratic, upper_quadratic), pattern = "[{1}, {2}]") |> 
+cols_merge(c(lower_cubic, upper_cubic), pattern = "[{1}, {2}]") |>
 cols_label(value_intercept = md("b"),
@@
 value_cubic = md("b"),
-			   lower_cubic = md("95% *HDI*")) %>% 
+lower_cubic = md("95% *HDI*")) |> 
 tab_style(cell_text(align = "left", indent = px(10)),
-			  cells_stub()) %>% 
+cells_stub()) |> 
 tab_style(cell_fill(color = "grey90"),
-			  cells_body(matches("value"))) %>% 
+cells_body(matches("value"))) |> 
 tab_style(cell_text(weight = "bold"),
-			  cells_column_spanners()) %>% 
+cells_column_spanners()) |> 
 tab_style(cell_text(weight = "bold"),
-			  cells_row_groups()) %>% 
+cells_row_groups()) |> 
 tab_style(cell_text(style = "oblique"),
-			  cells_column_labels(columns = matches("value"))) %>% 
+cells_column_labels(columns = matches("value"))) |> 
 tab_style(cell_fill(color = clrs[4], alpha = 0.75),
 cells_body(columns = value_intercept, 
-			  		   rows = (upper_intercept < 0) | (lower_intercept > 0))) %>% 
+rows = (upper_intercept < 0) | (lower_intercept > 0))) |> 
 tab_style(cell_fill(color = clrs[4], alpha = 0.75),
 cells_body(columns = value_linear, 
-			  		   rows = (upper_linear < 0) | (lower_linear > 0))) %>%
+rows = (upper_linear < 0) | (lower_linear > 0))) |>
 tab_style(cell_fill(color = clrs[4], alpha = 0.75),
 cells_body(columns = value_quadratic, 
-			  		   rows = (upper_quadratic < 0) | (lower_quadratic > 0))) %>%
+rows = (upper_quadratic < 0) | (lower_quadratic > 0))) |>
 tab_style(cell_fill(color = clrs[4], alpha = 0.75),
 cells_body(columns = value_cubic, 
-			  		   rows = (upper_cubic < 0) | (lower_cubic > 0))) %>% 
+rows = (upper_cubic < 0) | (lower_cubic > 0))) |> 
 tab_style(cell_text(size = "small"), 
-			  list(cells_body(), cells_stub())) %>% 
+list(cells_body(), cells_stub())) |> 
 tab_footnote("Sum-coded contrast between 21 and 25 month old participants.",
-				 cells_stub(rows = 2)) %>% 
+cells_stub(rows = 2)) |> 
 tab_footnote("Sum-coded contrast between 25 and 30 month old participants.",
-				 cells_stub(rows = 3)) %>% 
+cells_stub(rows = 3)) |> 
 tab_footnote("Sum-coded contrast between monolingual and bilingual participants.",
-				 cells_stub(rows = 4)) %>% 
+cells_stub(rows = 4)) |> 
 tab_footnote("Sum-coded contrast between related (cognate and non-cognate) and unrelated trials",
-				 cells_stub(rows = 5)) %>% 
+cells_stub(rows = 5)) |> 
 tab_footnote("Sum-coded contrast between cognate and non-cognate trials",
@@
 Coefficients on the intercept indicate changes in overal proportion of target looking, coefficients in the linear term indicate changes in the overall slope of target looking growth across time, coefficients in the quadratic and cubic terms reflect the steepness of the rise and fall or of the rise, fall and rise, respectivey,  of the curve."
-post_draws %>% 
-	median_hdi() %>%
+post_draws |> 
+median_hdi() |>
 mutate(poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
@@
 str_detect(.variable, "ot3") ~ "Cubic",
-							TRUE ~ "Intercept") %>% 
+TRUE ~ "Intercept") |> 
 factor(levels = c("Intercept", "Linear", "Quadratic", "Cubic")),
 .variable_name = case_when(.variable %in% paste0("b_ot", 1:3) ~ .variable,
-		   						   TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) %>% 
+TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) |> 
 factor(levels = names(str_repl),
@@
 .variable_name %in% str_repl[18:length(str_repl)] ~ "Three-way interactions"),
-		   excludes_zero = ifelse((.lower > 0) | (.upper < 0), "Yes", "No")) %>%
-	select(.variable_name, type, poly, .value:.upper, excludes_zero) %>%
-	arrange(.variable_name) %>% 
+excludes_zero = ifelse((.lower > 0) | (.upper < 0), "Yes", "No")) |>
+select(.variable_name, type, poly, .value:.upper, excludes_zero) |>
+arrange(.variable_name) |> 
 ggplot(aes(x = .value, y = fct_rev(.variable_name), 
@@
 #| fig-height: 8
-nd <- expand_grid(time_bin = seq(0, 20, 0.1),
-				  age_group = levels(fit_1$data$age_group),
-				  lp = levels(fit_2$data$lp),
-				  trial_type = levels(fit_4$data$trial_type)) %>% 
-	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)
-
-m <- add_epred_draws(nd, fit_3, ndraws = 25, re_formula = NA) %>% 
+nd <- expand_grid(timebin = seq(0, 20, 0.1),
+age_group = levels(data_time$age_group),
+lp = levels(data_time$lp),
+trial_type = levels(data_time$trial_type)
+) |> 
+polypoly::poly_add_columns(timebin,
+degree = 3,
+prefix = "ot",
+scale_width = 1)
+
+m <- fitted(fit_timecourse_2 , newdata = nd, re_formula = NA) |> 
+bind_cols(nd) |> 
+mutate(across(Estimate:Q97.5, plogis))
+
+m <- add_epred_draws(nd,
+fit_timecourse_2 ,
+ndraws = 200,
+re_formula = NA) |> 
 mutate(.epred = plogis(.epred))
 
-ptlt_means <- df %>% 
-	group_by(id, age_group, lp, trial_type, time_bin) %>% 
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	group_by(age_group, lp, trial_type, time_bin) %>% 
-	summarise(prop = mean(prop), .groups = "drop")
-
-m %>% 
-	ggplot(aes(time_bin, .epred, colour = trial_type, shape = trial_type)) +
+ptlt_means <- data_time |> 
+summarise(.prop = mean(.prop), 
+.by = c(id, age_group, lp, trial_type, timebin)) |> 
+summarise(.prop = mean(.prop),
+.by = c(age_group, lp, trial_type, timebin))
+
+m |> 
+ggplot(aes(timebin,
+Estimate,
+colour = trial_type,
+fill = trial_type)) +
 facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_line(aes(group = interaction(.draw, trial_type)), alpha = 0.15, size = 0.75) +
+geom_hline(yintercept = 0.5, 
+size = 1,
+colour = "grey") +
+geom_ribbon(aes(ymin = Q2.5,
+ymax = Q97.5),
+colour = NA,
+alpha = 1/3) +
+geom_line(linewidth = 3/4) +
 # stat_summary(fun = median, geom = "line", size = 1) +
-	geom_point(data = ptlt_means, aes(y = prop)) +
+geom_point(data = ptlt_means, aes(y = .prop)) +
 labs(x = "Time (ms)",
@@
 linetype = "Trial type") +
-	scale_x_continuous(labels = function(x) format(x*100, big.mark = ",")) +
-	scale_y_continuous(labels = percent) +
+scale_x_continuous(labels = \(x) format(250 + x*100, big.mark = ",")) +
+scale_y_continuous(limits = c(0, 1)) +
 theme(legend.position = "top",
@@
 
-## Longitudinal participants
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r}
-#| label: fig-participants-longitudinal
-#| fig-height: 10
-#| fig-width: 4
-participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	filter(valid_participant) %>% 
-	add_count(id, lp, name = "n_total") %>% 
-	count(id, age_group, test_language, lp, n_total) %>% 
-	pivot_wider(id_cols = c(id, lp, test_language, n_total),
-				names_from = age_group,
-				values_from = n,
-				values_fill = 0) %>% 
-	pivot_longer(5:7,
-				 names_to = "age_group",
-				 values_to = "n") %>% 
-	mutate(id_reordered = reorder_within(id, by = n_total, within = list(test_language, lp))) %>% 
-	ggplot(aes(age_group, id_reordered, fill = as.factor(n))) + 
-	facet_wrap(test_language~lp, 
-			   scales = "free_y",
-			   labeller = label_wrap_gen(multi_line = FALSE)) +
-	geom_tile(colour = "white") +
-	labs(x = "Age (months)", 
-		 y = "Exposure to 2nd language", 
-		 fill = "Lang. Profile") +
-	scale_fill_manual(values = c("white", clrs[4], "white")) +
-	theme(legend.position = "none",
-		  legend.title = element_blank(),
-		  panel.grid = element_blank(),
-		  axis.text.x = element_text(size = 6),
-		  axis.title.y = element_blank(),
-		  axis.title.x = element_text(size = 6),
-		  axis.text.y = element_blank(),
-		  axis.ticks.y = element_blank(),
-		  strip.text = element_text(size = 6))
-
-```
-
 ## Additional stimuli properties
@@
 #| fig-height: 6
-animacy <- stimuli %>%
+animacy <- stimuli |>
 distinct(test_language, 
@@
 prime, 
-			 .keep_all = TRUE) %>% 
+.keep_all = TRUE) |> 
 pivot_longer(c(is_animate_prime, is_animate_target), 
 names_to = "role",
-				 values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(test_language,  trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
+values_to = "is_animate") |> 
+mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) |> 
+count(test_language,  trial_type, role, is_animate) |> 
+drop_na(is_animate) |> 
 mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
 
-animacy %>% 
-	# filter(role=="Prime") %>% 
+animacy |> 
+# filter(role=="Prime") |> 
 ggplot() +
@@
 fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
+scale_y_continuous(labels = scales::percent) +
 coord_flip() + 
@@
 #| fig-height: 5
+#| eval: false
 #| fig-width: 10
-stimuli %>% 
-	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
-	drop_na(trial_type, semantic_category_prime) %>% 
-	count(trial_type, test_language, semantic_category_prime, name = "sum") %>% 
-	right_join(expand(., trial_type,  test_language,  semantic_category_prime)) %>%
-	replace_na(list(sum = 0)) %>% 
-	group_by(trial_type, test_language) %>% 
-	mutate(n =  sum(sum), prop = sum/n) %>% 
-	ungroup() %>% 
+stimuli |> 
+distinct(test_language,  target,  prime, .keep_all = TRUE) |> 
+drop_na(trial_type, semantic_category_prime) |> 
+count(trial_type, test_language, semantic_category_prime, name = "sum") |> 
+right_join(expand(., trial_type,
+test_language, 
+semantic_category_prime)) |>
+replace_na(list(sum = 0)) |> 
+group_by(trial_type, test_language) |> 
+mutate(n =  sum(sum), prop = sum/n) |> 
+ungroup() |> 
 ggplot() +
 aes(x = prop,
-		y = reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
+y = tidytext::reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
 fill = test_language,
@@
 fill = "Trial type") +
-	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
+scale_x_continuous(labels = \(x) scales::percent(x, accuracy = 1)) +
 scale_y_reordered() +
@@
 #| fig-width: 10
-stimuli %>% 
-	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
-	drop_na(trial_type, semantic_category_target) %>% 
-	count(trial_type, test_language, semantic_category_target, name = "sum") %>% 
-	right_join(expand(., trial_type,  test_language,  semantic_category_target)) %>%
-	replace_na(list(sum = 0)) %>% 
-	group_by(trial_type, test_language) %>% 
-	mutate(n =  sum(sum), prop = sum/n) %>% 
-	ungroup() %>% 
+#| eval: false
+stimuli |> 
+distinct(test_language,  target,  prime, .keep_all = TRUE) |> 
+drop_na(trial_type, semantic_category_target) |> 
+count(trial_type, test_language, semantic_category_target, name = "sum") |> 
+right_join(expand(., trial_type,  test_language,  semantic_category_target)) |>
+replace_na(list(sum = 0)) |> 
+group_by(trial_type, test_language) |> 
+mutate(n =  sum(sum), prop = sum/n) |> 
+ungroup() |> 
 ggplot() +

### 2023-07-07 docs/test.qmd
Fix attrition

---
title: "Test"
format: html
---

```{r setup}
gaze_aoi_plot <- readr::read_csv("gaze_aoi_plot.csv") |> 
	dplyr::filter(timestamp > 1) |> 
	dplyr::rename(file = filename)

ojs_define(mydata = gaze_aoi_plot)
```

```{ojs}
transposed = transpose(mydata)

trial_list = Array.from(Array(32).keys()).map(d => d + 1)
id_list = Array.from(Array(185).keys()).map(d => d + 18)
age_list = ["21 months", "25 months", "30 months"]

viewof input_id = Inputs.select(id_list, {label: "Participant", value: 18})
viewof input_age = Inputs.select(age_list, {label: "Age", value: "21 months"})
viewof input_trial = Inputs.select(trial_list, {label: "Trial", value: 1})

filtered = transposed.filter(d => d.trial==input_trial && 
									d.age_group==input_age &&
									d.input_id==input_id)

viewof data_table = Inputs.table(filtered)
```

### 2023-07-07 R/models.R

@@ -1,0 +1,14 @@
+get_model_fit <- function(formula, data,...) {
+	
+	fit <- brm(
+		formula,
+		data = data,
+		iter = 1000,
+		chains = 4,
+		cores = 4,
+		file_refit = "on_change",
+		...
+	)
+	
+	return(fit)
+}

### 2023-07-07 R/utils.R

@@ -1,97 +1,0 @@
-# eyetracking utils ------------------------------------------------------------
-
-# get name dictionary 
-get_name_dictionary <- function(...) {
-	
-	col_name_changes <- c("participant" = "id",
-						  "system_time_stamp" = "time",
-						  "l_1" = "l_x",
-						  "l_2" = "l_y",
-						  "process" = "phase",
-						  "r_1" = "r_x",
-						  "r_2" = "r_y",
-						  "l_user_coord_3" = "l_user_coord_z",
-						  "r_user_coord_3" = "r_user_coord_z",
-						  "suje_num" = "id",
-						  "numtrial_lista" = "trial_num",
-						  "trial_num" = "trial_id")
-	
-	phase_name_changes <- c("GETTER" = "Getter",
-							"PRIMEIMAGE" = "Prime",
-							"TARGET_DISTRACTOR" = "Target-Distractor",
-							"prime" = "Prime",
-							"primeimage" = "Prime",
-							"target_distractor" = "Target-Distractor")
-	
-	relevant_variables <- c("id", "trial", "trial_id", "phase", "x", "y", "valid_sample")
-	
-	name_dict <- lst(col_name_changes, 
-					 phase_name_changes, 
-					 relevant_variables)
-	
-	return(name_dict)
-}
-
-fix_timestamps <- function(x) {
-	x_cols <- select(x, l_x, r_x, l_y, r_y)
-	is_any_char <- any(map_chr(x_cols, class)=="character")
-	if (is_any_char) {
-		x <- mutate(
-			x,
-			across(
-				c(l_x, r_x, l_y, r_y),
-				function(x) {
-					out <- gsub("\\.", "", x)
-					out <- gsub("^(.{1})(.*)$", "\\1.\\2", out,
-								perl = TRUE)
-					out <- as.double(out)
-					return(out)
-				}
-			)
-		)
-	}
-	return(x)
-}
-
-fix_validity <- function(x) {
-	x_cols <- select(x, l_v, r_v)
-	is_any_char <- any(map_chr(x_cols, class)=="character")
-	if (is_any_char) {
-		x <- mutate(
-			x,
-			across(
-				c(l_v, r_v),
-				function(x) {
-					out <- ifelse(!(x %in% c("0", "1")), "0", "1")
-					return(out)
-				}
-			)
-		)
-	}
[…]

### 2023-07-07 R/vocabulary.R

@@ -2,49 +2,51 @@
 get_vocabulary <- function(participants, # participants dataset (get_participants output)
 						   bvq_data
 ){
-	suppressMessages({
-		
-		# vocabulary sizes BVQ database and Cognate Priming
-		
-		participants_tmp <- select(participants, id, age_group, lp)
-		
-		to_impute <- bvq_data$vocabulary %>%
-			right_join(select(participants_tmp, id, age_group, lp),
-					   by = join_by(id, age_group)) |> 
-			rowwise() |> 
-			mutate(is_imputed = any(is.na(c_across(total_prop:te_prop)))) %>% 
-			ungroup() |> 
-			relocate(id, age_group, is_imputed)
-		
-		impute <- function(x) {
-			# index of missing observations to impute
-			x <- select(x, id, lp, age_group, ends_with("_prop"))
+	
+	# vocabulary sizes BVQ database and Cognate Priming
+	
+	participants_tmp <- select(participants, id_db, age_group, lp)
+	
+	to_impute <- bvq_data$vocabulary_comp |>
+		mutate(id_db = id) |> 
+		right_join(select(participants_tmp, id_db, age_group, lp),
+				   by = join_by(id_db, age_group)) |> 
+		rowwise() |> 
+		mutate(is_imputed = any(is.na(c_across(total_prop:te_prop)))) |> 
+		ungroup() |> 
+		relocate(id, age_group, is_imputed)
+	
+	# index of missing observations to impute
+	impute <- function(x) {
+		suppressWarnings({
+			x <- select(x, id_db, lp, age_group, ends_with("_prop"))
 			impute_index <- is.na(x)
 			impute_index[, 1:3] <- FALSE
 			
-			mice(x, 
-				 m = 5,
-				 where = impute_index,
-				 method = "pmm", 
-				 seed = 888) %>% 
-				complete() %>% 
+			mice::mice(x, 
+					   m = 5,
+					   printFlag = FALSE,
+					   where = impute_index,
+					   method = "pmm", 
+					   seed = 888) |> 
+				mice::complete() |> 
 				as_tibble()
-		}
-		
+		})
+	}
+	
 	# multiple imputation
-		imputed <- to_impute %>%
-			filter(age_group != "Other") %>% 
-			impute()
-		
-		# merge both datasets ----
-		vocabulary <- left_join(participants_tmp, imputed,
-								by = join_by(id, age_group, lp)) %>% 
[…]

### 2023-07-07 data-raw/bvq.R

@@ -1,0 +1,64 @@
+# get participants
+p <- bvq::bvq_participants()
+
+# get responses
+r <- bvq::bvq_responses(p)
+
+# get logs
+# merge participant data with questionnaire responses
+edu_dict <- c("noeducation" = "No education",
+			  "primary" = "Primary",
+			  "secondary" = "Secondary",
+			  "complementary" = "Complementary",
+			  "vocational" = "Vocational",
+			  "university" = "University")
+
+l <- bvq::bvq_logs(p, r) |> 
+	mutate(age_group = case_when(age>=19 & age<24 ~ "21 months",
+								 age>=24 & age<28 ~ "25 months",
+								 age>=28 & age<=34 ~ "30 months",
+								 TRUE ~ "Other"),
+		   age_group = as.factor(age_group),
+		   across(starts_with("edu_"), 
+		   	   function(x) {
+		   	   	factor(x, 
+		   	   		   levels = names(edu_dict),
+		   	   		   ordered = TRUE) |> 
+		   	   		as.numeric()
+		   	   }),
+		   # get maximum educational attainment of parents
+		   edu_parent = apply(cbind(edu_parent1, edu_parent2), 1,
+		   				   function(x) max(x, na.rm = FALSE)),
+		   # recode it as factor
+		   edu_parent = factor(edu_parent,
+		   					levels = 1:6, 
+		   					labels = edu_dict)) |>
+	left_join(select(p, id, time, id_exp),
+			  by = join_by(id, time)) |> 
+	distinct(id, age_group, .keep_all = TRUE) |> 
+	select(id, id_exp, time, age, age_group, lp, edu_parent)
+
+v_comp <- bvq::bvq_vocabulary(participants = p, 
+							  responses = r, 
+							  .scale = c("prop", "count")) |> 
+	dplyr::filter(type=="understands") |> 
+	inner_join(distinct(l, id, time, id_exp, age_group),
+			   by = join_by(id, time)) |> 
+	select(id, id_exp, age_group, type, matches("prop|count"))
+
+v_prod <- bvq::bvq_vocabulary(participants = p, 
+							  responses = r, 
+							  .scale = c("prop", "count")) |> 
+	dplyr::filter(type=="produces") |> 
+	inner_join(distinct(l, id, time, id_exp, age_group),
+			   by = join_by(id, time)) |> 
+	select(id, id_exp, age_group, type, matches("prop|count"))
+
[…]

### 2023-07-07 tests/testthat/test-gaze_imputed.R

@@ -1,52 +1,0 @@
-test_gaze_imputed <- function(gaze_imputed){
-	
-	test_that("gaze_imputed has the right columns", {
-		expect_equal(
-			colnames(gaze_imputed),
-			c("id",
-			  "age_group",
-			  "trial",
-			  "trial_id",
-			  "phase",
-			  "time",
-			  "valid_sample",
-			  "x",
-			  "y",
-			  "is_imputed",
-			  "filename"))
-	})
-	
-	test_that("gaze_imputed has the variable classes", {
-		expect_type(gaze_imputed$id, "character")
-		expect_equal(class(gaze_imputed$age_group), "character")
-		expect_equal(class(gaze_imputed$trial), "integer")
-		expect_type(gaze_imputed$phase, "character")
-		expect_type(gaze_imputed$time, "double")
-		expect_type(gaze_imputed$x, "double")
-		expect_type(gaze_imputed$y, "double")
-		expect_type(gaze_imputed$valid_sample, "logical")
-		expect_type(gaze_imputed$is_imputed, "logical")
-		expect_type(gaze_imputed$filename, "character")
-		
-	})
-	
-	test_that("gaze_imputed missing data is dealt with", {
-		expect_false(any(is.na(gaze_imputed$id)))
-		expect_false(any(is.na(gaze_imputed$age_group)))
-		expect_false(any(is.na(gaze_imputed$trial)))
-		expect_false(any(is.na(gaze_imputed$valid_sample)))
-		expect_false(any(is.na(gaze_imputed$is_imputed)))
-		
-	})
-	
-	test_that("gaze_imputed variables have the right values", {
-		expect_true(all(unique(gaze_imputed$age_group) %in% paste0(c(21, 25, 30), " months")))
-		expect_true(all(between(unique(gaze_imputed$trial), 0, 32)))
-		expect_true(all(unique(gaze_imputed$phase) %in% c("Prime", "Target-Distractor")))
-		expect_true(all(between(unique(gaze_imputed$time[gaze_imputed$phase=="Prime"]), 0, 1.5)))
-		expect_true(all(between(unique(gaze_imputed$time[gaze_imputed$phase=="Target-Distractor"]), 0, 2)))
-		expect_true(all(unique(gaze_imputed$valid_sample %in% c(TRUE, FALSE))))
-		expect_true(all(unique(gaze_imputed$is_imputed) %in% c(TRUE, FALSE)))
-	})
-	
-}

### 2023-07-10 docs/index.qmd
Poossible coding problem

@@
 		   attrition_participants,
-		   gaze_aoi,
+		   gaze_aoi, vocabulary,
+		   loos_aggregated, loos_timecourse,
 		   data_time, data_summary))
@@
 
-Trial-level inclusion criteria:
-
-1. Valid prime: $\text{Prime}_{LT} \geq 750 \text{ms}$ (50%)
-2. Valid test: $\text{Target}_{LT} + \text{Distractor}_{LT} \geq 1,000 \text{ms}$ (50%)
-3. Minimum 100ms looking time to target, and minimum 100ms looking time to target (5%)
-
-Participant-level inclusion criteria:
-
-4. At least two valid trial of each type (cognate, non-cognate, unrelated)
+```{r attrition-numbers}
+n_trials <- nrow(attrition_trials)
+n_sessions <- distinct(attrition_trials, id, age_group) |> 
+	nrow()
+n_participants <- distinct(attrition_trials, id) |> 
+	nrow()
+
+n_trials_prime <- attrition_trials |> 
+	filter(is_valid_gaze_prime)
+
+n_trials_test <- n_trials_prime |> 
+	filter(is_valid_gaze_test)
+
+n_trials_each <- n_trials_test |> 
+	filter(is_valid_gaze_test_each)
+
+n_trials_participant <- n_trials_each |> 
+	inner_join(filter(attrition_participants,
+					  is_valid_participant),
+			   by = join_by(id, age_group))
+
+n_sessions_valid <- attrition_participants |> 
+	filter(is_valid_participant)
+
+n_participants_valid <- n_trials_participant |> 
+	distinct(id)
+
+n_longitudinal <- count(n_sessions_valid, id, name = "sessions") |> 
+	count(sessions)
+
+n_participants_include <- read_csv("data-raw/participants.csv",
+								   show_col_types = FALSE)
+```
+
+We gathered data for `r format(n_trials, big.mark = ",")` trials from `r n_sessions` experimental sessions, provided by `r n_participants` distinct participants.
+Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach].
+We excluded trials in which the participant did not fixate the prime at least half of the time of the prime phase ($\geq$750 ms, *n* = `r format(n_trials - nrow(n_trials_prime), big.mark = ",")`), or the target and distractor during the test phase ($\geq$1,000 ms, *n* = `r format(nrow(n_trials_prime) - nrow(n_trials_test), big.mark = ",")`).
+Additionally, we also excluded trials in which the participant failed to fixate both target *and* distractor pictures for at least 100 ms (5% of the time, `r format(nrow(n_trials_test) - nrow(n_trials_each), big.mark = ",")`).
+Finally we excluded trials from experimental sessions in which the participant did not provide at least two valid trials in each of the three experimental conditions (cognate prime, non-cognate prime, and unrelated prime) which resulted in the exclusion of `r nrow(distinct(n_trials_each, id, age_group)) - nrow(n_sessions_valid)` experimental sessions and their `r nrow(n_trials_each) - nrow(n_trials_participant)` remaining trials.
+The final data set comprised `r format(sum(data_summary$.ntrials), big.mark = ",")` from `r n_sessions_valid` experimental sessions, provided by `r n_participants_valid` distinct participants.
+Of those participants, `r n_longitudinal[1]` provided data from one experimental session, `r n_longitudinal[2]` provided data from two experimental sessions, and `r n_longitudinal[1]` provided data from three experimental sessions.
+
+We defined our time window of interest from 300 ms after the onset of the test phase (target and distractor presentation) until the end of the test phase (2,000 ms).
+For each trial, we chunked the time domain into 17 time bins of 100 ms of duration.
+We then calculated, for each experimental session, time bin, and condition, participant's proportion of target and distractor fixations.
+Finally, we computed the empirical log-odds of target and distractor fixations, which we introduced in the statistical analyses as our response variable.
 
@@
 
-```{r}
-#| label: fig-prior-epred
-#| fig-width: 9
+# Results
+
+## Aggregated target looking
+
+```{r}
+#| label: tbl-loos-agreggated
+loos_aggregated |> 
+	as_tibble(.name_repair = janitor::make_clean_names) |> 
+	rownames_to_column("model") |> 
+	relocate(
+		model, 
+		matches("diff"),
+		matches("elpd_loo"),
+		matches("p_loo"), 
+		matches("looic")
+	) |>
+	mutate(across(everything(), as.numeric),
+		   model = attr(loos_aggregated, "dimnames")[[1]]) |> 
+	select(-matches("subsampling")) |> 
+	gt(rowname_col = "model") |>
+	fmt_number(is.numeric, decimals = 1) |> 
+	cols_merge_uncert(col_val = elpd_diff, col_uncert = se_diff) |> 
+	cols_merge_uncert(col_val = elpd_loo, col_uncert = se_elpd_loo) |> 
+	cols_merge_uncert(col_val = p_loo, col_uncert = se_p_loo) |> 
+	cols_merge_uncert(col_val = looic, col_uncert = se_looic) |> 
+	cols_label(model = "Model",
+			   elpd_loo = md("*ELPD*"),
+			   p_loo = md("*p*"),
+			   looic = md("*LOO-IC*"),
+			   elpd_diff = md("Difference")) |> 
+	tab_source_note(md("Pareto-*k* estimates of all models were acceptable (*k* < 0.5)"))
+
+```
+
+## Growth Curve Analysis
+
+```{r}
+#| label: tbl-loos-timecourse
+loos_timecourse |> 
+	as_tibble(.name_repair = janitor::make_clean_names) |> 
+	rownames_to_column("model") |> 
+	relocate(
+		model, 
+		matches("diff"),
+		matches("elpd_loo"),
+		matches("p_loo"), 
+		matches("looic")
+	) |>
+	mutate(across(everything(), as.numeric),
+		   model = attr(loos_timecourse, "dimnames")[[1]]) |> 
+	select(-matches("subsampling")) |> 
+	gt(rowname_col = "model") |>
+	fmt_number(is.numeric, decimals = 1) |> 
+	cols_merge_uncert(col_val = elpd_diff, col_uncert = se_diff) |> 
+	cols_merge_uncert(col_val = elpd_loo, col_uncert = se_elpd_loo) |> 
+	cols_merge_uncert(col_val = p_loo, col_uncert = se_p_loo) |> 
+	cols_merge_uncert(col_val = looic, col_uncert = se_looic) |> 
+	cols_label(model = "Model",
+			   elpd_loo = md("*ELPD*"),
+			   p_loo = md("*p*"),
+			   looic = md("*LOO-IC*"),
+			   elpd_diff = md("Difference")) |> 
+	tab_source_note(md("Pareto-*k* estimates of all models were acceptable (*k* < 0.5)"))
+
+```
+
+### Marginal means
+
+```{r}
+#| label: fig-posterior-epred
+#| fig-width: 12
+#| fig-height: 8
+nd <- expand_grid(timebin = seq(1, 17, 0.1),
+				  age_group = levels(data_time$age_group),
+				  lp = levels(data_time$lp),
+				  trial_type = levels(data_time$trial_type)) |> 
+	polypoly::poly_add_columns(timebin,
+							   degree = 3,
+							   prefix = "ot",
+							   scale_width = 1)
+
+m <- fitted(fit_timecourse_2 , newdata = nd, re_formula = NA) |> 
+	bind_cols(nd) |> 
+	mutate(across(Estimate:Q97.5, plogis))
+
+# m <- add_epred_draws(nd,
+# 					 fit_timecourse_2 ,
+# 					 ndraws = 200,
+# 					 re_formula = NA) |> 
+# 	mutate(.epred = plogis(.epred))
+
+ptlt_means <- data_time |> 
+	summarise(.logit = mean(.logit), 
+			  .by = c(id, age_group, lp, trial_type, timebin)) |> 
+	summarise(.logit = mean(.logit),
+			  .by = c(age_group, lp, trial_type, timebin))
+
+m |> 
+	ggplot(aes(timebin,
+			   Estimate,
+			   colour = trial_type,
+			   fill = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_hline(yintercept = 0.5, 
+			   size = 1,
+			   colour = "grey") +
+	geom_ribbon(aes(ymin = Q2.5,
+					ymax = Q97.5),
+				colour = NA,
+				alpha = 1/3) +
+	geom_line(linewidth = 3/4) +
+	stat_summary(fun = median, geom = "line", size = 1) +
+	geom_point(data = ptlt_means,
+			   aes(y = plogis(.logit))) +
+	labs(x = "Time (ms)",
+		 y = "Proportion of target looking time",
+		 colour = "Prime",
+		 fill = "Prime",
+		 shape = "Prime",
+		 linetype = "Trial type") +
+	scale_x_continuous(labels = \(x) format(250 + x*100, big.mark = ",")) +
+	scale_y_continuous(limits = c(0, 1)) +
+	theme(legend.position = "top",
+		  panel.grid = element_line(linetype = "dotted", colour = "grey"),
+		  panel.grid.minor = element_blank(),
+		  legend.title = element_blank())
+```
+
+# Appendix
+
+## Additional stimuli properties
+
+### Animacy
+
+```{r}
+#| label: fig-stimuli-animacy
 #| fig-height: 6
-nd <- tibble(time_bin = seq(0, 20, 0.1)) |> 
-polypoly::poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)
-
-m <- add_epred_draws(nd, fit_prior, ndraws = 50, re_formula = NA) |> 
-mutate(.epred = plogis(.epred))
-
-ggplot(m, aes(time_bin, .epred)) +
-geom_hline(yintercept = 0.5, colour = "grey", size = 1) +
-geom_line(aes(group = .draw), colour = clrs[4], size = 1, alpha = 0.5) +
-labs(x = "Time (ms)",
-y = "Proportion of target looking time") +
-scale_y_continuous(labels = percent) +
-scale_x_continuous(labels = function(x) format(x*100, big.mark = ","))
-```
-
-# Results
-
-## Attrition
-
-::: {.tabset-panel}
-
-### By participants
+animacy <- stimuli |>
+	distinct(test_language, 
+			 target, 
+			 prime, 
+			 .keep_all = TRUE) |> 
+	pivot_longer(c(is_animate_prime, is_animate_target), 
+				 names_to = "role",
+				 values_to = "is_animate") |> 
+	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) |> 
+	count(test_language,  trial_type, role, is_animate) |> 
+	drop_na(is_animate) |> 
+	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
+
+animacy |> 
+	# filter(role=="Prime") |> 
+	ggplot() +
+	aes(x = trial_type, 
+		y = n, 
+		fill = is_animate,
+		colour = is_animate) + 
+	facet_grid(test_language~role) +
+	geom_col(position = position_fill(), colour = "white", size = 0.75) +
+	geom_hline(yintercept = 0.5,  size = 1, colour = "grey") +
+	labs(title = "Prime", 
+		 x = "Trial type", 
+		 y = "# trials",
+		 colour = "Animacy", 
+		 fill = "Animacy") +
+	scale_y_continuous(labels = scales::percent) +
+	coord_flip() + 
+	theme(legend.position = "top",
+		  legend.title = element_blank(),
+		  panel.grid = element_blank(),
+		  axis.title.y = element_blank(),
+		  axis.text = element_text(size = 7),
+		  axis.text.y = element_text(hjust = 1),
+		  strip.text = element_text(size = 11))
+```
+
+### Semantic category
+
+::: {.panel-tabset}
+
+#### Prime
+
+```{r}
+#| label: fig-stimuli-category-prime
+#| fig-height: 5
+#| eval: false
+#| fig-width: 10
+stimuli |> 
+	distinct(test_language,  target,  prime, .keep_all = TRUE) |> 
+	drop_na(trial_type, semantic_category_prime) |> 
+	count(trial_type, test_language, semantic_category_prime, name = "sum") |> 
+	right_join(expand(., trial_type,
+					  test_language, 
+					  semantic_category_prime)) |>
+	replace_na(list(sum = 0)) |> 
+	group_by(trial_type, test_language) |> 
+	mutate(n =  sum(sum), prop = sum/n) |> 
+	ungroup() |> 
+	ggplot() +
+	aes(x = prop,
+		y = tidytext::reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
+		fill = test_language,
+		order = prop) + 
+	facet_wrap(test_language~trial_type,
+			   scales = "free_y",
+			   labeller = label_wrap_gen(multi_line = FALSE)) +
+	geom_col(colour = "white",
+			 position = position_dodge(),
+			 width = 1) +
+	labs(x = "% of trials",
+		 y = "Trial type",
+		 colour = "Trial type",
+		 fill = "Trial type") +
+	scale_x_continuous(labels = \(x) scales::percent(x, accuracy = 1)) +
+	scale_y_reordered() +
+	theme(legend.position = "none",
+		  legend.title = element_blank(),
+		  axis.text.y = element_text(size = 9, hjust = 1),
+		  axis.text.x = element_text(size = 8, hjust = 1),
+		  axis.title.y = element_blank(),
+		  axis.ticks.y = element_blank(),
+		  plot.caption = element_text(size = 10, hjust = 0),
+		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
+		  strip.text = element_text(size = 10))
+```
+
+#### Target
+
+```{r}
+#| label: fig-stimuli-category-target
+#| fig-height: 5
+#| fig-width: 10
+#| eval: false
+stimuli |> 
+	distinct(test_language,  target,  prime, .keep_all = TRUE) |> 
+	drop_na(trial_type, semantic_category_target) |> 
+	count(trial_type, test_language, semantic_category_target, name = "sum") |> 
+	right_join(expand(., trial_type,  test_language,  semantic_category_target)) |>
+	replace_na(list(sum = 0)) |> 
+	group_by(trial_type, test_language) |> 
+	mutate(n =  sum(sum), prop = sum/n) |> 
+	ungroup() |> 
+	ggplot() +
+	aes(x = prop,
+		y = reorder_within(semantic_category_target, desc(prop), list(trial_type, test_language)),
+		fill = test_language,
+		order = prop) + 
+	facet_wrap(test_language~trial_type,
+			   scales = "free_y",
+			   labeller = label_wrap_gen(multi_line = FALSE)) +
+	geom_col(colour = "white",
+			 position = position_dodge(),
+			 width = 1) +
+	labs(x = "% of trials",
+		 y = "Trial type",
+		 colour = "Trial type",
+		 fill = "Trial type") +
+	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
+	scale_y_reordered() +
+	theme(legend.position = "none",
+		  legend.title = element_blank(),
+		  axis.text.y = element_text(size = 9, hjust = 1),
+		  axis.text.x = element_text(size = 8, hjust = 1),
+		  axis.title.y = element_blank(),
+		  axis.ticks.y = element_blank(),
+		  plot.caption = element_text(size = 10, hjust = 0),
+		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
+		  strip.text = element_text(size = 10))
+```
+
+:::
+
+## Trial-level attrition by participant
 
@@
 
-### By stimuli properties
+### Trial-level attrition by stimuli properties
 
@@
 :::
-
-## Descriptive statistics
-
-### Aggregated target looking
-
-```{r}
-#| label: fig-descriptives-aggregated
-#| fig-width: 10
-#| fig-height: 6
-data_summary |> 
-summarise(.prop = mean(.prop),
-.by = c(id, lp, trial_type, age_group)) |> 
-ggplot(aes(trial_type, 
-.prop, 
-colour = trial_type,
-fill = trial_type)) +
-facet_grid(lp~age_group) +
-geom_hline(yintercept = 0.5, 
-size = 1, 
-colour = "grey") +
-geom_line(aes(group = id),
-colour = "grey",
-alpha = 0.25) +
-geom_dots(layout = "swarm") +
-geom_boxplot(width = 0.1,
-fill = "white", 
-colour = "black",
-outlier.colour = NA) +
-labs(x = "Trial type",
-y = "Proportion of target looking",
-colour = "Trial type", 
-fill = "Trial type") +
-scale_y_continuous(labels = \(x) scales::percent(x, accuracy = 1)) +
-theme(legend.position = "none")
-```
-
-### Time-course target looking
-
-```{r}
-#| label: fig-descriptives-time-course
-#| fig-width: 12
-#| fig-height: 8
-data_time |> 
-summarise(.logit = mean(.logit),
-.by = c(id, timebin, lp, trial_type, age_group)) |> 
-ggplot(aes(timebin, .logit,
-colour = trial_type, 
-fill = trial_type, 
-shape = trial_type)) +
-facet_grid(lp~age_group) +
-geom_hline(yintercept = 0, 
-size = 1,
-colour = "grey") +
-stat_summary(fun.data = mean_se,
-geom = "ribbon",
-colour = NA,
-alpha = 0.5) +
-stat_summary(fun = mean,
-geom = "point",
-size = 2) +
-stat_summary(fun = mean,
-geom = "line", 
-size = 0.75) +
-labs(x = "Time bin (100 ms)",
-y = "Proportion of target looking",
-colour = "Trial type", 
-fill = "Trial type", 
-shape = "Trial type") +
-scale_y_continuous(labels = \(x) scales::percent(x, accuracy = 1)) +
-scale_x_continuous(labels = \(x) format(x * 100, big.mark = ",")) +
-theme(legend.position = "top",
-legend.title = element_blank(),
-panel.grid = element_line(linetype = "dotted", 
-colour = "grey"),
-panel.grid.major = element_line(colour = "grey", 
-linetype = "dotted"))
-```
-
-## Model outputs
-
-### Model comparison
-
-```{r}
-#| label: tab-model-comparison
-loos |> 
-as_tibble(.name_repair = make_clean_names) |> 
-rownames_to_column("model") |> 
-relocate(
-model, 
-matches("diff"),
-matches("elpd_loo"),
-matches("p_loo"), 
-matches("looic")
-) |>
-mutate(across(everything(), as.numeric),
-model = attr(loos, "dimnames")[[1]]) |> 
-select(-matches("subsampling")) |> 
-gt(rowname_col = "model") |>
-fmt_number(is.numeric, decimals = 1) |> 
-cols_merge_uncert(col_val = elpd_diff, col_uncert = se_diff) |> 
-cols_merge_uncert(col_val = elpd_loo, col_uncert = se_elpd_loo) |> 
-cols_merge_uncert(col_val = p_loo, col_uncert = se_p_loo) |> 
-cols_merge_uncert(col_val = looic, col_uncert = se_looic) |> 
-cols_label(model = "Model",
-elpd_loo = md("*ELPD*"),
-p_loo = md("*p*"),
-looic = md("*LOO-IC*"),
-elpd_diff = md("Difference")) |> 
-tab_source_note(md("Pareto-*k* estimates of all models were acceptable (*k* < 0.5)")) |> 
-tab_style(cell_text(weight = "bold"),
-cells_column_labels()) |> 
-tab_style(cell_fill(color = "grey", alpha = 0.5),
-cells_body(matches("diff"))) |> 
-tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-cells_body(everything(), 1))
-```
-
-### Fixed effects
-
-::: {.panel-tabset}
-
-#### Table
-
-```{r}
-#| label: tbl-fixed-effects
-#| tbl-cap: "Summary of the posterior distribution of the Growth Curve Analysis model.
-We report the median and 95% highest density interval (*HDI*) of each fixed coefficient.
-The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability.
-Values are in *logit* scale.
-Coefficients whose 95% HDI excludes zero are highlighted in red.
-Coefficients on the intercept indicate changes in overal proportion of target looking, coefficients in the linear term indicate changes in the overall slope of target looking growth across time, coefficients in the quadratic and cubic terms reflect the steepness of the rise and fall or of the rise, fall and rise, respectivey,  of the curve."
-post_draws <- gather_draws(fit_3, `b_.*`, regex = TRUE)
-
-str_repl <- c(
-"b_Intercept" = "Base",
-"b_ot1" = "Base",
-"b_ot2" = "Base",
-"b_ot3" = "Base",
-"b_age_group21_25" = "Age [21-25]",
-"b_age_group25_30" = "Age [25-30]",
-"b_lpmon_bil" = "Group",
-"b_trial_typerelated_unrelated" = "Prime (R)",
-"b_trial_typecognate_noncognate" = "Prime (C)",
-
-"b_age_group21_25:lpmon_bil" = "Age [21-25] × Group",
-"b_age_group25_30:lpmon_bil" = "Age [25-30] × Group",
-"b_age_group21_25:trial_typerelated_unrelated" = "Age [21-25] × Prime (R)",
-"b_age_group21_25:trial_typecognate_noncognate" = "Age [21-25] × Prime (C)",
-"b_age_group25_30:trial_typerelated_unrelated" = "Age [25-30] × Prime (R)",
-"b_age_group25_30:trial_typecognate_noncognate" = "Age [25-30] × Prime (C)",
-"b_lpmon_bil:trial_typerelated_unrelated" = "Group × Prime (R)",
-"b_lpmon_bil:trial_typecognate_noncognate" = "Group × Prime (C)",
-
-"b_age_group21_25:lpmon_bil:trial_typerelated_unrelated" = "Age [21-25] × Group × Prime (R)",
-"b_age_group21_25:lpmon_bil:trial_typecognate_noncognate" = "Age [21-25] × Group × Prime (C)",
-"b_age_group25_30:lpmon_bil:trial_typerelated_unrelated" = "Age [25-30] × Group × Prime (R)",
-"b_age_group25_30:lpmon_bil:trial_typecognate_noncognate" = "Age [25-30] × Group × Prime (C)"
-)
-
-post_draws |> 
-median_hdi() |>
-mutate(poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
-str_detect(.variable, "ot2") ~ "Quadratic",
-str_detect(.variable, "ot3") ~ "Cubic",
-TRUE ~ "Intercept"),
-.variable_name = case_when(.variable %in% paste0("b_ot", 1:3) ~ .variable,
-TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) |> 
-factor(levels = names(str_repl),
-label = str_repl,
-ordered = TRUE),
-type = case_when(.variable_name %in% str_repl[1:9] ~ "Main effect",
-.variable_name %in% str_repl[10:17] ~ "Two-way interactions",
-.variable_name %in% str_repl[18:length(str_repl)] ~ "Three-way interactions")) |>
-select(.variable_name, type, poly, .value:.upper) |>
-arrange(.variable_name) |> 
-pivot_wider(names_from = poly, 
-values_from = is.numeric,
-id_cols = c(.variable_name, type),
-values_fill = NA,
-names_repair = make_clean_names) |> 
-relocate(variable_name, starts_with("value_")) |> 
-gt(rowname_col = "variable_name",
-groupname_col = "type") |> 
-fmt_number(is.numeric) |>
-tab_spanner("Intercept", matches("intercept")) |> 
-sub_missing(everything(), rows = everything(), missing_text = "--") |> 
-tab_spanner("Linear", matches("linear")) |> 
-tab_spanner("Quadratic", matches("quadratic")) |> 
-tab_spanner("Cubic", matches("cubic")) |> 
-cols_merge(c(lower_intercept, upper_intercept), pattern = "[{1}, {2}]") |> 
-cols_merge(c(lower_linear, upper_linear), pattern = "[{1}, {2}]") |> 
-cols_merge(c(lower_quadratic, upper_quadratic), pattern = "[{1}, {2}]") |> 
-cols_merge(c(lower_cubic, upper_cubic), pattern = "[{1}, {2}]") |>
-cols_label(value_intercept = md("b"),
-lower_intercept = md("95% *HDI*"),
-value_linear = md("b"),
-lower_linear = md("95% *HDI*"),
-value_quadratic = md("b"),
-lower_quadratic = md("95% *HDI*"),
-value_cubic = md("b"),
-lower_cubic = md("95% *HDI*")) |> 
-tab_style(cell_text(align = "left", indent = px(10)),
-cells_stub()) |> 
-tab_style(cell_fill(color = "grey90"),
-cells_body(matches("value"))) |> 
-tab_style(cell_text(weight = "bold"),
-cells_column_spanners()) |> 
-tab_style(cell_text(weight = "bold"),
-cells_row_groups()) |> 
-tab_style(cell_text(style = "oblique"),
-cells_column_labels(columns = matches("value"))) |> 
-tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-cells_body(columns = value_intercept, 
-rows = (upper_intercept < 0) | (lower_intercept > 0))) |> 
-tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-cells_body(columns = value_linear, 
-rows = (upper_linear < 0) | (lower_linear > 0))) |>
-tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-cells_body(columns = value_quadratic, 
-rows = (upper_quadratic < 0) | (lower_quadratic > 0))) |>
-tab_style(cell_fill(color = clrs[4], alpha = 0.75),
-cells_body(columns = value_cubic, 
-rows = (upper_cubic < 0) | (lower_cubic > 0))) |> 
-tab_style(cell_text(size = "small"), 
-list(cells_body(), cells_stub())) |> 
-tab_footnote("Sum-coded contrast between 21 and 25 month old participants.",
-cells_stub(rows = 2)) |> 
-tab_footnote("Sum-coded contrast between 25 and 30 month old participants.",
-cells_stub(rows = 3)) |> 
-tab_footnote("Sum-coded contrast between monolingual and bilingual participants.",
-cells_stub(rows = 4)) |> 
-tab_footnote("Sum-coded contrast between related (cognate and non-cognate) and unrelated trials",
-cells_stub(rows = 5)) |> 
-tab_footnote("Sum-coded contrast between cognate and non-cognate trials",
-cells_stub(rows = 6))
-```
-
-#### Plot
-
-```{r}
-#| label: fig-fixed-effects
-#| fig-height: 7
-#| fig-width: 13
-#| fig-cap: "Summary of the posterior of the Growth Curve Analysis model.
-We report the median and 95% highest density interval (*HDI*) of each fixed coefficient.
-The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability.
-Values are in *logit* scale.
-Coefficients whose 95% HDI excludes zero are highlighted in red.
-Summary of the posterior distribution of the Growth Curve Analysis model.
-We report the median and 95% highest density interval (*HDI*) of each fixed coefficient.
-The 95% interval indicates the range of values that contains the true value of the parameter with 95% probability.
-Values are in *logit* scale.
-Coefficients whose 95% HDI excludes zero are highlighted in red.
-Coefficients on the intercept indicate changes in overal proportion of target looking, coefficients in the linear term indicate changes in the overall slope of target looking growth across time, coefficients in the quadratic and cubic terms reflect the steepness of the rise and fall or of the rise, fall and rise, respectivey,  of the curve."
-post_draws |> 
-median_hdi() |>
-mutate(poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
-str_detect(.variable, "ot2") ~ "Quadratic",
-str_detect(.variable, "ot3") ~ "Cubic",
-TRUE ~ "Intercept") |> 
-factor(levels = c("Intercept", "Linear", "Quadratic", "Cubic")),
-.variable_name = case_when(.variable %in% paste0("b_ot", 1:3) ~ .variable,
-TRUE ~ str_remove_all(.variable, "ot1\\:|ot2\\:|ot3\\:")) |> 
-factor(levels = names(str_repl),
-label = str_repl,
-ordered = TRUE),
-type = case_when(.variable_name %in% str_repl[1:9] ~ "Main effect",
-.variable_name %in% str_repl[10:17] ~ "Two-way interactions",
-.variable_name %in% str_repl[18:length(str_repl)] ~ "Three-way interactions"),
-excludes_zero = ifelse((.lower > 0) | (.upper < 0), "Yes", "No")) |>
-select(.variable_name, type, poly, .value:.upper, excludes_zero) |>
-arrange(.variable_name) |> 
-ggplot(aes(x = .value, y = fct_rev(.variable_name), 
-colour = excludes_zero,
-xmin = .lower, xmax = .upper)) +
-facet_wrap(~poly, scales = "free_x", nrow = 1) +
-geom_vline(xintercept = 0, colour = "grey", size = 1) +
-geom_errorbar(width = 0.2, size = 0.75) +
-geom_point(size = 3) +
-labs(x = "Estimate (Logit scale)", 
-y = "Variable", 
-fill = "CrI", 
-alpha = "CrI",
-colour = "Interval excludes zero?") +
-theme(legend.position = "top",
-axis.title.y = element_blank(),
-axis.text.y = element_text(face = "plain", hjust = 1),
-panel.border = element_rect(colour = "black", fill = NA))
-```
-
-:::
-
-### Marginal means
-
-```{r}
-#| label: fig-posterior-epred
-#| fig-width: 12
-#| fig-height: 8
-nd <- expand_grid(timebin = seq(0, 20, 0.1),
-age_group = levels(data_time$age_group),
-lp = levels(data_time$lp),
-trial_type = levels(data_time$trial_type)
-) |> 
-polypoly::poly_add_columns(timebin,
-degree = 3,
-prefix = "ot",
-scale_width = 1)
-
-m <- fitted(fit_timecourse_2 , newdata = nd, re_formula = NA) |> 
-bind_cols(nd) |> 
-mutate(across(Estimate:Q97.5, plogis))
-
-m <- add_epred_draws(nd,
-fit_timecourse_2 ,
-ndraws = 200,
-re_formula = NA) |> 
-mutate(.epred = plogis(.epred))
-
-ptlt_means <- data_time |> 
-summarise(.prop = mean(.prop), 
-.by = c(id, age_group, lp, trial_type, timebin)) |> 
-summarise(.prop = mean(.prop),
-.by = c(age_group, lp, trial_type, timebin))
-
-m |> 
-ggplot(aes(timebin,
-Estimate,
-colour = trial_type,
-fill = trial_type)) +
-facet_grid(lp~age_group) +
-geom_hline(yintercept = 0.5, 
-size = 1,
-colour = "grey") +
-geom_ribbon(aes(ymin = Q2.5,
-ymax = Q97.5),
-colour = NA,
-alpha = 1/3) +
-geom_line(linewidth = 3/4) +
-# stat_summary(fun = median, geom = "line", size = 1) +
-geom_point(data = ptlt_means, aes(y = .prop)) +
-labs(x = "Time (ms)",
-y = "Proportion of target looking time",
-colour = "Prime",
-fill = "Prime",
-shape = "Prime",
-linetype = "Trial type") +
-scale_x_continuous(labels = \(x) format(250 + x*100, big.mark = ",")) +
-scale_y_continuous(limits = c(0, 1)) +
-theme(legend.position = "top",
-panel.grid = element_line(linetype = "dotted", colour = "grey"),
-panel.grid.minor = element_blank(),
-legend.title = element_blank())
-```
-
-# Appendix
-
-## Additional stimuli properties
-
-### Animacy
-
-```{r}
-#| label: fig-stimuli-animacy
-#| fig-height: 6
-animacy <- stimuli |>
-distinct(test_language, 
-target, 
-prime, 
-.keep_all = TRUE) |> 
-pivot_longer(c(is_animate_prime, is_animate_target), 
-names_to = "role",
-values_to = "is_animate") |> 
-mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) |> 
-count(test_language,  trial_type, role, is_animate) |> 
-drop_na(is_animate) |> 
-mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy |> 
-# filter(role=="Prime") |> 
-ggplot() +
-aes(x = trial_type, 
-y = n, 
-fill = is_animate,
-colour = is_animate) + 
-facet_grid(test_language~role) +
-geom_col(position = position_fill(), colour = "white", size = 0.75) +
-geom_hline(yintercept = 0.5,  size = 1, colour = "grey") +
-labs(title = "Prime", 
-x = "Trial type", 
-y = "# trials",
-colour = "Animacy", 
-fill = "Animacy") +
-scale_y_continuous(labels = scales::percent) +
-coord_flip() + 
-theme(legend.position = "top",
-legend.title = element_blank(),
-panel.grid = element_blank(),
-axis.title.y = element_blank(),
-axis.text = element_text(size = 7),
-axis.text.y = element_text(hjust = 1),
-strip.text = element_text(size = 11))
-```
-
-### Semantic category
-
-::: {.panel-tabset}
-
-#### Prime
-
-```{r}
-#| label: fig-stimuli-category-prime
-#| fig-height: 5
-#| eval: false
-#| fig-width: 10
-stimuli |> 
-distinct(test_language,  target,  prime, .keep_all = TRUE) |> 
-drop_na(trial_type, semantic_category_prime) |> 
-count(trial_type, test_language, semantic_category_prime, name = "sum") |> 
-right_join(expand(., trial_type,
-test_language, 
-semantic_category_prime)) |>
-replace_na(list(sum = 0)) |> 
-group_by(trial_type, test_language) |> 
-mutate(n =  sum(sum), prop = sum/n) |> 
-ungroup() |> 
-ggplot() +
-aes(x = prop,
-y = tidytext::reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
-fill = test_language,
-order = prop) + 
-facet_wrap(test_language~trial_type,
-scales = "free_y",
-labeller = label_wrap_gen(multi_line = FALSE)) +
-geom_col(colour = "white",
-position = position_dodge(),
-width = 1) +
-labs(x = "% of trials",
-y = "Trial type",
-colour = "Trial type",
-fill = "Trial type") +
-scale_x_continuous(labels = \(x) scales::percent(x, accuracy = 1)) +
-scale_y_reordered() +
-theme(legend.position = "none",
-legend.title = element_blank(),
-axis.text.y = element_text(size = 9, hjust = 1),
-axis.text.x = element_text(size = 8, hjust = 1),
-axis.title.y = element_blank(),
-axis.ticks.y = element_blank(),
-plot.caption = element_text(size = 10, hjust = 0),
-panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-strip.text = element_text(size = 10))
-```
-
-#### Target
-
-```{r}
-#| label: fig-stimuli-category-target
-#| fig-height: 5
-#| fig-width: 10
-#| eval: false
-stimuli |> 
-distinct(test_language,  target,  prime, .keep_all = TRUE) |> 
-drop_na(trial_type, semantic_category_target) |> 
-count(trial_type, test_language, semantic_category_target, name = "sum") |> 
-right_join(expand(., trial_type,  test_language,  semantic_category_target)) |>
-replace_na(list(sum = 0)) |> 
-group_by(trial_type, test_language) |> 
-mutate(n =  sum(sum), prop = sum/n) |> 
-ungroup() |> 
-ggplot() +
-aes(x = prop,
-y = reorder_within(semantic_category_target, desc(prop), list(trial_type, test_language)),
-fill = test_language,
-order = prop) + 
-facet_wrap(test_language~trial_type,
-scales = "free_y",
-labeller = label_wrap_gen(multi_line = FALSE)) +
-geom_col(colour = "white",
-position = position_dodge(),
-width = 1) +
-labs(x = "% of trials",
-y = "Trial type",
-colour = "Trial type",
-fill = "Trial type") +
-scale_x_continuous(labels = ~percent(., accuracy = 1)) +
-scale_y_reordered() +
-theme(legend.position = "none",
-legend.title = element_blank(),
-axis.text.y = element_text(size = 9, hjust = 1),
-axis.text.x = element_text(size = 8, hjust = 1),
-axis.title.y = element_blank(),
-axis.ticks.y = element_blank(),
-plot.caption = element_text(size = 10, hjust = 0),
-panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-strip.text = element_text(size = 10))
-```
-
-:::

### 2023-07-10 R/prepare.R

@@ -90,10 +90,10 @@ get_data_time <- function(gaze_aoi,
 get_data_summary <- function(data_time){
 	
 	data_summary <- data_time |> 
-		reframe(across(c(.prop, .logit),
-					   \(x) mean(x, na.rm = TRUE)),
-				.ntrials = unique(.ntrials),
-				.by = c(id, age_group, lp, trial_type, vocab))
+		summarise(across(c(.prop, .logit),
+						 \(x) mean(x, na.rm = TRUE)),
+				  .ntrials = first(.ntrials),
+				  .by = c(id, age_group, lp, trial_type, vocab))
 	
 	return(data_summary)
 }

### 2023-07-10 cognate-priming-app/R/vocabularyUI.R

@@ -1,18 +1,0 @@
-vocabularyUI <- function(){
-	
-	tagList(
-		# title
-		titlePanel("Vocabulary"),
-		
-		# tabs
-		tabsetPanel(
-			tabPanel("Summary"),
-			tabPanel("Total"),
-			tabPanel("L1"),
-			tabPanel("L2"),
-			tabPanel("Conceptual"),
-			tabPanel("Translation equivalents")
-		)	
-	)
-	
-}

### 2023-07-10 cognate-priming-app/ui.R

@@ -1,21 +1,0 @@
-library(shiny)
-library(here)
-library(tidyr)
-library(dplyr)
-library(ggplot2)
-
-# Define UI for application that draws a histogram
-shinyUI(
-    # Application title
-    
-    navbarPage(
-        "Cognate Priming",
-        tabPanel("Summary", summaryUI()),
-        tabPanel("Participants", participantsUI()),
-        tabPanel("Vocabulary", vocabularyUI()),
-        tabPanel("Stimuli", stimuliUI()),
-        tabPanel("Gaze data", gazeUI()),
-        tabPanel("Model outputs", modelUI()),
-        navbarMenu("More", tabPanel("Documentation"), tabPanel("Code"))
-    )
-)

### 2023-07-17 manuscript/manuscript.qmd
Update docs

--- 2023-05-03 manuscript/manuscript.qmd
@@
----
-title: "Developmental trajectories of word recognition: a priming study in bilinguals"
-editor: source
-author:
-  - name: Gonzalo Garcia-Castro
-    orcid: 0000-0002-8553-4209
-    email: gonzalo.garciadecastro@upf.edu
-    affiliations:
-      - ref: upf
-    corresponding: true
-  - name: Serene Siow
-    affiliations:
-      - ref: oxf
-  - name: Núria Sebastian-Galles
-    affiliations:
-      - ref: upf
-  - name: Kim Plunkett
-    affiliations:
-      - ref: oxf
-affiliations:
-  - id: upf
-    name: Center for Brain and Cognition, Universitat Pompeu Fabra
-  - id: oxf
-    name: Department of Experimental Psychology, University of Oxford
-
-pagetitle: Cross-linguistic similarity and  word acquisition
-abstract: "Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language (e.g., Costa et al., 2000; Thierry & Wu, 2007).
-It has been suggested that this parallel activation is already present during toddlerhood (Jardak & Byers-Heinlein, 2019; Von Holzen & Mani, 2012), but it is unclear how it impacts the developing lexicon.
-In the present study, we tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task, in which they were presented with words in their dominant language exclusively.
-In each trial, two pictures were presented side-by-side and one of them was named (target picture).
-Participants' visual preference for the named picture was taken as an indicator of word recognition.
-Each pair of pictures was preceded by the presentation of a silent image (prime picture).
-We designed three types of trials: (1) cognate trials in which prime and target labels shared phonological onset and the prime label was a cognate (e.g., flower-flor / fork), (2) non-cognate trials, in which prime and target labels shared phonological onset but the prime label was a non-cognate (e.g., frog-rana / fork), and (3) unrelated trials, in which prime and target labels did not share onset (unrelated trials; car-coche / fork).
-In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset (e.g., Mani & Plunkett, 2011).
-Additionally, under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we predicted that interference would be stronger after cognate primes (labels from both languages share phonological overlap with target word recognition) than after non-cognate primes (only the label in the target language share phonological overlap with target word recognition).
-We tested bilinguals (n = 46) and same-aged monolingual controls, n = 123) at three age points (21, 25, and 30 months) to investigate how any cross-language priming effect emerged or changed across these ages."
-thanks: "This research was supported by grants from the Spanish Ministerio de Ciencia, Innovación y Universidades (PGC2018-101831-B-I00 and PRE2019-088165), and the Catalan Government [ICREA (Catalan Institution for Research and Advanced Studies) Academia 2019 award].
-Gonzalo Garcia-Castro was supported by a fellowship of the Spanish Ministerio de Ciencia, Innovación y Universidades (FPI 2019).
-The authors declare no conflicts of interest with regard to the funding source of this study.
-We thank Xavier Mayoral, Silvia Blanch, Cristina Cuadrado, and Irina Lepadatu for their technical support.
-We also thank Cristina Dominguez, Katia Pistrin, and Nicola Gillen for their efforts in recruiting infants.
-We would like to thank the clinics Quirón and Sagrada Familia that allowed us to recruit participants in their premises.
-We also thank all families and infants who participated in the experiments.
-Data collection was half-way when the COVID-19 pandemic started.
-We would like to pay special tribute to the families that collaborated with us under these difficult circumstances."
-keywords: word recognition, cognate, vocabulary, bilingualism, eye-tracking, growth curve analysis, bayesian
-csl: assets/bibliography/apa7.csl
-bibliography: assets/bibliography/references.bib
-format:
-  pdf:
-    pdf-engine: lualatex
-    number-sections: true
-    whitespace: small
-  docx:
-  	reference-doc: assets/templates/template.docx
-linestretch: 1.5
-toc: false
-fig-dpi: 1000
-echo: false
-warning: false
 ---
 
-```{r}
+---
+
+```{r setup}
 #| label: setup
-#| include: false
+#| echo: false
+#| message: false
+#| warning: false
+# load objects -----------------------------------------------------------------
 
-tar_load_everything() # load target objects
+targets::tar_config_set(store = here::here('_targets'),
+						script = here::here('_targets.R'))
 
-# load packages
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(tibble)
-library(purrr)
-library(lubridate)
+targets::tar_load_globals()
+
+targets::tar_load(c(participants, stimuli, vocabulary,
+					attrition_trials, attrition_participants,
+					gaze_aoi,
+					data_time, data_summary))
+
+library(knitr)
+library(kableExtra)
 library(ggplot2)
 library(gt)
-library(tidybayes)
-library(brms)
-library(polypoly)
-library(tidytext)
-library(janitor)
-library(forcats)
-library(scales)
-library(patchwork)
-library(bvq)
 
-# set ggplot theme and colour palette
-theme_set(theme_custom()) # set custom ggplot theme
-clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
+# set ggplot theme and colour palette ------------------------------------------
 
-options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
-		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
-		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
-		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
-		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
-		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
+my_theme <- theme_minimal() +
+	theme(panel.grid = element_line(colour = "grey",
+									linetype = "dotted"),
+		  axis.line = element_line(colour = "black"),
+		  text = element_text(size = 12, colour = "black"),
+		  axis.text = element_text(colour = "black"))
+
+theme_set(my_theme)
+
+set.seed(888)
 
 # prepare data
-attrition <- attrition %>% 
+attrition_participant <- attrition_participants |> 
 	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
 		valid_status = case_when(
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
+			!is_valid_gaze ~ "Invalid gaze",
+			!is_valid_participant ~ "Invalid participant",
 			TRUE ~ "Valid"
@@
 
-participants <- participants %>% 
-	left_join(distinct(attrition, id, age_group, valid_participant)) %>% 
-	drop_na(id) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
+participants <- participants |> 
+	left_join(distinct(attrition_participants,
+					   id, age_group, is_valid_participant)) |> 
+	drop_na(id) |> 
+	left_join(vocabulary) |> 
+	mutate(prop_l1_c = scale(prop_l1)[,1])
 
@@
 This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I.
+Before every testing session, caretakers were asked to read and sign an informed consent form, and were given a small gift at the end of it
 
@@
 n_participants_total <- length(unique(participants$id))
-n_participants_sessions <- count(participants, id, name = "n_sessions") %>% 
-	count(n_sessions) %>% 
+n_participants_sessions <- count(participants, id, name = "n_sessions") |> 
+	count(n_sessions) |> 
 	split(.$n_sessions)
 n_sessions_total <- count(participants)
-n_sessions_age_group <- participants %>% 
-	group_by(age_group) %>% 
+n_sessions_age_group <- participants |> 
+	group_by(age_group) |> 
 	summarise(across(age, lst(mean, sd, min, max)),
 			  n = n(),
-			  .groups = "drop") %>% 
-	mutate(across(age_mean:age_max, round, 2)) %>% 
-	split(f = .$age_group) %>% 
+			  .groups = "drop") |> 
+	mutate(across(age_mean:age_max, round, 2)) |> 
+	split(f = .$age_group) |> 
 	set_names(c("age_21", "age_25", "age_30"))
-n_sessions_dominance <- count(participants, test_language) %>% 
-	split(f = .$test_language) %>% 
+n_sessions_dominance <- count(participants, test_language) |> 
+	split(f = .$test_language) |> 
 	set_names(c("catalan", "spanish"))
-n_sessions_dominance_age_group <- count(participants, age_group, test_language) %>% 
-	split(f = .$test_language) %>% 
-	set_names(c("catalan", "spanish")) %>% 
-	map(~split(., f = .$age_group) %>% 
+n_sessions_dominance_age_group <- count(participants, age_group, test_language) |> 
+	split(f = .$test_language) |> 
+	set_names(c("catalan", "spanish")) |> 
+	map(~split(., f = .$age_group) |> 
 			set_names(c("age_21", "age_25", "age_30")))
-n_sessions_lp <- participants %>% 
-	count(lp) %>% 
-	split(f = .$lp) %>% 
+n_sessions_lp <- participants |> 
+	count(lp) |> 
+	split(f = .$lp) |> 
 	set_names(c("monolingual", "bilingual"))
-n_sessions_lp_age_group <- participants %>% 
-	count(lp, age_group) %>% 
-	split(f = .$lp) %>% 
-	set_names(c("monolingual", "bilingual")) %>% 
-	map(~split(., f = .$age_group) %>% 
+n_sessions_lp_age_group <- participants |> 
+	count(lp, age_group) |> 
+	split(f = .$lp) |> 
+	set_names(c("monolingual", "bilingual")) |> 
+	map(~split(., f = .$age_group) |> 
 			set_names(c("age_21", "age_25", "age_30")))
@@
 This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
-tbl-participants-lp summarises the linguistic profile of our sample.
+@tbl-participants-lp shows a detailed description of the linguistic profile of our sample.
+
+```{r}
+#| label: tbl-participants-lp
+#| tbl-cap: "Description of language profile of test participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
+participants |> 
+	left_join(attrition_participants,
+			  by = join_by(id, 
+			  			 age_group,
+			  			 is_valid_participant)) |> 
+	filter(is_valid_participant) |> 
+	select(id, age_group, age, lp,
+		   doe_catalan, doe_spanish, test_language) |> 
+	mutate(id = paste0(id, " (", age_group, ")")) |>
+	add_count(lp, 
+			  name = "n_lp") |> 
+	add_count(age_group, 
+			  name = "n_age_group") |> 
+	pivot_longer(starts_with("doe_"),
+				 names_to = "language",
+				 values_to = "doe") |>
+	add_count(age_group,
+			  test_language,
+			  name = "n_age_test") |> 
+	mutate(language = str_to_sentence(str_remove_all(language, "doe_")),
+		   age_group = paste0(age_group, " (N = ", n_age_group, ")"),
+		   test_language = paste0("Tested in ", test_language, 
+		   					   " (N = ", n_age_test, ")"),
+		   lp = factor(lp, levels = rev(unique(lp))))  |> 
+	summarise(across(c(doe, age), lst(mean, sd)),
+			  .by = c(age_group, lp, test_language, language)) |> 
+	pivot_wider(id_cols = c(age_group, test_language),
+				names_from = c(language, lp),
+				values_from = c(matches("doe"), age_mean, age_sd),
+				names_repair = janitor::make_clean_names) |> 
+	relocate(age_group, test_language,
+			 matches("monolingual"),
+			 matches("bilingual")) |> 
+	select(-c(age_mean_spanish_monolingual,
+			  age_mean_spanish_bilingual,
+			  age_sd_spanish_monolingual,
+			  age_sd_spanish_bilingual)) |> 
+	arrange(age_group, test_language) |> 
+	gt(rowname_col = "test_language", 
+	   groupname_col = "age_group", 
+	   row_group.sep = ": ") |> 
+	tab_spanner(md("Monolingual (*N* = 162)"), matches("monolingual")) |> 
+	tab_spanner(md("Bilingual (*N* = 133)"), matches("bilingual")) |>
+	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
+	fmt_number(matches("age"), decimals = 1) |> 
+	cols_merge_uncert(col_val = age_mean_catalan_monolingual, 
+					  col_uncert = age_sd_catalan_monolingual) |> 
+	cols_merge_uncert(col_val = age_mean_catalan_bilingual, 
+					  col_uncert = age_sd_catalan_bilingual) |> 
+	cols_merge_uncert(col_val = doe_mean_catalan_monolingual,
+					  col_uncert = doe_sd_catalan_monolingual) |> 
+	cols_merge_uncert(col_val = doe_mean_catalan_bilingual,
+					  col_uncert = doe_sd_catalan_bilingual) |> 
+	cols_merge_uncert(col_val = doe_mean_spanish_monolingual, 
+					  col_uncert = doe_sd_spanish_monolingual) |> 
+	cols_merge_uncert(col_val = doe_mean_spanish_bilingual, 
+					  col_uncert = doe_sd_spanish_bilingual) |> 
+	cols_label(age_mean_catalan_monolingual = "Age (months)",
+			   age_mean_catalan_bilingual = "Age (months)",
+			   doe_mean_catalan_monolingual = "Catalan (%)",
+			   doe_mean_catalan_bilingual = "Catalan (%)",
+			   doe_mean_spanish_monolingual = "Spanish (%)",
+			   doe_mean_spanish_bilingual = "Spanish (%)") |> 
+	tab_style(cell_text(weight = "bold"),
+			  list(cells_column_spanners())) |> 
+	tab_style(cell_text(size = "medium"),
+			  list(cells_body(),
+			  	 cells_stub()))
+```
+
+We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson2004variability] developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers.
+Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
+Two weeks after being sent the link, `r table(vocabulary$is_imputed)[2]` (`r scales::percent(table(vocabulary$is_imputed)[2]/nrow(vocabulary))` families failed to provide a complete response to the BVQ.
+We imputed their vocabulary size scores using multiple imputation [@vanbuuren2018flexible].
+We used predictive mean matching to impute missing scores using participants' information about their age group and language profile.
+We obtained several receptive and expressive vocabulary size measures from each participant's vocabulary: Catalan vocabulary size (proportion of the words in the Catalan checklist reported as acquired), Spanish vocabulary size (proportion of the words in the Catalan checklist reported as acquired), and total vocabulary size (proportion of the words in both checklists reported as acquired).
+@tbl-participants-vocabulary shows a detailed description of participants' observed and imputed vocabulary size scores.
+
+```{r tbl-participants-vocabulary}
+participants |> 
+	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"),
+		   cat_prop = ifelse(test_language=="Catalan",
+		   				  l1_prop, 
+		   				  l2_prop),
+		   spa_prop = ifelse(test_language=="Spanish",
+		   				  l1_prop,
+		   				  l2_prop)) |> 
+	select(id, age_group, lp, matches("prop"), is_imputed,
+		   -c(matches("l1|l2"), starts_with("te_"))) |> 
+	summarise(across(matches("prop"), lst(mean, sd)),
+			  .by = c(age_group, lp, is_imputed)) |> 
+	pivot_wider(names_from = is_imputed,
+				values_from = matches("prop"),
+				names_repair = janitor::make_clean_names) |> 
+	select(-matches("concept")) |> 
+	arrange(age_group, lp) |> 
+	gt(rowname_col = "lp",
+	   groupname_col = "age_group") |> 
+	fmt_number(matches("prop"), 
+			   decimals = 1,
+			   scale_by = 100) |> 
+	cols_merge(c(total_prop_mean_observed,
+				 total_prop_sd_observed), 
+				 pattern = "{1} ({2})") |> 
+	cols_merge(c(total_prop_mean_imputed, 
+				 total_prop_sd_imputed),
+				 pattern = "{1} ({2})") |> 
+	cols_merge(c(cat_prop_mean_observed,
+				 cat_prop_sd_observed),
+				 pattern = "{1} ({2})") |> 
+	cols_merge(c(cat_prop_mean_imputed, 
+				 cat_prop_sd_imputed),
+				 pattern = "{1} ({2})") |> 
+	cols_merge(c(spa_prop_mean_observed,
+				 spa_prop_sd_observed),
+				 pattern = "{1} ({2})") |> 
+	cols_merge(c(spa_prop_mean_imputed,
+				 spa_prop_sd_imputed),
+				 pattern = "{1} ({2})") |> 
+	tab_spanner("Total", matches("total")) |> 
+	tab_spanner("Catalan", matches("cat")) |> 
+	tab_spanner("Spanish", matches("spa")) |> 
+	cols_label(total_prop_mean_observed = "Observed",
+			   cat_prop_mean_observed = "Observed",
+			   spa_prop_mean_observed = "Observed",
+			   total_prop_mean_imputed = "Imputed",
+			   cat_prop_mean_imputed = "Imputed",
+			   spa_prop_mean_imputed = "Imputed") |> 
+	tab_style(cell_text(weight = "bold"),
+			  list(cells_column_spanners())) |> 
+	tab_style(cell_text(size = "medium"),
+			  list(cells_body(),
+			  	 cells_stub()))
+```
 
@@
 
+### Data processing
+
+```{r attrition-numbers}
+n_trials <- nrow(attrition_trials)
+n_sessions <- distinct(attrition_trials, id, age_group) |> 
+	nrow()
+n_participants <- distinct(attrition_trials, id) |> 
+	nrow()
+
+n_trials_prime <- attrition_trials |> 
+	filter(is_valid_gaze_prime)
+
+n_trials_test <- n_trials_prime |> 
+	filter(is_valid_gaze_test)
+
+n_trials_each <- n_trials_test |> 
+	filter(is_valid_gaze_test_each)
+
+n_trials_participant <- n_trials_each |> 
+	inner_join(filter(attrition_participants,
+					  is_valid_participant),
+			   by = join_by(id, age_group))
+
+n_sessions_valid <- attrition_participants |> 
+	filter(is_valid_participant)
+
+n_participants_valid <- n_trials_participant |> 
+	distinct(id)
+
+n_longitudinal <- count(n_sessions_valid, id, name = "sessions") |> 
+	count(sessions)
+
+n_participants_include <- read_csv("data-raw/participants.csv",
+								   show_col_types = FALSE)
+```
+
+We gathered data for `r format(n_trials, big.mark = ",")` trials from `r n_sessions` experimental sessions, provided by `r n_participants` distinct participants.
+Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach].
+We excluded trials in which the participant did not fixate the prime at least half of the time of the prime phase ($\geq$750 ms, *n* = `r format(n_trials - nrow(n_trials_prime), big.mark = ",")`), or the target and distractor during the test phase ($\geq$1,000 ms, *n* = `r format(nrow(n_trials_prime) - nrow(n_trials_test), big.mark = ",")`).
+Additionally, we also excluded trials in which the participant failed to fixate both target *and* distractor pictures for at least 100 ms (5% of the time, `r format(nrow(n_trials_test) - nrow(n_trials_each), big.mark = ",")`).
+Finally we excluded trials from experimental sessions in which the participant did not provide at least two valid trials in each of the three experimental conditions (cognate prime, non-cognate prime, and unrelated prime) which resulted in the exclusion of `r nrow(distinct(n_trials_each, id, age_group)) - nrow(n_sessions_valid)` experimental sessions and their `r nrow(n_trials_each) - nrow(n_trials_participant)` remaining trials.
+The final data set comprised `r format(sum(data_summary$.ntrials), big.mark = ",")` from `r n_sessions_valid` experimental sessions, provided by `r n_participants_valid` distinct participants.
+Of those participants, `r n_longitudinal[1]` provided data from one experimental session, `r n_longitudinal[2]` provided data from two experimental sessions, and `r n_longitudinal[1]` provided data from three experimental sessions.
+
+We defined our time window of interest from 300 ms after the onset of the test phase (target and distractor presentation) until the end of the test phase (2,000 ms).
+For each trial, we chunked the time domain into 17 time bins of 100 ms of duration.
+We then calculated, for each experimental session, time bin, and condition, participant's proportion of target and distractor fixations.
+Finally, we computed the empirical log-odds of target and distractor fixations, which we introduced in the statistical analyses as our response variable.
+
+```{r} 
+#| label: tbl-attrition-group
+#| tbl-cap: "Summary of the dataset."
+attrition_trials |> 
+	left_join(select(participants, age_group, lp, id, date_test),
+			  by = join_by(id, age_group)) |> 
+	left_join(attrition_participants,
+			  by = join_by(id, age_group)) |> 
+	add_count(age_group, lp, name = "n_trials") |> 
+	summarise(valid_trial_count = sum(is_valid_trial, na.rm = TRUE),
+			  .by = c(id, lp, trial_type, date_test,
+			  		age_group, is_valid_participant, n_trials)) |> 
+	pivot_wider(names_from = trial_type, 
+				values_from = valid_trial_count, 
+				values_fill = 0,
+				names_repair = janitor::make_clean_names) |> 
+	rename(noncognate = non_cognate) |> 
+	add_count(lp, age_group) |>
+	summarise(across(c(cognate, noncognate, unrelated),
+					 lst(sum, mean, sd)),
+			  n_valid = sum(is_valid_participant),
+			  .by = c(lp, age_group, n, n_trials)) |>
+	relocate(n_valid, .after = n) |> 
+	mutate(n_prop = n_valid/n) |> 
+	arrange(age_group, lp) |> 
+	relocate(age_group, lp, n_valid, n_prop, 
+			 matches("cognate"),
+			 matches("noncognate"),
+			 matches("unrelated")) |> 
+	gt(groupname_col = "age_group",
+	   rowname_col = "lp")  |>
+	cols_hide(c(n, n_trials)) |> 
+	fmt_number(matches("_mean|_sd"), 
+			   decimals = 1) |>
+	fmt_percent(matches("_prop"),
+				decimals = 1) |> 
+	cols_merge_n_pct(col_n = n_valid, 
+					 col_pct = n_prop,
+					 autohide = TRUE)  |> 
+	tab_spanner("Non-cognate", matches("noncognate")) |>
+	tab_spanner("Cognate", starts_with("cognate")) |>
+	tab_spanner("Unrelated", matches("unrelated")) |>
+	tab_spanner("Related", matches("cognate")) |> 
+	cols_merge_uncert(col_val = cognate_mean,
+					  col_uncert = cognate_sd) |> 
+	cols_merge_uncert(col_val = noncognate_mean,
+					  col_uncert = noncognate_sd) |> 
+	cols_merge_uncert(col_val = unrelated_mean, 
+					  col_uncert = unrelated_sd) |> 
+	cols_label(age_group = "Age",
+			   n_valid = "Participants (included)",
+			   cognate_sum = "Trials",
+			   cognate_mean = "Mean ± SD",
+			   noncognate_sum = "Trials",
+			   noncognate_mean = "Mean ± SD",
+			   unrelated_sum = "Trials",
+			   unrelated_mean = "Mean ± SD") |> 
+	summary_rows(groups = TRUE,
+				 columns = where(is.integer),
+				 fns = list("Sum" = "sum"),
+				 fmt = fmt_number,
+				 decimals = 0) |>
+	summary_rows(groups = TRUE,
+				 columns = c(where(is.numeric), -n_valid),
+				 fns = list("Mean" = "mean"),
+				 fmt = fmt_number,
+				 decimals = 1) |>
+	grand_summary_rows(columns = where(is.integer),
+					   fns = list("N" = "sum"),
+					   formatter = fmt_integer) 
+```
+
 # Results

### 2023-07-17 src/visualisation.R

@@ -1,0 +1,516 @@
+# functions
+make_plots_gaze <- function(gaze_aoi, 
+							aoi_coords,
+							participants,
+							stimuli,
+							attrition_trials,
+							attrition_participants){
+	
+	files <- unique(gaze_aoi$filename[!is.na(gaze_aoi$filename)])
+	n_files <- length(files)
+	
+	i <- 0
+	pb_msg <- "{pb_spin} Plotting {pb_current}/{pb_total} | {col_blue(pb_percent)}"
+	cli_progress_bar("Plotting",
+					 total = n_files, 
+					 format = pb_msg)
+	
+	attrition_trials$is_valid_trial <- ifelse(
+		is.na(attrition_trials$is_valid_vocab),
+		attrition_trials$is_valid_gaze_test & 
+			attrition_trials$is_valid_gaze_test_each,
+		attrition_trials$is_valid_trial
+	)
+	
+	plot_data <- get_plot_data(gaze_aoi,
+							   attrition_trials,
+							   attrition_participants)
+	
+	plot_data_split <- plot_data |> 
+		group_split(filename) |> 
+		set_names(files)
+	
+	for (i in 1:n_files) {
+		
+		plot <- plot_gaze_data(plot_data_split[[i]], files[i])
+		
+		file_name <- gsub(".csv", ".png", files[i])
+		plot_height <- length(unique(plot_data_split[[i]]$trial))*0.75
+		
+		ggsave(paste0("img/01_raw/", file_name),
+			   plot = plot, 
+			   height = plot_height,
+			   width = 6)
+		
+		cli_progress_update()
+	}
+	cli_progress_done(result = "done")
+}
+
+get_plot_data <- function(gaze_aoi,
+						  attrition_trials, 
+						  attrition_participant) {
+	
+	plot_data <- gaze_aoi |> 
+		left_join(attrition_trials,
+				  by = join_by(id, age_group, trial, trial_type)) |> 
+		left_join(attrition_participants,
+				  by = join_by(id, age_group)) |> 
+		left_join(select(participants, id, filename, test_language, list, version),
+				  by = join_by(id, filename)) |> 
+		mutate(target_y = ifelse(target_location=="l", 
+								 mean(c(aoi_coords$left[["xmin"]],
+								 	   aoi_coords$left[["xmax"]])), 
+								 mean(c(aoi_coords$right[["xmin"]],
+								 	   aoi_coords$right[["xmax"]]))), 
[…]

### 2023-07-17 docs/dashboard.qmd
Make dashboard in Quarto

---
title: "Dashboard"
format: html
server: shiny
echo: false
warning: false
message: false
---

```{r setup}
# load target objects
library(tidyverse)
library(ggdist)

plot_data <- readRDS(here::here("docs", "plot_data.rds"))

# set ggplot theme and colour palette
theme_set(theme_ggdist() + 
		  	theme(text = element_text(size = 15),
		  		  legend.position = "top",
		  		  legend.key = element_rect(fill = NA),
		  		  legend.title = element_text(size = 10),
		  		  axis.text.x = element_text(size = 6.5),
		  		  axis.text.y = element_text(size = 4.5),
		  		  panel.border = element_rect(fill = NA, colour = "grey"),
		  		  panel.grid.major.x = element_line(colour = "grey", 
		  		  								  linetype = "dotted",
		  		  								  linewidth = 0.25),
		  		  plot.title = element_text(size = 10),
		  		  strip.text = element_text(size = 6),
		  		  strip.background = element_rect(fill = "white",
		  		  								colour = NA),
		  		  strip.text.y = element_text(angle = 0)))

clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")

options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
```

## Eye-tracker data

This visualisation shows participants gaze coordinates in the X and Y dimensions across the time course of each trial. Black points indicate observed samples, while red points indicate imputed samples. Grey rectangles indicate the coordinates of the areas of interest in the trial phase displayed: `center` during the prime phase, and `right` (top) and `left` (bottom) in the test phase. Gaze samples within X and Y AOI coordinates indicate that the participant was fixating such AOI at that specific time point. The location of the target picture during the test phase in each trial is indicated with a capital *T* within the AOI rectangle.

```{r prepare-input}
#| eval: true
#| panel: sidebar
id_age_group_choices <- unique(plot_data$id_age_group, decreasing = TRUE)

selectInput("id_age_group", "Participant", 
			choices = id_age_group_choices,
			selected = last(id_age_group_choices))

selectInput("trial", "Trial", 
			choices = 1:32,
			selected = 1)

selectInput("phase", "Trial phase", 
			choices = c("Prime" = "Prime", 
						"Test" = "Target"),
			selected = "Target")

textOutput("gaze_plot_valid_phase")
textOutput("gaze_plot_valid_gaze")
textOutput("gaze_plot_valid_vocab")
textOutput("gaze_plot_valid_trial")
textOutput("gaze_plot_valid_participant")

```

```{r show-output}
#| eval: true
#| panel: fill
plotOutput("gaze_plot")
```

```{r}
#| context: server
#| standalone: true
#| fig-width: 7
#| fig-height: 4
output$gaze_plot_valid_phase <- renderText({
	value <- selectedData() |> 
		filter(dim=="x",
			   timestamp==0) |> 
		mutate(is_phase_valid = case_when(
			is_phase_valid ~ "Valid phase",
			!is_phase_valid ~ "Invalid phase")
		) |> 
		pull(is_phase_valid)
})

output$gaze_plot_valid_gaze <- renderText({
	value <- selectedData() |> 
		filter(dim=="x",
			   timestamp==0) |> 
		mutate(is_valid_gaze = case_when(
			is_valid_gaze ~ "Valid gaze",
			!is_valid_gaze ~ "Invalid gaze")
		) |> 
		pull(is_valid_gaze)

})

output$gaze_plot_valid_vocab <- renderText({
	value <- selectedData() |> 
		filter(dim=="x",
			   timestamp==0) |> 
		mutate(is_valid_vocab = case_when(
			is_valid_vocab ~ "Valid vocabulary",
			!is_valid_vocab ~ "Invalid vocabulary",
			is.na(is_valid_vocab) ~ "Missing vocabulary")
		) |> 
		pull(is_valid_vocab)

})

output$gaze_plot_valid_trial <- renderText({
	value <- selectedData() |> 
		filter(dim=="x",
			   timestamp==0) |>
		mutate(is_valid_trial = case_when(
			is_valid_trial ~ "Valid trial",
			!is_valid_trial ~ "Invalid trial",
			is.na(is_valid_trial) ~ "Invalid trial")) |> 
		pull(is_valid_trial)

})

output$gaze_plot_valid_participant <- renderText({
	selectedData() |> 
		filter(dim=="x") |> 
		distinct(is_valid_participant) |> 
		mutate(is_valid_participant = case_when(
			is_valid_participant ~ "Valid participant",
			!is_valid_participant ~ "Excluded participant")) |> 
		pull(is_valid_participant)

})

aoi_coords <- list(center = c(xmin = 710, xmax = 1210, ymin = 290, ymax = 790),
				   left = c(xmin = 180, xmax = 680, ymin = 290, ymax = 790),
				   right = c(xmin = 1240, xmax = 1740, ymin = 290, ymax = 790))

get_aois_viz <- function(aoi_coords) {
	ymin_coords <- c(
		aoi_coords$center["xmin"], 
		aoi_coords$center["ymin"], 
		aoi_coords$right["xmin"], 
		aoi_coords$right["ymin"], 
		aoi_coords$left["xmin"], 
		aoi_coords$left["ymin"]
	)

	ymax_coords <- c(
		aoi_coords$center["xmax"],
		aoi_coords$center["ymax"],
		aoi_coords$right["xmax"],
		aoi_coords$right["ymax"],
		aoi_coords$left["xmax"],
		aoi_coords$left["ymax"]
	)

	aois <- tibble(
		phase = rep(c("Prime", "Target", "Target"), each = 2),
		dim = rep(c("x", "y"), each = 1, times = 3),
		xmin = -Inf,
		xmax = -Inf,
		ymin = ymin_coords,
		ymax = ymax_coords
	) |> 
		distinct(pick(everything()))

	aois$phase_dim <- paste0(aois$phase, " - ", aois$dim)

	return(aois)
}

aois <- get_aois_viz(aoi_coords)

dummy_data <- tibble(dim = c("x", "y"),
					 ymin = c(0, 0),
					 ymax = c(1920, 1080)) |> 
	expand_grid(phase = c("Prime", "Target")) |> 
	mutate(phase_dim = paste0(phase, " - ", dim))

selectedData <- reactive({
	rowindex <- which(plot_data$id_age_group==input$id_age_group &
					  	plot_data$trial==as.integer(input$trial) &
					  	plot_data$phase==input$phase)
	plot_data[rowindex, ] 
	# filter(id_age_group=="100 (30 months)",
	# 	   trial==as.integer("1"),
	# 	   phase=="Target") |> 
})

output$gaze_plot <- renderPlot({

	ggplot(selectedData(),
		   aes(x = timestamp,
		   	y = value, 
		   	colour = is_imputed)) + 
		facet_wrap(~ dim,
				   ncol = 1,
				   scales = "free_y",
				   labeller = label_wrap_gen(multi_line = FALSE)) +
		geom_blank(data = dummy_data,
				   aes(xmin = 0,
				   	xmax = 2,
				   	ymin = ymin,
				   	ymax = ymax),
				   inherit.aes = FALSE) + 
		geom_vline(xintercept = 0.3, 
				   linewidth = 0.25,
				   colour = "grey") +
		geom_rug(data = filter(selectedData(), 
							   is_gaze_target,
							   phase=="Target"),
				 length = unit(0.1, "cm"),
				 sides = "t",
				 colour = "mediumspringgreen") +
		geom_rug(data = filter(selectedData(), 
							   is_gaze_distractor,
							   phase=="Target"),
				 length = unit(0.05, "cm"),
				 sides = "b",
				 colour = "mediumspringgreen") +
		geom_rect(data = filter(aois, phase==input$phase),
				  aes(xmin = -Inf,
				  	xmax = Inf,
				  	ymin = ymin,
				  	ymax = ymax),
				  alpha = 0.25, 
				  colour = NA,
				  inherit.aes = FALSE) +
		geom_text(aes(x = 0, 
					  y = target_y,
					  label = "T"),
				  na.rm = TRUE,
				  colour = "grey50",
				  size = 5,
				  hjust = 0.5) +
		geom_point(size = 2,
				   shape = 20, 
				   alpha = 0.5,
				   na.rm = TRUE) +
		labs(x = "Time (ms)",
			 y = "Gaze position in screen",
			 colour = "Imputed?") +
		theme_ggdist() +
		scale_colour_manual(values = c("black", "red")) +
		scale_y_continuous(breaks = c(aoi_coords$left[["xmin"]],
									  aoi_coords$left[["xmax"]],
									  aoi_coords$right[["xmin"]],
									  aoi_coords$right[["xmax"]])) +
		scale_x_continuous(limits = c(0, 2),
						   breaks = seq(0, 2, 0.5),
						   labels = function(x) {
						   	format(x * 1000,
						   		   big.mark = ",",
						   		   scientific = FALSE)
						   },
						   sec.axis = dup_axis()) +
		guides(colour = guide_legend(override.aes = list(alpha = 1,
														 size = 3)))

})
```

### 2023-07-17 docs/index.qmd
Make dashboard in Quarto

@@
 			   colour = "grey") +
-	geom_ribbon(aes(ymin = Q2.5,
-					ymax = Q97.5),
-				colour = NA,
-				alpha = 1/3) +
-	geom_line(linewidth = 3/4) +
-	stat_summary(fun = median, geom = "line", size = 1) +
+	# geom_ribbon(aes(ymin = Q2.5,
+	# 				ymax = Q97.5),
+	# 			colour = NA,
+	# 			alpha = 1/3) +
+	# geom_line(linewidth = 3/4) +
+	# stat_summary(fun = median, geom = "line", size = 1) +
 	geom_point(data = ptlt_means,

### 2023-07-17 docs/sanity-checks.qmd
Make dashboard in Quarto

---
title: "Sanity checks"
format: pdf
echo: false
message: false
warning: false
---

```{r setup}
# load target objects
targets::tar_load_globals()
targets::tar_load(c(participants, stimuli, 
					attrition_trials,
					attrition_participants,
					gaze_aoi, vocabulary,
					data_time, data_summary))

# set ggplot theme and colour palette
theme_set(theme_ggdist()) # set custom ggplot theme

clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")

options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
```

```{r fig-target-timecourse}
#| label: fig-target-timecourse
#| fig-height: 9
#| fig-width: 12
#| fig-cap: "Time course of the empirical logit of target fixations. Data are presented separately for each target picture \\(named\\), with different colours indicating data generated by participants of different age groups. Depicted data correspond to trials in which participants were reported to understand the target word in the vocabulary checklist. All other inclusion criteria have been applied. Thin lines correspond to fixation trajectories from individual participants. Each thicker line corresponds to the mean fixation trajectory of each age group."
data_time |> 
	summarise(.logit = mean(.logit), 
			  .by = c(id, target, age_group, target, timebin, trial_type)) |>
	ggplot(aes(timebin, .logit,
			   colour = age_group,
			   group = interaction(id, age_group))) +
	geom_smooth(se = FALSE, alpha = 0.15, linewidth = 0.15) +
	facet_wrap(~target) +
	geom_smooth(aes(group = age_group),
				se = FALSE,
				method = 'loess',
				formula = 'y ~ x') +
	labs(x = "Time bin (100 ms)",
		 y = "Empirical logit of target fixations\n(Target + 0.5)/(Distractor + 0.5)",
		 colour = "Age group",
		 fill = "Age group")
```

### 2023-08-03 _targets.R
Clean git

@@ -98,16 +98,13 @@ list(
 	
 	# join datasets
 	# see R/01_participants.R for details on this function
-	tar_target(participants_file,
-			   "data-raw/participants.csv",
-			   format = "file"),
+	tar_target(participants_file, "data-raw/participants.csv", format = "file"),
 	tar_target(participants, get_participants(participants_file)),
 	tar_target(participants_test, test_participants(participants)),
 	
 	# vocabulary ---------------------------------------------------------------
 	
 	tar_target(vocabulary,
-			   # see R/02_vocabulary.R for details on this function
 			   get_vocabulary(participants = participants, 
 			   			   bvq_data = bvq_data)),
 	tar_target(vocabulary_test, test_vocabulary(vocabulary)),
@@ -127,22 +124,14 @@ list(
 			   ), 
 			   format = "file"),
 	
-	tar_target(
-		gaze_raw,
-		get_gaze_raw(gaze_files)
-	),
+	tar_target(gaze_raw, get_gaze_raw(gaze_files)),
+	tar_target(gaze_raw_test, test_gaze_raw(gaze_raw)),
 	
 	tar_target(gaze_processed, get_gaze_processed(gaze_raw)),
-	# tar_target(
-	# 	gaze_raw_test,
-	# 	test_gaze_raw(gaze_raw)
-	# ),
+	tar_target(gaze_processed_test, test_gaze_processed(gaze_processed)),
 	
-	tar_target(gaze_aoi,
-			   get_gaze_aoi(gaze_processed,
-			   			 participants,
-			   			 stimuli, 
-			   			 aoi_coords)),
+	tar_target(gaze_aoi, get_gaze_aoi(gaze_processed, participants, stimuli, aoi_coords)),
+	tar_target(gaze_aoi_test, test_gaze_aoi(gaze_aoi)),
 	
 	# attrition ----------------------------------------------------------------
 	
@@ -155,17 +144,17 @@ list(
 			   		prime = 0.75, 
 			   		test = 1,
 			   		test_each = 0.1))),
-	# 
-	# tar_target(attrition_trials_test,
-	# 		   test_attrition_trials(attrition_trials)),
-	# 
+
+	tar_target(attrition_trials_test,
+			   test_attrition_trials(attrition_trials)),
+
 	tar_target(attrition_participants,
 			   get_attrition_participants(attrition_trials,
 			   						   min_trials = c(cognate = 2, 
 			   						   			   noncognate = 2,
 			   						   			   unrelated = 2))),
[…]

### 2023-09-12 docs/index.qmd
Clean git
Update

@@
 \textbf{Linear model:} \\
-logit(p) = \text{ln} \frac{p}{1-p} &= (\beta_{0} + u_{0_{i}}) + \\
-& (\beta_{1} + u_{1_{i}}) · \text{Age group}_{i} + & \\
-& \beta_{2} · \text{Language Profile}_{i} + & \\
-& (\beta_{3} + u_{2_{i}}) · \text{Trial type}_{i} + & \\
-& \beta_{4} · (\text{Age group}_{i} \times \text{Language Profile}_{i}) & \\
-& (\beta_{5} + u_{3_{i}}) · (\text{Age group}_{i} \times \text{Trial type}_{i}) + & \\
-& \beta_{6} · (\text{Language Profile}_{ij} \times \text{Trial type}_{i}) & \\
-& \beta_{7} · (\text{Age group}_{i} \times \text{Language Profile}_{i} \times \text{Trial type}_{i}) & \\
+\text{Logit}(p) = \text{ln} \frac{p}{1-p} &= (\beta_{0} + u_{0_{i}}) + (\beta_{1} + u_{1_{i}}) · \text{Age}_{i} + \beta_{2} · \text{Group}_{i} + & \\
+& (\beta_{3} + u_{2_{i}}) · \text{Condition}_{i} + \beta_{4} · (\text{Age}_{i} \times \text{Group}_{i}) & \\
+& (\beta_{5} + u_{3_{i}}) · (\text{Age}_{i} \times \text{Condition}_{i}) + \beta_{6} · (\text{Group}_{ij} \times \text{Condition}_{i}) & \\
+& \beta_{7} · (\text{Age}_{i} \times \text{Group}_{i} \times \text{Condition}_{i}) & \\
 \end{aligned}

### 2023-09-12 manuscript/manuscript.qmd
Update data-raw
Update

@@
----
-
----
-
 ```{r setup}
@@
 					attrition_trials, attrition_participants,
-					gaze_aoi,
-					data_time, data_summary))
+					bvq_data, gaze_aoi, 
+					data_time_related, data_time_cognate,
+					data_summary))
+
+targets::tar_load(c(model_fit_related_0,
+					model_fit_related_1,
+					model_fit_related_2,
+					model_fit_related_3,
+					model_fit_cognate_0,
+					model_fit_cognate_1,
+					model_fit_cognate_2,
+					model_fit_cognate_3,
+					model_loo_related,
+					model_loo_cognate))
 
@@
 library(gt)
+library(patchwork)
 
@@
 my_theme <- theme_minimal() +
-	theme(panel.grid = element_line(colour = "grey",
-									linetype = "dotted"),
+	theme(panel.grid = element_blank(),
 		  axis.line = element_line(colour = "black"),
@@
 # prepare data
-attrition_participant <- attrition_participants |> 
-	mutate(
-		valid_status = case_when(
-			!is_valid_gaze ~ "Invalid gaze",
-			!is_valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
+attrition_participants <- attrition_participants |> 
+	left_join(select(participants, id, age_group, lp, filename))
+
+attrition_trials <- left_join(attrition_trials, 
+							  select(participants, id, age_group, lp, filename))
 
@@
 	left_join(distinct(attrition_participants,
-					   id, age_group, is_valid_participant)) |> 
-	drop_na(id) |> 
-	left_join(vocabulary) |> 
-	mutate(prop_l1_c = scale(prop_l1)[,1])
+					   filename, is_valid_participant)) |> 
+	drop_na(id)
 
@@
 # Introduction
+
+The formation of a mental lexicon is a critical developmental achievement for infants_ learning words allows infants to retrieve socially relevant concepts from fairly arbitrary linguistic forms embedded in speech.
+
+Learning words allows infants to access the rich world made of concepts through the recognition of fairly arbitrary linguistic forms, i.e., words. This remarkable developmental achievement is
+
+The bilingual lexicon is language-non selective.
+
+The role of cognates in lexical processing.
+
+How does language co-activation shape lexical development?
+
+Implicit naming as a paradigm to study cross-language activation. (Mani & Plunkett, 2010, 2011a).
 
@@
 n_participants_total <- length(unique(participants$id))
+
 n_participants_sessions <- count(participants, id, name = "n_sessions") |> 
 	count(n_sessions) |> 
-	split(.$n_sessions)
+	group_split(n_sessions) |> 
+	set_names(paste0("session_", 1:3))
+
 n_sessions_total <- count(participants)
+
 n_sessions_age_group <- participants |> 
@@
 			  .groups = "drop") |> 
-	mutate(across(age_mean:age_max, round, 2)) |> 
-	split(f = .$age_group) |> 
+	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
+	group_split(age_group) |> 
 	set_names(c("age_21", "age_25", "age_30"))
+
 n_sessions_dominance <- count(participants, test_language) |> 
-	split(f = .$test_language) |> 
+	group_split(test_language) |> 
 	set_names(c("catalan", "spanish"))
+
 n_sessions_dominance_age_group <- count(participants, age_group, test_language) |> 
-	split(f = .$test_language) |> 
+	group_split(test_language) |> 
 	set_names(c("catalan", "spanish")) |> 
-	map(~split(., f = .$age_group) |> 
+	map(\(x) group_split(x, age_group) |> 
 			set_names(c("age_21", "age_25", "age_30")))
+
 n_sessions_lp <- participants |> 
 	count(lp) |> 
-	split(f = .$lp) |> 
+	group_split(lp) |> 
 	set_names(c("monolingual", "bilingual"))
+
 n_sessions_lp_age_group <- participants |> 
 	count(lp, age_group) |> 
-	split(f = .$lp) |> 
+	group_split(lp) |> 
 	set_names(c("monolingual", "bilingual")) |> 
-	map(~split(., f = .$age_group) |> 
+	map(\(x) group_split(x, age_group) |> 
 			set_names(c("age_21", "age_25", "age_30")))
@@
 In total, we gathered data from `r n_sessions_total$n` testing sessions: `r n_sessions_age_group$age_21$n` at 21 months (*Mean* = `r round(n_sessions_age_group$age_21$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_21$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_21$age_min`--`r n_sessions_age_group$age_21$age_max`), `r n_sessions_age_group$age_25$n` at 25 months (*Mean* = `r round(n_sessions_age_group$age_25$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_25$age_min`--`r n_sessions_age_group$age_25$age_max`), and `r n_sessions_age_group$age_30$n` at 30 months (*Mean* = `r round(n_sessions_age_group$age_30$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_30$age_min`--`r n_sessions_age_group$age_30$age_max`).
+
+### Language profile {#sec-lp}
 
@@
 participants |> 
-	left_join(attrition_participants,
-			  by = join_by(id, 
-			  			 age_group,
-			  			 is_valid_participant)) |> 
 	filter(is_valid_participant) |> 
@@
 
+## Vocabulary size
+
+```{r vocab-values}
+n_imputed <- table(vocabulary$is_imputed)[2]
+prop_imputed <- scales::percent(n_imputed/nrow(vocabulary))
+n_pool <- nrow(bvq_data$vocabulary)
+```
+
 We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson2004variability] developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers.
 Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
-Two weeks after being sent the link, `r table(vocabulary$is_imputed)[2]` (`r scales::percent(table(vocabulary$is_imputed)[2]/nrow(vocabulary))` families failed to provide a complete response to the BVQ.
-We imputed their vocabulary size scores using multiple imputation [@vanbuuren2018flexible].
-We used predictive mean matching to impute missing scores using participants' information about their age group and language profile.
-We obtained several receptive and expressive vocabulary size measures from each participant's vocabulary: Catalan vocabulary size (proportion of the words in the Catalan checklist reported as acquired), Spanish vocabulary size (proportion of the words in the Catalan checklist reported as acquired), and total vocabulary size (proportion of the words in both checklists reported as acquired).
-@tbl-participants-vocabulary shows a detailed description of participants' observed and imputed vocabulary size scores.
 
-```{r tbl-participants-vocabulary}
-participants |> 
-	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"),
-		   cat_prop = ifelse(test_language=="Catalan",
-		   				  l1_prop, 
-		   				  l2_prop),
-		   spa_prop = ifelse(test_language=="Spanish",
-		   				  l1_prop,
-		   				  l2_prop)) |> 
-	select(id, age_group, lp, matches("prop"), is_imputed,
-		   -c(matches("l1|l2"), starts_with("te_"))) |> 
-	summarise(across(matches("prop"), lst(mean, sd)),
-			  .by = c(age_group, lp, is_imputed)) |> 
-	pivot_wider(names_from = is_imputed,
-				values_from = matches("prop"),
-				names_repair = janitor::make_clean_names) |> 
-	select(-matches("concept")) |> 
+We calculated several measures of receptive vocabulary size from each participant's vocabulary: L1 vocabulary size (proportion of words  reported as acquired in the checklist of the dominant language), L2 vocabulary size (proportion of words  reported as acquired in the checklist of the non-dominant language), total vocabulary size (proportion of the words in both checklists reported as acquired), conceptual vocabulary (proportion of concepts for which the participant was reported to have acquired at least one label, in any language), and translation equivalent vocabulary (proportion of concepts for which the participant was reported to have acquired at two labels, one in each language).
+
+`r n_imputed` (`r prop_imputed`) Families failed to provide a complete response to the BVQ within the two-week time limit, or did not provide a successful response to the questionnaire.
+For missing questionnaire responses, we imputed the vocabulary size of the participant using multiple imputation [@vanbuuren2018flexible], using the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
+We used participants age in months and their language profile (monolingual/bilingual) as predictors.
+We used the `mice` R package [@mice] to perform imputation using the Bayesian linear regression method.
+
+```{r tbl-vocabulary}
+vocabulary |> 
+	left_join(select(participants, filename, id, age_group, lp),
+			  by = join_by(filename)) |> 
+	summarise(across(matches("prop"), 
+					 tibble::lst(mean, sd, min, max)),
+			  .by = c(age_group, lp)) |>
 	arrange(age_group, lp) |> 
-	gt(rowname_col = "lp",
-	   groupname_col = "age_group") |> 
-	fmt_number(matches("prop"), 
-			   decimals = 1,
-			   scale_by = 100) |> 
-	cols_merge(c(total_prop_mean_observed,
-				 total_prop_sd_observed), 
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(total_prop_mean_imputed, 
-				 total_prop_sd_imputed),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(cat_prop_mean_observed,
-				 cat_prop_sd_observed),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(cat_prop_mean_imputed, 
-				 cat_prop_sd_imputed),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(spa_prop_mean_observed,
-				 spa_prop_sd_observed),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(spa_prop_mean_imputed,
-				 spa_prop_sd_imputed),
-				 pattern = "{1} ({2})") |> 
-	tab_spanner("Total", matches("total")) |> 
-	tab_spanner("Catalan", matches("cat")) |> 
-	tab_spanner("Spanish", matches("spa")) |> 
-	cols_label(total_prop_mean_observed = "Observed",
-			   cat_prop_mean_observed = "Observed",
-			   spa_prop_mean_observed = "Observed",
-			   total_prop_mean_imputed = "Imputed",
-			   cat_prop_mean_imputed = "Imputed",
-			   spa_prop_mean_imputed = "Imputed") |> 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) |> 
-	tab_style(cell_text(size = "medium"),
-			  list(cells_body(),
-			  	 cells_stub()))
+	gt(groupname_col = "age_group",
+	   rowname_col = "lp") |> 
+	cols_hide(lp) |> 
+	tab_spanner("Total ", matches("total")) |> 
+	tab_spanner("L1", matches("l1")) |> 
+	tab_spanner("L2", matches("l2")) |> 
+	tab_spanner("Conceptual", matches("concept")) |> 
+	tab_spanner("TE", matches("te_")) |> 
+	tab_spanner("Vocabulary size (%)", matches("prop_")) |> 
+	cols_merge_uncert(total_prop_mean, total_prop_sd) |> 
+	cols_merge_uncert(l1_prop_mean, l1_prop_sd) |> 
+	cols_merge_uncert(l2_prop_mean, l2_prop_sd) |> 
+	cols_merge_uncert(concept_prop_mean, concept_prop_sd) |> 
+	cols_merge_uncert(te_prop_mean, te_prop_sd) |> 
+	cols_merge_range(total_prop_min, total_prop_max) |> 
+	cols_merge_range(l1_prop_min, l1_prop_max) |> 
+	cols_merge_range(l2_prop_min, l2_prop_max) |> 
+	cols_merge_range(concept_prop_min, concept_prop_max) |> 
+	cols_merge_range(te_prop_min, te_prop_max) |> 
+	fmt_number(is.numeric, 
+			   drop_trailing_zeros = FALSE) |> 
+	cols_label(total_prop_mean = "Mean (SD)",
+			   total_prop_min = "Range",
+			   l1_prop_mean = "Mean (SD)",
+			   l1_prop_min = "Range",
+			   l2_prop_mean = "Mean (SD)",
+			   l2_prop_min = "Range",
+			   concept_prop_mean = "Mean (SD)",
+			   concept_prop_min = "Range",
+			   te_prop_mean = "Mean (SD)",
+			   te_prop_min = "Range") |> 
+	tab_stub_indent(rows = everything(),
+					indent = 2) |> 
+	tab_style(cell_text(align = "left"),
+			  cells_stub())
 ```
 
-## Stimuli
+### Stimuli
+
+```{r stimuli-values}
+n_words <- length(unique(with(stimuli, unlist(prime, target, distractor))))
+```
+
+We used `r n_words` distinct words included in the BVQ to create the stimuli lists.
+We created six stimuli lists: three in Catalan, and three in Spanish.
+Each list contained 32 trials, each involving a prime-target-distractor group.
+Each word played a role as either prime, *or* as target and distractor across the three lists in their corresponding language.
+For instance, the Catalan word *cadira* appeared as *prime* in the three lists, but never as *target* or *distractor*; the Catalan word *bici* appeared as *target* and *distractor* across the three lists, but never as a prime.
+Target-distractor pairings were held constant across the three lists in each language.
+For instance, in all Catalan lists the word *bici* was paired with the word *porta*.
+Target-distractor pairings were also yoked, so that each member of the same target-distractor pair appeared once as target and once as distractor in each list.
+For instance, the *bici*-*porta* paired appeared twice in each of the three Catalan lists: once with *bici* as target and *porta* as distractor, and once with *porta* as target and *bici* as distractor.
+This counterbalancing avoided participants encountering looking at the target word guided solely by that word having being named in a previous trial.
+Finally, prime words appeared only once in each list: each target-distractor pair was associated with a different prime word in both appearances.
+In each list, the same prime word was presented alongside a different target-distractor pair.
+For instance, the Catalan prime word *barret* was presented with the *bici*-*porta* target-distractor pair in one list, with the *bici*-*porta* pair in another list, and with *berenar*-*amanida* in the remaining list.
+The order of the trials was randomised across experimental session, so that each time a participant was tested, the order in which the prime-target-distractor was presented was randomised.
+Each participant was randomly assigned to one of the three list in the corresponding language (their dominant language, see @sec-lp), and always the same list across their experimental sessions in the case of a recurrent participant.
+
+In 16 of the 32 trials of the same list (henceforth *related* trials), the prime and the target words were phonologically related, sharing phonological onset (at least first phoneme).
+In the other 16 trials (*unrelated* trials), prime and target did not share phonological onset.
+8 of the 16 *related* trials included a cognate prime (*cognate* trials), and the other 8 included a non-cognate trials (*non-cognate* trials).
+A prime word was considered cognate if its Catalan and Spanish translation shared phonological onset.
+Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
+Target and distractor word pairs were phonologically unrelated (did not share phonological onset).
+Some of them shared semantic features or a taxonomic relationship.
+This is the case of words associated with especially salient referents such as animals or food.
+To avoid infants guiding their gaze to these objects based on their saliency, we paired animals and food items together.
+
+We examined the overall equivalence of the three trial types by comparing them across three variables relating to the target word: lexical frequency, word prevalence, animacy
+@tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
+Lexical frequencies were extracted from the Catalan and Spanish corpora of the CHILDES database [@reference; @reference] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@reference; @reference].
+We defined word prevalence as the proportion of same-aged infants who were reported to understand the word in the BVQ database.
+
+#### Auditory stimuli
+
+The auditory stimuli were natural exemplars of the selected target words, spoken by Catalan-Spanish proficient bilingual female speaker who was instructed to pronounce each word in a toddler-directed manner.
+Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
+We used the Audacity [@reference] and Praat [@reference] to record and edit the audio files.
+The speaker was presented with a list of words in Catalan.
+The order of the words was pseudo-randomised, and each word was produced three times in a row before moving to the next word in the list.
+After going through all the words in the list, the speaker went through the word list again generating three tokens for each word, now in an inverse order (from bottom of the list to the top).
+We then repeated the same procedure for the list of Spanish words.
+The resulting audios were manually chunked into individual word-forms.
+For each of the six tokens produced for each word, the most adequate was selected for further processing.
+The audios were then transformed to stereo by duplicating them into two channels, denoised, and finally normalised.
+The mean duration of the final audios was `r round(mean(stimuli$duration[stimuli$test_language=="Catalan"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Catalan"]), 2)`) and `r round(mean(stimuli$duration[stimuli$test_language=="Spanish"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Spanish"]), 2)`) seconds for the Catalan and Spanish lists.
+
+To make the pronunciation of the words as familiar as possible to each infant, we generated additional pronunciation variants for some words in Catalan and Spanish.
+Catalan words involving the /\textipa{L}/ phoneme in their Central Catalan variant (e.g., /\textipa{'Lu.n@}) were also recorded with such phoneme replaced by /j/ (e.g., /\textipa{'ju.n@}), a phonological process common in the Metropolitan Area of Barcelona [@reference].
+Spanish words involving the /\textipa{T}/ phoneme were also generated replacing such phoneme with /\textipa{s}/ to better accommodate Latin variants of Spanish.
+Before every experimental session, caregivers were asked to utter three written words involving the /\textipa{L}/ phoneme (in the case of participants tested in Catalan) or the /\textipa{T}/ phoneme (in the case of participants tested in Spanish).
+Each token contained the critical phoneme at onset, inter-vocalic position, and coda.
+The experimenter assigned the participant to the Catalan or Spanish stimuli list involving the closest variant to that of caregivers'.
+
+#### Visual stimuli
+
+For each word, we created a picture with a typical referent.
+
+```{r tbl-stimuli}
+#| label: tbl-stimuli
+#| tbl-cap: "Summary of stimuli properties by trial type."
+stimuli |> 
+	summarise(across(c(matches("familiarity_|freq_|animate_"), duration),
+					 tibble::lst(mean, sd, min, max)),
+			  .by = c(test_language, trial_type)) |> 
+	select(-matches("familiarity_se"), -matches("prime"),
+		   -c(is_animate_target_sd,
+		      is_animate_target_min,
+		      is_animate_target_max)) |> 
+	gt(groupname_col = "test_language",
+	   rowname_col = "list") |> 
+	tab_spanner("Prevalence (%)", matches("familiarity")) |> 
+	tab_spanner("Frequency (Zipf)", matches("freq")) |>
+	tab_spanner("Animacy (%)", matches("animate")) |> 
+	tab_spanner("Duration (s)", matches("duration")) |> 
+	fmt_number(is.numeric) |> 
+	cols_merge_range(familiarity_target_min, familiarity_target_max) |> 
+	cols_merge_range(freq_target_min, freq_target_max) |> 
+	cols_merge_range(duration_min, duration_max) |>
+	cols_merge_uncert(freq_target_mean, freq_target_sd) |> 
+	cols_merge_uncert(familiarity_target_mean, familiarity_target_sd) |> 
+	cols_merge_uncert(duration_mean, duration_sd) |> 
+	cols_label(trial_type = "",
+			   familiarity_target_mean = "Mean ± SD",
+			   # familiarity_target_sd = "SD",
+			   familiarity_target_min = "Range",
+			   freq_target_mean = "Mean ± SD",
+			   # freq_target_sd = "SD",
+			   freq_target_min = "Range",
+			   is_animate_target_mean = "",
+			   duration_mean = "Mean ± SD",
+			   # duration_sd = "SD",
+			   duration_min = "Range") 
+```
 
@@
 
-## Apparatus
+Testing took place in a sound-proof room.
+Participants sat on their caregivers' lap in a dimly lit testing booth while the experimenter conducted the experiment from outside.
+Caregivers were instructed to keep their eyes shut (to avoid recording their gaze, instead of the participant's), to be still, and to avoid interacting with the participant verbally or non-verbally.
+Participants sat at approximately 65 cm from the eye-tracker and a XX-in screen of $1929\times1080$ screen resolution.
+We used a custom Matlab XXXX script using the PsychToolbox XXX extension [@brainard] to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
+Sampling rate was set at 120 Hz.
+A 5-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
+We set a 55% grey background for the calibration and stimuli presentation.
+Auditory stimuli were presented through two loudspeakers located behind the screen, one to each side.
+The experimenter monitored the experimental from outside the room using a centrally located video camera place above the screen.
+After a successful calibration the experimenter triggered the onset of the first trial.
+Trials were presented uninterruptedly and  without intervention of the experimenter until the 32 trials were presented, or the experimental session had to be stopped because of the participant's behaviour.
+
+Each trial started with the presentation of an attention getter for 3,000 milliseconds.
+Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
+Fifty milliseconds after the offset of the prime image, an auditory label was played from the loudspeakers and, 700 milliseconds after the onset of the auditory label, the target and distractor pictures were presented side-by-side during 1,000 milliseconds until the end of the trial.
+After this, the attention getter of the next trial was immediately presented.
+Each experimental session took approximately 10 minutes.
 
@@
 n_trials <- nrow(attrition_trials)
-n_sessions <- distinct(attrition_trials, id, age_group) |> 
+
+n_sessions <- distinct(attrition_trials, filename) |> 
 	nrow()
+
 n_participants <- distinct(attrition_trials, id) |> 
@@
 
-n_trials_participant <- n_trials_each |> 
+n_trials_vocab <- n_trials_each |> 
+	filter(is_valid_vocab)
+
+n_trials_participant <- n_trials_vocab |> 
 	inner_join(filter(attrition_participants,
 					  is_valid_participant),
-			   by = join_by(id, age_group))
+			   by = join_by(filename))
 
@@
 n_participants_valid <- n_trials_participant |> 
-	distinct(id)
+	distinct(filename)
 
-n_longitudinal <- count(n_sessions_valid, id, name = "sessions") |> 
+n_longitudinal <- n_sessions_valid |> 
+	left_join(select(participants, id, age_group, filename),
+			  by = join_by(filename, id, age_group)) |> 
+	count(id, name = "sessions") |> 
 	count(sessions)
 
-n_participants_include <- read_csv("data-raw/participants.csv",
-								   show_col_types = FALSE)
+n_participants_include <- read_csv(
+	file.path("data-raw", "participants.csv"),
+	show_col_types = FALSE
+)
 ```
@@
 Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach].
-We excluded trials in which the participant did not fixate the prime at least half of the time of the prime phase ($\geq$750 ms, *n* = `r format(n_trials - nrow(n_trials_prime), big.mark = ",")`), or the target and distractor during the test phase ($\geq$1,000 ms, *n* = `r format(nrow(n_trials_prime) - nrow(n_trials_test), big.mark = ",")`).
-Additionally, we also excluded trials in which the participant failed to fixate both target *and* distractor pictures for at least 100 ms (5% of the time, `r format(nrow(n_trials_test) - nrow(n_trials_each), big.mark = ",")`).
-Finally we excluded trials from experimental sessions in which the participant did not provide at least two valid trials in each of the three experimental conditions (cognate prime, non-cognate prime, and unrelated prime) which resulted in the exclusion of `r nrow(distinct(n_trials_each, id, age_group)) - nrow(n_sessions_valid)` experimental sessions and their `r nrow(n_trials_each) - nrow(n_trials_participant)` remaining trials.
-The final data set comprised `r format(sum(data_summary$.ntrials), big.mark = ",")` from `r n_sessions_valid` experimental sessions, provided by `r n_participants_valid` distinct participants.
-Of those participants, `r n_longitudinal[1]` provided data from one experimental session, `r n_longitudinal[2]` provided data from two experimental sessions, and `r n_longitudinal[1]` provided data from three experimental sessions.
+We excluded trials in which the participant did not fixate the prime at least half of the time of the prime phase ($\geq$ 750 ms, *n* = `r format(n_trials - nrow(n_trials_prime), big.mark = ",")`), or the target and distractor during the test phase ($\geq$ 1,000 ms, *n* = `r format(nrow(n_trials_prime) - nrow(n_trials_test), big.mark = ",")`).
+We also excluded trials in which the participant failed to fixate both target *and* distractor pictures for at least 100 ms (i.e., 5% of the time) (`r format(nrow(n_trials_test) - nrow(n_trials_each), big.mark = ",")` trials excluded).
+We then excluded trials in which the participant was not reported to understand the prime *and* the target words, according to their caregivers' responses to the vocabulary checklist.
+This resulted in the exclusion of `r format(nrow(n_trials_each) - nrow(n_trials_vocab), big.mark = ",")` trials.
+Finally, we excluded trials from experimental sessions in which the participant did not provide at least two valid trials in each of the three experimental conditions (cognate prime, non-cognate prime, and unrelated prime) which resulted in the exclusion of `r nrow(distinct(n_trials_vocab, id, age_group)) - nrow(n_sessions_valid)` experimental sessions and their `r nrow(n_trials_vocab) - nrow(n_trials_participant)` remaining trials.
+The final data set comprised `r format(sum(with(attrition_trials, is_valid_trial)), big.mark = ",")` from `r nrow(n_sessions_valid)` experimental sessions, provided by `r nrow(n_participants_valid)` distinct participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
 
@@
 We then calculated, for each experimental session, time bin, and condition, participant's proportion of target and distractor fixations.
-Finally, we computed the empirical log-odds of target and distractor fixations, which we introduced in the statistical analyses as our response variable.
+Finally, we computed the empirical logit of target fixations, which we introduced in the statistical analyses as our response variable.
 
@@
 
+### Modelling approach
+
+We conducted two main analyses.
+First, we estimated the effect of phonological priming on participants' target looking, comparing *related* trials with *unrelated* trials.
+This analysis included all trials on the data set.
+Second, we estimated the effect of cognateness on phonological priming, comparing *cognate* with *non-cognate* trials, leaving out *unrelated* trials.
+In both analyses, we used General Additive Mixed Models (GAMMs) to model the probability of target fixations across the time course of the trial using a normal distribution.
+
+In the first analysis.
+We included *Relatedness* (`Related` vs.
+`Unrelated`, sum-coded as `-0.5` and `+0.5`), *Group* (`Monolingual` vs.
+`Bilingual`, sum-coded as `-0.5` and `+0.5`), and *Age* (participants' standardised age in months) as fixed, main effects.
+We also included cubic regression splines for the main effect of *Time*, and one for an adjustment of the previous cubic spline by *Group* [@wood2017generalized].
+For both splines, we specified $k = 10$ basis functions or *knots*--half the number of time bins, for computational convenience.
+Finally, we added by-participant random intercepts, and random slopes for the main effect of *Relatedness* and the main effect of *Age*, both including repeated measures per participant.
+
+To test the contribution of each of the predictors of interest--*Relatedness*/*Cognateness*, and *Group*--, we compared each model ($\mathcal{M_0}$) against a simplified model dropping each of the main effects, *Relatedness*/*Cognateness* ($\mathcal{M}_1$) or *Group* ($\mathcal{M_2}$).
+In both simplified models, the interaction term was dropped.
+We used leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it.
+We then examined the posterior predictions of the best-performing model for interpretation.
+
+$$
+\begin{aligned}
+\textbf{Likelihood:} \\
+y_i &\sim \mathcal{N}(\mu_i, \sigma_i) \\ \\
+\textbf{Linear model} \\
+\text{logit}(\mu_i) &= (\beta_0 + u _{0_{i}}) + (\beta_1 + u _{1_{i}}) \cdot \text{Relatedness} + \beta_{2} \cdot \text{Group} + \\
+&\beta_{3} \cdot (\text{Relatedness} \times \text{Group}) + (\beta_4 + u_{3_{i}}) \cdot \text{Age} + \\
+&\sum_{j = 1}^k b_{j_{1}}(\beta_{5_{k}} + u_{4_{i}}) \cdot \text{Time} + \\
+&\sum_{j = 1}^k b_{j_{1}} (\beta_{6_{k }} + u_{5_{i}}) \cdot (\text{Time} \times \text{Group}) \\
+\text{where:} \\
+&k \text{ is the number of knots in the spline (10)} \\
+\textbf{Prior:} \\
+\beta_{0-6} &\sim \mathcal{N}(0, 1) \\
+b_{0-1} &\sim MVN(0, 1) \\
+\sigma_i &\sim Exp(4) 
+\end{aligned}
+$$
+
 # Results
 
+## Phonological priming: Related vs. Unrelated
+
+A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related[2, 1], 3)`, *SE* = `r round(model_loo_related[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related[3, 1], 3)`, *SE* = `r round(model_loo_related[3, 2], 3)`).
+This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-related}
+#| label: fig-related
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_related$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_related$age),
+					  lp = levels(data_time_related$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fit_related_3,
+					ndraws = NULL,
+					re_formula = NA, 
+					value = ".value") |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .value,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = related - unrelated)
+
+diff_rect <- epreds_diff |> 
+	mean_qi(diff) |> 
+	mutate(is_cluster = .lower > 0 | .upper < 0)
+
+clusters <- rle(diff(diff_rect$is_cluster))
+diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
+
+diff_rect <- diff_rect |> 
+		arrange(lp, timebin)
+
+diff_rect <- 
+	cluster_number = 
+	summarise(xmin = min(timebin),
+			  xmax = max(timebin),
+			  .by = c(lp, is_cluster)) |> 
+	filter(is_cluster)
+
+# diff_obs <- data_time_related |>
+# 	pivot_wider(names_from = condition, 
+# 				values_from = elog,
+# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
+
+data_time_related |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition,
+			   linetype = condition)) +
+	facet_wrap(~lp) +
+	geom_rect(data = diff_rect,
+			  aes(xmin = xmin,
+			  	xmax = xmax,
+			  	ymin = -Inf,
+			  	ymax = Inf),
+			  colour = NA,
+			  fill = "orange",
+			  alpha = 1/2,
+			  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+	# 		  	group = interaction(condition, .draw)),
+	# 		  linetype = "solid",
+	# 		  alpha = 0.1,
+	# 		  linewidth = 3/4) +
+	stat_summary(data = epreds,
+				 aes(y = .value),
+				 fun.data = \(x) mean_qi(x, .width = 0.95),
+				 geom = "ribbon",
+				 alpha = 0.5,
+				 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .value,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 1/2, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	geom_rect(data = diff_rect,
+			  aes(xmin = xmin,
+			  	xmax = xmax,
+			  	ymin = -Inf,
+			  	ymax = Inf),
+			  colour = NA,
+			  fill = "orange",
+			  alpha = 1/2,
+			  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0) +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	# geom_point(data = diff_obs) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_colour_grey(start = 0.8, end = 0) &
+	scale_fill_grey(start = 0.85, end = 0.35) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
+## Cognate priming: Cognate vs. Non-cognate
+
+A model including the *Cognateness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Cognateness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate[2, 1], 3)`, *SE* = `r round(model_loo_cognate[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate[3, 1], 3)`, *SE* = `r round(model_loo_cognate[3, 2], 3)`).
+This indicates that including the *Cognateness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-cognate}
+#| label: fig-cognate
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_cognate$condition),
+					  timebin = seq(0, 20, length.out = 100),
+					  age = mean(data_time_cognate$age),
+					  lp = levels(data_time_cognate$lp)) |>
+	add_epred_draws(model_fit_cognate_3,
+					ndraws = NULL,
+					re_formula = NA) |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .epred,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = cognate - non_cognate)
+
+diff_rect <- epreds_diff |> 
+	mean_qi(diff) |> 
+	filter(.lower > 0 | .upper < 0) |> 
+	summarise(xmin = min(timebin),
+			  xmax = max(timebin),
+			  .by = lp)
+
+data_time_cognate |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_wrap(~lp) +
+	geom_rect(data = diff_rect,
+			  aes(xmin = xmin,
+			  	xmax = xmax,
+			  	ymin = -1.5,
+			  	ymax = 1.5),
+			  colour = NA,
+			  fill = "orange",
+			  alpha = 1/2,
+			  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+	# 		  	group = interaction(condition, .draw)),
+	# 		  linetype = "solid",
+	# 		  alpha = 0.1,
+	# 		  linewidth = 3/4) +
+	stat_summary(data = epreds,
+				 aes(y = .epred),
+				 fun.data = \(x) mean_qi(x, .width = 0.95),
+				 geom = "ribbon",
+				 alpha = 0.5,
+				 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .epred,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 linetype = "Prime type",
+		 shape = "Prime type") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	geom_rect(data = diff_rect,
+			  aes(xmin = xmin,
+			  	xmax = xmax,
+			  	ymin = -3/4,
+			  	ymax = 3/4),
+			  colour = NA,
+			  fill = "orange",
+			  alpha = 1/2,
+			  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0) +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_colour_grey(start = 0.8, end = 0) &
+	scale_fill_grey(start = 0.85, end = 0.35) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format(x * 1e2, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank()) 
+```
+
 # Discussion
+
+# Appendix

### 2023-09-12 manuscript/manuscript.tex
Update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{tipa}
\usepackage{booktabs}
\hyphenpenalty=100000
\exhyphenpenalty=100000
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Developmental trajectories of bilingual word recognition},
  pdfauthor={Gonzalo Garcia-Castro; Serene Siow; Nuria Sebastian-Galles; Kim Plunkett},
  pdflang={en},
  pdfkeywords={cognate, word recognition, lexicon, language
acquisition, vocabulary, bilingualism, general additive mixed
models, bayesian},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Developmental trajectories of bilingual word recognition}
\author{Gonzalo Garcia-Castro \and Serene Siow \and Nuria
Sebastian-Galles \and Kim Plunkett}
\date{}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, enhanced, interior hidden, breakable]}{\end{tcolorbox}}\fi

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The formation of a mental lexicon is a critical developmental
achievement for infants\_ learning words allows infants to retrieve
socially relevant concepts from fairly arbitrary linguistic forms
embedded in speech.

Learning words allows infants to access the rich world made of concepts
through the recognition of fairly arbitrary linguistic forms, i.e.,
words. This remarkable developmental achievement is

The bilingual lexicon is language-non selective.

The role of cognates in lexical processing.

How does language co-activation shape lexical development?

Implicit naming as a paradigm to study cross-language activation. (Mani
\& Plunkett, 2010, 2011a).

\hypertarget{methods}{%
\section{Methods}\label{methods}}

All materials, data, and reproducible code can be found at the OSF
(\href{https://osf.io/ckydb/}{https://osf.io/hy984/}) and GitHub
(\url{https://github.com/gongcastro/cognate-priming}) repositories. This
study was conducted according to guidelines laid down in the Declaration
of Helsinki, and was approved by the Drug Research Ethical Committee
(CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I. Before
every testing session, caretakers were asked to read and sign an
informed consent form, and were given a small gift at the end of it

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{n\_participants\_total }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(}\FunctionTok{unique}\NormalTok{(participants}\SpecialCharTok{$}\NormalTok{id))}

\NormalTok{n\_participants\_sessions }\OtherTok{\textless{}{-}} \FunctionTok{count}\NormalTok{(participants, id, }\AttributeTok{name =} \StringTok{"n\_sessions"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{count}\NormalTok{(n\_sessions) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{group\_split}\NormalTok{(n\_sessions) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{set\_names}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(}\StringTok{"session\_"}\NormalTok{, }\DecValTok{1}\SpecialCharTok{:}\DecValTok{3}\NormalTok{))}

\NormalTok{n\_sessions\_total }\OtherTok{\textless{}{-}} \FunctionTok{count}\NormalTok{(participants)}

\NormalTok{n\_sessions\_age\_group }\OtherTok{\textless{}{-}}\NormalTok{ participants }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{group\_by}\NormalTok{(age\_group) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(age, }\FunctionTok{lst}\NormalTok{(mean, sd, min, max)),}
              \AttributeTok{n =} \FunctionTok{n}\NormalTok{(),}
              \AttributeTok{.groups =} \StringTok{"drop"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(age\_mean}\SpecialCharTok{:}\NormalTok{age\_max, round, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{group\_split}\NormalTok{(age\_group) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{set\_names}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"age\_21"}\NormalTok{, }\StringTok{"age\_25"}\NormalTok{, }\StringTok{"age\_30"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: [1m[22mThere was 1 warning in `mutate()`.
[1m[22m[36mi[39m In argument: `across(age_mean:age_max, round, 2)`.
Caused by warning:
[1m[22m[33m![39m The `...` argument of `across()` is deprecated as of dplyr 1.1.0.
Supply arguments directly to `.fns` through an anonymous function instead.

  # Previously
  across(a:b, mean, na.rm = TRUE)

  # Now
  across(a:b, \(x) mean(x, na.rm = TRUE))
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{n\_sessions\_dominance }\OtherTok{\textless{}{-}} \FunctionTok{count}\NormalTok{(participants, test\_language) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{group\_split}\NormalTok{(test\_language) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{set\_names}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"catalan"}\NormalTok{, }\StringTok{"spanish"}\NormalTok{))}

\NormalTok{n\_sessions\_dominance\_age\_group }\OtherTok{\textless{}{-}} \FunctionTok{count}\NormalTok{(participants, age\_group, test\_language) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{group\_split}\NormalTok{(test\_language) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{set\_names}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"catalan"}\NormalTok{, }\StringTok{"spanish"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{map}\NormalTok{(\textbackslash{}(x) }\FunctionTok{group\_split}\NormalTok{(x, age\_group) }\SpecialCharTok{|\textgreater{}} 
            \FunctionTok{set\_names}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"age\_21"}\NormalTok{, }\StringTok{"age\_25"}\NormalTok{, }\StringTok{"age\_30"}\NormalTok{)))}

\NormalTok{n\_sessions\_lp }\OtherTok{\textless{}{-}}\NormalTok{ participants }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{count}\NormalTok{(lp) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{group\_split}\NormalTok{(lp) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{set\_names}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"monolingual"}\NormalTok{, }\StringTok{"bilingual"}\NormalTok{))}

\NormalTok{n\_sessions\_lp\_age\_group }\OtherTok{\textless{}{-}}\NormalTok{ participants }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{count}\NormalTok{(lp, age\_group) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{group\_split}\NormalTok{(lp) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{set\_names}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"monolingual"}\NormalTok{, }\StringTok{"bilingual"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{map}\NormalTok{(\textbackslash{}(x) }\FunctionTok{group\_split}\NormalTok{(x, age\_group) }\SpecialCharTok{|\textgreater{}} 
            \FunctionTok{set\_names}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"age\_21"}\NormalTok{, }\StringTok{"age\_25"}\NormalTok{, }\StringTok{"age\_30"}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

We collected data from 180 monolingual and bilingual participants living
in the Metropolitan Area of Barcelona (Spain), who were exposed to at
least Catalan and/or Spanish from birth. Families were recruited from
maternity room in private hospitals in Barcelona, and contacted via
phone when the child's age spanned between our age intervals of
interest. Families were invited to participate at three age points: 21,
25, and 30 months. 94 participants were tested at one age point, 56 at
two age points, and 30 at the three age points. In total, we gathered
data from 296 testing sessions: 94 at 21 months (\emph{Mean} = 20.98,
\emph{SD} = 0.97, \emph{Range} = 20--26.35), 96 at 25 months
(\emph{Mean} = 25.15, \emph{SD} = 0.99, \emph{Range} = 23.35--30.77),
and 106 at 30 months (\emph{Mean} = 29.42, \emph{SD} = 0.99,
\emph{Range} = 19.37--36.07).

\hypertarget{sec-lp}{%
\subsubsection{Language profile}\label{sec-lp}}

We assessed participants' language profile using the Language Exposure
Questionnaire (LEQ, \protect\hyperlink{ref-bosch2001evidence}{Bosch \&
Sebastián-Gallés, 2001}). Before each experimental session, the
experimenter asked the caretakers to estimate the amount of hours per
day they and other people in the infant's social circle have spent
speaking to the infant in any language since birth. The output of this
interview is an estimated degree of exposure (DoE) to each language,
indicated by the proportion of time the infant was reported to have
listened to each language. According to this estimate, we classified
participants as Catalan- or Spanish-dominant if the language with
highest DoE was Catalan or Spanish, respectively, and tested the
participant in the stimuli set that contained words in their native
language. We collected data from 178 Catalan-dominant participants in
Catalan (52 at 21 months, 62 at 25 months, and 64 at 30 months). We
further classified participants as monolinguals if the DoE to their
dominant language exceeded 80\% of the total DoE to Catalan and Spanish,
and as bilinguals otherwise. Participants with DoE to language other
than Catalan or Spanish were excluded from analyses. This divided the
sample into 162 monolinguals ( at 21 months, at 25 months, and at 30
months), and 134 bilinguals ( at 21 months, 2, 2, 44 at 25 months, and
2, 3, 46 at 30 months). Table~\ref{tbl-participants-lp} shows a detailed
description of the linguistic profile of our sample.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{participants }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{filter}\NormalTok{(is\_valid\_participant) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{select}\NormalTok{(id, age\_group, age, lp,}
\NormalTok{           doe\_catalan, doe\_spanish, test\_language) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{id =} \FunctionTok{paste0}\NormalTok{(id, }\StringTok{" ("}\NormalTok{, age\_group, }\StringTok{")"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{add\_count}\NormalTok{(lp, }
              \AttributeTok{name =} \StringTok{"n\_lp"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{add\_count}\NormalTok{(age\_group, }
              \AttributeTok{name =} \StringTok{"n\_age\_group"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{pivot\_longer}\NormalTok{(}\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"doe\_"}\NormalTok{),}
                 \AttributeTok{names\_to =} \StringTok{"language"}\NormalTok{,}
                 \AttributeTok{values\_to =} \StringTok{"doe"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{add\_count}\NormalTok{(age\_group,}
\NormalTok{              test\_language,}
              \AttributeTok{name =} \StringTok{"n\_age\_test"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{language =} \FunctionTok{str\_to\_sentence}\NormalTok{(}\FunctionTok{str\_remove\_all}\NormalTok{(language, }\StringTok{"doe\_"}\NormalTok{)),}
           \AttributeTok{age\_group =} \FunctionTok{paste0}\NormalTok{(age\_group, }\StringTok{" (N = "}\NormalTok{, n\_age\_group, }\StringTok{")"}\NormalTok{),}
           \AttributeTok{test\_language =} \FunctionTok{paste0}\NormalTok{(}\StringTok{"Tested in "}\NormalTok{, test\_language, }
                               \StringTok{" (N = "}\NormalTok{, n\_age\_test, }\StringTok{")"}\NormalTok{),}
           \AttributeTok{lp =} \FunctionTok{factor}\NormalTok{(lp, }\AttributeTok{levels =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{unique}\NormalTok{(lp))))  }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{c}\NormalTok{(doe, age), }\FunctionTok{lst}\NormalTok{(mean, sd)),}
              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(age\_group, lp, test\_language, language)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{id\_cols =} \FunctionTok{c}\NormalTok{(age\_group, test\_language),}
                \AttributeTok{names\_from =} \FunctionTok{c}\NormalTok{(language, lp),}
                \AttributeTok{values\_from =} \FunctionTok{c}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"doe"}\NormalTok{), age\_mean, age\_sd),}
                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{relocate}\NormalTok{(age\_group, test\_language,}
             \FunctionTok{matches}\NormalTok{(}\StringTok{"monolingual"}\NormalTok{),}
             \FunctionTok{matches}\NormalTok{(}\StringTok{"bilingual"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(age\_mean\_spanish\_monolingual,}
\NormalTok{              age\_mean\_spanish\_bilingual,}
\NormalTok{              age\_sd\_spanish\_monolingual,}
\NormalTok{              age\_sd\_spanish\_bilingual)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{arrange}\NormalTok{(age\_group, test\_language) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{gt}\NormalTok{(}\AttributeTok{rowname\_col =} \StringTok{"test\_language"}\NormalTok{, }
       \AttributeTok{groupname\_col =} \StringTok{"age\_group"}\NormalTok{, }
       \AttributeTok{row\_group.sep =} \StringTok{": "}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{tab\_spanner}\NormalTok{(}\FunctionTok{md}\NormalTok{(}\StringTok{"Monolingual (*N* = 162)"}\NormalTok{), }\FunctionTok{matches}\NormalTok{(}\StringTok{"monolingual"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{tab\_spanner}\NormalTok{(}\FunctionTok{md}\NormalTok{(}\StringTok{"Bilingual (*N* = 133)"}\NormalTok{), }\FunctionTok{matches}\NormalTok{(}\StringTok{"bilingual"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{fmt\_number}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"doe"}\NormalTok{), }\AttributeTok{decimals =} \DecValTok{1}\NormalTok{, }\AttributeTok{scale\_by =} \DecValTok{100}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{fmt\_number}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"age"}\NormalTok{), }\AttributeTok{decimals =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ age\_mean\_catalan\_monolingual, }
                      \AttributeTok{col\_uncert =}\NormalTok{ age\_sd\_catalan\_monolingual) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ age\_mean\_catalan\_bilingual, }
                      \AttributeTok{col\_uncert =}\NormalTok{ age\_sd\_catalan\_bilingual) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ doe\_mean\_catalan\_monolingual,}
                      \AttributeTok{col\_uncert =}\NormalTok{ doe\_sd\_catalan\_monolingual) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ doe\_mean\_catalan\_bilingual,}
                      \AttributeTok{col\_uncert =}\NormalTok{ doe\_sd\_catalan\_bilingual) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ doe\_mean\_spanish\_monolingual, }
                      \AttributeTok{col\_uncert =}\NormalTok{ doe\_sd\_spanish\_monolingual) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ doe\_mean\_spanish\_bilingual, }
                      \AttributeTok{col\_uncert =}\NormalTok{ doe\_sd\_spanish\_bilingual) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_label}\NormalTok{(}\AttributeTok{age\_mean\_catalan\_monolingual =} \StringTok{"Age (months)"}\NormalTok{,}
               \AttributeTok{age\_mean\_catalan\_bilingual =} \StringTok{"Age (months)"}\NormalTok{,}
               \AttributeTok{doe\_mean\_catalan\_monolingual =} \StringTok{"Catalan (\%)"}\NormalTok{,}
               \AttributeTok{doe\_mean\_catalan\_bilingual =} \StringTok{"Catalan (\%)"}\NormalTok{,}
               \AttributeTok{doe\_mean\_spanish\_monolingual =} \StringTok{"Spanish (\%)"}\NormalTok{,}
               \AttributeTok{doe\_mean\_spanish\_bilingual =} \StringTok{"Spanish (\%)"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{tab\_style}\NormalTok{(}\FunctionTok{cell\_text}\NormalTok{(}\AttributeTok{weight =} \StringTok{"bold"}\NormalTok{),}
              \FunctionTok{list}\NormalTok{(}\FunctionTok{cells\_column\_spanners}\NormalTok{())) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{tab\_style}\NormalTok{(}\FunctionTok{cell\_text}\NormalTok{(}\AttributeTok{size =} \StringTok{"medium"}\NormalTok{),}
              \FunctionTok{list}\NormalTok{(}\FunctionTok{cells\_body}\NormalTok{(),}
                 \FunctionTok{cells\_stub}\NormalTok{()))}
\end{Highlighting}
\end{Shaded}

\hypertarget{tbl-participants-lp}{}
\begin{longtable}{l|rrrrrr}
\caption{\label{tbl-participants-lp}Description of language profile of test participants. Data are
summarised for each age group, and for monolinguals and bilinguals
separately. }\tabularnewline

\toprule
\multicolumn{1}{l}{} & \multicolumn{3}{c}{Monolingual (\emph{N} = 162)} & \multicolumn{3}{c}{Bilingual (\emph{N} = 133)} \\ 
\cmidrule(lr){2-4} \cmidrule(lr){5-7}
\multicolumn{1}{l}{} & Catalan (\%) & Spanish (\%) & Age (months) & Catalan (\%) & Spanish (\%) & Age (months) \\ 
\midrule
\multicolumn{7}{l}{21 months (N = 29)} \\ 
\midrule
Tested in Catalan (N = 38) & $98.8$ ± $1.8$ & $1.2$ ± $1.8$ & $20.8$ ± $0.4$ & $61.6$ ± $7.3$ & $38.4$ ± $7.3$ & $21.1$ ± $0.4$ \\ 
Tested in Spanish (N = 20) & $10.1$ ± $6.2$ & $89.9$ ± $6.2$ & $20.8$ ± $0.5$ & $56.0$ ± $17.0$ & $44.0$ ± $17.0$ & $20.4$ ± $0.3$ \\ 
\midrule
\multicolumn{7}{l}{25 months (N = 45)} \\ 
\midrule
Tested in Catalan (N = 68) & $85.5$ ± $25.1$ & $14.5$ ± $25.1$ & $25.1$ ± $0.5$ & $58.9$ ± $12.7$ & $40.3$ ± $13.1$ & $24.7$ ± $0.6$ \\ 
Tested in Spanish (N = 22) & $45.9$ ± $44.3$ & $53.7$ ± $43.9$ & $25.5$ ± $0.4$ & $43.8$ ± $6.2$ & $55.2$ ± $6.2$ & $25.3$ ± $0.6$ \\ 
\midrule
\multicolumn{7}{l}{30 months (N = 39)} \\ 
\midrule
Tested in Catalan (N = 52) & $94.7$ ± $5.9$ & $5.3$ ± $5.8$ & $30.2$ ± $1.1$ & $59.7$ ± $8.8$ & $40.0$ ± $8.7$ & $29.6$ ± $1.3$ \\ 
Tested in Spanish (N = 26) & $9.2$ ± $7.8$ & $89.4$ ± $6.6$ & $29.7$ ± $1.0$ & $42.5$ ± $12.2$ & $55.9$ ± $13.8$ & $29.9$ ± $1.1$ \\ 
\bottomrule
\end{longtable}

\hypertarget{vocabulary-size}{%
\subsection{Vocabulary size}\label{vocabulary-size}}

We collected vocabulary data using parental responses to the Barcelona
Vocabulary Inventory (BVQ,
\protect\hyperlink{ref-garcia-castro2023bvq}{\textbf{garcia-castro2023bvq?}}),
an online vocabulary checklist inspired in several adaptations of the
the Communicative Developmental Inventory (CDI,
\protect\hyperlink{ref-fenson2004variability}{\textbf{fenson2004variability?}})
developed to assess the vocabulary size of Catalan-Spanish bilingual
toddlers. Families received a link to the BVQ immediately after each
experimental session, and were given two weeks to fill it. Two weeks
after being sent the link, 141 (48\% families failed to provide a
complete response to the BVQ. We imputed their vocabulary size scores
using multiple imputation
(\protect\hyperlink{ref-vanbuuren2018flexible}{\textbf{vanbuuren2018flexible?}}).
We used predictive mean matching to impute missing scores using
participants' information about their age group and language profile. We
obtained several receptive and expressive vocabulary size measures from
each participant's vocabulary: Catalan vocabulary size (proportion of
the words in the Catalan checklist reported as acquired), Spanish
vocabulary size (proportion of the words in the Catalan checklist
reported as acquired), and total vocabulary size (proportion of the
words in both checklists reported as acquired).

\hypertarget{stimuli}{%
\subsubsection{Stimuli}\label{stimuli}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{n\_words }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(}\FunctionTok{with}\NormalTok{(stimuli, }\FunctionTok{unlist}\NormalTok{(prime, target, distractor)))}
\end{Highlighting}
\end{Shaded}

We used arbre, ànec, camió, finestra, vaca, barret, osset, claus, cotxe,
cadira, vaixell, ampolla, flor, formatge, botó, ulleres, gat, gos, mico,
pa, moto, mitjó, avió, granota, ovella, ocell, peix, plàtan, pilota,
poma, guitarra, maduixa, botella, globo, mono, coche, cama, zumo, pato,
cebra, cerdo, oreja, mesa, galleta, gafas, tomate, zapato, manzana,
vaso, queso, oveja, ojo, pelota, tele, pez, perro, barco, hoja, tren,
tenedor, casa, gato distinct words included in the BVQ to create the
stimuli lists. We created six stimuli lists: three in Catalan, and three
in Spanish. Each list contained 32 trials, each involving a
prime-target-distractor group. Each word played a role as either prime,
\emph{or} as target and distractor across the three lists in their
corresponding language. For instance, the Catalan word \emph{cadira}
appeared as \emph{prime} in the three lists, but never as \emph{target}
or \emph{distractor}; the Catalan word \emph{bici} appeared as
\emph{target} and \emph{distractor} across the three lists, but never as
a prime. Target-distractor pairings were held constant across the three
lists in each language. For instance, in all Catalan lists the word
\emph{bici} was paired with the word \emph{porta}. Target-distractor
pairings were also yoked, so that each member of the same
target-distractor pair appeared once as target and once as distractor in
each list. For instance, the \emph{bici}-\emph{porta} paired appeared
twice in each of the three Catalan lists: once with \emph{bici} as
target and \emph{porta} as distractor, and once with \emph{porta} as
target and \emph{bici} as distractor. This counterbalancing avoided
participants encountering looking at the target word guided solely by
that word having being named in a previous trial. Finally, prime words
appeared only once in each list: each target-distractor pair was
associated with a different prime word in both appearances. In each
list, the same prime word was presented alongside a different
target-distractor pair. For instance, the Catalan prime word
\emph{barret} was presented with the \emph{bici}-\emph{porta}
target-distractor pair in one list, with the \emph{bici}-\emph{porta}
pair in another list, and with \emph{berenar}-\emph{amanida} in the
remaining list. The order of the trials was randomised across
experimental session, so that each time a participant was tested, the
order in which the prime-target-distractor was presented was randomised.
Each participant was randomly assigned to one of the three list in the
corresponding language (their dominant language, see
Section~\ref{sec-lp}), and always the same list across their
experimental sessions in the case of a recurrent participant.

In 16 of the 32 trials of the same list (henceforth \emph{related}
trials), the prime and the target words were phonologically related,
sharing phonological onset (at least first phoneme). In the other 16
trials (\emph{unrelated} trials), prime and target did not share
phonological onset. 8 of the 16 \emph{related} trials included a cognate
prime (\emph{cognate} trials), and the other 8 included a non-cognate
trials (\emph{non-cognate} trials). A prime word was considered cognate
if its Catalan and Spanish translation shared phonological onset.
Especial attention was paid to avoiding semantic or taxonomic
relationships between prime and target words, and between prime and
distractor words. Target and distractor word pairs were phonologically
unrelated (did not share phonological onset). Some of them shared
semantic features or a taxonomic relationship. This is the case of words
associated with especially salient referents such as animals or food. To
avoid infants guiding their gaze to these objects based on their
saliency, we paired animals and food items together.

We examined the overall equivalence of the three trial types by
comparing them across three variables relating to the target word:
lexical frequency, word prevalence, animacy Table~\ref{tbl-stimuli}
shows a detailed summary of the stimuli properties, broken down by trial
type and testing language. Lexical frequencies were extracted from the
Catalan and Spanish corpora of the CHILDES database
(\protect\hyperlink{ref-reference}{\textbf{reference?}};
\protect\hyperlink{ref-reference}{\textbf{reference?}}) as counts per
million words, and transformed into Zipf scores for easier
cross-language comparison
(\protect\hyperlink{ref-reference}{\textbf{reference?}};
\protect\hyperlink{ref-reference}{\textbf{reference?}}). We defined word
prevalence as the proportion of same-aged infants who were reported to
understand the word in the BVQ database.

\hypertarget{auditory-stimuli}{%
\paragraph{Auditory stimuli}\label{auditory-stimuli}}

The auditory stimuli were natural exemplars of the selected target
words, spoken by Catalan-Spanish proficient bilingual female speaker who
was instructed to pronounce each word in a toddler-directed manner.
Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a
sampling rate of 44100 Hz, in a soundproof room at the \emph{Laboratori
de Recerca en Infancia} at University Pompeu Fabra. We used the Audacity
(\protect\hyperlink{ref-reference}{\textbf{reference?}}) and Praat
(\protect\hyperlink{ref-reference}{\textbf{reference?}}) to record and
edit the audio files. The speaker was presented with a list of words in
Catalan. The order of the words was pseudo-randomised, and each word was
produced three times in a row before moving to the next word in the
list. After going through all the words in the list, the speaker went
through the word list again generating three tokens for each word, now
in an inverse order (from bottom of the list to the top). We then
repeated the same procedure for the list of Spanish words. The resulting
audios were manually chunked into individual word-forms. For each of the
six tokens produced for each word, the most adequate was selected for
further processing. The audios were then transformed to stereo by
duplicating them into two channels, denoised, and finally normalised.
The mean duration of the final audios was 1.23 (\emph{SD} = 0.17) and
1.08 (\emph{SD} = 0.14) seconds for the Catalan and Spanish lists.

To make the pronunciation of the words as familiar as possible to each
infant, we generated additional pronunciation variants for some words in
Catalan and Spanish. Catalan words involving the /\textipa{L}/ phoneme
in their Central Catalan variant (e.g., /\textipa{'Lu.n@}) were also
recorded with such phoneme replaced by /j/ (e.g., /\textipa{'ju.n@}), a
phonological process common in the Metropolitan Area of Barcelona
(\protect\hyperlink{ref-reference}{\textbf{reference?}}). Spanish words
involving the /\textipa{T}/ phoneme were also generated replacing such
phoneme with /\textipa{s}/ to better accommodate Latin variants of
Spanish. Before every experimental session, caregivers were asked to
utter three written words involving the /\textipa{L}/ phoneme (in the
case of participants tested in Catalan) or the /\textipa{T}/ phoneme (in
the case of participants tested in Spanish). Each token contained the
critical phoneme at onset, inter-vocalic position, and coda. The
experimenter assigned the participant to the Catalan or Spanish stimuli
list involving the closest variant to that of caregivers'.

\hypertarget{visual-stimuli}{%
\paragraph{Visual stimuli}\label{visual-stimuli}}

For each word, we created a picture with a typical referent.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{stimuli }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"familiarity\_|freq\_|animate\_"}\NormalTok{), duration),}
\NormalTok{                     tibble}\SpecialCharTok{::}\FunctionTok{lst}\NormalTok{(mean, sd, min, max)),}
              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(test\_language, trial\_type)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\FunctionTok{matches}\NormalTok{(}\StringTok{"familiarity\_se"}\NormalTok{), }\SpecialCharTok{{-}}\FunctionTok{matches}\NormalTok{(}\StringTok{"prime"}\NormalTok{),}
           \SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(is\_animate\_target\_sd,}
\NormalTok{              is\_animate\_target\_min,}
\NormalTok{              is\_animate\_target\_max)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{gt}\NormalTok{(}\AttributeTok{groupname\_col =} \StringTok{"test\_language"}\NormalTok{,}
       \AttributeTok{rowname\_col =} \StringTok{"list"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Prevalence (\%)"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"familiarity"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Frequency (Zipf)"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"freq"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Animacy (\%)"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"animate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Duration (s)"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"duration"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{fmt\_number}\NormalTok{(is.numeric) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_range}\NormalTok{(familiarity\_target\_min, familiarity\_target\_max) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_range}\NormalTok{(freq\_target\_min, freq\_target\_max) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_range}\NormalTok{(duration\_min, duration\_max) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(freq\_target\_mean, freq\_target\_sd) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(familiarity\_target\_mean, familiarity\_target\_sd) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(duration\_mean, duration\_sd) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_label}\NormalTok{(}\AttributeTok{trial\_type =} \StringTok{""}\NormalTok{,}
               \AttributeTok{familiarity\_target\_mean =} \StringTok{"Mean ± SD"}\NormalTok{,}
               \CommentTok{\# familiarity\_target\_sd = "SD",}
               \AttributeTok{familiarity\_target\_min =} \StringTok{"Range"}\NormalTok{,}
               \AttributeTok{freq\_target\_mean =} \StringTok{"Mean ± SD"}\NormalTok{,}
               \CommentTok{\# freq\_target\_sd = "SD",}
               \AttributeTok{freq\_target\_min =} \StringTok{"Range"}\NormalTok{,}
               \AttributeTok{is\_animate\_target\_mean =} \StringTok{""}\NormalTok{,}
               \AttributeTok{duration\_mean =} \StringTok{"Mean ± SD"}\NormalTok{,}
               \CommentTok{\# duration\_sd = "SD",}
               \AttributeTok{duration\_min =} \StringTok{"Range"}\NormalTok{) }
\end{Highlighting}
\end{Shaded}

\hypertarget{tbl-stimuli}{}
\begin{longtable}{lrrrrrrr}
\caption{\label{tbl-stimuli}Summary of stimuli properties by trial type. }\tabularnewline

\toprule
 & \multicolumn{2}{c}{Prevalence (\%)} & \multicolumn{2}{c}{Frequency (Zipf)} & Animacy (\%) & \multicolumn{2}{c}{Duration (s)} \\ 
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-6} \cmidrule(lr){7-8}
 & Mean ± SD & Range & Mean ± SD & Range &  & Mean ± SD & Range \\ 
\midrule
\multicolumn{8}{l}{Catalan} \\ 
\midrule
Cognate & $0.37$ ± $0.18$ & $0.09$–$0.84$ & $3.90$ ± $0.61$ & $3.04$–$5.05$ & $0.21$ & $1.20$ ± $0.17$ & $0.86$–$1.55$ \\ 
Non-cognate & $0.38$ ± $0.16$ & $0.09$–$0.84$ & $3.90$ ± $0.52$ & $3.04$–$5.05$ & $0.25$ & $1.25$ ± $0.17$ & $0.88$–$1.55$ \\ 
Unrelated & $0.36$ ± $0.15$ & $0.09$–$0.84$ & $3.86$ ± $0.58$ & $2.94$–$5.05$ & $0.22$ & $1.23$ ± $0.17$ & $0.86$–$1.55$ \\ 
\midrule
\multicolumn{8}{l}{Spanish} \\ 
\midrule
Cognate & $0.29$ ± $0.13$ & $0.04$–$0.50$ & $4.21$ ± $0.51$ & $2.94$–$5.11$ & $0.10$ & $1.11$ ± $0.14$ & $0.85$–$1.45$ \\ 
Non-cognate & $0.30$ ± $0.14$ & $0.04$–$0.50$ & $4.27$ ± $0.53$ & $2.94$–$5.11$ & $0.15$ & $1.09$ ± $0.14$ & $0.83$–$1.45$ \\ 
Unrelated & $0.28$ ± $0.14$ & $0.04$–$0.50$ & $4.23$ ± $0.46$ & $2.94$–$5.11$ & $0.17$ & $1.07$ ± $0.15$ & $0.83$–$1.54$ \\ 
\bottomrule
\end{longtable}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Testing took place in a sound-proof room. Participants sat on their
caregivers' lap in a dimly lit testing booth while the experimenter
conducted the experiment from outside. Caregivers were instructed to
keep their eyes shut (to avoid recording their gaze, instead of the
participant's), to be still, and to avoid interacting with the
participant verbally or non-verbally. Participants sat at approximately
65 cm from the eye-tracker and a XX-in screen of \(1929\times1080\)
screen resolution. We used a custom Matlab XXXX script using the
PsychToolbox XXX extension
(\protect\hyperlink{ref-brainard}{\textbf{brainard?}}) to present the
stimuli, and the Tobii Analytics SDK 3.0 to interact with the
eye-tracking while the experiment was running. Sampling rate was set at
120 Hz. A 5-point calibration was performed before every experimental
session, in which the picture of a colourful beach ball was presented.
We set a 55\% grey background for the calibration and stimuli
presentation. Auditory stimuli were presented through two loudspeakers
located behind the screen, one to each side. The experimenter monitored
the experimental from outside the room using a centrally located video
camera place above the screen. After a successful calibration the
experimenter triggered the onset of the first trial. Trials were
presented uninterruptedly and without intervention of the experimenter
until the 32 trials were presented, or the experimental session had to
be stopped because of the participant's behaviour.

Each trial started with the presentation of an attention getter for
3,000 milliseconds. Then, the prime picture was presented in silence in
the centre of the screen for 1,500 milliseconds. Fifty milliseconds
after the offset of the prime image, an auditory label was played from
the loudspeakers and, 700 milliseconds after the onset of the auditory
label, the target and distractor pictures were presented side-by-side
during 1,000 milliseconds until the end of the trial. After this, the
attention getter of the next trial was immediately presented. Each
experimental session took approximately 10 minutes.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

\hypertarget{data-processing}{%
\subsubsection{Data processing}\label{data-processing}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{n\_trials }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(attrition\_trials)}

\NormalTok{n\_sessions }\OtherTok{\textless{}{-}} \FunctionTok{distinct}\NormalTok{(attrition\_trials, filename) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{nrow}\NormalTok{()}

\NormalTok{n\_participants }\OtherTok{\textless{}{-}} \FunctionTok{distinct}\NormalTok{(attrition\_trials, id) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{nrow}\NormalTok{()}

\NormalTok{n\_trials\_prime }\OtherTok{\textless{}{-}}\NormalTok{ attrition\_trials }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{filter}\NormalTok{(is\_valid\_gaze\_prime)}

\NormalTok{n\_trials\_test }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_prime }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{filter}\NormalTok{(is\_valid\_gaze\_test)}

\NormalTok{n\_trials\_each }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_test }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{filter}\NormalTok{(is\_valid\_gaze\_test\_each)}

\NormalTok{n\_trials\_vocab }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_each }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{filter}\NormalTok{(is\_valid\_vocab)}

\NormalTok{n\_trials\_participant }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_vocab }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{inner\_join}\NormalTok{(}\FunctionTok{filter}\NormalTok{(attrition\_participants,}
\NormalTok{                      is\_valid\_participant),}
               \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename))}

\NormalTok{n\_sessions\_valid }\OtherTok{\textless{}{-}}\NormalTok{ attrition\_participants }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{filter}\NormalTok{(is\_valid\_participant)}

\NormalTok{n\_participants\_valid }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_participant }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{distinct}\NormalTok{(filename)}

\NormalTok{n\_longitudinal }\OtherTok{\textless{}{-}} \FunctionTok{count}\NormalTok{(n\_sessions\_valid, filename, }\AttributeTok{name =} \StringTok{"sessions"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{count}\NormalTok{(sessions)}

\NormalTok{n\_participants\_include }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"data{-}raw/participants.csv"}\NormalTok{,}
                                   \AttributeTok{show\_col\_types =} \ConstantTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

We gathered data for 9,472 trials from 296 experimental sessions,
provided by 180 distinct participants. Missing eye-tracker samples were
interpolated using the last-observation-carried-forward (see
\protect\hyperlink{ref-zettersten2022peekbank}{\textbf{zettersten2022peekbank?}}
for a similar approach). We excluded trials in which the participant did
not fixate the prime at least half of the time of the prime phase
(\$\geq\(750 ms, *n* = 1,810), or the target and distractor during the test phase (\)\geq\$1,000
ms, \emph{n} = 502). We also excluded trials in which the participant
failed to fixate both target \emph{and} distractor pictures for at least
100 ms (i.e., 5\% of the time) (1,304 trials excluded). We then excluded
trials in which the participant was not reported to understand the prime
\emph{and} the target words, according to their caregivers' responses to
the vocabulary checklist. This resulted in the exclusion of 3,641
trials. Finally, we excluded trials from experimental sessions in which
the participant did not provide at least two valid trials in each of the
three experimental conditions (cognate prime, non-cognate prime, and
unrelated prime) which resulted in the exclusion of 34 experimental
sessions and their 219 remaining trials. The final data set comprised 0
from c(``CognatePriming\_019\_2019-11-28.csv'',
``CognatePriming\_021\_2019-11-30.csv'',
``CognatePriming\_026\_2019-12-14.csv'',
``CognatePriming\_027\_2019-12-14\_1.csv'',
``CognatePriming\_049\_2021-02-13.csv'',
``CognatePriming\_050\_2020-11-07.csv'',
``CognatePriming\_050\_2021-03-13.csv'',
``CognatePriming\_050\_2021-10-02.csv'',
``CognatePriming\_051\_2021-03-06\_1.csv'',
``CognatePriming\_051\_2021-10-01.csv'',
``CognatePriming\_053\_2021-04-17.csv'',
``CognatePriming\_054\_2020-11-14.csv'',
``CognatePriming\_055\_2020-11-14.csv'',
``CognatePriming\_055\_2021-02-20\_1.csv'',
``CognatePriming\_056\_2020-11-14.csv'',
``CognatePriming\_058\_2020-11-17.csv'',
``CognatePriming\_059\_2020-11-18.csv'',
``CognatePriming\_060\_2021-04-26.csv'',
``CognatePriming\_064\_2020-11-21.csv'',
``CognatePriming\_065\_2020-11-25.csv'',
``CognatePriming\_066\_2020-11-26.csv'',
``CognatePriming\_067\_2020-11-27.csv'',
``CognatePriming\_068\_2020-11-27.csv'',
``CognatePriming\_069\_2020-11-28.csv'',
``CognatePriming\_069\_2021-05-08.csv'',
``CognatePriming\_070\_2020-12-01.csv'',
``CognatePriming\_070\_2021-09-30\_1.csv'',
``CognatePriming\_071\_2020-12-01.csv'',
``CognatePriming\_072\_2020-12-04.csv'',
``CognatePriming\_073\_2021-10-02.csv'',
``CognatePriming\_074\_2020-12-05.csv'',
``CognatePriming\_075\_2020-12-09.csv'',
``CognatePriming\_076\_2021-05-08.csv'',
``CognatePriming\_076\_2021-10-16.csv'',
``CognatePriming\_078\_2021-04-29.csv'',
``CognatePriming\_079\_2020-12-16.csv'',
``CognatePriming\_079\_2021-10-07\_1.csv'',
``CognatePriming\_080\_2021-04-10.csv'',
``CognatePriming\_081\_2020-12-21.csv'',
``CognatePriming\_081\_2021-05-03.csv'',
``CognatePriming\_081\_2021-10-19.csv'',
``CognatePriming\_084\_2021-10-15.csv'',
``CognatePriming\_089\_2021-02-02.csv'',
``CognatePriming\_089\_2021-07-06.csv'',
``CognatePriming\_090\_2021-02-06\_2.csv'',
``CognatePriming\_090\_2021-06-19.csv'',
``CognatePriming\_091\_2021-06-18.csv'',
``CognatePriming\_092\_2021-06-08.csv'',
``CognatePriming\_094\_2021-02-13.csv'',
``CognatePriming\_095\_2021-02-13\_1.csv'',
``CognatePriming\_098\_2021-11-13.csv'',
``CognatePriming\_100\_2021-02-20\_1.csv'',
``CognatePriming\_100\_2021-06-14.csv'',
``CognatePriming\_101\_2021-02-20\_1.csv'',
``CognatePriming\_101\_2021-11-20.csv'',
``CognatePriming\_102\_2021-02-26.csv'',
``CognatePriming\_102\_2021-07-05.csv'',
``CognatePriming\_102\_2021-11-12.csv'',
``CognatePriming\_105\_2021-02-27\_1.csv'',
``CognatePriming\_105\_2021-07-24\_1.csv'',
``CognatePriming\_105\_2021-11-27.csv'',
``CognatePriming\_107\_2022-02-21.csv'',
``CognatePriming\_108\_2021-03-15.csv'',
``CognatePriming\_108\_2022-01-26\_1.csv'',
``CognatePriming\_110\_2022-01-22\_1.csv'',
``CognatePriming\_112\_2022-02-18.csv'',
``CognatePriming\_113\_2021-05-15.csv'',
``CognatePriming\_114\_2021-05-19.csv'',
``CognatePriming\_115\_2021-05-22.csv'',
``CognatePriming\_115\_2021-10-23.csv'',
``CognatePriming\_115\_2022-01-29.csv'',
``CognatePriming\_117\_2021-11-16.csv'',
``CognatePriming\_117\_2022-03-11\_1.csv'',
``CognatePriming\_119\_2021-06-01.csv'',
``CognatePriming\_119\_2022-01-26.csv'',
``CognatePriming\_121\_2021-06-08.csv'',
``CognatePriming\_121\_2021-10-18.csv'',
``CognatePriming\_123\_2021-10-23.csv'',
``CognatePriming\_124\_2022-02-18.csv'',
``CognatePriming\_125\_2021-06-26.csv'',
``CognatePriming\_127\_2021-06-28.csv'',
``CognatePriming\_127\_2021-10-25.csv'',
``CognatePriming\_128\_2021-11-02.csv'',
``CognatePriming\_131\_2022-02-18.csv'',
``CognatePriming\_133\_2021-07-06.csv'',
``CognatePriming\_135\_2021-12-01.csv'',
``CognatePriming\_136\_2021-12-03.csv'',
``CognatePriming\_140\_2021-12-11\_2.csv'',
``CognatePriming\_142\_2022-03-31.csv'',
``CognatePriming\_144\_2022-01-07.csv'',
``CognatePriming\_146\_2022-01-27.csv'',
``CognatePriming\_146\_2022-06-14.csv'',
``CognatePriming\_147\_2022-01-28.csv'',
``CognatePriming\_147\_2022-06-17.csv'',
``CognatePriming\_152\_2022-02-05.csv'',
``CognatePriming\_154\_2022-02-08\_1.csv'',
``CognatePriming\_154\_2022-05-24\_1.csv'',
``CognatePriming\_157\_2022-02-10.csv'',
``CognatePriming\_157\_2022-10-03.csv'',
``CognatePriming\_160\_2022-02-28.csv'',
``CognatePriming\_171\_2022-03-14.csv'',
``CognatePriming\_172\_2022-03-15.csv'',
``CognatePriming\_176\_2022-03-22.csv'',
``CognatePriming\_178\_2022-03-23\_1.csv'',
``CognatePriming\_183\_2022-10-06.csv'',
``CognatePriming\_190\_2022-06-20.csv'',
``CognatePriming\_192\_2022-06-21.csv'',
``CognatePriming\_196\_2022-06-28\_2.csv'',
``CognatePriming\_198\_2022-10-01.csv'',
``CognatePriming\_199\_2022-10-03.csv'',
``CognatePriming\_200\_2022-10-04.csv'',
``CognatePriming\_201\_2022-10-07.csv'',
``CognatePriming\_202\_2022-10-08.csv''), c(8, 5, 8, 7, 7, 6, 7, 7, 3,
5, 4, 5, 3, 3, 2, 4, 6, 8, 4, 4, 2, 5, 7, 4, 6, 3, 6, 3, 2, 3, 6, 4, 4,
6, 4, 3, 5, 2, 2, 5, 6, 6, 6, 5, 5, 5, 4, 2, 5, 2, 4, 6, 3, 3, 5, 6, 6,
6, 3, 5, 6, 5, 2, 5, 5, 6, 8, 2, 5, 5, 7, 5, 7, 7, 6, 5, 4, 4, 4, 5, 2,
4, 4, 5, 7, 5, 4, 5, 2, 7, 6, 3, 2, 7, 3, 8, 6, 2, 5, 3, 6, 3, 5, 4, 7,
6, 7, 4, 7, 4, 7, 3, 2), c(7, 7, 7, 8, 7, 5, 8, 7, 6, 5, 5, 6, 2, 2, 2,
4, 8, 7, 3, 4, 3, 2, 4, 2, 3, 2, 7, 5, 6, 3, 4, 5, 4, 5, 6, 2, 5, 6, 4,
6, 3, 3, 6, 4, 6, 5, 4, 2, 3, 3, 4, 3, 5, 4, 6, 4, 6, 6, 4, 7, 8, 6, 2,
4, 4, 7, 4, 3, 5, 4, 6, 7, 7, 6, 6, 7, 6, 4, 6, 3, 4, 5, 4, 6, 4, 5, 5,
3, 4, 6, 6, 2, 4, 4, 5, 4, 5, 3, 7, 4, 4, 3, 6, 2, 6, 2, 5, 2, 6, 4, 6,
3, 2), c(9, 8, 9, 10, 10, 6, 11, 14, 8, 9, 9, 9, 3, 4, 5, 10, 15, 12, 3,
5, 5, 6, 6, 6, 6, 9, 14, 5, 10, 2, 10, 10, 7, 13, 9, 5, 8, 10, 2, 5, 7,
10, 11, 10, 12, 10, 7, 5, 11, 4, 7, 8, 6, 4, 11, 9, 12, 14, 10, 13, 13,
11, 3, 5, 6, 14, 11, 2, 6, 11, 12, 8, 14, 7, 10, 6, 6, 11, 8, 7, 3, 5,
6, 6, 7, 10, 8, 7, 5, 12, 8, 14, 8, 8, 7, 7, 6, 8, 10, 9, 7, 6, 10, 7,
10, 4, 9, 7, 12, 7, 13, 11, 3), c(TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE),
c(TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE), c(TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE),
c(TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
TRUE, TRUE, TRUE, TRUE, TRUE, TRUE), c(19, 21, 26, 27, 49, 50, 50, 50,
51, 51, 53, 54, 55, 55, 56, 58, 59, 60, 64, 65, 66, 67, 68, 69, 69, 70,
70, 71, 72, 73, 74, 75, 76, 76, 78, 79, 79, 80, 81, 81, 81, 84, 89, 89,
90, 90, 91, 92, 94, 95, 98, 100, 100, 101, 101, 102, 102, 102, 105, 105,
105, 107, 108, 108, 110, 112, 113, 114, 115, 115, 115, 117, 117, 119,
119, 121, 121, 123, 124, 125, 127, 127, 128, 131, 133, 135, 136, 140,
142, 144, 146, 146, 147, 147, 152, 154, 154, 157, 157, 160, 171, 172,
176, 178, 183, 190, 192, 196, 198, 199, 200, 201, 202), c(3, 3, 3, 3, 2,
1, 2, 3, 2, 3, 3, 1, 1, 2, 1, 2, 2, 3, 2, 2, 2, 2, 2, 2, 3, 1, 3, 1, 1,
3, 2, 2, 2, 3, 2, 1, 3, 3, 1, 2, 3, 3, 1, 2, 1, 2, 2, 2, 1, 1, 3, 1, 2,
1, 3, 1, 2, 3, 1, 2, 3, 3, 1, 3, 3, 3, 1, 1, 1, 2, 3, 2, 3, 1, 3, 1, 2,
2, 3, 1, 1, 2, 2, 3, 1, 2, 2, 2, 2, 2, 2, 3, 2, 3, 1, 2, 3, 2, 3, 1, 2,
2, 2, 2, 3, 2, 3, 1, 3, 3, 3, 2, 3), c(2, 2, 2, 1, 1, 1, 1, 1, 1, 1, 1,
1, 2, 2, 1, 1, 1, 2, 1, 1, 2, 2, 2, 1, 1, 1, 1, 2, 1, 1, 1, 1, 2, 2, 1,
1, 1, 2, 1, 1, 1, 1, 1, 1, 2, 2, 1, 1, 1, 1, 2, 2, 2, 1, 1, 1, 1, 1, 2,
2, 2, 1, 2, 2, 2, 1, 1, 1, 1, 1, 1, 2, 2, 1, 1, 1, 1, 2, 2, 1, 1, 1, 2,
1, 1, 1, 2, 1, 2, 2, 1, 1, 1, 1, 2, 1, 1, 1, 1, 2, 1, 1, 1, 2, 1, 2, 2,
2, 1, 1, 2, 1, 1) experimental sessions, provided by
c(``CognatePriming\_019\_2019-11-28.csv'',
``CognatePriming\_021\_2019-11-30.csv'',
``CognatePriming\_026\_2019-12-14.csv'',
``CognatePriming\_027\_2019-12-14\_1.csv'',
``CognatePriming\_049\_2021-02-13.csv'',
``CognatePriming\_050\_2020-11-07.csv'',
``CognatePriming\_050\_2021-03-13.csv'',
``CognatePriming\_050\_2021-10-02.csv'',
``CognatePriming\_051\_2021-03-06\_1.csv'',
``CognatePriming\_051\_2021-10-01.csv'',
``CognatePriming\_053\_2021-04-17.csv'',
``CognatePriming\_054\_2020-11-14.csv'',
``CognatePriming\_055\_2020-11-14.csv'',
``CognatePriming\_055\_2021-02-20\_1.csv'',
``CognatePriming\_056\_2020-11-14.csv'',
``CognatePriming\_058\_2020-11-17.csv'',
``CognatePriming\_059\_2020-11-18.csv'',
``CognatePriming\_060\_2021-04-26.csv'',
``CognatePriming\_064\_2020-11-21.csv'',
``CognatePriming\_065\_2020-11-25.csv'',
``CognatePriming\_066\_2020-11-26.csv'',
``CognatePriming\_067\_2020-11-27.csv'',
``CognatePriming\_068\_2020-11-27.csv'',
``CognatePriming\_069\_2020-11-28.csv'',
``CognatePriming\_069\_2021-05-08.csv'',
``CognatePriming\_070\_2020-12-01.csv'',
``CognatePriming\_070\_2021-09-30\_1.csv'',
``CognatePriming\_071\_2020-12-01.csv'',
``CognatePriming\_072\_2020-12-04.csv'',
``CognatePriming\_073\_2021-10-02.csv'',
``CognatePriming\_074\_2020-12-05.csv'',
``CognatePriming\_075\_2020-12-09.csv'',
``CognatePriming\_076\_2021-05-08.csv'',
``CognatePriming\_076\_2021-10-16.csv'',
``CognatePriming\_078\_2021-04-29.csv'',
``CognatePriming\_079\_2020-12-16.csv'',
``CognatePriming\_079\_2021-10-07\_1.csv'',
``CognatePriming\_080\_2021-04-10.csv'',
``CognatePriming\_081\_2020-12-21.csv'',
``CognatePriming\_081\_2021-05-03.csv'',
``CognatePriming\_081\_2021-10-19.csv'',
``CognatePriming\_084\_2021-10-15.csv'',
``CognatePriming\_089\_2021-02-02.csv'',
``CognatePriming\_089\_2021-07-06.csv'',
``CognatePriming\_090\_2021-02-06\_2.csv'',
``CognatePriming\_090\_2021-06-19.csv'',
``CognatePriming\_091\_2021-06-18.csv'',
``CognatePriming\_092\_2021-06-08.csv'',
``CognatePriming\_094\_2021-02-13.csv'',
``CognatePriming\_095\_2021-02-13\_1.csv'',
``CognatePriming\_098\_2021-11-13.csv'',
``CognatePriming\_100\_2021-02-20\_1.csv'',
``CognatePriming\_100\_2021-06-14.csv'',
``CognatePriming\_101\_2021-02-20\_1.csv'',
``CognatePriming\_101\_2021-11-20.csv'',
``CognatePriming\_102\_2021-02-26.csv'',
``CognatePriming\_102\_2021-07-05.csv'',
``CognatePriming\_102\_2021-11-12.csv'',
``CognatePriming\_105\_2021-02-27\_1.csv'',
``CognatePriming\_105\_2021-07-24\_1.csv'',
``CognatePriming\_105\_2021-11-27.csv'',
``CognatePriming\_107\_2022-02-21.csv'',
``CognatePriming\_108\_2021-03-15.csv'',
``CognatePriming\_108\_2022-01-26\_1.csv'',
``CognatePriming\_110\_2022-01-22\_1.csv'',
``CognatePriming\_112\_2022-02-18.csv'',
``CognatePriming\_113\_2021-05-15.csv'',
``CognatePriming\_114\_2021-05-19.csv'',
``CognatePriming\_115\_2021-05-22.csv'',
``CognatePriming\_115\_2021-10-23.csv'',
``CognatePriming\_115\_2022-01-29.csv'',
``CognatePriming\_117\_2021-11-16.csv'',
``CognatePriming\_117\_2022-03-11\_1.csv'',
``CognatePriming\_119\_2021-06-01.csv'',
``CognatePriming\_119\_2022-01-26.csv'',
``CognatePriming\_121\_2021-06-08.csv'',
``CognatePriming\_121\_2021-10-18.csv'',
``CognatePriming\_123\_2021-10-23.csv'',
``CognatePriming\_124\_2022-02-18.csv'',
``CognatePriming\_125\_2021-06-26.csv'',
``CognatePriming\_127\_2021-06-28.csv'',
``CognatePriming\_127\_2021-10-25.csv'',
``CognatePriming\_128\_2021-11-02.csv'',
``CognatePriming\_131\_2022-02-18.csv'',
``CognatePriming\_133\_2021-07-06.csv'',
``CognatePriming\_135\_2021-12-01.csv'',
``CognatePriming\_136\_2021-12-03.csv'',
``CognatePriming\_140\_2021-12-11\_2.csv'',
``CognatePriming\_142\_2022-03-31.csv'',
``CognatePriming\_144\_2022-01-07.csv'',
``CognatePriming\_146\_2022-01-27.csv'',
``CognatePriming\_146\_2022-06-14.csv'',
``CognatePriming\_147\_2022-01-28.csv'',
``CognatePriming\_147\_2022-06-17.csv'',
``CognatePriming\_152\_2022-02-05.csv'',
``CognatePriming\_154\_2022-02-08\_1.csv'',
``CognatePriming\_154\_2022-05-24\_1.csv'',
``CognatePriming\_157\_2022-02-10.csv'',
``CognatePriming\_157\_2022-10-03.csv'',
``CognatePriming\_160\_2022-02-28.csv'',
``CognatePriming\_171\_2022-03-14.csv'',
``CognatePriming\_172\_2022-03-15.csv'',
``CognatePriming\_176\_2022-03-22.csv'',
``CognatePriming\_178\_2022-03-23\_1.csv'',
``CognatePriming\_183\_2022-10-06.csv'',
``CognatePriming\_190\_2022-06-20.csv'',
``CognatePriming\_192\_2022-06-21.csv'',
``CognatePriming\_196\_2022-06-28\_2.csv'',
``CognatePriming\_198\_2022-10-01.csv'',
``CognatePriming\_199\_2022-10-03.csv'',
``CognatePriming\_200\_2022-10-04.csv'',
``CognatePriming\_201\_2022-10-07.csv'',
``CognatePriming\_202\_2022-10-08.csv'') distinct participants. Of those
participants, 1 provided data from one experimental session, 113
provided data from two experimental sessions, and 1 provided data from
three experimental sessions.

We defined our time window of interest from 300 ms after the onset of
the test phase (target and distractor presentation) until the end of the
test phase (2,000 ms). For each trial, we chunked the time domain into
17 time bins of 100 ms of duration. We then calculated, for each
experimental session, time bin, and condition, participant's proportion
of target and distractor fixations. Finally, we computed the empirical
logit of target fixations, which we introduced in the statistical
analyses as our response variable.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{attrition\_trials }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(participants, age\_group, lp, id, date\_test),}
              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(id, age\_group)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{left\_join}\NormalTok{(attrition\_participants,}
              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(id, age\_group)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{add\_count}\NormalTok{(age\_group, lp, }\AttributeTok{name =} \StringTok{"n\_trials"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{valid\_trial\_count =} \FunctionTok{sum}\NormalTok{(is\_valid\_trial, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{),}
              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, lp, trial\_type, date\_test,}
\NormalTok{                    age\_group, is\_valid\_participant, n\_trials)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ trial\_type, }
                \AttributeTok{values\_from =}\NormalTok{ valid\_trial\_count, }
                \AttributeTok{values\_fill =} \DecValTok{0}\NormalTok{,}
                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{rename}\NormalTok{(}\AttributeTok{noncognate =}\NormalTok{ non\_cognate) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{add\_count}\NormalTok{(lp, age\_group) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{c}\NormalTok{(cognate, noncognate, unrelated),}
                     \FunctionTok{lst}\NormalTok{(sum, mean, sd)),}
              \AttributeTok{n\_valid =} \FunctionTok{sum}\NormalTok{(is\_valid\_participant),}
              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(lp, age\_group, n, n\_trials)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{relocate}\NormalTok{(n\_valid, }\AttributeTok{.after =}\NormalTok{ n) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{n\_prop =}\NormalTok{ n\_valid}\SpecialCharTok{/}\NormalTok{n) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{arrange}\NormalTok{(age\_group, lp) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{relocate}\NormalTok{(age\_group, lp, n\_valid, n\_prop, }
             \FunctionTok{matches}\NormalTok{(}\StringTok{"cognate"}\NormalTok{),}
             \FunctionTok{matches}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{),}
             \FunctionTok{matches}\NormalTok{(}\StringTok{"unrelated"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{gt}\NormalTok{(}\AttributeTok{groupname\_col =} \StringTok{"age\_group"}\NormalTok{,}
       \AttributeTok{rowname\_col =} \StringTok{"lp"}\NormalTok{)  }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{cols\_hide}\NormalTok{(}\FunctionTok{c}\NormalTok{(n, n\_trials)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{fmt\_number}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"\_mean|\_sd"}\NormalTok{), }
               \AttributeTok{decimals =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{fmt\_percent}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"\_prop"}\NormalTok{),}
                \AttributeTok{decimals =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_n\_pct}\NormalTok{(}\AttributeTok{col\_n =}\NormalTok{ n\_valid, }
                     \AttributeTok{col\_pct =}\NormalTok{ n\_prop,}
                     \AttributeTok{autohide =} \ConstantTok{TRUE}\NormalTok{)  }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Non{-}cognate"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Cognate"}\NormalTok{, }\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Unrelated"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"unrelated"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Related"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ cognate\_mean,}
                      \AttributeTok{col\_uncert =}\NormalTok{ cognate\_sd) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ noncognate\_mean,}
                      \AttributeTok{col\_uncert =}\NormalTok{ noncognate\_sd) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ unrelated\_mean, }
                      \AttributeTok{col\_uncert =}\NormalTok{ unrelated\_sd) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{cols\_label}\NormalTok{(}\AttributeTok{age\_group =} \StringTok{"Age"}\NormalTok{,}
               \AttributeTok{n\_valid =} \StringTok{"Participants (included)"}\NormalTok{,}
               \AttributeTok{cognate\_sum =} \StringTok{"Trials"}\NormalTok{,}
               \AttributeTok{cognate\_mean =} \StringTok{"Mean ± SD"}\NormalTok{,}
               \AttributeTok{noncognate\_sum =} \StringTok{"Trials"}\NormalTok{,}
               \AttributeTok{noncognate\_mean =} \StringTok{"Mean ± SD"}\NormalTok{,}
               \AttributeTok{unrelated\_sum =} \StringTok{"Trials"}\NormalTok{,}
               \AttributeTok{unrelated\_mean =} \StringTok{"Mean ± SD"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{summary\_rows}\NormalTok{(}\AttributeTok{groups =} \ConstantTok{TRUE}\NormalTok{,}
                 \AttributeTok{columns =} \FunctionTok{where}\NormalTok{(is.integer),}
                 \AttributeTok{fns =} \FunctionTok{list}\NormalTok{(}\StringTok{"Sum"} \OtherTok{=} \StringTok{"sum"}\NormalTok{),}
                 \AttributeTok{fmt =}\NormalTok{ fmt\_number,}
                 \AttributeTok{decimals =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{summary\_rows}\NormalTok{(}\AttributeTok{groups =} \ConstantTok{TRUE}\NormalTok{,}
                 \AttributeTok{columns =} \FunctionTok{c}\NormalTok{(}\FunctionTok{where}\NormalTok{(is.numeric), }\SpecialCharTok{{-}}\NormalTok{n\_valid),}
                 \AttributeTok{fns =} \FunctionTok{list}\NormalTok{(}\StringTok{"Mean"} \OtherTok{=} \StringTok{"mean"}\NormalTok{),}
                 \AttributeTok{fmt =}\NormalTok{ fmt\_number,}
                 \AttributeTok{decimals =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{where}\NormalTok{(is.integer),}
                       \AttributeTok{fns =} \FunctionTok{list}\NormalTok{(}\StringTok{"N"} \OtherTok{=} \StringTok{"sum"}\NormalTok{),}
                       \AttributeTok{formatter =}\NormalTok{ fmt\_integer) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: [1m[22mSince gt v0.9.0, the `formatter` argument (and associated `...`) has been
deprecated.
[36m*[39m Please use the `fmt` argument to provide formatting directives.
[90mThis warning is displayed once every 8 hours.[39m
\end{verbatim}

\hypertarget{tbl-attrition-group}{}
\begin{longtable}{l|rrrrrrr}
\caption{\label{tbl-attrition-group}Summary of the dataset. }\tabularnewline

\toprule
\multicolumn{1}{l}{} &  & \multicolumn{4}{c}{Related} &  &  \\ 
\cmidrule(lr){3-6}
\multicolumn{1}{l}{} &  & \multicolumn{2}{c}{Cognate} & \multicolumn{2}{c}{Non-cognate} & \multicolumn{2}{c}{Unrelated} \\ 
\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8}
\multicolumn{1}{l}{} & Participants (included) & Trials & Mean ± SD & Trials & Mean ± SD & Trials & Mean ± SD \\ 
\midrule
\multicolumn{8}{l}{21 months} \\ 
\midrule
Monolingual & 20 ($40.0\%$) & 103 & $2.1$ ± $2.4$ & 110 & $2.2$ ± $2.2$ & 180 & $3.6$ ± $3.6$ \\ 
Bilingual & 9 ($20.5\%$) & 42 & $1.0$ ± $1.5$ & 52 & $1.2$ ± $1.7$ & 91 & $2.1$ ± $3.2$ \\ 
\midrule
\multicolumn{8}{l}{25 months} \\ 
\midrule
Monolingual & 29 ($55.8\%$) & 142 & $2.7$ ± $2.5$ & 142 & $2.7$ ± $2.5$ & 254 & $4.9$ ± $4.5$ \\ 
Bilingual & 16 ($36.4\%$) & 71 & $1.6$ ± $2.3$ & 67 & $1.5$ ± $2.2$ & 123 & $2.8$ ± $3.9$ \\ 
\midrule
\multicolumn{8}{l}{30 months} \\ 
\midrule
Monolingual & 25 ($41.7\%$) & 140 & $2.3$ ± $2.8$ & 134 & $2.2$ ± $2.7$ & 255 & $4.2$ ± $5.1$ \\ 
Bilingual & 14 ($30.4\%$) & 86 & $1.9$ ± $2.9$ & 83 & $1.8$ ± $2.8$ & 140 & $3.0$ ± $4.8$ \\ 
\midrule 
\midrule 
sum & $113$ & $584$ & — & $588$ & — & $1,043$ & — \\ 
\bottomrule
\end{longtable}

\hypertarget{modelling-approach}{%
\subsubsection{Modelling approach}\label{modelling-approach}}

We conducted two main analyses. First, we estimated the effect of
phonological priming on participants' target looking, comparing
\emph{related} trials with \emph{unrelated} trials. This analysis
included all trials on the data set. Second, we estimated the effect of
cognateness on phonological priming, comparing \emph{cognate} with
\emph{non-cognate} trials, leaving out \emph{unrelated} trials. In both
analyses, we used General Additive Mixed Models (GAMMs) to model the
probability of target fixations across the time course of the trial
using a normal distribution.

In the first analysis. We included \emph{Relatedness} (\texttt{Related}
vs.~\texttt{Unrelated}, sum-coded as \texttt{-0.5} and \texttt{+0.5}),
\emph{Group} (\texttt{Monolingual} vs.~\texttt{Bilingual}, sum-coded as
\texttt{-0.5} and \texttt{+0.5}), and \emph{Age} (participants'
standardised age in months) as fixed, main effects. We also included
cubic regression splines for the main effect of \emph{Time}, and one for
an adjustment of the previous cubic spline by \emph{Group}
(\protect\hyperlink{ref-wood2017generalized}{Wood, 2017}). For both
splines, we specified \(k = 10\) basis functions or \emph{knots}--half
the number of time bins, for computational convenience. Finally, we
added by-participant random intercepts, and random slopes for the main
effect of \emph{Relatedness} and the main effect of \emph{Age}, both
including repeated measures per participant.

To test the contribution of each of the predictors of
interest--\emph{Relatedness}/\emph{Cognateness}, and \emph{Group}--, we
compared each model (\(\mathcal{M_0}\)) against a simplified model
dropping each of the main effects, \emph{Relatedness}/\emph{Cognateness}
(\(\mathcal{M}_1\)) or \emph{Group} (\(\mathcal{M_2}\)). In both
simplified models, the interaction term was dropped. We used
leave-one-out cross-validation (LOO-CV) as a benchmark of model
performance, using Pareto-smoothed importance sampling (PSIS) to
approximate it. We then examined the posterior predictions of the
best-performing model for interpretation.

\[
\begin{aligned}
\textbf{Likelihood:} \\
y_i &\sim \mathcal{N}(\mu_i, \sigma_i) \\ \\
\textbf{Linear model} \\
\text{logit}(\mu_i) &= (\beta_0 + u _{0_{i}}) + (\beta_1 + u _{1_{i}}) \cdot \text{Relatedness} + \beta_{2} \cdot \text{Group} + \\
&\beta_{3} \cdot (\text{Relatedness} \times \text{Group}) + (\beta_4 + u_{3_{i}}) \cdot \text{Age} + \\
&\sum_{j = 1}^k b_{j_{1}}(\beta_{5_{k}} + u_{4_{i}}) \cdot \text{Time} + \\
&\sum_{j = 1}^k b_{j_{1}} (\beta_{6_{k }} + u_{5_{i}}) \cdot (\text{Time} \times \text{Group}) \\
\text{where:} \\
&k \text{ is the number of knots in the spline (10)} \\
\textbf{Prior:} \\
\beta_{0-6} &\sim \mathcal{N}(0, 1) \\
b_{0-1} &\sim MVN(0, 1) \\
\sigma_i &\sim Exp(4) 
\end{aligned}
\]

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{phonological-priming-related-vs.-unrelated}{%
\subsection{Phonological priming: Related
vs.~Unrelated}\label{phonological-priming-related-vs.-unrelated}}

A model including the \emph{Relatedness} \(\times\) \emph{Group}
interaction showed the best of-of-sample predictive performance,
although the model including only \emph{Relatedness} performed
equivalently
(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) = -0.724,
\emph{SE} = 3.487). Both models showed substantially better predictive
performance than the model including only \emph{Group}
(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}\) =
-48.179, \emph{SE} = 11.672). This indicates that including the
\emph{Relatedness} predictor improved the predictive performance of the
model significantly, that including its interaction with \emph{Group}
slightly increased the performance of the model, and that the main
effect of \emph{Group} by itself barely changed the predictive
performance of the model.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{relatedness =} \FunctionTok{levels}\NormalTok{(data\_time}\SpecialCharTok{$}\NormalTok{relatedness),}
                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{20}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time}\SpecialCharTok{$}\NormalTok{age),}
                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time}\SpecialCharTok{$}\NormalTok{lp)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fit\_related,}
                    \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }

\NormalTok{data\_time }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{logit\_t =} \FunctionTok{mean}\NormalTok{(logit\_t),}
              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, relatedness, age)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, logit\_t, }
               \AttributeTok{colour =}\NormalTok{ relatedness,}
               \AttributeTok{fill =}\NormalTok{ relatedness,}
               \AttributeTok{shape =}\NormalTok{ relatedness)) }\SpecialCharTok{+}
    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
    \CommentTok{\# geom\_line(data = epreds,}
    \CommentTok{\#         aes(y = .epred,}
    \CommentTok{\#           group = interaction(relatedness, .draw)),}
    \CommentTok{\#         linetype = "solid",}
    \CommentTok{\#         alpha = 0.1,}
    \CommentTok{\#         linewidth = 3/4) +}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred),}
                 \AttributeTok{fun.data =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{mean\_qi}\NormalTok{(x, }\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{),}
                 \AttributeTok{geom =} \StringTok{"ribbon"}\NormalTok{,}
                 \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
                 \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred,}
                    \AttributeTok{linetype =}\NormalTok{ relatedness),}
                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean,}
                 \AttributeTok{geom =} \StringTok{"point"}\NormalTok{,}
                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
                 \AttributeTok{size =} \FloatTok{2.5}\NormalTok{,}
                 \AttributeTok{stroke =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
         \AttributeTok{colour =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{fill =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{linetype =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{shape =} \StringTok{"Prime type"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{+}
    \FunctionTok{scale\_colour\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{end =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_fill\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.85}\NormalTok{, }\AttributeTok{end =} \FloatTok{0.35}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{+}
    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{(x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{, }\AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{+}
    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{,}
          \AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{manuscript_files/figure-pdf/fig-related-1.pdf}

}

\caption{\label{fig-related}\textbf{?(caption)}}

\end{figure}

\hypertarget{cognate-priming-cognate-vs.-non-cognate}{%
\subsection{Cognate priming: Cognate
vs.~Non-cognate}\label{cognate-priming-cognate-vs.-non-cognate}}

A model including the \emph{Cognateness} \(\times\) \emph{Group}
interaction showed the best of-of-sample predictive performance,
although the model including only \emph{Cognateness} performed
equivalently
(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) = -1.835,
\emph{SE} = 2.279). Both models showed substantially better predictive
performance than the model including only \emph{Group}
(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) =
-43.201, \emph{SE} = 10.598). This indicates that including the
\emph{Cognateness} predictor improved the predictive performance of the
model significantly, that including its interaction with \emph{Group}
slightly increased the performance of the model, and that the main
effect of \emph{Group} by itself barely changed the predictive
performance of the model.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{cognateness =} \FunctionTok{levels}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{cognateness),}
                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{20}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{age),}
                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{lp)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fit\_cognate\_alt,}
                    \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }

\NormalTok{data\_time\_cognateness\_alt }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{logit\_t =} \FunctionTok{mean}\NormalTok{(logit\_t),}
              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, cognateness, age)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, logit\_t, }
               \AttributeTok{colour =}\NormalTok{ cognateness,}
               \AttributeTok{fill =}\NormalTok{ cognateness,}
               \AttributeTok{shape =}\NormalTok{ cognateness)) }\SpecialCharTok{+}
    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
    \CommentTok{\# geom\_line(data = epreds,}
    \CommentTok{\#         aes(y = .epred,}
    \CommentTok{\#           group = interaction(cognateness, .draw)),}
    \CommentTok{\#         linetype = "solid",}
    \CommentTok{\#         alpha = 0.1,}
    \CommentTok{\#         linewidth = 3/4) +}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred),}
                 \AttributeTok{fun.data =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{mean\_qi}\NormalTok{(x, }\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{),}
                 \AttributeTok{geom =} \StringTok{"ribbon"}\NormalTok{,}
                 \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
                 \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred,}
                    \AttributeTok{linetype =}\NormalTok{ cognateness),}
                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean,}
                 \AttributeTok{geom =} \StringTok{"point"}\NormalTok{,}
                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
                 \AttributeTok{size =} \FloatTok{2.5}\NormalTok{,}
                 \AttributeTok{stroke =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
         \AttributeTok{colour =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{fill =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{linetype =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{shape =} \StringTok{"Prime type"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{+}
    \FunctionTok{scale\_colour\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{end =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_fill\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.85}\NormalTok{, }\AttributeTok{end =} \FloatTok{0.35}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{+}
    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{(x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{, }\AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{+}
    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{,}
          \AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{manuscript_files/figure-pdf/fig-cognate-1.pdf}

}

\caption{\label{fig-cognate}\textbf{?(caption)}}

\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\hypertarget{relaxing-trial-inclusion-criteria}{%
\subsection{Relaxing trial inclusion
criteria}\label{relaxing-trial-inclusion-criteria}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{relatedness =} \FunctionTok{levels}\NormalTok{(data\_time\_alt}\SpecialCharTok{$}\NormalTok{relatedness),}
                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{20}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time}\SpecialCharTok{$}\NormalTok{age),}
                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_alt}\SpecialCharTok{$}\NormalTok{lp)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fit\_related\_alt,}
                    \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }

\NormalTok{data\_time\_alt }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{logit\_t =} \FunctionTok{mean}\NormalTok{(logit\_t),}
              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, relatedness, age)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, logit\_t, }
               \AttributeTok{colour =}\NormalTok{ relatedness,}
               \AttributeTok{fill =}\NormalTok{ relatedness,}
               \AttributeTok{shape =}\NormalTok{ relatedness)) }\SpecialCharTok{+}
    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
    \CommentTok{\# geom\_line(data = epreds,}
    \CommentTok{\#         aes(y = .epred,}
    \CommentTok{\#           group = interaction(relatedness, .draw)),}
    \CommentTok{\#         linetype = "solid",}
    \CommentTok{\#         alpha = 0.1,}
    \CommentTok{\#         linewidth = 3/4) +}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred),}
                 \AttributeTok{fun.data =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{mean\_qi}\NormalTok{(x, }\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{),}
                 \AttributeTok{geom =} \StringTok{"ribbon"}\NormalTok{,}
                 \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
                 \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred,}
                    \AttributeTok{linetype =}\NormalTok{ relatedness),}
                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean,}
                 \AttributeTok{geom =} \StringTok{"point"}\NormalTok{,}
                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
                 \AttributeTok{size =} \FloatTok{2.5}\NormalTok{,}
                 \AttributeTok{stroke =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
         \AttributeTok{colour =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{fill =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{linetype =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{shape =} \StringTok{"Prime type"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{+}
    \FunctionTok{scale\_colour\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{end =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_fill\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.85}\NormalTok{, }\AttributeTok{end =} \FloatTok{0.35}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{+}
    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{(x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{, }\AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{+}
    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{,}
          \AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{manuscript_files/figure-pdf/fig-related-alt-1.pdf}

}

\caption{\label{fig-related-alt}\textbf{?(caption)}}

\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{cognateness =} \FunctionTok{levels}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{cognateness),}
                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{20}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{age),}
                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{lp)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fit\_cognate\_alt,}
                    \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }

\NormalTok{data\_time\_cognateness\_alt }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{logit\_t =} \FunctionTok{mean}\NormalTok{(logit\_t),}
              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, cognateness, age)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, logit\_t, }
               \AttributeTok{colour =}\NormalTok{ cognateness,}
               \AttributeTok{fill =}\NormalTok{ cognateness,}
               \AttributeTok{shape =}\NormalTok{ cognateness)) }\SpecialCharTok{+}
    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
    \CommentTok{\# geom\_line(data = epreds,}
    \CommentTok{\#         aes(y = .epred,}
    \CommentTok{\#           group = interaction(cognateness, .draw)),}
    \CommentTok{\#         linetype = "solid",}
    \CommentTok{\#         alpha = 0.1,}
    \CommentTok{\#         linewidth = 3/4) +}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred),}
                 \AttributeTok{fun.data =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{mean\_qi}\NormalTok{(x, }\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{),}
                 \AttributeTok{geom =} \StringTok{"ribbon"}\NormalTok{,}
                 \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
                 \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred,}
                    \AttributeTok{linetype =}\NormalTok{ cognateness),}
                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean,}
                 \AttributeTok{geom =} \StringTok{"point"}\NormalTok{,}
                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
                 \AttributeTok{size =} \FloatTok{2.5}\NormalTok{,}
                 \AttributeTok{stroke =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
         \AttributeTok{colour =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{fill =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{linetype =} \StringTok{"Prime type"}\NormalTok{,}
         \AttributeTok{shape =} \StringTok{"Prime type"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{+}
    \FunctionTok{scale\_colour\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{end =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_fill\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.85}\NormalTok{, }\AttributeTok{end =} \FloatTok{0.35}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{+}
    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{(x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{, }\AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{+}
    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{,}
          \AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{manuscript_files/figure-pdf/fig-cognate-alt-1.pdf}

}

\caption{\label{fig-cognate-alt}\textbf{?(caption)}}

\end{figure}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bosch2001evidence}{}}%
Bosch, L., \& Sebastián-Gallés, N. (2001). Evidence of early language
discrimination abilities in infants from bilingual environments.
\emph{Infancy}, \emph{2}(1), 29--49.

\leavevmode\vadjust pre{\hypertarget{ref-wood2017generalized}{}}%
Wood, S. N. (2017). \emph{Generalized additive models: An introduction
with r}. CRC press.

\leavevmode\vadjust pre{\hypertarget{ref-bosch2001evidence}{}}%
Bosch, L., \& Sebastián-Gallés, N. (2001). Evidence of early language
discrimination abilities in infants from bilingual environments.
\emph{Infancy}, \emph{2}(1), 29--49.

\leavevmode\vadjust pre{\hypertarget{ref-wood2017generalized}{}}%
Wood, S. N. (2017). \emph{Generalized additive models: An introduction
with r}. CRC press.

\end{CSLReferences}

\end{document}

### 2023-09-12 manuscript/test.qmd
Update

---
project:
  render:
    - manuscript.qmd

format:
  pdf:
    keep-tex: true  
    linenumbers: true
    doublespacing: false
    include-in-header: 
      text: |
        \usepackage{tipa}
        \usepackage{booktabs}
        \hyphenpenalty=100000
        \exhyphenpenalty=100000
    knitr:
      opts_chunk:
        dev: "cairo_pdf"
    filters: 
      - "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"

title: "Developmental trajectories of bilingual word recognition"
short-title: "Developmental trajectories of bilingual word recognition"
author:
  - name: Gonzalo Garcia-Castro
    corresponding: true
    orcid: 0000-0002-8553-4209
    email: gonzalo.garciadecastro@upf.edu
    affiliations:
      - id: cbc
        name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
        city: Barcelona, 08005
  - name: Serene Siow
    orcid: 0000-0001-6482-2191
    email: siow.serene@gmail.com
    affiliations: 
      - id: oxf
        name: University of Oxford
        department: Department of Experimental Psychology
        city: Oxford, OX2 6GG
  - name: Nuria Sebastian-Galles
    orcid: 0000-0001-6938-2498
    email: nuria.sebastian@upf.edu
    affiliations: 
      - ref: cbc
  - name: Kim Plunkett
    orcid: 0000-0003-0216-7480
    email: kim.plunkett@psy.ox.ac.uk
    affiliations: 
      - ref: oxf
keywords:
  - cognate
  - word recognition
  - lexicon
  - language acquisition
  - vocabulary
  - bilingualism
  - general additive mixed models
  - bayesian
csl: "../assets/apa7.csl"
bibliography: "../assets/references.bib"
link-citations: true
editor: source
lang: en
freeze: true
fig-dpi: 1000
---

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2023-09-12 R/vocabulary.R

@@ -4,51 +4,168 @@ get_vocabulary <- function(participants, # participants dataset (get_participant
 ){
 	
 	# vocabulary sizes BVQ database and Cognate Priming
+	participants_tmp <- subset(participants, select = c(id_db, age_group, age, lp, filename))
 	
-	participants_tmp <- select(participants, id_db, age_group, lp)
+	# get vocabulary contents
+	vocab_contents <- get_vocabulary_contents(participants, bvq_data)
 	
-	to_impute <- bvq_data$vocabulary_comp |>
+	vocabulary <- bvq_data$vocabulary |>
 		mutate(id_db = id) |> 
 		right_join(select(participants_tmp, id_db, age_group, lp),
 				   by = join_by(id_db, age_group)) |> 
 		rowwise() |> 
 		mutate(is_imputed = any(is.na(c_across(total_prop:te_prop)))) |> 
 		ungroup() |> 
-		relocate(id, age_group, is_imputed)
-	
-	# index of missing observations to impute
-	impute <- function(x) {
-		suppressWarnings({
-			x <- select(x, id_db, lp, age_group, ends_with("_prop"))
-			impute_index <- is.na(x)
-			impute_index[, 1:3] <- FALSE
-			
-			mice::mice(x, 
-					   m = 5,
-					   printFlag = FALSE,
-					   where = impute_index,
-					   method = "pmm", 
-					   seed = 888) |> 
-				mice::complete() |> 
-				as_tibble()
-		})
-	}
-	
-	# multiple imputation
-	imputed <- to_impute |>
-		filter(age_group != "Other") |> 
-		impute()
-	
-	# merge both datasets
-	vocabulary <- left_join(participants_tmp, imputed,
-							by = join_by(id_db, age_group, lp)) |> 
-		left_join(select(to_impute, id_db, age_group, is_imputed),
-				  by = join_by(id_db, age_group)) |> 
+		relocate(id, age_group, is_imputed) |> 
+		left_join(select(participants_tmp, id_db, age_group, age),
+				  by = join_by(age_group, id_db)) |> 
+		# multiple imputation
+		impute_vocabulary(cols_impute = c("total_prop", "l1_prop",
+										  "l2_prop", "concept_prop",
+										  "te_prop"), 
+						  cols_predictor = c("age", "lp"), 
+						  bvq_data = bvq_data) |> 
+		# merge both datasets
[…]

### 2023-09-18 docs/index.qmd

@@
 		   loos_aggregated, loos_timecourse,
-		   data_time, data_summary))
+		   data_time, data_summary,
+		   model_fits_related,
+		   model_fits_cognate))
 

### 2023-09-19 manuscript/manuscript.qmd
Add alternative data processing filters

@@
 					attrition_trials, attrition_participants,
+					attrition_trials_vtarget, attrition_participants_vtarget,
+					attrition_trials_vnone, attrition_participants_vnone,
+					attrition_trials_noeach, attrition_participants_noeach,
 					bvq_data, gaze_aoi, 
 					data_time_related, data_time_cognate,
-					data_summary))
-
-targets::tar_load(c(model_fit_related_0,
-					model_fit_related_1,
-					model_fit_related_2,
-					model_fit_related_3,
-					model_fit_cognate_0,
-					model_fit_cognate_1,
-					model_fit_cognate_2,
-					model_fit_cognate_3,
+					data_time_related_vtarget, data_time_cognate_vtarget,
+					data_time_related_vnone, data_time_cognate_vnone,
+					data_time_related_noeach, data_time_cognate_noeach))
+
+targets::tar_load(
+	c(model_fits_related,
+	  model_fits_cognate,
+	  model_fits_related_vtarget,
+	  model_fits_cognate_vtarget,
+	  model_fits_related_vnone,
+	  model_fits_cognate_vnone,
+	  model_fits_related_noeach,
+	  model_fits_cognate_noeach,
 	  model_loo_related,
-					model_loo_cognate))
+	  model_loo_cognate,
+	  model_loo_related_vtarget,
+	  model_loo_cognate_vtarget,
+	  model_loo_related_vnone,
+	  model_loo_cognate_vnone,
+	  model_loo_related_noeach,
+	  model_loo_cognate_noeach
+	))
 
@@
 library(patchwork)
+library(english)
 
@@
 
+clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
+
+options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
+		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
+		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
+		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
+		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
+		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
+
 set.seed(888)
@@
 
-```
-
-# Introduction
-
+attrition_participants_vtarget <- attrition_participants_vtarget |> 
+	left_join(select(participants, id, age_group, lp, filename))
+
+attrition_trials_vtarget <- left_join(attrition_trials_vtarget, 
+									  select(participants, id, age_group, lp, filename))
+
+attrition_participants_vnone <- attrition_participants_vnone |> 
+	left_join(select(participants, id, age_group, lp, filename))
+
+attrition_trials_vnone <- left_join(attrition_trials_vnone, 
+									select(participants, id, age_group, lp, filename))
+
+attrition_participants_noeach <- attrition_participants_noeach |> 
+	left_join(select(participants, id, age_group, lp, filename))
+
+attrition_trials_noeach <- left_join(attrition_trials_noeach, 
+									 select(participants, id, age_group, lp, filename))
+
+```
+
+<!--
 The formation of a mental lexicon is a critical developmental achievement for infants_ learning words allows infants to retrieve socially relevant concepts from fairly arbitrary linguistic forms embedded in speech.
@@
 Implicit naming as a paradigm to study cross-language activation. (Mani & Plunkett, 2010, 2011a).
+-->
 
@@
 
-We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson2004variability] developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers.
+We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability] developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers.
 Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
@@
 `r n_imputed` (`r prop_imputed`) Families failed to provide a complete response to the BVQ within the two-week time limit, or did not provide a successful response to the questionnaire.
-For missing questionnaire responses, we imputed the vocabulary size of the participant using multiple imputation [@vanbuuren2018flexible], using the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
+For missing questionnaire responses, we imputed the vocabulary size of the participant using single imputation, using the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
 We used participants age in months and their language profile (monolingual/bilingual) as predictors.
-We used the `mice` R package [@mice] to perform imputation using the Bayesian linear regression method.
+We used the `mice` R package [@van2011mice] to perform imputation using the Bayesian linear regression method.
 
 ```{r tbl-vocabulary}
+#| label: tbl-vocabulary
+#| tbl-cap: "Vocabulary sizes.
+Total: proportion of words in both languages marked as *Understands*.
+L1: proportion of words in the dominant language marked as *Understands*.
+L2: proportion of words in the non-cominant language marked as *Understands*.
+Conceptual: proportion of translation equivalents for which at least one of the words has ben marked as *Understands*.
+TE: proportion of translation equivalents for which *both* words have been marked as *Understands*."
 vocabulary |> 
@@
 	summarise(across(matches("prop"), 
-					 tibble::lst(mean, sd, min, max)),
+					 tibble::lst(mean, sd)),
 			  .by = c(age_group, lp)) |>
@@
 	cols_merge_uncert(te_prop_mean, te_prop_sd) |> 
-	cols_merge_range(total_prop_min, total_prop_max) |> 
-	cols_merge_range(l1_prop_min, l1_prop_max) |> 
-	cols_merge_range(l2_prop_min, l2_prop_max) |> 
-	cols_merge_range(concept_prop_min, concept_prop_max) |> 
-	cols_merge_range(te_prop_min, te_prop_max) |> 
 	fmt_number(is.numeric, 
@@
 	cols_label(total_prop_mean = "Mean (SD)",
-			   total_prop_min = "Range",
 			   l1_prop_mean = "Mean (SD)",
-			   l1_prop_min = "Range",
 			   l2_prop_mean = "Mean (SD)",
-			   l2_prop_min = "Range",
 			   concept_prop_mean = "Mean (SD)",
-			   concept_prop_min = "Range",
-			   te_prop_mean = "Mean (SD)",
-			   te_prop_min = "Range") |> 
+			   te_prop_mean = "Mean (SD)") |> 
 	tab_stub_indent(rows = everything(),
@@
 
-### Stimuli
+## Stimuli
 
@@
 
-#### Auditory stimuli
+### Auditory stimuli
 
@@
 Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
-We used the Audacity [@reference] and Praat [@reference] to record and edit the audio files.
+We used the Audacity [@reference] and Praat [@boersma2001speak] to record and edit the audio files.
 The speaker was presented with a list of words in Catalan.
@@
 
-#### Visual stimuli
+### Visual stimuli
 
@@
 
-### Data processing
-
-```{r attrition-numbers}
-n_trials <- nrow(attrition_trials)
-
-n_sessions <- distinct(attrition_trials, filename) |> 
-	nrow()
-
-n_participants <- distinct(attrition_trials, id) |> 
-	nrow()
-
-n_trials_prime <- attrition_trials |> 
-	filter(is_valid_gaze_prime)
-
-n_trials_test <- n_trials_prime |> 
-	filter(is_valid_gaze_test)
-
-n_trials_each <- n_trials_test |> 
-	filter(is_valid_gaze_test_each)
-
-n_trials_vocab <- n_trials_each |> 
-	filter(is_valid_vocab)
-
-n_trials_participant <- n_trials_vocab |> 
-	inner_join(filter(attrition_participants,
-					  is_valid_participant),
-			   by = join_by(filename))
-
-n_sessions_valid <- attrition_participants |> 
-	filter(is_valid_participant)
-
-n_participants_valid <- n_trials_participant |> 
-	distinct(filename)
-
-n_longitudinal <- n_sessions_valid |> 
-	left_join(select(participants, id, age_group, filename),
-			  by = join_by(filename, id, age_group)) |> 
-	count(id, name = "sessions") |> 
-	count(sessions)
-
-n_participants_include <- read_csv(
-	file.path("data-raw", "participants.csv"),
-	show_col_types = FALSE
-)
-```
-
-We gathered data for `r format(n_trials, big.mark = ",")` trials from `r n_sessions` experimental sessions, provided by `r n_participants` distinct participants.
-Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach].
-We excluded trials in which the participant did not fixate the prime at least half of the time of the prime phase ($\geq$ 750 ms, *n* = `r format(n_trials - nrow(n_trials_prime), big.mark = ",")`), or the target and distractor during the test phase ($\geq$ 1,000 ms, *n* = `r format(nrow(n_trials_prime) - nrow(n_trials_test), big.mark = ",")`).
-We also excluded trials in which the participant failed to fixate both target *and* distractor pictures for at least 100 ms (i.e., 5% of the time) (`r format(nrow(n_trials_test) - nrow(n_trials_each), big.mark = ",")` trials excluded).
-We then excluded trials in which the participant was not reported to understand the prime *and* the target words, according to their caregivers' responses to the vocabulary checklist.
-This resulted in the exclusion of `r format(nrow(n_trials_each) - nrow(n_trials_vocab), big.mark = ",")` trials.
-Finally, we excluded trials from experimental sessions in which the participant did not provide at least two valid trials in each of the three experimental conditions (cognate prime, non-cognate prime, and unrelated prime) which resulted in the exclusion of `r nrow(distinct(n_trials_vocab, id, age_group)) - nrow(n_sessions_valid)` experimental sessions and their `r nrow(n_trials_vocab) - nrow(n_trials_participant)` remaining trials.
-The final data set comprised `r format(sum(with(attrition_trials, is_valid_trial)), big.mark = ",")` from `r nrow(n_sessions_valid)` experimental sessions, provided by `r nrow(n_participants_valid)` distinct participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-
 We defined our time window of interest from 300 ms after the onset of the test phase (target and distractor presentation) until the end of the test phase (2,000 ms).
@@
 Finally, we computed the empirical logit of target fixations, which we introduced in the statistical analyses as our response variable.
-
-```{r} 
-#| label: tbl-attrition-group
-#| tbl-cap: "Summary of the dataset."
-attrition_trials |> 
-	left_join(select(participants, age_group, lp, id, date_test),
-			  by = join_by(id, age_group)) |> 
-	left_join(attrition_participants,
-			  by = join_by(id, age_group)) |> 
-	add_count(age_group, lp, name = "n_trials") |> 
-	summarise(valid_trial_count = sum(is_valid_trial, na.rm = TRUE),
-			  .by = c(id, lp, trial_type, date_test,
-			  		age_group, is_valid_participant, n_trials)) |> 
-	pivot_wider(names_from = trial_type, 
-				values_from = valid_trial_count, 
-				values_fill = 0,
-				names_repair = janitor::make_clean_names) |> 
-	rename(noncognate = non_cognate) |> 
-	add_count(lp, age_group) |>
-	summarise(across(c(cognate, noncognate, unrelated),
-					 lst(sum, mean, sd)),
-			  n_valid = sum(is_valid_participant),
-			  .by = c(lp, age_group, n, n_trials)) |>
-	relocate(n_valid, .after = n) |> 
-	mutate(n_prop = n_valid/n) |> 
-	arrange(age_group, lp) |> 
-	relocate(age_group, lp, n_valid, n_prop, 
-			 matches("cognate"),
-			 matches("noncognate"),
-			 matches("unrelated")) |> 
-	gt(groupname_col = "age_group",
-	   rowname_col = "lp")  |>
-	cols_hide(c(n, n_trials)) |> 
-	fmt_number(matches("_mean|_sd"), 
-			   decimals = 1) |>
-	fmt_percent(matches("_prop"),
-				decimals = 1) |> 
-	cols_merge_n_pct(col_n = n_valid, 
-					 col_pct = n_prop,
-					 autohide = TRUE)  |> 
-	tab_spanner("Non-cognate", matches("noncognate")) |>
-	tab_spanner("Cognate", starts_with("cognate")) |>
-	tab_spanner("Unrelated", matches("unrelated")) |>
-	tab_spanner("Related", matches("cognate")) |> 
-	cols_merge_uncert(col_val = cognate_mean,
-					  col_uncert = cognate_sd) |> 
-	cols_merge_uncert(col_val = noncognate_mean,
-					  col_uncert = noncognate_sd) |> 
-	cols_merge_uncert(col_val = unrelated_mean, 
-					  col_uncert = unrelated_sd) |> 
-	cols_label(age_group = "Age",
-			   n_valid = "Participants (included)",
-			   cognate_sum = "Trials",
-			   cognate_mean = "Mean ± SD",
-			   noncognate_sum = "Trials",
-			   noncognate_mean = "Mean ± SD",
-			   unrelated_sum = "Trials",
-			   unrelated_mean = "Mean ± SD") |> 
-	summary_rows(groups = TRUE,
-				 columns = where(is.integer),
-				 fns = list("Sum" = "sum"),
-				 fmt = fmt_number,
-				 decimals = 0) |>
-	summary_rows(groups = TRUE,
-				 columns = c(where(is.numeric), -n_valid),
-				 fns = list("Mean" = "mean"),
-				 fmt = fmt_number,
-				 decimals = 1) |>
-	grand_summary_rows(columns = where(is.integer),
-					   fns = list("N" = "sum"),
-					   formatter = fmt_integer) 
-```
-
-### Modelling approach
+Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach].
 
@@
 
-## Phonological priming: Related vs. Unrelated
+## Analysis 1
+
+Participants must know **prime** *and* **target** words, and must look at least 10 ms to each target and distractor.
+
+```{r dataset}
+n_trials <- nrow(attrition_trials)
+n_total <- n_distinct(attrition_trials$id)
+n_trials_valid <- inner_join(attrition_participants,
+							 attrition_trials,
+							 by = join_by(id)) |> 
+	filter(is_valid_participant) |> 
+	pull(is_valid_trial) |> 
+	sum()
+n_participants_valid <- sum(attrition_participants$is_valid_participant)
+n_exc_prime <- sum(!attrition_trials$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition_trials$is_valid_gaze_test)
+n_exc_test_each <- sum(!attrition_trials$is_valid_gaze_test_each)
+n_exc_vocab <- sum(!attrition_trials$is_valid_vocab)
+n_exc_cognate <- sum(!attrition_participants$is_valid_cognate)
+n_exc_noncognate <- sum(!attrition_participants$is_valid_noncognate)
+n_exc_unrelated <- sum(!attrition_participants$is_valid_unrelated)
+
+n_longitudinal <- attrition_participants |>
+	filter(is_valid_participant) |>
+	count(id, name = "times") |> 
+	count(times)
+```
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
+We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+We also excluded trials in which participants did not provide at least 5% of valid samples to *both* target and distractor in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
+Finally, we excluded trials in which participants did not understand the prime *or* the target word, according to a supplementary vocabulary checklist filled by their caregivers upon experiment completion (*n* = `r format(n_exc_vocab, big.mark = ",")`).
+After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
+The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+@tbl-attrition-trials shows a detailed description of the trial attrition.
+
+```{r tbl-attrition-trials}
+#| label: tbl-attrition-trials
+#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
+attrition_trials |> 
+	filter(id %in% attrition_participants$id[attrition_participants$is_valid_participant]) |> 
+	left_join(select(participants, filename, id, age_group),
+			  by = join_by(filename, id, age_group)) |> 
+	summarise(n_valid = sum(is_valid_trial),
+			  n_total = n(),
+			  .by = c(id, age_group, trial_type)) |> 
+	summarise(across(n_valid, lst(sum, mean, sd),
+					 .names = "{.fn}"),
+			  n_total = sum(n_total),
+			  .by = c(age_group, trial_type)) |> 
+	mutate(n_excluded = n_total-sum) |> 
+	select(-c(n_total)) |> 
+	pivot_wider(names_from = trial_type,
+				values_from = c(sum:sd, n_excluded),
+				names_repair = janitor::make_clean_names) |> 
+	rename_with(\(x) gsub("non_cognate", 
+						  "noncognate",
+						  x)) |> 
+	arrange(age_group) |> 
+	relocate(age_group,
+			 matches("_cognate"),
+			 matches("noncognate")) |> 
+	gt(rowname_col = "age_group") |> 
+	grand_summary_rows(columns = matches("mean_"),
+					   fns = lst(Mean ~ mean(.)),
+					   fmt = ~fmt_number(.)) |>
+	grand_summary_rows(columns = matches("sum_"),
+					   fns = lst(Sum ~ sum(.)),
+					   fmt = ~fmt_integer(.)) |>
+	cols_merge(c(sum_cognate, n_excluded_cognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_unrelated, n_excluded_unrelated),
+			   pattern = "{1} ({2})") |> 
+	cols_merge_uncert(mean_cognate, sd_cognate) |> 
+	cols_merge_uncert(mean_noncognate, sd_noncognate) |> 
+	cols_merge_uncert(mean_unrelated, sd_unrelated) |> 
+	tab_spanner("Cognate trials", ends_with("_cognate")) |>
+	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
+	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
+	tab_spanner("Related trials", matches("cognate")) |>
+	fmt_number(matches("mean|sd")) |> 
+	fmt_integer(matches("sum"), sep_mark = ",") |> 
+	cols_label(sum_cognate = "N",
+			   sum_noncognate = "N",
+			   sum_unrelated = "N",
+			   mean_cognate = "Mean",
+			   mean_noncognate = "Mean",
+			   mean_unrelated = "Mean")
+```
+
+### Phonological priming: Related vs. Unrelated
 
@@
 					  .nsamples = 1) |>
-	add_epred_draws(model_fit_related_3,
+	add_epred_draws(model_fits_related[[4]],
 					ndraws = NULL,
@@
 
-diff_rect <- epreds_diff |> 
-	mean_qi(diff) |> 
-	mutate(is_cluster = .lower > 0 | .upper < 0)
-
-clusters <- rle(diff(diff_rect$is_cluster))
-diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
-
-diff_rect <- diff_rect |> 
-		arrange(lp, timebin)
-
-diff_rect <- 
-	cluster_number = 
-	summarise(xmin = min(timebin),
-			  xmax = max(timebin),
-			  .by = c(lp, is_cluster)) |> 
-	filter(is_cluster)
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
+# 
+# clusters <- rle(diff(diff_rect$is_cluster))
+# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
+# 
+# diff_rect <- diff_rect |> 
+# 	arrange(lp, timebin)
+# 
+# diff_rect <- 
+# 	cluster_number = 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = c(lp, is_cluster)) |> 
+# 	filter(is_cluster)
 
@@
 	facet_wrap(~lp) +
-	geom_rect(data = diff_rect,
-			  aes(xmin = xmin,
-			  	xmax = xmax,
-			  	ymin = -Inf,
-			  	ymax = Inf),
-			  colour = NA,
-			  fill = "orange",
-			  alpha = 1/2,
-			  inherit.aes = FALSE) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
 	# geom_line(data = epreds,
@@
 	facet_wrap(~lp) +
-	geom_rect(data = diff_rect,
-			  aes(xmin = xmin,
-			  	xmax = xmax,
-			  	ymin = -Inf,
-			  	ymax = Inf),
-			  colour = NA,
-			  fill = "orange",
-			  alpha = 1/2,
-			  inherit.aes = FALSE) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
 	stat_lineribbon(.width = 0.95,
-					linewidth = 0) +
+					linewidth = 0,
+					fill = "grey") +
 	stat_summary(data = epreds_diff,
@@
 	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_colour_grey(start = 0.8, end = 0) &
-	scale_fill_grey(start = 0.85, end = 0.35) &
 	scale_shape_manual(values = c(1, 2)) &
@@
 
-## Cognate priming: Cognate vs. Non-cognate
+### Cognate priming: Cognate vs. Non-cognate
 
@@
 epreds <- expand_grid(condition = levels(data_time_cognate$condition),
-					  timebin = seq(0, 20, length.out = 100),
+					  timebin = seq(0, 17, length.out = 100),
 					  age = mean(data_time_cognate$age),
-					  lp = levels(data_time_cognate$lp)) |>
-	add_epred_draws(model_fit_cognate_3,
+					  lp = levels(data_time_cognate$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_cognate[[4]],
 					ndraws = NULL,
@@
 	mutate(diff = cognate - non_cognate) 
-
-diff_rect <- epreds_diff |> 
-	mean_qi(diff) |> 
-	filter(.lower > 0 | .upper < 0) |> 
-	summarise(xmin = min(timebin),
-			  xmax = max(timebin),
-			  .by = lp)
+# 
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	filter(.lower > 0 | .upper < 0) |> 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = lp)
 
@@
 	facet_wrap(~lp) +
-	geom_rect(data = diff_rect,
-			  aes(xmin = xmin,
-			  	xmax = xmax,
-			  	ymin = -1.5,
-			  	ymax = 1.5),
-			  colour = NA,
-			  fill = "orange",
-			  alpha = 1/2,
-			  inherit.aes = FALSE) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -1.5,
+	# 		  	ymax = 1.5),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
 	# geom_line(data = epreds,
@@
 				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
+	geom_hline(yintercept = 0.5, 
 			   linewidth = 1/2,
@@
 	facet_wrap(~lp) +
-	geom_rect(data = diff_rect,
-			  aes(xmin = xmin,
-			  	xmax = xmax,
-			  	ymin = -3/4,
-			  	ymax = 3/4),
-			  colour = NA,
-			  fill = "orange",
-			  alpha = 1/2,
-			  inherit.aes = FALSE) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -3/4,
+	# 		  	ymax = 3/4),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
 	stat_lineribbon(.width = 0.95,
-					linewidth = 0) +
+					linewidth = 0,
+					fill = "grey") +
 	stat_summary(data = epreds_diff,
@@
 	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_colour_grey(start = 0.8, end = 0) &
-	scale_fill_grey(start = 0.85, end = 0.35) &
 	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format(x * 1e2, 
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
 											big.mark = ",")) &
-	theme(panel.grid = element_blank()) 
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
+## Analysis 2
+
+Participants must know the target **target** word (no need to know the prime word), and must look at least 10 ms to each target and distractor.
+
+```{r dataset-vtarget}
+n_trials <- nrow(attrition_trials_vtarget)
+n_trials_valid <- inner_join(attrition_participants_vtarget,
+							 attrition_trials_vtarget) |> 
+	filter(is_valid_participant) |> 
+	pull(is_valid_trial) |> 
+	sum()
+n_participants_valid <- sum(attrition_participants_vtarget$is_valid_participant)
+n_exc_prime <- sum(!attrition_trials_vtarget$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition_trials_vtarget$is_valid_gaze_test)
+n_exc_test_each <- sum(!attrition_trials_vtarget$is_valid_gaze_test_each)
+n_exc_vocab <- sum(!attrition_trials_vtarget$is_valid_vocab)
+n_exc_cognate <- sum(!attrition_participants_vtarget$is_valid_cognate)
+n_exc_noncognate <- sum(!attrition_participants_vtarget$is_valid_noncognate)
+n_exc_unrelated <- sum(!attrition_participants_vtarget$is_valid_unrelated)
+
+n_longitudinal <- attrition_participants_vtarget |>
+	filter(is_valid_participant) |>
+	count(id, name = "times") |> 
+	count(times)
+```
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
+We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+We also excluded trials in which participants did not provide at least 5% of valid samples to *both* target and distractor in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
+Finally, we excluded trials in which participants did not understand the target word, according to a supplementary vocabulary checklist filled by their caregivers upon experiment completion (*n* = `r format(n_exc_vocab, big.mark = ",")`).
+After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
+The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+@tbl-attrition-trials shows a detailed description of the trial attrition.
+
+```{r tbl-attrition-trials-vtarget}
+#| label: tbl-attrition-trials-vtarget
+#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
+attrition_trials_vtarget |> 
+	filter(id %in% attrition_participants_vtarget$id[attrition_participants_vtarget$is_valid_participant]) |> 
+	left_join(select(participants, filename, id, age_group),
+			  by = join_by(filename, id, age_group)) |> 
+	summarise(n_valid = sum(is_valid_trial),
+			  n_total = n(),
+			  .by = c(id, age_group, trial_type)) |> 
+	summarise(across(n_valid, lst(sum, mean, sd),
+					 .names = "{.fn}"),
+			  n_total = sum(n_total),
+			  .by = c(age_group, trial_type)) |> 
+	mutate(n_excluded = n_total-sum) |> 
+	select(-c(n_total)) |> 
+	pivot_wider(names_from = trial_type,
+				values_from = c(sum:sd, n_excluded),
+				names_repair = janitor::make_clean_names) |> 
+	rename_with(\(x) gsub("non_cognate", 
+						  "noncognate",
+						  x)) |> 
+	arrange(age_group) |> 
+	relocate(age_group,
+			 matches("_cognate"),
+			 matches("noncognate")) |> 
+	gt(rowname_col = "age_group") |> 
+	grand_summary_rows(columns = matches("mean_"),
+					   fns = lst(Mean ~ mean(.)),
+					   fmt = ~fmt_number(.)) |>
+	grand_summary_rows(columns = matches("sum_"),
+					   fns = lst(Sum ~ sum(.)),
+					   fmt = ~fmt_integer(.)) |>
+	cols_merge(c(sum_cognate, n_excluded_cognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_unrelated, n_excluded_unrelated),
+			   pattern = "{1} ({2})") |> 
+	cols_merge_uncert(mean_cognate, sd_cognate) |> 
+	cols_merge_uncert(mean_noncognate, sd_noncognate) |> 
+	cols_merge_uncert(mean_unrelated, sd_unrelated) |> 
+	tab_spanner("Cognate trials", ends_with("_cognate")) |>
+	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
+	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
+	tab_spanner("Related trials", matches("cognate")) |>
+	fmt_number(matches("mean|sd")) |> 
+	fmt_integer(matches("sum"), sep_mark = ",") |> 
+	cols_label(sum_cognate = "N",
+			   sum_noncognate = "N",
+			   sum_unrelated = "N",
+			   mean_cognate = "Mean",
+			   mean_noncognate = "Mean",
+			   mean_unrelated = "Mean")
+```
+
+### Phonological priming: Related vs. Unrelated
+
+A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related_vtarget[2, 1], 3)`, *SE* = `r round(model_loo_related_vtarget[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related_vtarget[3, 1], 3)`, *SE* = `r round(model_loo_related_vtarget[3, 2], 3)`).
+This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-related-vtarget}
+#| label: fig-related-vtarget
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_related_vtarget$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_related_vtarget$age),
+					  lp = levels(data_time_related_vtarget$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_related_vtarget[[4]],
+					ndraws = NULL,
+					re_formula = NA, 
+					value = ".value") |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .value,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = related - unrelated)
+
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
+# 
+# clusters <- rle(diff(diff_rect$is_cluster))
+# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
+# 
+# diff_rect <- diff_rect |> 
+# 	arrange(lp, timebin)
+# 
+# diff_rect <- 
+# 	cluster_number = 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = c(lp, is_cluster)) |> 
+# 	filter(is_cluster)
+
+# diff_obs <- data_time_related |>
+# 	pivot_wider(names_from = condition, 
+# 				values_from = elog,
+# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
+
+data_time_related_vtarget |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition,
+			   linetype = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .value),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .value,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 1/2, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	# geom_point(data = diff_obs) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
+### Cognate priming: Cognate vs. Non-cognate
+
+A model including the *Cognateness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Cognateness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate_vtarget[2, 1], 3)`, *SE* = `r round(model_loo_cognate_vtarget[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate_vtarget[3, 1], 3)`, *SE* = `r round(model_loo_cognate_vtarget[3, 2], 3)`).
+This indicates that including the *Cognateness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-cognate-vtarget}
+#| label: fig-cognate-vtarget
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_cognate_vtarget$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_cognate_vtarget$age),
+					  lp = levels(data_time_cognate_vtarget$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_cognate_vtarget[[4]],
+					ndraws = NULL,
+					re_formula = NA) |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .epred,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = cognate - non_cognate) 
+# 
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	filter(.lower > 0 | .upper < 0) |> 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = lp)
+
+data_time_cognate_vtarget |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -1.5,
+	# 		  	ymax = 1.5),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .epred),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .epred,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0.5, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 linetype = "Prime type",
+		 shape = "Prime type") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -3/4,
+	# 		  	ymax = 3/4),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
+## Analysis 3
+
+Participants do not need to know the prime or target words, but must look at least 10 ms to each target and distractor.
+
+```{r dataset-vnone}
+n_trials <- nrow(attrition_trials_vnone)
+n_trials_valid <- inner_join(attrition_participants_vnone,
+							 attrition_trials_vnone) |> 
+	filter(is_valid_participant) |> 
+	pull(is_valid_trial) |> 
+	sum()
+n_participants_valid <- sum(attrition_participants_vnone$is_valid_participant)
+n_exc_prime <- sum(!attrition_trials_vnone$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition_trials_vnone$is_valid_gaze_test)
+n_exc_test_each <- sum(!attrition_trials_vnone$is_valid_gaze_test_each)
+n_exc_vocab <- sum(!attrition_trials_vnone$is_valid_vocab)
+n_exc_cognate <- sum(!attrition_participants_vnone$is_valid_cognate)
+n_exc_noncognate <- sum(!attrition_participants_vnone$is_valid_noncognate)
+n_exc_unrelated <- sum(!attrition_participants_vnone$is_valid_unrelated)
+
+n_longitudinal <- attrition_participants_vnone |>
+	filter(is_valid_participant) |>
+	count(id, name = "times") |> 
+	count(times)
+```
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
+We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+We also excluded trials in which participants did not provide at least 5% of valid samples to *both* target and distractor in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
+After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
+The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+@tbl-attrition-trials shows a detailed description of the trial attrition.
+
+```{r tbl-attrition-trials-vnone}
+#| label: tbl-attrition-trials-vnone
+#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
+attrition_trials_vnone |> 
+	filter(id %in% attrition_participants_vnone$id[attrition_participants_vnone$is_valid_participant]) |> 
+	left_join(select(participants, filename, id, age_group),
+			  by = join_by(filename, id, age_group)) |> 
+	summarise(n_valid = sum(is_valid_trial),
+			  n_total = n(),
+			  .by = c(id, age_group, trial_type)) |> 
+	summarise(across(n_valid, lst(sum, mean, sd),
+					 .names = "{.fn}"),
+			  n_total = sum(n_total),
+			  .by = c(age_group, trial_type)) |> 
+	mutate(n_excluded = n_total-sum) |> 
+	select(-c(n_total)) |> 
+	pivot_wider(names_from = trial_type,
+				values_from = c(sum:sd, n_excluded),
+				names_repair = janitor::make_clean_names) |> 
+	rename_with(\(x) gsub("non_cognate", 
+						  "noncognate",
+						  x)) |> 
+	arrange(age_group) |> 
+	relocate(age_group,
+			 matches("_cognate"),
+			 matches("noncognate")) |> 
+	gt(rowname_col = "age_group") |> 
+	grand_summary_rows(columns = matches("mean_"),
+					   fns = lst(Mean ~ mean(.)),
+					   fmt = ~fmt_number(.)) |>
+	grand_summary_rows(columns = matches("sum_"),
+					   fns = lst(Sum ~ sum(.)),
+					   fmt = ~fmt_integer(.)) |>
+	cols_merge(c(sum_cognate, n_excluded_cognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_unrelated, n_excluded_unrelated),
+			   pattern = "{1} ({2})") |> 
+	cols_merge_uncert(mean_cognate, sd_cognate) |> 
+	cols_merge_uncert(mean_noncognate, sd_noncognate) |> 
+	cols_merge_uncert(mean_unrelated, sd_unrelated) |> 
+	tab_spanner("Cognate trials", ends_with("_cognate")) |>
+	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
+	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
+	tab_spanner("Related trials", matches("cognate")) |>
+	fmt_number(matches("mean|sd")) |> 
+	fmt_integer(matches("sum"), sep_mark = ",") |> 
+	cols_label(sum_cognate = "N",
+			   sum_noncognate = "N",
+			   sum_unrelated = "N",
+			   mean_cognate = "Mean",
+			   mean_noncognate = "Mean",
+			   mean_unrelated = "Mean")
+```
+
+### Phonological priming: Related vs. Unrelated
+
+A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related_vnone[2, 1], 3)`, *SE* = `r round(model_loo_related_vnone[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related_vnone[3, 1], 3)`, *SE* = `r round(model_loo_related_vnone[3, 2], 3)`).
+This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-related-vnone}
+#| label: fig-related-vnone
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_related_vnone$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_related_vnone$age),
+					  lp = levels(data_time_related_vnone$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_related_vnone[[4]],
+					ndraws = NULL,
+					re_formula = NA, 
+					value = ".value") |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .value,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = related - unrelated)
+
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
+# 
+# clusters <- rle(diff(diff_rect$is_cluster))
+# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
+# 
+# diff_rect <- diff_rect |> 
+# 	arrange(lp, timebin)
+# 
+# diff_rect <- 
+# 	cluster_number = 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = c(lp, is_cluster)) |> 
+# 	filter(is_cluster)
+
+# diff_obs <- data_time_related |>
+# 	pivot_wider(names_from = condition, 
+# 				values_from = elog,
+# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
+
+data_time_related_vnone |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition,
+			   linetype = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .value),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .value,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 1/2, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	# geom_point(data = diff_obs) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
+### Cognate priming: Cognate vs. Non-cognate
+
+A model including the *Cognateness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Cognateness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate_vnone[2, 1], 3)`, *SE* = `r round(model_loo_cognate_vnone[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate_vnone[3, 1], 3)`, *SE* = `r round(model_loo_cognate_vnone[3, 2], 3)`).
+This indicates that including the *Cognateness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-cognate-vnone}
+#| label: fig-cognate-vnone
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_cognate_vnone$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_cognate_vnone$age),
+					  lp = levels(data_time_cognate_vnone$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_cognate_vnone[[4]],
+					ndraws = NULL,
+					re_formula = NA) |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .epred,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = cognate - non_cognate) 
+# 
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	filter(.lower > 0 | .upper < 0) |> 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = lp)
+
+data_time_cognate_vnone |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -1.5,
+	# 		  	ymax = 1.5),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .epred),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .epred,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0.5, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 linetype = "Prime type",
+		 shape = "Prime type") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -3/4,
+	# 		  	ymax = 3/4),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
+## Analysis 4
+
+Participants do not need to know the prime or target words, and do not need to look to both pictures.
+
+```{r dataset-noeach}
+n_trials <- nrow(attrition_trials_noeach)
+n_trials_valid <- inner_join(attrition_participants_noeach,
+							 attrition_trials_noeach) |> 
+	filter(is_valid_participant) |> 
+	pull(is_valid_trial) |> 
+	sum()
+n_participants_valid <- sum(attrition_participants_noeach$is_valid_participant)
+n_exc_prime <- sum(!attrition_trials_noeach$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition_trials_noeach$is_valid_gaze_test)
+n_exc_test_each <- sum(!attrition_trials_noeach$is_valid_gaze_test_each)
+n_exc_vocab <- sum(!attrition_trials_noeach$is_valid_vocab)
+n_exc_cognate <- sum(!attrition_participants_noeach$is_valid_cognate)
+n_exc_noncognate <- sum(!attrition_participants_noeach$is_valid_noncognate)
+n_exc_unrelated <- sum(!attrition_participants_noeach$is_valid_unrelated)
+
+n_longitudinal <- attrition_participants_noeach |>
+	filter(is_valid_participant) |>
+	count(id, name = "times") |> 
+	count(times)
+```
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
+We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
+The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+@tbl-attrition-trials shows a detailed description of the trial attrition.
+
+```{r tbl-attrition-trials-noeach}
+#| label: tbl-attrition-trials-noeach
+#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
+attrition_trials_noeach |> 
+	filter(id %in% attrition_participants_noeach$id[attrition_participants_noeach$is_valid_participant]) |> 
+	left_join(select(participants, filename, id, age_group),
+			  by = join_by(filename, id, age_group)) |> 
+	summarise(n_valid = sum(is_valid_trial),
+			  n_total = n(),
+			  .by = c(id, age_group, trial_type)) |> 
+	summarise(across(n_valid, lst(sum, mean, sd),
+					 .names = "{.fn}"),
+			  n_total = sum(n_total),
+			  .by = c(age_group, trial_type)) |> 
+	mutate(n_excluded = n_total-sum) |> 
+	select(-c(n_total)) |> 
+	pivot_wider(names_from = trial_type,
+				values_from = c(sum:sd, n_excluded),
+				names_repair = janitor::make_clean_names) |> 
+	rename_with(\(x) gsub("non_cognate", 
+						  "noncognate",
+						  x)) |> 
+	arrange(age_group) |> 
+	relocate(age_group,
+			 matches("_cognate"),
+			 matches("noncognate")) |> 
+	gt(rowname_col = "age_group") |> 
+	grand_summary_rows(columns = matches("mean_"),
+					   fns = lst(Mean ~ mean(.)),
+					   fmt = ~fmt_number(.)) |>
+	grand_summary_rows(columns = matches("sum_"),
+					   fns = lst(Sum ~ sum(.)),
+					   fmt = ~fmt_integer(.)) |>
+	cols_merge(c(sum_cognate, n_excluded_cognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_unrelated, n_excluded_unrelated),
+			   pattern = "{1} ({2})") |> 
+	cols_merge_uncert(mean_cognate, sd_cognate) |> 
+	cols_merge_uncert(mean_noncognate, sd_noncognate) |> 
+	cols_merge_uncert(mean_unrelated, sd_unrelated) |> 
+	tab_spanner("Cognate trials", ends_with("_cognate")) |>
+	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
+	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
+	tab_spanner("Related trials", matches("cognate")) |>
+	fmt_number(matches("mean|sd")) |> 
+	fmt_integer(matches("sum"), sep_mark = ",") |> 
+	cols_label(sum_cognate = "N",
+			   sum_noncognate = "N",
+			   sum_unrelated = "N",
+			   mean_cognate = "Mean",
+			   mean_noncognate = "Mean",
+			   mean_unrelated = "Mean")
+```
+
+### Phonological priming: Related vs. Unrelated
+
+A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related_noeach[2, 1], 3)`, *SE* = `r round(model_loo_related_noeach[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related_noeach[3, 1], 3)`, *SE* = `r round(model_loo_related[3, 2], 3)`).
+This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-related-noeach}
+#| label: fig-related-noeach
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_related_noeach$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_related_noeach$age),
+					  lp = levels(data_time_related_noeach$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_related_noeach[[4]],
+					ndraws = NULL,
+					re_formula = NA, 
+					value = ".value") |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .value,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = related - unrelated)
+
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
+# 
+# clusters <- rle(diff(diff_rect$is_cluster))
+# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
+# 
+# diff_rect <- diff_rect |> 
+# 	arrange(lp, timebin)
+# 
+# diff_rect <- 
+# 	cluster_number = 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = c(lp, is_cluster)) |> 
+# 	filter(is_cluster)
+
+# diff_obs <- data_time_related |>
+# 	pivot_wider(names_from = condition, 
+# 				values_from = elog,
+# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
+
+data_time_related_noeach |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition,
+			   linetype = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .value),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .value,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 1/2, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	# geom_point(data = diff_obs) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
+### Cognate priming: Cognate vs. Non-cognate
+
+A model including the *Cognateness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Cognateness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate[2, 1], 3)`, *SE* = `r round(model_loo_cognate[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate[3, 1], 3)`, *SE* = `r round(model_loo_cognate[3, 2], 3)`).
+This indicates that including the *Cognateness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-cognate-noeach}
+#| label: fig-cognate-noeach
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_cognate_noeach$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_cognate_noeach$age),
+					  lp = levels(data_time_cognate_noeach$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_cognate_noeach[[4]],
+					ndraws = NULL,
+					re_formula = NA) |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .epred,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = cognate - non_cognate) 
+# 
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	filter(.lower > 0 | .upper < 0) |> 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = lp)
+
+data_time_cognate_noeach |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -1.5,
+	# 		  	ymax = 1.5),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .epred),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .epred,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0.5, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 linetype = "Prime type",
+		 shape = "Prime type") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -3/4,
+	# 		  	ymax = 3/4),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
 ```

### 2023-10-06 manuscript/manuscript.qmd
Add new analyses and sanity checks

@@
 
-targets::tar_load(c(participants, stimuli, vocabulary,
-					attrition_trials, attrition_participants,
-					attrition_trials_vtarget, attrition_participants_vtarget,
-					attrition_trials_vnone, attrition_participants_vnone,
-					attrition_trials_noeach, attrition_participants_noeach,
-					bvq_data, gaze_aoi, 
-					data_time_related, data_time_cognate,
-					data_time_related_vtarget, data_time_cognate_vtarget,
-					data_time_related_vnone, data_time_cognate_vnone,
-					data_time_related_noeach, data_time_cognate_noeach))
+targets::tar_load(
+	c(participants,
+	  stimuli,
+	  vocabulary,
+	  attrition_trials, 
+	  attrition_participants,
+	  attrition_trials_vtarget,
+	  attrition_participants_vtarget,
+	  attrition_trials_vnone, 
+	  attrition_participants_vnone,
+	  attrition_trials_noeach,
+	  attrition_participants_noeach,
+	  bvq_data, 
+	  gaze_aoi, 
+	  looking_times,
+	  data_time_related, 
+	  data_time_cognate,
+	  data_time_related_vtarget,
+	  data_time_cognate_vtarget,
+	  data_time_related_vnone,
+	  data_time_cognate_vnone,
+	  data_time_related_noeach, 
+	  data_time_cognate_noeach))
 
@@
 Implicit naming as a paradigm to study cross-language activation. (Mani & Plunkett, 2010, 2011a).
+
+Floccia et al.
+(2020) tested toddlers in a cross-language priming paradigm.
+A prime word was embedded at the end of a carrier sentence that participants listened to.
+Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
+Some critiques:
+
+- Since participants heard the auditory label in one of the languages, priming through translation might be compromised.
+- Translation equivalents (Exp.
+1) are more strongly related at the semantic level with each other than other pairs of semantically related words that are not translations of each other (table-mesa are more strongly associated than table-silla).
+- We used longitudinal participants, so we can examine the developmental trajectories of cross-language lateral inhibitory or excitatory connections better.
+- Larger sample size.
 -->
@@
 This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I.
-Before every testing session, caretakers were asked to read and sign an informed consent form, and were given a small gift at the end of it
+Before every testing session, caregivers were asked to read and sign an informed consent form, and were given a token of appreciation at the end of it.
 
@@
 The order of the trials was randomised across experimental session, so that each time a participant was tested, the order in which the prime-target-distractor was presented was randomised.
-Each participant was randomly assigned to one of the three list in the corresponding language (their dominant language, see @sec-lp), and always the same list across their experimental sessions in the case of a recurrent participant.
+Each participant was randomly assigned to one of the three lists in the corresponding language (their dominant language, see @sec-lp), and always the same list across their experimental sessions in the case of a recurrent participant.
 
@@
 To avoid infants guiding their gaze to these objects based on their saliency, we paired animals and food items together.
+The position of the target and distractor pictures (right or left) for each target-distractor pair was alternated, so that in one list the target would appear on the left, in another list it would appear on the right, and so on.
 
@@
 For each word, we created a picture with a typical referent.
+To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias-trejo2010].
 
@@
 
+We know present the results under four different trial-level inclusion criteria In Analysis 1, the child is required to understand the prime *and* the target words, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
+In Analysis 2, the child is required to understand the target word, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
+In Analysis 3, the child is not required to understand any word, but is still required to fixate both target and distractor for at last 50 ms each during the target-distractor phase.
+In Analysis 4, the child is not required to understand any word, nor to fixate at both target and distractor.
+
+For reference:
+
+* [@floccia2020] requires participants to know prime and target, but not to look at target *and* distractor (looking at at least one of them is enough).
+
+The fact that in some time course analyses participants seem to be looking predominantly towards one of the objects (despite the target and distractor pictures having been presented less than 300 ms before) is a common finding in previous studies using preferential looking procedures [e.g., @floccia2020translation].
+
+```{r fig-related-summary}
+#| label: fig-related-summary
+#| fig-height: 10
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+tibble::lst(data_time_related,
+			data_time_related_vtarget,
+			data_time_related_vnone,
+			data_time_related_noeach,
+			data_time_related_vnoeach) |> 
+	bind_rows(.id = "analysis") |>
+	mutate(analysis = case_when(
+		analysis=="data_time_related" ~ "Analysis 1",
+		analysis=="data_time_related_vtarget" ~ "Analysis 2",
+		analysis=="data_time_related_vnone" ~ "Analysis 3",
+		analysis=="data_time_related_noeach" ~ "Analysis 4",
+		analysis=="data_time_related_vnoeach" ~ "Analysis 5"
+	)) |> 
+	# summarise(.elog_mean = mean(.elog),
+	# 		  n = n(),
+	# 		  .elog_std = sd(.elog),
+	# 		  .by = c(condition, timebin, analysis, lp)) |>
+	# mutate(.elog_se = .elog_std/n) |> 
+	ggplot(aes(timebin, .elog,
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_grid(analysis~lp) +
+	geom_hline(yintercept = 0.5, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	geom_smooth(method = lm, 
+				se = FALSE, 
+				formula = y ~ splines::bs(x, 4)) +
+	# geom_errorbar(aes(ymin = .elog_mean - .elog_se*1.96, 
+	# 				  ymax = .elog_mean + .elog_se*1.96),
+	# 			  width = 0.25,
+	# 			  linewidth = 3/4) + 
+	# geom_line(size = 3/4) + 
+	stat_summary(fun = mean, geom = "point") +
+	stat_summary(fun.data = mean_se,
+				 geom = "errorbar",
+				 width = 0.25) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) +
+	# scale_shape_manual(values = c(1, 2)) +
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) 
+```
+
+```{r fig-cognate-summary}
+#| label: fig-cognate-summary
+#| fig-height: 10
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+tibble::lst(data_time_cognate,
+			data_time_cognate_vtarget,
+			data_time_cognate_vnone,
+			data_time_cognate_noeach,
+			data_time_cognate_vnoeach) |> 
+	bind_rows(.id = "analysis") |>
+	mutate(analysis = case_when(
+		analysis=="data_time_cognate" ~ "Analysis 1",
+		analysis=="data_time_cognate_vtarget" ~ "Analysis 2",
+		analysis=="data_time_cognate_vnone" ~ "Analysis 3",
+		analysis=="data_time_cognate_noeach" ~ "Analysis 4",
+		analysis=="data_time_cognate_vnoeach" ~ "Analysis 5"
+	)) |> 
+	# summarise(.elog_mean = mean(.elog),
+	# 		  n = n(),
+	# 		  .elog_std = sd(.elog),
+	# 		  .by = c(condition, timebin, analysis, lp)) |>
+	# mutate(.elog_se = .elog_std/n) |> 
+	ggplot(aes(timebin, .elog,
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_grid(analysis~lp) +
+	geom_hline(yintercept = 0.5, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	geom_smooth(method = lm, 
+				se = FALSE, 
+				formula = y ~ splines::bs(x, 4)) +
+	# geom_errorbar(aes(ymin = .elog_mean - .elog_se*1.96, 
+	# 				  ymax = .elog_mean + .elog_se*1.96),
+	# 			  width = 0.25,
+	# 			  linewidth = 3/4) + 
+	# geom_line(size = 3/4) + 
+	stat_summary(fun = mean, geom = "point") +
+	stat_summary(fun.data = mean_se,
+				 geom = "errorbar",
+				 width = 0.25) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) +
+	# scale_shape_manual(values = c(1, 2)) +
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) 
+```
 ## Analysis 1
@@
 Participants do not need to know the prime or target words, and do not need to look to both pictures. 
-
 ```{r dataset-noeach}
@@
 # Appendix
+
+## Appendix A: imputing voabulary size scores
+
+```{r fig-vocabulary-imputation}
+vocabulary_tmp <- vocabulary |> 
+	left_join(select(participants, id = id_db, age, age_group, filename),
+			  by = join_by(filename)) |> 
+	relocate(id, age) |> 
+	select(-filename) |> 
+	filter(is_imputed) |> 
+	mutate(id = as.character(id))
+
+bvq_data$vocabulary |> 
+	inner_join(distinct(bvq_data$logs, id, age_group, age),
+			   by = join_by(id, age_group)) |> 
+	mutate(is_imputed = FALSE) |> 
+	bind_rows(vocabulary_tmp) |> 
+	pivot_longer(ends_with("_prop"),
+				 names_to = "measure",
+				 values_to = "prop") |> 
+	drop_na(prop) |> 
+	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"),
+		   measure = factor(measure,
+		   				 levels = c("total_prop",
+		   				 		   "l1_prop",
+		   				 		   "l2_prop",
+		   				 		   "concept_prop",
+		   				 		   "te_prop"),
+		   				 labels = c("Total",
+		   				 		   "L1",
+		   				 		   "L2",
+		   				 		   "Conceptual",
+		   				 		   "TE"))) |> 
+	ggplot(aes(age, prop, 
+			   colour = is_imputed,
+			   fill = is_imputed)) +
+	facet_wrap(~measure) +
+	geom_point(alpha = 1/4, size = 1) +
+	geom_smooth(method = "glm", 
+				formula = "y ~ x",
+				method.args = list(family = "binomial"), 
+				# se = FALSE,
+				size = 1) +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size",
+		 colour = "Imputed") +
+	theme(legend.position = c(1, 0),
+		  legend.justification = c(1, 0),
+		  legend.title = element_blank())
+
+```
+
+## Appendix B: distribution of prime and target looking times
+
+```{fig-dist-prime}
+looking_times |> 
+	mutate(prime_time = cut(prime_time, 
+							seq(0, 1.5, 0.1),
+							labels = FALSE,
+							include.lowest = TRUE)) |> 
+	add_count(lp, age_group, name = "n_total") |> 
+	count(lp, age_group, prime_time, n_total) |> 
+	mutate(n = n / n_total) |> 
+	ggplot(aes(prime_time, n)) +
+	facet_grid(lp~age_group) +
+	annotate(geom = "rect",
+			 fill = "orange",
+			 ymin = -Inf,
+			 ymax = Inf,
+			 xmin = 0,
+			 xmax = 0.75*10,
+			 alpha = 1/3,
+			 colour = NA) +
+	# annotate(label = "Excluded trials",
+	# 		 geom = "text",
+	# 		  x = (0.75/2)*10,
+	# 		  y = 1)
+	geom_col(fill = "black") +
+	labs(x = "Prime looking time (s)",
+		 y = "Proportion of trials") +
+	scale_x_continuous(labels = \(x) x/10) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"))
+```
+
+```{fig-dist-target}
+looking_times |> 
+	mutate(target_time = cut(target_time, 
+							seq(0, 2, 0.1),
+							labels = FALSE,
+							include.lowest = TRUE)) |> 
+	add_count(lp, age_group, name = "n_total") |> 
+	count(lp, age_group, target_time, n_total) |> 
+	mutate(n = n / n_total) |> 
+	ggplot(aes(target_time, n)) +
+	facet_grid(lp~age_group) +
+	# annotate(label = "Excluded trials",
+	# 		 geom = "text",
+	# 		  x = (0.75/2)*10,
+	# 		  y = 1)
+	geom_col(fill = "black") +
+	labs(x = "Targets looking time (s)",
+		 y = "Proportion of trials") +
+	scale_x_continuous(labels = \(x) x/10) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"))
+```
+
+## Appendix C: prime and test looking times
+
+```{r fig-prime-times}
+#| label: fig-looking-times
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Looking time (s) to the prime AOI against audio duration. In longer audios, participants are expected to look longer to the target picture."
+looking_times |>
+	left_join(select(attrition_trials, 
+					 filename, trial, is_valid_trial),
+			  by = join_by(filename, trial)) |>
+	filter(is_valid_trial) |> 
+	ggplot(aes(duration,
+			   prime_time,
+			   colour = trial_type, 
+			   fill = trial_type,
+			   shape = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_point(alpha = 0.5, 
+			   size = 0.5) +
+	geom_smooth(method = "lm") +
+	labs(x = "Audio duration (s)",
+		 y = "Looking time (1.0-2.0 seconds)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 shape = "Prime type")
+```
+
+```{r fig-prime-times}
+#| label: fig-target-times
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Looking time (s) to the prime AOI against audio duration. In longer audios, participants are expected to look longer to the target picture."
+looking_times |>
+	left_join(select(attrition_trials, 
+					 filename, trial, is_valid_trial),
+			  by = join_by(filename, trial)) |>
+	filter(is_valid_trial) |> 
+	ggplot(aes(duration,
+			   target_time,
+			   colour = trial_type, 
+			   fill = trial_type,
+			   shape = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_point(alpha = 0.5,
+			   size = 0.5) +
+	geom_smooth(method = "lm",
+				formula = "y ~ x") +
+	labs(x = "Audio duration (s)",
+		 y = "Looking time (1.0-2.0 seconds)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 shape = "Prime type")
+```

### 2023-10-06 R/responses.R

@@ -1,0 +1,58 @@
+
+#' Prepare data for analyses
+#' 
+#' @param bvq_data A named list resulting from calling [get_bvq()].
+#' @param items A data frame resulting from calling [get_items()].
+#' @param participants A data frame resulting from calling [get_participants()].
+get_responses <- function(bvq_data, items, participants) {
+    # merge all datasets
+    responses_tmp <- bvq_data$responses |>
+        mutate(time = as.integer(time),
+               language = ifelse(grepl("cat_", item), "Catalan", "Spanish"),
+               item = stringr::str_remove(item, "cat_|spa_")) |>
+        # drop missing responses
+        # by default datasets are expanded so that every participant has rows for all items,
+        # even for those that were not included in their version of the questionnaire
+        drop_na(response) |>
+        inner_join(distinct(participants, id),
+                   by = join_by(id)) |>
+        select(id, time, code, language, item, response)
+    
+    response_levels <- c("No", "Understands", "Understands and Says")
+    responses <- items |> 
+        select(-list) |> 
+        inner_join(responses_tmp,
+                   by = join_by(language, item)) |> 
+        inner_join(participants,
+                   by = join_by(id, time)) |> 
+        mutate(
+            # code responses as factor
+            response = factor(response,
+                              levels = c(1, 2, 3),
+                              labels = response_levels,
+                              ordered = TRUE),
+            # does should have the value of the corresponding language
+            doe = ifelse(language == "Catalan", doe_catalan, doe_spanish),
+            # standardise numeric predictors
+            n_phon_std = scale(n_phon)[, 1],
+            freq_std = scale(freq)[, 1],
+            lv_std = scale(lv)[, 1],
+            age_std = scale(age)[, 1],
+            doe_std = scale(doe)[, 1],
+            exposure = freq * doe,
+            exposure_std = scale(exposure)[, 1]) |>
+        # get only relevant variables
+        select(id, time, age, age_std, te, language, meaning, item, response,
+               lv, lv_std, freq, freq_std, n_phon, n_phon_std, doe, doe_std,
+               exposure, exposure_std) |>
+        # reorder rows
+        arrange(id, te, language)
+    
+    # export data
+    save_files(responses,
+               formats = "csv",
+               folder = "data")
+    
+    return(responses)
+    
+}

### 2023-10-06 _targets.R

@@ -217,8 +217,17 @@ list(
 			   		(1 + timebin + age + condition | id)
 			   )),
 	
+	tar_target(model_names, 
+			   list(
+			   	related = apply(expand.grid("fit_related_", 1:4), 1,
+			   					\(x) paste0(x[1], x[2])),
+			   	cognate = apply(expand.grid("fit_cognate_", 1:4), 1, 
+			   					\(x) paste0(x[1], x[2]))
+			   )),
+	
 	tar_target(model_fits_related,
-			   get_model_fit(model_formulas,
+			   get_model_fit(model_names$related,
+			   			  model_formulas,
 			   			  data = data_time_related,
 			   			  family = binomial("logit"),
 			   			  prior = model_prior)),
@@ -228,7 +237,8 @@ list(
 	
 	# cognate vs. non-cognate models	
 	tar_target(model_fits_cognate,
-			   get_model_fit(model_formulas,
+			   get_model_fit(model_names$cognate,
+			   			  model_formulas,
 			   			  data = data_time_cognate,
 			   			  family = binomial("logit"),
 			   			  prior = model_prior)),
@@ -239,6 +249,14 @@ list(
 	
 	# FILTER BY ONLY TARGET WORD
 	# attrition ----------------------------------------------------------------
+	
+	tar_target(model_names_vtarget, 
+			   list(
+			   	related = apply(expand.grid("fit_related_vtarget", 1:4), 1,
+			   					\(x) paste0(x[1], x[2])),
+			   	cognate = apply(expand.grid("fit_cognate_vtarget", 1:4), 1, 
+			   					\(x) paste0(x[1], x[2]))
+			   )),
 	
 	tar_target(attrition_trials_vtarget,
 			   get_attrition_trials(
@@ -283,7 +301,8 @@ list(
 	# tar_target(data_time_test, test_data_time(data_time)),
 	
 	tar_target(model_fits_related_vtarget,
-			   get_model_fit(model_formulas,
+			   get_model_fit(model_names_vtarget$related,
+			   			  model_formulas,
 			   			  data = data_time_related_vtarget,
 			   			  family = binomial("logit"),
 			   			  prior = model_prior)),
@@ -293,7 +312,8 @@ list(
 	
 	# cognate vs. non-cognate models	
 	tar_target(model_fits_cognate_vtarget,
-			   get_model_fit(model_formulas,
+			   get_model_fit(model_names_vtarget$cognate,
+			   			  model_formulas,
 			   			  data = data_time_cognate_vtarget,
[…]

### 2023-10-12 manuscript/manuscript.qmd
Fix data preparation and finish models

@@
 	  attrition_participants_noeach,
+	  attrition_trials_vnoeach,
+	  attrition_participants_vnoeach,
 	  bvq_data, 
@@
 	  data_time_related_noeach, 
-	  data_time_cognate_noeach))
+	  data_time_cognate_noeach,
+	  data_time_related_vnoeach,
+	  data_time_cognate_vnoeach))
 
@@
 	  model_fits_cognate_noeach,
+	  model_fits_related_vnoeach,
+	  model_fits_cognate_vnoeach,
 	  model_loo_related,
@@
 	  model_loo_related_noeach,
-	  model_loo_cognate_noeach
+	  model_loo_cognate_noeach,
+	  model_loo_related_vnoeach,
+	  model_loo_cognate_vnoeach
 	))
@@
 
+## Analysis 5
+
+Participants need to know the prime or target words, and do not need to look to both pictures.
+
+```{r dataset-vnoeach}
+n_trials <- nrow(attrition_trials_vnoeach)
+n_trials_valid <- inner_join(attrition_participants_vnoeach,
+							 attrition_trials_vnoeach) |> 
+	filter(is_valid_participant) |> 
+	pull(is_valid_trial) |> 
+	sum()
+n_participants_valid <- sum(attrition_participants_vnoeach$is_valid_participant)
+n_exc_prime <- sum(!attrition_trials_vnoeach$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition_trials_vnoeach$is_valid_gaze_test)
+n_exc_test_each <- sum(!attrition_trials_vnoeach$is_valid_gaze_test_each)
+n_exc_vocab <- sum(!attrition_trials_vnoeach$is_valid_vocab)
+n_exc_cognate <- sum(!attrition_participants_vnoeach$is_valid_cognate)
+n_exc_noncognate <- sum(!attrition_participants_vnoeach$is_valid_noncognate)
+n_exc_unrelated <- sum(!attrition_participants_vnoeach$is_valid_unrelated)
+
+n_longitudinal <- attrition_participants_vnoeach |>
+	filter(is_valid_participant) |>
+	count(id, name = "times") |> 
+	count(times)
+```
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
+We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
+The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+@tbl-attrition-trials shows a detailed description of the trial attrition.
+
+```{r tbl-attrition-trials-vnoeach}
+#| label: tbl-attrition-trials-vnoeach
+#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
+attrition_trials_vnoeach |> 
+	filter(id %in% attrition_participants_vnoeach$id[attrition_participants_vnoeach$is_valid_participant]) |> 
+	left_join(select(participants, filename, id, age_group),
+			  by = join_by(filename, id, age_group)) |> 
+	summarise(n_valid = sum(is_valid_trial),
+			  n_total = n(),
+			  .by = c(id, age_group, trial_type)) |> 
+	summarise(across(n_valid, lst(sum, mean, sd),
+					 .names = "{.fn}"),
+			  n_total = sum(n_total),
+			  .by = c(age_group, trial_type)) |> 
+	mutate(n_excluded = n_total-sum) |> 
+	select(-c(n_total)) |> 
+	pivot_wider(names_from = trial_type,
+				values_from = c(sum:sd, n_excluded),
+				names_repair = janitor::make_clean_names) |> 
+	rename_with(\(x) gsub("non_cognate", 
+						  "noncognate",
+						  x)) |> 
+	arrange(age_group) |> 
+	relocate(age_group,
+			 matches("_cognate"),
+			 matches("noncognate")) |> 
+	gt(rowname_col = "age_group") |> 
+	grand_summary_rows(columns = matches("mean_"),
+					   fns = lst(Mean ~ mean(.)),
+					   fmt = ~fmt_number(.)) |>
+	grand_summary_rows(columns = matches("sum_"),
+					   fns = lst(Sum ~ sum(.)),
+					   fmt = ~fmt_integer(.)) |>
+	cols_merge(c(sum_cognate, n_excluded_cognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_unrelated, n_excluded_unrelated),
+			   pattern = "{1} ({2})") |> 
+	cols_merge_uncert(mean_cognate, sd_cognate) |> 
+	cols_merge_uncert(mean_noncognate, sd_noncognate) |> 
+	cols_merge_uncert(mean_unrelated, sd_unrelated) |> 
+	tab_spanner("Cognate trials", ends_with("_cognate")) |>
+	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
+	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
+	tab_spanner("Related trials", matches("cognate")) |>
+	fmt_number(matches("mean|sd")) |> 
+	fmt_integer(matches("sum"), sep_mark = ",") |> 
+	cols_label(sum_cognate = "N",
+			   sum_noncognate = "N",
+			   sum_unrelated = "N",
+			   mean_cognate = "Mean",
+			   mean_noncognate = "Mean",
+			   mean_unrelated = "Mean")
+```
+
+### Phonological priming: Related vs. Unrelated
+
+A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related_vnoeach[2, 1], 3)`, *SE* = `r round(model_loo_related_vnoeach[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related_vnoeach[3, 1], 3)`, *SE* = `r round(model_loo_related[3, 2], 3)`).
+This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-related-vnoeach}
+#| label: fig-related-vnoeach
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_related_vnoeach$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_related_vnoeach$age),
+					  lp = levels(data_time_related_vnoeach$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_related_vnoeach[[4]],
+					ndraws = NULL,
+					re_formula = NA, 
+					value = ".value") |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .value,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = related - unrelated)
+
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
+# 
+# clusters <- rle(diff(diff_rect$is_cluster))
+# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
+# 
+# diff_rect <- diff_rect |> 
+# 	arrange(lp, timebin)
+# 
+# diff_rect <- 
+# 	cluster_number = 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = c(lp, is_cluster)) |> 
+# 	filter(is_cluster)
+
+# diff_obs <- data_time_related |>
+# 	pivot_wider(names_from = condition, 
+# 				values_from = elog,
+# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
+
+data_time_related_vnoeach |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition,
+			   linetype = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .value),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .value,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 1/2, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	# geom_point(data = diff_obs) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
+### Cognate priming: Cognate vs. Non-cognate
+
+A model including the *Cognateness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Cognateness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate[2, 1], 3)`, *SE* = `r round(model_loo_cognate[2, 2], 3)`).
+Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate[3, 1], 3)`, *SE* = `r round(model_loo_cognate[3, 2], 3)`).
+This indicates that including the *Cognateness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+
+```{r fig-cognate-vnoeach}
+#| label: fig-cognate-vnoeach
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_cognate_vnoeach$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_cognate_vnoeach$age),
+					  lp = levels(data_time_cognate_vnoeach$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_cognate_vnoeach[[4]],
+					ndraws = NULL,
+					re_formula = NA) |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .epred,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = cognate - non_cognate) 
+# 
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	filter(.lower > 0 | .upper < 0) |> 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = lp)
+
+data_time_cognate_vnoeach |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -1.5,
+	# 		  	ymax = 1.5),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .epred),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .epred,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0.5, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 linetype = "Prime type",
+		 shape = "Prime type") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -3/4,
+	# 		  	ymax = 3/4),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
 # Discussion

### 2023-10-13 manuscript/manuscript.tex

@@
 \maketitle
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, enhanced, interior hidden, breakable]}{\end{tcolorbox}}\fi
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-The formation of a mental lexicon is a critical developmental
-achievement for infants\_ learning words allows infants to retrieve
-socially relevant concepts from fairly arbitrary linguistic forms
-embedded in speech.
-
-Learning words allows infants to access the rich world made of concepts
-through the recognition of fairly arbitrary linguistic forms, i.e.,
-words. This remarkable developmental achievement is
-
-The bilingual lexicon is language-non selective.
-
-The role of cognates in lexical processing.
-
-How does language co-activation shape lexical development?
-
-Implicit naming as a paradigm to study cross-language activation. (Mani
-\& Plunkett, 2010, 2011a).
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi
 
@@
 (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I. Before
-every testing session, caretakers were asked to read and sign an
-informed consent form, and were given a small gift at the end of it
+every testing session, caregivers were asked to read and sign an
+informed consent form, and were given a token of appreciation at the end
+of it.
 
@@
               \AttributeTok{.groups =} \StringTok{"drop"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(age\_mean}\SpecialCharTok{:}\NormalTok{age\_max, round, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(age\_mean}\SpecialCharTok{:}\NormalTok{age\_max, \textbackslash{}(x) }\FunctionTok{round}\NormalTok{(x, }\DecValTok{2}\NormalTok{))) }\SpecialCharTok{|\textgreater{}}
     \FunctionTok{group\_split}\NormalTok{(age\_group) }\SpecialCharTok{|\textgreater{}} 
     \FunctionTok{set\_names}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"age\_21"}\NormalTok{, }\StringTok{"age\_25"}\NormalTok{, }\StringTok{"age\_30"}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-Warning: [1m[22mThere was 1 warning in `mutate()`.
-[1m[22m[36mi[39m In argument: `across(age_mean:age_max, round, 2)`.
-Caused by warning:
-[1m[22m[33m![39m The `...` argument of `across()` is deprecated as of dplyr 1.1.0.
-Supply arguments directly to `.fns` through an anonymous function instead.
-
-  # Previously
-  across(a:b, mean, na.rm = TRUE)
-
-  # Now
-  across(a:b, \(x) mean(x, na.rm = TRUE))
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+
 \NormalTok{n\_sessions\_dominance }\OtherTok{\textless{}{-}} \FunctionTok{count}\NormalTok{(participants, test\_language) }\SpecialCharTok{|\textgreater{}} 
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{n\_imputed }\OtherTok{\textless{}{-}} \FunctionTok{table}\NormalTok{(vocabulary}\SpecialCharTok{$}\NormalTok{is\_imputed)[}\DecValTok{2}\NormalTok{]}
+\NormalTok{prop\_imputed }\OtherTok{\textless{}{-}}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{percent}\NormalTok{(n\_imputed}\SpecialCharTok{/}\FunctionTok{nrow}\NormalTok{(vocabulary))}
+\NormalTok{n\_pool }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(bvq\_data}\SpecialCharTok{$}\NormalTok{vocabulary)}
+\end{Highlighting}
+\end{Shaded}
+
 We collected vocabulary data using parental responses to the Barcelona
 Vocabulary Inventory (BVQ,
-\protect\hyperlink{ref-garcia-castro2023bvq}{\textbf{garcia-castro2023bvq?}}),
-an online vocabulary checklist inspired in several adaptations of the
-the Communicative Developmental Inventory (CDI,
-\protect\hyperlink{ref-fenson2004variability}{\textbf{fenson2004variability?}})
+\protect\hyperlink{ref-garcia-castro2023bvq}{Garcia-Castro et al.,
+2023}), an online vocabulary checklist inspired in several adaptations
+of the the Communicative Developmental Inventory (CDI,
+\protect\hyperlink{ref-fenson1994variability}{Fenson et al., 1994})
 developed to assess the vocabulary size of Catalan-Spanish bilingual
 toddlers. Families received a link to the BVQ immediately after each
-experimental session, and were given two weeks to fill it. Two weeks
-after being sent the link, 141 (48\% families failed to provide a
-complete response to the BVQ. We imputed their vocabulary size scores
-using multiple imputation
-(\protect\hyperlink{ref-vanbuuren2018flexible}{\textbf{vanbuuren2018flexible?}}).
-We used predictive mean matching to impute missing scores using
-participants' information about their age group and language profile. We
-obtained several receptive and expressive vocabulary size measures from
-each participant's vocabulary: Catalan vocabulary size (proportion of
-the words in the Catalan checklist reported as acquired), Spanish
-vocabulary size (proportion of the words in the Catalan checklist
-reported as acquired), and total vocabulary size (proportion of the
-words in both checklists reported as acquired).
-
-\hypertarget{stimuli}{%
-\subsubsection{Stimuli}\label{stimuli}}
+experimental session, and were given two weeks to fill it.
+
+We calculated several measures of receptive vocabulary size from each
+participant's vocabulary: L1 vocabulary size (proportion of words
+reported as acquired in the checklist of the dominant language), L2
+vocabulary size (proportion of words reported as acquired in the
+checklist of the non-dominant language), total vocabulary size
+(proportion of the words in both checklists reported as acquired),
+conceptual vocabulary (proportion of concepts for which the participant
+was reported to have acquired at least one label, in any language), and
+translation equivalent vocabulary (proportion of concepts for which the
+participant was reported to have acquired at two labels, one in each
+language).
+
+141 (48\%) Families failed to provide a complete response to the BVQ
+within the two-week time limit, or did not provide a successful response
+to the questionnaire. For missing questionnaire responses, we imputed
+the vocabulary size of the participant using single imputation, using
+the vocabulary size scores of a pool of 600 additional participants for
+which a successful response for the questionnaire had been gathered. We
+used participants age in months and their language profile
+(monolingual/bilingual) as predictors. We used the \texttt{mice} R
+package (\protect\hyperlink{ref-van2011mice}{Van Buuren \&
+Groothuis-Oudshoorn, 2011}) to perform imputation using the Bayesian
+linear regression method.
 
@@
 \begin{Highlighting}[]
-\NormalTok{n\_words }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(}\FunctionTok{with}\NormalTok{(stimuli, }\FunctionTok{unlist}\NormalTok{(prime, target, distractor)))}
+\NormalTok{vocabulary }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(participants, filename, id, age\_group, lp),}
+              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"prop"}\NormalTok{), }
+\NormalTok{                     tibble}\SpecialCharTok{::}\FunctionTok{lst}\NormalTok{(mean, sd)),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(age\_group, lp)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{arrange}\NormalTok{(age\_group, lp) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{gt}\NormalTok{(}\AttributeTok{groupname\_col =} \StringTok{"age\_group"}\NormalTok{,}
+       \AttributeTok{rowname\_col =} \StringTok{"lp"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_hide}\NormalTok{(lp) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Total "}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"total"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"L1"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"l1"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"L2"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"l2"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Conceptual"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"concept"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"TE"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"te\_"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Vocabulary size (\%)"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"prop\_"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(total\_prop\_mean, total\_prop\_sd) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(l1\_prop\_mean, l1\_prop\_sd) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(l2\_prop\_mean, l2\_prop\_sd) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(concept\_prop\_mean, concept\_prop\_sd) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(te\_prop\_mean, te\_prop\_sd) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{fmt\_number}\NormalTok{(is.numeric, }
+               \AttributeTok{drop\_trailing\_zeros =} \ConstantTok{FALSE}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_label}\NormalTok{(}\AttributeTok{total\_prop\_mean =} \StringTok{"Mean (SD)"}\NormalTok{,}
+               \AttributeTok{l1\_prop\_mean =} \StringTok{"Mean (SD)"}\NormalTok{,}
+               \AttributeTok{l2\_prop\_mean =} \StringTok{"Mean (SD)"}\NormalTok{,}
+               \AttributeTok{concept\_prop\_mean =} \StringTok{"Mean (SD)"}\NormalTok{,}
+               \AttributeTok{te\_prop\_mean =} \StringTok{"Mean (SD)"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_stub\_indent}\NormalTok{(}\AttributeTok{rows =} \FunctionTok{everything}\NormalTok{(),}
+                    \AttributeTok{indent =} \DecValTok{2}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_style}\NormalTok{(}\FunctionTok{cell\_text}\NormalTok{(}\AttributeTok{align =} \StringTok{"left"}\NormalTok{),}
+              \FunctionTok{cells\_stub}\NormalTok{())}
 \end{Highlighting}
@@
 
-We used arbre, ànec, camió, finestra, vaca, barret, osset, claus, cotxe,
-cadira, vaixell, ampolla, flor, formatge, botó, ulleres, gat, gos, mico,
-pa, moto, mitjó, avió, granota, ovella, ocell, peix, plàtan, pilota,
-poma, guitarra, maduixa, botella, globo, mono, coche, cama, zumo, pato,
-cebra, cerdo, oreja, mesa, galleta, gafas, tomate, zapato, manzana,
-vaso, queso, oveja, ojo, pelota, tele, pez, perro, barco, hoja, tren,
-tenedor, casa, gato distinct words included in the BVQ to create the
-stimuli lists. We created six stimuli lists: three in Catalan, and three
-in Spanish. Each list contained 32 trials, each involving a
+\hypertarget{tbl-vocabulary}{}
+\begin{longtable}{l|rrrrr}
+\caption{\label{tbl-vocabulary}Vocabulary sizes. Total: proportion of words in both languages marked as
+\emph{Understands}. L1: proportion of words in the dominant language
+marked as \emph{Understands}. L2: proportion of words in the
+non-cominant language marked as \emph{Understands}. Conceptual:
+proportion of translation equivalents for which at least one of the
+words has ben marked as \emph{Understands}. TE: proportion of
+translation equivalents for which \emph{both} words have been marked as
+\emph{Understands}. }\tabularnewline
+
+\toprule
+\multicolumn{1}{l}{} & \multicolumn{5}{c}{Vocabulary size (\%)} \\ 
+\cmidrule(lr){2-6}
+\multicolumn{1}{l}{} & Total  & L1 & L2 & Conceptual & TE \\ 
+\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6}
+\multicolumn{1}{l}{} & Mean (SD) & Mean (SD) & Mean (SD) & Mean (SD) & Mean (SD) \\ 
+\midrule
+\multicolumn{6}{l}{21 months} \\ 
+\midrule
+\hspace*{10px} Monolingual & $0.39$ ± $0.18$ & $0.53$ ± $0.18$ & $0.26$ ± $0.22$ & $0.61$ ± $0.18$ & $0.19$ ± $0.20$ \\ 
+\hspace*{10px} Bilingual & $0.42$ ± $0.23$ & $0.50$ ± $0.22$ & $0.42$ ± $0.24$ & $0.56$ ± $0.21$ & $0.33$ ± $0.23$ \\ 
+\midrule
+\multicolumn{6}{l}{25 months} \\ 
+\midrule
+\hspace*{10px} Monolingual & $0.55$ ± $0.22$ & $0.76$ ± $0.14$ & $0.48$ ± $0.29$ & $0.77$ ± $0.14$ & $0.39$ ± $0.27$ \\ 
+\hspace*{10px} Bilingual & $0.64$ ± $0.20$ & $0.71$ ± $0.17$ & $0.57$ ± $0.25$ & $0.75$ ± $0.20$ & $0.51$ ± $0.24$ \\ 
+\midrule
+\multicolumn{6}{l}{30 months} \\ 
+\midrule
+\hspace*{10px} Monolingual & $0.67$ ± $0.20$ & $0.81$ ± $0.16$ & $0.53$ ± $0.28$ & $0.83$ ± $0.15$ & $0.43$ ± $0.29$ \\ 
+\hspace*{10px} Bilingual & $0.76$ ± $0.18$ & $0.79$ ± $0.14$ & $0.71$ ± $0.23$ & $0.85$ ± $0.10$ & $0.64$ ± $0.21$ \\ 
+\bottomrule
+\end{longtable}
+
+\hypertarget{stimuli}{%
+\subsection{Stimuli}\label{stimuli}}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{n\_words }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(}\FunctionTok{unique}\NormalTok{(}\FunctionTok{with}\NormalTok{(stimuli, }\FunctionTok{unlist}\NormalTok{(prime, target, distractor))))}
+\end{Highlighting}
+\end{Shaded}
+
+We used 62 distinct words included in the BVQ to create the stimuli
+lists. We created six stimuli lists: three in Catalan, and three in
+Spanish. Each list contained 32 trials, each involving a
 prime-target-distractor group. Each word played a role as either prime,
@@
 order in which the prime-target-distractor was presented was randomised.
-Each participant was randomly assigned to one of the three list in the
+Each participant was randomly assigned to one of the three lists in the
 corresponding language (their dominant language, see
@@
 avoid infants guiding their gaze to these objects based on their
-saliency, we paired animals and food items together.
+saliency, we paired animals and food items together. The position of the
+target and distractor pictures (right or left) for each
+target-distractor pair was alternated, so that in one list the target
+would appear on the left, in another list it would appear on the right,
+and so on.
 
@@
 \hypertarget{auditory-stimuli}{%
-\paragraph{Auditory stimuli}\label{auditory-stimuli}}
+\subsubsection{Auditory stimuli}\label{auditory-stimuli}}
 
@@
 (\protect\hyperlink{ref-reference}{\textbf{reference?}}) and Praat
-(\protect\hyperlink{ref-reference}{\textbf{reference?}}) to record and
-edit the audio files. The speaker was presented with a list of words in
-Catalan. The order of the words was pseudo-randomised, and each word was
-produced three times in a row before moving to the next word in the
-list. After going through all the words in the list, the speaker went
-through the word list again generating three tokens for each word, now
-in an inverse order (from bottom of the list to the top). We then
-repeated the same procedure for the list of Spanish words. The resulting
-audios were manually chunked into individual word-forms. For each of the
-six tokens produced for each word, the most adequate was selected for
-further processing. The audios were then transformed to stereo by
-duplicating them into two channels, denoised, and finally normalised.
-The mean duration of the final audios was 1.23 (\emph{SD} = 0.17) and
-1.08 (\emph{SD} = 0.14) seconds for the Catalan and Spanish lists.
+(\protect\hyperlink{ref-boersma2001speak}{Boersma \& Van Heuven, 2001})
+to record and edit the audio files. The speaker was presented with a
+list of words in Catalan. The order of the words was pseudo-randomised,
+and each word was produced three times in a row before moving to the
+next word in the list. After going through all the words in the list,
+the speaker went through the word list again generating three tokens for
+each word, now in an inverse order (from bottom of the list to the top).
+We then repeated the same procedure for the list of Spanish words. The
+resulting audios were manually chunked into individual word-forms. For
+each of the six tokens produced for each word, the most adequate was
+selected for further processing. The audios were then transformed to
+stereo by duplicating them into two channels, denoised, and finally
+normalised. The mean duration of the final audios was 1.23 (\emph{SD} =
+0.17) and 1.08 (\emph{SD} = 0.14) seconds for the Catalan and Spanish
+lists.
 
@@
 \hypertarget{visual-stimuli}{%
-\paragraph{Visual stimuli}\label{visual-stimuli}}
-
-For each word, we created a picture with a typical referent.
+\subsubsection{Visual stimuli}\label{visual-stimuli}}
+
+For each word, we created a picture with a typical referent. To avoid
+competition between target and distractor pictures, semantically related
+target-distractor pairs were perceptually distinct
+(\protect\hyperlink{ref-floccia2020translation}{\textbf{floccia2020translation?}};
+\protect\hyperlink{ref-arias-trejo2010}{\textbf{arias-trejo2010?}}).
 
@@
 
-\hypertarget{data-processing}{%
-\subsubsection{Data processing}\label{data-processing}}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{n\_trials }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(attrition\_trials)}
-
-\NormalTok{n\_sessions }\OtherTok{\textless{}{-}} \FunctionTok{distinct}\NormalTok{(attrition\_trials, filename) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{nrow}\NormalTok{()}
-
-\NormalTok{n\_participants }\OtherTok{\textless{}{-}} \FunctionTok{distinct}\NormalTok{(attrition\_trials, id) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{nrow}\NormalTok{()}
-
-\NormalTok{n\_trials\_prime }\OtherTok{\textless{}{-}}\NormalTok{ attrition\_trials }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{filter}\NormalTok{(is\_valid\_gaze\_prime)}
-
-\NormalTok{n\_trials\_test }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_prime }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{filter}\NormalTok{(is\_valid\_gaze\_test)}
-
-\NormalTok{n\_trials\_each }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_test }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{filter}\NormalTok{(is\_valid\_gaze\_test\_each)}
-
-\NormalTok{n\_trials\_vocab }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_each }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{filter}\NormalTok{(is\_valid\_vocab)}
-
-\NormalTok{n\_trials\_participant }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_vocab }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{inner\_join}\NormalTok{(}\FunctionTok{filter}\NormalTok{(attrition\_participants,}
-\NormalTok{                      is\_valid\_participant),}
-               \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename))}
-
-\NormalTok{n\_sessions\_valid }\OtherTok{\textless{}{-}}\NormalTok{ attrition\_participants }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{filter}\NormalTok{(is\_valid\_participant)}
-
-\NormalTok{n\_participants\_valid }\OtherTok{\textless{}{-}}\NormalTok{ n\_trials\_participant }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{distinct}\NormalTok{(filename)}
-
-\NormalTok{n\_longitudinal }\OtherTok{\textless{}{-}} \FunctionTok{count}\NormalTok{(n\_sessions\_valid, filename, }\AttributeTok{name =} \StringTok{"sessions"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{count}\NormalTok{(sessions)}
-
-\NormalTok{n\_participants\_include }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"data{-}raw/participants.csv"}\NormalTok{,}
-                                   \AttributeTok{show\_col\_types =} \ConstantTok{FALSE}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-We gathered data for 9,472 trials from 296 experimental sessions,
-provided by 180 distinct participants. Missing eye-tracker samples were
-interpolated using the last-observation-carried-forward (see
-\protect\hyperlink{ref-zettersten2022peekbank}{\textbf{zettersten2022peekbank?}}
-for a similar approach). We excluded trials in which the participant did
-not fixate the prime at least half of the time of the prime phase
-(\$\geq\(750 ms, *n* = 1,810), or the target and distractor during the test phase (\)\geq\$1,000
-ms, \emph{n} = 502). We also excluded trials in which the participant
-failed to fixate both target \emph{and} distractor pictures for at least
-100 ms (i.e., 5\% of the time) (1,304 trials excluded). We then excluded
-trials in which the participant was not reported to understand the prime
-\emph{and} the target words, according to their caregivers' responses to
-the vocabulary checklist. This resulted in the exclusion of 3,641
-trials. Finally, we excluded trials from experimental sessions in which
-the participant did not provide at least two valid trials in each of the
-three experimental conditions (cognate prime, non-cognate prime, and
-unrelated prime) which resulted in the exclusion of 34 experimental
-sessions and their 219 remaining trials. The final data set comprised 0
-from c(``CognatePriming\_019\_2019-11-28.csv'',
-``CognatePriming\_021\_2019-11-30.csv'',
-``CognatePriming\_026\_2019-12-14.csv'',
-``CognatePriming\_027\_2019-12-14\_1.csv'',
-``CognatePriming\_049\_2021-02-13.csv'',
-``CognatePriming\_050\_2020-11-07.csv'',
-``CognatePriming\_050\_2021-03-13.csv'',
-``CognatePriming\_050\_2021-10-02.csv'',
-``CognatePriming\_051\_2021-03-06\_1.csv'',
-``CognatePriming\_051\_2021-10-01.csv'',
-``CognatePriming\_053\_2021-04-17.csv'',
-``CognatePriming\_054\_2020-11-14.csv'',
-``CognatePriming\_055\_2020-11-14.csv'',
-``CognatePriming\_055\_2021-02-20\_1.csv'',
-``CognatePriming\_056\_2020-11-14.csv'',
-``CognatePriming\_058\_2020-11-17.csv'',
-``CognatePriming\_059\_2020-11-18.csv'',
-``CognatePriming\_060\_2021-04-26.csv'',
-``CognatePriming\_064\_2020-11-21.csv'',
-``CognatePriming\_065\_2020-11-25.csv'',
-``CognatePriming\_066\_2020-11-26.csv'',
-``CognatePriming\_067\_2020-11-27.csv'',
-``CognatePriming\_068\_2020-11-27.csv'',
-``CognatePriming\_069\_2020-11-28.csv'',
-``CognatePriming\_069\_2021-05-08.csv'',
-``CognatePriming\_070\_2020-12-01.csv'',
-``CognatePriming\_070\_2021-09-30\_1.csv'',
-``CognatePriming\_071\_2020-12-01.csv'',
-``CognatePriming\_072\_2020-12-04.csv'',
-``CognatePriming\_073\_2021-10-02.csv'',
-``CognatePriming\_074\_2020-12-05.csv'',
-``CognatePriming\_075\_2020-12-09.csv'',
-``CognatePriming\_076\_2021-05-08.csv'',
-``CognatePriming\_076\_2021-10-16.csv'',
-``CognatePriming\_078\_2021-04-29.csv'',
-``CognatePriming\_079\_2020-12-16.csv'',
-``CognatePriming\_079\_2021-10-07\_1.csv'',
-``CognatePriming\_080\_2021-04-10.csv'',
-``CognatePriming\_081\_2020-12-21.csv'',
-``CognatePriming\_081\_2021-05-03.csv'',
-``CognatePriming\_081\_2021-10-19.csv'',
-``CognatePriming\_084\_2021-10-15.csv'',
-``CognatePriming\_089\_2021-02-02.csv'',
-``CognatePriming\_089\_2021-07-06.csv'',
-``CognatePriming\_090\_2021-02-06\_2.csv'',
-``CognatePriming\_090\_2021-06-19.csv'',
-``CognatePriming\_091\_2021-06-18.csv'',
-``CognatePriming\_092\_2021-06-08.csv'',
-``CognatePriming\_094\_2021-02-13.csv'',
-``CognatePriming\_095\_2021-02-13\_1.csv'',
-``CognatePriming\_098\_2021-11-13.csv'',
-``CognatePriming\_100\_2021-02-20\_1.csv'',
-``CognatePriming\_100\_2021-06-14.csv'',
-``CognatePriming\_101\_2021-02-20\_1.csv'',
-``CognatePriming\_101\_2021-11-20.csv'',
-``CognatePriming\_102\_2021-02-26.csv'',
-``CognatePriming\_102\_2021-07-05.csv'',
-``CognatePriming\_102\_2021-11-12.csv'',
-``CognatePriming\_105\_2021-02-27\_1.csv'',
-``CognatePriming\_105\_2021-07-24\_1.csv'',
-``CognatePriming\_105\_2021-11-27.csv'',
-``CognatePriming\_107\_2022-02-21.csv'',
-``CognatePriming\_108\_2021-03-15.csv'',
-``CognatePriming\_108\_2022-01-26\_1.csv'',
-``CognatePriming\_110\_2022-01-22\_1.csv'',
-``CognatePriming\_112\_2022-02-18.csv'',
-``CognatePriming\_113\_2021-05-15.csv'',
-``CognatePriming\_114\_2021-05-19.csv'',
-``CognatePriming\_115\_2021-05-22.csv'',
-``CognatePriming\_115\_2021-10-23.csv'',
-``CognatePriming\_115\_2022-01-29.csv'',
-``CognatePriming\_117\_2021-11-16.csv'',
-``CognatePriming\_117\_2022-03-11\_1.csv'',
-``CognatePriming\_119\_2021-06-01.csv'',
-``CognatePriming\_119\_2022-01-26.csv'',
-``CognatePriming\_121\_2021-06-08.csv'',
-``CognatePriming\_121\_2021-10-18.csv'',
-``CognatePriming\_123\_2021-10-23.csv'',
-``CognatePriming\_124\_2022-02-18.csv'',
-``CognatePriming\_125\_2021-06-26.csv'',
-``CognatePriming\_127\_2021-06-28.csv'',
-``CognatePriming\_127\_2021-10-25.csv'',
-``CognatePriming\_128\_2021-11-02.csv'',
-``CognatePriming\_131\_2022-02-18.csv'',
-``CognatePriming\_133\_2021-07-06.csv'',
-``CognatePriming\_135\_2021-12-01.csv'',
-``CognatePriming\_136\_2021-12-03.csv'',
-``CognatePriming\_140\_2021-12-11\_2.csv'',
-``CognatePriming\_142\_2022-03-31.csv'',
-``CognatePriming\_144\_2022-01-07.csv'',
-``CognatePriming\_146\_2022-01-27.csv'',
-``CognatePriming\_146\_2022-06-14.csv'',
-``CognatePriming\_147\_2022-01-28.csv'',
-``CognatePriming\_147\_2022-06-17.csv'',
-``CognatePriming\_152\_2022-02-05.csv'',
-``CognatePriming\_154\_2022-02-08\_1.csv'',
-``CognatePriming\_154\_2022-05-24\_1.csv'',
-``CognatePriming\_157\_2022-02-10.csv'',
-``CognatePriming\_157\_2022-10-03.csv'',
-``CognatePriming\_160\_2022-02-28.csv'',
-``CognatePriming\_171\_2022-03-14.csv'',
-``CognatePriming\_172\_2022-03-15.csv'',
-``CognatePriming\_176\_2022-03-22.csv'',
-``CognatePriming\_178\_2022-03-23\_1.csv'',
-``CognatePriming\_183\_2022-10-06.csv'',
-``CognatePriming\_190\_2022-06-20.csv'',
-``CognatePriming\_192\_2022-06-21.csv'',
-``CognatePriming\_196\_2022-06-28\_2.csv'',
-``CognatePriming\_198\_2022-10-01.csv'',
-``CognatePriming\_199\_2022-10-03.csv'',
-``CognatePriming\_200\_2022-10-04.csv'',
-``CognatePriming\_201\_2022-10-07.csv'',
-``CognatePriming\_202\_2022-10-08.csv''), c(8, 5, 8, 7, 7, 6, 7, 7, 3,
-5, 4, 5, 3, 3, 2, 4, 6, 8, 4, 4, 2, 5, 7, 4, 6, 3, 6, 3, 2, 3, 6, 4, 4,
-6, 4, 3, 5, 2, 2, 5, 6, 6, 6, 5, 5, 5, 4, 2, 5, 2, 4, 6, 3, 3, 5, 6, 6,
-6, 3, 5, 6, 5, 2, 5, 5, 6, 8, 2, 5, 5, 7, 5, 7, 7, 6, 5, 4, 4, 4, 5, 2,
-4, 4, 5, 7, 5, 4, 5, 2, 7, 6, 3, 2, 7, 3, 8, 6, 2, 5, 3, 6, 3, 5, 4, 7,
-6, 7, 4, 7, 4, 7, 3, 2), c(7, 7, 7, 8, 7, 5, 8, 7, 6, 5, 5, 6, 2, 2, 2,
-4, 8, 7, 3, 4, 3, 2, 4, 2, 3, 2, 7, 5, 6, 3, 4, 5, 4, 5, 6, 2, 5, 6, 4,
-6, 3, 3, 6, 4, 6, 5, 4, 2, 3, 3, 4, 3, 5, 4, 6, 4, 6, 6, 4, 7, 8, 6, 2,
-4, 4, 7, 4, 3, 5, 4, 6, 7, 7, 6, 6, 7, 6, 4, 6, 3, 4, 5, 4, 6, 4, 5, 5,
-3, 4, 6, 6, 2, 4, 4, 5, 4, 5, 3, 7, 4, 4, 3, 6, 2, 6, 2, 5, 2, 6, 4, 6,
-3, 2), c(9, 8, 9, 10, 10, 6, 11, 14, 8, 9, 9, 9, 3, 4, 5, 10, 15, 12, 3,
-5, 5, 6, 6, 6, 6, 9, 14, 5, 10, 2, 10, 10, 7, 13, 9, 5, 8, 10, 2, 5, 7,
-10, 11, 10, 12, 10, 7, 5, 11, 4, 7, 8, 6, 4, 11, 9, 12, 14, 10, 13, 13,
-11, 3, 5, 6, 14, 11, 2, 6, 11, 12, 8, 14, 7, 10, 6, 6, 11, 8, 7, 3, 5,
-6, 6, 7, 10, 8, 7, 5, 12, 8, 14, 8, 8, 7, 7, 6, 8, 10, 9, 7, 6, 10, 7,
-10, 4, 9, 7, 12, 7, 13, 11, 3), c(TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE),
-c(TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE), c(TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE),
-c(TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE,
-TRUE, TRUE, TRUE, TRUE, TRUE, TRUE), c(19, 21, 26, 27, 49, 50, 50, 50,
-51, 51, 53, 54, 55, 55, 56, 58, 59, 60, 64, 65, 66, 67, 68, 69, 69, 70,
-70, 71, 72, 73, 74, 75, 76, 76, 78, 79, 79, 80, 81, 81, 81, 84, 89, 89,
-90, 90, 91, 92, 94, 95, 98, 100, 100, 101, 101, 102, 102, 102, 105, 105,
-105, 107, 108, 108, 110, 112, 113, 114, 115, 115, 115, 117, 117, 119,
-119, 121, 121, 123, 124, 125, 127, 127, 128, 131, 133, 135, 136, 140,
-142, 144, 146, 146, 147, 147, 152, 154, 154, 157, 157, 160, 171, 172,
-176, 178, 183, 190, 192, 196, 198, 199, 200, 201, 202), c(3, 3, 3, 3, 2,
-1, 2, 3, 2, 3, 3, 1, 1, 2, 1, 2, 2, 3, 2, 2, 2, 2, 2, 2, 3, 1, 3, 1, 1,
-3, 2, 2, 2, 3, 2, 1, 3, 3, 1, 2, 3, 3, 1, 2, 1, 2, 2, 2, 1, 1, 3, 1, 2,
-1, 3, 1, 2, 3, 1, 2, 3, 3, 1, 3, 3, 3, 1, 1, 1, 2, 3, 2, 3, 1, 3, 1, 2,
-2, 3, 1, 1, 2, 2, 3, 1, 2, 2, 2, 2, 2, 2, 3, 2, 3, 1, 2, 3, 2, 3, 1, 2,
-2, 2, 2, 3, 2, 3, 1, 3, 3, 3, 2, 3), c(2, 2, 2, 1, 1, 1, 1, 1, 1, 1, 1,
-1, 2, 2, 1, 1, 1, 2, 1, 1, 2, 2, 2, 1, 1, 1, 1, 2, 1, 1, 1, 1, 2, 2, 1,
-1, 1, 2, 1, 1, 1, 1, 1, 1, 2, 2, 1, 1, 1, 1, 2, 2, 2, 1, 1, 1, 1, 1, 2,
-2, 2, 1, 2, 2, 2, 1, 1, 1, 1, 1, 1, 2, 2, 1, 1, 1, 1, 2, 2, 1, 1, 1, 2,
-1, 1, 1, 2, 1, 2, 2, 1, 1, 1, 1, 2, 1, 1, 1, 1, 2, 1, 1, 1, 2, 1, 2, 2,
-2, 1, 1, 2, 1, 1) experimental sessions, provided by
-c(``CognatePriming\_019\_2019-11-28.csv'',
-``CognatePriming\_021\_2019-11-30.csv'',
-``CognatePriming\_026\_2019-12-14.csv'',
-``CognatePriming\_027\_2019-12-14\_1.csv'',
-``CognatePriming\_049\_2021-02-13.csv'',
-``CognatePriming\_050\_2020-11-07.csv'',
-``CognatePriming\_050\_2021-03-13.csv'',
-``CognatePriming\_050\_2021-10-02.csv'',
-``CognatePriming\_051\_2021-03-06\_1.csv'',
-``CognatePriming\_051\_2021-10-01.csv'',
-``CognatePriming\_053\_2021-04-17.csv'',
-``CognatePriming\_054\_2020-11-14.csv'',
-``CognatePriming\_055\_2020-11-14.csv'',
-``CognatePriming\_055\_2021-02-20\_1.csv'',
-``CognatePriming\_056\_2020-11-14.csv'',
-``CognatePriming\_058\_2020-11-17.csv'',
-``CognatePriming\_059\_2020-11-18.csv'',
-``CognatePriming\_060\_2021-04-26.csv'',
-``CognatePriming\_064\_2020-11-21.csv'',
-``CognatePriming\_065\_2020-11-25.csv'',
-``CognatePriming\_066\_2020-11-26.csv'',
-``CognatePriming\_067\_2020-11-27.csv'',
-``CognatePriming\_068\_2020-11-27.csv'',
-``CognatePriming\_069\_2020-11-28.csv'',
-``CognatePriming\_069\_2021-05-08.csv'',
-``CognatePriming\_070\_2020-12-01.csv'',
-``CognatePriming\_070\_2021-09-30\_1.csv'',
-``CognatePriming\_071\_2020-12-01.csv'',
-``CognatePriming\_072\_2020-12-04.csv'',
-``CognatePriming\_073\_2021-10-02.csv'',
-``CognatePriming\_074\_2020-12-05.csv'',
-``CognatePriming\_075\_2020-12-09.csv'',
-``CognatePriming\_076\_2021-05-08.csv'',
-``CognatePriming\_076\_2021-10-16.csv'',
-``CognatePriming\_078\_2021-04-29.csv'',
-``CognatePriming\_079\_2020-12-16.csv'',
-``CognatePriming\_079\_2021-10-07\_1.csv'',
-``CognatePriming\_080\_2021-04-10.csv'',
-``CognatePriming\_081\_2020-12-21.csv'',
-``CognatePriming\_081\_2021-05-03.csv'',
-``CognatePriming\_081\_2021-10-19.csv'',
-``CognatePriming\_084\_2021-10-15.csv'',
-``CognatePriming\_089\_2021-02-02.csv'',
-``CognatePriming\_089\_2021-07-06.csv'',
-``CognatePriming\_090\_2021-02-06\_2.csv'',
-``CognatePriming\_090\_2021-06-19.csv'',
-``CognatePriming\_091\_2021-06-18.csv'',
-``CognatePriming\_092\_2021-06-08.csv'',
-``CognatePriming\_094\_2021-02-13.csv'',
-``CognatePriming\_095\_2021-02-13\_1.csv'',
-``CognatePriming\_098\_2021-11-13.csv'',
-``CognatePriming\_100\_2021-02-20\_1.csv'',
-``CognatePriming\_100\_2021-06-14.csv'',
-``CognatePriming\_101\_2021-02-20\_1.csv'',
-``CognatePriming\_101\_2021-11-20.csv'',
-``CognatePriming\_102\_2021-02-26.csv'',
-``CognatePriming\_102\_2021-07-05.csv'',
-``CognatePriming\_102\_2021-11-12.csv'',
-``CognatePriming\_105\_2021-02-27\_1.csv'',
-``CognatePriming\_105\_2021-07-24\_1.csv'',
-``CognatePriming\_105\_2021-11-27.csv'',
-``CognatePriming\_107\_2022-02-21.csv'',
-``CognatePriming\_108\_2021-03-15.csv'',
-``CognatePriming\_108\_2022-01-26\_1.csv'',
-``CognatePriming\_110\_2022-01-22\_1.csv'',
-``CognatePriming\_112\_2022-02-18.csv'',
-``CognatePriming\_113\_2021-05-15.csv'',
-``CognatePriming\_114\_2021-05-19.csv'',
-``CognatePriming\_115\_2021-05-22.csv'',
-``CognatePriming\_115\_2021-10-23.csv'',
-``CognatePriming\_115\_2022-01-29.csv'',
-``CognatePriming\_117\_2021-11-16.csv'',
-``CognatePriming\_117\_2022-03-11\_1.csv'',
-``CognatePriming\_119\_2021-06-01.csv'',
-``CognatePriming\_119\_2022-01-26.csv'',
-``CognatePriming\_121\_2021-06-08.csv'',
-``CognatePriming\_121\_2021-10-18.csv'',
-``CognatePriming\_123\_2021-10-23.csv'',
-``CognatePriming\_124\_2022-02-18.csv'',
-``CognatePriming\_125\_2021-06-26.csv'',
-``CognatePriming\_127\_2021-06-28.csv'',
-``CognatePriming\_127\_2021-10-25.csv'',
-``CognatePriming\_128\_2021-11-02.csv'',
-``CognatePriming\_131\_2022-02-18.csv'',
-``CognatePriming\_133\_2021-07-06.csv'',
-``CognatePriming\_135\_2021-12-01.csv'',
-``CognatePriming\_136\_2021-12-03.csv'',
-``CognatePriming\_140\_2021-12-11\_2.csv'',
-``CognatePriming\_142\_2022-03-31.csv'',
-``CognatePriming\_144\_2022-01-07.csv'',
-``CognatePriming\_146\_2022-01-27.csv'',
-``CognatePriming\_146\_2022-06-14.csv'',
-``CognatePriming\_147\_2022-01-28.csv'',
-``CognatePriming\_147\_2022-06-17.csv'',
-``CognatePriming\_152\_2022-02-05.csv'',
-``CognatePriming\_154\_2022-02-08\_1.csv'',
-``CognatePriming\_154\_2022-05-24\_1.csv'',
-``CognatePriming\_157\_2022-02-10.csv'',
-``CognatePriming\_157\_2022-10-03.csv'',
-``CognatePriming\_160\_2022-02-28.csv'',
-``CognatePriming\_171\_2022-03-14.csv'',
-``CognatePriming\_172\_2022-03-15.csv'',
-``CognatePriming\_176\_2022-03-22.csv'',
-``CognatePriming\_178\_2022-03-23\_1.csv'',
-``CognatePriming\_183\_2022-10-06.csv'',
-``CognatePriming\_190\_2022-06-20.csv'',
-``CognatePriming\_192\_2022-06-21.csv'',
-``CognatePriming\_196\_2022-06-28\_2.csv'',
-``CognatePriming\_198\_2022-10-01.csv'',
-``CognatePriming\_199\_2022-10-03.csv'',
-``CognatePriming\_200\_2022-10-04.csv'',
-``CognatePriming\_201\_2022-10-07.csv'',
-``CognatePriming\_202\_2022-10-08.csv'') distinct participants. Of those
-participants, 1 provided data from one experimental session, 113
-provided data from two experimental sessions, and 1 provided data from
-three experimental sessions.
-
 We defined our time window of interest from 300 ms after the onset of
@@
 logit of target fixations, which we introduced in the statistical
-analyses as our response variable.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{attrition\_trials }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(participants, age\_group, lp, id, date\_test),}
-              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(id, age\_group)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{left\_join}\NormalTok{(attrition\_participants,}
-              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(id, age\_group)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{add\_count}\NormalTok{(age\_group, lp, }\AttributeTok{name =} \StringTok{"n\_trials"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{valid\_trial\_count =} \FunctionTok{sum}\NormalTok{(is\_valid\_trial, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{),}
-              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, lp, trial\_type, date\_test,}
-\NormalTok{                    age\_group, is\_valid\_participant, n\_trials)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ trial\_type, }
-                \AttributeTok{values\_from =}\NormalTok{ valid\_trial\_count, }
-                \AttributeTok{values\_fill =} \DecValTok{0}\NormalTok{,}
-                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{rename}\NormalTok{(}\AttributeTok{noncognate =}\NormalTok{ non\_cognate) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{add\_count}\NormalTok{(lp, age\_group) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{c}\NormalTok{(cognate, noncognate, unrelated),}
-                     \FunctionTok{lst}\NormalTok{(sum, mean, sd)),}
-              \AttributeTok{n\_valid =} \FunctionTok{sum}\NormalTok{(is\_valid\_participant),}
-              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(lp, age\_group, n, n\_trials)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{relocate}\NormalTok{(n\_valid, }\AttributeTok{.after =}\NormalTok{ n) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{n\_prop =}\NormalTok{ n\_valid}\SpecialCharTok{/}\NormalTok{n) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{arrange}\NormalTok{(age\_group, lp) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{relocate}\NormalTok{(age\_group, lp, n\_valid, n\_prop, }
-             \FunctionTok{matches}\NormalTok{(}\StringTok{"cognate"}\NormalTok{),}
-             \FunctionTok{matches}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{),}
-             \FunctionTok{matches}\NormalTok{(}\StringTok{"unrelated"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{gt}\NormalTok{(}\AttributeTok{groupname\_col =} \StringTok{"age\_group"}\NormalTok{,}
-       \AttributeTok{rowname\_col =} \StringTok{"lp"}\NormalTok{)  }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{cols\_hide}\NormalTok{(}\FunctionTok{c}\NormalTok{(n, n\_trials)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{fmt\_number}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"\_mean|\_sd"}\NormalTok{), }
-               \AttributeTok{decimals =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{fmt\_percent}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"\_prop"}\NormalTok{),}
-                \AttributeTok{decimals =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{cols\_merge\_n\_pct}\NormalTok{(}\AttributeTok{col\_n =}\NormalTok{ n\_valid, }
-                     \AttributeTok{col\_pct =}\NormalTok{ n\_prop,}
-                     \AttributeTok{autohide =} \ConstantTok{TRUE}\NormalTok{)  }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Non{-}cognate"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Cognate"}\NormalTok{, }\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Unrelated"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"unrelated"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Related"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ cognate\_mean,}
-                      \AttributeTok{col\_uncert =}\NormalTok{ cognate\_sd) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ noncognate\_mean,}
-                      \AttributeTok{col\_uncert =}\NormalTok{ noncognate\_sd) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{cols\_merge\_uncert}\NormalTok{(}\AttributeTok{col\_val =}\NormalTok{ unrelated\_mean, }
-                      \AttributeTok{col\_uncert =}\NormalTok{ unrelated\_sd) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{cols\_label}\NormalTok{(}\AttributeTok{age\_group =} \StringTok{"Age"}\NormalTok{,}
-               \AttributeTok{n\_valid =} \StringTok{"Participants (included)"}\NormalTok{,}
-               \AttributeTok{cognate\_sum =} \StringTok{"Trials"}\NormalTok{,}
-               \AttributeTok{cognate\_mean =} \StringTok{"Mean ± SD"}\NormalTok{,}
-               \AttributeTok{noncognate\_sum =} \StringTok{"Trials"}\NormalTok{,}
-               \AttributeTok{noncognate\_mean =} \StringTok{"Mean ± SD"}\NormalTok{,}
-               \AttributeTok{unrelated\_sum =} \StringTok{"Trials"}\NormalTok{,}
-               \AttributeTok{unrelated\_mean =} \StringTok{"Mean ± SD"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{summary\_rows}\NormalTok{(}\AttributeTok{groups =} \ConstantTok{TRUE}\NormalTok{,}
-                 \AttributeTok{columns =} \FunctionTok{where}\NormalTok{(is.integer),}
-                 \AttributeTok{fns =} \FunctionTok{list}\NormalTok{(}\StringTok{"Sum"} \OtherTok{=} \StringTok{"sum"}\NormalTok{),}
-                 \AttributeTok{fmt =}\NormalTok{ fmt\_number,}
-                 \AttributeTok{decimals =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{summary\_rows}\NormalTok{(}\AttributeTok{groups =} \ConstantTok{TRUE}\NormalTok{,}
-                 \AttributeTok{columns =} \FunctionTok{c}\NormalTok{(}\FunctionTok{where}\NormalTok{(is.numeric), }\SpecialCharTok{{-}}\NormalTok{n\_valid),}
-                 \AttributeTok{fns =} \FunctionTok{list}\NormalTok{(}\StringTok{"Mean"} \OtherTok{=} \StringTok{"mean"}\NormalTok{),}
-                 \AttributeTok{fmt =}\NormalTok{ fmt\_number,}
-                 \AttributeTok{decimals =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{where}\NormalTok{(is.integer),}
-                       \AttributeTok{fns =} \FunctionTok{list}\NormalTok{(}\StringTok{"N"} \OtherTok{=} \StringTok{"sum"}\NormalTok{),}
-                       \AttributeTok{formatter =}\NormalTok{ fmt\_integer) }
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-Warning: [1m[22mSince gt v0.9.0, the `formatter` argument (and associated `...`) has been
-deprecated.
-[36m*[39m Please use the `fmt` argument to provide formatting directives.
-[90mThis warning is displayed once every 8 hours.[39m
-\end{verbatim}
-
-\hypertarget{tbl-attrition-group}{}
-\begin{longtable}{l|rrrrrrr}
-\caption{\label{tbl-attrition-group}Summary of the dataset. }\tabularnewline
-
-\toprule
-\multicolumn{1}{l}{} &  & \multicolumn{4}{c}{Related} &  &  \\ 
-\cmidrule(lr){3-6}
-\multicolumn{1}{l}{} &  & \multicolumn{2}{c}{Cognate} & \multicolumn{2}{c}{Non-cognate} & \multicolumn{2}{c}{Unrelated} \\ 
-\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8}
-\multicolumn{1}{l}{} & Participants (included) & Trials & Mean ± SD & Trials & Mean ± SD & Trials & Mean ± SD \\ 
-\midrule
-\multicolumn{8}{l}{21 months} \\ 
-\midrule
-Monolingual & 20 ($40.0\%$) & 103 & $2.1$ ± $2.4$ & 110 & $2.2$ ± $2.2$ & 180 & $3.6$ ± $3.6$ \\ 
-Bilingual & 9 ($20.5\%$) & 42 & $1.0$ ± $1.5$ & 52 & $1.2$ ± $1.7$ & 91 & $2.1$ ± $3.2$ \\ 
-\midrule
-\multicolumn{8}{l}{25 months} \\ 
-\midrule
-Monolingual & 29 ($55.8\%$) & 142 & $2.7$ ± $2.5$ & 142 & $2.7$ ± $2.5$ & 254 & $4.9$ ± $4.5$ \\ 
-Bilingual & 16 ($36.4\%$) & 71 & $1.6$ ± $2.3$ & 67 & $1.5$ ± $2.2$ & 123 & $2.8$ ± $3.9$ \\ 
-\midrule
-\multicolumn{8}{l}{30 months} \\ 
-\midrule
-Monolingual & 25 ($41.7\%$) & 140 & $2.3$ ± $2.8$ & 134 & $2.2$ ± $2.7$ & 255 & $4.2$ ± $5.1$ \\ 
-Bilingual & 14 ($30.4\%$) & 86 & $1.9$ ± $2.9$ & 83 & $1.8$ ± $2.8$ & 140 & $3.0$ ± $4.8$ \\ 
-\midrule 
-\midrule 
-sum & $113$ & $584$ & — & $588$ & — & $1,043$ & — \\ 
-\bottomrule
-\end{longtable}
-
-\hypertarget{modelling-approach}{%
-\subsubsection{Modelling approach}\label{modelling-approach}}
+analyses as our response variable. Missing eye-tracker samples were
+interpolated using the last-observation-carried-forward (see
+\protect\hyperlink{ref-zettersten2022peekbank}{Zettersten et al., 2022}
+for a similar approach).
 
@@
 
+We know present the results under four different trial-level inclusion
+criteria In Analysis 1, the child is required to understand the prime
+\emph{and} the target words, on top of having to fixate both target and
+distractor for at last 50 ms each during the target-distractor phase. In
+Analysis 2, the child is required to understand the target word, on top
+of having to fixate both target and distractor for at last 50 ms each
+during the target-distractor phase. In Analysis 3, the child is not
+required to understand any word, but is still required to fixate both
+target and distractor for at last 50 ms each during the
+target-distractor phase. In Analysis 4, the child is not required to
+understand any word, nor to fixate at both target and distractor.
+
+For reference:
+
+\begin{itemize}
+\tightlist
+\item
+  (\protect\hyperlink{ref-floccia2020}{\textbf{floccia2020?}}) requires
+  participants to know prime and target, but not to look at target
+  \emph{and} distractor (looking at at least one of them is enough).
+\end{itemize}
+
+The fact that in some time course analyses participants seem to be
+looking predominantly towards one of the objects (despite the target and
+distractor pictures having been presented less than 300 ms before) is a
+common finding in previous studies using preferential looking procedures
+(e.g.,
+\protect\hyperlink{ref-floccia2020translation}{\textbf{floccia2020translation?}}).
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{tibble}\SpecialCharTok{::}\FunctionTok{lst}\NormalTok{(data\_time\_related,}
+\NormalTok{            data\_time\_related\_vtarget,}
+\NormalTok{            data\_time\_related\_vnone,}
+\NormalTok{            data\_time\_related\_noeach,}
+\NormalTok{            data\_time\_related\_vnoeach) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{bind\_rows}\NormalTok{(}\AttributeTok{.id =} \StringTok{"analysis"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{analysis =} \FunctionTok{case\_when}\NormalTok{(}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_related"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 1"}\NormalTok{,}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_related\_vtarget"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 2"}\NormalTok{,}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_related\_vnone"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 3"}\NormalTok{,}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_related\_noeach"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 4"}\NormalTok{,}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_related\_vnoeach"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 5"}
+\NormalTok{    )) }\SpecialCharTok{|\textgreater{}} 
+    \CommentTok{\# summarise(.elog\_mean = mean(.elog),}
+    \CommentTok{\#         n = n(),}
+    \CommentTok{\#         .elog\_std = sd(.elog),}
+    \CommentTok{\#         .by = c(condition, timebin, analysis, lp)) |\textgreater{}}
+    \CommentTok{\# mutate(.elog\_se = .elog\_std/n) |\textgreater{} }
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .elog,}
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_grid}\NormalTok{(analysis}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \FloatTok{0.5}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =}\NormalTok{ lm, }
+                \AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }
+                \AttributeTok{formula =}\NormalTok{ y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ splines}\SpecialCharTok{::}\FunctionTok{bs}\NormalTok{(x, }\DecValTok{4}\NormalTok{)) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_errorbar(aes(ymin = .elog\_mean {-} .elog\_se*1.96, }
+    \CommentTok{\#                 ymax = .elog\_mean + .elog\_se*1.96),}
+    \CommentTok{\#             width = 0.25,}
+    \CommentTok{\#             linewidth = 3/4) + }
+    \CommentTok{\# geom\_line(size = 3/4) + }
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean, }\AttributeTok{geom =} \StringTok{"point"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun.data =}\NormalTok{ mean\_se,}
+                 \AttributeTok{geom =} \StringTok{"errorbar"}\NormalTok{,}
+                 \AttributeTok{width =} \FloatTok{0.25}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{colour =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{linetype =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{shape =} \StringTok{"Condition"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{+}
+    \CommentTok{\# scale\_shape\_manual(values = c(1, 2)) +}
+    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{((x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{)}\SpecialCharTok{+}\DecValTok{300}\NormalTok{, }
+                                            \AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{()) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-related-summary-1.pdf}
+
+}
+
+\caption{\label{fig-related-summary}Marginal posterior predictions of
+the GAMMs. (A) Mean posterior probability of target looking across the
+time course of the trial. Black lines and intervals indicate the
+psoterior mean and 95\% credible intervals. Points indicate the mean
+probability of target looking across participants. (B) Difference in
+posterior probability of target looking between \emph{related} and
+\emph{unrelated} trials. The yellow rectangle indicates, in both A and
+B, the range of time points in which the 95\% credible interval of the
+differences excluded zero.}
+
+\end{figure}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{tibble}\SpecialCharTok{::}\FunctionTok{lst}\NormalTok{(data\_time\_cognate,}
+\NormalTok{            data\_time\_cognate\_vtarget,}
+\NormalTok{            data\_time\_cognate\_vnone,}
+\NormalTok{            data\_time\_cognate\_noeach,}
+\NormalTok{            data\_time\_cognate\_vnoeach) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{bind\_rows}\NormalTok{(}\AttributeTok{.id =} \StringTok{"analysis"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{analysis =} \FunctionTok{case\_when}\NormalTok{(}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_cognate"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 1"}\NormalTok{,}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_cognate\_vtarget"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 2"}\NormalTok{,}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_cognate\_vnone"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 3"}\NormalTok{,}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_cognate\_noeach"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 4"}\NormalTok{,}
+\NormalTok{        analysis}\SpecialCharTok{==}\StringTok{"data\_time\_cognate\_vnoeach"} \SpecialCharTok{\textasciitilde{}} \StringTok{"Analysis 5"}
+\NormalTok{    )) }\SpecialCharTok{|\textgreater{}} 
+    \CommentTok{\# summarise(.elog\_mean = mean(.elog),}
+    \CommentTok{\#         n = n(),}
+    \CommentTok{\#         .elog\_std = sd(.elog),}
+    \CommentTok{\#         .by = c(condition, timebin, analysis, lp)) |\textgreater{}}
+    \CommentTok{\# mutate(.elog\_se = .elog\_std/n) |\textgreater{} }
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .elog,}
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_grid}\NormalTok{(analysis}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \FloatTok{0.5}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =}\NormalTok{ lm, }
+                \AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }
+                \AttributeTok{formula =}\NormalTok{ y }\SpecialCharTok{\textasciitilde{}}\NormalTok{ splines}\SpecialCharTok{::}\FunctionTok{bs}\NormalTok{(x, }\DecValTok{4}\NormalTok{)) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_errorbar(aes(ymin = .elog\_mean {-} .elog\_se*1.96, }
+    \CommentTok{\#                 ymax = .elog\_mean + .elog\_se*1.96),}
+    \CommentTok{\#             width = 0.25,}
+    \CommentTok{\#             linewidth = 3/4) + }
+    \CommentTok{\# geom\_line(size = 3/4) + }
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean, }\AttributeTok{geom =} \StringTok{"point"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun.data =}\NormalTok{ mean\_se,}
+                 \AttributeTok{geom =} \StringTok{"errorbar"}\NormalTok{,}
+                 \AttributeTok{width =} \FloatTok{0.25}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{colour =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{linetype =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{shape =} \StringTok{"Condition"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{+}
+    \CommentTok{\# scale\_shape\_manual(values = c(1, 2)) +}
+    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{((x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{)}\SpecialCharTok{+}\DecValTok{300}\NormalTok{, }
+                                            \AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{()) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-cognate-summary-1.pdf}
+
+}
+
+\caption{\label{fig-cognate-summary}Marginal posterior predictions of
+the GAMMs. (A) Mean posterior probability of target looking across the
+time course of the trial. Black lines and intervals indicate the
+psoterior mean and 95\% credible intervals. Points indicate the mean
+probability of target looking across participants. (B) Difference in
+posterior probability of target looking between \emph{related} and
+\emph{unrelated} trials. The yellow rectangle indicates, in both A and
+B, the range of time points in which the 95\% credible interval of the
+differences excluded zero.}
+
+\end{figure}
+
+\hypertarget{analysis-1}{%
+\subsection{Analysis 1}\label{analysis-1}}
+
+Participants must know \textbf{prime} \emph{and} \textbf{target} words,
+and must look at least 10 ms to each target and distractor.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{n\_trials }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(attrition\_trials)}
+\NormalTok{n\_total }\OtherTok{\textless{}{-}} \FunctionTok{n\_distinct}\NormalTok{(attrition\_trials}\SpecialCharTok{$}\NormalTok{id)}
+\NormalTok{n\_trials\_valid }\OtherTok{\textless{}{-}} \FunctionTok{inner\_join}\NormalTok{(attrition\_participants,}
+\NormalTok{                             attrition\_trials,}
+                             \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(id)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{filter}\NormalTok{(is\_valid\_participant) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pull}\NormalTok{(is\_valid\_trial) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{sum}\NormalTok{()}
+\NormalTok{n\_participants\_valid }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(attrition\_participants}\SpecialCharTok{$}\NormalTok{is\_valid\_participant)}
+\NormalTok{n\_exc\_prime }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_prime)}
+\NormalTok{n\_exc\_test }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_test)}
+\NormalTok{n\_exc\_test\_each }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_test\_each)}
+\NormalTok{n\_exc\_vocab }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials}\SpecialCharTok{$}\NormalTok{is\_valid\_vocab)}
+\NormalTok{n\_exc\_cognate }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants}\SpecialCharTok{$}\NormalTok{is\_valid\_cognate)}
+\NormalTok{n\_exc\_noncognate }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants}\SpecialCharTok{$}\NormalTok{is\_valid\_noncognate)}
+\NormalTok{n\_exc\_unrelated }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants}\SpecialCharTok{$}\NormalTok{is\_valid\_unrelated)}
+
+\NormalTok{n\_longitudinal }\OtherTok{\textless{}{-}}\NormalTok{ attrition\_participants }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{filter}\NormalTok{(is\_valid\_participant) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{count}\NormalTok{(id, }\AttributeTok{name =} \StringTok{"times"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{count}\NormalTok{(times)}
+\end{Highlighting}
+\end{Shaded}
+
+We gathered data from 9,472 trials from 180 distinct participants. We
+excluded trials in which participants failed to provide 50\% valid
+eye-tracking samples during the prime phase (\emph{n} = 1,810) or during
+the target-distractor phase (\emph{n} = 1,493). We also excluded trials
+in which participants did not provide at least 5\% of valid samples to
+\emph{both} target and distractor in the test phase (\emph{n} = 2,793).
+Finally, we excluded trials in which participants did not understand the
+prime \emph{or} the target word, according to a supplementary vocabulary
+checklist filled by their caregivers upon experiment completion
+(\emph{n} = 5,884). After applying these trial-level inclusion criteria,
+we excluded participants who did not provide at least two valid trials
+in the \emph{cognate prime} condition (\emph{n} = 173), the
+\emph{non-cognate prime} condition (\emph{n} = 168), or the
+\emph{unrelated prime} condition (\emph{n} = 157). The resulting dataset
+included 3,393 trials from 113 participants. Of those participants, 60
+provided data from one experimental session, 19 provided data from two
+experimental sessions, and 5 provided data from three experimental
+sessions. Table~\ref{tbl-attrition-trials} shows a detailed description
+of the trial attrition.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{attrition\_trials }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ attrition\_participants}\SpecialCharTok{$}\NormalTok{id[attrition\_participants}\SpecialCharTok{$}\NormalTok{is\_valid\_participant]) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(participants, filename, id, age\_group),}
+              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename, id, age\_group)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{n\_valid =} \FunctionTok{sum}\NormalTok{(is\_valid\_trial),}
+              \AttributeTok{n\_total =} \FunctionTok{n}\NormalTok{(),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, age\_group, trial\_type)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(n\_valid, }\FunctionTok{lst}\NormalTok{(sum, mean, sd),}
+                     \AttributeTok{.names =} \StringTok{"\{.fn\}"}\NormalTok{),}
+              \AttributeTok{n\_total =} \FunctionTok{sum}\NormalTok{(n\_total),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(age\_group, trial\_type)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{n\_excluded =}\NormalTok{ n\_total}\SpecialCharTok{{-}}\NormalTok{sum) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(n\_total)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ trial\_type,}
+                \AttributeTok{values\_from =} \FunctionTok{c}\NormalTok{(sum}\SpecialCharTok{:}\NormalTok{sd, n\_excluded),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{rename\_with}\NormalTok{(\textbackslash{}(x) }\FunctionTok{gsub}\NormalTok{(}\StringTok{"non\_cognate"}\NormalTok{, }
+                          \StringTok{"noncognate"}\NormalTok{,}
+\NormalTok{                          x)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{arrange}\NormalTok{(age\_group) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{relocate}\NormalTok{(age\_group,}
+             \FunctionTok{matches}\NormalTok{(}\StringTok{"\_cognate"}\NormalTok{),}
+             \FunctionTok{matches}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{gt}\NormalTok{(}\AttributeTok{rowname\_col =} \StringTok{"age\_group"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{matches}\NormalTok{(}\StringTok{"mean\_"}\NormalTok{),}
+                       \AttributeTok{fns =} \FunctionTok{lst}\NormalTok{(Mean }\SpecialCharTok{\textasciitilde{}} \FunctionTok{mean}\NormalTok{(.)),}
+                       \AttributeTok{fmt =} \SpecialCharTok{\textasciitilde{}}\FunctionTok{fmt\_number}\NormalTok{(.)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{matches}\NormalTok{(}\StringTok{"sum\_"}\NormalTok{),}
+                       \AttributeTok{fns =} \FunctionTok{lst}\NormalTok{(Sum }\SpecialCharTok{\textasciitilde{}} \FunctionTok{sum}\NormalTok{(.)),}
+                       \AttributeTok{fmt =} \SpecialCharTok{\textasciitilde{}}\FunctionTok{fmt\_integer}\NormalTok{(.)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_cognate, n\_excluded\_cognate), }
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_noncognate, n\_excluded\_noncognate), }
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_unrelated, n\_excluded\_unrelated),}
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_cognate, sd\_cognate) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_noncognate, sd\_noncognate) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_unrelated, sd\_unrelated) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Cognate trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"\_cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Non{-}cognate trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Unrelated trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"unrelated"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Related trials"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{fmt\_number}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"mean|sd"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{fmt\_integer}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"sum"}\NormalTok{), }\AttributeTok{sep\_mark =} \StringTok{","}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_label}\NormalTok{(}\AttributeTok{sum\_cognate =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{sum\_noncognate =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{sum\_unrelated =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{mean\_cognate =} \StringTok{"Mean"}\NormalTok{,}
+               \AttributeTok{mean\_noncognate =} \StringTok{"Mean"}\NormalTok{,}
+               \AttributeTok{mean\_unrelated =} \StringTok{"Mean"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{tbl-attrition-trials}{}
+\begin{longtable}{l|rrrrrr}
+\caption{\label{tbl-attrition-trials}Trial attrition rate by condition for included participants. Additional
+excluded trials are indicated between parentheses. }\tabularnewline
+
+\toprule
+\multicolumn{1}{l}{} & \multicolumn{4}{c}{Related trials} &  &  \\ 
+\cmidrule(lr){2-5}
+\multicolumn{1}{l}{} & \multicolumn{2}{c}{Cognate trials} & \multicolumn{2}{c}{Non-cognate trials} & \multicolumn{2}{c}{Unrelated trials} \\ 
+\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
+\multicolumn{1}{l}{} & N & Mean & N & Mean & N & Mean \\ 
+\midrule
+21 months & $131$ (245) & $2.79$ ± $2.25$ & $140$ (236) & $2.98$ ± $1.98$ & $237$ (515) & $5.04$ ± $3.61$ \\ 
+25 months & $208$ (272) & $3.47$ ± $2.28$ & $203$ (277) & $3.38$ ± $2.37$ & $369$ (591) & $6.15$ ± $4.03$ \\ 
+30 months & $218$ (230) & $3.89$ ± $2.89$ & $214$ (234) & $3.82$ ± $2.80$ & $379$ (517) & $6.77$ ± $5.08$ \\ 
+\midrule 
+\midrule 
+Mean & — & $3.38$ & — & $3.39$ & — & $5.99$ \\ 
+Sum & $557$ & — & $557$ & — & $985$ & — \\ 
+\bottomrule
+\end{longtable}
+
 \hypertarget{phonological-priming-related-vs.-unrelated}{%
-\subsection{Phonological priming: Related
+\subsubsection{Phonological priming: Related
 vs.~Unrelated}\label{phonological-priming-related-vs.-unrelated}}
@@
 equivalently
-(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) = -0.724,
-\emph{SE} = 3.487). Both models showed substantially better predictive
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) = -5.146,
+\emph{SE} = 4.634). Both models showed substantially better predictive
 performance than the model including only \emph{Group}
 (\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}\) =
--48.179, \emph{SE} = 11.672). This indicates that including the
+-55.182, \emph{SE} = 42.373). This indicates that including the
 \emph{Relatedness} predictor improved the predictive performance of the
@@
 \begin{Highlighting}[]
-\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{relatedness =} \FunctionTok{levels}\NormalTok{(data\_time}\SpecialCharTok{$}\NormalTok{relatedness),}
-                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{20}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
-                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time}\SpecialCharTok{$}\NormalTok{age),}
-                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time}\SpecialCharTok{$}\NormalTok{lp)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fit\_related,}
+\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{condition =} \FunctionTok{levels}\NormalTok{(data\_time\_related}\SpecialCharTok{$}\NormalTok{condition),}
+                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{17}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
+                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_related}\SpecialCharTok{$}\NormalTok{age),}
+                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_related}\SpecialCharTok{$}\NormalTok{lp),}
+                      \AttributeTok{.nsamples =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fits\_related[[}\DecValTok{4}\NormalTok{]],}
                     \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
-                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }
-
-\NormalTok{data\_time }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{logit\_t =} \FunctionTok{mean}\NormalTok{(logit\_t),}
-              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, relatedness, age)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, logit\_t, }
-               \AttributeTok{colour =}\NormalTok{ relatedness,}
-               \AttributeTok{fill =}\NormalTok{ relatedness,}
-               \AttributeTok{shape =}\NormalTok{ relatedness)) }\SpecialCharTok{+}
+                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{, }
+                    \AttributeTok{value =} \StringTok{".value"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{lp =} \FunctionTok{factor}\NormalTok{(lp, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Monolingual"}\NormalTok{, }\StringTok{"Bilingual"}\NormalTok{)))}
+
+\NormalTok{epreds\_diff }\OtherTok{\textless{}{-}}\NormalTok{ epreds }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ condition,}
+                \AttributeTok{values\_from =}\NormalTok{ .value,}
+                \AttributeTok{id\_cols =} \FunctionTok{c}\NormalTok{(timebin, age, lp, .draw),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{diff =}\NormalTok{ related }\SpecialCharTok{{-}}\NormalTok{ unrelated) }
+
+\CommentTok{\# diff\_rect \textless{}{-} epreds\_diff |\textgreater{} }
+\CommentTok{\#   mean\_qi(diff) |\textgreater{} }
+\CommentTok{\#   mutate(is\_cluster = .lower \textgreater{} 0 | .upper \textless{} 0) }
+\CommentTok{\# }
+\CommentTok{\# clusters \textless{}{-} rle(diff(diff\_rect$is\_cluster))}
+\CommentTok{\# diff\_rect$cluster\_id \textless{}{-} c(0, rep(clusters$values, clusters$lengths))}
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} diff\_rect |\textgreater{} }
+\CommentTok{\#   arrange(lp, timebin)}
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} }
+\CommentTok{\#   cluster\_number = }
+\CommentTok{\#   summarise(xmin = min(timebin),}
+\CommentTok{\#             xmax = max(timebin),}
+\CommentTok{\#             .by = c(lp, is\_cluster)) |\textgreater{} }
+\CommentTok{\#   filter(is\_cluster)}
+
+\CommentTok{\# diff\_obs \textless{}{-} data\_time\_related |\textgreater{}}
+\CommentTok{\#   pivot\_wider(names\_from = condition, }
+\CommentTok{\#               values\_from = elog,}
+\CommentTok{\#               names\_repair = janitor::make\_clean\_names) |\textgreater{} mutate(diff = related {-} unrelated)}
+
+\NormalTok{data\_time\_related }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{.prop =} \FunctionTok{mean}\NormalTok{(.prop),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, condition, age)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .prop, }
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition,}
+               \AttributeTok{linetype =}\NormalTok{ condition)) }\SpecialCharTok{+}
     \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}Inf,}
+    \CommentTok{\#           ymax = Inf),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
     \CommentTok{\# geom\_line(data = epreds,}
     \CommentTok{\#         aes(y = .epred,}
-    \CommentTok{\#           group = interaction(relatedness, .draw)),}
+\CommentTok{\#           group = interaction(condition, .draw)),}
+\CommentTok{\#         linetype = "solid",}
+\CommentTok{\#         alpha = 0.1,}
+\CommentTok{\#         linewidth = 3/4) +}
+\FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
+             \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .value),}
+             \AttributeTok{fun.data =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{mean\_qi}\NormalTok{(x, }\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{),}
+             \AttributeTok{geom =} \StringTok{"ribbon"}\NormalTok{,}
+             \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
+             \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
+                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .value,}
+                    \AttributeTok{linetype =}\NormalTok{ condition),}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean,}
+                 \AttributeTok{geom =} \StringTok{"point"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{size =} \FloatTok{2.5}\NormalTok{,}
+                 \AttributeTok{stroke =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{colour =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{linetype =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{shape =} \StringTok{"Condition"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{()) }\SpecialCharTok{+}
+
+\NormalTok{    epreds\_diff }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, diff)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}Inf,}
+    \CommentTok{\#           ymax = Inf),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \FunctionTok{stat\_lineribbon}\NormalTok{(}\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{,}
+                    \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{,}
+                    \AttributeTok{fill =} \StringTok{"grey"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds\_diff,}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_point(data = diff\_obs) +}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"CrI"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{strip.text =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+}
+
+    \FunctionTok{plot\_layout}\NormalTok{(}\AttributeTok{ncol =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{\&}
+    \FunctionTok{plot\_annotation}\NormalTok{(}\AttributeTok{tag\_levels =} \StringTok{"A"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{((x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{)}\SpecialCharTok{+}\DecValTok{300}\NormalTok{, }
+                                            \AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{panel.grid =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-related-1.pdf}
+
+}
+
+\caption{\label{fig-related}Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course
+of the trial. Black lines and intervals indicate the psoterior mean and
+95\% credible intervals. Points indicate the mean probability of target
+looking across participants. (B) Difference in posterior probability of
+target looking between \emph{related} and \emph{unrelated} trials. The
+yellow rectangle indicates, in both A and B, the range of time points in
+which the 95\% credible interval of the differences excluded zero.}
+
+\end{figure}
+
+\hypertarget{cognate-priming-cognate-vs.-non-cognate}{%
+\subsubsection{Cognate priming: Cognate
+vs.~Non-cognate}\label{cognate-priming-cognate-vs.-non-cognate}}
+
+A model including the \emph{Cognateness} \(\times\) \emph{Group}
+interaction showed the best of-of-sample predictive performance,
+although the model including only \emph{Cognateness} performed
+equivalently
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) =
+-25.189, \emph{SE} = 5.023). Both models showed substantially better
+predictive performance than the model including only \emph{Group}
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) =
+-60.098, \emph{SE} = 41.472). This indicates that including the
+\emph{Cognateness} predictor improved the predictive performance of the
+model significantly, that including its interaction with \emph{Group}
+slightly increased the performance of the model, and that the main
+effect of \emph{Group} by itself barely changed the predictive
+performance of the model.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{condition =} \FunctionTok{levels}\NormalTok{(data\_time\_cognate}\SpecialCharTok{$}\NormalTok{condition),}
+                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{17}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
+                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_cognate}\SpecialCharTok{$}\NormalTok{age),}
+                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_cognate}\SpecialCharTok{$}\NormalTok{lp),}
+                      \AttributeTok{.nsamples =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fits\_cognate[[}\DecValTok{4}\NormalTok{]],}
+                    \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
+                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{lp =} \FunctionTok{factor}\NormalTok{(lp, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Monolingual"}\NormalTok{, }\StringTok{"Bilingual"}\NormalTok{)))}
+
+\NormalTok{epreds\_diff }\OtherTok{\textless{}{-}}\NormalTok{ epreds }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ condition,}
+                \AttributeTok{values\_from =}\NormalTok{ .epred,}
+                \AttributeTok{id\_cols =} \FunctionTok{c}\NormalTok{(timebin, age, lp, .draw),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{diff =}\NormalTok{ cognate }\SpecialCharTok{{-}}\NormalTok{ non\_cognate) }
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} epreds\_diff |\textgreater{} }
+\CommentTok{\#   mean\_qi(diff) |\textgreater{} }
+\CommentTok{\#   filter(.lower \textgreater{} 0 | .upper \textless{} 0) |\textgreater{} }
+\CommentTok{\#   summarise(xmin = min(timebin),}
+\CommentTok{\#             xmax = max(timebin),}
+\CommentTok{\#             .by = lp)}
+
+\NormalTok{data\_time\_cognate }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{.prop =} \FunctionTok{mean}\NormalTok{(.prop),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, condition, age)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .prop, }
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}1.5,}
+    \CommentTok{\#           ymax = 1.5),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \CommentTok{\# geom\_line(data = epreds,}
+    \CommentTok{\#         aes(y = .epred,}
+\CommentTok{\#           group = interaction(condition, .draw)),}
 \CommentTok{\#         linetype = "solid",}
@@
                  \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred,}
-                    \AttributeTok{linetype =}\NormalTok{ relatedness),}
+                    \AttributeTok{linetype =}\NormalTok{ condition),}
                  \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
@@
                  \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \FloatTok{0.5}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
     \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean,}
@@
          \AttributeTok{shape =} \StringTok{"Prime type"}\NormalTok{) }\SpecialCharTok{+}
-    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{+}
-    \FunctionTok{scale\_colour\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{end =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
-    \FunctionTok{scale\_fill\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.85}\NormalTok{, }\AttributeTok{end =} \FloatTok{0.35}\NormalTok{) }\SpecialCharTok{+}
-    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{+}
-    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{(x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{, }\AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{+}
-    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{,}
-          \AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{())}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{()) }\SpecialCharTok{+}
+
+\NormalTok{    epreds\_diff }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, diff)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}3/4,}
+    \CommentTok{\#           ymax = 3/4),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \FunctionTok{stat\_lineribbon}\NormalTok{(}\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{,}
+                    \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{,}
+                    \AttributeTok{fill =} \StringTok{"grey"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds\_diff,}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"CrI"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{strip.text =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+}
+
+    \FunctionTok{plot\_layout}\NormalTok{(}\AttributeTok{ncol =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{\&}
+    \FunctionTok{plot\_annotation}\NormalTok{(}\AttributeTok{tag\_levels =} \StringTok{"A"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{((x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{)}\SpecialCharTok{+}\DecValTok{300}\NormalTok{, }
+                                            \AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{panel.grid =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{) }
 \end{Highlighting}
@@
 
-{\centering \includegraphics{manuscript_files/figure-pdf/fig-related-1.pdf}
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-cognate-1.pdf}
 
@@
 
-\caption{\label{fig-related}\textbf{?(caption)}}
+\caption{\label{fig-cognate}Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course
+of the trial. Black lines and intervals indicate the psoterior mean and
+95\% credible intervals. Points indicate the mean probability of target
+looking across participants. (B) Difference in posterior probability of
+target looking between \emph{cognate} and \emph{non-cognate} trials. The
+yellow rectangle indicates, in both A and B, the range of time points in
+which the 95\% credible interval of the differences excluded zero.}
 
@@
 
-\hypertarget{cognate-priming-cognate-vs.-non-cognate}{%
-\subsection{Cognate priming: Cognate
-vs.~Non-cognate}\label{cognate-priming-cognate-vs.-non-cognate}}
+\hypertarget{analysis-2}{%
+\subsection{Analysis 2}\label{analysis-2}}
+
+Participants must know the target \textbf{target} word (no need to know
+the prime word), and must look at least 10 ms to each target and
+distractor.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{n\_trials }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(attrition\_trials\_vtarget)}
+\NormalTok{n\_trials\_valid }\OtherTok{\textless{}{-}} \FunctionTok{inner\_join}\NormalTok{(attrition\_participants\_vtarget,}
+\NormalTok{                             attrition\_trials\_vtarget) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{filter}\NormalTok{(is\_valid\_participant) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pull}\NormalTok{(is\_valid\_trial) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{sum}\NormalTok{()}
+\NormalTok{n\_participants\_valid }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(attrition\_participants\_vtarget}\SpecialCharTok{$}\NormalTok{is\_valid\_participant)}
+\NormalTok{n\_exc\_prime }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_vtarget}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_prime)}
+\NormalTok{n\_exc\_test }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_vtarget}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_test)}
+\NormalTok{n\_exc\_test\_each }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_vtarget}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_test\_each)}
+\NormalTok{n\_exc\_vocab }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_vtarget}\SpecialCharTok{$}\NormalTok{is\_valid\_vocab)}
+\NormalTok{n\_exc\_cognate }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants\_vtarget}\SpecialCharTok{$}\NormalTok{is\_valid\_cognate)}
+\NormalTok{n\_exc\_noncognate }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants\_vtarget}\SpecialCharTok{$}\NormalTok{is\_valid\_noncognate)}
+\NormalTok{n\_exc\_unrelated }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants\_vtarget}\SpecialCharTok{$}\NormalTok{is\_valid\_unrelated)}
+
+\NormalTok{n\_longitudinal }\OtherTok{\textless{}{-}}\NormalTok{ attrition\_participants\_vtarget }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{filter}\NormalTok{(is\_valid\_participant) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{count}\NormalTok{(id, }\AttributeTok{name =} \StringTok{"times"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{count}\NormalTok{(times)}
+\end{Highlighting}
+\end{Shaded}
+
+We gathered data from 9,472 trials from 180 distinct participants. We
+excluded trials in which participants failed to provide 50\% valid
+eye-tracking samples during the prime phase (\emph{n} = 1,810) or during
+the target-distractor phase (\emph{n} = 1,493). We also excluded trials
+in which participants did not provide at least 5\% of valid samples to
+\emph{both} target and distractor in the test phase (\emph{n} = 2,793).
+Finally, we excluded trials in which participants did not understand the
+target word, according to a supplementary vocabulary checklist filled by
+their caregivers upon experiment completion (\emph{n} = 5,539). After
+applying these trial-level inclusion criteria, we excluded participants
+who did not provide at least two valid trials in the \emph{cognate
+prime} condition (\emph{n} = 165), the \emph{non-cognate prime}
+condition (\emph{n} = 165), or the \emph{unrelated prime} condition
+(\emph{n} = 151). The resulting dataset included 2,219 trials from 121
+participants. Of those participants, 62 provided data from one
+experimental session, 22 provided data from two experimental sessions,
+and 5 provided data from three experimental sessions.
+Table~\ref{tbl-attrition-trials} shows a detailed description of the
+trial attrition.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{attrition\_trials\_vtarget }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ attrition\_participants\_vtarget}\SpecialCharTok{$}\NormalTok{id[attrition\_participants\_vtarget}\SpecialCharTok{$}\NormalTok{is\_valid\_participant]) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(participants, filename, id, age\_group),}
+              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename, id, age\_group)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{n\_valid =} \FunctionTok{sum}\NormalTok{(is\_valid\_trial),}
+              \AttributeTok{n\_total =} \FunctionTok{n}\NormalTok{(),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, age\_group, trial\_type)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(n\_valid, }\FunctionTok{lst}\NormalTok{(sum, mean, sd),}
+                     \AttributeTok{.names =} \StringTok{"\{.fn\}"}\NormalTok{),}
+              \AttributeTok{n\_total =} \FunctionTok{sum}\NormalTok{(n\_total),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(age\_group, trial\_type)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{n\_excluded =}\NormalTok{ n\_total}\SpecialCharTok{{-}}\NormalTok{sum) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(n\_total)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ trial\_type,}
+                \AttributeTok{values\_from =} \FunctionTok{c}\NormalTok{(sum}\SpecialCharTok{:}\NormalTok{sd, n\_excluded),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{rename\_with}\NormalTok{(\textbackslash{}(x) }\FunctionTok{gsub}\NormalTok{(}\StringTok{"non\_cognate"}\NormalTok{, }
+                          \StringTok{"noncognate"}\NormalTok{,}
+\NormalTok{                          x)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{arrange}\NormalTok{(age\_group) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{relocate}\NormalTok{(age\_group,}
+             \FunctionTok{matches}\NormalTok{(}\StringTok{"\_cognate"}\NormalTok{),}
+             \FunctionTok{matches}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{gt}\NormalTok{(}\AttributeTok{rowname\_col =} \StringTok{"age\_group"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{matches}\NormalTok{(}\StringTok{"mean\_"}\NormalTok{),}
+                       \AttributeTok{fns =} \FunctionTok{lst}\NormalTok{(Mean }\SpecialCharTok{\textasciitilde{}} \FunctionTok{mean}\NormalTok{(.)),}
+                       \AttributeTok{fmt =} \SpecialCharTok{\textasciitilde{}}\FunctionTok{fmt\_number}\NormalTok{(.)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{matches}\NormalTok{(}\StringTok{"sum\_"}\NormalTok{),}
+                       \AttributeTok{fns =} \FunctionTok{lst}\NormalTok{(Sum }\SpecialCharTok{\textasciitilde{}} \FunctionTok{sum}\NormalTok{(.)),}
+                       \AttributeTok{fmt =} \SpecialCharTok{\textasciitilde{}}\FunctionTok{fmt\_integer}\NormalTok{(.)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_cognate, n\_excluded\_cognate), }
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_noncognate, n\_excluded\_noncognate), }
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_unrelated, n\_excluded\_unrelated),}
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_cognate, sd\_cognate) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_noncognate, sd\_noncognate) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_unrelated, sd\_unrelated) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Cognate trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"\_cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Non{-}cognate trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Unrelated trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"unrelated"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Related trials"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{fmt\_number}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"mean|sd"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{fmt\_integer}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"sum"}\NormalTok{), }\AttributeTok{sep\_mark =} \StringTok{","}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_label}\NormalTok{(}\AttributeTok{sum\_cognate =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{sum\_noncognate =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{sum\_unrelated =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{mean\_cognate =} \StringTok{"Mean"}\NormalTok{,}
+               \AttributeTok{mean\_noncognate =} \StringTok{"Mean"}\NormalTok{,}
+               \AttributeTok{mean\_unrelated =} \StringTok{"Mean"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{tbl-attrition-trials-vtarget}{}
+\begin{longtable}{l|rrrrrr}
+\caption{\label{tbl-attrition-trials-vtarget}Trial attrition rate by condition for included participants. Additional
+excluded trials are indicated between parentheses. }\tabularnewline
+
+\toprule
+\multicolumn{1}{l}{} & \multicolumn{4}{c}{Related trials} &  &  \\ 
+\cmidrule(lr){2-5}
+\multicolumn{1}{l}{} & \multicolumn{2}{c}{Cognate trials} & \multicolumn{2}{c}{Non-cognate trials} & \multicolumn{2}{c}{Unrelated trials} \\ 
+\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
+\multicolumn{1}{l}{} & N & Mean & N & Mean & N & Mean \\ 
+\midrule
+21 months & $152$ (256) & $2.98$ ± $2.10$ & $158$ (250) & $3.10$ ± $1.94$ & $317$ (499) & $6.22$ ± $3.80$ \\ 
+25 months & $220$ (284) & $3.49$ ± $2.39$ & $214$ (290) & $3.40$ ± $2.46$ & $416$ (592) & $6.60$ ± $4.51$ \\ 
+30 months & $226$ (254) & $3.77$ ± $2.96$ & $219$ (261) & $3.65$ ± $2.85$ & $409$ (551) & $6.82$ ± $5.31$ \\ 
+\midrule 
+\midrule 
+Mean & — & $3.41$ & — & $3.38$ & — & $6.55$ \\ 
+Sum & $598$ & — & $591$ & — & $1,142$ & — \\ 
+\bottomrule
+\end{longtable}
+
+\hypertarget{phonological-priming-related-vs.-unrelated-1}{%
+\subsubsection{Phonological priming: Related
+vs.~Unrelated}\label{phonological-priming-related-vs.-unrelated-1}}
+
+A model including the \emph{Relatedness} \(\times\) \emph{Group}
+interaction showed the best of-of-sample predictive performance,
+although the model including only \emph{Relatedness} performed
+equivalently
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) =
+-14.134, \emph{SE} = 5.25). Both models showed substantially better
+predictive performance than the model including only \emph{Group}
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}\) =
+-38.505, \emph{SE} = 38.46). This indicates that including the
+\emph{Relatedness} predictor improved the predictive performance of the
+model significantly, that including its interaction with \emph{Group}
+slightly increased the performance of the model, and that the main
+effect of \emph{Group} by itself barely changed the predictive
+performance of the model.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{condition =} \FunctionTok{levels}\NormalTok{(data\_time\_related\_vtarget}\SpecialCharTok{$}\NormalTok{condition),}
+                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{17}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
+                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_related\_vtarget}\SpecialCharTok{$}\NormalTok{age),}
+                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_related\_vtarget}\SpecialCharTok{$}\NormalTok{lp),}
+                      \AttributeTok{.nsamples =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fits\_related\_vtarget[[}\DecValTok{4}\NormalTok{]],}
+                    \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
+                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{, }
+                    \AttributeTok{value =} \StringTok{".value"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{lp =} \FunctionTok{factor}\NormalTok{(lp, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Monolingual"}\NormalTok{, }\StringTok{"Bilingual"}\NormalTok{)))}
+
+\NormalTok{epreds\_diff }\OtherTok{\textless{}{-}}\NormalTok{ epreds }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ condition,}
+                \AttributeTok{values\_from =}\NormalTok{ .value,}
+                \AttributeTok{id\_cols =} \FunctionTok{c}\NormalTok{(timebin, age, lp, .draw),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{diff =}\NormalTok{ related }\SpecialCharTok{{-}}\NormalTok{ unrelated) }
+
+\CommentTok{\# diff\_rect \textless{}{-} epreds\_diff |\textgreater{} }
+\CommentTok{\#   mean\_qi(diff) |\textgreater{} }
+\CommentTok{\#   mutate(is\_cluster = .lower \textgreater{} 0 | .upper \textless{} 0) }
+\CommentTok{\# }
+\CommentTok{\# clusters \textless{}{-} rle(diff(diff\_rect$is\_cluster))}
+\CommentTok{\# diff\_rect$cluster\_id \textless{}{-} c(0, rep(clusters$values, clusters$lengths))}
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} diff\_rect |\textgreater{} }
+\CommentTok{\#   arrange(lp, timebin)}
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} }
+\CommentTok{\#   cluster\_number = }
+\CommentTok{\#   summarise(xmin = min(timebin),}
+\CommentTok{\#             xmax = max(timebin),}
+\CommentTok{\#             .by = c(lp, is\_cluster)) |\textgreater{} }
+\CommentTok{\#   filter(is\_cluster)}
+
+\CommentTok{\# diff\_obs \textless{}{-} data\_time\_related |\textgreater{}}
+\CommentTok{\#   pivot\_wider(names\_from = condition, }
+\CommentTok{\#               values\_from = elog,}
+\CommentTok{\#               names\_repair = janitor::make\_clean\_names) |\textgreater{} mutate(diff = related {-} unrelated)}
+
+\NormalTok{data\_time\_related\_vtarget }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{.prop =} \FunctionTok{mean}\NormalTok{(.prop),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, condition, age)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .prop, }
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition,}
+               \AttributeTok{linetype =}\NormalTok{ condition)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}Inf,}
+    \CommentTok{\#           ymax = Inf),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \CommentTok{\# geom\_line(data = epreds,}
+    \CommentTok{\#         aes(y = .epred,}
+\CommentTok{\#           group = interaction(condition, .draw)),}
+\CommentTok{\#         linetype = "solid",}
+\CommentTok{\#         alpha = 0.1,}
+\CommentTok{\#         linewidth = 3/4) +}
+\FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
+             \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .value),}
+             \AttributeTok{fun.data =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{mean\_qi}\NormalTok{(x, }\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{),}
+             \AttributeTok{geom =} \StringTok{"ribbon"}\NormalTok{,}
+             \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
+             \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
+                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .value,}
+                    \AttributeTok{linetype =}\NormalTok{ condition),}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean,}
+                 \AttributeTok{geom =} \StringTok{"point"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{size =} \FloatTok{2.5}\NormalTok{,}
+                 \AttributeTok{stroke =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{colour =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{linetype =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{shape =} \StringTok{"Condition"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{()) }\SpecialCharTok{+}
+
+\NormalTok{    epreds\_diff }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, diff)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}Inf,}
+    \CommentTok{\#           ymax = Inf),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \FunctionTok{stat\_lineribbon}\NormalTok{(}\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{,}
+                    \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{,}
+                    \AttributeTok{fill =} \StringTok{"grey"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds\_diff,}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_point(data = diff\_obs) +}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"CrI"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{strip.text =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+}
+
+    \FunctionTok{plot\_layout}\NormalTok{(}\AttributeTok{ncol =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{\&}
+    \FunctionTok{plot\_annotation}\NormalTok{(}\AttributeTok{tag\_levels =} \StringTok{"A"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{((x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{)}\SpecialCharTok{+}\DecValTok{300}\NormalTok{, }
+                                            \AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{panel.grid =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-related-vtarget-1.pdf}
+
+}
+
+\caption{\label{fig-related-vtarget}Marginal posterior predictions of
+the GAMMs. (A) Mean posterior probability of target looking across the
+time course of the trial. Black lines and intervals indicate the
+psoterior mean and 95\% credible intervals. Points indicate the mean
+probability of target looking across participants. (B) Difference in
+posterior probability of target looking between \emph{related} and
+\emph{unrelated} trials. The yellow rectangle indicates, in both A and
+B, the range of time points in which the 95\% credible interval of the
+differences excluded zero.}
+
+\end{figure}
+
+\hypertarget{cognate-priming-cognate-vs.-non-cognate-1}{%
+\subsubsection{Cognate priming: Cognate
+vs.~Non-cognate}\label{cognate-priming-cognate-vs.-non-cognate-1}}
 
@@
 equivalently
-(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) = -1.835,
-\emph{SE} = 2.279). Both models showed substantially better predictive
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) = -3.684,
+\emph{SE} = 4.241). Both models showed substantially better predictive
 performance than the model including only \emph{Group}
 (\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) =
--43.201, \emph{SE} = 10.598). This indicates that including the
+-50.588, \emph{SE} = 43.666). This indicates that including the
 \emph{Cognateness} predictor improved the predictive performance of the
@@
 \begin{Highlighting}[]
-\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{cognateness =} \FunctionTok{levels}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{cognateness),}
-                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{20}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
-                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{age),}
-                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{lp)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fit\_cognate\_alt,}
+\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{condition =} \FunctionTok{levels}\NormalTok{(data\_time\_cognate\_vtarget}\SpecialCharTok{$}\NormalTok{condition),}
+                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{17}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
+                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_cognate\_vtarget}\SpecialCharTok{$}\NormalTok{age),}
+                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_cognate\_vtarget}\SpecialCharTok{$}\NormalTok{lp),}
+                      \AttributeTok{.nsamples =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fits\_cognate\_vtarget[[}\DecValTok{4}\NormalTok{]],}
                     \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
-                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }
-
-\NormalTok{data\_time\_cognateness\_alt }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{logit\_t =} \FunctionTok{mean}\NormalTok{(logit\_t),}
-              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, cognateness, age)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, logit\_t, }
-               \AttributeTok{colour =}\NormalTok{ cognateness,}
-               \AttributeTok{fill =}\NormalTok{ cognateness,}
-               \AttributeTok{shape =}\NormalTok{ cognateness)) }\SpecialCharTok{+}
+                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{lp =} \FunctionTok{factor}\NormalTok{(lp, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Monolingual"}\NormalTok{, }\StringTok{"Bilingual"}\NormalTok{)))}
+
+\NormalTok{epreds\_diff }\OtherTok{\textless{}{-}}\NormalTok{ epreds }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ condition,}
+                \AttributeTok{values\_from =}\NormalTok{ .epred,}
+                \AttributeTok{id\_cols =} \FunctionTok{c}\NormalTok{(timebin, age, lp, .draw),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{diff =}\NormalTok{ cognate }\SpecialCharTok{{-}}\NormalTok{ non\_cognate) }
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} epreds\_diff |\textgreater{} }
+\CommentTok{\#   mean\_qi(diff) |\textgreater{} }
+\CommentTok{\#   filter(.lower \textgreater{} 0 | .upper \textless{} 0) |\textgreater{} }
+\CommentTok{\#   summarise(xmin = min(timebin),}
+\CommentTok{\#             xmax = max(timebin),}
+\CommentTok{\#             .by = lp)}
+
+\NormalTok{data\_time\_cognate\_vtarget }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{.prop =} \FunctionTok{mean}\NormalTok{(.prop),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, condition, age)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .prop, }
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition)) }\SpecialCharTok{+}
     \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}1.5,}
+    \CommentTok{\#           ymax = 1.5),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
     \CommentTok{\# geom\_line(data = epreds,}
     \CommentTok{\#         aes(y = .epred,}
-    \CommentTok{\#           group = interaction(cognateness, .draw)),}
+\CommentTok{\#           group = interaction(condition, .draw)),}
 \CommentTok{\#         linetype = "solid",}
@@
                  \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .epred,}
-                    \AttributeTok{linetype =}\NormalTok{ cognateness),}
+                    \AttributeTok{linetype =}\NormalTok{ condition),}
                  \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
@@
 
-{\centering \includegraphics{manuscript_files/figure-pdf/fig-cognate-1.pdf}
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-cognate-vtarget-1.pdf}
 
@@
 
-\caption{\label{fig-cognate}\textbf{?(caption)}}
+\caption{\label{fig-cognate-vtarget}Marginal posterior predictions of
+the GAMMs. (A) Mean posterior probability of target looking across the
+time course of the trial. Black lines and intervals indicate the
+psoterior mean and 95\% credible intervals. Points indicate the mean
+probability of target looking across participants. (B) Difference in
+posterior probability of target looking between \emph{cognate} and
+\emph{non-cognate} trials. The yellow rectangle indicates, in both A and
+B, the range of time points in which the 95\% credible interval of the
+differences excluded zero.}
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\hypertarget{relaxing-trial-inclusion-criteria}{%
-\subsection{Relaxing trial inclusion
-criteria}\label{relaxing-trial-inclusion-criteria}}
+\hypertarget{analysis-3}{%
+\subsection{Analysis 3}\label{analysis-3}}
+
+Participants do not need to know the prime or target words, but must
+look at least 10 ms to each target and distractor.
 
@@
 \begin{Highlighting}[]
-\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{relatedness =} \FunctionTok{levels}\NormalTok{(data\_time\_alt}\SpecialCharTok{$}\NormalTok{relatedness),}
-                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{20}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
-                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time}\SpecialCharTok{$}\NormalTok{age),}
-                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_alt}\SpecialCharTok{$}\NormalTok{lp)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fit\_related\_alt,}
+\NormalTok{n\_trials }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(attrition\_trials\_vnone)}
+\NormalTok{n\_trials\_valid }\OtherTok{\textless{}{-}} \FunctionTok{inner\_join}\NormalTok{(attrition\_participants\_vnone,}
+\NormalTok{                             attrition\_trials\_vnone) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{filter}\NormalTok{(is\_valid\_participant) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pull}\NormalTok{(is\_valid\_trial) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{sum}\NormalTok{()}
+\NormalTok{n\_participants\_valid }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(attrition\_participants\_vnone}\SpecialCharTok{$}\NormalTok{is\_valid\_participant)}
+\NormalTok{n\_exc\_prime }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_vnone}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_prime)}
+\NormalTok{n\_exc\_test }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_vnone}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_test)}
+\NormalTok{n\_exc\_test\_each }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_vnone}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_test\_each)}
+\NormalTok{n\_exc\_vocab }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_vnone}\SpecialCharTok{$}\NormalTok{is\_valid\_vocab)}
+\NormalTok{n\_exc\_cognate }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants\_vnone}\SpecialCharTok{$}\NormalTok{is\_valid\_cognate)}
+\NormalTok{n\_exc\_noncognate }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants\_vnone}\SpecialCharTok{$}\NormalTok{is\_valid\_noncognate)}
+\NormalTok{n\_exc\_unrelated }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants\_vnone}\SpecialCharTok{$}\NormalTok{is\_valid\_unrelated)}
+
+\NormalTok{n\_longitudinal }\OtherTok{\textless{}{-}}\NormalTok{ attrition\_participants\_vnone }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{filter}\NormalTok{(is\_valid\_participant) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{count}\NormalTok{(id, }\AttributeTok{name =} \StringTok{"times"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{count}\NormalTok{(times)}
+\end{Highlighting}
+\end{Shaded}
+
+We gathered data from 9,472 trials from 180 distinct participants. We
+excluded trials in which participants failed to provide 50\% valid
+eye-tracking samples during the prime phase (\emph{n} = 1,810) or during
+the target-distractor phase (\emph{n} = 1,493). We also excluded trials
+in which participants did not provide at least 5\% of valid samples to
+\emph{both} target and distractor in the test phase (\emph{n} = 2,793).
+After applying these trial-level inclusion criteria, we excluded
+participants who did not provide at least two valid trials in the
+\emph{cognate prime} condition (\emph{n} = 22), the \emph{non-cognate
+prime} condition (\emph{n} = 23), or the \emph{unrelated prime}
+condition (\emph{n} = 12). The resulting dataset included 5,671 trials
+from 264 participants. Of those participants, 92 provided data from one
+experimental session, 53 provided data from two experimental sessions,
+and 22 provided data from three experimental sessions.
+Table~\ref{tbl-attrition-trials} shows a detailed description of the
+trial attrition.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{attrition\_trials\_vnone }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ attrition\_participants\_vnone}\SpecialCharTok{$}\NormalTok{id[attrition\_participants\_vnone}\SpecialCharTok{$}\NormalTok{is\_valid\_participant]) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(participants, filename, id, age\_group),}
+              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename, id, age\_group)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{n\_valid =} \FunctionTok{sum}\NormalTok{(is\_valid\_trial),}
+              \AttributeTok{n\_total =} \FunctionTok{n}\NormalTok{(),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, age\_group, trial\_type)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(n\_valid, }\FunctionTok{lst}\NormalTok{(sum, mean, sd),}
+                     \AttributeTok{.names =} \StringTok{"\{.fn\}"}\NormalTok{),}
+              \AttributeTok{n\_total =} \FunctionTok{sum}\NormalTok{(n\_total),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(age\_group, trial\_type)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{n\_excluded =}\NormalTok{ n\_total}\SpecialCharTok{{-}}\NormalTok{sum) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(n\_total)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ trial\_type,}
+                \AttributeTok{values\_from =} \FunctionTok{c}\NormalTok{(sum}\SpecialCharTok{:}\NormalTok{sd, n\_excluded),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{rename\_with}\NormalTok{(\textbackslash{}(x) }\FunctionTok{gsub}\NormalTok{(}\StringTok{"non\_cognate"}\NormalTok{, }
+                          \StringTok{"noncognate"}\NormalTok{,}
+\NormalTok{                          x)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{arrange}\NormalTok{(age\_group) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{relocate}\NormalTok{(age\_group,}
+             \FunctionTok{matches}\NormalTok{(}\StringTok{"\_cognate"}\NormalTok{),}
+             \FunctionTok{matches}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{gt}\NormalTok{(}\AttributeTok{rowname\_col =} \StringTok{"age\_group"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{matches}\NormalTok{(}\StringTok{"mean\_"}\NormalTok{),}
+                       \AttributeTok{fns =} \FunctionTok{lst}\NormalTok{(Mean }\SpecialCharTok{\textasciitilde{}} \FunctionTok{mean}\NormalTok{(.)),}
+                       \AttributeTok{fmt =} \SpecialCharTok{\textasciitilde{}}\FunctionTok{fmt\_number}\NormalTok{(.)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{matches}\NormalTok{(}\StringTok{"sum\_"}\NormalTok{),}
+                       \AttributeTok{fns =} \FunctionTok{lst}\NormalTok{(Sum }\SpecialCharTok{\textasciitilde{}} \FunctionTok{sum}\NormalTok{(.)),}
+                       \AttributeTok{fmt =} \SpecialCharTok{\textasciitilde{}}\FunctionTok{fmt\_integer}\NormalTok{(.)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_cognate, n\_excluded\_cognate), }
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_noncognate, n\_excluded\_noncognate), }
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_unrelated, n\_excluded\_unrelated),}
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_cognate, sd\_cognate) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_noncognate, sd\_noncognate) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_unrelated, sd\_unrelated) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Cognate trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"\_cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Non{-}cognate trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Unrelated trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"unrelated"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Related trials"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{fmt\_number}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"mean|sd"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{fmt\_integer}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"sum"}\NormalTok{), }\AttributeTok{sep\_mark =} \StringTok{","}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_label}\NormalTok{(}\AttributeTok{sum\_cognate =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{sum\_noncognate =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{sum\_unrelated =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{mean\_cognate =} \StringTok{"Mean"}\NormalTok{,}
+               \AttributeTok{mean\_noncognate =} \StringTok{"Mean"}\NormalTok{,}
+               \AttributeTok{mean\_unrelated =} \StringTok{"Mean"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{tbl-attrition-trials-vnone}{}
+\begin{longtable}{l|rrrrrr}
+\caption{\label{tbl-attrition-trials-vnone}Trial attrition rate by condition for included participants. Additional
+excluded trials are indicated between parentheses. }\tabularnewline
+
+\toprule
+\multicolumn{1}{l}{} & \multicolumn{4}{c}{Related trials} &  &  \\ 
+\cmidrule(lr){2-5}
+\multicolumn{1}{l}{} & \multicolumn{2}{c}{Cognate trials} & \multicolumn{2}{c}{Non-cognate trials} & \multicolumn{2}{c}{Unrelated trials} \\ 
+\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
+\multicolumn{1}{l}{} & N & Mean & N & Mean & N & Mean \\ 
+\midrule
+21 months & $428$ (300) & $4.70$ ± $2.00$ & $425$ (303) & $4.67$ ± $1.87$ & $854$ (602) & $9.38$ ± $3.30$ \\ 
+25 months & $481$ (247) & $5.29$ ± $1.81$ & $469$ (259) & $5.15$ ± $1.78$ & $952$ (504) & $10.46$ ± $3.36$ \\ 
+30 months & $556$ (236) & $5.62$ ± $1.91$ & $536$ (256) & $5.41$ ± $2.11$ & $1,068$ (516) & $10.79$ ± $3.54$ \\ 
+\midrule 
+\midrule 
+Mean & — & $5.20$ & — & $5.08$ & — & $10.21$ \\ 
+Sum & $1,465$ & — & $1,430$ & — & $2,874$ & — \\ 
+\bottomrule
+\end{longtable}
+
+\hypertarget{phonological-priming-related-vs.-unrelated-2}{%
+\subsubsection{Phonological priming: Related
+vs.~Unrelated}\label{phonological-priming-related-vs.-unrelated-2}}
+
+A model including the \emph{Relatedness} \(\times\) \emph{Group}
+interaction showed the best of-of-sample predictive performance,
+although the model including only \emph{Relatedness} performed
+equivalently
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) = -6.303,
+\emph{SE} = 7.273). Both models showed substantially better predictive
+performance than the model including only \emph{Group}
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}\) =
+-135.716, \emph{SE} = 52.934). This indicates that including the
+\emph{Relatedness} predictor improved the predictive performance of the
+model significantly, that including its interaction with \emph{Group}
+slightly increased the performance of the model, and that the main
+effect of \emph{Group} by itself barely changed the predictive
+performance of the model.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{condition =} \FunctionTok{levels}\NormalTok{(data\_time\_related\_vnone}\SpecialCharTok{$}\NormalTok{condition),}
+                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{17}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
+                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_related\_vnone}\SpecialCharTok{$}\NormalTok{age),}
+                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_related\_vnone}\SpecialCharTok{$}\NormalTok{lp),}
+                      \AttributeTok{.nsamples =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fits\_related\_vnone[[}\DecValTok{4}\NormalTok{]],}
                     \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
-                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }
-
-\NormalTok{data\_time\_alt }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{logit\_t =} \FunctionTok{mean}\NormalTok{(logit\_t),}
-              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, relatedness, age)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, logit\_t, }
-               \AttributeTok{colour =}\NormalTok{ relatedness,}
-               \AttributeTok{fill =}\NormalTok{ relatedness,}
-               \AttributeTok{shape =}\NormalTok{ relatedness)) }\SpecialCharTok{+}
+                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{, }
+                    \AttributeTok{value =} \StringTok{".value"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{lp =} \FunctionTok{factor}\NormalTok{(lp, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Monolingual"}\NormalTok{, }\StringTok{"Bilingual"}\NormalTok{)))}
+
+\NormalTok{epreds\_diff }\OtherTok{\textless{}{-}}\NormalTok{ epreds }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ condition,}
+                \AttributeTok{values\_from =}\NormalTok{ .value,}
+                \AttributeTok{id\_cols =} \FunctionTok{c}\NormalTok{(timebin, age, lp, .draw),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{diff =}\NormalTok{ related }\SpecialCharTok{{-}}\NormalTok{ unrelated) }
+
+\CommentTok{\# diff\_rect \textless{}{-} epreds\_diff |\textgreater{} }
+\CommentTok{\#   mean\_qi(diff) |\textgreater{} }
+\CommentTok{\#   mutate(is\_cluster = .lower \textgreater{} 0 | .upper \textless{} 0) }
+\CommentTok{\# }
+\CommentTok{\# clusters \textless{}{-} rle(diff(diff\_rect$is\_cluster))}
+\CommentTok{\# diff\_rect$cluster\_id \textless{}{-} c(0, rep(clusters$values, clusters$lengths))}
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} diff\_rect |\textgreater{} }
+\CommentTok{\#   arrange(lp, timebin)}
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} }
+\CommentTok{\#   cluster\_number = }
+\CommentTok{\#   summarise(xmin = min(timebin),}
+\CommentTok{\#             xmax = max(timebin),}
+\CommentTok{\#             .by = c(lp, is\_cluster)) |\textgreater{} }
+\CommentTok{\#   filter(is\_cluster)}
+
+\CommentTok{\# diff\_obs \textless{}{-} data\_time\_related |\textgreater{}}
+\CommentTok{\#   pivot\_wider(names\_from = condition, }
+\CommentTok{\#               values\_from = elog,}
+\CommentTok{\#               names\_repair = janitor::make\_clean\_names) |\textgreater{} mutate(diff = related {-} unrelated)}
+
+\NormalTok{data\_time\_related\_vnone }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{.prop =} \FunctionTok{mean}\NormalTok{(.prop),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, condition, age)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .prop, }
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition,}
+               \AttributeTok{linetype =}\NormalTok{ condition)) }\SpecialCharTok{+}
     \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}Inf,}
+    \CommentTok{\#           ymax = Inf),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
     \CommentTok{\# geom\_line(data = epreds,}
     \CommentTok{\#         aes(y = .epred,}
-    \CommentTok{\#           group = interaction(relatedness, .draw)),}
+\CommentTok{\#           group = interaction(condition, .draw)),}
+\CommentTok{\#         linetype = "solid",}
+\CommentTok{\#         alpha = 0.1,}
+\CommentTok{\#         linewidth = 3/4) +}
+\FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
+             \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .value),}
+             \AttributeTok{fun.data =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{mean\_qi}\NormalTok{(x, }\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{),}
+             \AttributeTok{geom =} \StringTok{"ribbon"}\NormalTok{,}
+             \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
+             \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
+                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .value,}
+                    \AttributeTok{linetype =}\NormalTok{ condition),}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean,}
+                 \AttributeTok{geom =} \StringTok{"point"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{size =} \FloatTok{2.5}\NormalTok{,}
+                 \AttributeTok{stroke =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{colour =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{linetype =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{shape =} \StringTok{"Condition"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{()) }\SpecialCharTok{+}
+
+\NormalTok{    epreds\_diff }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, diff)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}Inf,}
+    \CommentTok{\#           ymax = Inf),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \FunctionTok{stat\_lineribbon}\NormalTok{(}\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{,}
+                    \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{,}
+                    \AttributeTok{fill =} \StringTok{"grey"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds\_diff,}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_point(data = diff\_obs) +}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"CrI"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{strip.text =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+}
+
+    \FunctionTok{plot\_layout}\NormalTok{(}\AttributeTok{ncol =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{\&}
+    \FunctionTok{plot\_annotation}\NormalTok{(}\AttributeTok{tag\_levels =} \StringTok{"A"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{((x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{)}\SpecialCharTok{+}\DecValTok{300}\NormalTok{, }
+                                            \AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{panel.grid =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-related-vnone-1.pdf}
+
+}
+
+\caption{\label{fig-related-vnone}Marginal posterior predictions of the
+GAMMs. (A) Mean posterior probability of target looking across the time
+course of the trial. Black lines and intervals indicate the psoterior
+mean and 95\% credible intervals. Points indicate the mean probability
+of target looking across participants. (B) Difference in posterior
+probability of target looking between \emph{related} and
+\emph{unrelated} trials. The yellow rectangle indicates, in both A and
+B, the range of time points in which the 95\% credible interval of the
+differences excluded zero.}
+
+\end{figure}
+
+\hypertarget{cognate-priming-cognate-vs.-non-cognate-2}{%
+\subsubsection{Cognate priming: Cognate
+vs.~Non-cognate}\label{cognate-priming-cognate-vs.-non-cognate-2}}
+
+A model including the \emph{Cognateness} \(\times\) \emph{Group}
+interaction showed the best of-of-sample predictive performance,
+although the model including only \emph{Cognateness} performed
+equivalently
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) = -1.476,
+\emph{SE} = 5.759). Both models showed substantially better predictive
+performance than the model including only \emph{Group}
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) =
+-131.841, \emph{SE} = 49.45). This indicates that including the
+\emph{Cognateness} predictor improved the predictive performance of the
+model significantly, that including its interaction with \emph{Group}
+slightly increased the performance of the model, and that the main
+effect of \emph{Group} by itself barely changed the predictive
+performance of the model.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{condition =} \FunctionTok{levels}\NormalTok{(data\_time\_cognate\_vnone}\SpecialCharTok{$}\NormalTok{condition),}
+                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{17}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
+                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_cognate\_vnone}\SpecialCharTok{$}\NormalTok{age),}
+                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_cognate\_vnone}\SpecialCharTok{$}\NormalTok{lp),}
+                      \AttributeTok{.nsamples =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fits\_cognate\_vnone[[}\DecValTok{4}\NormalTok{]],}
+                    \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
+                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{lp =} \FunctionTok{factor}\NormalTok{(lp, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Monolingual"}\NormalTok{, }\StringTok{"Bilingual"}\NormalTok{)))}
+
+\NormalTok{epreds\_diff }\OtherTok{\textless{}{-}}\NormalTok{ epreds }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ condition,}
+                \AttributeTok{values\_from =}\NormalTok{ .epred,}
+                \AttributeTok{id\_cols =} \FunctionTok{c}\NormalTok{(timebin, age, lp, .draw),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{diff =}\NormalTok{ cognate }\SpecialCharTok{{-}}\NormalTok{ non\_cognate) }
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} epreds\_diff |\textgreater{} }
+\CommentTok{\#   mean\_qi(diff) |\textgreater{} }
+\CommentTok{\#   filter(.lower \textgreater{} 0 | .upper \textless{} 0) |\textgreater{} }
+\CommentTok{\#   summarise(xmin = min(timebin),}
+\CommentTok{\#             xmax = max(timebin),}
+\CommentTok{\#             .by = lp)}
+
+\NormalTok{data\_time\_cognate\_vnone }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{.prop =} \FunctionTok{mean}\NormalTok{(.prop),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, condition, age)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .prop, }
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}1.5,}
+    \CommentTok{\#           ymax = 1.5),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \CommentTok{\# geom\_line(data = epreds,}
+    \CommentTok{\#         aes(y = .epred,}
+\CommentTok{\#           group = interaction(condition, .draw)),}
 \CommentTok{\#         linetype = "solid",}
@@
 
-{\centering \includegraphics{manuscript_files/figure-pdf/fig-related-alt-1.pdf}
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-cognate-vnone-1.pdf}
 
@@
 
-\caption{\label{fig-related-alt}\textbf{?(caption)}}
+\caption{\label{fig-cognate-vnone}Marginal posterior predictions of the
+GAMMs. (A) Mean posterior probability of target looking across the time
+course of the trial. Black lines and intervals indicate the psoterior
+mean and 95\% credible intervals. Points indicate the mean probability
+of target looking across participants. (B) Difference in posterior
+probability of target looking between \emph{cognate} and
+\emph{non-cognate} trials. The yellow rectangle indicates, in both A and
+B, the range of time points in which the 95\% credible interval of the
+differences excluded zero.}
 
 \end{figure}
+
+\hypertarget{analysis-4}{%
+\subsection{Analysis 4}\label{analysis-4}}
+
+Participants do not need to know the prime or target words, and do not
+need to look to both pictures.
 
@@
 \begin{Highlighting}[]
-\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{cognateness =} \FunctionTok{levels}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{cognateness),}
-                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{20}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
-                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{age),}
-                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_cognateness\_alt}\SpecialCharTok{$}\NormalTok{lp)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fit\_cognate\_alt,}
+\NormalTok{n\_trials }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(attrition\_trials\_noeach)}
+\NormalTok{n\_trials\_valid }\OtherTok{\textless{}{-}} \FunctionTok{inner\_join}\NormalTok{(attrition\_participants\_noeach,}
+\NormalTok{                             attrition\_trials\_noeach) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{filter}\NormalTok{(is\_valid\_participant) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pull}\NormalTok{(is\_valid\_trial) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{sum}\NormalTok{()}
+\NormalTok{n\_participants\_valid }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(attrition\_participants\_noeach}\SpecialCharTok{$}\NormalTok{is\_valid\_participant)}
+\NormalTok{n\_exc\_prime }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_noeach}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_prime)}
+\NormalTok{n\_exc\_test }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_noeach}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_test)}
+\NormalTok{n\_exc\_test\_each }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_noeach}\SpecialCharTok{$}\NormalTok{is\_valid\_gaze\_test\_each)}
+\NormalTok{n\_exc\_vocab }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_trials\_noeach}\SpecialCharTok{$}\NormalTok{is\_valid\_vocab)}
+\NormalTok{n\_exc\_cognate }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants\_noeach}\SpecialCharTok{$}\NormalTok{is\_valid\_cognate)}
+\NormalTok{n\_exc\_noncognate }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants\_noeach}\SpecialCharTok{$}\NormalTok{is\_valid\_noncognate)}
+\NormalTok{n\_exc\_unrelated }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\NormalTok{attrition\_participants\_noeach}\SpecialCharTok{$}\NormalTok{is\_valid\_unrelated)}
+
+\NormalTok{n\_longitudinal }\OtherTok{\textless{}{-}}\NormalTok{ attrition\_participants\_noeach }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{filter}\NormalTok{(is\_valid\_participant) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{count}\NormalTok{(id, }\AttributeTok{name =} \StringTok{"times"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{count}\NormalTok{(times)}
+\end{Highlighting}
+\end{Shaded}
+
+We gathered data from 9,472 trials from 180 distinct participants. We
+excluded trials in which participants failed to provide 50\% valid
+eye-tracking samples during the prime phase (\emph{n} = 1,810) or during
+the target-distractor phase (\emph{n} = 1,493). After applying these
+trial-level inclusion criteria, we excluded participants who did not
+provide at least two valid trials in the \emph{cognate prime} condition
+(\emph{n} = 15), the \emph{non-cognate prime} condition (\emph{n} = 17),
+or the \emph{unrelated prime} condition (\emph{n} = 7). The resulting
+dataset included 7,078 trials from 277 participants. Of those
+participants, 93 provided data from one experimental session, 53
+provided data from two experimental sessions, and 26 provided data from
+three experimental sessions. Table~\ref{tbl-attrition-trials} shows a
+detailed description of the trial attrition.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{attrition\_trials\_noeach }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ attrition\_participants\_noeach}\SpecialCharTok{$}\NormalTok{id[attrition\_participants\_noeach}\SpecialCharTok{$}\NormalTok{is\_valid\_participant]) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(participants, filename, id, age\_group),}
+              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename, id, age\_group)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{n\_valid =} \FunctionTok{sum}\NormalTok{(is\_valid\_trial),}
+              \AttributeTok{n\_total =} \FunctionTok{n}\NormalTok{(),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, age\_group, trial\_type)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\FunctionTok{across}\NormalTok{(n\_valid, }\FunctionTok{lst}\NormalTok{(sum, mean, sd),}
+                     \AttributeTok{.names =} \StringTok{"\{.fn\}"}\NormalTok{),}
+              \AttributeTok{n\_total =} \FunctionTok{sum}\NormalTok{(n\_total),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(age\_group, trial\_type)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{n\_excluded =}\NormalTok{ n\_total}\SpecialCharTok{{-}}\NormalTok{sum) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(n\_total)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ trial\_type,}
+                \AttributeTok{values\_from =} \FunctionTok{c}\NormalTok{(sum}\SpecialCharTok{:}\NormalTok{sd, n\_excluded),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{rename\_with}\NormalTok{(\textbackslash{}(x) }\FunctionTok{gsub}\NormalTok{(}\StringTok{"non\_cognate"}\NormalTok{, }
+                          \StringTok{"noncognate"}\NormalTok{,}
+\NormalTok{                          x)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{arrange}\NormalTok{(age\_group) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{relocate}\NormalTok{(age\_group,}
+             \FunctionTok{matches}\NormalTok{(}\StringTok{"\_cognate"}\NormalTok{),}
+             \FunctionTok{matches}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{gt}\NormalTok{(}\AttributeTok{rowname\_col =} \StringTok{"age\_group"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{matches}\NormalTok{(}\StringTok{"mean\_"}\NormalTok{),}
+                       \AttributeTok{fns =} \FunctionTok{lst}\NormalTok{(Mean }\SpecialCharTok{\textasciitilde{}} \FunctionTok{mean}\NormalTok{(.)),}
+                       \AttributeTok{fmt =} \SpecialCharTok{\textasciitilde{}}\FunctionTok{fmt\_number}\NormalTok{(.)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{grand\_summary\_rows}\NormalTok{(}\AttributeTok{columns =} \FunctionTok{matches}\NormalTok{(}\StringTok{"sum\_"}\NormalTok{),}
+                       \AttributeTok{fns =} \FunctionTok{lst}\NormalTok{(Sum }\SpecialCharTok{\textasciitilde{}} \FunctionTok{sum}\NormalTok{(.)),}
+                       \AttributeTok{fmt =} \SpecialCharTok{\textasciitilde{}}\FunctionTok{fmt\_integer}\NormalTok{(.)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_cognate, n\_excluded\_cognate), }
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_noncognate, n\_excluded\_noncognate), }
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge}\NormalTok{(}\FunctionTok{c}\NormalTok{(sum\_unrelated, n\_excluded\_unrelated),}
+               \AttributeTok{pattern =} \StringTok{"\{1\} (\{2\})"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_cognate, sd\_cognate) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_noncognate, sd\_noncognate) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_merge\_uncert}\NormalTok{(mean\_unrelated, sd\_unrelated) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Cognate trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"\_cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Non{-}cognate trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"noncognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Unrelated trials"}\NormalTok{, }\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"unrelated"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{tab\_spanner}\NormalTok{(}\StringTok{"Related trials"}\NormalTok{, }\FunctionTok{matches}\NormalTok{(}\StringTok{"cognate"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{fmt\_number}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"mean|sd"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{fmt\_integer}\NormalTok{(}\FunctionTok{matches}\NormalTok{(}\StringTok{"sum"}\NormalTok{), }\AttributeTok{sep\_mark =} \StringTok{","}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{cols\_label}\NormalTok{(}\AttributeTok{sum\_cognate =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{sum\_noncognate =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{sum\_unrelated =} \StringTok{"N"}\NormalTok{,}
+               \AttributeTok{mean\_cognate =} \StringTok{"Mean"}\NormalTok{,}
+               \AttributeTok{mean\_noncognate =} \StringTok{"Mean"}\NormalTok{,}
+               \AttributeTok{mean\_unrelated =} \StringTok{"Mean"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{tbl-attrition-trials-noeach}{}
+\begin{longtable}{l|rrrrrr}
+\caption{\label{tbl-attrition-trials-noeach}Trial attrition rate by condition for included participants. Additional
+excluded trials are indicated between parentheses. }\tabularnewline
+
+\toprule
+\multicolumn{1}{l}{} & \multicolumn{4}{c}{Related trials} &  &  \\ 
+\cmidrule(lr){2-5}
+\multicolumn{1}{l}{} & \multicolumn{2}{c}{Cognate trials} & \multicolumn{2}{c}{Non-cognate trials} & \multicolumn{2}{c}{Unrelated trials} \\ 
+\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
+\multicolumn{1}{l}{} & N & Mean & N & Mean & N & Mean \\ 
+\midrule
+21 months & $541$ (195) & $5.88$ ± $1.94$ & $561$ (175) & $6.10$ ± $1.82$ & $1,089$ (383) & $11.84$ ± $3.46$ \\ 
+25 months & $579$ (173) & $6.16$ ± $1.94$ & $586$ (166) & $6.23$ ± $1.85$ & $1,169$ (335) & $12.44$ ± $3.43$ \\ 
+30 months & $649$ (167) & $6.36$ ± $2.01$ & $644$ (172) & $6.31$ ± $2.16$ & $1,300$ (332) & $12.75$ ± $3.65$ \\ 
+\midrule 
+\midrule 
+Mean & — & $6.13$ & — & $6.22$ & — & $12.34$ \\ 
+Sum & $1,769$ & — & $1,791$ & — & $3,558$ & — \\ 
+\bottomrule
+\end{longtable}
+
+\hypertarget{phonological-priming-related-vs.-unrelated-3}{%
+\subsubsection{Phonological priming: Related
+vs.~Unrelated}\label{phonological-priming-related-vs.-unrelated-3}}
+
+A model including the \emph{Relatedness} \(\times\) \emph{Group}
+interaction showed the best of-of-sample predictive performance,
+although the model including only \emph{Relatedness} performed
+equivalently
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) =
+-27.368, \emph{SE} = 5.299). Both models showed substantially better
+predictive performance than the model including only \emph{Group}
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}\) =
+-93.323, \emph{SE} = 42.373). This indicates that including the
+\emph{Relatedness} predictor improved the predictive performance of the
+model significantly, that including its interaction with \emph{Group}
+slightly increased the performance of the model, and that the main
+effect of \emph{Group} by itself barely changed the predictive
+performance of the model.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{condition =} \FunctionTok{levels}\NormalTok{(data\_time\_related\_noeach}\SpecialCharTok{$}\NormalTok{condition),}
+                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{17}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
+                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_related\_noeach}\SpecialCharTok{$}\NormalTok{age),}
+                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_related\_noeach}\SpecialCharTok{$}\NormalTok{lp),}
+                      \AttributeTok{.nsamples =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fits\_related\_noeach[[}\DecValTok{4}\NormalTok{]],}
                     \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
-                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }
-
-\NormalTok{data\_time\_cognateness\_alt }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{logit\_t =} \FunctionTok{mean}\NormalTok{(logit\_t),}
-              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, cognateness, age)) }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, logit\_t, }
-               \AttributeTok{colour =}\NormalTok{ cognateness,}
-               \AttributeTok{fill =}\NormalTok{ cognateness,}
-               \AttributeTok{shape =}\NormalTok{ cognateness)) }\SpecialCharTok{+}
+                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{, }
+                    \AttributeTok{value =} \StringTok{".value"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{lp =} \FunctionTok{factor}\NormalTok{(lp, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Monolingual"}\NormalTok{, }\StringTok{"Bilingual"}\NormalTok{)))}
+
+\NormalTok{epreds\_diff }\OtherTok{\textless{}{-}}\NormalTok{ epreds }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ condition,}
+                \AttributeTok{values\_from =}\NormalTok{ .value,}
+                \AttributeTok{id\_cols =} \FunctionTok{c}\NormalTok{(timebin, age, lp, .draw),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{diff =}\NormalTok{ related }\SpecialCharTok{{-}}\NormalTok{ unrelated) }
+
+\CommentTok{\# diff\_rect \textless{}{-} epreds\_diff |\textgreater{} }
+\CommentTok{\#   mean\_qi(diff) |\textgreater{} }
+\CommentTok{\#   mutate(is\_cluster = .lower \textgreater{} 0 | .upper \textless{} 0) }
+\CommentTok{\# }
+\CommentTok{\# clusters \textless{}{-} rle(diff(diff\_rect$is\_cluster))}
+\CommentTok{\# diff\_rect$cluster\_id \textless{}{-} c(0, rep(clusters$values, clusters$lengths))}
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} diff\_rect |\textgreater{} }
+\CommentTok{\#   arrange(lp, timebin)}
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} }
+\CommentTok{\#   cluster\_number = }
+\CommentTok{\#   summarise(xmin = min(timebin),}
+\CommentTok{\#             xmax = max(timebin),}
+\CommentTok{\#             .by = c(lp, is\_cluster)) |\textgreater{} }
+\CommentTok{\#   filter(is\_cluster)}
+
+\CommentTok{\# diff\_obs \textless{}{-} data\_time\_related |\textgreater{}}
+\CommentTok{\#   pivot\_wider(names\_from = condition, }
+\CommentTok{\#               values\_from = elog,}
+\CommentTok{\#               names\_repair = janitor::make\_clean\_names) |\textgreater{} mutate(diff = related {-} unrelated)}
+
+\NormalTok{data\_time\_related\_noeach }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{.prop =} \FunctionTok{mean}\NormalTok{(.prop),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, condition, age)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .prop, }
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition,}
+               \AttributeTok{linetype =}\NormalTok{ condition)) }\SpecialCharTok{+}
     \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}Inf,}
+    \CommentTok{\#           ymax = Inf),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
     \CommentTok{\# geom\_line(data = epreds,}
     \CommentTok{\#         aes(y = .epred,}
-    \CommentTok{\#           group = interaction(cognateness, .draw)),}
+\CommentTok{\#           group = interaction(condition, .draw)),}
+\CommentTok{\#         linetype = "solid",}
+\CommentTok{\#         alpha = 0.1,}
+\CommentTok{\#         linewidth = 3/4) +}
+\FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
+             \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .value),}
+             \AttributeTok{fun.data =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{mean\_qi}\NormalTok{(x, }\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{),}
+             \AttributeTok{geom =} \StringTok{"ribbon"}\NormalTok{,}
+             \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
+             \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds,}
+                 \FunctionTok{aes}\NormalTok{(}\AttributeTok{y =}\NormalTok{ .value,}
+                    \AttributeTok{linetype =}\NormalTok{ condition),}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{fun =}\NormalTok{ mean,}
+                 \AttributeTok{geom =} \StringTok{"point"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{size =} \FloatTok{2.5}\NormalTok{,}
+                 \AttributeTok{stroke =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{colour =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{linetype =} \StringTok{"Condition"}\NormalTok{,}
+         \AttributeTok{shape =} \StringTok{"Condition"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{()) }\SpecialCharTok{+}
+
+\NormalTok{    epreds\_diff }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, diff)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}Inf,}
+    \CommentTok{\#           ymax = Inf),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \FunctionTok{stat\_lineribbon}\NormalTok{(}\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{,}
+                    \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{,}
+                    \AttributeTok{fill =} \StringTok{"grey"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds\_diff,}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_point(data = diff\_obs) +}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"CrI"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{strip.text =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+}
+
+    \FunctionTok{plot\_layout}\NormalTok{(}\AttributeTok{ncol =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{\&}
+    \FunctionTok{plot\_annotation}\NormalTok{(}\AttributeTok{tag\_levels =} \StringTok{"A"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{((x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{)}\SpecialCharTok{+}\DecValTok{300}\NormalTok{, }
+                                            \AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{panel.grid =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-related-noeach-1.pdf}
+
+}
+
+\caption{\label{fig-related-noeach}Marginal posterior predictions of the
+GAMMs. (A) Mean posterior probability of target looking across the time
+course of the trial. Black lines and intervals indicate the psoterior
+mean and 95\% credible intervals. Points indicate the mean probability
+of target looking across participants. (B) Difference in posterior
+probability of target looking between \emph{related} and
+\emph{unrelated} trials. The yellow rectangle indicates, in both A and
+B, the range of time points in which the 95\% credible interval of the
+differences excluded zero.}
+
+\end{figure}
+
+\hypertarget{cognate-priming-cognate-vs.-non-cognate-3}{%
+\subsubsection{Cognate priming: Cognate
+vs.~Non-cognate}\label{cognate-priming-cognate-vs.-non-cognate-3}}
+
+A model including the \emph{Cognateness} \(\times\) \emph{Group}
+interaction showed the best of-of-sample predictive performance,
+although the model including only \emph{Cognateness} performed
+equivalently
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) =
+-25.189, \emph{SE} = 5.023). Both models showed substantially better
+predictive performance than the model including only \emph{Group}
+(\(\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}\) =
+-60.098, \emph{SE} = 41.472). This indicates that including the
+\emph{Cognateness} predictor improved the predictive performance of the
+model significantly, that including its interaction with \emph{Group}
+slightly increased the performance of the model, and that the main
+effect of \emph{Group} by itself barely changed the predictive
+performance of the model.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{epreds }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}\AttributeTok{condition =} \FunctionTok{levels}\NormalTok{(data\_time\_cognate\_noeach}\SpecialCharTok{$}\NormalTok{condition),}
+                      \AttributeTok{timebin =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{17}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{100}\NormalTok{),}
+                      \AttributeTok{age =} \FunctionTok{mean}\NormalTok{(data\_time\_cognate\_noeach}\SpecialCharTok{$}\NormalTok{age),}
+                      \AttributeTok{lp =} \FunctionTok{levels}\NormalTok{(data\_time\_cognate\_noeach}\SpecialCharTok{$}\NormalTok{lp),}
+                      \AttributeTok{.nsamples =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{add\_epred\_draws}\NormalTok{(model\_fits\_cognate\_noeach[[}\DecValTok{4}\NormalTok{]],}
+                    \AttributeTok{ndraws =} \ConstantTok{NULL}\NormalTok{,}
+                    \AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{lp =} \FunctionTok{factor}\NormalTok{(lp, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Monolingual"}\NormalTok{, }\StringTok{"Bilingual"}\NormalTok{)))}
+
+\NormalTok{epreds\_diff }\OtherTok{\textless{}{-}}\NormalTok{ epreds }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ condition,}
+                \AttributeTok{values\_from =}\NormalTok{ .epred,}
+                \AttributeTok{id\_cols =} \FunctionTok{c}\NormalTok{(timebin, age, lp, .draw),}
+                \AttributeTok{names\_repair =}\NormalTok{ janitor}\SpecialCharTok{::}\NormalTok{make\_clean\_names) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{diff =}\NormalTok{ cognate }\SpecialCharTok{{-}}\NormalTok{ non\_cognate) }
+\CommentTok{\# }
+\CommentTok{\# diff\_rect \textless{}{-} epreds\_diff |\textgreater{} }
+\CommentTok{\#   mean\_qi(diff) |\textgreater{} }
+\CommentTok{\#   filter(.lower \textgreater{} 0 | .upper \textless{} 0) |\textgreater{} }
+\CommentTok{\#   summarise(xmin = min(timebin),}
+\CommentTok{\#             xmax = max(timebin),}
+\CommentTok{\#             .by = lp)}
+
+\NormalTok{data\_time\_cognate\_noeach }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{.prop =} \FunctionTok{mean}\NormalTok{(.prop),}
+              \AttributeTok{.by =} \FunctionTok{c}\NormalTok{(id, timebin, lp, condition, age)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, .prop, }
+               \AttributeTok{colour =}\NormalTok{ condition,}
+               \AttributeTok{fill =}\NormalTok{ condition,}
+               \AttributeTok{shape =}\NormalTok{ condition)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}1.5,}
+    \CommentTok{\#           ymax = 1.5),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \CommentTok{\# geom\_line(data = epreds,}
+    \CommentTok{\#         aes(y = .epred,}
+\CommentTok{\#           group = interaction(condition, .draw)),}
 \CommentTok{\#         linetype = "solid",}
@@
          \AttributeTok{shape =} \StringTok{"Prime type"}\NormalTok{) }\SpecialCharTok{+}
-    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{+}
-    \FunctionTok{scale\_colour\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{end =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+}
-    \FunctionTok{scale\_fill\_grey}\NormalTok{(}\AttributeTok{start =} \FloatTok{0.85}\NormalTok{, }\AttributeTok{end =} \FloatTok{0.35}\NormalTok{) }\SpecialCharTok{+}
-    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{+}
-    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{(x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{, }\AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{+}
-    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{,}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{()) }\SpecialCharTok{+}
+
+\NormalTok{    epreds\_diff }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(timebin, diff)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{lp) }\SpecialCharTok{+}
+    \CommentTok{\# geom\_rect(data = diff\_rect,}
+    \CommentTok{\#         aes(xmin = xmin,}
+    \CommentTok{\#           xmax = xmax,}
+    \CommentTok{\#           ymin = {-}3/4,}
+    \CommentTok{\#           ymax = 3/4),}
+    \CommentTok{\#         colour = NA,}
+    \CommentTok{\#         fill = "orange",}
+    \CommentTok{\#         alpha = 1/2,}
+    \CommentTok{\#         inherit.aes = FALSE) +}
+    \FunctionTok{stat\_lineribbon}\NormalTok{(}\AttributeTok{.width =} \FloatTok{0.95}\NormalTok{,}
+                    \AttributeTok{linewidth =} \DecValTok{0}\NormalTok{,}
+                    \AttributeTok{fill =} \StringTok{"grey"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{stat\_summary}\NormalTok{(}\AttributeTok{data =}\NormalTok{ epreds\_diff,}
+                 \AttributeTok{fun =} \StringTok{"mean"}\NormalTok{,}
+                 \AttributeTok{geom =} \StringTok{"line"}\NormalTok{,}
+                 \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+                 \AttributeTok{linewidth =} \DecValTok{3}\SpecialCharTok{/}\DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{, }
+               \AttributeTok{linewidth =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{,}
+               \AttributeTok{linetype =} \StringTok{"dotted"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Time (ms)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"P(Target looking)"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"CrI"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{strip.text =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+}
+
+    \FunctionTok{plot\_layout}\NormalTok{(}\AttributeTok{ncol =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{\&}
+    \FunctionTok{plot\_annotation}\NormalTok{(}\AttributeTok{tag\_levels =} \StringTok{"A"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_linetype\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{rev}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"dashed"}\NormalTok{))) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_shape\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ \textbackslash{}(x) }\FunctionTok{format}\NormalTok{((x }\SpecialCharTok{*} \FloatTok{1e2}\NormalTok{)}\SpecialCharTok{+}\DecValTok{300}\NormalTok{, }
+                                            \AttributeTok{big.mark =} \StringTok{","}\NormalTok{)) }\SpecialCharTok{\&}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{panel.grid =} \FunctionTok{element\_blank}\NormalTok{(),}
+          \AttributeTok{legend.position =} \StringTok{"top"}\NormalTok{) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-cognate-noeach-1.pdf}
+
+}
+
+\caption{\label{fig-cognate-noeach}Marginal posterior predictions of the
+GAMMs. (A) Mean posterior probability of target looking across the time
+course of the trial. Black lines and intervals indicate the psoterior
+mean and 95\% credible intervals. Points indicate the mean probability
+of target looking across participants. (B) Difference in posterior
+probability of target looking between \emph{cognate} and
+\emph{non-cognate} trials. The yellow rectangle indicates, in both A and
+B, the range of time points in which the 95\% credible interval of the
+differences excluded zero.}
+
+\end{figure}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\hypertarget{appendix-a-imputing-voabulary-size-scores}{%
+\subsection{Appendix A: imputing voabulary size
+scores}\label{appendix-a-imputing-voabulary-size-scores}}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{vocabulary\_tmp }\OtherTok{\textless{}{-}}\NormalTok{ vocabulary }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(participants, }\AttributeTok{id =}\NormalTok{ id\_db, age, age\_group, filename),}
+              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{relocate}\NormalTok{(id, age) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{filename) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{filter}\NormalTok{(is\_imputed) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{id =} \FunctionTok{as.character}\NormalTok{(id))}
+
+\NormalTok{bvq\_data}\SpecialCharTok{$}\NormalTok{vocabulary }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{inner\_join}\NormalTok{(}\FunctionTok{distinct}\NormalTok{(bvq\_data}\SpecialCharTok{$}\NormalTok{logs, id, age\_group, age),}
+               \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(id, age\_group)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{is\_imputed =} \ConstantTok{FALSE}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{bind\_rows}\NormalTok{(vocabulary\_tmp) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{pivot\_longer}\NormalTok{(}\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"\_prop"}\NormalTok{),}
+                 \AttributeTok{names\_to =} \StringTok{"measure"}\NormalTok{,}
+                 \AttributeTok{values\_to =} \StringTok{"prop"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{drop\_na}\NormalTok{(prop) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{is\_imputed =} \FunctionTok{ifelse}\NormalTok{(is\_imputed, }\StringTok{"Imputed"}\NormalTok{, }\StringTok{"Observed"}\NormalTok{),}
+           \AttributeTok{measure =} \FunctionTok{factor}\NormalTok{(measure,}
+                         \AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"total\_prop"}\NormalTok{,}
+                                   \StringTok{"l1\_prop"}\NormalTok{,}
+                                   \StringTok{"l2\_prop"}\NormalTok{,}
+                                   \StringTok{"concept\_prop"}\NormalTok{,}
+                                   \StringTok{"te\_prop"}\NormalTok{),}
+                         \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Total"}\NormalTok{,}
+                                   \StringTok{"L1"}\NormalTok{,}
+                                   \StringTok{"L2"}\NormalTok{,}
+                                   \StringTok{"Conceptual"}\NormalTok{,}
+                                   \StringTok{"TE"}\NormalTok{))) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(age, prop, }
+               \AttributeTok{colour =}\NormalTok{ is\_imputed,}
+               \AttributeTok{fill =}\NormalTok{ is\_imputed)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{measure) }\SpecialCharTok{+}
+    \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =} \DecValTok{1}\SpecialCharTok{/}\DecValTok{4}\NormalTok{, }\AttributeTok{size =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"glm"}\NormalTok{, }
+                \AttributeTok{formula =} \StringTok{"y \textasciitilde{} x"}\NormalTok{,}
+                \AttributeTok{method.args =} \FunctionTok{list}\NormalTok{(}\AttributeTok{family =} \StringTok{"binomial"}\NormalTok{), }
+                \CommentTok{\# se = FALSE,}
+                \AttributeTok{size =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Age (months)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"Vocabulary size"}\NormalTok{,}
+         \AttributeTok{colour =} \StringTok{"Imputed"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{),}
+          \AttributeTok{legend.justification =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{),}
           \AttributeTok{legend.title =} \FunctionTok{element\_blank}\NormalTok{())}
@@
 
-{\centering \includegraphics{manuscript_files/figure-pdf/fig-cognate-alt-1.pdf}
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-vocabulary-imputation-1.pdf}
 
@@
 
-\caption{\label{fig-cognate-alt}\textbf{?(caption)}}
+\caption{\label{fig-vocabulary-imputation}\textbf{?(caption)}}
+
+\end{figure}
+
+\hypertarget{appendix-b-distribution-of-prime-and-target-looking-times}{%
+\subsection{Appendix B: distribution of prime and target looking
+times}\label{appendix-b-distribution-of-prime-and-target-looking-times}}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{looking\_times |\textgreater{} }
+\NormalTok{    mutate(prime\_time = cut(prime\_time, }
+\NormalTok{                            seq(0, 1.5, 0.1),}
+\NormalTok{                            labels = FALSE,}
+\NormalTok{                            include.lowest = TRUE)) |\textgreater{} }
+\NormalTok{    add\_count(lp, age\_group, name = "n\_total") |\textgreater{} }
+\NormalTok{    count(lp, age\_group, prime\_time, n\_total) |\textgreater{} }
+\NormalTok{    mutate(n = n / n\_total) |\textgreater{} }
+\NormalTok{    ggplot(aes(prime\_time, n)) +}
+\NormalTok{    facet\_grid(lp\textasciitilde{}age\_group) +}
+\NormalTok{    annotate(geom = "rect",}
+\NormalTok{             fill = "orange",}
+\NormalTok{             ymin = {-}Inf,}
+\NormalTok{             ymax = Inf,}
+\NormalTok{             xmin = 0,}
+\NormalTok{             xmax = 0.75*10,}
+\NormalTok{             alpha = 1/3,}
+\NormalTok{             colour = NA) +}
+\NormalTok{    \# annotate(label = "Excluded trials",}
+\NormalTok{    \#        geom = "text",}
+\NormalTok{    \#         x = (0.75/2)*10,}
+\NormalTok{    \#         y = 1)}
+\NormalTok{    geom\_col(fill = "black") +}
+\NormalTok{    labs(x = "Prime looking time (s)",}
+\NormalTok{         y = "Proportion of trials") +}
+\NormalTok{    scale\_x\_continuous(labels = \textbackslash{}(x) x/10) +}
+\NormalTok{    theme(panel.grid.major.y = element\_line(linetype = "dotted",}
+\NormalTok{                                            colour = "grey"))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{looking\_times |\textgreater{} }
+\NormalTok{    mutate(target\_time = cut(target\_time, }
+\NormalTok{                            seq(0, 2, 0.1),}
+\NormalTok{                            labels = FALSE,}
+\NormalTok{                            include.lowest = TRUE)) |\textgreater{} }
+\NormalTok{    add\_count(lp, age\_group, name = "n\_total") |\textgreater{} }
+\NormalTok{    count(lp, age\_group, target\_time, n\_total) |\textgreater{} }
+\NormalTok{    mutate(n = n / n\_total) |\textgreater{} }
+\NormalTok{    ggplot(aes(target\_time, n)) +}
+\NormalTok{    facet\_grid(lp\textasciitilde{}age\_group) +}
+\NormalTok{    \# annotate(label = "Excluded trials",}
+\NormalTok{    \#        geom = "text",}
+\NormalTok{    \#         x = (0.75/2)*10,}
+\NormalTok{    \#         y = 1)}
+\NormalTok{    geom\_col(fill = "black") +}
+\NormalTok{    labs(x = "Targets looking time (s)",}
+\NormalTok{         y = "Proportion of trials") +}
+\NormalTok{    scale\_x\_continuous(labels = \textbackslash{}(x) x/10) +}
+\NormalTok{    theme(panel.grid.major.y = element\_line(linetype = "dotted",}
+\NormalTok{                                            colour = "grey"))}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{appendix-c-prime-and-test-looking-times}{%
+\subsection{Appendix C: prime and test looking
+times}\label{appendix-c-prime-and-test-looking-times}}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{looking\_times }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(attrition\_trials, }
+\NormalTok{                     filename, trial, is\_valid\_trial),}
+              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename, trial)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{filter}\NormalTok{(is\_valid\_trial) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(duration,}
+\NormalTok{               prime\_time,}
+               \AttributeTok{colour =}\NormalTok{ trial\_type, }
+               \AttributeTok{fill =}\NormalTok{ trial\_type,}
+               \AttributeTok{shape =}\NormalTok{ trial\_type)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_grid}\NormalTok{(lp}\SpecialCharTok{\textasciitilde{}}\NormalTok{age\_group) }\SpecialCharTok{+}
+    \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{, }
+               \AttributeTok{size =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Audio duration (s)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"Looking time (1.0{-}2.0 seconds)"}\NormalTok{,}
+         \AttributeTok{colour =} \StringTok{"Prime type"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"Prime type"}\NormalTok{,}
+         \AttributeTok{shape =} \StringTok{"Prime type"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-looking-times-1.pdf}
+
+}
+
+\caption{\label{fig-looking-times}Looking time (s) to the prime AOI
+against audio duration. In longer audios, participants are expected to
+look longer to the target picture.}
+
+\end{figure}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{looking\_times }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{select}\NormalTok{(attrition\_trials, }
+\NormalTok{                     filename, trial, is\_valid\_trial),}
+              \AttributeTok{by =} \FunctionTok{join\_by}\NormalTok{(filename, trial)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{filter}\NormalTok{(is\_valid\_trial) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(duration,}
+\NormalTok{               target\_time,}
+               \AttributeTok{colour =}\NormalTok{ trial\_type, }
+               \AttributeTok{fill =}\NormalTok{ trial\_type,}
+               \AttributeTok{shape =}\NormalTok{ trial\_type)) }\SpecialCharTok{+}
+    \FunctionTok{facet\_grid}\NormalTok{(lp}\SpecialCharTok{\textasciitilde{}}\NormalTok{age\_group) }\SpecialCharTok{+}
+    \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
+               \AttributeTok{size =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{,}
+                \AttributeTok{formula =} \StringTok{"y \textasciitilde{} x"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Audio duration (s)"}\NormalTok{,}
+         \AttributeTok{y =} \StringTok{"Looking time (1.0{-}2.0 seconds)"}\NormalTok{,}
+         \AttributeTok{colour =} \StringTok{"Prime type"}\NormalTok{,}
+         \AttributeTok{fill =} \StringTok{"Prime type"}\NormalTok{,}
+         \AttributeTok{shape =} \StringTok{"Prime type"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{manuscript_files/figure-pdf/fig-target-times-1.pdf}
+
+}
+
+\caption{\label{fig-target-times}Looking time (s) to the prime AOI
+against audio duration. In longer audios, participants are expected to
+look longer to the target picture.}
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-boersma2001speak}{}}%
+Boersma, P., \& Van Heuven, V. (2001). Speak and unSpeak with PRAAT.
+\emph{Glot International}, \emph{5}(9/10), 341--347.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bosch2001evidence}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-fenson1994variability}{}}%
+Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J.,
+Pethick, S. J., Tomasello, M., Mervis, C. B., \& Stiles, J. (1994).
+Variability in early communicative development. \emph{Monographs of the
+Society for Research in Child Development}, i--185.
+
+\leavevmode\vadjust pre{\hypertarget{ref-garcia-castro2023bvq}{}}%
+Garcia-Castro, G., Ávila-Varela, D. S., \& Sebastian-Galles, N. (2023).
+\emph{Bvq: Barcelona vocabulary questionnaire database and helper
+functions}. \url{https://gongcastro.github.io/bvq}
+
+\leavevmode\vadjust pre{\hypertarget{ref-van2011mice}{}}%
+Van Buuren, S., \& Groothuis-Oudshoorn, K. (2011). Mice: Multivariate
+imputation by chained equations in r. \emph{Journal of Statistical
+Software}, \emph{45}, 1--67.
+
 \leavevmode\vadjust pre{\hypertarget{ref-wood2017generalized}{}}%
@@
 with r}. CRC press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zettersten2022peekbank}{}}%
+Zettersten, M., Yurovsky, D., Xu, T. L., Uner, S., Tsui, A. S. M.,
+Schneider, R. M., Saleh, A. N., Meylan, S. C., Marchman, V. A.,
+Mankewitz, J., et al. (2022). Peekbank: An open, large-scale repository
+for developmental eye-tracking data of children's word recognition.
+\emph{Behavior Research Methods}, 1--16.
+
+\leavevmode\vadjust pre{\hypertarget{ref-boersma2001speak}{}}%
+Boersma, P., \& Van Heuven, V. (2001). Speak and unSpeak with PRAAT.
+\emph{Glot International}, \emph{5}(9/10), 341--347.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-zettersten2022peekbank}{}}%
+Zettersten, M., Yurovsky, D., Xu, T. L., Uner, S., Tsui, A. S. M.,
+Schneider, R. M., Saleh, A. N., Meylan, S. C., Marchman, V. A.,
+Mankewitz, J., et al. (2022). Peekbank: An open, large-scale repository
+for developmental eye-tracking data of children's word recognition.
+\emph{Behavior Research Methods}, 1--16.
+
 \end{CSLReferences}

### 2023-10-18 manuscript/manuscript.qmd
Render manuscript to arxiv-pdf and add Oxford data

--- 2023-09-19 manuscript/manuscript.qmd
@@
 
-targets::tar_load(c(participants, stimuli, vocabulary,
-					attrition_trials, attrition_participants,
-					attrition_trials_vtarget, attrition_participants_vtarget,
-					attrition_trials_vnone, attrition_participants_vnone,
-					attrition_trials_noeach, attrition_participants_noeach,
-					bvq_data, gaze_aoi, 
-					data_time_related, data_time_cognate,
-					data_time_related_vtarget, data_time_cognate_vtarget,
-					data_time_related_vnone, data_time_cognate_vnone,
-					data_time_related_noeach, data_time_cognate_noeach))
+targets::tar_load(
+	c(participants,
+	  participants_oxf,
+	  stimuli,
+	  stimuli_oxf,
+	  vocabulary,
+	  vocabulary_oxf,
+	  attrition_trials, 
+	  attrition_participants,
+	  attrition_trials_vtarget,
+	  attrition_participants_vtarget,
+	  attrition_trials_vnone, 
+	  attrition_participants_vnone,
+	  attrition_trials_noeach,
+	  attrition_participants_noeach,
+	  attrition_trials_vnoeach,
+	  attrition_participants_vnoeach,
+	  attrition_trials_oxf, 
+	  attrition_participants_oxf,
+	  attrition_trials_vtarget_oxf,
+	  attrition_participants_vtarget_oxf,
+	  attrition_trials_vnone_oxf, 
+	  attrition_participants_vnone_oxf,
+	  attrition_trials_noeach_oxf,
+	  attrition_participants_noeach_oxf,
+	  attrition_trials_vnoeach_oxf,
+	  attrition_participants_vnoeach_oxf,
+	  bvq_data, 
+	  gaze_aoi, 
+	  looking_times,
+	  data_time_related, 
+	  data_time_cognate,
+	  data_time_related_vtarget,
+	  data_time_cognate_vtarget,
+	  data_time_related_vnone,
+	  data_time_cognate_vnone,
+	  data_time_related_noeach, 
+	  data_time_cognate_noeach,
+	  data_time_related_vnoeach,
+	  data_time_cognate_vnoeach,
+	  data_time_related_oxf, 
+	  data_time_cognate_oxf,
+	  data_time_related_vtarget_oxf,
+	  data_time_cognate_vtarget_oxf,
+	  data_time_related_vnone_oxf,
+	  data_time_cognate_vnone_oxf,
+	  data_time_related_noeach_oxf, 
+	  data_time_cognate_noeach_oxf,
+	  data_time_related_vnoeach_oxf,
+	  data_time_cognate_vnoeach_oxf
+	))
 
@@
 	  model_fits_cognate_noeach,
-	  model_loo_related,
-	  model_loo_cognate,
-	  model_loo_related_vtarget,
-	  model_loo_cognate_vtarget,
-	  model_loo_related_vnone,
-	  model_loo_cognate_vnone,
-	  model_loo_related_noeach,
-	  model_loo_cognate_noeach
+	  model_fits_related_vnoeach,
+	  model_fits_cognate_vnoeach
+	  # model_loo_related,
+	  # model_loo_cognate,
+	  # model_loo_related_vtarget,
+	  # model_loo_cognate_vtarget,
+	  # model_loo_related_vnone,
+	  # model_loo_cognate_vnone,
+	  # model_loo_related_noeach,
+	  # model_loo_cognate_noeach,
+	  # model_loo_related_vnoeach,
+	  # model_loo_cognate_vnoeach
 	))
@@
 
-attrition_trials_vtarget <- left_join(attrition_trials_vtarget, 
-									  select(participants, id, age_group, lp, filename))
+attrition_trials_vtarget <- attrition_trials_vtarget |> 
+	left_join(select(participants, id, age_group, lp, filename))
 
@@
 
-attrition_trials_vnone <- left_join(attrition_trials_vnone, 
-									select(participants, id, age_group, lp, filename))
+attrition_trials_vnone <- attrition_trials_vnone |> 
+	left_join(select(participants, id, age_group, lp, filename))
 
@@
 
-attrition_trials_noeach <- left_join(attrition_trials_noeach, 
-									 select(participants, id, age_group, lp, filename))
+attrition_trials_noeach <- attrition_trials_noeach |> 
+	left_join(select(participants, id, age_group, lp, filename))
+
+attrition_participants_vnoeach <- attrition_participants_vnoeach |> 
+	left_join(select(participants, id, age_group, lp, filename))
+
+attrition_trials_vnoeach <- attrition_trials_vnoeach |> 
+	left_join(select(participants, id, age_group, lp, filename))
 
@@
 #| tbl-cap: "Description of language profile of test participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
-participants |> 
+participants_oxf |> 
+	left_join(attrition_participants_oxf,
+			  by = join_by(id)) |> 
+	mutate(lp = "Monolingual (English)",
+		   id = as.character(id)) |> 
+	bind_rows(mutate(participants, id = as.character(id))) |> 
 	filter(is_valid_participant) |> 
-	select(id, age_group, age, lp,
-		   doe_catalan, doe_spanish, test_language) |> 
-	mutate(id = paste0(id, " (", age_group, ")")) |>
+	select(id, age_group, age, lp, test_language) |> 
 	add_count(lp, 
@@
 			  name = "n_age_group") |> 
-	pivot_longer(starts_with("doe_"),
-				 names_to = "language",
-				 values_to = "doe") |>
 	add_count(age_group,
@@
 			  name = "n_age_test") |> 
-	mutate(language = str_to_sentence(str_remove_all(language, "doe_")),
-		   age_group = paste0(age_group, " (N = ", n_age_group, ")"),
-		   test_language = paste0("Tested in ", test_language, 
-		   					   " (N = ", n_age_test, ")"),
-		   lp = factor(lp, levels = rev(unique(lp))))  |> 
-	summarise(across(c(doe, age), lst(mean, sd)),
-			  .by = c(age_group, lp, test_language, language)) |> 
-	pivot_wider(id_cols = c(age_group, test_language),
-				names_from = c(language, lp),
-				values_from = c(matches("doe"), age_mean, age_sd),
+	mutate(lp = factor(lp, levels = rev(unique(lp))))  |> 
+	summarise(across(c(age), lst(mean, sd)),
+			  n = n(),
+			  .by = c(age_group, lp, test_language)) |> 
+	pivot_wider(id_cols = c(test_language, lp),
+				names_from = c(age_group),
+				values_from = c(matches("doe"), age_mean, age_sd, n),
 				names_repair = janitor::make_clean_names) |> 
-	relocate(age_group, test_language,
-			 matches("monolingual"),
-			 matches("bilingual")) |> 
-	select(-c(age_mean_spanish_monolingual,
-			  age_mean_spanish_bilingual,
-			  age_sd_spanish_monolingual,
-			  age_sd_spanish_bilingual)) |> 
-	arrange(age_group, test_language) |> 
+	relocate(lp, test_language,
+			 matches("21"),
+			 matches("25"),
+			 matches("30"),
+	) |> 
+	arrange(lp, test_language) |> 
 	gt(rowname_col = "test_language", 
-	   groupname_col = "age_group", 
+	   groupname_col = "lp", 
 	   row_group.sep = ": ") |> 
-	tab_spanner(md("Monolingual (*N* = 162)"), matches("monolingual")) |> 
-	tab_spanner(md("Bilingual (*N* = 133)"), matches("bilingual")) |>
-	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
+	tab_spanner(md("21 months"), matches("21")) |> 
+	tab_spanner(md("25 months"), matches("25")) |>
+	tab_spanner(md("30 months"), matches("30")) |> 
 	fmt_number(matches("age"), decimals = 1) |>
-	cols_merge_uncert(col_val = age_mean_catalan_monolingual, 
-					  col_uncert = age_sd_catalan_monolingual) |> 
-	cols_merge_uncert(col_val = age_mean_catalan_bilingual, 
-					  col_uncert = age_sd_catalan_bilingual) |> 
-	cols_merge_uncert(col_val = doe_mean_catalan_monolingual,
-					  col_uncert = doe_sd_catalan_monolingual) |> 
-	cols_merge_uncert(col_val = doe_mean_catalan_bilingual,
-					  col_uncert = doe_sd_catalan_bilingual) |> 
-	cols_merge_uncert(col_val = doe_mean_spanish_monolingual, 
-					  col_uncert = doe_sd_spanish_monolingual) |> 
-	cols_merge_uncert(col_val = doe_mean_spanish_bilingual, 
-					  col_uncert = doe_sd_spanish_bilingual) |> 
-	cols_label(age_mean_catalan_monolingual = "Age (months)",
-			   age_mean_catalan_bilingual = "Age (months)",
-			   doe_mean_catalan_monolingual = "Catalan (%)",
-			   doe_mean_catalan_bilingual = "Catalan (%)",
-			   doe_mean_spanish_monolingual = "Spanish (%)",
-			   doe_mean_spanish_bilingual = "Spanish (%)") |> 
+	cols_merge(c(age_mean_21_months, age_sd_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_25_months, age_sd_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_30_months, age_sd_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_label(n_21_months = md("*N*"),
+			   n_25_months = md("*N*"),
+			   n_30_months = md("*N*"),
+			   age_mean_21_months = "Age (months)",
+			   age_mean_25_months = "Age (months)",
+			   age_mean_30_months = "Age (months)") |> 
 	tab_style(cell_text(weight = "bold"),
@@
 
-## Vocabulary size
+### Vocabulary size
 
@@
 #| label: tbl-vocabulary
-#| tbl-cap: "Vocabulary sizes.
+#| tbl-cap: "Summary of participant vocabulary sizes.
+vocabulary sizes are expressed as percentage points, and summarised as the mean (*M*) and the standard deviation (*SD*).
 Total: proportion of words in both languages marked as *Understands*.
@@
 TE: proportion of translation equivalents for which *both* words have been marked as *Understands*."
+#| eval: false
 vocabulary |> 
@@
 	cols_hide(lp) |> 
-	tab_spanner("Total ", matches("total")) |> 
-	tab_spanner("L1", matches("l1")) |> 
-	tab_spanner("L2", matches("l2")) |> 
-	tab_spanner("Conceptual", matches("concept")) |> 
-	tab_spanner("TE", matches("te_")) |> 
-	tab_spanner("Vocabulary size (%)", matches("prop_")) |> 
-	cols_merge_uncert(total_prop_mean, total_prop_sd) |> 
-	cols_merge_uncert(l1_prop_mean, l1_prop_sd) |> 
-	cols_merge_uncert(l2_prop_mean, l2_prop_sd) |> 
-	cols_merge_uncert(concept_prop_mean, concept_prop_sd) |> 
-	cols_merge_uncert(te_prop_mean, te_prop_sd) |> 
+	tab_spanner("Vocabulary size ", matches("prop")) |> 
+	cols_merge(c(total_prop_mean, total_prop_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(l1_prop_mean, l1_prop_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(l2_prop_mean, l2_prop_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(concept_prop_mean, concept_prop_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(te_prop_mean, te_prop_sd),
+			   pattern = "{1} ({2})") |> 
 	fmt_number(is.numeric,
+			   decimals = 1,
+			   scale_by = 100,
 			   drop_trailing_zeros = FALSE) |>
-	cols_label(total_prop_mean = "Mean (SD)",
-			   l1_prop_mean = "Mean (SD)",
-			   l2_prop_mean = "Mean (SD)",
-			   concept_prop_mean = "Mean (SD)",
-			   te_prop_mean = "Mean (SD)") |> 
+	cols_label(total_prop_mean = "Total",
+			   l1_prop_mean = "L1",
+			   l2_prop_mean = "L2",
+			   concept_prop_mean = "Concept",
+			   te_prop_mean = "TE") |> 
 	tab_stub_indent(rows = everything(),
@@
 		      is_animate_target_min,
-		      is_animate_target_max)) |> 
+		      is_animate_target_max),
+		   -matches("min"), -matches("max")) |> 
 	gt(groupname_col = "test_language",
 	   rowname_col = "list") |> 
-	tab_spanner("Prevalence (%)", matches("familiarity")) |> 
-	tab_spanner("Frequency (Zipf)", matches("freq")) |>
-	tab_spanner("Animacy (%)", matches("animate")) |> 
-	tab_spanner("Duration (s)", matches("duration")) |> 
-	fmt_number(is.numeric) |> 
-	cols_merge_range(familiarity_target_min, familiarity_target_max) |> 
-	cols_merge_range(freq_target_min, freq_target_max) |> 
-	cols_merge_range(duration_min, duration_max) |>
-	cols_merge_uncert(freq_target_mean, freq_target_sd) |> 
-	cols_merge_uncert(familiarity_target_mean, familiarity_target_sd) |> 
-	cols_merge_uncert(duration_mean, duration_sd) |> 
+	fmt_number(is.numeric,
+			   decimals = 1) |> 
+	fmt_number(matches("familiarity|animate"),
+			   scale_by = 100,
+			   decimals = 1) |> 
+	cols_merge(c(freq_target_mean, freq_target_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(familiarity_target_mean, familiarity_target_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(duration_mean, duration_sd),
+			   pattern = "{1} ({2})") |> 
 	cols_label(trial_type = "",
-			   familiarity_target_mean = "Mean ± SD",
-			   # familiarity_target_sd = "SD",
-			   familiarity_target_min = "Range",
-			   freq_target_mean = "Mean ± SD",
-			   # freq_target_sd = "SD",
-			   freq_target_min = "Range",
-			   is_animate_target_mean = "",
-			   duration_mean = "Mean ± SD",
-			   # duration_sd = "SD",
-			   duration_min = "Range") 
+			   familiarity_target_mean = "Prevalence (%)",
+			   freq_target_mean = "Frequency",
+			   is_animate_target_mean = "Animacy (%)",
+			   duration_mean = "Duration (s)") 
 ```
@@
 # Results
+
+We know present the results under four different trial-level inclusion criteria In Analysis 1, the child is required to understand the prime *and* the target words, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
+In Analysis 2, the child is required to understand the target word, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
+In Analysis 3, the child is not required to understand any word, but is still required to fixate both target and distractor for at last 50 ms each during the target-distractor phase.
+In Analysis 4, the child is not required to understand any word, nor to fixate at both target and distractor.
+
+For reference:
+
+* [@floccia2020translation] requires participants to know prime and target, but not to look at target *and* distractor (looking at at least one of them is enough).
+
+The fact that in some time course analyses participants seem to be looking predominantly towards one of the objects (despite the target and distractor pictures having been presented less than 300 ms before) is a common finding in previous studies using preferential looking procedures [e.g., @floccia2020translation].
+
+```{r tbl-multi-trials}
+tibble::lst(data_time_related,
+			data_time_related_oxf,
+			data_time_related_vtarget,
+			data_time_related_vtarget_oxf,
+			data_time_related_vnone,
+			data_time_related_vnone_oxf,
+			data_time_related_noeach,
+			data_time_related_noeach_oxf,
+			data_time_related_vnoeach,
+			data_time_related_vnoeach_oxf) |> 
+	bind_rows(.id = "analysis") |>
+	mutate(analysis_lab = case_when(
+		analysis=="data_time_related" ~ "Analysis 1",
+		grepl("_vtarget", analysis) ~ "Analysis 2",
+		grepl("_vnone", analysis) ~ "Analysis 3",
+		grepl("_noeach", analysis) ~ "Analysis 4",
+		grepl("_vnoeach", analysis) ~ "Analysis 5",
+		.default = "Analysis 1"
+	),
+	lp = case_when(grepl("_oxf", analysis) ~ "Monolingual (Oxford)", 
+				   lp=="Bilingual" ~ "Bilingual (Barcelona)",
+				   .default = "Monolingual (Barcelona)"),
+	lp = factor(lp, 
+				levels = c("Monolingual (Oxford)",
+						   "Monolingual (Barcelona)",
+						   "Bilingual (Barcelona)")),
+	condition = factor(condition, levels = c("Related", "Unrelated"))) |> 
+	distinct(analysis, analysis_lab, lp, condition, .ntrials) |> 
+	summarise(.ntrials = sum(.ntrials),
+			  .by = c(lp, analysis_lab, condition)) |> 
+	pivot_wider(names_from = c(lp, condition),
+				values_from = .ntrials,
+				names_repair = janitor::make_clean_names) |> 
+	relocate(matches("oxford"), matches("barcelona")) |> 
+	gt(rowname_col = "analysis_lab") |> 
+	tab_spanner("Monolingual", matches("monolingual")) |> 
+	tab_spanner("Bilingual", matches("bilingual")) |> 
+	tab_spanner("Barcelona", matches("barcelona")) |> 
+	tab_spanner("Oxford", matches("oxford")) |>
+
+	cols_label(monolingual_oxford_related = "Related",
+			   monolingual_oxford_unrelated = "Unrelated",
+			   monolingual_barcelona_related = "Related",
+			   monolingual_barcelona_unrelated = "Unrelated",
+			   bilingual_barcelona_related = "Related",
+			   bilingual_barcelona_unrelated = "Unrelated")
+
+```
+
+```{r fig-related-summary}
+#| label: fig-related-summary
+#| fig-height: 6.5
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+tibble::lst(data_time_related,
+			data_time_related_oxf,
+			data_time_related_vtarget,
+			data_time_related_vtarget_oxf,
+			data_time_related_vnone,
+			data_time_related_vnone_oxf,
+			data_time_related_noeach,
+			data_time_related_noeach_oxf,
+			data_time_related_vnoeach,
+			data_time_related_vnoeach_oxf) |> 
+	bind_rows(.id = "analysis") |>
+	mutate(analysis_lab = case_when(
+		analysis=="data_time_related" ~ "Analysis 1",
+		grepl("_vtarget", analysis) ~ "Analysis 2",
+		grepl("_vnone", analysis) ~ "Analysis 3",
+		grepl("_noeach", analysis) ~ "Analysis 4",
+		grepl("_vnoeach", analysis) ~ "Analysis 5",
+		.default = "Analysis 1"
+	),
+	lp = ifelse(grepl("_oxf", analysis), 
+				"Monolingual (English)", 
+				as.character(lp)),
+	lp = factor(lp, levels = c("Monolingual (English)",
+							   "Monolingual",
+							   "Bilingual"))) |> 
+	# summarise(.elog_mean = mean(.elog),
+	# 		  n = n(),
+	# 		  .elog_std = sd(.elog),
+	# 		  .by = c(condition, timebin, analysis, lp)) |>
+	# mutate(.elog_se = .elog_std/n) |> 
+	ggplot(aes(timebin, .elog,
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_grid(analysis_lab~lp) +
+	geom_hline(yintercept = 0.5, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	geom_smooth(method = lm, 
+				se = FALSE, 
+				formula = y ~ splines::bs(x, 4)) +
+	# geom_errorbar(aes(ymin = .elog_mean - .elog_se*1.96, 
+	# 				  ymax = .elog_mean + .elog_se*1.96),
+	# 			  width = 0.25,
+	# 			  linewidth = 3/4) + 
+	# geom_line(size = 3/4) + 
+	stat_summary(fun = mean, geom = "point") +
+	stat_summary(fun.data = mean_se,
+				 geom = "errorbar",
+				 width = 0.25) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) +
+	# scale_shape_manual(values = c(1, 2)) +
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank(),
+		  panel.border = element_rect(fill = NA),
+		  axis.line = element_line(),
+		  legend.position = "top") 
+```
+
+```{r fig-cognate-summary}
+#| label: fig-cognate-summary
+#| fig-height: 6.5
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+tibble::lst(data_time_cognate,
+			data_time_cognate_oxf,
+			data_time_cognate_vtarget,
+			data_time_cognate_vtarget_oxf,
+			data_time_cognate_vnone,
+			data_time_cognate_vnone_oxf,
+			data_time_cognate_noeach,
+			data_time_cognate_noeach_oxf,
+			data_time_cognate_vnoeach,
+			data_time_cognate_vnoeach_oxf) |> 
+	bind_rows(.id = "analysis") |>
+	mutate(analysis_lab = case_when(
+		analysis=="data_time_cognate" ~ "Analysis 1",
+		grepl("_vtarget", analysis) ~ "Analysis 2",
+		grepl("_vnone", analysis) ~ "Analysis 3",
+		grepl("_noeach", analysis) ~ "Analysis 4",
+		grepl("_vnoeach", analysis) ~ "Analysis 5",
+		.default = "Analysis 1"
+	),
+	lp = ifelse(grepl("_oxf", analysis), 
+				"Monolingual (English)", 
+				as.character(lp)),
+	lp = factor(lp, levels = c("Monolingual (English)",
+							   "Monolingual",
+							   "Bilingual"))) |> 
+	# summarise(.elog_mean = mean(.elog),
+	# 		  n = n(),
+	# 		  .elog_std = sd(.elog),
+	# 		  .by = c(condition, timebin, analysis, lp)) |>
+	# mutate(.elog_se = .elog_std/n) |> 
+	ggplot(aes(timebin, .elog,
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_grid(analysis_lab~lp) +
+	geom_hline(yintercept = 0.5, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	geom_smooth(method = lm, 
+				se = FALSE, 
+				formula = y ~ splines::bs(x, 4)) +
+	# geom_errorbar(aes(ymin = .elog_mean - .elog_se*1.96, 
+	# 				  ymax = .elog_mean + .elog_se*1.96),
+	# 			  width = 0.25,
+	# 			  linewidth = 3/4) + 
+	# geom_line(size = 3/4) + 
+	stat_summary(fun = mean, geom = "point") +
+	stat_summary(fun.data = mean_se,
+				 geom = "errorbar",
+				 width = 0.25) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) +
+	# scale_shape_manual(values = c(1, 2)) +
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank(),
+		  panel.border = element_rect(fill = NA),
+		  axis.line = element_line(),
+		  legend.position = "top")
+```
 
@@
 			   pattern = "{1} ({2})") |> 
-	cols_merge_uncert(mean_cognate, sd_cognate) |> 
-	cols_merge_uncert(mean_noncognate, sd_noncognate) |> 
-	cols_merge_uncert(mean_unrelated, sd_unrelated) |> 
+	cols_merge(c(mean_cognate, sd_cognate),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(mean_noncognate, sd_noncognate),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(mean_unrelated, sd_unrelated),
+			   pattern = "{1} ({2})") |>
 	tab_spanner("Cognate trials", ends_with("_cognate")) |>
@@
 	tab_spanner("Related trials", matches("cognate")) |>
-	fmt_number(matches("mean|sd")) |> 
+	fmt_number(matches("mean|sd"), decimals = 1) |> 
 	fmt_integer(matches("sum"), sep_mark = ",") |> 
@@
 
-A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related[2, 1], 3)`, *SE* = `r round(model_loo_related[2, 2], 3)`).
-Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related[3, 1], 3)`, *SE* = `r round(model_loo_related[3, 2], 3)`).
-This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+<!--
+-->
 
@@
 					  .nsamples = 1) |>
-	add_epred_draws(model_fits_related[[4]],
+	add_epred_draws(model_fits_related[[1]],
 					ndraws = NULL,
@@
 
-A model including the *Cognateness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Cognateness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate[2, 1], 3)`, *SE* = `r round(model_loo_cognate[2, 2], 3)`).
-Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate[3, 1], 3)`, *SE* = `r round(model_loo_cognate[3, 2], 3)`).
-This indicates that including the *Cognateness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+<!--
+-->
 
@@
 					  .nsamples = 1) |>
-	add_epred_draws(model_fits_cognate[[4]],
+	add_epred_draws(model_fits_cognate[[1]],
 					ndraws = NULL,
@@
 
-A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related_vtarget[2, 1], 3)`, *SE* = `r round(model_loo_related_vtarget[2, 2], 3)`).
-Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related_vtarget[3, 1], 3)`, *SE* = `r round(model_loo_related_vtarget[3, 2], 3)`).
-This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+<!--
+-->
 
@@
 					  .nsamples = 1) |>
-	add_epred_draws(model_fits_related_vtarget[[4]],
+	add_epred_draws(model_fits_related_vtarget[[1]],
 					ndraws = NULL,
@@
 
-A model including the *Cognateness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Cognateness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate_vtarget[2, 1], 3)`, *SE* = `r round(model_loo_cognate_vtarget[2, 2], 3)`).
-Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate_vtarget[3, 1], 3)`, *SE* = `r round(model_loo_cognate_vtarget[3, 2], 3)`).
-This indicates that including the *Cognateness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+<!--
+-->
 
@@
 					  .nsamples = 1) |>
-	add_epred_draws(model_fits_cognate_vtarget[[4]],
+	add_epred_draws(model_fits_cognate_vtarget[[1]],
 					ndraws = NULL,
@@
 
-A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related_vnone[2, 1], 3)`, *SE* = `r round(model_loo_related_vnone[2, 2], 3)`).
-Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related_vnone[3, 1], 3)`, *SE* = `r round(model_loo_related_vnone[3, 2], 3)`).
-This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+<!--
+-->
 
@@
 					  .nsamples = 1) |>
-	add_epred_draws(model_fits_related_vnone[[4]],
+	add_epred_draws(model_fits_related_vnone[[1]],
 					ndraws = NULL,
@@
 
-A model including the *Cognateness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Cognateness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate_vnone[2, 1], 3)`, *SE* = `r round(model_loo_cognate_vnone[2, 2], 3)`).
-Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_cognate_vnone[3, 1], 3)`, *SE* = `r round(model_loo_cognate_vnone[3, 2], 3)`).
-This indicates that including the *Cognateness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+<!--
+-->
 
@@
 					  .nsamples = 1) |>
-	add_epred_draws(model_fits_cognate_vnone[[4]],
+	add_epred_draws(model_fits_cognate_vnone[[1]],
 					ndraws = NULL,
@@
 
-A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related_noeach[2, 1], 3)`, *SE* = `r round(model_loo_related_noeach[2, 2], 3)`).
-Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related_noeach[3, 1], 3)`, *SE* = `r round(model_loo_related[3, 2], 3)`).
-This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.
+<!--
+-->
 
@@
 					  .nsamples = 1) |>
-	add_epred_draws(model_fits_related_noeach[[4]],
+	add_epred_draws(model_fits_related_noeach[[1]],
 					ndraws = NULL,
@@
 					  .nsamples = 1) |>
-	add_epred_draws(model_fits_cognate_noeach[[4]],
+	add_epred_draws(model_fits_cognate_noeach[[1]],
 					ndraws = NULL,
@@
 
+## Analysis 5
+
+Participants need to know the prime or target words, and do not need to look to both pictures.
+
+```{r dataset-vnoeach}
+n_trials <- nrow(attrition_trials_vnoeach)
+n_trials_valid <- inner_join(attrition_participants_vnoeach,
+							 attrition_trials_vnoeach) |> 
+	filter(is_valid_participant) |> 
+	pull(is_valid_trial) |> 
+	sum()
+n_participants_valid <- sum(attrition_participants_vnoeach$is_valid_participant)
+n_exc_prime <- sum(!attrition_trials_vnoeach$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition_trials_vnoeach$is_valid_gaze_test)
+n_exc_test_each <- sum(!attrition_trials_vnoeach$is_valid_gaze_test_each)
+n_exc_vocab <- sum(!attrition_trials_vnoeach$is_valid_vocab)
+n_exc_cognate <- sum(!attrition_participants_vnoeach$is_valid_cognate)
+n_exc_noncognate <- sum(!attrition_participants_vnoeach$is_valid_noncognate)
+n_exc_unrelated <- sum(!attrition_participants_vnoeach$is_valid_unrelated)
+
+n_longitudinal <- attrition_participants_vnoeach |>
+	filter(is_valid_participant) |>
+	count(id, name = "times") |> 
+	count(times)
+```
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
+We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
+The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+@tbl-attrition-trials shows a detailed description of the trial attrition.
+
+```{r tbl-attrition-trials-vnoeach}
+#| label: tbl-attrition-trials-vnoeach
+#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
+attrition_trials_vnoeach |> 
+	filter(id %in% attrition_participants_vnoeach$id[attrition_participants_vnoeach$is_valid_participant]) |> 
+	left_join(select(participants, filename, id, age_group),
+			  by = join_by(filename, id, age_group)) |> 
+	summarise(n_valid = sum(is_valid_trial),
+			  n_total = n(),
+			  .by = c(id, age_group, trial_type)) |> 
+	summarise(across(n_valid, lst(sum, mean, sd),
+					 .names = "{.fn}"),
+			  n_total = sum(n_total),
+			  .by = c(age_group, trial_type)) |> 
+	mutate(n_excluded = n_total-sum) |> 
+	select(-c(n_total)) |> 
+	pivot_wider(names_from = trial_type,
+				values_from = c(sum:sd, n_excluded),
+				names_repair = janitor::make_clean_names) |> 
+	rename_with(\(x) gsub("non_cognate", 
+						  "noncognate",
+						  x)) |> 
+	arrange(age_group) |> 
+	relocate(age_group,
+			 matches("_cognate"),
+			 matches("noncognate")) |> 
+	gt(rowname_col = "age_group") |> 
+	grand_summary_rows(columns = matches("mean_"),
+					   fns = lst(Mean ~ mean(.)),
+					   fmt = ~fmt_number(.)) |>
+	grand_summary_rows(columns = matches("sum_"),
+					   fns = lst(Sum ~ sum(.)),
+					   fmt = ~fmt_integer(.)) |>
+	cols_merge(c(sum_cognate, n_excluded_cognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(sum_unrelated, n_excluded_unrelated),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(mean_cognate, sd_cognate),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(mean_noncognate, sd_noncognate),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(mean_unrelated, sd_unrelated),
+			   pattern = "{1} ({2})") |>
+	tab_spanner("Cognate trials", ends_with("_cognate")) |>
+	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
+	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
+	tab_spanner("Related trials", matches("cognate")) |>
+	fmt_number(matches("mean|sd"), decimals = 1) |> 
+	fmt_integer(matches("sum"), sep_mark = ",") |> 
+	cols_label(sum_cognate = "N",
+			   sum_noncognate = "N",
+			   sum_unrelated = "N",
+			   mean_cognate = "Mean",
+			   mean_noncognate = "Mean",
+			   mean_unrelated = "Mean")
+```
+
+### Phonological priming: Related vs. Unrelated
+
+<!--
+-->
+
+```{r fig-related-vnoeach}
+#| label: fig-related-vnoeach
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_related_vnoeach$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_related_vnoeach$age),
+					  lp = levels(data_time_related_vnoeach$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_related_vnoeach[[1]],
+					ndraws = NULL,
+					re_formula = NA, 
+					value = ".value") |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .value,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = related - unrelated)
+
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
+# 
+# clusters <- rle(diff(diff_rect$is_cluster))
+# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
+# 
+# diff_rect <- diff_rect |> 
+# 	arrange(lp, timebin)
+# 
+# diff_rect <- 
+# 	cluster_number = 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = c(lp, is_cluster)) |> 
+# 	filter(is_cluster)
+
+# diff_obs <- data_time_related |>
+# 	pivot_wider(names_from = condition, 
+# 				values_from = elog,
+# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
+
+data_time_related_vnoeach |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition,
+			   linetype = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .value),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .value,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 1/2, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -Inf,
+	# 		  	ymax = Inf),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	# geom_point(data = diff_obs) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
+### Cognate priming: Cognate vs. Non-cognate
+
+<!--
+-->
+
+```{r fig-cognate-vnoeach}
+#| label: fig-cognate-vnoeach
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+epreds <- expand_grid(condition = levels(data_time_cognate_vnoeach$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data_time_cognate_vnoeach$age),
+					  lp = levels(data_time_cognate_vnoeach$lp),
+					  .nsamples = 1) |>
+	add_epred_draws(model_fits_cognate_vnoeach[[1]],
+					ndraws = NULL,
+					re_formula = NA) |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+
+epreds_diff <- epreds |> 
+	pivot_wider(names_from = condition,
+				values_from = .epred,
+				id_cols = c(timebin, age, lp, .draw),
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff = cognate - non_cognate) 
+# 
+# diff_rect <- epreds_diff |> 
+# 	mean_qi(diff) |> 
+# 	filter(.lower > 0 | .upper < 0) |> 
+# 	summarise(xmin = min(timebin),
+# 			  xmax = max(timebin),
+# 			  .by = lp)
+
+data_time_cognate_vnoeach |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(id, timebin, lp, condition, age)) |> 
+	ggplot(aes(timebin, .prop, 
+			   colour = condition,
+			   fill = condition,
+			   shape = condition)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -1.5,
+	# 		  	ymax = 1.5),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	# geom_line(data = epreds,
+	# 		  aes(y = .epred,
+# 		  	group = interaction(condition, .draw)),
+# 		  linetype = "solid",
+# 		  alpha = 0.1,
+# 		  linewidth = 3/4) +
+stat_summary(data = epreds,
+			 aes(y = .epred),
+			 fun.data = \(x) mean_qi(x, .width = 0.95),
+			 geom = "ribbon",
+			 alpha = 0.5,
+			 linewidth = 0) +
+	stat_summary(data = epreds,
+				 aes(y = .epred,
+				 	linetype = condition),
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0.5, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 colour = "black",
+				 size = 2.5,
+				 stroke = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 linetype = "Prime type",
+		 shape = "Prime type") +
+	theme(legend.title = element_blank(),
+		  axis.title.x = element_blank()) +
+
+	epreds_diff |> 
+	ggplot(aes(timebin, diff)) +
+	facet_wrap(~lp) +
+	# geom_rect(data = diff_rect,
+	# 		  aes(xmin = xmin,
+	# 		  	xmax = xmax,
+	# 		  	ymin = -3/4,
+	# 		  	ymax = 3/4),
+	# 		  colour = NA,
+	# 		  fill = "orange",
+	# 		  alpha = 1/2,
+	# 		  inherit.aes = FALSE) +
+	stat_lineribbon(.width = 0.95,
+					linewidth = 0,
+					fill = "grey") +
+	stat_summary(data = epreds_diff,
+				 fun = "mean",
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0, 
+			   linewidth = 1/2,
+			   colour = "black",
+			   linetype = "dotted") +
+	labs(x = "Time (ms)",
+		 y = "P(Target looking)",
+		 fill = "CrI") +
+	theme(strip.text = element_blank(),
+		  legend.position = "none") +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") +
+	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
+	scale_shape_manual(values = c(1, 2)) &
+	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+											big.mark = ",")) &
+	theme(panel.grid = element_blank(),
+		  legend.position = "top") 
+```
+
 # Discussion
 
+# References
+
+{{< pagebreak >}}
+
 # Appendix
+
+## Appendix A: imputing voabulary size scores
+
+```{r fig-vocabulary-imputation}
+vocabulary_tmp <- vocabulary |> 
+	left_join(select(participants, child_id = id_db, age, age_group, filename),
+			  by = join_by(filename)) |> 
+	relocate(child_id) |> 
+	select(-filename) |> 
+	filter(is_imputed) |> 
+	mutate(child_id = as.character(child_id))
+
+bvq_data$vocabulary |> 
+	inner_join(distinct(bvq_data$logs, id, age_group, age),
+			   by = join_by(id, age_group)) |> 
+	rename(child_id = id) |> 
+	mutate(is_imputed = FALSE) |> 
+	bind_rows(vocabulary_tmp) |> 
+	pivot_longer(ends_with("_prop"),
+				 names_to = "measure",
+				 values_to = "prop") |> 
+	drop_na(prop) |> 
+	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"),
+		   measure = factor(measure,
+		   				 levels = c("total_prop",
+		   				 		   "l1_prop",
+		   				 		   "l2_prop",
+		   				 		   "concept_prop",
+		   				 		   "te_prop"),
+		   				 labels = c("Total",
+		   				 		   "L1",
+		   				 		   "L2",
+		   				 		   "Conceptual",
+		   				 		   "TE"))) |> 
+	ggplot(aes(age, prop, 
+			   colour = is_imputed,
+			   fill = is_imputed)) +
+	facet_wrap(~measure) +
+	geom_point(alpha = 1/4, size = 1) +
+	geom_smooth(method = "glm", 
+				formula = "y ~ x",
+				method.args = list(family = "binomial"), 
+				# se = FALSE,
+				size = 1) +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size",
+		 fill = "Imputed",
+		 colour = "Imputed") +
+	theme(legend.position = c(1, 0),
+		  legend.justification = c(1, 0),
+		  legend.title = element_blank())
+
+```
+
+{{< pagebreak >}}
+
+## Appendix B: distribution of prime and target looking times
+
+```{r fig-dist-prime}
+#| label: fig-dist-prime
+#| fig-height: 4
+#| fig-width: 8
+looking_times |> 
+	mutate(prime_time = cut(prime_time, 
+							seq(0, 1.5, 0.1),
+							labels = FALSE,
+							include.lowest = TRUE)) |> 
+	add_count(lp, age_group, name = "n_total") |> 
+	count(lp, age_group, prime_time, n_total) |> 
+	mutate(n = n / n_total) |> 
+	ggplot(aes(prime_time, n)) +
+	facet_grid(lp~age_group) +
+	annotate(geom = "rect",
+			 fill = "orange",
+			 ymin = -Inf,
+			 ymax = Inf,
+			 xmin = 0,
+			 xmax = 0.75*10,
+			 alpha = 1/3,
+			 colour = NA) +
+	# annotate(label = "Excluded trials",
+	# 		 geom = "text",
+	# 		  x = (0.75/2)*10,
+	# 		  y = 1)
+	geom_col(fill = "black") +
+	labs(x = "Prime looking time (s)",
+		 y = "Proportion of trials") +
+	scale_x_continuous(labels = \(x) x/10) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"))
+```
+
+```{r fig-dist-target}
+#| label: fig-dist-target
+#| fig-height: 4
+#| fig-width: 8
+looking_times |> 
+	mutate(target_time = cut(target_time, 
+							 seq(0, 2, 0.1),
+							 labels = FALSE,
+							 include.lowest = TRUE)) |> 
+	add_count(lp, age_group, name = "n_total") |> 
+	count(lp, age_group, target_time, n_total) |> 
+	mutate(n = n / n_total) |> 
+	ggplot(aes(target_time, n)) +
+	facet_grid(lp~age_group) +
+	# annotate(label = "Excluded trials",
+	# 		 geom = "text",
+	# 		  x = (0.75/2)*10,
+	# 		  y = 1)
+	geom_col(fill = "black") +
+	labs(x = "Targets looking time (s)",
+		 y = "Proportion of trials") +
+	scale_x_continuous(labels = \(x) x/10) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"))
+```
+
+{{< pagebreak >}}
+
+## Appendix C: prime and test looking times
+
+```{r fig-looking-times}
+#| label: fig-looking-times
+#| fig-height: 8
+#| fig-width: 8
+#| fig-cap: "Looking time (s) to the prime and target AOI against audio duration. In longer audios, participants are expected to look longer to the prime and target picture."
+
+looking_times |>
+	left_join(select(attrition_trials, 
+					 filename, trial, is_valid_trial),
+			  by = join_by(filename, trial)) |>
+	filter(is_valid_trial) |> 
+	ggplot(aes(duration,
+			   prime_time,
+			   colour = trial_type, 
+			   fill = trial_type,
+			   shape = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_point(alpha = 0.5, 
+			   size = 1) +
+	geom_smooth(method = "lm") +
+	theme(axis.title.x = element_blank()) +
+
+	looking_times |>
+	left_join(select(attrition_trials, 
+					 filename, trial, is_valid_trial),
+			  by = join_by(filename, trial)) |>
+	filter(is_valid_trial) |> 
+	ggplot(aes(duration,
+			   target_time,
+			   colour = trial_type, 
+			   fill = trial_type,
+			   shape = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_point(alpha = 0.5,
+			   size = 1) +
+	geom_smooth(method = "lm",
+				formula = "y ~ x") +
+	plot_layout(ncol = 1, guides = "collect") &
+	plot_annotation(tag_levels = "A") &
+	labs(x = "Audio duration (s)",
+		 y = "Looking time (1.0-2.0 seconds)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 shape = "Prime type") 
+```

### 2023-10-19 manuscript/manuscript.qmd

@@
 # prepare data
-attrition_participants <- attrition_participants |> 
-	left_join(select(participants, id, age_group, lp, filename))
-
-attrition_trials <- left_join(attrition_trials, 
-							  select(participants, id, age_group, lp, filename))
-
-participants <- participants |> 
-	left_join(distinct(attrition_participants,
-					   filename, is_valid_participant)) |> 
-	drop_na(id)
-
-attrition_participants_vtarget <- attrition_participants_vtarget |> 
-	left_join(select(participants, id, age_group, lp, filename))
-
-attrition_trials_vtarget <- attrition_trials_vtarget |> 
-	left_join(select(participants, id, age_group, lp, filename))
-
-attrition_participants_vnone <- attrition_participants_vnone |> 
-	left_join(select(participants, id, age_group, lp, filename))
-
-attrition_trials_vnone <- attrition_trials_vnone |> 
-	left_join(select(participants, id, age_group, lp, filename))
-
-attrition_participants_noeach <- attrition_participants_noeach |> 
-	left_join(select(participants, id, age_group, lp, filename))
-
-attrition_trials_noeach <- attrition_trials_noeach |> 
-	left_join(select(participants, id, age_group, lp, filename))
-
-attrition_participants_vnoeach <- attrition_participants_vnoeach |> 
-	left_join(select(participants, id, age_group, lp, filename))
-
-attrition_trials_vnoeach <- attrition_trials_vnoeach |> 
-	left_join(select(participants, id, age_group, lp, filename))
-
-```
-
-<!--
+attrition <- lst(participants,
+				 attrition_participants,
+				 attrition_trials) |> 
+	purrr::reduce(left_join, by = join_by(filename))
+
+attrition_vtarget <- lst(participants,
+						 attrition_participants_vtarget,
+						 attrition_trials_vtarget) |> 
+	purrr::reduce(left_join, by = join_by(filename))
+
+attrition_vnone <- lst(participants,
+					   attrition_participants_vnone,
+					   attrition_trials_vnone) |> 
+	purrr::reduce(left_join, by = join_by(filename))
+
+attrition_noeach <- lst(participants,
+						attrition_participants_noeach,
+						attrition_trials_noeach) |> 
+	purrr::reduce(left_join, by = join_by(filename))
+
+attrition_vnoeach <- lst(participants,
+						 attrition_participants_vnoeach,
+						 attrition_trials_vnoeach) |> 
+	purrr::reduce(left_join, by = join_by(filename))
+
+attrition_oxf <- lst(participants_oxf,
+					 attrition_participants_oxf,
+					 attrition_trials_oxf) |> 
+	purrr::reduce(left_join, by = join_by(id))
+
+attrition_vtarget_oxf <- lst(participants_oxf,
+							 attrition_participants_vtarget_oxf,
+							 attrition_trials_vtarget_oxf) |> 
+	purrr::reduce(left_join, by = join_by(id))
+
+attrition_vnone_oxf <- lst(participants_oxf,
+						   attrition_participants_vnone_oxf,
+						   attrition_trials_vnone_oxf) |> 
+	purrr::reduce(left_join, by = join_by(id))
+
+attrition_noeach_oxf <- lst(participants_oxf,
+							attrition_participants_noeach_oxf,
+							attrition_trials_noeach_oxf) |> 
+	purrr::reduce(left_join, by = join_by(id))
+
+attrition_vnoeach_oxf <- lst(participants_oxf,
+							 attrition_participants_vnoeach_oxf,
+							 attrition_trials_vnoeach_oxf) |> 
+	purrr::reduce(left_join, by = join_by(id))
+
+```
+
+# Introduction
+
+## The early lexicon
+
 The formation of a mental lexicon is a critical developmental achievement for infants_ learning words allows infants to retrieve socially relevant concepts from fairly arbitrary linguistic forms embedded in speech.
@@
 
+There is evidence of cascaded activation during lexical access.
+
+@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
+In each trial, the authors presented participants with four semantically and phonologically pictures.
+Four seconds after pictures onset, a word-form was auditorily presented.
+The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category.
+For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
+Then they would hear the carrier phrase "Look at the **bee**!".
+The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
+These results support a cascaded activation account of lexical access during the first stages of lexical development.
+
+Another important source of evidence in favour of a cascaded activation account comes from studies on implicit naming.
+@mani2010infant showed that 18 month-old infants implicitly generate the labels of name-known pictures presented in silence.
+In each trial, infants were presented with prime pictures presented in silence, and then with a target and a distractor picture, both presented side-by-side.
+Finally, the target picture's label was presented auditorily.
+The authors manipulated the phonological overlap between the prime label and the target label, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
+Prime and target-distractor pairs were semantically unrelated.
+Interestingly, infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
+This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
+In particular, the authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
+
+@mani2011phonological used the same paradigm in 24-months-old toddlers, and also found evidence of implicit naming, but in the opposite direction.
+After phonologically related primes, infants showed weaker target looking preference than after phonologically unrelated primes.
+These results interpreted these outcome as the result of the implicitly generated prime label interfering with the subsequent recognition of the (phonologically related) target word.
+The authors suggested that the shift from facilitation to interference from 18 to 24 months they found in both studies might be the result of a developmental shift in which 18-month-olds' lexicon is not yet organised based on phonological similarity, while 24-month-olds' is.
+This would lead to the former showing a pre-lexical facilitation effect in which such facilitation occurs via the activation of phonological segments, while the latter would show an interference effect due to lateral links between lexical representation having been established.
+Both studies by Mani and Plunkett provide evidence of implicit naming of name-known pictures by 18-month old toddlers and older, and that the resulting labels interact with the dynamics of recognition of subsequently presented word-forms.
+
+Evidence from cascaded activation in lexical access is also provided by bilinguals.
 The bilingual lexicon is language-non selective.
-
+There is strong evidence in support of bilinguals activating lexical representations from both languages during both speech production and comprehension.
+Previous studies on bilingual word production support a cascade account for lexical activation in which the phonology of non-selected lexical representations engages in excitatory or inhibitory dynamics in the lexical selection process.
+
+## Co-activation in adults
+
+How does language co-activation shape lexical development?
+Marian and Spivey (1999)
+Costa et al. (2000)
+
+## Evidence from co-activation though translation
 The role of cognates in lexical processing.
 
-How does language co-activation shape lexical development?
-
-Implicit naming as a paradigm to study cross-language activation. (Mani & Plunkett, 2010, 2011a).
+Another source of evidence are studies studies involving phonological priming of non-cognates through translation. [SEE REFERENCES FROM VON HOLZEN 2012]
+
+Using an adaptation of @mani2010infant's implicit naming paradigm, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
+The authors presented German-English bilinguals with 120 prime-target pairs.
+Primes were presented as familiar pictures in silence.
+After prime picture offset, target words were presented auditorily.
+Participants' N400 ERP components were recorded from target word onset.
+The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
+When prime and target were phonologically identical (*Affe*-*Affe*, German for *monkey*), or similar (*Fahne*-*Sahne*, German for *flag* and *ice-cream*, respectively) within L1, participants' showed a reduced N400 amplitude, compared to when prime and target were phonologically unrelated (*Messer*-*Seil*, German for *knife* and *rope*).
+Critically, a similar effect was found when prime and target were phonologically related through translation (*Rustsche*-*Kleid*, German for *slide* and *dress*).
+This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
+
+Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
+@duta2012erp presented name-known pictures in silence for one second.
+After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
+In some trials the auditory label corresponded to a canonical realisation of the word-form.
+In other trials, the word was mispronounced.
+Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
+A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
+This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
 
@@
 
+Evidence from cognates.
+
 - Since participants heard the auditory label in one of the languages, priming through translation might be compromised.
@@
 - Larger sample size.
--->
+
+Onset vs. offset overlap:
+
+- Wu and Thierry (2011): rhyme
 
@@
 n_sessions_age_group <- participants |> 
-	group_by(age_group) |> 
 	summarise(across(age, lst(mean, sd, min, max)),
 			  n = n(),
-			  .groups = "drop") |> 
+			  .by = c(age_group)) |> 
 	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
@@
 @tbl-participants-lp shows a detailed description of the linguistic profile of our sample.
-
-```{r}
-#| label: tbl-participants-lp
-#| tbl-cap: "Description of language profile of test participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
-participants_oxf |> 
-	left_join(attrition_participants_oxf,
-			  by = join_by(id)) |> 
-	mutate(lp = "Monolingual (English)",
-		   id = as.character(id)) |> 
-	bind_rows(mutate(participants, id = as.character(id))) |> 
-	filter(is_valid_participant) |> 
-	select(id, age_group, age, lp, test_language) |> 
-	add_count(lp, 
-			  name = "n_lp") |> 
-	add_count(age_group, 
-			  name = "n_age_group") |> 
-	add_count(age_group,
-			  test_language,
-			  name = "n_age_test") |> 
-	mutate(lp = factor(lp, levels = rev(unique(lp))))  |> 
-	summarise(across(c(age), lst(mean, sd)),
-			  n = n(),
-			  .by = c(age_group, lp, test_language)) |> 
-	pivot_wider(id_cols = c(test_language, lp),
-				names_from = c(age_group),
-				values_from = c(matches("doe"), age_mean, age_sd, n),
-				names_repair = janitor::make_clean_names) |> 
-	relocate(lp, test_language,
-			 matches("21"),
-			 matches("25"),
-			 matches("30"),
-	) |> 
-	arrange(lp, test_language) |> 
-	gt(rowname_col = "test_language", 
-	   groupname_col = "lp", 
-	   row_group.sep = ": ") |> 
-	tab_spanner(md("21 months"), matches("21")) |> 
-	tab_spanner(md("25 months"), matches("25")) |>
-	tab_spanner(md("30 months"), matches("30")) |> 
-	fmt_number(matches("age"), decimals = 1) |>
-	cols_merge(c(age_mean_21_months, age_sd_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_25_months, age_sd_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_30_months, age_sd_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_label(n_21_months = md("*N*"),
-			   n_25_months = md("*N*"),
-			   n_30_months = md("*N*"),
-			   age_mean_21_months = "Age (months)",
-			   age_mean_25_months = "Age (months)",
-			   age_mean_30_months = "Age (months)") |> 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) |> 
-	tab_style(cell_text(size = "medium"),
-			  list(cells_body(),
-			  	 cells_stub()))
-```
 
@@
 
+![Experimental task design with examples in Catalan.
+In each trial, the prime image is presented in silence for 3,000 ms.
+The the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
+In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
+In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
+In unrelated trials (*n* = 32), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){fig-align="center"}
+
 Each trial started with the presentation of an attention getter for 3,000 milliseconds.
@@
 
-We know present the results under four different trial-level inclusion criteria In Analysis 1, the child is required to understand the prime *and* the target words, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
+We know present the results under four different trial-level inclusion criteria.
+In Analysis 1, the child is required to understand the prime *and* the target words, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
 In Analysis 2, the child is required to understand the target word, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
@@
 In Analysis 4, the child is not required to understand any word, nor to fixate at both target and distractor.
-
-For reference:
-
-* [@floccia2020translation] requires participants to know prime and target, but not to look at target *and* distractor (looking at at least one of them is enough).
+In Analysis 5, the child is required to understand the prime *and* target words, but is not required to look at both target *and* distractor in the test phase.
+
+::: {.callout-note}
+
+@floccia2020translation required participants to know prime and target, but not to look at target *and* distractor (looking at at least one of them is enough).
+@mani2010infants did not require participants to know either word, but required infants to *not* look exclusively to the target or the distractor throughout the trial, and in an alternative analysis, to *not* look exclusively to the distractor.
 
@@
 
+:::
+
 ```{r tbl-multi-trials}
+#| tbl-cap: "Number of valid trials by age group, profile, and attrition criteria."
 tibble::lst(data_time_related,
@@
 				names_repair = janitor::make_clean_names) |> 
-	relocate(matches("oxford"), matches("barcelona")) |> 
+	relocate(analysis_lab,
+			 monolingual_barcelona_related,
+			 monolingual_barcelona_unrelated,
+			 bilingual_barcelona_related,
+			 bilingual_barcelona_unrelated,
+			 monolingual_oxford_related,
+			 monolingual_oxford_unrelated) |> 
 	gt(rowname_col = "analysis_lab") |> 
+	tab_spanner("Bilingual", matches("bilingual")) |>
+
 	tab_spanner("Monolingual", matches("monolingual")) |> 
-	tab_spanner("Bilingual", matches("bilingual")) |> 
 	tab_spanner("Barcelona", matches("barcelona")) |> 
@@
 #| fig-cap: "Marginal posterior predictions of the GAMMs.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Lines and inetervals indicate the mean and 95% credible intervals of the posterior probability of target looking across the time course of the trial.
 Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+In Analysis 1, the child is required to understand the prime *and* the target words, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
+In Analysis 2, the child is required to understand the target word, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
+In Analysis 3, the child is not required to understand any word, but is still required to fixate both target and distractor for at last 50 ms each during the target-distractor phase.
+In Analysis 4, the child is not required to understand any word, nor to fixate at both target and distractor.
+In Analysis 5, the child is required to understand the prime *and* target words, but is not required to look at both target *and* distractor in the test phase."
 tibble::lst(data_time_cognate,
@@
 
+::: {.callout-note}
+
 Participants must know **prime** *and* **target** words, and must look at least 10 ms to each target and distractor.
+
+:::
 
@@
 
+```{r tbl-participants-lp}
+#| label: tbl-participants-lp
+#| tbl-cap: "Participant details for Analysis 1.
+Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
+Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
+participants_tmp <- participants |> 
+	left_join(attrition_participants, by = join_by(filename)) |> 
+	mutate(id = as.character(id))
+
+participants_oxf_tmp <- participants_oxf |> 
+	inner_join(attrition_participants_oxf,
+			   by = join_by(id)) |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id))
+
+bind_rows(participants_tmp, participants_oxf_tmp) |> 
+	add_count(lp, 
+			  name = "n_lp") |> 
+	add_count(age_group, 
+			  name = "n_age_group") |> 
+	add_count(age_group,
+			  test_language,
+			  name = "n_age_test") |> 
+	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
+	summarise(across(c(age), lst(mean, sd)),
+			  n_inc = sum(is_valid_participant),
+			  n_exc = sum(!is_valid_participant),
+			  .by = c(age_group, lp, test_language)) |> 
+	pivot_wider(id_cols = c(test_language, lp),
+				names_from = c(age_group),
+				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
+				names_repair = janitor::make_clean_names) |>
+	relocate(lp, test_language, 
+			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
+			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
+			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
+	arrange(lp, test_language) |> 
+	gt(rowname_col = "test_language", 
+	   groupname_col = "lp", 
+	   row_group.sep = ": ") |> 
+	tab_spanner(md("21 months"), matches("21")) |> 
+	tab_spanner(md("25 months"), matches("25")) |>
+	tab_spanner(md("30 months"), matches("30")) |> 
+	fmt_number(matches("age"), decimals = 1) |>
+	cols_merge(c(n_inc_21_months, n_exc_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_25_months, n_exc_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_30_months, n_exc_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_21_months, age_sd_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_25_months, age_sd_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_30_months, age_sd_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_label(n_inc_21_months = md("*N*"),
+			   n_inc_25_months = md("*N*"),
+			   n_inc_30_months = md("*N*"),
+			   age_mean_21_months = "Age (months)",
+			   age_mean_25_months = "Age (months)",
+			   age_mean_30_months = "Age (months)") |> 
+	tab_style(cell_text(weight = "bold"),
+			  list(cells_column_spanners())) |> 
+	tab_style(cell_text(size = "medium"),
+			  list(cells_body(),
+			  	 cells_stub())) |> 
+	summary_rows(groups = c("Monolingual (Oxford)",
+							"Monolingual",
+							"Bilingual"),
+				 starts_with("n"), 
+				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
+	grand_summary_rows(starts_with("n"), 
+					   fns = list(label = md("*N*")) ~ sum(.),
+					   fmt = ~fmt_integer(.))
+```
+
 ```{r tbl-attrition-trials}
 #| label: tbl-attrition-trials
-#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
-attrition_trials |> 
-	filter(id %in% attrition_participants$id[attrition_participants$is_valid_participant]) |> 
-	left_join(select(participants, filename, id, age_group),
-			  by = join_by(filename, id, age_group)) |> 
+#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 1. Additional excluded trials are indicated between parentheses."
+attrition_oxf |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id)) |> 
+	bind_rows(mutate(attrition, id = as.character(id))) |> 
+	filter(is_valid_participant) |> 
 	summarise(n_valid = sum(is_valid_trial),
 			  n_total = n(),
-			  .by = c(id, age_group, trial_type)) |> 
+			  .by = c(id, age_group, lp, trial_type)) |> 
 	summarise(across(n_valid, lst(sum, mean, sd),
@@
 			  n_total = sum(n_total),
-			  .by = c(age_group, trial_type)) |> 
+			  .by = c(age_group, lp, trial_type)) |> 
 	mutate(n_excluded = n_total-sum) |> 
@@
 				names_repair = janitor::make_clean_names) |> 
-	rename_with(\(x) gsub("non_cognate", 
-						  "noncognate",
-						  x)) |> 
+	rename_with(\(x) gsub("non_cognate", "noncognate", x)) |> 
 	arrange(age_group) |> 
@@
 			 matches("noncognate")) |> 
-	gt(rowname_col = "age_group") |> 
+	gt(rowname_col = "age_group",
+	   groupname_col = "lp") |> 
+	summary_rows(groups = c("Monolingual (Oxford)",
+							"Monolingual",
+							"Bilingual"),
+				 starts_with("sum"), 
+				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
+	summary_rows(groups = c("Monolingual (Oxford)",
+							"Monolingual",
+							"Bilingual"),
+				 matches("mean"), 
+				 fns = list(label = md("*Mean*"), id = "totals") ~ mean(.),
+				 fmt = ~fmt_number(.)) |> 
 	grand_summary_rows(columns = matches("mean_"),
@@
 	fmt_integer(matches("sum"), sep_mark = ",") |> 
-	cols_label(sum_cognate = "N",
-			   sum_noncognate = "N",
-			   sum_unrelated = "N",
-			   mean_cognate = "Mean",
-			   mean_noncognate = "Mean",
-			   mean_unrelated = "Mean")
+	cols_label(sum_cognate = md("*N*"),
+			   sum_noncognate = md("*N*"),
+			   sum_unrelated = md("*N*"),
+			   mean_cognate = md("*Mean (SD)*"),
+			   mean_noncognate = md("*Mean (SD)*"),
+			   mean_unrelated = md("*Mean (SD)*"))
 ```
@@
 ### Phonological priming: Related vs. Unrelated
-
-<!--
--->
 
@@
 #| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs.
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
 (A) Mean posterior probability of target looking across the time course of the trial.
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_related$condition),
+plot_gamm <- function(data, model, contrast = "related") {
+	epreds <- expand_grid(condition = levels(data$condition),
 						  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_related$age),
-					  lp = levels(data_time_related$lp),
+						  age = mean(data$age),
+						  lp = levels(data$lp),
 						  .nsamples = 1) |>
-	add_epred_draws(model_fits_related[[1]],
+		add_epred_draws(model,
 						ndraws = NULL,
@@
 					id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = related - unrelated)
-
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
-# 
-# clusters <- rle(diff(diff_rect$is_cluster))
-# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
-# 
-# diff_rect <- diff_rect |> 
-# 	arrange(lp, timebin)
-# 
-# diff_rect <- 
-# 	cluster_number = 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = c(lp, is_cluster)) |> 
-# 	filter(is_cluster)
-
-# diff_obs <- data_time_related |>
-# 	pivot_wider(names_from = condition, 
-# 				values_from = elog,
-# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
-
-data_time_related |> 
+					names_repair = janitor::make_clean_names)
+
+	if (contrast=="related") {
+		epreds_diff$diff <- epreds_diff$related - epreds_diff$unrelated
+	} else {
+		epreds_diff$diff <- epreds_diff$cognate - epreds_diff$non_cognate
+	}
+
+	data |> 
 		summarise(.prop = mean(.prop),
@@
 		facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
 		stat_summary(data = epreds,
@@
 					 geom = "line",
-				 colour = "black",
 					 linewidth = 3/4) +
@@
 				   linetype = "dotted") +
+		stat_summary(fun.data = mean_se,
+					 geom = "errorbar",
+					 linetype = "solid",
+					 width = 0.25) +
 		stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
+					 geom = "point") +
 		labs(x = "Time (ms)",
@@
 		facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	stat_lineribbon(.width = 0.95,
-					linewidth = 0,
-					fill = "grey") +
-	stat_summary(data = epreds_diff,
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	# geom_point(data = diff_obs) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 fill = "CrI") +
-	theme(strip.text = element_blank(),
-		  legend.position = "none") +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) &
-	theme(panel.grid = element_blank(),
-		  legend.position = "top") 
-```
-
-### Cognate priming: Cognate vs. Non-cognate
-
-<!--
--->
-
-```{r fig-cognate}
-#| label: fig-cognate
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_cognate$condition),
-					  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_cognate$age),
-					  lp = levels(data_time_cognate$lp),
-					  .nsamples = 1) |>
-	add_epred_draws(model_fits_cognate[[1]],
-					ndraws = NULL,
-					re_formula = NA) |> 
-	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
-
-epreds_diff <- epreds |> 
-	pivot_wider(names_from = condition,
-				values_from = .epred,
-				id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = cognate - non_cognate) 
-# 
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	filter(.lower > 0 | .upper < 0) |> 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = lp)
-
-data_time_cognate |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(id, timebin, lp, condition, age)) |> 
-	ggplot(aes(timebin, .prop, 
-			   colour = condition,
-			   fill = condition,
-			   shape = condition)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -1.5,
-	# 		  	ymax = 1.5),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
-stat_summary(data = epreds,
-			 aes(y = .epred),
-			 fun.data = \(x) mean_qi(x, .width = 0.95),
-			 geom = "ribbon",
-			 alpha = 0.5,
-			 linewidth = 0) +
-	stat_summary(data = epreds,
-				 aes(y = .epred,
-				 	linetype = condition),
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0.5, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 colour = "Prime type",
-		 fill = "Prime type",
-		 linetype = "Prime type",
-		 shape = "Prime type") +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank()) +
-
-	epreds_diff |> 
-	ggplot(aes(timebin, diff)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -3/4,
-	# 		  	ymax = 3/4),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
 		stat_lineribbon(.width = 0.95,
@@
 		labs(x = "Time (ms)",
-		 y = "P(Target looking)",
+			 y = "Related - Unrelated",
 			 fill = "CrI") +
@@
 		scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
+		# scale_shape_manual(values = c(1, 2)) &
 		scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
@@
 			  legend.position = "top") 
-```
+}
+
+plot_gamm(data_time_related, model_fits_related[[1]])
+
+```
+
+### Cognate priming: Cognate vs. Non-cognate
+
+```{r fig-cognate}
+#| label: fig-cognate
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+plot_gamm(data_time_cognate, model_fits_cognate[[1]], contrast = "cognate")
+```
+
+{{< pagebreak >}}
 
@@
 
+::: {.callout-note}
+
 Participants must know the target **target** word (no need to know the prime word), and must look at least 10 ms to each target and distractor.
+
+:::
 
@@
 
+```{r tbl-participants-lp-vtarget}
+#| label: tbl-participants-lp-vtarget
+#| tbl-cap: "Participant details for Analysis 2.
+Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
+Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
+participants_tmp <- participants |> 
+	left_join(attrition_participants_vtarget, by = join_by(filename)) |> 
+	mutate(id = as.character(id))
+
+participants_oxf_tmp <- participants_oxf |> 
+	inner_join(attrition_participants_vtarget_oxf,
+			   by = join_by(id)) |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id))
+
+bind_rows(participants_tmp, participants_oxf_tmp) |> 
+	add_count(lp, 
+			  name = "n_lp") |> 
+	add_count(age_group, 
+			  name = "n_age_group") |> 
+	add_count(age_group,
+			  test_language,
+			  name = "n_age_test") |> 
+	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
+	summarise(across(c(age), lst(mean, sd)),
+			  n_inc = sum(is_valid_participant),
+			  n_exc = sum(!is_valid_participant),
+			  .by = c(age_group, lp, test_language)) |> 
+	pivot_wider(id_cols = c(test_language, lp),
+				names_from = c(age_group),
+				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
+				names_repair = janitor::make_clean_names) |>
+	relocate(lp, test_language, 
+			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
+			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
+			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
+	arrange(lp, test_language) |> 
+	gt(rowname_col = "test_language", 
+	   groupname_col = "lp", 
+	   row_group.sep = ": ") |> 
+	tab_spanner(md("21 months"), matches("21")) |> 
+	tab_spanner(md("25 months"), matches("25")) |>
+	tab_spanner(md("30 months"), matches("30")) |> 
+	fmt_number(matches("age"), decimals = 1) |>
+	cols_merge(c(n_inc_21_months, n_exc_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_25_months, n_exc_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_30_months, n_exc_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_21_months, age_sd_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_25_months, age_sd_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_30_months, age_sd_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_label(n_inc_21_months = md("*N*"),
+			   n_inc_25_months = md("*N*"),
+			   n_inc_30_months = md("*N*"),
+			   age_mean_21_months = "Age (months)",
+			   age_mean_25_months = "Age (months)",
+			   age_mean_30_months = "Age (months)") |> 
+	tab_style(cell_text(weight = "bold"),
+			  list(cells_column_spanners())) |> 
+	tab_style(cell_text(size = "medium"),
+			  list(cells_body(),
+			  	 cells_stub())) |> 
+	summary_rows(groups = c("Monolingual (Oxford)",
+							"Monolingual",
+							"Bilingual"),
+				 starts_with("n"), 
+				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
+	grand_summary_rows(starts_with("n"), 
+					   fns = list(label = md("*N*")) ~ sum(.),
+					   fmt = ~fmt_integer(.))
+```
+
 ```{r tbl-attrition-trials-vtarget}
 #| label: tbl-attrition-trials-vtarget
-#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
-attrition_trials_vtarget |> 
-	filter(id %in% attrition_participants_vtarget$id[attrition_participants_vtarget$is_valid_participant]) |> 
-	left_join(select(participants, filename, id, age_group),
-			  by = join_by(filename, id, age_group)) |> 
+#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 2. Additional excluded trials are indicated between parentheses."
+attrition_vtarget_oxf |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id)) |> 
+	bind_rows(mutate(attrition, id = as.character(id))) |> 
+	filter(is_valid_participant) |> 
 	summarise(n_valid = sum(is_valid_trial),
 			  n_total = n(),
-			  .by = c(id, age_group, trial_type)) |> 
+			  .by = c(id, age_group, lp, trial_type)) |> 
 	summarise(across(n_valid, lst(sum, mean, sd),
@@
 #| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs.
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 2.
 (A) Mean posterior probability of target looking across the time course of the trial.
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_related_vtarget$condition),
-					  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_related_vtarget$age),
-					  lp = levels(data_time_related_vtarget$lp),
-					  .nsamples = 1) |>
-	add_epred_draws(model_fits_related_vtarget[[1]],
-					ndraws = NULL,
-					re_formula = NA, 
-					value = ".value") |> 
-	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
-
-epreds_diff <- epreds |> 
-	pivot_wider(names_from = condition,
-				values_from = .value,
-				id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = related - unrelated)
-
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
-# 
-# clusters <- rle(diff(diff_rect$is_cluster))
-# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
-# 
-# diff_rect <- diff_rect |> 
-# 	arrange(lp, timebin)
-# 
-# diff_rect <- 
-# 	cluster_number = 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = c(lp, is_cluster)) |> 
-# 	filter(is_cluster)
-
-# diff_obs <- data_time_related |>
-# 	pivot_wider(names_from = condition, 
-# 				values_from = elog,
-# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
-
-data_time_related_vtarget |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(id, timebin, lp, condition, age)) |> 
-	ggplot(aes(timebin, .prop, 
-			   colour = condition,
-			   fill = condition,
-			   shape = condition,
-			   linetype = condition)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
-stat_summary(data = epreds,
-			 aes(y = .value),
-			 fun.data = \(x) mean_qi(x, .width = 0.95),
-			 geom = "ribbon",
-			 alpha = 0.5,
-			 linewidth = 0) +
-	stat_summary(data = epreds,
-				 aes(y = .value,
-				 	linetype = condition),
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 1/2, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 colour = "Condition",
-		 fill = "Condition",
-		 linetype = "Condition",
-		 shape = "Condition") +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank()) +
-
-	epreds_diff |> 
-	ggplot(aes(timebin, diff)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	stat_lineribbon(.width = 0.95,
-					linewidth = 0,
-					fill = "grey") +
-	stat_summary(data = epreds_diff,
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	# geom_point(data = diff_obs) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 fill = "CrI") +
-	theme(strip.text = element_blank(),
-		  legend.position = "none") +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) &
-	theme(panel.grid = element_blank(),
-		  legend.position = "top") 
+plot_gamm(data_time_related_vtarget, 
+		  model_fits_related_vtarget[[1]], 
+		  contrast = "related")
 ```
@@
 ### Cognate priming: Cognate vs. Non-cognate
-
-<!--
--->
 
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_cognate_vtarget$condition),
-					  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_cognate_vtarget$age),
-					  lp = levels(data_time_cognate_vtarget$lp),
-					  .nsamples = 1) |>
-	add_epred_draws(model_fits_cognate_vtarget[[1]],
-					ndraws = NULL,
-					re_formula = NA) |> 
-	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
-
-epreds_diff <- epreds |> 
-	pivot_wider(names_from = condition,
-				values_from = .epred,
-				id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = cognate - non_cognate) 
-# 
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	filter(.lower > 0 | .upper < 0) |> 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = lp)
-
-data_time_cognate_vtarget |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(id, timebin, lp, condition, age)) |> 
-	ggplot(aes(timebin, .prop, 
-			   colour = condition,
-			   fill = condition,
-			   shape = condition)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -1.5,
-	# 		  	ymax = 1.5),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
-stat_summary(data = epreds,
-			 aes(y = .epred),
-			 fun.data = \(x) mean_qi(x, .width = 0.95),
-			 geom = "ribbon",
-			 alpha = 0.5,
-			 linewidth = 0) +
-	stat_summary(data = epreds,
-				 aes(y = .epred,
-				 	linetype = condition),
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0.5, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 colour = "Prime type",
-		 fill = "Prime type",
-		 linetype = "Prime type",
-		 shape = "Prime type") +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank()) +
-
-	epreds_diff |> 
-	ggplot(aes(timebin, diff)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -3/4,
-	# 		  	ymax = 3/4),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	stat_lineribbon(.width = 0.95,
-					linewidth = 0,
-					fill = "grey") +
-	stat_summary(data = epreds_diff,
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 fill = "CrI") +
-	theme(strip.text = element_blank(),
-		  legend.position = "none") +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) &
-	theme(panel.grid = element_blank(),
-		  legend.position = "top") 
-```
+plot_gamm(data_time_cognate_vtarget, 
+		  model_fits_cognate_vtarget[[1]], 
+		  contrast = "cognate")
+```
+
+{{< pagebreak >}}
 
@@
 
+::: {.callout-note}
+
 Participants do not need to know the prime or target words, but must look at least 10 ms to each target and distractor.
+
+:::
 
@@
 
+```{r tbl-participants-lp-vnone}
+#| label: tbl-participants-lp-vnone
+#| tbl-cap: "Participant details for Analysis 3.
+Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
+Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
+participants_tmp <- participants |> 
+	left_join(attrition_participants_vnone, by = join_by(filename)) |> 
+	mutate(id = as.character(id))
+
+participants_oxf_tmp <- participants_oxf |> 
+	inner_join(attrition_participants_vnone_oxf,
+			   by = join_by(id)) |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id))
+
+bind_rows(participants_tmp, participants_oxf_tmp) |> 
+	add_count(lp, 
+			  name = "n_lp") |> 
+	add_count(age_group, 
+			  name = "n_age_group") |> 
+	add_count(age_group,
+			  test_language,
+			  name = "n_age_test") |> 
+	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
+	summarise(across(c(age), lst(mean, sd)),
+			  n_inc = sum(is_valid_participant),
+			  n_exc = sum(!is_valid_participant),
+			  .by = c(age_group, lp, test_language)) |> 
+	pivot_wider(id_cols = c(test_language, lp),
+				names_from = c(age_group),
+				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
+				names_repair = janitor::make_clean_names) |>
+	relocate(lp, test_language, 
+			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
+			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
+			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
+	arrange(lp, test_language) |> 
+	gt(rowname_col = "test_language", 
+	   groupname_col = "lp", 
+	   row_group.sep = ": ") |> 
+	tab_spanner(md("21 months"), matches("21")) |> 
+	tab_spanner(md("25 months"), matches("25")) |>
+	tab_spanner(md("30 months"), matches("30")) |> 
+	fmt_number(matches("age"), decimals = 1) |>
+	cols_merge(c(n_inc_21_months, n_exc_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_25_months, n_exc_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_30_months, n_exc_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_21_months, age_sd_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_25_months, age_sd_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_30_months, age_sd_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_label(n_inc_21_months = md("*N*"),
+			   n_inc_25_months = md("*N*"),
+			   n_inc_30_months = md("*N*"),
+			   age_mean_21_months = "Age (months)",
+			   age_mean_25_months = "Age (months)",
+			   age_mean_30_months = "Age (months)") |> 
+	tab_style(cell_text(weight = "bold"),
+			  list(cells_column_spanners())) |> 
+	tab_style(cell_text(size = "medium"),
+			  list(cells_body(),
+			  	 cells_stub())) |> 
+	summary_rows(groups = c("Monolingual (Oxford)",
+							"Monolingual",
+							"Bilingual"),
+				 starts_with("n"), 
+				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
+	grand_summary_rows(starts_with("n"), 
+					   fns = list(label = md("*N*")) ~ sum(.),
+					   fmt = ~fmt_integer(.))
+```
+
 ```{r tbl-attrition-trials-vnone}
 #| label: tbl-attrition-trials-vnone
-#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
-attrition_trials_vnone |> 
-	filter(id %in% attrition_participants_vnone$id[attrition_participants_vnone$is_valid_participant]) |> 
-	left_join(select(participants, filename, id, age_group),
-			  by = join_by(filename, id, age_group)) |> 
+#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 3. Additional excluded trials are indicated between parentheses."
+attrition_vnone_oxf |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id)) |> 
+	bind_rows(mutate(attrition, id = as.character(id))) |> 
+	filter(is_valid_participant) |> 
 	summarise(n_valid = sum(is_valid_trial),
 			  n_total = n(),
-			  .by = c(id, age_group, trial_type)) |> 
+			  .by = c(id, age_group, lp, trial_type)) |> 
 	summarise(across(n_valid, lst(sum, mean, sd),
@@
 #| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs.
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 3.
 (A) Mean posterior probability of target looking across the time course of the trial.
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_related_vnone$condition),
-					  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_related_vnone$age),
-					  lp = levels(data_time_related_vnone$lp),
-					  .nsamples = 1) |>
-	add_epred_draws(model_fits_related_vnone[[1]],
-					ndraws = NULL,
-					re_formula = NA, 
-					value = ".value") |> 
-	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
-
-epreds_diff <- epreds |> 
-	pivot_wider(names_from = condition,
-				values_from = .value,
-				id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = related - unrelated)
-
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
-# 
-# clusters <- rle(diff(diff_rect$is_cluster))
-# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
-# 
-# diff_rect <- diff_rect |> 
-# 	arrange(lp, timebin)
-# 
-# diff_rect <- 
-# 	cluster_number = 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = c(lp, is_cluster)) |> 
-# 	filter(is_cluster)
-
-# diff_obs <- data_time_related |>
-# 	pivot_wider(names_from = condition, 
-# 				values_from = elog,
-# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
-
-data_time_related_vnone |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(id, timebin, lp, condition, age)) |> 
-	ggplot(aes(timebin, .prop, 
-			   colour = condition,
-			   fill = condition,
-			   shape = condition,
-			   linetype = condition)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
-stat_summary(data = epreds,
-			 aes(y = .value),
-			 fun.data = \(x) mean_qi(x, .width = 0.95),
-			 geom = "ribbon",
-			 alpha = 0.5,
-			 linewidth = 0) +
-	stat_summary(data = epreds,
-				 aes(y = .value,
-				 	linetype = condition),
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 1/2, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 colour = "Condition",
-		 fill = "Condition",
-		 linetype = "Condition",
-		 shape = "Condition") +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank()) +
-
-	epreds_diff |> 
-	ggplot(aes(timebin, diff)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	stat_lineribbon(.width = 0.95,
-					linewidth = 0,
-					fill = "grey") +
-	stat_summary(data = epreds_diff,
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	# geom_point(data = diff_obs) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 fill = "CrI") +
-	theme(strip.text = element_blank(),
-		  legend.position = "none") +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) &
-	theme(panel.grid = element_blank(),
-		  legend.position = "top") 
+plot_gamm(data_time_related_vnone, 
+		  model_fits_related_vnone[[1]], 
+		  contrast = "related")
 ```
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_cognate_vnone$condition),
-					  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_cognate_vnone$age),
-					  lp = levels(data_time_cognate_vnone$lp),
-					  .nsamples = 1) |>
-	add_epred_draws(model_fits_cognate_vnone[[1]],
-					ndraws = NULL,
-					re_formula = NA) |> 
-	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
-
-epreds_diff <- epreds |> 
-	pivot_wider(names_from = condition,
-				values_from = .epred,
-				id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = cognate - non_cognate) 
-# 
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	filter(.lower > 0 | .upper < 0) |> 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = lp)
-
-data_time_cognate_vnone |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(id, timebin, lp, condition, age)) |> 
-	ggplot(aes(timebin, .prop, 
-			   colour = condition,
-			   fill = condition,
-			   shape = condition)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -1.5,
-	# 		  	ymax = 1.5),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
-stat_summary(data = epreds,
-			 aes(y = .epred),
-			 fun.data = \(x) mean_qi(x, .width = 0.95),
-			 geom = "ribbon",
-			 alpha = 0.5,
-			 linewidth = 0) +
-	stat_summary(data = epreds,
-				 aes(y = .epred,
-				 	linetype = condition),
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0.5, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 colour = "Prime type",
-		 fill = "Prime type",
-		 linetype = "Prime type",
-		 shape = "Prime type") +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank()) +
-
-	epreds_diff |> 
-	ggplot(aes(timebin, diff)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -3/4,
-	# 		  	ymax = 3/4),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	stat_lineribbon(.width = 0.95,
-					linewidth = 0,
-					fill = "grey") +
-	stat_summary(data = epreds_diff,
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 fill = "CrI") +
-	theme(strip.text = element_blank(),
-		  legend.position = "none") +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) &
-	theme(panel.grid = element_blank(),
-		  legend.position = "top") 
-```
+plot_gamm(data_time_cognate_vnone, 
+		  model_fits_cognate_vnone[[1]], 
+		  contrast = "cognate")
+```
+
+{{< pagebreak >}}
 
@@
 
+::: {.callout-note}
+
 Participants do not need to know the prime or target words, and do not need to look to both pictures.
+
+:::
+
 ```{r dataset-noeach}
@@
 
-```{r tbl-attrition-trials-noeach}
+```{r tbl-participants-lp-noeach}
+#| label: tbl-participants-lp-noeach
+#| tbl-cap: "Participant details for Analysis 4.
+Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
+Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
+participants_tmp <- participants |> 
+	left_join(attrition_participants_noeach, by = join_by(filename)) |> 
+	mutate(id = as.character(id))
+
+participants_oxf_tmp <- participants_oxf |> 
+	inner_join(attrition_participants_noeach_oxf,
+			   by = join_by(id)) |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id))
+
+bind_rows(participants_tmp, participants_oxf_tmp) |> 
+	add_count(lp, 
+			  name = "n_lp") |> 
+	add_count(age_group, 
+			  name = "n_age_group") |> 
+	add_count(age_group,
+			  test_language,
+			  name = "n_age_test") |> 
+	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
+	summarise(across(c(age), lst(mean, sd)),
+			  n_inc = sum(is_valid_participant),
+			  n_exc = sum(!is_valid_participant),
+			  .by = c(age_group, lp, test_language)) |> 
+	pivot_wider(id_cols = c(test_language, lp),
+				names_from = c(age_group),
+				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
+				names_repair = janitor::make_clean_names) |>
+	relocate(lp, test_language, 
+			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
+			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
+			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
+	arrange(lp, test_language) |> 
+	gt(rowname_col = "test_language", 
+	   groupname_col = "lp", 
+	   row_group.sep = ": ") |> 
+	tab_spanner(md("21 months"), matches("21")) |> 
+	tab_spanner(md("25 months"), matches("25")) |>
+	tab_spanner(md("30 months"), matches("30")) |> 
+	fmt_number(matches("age"), decimals = 1) |>
+	cols_merge(c(n_inc_21_months, n_exc_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_25_months, n_exc_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_30_months, n_exc_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_21_months, age_sd_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_25_months, age_sd_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_30_months, age_sd_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_label(n_inc_21_months = md("*N*"),
+			   n_inc_25_months = md("*N*"),
+			   n_inc_30_months = md("*N*"),
+			   age_mean_21_months = "Age (months)",
+			   age_mean_25_months = "Age (months)",
+			   age_mean_30_months = "Age (months)") |> 
+	tab_style(cell_text(weight = "bold"),
+			  list(cells_column_spanners())) |> 
+	tab_style(cell_text(size = "medium"),
+			  list(cells_body(),
+			  	 cells_stub())) |> 
+	summary_rows(groups = c("Monolingual (Oxford)",
+							"Monolingual",
+							"Bilingual"),
+				 starts_with("n"), 
+				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
+	grand_summary_rows(starts_with("n"), 
+					   fns = list(label = md("*N*")) ~ sum(.),
+					   fmt = ~fmt_integer(.))
+```
+
+```{r tbl-attrition-trials-vnone}
 #| label: tbl-attrition-trials-noeach
-#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
-attrition_trials_noeach |> 
-	filter(id %in% attrition_participants_noeach$id[attrition_participants_noeach$is_valid_participant]) |> 
-	left_join(select(participants, filename, id, age_group),
-			  by = join_by(filename, id, age_group)) |> 
+#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 4. Additional excluded trials are indicated between parentheses."
+attrition_noeach_oxf |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id)) |> 
+	bind_rows(mutate(attrition, id = as.character(id))) |> 
+	filter(is_valid_participant) |> 
 	summarise(n_valid = sum(is_valid_trial),
 			  n_total = n(),
-			  .by = c(id, age_group, trial_type)) |> 
+			  .by = c(id, age_group, lp, trial_type)) |> 
 	summarise(across(n_valid, lst(sum, mean, sd),
@@
 #| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs.
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 4.
 (A) Mean posterior probability of target looking across the time course of the trial.
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_related_noeach$condition),
-					  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_related_noeach$age),
-					  lp = levels(data_time_related_noeach$lp),
-					  .nsamples = 1) |>
-	add_epred_draws(model_fits_related_noeach[[1]],
-					ndraws = NULL,
-					re_formula = NA, 
-					value = ".value") |> 
-	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
-
-epreds_diff <- epreds |> 
-	pivot_wider(names_from = condition,
-				values_from = .value,
-				id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = related - unrelated)
-
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
-# 
-# clusters <- rle(diff(diff_rect$is_cluster))
-# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
-# 
-# diff_rect <- diff_rect |> 
-# 	arrange(lp, timebin)
-# 
-# diff_rect <- 
-# 	cluster_number = 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = c(lp, is_cluster)) |> 
-# 	filter(is_cluster)
-
-# diff_obs <- data_time_related |>
-# 	pivot_wider(names_from = condition, 
-# 				values_from = elog,
-# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
-
-data_time_related_noeach |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(id, timebin, lp, condition, age)) |> 
-	ggplot(aes(timebin, .prop, 
-			   colour = condition,
-			   fill = condition,
-			   shape = condition,
-			   linetype = condition)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
-stat_summary(data = epreds,
-			 aes(y = .value),
-			 fun.data = \(x) mean_qi(x, .width = 0.95),
-			 geom = "ribbon",
-			 alpha = 0.5,
-			 linewidth = 0) +
-	stat_summary(data = epreds,
-				 aes(y = .value,
-				 	linetype = condition),
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 1/2, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 colour = "Condition",
-		 fill = "Condition",
-		 linetype = "Condition",
-		 shape = "Condition") +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank()) +
-
-	epreds_diff |> 
-	ggplot(aes(timebin, diff)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	stat_lineribbon(.width = 0.95,
-					linewidth = 0,
-					fill = "grey") +
-	stat_summary(data = epreds_diff,
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	# geom_point(data = diff_obs) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 fill = "CrI") +
-	theme(strip.text = element_blank(),
-		  legend.position = "none") +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) &
-	theme(panel.grid = element_blank(),
-		  legend.position = "top") 
+plot_gamm(data_time_related_noeach, 
+		  model_fits_related_noeach[[1]], 
+		  contrast = "related")
 ```
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_cognate_noeach$condition),
-					  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_cognate_noeach$age),
-					  lp = levels(data_time_cognate_noeach$lp),
-					  .nsamples = 1) |>
-	add_epred_draws(model_fits_cognate_noeach[[1]],
-					ndraws = NULL,
-					re_formula = NA) |> 
-	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
-
-epreds_diff <- epreds |> 
-	pivot_wider(names_from = condition,
-				values_from = .epred,
-				id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = cognate - non_cognate) 
-# 
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	filter(.lower > 0 | .upper < 0) |> 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = lp)
-
-data_time_cognate_noeach |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(id, timebin, lp, condition, age)) |> 
-	ggplot(aes(timebin, .prop, 
-			   colour = condition,
-			   fill = condition,
-			   shape = condition)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -1.5,
-	# 		  	ymax = 1.5),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
-stat_summary(data = epreds,
-			 aes(y = .epred),
-			 fun.data = \(x) mean_qi(x, .width = 0.95),
-			 geom = "ribbon",
-			 alpha = 0.5,
-			 linewidth = 0) +
-	stat_summary(data = epreds,
-				 aes(y = .epred,
-				 	linetype = condition),
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0.5, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 colour = "Prime type",
-		 fill = "Prime type",
-		 linetype = "Prime type",
-		 shape = "Prime type") +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank()) +
-
-	epreds_diff |> 
-	ggplot(aes(timebin, diff)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -3/4,
-	# 		  	ymax = 3/4),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	stat_lineribbon(.width = 0.95,
-					linewidth = 0,
-					fill = "grey") +
-	stat_summary(data = epreds_diff,
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 fill = "CrI") +
-	theme(strip.text = element_blank(),
-		  legend.position = "none") +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) &
-	theme(panel.grid = element_blank(),
-		  legend.position = "top") 
-```
+plot_gamm(data_time_cognate_noeach, 
+		  model_fits_cognate_noeach[[1]], 
+		  contrast = "cognate")
+```
+
+{{< pagebreak >}}
 
@@
 
+::: {.callout-note}
+
 Participants need to know the prime or target words, and do not need to look to both pictures.
+
+:::
 
@@
 
+```{r tbl-participants-lp-vnoeach}
+#| label: tbl-participants-lp-vnoeach
+#| tbl-cap: "Participant details for Analysis 5.
+Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
+Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
+participants_tmp <- participants |> 
+	left_join(attrition_participants_vnoeach, by = join_by(filename)) |> 
+	mutate(id = as.character(id))
+
+participants_oxf_tmp <- participants_oxf |> 
+	inner_join(attrition_participants_vnoeach_oxf,
+			   by = join_by(id)) |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id))
+
+bind_rows(participants_tmp, participants_oxf_tmp) |> 
+	add_count(lp, 
+			  name = "n_lp") |> 
+	add_count(age_group, 
+			  name = "n_age_group") |> 
+	add_count(age_group,
+			  test_language,
+			  name = "n_age_test") |> 
+	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
+	summarise(across(c(age), lst(mean, sd)),
+			  n_inc = sum(is_valid_participant),
+			  n_exc = sum(!is_valid_participant),
+			  .by = c(age_group, lp, test_language)) |> 
+	pivot_wider(id_cols = c(test_language, lp),
+				names_from = c(age_group),
+				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
+				names_repair = janitor::make_clean_names) |>
+	relocate(lp, test_language, 
+			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
+			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
+			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
+	arrange(lp, test_language) |> 
+	gt(rowname_col = "test_language", 
+	   groupname_col = "lp", 
+	   row_group.sep = ": ") |> 
+	tab_spanner(md("21 months"), matches("21")) |> 
+	tab_spanner(md("25 months"), matches("25")) |>
+	tab_spanner(md("30 months"), matches("30")) |> 
+	fmt_number(matches("age"), decimals = 1) |>
+	cols_merge(c(n_inc_21_months, n_exc_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_25_months, n_exc_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_inc_30_months, n_exc_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_21_months, age_sd_21_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_25_months, age_sd_25_months),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean_30_months, age_sd_30_months),
+			   pattern = "{1} ({2})") |> 
+	cols_label(n_inc_21_months = md("*N*"),
+			   n_inc_25_months = md("*N*"),
+			   n_inc_30_months = md("*N*"),
+			   age_mean_21_months = "Age (months)",
+			   age_mean_25_months = "Age (months)",
+			   age_mean_30_months = "Age (months)") |> 
+	tab_style(cell_text(weight = "bold"),
+			  list(cells_column_spanners())) |> 
+	tab_style(cell_text(size = "medium"),
+			  list(cells_body(),
+			  	 cells_stub())) |> 
+	summary_rows(groups = c("Monolingual (Oxford)",
+							"Monolingual",
+							"Bilingual"),
+				 starts_with("n"), 
+				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
+	grand_summary_rows(starts_with("n"), 
+					   fns = list(label = md("*N*")) ~ sum(.),
+					   fmt = ~fmt_integer(.))
+```
+
 ```{r tbl-attrition-trials-vnoeach}
 #| label: tbl-attrition-trials-vnoeach
-#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
-attrition_trials_vnoeach |> 
-	filter(id %in% attrition_participants_vnoeach$id[attrition_participants_vnoeach$is_valid_participant]) |> 
-	left_join(select(participants, filename, id, age_group),
-			  by = join_by(filename, id, age_group)) |> 
+#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 4. Additional excluded trials are indicated between parentheses."
+attrition_vnoeach_oxf |> 
+	mutate(lp = "Monolingual (Oxford)",
+		   id = as.character(id)) |> 
+	bind_rows(mutate(attrition, id = as.character(id))) |> 
+	filter(is_valid_participant) |> 
 	summarise(n_valid = sum(is_valid_trial),
 			  n_total = n(),
-			  .by = c(id, age_group, trial_type)) |> 
+			  .by = c(id, age_group, lp, trial_type)) |> 
 	summarise(across(n_valid, lst(sum, mean, sd),
@@
 #| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs.
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 5.
 (A) Mean posterior probability of target looking across the time course of the trial.
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_related_vnoeach$condition),
-					  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_related_vnoeach$age),
-					  lp = levels(data_time_related_vnoeach$lp),
-					  .nsamples = 1) |>
-	add_epred_draws(model_fits_related_vnoeach[[1]],
-					ndraws = NULL,
-					re_formula = NA, 
-					value = ".value") |> 
-	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
-
-epreds_diff <- epreds |> 
-	pivot_wider(names_from = condition,
-				values_from = .value,
-				id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = related - unrelated)
-
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	mutate(is_cluster = .lower > 0 | .upper < 0) 
-# 
-# clusters <- rle(diff(diff_rect$is_cluster))
-# diff_rect$cluster_id <- c(0, rep(clusters$values, clusters$lengths))
-# 
-# diff_rect <- diff_rect |> 
-# 	arrange(lp, timebin)
-# 
-# diff_rect <- 
-# 	cluster_number = 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = c(lp, is_cluster)) |> 
-# 	filter(is_cluster)
-
-# diff_obs <- data_time_related |>
-# 	pivot_wider(names_from = condition, 
-# 				values_from = elog,
-# 				names_repair = janitor::make_clean_names) |> mutate(diff = related - unrelated)
-
-data_time_related_vnoeach |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(id, timebin, lp, condition, age)) |> 
-	ggplot(aes(timebin, .prop, 
-			   colour = condition,
-			   fill = condition,
-			   shape = condition,
-			   linetype = condition)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
-stat_summary(data = epreds,
-			 aes(y = .value),
-			 fun.data = \(x) mean_qi(x, .width = 0.95),
-			 geom = "ribbon",
-			 alpha = 0.5,
-			 linewidth = 0) +
-	stat_summary(data = epreds,
-				 aes(y = .value,
-				 	linetype = condition),
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 1/2, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 colour = "Condition",
-		 fill = "Condition",
-		 linetype = "Condition",
-		 shape = "Condition") +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank()) +
-
-	epreds_diff |> 
-	ggplot(aes(timebin, diff)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -Inf,
-	# 		  	ymax = Inf),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	stat_lineribbon(.width = 0.95,
-					linewidth = 0,
-					fill = "grey") +
-	stat_summary(data = epreds_diff,
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	# geom_point(data = diff_obs) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 fill = "CrI") +
-	theme(strip.text = element_blank(),
-		  legend.position = "none") +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) &
-	theme(panel.grid = element_blank(),
-		  legend.position = "top") 
+plot_gamm(data_time_related_vnoeach, 
+		  model_fits_related_vnoeach[[1]], 
+		  contrast = "related")
 ```
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-epreds <- expand_grid(condition = levels(data_time_cognate_vnoeach$condition),
-					  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data_time_cognate_vnoeach$age),
-					  lp = levels(data_time_cognate_vnoeach$lp),
-					  .nsamples = 1) |>
-	add_epred_draws(model_fits_cognate_vnoeach[[1]],
-					ndraws = NULL,
-					re_formula = NA) |> 
-	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
-
-epreds_diff <- epreds |> 
-	pivot_wider(names_from = condition,
-				values_from = .epred,
-				id_cols = c(timebin, age, lp, .draw),
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff = cognate - non_cognate) 
-# 
-# diff_rect <- epreds_diff |> 
-# 	mean_qi(diff) |> 
-# 	filter(.lower > 0 | .upper < 0) |> 
-# 	summarise(xmin = min(timebin),
-# 			  xmax = max(timebin),
-# 			  .by = lp)
-
-data_time_cognate_vnoeach |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(id, timebin, lp, condition, age)) |> 
-	ggplot(aes(timebin, .prop, 
-			   colour = condition,
-			   fill = condition,
-			   shape = condition)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -1.5,
-	# 		  	ymax = 1.5),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	# geom_line(data = epreds,
-	# 		  aes(y = .epred,
-# 		  	group = interaction(condition, .draw)),
-# 		  linetype = "solid",
-# 		  alpha = 0.1,
-# 		  linewidth = 3/4) +
-stat_summary(data = epreds,
-			 aes(y = .epred),
-			 fun.data = \(x) mean_qi(x, .width = 0.95),
-			 geom = "ribbon",
-			 alpha = 0.5,
-			 linewidth = 0) +
-	stat_summary(data = epreds,
-				 aes(y = .epred,
-				 	linetype = condition),
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0.5, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 colour = "black",
-				 size = 2.5,
-				 stroke = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 colour = "Prime type",
-		 fill = "Prime type",
-		 linetype = "Prime type",
-		 shape = "Prime type") +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank()) +
-
-	epreds_diff |> 
-	ggplot(aes(timebin, diff)) +
-	facet_wrap(~lp) +
-	# geom_rect(data = diff_rect,
-	# 		  aes(xmin = xmin,
-	# 		  	xmax = xmax,
-	# 		  	ymin = -3/4,
-	# 		  	ymax = 3/4),
-	# 		  colour = NA,
-	# 		  fill = "orange",
-	# 		  alpha = 1/2,
-	# 		  inherit.aes = FALSE) +
-	stat_lineribbon(.width = 0.95,
-					linewidth = 0,
-					fill = "grey") +
-	stat_summary(data = epreds_diff,
-				 fun = "mean",
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	labs(x = "Time (ms)",
-		 y = "P(Target looking)",
-		 fill = "CrI") +
-	theme(strip.text = element_blank(),
-		  legend.position = "none") +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-	scale_shape_manual(values = c(1, 2)) &
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) &
-	theme(panel.grid = element_blank(),
-		  legend.position = "top") 
+plot_gamm(data_time_cognate_vnoeach, 
+		  model_fits_cognate_vnoeach[[1]], 
+		  contrast = "cognate")
 ```

### 2023-10-20 _targets.R
Update manuscript

@@ -38,6 +38,10 @@ options(mc.cores = 2,
 		knitr.duplicate.label = "allow",
 		cli.progress_bar_style = "dot")
 
+tar_option_set(
+	seed = 1234
+)
+
 # define targets (see https://books.ropensci.org/targets/)
 # in each target, the value returned by a function (second argument) is assigned to 
 # a variable name (first argument). This object is stored in in the _targets folder
@@ -320,9 +324,9 @@ list(
 
 	tar_target(model_names_vnone, 
 			   list(
-			   	related = apply(expand.grid("fit_related_vnone_", 0:3), 1,
+			   	related = apply(expand.grid("fit_related_none_", 0:3), 1,
 			   					\(x) paste0(x[1], x[2])),
-			   	cognate = apply(expand.grid("fit_cognate_vnone_", 0:3), 1, 
+			   	cognate = apply(expand.grid("fit_cognate_none_", 0:3), 1, 
 			   					\(x) paste0(x[1], x[2]))
 			   )),
 	
@@ -338,7 +342,7 @@ list(
 			   		test = 1,
 			   		test_each = 0.1))),
 	
-	tar_target(attrition_participants_vnone,
+	tar_target(attrition_participants_none,
 			   get_attrition_participants(attrition_trials_vnone,
 			   						   min_trials = c(cognate = 2, 
 			   						   			   noncognate = 2,

### 2023-10-21 manuscript/manuscript.qmd
Update manuscript
Add references and remove HTML manuscript

@@
 
-The formation of a mental lexicon is a critical developmental achievement for infants_ learning words allows infants to retrieve socially relevant concepts from fairly arbitrary linguistic forms embedded in speech.
-
-Learning words allows infants to access the rich world made of concepts through the recognition of fairly arbitrary linguistic forms, i.e., words. This remarkable developmental achievement is
+::: {.callout-note}
+How do  bilinguals keep up with monolinguals?
+:::
+
+Bilingual infants receive a relative impoverished linguistic input in each of their languages compared to their monolingual peers.
+There is not reason to think bilinguals receive an increased amount of total linguistic input, so the fact that such input is divided between at least two languages means that they receive less input from each of their languages [@costa2014does].
+The input bilinguals receive is also more complex than that of monolinguals.
+This is reflected in multiple dimensions.
+For instance, bilinguals are presented with two different, but possible overlapping phoneme inventories, they may be presented with two different grammatical systems, and often presented with more than one label per referent.
+This does not keep bilinguals from tuning their perceptual abilities to both phoneme inventories of their native languages, distinguishing grammatical irregularities in both languages, or learning more than one label per object.
+Bilinguals' developmental trajectories might not always be identical to monolinguals', but they achieve their language acquisition milestones at equivalent ages.
+
+::: {.callout-note}
+Developmental trajectories of lexical acquisition.
+:::
+
+For instance, previous work on lexical acquisition has provided some insight into how bilinguals' vocabulary size is equivalent to monolingual's across ages, and the possible mechanisms behind this.
+@hoff2012 found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
+This is consistent with previous accounnts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
+A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languiages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
+Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
+Cognates are form-simlar translation equivalents.
+Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
+
+::: {.callout-note}
+Lexical structure, as reflected by word processing.
+:::
+
+It is well established that, across languages, monolingual infants start recognising their first word-forms before their first year of life [@jusczyk1999; @halle1994; @vihman2004], with the earliest age at which there is evidencer of familiar word recognition being 6 months [@bergelson2012].
+Bilinguals start recognising words at similar ages.
+Using a Head-turn Prefernce Procedure and ERP registration,  @vihman2013 found English-Welsh bilinguals to be sensitive to the prevalence of auditorily presented words.
+Infants' looking times and ERP differed when presented with words frequently marked as "familiar" by caregivers of demogrtaphically equivalent peers (e.g., *nappy*, *thank you*, *bottle*, *apple*, and *naughty*), compared to when presented with rare words (e.g., *Eiffel*, *courtly*, *nettle*, *wacky*, and *juncture*).
+
+::: {.callout-note}
+Language-non selective lexical access in bilinguals
+:::
+
+A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
+When listening to speech, bilinguals activate all lexical candidates from either language consistent with the speech signal.
+Even more surprising, when speaking, bilinguals activate all potential words consistent with the concepts they want to express.
+This effect has been systematically reported in adults [@marian1999activation; @costa2000cognate; @thierry2007brain; @dunabeitia2009masked].
+
+Also in toddlers [@von2012language; @von2014bilinguals] and school-aged children [@persici2019lexical; @bosma2020cognate].
+Relatedly, some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
+Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
+Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that SpanishCatalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
+
+Although recent work has provided strong eviodence of parallel activation in early ages, how cognateness shapes that organisation of the early bilingual lexicon, and how this is reflected on the dynamics of lexical access during word comprehension and production is unclear.
+
+Using the experimental paradigm developed by [@arias2009lexical; @arias2013s; @singh2014one] compared within and across language
+priming effects in Chinese-English toddlers.
+@kuipers2015bilingualism compared ERP responses to picture-word pairs in English monolinguals and Welsh-English bilinguals where the words were either semantically related or unrelated to a pictured object.
+Although both studies tested 30-month-olds, the conclusions the authors reached do not fully agree.
+@singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
 
 There is evidence of cascaded activation during lexical access.
-
 @chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
@@
 Four seconds after pictures onset, a word-form was auditorily presented.
-The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category.
+The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category).
 For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
@@
 
-Another important source of evidence in favour of a cascaded activation account comes from studies on implicit naming.
-@mani2010infant showed that 18 month-old infants implicitly generate the labels of name-known pictures presented in silence.
+Bilinguals' trajectories of word recognition  [@vihman2013]
+
+@floccia2020translation tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
+The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, Fench, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
+A prime word was embedded at the end of a carrier sentence that participants listened to.
+Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
+In Study 1, the target word was the translation equivalent of the prime word (*cheese*-*fromage* for an English-French bilingual).
+In other trials, prime and target words were unrelated (e.g., *sock*-*fromage*).
+There was no phonological overlap at onset between prime and target or distractor labels in either of the two conditions.
+Participants were presented with two blocks of related and unrelated trials.
+In one of the blocks, participants were presented with English prime words and Home Language target words (*sock*-*fromage*), and in the other block they were presented with Additional Language prime words and English target words (*fromage*-*sock*).
+The authors found a cross-linguistic priming effect, in which participants showed a stronger preference for the target picture in the post-naming phase in related trials, as compared to unrelated trials.
+This effect was found regardless of the language of the prime (English or Home Language), or the dominance of the language of the prime (i.e., whether the prime word belonged to the dominant language).
+Target preference exceeded chance level in both conditions.
+In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priing task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vive versa).
+This time, prime and target words were not translation equivalents, butr rather words whose referents shared semantic features.
+Results from Study  2 were parallel to those from Study 1.
+The authors found a strong semantic priming effect accross languages, regardless of the language of the prime or the dominance of the language of the prime.
+Overall these results suggest that bilinguals recognosed target words in both conditions, and benefitted from a cross-linguistic facilitation effect from translation equivalents.
+The symmetry of such effect across both languages suggests that participants lexical access ocurred in parallel for the two members of translation equivalents.
+As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languiages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
+The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
+However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generatd by an interaction by the phonological and semantic overlap between cognate primes and targets.
+
+Another source of evidence supporting the language non-selective account of lexical access is provided by cross-languistic priming priuming thorught translation paradigms.
+In line with @floccia2020translation, @von2012language found that bilingual toddlers aged 21-to-43-months, and who were learning German and English, showed a stronger target preference in a German word recognition task after being primed with a phonologically related English word, which shared phonological onset with the prime word (e.g., *slide*-*Klide* [German for *dress*]), compared to when prime and target words were phonologically unrelated (e.g., *bottle*-*Ohr* [German for *ear*]).
+Interestingly, they also found evidence of such priming effect when participants were prime with an English word which was *not* phonologically related to the German target word, but rather its German translation was (e.g., *leg* [with German trasnlation *Bein*]-*Stein* [German for *stone*]).
+Altogether, these results indicate that bilingual toddlers activate translation equivalents in parallel during word recognition, and that the phonology of both labels may interact with lexical access in the recognition of subsequet words.
+Importantly, cross-linguitic priming through translation demonstrates that previous findings of a cognateness facilitation in word production and recognition do not result from the mere phonological overlap between auditorily presented and target labels, but also from the phonological overlap between the prime translation (not presented) and the target.
+
+Evidence from cognates.
+
+## Implicit naming
+
+The aforementioned studies use priming-though-translation paradigms.
+In these paradigms, cross-linguistic priming results from activation spreading from the lexical representation of the the (auditorily presented) prime word to the lexical representation of its translation through semantic associations (e.g., translation equivalence).
+When prime words are auditorily presented, the task design constraints the naming context to one of the languages.
+The consequence is a potential asymmtry between the activation dynamics of the lexical represetnation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
+This might lead to a lower strength, and higher lacenty of the activation of the translation.
+
+In the present study, we use an adaptation of an implicit naming paradigm by @mani2010infant, in which participants are primed with a picture, instead of an auditorily presented label.
+@mani2010infant showed that 18 month-old monolinguals implicitly generate the labels of name-known pictures presented in silence.
 In each trial, infants were presented with prime pictures presented in silence, and then with a target and a distractor picture, both presented side-by-side.
@@
 
-@mani2011phonological used the same paradigm in 24-months-old toddlers, and also found evidence of implicit naming, but in the opposite direction.
+@mani2011phonological used the same paradigm in 24-months-old monolinguals, and also found evidence of implicit naming, but in the opposite direction.
 After phonologically related primes, infants showed weaker target looking preference than after phonologically unrelated primes.
@@
 
-Evidence from cascaded activation in lexical access is also provided by bilinguals.
-The bilingual lexicon is language-non selective.
-There is strong evidence in support of bilinguals activating lexical representations from both languages during both speech production and comprehension.
-Previous studies on bilingual word production support a cascade account for lexical activation in which the phonology of non-selected lexical representations engages in excitatory or inhibitory dynamics in the lexical selection process.
-
-## Co-activation in adults
-
-How does language co-activation shape lexical development?
-Marian and Spivey (1999)
-Costa et al. (2000)
-
-## Evidence from co-activation though translation
-The role of cognates in lexical processing.
-
-Another source of evidence are studies studies involving phonological priming of non-cognates through translation. [SEE REFERENCES FROM VON HOLZEN 2012]
-
+Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
+@duta2012erp presented name-known pictures in silence for one second.
+After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
+In some trials the auditory label corresponded to a canonical realisation of the word-form.
+In other trials, the word was mispronounced.
+Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
+A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
+This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
+
+When extended to the bilingual case, this implicit naming task may offer bilingual participants with an uncontrained naming context in whcih the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
 Using an adaptation of @mani2010infant's implicit naming paradigm, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
@@
 
-Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
-@duta2012erp presented name-known pictures in silence for one second.
-After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
-In some trials the auditory label corresponded to a canonical realisation of the word-form.
-In other trials, the word was mispronounced.
-Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
-A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
-This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
-
-Floccia et al.
-(2020) tested toddlers in a cross-language priming paradigm.
-A prime word was embedded at the end of a carrier sentence that participants listened to.
-Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
-Some critiques:
-
-Evidence from cognates.
-
-- Since participants heard the auditory label in one of the languages, priming through translation might be compromised.
-- Translation equivalents (Exp.
-1) are more strongly related at the semantic level with each other than other pairs of semantically related words that are not translations of each other (table-mesa are more strongly associated than table-silla).
-- We used longitudinal participants, so we can examine the developmental trajectories of cross-language lateral inhibitory or excitatory connections better.
-- Larger sample size.
-
-Onset vs. offset overlap:
-
-- Wu and Thierry (2011): rhyme
+The role of cognates in lexical processing.
+
+This study also provides a more suitable design for drawing conslusions about developmental change in word recognition trajectories frot wo reasons.
+First, it extends the age range of participants, compared to previous studies.
+Second, participants were tested at three selected age points to ensure a more balanced sample size across ages.
+Third, the partially longitudinal design allows modelling the performance of participants across testing sessions altogether.
+
+. In order to circumvent the problem of limited vocabulary knowledge
+in the non-dominant language, we propose to test participants only in their dominant language, therefore
+directing our research to the question of how possessing a second language affects processing of the
+dominant one in bilingual toddlers [@costa2014does provide a fuller description of the
+advantages of such approach].
 
@@
 
+## Summary
+
+## Context
+
+## Facilitation vs. inhibition
+
+## Onsets vs. offsets
+
+## Problems and generalisatility
+
+## Future steps
+
+## Conclusions
+
 # References

### 2023-10-26 manuscript/manuscript.qmd
Add supplementary vocabulary checklists and describe GAMMS

--- 2023-10-19 manuscript/manuscript.qmd
@@
 #| warning: false
-# load objects -----------------------------------------------------------------
-
-targets::tar_config_set(store = here::here('_targets'),
-						script = here::here('_targets.R'))
+# load objects
+targets::tar_config_set(store = here::here("_targets"),
+						script = here::here("_targets.R"))
 
@@
 	c(participants,
-	  participants_oxf,
 	  stimuli,
-	  stimuli_oxf,
 	  vocabulary,
-	  vocabulary_oxf,
 	  attrition_trials, 
 	  attrition_participants,
-	  attrition_trials_vtarget,
-	  attrition_participants_vtarget,
-	  attrition_trials_vnone, 
-	  attrition_participants_vnone,
-	  attrition_trials_noeach,
-	  attrition_participants_noeach,
-	  attrition_trials_vnoeach,
-	  attrition_participants_vnoeach,
-	  attrition_trials_oxf, 
-	  attrition_participants_oxf,
-	  attrition_trials_vtarget_oxf,
-	  attrition_participants_vtarget_oxf,
-	  attrition_trials_vnone_oxf, 
-	  attrition_participants_vnone_oxf,
-	  attrition_trials_noeach_oxf,
-	  attrition_participants_noeach_oxf,
-	  attrition_trials_vnoeach_oxf,
-	  attrition_participants_vnoeach_oxf,
 	  bvq_data, 
 	  gaze_aoi, 
-	  looking_times,
+	  data_related,
+	  data_cognate,
 	  data_time_related, 
 	  data_time_cognate,
-	  data_time_related_vtarget,
-	  data_time_cognate_vtarget,
-	  data_time_related_vnone,
-	  data_time_cognate_vnone,
-	  data_time_related_noeach, 
-	  data_time_cognate_noeach,
-	  data_time_related_vnoeach,
-	  data_time_cognate_vnoeach,
-	  data_time_related_oxf, 
-	  data_time_cognate_oxf,
-	  data_time_related_vtarget_oxf,
-	  data_time_cognate_vtarget_oxf,
-	  data_time_related_vnone_oxf,
-	  data_time_cognate_vnone_oxf,
-	  data_time_related_noeach_oxf, 
-	  data_time_cognate_noeach_oxf,
-	  data_time_related_vnoeach_oxf,
-	  data_time_cognate_vnoeach_oxf
 	))
@@
 	  model_fits_cognate,
-	  model_fits_related_vtarget,
-	  model_fits_cognate_vtarget,
-	  model_fits_related_vnone,
-	  model_fits_cognate_vnone,
-	  model_fits_related_noeach,
-	  model_fits_cognate_noeach,
-	  model_fits_related_vnoeach,
-	  model_fits_cognate_vnoeach
+	  # model_fits_related_time,
+	  # model_fits_cognate_time,
 	  # model_loo_related,
 	  # model_loo_cognate,
-	  # model_loo_related_vtarget,
-	  # model_loo_cognate_vtarget,
-	  # model_loo_related_vnone,
-	  # model_loo_cognate_vnone,
-	  # model_loo_related_noeach,
-	  # model_loo_cognate_noeach,
-	  # model_loo_related_vnoeach,
-	  # model_loo_cognate_vnoeach
 	))
@@
 library(english)
-
-# set ggplot theme and colour palette ------------------------------------------
+library(gtExtras)
+
+# set ggplot theme and colour palette
 
@@
 				 attrition_trials) |> 
-	purrr::reduce(left_join, by = join_by(filename))
-
-attrition_vtarget <- lst(participants,
-						 attrition_participants_vtarget,
-						 attrition_trials_vtarget) |> 
-	purrr::reduce(left_join, by = join_by(filename))
-
-attrition_vnone <- lst(participants,
-					   attrition_participants_vnone,
-					   attrition_trials_vnone) |> 
-	purrr::reduce(left_join, by = join_by(filename))
-
-attrition_noeach <- lst(participants,
-						attrition_participants_noeach,
-						attrition_trials_noeach) |> 
-	purrr::reduce(left_join, by = join_by(filename))
-
-attrition_vnoeach <- lst(participants,
-						 attrition_participants_vnoeach,
-						 attrition_trials_vnoeach) |> 
-	purrr::reduce(left_join, by = join_by(filename))
-
-attrition_oxf <- lst(participants_oxf,
-					 attrition_participants_oxf,
-					 attrition_trials_oxf) |> 
-	purrr::reduce(left_join, by = join_by(id))
-
-attrition_vtarget_oxf <- lst(participants_oxf,
-							 attrition_participants_vtarget_oxf,
-							 attrition_trials_vtarget_oxf) |> 
-	purrr::reduce(left_join, by = join_by(id))
-
-attrition_vnone_oxf <- lst(participants_oxf,
-						   attrition_participants_vnone_oxf,
-						   attrition_trials_vnone_oxf) |> 
-	purrr::reduce(left_join, by = join_by(id))
-
-attrition_noeach_oxf <- lst(participants_oxf,
-							attrition_participants_noeach_oxf,
-							attrition_trials_noeach_oxf) |> 
-	purrr::reduce(left_join, by = join_by(id))
-
-attrition_vnoeach_oxf <- lst(participants_oxf,
-							 attrition_participants_vnoeach_oxf,
-							 attrition_trials_vnoeach_oxf) |> 
-	purrr::reduce(left_join, by = join_by(id))
+	reduce(inner_join, by = join_by(session_id)) |> 
+	unnest_wider(matches("all"), names_sep = "_")
 
@@
 #| label: participants-numbers
-n_participants_total <- length(unique(participants$id))
-
-n_participants_sessions <- count(participants, id, name = "n_sessions") |> 
+n_participants_total <- participants |> 
+	distinct(location, child_id) |> 
+	count(location)
+
+n_participants_sex <- participants |> 
+	distinct(location, sex, child_id) |> 
+	count(location, sex)
+
+n_participants_sessions <- count(participants,
+								 child_id,
+								 name = "n_sessions") |> 
 	count(n_sessions) |> 
@@
 
-n_sessions_age_group <- participants |> 
+n_sessions_lp <- participants |> 
 	summarise(across(age, lst(mean, sd, min, max)),
 			  n = n(),
-			  .by = c(age_group)) |> 
+			  .by = c(lp)) |> 
 	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
-	group_split(age_group) |> 
-	set_names(c("age_21", "age_25", "age_30"))
-
-n_sessions_dominance <- count(participants, test_language) |> 
+	group_split(lp) |> 
+	set_names(janitor::make_clean_names(unique(participants$lp)))
+
+n_sessions_dominance_lp <- count(participants, lp, test_language) |> 
 	group_split(test_language) |> 
-	set_names(c("catalan", "spanish"))
-
-n_sessions_dominance_age_group <- count(participants, age_group, test_language) |> 
-	group_split(test_language) |> 
-	set_names(c("catalan", "spanish")) |> 
-	map(\(x) group_split(x, age_group) |> 
-			set_names(c("age_21", "age_25", "age_30")))
+	set_names(c("catalan", "english", "spanish")) |> 
+	map(group_split, lp)
 
@@
 	group_split(lp) |> 
-	set_names(c("monolingual", "bilingual"))
-
-n_sessions_lp_age_group <- participants |> 
-	count(lp, age_group) |> 
-	group_split(lp) |> 
-	set_names(c("monolingual", "bilingual")) |> 
-	map(\(x) group_split(x, age_group) |> 
-			set_names(c("age_21", "age_25", "age_30")))
-```
-
-We collected data from `r n_participants_total` monolingual and bilingual participants living in the Metropolitan Area of Barcelona (Spain), who were exposed to at least Catalan and/or Spanish from birth.
-Families were recruited from maternity room in private hospitals in Barcelona, and contacted via phone when the child's age spanned between our age intervals of interest.
-Families were invited to participate at three age points: 21, 25, and 30 months.
-`r n_participants_sessions[[1]]$n` participants were tested at one age point,  `r n_participants_sessions[[2]]$n` at two age points, and `r n_participants_sessions[[3]]$n` at the three age points.
-In total, we gathered data from `r n_sessions_total$n` testing sessions: `r n_sessions_age_group$age_21$n` at 21 months (*Mean* = `r round(n_sessions_age_group$age_21$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_21$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_21$age_min`--`r n_sessions_age_group$age_21$age_max`), `r n_sessions_age_group$age_25$n` at 25 months (*Mean* = `r round(n_sessions_age_group$age_25$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_25$age_min`--`r n_sessions_age_group$age_25$age_max`), and `r n_sessions_age_group$age_30$n` at 30 months (*Mean* = `r round(n_sessions_age_group$age_30$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_30$age_min`--`r n_sessions_age_group$age_30$age_max`).
-
-### Language profile {#sec-lp}
+	set_names(c("monolingual_eng", "monolingual", "bilingual"))
+```
+
+We collected data from `r n_participants_total$n[1]` participants living in the Metropolitan Area of Barcelona (Spain) tested at the Laboratori de recerca en Infància at the Universitat Pompeu Fabra (`r n_participants_sex$n[1]` female, `n_participants_sex$n[2]` male), and `r n_participants_total$n[2]` participants living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford (`r n_participants_sex$n[3]` female, `n_participants_sex$n[4]`, `n_participants_sex$n[5]` not reported).
+Families were recruited from maternity room in private hospitals or from social media, and contacted via phone when the child's age spanned between 20 and 32 months.
+From the `r sum(n_participants_total$n)` children that participated, `r n_participants_sessions$session_1$n` participated once, `r n_participants_sessions$session_2$n` participated twice, and `r n_participants_sessions$session_3$n` participated three times.
+Recurrent participants were tested with at least XXX months of difference.
+We gathered a total of `r n_sessions_total$n` testing sessions: `r n_sessions_lp$monolingual_english$n` from participants in Oxford, and `r n_sessions_lp$monolingual$n + n_sessions_lp$bilingual$n` from participants in Barcelona.
 
@@
 Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
-The output of this interview is an estimated degree of exposure (DoE) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
-According to this estimate, we classified participants as Catalan- or Spanish-dominant if the language with highest DoE was Catalan or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
-We collected data from `r n_sessions_dominance$catalan$n` Catalan-dominant participants in Catalan (`r n_sessions_dominance_age_group$catalan$age_21$n` at 21 months, `r n_sessions_dominance_age_group$catalan$age_25$n` at 25 months, and `r n_sessions_dominance_age_group$catalan$age_30$n` at 30 months).
-We further classified participants as monolinguals if the DoE to their dominant language exceeded 80% of the total DoE to Catalan and Spanish, and as bilinguals otherwise.
-Participants with DoE to language other than Catalan or Spanish were excluded from analyses.
-This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
-@tbl-participants-lp shows a detailed description of the linguistic profile of our sample.
+The output of this interview is an estimated degree of exposure (*DoE*) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
+According to this estimate, we classified participants as Catalan-, English-, or Spanish-dominant if the language with highest *DoE* was Catalan, English, or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
+From the `r n_sessions_total$n` testing sessions, `r n_sessions_lp$monolingual_english$n` belonged to English monolinguals,  `r n_sessions_lp$monolingual$n` to Catalan or Spanish monolinguals, and  `r n_sessions_lp$bilingual$n` to Catalan-Spanish bilinguals.
+@tbl-participants shows a detailed description of the linguistic profile of our sample.
+
+```{r tbl-participants}
+#| label: tbl-partiicpants
+#| tbl-cap: "Demographic and linguistic profile of participants."
+participants |> 
+	unnest_wider(doe) |> 
+	select(-matches("others")) |> 
+	mutate(lp = case_when(
+		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
+		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
+		.default = lp)) |> 
+	arrange(desc(lp)) |> 
+	summarise(n = n(),
+			  across(age, lst(mean, sd, min, max)),
+			  across(matches("doe_"), lst(mean, sd)),
+			  age_vctr = list(age),
+			  .by = c(lp, test_language)) |> 
+	gt(rowname_col = "test_language",
+	   groupname_col = "lp") |> 
+	gt_plt_dist(age_vctr, type = "histogram") |> 
+	fmt_number(is.numeric, decimals = 1) |> 
+	fmt_integer(n) |> 
+	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
+	cols_merge_range(age_min, age_max) |> 
+	cols_merge_uncert(age_mean, age_sd) |> 
+	cols_merge_uncert(doe_catalan_mean, doe_catalan_sd) |> 
+	cols_merge_uncert(doe_english_mean, doe_english_sd) |> 
+	cols_merge_uncert(doe_spanish_mean, doe_spanish_sd) |> 
+	tab_spanner("Age (months)", matches("age")) |> 
+	tab_spanner("Catalan", matches("catalan")) |> 
+	tab_spanner("English", matches("english")) |> 
+	tab_spanner("Spanish", matches("spanish")) |> 
+	tab_spanner("Degree of Exposure (%)", matches("doe")) |> 
+	cols_label(n = "N",
+			   age_mean = "M (SD)",
+			   age_min = "Range",
+			   age_vctr = "Distribution",
+			   doe_catalan_mean = "M (SD)",
+			   doe_english_mean = "M (SD)",
+			   doe_spanish_mean = "M (SD)") |> 
+	tab_style(cell_text(style = "italic"),
+			  cells_column_labels()) |> 
+	tab_style(cell_text(weight = "bold"),
+			  cells_column_spanners())
+```
 
@@
 #| label: tbl-vocabulary
-#| tbl-cap: "Summary of participant vocabulary sizes.
-vocabulary sizes are expressed as percentage points, and summarised as the mean (*M*) and the standard deviation (*SD*).
-Total: proportion of words in both languages marked as *Understands*.
-L1: proportion of words in the dominant language marked as *Understands*.
-L2: proportion of words in the non-cominant language marked as *Understands*.
-Conceptual: proportion of translation equivalents for which at least one of the words has ben marked as *Understands*.
-TE: proportion of translation equivalents for which *both* words have been marked as *Understands*."
+#| tbl-cap: "Participant vocabulary sizes across ages and language profiles.
+Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
+Vocabulary size scores from the recurrent participants are shown linked."
 #| eval: false
 vocabulary |> 
-	left_join(select(participants, filename, id, age_group, lp),
-			  by = join_by(filename)) |> 
-	summarise(across(matches("prop"), 
-					 tibble::lst(mean, sd)),
-			  .by = c(age_group, lp)) |>
-	arrange(age_group, lp) |> 
-	gt(groupname_col = "age_group",
-	   rowname_col = "lp") |> 
-	cols_hide(lp) |> 
-	tab_spanner("Vocabulary size ", matches("prop")) |> 
-	cols_merge(c(total_prop_mean, total_prop_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(l1_prop_mean, l1_prop_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(l2_prop_mean, l2_prop_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(concept_prop_mean, concept_prop_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(te_prop_mean, te_prop_sd),
-			   pattern = "{1} ({2})") |> 
-	fmt_number(is.numeric,
-			   decimals = 1,
-			   scale_by = 100,
-			   drop_trailing_zeros = FALSE) |>
-	cols_label(total_prop_mean = "Total",
-			   l1_prop_mean = "L1",
-			   l2_prop_mean = "L2",
-			   concept_prop_mean = "Concept",
-			   te_prop_mean = "TE") |> 
-	tab_stub_indent(rows = everything(),
-					indent = 2) |> 
-	tab_style(cell_text(align = "left"),
-			  cells_stub())
+	inner_join(select(participants, child_id, session_id, age, lp),
+			   by = join_by(child_id, session_id)) |> 
+	pivot_longer(c(total_prop, l1_prop),
+				 names_to = "measure",
+				 values_to = "prop",
+				 names_transform = \(x) gsub("_prop", "", x)) |> 
+	mutate(lp = case_when(
+		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
+		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
+		.default = lp) |> 
+			factor(levels = c("Monolingual (English)",
+							  "Monolingual (Catalan or Spanish)",
+							  "Bilingual (Catalan-Spanish)")),
+		measure = if_else(measure=="l1", 
+						  "L1 vocabulary", 
+						  "Total vocabulary"),
+		is_imputed = if_else(is_imputed, "Imputed", "Observed") |> 
+			factor(levels = c("Observed", "Imputed"))) |> 
+	ggplot(aes(age, prop, colour = is_imputed)) +
+	facet_grid(measure ~ lp) +
+	geom_line(aes(group = child_id),
+			  alpha = 1/2,
+			  colour = "grey") +
+	geom_point() +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size (%)") +
+	theme(panel.grid = element_line(linetype = "dotted",
+									colour = "grey"),
+		  legend.position = "right",
+		  legend.title = element_blank())
 ```
@@
 
+## Data processing
+
+```{r dataset}
+n_trials <- nrow(attrition)
+n_sessions <- n_distinct(attrition$session_id)
+n_participants <- n_distinct(attrition$child_id)
+n_trials_valid <- nrow(filter(attrition,
+							  is_valid_participant,
+							  is_valid_trial))
+n_sessions_valid <- sum(attrition_participants$is_valid_participant)
+n_participants_valid <- n_distinct(
+	attrition[attrition$is_valid_participant, ]$child_id)
+
+n_exc_prime <- sum(!attrition$is_valid_gaze_all_prime)
+n_exc_test <- sum(!attrition$is_valid_gaze_all_test)
+n_exc_test_each <- sum(!attrition$is_valid_gaze_all_test_each)
+n_exc_vocab <- sum(!attrition$is_valid_vocab)
+n_exc_participants <- sum(!attrition_participants$is_valid_participant)
+
+n_longitudinal <- attrition |>
+	filter(is_valid_participant,
+		   is_valid_trial) |>
+	distinct(child_id, session_n) |> 
+	count(child_id, name = "times") |> 
+	count(times)
+```
+
+Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
+We excluded trials in which participants failed to provide 50%  valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target-looking *and* distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
+Finally, we excluded trials in which participants did not understand the prime *or* the target word, according to a supplementary vocabulary checklist filled by their caregivers upon experiment completion (*n* = `r format(n_exc_vocab, big.mark = ",")`).
+After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`).
+The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+@tbl-attrition-trials shows a detailed description of the trial attrition.
+
+```{r tbl-attrition}
+#| label: tbl-attrition
+#| tbl-cap: "Participant-level and trial-level sample size after applying inclusion criteria. The number of excluded participants and trials is indicated between parentheses."
+expanded <- expand(attrition, lp, trial_type, is_valid_trial)
+
+n_lp <- attrition |> 
+	distinct(is_valid_participant, lp, session_id) |> 
+	count(is_valid_participant, lp) |> 
+	pivot_wider(names_from = is_valid_participant,
+				values_from = n,
+				names_repair = janitor::make_clean_names) |> 
+	mutate(n_participants_true = true,
+		   n_participants_false = false) |> 
+	select(lp, true, false)
+
+attrition |> 
+	summarise(n_trials_true = sum(is_valid_trial),
+			  n_trials_false = sum(!is_valid_trial),
+			  .by = c(lp, trial_type)) |> 
+	arrange(desc(lp)) |> 
+	# across(n_trials, lst(mean, sd, sum), na.rm = TRUE),
+
+	pivot_wider(id_cols = lp,
+				names_from = c(trial_type),
+				values_from = matches("trials"),
+				names_repair = janitor::make_clean_names) |> 
+	left_join(n_lp, by = join_by(lp)) |> 
+	mutate(lp = case_when(
+		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
+		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
+		.default = lp)) |>
+	select(lp, true, false,
+		   matches("n_trials")) |> 
+	gt(rowname_col = "lp") |> 
+	tab_spanner("Participants", matches("participant")) |> 
+	tab_spanner("Trials", matches("trial")) |> 
+	fmt_integer(everything()) |> 
+	cols_merge(c(true, false),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_trials_true_cognate,
+				 n_trials_false_cognate),
+				 pattern = "{1} ({2})") |> 
+	cols_merge(c(n_trials_true_non_cognate,
+				 n_trials_false_non_cognate),
+				 pattern = "{1} ({2})") |> 
+	cols_merge(c(n_trials_true_unrelated, 
+				 n_trials_false_unrelated),
+				 pattern = "{1} ({2})") |> 
+	cols_label(true = "N", 
+			   n_trials_true_cognate = "Cognate",
+			   n_trials_true_non_cognate = "Non-cognate",
+			   n_trials_true_unrelated = "Unrelated") |> 
+	tab_style(cell_text(style = "italic"),
+			  cells_column_labels()) |>
+	grand_summary_rows(fns = list(label = md("*N*")) ~ sum(.),
+					   fmt = ~ fmt_integer(.))
+```
+
 ## Data analysis
 
-We defined our time window of interest from 300 ms after the onset of the test phase (target and distractor presentation) until the end of the test phase (2,000 ms).
-For each trial, we chunked the time domain into 17 time bins of 100 ms of duration.
-We then calculated, for each experimental session, time bin, and condition, participant's proportion of target and distractor fixations.
-Finally, we computed the empirical logit of target fixations, which we introduced in the statistical analyses as our response variable.
-Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach].
-
 We conducted two main analyses.
-First, we estimated the effect of phonological priming on participants' target looking, comparing *related* trials with *unrelated* trials.
+In the first analysis, we estimated the effect of phonological priming on participants' target looking comparing *related* trials---in which prime and target share phonological onset, and the prime was not a cognate word---with *unrelated* trials---in which prime and target did not share phonological onset, and neither was the prime a cognate word, leaving out *cognate* trials.
 This analysis included all trials on the data set.
-Second, we estimated the effect of cognateness on phonological priming, comparing *cognate* with *non-cognate* trials, leaving out *unrelated* trials.
-In both analyses, we used General Additive Mixed Models (GAMMs) to model the probability of target fixations across the time course of the trial using a normal distribution.
-
-In the first analysis.
-We included *Relatedness* (`Related` vs.
+Second, we estimated the effect of cognateness on phonological priming, comparing *cognate* trials---in which prime and target shared phonological onset, and the prime was a cognate word that also shared phonological onset with the target, with *non-cognate* trials---in which prime a target shared phonological onset, and the prime was not a cognate---, leaving out *unrelated* trials.
+
+In both analyses, we modelled the probability of target looking across the time course of the trial.
+For each trial, we chunked the time domain of the target-distractor phase into 20 time bins of 100 ms of duration.
+We then calculated, for each experimental session, time bin, and condition, the number of eye-tracker samples in which the participant was looking to the target and the distractor pictures.
+Finally, we computed the empirical logit of target fixations using @eq-elogit [@barr2008analyzing; @agresti2012categorical], which modelled in our analyses using a Gaussian distribution.
+
+$$
+\eta' = \ln\bigg(\frac{\text{Target} + 0.5}{ \text{Distractor} + 0.5}\bigg)
+$$ {#eq-elogit}
+
+In the first analysis, we included *Relatedness* (`Related` vs.
 `Unrelated`, sum-coded as `-0.5` and `+0.5`), *Group* (`Monolingual` vs.
-`Bilingual`, sum-coded as `-0.5` and `+0.5`), and *Age* (participants' standardised age in months) as fixed, main effects.
-We also included cubic regression splines for the main effect of *Time*, and one for an adjustment of the previous cubic spline by *Group* [@wood2017generalized].
-For both splines, we specified $k = 10$ basis functions or *knots*--half the number of time bins, for computational convenience.
-Finally, we added by-participant random intercepts, and random slopes for the main effect of *Relatedness* and the main effect of *Age*, both including repeated measures per participant.
+`Bilingual`, sum-coded as `-0.5` and `+0.5`), and *Age* (participants' standardised age in months) as fixed, main effects, together with their two- and three-way interactions.
+We used multilevel General Additive Mixed Models (GAMMs) to model the time course of target looking, including cubic regression splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
+For both splines, we specified $k = 10$ basis functions or *knots*--half the number of time bins---for computational convenience.
+Finally, we added by-participant random intercepts, and random slopes for the main effect of *Relatedness* and the main effect of *Age*, both including repeated measures per participant [@pedersen2019hierarchical].
+In the second analysis, we included *Cognateness* (`Cognate` vs.
+`Non-cognate`, sum-coded as `-0.5` and `+0.5`) replacing *Relatedness*.
+@eq-model shows the formal implementation of the model.
 
@@
 y_i &\sim \mathcal{N}(\mu_i, \sigma_i) \\ \\
-\textbf{Linear model} \\
-\text{logit}(\mu_i) &= (\beta_0 + u _{0_{i}}) + (\beta_1 + u _{1_{i}}) \cdot \text{Relatedness} + \beta_{2} \cdot \text{Group} + \\
-&\beta_{3} \cdot (\text{Relatedness} \times \text{Group}) + (\beta_4 + u_{3_{i}}) \cdot \text{Age} + \\
-&\sum_{j = 1}^k b_{j_{1}}(\beta_{5_{k}} + u_{4_{i}}) \cdot \text{Time} + \\
-&\sum_{j = 1}^k b_{j_{1}} (\beta_{6_{k }} + u_{5_{i}}) \cdot (\text{Time} \times \text{Group}) \\
+\textbf{Linear model:} \\
+\eta'(\mu_i) &= (\beta_0 + u _{0_{i}}) + (\beta_1 + u _{1_{i}}) \cdot \text{[Condition]} +\\
+&\beta_{2} \cdot \text{Group} + \beta_{3} \cdot (\text{[Condition]} \times \text{Group}) +\\
+& (\beta_4 + u_{2_{i}}) \cdot \text{Age} + \sum_{j = 1}^k b_{j_{1}} \cdot \beta_{5_{k}} \cdot \text{Time} + \sum_{j = 1}^k b_{j_{1}} \cdot\beta_{6_{k}} \cdot (\text{Time} \times \text{Group}) \\
 \text{where:} \\
+&\eta'\text{ is the empirical logit of target fixations} \\
+& \text{[Condition] should be replaced with } Relatedness \text{ or } Cognateness \\
 &k \text{ is the number of knots in the spline (10)} \\
 \textbf{Prior:} \\
-\beta_{0-6} &\sim \mathcal{N}(0, 1) \\
-b_{0-1} &\sim MVN(0, 1) \\
-\sigma_i &\sim Exp(4) 
+\beta_{0-6} &\sim \mathcal{N}(0, 0.5) \\
+u_{0-2} &\sim \mathcal{N}(0, \sigma_{0-2})\\
+b_{0-1} &\sim \text{MVN}(0, \tau_{0-1}) \\
+\sigma_{0-2}, \tau_{0-1} &\sim \text{Exponential}(6)\\
+\rho_{0-2} &\sim LKJCorr(6)\\
+\text{where:}\\
+&\rho_{0-2} \text{ are the correlation parameters for } \sigma_{0-2}
 \end{aligned}
-$$
+$$ {#eq-model}
 
@@
 
-We know present the results under four different trial-level inclusion criteria.
-In Analysis 1, the child is required to understand the prime *and* the target words, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
-In Analysis 2, the child is required to understand the target word, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
-In Analysis 3, the child is not required to understand any word, but is still required to fixate both target and distractor for at last 50 ms each during the target-distractor phase.
-In Analysis 4, the child is not required to understand any word, nor to fixate at both target and distractor.
-In Analysis 5, the child is required to understand the prime *and* target words, but is not required to look at both target *and* distractor in the test phase.
-
-::: {.callout-note}
-
-@floccia2020translation required participants to know prime and target, but not to look at target *and* distractor (looking at at least one of them is enough).
-@mani2010infants did not require participants to know either word, but required infants to *not* look exclusively to the target or the distractor throughout the trial, and in an alternative analysis, to *not* look exclusively to the distractor.
-
-The fact that in some time course analyses participants seem to be looking predominantly towards one of the objects (despite the target and distractor pictures having been presented less than 300 ms before) is a common finding in previous studies using preferential looking procedures [e.g., @floccia2020translation].
-
-:::
-
-```{r tbl-multi-trials}
-#| tbl-cap: "Number of valid trials by age group, profile, and attrition criteria."
-tibble::lst(data_time_related,
-			data_time_related_oxf,
-			data_time_related_vtarget,
-			data_time_related_vtarget_oxf,
-			data_time_related_vnone,
-			data_time_related_vnone_oxf,
-			data_time_related_noeach,
-			data_time_related_noeach_oxf,
-			data_time_related_vnoeach,
-			data_time_related_vnoeach_oxf) |> 
-	bind_rows(.id = "analysis") |>
-	mutate(analysis_lab = case_when(
-		analysis=="data_time_related" ~ "Analysis 1",
-		grepl("_vtarget", analysis) ~ "Analysis 2",
-		grepl("_vnone", analysis) ~ "Analysis 3",
-		grepl("_noeach", analysis) ~ "Analysis 4",
-		grepl("_vnoeach", analysis) ~ "Analysis 5",
-		.default = "Analysis 1"
-	),
-	lp = case_when(grepl("_oxf", analysis) ~ "Monolingual (Oxford)", 
-				   lp=="Bilingual" ~ "Bilingual (Barcelona)",
-				   .default = "Monolingual (Barcelona)"),
-	lp = factor(lp, 
-				levels = c("Monolingual (Oxford)",
-						   "Monolingual (Barcelona)",
-						   "Bilingual (Barcelona)")),
-	condition = factor(condition, levels = c("Related", "Unrelated"))) |> 
-	distinct(analysis, analysis_lab, lp, condition, .ntrials) |> 
-	summarise(.ntrials = sum(.ntrials),
-			  .by = c(lp, analysis_lab, condition)) |> 
-	pivot_wider(names_from = c(lp, condition),
-				values_from = .ntrials,
-				names_repair = janitor::make_clean_names) |> 
-	relocate(analysis_lab,
-			 monolingual_barcelona_related,
-			 monolingual_barcelona_unrelated,
-			 bilingual_barcelona_related,
-			 bilingual_barcelona_unrelated,
-			 monolingual_oxford_related,
-			 monolingual_oxford_unrelated) |> 
-	gt(rowname_col = "analysis_lab") |> 
-	tab_spanner("Bilingual", matches("bilingual")) |>
-
-	tab_spanner("Monolingual", matches("monolingual")) |> 
-	tab_spanner("Barcelona", matches("barcelona")) |> 
-	tab_spanner("Oxford", matches("oxford")) |>
-
-	cols_label(monolingual_oxford_related = "Related",
-			   monolingual_oxford_unrelated = "Unrelated",
-			   monolingual_barcelona_related = "Related",
-			   monolingual_barcelona_unrelated = "Unrelated",
-			   bilingual_barcelona_related = "Related",
-			   bilingual_barcelona_unrelated = "Unrelated")
-
-```
-
-```{r fig-related-summary}
-#| label: fig-related-summary
-#| fig-height: 6.5
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-tibble::lst(data_time_related,
-			data_time_related_oxf,
-			data_time_related_vtarget,
-			data_time_related_vtarget_oxf,
-			data_time_related_vnone,
-			data_time_related_vnone_oxf,
-			data_time_related_noeach,
-			data_time_related_noeach_oxf,
-			data_time_related_vnoeach,
-			data_time_related_vnoeach_oxf) |> 
-	bind_rows(.id = "analysis") |>
-	mutate(analysis_lab = case_when(
-		analysis=="data_time_related" ~ "Analysis 1",
-		grepl("_vtarget", analysis) ~ "Analysis 2",
-		grepl("_vnone", analysis) ~ "Analysis 3",
-		grepl("_noeach", analysis) ~ "Analysis 4",
-		grepl("_vnoeach", analysis) ~ "Analysis 5",
-		.default = "Analysis 1"
-	),
-	lp = ifelse(grepl("_oxf", analysis), 
-				"Monolingual (English)", 
-				as.character(lp)),
-	lp = factor(lp, levels = c("Monolingual (English)",
-							   "Monolingual",
-							   "Bilingual"))) |> 
-	# summarise(.elog_mean = mean(.elog),
-	# 		  n = n(),
-	# 		  .elog_std = sd(.elog),
-	# 		  .by = c(condition, timebin, analysis, lp)) |>
-	# mutate(.elog_se = .elog_std/n) |> 
-	ggplot(aes(timebin, .elog,
-			   colour = condition,
-			   fill = condition,
-			   shape = condition)) +
-	facet_grid(analysis_lab~lp) +
-	geom_hline(yintercept = 0.5, 
-			   linewidth = 1/2,
-			   colour = "black",
-			   linetype = "dotted") +
-	geom_smooth(method = lm, 
-				se = FALSE, 
-				formula = y ~ splines::bs(x, 4)) +
-	# geom_errorbar(aes(ymin = .elog_mean - .elog_se*1.96, 
-	# 				  ymax = .elog_mean + .elog_se*1.96),
-	# 			  width = 0.25,
-	# 			  linewidth = 3/4) + 
-	# geom_line(size = 3/4) + 
-	stat_summary(fun = mean, geom = "point") +
+```{r fig-ptlt-descriptive}
+#| label: fig-ptlt-descriptive
+#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+data_time_related |> 
+	summarise(.elog = mean(.elog),
+			  .by = c(session_id, timebin, lp, condition)) |> 
+	ggplot(aes(timebin, .elog, colour = condition, fill = condition)) +
+	facet_wrap(~lp) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
 	stat_summary(fun.data = mean_se,
 				 geom = "errorbar",
-				 width = 0.25) +
-	labs(x = "Time (ms)",
+				 width = 0.5) +
+	stat_summary(fun = mean,
+				 geom = "line") +
+	stat_summary(fun = mean,
+				 geom = "point") +
+	theme(axis.title.x = element_blank()) +
+
+	data_time_cognate |> 
+	summarise(.elog = mean(.elog),
+			  .by = c(session_id, timebin, lp, condition)) |> 
+	ggplot(aes(timebin, .elog, colour = condition, fill = condition)) +
+	facet_wrap(~lp) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	stat_summary(fun.data = mean_se,
+				 geom = "errorbar",
+				 width = 0.5) +
+	stat_summary(fun = mean,
+				 geom = "line") +
+	stat_summary(fun = mean,
+				 geom = "point") +
+	theme(strip.text = element_blank()) +
+
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") &
+	labs(x = "Time bin (100 ms)",
 		 y = "P(Target looking)",
 		 colour = "Condition",
-		 fill = "Condition",
-		 linetype = "Condition",
-		 shape = "Condition") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) +
-	# scale_shape_manual(values = c(1, 2)) +
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) +
-	theme(legend.title = element_blank(),
-		  axis.title.x = element_blank(),
-		  panel.border = element_rect(fill = NA),
-		  axis.line = element_line(),
-		  legend.position = "top") 
-```
-
-```{r fig-cognate-summary}
-#| label: fig-cognate-summary
-#| fig-height: 6.5
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs.
-Lines and inetervals indicate the mean and 95% credible intervals of the posterior probability of target looking across the time course of the trial.
-Points indicate the mean probability of target looking across participants.
-In Analysis 1, the child is required to understand the prime *and* the target words, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
-In Analysis 2, the child is required to understand the target word, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase.
-In Analysis 3, the child is not required to understand any word, but is still required to fixate both target and distractor for at last 50 ms each during the target-distractor phase.
-In Analysis 4, the child is not required to understand any word, nor to fixate at both target and distractor.
-In Analysis 5, the child is required to understand the prime *and* target words, but is not required to look at both target *and* distractor in the test phase."
-tibble::lst(data_time_cognate,
-			data_time_cognate_oxf,
-			data_time_cognate_vtarget,
-			data_time_cognate_vtarget_oxf,
-			data_time_cognate_vnone,
-			data_time_cognate_vnone_oxf,
-			data_time_cognate_noeach,
-			data_time_cognate_noeach_oxf,
-			data_time_cognate_vnoeach,
-			data_time_cognate_vnoeach_oxf) |> 
-	bind_rows(.id = "analysis") |>
-	mutate(analysis_lab = case_when(
-		analysis=="data_time_cognate" ~ "Analysis 1",
-		grepl("_vtarget", analysis) ~ "Analysis 2",
-		grepl("_vnone", analysis) ~ "Analysis 3",
-		grepl("_noeach", analysis) ~ "Analysis 4",
-		grepl("_vnoeach", analysis) ~ "Analysis 5",
-		.default = "Analysis 1"
-	),
-	lp = ifelse(grepl("_oxf", analysis), 
-				"Monolingual (English)", 
-				as.character(lp)),
-	lp = factor(lp, levels = c("Monolingual (English)",
-							   "Monolingual",
-							   "Bilingual"))) |> 
-	# summarise(.elog_mean = mean(.elog),
-	# 		  n = n(),
-	# 		  .elog_std = sd(.elog),
-	# 		  .by = c(condition, timebin, analysis, lp)) |>
-	# mutate(.elog_se = .elog_std/n) |> 
-	ggplot(aes(timebin, .elog,
+		 fill = "Condition") &
+	# scale_y_continuous(breaks = seq(0, 1, 0.1)) &
+	theme(legend.position = "right",
+		  panel.grid.major.x = element_line(colour = "grey",
+		  								  linetype = "dotted"),
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+
+```
+
+### Phonological priming: Related vs. Unrelated primes
+
+In a first analysis, we examined the effect of phonological priming.
+We compared participants' looking preference for the target in related and unrelated trials.
+We first compared the aggregated probability of target looking across time bins in both conditions for each language group.
+
+```{r fig-related-aggregated}
+#| label: fig-related-aggregated
+#| fig-cap: "A) Aggregated probability of target looking for related and unrelated trials.
+Each point represents the mean probability of target looking for one participant in one testing session.
+Lines link observations from the same testing session across conditions.
+Black dots and errorbars indicate the mean and 95% CrI.
+B) Aggregated probability of target looking across ages for related and unrelated trials.
+Lines and error bands indicate the mean and standard error of the mean."
+nd <- expand(data_related, lp, condition, age = mean(data_related$age))
+
+epreds <- add_epred_draws(newdata = nd,
+						  object = model_fits_related[[1]],
+						  re_formula = NA) |> 
+	mean_qi() |> 
+	mutate(label = sprintf("%.2f\n[%.2f, %.2f]", .epred, .lower, .upper))
+
+epreds |> 
+	ggplot(aes(condition, .epred, 
 			   colour = condition,
-			   fill = condition,
-			   shape = condition)) +
-	facet_grid(analysis_lab~lp) +
-	geom_hline(yintercept = 0.5, 
-			   linewidth = 1/2,
+			   fill = condition)) +
+	facet_wrap(~lp) +
+	# geom_line(data = data_related,
+	# 		  aes(y = .elog,
+	# 		  	group = session_id),
+	# 		  colour = "grey",
+	# 		  alpha = 1/4) +
+	geom_dots(dat = data_related,
+			  aes(y = .elog,
+			  	side = ifelse(condition=="Related",
+			  				  "left", 
+			  				  "right")),
+			  show.legend = FALSE) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	geom_line(aes(group = lp),
 			  colour = "black",
-			   linetype = "dotted") +
-	geom_smooth(method = lm, 
-				se = FALSE, 
-				formula = y ~ splines::bs(x, 4)) +
-	# geom_errorbar(aes(ymin = .elog_mean - .elog_se*1.96, 
-	# 				  ymax = .elog_mean + .elog_se*1.96),
-	# 			  width = 0.25,
-	# 			  linewidth = 3/4) + 
-	# geom_line(size = 3/4) + 
-	stat_summary(fun = mean, geom = "point") +
-	stat_summary(fun.data = mean_se,
-				 geom = "errorbar",
-				 width = 0.25) +
-	labs(x = "Time (ms)",
+			  linewidth = 3/4) +
+	geom_errorbar(aes(ymin = .lower,
+					  ymax = .upper),
+				  width = 0.15,
+				  linewidth = 3/4,
+				  colour = "black") +
+	geom_point(size = 2, colour = "black") +
+	geom_label(aes(label = label,
+				   y = -1.5),
+			   fill = "white",
+			   colour = "black",
+			   label.r = unit(0, "lines"),
+			   label.size = 0,
+			   vjust = 0,
+			   size = 3,
+			   alpha = 1/2) +
+	labs(x = "Condition",
 		 y = "P(Target looking)",
 		 colour = "Condition",
-		 fill = "Condition",
-		 linetype = "Condition",
-		 shape = "Condition") +
-	scale_linetype_manual(values = rev(c("solid", "dashed"))) +
-	# scale_shape_manual(values = c(1, 2)) +
-	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
-											big.mark = ",")) +
-	theme(legend.title = element_blank(),
+		 fill = "Condition") +
+	scale_y_continuous(breaks = seq(-4, 4, 0.5)) +
+	theme(legend.position = "none",
 		  axis.title.x = element_blank(),
-		  panel.border = element_rect(fill = NA),
-		  axis.line = element_line(),
-		  legend.position = "top")
-```
-
-## Analysis 1
-
-::: {.callout-note}
-
-Participants must know **prime** *and* **target** words, and must look at least 10 ms to each target and distractor.
-
-:::
-
-```{r dataset}
-n_trials <- nrow(attrition_trials)
-n_total <- n_distinct(attrition_trials$id)
-n_trials_valid <- inner_join(attrition_participants,
-							 attrition_trials,
-							 by = join_by(id)) |> 
-	filter(is_valid_participant) |> 
-	pull(is_valid_trial) |> 
-	sum()
-n_participants_valid <- sum(attrition_participants$is_valid_participant)
-n_exc_prime <- sum(!attrition_trials$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition_trials$is_valid_gaze_test)
-n_exc_test_each <- sum(!attrition_trials$is_valid_gaze_test_each)
-n_exc_vocab <- sum(!attrition_trials$is_valid_vocab)
-n_exc_cognate <- sum(!attrition_participants$is_valid_cognate)
-n_exc_noncognate <- sum(!attrition_participants$is_valid_noncognate)
-n_exc_unrelated <- sum(!attrition_participants$is_valid_unrelated)
-
-n_longitudinal <- attrition_participants |>
-	filter(is_valid_participant) |>
-	count(id, name = "times") |> 
-	count(times)
-```
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
-We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples to *both* target and distractor in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
-Finally, we excluded trials in which participants did not understand the prime *or* the target word, according to a supplementary vocabulary checklist filled by their caregivers upon experiment completion (*n* = `r format(n_exc_vocab, big.mark = ",")`).
-After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
-The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition-trials shows a detailed description of the trial attrition.
-
-```{r tbl-participants-lp}
-#| label: tbl-participants-lp
-#| tbl-cap: "Participant details for Analysis 1.
-Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
-Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
-participants_tmp <- participants |> 
-	left_join(attrition_participants, by = join_by(filename)) |> 
-	mutate(id = as.character(id))
-
-participants_oxf_tmp <- participants_oxf |> 
-	inner_join(attrition_participants_oxf,
-			   by = join_by(id)) |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id))
-
-bind_rows(participants_tmp, participants_oxf_tmp) |> 
-	add_count(lp, 
-			  name = "n_lp") |> 
-	add_count(age_group, 
-			  name = "n_age_group") |> 
-	add_count(age_group,
-			  test_language,
-			  name = "n_age_test") |> 
-	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
-	summarise(across(c(age), lst(mean, sd)),
-			  n_inc = sum(is_valid_participant),
-			  n_exc = sum(!is_valid_participant),
-			  .by = c(age_group, lp, test_language)) |> 
-	pivot_wider(id_cols = c(test_language, lp),
-				names_from = c(age_group),
-				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
-				names_repair = janitor::make_clean_names) |>
-	relocate(lp, test_language, 
-			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
-			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
-			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
-	arrange(lp, test_language) |> 
-	gt(rowname_col = "test_language", 
-	   groupname_col = "lp", 
-	   row_group.sep = ": ") |> 
-	tab_spanner(md("21 months"), matches("21")) |> 
-	tab_spanner(md("25 months"), matches("25")) |>
-	tab_spanner(md("30 months"), matches("30")) |> 
-	fmt_number(matches("age"), decimals = 1) |>
-	cols_merge(c(n_inc_21_months, n_exc_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_25_months, n_exc_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_30_months, n_exc_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_21_months, age_sd_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_25_months, age_sd_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_30_months, age_sd_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_label(n_inc_21_months = md("*N*"),
-			   n_inc_25_months = md("*N*"),
-			   n_inc_30_months = md("*N*"),
-			   age_mean_21_months = "Age (months)",
-			   age_mean_25_months = "Age (months)",
-			   age_mean_30_months = "Age (months)") |> 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) |> 
-	tab_style(cell_text(size = "medium"),
-			  list(cells_body(),
-			  	 cells_stub())) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("n"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	grand_summary_rows(starts_with("n"), 
-					   fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~fmt_integer(.))
-```
-
-```{r tbl-attrition-trials}
-#| label: tbl-attrition-trials
-#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 1. Additional excluded trials are indicated between parentheses."
-attrition_oxf |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id)) |> 
-	bind_rows(mutate(attrition, id = as.character(id))) |> 
-	filter(is_valid_participant) |> 
-	summarise(n_valid = sum(is_valid_trial),
-			  n_total = n(),
-			  .by = c(id, age_group, lp, trial_type)) |> 
-	summarise(across(n_valid, lst(sum, mean, sd),
-					 .names = "{.fn}"),
-			  n_total = sum(n_total),
-			  .by = c(age_group, lp, trial_type)) |> 
-	mutate(n_excluded = n_total-sum) |> 
-	select(-c(n_total)) |> 
-	pivot_wider(names_from = trial_type,
-				values_from = c(sum:sd, n_excluded),
-				names_repair = janitor::make_clean_names) |> 
-	rename_with(\(x) gsub("non_cognate", "noncognate", x)) |> 
-	arrange(age_group) |> 
-	relocate(age_group,
-			 matches("_cognate"),
-			 matches("noncognate")) |> 
-	gt(rowname_col = "age_group",
-	   groupname_col = "lp") |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("sum"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 matches("mean"), 
-				 fns = list(label = md("*Mean*"), id = "totals") ~ mean(.),
-				 fmt = ~fmt_number(.)) |> 
-	grand_summary_rows(columns = matches("mean_"),
-					   fns = lst(Mean ~ mean(.)),
-					   fmt = ~fmt_number(.)) |>
-	grand_summary_rows(columns = matches("sum_"),
-					   fns = lst(Sum ~ sum(.)),
-					   fmt = ~fmt_integer(.)) |>
-	cols_merge(c(sum_cognate, n_excluded_cognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_unrelated, n_excluded_unrelated),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(mean_cognate, sd_cognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_noncognate, sd_noncognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_unrelated, sd_unrelated),
-			   pattern = "{1} ({2})") |>
-	tab_spanner("Cognate trials", ends_with("_cognate")) |>
-	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
-	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
-	tab_spanner("Related trials", matches("cognate")) |>
-	fmt_number(matches("mean|sd"), decimals = 1) |> 
-	fmt_integer(matches("sum"), sep_mark = ",") |> 
-	cols_label(sum_cognate = md("*N*"),
-			   sum_noncognate = md("*N*"),
-			   sum_unrelated = md("*N*"),
-			   mean_cognate = md("*Mean (SD)*"),
-			   mean_noncognate = md("*Mean (SD)*"),
-			   mean_unrelated = md("*Mean (SD)*"))
-```
-
-### Phonological priming: Related vs. Unrelated
+		  strip.background = element_rect(fill = "grey90",
+		  								colour = "grey90"),
+		  panel.grid.major.y = element_line(linetype = "dotted",
+		  								  colour = "grey")) 
+```
+
+#### Time course analysis
 
@@
 plot_gamm <- function(data, model, contrast = "related") {
+
 	epreds <- expand_grid(condition = levels(data$condition),
-						  timebin = seq(0, 17, length.out = 100),
-						  age = mean(data$age),
+						  timebin = seq(0, 20, length.out = 100),
+						  age = c(21, 25, 30),
 						  lp = levels(data$lp),
@@
 		add_epred_draws(model,
-						ndraws = NULL,
+						ndraws = 100,
 						re_formula = NA, 
 						value = ".value") |> 
-		mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))
+		mutate(lp = factor(lp, 
+						   levels = c("Monolingual (English)",
+						   		   "Monolingual",
+						   		   "Bilingual")),
+			   age = factor(age, levels = c(21, 25, 30),
+			   			 labels = paste0(c(21, 25, 30), " months")))
 
@@
 	data |> 
+		mutate(age = factor(age, levels = c(21, 25, 30),
+							labels = paste0(c(21, 25, 30), " months"))) |> 
 		summarise(.prop = mean(.prop),
-				  .by = c(id, timebin, lp, condition, age)) |> 
-		ggplot(aes(timebin, .prop, 
+				  .by = c(child_id, timebin, lp, condition, age))
+
+	epreds |> 
+		ggplot(aes(timebin, y = .value,
 				   colour = condition,
@@
 				   linetype = condition)) +
-		facet_wrap(~lp) +
-		stat_summary(data = epreds,
-					 aes(y = .value),
-					 fun.data = \(x) mean_qi(x, .width = 0.95),
+		facet_grid(age~lp) +
+		stat_summary(fun.data = \(x) mean_qi(x, .width = 0.95),
 					 geom = "ribbon",
@@
 					 linewidth = 0) +
-		stat_summary(data = epreds,
-					 aes(y = .value,
-					 	linetype = condition),
+		stat_summary(aes(linetype = condition),
 					 fun = "mean",
@@
 				   linetype = "dotted") +
-		stat_summary(fun.data = mean_se,
-					 geom = "errorbar",
-					 linetype = "solid",
-					 width = 0.25) +
-		stat_summary(fun = mean,
-					 geom = "point") +
+		# stat_summary(fun.data = mean_se,
+		# 			 geom = "errorbar",
+		# 			 linetype = "solid",
+		# 			 width = 0.25) +
+		# stat_summary(fun = mean,
+		# 			 geom = "point") +
 		labs(x = "Time (ms)",
@@
 		theme(legend.title = element_blank(),
-			  axis.title.x = element_blank()) +
+			  legend.position = "top",
+			  axis.title.x = element_blank())
 
@@
 		# scale_shape_manual(values = c(1, 2)) &
-		scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
+		scale_x_continuous(labels = \(x) format((x * 1e2), 
 												big.mark = ",")) &
@@
 
-plot_gamm(data_time_related, model_fits_related[[1]])
+plot_gamm(data_time_related, 
+		  model_fits_related[[1]],
+		  contrast = "related")
 
@@
 ### Cognate priming: Cognate vs. Non-cognate
+
+```{r fig-cognate-aggregated}
+#| label: fig-related-aggregated
+#| fig-cap: "A) Aggregated probability of target looking for cognate and non-cognate trials.
+Each point represents the mean probability of target looking for one participant in one testing session.
+Lines link observations from the same testing session across conditions.
+Black dots and errorbars indicate the mean and 95% CrI.
+B) Aggregated probability of target looking across ages for cognate and non-cognate trials.
+Lines and error bands indicate the mean and standard error of the mean."
+nd <- expand(data_cognate, lp, condition, age = mean(data_cognate$age))
+
+epreds <- add_epred_draws(newdata = nd,
+						  object = model_fits_cognate[[1]],
+						  re_formula = NA) |> 
+	mean_qi() |> 
+	mutate(label = sprintf("%.2f\n[%.2f, %.2f]", .epred, .lower, .upper))
+
+epreds |> 
+	ggplot(aes(condition, .epred, 
+			   colour = condition,
+			   fill = condition)) +
+	facet_wrap(~lp) +
+	# geom_line(data = data_cognate,
+	# 		  aes(y = .elog,
+	# 		  	group = session_id),
+	# 		  colour = "grey",
+	# 		  alpha = 1/4) +
+	geom_dots(dat = data_cognate,
+			  aes(y = .elog,
+			  	side = ifelse(condition=="Cognate",
+			  				  "left", 
+			  				  "right")),
+			  show.legend = FALSE) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	geom_line(aes(group = lp),
+			  colour = "black",
+			  linewidth = 3/4) +
+	geom_errorbar(aes(ymin = .lower,
+					  ymax = .upper),
+				  width = 0.15,
+				  linewidth = 3/4,
+				  colour = "black") +
+	geom_point(size = 2, colour = "black") +
+	geom_label(aes(label = label,
+				   y = -1.5),
+			   fill = "white",
+			   colour = "black",
+			   label.r = unit(0, "lines"),
+			   label.size = 0,
+			   vjust = 0,
+			   size = 3,
+			   alpha = 1/2) +
+	labs(x = "Condition",
+		 y = "P(Target looking)",
+		 colour = "Condition",
+		 fill = "Condition") +
+	scale_y_continuous(breaks = seq(-4, 4, 0.5)) +
+	theme(legend.position = "none",
+		  axis.title.x = element_blank(),
+		  strip.background = element_rect(fill = "grey90",
+		  								colour = "grey90"),
+		  panel.grid.major.y = element_line(linetype = "dotted",
+		  								  colour = "grey")) 
+```
+
+#### Time course analysis
 
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_cognate, model_fits_cognate[[1]], contrast = "cognate")
+plot_gamm(data_time_cognate,
+		  model_fits_cognate[[1]],
+		  contrast = "cognate")
 ```
@@
 {{< pagebreak >}}
-
-## Analysis 2
-
-::: {.callout-note}
-
-Participants must know the target **target** word (no need to know the prime word), and must look at least 10 ms to each target and distractor.
-
-:::
-
-```{r dataset-vtarget}
-n_trials <- nrow(attrition_trials_vtarget)
-n_trials_valid <- inner_join(attrition_participants_vtarget,
-							 attrition_trials_vtarget) |> 
-	filter(is_valid_participant) |> 
-	pull(is_valid_trial) |> 
-	sum()
-n_participants_valid <- sum(attrition_participants_vtarget$is_valid_participant)
-n_exc_prime <- sum(!attrition_trials_vtarget$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition_trials_vtarget$is_valid_gaze_test)
-n_exc_test_each <- sum(!attrition_trials_vtarget$is_valid_gaze_test_each)
-n_exc_vocab <- sum(!attrition_trials_vtarget$is_valid_vocab)
-n_exc_cognate <- sum(!attrition_participants_vtarget$is_valid_cognate)
-n_exc_noncognate <- sum(!attrition_participants_vtarget$is_valid_noncognate)
-n_exc_unrelated <- sum(!attrition_participants_vtarget$is_valid_unrelated)
-
-n_longitudinal <- attrition_participants_vtarget |>
-	filter(is_valid_participant) |>
-	count(id, name = "times") |> 
-	count(times)
-```
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
-We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples to *both* target and distractor in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
-Finally, we excluded trials in which participants did not understand the target word, according to a supplementary vocabulary checklist filled by their caregivers upon experiment completion (*n* = `r format(n_exc_vocab, big.mark = ",")`).
-After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
-The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition-trials shows a detailed description of the trial attrition.
-
-```{r tbl-participants-lp-vtarget}
-#| label: tbl-participants-lp-vtarget
-#| tbl-cap: "Participant details for Analysis 2.
-Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
-Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
-participants_tmp <- participants |> 
-	left_join(attrition_participants_vtarget, by = join_by(filename)) |> 
-	mutate(id = as.character(id))
-
-participants_oxf_tmp <- participants_oxf |> 
-	inner_join(attrition_participants_vtarget_oxf,
-			   by = join_by(id)) |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id))
-
-bind_rows(participants_tmp, participants_oxf_tmp) |> 
-	add_count(lp, 
-			  name = "n_lp") |> 
-	add_count(age_group, 
-			  name = "n_age_group") |> 
-	add_count(age_group,
-			  test_language,
-			  name = "n_age_test") |> 
-	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
-	summarise(across(c(age), lst(mean, sd)),
-			  n_inc = sum(is_valid_participant),
-			  n_exc = sum(!is_valid_participant),
-			  .by = c(age_group, lp, test_language)) |> 
-	pivot_wider(id_cols = c(test_language, lp),
-				names_from = c(age_group),
-				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
-				names_repair = janitor::make_clean_names) |>
-	relocate(lp, test_language, 
-			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
-			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
-			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
-	arrange(lp, test_language) |> 
-	gt(rowname_col = "test_language", 
-	   groupname_col = "lp", 
-	   row_group.sep = ": ") |> 
-	tab_spanner(md("21 months"), matches("21")) |> 
-	tab_spanner(md("25 months"), matches("25")) |>
-	tab_spanner(md("30 months"), matches("30")) |> 
-	fmt_number(matches("age"), decimals = 1) |>
-	cols_merge(c(n_inc_21_months, n_exc_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_25_months, n_exc_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_30_months, n_exc_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_21_months, age_sd_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_25_months, age_sd_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_30_months, age_sd_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_label(n_inc_21_months = md("*N*"),
-			   n_inc_25_months = md("*N*"),
-			   n_inc_30_months = md("*N*"),
-			   age_mean_21_months = "Age (months)",
-			   age_mean_25_months = "Age (months)",
-			   age_mean_30_months = "Age (months)") |> 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) |> 
-	tab_style(cell_text(size = "medium"),
-			  list(cells_body(),
-			  	 cells_stub())) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("n"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	grand_summary_rows(starts_with("n"), 
-					   fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~fmt_integer(.))
-```
-
-```{r tbl-attrition-trials-vtarget}
-#| label: tbl-attrition-trials-vtarget
-#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 2. Additional excluded trials are indicated between parentheses."
-attrition_vtarget_oxf |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id)) |> 
-	bind_rows(mutate(attrition, id = as.character(id))) |> 
-	filter(is_valid_participant) |> 
-	summarise(n_valid = sum(is_valid_trial),
-			  n_total = n(),
-			  .by = c(id, age_group, lp, trial_type)) |> 
-	summarise(across(n_valid, lst(sum, mean, sd),
-					 .names = "{.fn}"),
-			  n_total = sum(n_total),
-			  .by = c(age_group, lp, trial_type)) |> 
-	mutate(n_excluded = n_total-sum) |> 
-	select(-c(n_total)) |> 
-	pivot_wider(names_from = trial_type,
-				values_from = c(sum:sd, n_excluded),
-				names_repair = janitor::make_clean_names) |> 
-	rename_with(\(x) gsub("non_cognate", "noncognate", x)) |> 
-	arrange(age_group) |> 
-	relocate(age_group,
-			 matches("_cognate"),
-			 matches("noncognate")) |> 
-	gt(rowname_col = "age_group",
-	   groupname_col = "lp") |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("sum"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 matches("mean"), 
-				 fns = list(label = md("*Mean*"), id = "totals") ~ mean(.),
-				 fmt = ~fmt_number(.)) |> 
-	grand_summary_rows(columns = matches("mean_"),
-					   fns = lst(Mean ~ mean(.)),
-					   fmt = ~fmt_number(.)) |>
-	grand_summary_rows(columns = matches("sum_"),
-					   fns = lst(Sum ~ sum(.)),
-					   fmt = ~fmt_integer(.)) |>
-	cols_merge(c(sum_cognate, n_excluded_cognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_unrelated, n_excluded_unrelated),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(mean_cognate, sd_cognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_noncognate, sd_noncognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_unrelated, sd_unrelated),
-			   pattern = "{1} ({2})") |>
-	tab_spanner("Cognate trials", ends_with("_cognate")) |>
-	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
-	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
-	tab_spanner("Related trials", matches("cognate")) |>
-	fmt_number(matches("mean|sd"), decimals = 1) |> 
-	fmt_integer(matches("sum"), sep_mark = ",") |> 
-	cols_label(sum_cognate = md("*N*"),
-			   sum_noncognate = md("*N*"),
-			   sum_unrelated = md("*N*"),
-			   mean_cognate = md("*Mean (SD)*"),
-			   mean_noncognate = md("*Mean (SD)*"),
-			   mean_unrelated = md("*Mean (SD)*"))
-```
-
-### Phonological priming: Related vs. Unrelated
-
-```{r fig-related-vtarget}
-#| label: fig-related-vtarget
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 2.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_related_vtarget, 
-		  model_fits_related_vtarget[[1]], 
-		  contrast = "related")
-```
-
-### Cognate priming: Cognate vs. Non-cognate
-
-```{r fig-cognate-vtarget}
-#| label: fig-cognate-vtarget
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 2.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_cognate_vtarget, 
-		  model_fits_cognate_vtarget[[1]], 
-		  contrast = "cognate")
-```
-
-{{< pagebreak >}}
-
-## Analysis 3
-
-::: {.callout-note}
-
-Participants do not need to know the prime or target words, but must look at least 10 ms to each target and distractor.
-
-:::
-
-```{r dataset-vnone}
-n_trials <- nrow(attrition_trials_vnone)
-n_trials_valid <- inner_join(attrition_participants_vnone,
-							 attrition_trials_vnone) |> 
-	filter(is_valid_participant) |> 
-	pull(is_valid_trial) |> 
-	sum()
-n_participants_valid <- sum(attrition_participants_vnone$is_valid_participant)
-n_exc_prime <- sum(!attrition_trials_vnone$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition_trials_vnone$is_valid_gaze_test)
-n_exc_test_each <- sum(!attrition_trials_vnone$is_valid_gaze_test_each)
-n_exc_vocab <- sum(!attrition_trials_vnone$is_valid_vocab)
-n_exc_cognate <- sum(!attrition_participants_vnone$is_valid_cognate)
-n_exc_noncognate <- sum(!attrition_participants_vnone$is_valid_noncognate)
-n_exc_unrelated <- sum(!attrition_participants_vnone$is_valid_unrelated)
-
-n_longitudinal <- attrition_participants_vnone |>
-	filter(is_valid_participant) |>
-	count(id, name = "times") |> 
-	count(times)
-```
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
-We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples to *both* target and distractor in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
-After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
-The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition-trials shows a detailed description of the trial attrition.
-
-```{r tbl-participants-lp-vnone}
-#| label: tbl-participants-lp-vnone
-#| tbl-cap: "Participant details for Analysis 3.
-Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
-Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
-participants_tmp <- participants |> 
-	left_join(attrition_participants_vnone, by = join_by(filename)) |> 
-	mutate(id = as.character(id))
-
-participants_oxf_tmp <- participants_oxf |> 
-	inner_join(attrition_participants_vnone_oxf,
-			   by = join_by(id)) |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id))
-
-bind_rows(participants_tmp, participants_oxf_tmp) |> 
-	add_count(lp, 
-			  name = "n_lp") |> 
-	add_count(age_group, 
-			  name = "n_age_group") |> 
-	add_count(age_group,
-			  test_language,
-			  name = "n_age_test") |> 
-	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
-	summarise(across(c(age), lst(mean, sd)),
-			  n_inc = sum(is_valid_participant),
-			  n_exc = sum(!is_valid_participant),
-			  .by = c(age_group, lp, test_language)) |> 
-	pivot_wider(id_cols = c(test_language, lp),
-				names_from = c(age_group),
-				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
-				names_repair = janitor::make_clean_names) |>
-	relocate(lp, test_language, 
-			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
-			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
-			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
-	arrange(lp, test_language) |> 
-	gt(rowname_col = "test_language", 
-	   groupname_col = "lp", 
-	   row_group.sep = ": ") |> 
-	tab_spanner(md("21 months"), matches("21")) |> 
-	tab_spanner(md("25 months"), matches("25")) |>
-	tab_spanner(md("30 months"), matches("30")) |> 
-	fmt_number(matches("age"), decimals = 1) |>
-	cols_merge(c(n_inc_21_months, n_exc_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_25_months, n_exc_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_30_months, n_exc_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_21_months, age_sd_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_25_months, age_sd_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_30_months, age_sd_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_label(n_inc_21_months = md("*N*"),
-			   n_inc_25_months = md("*N*"),
-			   n_inc_30_months = md("*N*"),
-			   age_mean_21_months = "Age (months)",
-			   age_mean_25_months = "Age (months)",
-			   age_mean_30_months = "Age (months)") |> 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) |> 
-	tab_style(cell_text(size = "medium"),
-			  list(cells_body(),
-			  	 cells_stub())) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("n"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	grand_summary_rows(starts_with("n"), 
-					   fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~fmt_integer(.))
-```
-
-```{r tbl-attrition-trials-vnone}
-#| label: tbl-attrition-trials-vnone
-#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 3. Additional excluded trials are indicated between parentheses."
-attrition_vnone_oxf |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id)) |> 
-	bind_rows(mutate(attrition, id = as.character(id))) |> 
-	filter(is_valid_participant) |> 
-	summarise(n_valid = sum(is_valid_trial),
-			  n_total = n(),
-			  .by = c(id, age_group, lp, trial_type)) |> 
-	summarise(across(n_valid, lst(sum, mean, sd),
-					 .names = "{.fn}"),
-			  n_total = sum(n_total),
-			  .by = c(age_group, lp, trial_type)) |> 
-	mutate(n_excluded = n_total-sum) |> 
-	select(-c(n_total)) |> 
-	pivot_wider(names_from = trial_type,
-				values_from = c(sum:sd, n_excluded),
-				names_repair = janitor::make_clean_names) |> 
-	rename_with(\(x) gsub("non_cognate", "noncognate", x)) |> 
-	arrange(age_group) |> 
-	relocate(age_group,
-			 matches("_cognate"),
-			 matches("noncognate")) |> 
-	gt(rowname_col = "age_group",
-	   groupname_col = "lp") |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("sum"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 matches("mean"), 
-				 fns = list(label = md("*Mean*"), id = "totals") ~ mean(.),
-				 fmt = ~fmt_number(.)) |> 
-	grand_summary_rows(columns = matches("mean_"),
-					   fns = lst(Mean ~ mean(.)),
-					   fmt = ~fmt_number(.)) |>
-	grand_summary_rows(columns = matches("sum_"),
-					   fns = lst(Sum ~ sum(.)),
-					   fmt = ~fmt_integer(.)) |>
-	cols_merge(c(sum_cognate, n_excluded_cognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_unrelated, n_excluded_unrelated),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(mean_cognate, sd_cognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_noncognate, sd_noncognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_unrelated, sd_unrelated),
-			   pattern = "{1} ({2})") |>
-	tab_spanner("Cognate trials", ends_with("_cognate")) |>
-	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
-	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
-	tab_spanner("Related trials", matches("cognate")) |>
-	fmt_number(matches("mean|sd"), decimals = 1) |> 
-	fmt_integer(matches("sum"), sep_mark = ",") |> 
-	cols_label(sum_cognate = md("*N*"),
-			   sum_noncognate = md("*N*"),
-			   sum_unrelated = md("*N*"),
-			   mean_cognate = md("*Mean (SD)*"),
-			   mean_noncognate = md("*Mean (SD)*"),
-			   mean_unrelated = md("*Mean (SD)*"))
-```
-
-### Phonological priming: Related vs. Unrelated
-
-```{r fig-related-vnone}
-#| label: fig-related-vnone
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 3.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_related_vnone, 
-		  model_fits_related_vnone[[1]], 
-		  contrast = "related")
-```
-
-### Cognate priming: Cognate vs. Non-cognate
-
-```{r fig-cognate-vnone}
-#| label: fig-cognate-vnone
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 3.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_cognate_vnone, 
-		  model_fits_cognate_vnone[[1]], 
-		  contrast = "cognate")
-```
-
-{{< pagebreak >}}
-
-## Analysis 4
-
-::: {.callout-note}
-
-Participants do not need to know the prime or target words, and do not need to look to both pictures.
-
-:::
-
-```{r dataset-noeach}
-n_trials <- nrow(attrition_trials_noeach)
-n_trials_valid <- inner_join(attrition_participants_noeach,
-							 attrition_trials_noeach) |> 
-	filter(is_valid_participant) |> 
-	pull(is_valid_trial) |> 
-	sum()
-n_participants_valid <- sum(attrition_participants_noeach$is_valid_participant)
-n_exc_prime <- sum(!attrition_trials_noeach$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition_trials_noeach$is_valid_gaze_test)
-n_exc_test_each <- sum(!attrition_trials_noeach$is_valid_gaze_test_each)
-n_exc_vocab <- sum(!attrition_trials_noeach$is_valid_vocab)
-n_exc_cognate <- sum(!attrition_participants_noeach$is_valid_cognate)
-n_exc_noncognate <- sum(!attrition_participants_noeach$is_valid_noncognate)
-n_exc_unrelated <- sum(!attrition_participants_noeach$is_valid_unrelated)
-
-n_longitudinal <- attrition_participants_noeach |>
-	filter(is_valid_participant) |>
-	count(id, name = "times") |> 
-	count(times)
-```
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
-We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
-The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition-trials shows a detailed description of the trial attrition.
-
-```{r tbl-participants-lp-noeach}
-#| label: tbl-participants-lp-noeach
-#| tbl-cap: "Participant details for Analysis 4.
-Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
-Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
-participants_tmp <- participants |> 
-	left_join(attrition_participants_noeach, by = join_by(filename)) |> 
-	mutate(id = as.character(id))
-
-participants_oxf_tmp <- participants_oxf |> 
-	inner_join(attrition_participants_noeach_oxf,
-			   by = join_by(id)) |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id))
-
-bind_rows(participants_tmp, participants_oxf_tmp) |> 
-	add_count(lp, 
-			  name = "n_lp") |> 
-	add_count(age_group, 
-			  name = "n_age_group") |> 
-	add_count(age_group,
-			  test_language,
-			  name = "n_age_test") |> 
-	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
-	summarise(across(c(age), lst(mean, sd)),
-			  n_inc = sum(is_valid_participant),
-			  n_exc = sum(!is_valid_participant),
-			  .by = c(age_group, lp, test_language)) |> 
-	pivot_wider(id_cols = c(test_language, lp),
-				names_from = c(age_group),
-				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
-				names_repair = janitor::make_clean_names) |>
-	relocate(lp, test_language, 
-			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
-			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
-			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
-	arrange(lp, test_language) |> 
-	gt(rowname_col = "test_language", 
-	   groupname_col = "lp", 
-	   row_group.sep = ": ") |> 
-	tab_spanner(md("21 months"), matches("21")) |> 
-	tab_spanner(md("25 months"), matches("25")) |>
-	tab_spanner(md("30 months"), matches("30")) |> 
-	fmt_number(matches("age"), decimals = 1) |>
-	cols_merge(c(n_inc_21_months, n_exc_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_25_months, n_exc_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_30_months, n_exc_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_21_months, age_sd_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_25_months, age_sd_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_30_months, age_sd_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_label(n_inc_21_months = md("*N*"),
-			   n_inc_25_months = md("*N*"),
-			   n_inc_30_months = md("*N*"),
-			   age_mean_21_months = "Age (months)",
-			   age_mean_25_months = "Age (months)",
-			   age_mean_30_months = "Age (months)") |> 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) |> 
-	tab_style(cell_text(size = "medium"),
-			  list(cells_body(),
-			  	 cells_stub())) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("n"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	grand_summary_rows(starts_with("n"), 
-					   fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~fmt_integer(.))
-```
-
-```{r tbl-attrition-trials-vnone}
-#| label: tbl-attrition-trials-noeach
-#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 4. Additional excluded trials are indicated between parentheses."
-attrition_noeach_oxf |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id)) |> 
-	bind_rows(mutate(attrition, id = as.character(id))) |> 
-	filter(is_valid_participant) |> 
-	summarise(n_valid = sum(is_valid_trial),
-			  n_total = n(),
-			  .by = c(id, age_group, lp, trial_type)) |> 
-	summarise(across(n_valid, lst(sum, mean, sd),
-					 .names = "{.fn}"),
-			  n_total = sum(n_total),
-			  .by = c(age_group, lp, trial_type)) |> 
-	mutate(n_excluded = n_total-sum) |> 
-	select(-c(n_total)) |> 
-	pivot_wider(names_from = trial_type,
-				values_from = c(sum:sd, n_excluded),
-				names_repair = janitor::make_clean_names) |> 
-	rename_with(\(x) gsub("non_cognate", "noncognate", x)) |> 
-	arrange(age_group) |> 
-	relocate(age_group,
-			 matches("_cognate"),
-			 matches("noncognate")) |> 
-	gt(rowname_col = "age_group",
-	   groupname_col = "lp") |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("sum"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 matches("mean"), 
-				 fns = list(label = md("*Mean*"), id = "totals") ~ mean(.),
-				 fmt = ~fmt_number(.)) |> 
-	grand_summary_rows(columns = matches("mean_"),
-					   fns = lst(Mean ~ mean(.)),
-					   fmt = ~fmt_number(.)) |>
-	grand_summary_rows(columns = matches("sum_"),
-					   fns = lst(Sum ~ sum(.)),
-					   fmt = ~fmt_integer(.)) |>
-	cols_merge(c(sum_cognate, n_excluded_cognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_unrelated, n_excluded_unrelated),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(mean_cognate, sd_cognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_noncognate, sd_noncognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_unrelated, sd_unrelated),
-			   pattern = "{1} ({2})") |>
-	tab_spanner("Cognate trials", ends_with("_cognate")) |>
-	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
-	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
-	tab_spanner("Related trials", matches("cognate")) |>
-	fmt_number(matches("mean|sd"), decimals = 1) |> 
-	fmt_integer(matches("sum"), sep_mark = ",") |> 
-	cols_label(sum_cognate = md("*N*"),
-			   sum_noncognate = md("*N*"),
-			   sum_unrelated = md("*N*"),
-			   mean_cognate = md("*Mean (SD)*"),
-			   mean_noncognate = md("*Mean (SD)*"),
-			   mean_unrelated = md("*Mean (SD)*"))
-```
-
-### Phonological priming: Related vs. Unrelated
-
-```{r fig-related-noeach}
-#| label: fig-related-noeach
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 4.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_related_noeach, 
-		  model_fits_related_noeach[[1]], 
-		  contrast = "related")
-```
-
-### Cognate priming: Cognate vs. Non-cognate
-
-```{r fig-cognate-noeach}
-#| label: fig-cognate-noeach
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 4.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_cognate_noeach, 
-		  model_fits_cognate_noeach[[1]], 
-		  contrast = "cognate")
-```
-
-{{< pagebreak >}}
-
-## Analysis 5
-
-::: {.callout-note}
-
-Participants need to know the prime or target words, and do not need to look to both pictures.
-
-:::
-
-```{r dataset-vnoeach}
-n_trials <- nrow(attrition_trials_vnoeach)
-n_trials_valid <- inner_join(attrition_participants_vnoeach,
-							 attrition_trials_vnoeach) |> 
-	filter(is_valid_participant) |> 
-	pull(is_valid_trial) |> 
-	sum()
-n_participants_valid <- sum(attrition_participants_vnoeach$is_valid_participant)
-n_exc_prime <- sum(!attrition_trials_vnoeach$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition_trials_vnoeach$is_valid_gaze_test)
-n_exc_test_each <- sum(!attrition_trials_vnoeach$is_valid_gaze_test_each)
-n_exc_vocab <- sum(!attrition_trials_vnoeach$is_valid_vocab)
-n_exc_cognate <- sum(!attrition_participants_vnoeach$is_valid_cognate)
-n_exc_noncognate <- sum(!attrition_participants_vnoeach$is_valid_noncognate)
-n_exc_unrelated <- sum(!attrition_participants_vnoeach$is_valid_unrelated)
-
-n_longitudinal <- attrition_participants_vnoeach |>
-	filter(is_valid_participant) |>
-	count(id, name = "times") |> 
-	count(times)
-```
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_total` distinct participants.
-We excluded trials in which participants failed to provide 50% valid eye-tracking samples during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-After applying these trial-level inclusion criteria, we excluded participants who did not provide at least two valid trials in the *cognate prime* condition (*n* = `r n_exc_cognate`), the *non-cognate prime* condition (*n* = `r n_exc_noncognate`), or the *unrelated prime* condition (*n* = `r n_exc_unrelated`).
-The resulting dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_participants_valid` participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition-trials shows a detailed description of the trial attrition.
-
-```{r tbl-participants-lp-vnoeach}
-#| label: tbl-participants-lp-vnoeach
-#| tbl-cap: "Participant details for Analysis 5.
-Sample sizes indicate the number of participants included and excluded (between parenthesis) after applying inclusion criteria.
-Age is summarised using the mean and standard deviation (betwen parenthesis) for each age and language group separately."
-participants_tmp <- participants |> 
-	left_join(attrition_participants_vnoeach, by = join_by(filename)) |> 
-	mutate(id = as.character(id))
-
-participants_oxf_tmp <- participants_oxf |> 
-	inner_join(attrition_participants_vnoeach_oxf,
-			   by = join_by(id)) |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id))
-
-bind_rows(participants_tmp, participants_oxf_tmp) |> 
-	add_count(lp, 
-			  name = "n_lp") |> 
-	add_count(age_group, 
-			  name = "n_age_group") |> 
-	add_count(age_group,
-			  test_language,
-			  name = "n_age_test") |> 
-	mutate(lp = factor(lp, levels = rev(unique(lp)))) |> 
-	summarise(across(c(age), lst(mean, sd)),
-			  n_inc = sum(is_valid_participant),
-			  n_exc = sum(!is_valid_participant),
-			  .by = c(age_group, lp, test_language)) |> 
-	pivot_wider(id_cols = c(test_language, lp),
-				names_from = c(age_group),
-				values_from = c(matches("doe"), age_mean, age_sd, n_inc, n_exc),
-				names_repair = janitor::make_clean_names) |>
-	relocate(lp, test_language, 
-			 n_inc_21_months, n_exc_21_months, age_mean_21_months, age_sd_21_months,
-			 n_inc_25_months, n_exc_25_months, age_mean_25_months, age_sd_25_months,
-			 n_inc_30_months, n_exc_30_months, age_mean_30_months, age_sd_30_months) |> 
-	arrange(lp, test_language) |> 
-	gt(rowname_col = "test_language", 
-	   groupname_col = "lp", 
-	   row_group.sep = ": ") |> 
-	tab_spanner(md("21 months"), matches("21")) |> 
-	tab_spanner(md("25 months"), matches("25")) |>
-	tab_spanner(md("30 months"), matches("30")) |> 
-	fmt_number(matches("age"), decimals = 1) |>
-	cols_merge(c(n_inc_21_months, n_exc_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_25_months, n_exc_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_inc_30_months, n_exc_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_21_months, age_sd_21_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_25_months, age_sd_25_months),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean_30_months, age_sd_30_months),
-			   pattern = "{1} ({2})") |> 
-	cols_label(n_inc_21_months = md("*N*"),
-			   n_inc_25_months = md("*N*"),
-			   n_inc_30_months = md("*N*"),
-			   age_mean_21_months = "Age (months)",
-			   age_mean_25_months = "Age (months)",
-			   age_mean_30_months = "Age (months)") |> 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) |> 
-	tab_style(cell_text(size = "medium"),
-			  list(cells_body(),
-			  	 cells_stub())) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("n"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	grand_summary_rows(starts_with("n"), 
-					   fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~fmt_integer(.))
-```
-
-```{r tbl-attrition-trials-vnoeach}
-#| label: tbl-attrition-trials-vnoeach
-#| tbl-cap: "Trial attrition rate by condition for included participants in Analysis 4. Additional excluded trials are indicated between parentheses."
-attrition_vnoeach_oxf |> 
-	mutate(lp = "Monolingual (Oxford)",
-		   id = as.character(id)) |> 
-	bind_rows(mutate(attrition, id = as.character(id))) |> 
-	filter(is_valid_participant) |> 
-	summarise(n_valid = sum(is_valid_trial),
-			  n_total = n(),
-			  .by = c(id, age_group, lp, trial_type)) |> 
-	summarise(across(n_valid, lst(sum, mean, sd),
-					 .names = "{.fn}"),
-			  n_total = sum(n_total),
-			  .by = c(age_group, lp, trial_type)) |> 
-	mutate(n_excluded = n_total-sum) |> 
-	select(-c(n_total)) |> 
-	pivot_wider(names_from = trial_type,
-				values_from = c(sum:sd, n_excluded),
-				names_repair = janitor::make_clean_names) |> 
-	rename_with(\(x) gsub("non_cognate", "noncognate", x)) |> 
-	arrange(age_group) |> 
-	relocate(age_group,
-			 matches("_cognate"),
-			 matches("noncognate")) |> 
-	gt(rowname_col = "age_group",
-	   groupname_col = "lp") |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 starts_with("sum"), 
-				 fns = list(label = md("*N*"), id = "totals") ~ sum(.)) |> 
-	summary_rows(groups = c("Monolingual (Oxford)",
-							"Monolingual",
-							"Bilingual"),
-				 matches("mean"), 
-				 fns = list(label = md("*Mean*"), id = "totals") ~ mean(.),
-				 fmt = ~fmt_number(.)) |> 
-	grand_summary_rows(columns = matches("mean_"),
-					   fns = lst(Mean ~ mean(.)),
-					   fmt = ~fmt_number(.)) |>
-	grand_summary_rows(columns = matches("sum_"),
-					   fns = lst(Sum ~ sum(.)),
-					   fmt = ~fmt_integer(.)) |>
-	cols_merge(c(sum_cognate, n_excluded_cognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(sum_unrelated, n_excluded_unrelated),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(mean_cognate, sd_cognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_noncognate, sd_noncognate),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(mean_unrelated, sd_unrelated),
-			   pattern = "{1} ({2})") |>
-	tab_spanner("Cognate trials", ends_with("_cognate")) |>
-	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
-	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
-	tab_spanner("Related trials", matches("cognate")) |>
-	fmt_number(matches("mean|sd"), decimals = 1) |> 
-	fmt_integer(matches("sum"), sep_mark = ",") |> 
-	cols_label(sum_cognate = md("*N*"),
-			   sum_noncognate = md("*N*"),
-			   sum_unrelated = md("*N*"),
-			   mean_cognate = md("*Mean (SD)*"),
-			   mean_noncognate = md("*Mean (SD)*"),
-			   mean_unrelated = md("*Mean (SD)*"))
-```
-
-### Phonological priming: Related vs. Unrelated
-
-```{r fig-related-vnoeach}
-#| label: fig-related-vnoeach
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 5.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_related_vnoeach, 
-		  model_fits_related_vnoeach[[1]], 
-		  contrast = "related")
-```
-
-### Cognate priming: Cognate vs. Non-cognate
-
-```{r fig-cognate-vnoeach}
-#| label: fig-cognate-vnoeach
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 5.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_cognate_vnoeach, 
-		  model_fits_cognate_vnoeach[[1]], 
-		  contrast = "cognate")
-```
 
@@
 vocabulary_tmp <- vocabulary |> 
-	left_join(select(participants, child_id = id_db, age, age_group, filename),
-			  by = join_by(filename)) |> 
+	left_join(select(participants, child_id, vocab_id, age),
+			  by = join_by(child_id, vocab_id)) |> 
 	relocate(child_id) |> 
-	select(-filename) |> 
-	filter(is_imputed) |> 
-	mutate(child_id = as.character(child_id))
+	filter(is_imputed)
 
 bvq_data$vocabulary |> 
-	inner_join(distinct(bvq_data$logs, id, age_group, age),
-			   by = join_by(id, age_group)) |> 
-	rename(child_id = id) |> 
+	inner_join(distinct(bvq_data$logs, child_id, response_id, lp, age),
+			   by = join_by(response_id)) |> 
 	mutate(is_imputed = FALSE) |> 
@@
 ```
+
+## Appendix D: vocabulary checklist validity
+
+```{r fig-validity-target}
+get_data(gaze = gaze,
+		 participants = participants,
+		 stimuli = stimuli,
+		 vocabulary = vocabulary,
+		 attrition_trials = attrition_trials,
+		 attrition_participants = attrition_participants,
+		 time_subset = c(0, 2),
+		 contrast = "related",
+		 is_valid_vocab_all) |> 
+	unnest_wider(is_valid_vocab_all) |>
+	select(session_id, lp, .elog, target) |> 
+	arrange(session_id, target) |> 
+	summarise(.elog_mean = mean(.elog),
+			  .elog_sd = sd(.elog),
+			  n = n(),
+			  .by = c(lp, target)) |> 
+	mutate(target = ifelse(target, "Yes", "No"),
+		   .elog_se = .elog_sd/sqrt(n),
+		   .elog_lower = .elog_mean - .elog_se*1.96,
+		   .elog_upper = .elog_mean + .elog_se*1.96,
+	) |> 
+	ggplot(aes(lp, .elog_mean, 
+			   ymin = .elog_lower,
+			   ymax = .elog_upper,
+			   colour = target)) +
+	facet_wrap(~lp, ncol = 1, scales = "free_x") +
+	geom_errorbar(width = 0.2, linewidth = 3/4, 
+				  position = position_dodge(width = 0.25)) +
+	geom_point(size = 2,
+			   position = position_dodge(width = 0.25)) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	labs(x = "Condition",
+		 y = "P(Target looking)", 
+		 colour = "Knows the target word") +
+	theme(legend.position = "none",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted")) +
+
+	get_data_time(gaze = gaze,
+				  participants = participants,
+				  stimuli = stimuli,
+				  vocabulary = vocabulary,
+				  attrition_trials = attrition_trials,
+				  attrition_participants = attrition_participants,
+				  time_subset = c(0, 2),
+				  contrast = "related",
+				  is_valid_vocab_all) |> 
+	unnest_wider(is_valid_vocab_all) |>
+	select(session_id, age, lp, timebin, .elog, target) |> 
+	arrange(session_id, target) |> 
+	summarise(.elog_mean = mean(.elog),
+			  .elog_sd = sd(.elog),
+			  n = n(),
+			  .by = c(timebin, lp, target)) |> 
+	mutate(target = ifelse(target, "Yes", "No"),
+		   .elog_se = .elog_sd/sqrt(n),
+		   .elog_lower = .elog_mean - .elog_se*1.96,
+		   .elog_upper = .elog_mean + .elog_se*1.96,
+	) |> 
+	ggplot(aes(timebin, .elog_mean,
+			   ymin = .elog_lower,
+			   ymax = .elog_upper,
+			   colour = target,
+			   fill = target)) +
+	facet_wrap(~lp, ncol = 1, scales = "free_x") +
+	geom_line(linewidth = 1/2) +
+	geom_ribbon(alpha = 1/2,
+				colour = NA) +
+	geom_point(size = 2) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	labs(x = "Condition",
+		 y = "P(Target looking)", 
+		 fill = "Knows the target word",
+		 colour = "Knows the target word") +
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"),
+		  axis.title.y = element_blank(),
+		  axis.line.x = element_line()) +
+
+	plot_layout(ncol = 2,
+				widths = c(0.2, 0.8)) &
+	scale_y_continuous(limits = c(-0.5, 1.25))
+```

### 2023-10-26 tests/testthat/test-data.R

@@ -1,9 +1,10 @@
-test_data_time <- function(data_time){
+test_data_time <- function(x) {
 	
-	test_that("data_time has the right columns", {
-		expect_setequal(
-			colnames(data_time),
-			c("id",
+	test_that("x has the right columns", {
+		expect_contains(
+			colnames(x),
+			c("child_id",
+			  "session_id",
 			  "age",
 			  "lp",
 			  "condition",
@@ -11,48 +12,46 @@ test_data_time <- function(data_time){
 			  ".sum",
 			  ".prop",
 			  ".elog",
-			  ".nsamples",
-			  ".ntrials")
+			  ".nsamples")
 		)
 	})
 	
-	test_that("data_time has the variable classes", {
-		expect_type(data_time$id, "integer")
-		expect_type(data_time$age, "double")
-		expect_equal(class(data_time$condition), "factor")
-		expect_type(data_time$timebin, "integer")
-		expect_type(data_time$.ntrials, "integer")
-		expect_type(data_time$.prop, "double")
-		expect_type(data_time$.elog, "double")
-		expect_type(data_time$.sum, "integer")
-		expect_type(data_time$.nsamples, "integer")
+	test_that("x has the variable classes", {
+		expect_type(x$child_id, "integer")
+		expect_type(x$session_id, "integer")
+		expect_type(x$age, "double")
+		expect_equal(class(x$condition), "factor")
+		expect_type(x$timebin, "integer")
+		expect_type(x$.prop, "double")
+		expect_type(x$.elog, "double")
+		expect_type(x$.sum, "integer")
+		expect_type(x$.nsamples, "integer")
 	})
 	
-	test_that("data_time missing data is dealt with", {
-		expect_false(any(is.na(data_time$id)))
-		expect_false(any(is.na(data_time$age)))
-		expect_false(any(is.na(data_time$lp)))
-		expect_false(any(is.na(data_time$condition)))
-		expect_false(any(is.na(data_time$timebin)))
-		expect_false(any(is.na(data_time$.ntrials)))
-		expect_false(any(is.na(data_time$.nsamples)))
-		expect_false(any(is.na(data_time$.prop)))
-		expect_false(any(is.na(data_time$.elog)))
-		expect_false(any(is.na(data_time$.sum)))
-		
+	test_that("x missing data is dealt with", {
[…]

### 2023-10-26 tests/testthat/test-gaze_aoi.R

@@ -1,62 +1,0 @@
-test_gaze_aoi <- function(gaze_aoi){
-	
-	test_that("gaze_aoi has the right columns", {
-		expect_equal(
-			colnames(gaze_aoi),
-			c("filename",
-			  "trial",
-			  "phase",
-			  "timestamp",
-			  "x",
-			  "y",
-			  "is_gaze_prime",
-			  "is_gaze_target",
-			  "is_gaze_distractor",
-			  "is_valid_gaze",
-			  "is_imputed",
-			  "trial_type",
-			  "prime_cdi",
-			  "target_cdi",
-			  "distractor_cdi")
-		)
-	})
-	
-	test_that("gaze_aoi has the variable classes", {
-		expect_type(gaze_aoi$filename, "character")
-		expect_equal(class(gaze_aoi$trial), "integer")
-		expect_type(gaze_aoi$phase, "character")
-		expect_type(gaze_aoi$timestamp, "double")
-		expect_type(gaze_aoi$x, "double")
-		expect_type(gaze_aoi$y, "double")
-		expect_type(gaze_aoi$is_gaze_prime, "logical")
-		expect_type(gaze_aoi$is_gaze_target, "logical")
-		expect_type(gaze_aoi$is_gaze_distractor, "logical")
-		expect_type(gaze_aoi$is_valid_gaze, "logical")
-		expect_type(gaze_aoi$is_imputed, "logical")
-		expect_type(gaze_aoi$trial_type, "character")
-
-		
-	})
-	
-	test_that("gaze_aoi missing data is dealt with", {
-		expect_false(any(is.na(gaze_aoi$filename)))
-		expect_false(any(is.na(gaze_aoi$trial)))
-		expect_false(any(is.na(gaze_aoi$phase)))
-		expect_false(any(is.na(unique(gaze_aoi$timestamp))))
-		expect_false(any(is.na(gaze_aoi$is_valid_gaze)))
-		expect_false(any(is.na(gaze_aoi$trial_type)))
-		expect_false(any(is.na(gaze_aoi$prime_cdi)))
-		expect_false(any(is.na(gaze_aoi$target_cdi)))
-		expect_false(any(is.na(gaze_aoi$distractor_cdi)))
-		
-	})
-	
-	test_that("gaze_aoi variables have the right values", {
-		expect_true(all(between(unique(gaze_aoi$trial), 0, 32)))
[…]

### 2023-10-26 tests/testthat/test-participants.R

@@ -1,11 +1,13 @@
-test_participants <- function(participants){
+test_participants <- function(x){
 	
-	test_that("participants has the right columns", {
+	test_that("x has the right columns", {
 		expect_setequal(
-			colnames(participants),
+			colnames(x),
 			c("child_id",
 			  "location",
 			  "date_test",
+			  "session_id",
+			  "session_n",
 			  "age",
 			  "sex",
 			  "lp",
@@ -19,30 +21,30 @@ test_participants <- function(participants){
 			  "filename"))
 	})
 	
-	test_that("participants variables are the right types", {
-		expect_type(participants$child_id, "character")
-		expect_type(participants$vocab_id, "character")
-		expect_type(participants$sex, "integer")
-		expect_equal(class(participants$date_test), "Date")
-		expect_type(participants$lp, "integer")
-		expect_type(participants$age, "double")
-		expect_type(participants$test_language, "integer")
-		expect_type(participants$list, "integer")
-		expect_type(participants$version, "character")
-		expect_type(participants$filename, "character")
-		expect_type(participants$doe, "list")
+	test_that("x variables are the right types", {
+		expect_type(x$child_id, "character")
+		expect_type(x$vocab_id, "character")
+		expect_type(x$sex, "integer")
+		expect_equal(class(x$date_test), "Date")
+		expect_type(x$lp, "integer")
+		expect_type(x$age, "double")
+		expect_type(x$test_language, "integer")
+		expect_type(x$list, "integer")
+		expect_type(x$version, "character")
+		expect_type(x$filename, "character")
+		expect_type(x$doe, "list")
 	})
 	
-	test_that("participants has no missing data", {
-		expect_false(any(is.na(participants$child_id)))
-		expect_false(any(is.na(participants$date_test)))
-		expect_false(any(is.na(participants$lp)))
-		expect_false(any(is.na(participants$age)))
-		expect_false(any(is.na(participants$test_language)))
-		expect_false(any(is.na(participants$list)))
-		expect_false(any(is.na(participants$version)))
-		expect_false(any(is.na(participants$filename[
-			participants$location=="Barcelona"
+	test_that("x has no missing data", {
+		expect_false(any(is.na(x$child_id)))
+		expect_false(any(is.na(x$date_test)))
+		expect_false(any(is.na(x$lp)))
+		expect_false(any(is.na(x$age)))
+		expect_false(any(is.na(x$test_language)))
[…]

### 2023-10-27 manuscript/manuscript.qmd
Simplify analysis, only one model with two contrasts

@@
 
-The formation of a mental lexicon is a critical developmental achievement for infants_ learning words allows infants to retrieve socially relevant concepts from fairly arbitrary linguistic forms embedded in speech.
-
-Learning words allows infants to access the rich world made of concepts through the recognition of fairly arbitrary linguistic forms, i.e., words. This remarkable developmental achievement is
-
-There is evidence of cascaded activation during lexical access.
-
+Growing a mental lexicon is one of the main achievements in the developmental journey of infants.
+Being able to store lexical representations of familiar words allows infants to later recognise them in speech, and to retrieve their associated concepts.
+The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal.
+This results in the activation of lexical representations whose associated phonological forms matches the acoustic signal to some extent.
+The activated word-forms then compete for selection: the lexical system uses the auditory input, together with top-down context provided by grammatical, supra-segmental, and semantic constraints, to select the candidate lexical representation with the best match.
+There is evidence that spoken word recognition occurs in a *cascaded* fashion.
+The activation and selection of candidate lexical representations overlap in time, relying on partial information that accumulates as the speech signal unfolds [@marslen1987functional; @marslen1978processing; @grosjean1980spoken].
+This cascaded activation triggered by lexical access also results in the activation of the concepts associated to the accesses phonological forms.
+@allopenna1998tracking.
+
+This is also the case in the developing lexicon.
+There is evidence that infants start forming their first lexical representations before their first year of life.
+Already at six months of age, infants show evidence of word recognition.
+When presented with pairs of familiar objects and hearing the label of one of them, 6-months-old infants and older show a looking preference towards the named object [@bergelson20126; @bergelson2015early].
 @chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
@@
 
-How does language co-activation shape lexical development?
 Marian and Spivey (1999)
 Costa et al. (2000)
+
+@dijkstra2019multilink
 
@@
 
+##  How does language co-activation shape lexical development?
+
 Floccia et al.
@@
 - Wu and Thierry (2011): rhyme
+
+## The present study
+
+The present study is aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
+Using an adaptation of [@mani2010infants], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
+We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
+If so, phonological priming effect should be larger when the prime label in  both languages shares phonological overlap with the target words (cognate condition), compared to when only the label of the prime in one language overlaps phonologically with the target (non-cognate condition).
+We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
 
@@
 #| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-data_time_related |> 
+data_time |> 
 	summarise(.elog = mean(.elog),
@@
 
-	data_time_cognate |> 
+	data_time |> 
 	summarise(.elog = mean(.elog),
@@
 
-### Phonological priming: Related vs. Unrelated primes
+## Aggregated analysis
 
@@
 Lines and error bands indicate the mean and standard error of the mean."
-nd <- expand(data_related, lp, condition, age = mean(data_related$age))
+nd <- expand(data_aggr, lp, condition, age = seq(20, 32, length.out = 100))
 
 epreds <- add_epred_draws(newdata = nd,
-						  object = model_fits_related[[1]],
+						  object = model_fits_aggr$fit_aggr_4,
 						  re_formula = NA) |> 
@@
 epreds |> 
-	ggplot(aes(condition, .epred, 
+	ggplot(aes(age, .epred, 
 			   colour = condition,
@@
 	# 		  alpha = 1/4) +
-	geom_dots(dat = data_related,
-			  aes(y = .elog,
-			  	side = ifelse(condition=="Related",
-			  				  "left", 
-			  				  "right")),
-			  show.legend = FALSE) +
+	# geom_dots(dat = data_aggr,
+	# 		  aes(y = .elog),
+	# 		  side = "both",
+	# 		  show.legend = FALSE) +
 	geom_hline(yintercept = 0,
 			   linetype = "dashed") +
-	geom_line(aes(group = lp),
-			  colour = "black",
-			  linewidth = 3/4) +
-	geom_errorbar(aes(ymin = .lower,
+	geom_ribbon(aes(ymin = .lower,
 					ymax = .upper),
-				  width = 0.15,
-				  linewidth = 3/4,
-				  colour = "black") +
-	geom_point(size = 2, colour = "black") +
-	geom_label(aes(label = label,
-				   y = -1.5),
-			   fill = "white",
-			   colour = "black",
-			   label.r = unit(0, "lines"),
-			   label.size = 0,
-			   vjust = 0,
-			   size = 3,
+				alpha = 1/3,
+				linewidth = NA) +
+	geom_line(linewidth = 3/4) +
+	geom_point(data = data_aggr,
+			   aes(y = .elog),
 			   alpha = 1/2) +
+	# geom_label(aes(label = label,
+	# 			   y = -1.5),
+	# 		   fill = "white",
+	# 		   colour = "black",
+	# 		   label.r = unit(0, "lines"),
+	# 		   label.size = 0,
+	# 		   vjust = 0,
+	# 		   size = 3,
+	# 		   alpha = 1/2) +
 	labs(x = "Condition",
@@
 
-#### Time course analysis
-
-```{r fig-related}
-#| label: fig-related
+## Time course analysis
+
+```{r fig-time}
+#| label: fig-time
 #| fig-height: 6
@@
 
-	epreds <- expand_grid(condition = levels(data$condition),
-						  timebin = seq(0, 20, length.out = 100),
-						  age = c(21, 25, 30),
-						  lp = levels(data$lp),
-						  .nsamples = 1) |> 
-		add_epred_draws(model,
-						ndraws = 100,
+	nd <- expand_grid(condition = levels(data$condition),
+					  timebin = seq(0, 17, length.out = 100),
+					  age = mean(data$age),
+					  # sesion_id = first(data$session_id),
+					  # age = c(21, 25, 30),
+					  lp = levels(data$lp))
+
+	epreds <- add_epred_draws(newdata = nd,
+							  object = model,
+							  # ndraws = NULL,
 							  re_formula = NA,
@@
 					names_repair = janitor::make_clean_names) 
-
-	if (contrast=="related") {
-		epreds_diff$diff <- epreds_diff$related - epreds_diff$unrelated
-	} else {
-		epreds_diff$diff <- epreds_diff$cognate - epreds_diff$non_cognate
-	}
-
-	data |> 
+	# 
+	# if (contrast=="related") {
+	# 	epreds_diff$diff <- epreds_diff$related - epreds_diff$unrelated
+	# } else {
+	# 	epreds_diff$diff <- epreds_diff$cognate - epreds_diff$non_cognate
+	# }
+
+	obs <- data |> 
 		mutate(age = factor(age, levels = c(21, 25, 30),
 							labels = paste0(c(21, 25, 30), " months"))) |> 
-		summarise(.prop = mean(.prop),
-				  .by = c(child_id, timebin, lp, condition, age))
+		summarise(.elog = mean(.elog),
+				  .by = c(session_id, timebin, lp, condition, age))
 
@@
 				   fill = condition,
-				   shape = condition,
-				   linetype = condition)) +
-		facet_grid(age~lp) +
-		stat_summary(fun.data = \(x) mean_qi(x, .width = 0.95),
-					 geom = "ribbon",
-					 alpha = 0.5,
-					 linewidth = 0) +
+				   shape = condition)) +
+		facet_wrap(~lp) +
+		# stat_summary(fun.data = mean_qi,
+		# 			 geom = "ribbon",
+		# 			 alpha = 0.5,
+		# 			 linewidth = 0) +
 		stat_summary(aes(linetype = condition),
-					 fun = "mean",
+					 fun = mean,
 					 geom = "line",
 					 linewidth = 3/4) +
-		geom_hline(yintercept = 1/2, 
+		geom_hline(yintercept = 0, 
 				   linewidth = 1/2,
@@
 				   linetype = "dotted") +
+		stat_summary(data = obs,
+					 aes(y = .elog),
+					 fun.data = "mean_se",
+					 geom = "errorbar",
+					 width = 1,
+					 linewidth = 3/4,
+					 position = position_dodge(width = 0.5)) +
+		stat_summary(data = obs,
+					 aes(y = .elog),
+					 fun = "mean",
+					 geom = "point",
+					 size = 2,
+					 position = position_dodge(width = 0.5)) +
 		# stat_summary(fun.data = mean_se,
@@
 
-```
-
-### Cognate priming: Cognate vs. Non-cognate
-
-```{r fig-cognate-aggregated}
-#| label: fig-related-aggregated
-#| fig-cap: "A) Aggregated probability of target looking for cognate and non-cognate trials.
-Each point represents the mean probability of target looking for one participant in one testing session.
-Lines link observations from the same testing session across conditions.
-Black dots and errorbars indicate the mean and 95% CrI.
-B) Aggregated probability of target looking across ages for cognate and non-cognate trials.
-Lines and error bands indicate the mean and standard error of the mean."
-nd <- expand(data_cognate, lp, condition, age = mean(data_cognate$age))
-
-epreds <- add_epred_draws(newdata = nd,
-						  object = model_fits_cognate[[1]],
-						  re_formula = NA) |> 
-	mean_qi() |> 
-	mutate(label = sprintf("%.2f\n[%.2f, %.2f]", .epred, .lower, .upper))
-
-epreds |> 
-	ggplot(aes(condition, .epred, 
-			   colour = condition,
-			   fill = condition)) +
-	facet_wrap(~lp) +
-	# geom_line(data = data_cognate,
-	# 		  aes(y = .elog,
-	# 		  	group = session_id),
-	# 		  colour = "grey",
-	# 		  alpha = 1/4) +
-	geom_dots(dat = data_cognate,
-			  aes(y = .elog,
-			  	side = ifelse(condition=="Cognate",
-			  				  "left", 
-			  				  "right")),
-			  show.legend = FALSE) +
-	geom_hline(yintercept = 0,
-			   linetype = "dashed") +
-	geom_line(aes(group = lp),
-			  colour = "black",
-			  linewidth = 3/4) +
-	geom_errorbar(aes(ymin = .lower,
-					  ymax = .upper),
-				  width = 0.15,
-				  linewidth = 3/4,
-				  colour = "black") +
-	geom_point(size = 2, colour = "black") +
-	geom_label(aes(label = label,
-				   y = -1.5),
-			   fill = "white",
-			   colour = "black",
-			   label.r = unit(0, "lines"),
-			   label.size = 0,
-			   vjust = 0,
-			   size = 3,
-			   alpha = 1/2) +
-	labs(x = "Condition",
-		 y = "P(Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_y_continuous(breaks = seq(-4, 4, 0.5)) +
-	theme(legend.position = "none",
-		  axis.title.x = element_blank(),
-		  strip.background = element_rect(fill = "grey90",
-		  								colour = "grey90"),
-		  panel.grid.major.y = element_line(linetype = "dotted",
-		  								  colour = "grey")) 
-```
-
-#### Time course analysis
-
-```{r fig-cognate}
-#| label: fig-cognate
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm(data_time_cognate,
-		  model_fits_cognate[[1]],
-		  contrast = "cognate")
 ```
@@
 		 contrast = "related",
-		 is_valid_vocab_all) |> 
+		 is_valid_vocab_all,
+		 clean = FALSE) |> 
 	unnest_wider(is_valid_vocab_all) |>
@@
 				  contrast = "related",
-				  is_valid_vocab_all) |> 
+				  is_valid_vocab_all,
+				  clean = FALSE) |> 
 	unnest_wider(is_valid_vocab_all) |>

### 2023-10-27 R/models.R

@@ -2,7 +2,7 @@
 get_model_fit <- function(names, formulas, data, prior, ...) {
 	
 	# check args
-	if (is.null(names(formulas)) || !is.list(formulas)) {
+	if (!is.list(formulas)) {
 		cli_abort("formula must be a named list")
 	}
 	if (!is.data.frame(data)) {
@@ -10,14 +10,15 @@ get_model_fit <- function(names, formulas, data, prior, ...) {
 	}
 	
 	# fit models
-	fit <- purrr::map2(.x = names,
-					   .y = formulas,
-					   .f = \(names, formulas) {
-					   	fit_single_model(names, formulas, data, prior, ...)
-					   },
-					   .progress = TRUE)
+	fit_lst <- map2(.x = names,
+					.y = formulas,
+					.f = \(names, formulas) {
+						fit_single_model(names, formulas, data, prior, ...)
+					},
+					.progress = TRUE) |> 
+		set_names(gsub("cognate_|related_", "", names))
 	
-	return(fit)
+	return(fit_lst)
 }
 
 #' Estimate model using Hamiltonian Monte Carlo via Stan

### 2023-10-27 src/visualisation.R

@@ -1,12 +1,12 @@
 # functions
-make_plots_gaze <- function(gaze_aoi, 
+make_plots_gaze <- function(gaze, 
 							aoi_coords,
 							participants,
 							stimuli,
 							attrition_trials,
 							attrition_participants){
 	
-	files <- unique(gaze_aoi$filename[!is.na(gaze_aoi$filename)])
+	files <- paste0("id_", unique(gaze$session_id[!is.na(gaze$session_id)]))
 	n_files <- length(files)
 	
 	i <- 0
@@ -15,29 +15,25 @@ make_plots_gaze <- function(gaze_aoi,
 					 total = n_files, 
 					 format = pb_msg)
 	
-	attrition_trials$is_valid_trial <- ifelse(
-		is.na(attrition_trials$is_valid_vocab),
-		attrition_trials$is_valid_gaze_test & 
-			attrition_trials$is_valid_gaze_test_each,
-		attrition_trials$is_valid_trial
-	)
-	
-	plot_data <- get_plot_data(gaze_aoi,
+	plot_data <- get_plot_data(gaze,
+							   participants,
+							   stimuli,
 							   attrition_trials,
-							   attrition_participants)
+							   attrition_participants,
+							   aoi_coords)
 	
 	plot_data_split <- plot_data |> 
-		group_split(filename) |> 
+		group_split(session_id) |> 
 		set_names(files)
 	
 	for (i in 1:n_files) {
 		
 		plot <- plot_gaze_data(plot_data_split[[i]], files[i])
 		
-		file_name <- gsub(".csv", ".png", files[i])
+		file_name <- paste0(first(plot_data_split[[i]]$session_id), ".png")
 		plot_height <- length(unique(plot_data_split[[i]]$trial))*0.75
 		
-		ggsave(paste0("img/01_raw/", file_name),
+		ggsave(file.path(paste0("img/01_raw/", file_name)),
 			   plot = plot, 
 			   height = plot_height,
 			   width = 6)
@@ -47,57 +43,71 @@ make_plots_gaze <- function(gaze_aoi,
 	cli_progress_done(result = "done")
 }
 
-get_plot_data <- function(gaze_aoi,
+get_plot_data <- function(gaze,
+						  participants, 
+						  stimuli,
 						  attrition_trials, 
-						  attrition_participant) {
+						  attrition_participant,
+						  aoi_coords) {
 	
-	plot_data <- gaze_aoi |> 
-		left_join(attrition_trials,
[…]

### 2023-10-27 tests/testthat/test-data.R

@@ -8,6 +8,7 @@ test_data_time <- function(x) {
 			  "age",
 			  "lp",
 			  "condition",
+			  "voc_l1",
 			  "timebin",
 			  ".sum",
 			  ".prop",
@@ -44,8 +45,9 @@ test_data_time <- function(x) {
 	test_that("x variables have the right values", {
 		expect_equal(levels(x$lp),
 					 c("Monolingual (English)", "Monolingual", "Bilingual"))
-		expect_in(levels(x$condition), c("Cognate", "Non-cognate",
-										 "Related" ,"Unrelated"))
+		expect_in(levels(x$condition), c("Unrelated", 
+										 "Related/Cognate",
+										 "Related/Non-cognate"))
 		expect_gte(min(x$.nsamples), 0)
 		expect_gte(min(x$age), 0)
 		expect_gte(min(x$.prop), 0)

### 2023-10-28 manuscript/manuscript.qmd

@@
 
+Bilingual infants receive a relative impoverished linguistic input in each of their languages compared to their monolingual peers.
+There is not reason to think bilinguals receive an increased amount of total linguistic input, so the fact that such input is divided between at least two languages means that they receive less input from each of their languages [@costa2014does].
+The input bilinguals receive is also more complex than that of monolinguals.
+This is reflected in multiple dimensions.
+For instance, bilinguals are presented with two different, but possible overlapping phoneme inventories, they may be presented with two different grammatical systems, and often presented with more than one label per referent.
+This does not keep bilinguals from tuning their perceptual abilities to both phoneme inventories of their native languages, distinguishing grammatical irregularities in both languages, or learning more than one label per object.
+Bilinguals' developmental trajectories might not always be identical to monolinguals', but they achieve their language acquisition milestones at equivalent ages.
+
+For instance, previous work on lexical acquisition has provided some insight into how bilinguals' vocabulary size is equivalent to monolingual's across ages, and the possible mechanisms behind this.
+@hoff2012 found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
+This is consistent with previous accounnts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
+A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languiages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
+Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
+Cognates are form-simlar translation equivalents.
+Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
+
+It is well established that, across languages, monolingual infants start recognising their first word-forms before their first year of life [@jusczyk1999; @halle1994; @vihman2004], with the earliest age at which there is evidencer of familiar word recognition being 6 months [@bergelson2012].
+Bilinguals start recognising words at similar ages.
+Using a Head-turn Prefernce Procedure and ERP registration,  @vihman2013 found English-Welsh bilinguals to be sensitive to the prevalence of auditorily presented words.
+Infants' looking times and ERP differed when presented with words frequently marked as "familiar" by caregivers of demogrtaphically equivalent peers (e.g., *nappy*, *thank you*, *bottle*, *apple*, and *naughty*), compared to when presented with rare words (e.g., *Eiffel*, *courtly*, *nettle*, *wacky*, and *juncture*).
+
 Growing a mental lexicon is one of the main achievements in the developmental journey of infants.
@@
 
-Another important source of evidence in favour of a cascaded activation account comes from studies on implicit naming.
-@mani2010infant showed that 18 month-old infants implicitly generate the labels of name-known pictures presented in silence.
+A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
+When listening to speech, bilinguals activate all lexical candidates from either language consistent with the speech signal.
+Even more surprising, when speaking, bilinguals activate all potential words consistent with the concepts they want to express.
+This effect has been systematically reported in adults [@marian1999activation; @costa2000cognate; @thierry2007brain; @dunabeitia2009masked].
+
+Also in toddlers [@von2012language; @von2014bilinguals] and school-aged children [@persici2019lexical; @bosma2020cognate].
+Relatedly, some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
+Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
+Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that SpanishCatalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
+
+Although recent work has provided strong eviodence of parallel activation in early ages, how cognateness shapes that organisation of the early bilingual lexicon, and how this is reflected on the dynamics of lexical access during word comprehension and production is unclear.
+
+Using the experimental paradigm developed by [@arias2009lexical; @arias2013s; @singh2014one] compared within and across language
+priming effects in Chinese-English toddlers.
+@kuipers2015bilingualism compared ERP responses to picture-word pairs in English monolinguals and Welsh-English bilinguals where the words were either semantically related or unrelated to a pictured object.
+Although both studies tested 30-month-olds, the conclusions the authors reached do not fully agree.
+@singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
+
+There is evidence of cascaded activation during lexical access.
+@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
+In each trial, the authors presented participants with four semantically and phonologically pictures.
+Four seconds after pictures onset, a word-form was auditorily presented.
+The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category).
+For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
+Then they would hear the carrier phrase "Look at the **bee**!".
+The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
+These results support a cascaded activation account of lexical access during the first stages of lexical development.
+
+Evidence from cascaded activation in lexical access is also provided by bilinguals.
+The bilingual lexicon is language-non selective.
+There is strong evidence in support of bilinguals activating lexical representations from both languages during both speech production and comprehension.
+Previous studies on bilingual word production support a cascade account for lexical activation in which the phonology of non-selected lexical representations engages in excitatory or inhibitory dynamics in the lexical selection process.
+
+Bilinguals' trajectories of word recognition  [@vihman2013]
+
+@floccia2020translation tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
+The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, Fench, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
+A prime word was embedded at the end of a carrier sentence that participants listened to.
+Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
+In Study 1, the target word was the translation equivalent of the prime word (*cheese*-*fromage* for an English-French bilingual).
+In other trials, prime and target words were unrelated (e.g., *sock*-*fromage*).
+There was no phonological overlap at onset between prime and target or distractor labels in either of the two conditions.
+Participants were presented with two blocks of related and unrelated trials.
+In one of the blocks, participants were presented with English prime words and Home Language target words (*sock*-*fromage*), and in the other block they were presented with Additional Language prime words and English target words (*fromage*-*sock*).
+The authors found a cross-linguistic priming effect, in which participants showed a stronger preference for the target picture in the post-naming phase in related trials, as compared to unrelated trials.
+This effect was found regardless of the language of the prime (English or Home Language), or the dominance of the language of the prime (i.e., whether the prime word belonged to the dominant language).
+Target preference exceeded chance level in both conditions.
+In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priing task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vive versa).
+This time, prime and target words were not translation equivalents, butr rather words whose referents shared semantic features.
+Results from Study  2 were parallel to those from Study 1.
+The authors found a strong semantic priming effect accross languages, regardless of the language of the prime or the dominance of the language of the prime.
+Overall these results suggest that bilinguals recognosed target words in both conditions, and benefitted from a cross-linguistic facilitation effect from translation equivalents.
+The symmetry of such effect across both languages suggests that participants lexical access ocurred in parallel for the two members of translation equivalents.
+As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languiages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
+The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
+However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generatd by an interaction by the phonological and semantic overlap between cognate primes and targets.
+
+Another source of evidence supporting the language non-selective account of lexical access is provided by cross-languistic priming priuming thorught translation paradigms.
+In line with @floccia2020translation, @von2012language found that bilingual toddlers aged 21-to-43-months, and who were learning German and English, showed a stronger target preference in a German word recognition task after being primed with a phonologically related English word, which shared phonological onset with the prime word (e.g., *slide*-*Klide* [German for *dress*]), compared to when prime and target words were phonologically unrelated (e.g., *bottle*-*Ohr* [German for *ear*]).
+Interestingly, they also found evidence of such priming effect when participants were prime with an English word which was *not* phonologically related to the German target word, but rather its German translation was (e.g., *leg* [with German trasnlation *Bein*]-*Stein* [German for *stone*]).
+Altogether, these results indicate that bilingual toddlers activate translation equivalents in parallel during word recognition, and that the phonology of both labels may interact with lexical access in the recognition of subsequet words.
+Importantly, cross-linguitic priming through translation demonstrates that previous findings of a cognateness facilitation in word production and recognition do not result from the mere phonological overlap between auditorily presented and target labels, but also from the phonological overlap between the prime translation (not presented) and the target.
+
+Evidence from cognates.
+Marian and Spivey (1999)
+Costa et al. (2000)
+
+@dijkstra2019multilink
+
+## Evidence from co-activation though translation
+The role of cognates in lexical processing.
+
+Another source of evidence are studies studies involving phonological priming of non-cognates through translation. [SEE REFERENCES FROM VON HOLZEN 2012]
+
+## Implicit naming
+
+The aforementioned studies use priming-though-translation paradigms.
+In these paradigms, cross-linguistic priming results from activation spreading from the lexical representation of the the (auditorily presented) prime word to the lexical representation of its translation through semantic associations (e.g., translation equivalence).
+When prime words are auditorily presented, the task design constraints the naming context to one of the languages.
+The consequence is a potential asymmtry between the activation dynamics of the lexical represetnation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
+This might lead to a lower strength, and higher lacenty of the activation of the translation.
+
+##  How does language co-activation shape lexical development?
+
+In the present study, we use an adaptation of an implicit naming paradigm by @mani2010infant, in which participants are primed with a picture, instead of an auditorily presented label.
+@mani2010infant showed that 18 month-old monolinguals implicitly generate the labels of name-known pictures presented in silence.
 In each trial, infants were presented with prime pictures presented in silence, and then with a target and a distractor picture, both presented side-by-side.
@@
 
-Evidence from cascaded activation in lexical access is also provided by bilinguals.
-The bilingual lexicon is language-non selective.
-There is strong evidence in support of bilinguals activating lexical representations from both languages during both speech production and comprehension.
-Previous studies on bilingual word production support a cascade account for lexical activation in which the phonology of non-selected lexical representations engages in excitatory or inhibitory dynamics in the lexical selection process.
-
-## Co-activation in adults
-
-Marian and Spivey (1999)
-Costa et al. (2000)
-
-@dijkstra2019multilink
-
-## Evidence from co-activation though translation
-The role of cognates in lexical processing.
-
-Another source of evidence are studies studies involving phonological priming of non-cognates through translation. [SEE REFERENCES FROM VON HOLZEN 2012]
-
+Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
+@duta2012erp presented name-known pictures in silence for one second.
+After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
+In some trials the auditory label corresponded to a canonical realisation of the word-form.
+In other trials, the word was mispronounced.
+Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
+A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
+This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
+
+When extended to the bilingual case, this implicit naming task may offer bilingual participants with an uncontrained naming context in whcih the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
 Using an adaptation of @mani2010infant's implicit naming paradigm, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
@@
 
-Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
-@duta2012erp presented name-known pictures in silence for one second.
-After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
-In some trials the auditory label corresponded to a canonical realisation of the word-form.
-In other trials, the word was mispronounced.
-Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
-A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
-This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
-
-##  How does language co-activation shape lexical development?
-
-Floccia et al.
-(2020) tested toddlers in a cross-language priming paradigm.
-A prime word was embedded at the end of a carrier sentence that participants listened to.
-Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
-Some critiques:
-
 Evidence from cognates.
 
-- Since participants heard the auditory label in one of the languages, priming through translation might be compromised.
-- Translation equivalents (Exp.
-1) are more strongly related at the semantic level with each other than other pairs of semantically related words that are not translations of each other (table-mesa are more strongly associated than table-silla).
-- We used longitudinal participants, so we can examine the developmental trajectories of cross-language lateral inhibitory or excitatory connections better.
-- Larger sample size.
-
-Onset vs. offset overlap:
-
-- Wu and Thierry (2011): rhyme
+The role of cognates in lexical processing.
+
+This study also provides a more suitable design for drawing conslusions about developmental change in word recognition trajectories frot wo reasons.
+First, it extends the age range of participants, compared to previous studies.
+Second, participants were tested at three selected age points to ensure a more balanced sample size across ages.
+Third, the partially longitudinal design allows modelling the performance of participants across testing sessions altogether.
+
+. In order to circumvent the problem of limited vocabulary knowledge
+in the non-dominant language, we propose to test participants only in their dominant language, therefore
+directing our research to the question of how possessing a second language affects processing of the
+dominant one in bilingual toddlers [@costa2014does provide a fuller description of the
+advantages of such approach].
 
@@
 
+We collected data from `r n_participants_total` monolingual and bilingual participants living in the Metropolitan Area of Barcelona (Spain), who were exposed to at least Catalan and/or Spanish from birth.
+Families were recruited from maternity room in private hospitals in Barcelona, and contacted via phone when the child's age spanned between our age intervals of interest.
+Families were invited to participate at three age points: 21, 25, and 30 months.
+`r n_participants_sessions[[1]]$n` participants were tested at one age point,  `r n_participants_sessions[[2]]$n` at two age points, and `r n_participants_sessions[[3]]$n` at the three age points.
+In total, we gathered data from `r n_sessions_total$n` testing sessions: `r n_sessions_age_group$age_21$n` at 21 months (*Mean* = `r round(n_sessions_age_group$age_21$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_21$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_21$age_min`--`r n_sessions_age_group$age_21$age_max`), `r n_sessions_age_group$age_25$n` at 25 months (*Mean* = `r round(n_sessions_age_group$age_25$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_25$age_min`--`r n_sessions_age_group$age_25$age_max`), and `r n_sessions_age_group$age_30$n` at 30 months (*Mean* = `r round(n_sessions_age_group$age_30$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_30$age_min`--`r n_sessions_age_group$age_30$age_max`).
+
+Participants' vision was normal, none used glasses or any other type of vision corrector.
+
+### Language profile {#sec-lp}
+
+We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
+Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
+The output of this interview is an estimated degree of exposure (DoE) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
+According to this estimate, we classified participants as Catalan- or Spanish-dominant if the language with highest DoE was Catalan or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
+We collected data from `r n_sessions_dominance$catalan$n` Catalan-dominant participants in Catalan (`r n_sessions_dominance_age_group$catalan$age_21$n` at 21 months, `r n_sessions_dominance_age_group$catalan$age_25$n` at 25 months, and `r n_sessions_dominance_age_group$catalan$age_30$n` at 30 months).
+We further classified participants as monolinguals if the DoE to their dominant language exceeded 80% of the total DoE to Catalan and Spanish, and as bilinguals otherwise.
+Participants with DoE to language other than Catalan or Spanish were excluded from analyses.
+This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
+@tbl-participants-lp shows a detailed description of the linguistic profile of our sample.
+
 ### Vocabulary size
@@
 Each experimental session took approximately 10 minutes.
+
+## Apparatus
+
+see https://link.springer.com/article/10.3758/s13428-021-01762-8
 

### 2023-10-30 manuscript/manuscript.qmd
Clean repo

@@
 targets::tar_load(
-	c(model_fits_related,
-	  model_fits_cognate,
-	  # model_fits_related_time,
-	  # model_fits_cognate_time,
-	  # model_loo_related,
-	  # model_loo_cognate,
+	c(model_fits_aggr,
+	  model_fits_time,
+	  model_loos_aggr,
+	  model_loos_time,
 	))
@@
 ## The early lexicon
-
-Bilingual infants receive a relative impoverished linguistic input in each of their languages compared to their monolingual peers.
-There is not reason to think bilinguals receive an increased amount of total linguistic input, so the fact that such input is divided between at least two languages means that they receive less input from each of their languages [@costa2014does].
-The input bilinguals receive is also more complex than that of monolinguals.
-This is reflected in multiple dimensions.
-For instance, bilinguals are presented with two different, but possible overlapping phoneme inventories, they may be presented with two different grammatical systems, and often presented with more than one label per referent.
-This does not keep bilinguals from tuning their perceptual abilities to both phoneme inventories of their native languages, distinguishing grammatical irregularities in both languages, or learning more than one label per object.
-Bilinguals' developmental trajectories might not always be identical to monolinguals', but they achieve their language acquisition milestones at equivalent ages.
-
-For instance, previous work on lexical acquisition has provided some insight into how bilinguals' vocabulary size is equivalent to monolingual's across ages, and the possible mechanisms behind this.
-@hoff2012 found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
-This is consistent with previous accounnts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
-A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languiages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
-Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
-Cognates are form-simlar translation equivalents.
-Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
-
-It is well established that, across languages, monolingual infants start recognising their first word-forms before their first year of life [@jusczyk1999; @halle1994; @vihman2004], with the earliest age at which there is evidencer of familiar word recognition being 6 months [@bergelson2012].
-Bilinguals start recognising words at similar ages.
-Using a Head-turn Prefernce Procedure and ERP registration,  @vihman2013 found English-Welsh bilinguals to be sensitive to the prevalence of auditorily presented words.
-Infants' looking times and ERP differed when presented with words frequently marked as "familiar" by caregivers of demogrtaphically equivalent peers (e.g., *nappy*, *thank you*, *bottle*, *apple*, and *naughty*), compared to when presented with rare words (e.g., *Eiffel*, *courtly*, *nettle*, *wacky*, and *juncture*).
 
@@
 There is evidence that infants start forming their first lexical representations before their first year of life.
+It is well established that, across languages, infants start recognising their first word-forms before their first year of life [@jusczyk1999; @halle1994; @vihman2004].
 Already at six months of age, infants show evidence of word recognition.
@@
 
-A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
+Evidence from cascaded activation in lexical access is also provided by bilinguals.A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
 When listening to speech, bilinguals activate all lexical candidates from either language consistent with the speech signal.
@@
 
+Bilinguals infants start recognising words at similar ages.
+Using a Head-turn Preference Procedure and ERP registration,  @vihman2013 found English-Welsh bilinguals to be sensitive to the prevalence of auditorily presented words.
+Infants' looking times and ERP differed when presented with words frequently marked as "familiar" by caregivers of demographically equivalent peers (e.g., *nappy*, *thank you*, *bottle*, *apple*, and *naughty*), compared to when presented with rare words (e.g., *Eiffel*, *courtly*, *nettle*, *wacky*, and *juncture*).
+Bilinguals' trajectories of word recognition  [@vihman2013].
+
+Bilingual infants receive a relative impoverished linguistic input in each of their languages compared to their monolingual peers.
+There is not reason to think bilinguals receive an increased amount of total linguistic input, so the fact that such input is divided between at least two languages means that they receive less input from each of their languages [@costa2014does].
+The input bilinguals receive is also more complex than that of monolinguals.
+This is reflected in multiple dimensions.
+For instance, bilinguals are presented with two different, but possible overlapping phoneme inventories, they may be presented with two different grammatical systems, and often presented with more than one label per referent.
+This does not keep bilinguals from tuning their perceptual abilities to both phoneme inventories of their native languages, distinguishing grammatical irregularities in both languages, or learning more than one label per object.
+Bilinguals' developmental trajectories might not always be identical to monolinguals', but they achieve their language acquisition milestones at equivalent ages.
+
+For instance, previous work on lexical acquisition has provided some insight into how bilinguals' vocabulary size is equivalent to monolinguals' across ages, and the possible mechanisms behind this.
+@hoff2012 found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
+This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
+A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
+Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
+Cognates are form-similar translation equivalents.
+Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
+
 Also in toddlers [@von2012language; @von2014bilinguals] and school-aged children [@persici2019lexical; @bosma2020cognate].
-Relatedly, some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
+Some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
 Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
-Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that SpanishCatalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
-
-Although recent work has provided strong eviodence of parallel activation in early ages, how cognateness shapes that organisation of the early bilingual lexicon, and how this is reflected on the dynamics of lexical access during word comprehension and production is unclear.
+Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that Spanish-Catalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
+
+Although recent work has provided strong evidence of parallel activation in early ages, how cognateness shapes that organisation of the early bilingual lexicon, and how this is reflected on the dynamics of lexical access during word comprehension and production is unclear.
 
@@
 
-There is evidence of cascaded activation during lexical access.
-@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
-In each trial, the authors presented participants with four semantically and phonologically pictures.
-Four seconds after pictures onset, a word-form was auditorily presented.
-The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category).
-For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
-Then they would hear the carrier phrase "Look at the **bee**!".
-The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
-These results support a cascaded activation account of lexical access during the first stages of lexical development.
-
-Evidence from cascaded activation in lexical access is also provided by bilinguals.
-The bilingual lexicon is language-non selective.
-There is strong evidence in support of bilinguals activating lexical representations from both languages during both speech production and comprehension.
-Previous studies on bilingual word production support a cascade account for lexical activation in which the phonology of non-selected lexical representations engages in excitatory or inhibitory dynamics in the lexical selection process.
-
-Bilinguals' trajectories of word recognition  [@vihman2013]
-
 @floccia2020translation tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
-The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, Fench, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
+The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, French, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
 A prime word was embedded at the end of a carrier sentence that participants listened to.
@@
 Target preference exceeded chance level in both conditions.
-In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priing task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vive versa).
-This time, prime and target words were not translation equivalents, butr rather words whose referents shared semantic features.
+In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
+This time, prime and target words were not translation equivalents, but rather words whose referents shared semantic features.
 Results from Study  2 were parallel to those from Study 1.
-The authors found a strong semantic priming effect accross languages, regardless of the language of the prime or the dominance of the language of the prime.
-Overall these results suggest that bilinguals recognosed target words in both conditions, and benefitted from a cross-linguistic facilitation effect from translation equivalents.
-The symmetry of such effect across both languages suggests that participants lexical access ocurred in parallel for the two members of translation equivalents.
-As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languiages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
+The authors found a strong semantic priming effect across languages, regardless of the language of the prime or the dominance of the language of the prime.
+Overall these results suggest that bilinguals recognised target words in both conditions, and benefited from a cross-linguistic facilitation effect from translation equivalents.
+The symmetry of such effect across both languages suggests that participants lexical access occurred in parallel for the two members of translation equivalents.
+As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
 The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
-However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generatd by an interaction by the phonological and semantic overlap between cognate primes and targets.
+However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generated by an interaction by the phonological and semantic overlap between cognate primes and targets.
 

### 2023-10-31 manuscript/manuscript.qmd
Progress with introduction and new models

@@
 	  gaze_aoi, 
-	  data_related,
-	  data_cognate,
-	  data_time_related, 
-	  data_time_cognate,
+	  data_time, 
+	  data_aggr,
 	))
@@
 	c(model_fits_aggr,
-	  model_fits_time,
-	  model_loos_aggr,
-	  model_loos_time,
+	  model_fits_time
+	  # model_loos_aggr,
+	  # model_loos_time,
 	))
+
+# prepare data
+attrition <- lst(participants,
+				 attrition_participants,
+				 attrition_trials) |> 
+	reduce(inner_join, by = join_by(session_id)) |> 
+	unnest_wider(matches("all"), names_sep = "_")
 
@@
 
-# prepare data
-attrition <- lst(participants,
-				 attrition_participants,
-				 attrition_trials) |> 
-	reduce(inner_join, by = join_by(session_id)) |> 
-	unnest_wider(matches("all"), names_sep = "_")
-
 ```
@@
 
-Growing a mental lexicon is one of the main achievements in the developmental journey of infants.
-Being able to store lexical representations of familiar words allows infants to later recognise them in speech, and to retrieve their associated concepts.
+Building a mental lexicon is a major achievement in the developmental journey of infants: by accumulating lexical representations of familiar words, infants are later able to recognise them in speech, and to extract meaning from the speech they are exposed to.
+Infants start forming their first lexical representations before their first year of life [@jusczyk1999; @halle1994; @vihman2004].
+When presented with pairs of pictures of familiar objects, 6-months-old infants already direct their gaze towards whichever is named [@bergelson20126; @bergelson2015early].
+This initial lexicon is hardly larger than around fifteen words [@REFERENCE], but it undergoes rapid growth [@REFERENCE] during their second year of life, at the end of which toddlers know an average of XXX words, and by 30 months of age, they know XXX words [@REFERENCE].
+This accelerated lexical developmental during the second year of life is also reflected in infants'  trajectories of word recognition: infants recognise familiar words faster and more efficiently [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
+Bilingual infants' trajectories of lexical acquisition [@hoff2012, @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes] and word recognition [@vihman2007onset; @vihman2013; @legacy2018vocabulary] are equivalent to their monolingual peers'.
+This is a remarkable deed: bilingual infants receive a relative impoverished linguistic input in each of their languages compared to monolinguals [@costa2014does].
+The mechanism that facilitate bilingual lexical development are still unclear.
+
+## (Early) Word recognition is cascaded
+
+Despite their different linguistic input, monolinguals and bilinguals share broadly common word recognition mechanisms.
 The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal.
@@
 
-This is also the case in the developing lexicon.
-There is evidence that infants start forming their first lexical representations before their first year of life.
-It is well established that, across languages, infants start recognising their first word-forms before their first year of life [@jusczyk1999; @halle1994; @vihman2004].
-Already at six months of age, infants show evidence of word recognition.
-When presented with pairs of familiar objects and hearing the label of one of them, 6-months-old infants and older show a looking preference towards the named object [@bergelson20126; @bergelson2015early].
+This is also the case of the developing lexicon: like adults, infants activate non-selected lexical representations.
+This is relfected by the fact that from 21 months of age, infants' lexicon seems to be systematically organised accordi to the semantic and phnological properties of the lexical representations.
+
+SEMANTICS
+@arias2009lexical showed evidence of semantic priming in 21-month-old infants.
+In a word recognition task, infants' recognition of a spoken word (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
+Later studies provided electrophysiological evidence of such effect as early as 14 months of age [@friedrich2005lexical].
+
+PHONOLOGY
+Initial lexical representations are also phonologically well-specified [@swingley2000spoken; @swingley2002lexical].
+Overall these results suggest that early lexical representations are systematically organised in the lexicon according to their semantic and phonological properties.
+
+BOTH
 @chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
@@
 These results support a cascaded activation account of lexical access during the first stages of lexical development.
-
-Evidence from cascaded activation in lexical access is also provided by bilinguals.A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
+@swingley1999continuous
+
+## Cascaded activation in bilingual parallel activation
+
+There is also evidence of cascaded activation in bilinguals.
+A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
 When listening to speech, bilinguals activate all lexical candidates from either language consistent with the speech signal.
@@
 
-Bilinguals infants start recognising words at similar ages.
-Using a Head-turn Preference Procedure and ERP registration,  @vihman2013 found English-Welsh bilinguals to be sensitive to the prevalence of auditorily presented words.
-Infants' looking times and ERP differed when presented with words frequently marked as "familiar" by caregivers of demographically equivalent peers (e.g., *nappy*, *thank you*, *bottle*, *apple*, and *naughty*), compared to when presented with rare words (e.g., *Eiffel*, *courtly*, *nettle*, *wacky*, and *juncture*).
-Bilinguals' trajectories of word recognition  [@vihman2013].
-
-Bilingual infants receive a relative impoverished linguistic input in each of their languages compared to their monolingual peers.
-There is not reason to think bilinguals receive an increased amount of total linguistic input, so the fact that such input is divided between at least two languages means that they receive less input from each of their languages [@costa2014does].
-The input bilinguals receive is also more complex than that of monolinguals.
-This is reflected in multiple dimensions.
-For instance, bilinguals are presented with two different, but possible overlapping phoneme inventories, they may be presented with two different grammatical systems, and often presented with more than one label per referent.
-This does not keep bilinguals from tuning their perceptual abilities to both phoneme inventories of their native languages, distinguishing grammatical irregularities in both languages, or learning more than one label per object.
-Bilinguals' developmental trajectories might not always be identical to monolinguals', but they achieve their language acquisition milestones at equivalent ages.
-
-For instance, previous work on lexical acquisition has provided some insight into how bilinguals' vocabulary size is equivalent to monolinguals' across ages, and the possible mechanisms behind this.
-@hoff2012 found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
+For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
 This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
+
 A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
@@
 @singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
+
+## Cognate word recogntiion
 
@@
 
-## Evidence from co-activation though translation
 The role of cognates in lexical processing.
@@
 
-## Implicit naming
+## The rpesent study
 
@@
 When prime words are auditorily presented, the task design constraints the naming context to one of the languages.
-The consequence is a potential asymmtry between the activation dynamics of the lexical represetnation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
+The consequence is a potential asymmtry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
 This might lead to a lower strength, and higher lacenty of the activation of the translation.
-
-##  How does language co-activation shape lexical development?
 
@@
 We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
+
+We compared the explanatory power of three measures of vocabulary size on participants' trajectories of word recognition: L1 vocabulary and total vocabulary.Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary]
 
@@
 
+We defined a time windows of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
+To avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
 Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
@@
 
-```{r fig-ptlt-descriptive}
-#| label: fig-ptlt-descriptive
+## Preliminary analyses
+
+```{r fig-ptlt-recognition}
+#| label: fig-ptlt-recognition-aggr
 #| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
 data_time |> 
-	summarise(.elog = mean(.elog),
-			  .by = c(session_id, timebin, lp, condition)) |> 
-	ggplot(aes(timebin, .elog, colour = condition, fill = condition)) +
-	facet_wrap(~lp) +
+	summarise(.prop = mean(.prop),
+			  .by = c(lp, timebin, session_id)) |> 
+	ggplot(aes(timebin, .prop, colour = lp)) +
+	facet_wrap(~lp, nrow = 1, scales = "free_x") +
+	geom_line(aes(group = session_id),
+			  # colour = "grey",
+			  alpha = 1/10) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = mean_se,
+	stat_summary(fun.data = "mean_se",
 				 geom = "errorbar",
-				 width = 0.5) +
-	stat_summary(fun = mean,
-				 geom = "line") +
-	stat_summary(fun = mean,
-				 geom = "point") +
-	theme(axis.title.x = element_blank()) +
-
+				 width = 0.35,
+				 linewidth = 2/4) +
+	stat_summary(fun = "mean",
+				 geom = "point",
+				 size = 1.2) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 linewidth = 2/4) +
+	labs(x = "Time (ms)",
+		 y = "PTLT") +
+	scale_x_continuous(breaks = seq(0, 20, 2),
+					   labels = \(x) format(x*100+300, big.mark = ",")) +
+	scale_y_continuous(labels = scales::percent,
+					   breaks = seq(0, 1, 0.2),
+					   limits = c(0, 1)) +
+	theme(panel.grid.major.y = element_line(colour = "grey",
+											linetype = "dotted"),
+		  legend.position = "none")
+```
+
+```{r fig-ptlt-recognition-age}
+#| label: fig-ptlt-recognition-age
+#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
 data_time |> 
-	summarise(.elog = mean(.elog),
-			  .by = c(session_id, timebin, lp, condition)) |> 
-	ggplot(aes(timebin, .elog, colour = condition, fill = condition)) +
-	facet_wrap(~lp) +
+	summarise(.prop = mean(.prop),
+			  .by = c(lp, timebin, age_group, session_id)) |> 
+	ggplot(aes(timebin, .prop, colour = age_group)) +
+	facet_wrap(~lp, nrow = 1, scales = "free_x") +
+	# geom_rug(aes(x = timebin[is.na(.prop)])) +
+	# geom_line(aes(group = session_id),
+	# 		  alpha = 1/8) +
 	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = mean_se,
+	stat_summary(fun.data = "mean_se",
 				 geom = "errorbar",
-				 width = 0.5) +
-	stat_summary(fun = mean,
-				 geom = "line") +
-	stat_summary(fun = mean,
-				 geom = "point") +
-	theme(strip.text = element_blank()) +
-
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") &
-	labs(x = "Time bin (100 ms)",
-		 y = "P(Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") &
-	# scale_y_continuous(breaks = seq(0, 1, 0.1)) &
-	theme(legend.position = "right",
-		  panel.grid.major.x = element_line(colour = "grey",
-		  								  linetype = "dotted"),
+				 width = 0.35,
+				 linewidth = 2/4) +
+	stat_summary(fun = "mean",
+				 geom = "point",
+				 size = 1.2) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 linewidth = 2/4) +
+	labs(x = "Time (ms)",
+		 y = "PTLT",
+		 colour = "Age") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	scale_y_continuous(labels = scales::percent,
+					   breaks = seq(0, 1, 0.05)) +
+	theme(legend.position = "top",
 		  panel.grid.major.y = element_line(colour = "grey",
 		  								  linetype = "dotted"))
-
+```
+
+```{r fig-ptlt-recognition-condition}
+#| label: fig-ptlt-recognition-condition
+#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+data_time |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(lp, timebin, condition, session_id)) |> 
+	ggplot(aes(timebin, .prop, colour = condition)) +
+	facet_grid(~lp) +
+	# geom_rug(aes(x = timebin[is.na(.prop)])) +
+	# geom_line(aes(group = interaction(condition, session_id)),
+	# 		  alpha = 1/8) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	stat_summary(fun.data = "mean_se",
+				 geom = "errorbar",
+				 width = 0.35,
+				 linewidth = 2/4) +
+	stat_summary(fun = "mean",
+				 geom = "point",
+				 size = 1.2) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 linewidth = 2/4) +
+	labs(x = "Time (ms)",
+		 y = "PTLT",
+		 colour = "Condition") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	scale_y_continuous(labels = scales::percent,
+					   breaks = seq(0, 1, 0.05)) +
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
 ```
@@
 Lines and error bands indicate the mean and standard error of the mean."
-nd <- expand(data_aggr, lp, condition, age = seq(20, 32, length.out = 100))
-
-epreds <- add_epred_draws(newdata = nd,
-						  object = model_fits_aggr$fit_aggr_4,
-						  re_formula = NA) |> 
-	mean_qi() |> 
-	mutate(label = sprintf("%.2f\n[%.2f, %.2f]", .epred, .lower, .upper))
-
-epreds |> 
-	ggplot(aes(age, .epred, 
+plot_agg_epreds <- function(newdata, object) {
+
+	epreds <- add_epred_draws(newdata = newdata,
+							  object = object,
+							  re_formula = NA)
+	return(mean_qi(epreds))
+}
+
+voc_values <- c(0.25, 0.5, 0.75, 1.00)
+age_values <- c(21, 25, 30)
+
+nd_0 <- expand(data_aggr, lp, condition, age = age_values)
+nd_1 <- expand(data_aggr, lp, condition, voc_l1 = voc_values)
+nd_2 <- expand(data_aggr, lp, condition, voc_total = voc_values)
+
+epreds <- map2(.x = list(nd_0, nd_1, nd_2),
+			   .y = model_fits_aggr,
+			   .f = plot_agg_epreds) |> 
+	map(\(x) {
+		mutate(x, 
+			   across(matches("voc"),
+			   	   \(x) factor(x = x, 
+			   	   			levels = voc_values,
+			   	   			labels = scales::percent(voc_values))),
+			   across(matches("age"),
+			   	   \(x) factor(x = x,
+			   	   			levels = age_values,
+			   	   			labels = age_values)))
+	}) |> 
+	map(\(x) rename_with(x, \(x) gsub("age|voc_total|voc_l1", "var", x))) |> 
+	set_names(names(model_fits_aggr))
+
+plot_epreds <- function(data, x) {
+	data |> 
+		ggplot(aes(var, .epred, 
 				   colour = condition,
 				   fill = condition)) +
-	facet_wrap(~lp) +
-	# geom_line(data = data_related,
-	# 		  aes(y = .elog,
-	# 		  	group = session_id),
-	# 		  colour = "grey",
-	# 		  alpha = 1/4) +
-	# geom_dots(dat = data_aggr,
-	# 		  aes(y = .elog),
-	# 		  side = "both",
-	# 		  show.legend = FALSE) +
+		facet_wrap(~lp, scales = "free_x") +
 		geom_hline(yintercept = 0,
 				   linetype = "dashed") +
-	geom_ribbon(aes(ymin = .lower,
+		geom_errorbar(aes(ymin = .lower,
 						  ymax = .upper),
-				alpha = 1/3,
-				linewidth = NA) +
-	geom_line(linewidth = 3/4) +
-	geom_point(data = data_aggr,
-			   aes(y = .elog),
-			   alpha = 1/2) +
-	# geom_label(aes(label = label,
-	# 			   y = -1.5),
-	# 		   fill = "white",
-	# 		   colour = "black",
-	# 		   label.r = unit(0, "lines"),
-	# 		   label.size = 0,
-	# 		   vjust = 0,
-	# 		   size = 3,
-	# 		   alpha = 1/2) +
-	labs(x = "Condition",
-		 y = "P(Target looking)",
+					  width = 0.5,
+					  linewidth = 3/4,
+					  position = position_dodge(width = 0.5)) +
+		geom_point(position = position_dodge(width = 0.5),
+				   size = 2)
+}
+
+plot_epreds(epreds$fit_aggr_0) +
+	labs(x = "Age (months)") +
+	plot_epreds(epreds$fit_aggr_1) +
+	labs(x = "L1 vocabulary size") +
+	theme(strip.text = element_blank()) +
+	plot_epreds(epreds$fit_aggr_2) +
+	theme(strip.text = element_blank()) +
+	labs(x = "Total vocabulary size") +
+	plot_layout(ncol = 1, guides = "collect") &
+	labs(y = "Logit (Target looking)",
 		 colour = "Condition",
-		 fill = "Condition") +
-	scale_y_continuous(breaks = seq(-4, 4, 0.5)) +
-	theme(legend.position = "none",
-		  axis.title.x = element_blank(),
-		  strip.background = element_rect(fill = "grey90",
-		  								colour = "grey90"),
-		  panel.grid.major.y = element_line(linetype = "dotted",
-		  								  colour = "grey")) 
+		 fill = "Condition") &
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+
 ```
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-plot_gamm <- function(data, model, contrast = "related") {
-
-	nd <- expand_grid(condition = levels(data$condition),
+nd <- expand_grid(condition = levels(model_fits_time$fit_time_2$data$condition),
 				  timebin = seq(0, 17, length.out = 100),
-					  age = mean(data$age),
+				  voc_total = mean(model_fits_time$fit_time_2$data$voc_total),
 				  # sesion_id = first(data$session_id),
 				  # age = c(21, 25, 30),
-					  lp = levels(data$lp))
+				  lp = levels(model_fits_time$fit_time_2$data$lp))
 
 epreds <- add_epred_draws(newdata = nd,
-							  object = model,
-							  # ndraws = NULL,
+						  object = model_fits_time$fit_time_2,
+						  ndraws = 20,
 						  re_formula = NA,
 						  value = ".value") |> 
+	mean_qi() |> 
+	mutate(lp = factor(lp, 
+					   levels = c("Monolingual (English)",
+					   		   "Monolingual",
+					   		   "Bilingual")))
+
+epreds |> 
+	ggplot(aes(timebin, .value,
+			   colour = condition,
+			   fill = condition)) +
+	facet_wrap(~lp) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	geom_ribbon(aes(ymin = .lower, ymax = .upper),
+				alpha = 0.5,
+				linewidth = 0) +
+	geom_line(linewidth = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	theme(legend.position = "top",
+		  panel.grid.major = element_line(colour = "grey",
+		  								linetype = "dotted"))
+```
+
+```{r fig-time-total}
+#| label: fig-time-total
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+voc_values <- seq(0.25, 1, 0.25)
+
+nd <- expand_grid(condition = levels(model_fits_time$fit_time_2$data$condition),
+				  timebin = seq(0, 17, length.out = 100),
+				  voc_total = voc_values,
+				  # sesion_id = first(data$session_id),
+				  # age = c(21, 25, 30),
+				  lp = levels(model_fits_time$fit_time_2$data$lp))
+
+epreds <- add_epred_draws(newdata = nd,
+						  object = model_fits_time$fit_time_2,
+						  ndraws = 20,
+						  re_formula = NA,
+						  value = ".value") |> 
+	mean_qi() |> 
 	mutate(lp = factor(lp, 
@@
 					   		   "Bilingual")),
-			   age = factor(age, levels = c(21, 25, 30),
-			   			 labels = paste0(c(21, 25, 30), " months")))
-
-	epreds_diff <- epreds |> 
-		pivot_wider(names_from = condition,
-					values_from = .value,
-					id_cols = c(timebin, age, lp, .draw),
-					names_repair = janitor::make_clean_names) 
-	# 
-	# if (contrast=="related") {
-	# 	epreds_diff$diff <- epreds_diff$related - epreds_diff$unrelated
-	# } else {
-	# 	epreds_diff$diff <- epreds_diff$cognate - epreds_diff$non_cognate
-	# }
-
-	obs <- data |> 
-		mutate(age = factor(age, levels = c(21, 25, 30),
-							labels = paste0(c(21, 25, 30), " months"))) |> 
-		summarise(.elog = mean(.elog),
-				  .by = c(session_id, timebin, lp, condition, age))
+		   voc_total = factor(x = voc_total, 
+		   				   levels = voc_values,
+		   				   labels = scales::percent(voc_values)))
 
 epreds |> 
-		ggplot(aes(timebin, y = .value,
+	ggplot(aes(timebin, .value,
 			   colour = condition,
-				   fill = condition,
-				   shape = condition)) +
-		facet_wrap(~lp) +
-		# stat_summary(fun.data = mean_qi,
-		# 			 geom = "ribbon",
-		# 			 alpha = 0.5,
-		# 			 linewidth = 0) +
-		stat_summary(aes(linetype = condition),
-					 fun = mean,
-					 geom = "line",
-					 linewidth = 3/4) +
+			   fill = condition)) +
+	facet_grid(lp~voc_total) +
 	geom_hline(yintercept = 0,
-				   linewidth = 1/2,
-				   colour = "black",
-				   linetype = "dotted") +
-		stat_summary(data = obs,
-					 aes(y = .elog),
-					 fun.data = "mean_se",
-					 geom = "errorbar",
-					 width = 1,
-					 linewidth = 3/4,
-					 position = position_dodge(width = 0.5)) +
-		stat_summary(data = obs,
-					 aes(y = .elog),
-					 fun = "mean",
-					 geom = "point",
-					 size = 2,
-					 position = position_dodge(width = 0.5)) +
-		# stat_summary(fun.data = mean_se,
-		# 			 geom = "errorbar",
-		# 			 linetype = "solid",
-		# 			 width = 0.25) +
-		# stat_summary(fun = mean,
-		# 			 geom = "point") +
+			   linetype = "dashed") +
+	geom_ribbon(aes(ymin = .lower, ymax = .upper),
+				alpha = 0.5,
+				linewidth = 0) +
+	geom_line(linewidth = 3/4) +
 	labs(x = "Time (ms)",
-			 y = "P(Target looking)",
+		 y = "Logit (Target looking)",
 		 colour = "Condition",
-			 fill = "Condition",
-			 linetype = "Condition",
-			 shape = "Condition") +
-		theme(legend.title = element_blank(),
-			  legend.position = "top",
-			  axis.title.x = element_blank())
-
-	epreds_diff |> 
-		ggplot(aes(timebin, diff)) +
-		facet_wrap(~lp) +
-		stat_lineribbon(.width = 0.95,
-						linewidth = 0,
-						fill = "grey") +
-		stat_summary(data = epreds_diff,
-					 fun = "mean",
-					 geom = "line",
-					 colour = "black",
-					 linewidth = 3/4) +
-		geom_hline(yintercept = 0, 
-				   linewidth = 1/2,
-				   colour = "black",
-				   linetype = "dotted") +
-		labs(x = "Time (ms)",
-			 y = "Related - Unrelated",
-			 fill = "CrI") +
-		theme(strip.text = element_blank(),
-			  legend.position = "none") +
-
-		plot_layout(ncol = 1) &
-		plot_annotation(tag_levels = "A") +
-		scale_linetype_manual(values = rev(c("solid", "dashed"))) &
-		# scale_shape_manual(values = c(1, 2)) &
-		scale_x_continuous(labels = \(x) format((x * 1e2), 
-												big.mark = ",")) &
-		theme(panel.grid = element_blank(),
-			  legend.position = "top") 
-}
-
-plot_gamm(data_time_related, 
-		  model_fits_related[[1]],
-		  contrast = "related")
-
+		 fill = "Condition") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	theme(legend.position = "top",
+		  panel.grid.major = element_line(colour = "grey",
+		  								linetype = "dotted"))
 ```

### 2023-10-31 R/gaze.R

@@ -77,8 +77,8 @@ get_gaze_processed_bcn <- function(gaze_files){
 			   .by = c(filename, trial, phase)) |> 
 		# trim timestamps outside the 2 seconds range
 		filter(between(trial, 1, 32),
-			   !(phase=="Prime" & timestamp > 1.5), 
-			   !(phase=="Target-Distractor" & timestamp > 2.0)) |> 
+			   !(phase=="Prime" & timestamp >= 1.5), 
+			   !(phase=="Target-Distractor" & timestamp >= 2.0)) |> 
 		# change gaze coordinates from 0-1 scale to screen resolution scale [1920x1080]
 		mutate(x = x*screen_resolution["x"],
 			   y = y*screen_resolution["y"]) |> 
@@ -157,6 +157,54 @@ get_gaze_raw_bcn <- function(gaze_files){
 	test_gaze_raw(gaze_raw)
 	
 	return(gaze_raw)
+}
+
+
+#' Get name dictionaries
+get_name_dictionary <- function(...) {
+	
+	col_name_changes <- c(
+		id = "participant",
+		id = "suje_num",
+		timestamp = "time",
+		timestamp = "system_time_stamp",
+		l_x = "l_1",
+		l_y = "l_2",
+		phase = "process",
+		phase = "baseline",
+		r_x = "r_1",
+		r_y = "r_2",
+		l_user_coord_z = "l_user_coord_3",
+		r_user_coord_z = "r_user_coord_3",
+		is_valid_gaze = "mean_validity",
+		is_valid_gaze = "is_valid_gaze",
+		id = "sujenum",
+		trial_num = "numtrial_lista"
+		# trial = "trial_num"
+	)
+	
+	phase_name_changes <- c(
+		"GETTER" = "Getter",
+		"baseline" = "Getter",
+		"PRIMEIMAGE" = "Prime",
+		"prime" = "Prime",
+		"primeimage" = "Prime",
+		"BLANK" = "Blank",
+		"Blank_AUDIO" = "Audio",
+		"BLANK_AUDIO" = "Audio",
+		"blank" = "Blank",
+		"audio" = "Audio",
+		"TARGET_DISTRACTOR" = "Target-Distractor",
+		"target_distractor" = "Target-Distractor"
+	)
+	
+	relevant_variables <- c("trial", "phase", "x", "y", "is_valid_gaze")
+	
+	name_dict <- list(col_name_changes = col_name_changes, 
+					  phase_name_changes = phase_name_changes, 
[…]

### 2023-10-31 docs/2023-10-31_report.qmd
Update targets progress

--- 2023-10-31 manuscript/manuscript.qmd
@@
+---
+title: "Cognate Priming: Report"
+format: html
+---
+
 ```{r setup}
@@
 						script = here::here("_targets.R"))
-
 targets::tar_load_globals()
@@
 
-# Introduction
-
-## The early lexicon
-
-Building a mental lexicon is a major achievement in the developmental journey of infants: by accumulating lexical representations of familiar words, infants are later able to recognise them in speech, and to extract meaning from the speech they are exposed to.
-Infants start forming their first lexical representations before their first year of life [@jusczyk1999; @halle1994; @vihman2004].
-When presented with pairs of pictures of familiar objects, 6-months-old infants already direct their gaze towards whichever is named [@bergelson20126; @bergelson2015early].
-This initial lexicon is hardly larger than around fifteen words [@REFERENCE], but it undergoes rapid growth [@REFERENCE] during their second year of life, at the end of which toddlers know an average of XXX words, and by 30 months of age, they know XXX words [@REFERENCE].
-This accelerated lexical developmental during the second year of life is also reflected in infants'  trajectories of word recognition: infants recognise familiar words faster and more efficiently [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
-Bilingual infants' trajectories of lexical acquisition [@hoff2012, @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes] and word recognition [@vihman2007onset; @vihman2013; @legacy2018vocabulary] are equivalent to their monolingual peers'.
-This is a remarkable deed: bilingual infants receive a relative impoverished linguistic input in each of their languages compared to monolinguals [@costa2014does].
-The mechanism that facilitate bilingual lexical development are still unclear.
-
-## (Early) Word recognition is cascaded
-
-Despite their different linguistic input, monolinguals and bilinguals share broadly common word recognition mechanisms.
-The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal.
-This results in the activation of lexical representations whose associated phonological forms matches the acoustic signal to some extent.
-The activated word-forms then compete for selection: the lexical system uses the auditory input, together with top-down context provided by grammatical, supra-segmental, and semantic constraints, to select the candidate lexical representation with the best match.
-There is evidence that spoken word recognition occurs in a *cascaded* fashion.
-The activation and selection of candidate lexical representations overlap in time, relying on partial information that accumulates as the speech signal unfolds [@marslen1987functional; @marslen1978processing; @grosjean1980spoken].
-This cascaded activation triggered by lexical access also results in the activation of the concepts associated to the accesses phonological forms.
-@allopenna1998tracking.
-
-This is also the case of the developing lexicon: like adults, infants activate non-selected lexical representations.
-This is relfected by the fact that from 21 months of age, infants' lexicon seems to be systematically organised accordi to the semantic and phnological properties of the lexical representations.
-
-SEMANTICS
-@arias2009lexical showed evidence of semantic priming in 21-month-old infants.
-In a word recognition task, infants' recognition of a spoken word (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
-Later studies provided electrophysiological evidence of such effect as early as 14 months of age [@friedrich2005lexical].
-
-PHONOLOGY
-Initial lexical representations are also phonologically well-specified [@swingley2000spoken; @swingley2002lexical].
-Overall these results suggest that early lexical representations are systematically organised in the lexicon according to their semantic and phonological properties.
-
-BOTH
-@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
-In each trial, the authors presented participants with four semantically and phonologically pictures.
-Four seconds after pictures onset, a word-form was auditorily presented.
-The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category.
-For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
-Then they would hear the carrier phrase "Look at the **bee**!".
-The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
-These results support a cascaded activation account of lexical access during the first stages of lexical development.
-@swingley1999continuous
-
-## Cascaded activation in bilingual parallel activation
-
-There is also evidence of cascaded activation in bilinguals.
-A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
-When listening to speech, bilinguals activate all lexical candidates from either language consistent with the speech signal.
-Even more surprising, when speaking, bilinguals activate all potential words consistent with the concepts they want to express.
-This effect has been systematically reported in adults [@marian1999activation; @costa2000cognate; @thierry2007brain; @dunabeitia2009masked].
-
-For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
-This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
-
-A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
-Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
-Cognates are form-similar translation equivalents.
-Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
-
-Also in toddlers [@von2012language; @von2014bilinguals] and school-aged children [@persici2019lexical; @bosma2020cognate].
-Some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
-Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
-Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that Spanish-Catalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
-
-Although recent work has provided strong evidence of parallel activation in early ages, how cognateness shapes that organisation of the early bilingual lexicon, and how this is reflected on the dynamics of lexical access during word comprehension and production is unclear.
-
-Using the experimental paradigm developed by [@arias2009lexical; @arias2013s; @singh2014one] compared within and across language
-priming effects in Chinese-English toddlers.
-@kuipers2015bilingualism compared ERP responses to picture-word pairs in English monolinguals and Welsh-English bilinguals where the words were either semantically related or unrelated to a pictured object.
-Although both studies tested 30-month-olds, the conclusions the authors reached do not fully agree.
-@singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
-
-## Cognate word recogntiion
-
-@floccia2020translation tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
-The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, French, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
-A prime word was embedded at the end of a carrier sentence that participants listened to.
-Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
-In Study 1, the target word was the translation equivalent of the prime word (*cheese*-*fromage* for an English-French bilingual).
-In other trials, prime and target words were unrelated (e.g., *sock*-*fromage*).
-There was no phonological overlap at onset between prime and target or distractor labels in either of the two conditions.
-Participants were presented with two blocks of related and unrelated trials.
-In one of the blocks, participants were presented with English prime words and Home Language target words (*sock*-*fromage*), and in the other block they were presented with Additional Language prime words and English target words (*fromage*-*sock*).
-The authors found a cross-linguistic priming effect, in which participants showed a stronger preference for the target picture in the post-naming phase in related trials, as compared to unrelated trials.
-This effect was found regardless of the language of the prime (English or Home Language), or the dominance of the language of the prime (i.e., whether the prime word belonged to the dominant language).
-Target preference exceeded chance level in both conditions.
-In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
-This time, prime and target words were not translation equivalents, but rather words whose referents shared semantic features.
-Results from Study  2 were parallel to those from Study 1.
-The authors found a strong semantic priming effect across languages, regardless of the language of the prime or the dominance of the language of the prime.
-Overall these results suggest that bilinguals recognised target words in both conditions, and benefited from a cross-linguistic facilitation effect from translation equivalents.
-The symmetry of such effect across both languages suggests that participants lexical access occurred in parallel for the two members of translation equivalents.
-As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
-The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
-However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generated by an interaction by the phonological and semantic overlap between cognate primes and targets.
-
-Another source of evidence supporting the language non-selective account of lexical access is provided by cross-languistic priming priuming thorught translation paradigms.
-In line with @floccia2020translation, @von2012language found that bilingual toddlers aged 21-to-43-months, and who were learning German and English, showed a stronger target preference in a German word recognition task after being primed with a phonologically related English word, which shared phonological onset with the prime word (e.g., *slide*-*Klide* [German for *dress*]), compared to when prime and target words were phonologically unrelated (e.g., *bottle*-*Ohr* [German for *ear*]).
-Interestingly, they also found evidence of such priming effect when participants were prime with an English word which was *not* phonologically related to the German target word, but rather its German translation was (e.g., *leg* [with German trasnlation *Bein*]-*Stein* [German for *stone*]).
-Altogether, these results indicate that bilingual toddlers activate translation equivalents in parallel during word recognition, and that the phonology of both labels may interact with lexical access in the recognition of subsequet words.
-Importantly, cross-linguitic priming through translation demonstrates that previous findings of a cognateness facilitation in word production and recognition do not result from the mere phonological overlap between auditorily presented and target labels, but also from the phonological overlap between the prime translation (not presented) and the target.
-
-Evidence from cognates.
-Marian and Spivey (1999)
-Costa et al. (2000)
-
-@dijkstra2019multilink
-
-The role of cognates in lexical processing.
-
-Another source of evidence are studies studies involving phonological priming of non-cognates through translation. [SEE REFERENCES FROM VON HOLZEN 2012]
-
-## The rpesent study
-
-The aforementioned studies use priming-though-translation paradigms.
-In these paradigms, cross-linguistic priming results from activation spreading from the lexical representation of the the (auditorily presented) prime word to the lexical representation of its translation through semantic associations (e.g., translation equivalence).
-When prime words are auditorily presented, the task design constraints the naming context to one of the languages.
-The consequence is a potential asymmtry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
-This might lead to a lower strength, and higher lacenty of the activation of the translation.
-
-In the present study, we use an adaptation of an implicit naming paradigm by @mani2010infant, in which participants are primed with a picture, instead of an auditorily presented label.
-@mani2010infant showed that 18 month-old monolinguals implicitly generate the labels of name-known pictures presented in silence.
-In each trial, infants were presented with prime pictures presented in silence, and then with a target and a distractor picture, both presented side-by-side.
-Finally, the target picture's label was presented auditorily.
-The authors manipulated the phonological overlap between the prime label and the target label, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
-Prime and target-distractor pairs were semantically unrelated.
-Interestingly, infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
-This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
-In particular, the authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
-
-@mani2011phonological used the same paradigm in 24-months-old monolinguals, and also found evidence of implicit naming, but in the opposite direction.
-After phonologically related primes, infants showed weaker target looking preference than after phonologically unrelated primes.
-These results interpreted these outcome as the result of the implicitly generated prime label interfering with the subsequent recognition of the (phonologically related) target word.
-The authors suggested that the shift from facilitation to interference from 18 to 24 months they found in both studies might be the result of a developmental shift in which 18-month-olds' lexicon is not yet organised based on phonological similarity, while 24-month-olds' is.
-This would lead to the former showing a pre-lexical facilitation effect in which such facilitation occurs via the activation of phonological segments, while the latter would show an interference effect due to lateral links between lexical representation having been established.
-Both studies by Mani and Plunkett provide evidence of implicit naming of name-known pictures by 18-month old toddlers and older, and that the resulting labels interact with the dynamics of recognition of subsequently presented word-forms.
-
-Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
-@duta2012erp presented name-known pictures in silence for one second.
-After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
-In some trials the auditory label corresponded to a canonical realisation of the word-form.
-In other trials, the word was mispronounced.
-Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
-A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
-This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
-
-When extended to the bilingual case, this implicit naming task may offer bilingual participants with an uncontrained naming context in whcih the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
-Using an adaptation of @mani2010infant's implicit naming paradigm, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
-The authors presented German-English bilinguals with 120 prime-target pairs.
-Primes were presented as familiar pictures in silence.
-After prime picture offset, target words were presented auditorily.
-Participants' N400 ERP components were recorded from target word onset.
-The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
-When prime and target were phonologically identical (*Affe*-*Affe*, German for *monkey*), or similar (*Fahne*-*Sahne*, German for *flag* and *ice-cream*, respectively) within L1, participants' showed a reduced N400 amplitude, compared to when prime and target were phonologically unrelated (*Messer*-*Seil*, German for *knife* and *rope*).
-Critically, a similar effect was found when prime and target were phonologically related through translation (*Rustsche*-*Kleid*, German for *slide* and *dress*).
-This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
-
-Evidence from cognates.
-
-The role of cognates in lexical processing.
-
-This study also provides a more suitable design for drawing conslusions about developmental change in word recognition trajectories frot wo reasons.
-First, it extends the age range of participants, compared to previous studies.
-Second, participants were tested at three selected age points to ensure a more balanced sample size across ages.
-Third, the partially longitudinal design allows modelling the performance of participants across testing sessions altogether.
-
-. In order to circumvent the problem of limited vocabulary knowledge
-in the non-dominant language, we propose to test participants only in their dominant language, therefore
-directing our research to the question of how possessing a second language affects processing of the
-dominant one in bilingual toddlers [@costa2014does provide a fuller description of the
-advantages of such approach].
-
-## The present study
-
-The present study is aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
-Using an adaptation of [@mani2010infants], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
-We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
-If so, phonological priming effect should be larger when the prime label in  both languages shares phonological overlap with the target words (cognate condition), compared to when only the label of the prime in one language overlaps phonologically with the target (non-cognate condition).
-We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
-
-We compared the explanatory power of three measures of vocabulary size on participants' trajectories of word recognition: L1 vocabulary and total vocabulary.Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary]
-
-# Methods
-
-All materials, data, and reproducible code can be found at the OSF ([https://osf.io/hy984/](https://osf.io/ckydb/)) and GitHub ([https://github.com/gongcastro/cognate-priming](https://github.com/gongcastro/cognate-priming)) repositories.
-This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I.
-Before every testing session, caregivers were asked to read and sign an informed consent form, and were given a token of appreciation at the end of it.
-
-## Participants
-
-```{r}
-#| label: participants-numbers
-n_participants_total <- participants |> 
-	distinct(location, child_id) |> 
-	count(location)
-
-n_participants_sex <- participants |> 
-	distinct(location, sex, child_id) |> 
-	count(location, sex)
-
-n_participants_sessions <- count(participants,
-								 child_id,
-								 name = "n_sessions") |> 
-	count(n_sessions) |> 
-	group_split(n_sessions) |> 
-	set_names(paste0("session_", 1:3))
-
-n_sessions_total <- count(participants)
-
-n_sessions_lp <- participants |> 
-	summarise(across(age, lst(mean, sd, min, max)),
-			  n = n(),
-			  .by = c(lp)) |> 
-	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
-	group_split(lp) |> 
-	set_names(janitor::make_clean_names(unique(participants$lp)))
-
-n_sessions_dominance_lp <- count(participants, lp, test_language) |> 
-	group_split(test_language) |> 
-	set_names(c("catalan", "english", "spanish")) |> 
-	map(group_split, lp)
-
-n_sessions_lp <- participants |> 
-	count(lp) |> 
-	group_split(lp) |> 
-	set_names(c("monolingual_eng", "monolingual", "bilingual"))
-```
-
-We collected data from `r n_participants_total$n[1]` participants living in the Metropolitan Area of Barcelona (Spain) tested at the Laboratori de recerca en Infància at the Universitat Pompeu Fabra (`r n_participants_sex$n[1]` female, `n_participants_sex$n[2]` male), and `r n_participants_total$n[2]` participants living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford (`r n_participants_sex$n[3]` female, `n_participants_sex$n[4]`, `n_participants_sex$n[5]` not reported).
-Families were recruited from maternity room in private hospitals or from social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r sum(n_participants_total$n)` children that participated, `r n_participants_sessions$session_1$n` participated once, `r n_participants_sessions$session_2$n` participated twice, and `r n_participants_sessions$session_3$n` participated three times.
-Recurrent participants were tested with at least XXX months of difference.
-We gathered a total of `r n_sessions_total$n` testing sessions: `r n_sessions_lp$monolingual_english$n` from participants in Oxford, and `r n_sessions_lp$monolingual$n + n_sessions_lp$bilingual$n` from participants in Barcelona.
-
-We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
-Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
-The output of this interview is an estimated degree of exposure (*DoE*) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
-According to this estimate, we classified participants as Catalan-, English-, or Spanish-dominant if the language with highest *DoE* was Catalan, English, or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
-From the `r n_sessions_total$n` testing sessions, `r n_sessions_lp$monolingual_english$n` belonged to English monolinguals,  `r n_sessions_lp$monolingual$n` to Catalan or Spanish monolinguals, and  `r n_sessions_lp$bilingual$n` to Catalan-Spanish bilinguals.
-@tbl-participants shows a detailed description of the linguistic profile of our sample.
+# Participants
 
@@
 	cols_merge_range(age_min, age_max) |> 
-	cols_merge_uncert(age_mean, age_sd) |> 
-	cols_merge_uncert(doe_catalan_mean, doe_catalan_sd) |> 
-	cols_merge_uncert(doe_english_mean, doe_english_sd) |> 
-	cols_merge_uncert(doe_spanish_mean, doe_spanish_sd) |> 
+	cols_merge(c(age_mean, age_sd), pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean, age_sd), pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_catalan_mean, doe_catalan_sd), pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_english_mean, doe_english_sd), pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_spanish_mean, doe_spanish_sd), pattern = "{1} ({2})") |> 
 	tab_spanner("Age (months)", matches("age")) |> 
@@
 
-We collected data from `r n_participants_total` monolingual and bilingual participants living in the Metropolitan Area of Barcelona (Spain), who were exposed to at least Catalan and/or Spanish from birth.
-Families were recruited from maternity room in private hospitals in Barcelona, and contacted via phone when the child's age spanned between our age intervals of interest.
-Families were invited to participate at three age points: 21, 25, and 30 months.
-`r n_participants_sessions[[1]]$n` participants were tested at one age point,  `r n_participants_sessions[[2]]$n` at two age points, and `r n_participants_sessions[[3]]$n` at the three age points.
-In total, we gathered data from `r n_sessions_total$n` testing sessions: `r n_sessions_age_group$age_21$n` at 21 months (*Mean* = `r round(n_sessions_age_group$age_21$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_21$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_21$age_min`--`r n_sessions_age_group$age_21$age_max`), `r n_sessions_age_group$age_25$n` at 25 months (*Mean* = `r round(n_sessions_age_group$age_25$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_25$age_min`--`r n_sessions_age_group$age_25$age_max`), and `r n_sessions_age_group$age_30$n` at 30 months (*Mean* = `r round(n_sessions_age_group$age_30$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_30$age_min`--`r n_sessions_age_group$age_30$age_max`).
-
-Participants' vision was normal, none used glasses or any other type of vision corrector.
-
-### Language profile {#sec-lp}
-
-We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
-Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
-The output of this interview is an estimated degree of exposure (DoE) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
-According to this estimate, we classified participants as Catalan- or Spanish-dominant if the language with highest DoE was Catalan or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
-We collected data from `r n_sessions_dominance$catalan$n` Catalan-dominant participants in Catalan (`r n_sessions_dominance_age_group$catalan$age_21$n` at 21 months, `r n_sessions_dominance_age_group$catalan$age_25$n` at 25 months, and `r n_sessions_dominance_age_group$catalan$age_30$n` at 30 months).
-We further classified participants as monolinguals if the DoE to their dominant language exceeded 80% of the total DoE to Catalan and Spanish, and as bilinguals otherwise.
-Participants with DoE to language other than Catalan or Spanish were excluded from analyses.
-This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
-@tbl-participants-lp shows a detailed description of the linguistic profile of our sample.
-
-### Vocabulary size
-
-```{r vocab-values}
-n_imputed <- table(vocabulary$is_imputed)[2]
-prop_imputed <- scales::percent(n_imputed/nrow(vocabulary))
-n_pool <- nrow(bvq_data$vocabulary)
-```
-
-We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability] developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers.
-Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
-
-We calculated several measures of receptive vocabulary size from each participant's vocabulary: L1 vocabulary size (proportion of words  reported as acquired in the checklist of the dominant language), L2 vocabulary size (proportion of words  reported as acquired in the checklist of the non-dominant language), total vocabulary size (proportion of the words in both checklists reported as acquired), conceptual vocabulary (proportion of concepts for which the participant was reported to have acquired at least one label, in any language), and translation equivalent vocabulary (proportion of concepts for which the participant was reported to have acquired at two labels, one in each language).
-
-`r n_imputed` (`r prop_imputed`) Families failed to provide a complete response to the BVQ within the two-week time limit, or did not provide a successful response to the questionnaire.
-For missing questionnaire responses, we imputed the vocabulary size of the participant using single imputation, using the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
-We used participants age in months and their language profile (monolingual/bilingual) as predictors.
-We used the `mice` R package [@van2011mice] to perform imputation using the Bayesian linear regression method.
+# Vocabulary size
 
@@
 
-## Stimuli
-
-```{r stimuli-values}
-n_words <- length(unique(with(stimuli, unlist(prime, target, distractor))))
-```
-
-We used `r n_words` distinct words included in the BVQ to create the stimuli lists.
-We created six stimuli lists: three in Catalan, and three in Spanish.
-Each list contained 32 trials, each involving a prime-target-distractor group.
-Each word played a role as either prime, *or* as target and distractor across the three lists in their corresponding language.
-For instance, the Catalan word *cadira* appeared as *prime* in the three lists, but never as *target* or *distractor*; the Catalan word *bici* appeared as *target* and *distractor* across the three lists, but never as a prime.
-Target-distractor pairings were held constant across the three lists in each language.
-For instance, in all Catalan lists the word *bici* was paired with the word *porta*.
-Target-distractor pairings were also yoked, so that each member of the same target-distractor pair appeared once as target and once as distractor in each list.
-For instance, the *bici*-*porta* paired appeared twice in each of the three Catalan lists: once with *bici* as target and *porta* as distractor, and once with *porta* as target and *bici* as distractor.
-This counterbalancing avoided participants encountering looking at the target word guided solely by that word having being named in a previous trial.
-Finally, prime words appeared only once in each list: each target-distractor pair was associated with a different prime word in both appearances.
-In each list, the same prime word was presented alongside a different target-distractor pair.
-For instance, the Catalan prime word *barret* was presented with the *bici*-*porta* target-distractor pair in one list, with the *bici*-*porta* pair in another list, and with *berenar*-*amanida* in the remaining list.
-The order of the trials was randomised across experimental session, so that each time a participant was tested, the order in which the prime-target-distractor was presented was randomised.
-Each participant was randomly assigned to one of the three lists in the corresponding language (their dominant language, see @sec-lp), and always the same list across their experimental sessions in the case of a recurrent participant.
-
-In 16 of the 32 trials of the same list (henceforth *related* trials), the prime and the target words were phonologically related, sharing phonological onset (at least first phoneme).
-In the other 16 trials (*unrelated* trials), prime and target did not share phonological onset.
-8 of the 16 *related* trials included a cognate prime (*cognate* trials), and the other 8 included a non-cognate trials (*non-cognate* trials).
-A prime word was considered cognate if its Catalan and Spanish translation shared phonological onset.
-Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
-Target and distractor word pairs were phonologically unrelated (did not share phonological onset).
-Some of them shared semantic features or a taxonomic relationship.
-This is the case of words associated with especially salient referents such as animals or food.
-To avoid infants guiding their gaze to these objects based on their saliency, we paired animals and food items together.
-The position of the target and distractor pictures (right or left) for each target-distractor pair was alternated, so that in one list the target would appear on the left, in another list it would appear on the right, and so on.
-
-We examined the overall equivalence of the three trial types by comparing them across three variables relating to the target word: lexical frequency, word prevalence, animacy
-@tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
-Lexical frequencies were extracted from the Catalan and Spanish corpora of the CHILDES database [@reference; @reference] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@reference; @reference].
-We defined word prevalence as the proportion of same-aged infants who were reported to understand the word in the BVQ database.
-
-### Auditory stimuli
-
-The auditory stimuli were natural exemplars of the selected target words, spoken by Catalan-Spanish proficient bilingual female speaker who was instructed to pronounce each word in a toddler-directed manner.
-Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
-We used the Audacity [@reference] and Praat [@boersma2001speak] to record and edit the audio files.
-The speaker was presented with a list of words in Catalan.
-The order of the words was pseudo-randomised, and each word was produced three times in a row before moving to the next word in the list.
-After going through all the words in the list, the speaker went through the word list again generating three tokens for each word, now in an inverse order (from bottom of the list to the top).
-We then repeated the same procedure for the list of Spanish words.
-The resulting audios were manually chunked into individual word-forms.
-For each of the six tokens produced for each word, the most adequate was selected for further processing.
-The audios were then transformed to stereo by duplicating them into two channels, denoised, and finally normalised.
-The mean duration of the final audios was `r round(mean(stimuli$duration[stimuli$test_language=="Catalan"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Catalan"]), 2)`) and `r round(mean(stimuli$duration[stimuli$test_language=="Spanish"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Spanish"]), 2)`) seconds for the Catalan and Spanish lists.
-
-To make the pronunciation of the words as familiar as possible to each infant, we generated additional pronunciation variants for some words in Catalan and Spanish.
-Catalan words involving the /\textipa{L}/ phoneme in their Central Catalan variant (e.g., /\textipa{'Lu.n@}) were also recorded with such phoneme replaced by /j/ (e.g., /\textipa{'ju.n@}), a phonological process common in the Metropolitan Area of Barcelona [@reference].
-Spanish words involving the /\textipa{T}/ phoneme were also generated replacing such phoneme with /\textipa{s}/ to better accommodate Latin variants of Spanish.
-Before every experimental session, caregivers were asked to utter three written words involving the /\textipa{L}/ phoneme (in the case of participants tested in Catalan) or the /\textipa{T}/ phoneme (in the case of participants tested in Spanish).
-Each token contained the critical phoneme at onset, inter-vocalic position, and coda.
-The experimenter assigned the participant to the Catalan or Spanish stimuli list involving the closest variant to that of caregivers'.
-
-### Visual stimuli
-
-For each word, we created a picture with a typical referent.
-To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias-trejo2010].
-
-```{r tbl-stimuli}
-#| label: tbl-stimuli
-#| tbl-cap: "Summary of stimuli properties by trial type."
-stimuli |> 
-	summarise(across(c(matches("familiarity_|freq_|animate_"), duration),
-					 tibble::lst(mean, sd, min, max)),
-			  .by = c(test_language, trial_type)) |> 
-	select(-matches("familiarity_se"), -matches("prime"),
-		   -c(is_animate_target_sd,
-		      is_animate_target_min,
-		      is_animate_target_max),
-		   -matches("min"), -matches("max")) |> 
-	gt(groupname_col = "test_language",
-	   rowname_col = "list") |> 
-	fmt_number(is.numeric,
-			   decimals = 1) |> 
-	fmt_number(matches("familiarity|animate"),
-			   scale_by = 100,
-			   decimals = 1) |> 
-	cols_merge(c(freq_target_mean, freq_target_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(familiarity_target_mean, familiarity_target_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(duration_mean, duration_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_label(trial_type = "",
-			   familiarity_target_mean = "Prevalence (%)",
-			   freq_target_mean = "Frequency",
-			   is_animate_target_mean = "Animacy (%)",
-			   duration_mean = "Duration (s)") 
-```
-
-## Procedure
-
-Testing took place in a sound-proof room.
-Participants sat on their caregivers' lap in a dimly lit testing booth while the experimenter conducted the experiment from outside.
-Caregivers were instructed to keep their eyes shut (to avoid recording their gaze, instead of the participant's), to be still, and to avoid interacting with the participant verbally or non-verbally.
-Participants sat at approximately 65 cm from the eye-tracker and a XX-in screen of $1929\times1080$ screen resolution.
-We used a custom Matlab XXXX script using the PsychToolbox XXX extension [@brainard] to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
-Sampling rate was set at 120 Hz.
-A 5-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
-We set a 55% grey background for the calibration and stimuli presentation.
-Auditory stimuli were presented through two loudspeakers located behind the screen, one to each side.
-The experimenter monitored the experimental from outside the room using a centrally located video camera place above the screen.
-After a successful calibration the experimenter triggered the onset of the first trial.
-Trials were presented uninterruptedly and  without intervention of the experimenter until the 32 trials were presented, or the experimental session had to be stopped because of the participant's behaviour.
-
-![Experimental task design with examples in Catalan.
-In each trial, the prime image is presented in silence for 3,000 ms.
-The the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
-In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
-In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
-In unrelated trials (*n* = 32), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){fig-align="center"}
-
-Each trial started with the presentation of an attention getter for 3,000 milliseconds.
-Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
-Fifty milliseconds after the offset of the prime image, an auditory label was played from the loudspeakers and, 700 milliseconds after the onset of the auditory label, the target and distractor pictures were presented side-by-side during 1,000 milliseconds until the end of the trial.
-After this, the attention getter of the next trial was immediately presented.
-Each experimental session took approximately 10 minutes.
-
-## Apparatus
-
-see https://link.springer.com/article/10.3758/s13428-021-01762-8
-
-## Data processing
-
-```{r dataset}
-n_trials <- nrow(attrition)
-n_sessions <- n_distinct(attrition$session_id)
-n_participants <- n_distinct(attrition$child_id)
-n_trials_valid <- nrow(filter(attrition,
-							  is_valid_participant,
-							  is_valid_trial))
-n_sessions_valid <- sum(attrition_participants$is_valid_participant)
-n_participants_valid <- n_distinct(
-	attrition[attrition$is_valid_participant, ]$child_id)
-
-n_exc_prime <- sum(!attrition$is_valid_gaze_all_prime)
-n_exc_test <- sum(!attrition$is_valid_gaze_all_test)
-n_exc_test_each <- sum(!attrition$is_valid_gaze_all_test_each)
-n_exc_vocab <- sum(!attrition$is_valid_vocab)
-n_exc_participants <- sum(!attrition_participants$is_valid_participant)
-
-n_longitudinal <- attrition |>
-	filter(is_valid_participant,
-		   is_valid_trial) |>
-	distinct(child_id, session_n) |> 
-	count(child_id, name = "times") |> 
-	count(times)
-```
-
-We defined a time windows of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
-To avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
-Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
-We excluded trials in which participants failed to provide 50%  valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target-looking *and* distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
-Finally, we excluded trials in which participants did not understand the prime *or* the target word, according to a supplementary vocabulary checklist filled by their caregivers upon experiment completion (*n* = `r format(n_exc_vocab, big.mark = ",")`).
-After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`).
-The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition-trials shows a detailed description of the trial attrition.
-
-```{r tbl-attrition}
-#| label: tbl-attrition
-#| tbl-cap: "Participant-level and trial-level sample size after applying inclusion criteria. The number of excluded participants and trials is indicated between parentheses."
-expanded <- expand(attrition, lp, trial_type, is_valid_trial)
-
-n_lp <- attrition |> 
-	distinct(is_valid_participant, lp, session_id) |> 
-	count(is_valid_participant, lp) |> 
-	pivot_wider(names_from = is_valid_participant,
-				values_from = n,
-				names_repair = janitor::make_clean_names) |> 
-	mutate(n_participants_true = true,
-		   n_participants_false = false) |> 
-	select(lp, true, false)
-
-attrition |> 
-	summarise(n_trials_true = sum(is_valid_trial),
-			  n_trials_false = sum(!is_valid_trial),
-			  .by = c(lp, trial_type)) |> 
-	arrange(desc(lp)) |> 
-	# across(n_trials, lst(mean, sd, sum), na.rm = TRUE),
-
-	pivot_wider(id_cols = lp,
-				names_from = c(trial_type),
-				values_from = matches("trials"),
-				names_repair = janitor::make_clean_names) |> 
-	left_join(n_lp, by = join_by(lp)) |> 
-	mutate(lp = case_when(
-		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
-		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
-		.default = lp)) |>
-	select(lp, true, false,
-		   matches("n_trials")) |> 
-	gt(rowname_col = "lp") |> 
-	tab_spanner("Participants", matches("participant")) |> 
-	tab_spanner("Trials", matches("trial")) |> 
-	fmt_integer(everything()) |> 
-	cols_merge(c(true, false),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_cognate,
-				 n_trials_false_cognate),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_non_cognate,
-				 n_trials_false_non_cognate),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_unrelated, 
-				 n_trials_false_unrelated),
-				 pattern = "{1} ({2})") |> 
-	cols_label(true = "N", 
-			   n_trials_true_cognate = "Cognate",
-			   n_trials_true_non_cognate = "Non-cognate",
-			   n_trials_true_unrelated = "Unrelated") |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |>
-	grand_summary_rows(fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~ fmt_integer(.))
-```
-
-## Data analysis
-
-We conducted two main analyses.
-In the first analysis, we estimated the effect of phonological priming on participants' target looking comparing *related* trials---in which prime and target share phonological onset, and the prime was not a cognate word---with *unrelated* trials---in which prime and target did not share phonological onset, and neither was the prime a cognate word, leaving out *cognate* trials.
-This analysis included all trials on the data set.
-Second, we estimated the effect of cognateness on phonological priming, comparing *cognate* trials---in which prime and target shared phonological onset, and the prime was a cognate word that also shared phonological onset with the target, with *non-cognate* trials---in which prime a target shared phonological onset, and the prime was not a cognate---, leaving out *unrelated* trials.
-
-In both analyses, we modelled the probability of target looking across the time course of the trial.
-For each trial, we chunked the time domain of the target-distractor phase into 20 time bins of 100 ms of duration.
-We then calculated, for each experimental session, time bin, and condition, the number of eye-tracker samples in which the participant was looking to the target and the distractor pictures.
-Finally, we computed the empirical logit of target fixations using @eq-elogit [@barr2008analyzing; @agresti2012categorical], which modelled in our analyses using a Gaussian distribution.
-
-$$
-\eta' = \ln\bigg(\frac{\text{Target} + 0.5}{ \text{Distractor} + 0.5}\bigg)
-$$ {#eq-elogit}
-
-In the first analysis, we included *Relatedness* (`Related` vs.
-`Unrelated`, sum-coded as `-0.5` and `+0.5`), *Group* (`Monolingual` vs.
-`Bilingual`, sum-coded as `-0.5` and `+0.5`), and *Age* (participants' standardised age in months) as fixed, main effects, together with their two- and three-way interactions.
-We used multilevel General Additive Mixed Models (GAMMs) to model the time course of target looking, including cubic regression splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
-For both splines, we specified $k = 10$ basis functions or *knots*--half the number of time bins---for computational convenience.
-Finally, we added by-participant random intercepts, and random slopes for the main effect of *Relatedness* and the main effect of *Age*, both including repeated measures per participant [@pedersen2019hierarchical].
-In the second analysis, we included *Cognateness* (`Cognate` vs.
-`Non-cognate`, sum-coded as `-0.5` and `+0.5`) replacing *Relatedness*.
-@eq-model shows the formal implementation of the model.
-
-To test the contribution of each of the predictors of interest--*Relatedness*/*Cognateness*, and *Group*--, we compared each model ($\mathcal{M_0}$) against a simplified model dropping each of the main effects, *Relatedness*/*Cognateness* ($\mathcal{M}_1$) or *Group* ($\mathcal{M_2}$).
-In both simplified models, the interaction term was dropped.
-We used leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it.
-We then examined the posterior predictions of the best-performing model for interpretation.
-
-$$
-\begin{aligned}
-\textbf{Likelihood:} \\
-y_i &\sim \mathcal{N}(\mu_i, \sigma_i) \\ \\
-\textbf{Linear model:} \\
-\eta'(\mu_i) &= (\beta_0 + u _{0_{i}}) + (\beta_1 + u _{1_{i}}) \cdot \text{[Condition]} +\\
-&\beta_{2} \cdot \text{Group} + \beta_{3} \cdot (\text{[Condition]} \times \text{Group}) +\\
-& (\beta_4 + u_{2_{i}}) \cdot \text{Age} + \sum_{j = 1}^k b_{j_{1}} \cdot \beta_{5_{k}} \cdot \text{Time} + \sum_{j = 1}^k b_{j_{1}} \cdot\beta_{6_{k}} \cdot (\text{Time} \times \text{Group}) \\
-\text{where:} \\
-&\eta'\text{ is the empirical logit of target fixations} \\
-& \text{[Condition] should be replaced with } Relatedness \text{ or } Cognateness \\
-&k \text{ is the number of knots in the spline (10)} \\
-\textbf{Prior:} \\
-\beta_{0-6} &\sim \mathcal{N}(0, 0.5) \\
-u_{0-2} &\sim \mathcal{N}(0, \sigma_{0-2})\\
-b_{0-1} &\sim \text{MVN}(0, \tau_{0-1}) \\
-\sigma_{0-2}, \tau_{0-1} &\sim \text{Exponential}(6)\\
-\rho_{0-2} &\sim LKJCorr(6)\\
-\text{where:}\\
-&\rho_{0-2} \text{ are the correlation parameters for } \sigma_{0-2}
-\end{aligned}
-$$ {#eq-model}
-
 # Results
 
-## Preliminary analyses
+## Observed data
 
-```{r fig-ptlt-recognition}
-#| label: fig-ptlt-recognition-aggr
-#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-data_time |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(lp, timebin, session_id)) |> 
-	ggplot(aes(timebin, .prop, colour = lp)) +
-	facet_wrap(~lp, nrow = 1, scales = "free_x") +
-	geom_line(aes(group = session_id),
-			  # colour = "grey",
-			  alpha = 1/10) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = "mean_se",
-				 geom = "errorbar",
-				 width = 0.35,
-				 linewidth = 2/4) +
-	stat_summary(fun = "mean",
-				 geom = "point",
-				 size = 1.2) +
-	stat_summary(fun = "mean",
-				 geom = "line",
-				 linewidth = 2/4) +
-	labs(x = "Time (ms)",
-		 y = "PTLT") +
-	scale_x_continuous(breaks = seq(0, 20, 2),
-					   labels = \(x) format(x*100+300, big.mark = ",")) +
-	scale_y_continuous(labels = scales::percent,
-					   breaks = seq(0, 1, 0.2),
-					   limits = c(0, 1)) +
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  legend.position = "none")
-```
+## Model-based estimates
 
-```{r fig-ptlt-recognition-age}
-#| label: fig-ptlt-recognition-age
-#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-data_time |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(lp, timebin, age_group, session_id)) |> 
-	ggplot(aes(timebin, .prop, colour = age_group)) +
-	facet_wrap(~lp, nrow = 1, scales = "free_x") +
-	# geom_rug(aes(x = timebin[is.na(.prop)])) +
-	# geom_line(aes(group = session_id),
-	# 		  alpha = 1/8) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = "mean_se",
-				 geom = "errorbar",
-				 width = 0.35,
-				 linewidth = 2/4) +
-	stat_summary(fun = "mean",
-				 geom = "point",
-				 size = 1.2) +
-	stat_summary(fun = "mean",
-				 geom = "line",
-				 linewidth = 2/4) +
-	labs(x = "Time (ms)",
-		 y = "PTLT",
-		 colour = "Age") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	scale_y_continuous(labels = scales::percent,
-					   breaks = seq(0, 1, 0.05)) +
-	theme(legend.position = "top",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-```
-
-```{r fig-ptlt-recognition-condition}
-#| label: fig-ptlt-recognition-condition
-#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-data_time |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(lp, timebin, condition, session_id)) |> 
-	ggplot(aes(timebin, .prop, colour = condition)) +
-	facet_grid(~lp) +
-	# geom_rug(aes(x = timebin[is.na(.prop)])) +
-	# geom_line(aes(group = interaction(condition, session_id)),
-	# 		  alpha = 1/8) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = "mean_se",
-				 geom = "errorbar",
-				 width = 0.35,
-				 linewidth = 2/4) +
-	stat_summary(fun = "mean",
-				 geom = "point",
-				 size = 1.2) +
-	stat_summary(fun = "mean",
-				 geom = "line",
-				 linewidth = 2/4) +
-	labs(x = "Time (ms)",
-		 y = "PTLT",
-		 colour = "Condition") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	scale_y_continuous(labels = scales::percent,
-					   breaks = seq(0, 1, 0.05)) +
-	theme(legend.position = "top",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-```
-
-## Aggregated analysis
-
-In a first analysis, we examined the effect of phonological priming.
-We compared participants' looking preference for the target in related and unrelated trials.
-We first compared the aggregated probability of target looking across time bins in both conditions for each language group.
+### Aggregated analyses
 
@@
 
-## Time course analysis
-
-```{r fig-time}
-#| label: fig-time
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-nd <- expand_grid(condition = levels(model_fits_time$fit_time_2$data$condition),
-				  timebin = seq(0, 17, length.out = 100),
-				  voc_total = mean(model_fits_time$fit_time_2$data$voc_total),
-				  # sesion_id = first(data$session_id),
-				  # age = c(21, 25, 30),
-				  lp = levels(model_fits_time$fit_time_2$data$lp))
-
-epreds <- add_epred_draws(newdata = nd,
-						  object = model_fits_time$fit_time_2,
-						  ndraws = 20,
-						  re_formula = NA,
-						  value = ".value") |> 
-	mean_qi() |> 
-	mutate(lp = factor(lp, 
-					   levels = c("Monolingual (English)",
-					   		   "Monolingual",
-					   		   "Bilingual")))
-
-epreds |> 
-	ggplot(aes(timebin, .value,
-			   colour = condition,
-			   fill = condition)) +
-	facet_wrap(~lp) +
-	geom_hline(yintercept = 0,
-			   linetype = "dashed") +
-	geom_ribbon(aes(ymin = .lower, ymax = .upper),
-				alpha = 0.5,
-				linewidth = 0) +
-	geom_line(linewidth = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "Logit (Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	theme(legend.position = "top",
-		  panel.grid.major = element_line(colour = "grey",
-		  								linetype = "dotted"))
-```
+### Time course analyses
 
@@
 ```
-
-{{< pagebreak >}}
-
-# Discussion
-
-## Summary
-
-## Context
-
-## Facilitation vs. inhibition
-
-## Onsets vs. offsets
-
-## Problems and generalisatility
-
-## Future steps
-
-## Conclusions
-
-# References
-
-{{< pagebreak >}}
-
-# Appendix
-
-## Appendix A: imputing voabulary size scores
-
-```{r fig-vocabulary-imputation}
-vocabulary_tmp <- vocabulary |> 
-	left_join(select(participants, child_id, vocab_id, age),
-			  by = join_by(child_id, vocab_id)) |> 
-	relocate(child_id) |> 
-	filter(is_imputed)
-
-bvq_data$vocabulary |> 
-	inner_join(distinct(bvq_data$logs, child_id, response_id, lp, age),
-			   by = join_by(response_id)) |> 
-	mutate(is_imputed = FALSE) |> 
-	bind_rows(vocabulary_tmp) |> 
-	pivot_longer(ends_with("_prop"),
-				 names_to = "measure",
-				 values_to = "prop") |> 
-	drop_na(prop) |> 
-	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"),
-		   measure = factor(measure,
-		   				 levels = c("total_prop",
-		   				 		   "l1_prop",
-		   				 		   "l2_prop",
-		   				 		   "concept_prop",
-		   				 		   "te_prop"),
-		   				 labels = c("Total",
-		   				 		   "L1",
-		   				 		   "L2",
-		   				 		   "Conceptual",
-		   				 		   "TE"))) |> 
-	ggplot(aes(age, prop, 
-			   colour = is_imputed,
-			   fill = is_imputed)) +
-	facet_wrap(~measure) +
-	geom_point(alpha = 1/4, size = 1) +
-	geom_smooth(method = "glm", 
-				formula = "y ~ x",
-				method.args = list(family = "binomial"), 
-				# se = FALSE,
-				size = 1) +
-	labs(x = "Age (months)",
-		 y = "Vocabulary size",
-		 fill = "Imputed",
-		 colour = "Imputed") +
-	theme(legend.position = c(1, 0),
-		  legend.justification = c(1, 0),
-		  legend.title = element_blank())
-
-```
-
-{{< pagebreak >}}
-
-## Appendix B: distribution of prime and target looking times
-
-```{r fig-dist-prime}
-#| label: fig-dist-prime
-#| fig-height: 4
-#| fig-width: 8
-looking_times |> 
-	mutate(prime_time = cut(prime_time, 
-							seq(0, 1.5, 0.1),
-							labels = FALSE,
-							include.lowest = TRUE)) |> 
-	add_count(lp, age_group, name = "n_total") |> 
-	count(lp, age_group, prime_time, n_total) |> 
-	mutate(n = n / n_total) |> 
-	ggplot(aes(prime_time, n)) +
-	facet_grid(lp~age_group) +
-	annotate(geom = "rect",
-			 fill = "orange",
-			 ymin = -Inf,
-			 ymax = Inf,
-			 xmin = 0,
-			 xmax = 0.75*10,
-			 alpha = 1/3,
-			 colour = NA) +
-	# annotate(label = "Excluded trials",
-	# 		 geom = "text",
-	# 		  x = (0.75/2)*10,
-	# 		  y = 1)
-	geom_col(fill = "black") +
-	labs(x = "Prime looking time (s)",
-		 y = "Proportion of trials") +
-	scale_x_continuous(labels = \(x) x/10) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"))
-```
-
-```{r fig-dist-target}
-#| label: fig-dist-target
-#| fig-height: 4
-#| fig-width: 8
-looking_times |> 
-	mutate(target_time = cut(target_time, 
-							 seq(0, 2, 0.1),
-							 labels = FALSE,
-							 include.lowest = TRUE)) |> 
-	add_count(lp, age_group, name = "n_total") |> 
-	count(lp, age_group, target_time, n_total) |> 
-	mutate(n = n / n_total) |> 
-	ggplot(aes(target_time, n)) +
-	facet_grid(lp~age_group) +
-	# annotate(label = "Excluded trials",
-	# 		 geom = "text",
-	# 		  x = (0.75/2)*10,
-	# 		  y = 1)
-	geom_col(fill = "black") +
-	labs(x = "Targets looking time (s)",
-		 y = "Proportion of trials") +
-	scale_x_continuous(labels = \(x) x/10) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"))
-```
-
-{{< pagebreak >}}
-
-## Appendix C: prime and test looking times
-
-```{r fig-looking-times}
-#| label: fig-looking-times
-#| fig-height: 8
-#| fig-width: 8
-#| fig-cap: "Looking time (s) to the prime and target AOI against audio duration. In longer audios, participants are expected to look longer to the prime and target picture."
-
-looking_times |>
-	left_join(select(attrition_trials, 
-					 filename, trial, is_valid_trial),
-			  by = join_by(filename, trial)) |>
-	filter(is_valid_trial) |> 
-	ggplot(aes(duration,
-			   prime_time,
-			   colour = trial_type, 
-			   fill = trial_type,
-			   shape = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_point(alpha = 0.5, 
-			   size = 1) +
-	geom_smooth(method = "lm") +
-	theme(axis.title.x = element_blank()) +
-
-	looking_times |>
-	left_join(select(attrition_trials, 
-					 filename, trial, is_valid_trial),
-			  by = join_by(filename, trial)) |>
-	filter(is_valid_trial) |> 
-	ggplot(aes(duration,
-			   target_time,
-			   colour = trial_type, 
-			   fill = trial_type,
-			   shape = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_point(alpha = 0.5,
-			   size = 1) +
-	geom_smooth(method = "lm",
-				formula = "y ~ x") +
-	plot_layout(ncol = 1, guides = "collect") &
-	plot_annotation(tag_levels = "A") &
-	labs(x = "Audio duration (s)",
-		 y = "Looking time (1.0-2.0 seconds)",
-		 colour = "Prime type",
-		 fill = "Prime type",
-		 shape = "Prime type") 
-```
-
-## Appendix D: vocabulary checklist validity
-
-```{r fig-validity-target}
-get_data(gaze = gaze,
-		 participants = participants,
-		 stimuli = stimuli,
-		 vocabulary = vocabulary,
-		 attrition_trials = attrition_trials,
-		 attrition_participants = attrition_participants,
-		 time_subset = c(0, 2),
-		 contrast = "related",
-		 is_valid_vocab_all,
-		 clean = FALSE) |> 
-	unnest_wider(is_valid_vocab_all) |>
-	select(session_id, lp, .elog, target) |> 
-	arrange(session_id, target) |> 
-	summarise(.elog_mean = mean(.elog),
-			  .elog_sd = sd(.elog),
-			  n = n(),
-			  .by = c(lp, target)) |> 
-	mutate(target = ifelse(target, "Yes", "No"),
-		   .elog_se = .elog_sd/sqrt(n),
-		   .elog_lower = .elog_mean - .elog_se*1.96,
-		   .elog_upper = .elog_mean + .elog_se*1.96,
-	) |> 
-	ggplot(aes(lp, .elog_mean, 
-			   ymin = .elog_lower,
-			   ymax = .elog_upper,
-			   colour = target)) +
-	facet_wrap(~lp, ncol = 1, scales = "free_x") +
-	geom_errorbar(width = 0.2, linewidth = 3/4, 
-				  position = position_dodge(width = 0.25)) +
-	geom_point(size = 2,
-			   position = position_dodge(width = 0.25)) +
-	geom_hline(yintercept = 0,
-			   linetype = "dashed") +
-	labs(x = "Condition",
-		 y = "P(Target looking)", 
-		 colour = "Knows the target word") +
-	theme(legend.position = "none",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted")) +
-
-	get_data_time(gaze = gaze,
-				  participants = participants,
-				  stimuli = stimuli,
-				  vocabulary = vocabulary,
-				  attrition_trials = attrition_trials,
-				  attrition_participants = attrition_participants,
-				  time_subset = c(0, 2),
-				  contrast = "related",
-				  is_valid_vocab_all,
-				  clean = FALSE) |> 
-	unnest_wider(is_valid_vocab_all) |>
-	select(session_id, age, lp, timebin, .elog, target) |> 
-	arrange(session_id, target) |> 
-	summarise(.elog_mean = mean(.elog),
-			  .elog_sd = sd(.elog),
-			  n = n(),
-			  .by = c(timebin, lp, target)) |> 
-	mutate(target = ifelse(target, "Yes", "No"),
-		   .elog_se = .elog_sd/sqrt(n),
-		   .elog_lower = .elog_mean - .elog_se*1.96,
-		   .elog_upper = .elog_mean + .elog_se*1.96,
-	) |> 
-	ggplot(aes(timebin, .elog_mean,
-			   ymin = .elog_lower,
-			   ymax = .elog_upper,
-			   colour = target,
-			   fill = target)) +
-	facet_wrap(~lp, ncol = 1, scales = "free_x") +
-	geom_line(linewidth = 1/2) +
-	geom_ribbon(alpha = 1/2,
-				colour = NA) +
-	geom_point(size = 2) +
-	geom_hline(yintercept = 0,
-			   linetype = "dashed") +
-	labs(x = "Condition",
-		 y = "P(Target looking)", 
-		 fill = "Knows the target word",
-		 colour = "Knows the target word") +
-	theme(legend.position = "top",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"),
-		  axis.title.y = element_blank(),
-		  axis.line.x = element_line()) +
-
-	plot_layout(ncol = 2,
-				widths = c(0.2, 0.8)) &
-	scale_y_continuous(limits = c(-0.5, 1.25))
-```

### 2023-10-31 docs/report.qmd
Update targets progress

--- 2023-10-31 docs/2023-10-31_report.qmd
@@
 ---
-title: "Cognate Priming: Report"
-format: html
 ---
@@
 						script = here::here("_targets.R"))
-targets::tar_load_globals()
 

### 2023-10-31 manuscript/manuscript.qmd
Fix manuscript setup code chunk

@@
+---
+---
+
 ```{r setup}
@@
 	  bvq_data,
-	  gaze_aoi, 
+	  gaze,
 	  data_time,
-	  data_aggr,
+	  data_aggr
 	))
@@
 	c(model_fits_aggr,
-	  model_fits_time
-	  # model_loos_aggr,
-	  # model_loos_time,
+	  model_fits_time,
+	  model_loos_aggr,
+	  model_loos_time
 	))
@@
 Recurrent participants were tested with at least XXX months of difference.
-We gathered a total of `r n_sessions_total$n` testing sessions: `r n_sessions_lp$monolingual_english$n` from participants in Oxford, and `r n_sessions_lp$monolingual$n + n_sessions_lp$bilingual$n` from participants in Barcelona.
+We gathered a total of `r n_sessions_total$n` testing sessions: `r n_sessions_lp$monolingual_eng$n` from participants in Oxford, and `r n_sessions_lp$monolingual$n + n_sessions_lp$bilingual$n` from participants in Barcelona.
 
@@
 According to this estimate, we classified participants as Catalan-, English-, or Spanish-dominant if the language with highest *DoE* was Catalan, English, or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
-From the `r n_sessions_total$n` testing sessions, `r n_sessions_lp$monolingual_english$n` belonged to English monolinguals,  `r n_sessions_lp$monolingual$n` to Catalan or Spanish monolinguals, and  `r n_sessions_lp$bilingual$n` to Catalan-Spanish bilinguals.
+From the `r n_sessions_total$n` testing sessions, `r n_sessions_lp$monolingual_eng$n` belonged to English monolinguals,  `r n_sessions_lp$monolingual$n` to Catalan or Spanish monolinguals, and  `r n_sessions_lp$bilingual$n` to Catalan-Spanish bilinguals.
 @tbl-participants shows a detailed description of the linguistic profile of our sample.

### 2023-10-31 manuscript/manuscript.qmd
Merge

--- 2023-10-31 manuscript/manuscript.qmd
@@
 		  legend.title = element_blank())
+
+ggsave(file.path("img", "vocabulary.jpeg"),
+	   dpi = 800, height = 8, height = 4)
 ```
@@
 	scale_x_continuous(breaks = seq(0, 20, 2),
-					   labels = \(x) format(x*100+300, big.mark = ",")) +
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
 	scale_y_continuous(labels = scales::percent,
@@
 		  legend.position = "none")
+
+ggsave(file.path("img", "recognition.jpeg"),
+	   height = 4, width = 11,
+	   dpi = 800)
 ```
@@
 		  								  linetype = "dotted"))
+
+ggsave(file.path("img", "recognition-age.jpeg"),
+	   height = 4, width = 11,
+	   dpi = 800)
 ```
@@
 		  								  linetype = "dotted"))
+
+ggsave(file.path("img", "recognition-condition.jpeg"),
+	   height = 4, width = 11,
+	   dpi = 800)
 ```
@@
 
+ggsave(file.path("img", "model-agg.jpeg"),
+	   height = 7.5, width = 10,
+	   dpi = 800)
 ```
@@
 		  								linetype = "dotted"))
+
+ggsave(file.path("img", "model-time.jpeg"),
+	   height = 4, width = 10,
+	   dpi = 800)
 ```
@@
 		  								linetype = "dotted"))
+
+ggsave(file.path("img", "model-time-voc-total.jpeg"),
+	   height = 5.5, width = 10,
+	   dpi = 800)
 ```

### 2023-11-01 docs/test.qmd
Target changes

@@
 ---
-title: "Test"
-format: html
 ---
@@
 ```{r setup}
-gaze_aoi_plot <- readr::read_csv("gaze_aoi_plot.csv") |> 
-	dplyr::filter(timestamp > 1) |> 
-	dplyr::rename(file = filename)
+#| label: setup
+#| echo: false
+#| message: false
+#| warning: false
+# load objects
+targets::tar_config_set(store = here::here("_targets"),
+						script = here::here("_targets.R"))
 
-ojs_define(mydata = gaze_aoi_plot)
+targets::tar_load_globals()
+
+targets::tar_load(
+	c(participants,
+	  stimuli,
+	  vocabulary,
+	  attrition_trials, 
+	  attrition_participants,
+	  bvq_data, 
+	  gaze_aoi, 
+	  data_time, 
+	  data_aggr,
+	))
+
+targets::tar_load(
+	c(model_fits_aggr,
+	  model_fits_time,
+	  model_loos_aggr,
+	  model_loos_time
+	))
+
+# prepare data
+attrition <- lst(participants,
+				 attrition_participants,
+				 attrition_trials) |> 
+	reduce(inner_join, by = join_by(session_id)) |> 
+	unnest_wider(matches("all"), names_sep = "_")
+
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(gt)
+library(patchwork)
+library(english)
+library(gtExtras)
+
+# set ggplot theme and colour palette
+
+my_theme <- theme_minimal() +
+	theme(panel.grid = element_blank(),
+		  axis.line = element_line(colour = "black"),
+		  text = element_text(size = 12, colour = "black"),
+		  axis.text = element_text(colour = "black"))
+
+theme_set(my_theme)
+
+clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
+
+options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
+		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
+		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
+		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
+		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
+		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
+
+set.seed(888)
+
 ```
 
-```{ojs}
-transposed = transpose(mydata)
+# Introduction
 
-trial_list = Array.from(Array(32).keys()).map(d => d + 1)
-id_list = Array.from(Array(185).keys()).map(d => d + 18)
-age_list = ["21 months", "25 months", "30 months"]
+## The early lexicon
 
-viewof input_id = Inputs.select(id_list, {label: "Participant", value: 18})
-viewof input_age = Inputs.select(age_list, {label: "Age", value: "21 months"})
-viewof input_trial = Inputs.select(trial_list, {label: "Trial", value: 1})
+Building a mental lexicon is a major achievement in the developmental journey of infants: by accumulating lexical representations of familiar words, infants are later able to recognise them in speech, and to extract meaning from the speech they are exposed to.
+Infants start forming their first lexical representations before their first year of life [@jusczyk1999; @halle1994; @vihman2004].
+When presented with pairs of pictures of familiar objects, 6-months-old infants already direct their gaze towards whichever is named [@bergelson20126; @bergelson2015early].
+This initial lexicon is hardly larger than around fifteen words [@REFERENCE], but it undergoes rapid growth [@REFERENCE] during their second year of life, at the end of which toddlers know an average of XXX words, and by 30 months of age, they know XXX words [@REFERENCE].
+This accelerated lexical developmental during the second year of life is also reflected in infants'  trajectories of word recognition: infants recognise familiar words faster and more efficiently [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
+Bilingual infants' trajectories of lexical acquisition [@hoff2012, @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes] and word recognition [@vihman2007onset; @vihman2013; @legacy2018vocabulary] are equivalent to their monolingual peers'.
+This is a remarkable deed: bilingual infants receive a relative impoverished linguistic input in each of their languages compared to monolinguals [@costa2014does].
+The mechanism that facilitate bilingual lexical development are still unclear.
 
-filtered = transposed.filter(d => d.trial==input_trial && 
-									d.age_group==input_age &&
-									d.input_id==input_id)
+## (Early) Word recognition is cascaded
 
-viewof data_table = Inputs.table(filtered)
-```
+Despite their different linguistic input, monolinguals and bilinguals share broadly common word recognition mechanisms.
+The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal.
+This results in the activation of lexical representations whose associated phonological forms matches the acoustic signal to some extent.
+The activated word-forms then compete for selection: the lexical system uses the auditory input, together with top-down context provided by grammatical, supra-segmental, and semantic constraints, to select the candidate lexical representation with the best match.
+There is evidence that spoken word recognition occurs in a *cascaded* fashion.
+The activation and selection of candidate lexical representations overlap in time, relying on partial information that accumulates as the speech signal unfolds [@marslen1987functional; @marslen1978processing; @grosjean1980spoken].
+This cascaded activation triggered by lexical access also results in the activation of the concepts associated to the accesses phonological forms.
+@allopenna1998tracking.
+
+This is also the case of the developing lexicon: like adults, infants activate non-selected lexical representations.
+This is relfected by the fact that from 21 months of age, infants' lexicon seems to be systematically organised accordi to the semantic and phnological properties of the lexical representations.
+
+SEMANTICS
+@arias2009lexical showed evidence of semantic priming in 21-month-old infants.
+In a word recognition task, infants' recognition of a spoken word (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
+Later studies provided electrophysiological evidence of such effect as early as 14 months of age [@friedrich2005lexical].
+
+PHONOLOGY
+Initial lexical representations are also phonologically well-specified [@swingley2000spoken; @swingley2002lexical].
+Overall these results suggest that early lexical representations are systematically organised in the lexicon according to their semantic and phonological properties.
+
+BOTH
+@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
+In each trial, the authors presented participants with four semantically and phonologically pictures.
+Four seconds after pictures onset, a word-form was auditorily presented.
+The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category.
+For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
+Then they would hear the carrier phrase "Look at the **bee**!".
+The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
+These results support a cascaded activation account of lexical access during the first stages of lexical development.
+@swingley1999continuous
+
+## Cascaded activation in bilingual parallel activation
+
+There is also evidence of cascaded activation in bilinguals.
+A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
+When listening to speech, bilinguals activate all lexical candidates from either language consistent with the speech signal.
+Even more surprising, when speaking, bilinguals activate all potential words consistent with the concepts they want to express.
+This effect has been systematically reported in adults [@marian1999activation; @costa2000cognate; @thierry2007brain; @dunabeitia2009masked].
+
+For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
+This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
+
+A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
+Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
+Cognates are form-similar translation equivalents.
+Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
+
+Also in toddlers [@von2012language; @von2014bilinguals] and school-aged children [@persici2019lexical; @bosma2020cognate].
+Some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
+Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
+Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that Spanish-Catalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
+
+Although recent work has provided strong evidence of parallel activation in early ages, how cognateness shapes that organisation of the early bilingual lexicon, and how this is reflected on the dynamics of lexical access during word comprehension and production is unclear.
+
+Using the experimental paradigm developed by [@arias2009lexical; @arias2013s; @singh2014one] compared within and across language
+priming effects in Chinese-English toddlers.
+@kuipers2015bilingualism compared ERP responses to picture-word pairs in English monolinguals and Welsh-English bilinguals where the words were either semantically related or unrelated to a pictured object.
+Although both studies tested 30-month-olds, the conclusions the authors reached do not fully agree.
+@singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
+
+## Cognate word recogntiion
+
+@floccia2020translation tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
+The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, French, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
+A prime word was embedded at the end of a carrier sentence that participants listened to.
+Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
+In Study 1, the target word was the translation equivalent of the prime word (*cheese*-*fromage* for an English-French bilingual).
+In other trials, prime and target words were unrelated (e.g., *sock*-*fromage*).
+There was no phonological overlap at onset between prime and target or distractor labels in either of the two conditions.
+Participants were presented with two blocks of related and unrelated trials.
+In one of the blocks, participants were presented with English prime words and Home Language target words (*sock*-*fromage*), and in the other block they were presented with Additional Language prime words and English target words (*fromage*-*sock*).
+The authors found a cross-linguistic priming effect, in which participants showed a stronger preference for the target picture in the post-naming phase in related trials, as compared to unrelated trials.
+This effect was found regardless of the language of the prime (English or Home Language), or the dominance of the language of the prime (i.e., whether the prime word belonged to the dominant language).
+Target preference exceeded chance level in both conditions.
+In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
+This time, prime and target words were not translation equivalents, but rather words whose referents shared semantic features.
+Results from Study  2 were parallel to those from Study 1.
+The authors found a strong semantic priming effect across languages, regardless of the language of the prime or the dominance of the language of the prime.
+Overall these results suggest that bilinguals recognised target words in both conditions, and benefited from a cross-linguistic facilitation effect from translation equivalents.
+The symmetry of such effect across both languages suggests that participants lexical access occurred in parallel for the two members of translation equivalents.
+As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
+The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
+However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generated by an interaction by the phonological and semantic overlap between cognate primes and targets.
+
+Another source of evidence supporting the language non-selective account of lexical access is provided by cross-languistic priming priuming thorught translation paradigms.
+In line with @floccia2020translation, @von2012language found that bilingual toddlers aged 21-to-43-months, and who were learning German and English, showed a stronger target preference in a German word recognition task after being primed with a phonologically related English word, which shared phonological onset with the prime word (e.g., *slide*-*Klide* [German for *dress*]), compared to when prime and target words were phonologically unrelated (e.g., *bottle*-*Ohr* [German for *ear*]).
+Interestingly, they also found evidence of such priming effect when participants were prime with an English word which was *not* phonologically related to the German target word, but rather its German translation was (e.g., *leg* [with German trasnlation *Bein*]-*Stein* [German for *stone*]).
+Altogether, these results indicate that bilingual toddlers activate translation equivalents in parallel during word recognition, and that the phonology of both labels may interact with lexical access in the recognition of subsequet words.
+Importantly, cross-linguitic priming through translation demonstrates that previous findings of a cognateness facilitation in word production and recognition do not result from the mere phonological overlap between auditorily presented and target labels, but also from the phonological overlap between the prime translation (not presented) and the target.
+
+Evidence from cognates.
+Marian and Spivey (1999)
+Costa et al. (2000)
+
+@dijkstra2019multilink
+
+The role of cognates in lexical processing.
+
+Another source of evidence are studies studies involving phonological priming of non-cognates through translation. [SEE REFERENCES FROM VON HOLZEN 2012]
+
+## The rpesent study
+
+The aforementioned studies use priming-though-translation paradigms.
+In these paradigms, cross-linguistic priming results from activation spreading from the lexical representation of the the (auditorily presented) prime word to the lexical representation of its translation through semantic associations (e.g., translation equivalence).
+When prime words are auditorily presented, the task design constraints the naming context to one of the languages.
+The consequence is a potential asymmtry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
+This might lead to a lower strength, and higher lacenty of the activation of the translation.
+
+In the present study, we use an adaptation of an implicit naming paradigm by @mani2010infant, in which participants are primed with a picture, instead of an auditorily presented label.
+@mani2010infant showed that 18 month-old monolinguals implicitly generate the labels of name-known pictures presented in silence.
+In each trial, infants were presented with prime pictures presented in silence, and then with a target and a distractor picture, both presented side-by-side.
+Finally, the target picture's label was presented auditorily.
+The authors manipulated the phonological overlap between the prime label and the target label, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
+Prime and target-distractor pairs were semantically unrelated.
+Interestingly, infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
+This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
+In particular, the authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
+
+@mani2011phonological used the same paradigm in 24-months-old monolinguals, and also found evidence of implicit naming, but in the opposite direction.
+After phonologically related primes, infants showed weaker target looking preference than after phonologically unrelated primes.
+These results interpreted these outcome as the result of the implicitly generated prime label interfering with the subsequent recognition of the (phonologically related) target word.
+The authors suggested that the shift from facilitation to interference from 18 to 24 months they found in both studies might be the result of a developmental shift in which 18-month-olds' lexicon is not yet organised based on phonological similarity, while 24-month-olds' is.
+This would lead to the former showing a pre-lexical facilitation effect in which such facilitation occurs via the activation of phonological segments, while the latter would show an interference effect due to lateral links between lexical representation having been established.
+Both studies by Mani and Plunkett provide evidence of implicit naming of name-known pictures by 18-month old toddlers and older, and that the resulting labels interact with the dynamics of recognition of subsequently presented word-forms.
+
+Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
+@duta2012erp presented name-known pictures in silence for one second.
+After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
+In some trials the auditory label corresponded to a canonical realisation of the word-form.
+In other trials, the word was mispronounced.
+Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
+A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
+This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
+
+When extended to the bilingual case, this implicit naming task may offer bilingual participants with an uncontrained naming context in whcih the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
+Using an adaptation of @mani2010infant's implicit naming paradigm, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
+The authors presented German-English bilinguals with 120 prime-target pairs.
+Primes were presented as familiar pictures in silence.
+After prime picture offset, target words were presented auditorily.
+Participants' N400 ERP components were recorded from target word onset.
+The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
+When prime and target were phonologically identical (*Affe*-*Affe*, German for *monkey*), or similar (*Fahne*-*Sahne*, German for *flag* and *ice-cream*, respectively) within L1, participants' showed a reduced N400 amplitude, compared to when prime and target were phonologically unrelated (*Messer*-*Seil*, German for *knife* and *rope*).
+Critically, a similar effect was found when prime and target were phonologically related through translation (*Rustsche*-*Kleid*, German for *slide* and *dress*).
+This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
+
+Evidence from cognates.
+
+The role of cognates in lexical processing.
+
+This study also provides a more suitable design for drawing conslusions about developmental change in word recognition trajectories frot wo reasons.
+First, it extends the age range of participants, compared to previous studies.
+Second, participants were tested at three selected age points to ensure a more balanced sample size across ages.
+Third, the partially longitudinal design allows modelling the performance of participants across testing sessions altogether.
+
+. In order to circumvent the problem of limited vocabulary knowledge
+in the non-dominant language, we propose to test participants only in their dominant language, therefore
+directing our research to the question of how possessing a second language affects processing of the
+dominant one in bilingual toddlers [@costa2014does provide a fuller description of the
+advantages of such approach].
+
+## The present study
+
+The present study is aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
+Using an adaptation of [@mani2010infants], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
+We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
+If so, phonological priming effect should be larger when the prime label in  both languages shares phonological overlap with the target words (cognate condition), compared to when only the label of the prime in one language overlaps phonologically with the target (non-cognate condition).
+We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
+
+We compared the explanatory power of three measures of vocabulary size on participants' trajectories of word recognition: L1 vocabulary and total vocabulary.Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary]

### 2023-11-01 manuscript/manuscript.qmd
Merge

@@
 set.seed(888)
-
 ```
@@
 #| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+#| fig-width: 11
+#| fig-height: 4
 data_time |> 
@@
 				 geom = "errorbar",
-				 width = 0.35,
-				 linewidth = 2/4) +
+				 width = 0.4,
+				 linewidth = 3/4) +
 	stat_summary(fun = "mean",
@@
 				 geom = "line",
-				 linewidth = 2/4) +
+				 linewidth = 3/4) +
 	labs(x = "Time (ms)",
@@
 	scale_y_continuous(labels = scales::percent,
-					   breaks = seq(0, 1, 0.05)) +
+					   limits = c(0.40, 0.75),
+					   breaks = seq(0, 1, 0.1)) +
 	theme(legend.position = "top",
@@
 Lines and error bands indicate the mean and standard error of the mean."
+#| fig-width: 10
+#| fig-height: 7.5
 plot_agg_epreds <- function(newdata, object) {

### 2023-11-01 manuscript/manuscript.qmd
Add results structure

--- 2023-10-31 manuscript/manuscript.qmd
@@
 	reduce(inner_join, by = join_by(session_id)) |>
-	unnest_wider(matches("all"), names_sep = "_")
+	unnest_wider(matches("all"), names_sep = "_") |> 
+	rename_with(\(x) gsub("is_valid_gaze_all_|is_valid_vocab_all", "", x))
 
@@
 # set ggplot theme and colour palette
-
 my_theme <- theme_minimal() +
@@
 We compared the explanatory power of three measures of vocabulary size on participants' trajectories of word recognition: L1 vocabulary and total vocabulary.Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary]
+
+Hypothesis 1: if lexical representations linked through inhibitory links (compete for selection), like in the adult lexicon, target looking should increase faster in *Unrelated* trials compared to *Related* trials.
+If lexical representations are linked through excitatory links, target preference should increase faster in *Related* trials, compared to *Unrelated* trials.
+If lexical representations are sparsely connected, participants should show equivalent patterns of target looking in *Related* and *Unrelated* trials.
+
+Hypothesis 2: if bilinguals' lexical representations linked across languages through inhibitory links (compete for selection), target looking should increase faster in this group in *Related/Non-cognate* trials compared to *Related/Cognate* trials.
+If lexical representations are linked across languages through excitatory links, target preference should increase faster in *Related/Cognate* trials, compared to *Unrelated/Cognate* trials.
+If lexical representations are sparsely connected across languages, bilinguals' patterns of target looking should be equivalent for *Related/Cognate* and *Related/Non-cognate* trials.
+This pattern is also expected for monolingual infants.
+
+Hypothesis 3: if the emergence of within-language or cross-language phonological links is explained (if at all) by the growth of within-language vocabulary size, the difference in target looking between *Related* and *Unrelated*, or between *Related/Cognate* and *Related/Non-cognate* trials should be larger in participants with larger vocabulary sizes in their dominant language, in which they were tested.
+This should be reflected by a $\text{Condition} \times \text{L1 vocabulary}$ two -way interaction, or a $\text{Condition} \times \text{Group} \times \text{Dominant vocabulary}$ three-way interaction.
+
+Hypothesis 4: if the emergence of within-language or cross-language phonological links is explained better by the growth of cross-language vocabulary size, compared to within-language vocabulary size, a model that incorporates total vocabulary size as a predictor instead of dominant vocabulary size should show better predictive performance.
+If the emergence of such links is explained at all by the growth of vocabulary size, both models incorporating voacbulary size as a predictor should show better predictive performance than a model incorporating participants' age.
 
@@
 
-n_exc_prime <- sum(!attrition$is_valid_gaze_all_prime)
-n_exc_test <- sum(!attrition$is_valid_gaze_all_test)
-n_exc_test_each <- sum(!attrition$is_valid_gaze_all_test_each)
-n_exc_vocab <- sum(!attrition$is_valid_vocab)
+n_exc_prime <- sum(!attrition$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition$is_valid_gaze_test)
+n_exc_test_any <- sum(!attrition$is_valid_gaze_test_any)
 n_exc_participants <- sum(!attrition_participants$is_valid_participant)
@@
 We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target-looking *and* distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
-Finally, we excluded trials in which participants did not understand the prime *or* the target word, according to a supplementary vocabulary checklist filled by their caregivers upon experiment completion (*n* = `r format(n_exc_vocab, big.mark = ",")`).
+We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_any, big.mark = ",")`) [see @floccia2020translation for a similar approach].
+
 After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`).
@@
 
-We conducted two main analyses.
-In the first analysis, we estimated the effect of phonological priming on participants' target looking comparing *related* trials---in which prime and target share phonological onset, and the prime was not a cognate word---with *unrelated* trials---in which prime and target did not share phonological onset, and neither was the prime a cognate word, leaving out *cognate* trials.
-This analysis included all trials on the data set.
-Second, we estimated the effect of cognateness on phonological priming, comparing *cognate* trials---in which prime and target shared phonological onset, and the prime was a cognate word that also shared phonological onset with the target, with *non-cognate* trials---in which prime a target shared phonological onset, and the prime was not a cognate---, leaving out *unrelated* trials.
-
-In both analyses, we modelled the probability of target looking across the time course of the trial.
-For each trial, we chunked the time domain of the target-distractor phase into 20 time bins of 100 ms of duration.
-We then calculated, for each experimental session, time bin, and condition, the number of eye-tracker samples in which the participant was looking to the target and the distractor pictures.
-Finally, we computed the empirical logit of target fixations using @eq-elogit [@barr2008analyzing; @agresti2012categorical], which modelled in our analyses using a Gaussian distribution.
+We used multilevel General Additive Models (GAMs) to model our data and test our hypotheses [@pedersen2019hierarchical].
+First, we defined our response variable as the empirical logit of target looking using @eq-elogit across all eye-tracking samples for each each participant in each condition [@barr2008analyzing; @agresti2012categorical].
+We used a Gaussian distribution to model our response variable.
+To test our hypotheses, we then included *Condition*, *Group*, and either *Age* ($\mathcal{M}_0$), *L1 vocabulary* ($\mathcal{M}_1$), or *Total vocabulary* ($\mathcal{M}_2$) as fixed effects in the model.
+We also added all two-way and three-way interactions between the predictors.
+We set two *a priori* contrasts for the *Condition* predictor: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
+We also set two *a priori* contrasts for the *Group* predictor: one comparing *Monolingual (ENG)* with *Monolingual (CAT/SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Bilingual (CAT-SPA)* participants coded as `0`), and another comparing *Monolingual (ENG)* with *Bilingual (CAT-SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Monolingual (CAT/SPA)* participants coded as `0`).
+Before entering the model, the numeric predictors *Age*, *L1 vocabulary*, and *Total vocabulary* were standardised by subtracting from each observation the mean of the predictor, and dividing the result from the standard deviation of the predictor.
 
@@
 
-In the first analysis, we included *Relatedness* (`Related` vs.
-`Unrelated`, sum-coded as `-0.5` and `+0.5`), *Group* (`Monolingual` vs.
-`Bilingual`, sum-coded as `-0.5` and `+0.5`), and *Age* (participants' standardised age in months) as fixed, main effects, together with their two- and three-way interactions.
-We used multilevel General Additive Mixed Models (GAMMs) to model the time course of target looking, including cubic regression splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
-For both splines, we specified $k = 10$ basis functions or *knots*--half the number of time bins---for computational convenience.
-Finally, we added by-participant random intercepts, and random slopes for the main effect of *Relatedness* and the main effect of *Age*, both including repeated measures per participant [@pedersen2019hierarchical].
-In the second analysis, we included *Cognateness* (`Cognate` vs.
-`Non-cognate`, sum-coded as `-0.5` and `+0.5`) replacing *Relatedness*.
-@eq-model shows the formal implementation of the model.
-
-To test the contribution of each of the predictors of interest--*Relatedness*/*Cognateness*, and *Group*--, we compared each model ($\mathcal{M_0}$) against a simplified model dropping each of the main effects, *Relatedness*/*Cognateness* ($\mathcal{M}_1$) or *Group* ($\mathcal{M_2}$).
-In both simplified models, the interaction term was dropped.
-We used leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it.
-We then examined the posterior predictions of the best-performing model for interpretation.
+We added *Session* as grouping variable, by by-session intercept and *Condition* slopes.
+Each level in the *Session* variable uniquely indexes all observations generated by a participant in a single testing session.
+Testing sessions from the same participant are identified by different indexes.
+For computational limitations, adding both participants and testing sessions as grouping variable in the random effects structure of the model was not possible.
+We instead included testing sessions alone, as observations from the same testing session are more likely to be highly correlated than those from the same participant in different testing sessions (which were recorded at least four months apart).
+To model the time course of target looking across time bins, we included cubic regression splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
+For both splines, we specified $k = 9$ basis functions or *knots*--half the number of time bins---for computational convenience.
+@eq-model shows a formal implementation of the model.
 
@@
 \textbf{Linear model:} \\
-\eta'(\mu_i) &= (\beta_0 + u _{0_{i}}) + (\beta_1 + u _{1_{i}}) \cdot \text{[Condition]} +\\
-&\beta_{2} \cdot \text{Group} + \beta_{3} \cdot (\text{[Condition]} \times \text{Group}) +\\
-& (\beta_4 + u_{2_{i}}) \cdot \text{Age} + \sum_{j = 1}^k b_{j_{1}} \cdot \beta_{5_{k}} \cdot \text{Time} + \sum_{j = 1}^k b_{j_{1}} \cdot\beta_{6_{k}} \cdot (\text{Time} \times \text{Group}) \\
+\eta'(\mu_i) &= (\beta_0 + u _{0_{i}}) +
+(\beta_1 + u _{1_{i}}) \cdot \text{Condition} +\\
+&\beta_{2} \cdot \text{Group} +
+\beta_{3} \cdot X + \beta_{4} \cdot (\text{Condition} \times \text{Group}) +\\
+&\beta_{5} \cdot (\text{Condition} \times X) + \beta_{6} \cdot (\text{Group} \times X) +\\
+&\beta_{7} \cdot (\text{Condition} \times \text{Group} \times X) +\\
+& \sum_{j = 1}^k b_{j_{0}} \cdot \beta_{8_{k}} \cdot \text{Time} +
+\sum_{j = 1}^k b_{j_{1}} \cdot\beta_{9_{k}} \cdot (\text{Time} \times \text{Group}) \\
 \text{where:} \\
 &\eta'\text{ is the empirical logit of target fixations} \\
-& \text{[Condition] should be replaced with } Relatedness \text{ or } Cognateness \\
+&X \in \{\text{Age}, \text{L1 vocabulary}, \text{Total vocabulary}\} \\
 &k \text{ is the number of knots in the spline (10)} \\
 \textbf{Prior:} \\
-\beta_{0-6} &\sim \mathcal{N}(0, 0.5) \\
+\beta_{0-9} &\sim \mathcal{N}(0, 0.5) \\
 u_{0-2} &\sim \mathcal{N}(0, \sigma_{0-2})\\
@@
 
+The comparison between the three models including *Age*, *L1 vocabulary*, *Total vocabulary* as predictors was performed using leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it [@vehtari2017practical].
+We implemented the model using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
+We ran `r english::words(dim(model_fit$fit_0)[2])` iteration chains using the by-default No U-Turn Sampler algorithm with `r format(niterations(model_fit$fit_0), big.mark = ",")` iterations each and an additional `r format(niterations(model_fits$fit_0), big.mark = ",")` warm-up iterations per chain.
+
 # Results
-
-## Preliminary analyses
 
@@
 		  legend.position = "none")
-
-ggsave(file.path("img", "recognition.jpeg"),
-	   height = 4, width = 11,
-	   dpi = 800)
-```
-
-```{r fig-ptlt-recognition-age}
-#| label: fig-ptlt-recognition-age
-#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-data_time |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(lp, timebin, age_group, session_id)) |> 
-	ggplot(aes(timebin, .prop, colour = age_group)) +
-	facet_wrap(~lp, nrow = 1, scales = "free_x") +
-	# geom_rug(aes(x = timebin[is.na(.prop)])) +
-	# geom_line(aes(group = session_id),
-	# 		  alpha = 1/8) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = "mean_se",
-				 geom = "errorbar",
-				 width = 0.35,
-				 linewidth = 2/4) +
-	stat_summary(fun = "mean",
-				 geom = "point",
-				 size = 1.2) +
-	stat_summary(fun = "mean",
-				 geom = "line",
-				 linewidth = 2/4) +
-	labs(x = "Time (ms)",
-		 y = "PTLT",
-		 colour = "Age") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	scale_y_continuous(labels = scales::percent,
-					   breaks = seq(0, 1, 0.05)) +
-	theme(legend.position = "top",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-
-ggsave(file.path("img", "recognition-age.jpeg"),
-	   height = 4, width = 11,
-	   dpi = 800)
-```
-
-```{r fig-ptlt-recognition-condition}
-#| label: fig-ptlt-recognition-condition
-#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-data_time |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(lp, timebin, condition, session_id)) |> 
-	ggplot(aes(timebin, .prop, colour = condition)) +
-	facet_grid(~lp) +
-	# geom_rug(aes(x = timebin[is.na(.prop)])) +
-	# geom_line(aes(group = interaction(condition, session_id)),
-	# 		  alpha = 1/8) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = "mean_se",
-				 geom = "errorbar",
-				 width = 0.35,
-				 linewidth = 2/4) +
-	stat_summary(fun = "mean",
-				 geom = "point",
-				 size = 1.2) +
-	stat_summary(fun = "mean",
-				 geom = "line",
-				 linewidth = 2/4) +
-	labs(x = "Time (ms)",
-		 y = "PTLT",
-		 colour = "Condition") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	scale_y_continuous(labels = scales::percent,
-					   breaks = seq(0, 1, 0.05)) +
-	theme(legend.position = "top",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-
-ggsave(file.path("img", "recognition-condition.jpeg"),
-	   height = 4, width = 11,
-	   dpi = 800)
-```
-
-## Aggregated analysis
-
-In a first analysis, we examined the effect of phonological priming.
-We compared participants' looking preference for the target in related and unrelated trials.
-We first compared the aggregated probability of target looking across time bins in both conditions for each language group.
-
-```{r fig-related-aggregated}
-#| label: fig-related-aggregated
-#| fig-cap: "A) Aggregated probability of target looking for related and unrelated trials.
-Each point represents the mean probability of target looking for one participant in one testing session.
-Lines link observations from the same testing session across conditions.
-Black dots and errorbars indicate the mean and 95% CrI.
-B) Aggregated probability of target looking across ages for related and unrelated trials.
-Lines and error bands indicate the mean and standard error of the mean."
-plot_agg_epreds <- function(newdata, object) {
-
-	epreds <- add_epred_draws(newdata = newdata,
-							  object = object,
-							  re_formula = NA)
-	return(mean_qi(epreds))
-}
-
-voc_values <- c(0.25, 0.5, 0.75, 1.00)
-age_values <- c(21, 25, 30)
-
-nd_0 <- expand(data_aggr, lp, condition, age = age_values)
-nd_1 <- expand(data_aggr, lp, condition, voc_l1 = voc_values)
-nd_2 <- expand(data_aggr, lp, condition, voc_total = voc_values)
-
-epreds <- map2(.x = list(nd_0, nd_1, nd_2),
-			   .y = model_fits_aggr,
-			   .f = plot_agg_epreds) |> 
-	map(\(x) {
-		mutate(x, 
-			   across(matches("voc"),
-			   	   \(x) factor(x = x, 
-			   	   			levels = voc_values,
-			   	   			labels = scales::percent(voc_values))),
-			   across(matches("age"),
-			   	   \(x) factor(x = x,
-			   	   			levels = age_values,
-			   	   			labels = age_values)))
-	}) |> 
-	map(\(x) rename_with(x, \(x) gsub("age|voc_total|voc_l1", "var", x))) |> 
-	set_names(names(model_fits_aggr))
-
-plot_epreds <- function(data, x) {
-	data |> 
-		ggplot(aes(var, .epred, 
-				   colour = condition,
-				   fill = condition)) +
-		facet_wrap(~lp, scales = "free_x") +
-		geom_hline(yintercept = 0,
-				   linetype = "dashed") +
-		geom_errorbar(aes(ymin = .lower,
-						  ymax = .upper),
-					  width = 0.5,
-					  linewidth = 3/4,
-					  position = position_dodge(width = 0.5)) +
-		geom_point(position = position_dodge(width = 0.5),
-				   size = 2)
-}
-
-plot_epreds(epreds$fit_aggr_0) +
-	labs(x = "Age (months)") +
-	plot_epreds(epreds$fit_aggr_1) +
-	labs(x = "L1 vocabulary size") +
-	theme(strip.text = element_blank()) +
-	plot_epreds(epreds$fit_aggr_2) +
-	theme(strip.text = element_blank()) +
-	labs(x = "Total vocabulary size") +
-	plot_layout(ncol = 1, guides = "collect") &
-	labs(y = "Logit (Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") &
-	theme(legend.position = "top",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-
-ggsave(file.path("img", "model-agg.jpeg"),
-	   height = 7.5, width = 10,
-	   dpi = 800)
-```
-
-## Time course analysis
+```
+
+```{r tbl-coefs}
+post <- gather_draws(fit_0, `b_.*`, regex = TRUE)
+
+ggplot(post, aes(.value)) +
+	facet_wrap(~.variable, scales = "free") +
+	geom_histogram(bins = 15, colour = "white") +
+	geom_errorbar(data = mean_qi(post),
+				  aes(xmin = .lower, xmax = .upper, y = 400),
+				  width = 1,
+				  linewidth = 3/4) +
+	geom_point(data = mean_qi(post),
+			   aes(x = .value, y = 400),
+			   size = 2) +
+	scale_y_continuous(limits = c(0, 500))
+```
+
+## Hypothesis 1: within-language phonological priming
+
+## Hypothesis 2: cross-language phonological priming
+
+## Hypothesis 3: emergence of phonological association
+
+## Hypothesis 4: the compating role of age and vocabulary
 
@@
 The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-nd <- expand_grid(condition = levels(model_fits_time$fit_time_2$data$condition),
-				  timebin = seq(0, 17, length.out = 100),
-				  voc_total = mean(model_fits_time$fit_time_2$data$voc_total),
+make_std <- function(x, mean, sd) (x - mean) / sd
+
+timebin_values <- make_std(seq(0, 17, length.out = 100),
+						   mean(data_time$timebin),
+						   sd(data_time$timebin))
+
+age_values <- make_std(c(21, 25, 30),
+					   mean(data_time$age),
+					   sd(data_time$age))
+
+nd <- expand_grid(condition = levels(fit_0$data$condition),
+				  timebin_std = timebin_values,
+				  age_std = age_values,
 				  # sesion_id = first(data$session_id),
 				  # age = c(21, 25, 30),
-				  lp = levels(model_fits_time$fit_time_2$data$lp))
+				  lp = levels(fit_0$data$lp))
 
 epreds <- add_epred_draws(newdata = nd,
-						  object = model_fits_time$fit_time_2,
-						  ndraws = 20,
+						  object = fit_0,
+						  ndraws = NULL,
 						  re_formula = NA,
@@
 					   		   "Monolingual",
-					   		   "Bilingual")))
+					   		   "Bilingual")),
+		   age_std = factor(age_std, 
+		   				 levels = age_values,
+		   				 labels = paste0(c(21, 25, 30), " months")))
 
 epreds |> 
-	ggplot(aes(timebin, .value,
+	ggplot(aes(timebin_std, .value,
 			   colour = condition,
 			   fill = condition)) +
-	facet_wrap(~lp) +
+	facet_wrap(lp ~ age_std) +
 	geom_hline(yintercept = 0,
@@
 ```{r fig-validity-target}
-get_data(gaze = gaze,
+gaze_tmp <- gaze |> 
+	filter(phase=="Target-Distractor",
+		   between(timestamp, time_subset[1], time_subset[2])) |> 
+	select(session_id, trial, phase, timestamp,
+		   is_gaze_target, is_gaze_distractor, trial_type) |> 
+	mutate(condition = recode_condition(trial_type))
+
+vocabulary_tmp <- rename_with(vocabulary,  
+							  \(x) gsub("_prop", "", paste0("voc_", x)), 
+							  matches("_prop"))
+
+participants_tmp <- participants |> 
+	select(child_id, session_id, age_group, age, lp)
+
+attrition_trials_tmp <- get_attrition_trials(
 	participants = participants,
-		 stimuli = stimuli,
 	vocabulary = vocabulary,
-		 attrition_trials = attrition_trials,
-		 attrition_participants = attrition_participants,
-		 time_subset = c(0, 2),
-		 contrast = "related",
-		 is_valid_vocab_all,
-		 clean = FALSE) |> 
+	vocabulary_by = c("target"),
+	aoi_coords = aoi_coords,
+	gaze = gaze,
+	min_looking = c(prime = 0.75,
+					test = 1.00,
+					test_each = 0.00,
+					test_any = 0.1)) |> 
+	select(session_id, trial, samples, is_valid_vocab_all) |> 
 	unnest_wider(is_valid_vocab_all) |> 
+	rename_with(\(x) gsub("is_valid_vocab_", "", x))
+
+attrition_participants_tmp <- attrition_participants |> 
+	filter(is_valid_participant) |> 
+	select(session_id)
+
+data <- gaze_tmp |>
+	inner_join(attrition_trials_tmp, by = join_by(session_id, trial)) |> 
+	inner_join(attrition_participants_tmp, by = join_by(session_id)) |> 
+	mutate(condition = recode_condition(trial_type)) |> 
+	select(session_id, trial, condition, is_gaze_target, is_gaze_distractor,
+		   is_valid_vocab_all) |> 
+	# aggregated across trials by participant, time bin and condition
+	# see Chow et al. (2018)
+	summarise(sum_target = sum(is_gaze_target, na.rm = TRUE),
+			  sum_distractor = sum(is_gaze_distractor, na.rm = TRUE),
+			  .nsamples = sum(is_gaze_target | is_gaze_distractor, na.rm = TRUE),
+			  .ntrials = length(unique(trial)),
+			  .by = c(session_id, condition, is_valid_vocab_all)) |> 
+	# empirical logit with adjustment
+	# see Barr et al. (2008)
+	mutate(.nsamples = sum_target + sum_distractor,
+		   .prop = ifelse(.nsamples==0, 0, sum_target / .nsamples),
+		   .elog = log((sum_target + .5)/(sum_distractor + .5))) |> 
+	rename(.sum = sum_target) |> 
+	arrange(desc(session_id), condition) |> 
+	inner_join(participants_tmp, by = join_by(session_id)) |> 
+	inner_join(vocabulary_tmp, by = join_by(child_id, session_id)) |> 
+	mutate(across(c(.nsamples), as.integer),
+		   across(c(child_id, session_id, lp, condition, age_group), as.factor),
+		   across(c(age, voc_l1),
+		   	   \(x) scale(x, scale = TRUE)[, 1],
+		   	   .names = "{.col}_std")) |> 
+	select(child_id, session_id, age_group, age, voc_l1, voc_total, lp,
+		   condition,  .sum, .prop, .elog, .nsamples,
+		   matches("std"), is_valid_vocab_all)
+
+# set a priori contrasts
+contrasts(data$condition) <- cbind(c(-0.5, 0.5, 0),
+								   c(0, -0.5, 0.5))
+contrasts(data$lp) <- cbind(c(-0.5, 0.25, 0.25),
+							c(0, -0.5, 0.5))
+contrasts(data$age_group) <- cbind(c(-0.5, 0.5, 0),
+								   c(0, -0.5, 0.5))
+
+data |> 
+	unnest_wider(is_valid_vocab_all) |>
+	rename_with(\(x) gsub("is_valid_vocab_", "", x)) |> 
 	select(session_id, lp, .elog, target) |> 
@@
 		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted")) +
+		  								  linetype = "dotted"))
 

### 2023-11-01 manuscript/manuscript.qmd
Simplify gaze functions and clean repository

@@
 #| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+#| fig-width: 11
+#| fig-height: 4
 data_time |> 
+	drop_na(.prop) |> 
 	summarise(.prop = mean(.prop),
@@
 	scale_x_continuous(breaks = seq(0, 20, 2),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
+					   labels = \(x) format(x*100+300, big.mark = ",")) +
 	scale_y_continuous(labels = scales::percent,
@@
 		  legend.position = "none")
+```
+
+```{r fig-ptlt-recognition-age}
+#| label: fig-ptlt-recognition-age
+#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+#| fig-width: 11
+#| fig-height: 4
+data_time |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(lp, timebin, age_group, session_id)) |> 
+	ggplot(aes(timebin, .prop, colour = age_group)) +
+	facet_wrap(~lp, nrow = 1, scales = "free_x") +
+	# geom_rug(aes(x = timebin[is.na(.prop)])) +
+	# geom_line(aes(group = session_id),
+	# 		  alpha = 1/8) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	stat_summary(fun.data = "mean_se",
+				 geom = "errorbar",
+				 width = 0.4,
+				 linewidth = 3/4) +
+	stat_summary(fun = "mean",
+				 geom = "point",
+				 size = 1.2) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 linewidth = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "PTLT",
+		 colour = "Age") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	scale_y_continuous(labels = scales::percent,
+					   limits = c(0.40, 0.75),
+					   breaks = seq(0, 1, 0.1)) +
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
 ```
@@
 
+```{r fig-ptlt-recognition-condition}
+#| label: fig-ptlt-recognition-condition
+#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+#| fig-width: 11
+#| fig-height: 4
+data_time |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(lp, timebin, condition, session_id)) |> 
+	ggplot(aes(timebin, .prop, colour = condition)) +
+	facet_grid(~lp) +
+	# geom_rug(aes(x = timebin[is.na(.prop)])) +
+	# geom_line(aes(group = interaction(condition, session_id)),
+	# 		  alpha = 1/8) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	stat_summary(fun.data = "mean_se",
+				 geom = "errorbar",
+				 width = 0.35,
+				 linewidth = 2/4) +
+	stat_summary(fun = "mean",
+				 geom = "point",
+				 size = 1.2) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 linewidth = 2/4) +
+	labs(x = "Time (ms)",
+		 y = "PTLT",
+		 colour = "Condition") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	scale_y_continuous(labels = scales::percent,
+					   breaks = seq(0, 1, 0.05)) +
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+```
+
 ## Hypothesis 2: cross-language phonological priming
@@
 ## Hypothesis 4: the compating role of age and vocabulary
+
+In a first analysis, we examined the effect of phonological priming.
+We compared participants' looking preference for the target in related and unrelated trials.
+We first compared the aggregated probability of target looking across time bins in both conditions for each language group.
+
+```{r fig-related-aggregated}
+#| label: fig-related-aggregated
+#| fig-cap: "A) Aggregated probability of target looking for related and unrelated trials.
+Each point represents the mean probability of target looking for one participant in one testing session.
+Lines link observations from the same testing session across conditions.
+Black dots and errorbars indicate the mean and 95% CrI.
+B) Aggregated probability of target looking across ages for related and unrelated trials.
+Lines and error bands indicate the mean and standard error of the mean."
+#| fig-width: 10
+#| fig-height: 7.5
+plot_agg_epreds <- function(newdata, object) {
+
+	epreds <- add_epred_draws(newdata = newdata,
+							  object = object,
+							  re_formula = NA)
+	return(mean_qi(epreds))
+}
+
+voc_values <- c(0.25, 0.5, 0.75, 1.00)
+age_values <- c(21, 25, 30)
+
+nd_0 <- expand(data_aggr, lp, condition, age = age_values)
+nd_1 <- expand(data_aggr, lp, condition, voc_l1 = voc_values)
+nd_2 <- expand(data_aggr, lp, condition, voc_total = voc_values)
+
+epreds <- map2(.x = list(nd_0, nd_1, nd_2),
+			   .y = model_fits_aggr,
+			   .f = plot_agg_epreds) |> 
+	map(\(x) {
+		mutate(x, 
+			   across(matches("voc"),
+			   	   \(x) factor(x = x, 
+			   	   			levels = voc_values,
+			   	   			labels = scales::percent(voc_values))),
+			   across(matches("age"),
+			   	   \(x) factor(x = x,
+			   	   			levels = age_values,
+			   	   			labels = age_values)))
+	}) |> 
+	map(\(x) rename_with(x, \(x) gsub("age|voc_total|voc_l1", "var", x))) |> 
+	set_names(names(model_fits_aggr))
+
+plot_epreds <- function(data, x) {
+	data |> 
+		ggplot(aes(var, .epred, 
+				   colour = condition,
+				   fill = condition)) +
+		facet_wrap(~lp, scales = "free_x") +
+		geom_hline(yintercept = 0,
+				   linetype = "dashed") +
+		geom_errorbar(aes(ymin = .lower,
+						  ymax = .upper),
+					  width = 0.5,
+					  linewidth = 3/4,
+					  position = position_dodge(width = 0.5)) +
+		geom_point(position = position_dodge(width = 0.5),
+				   size = 2)
+}
+
+plot_epreds(epreds$fit_aggr_0) +
+	labs(x = "Age (months)") +
+	plot_epreds(epreds$fit_aggr_1) +
+	labs(x = "L1 vocabulary size") +
+	theme(strip.text = element_blank()) +
+	plot_epreds(epreds$fit_aggr_2) +
+	theme(strip.text = element_blank()) +
+	labs(x = "Total vocabulary size") +
+	plot_layout(ncol = 1, guides = "collect") &
+	labs(y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition") &
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+
+ggsave(file.path("img", "model-agg.jpeg"),
+	   height = 7.5, width = 10,
+	   dpi = 800)
+```
+
+## Time course analysis
 

### 2023-11-02 manuscript/manuscript.qmd

--- 2023-11-01 manuscript/manuscript.qmd
@@
 	  gaze,
-	  data_time,
-	  data_aggr
+	  data_time_bcn
 	))
@@
 targets::tar_load(
-	c(model_fits_aggr,
-	  model_fits_time,
-	  model_loos_aggr,
-	  model_loos_time
+	c(model_fits_bcn,
+	  model_loos_bcn
 	))
@@
 library(gt)
+library(gtExtras)
 library(patchwork)
@@
 
-## The early lexicon
-
-Building a mental lexicon is a major achievement in the developmental journey of infants: by accumulating lexical representations of familiar words, infants are later able to recognise them in speech, and to extract meaning from the speech they are exposed to.
-Infants start forming their first lexical representations before their first year of life [@jusczyk1999; @halle1994; @vihman2004].
-When presented with pairs of pictures of familiar objects, 6-months-old infants already direct their gaze towards whichever is named [@bergelson20126; @bergelson2015early].
-This initial lexicon is hardly larger than around fifteen words [@REFERENCE], but it undergoes rapid growth [@REFERENCE] during their second year of life, at the end of which toddlers know an average of XXX words, and by 30 months of age, they know XXX words [@REFERENCE].
-This accelerated lexical developmental during the second year of life is also reflected in infants'  trajectories of word recognition: infants recognise familiar words faster and more efficiently [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
-Bilingual infants' trajectories of lexical acquisition [@hoff2012, @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes] and word recognition [@vihman2007onset; @vihman2013; @legacy2018vocabulary] are equivalent to their monolingual peers'.
-This is a remarkable deed: bilingual infants receive a relative impoverished linguistic input in each of their languages compared to monolinguals [@costa2014does].
-The mechanism that facilitate bilingual lexical development are still unclear.
-
-## (Early) Word recognition is cascaded
-
-Despite their different linguistic input, monolinguals and bilinguals share broadly common word recognition mechanisms.
-The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal.
-This results in the activation of lexical representations whose associated phonological forms matches the acoustic signal to some extent.
-The activated word-forms then compete for selection: the lexical system uses the auditory input, together with top-down context provided by grammatical, supra-segmental, and semantic constraints, to select the candidate lexical representation with the best match.
-There is evidence that spoken word recognition occurs in a *cascaded* fashion.
-The activation and selection of candidate lexical representations overlap in time, relying on partial information that accumulates as the speech signal unfolds [@marslen1987functional; @marslen1978processing; @grosjean1980spoken].
-This cascaded activation triggered by lexical access also results in the activation of the concepts associated to the accesses phonological forms.
-@allopenna1998tracking.
-
-This is also the case of the developing lexicon: like adults, infants activate non-selected lexical representations.
-This is relfected by the fact that from 21 months of age, infants' lexicon seems to be systematically organised accordi to the semantic and phnological properties of the lexical representations.
-
-SEMANTICS
-@arias2009lexical showed evidence of semantic priming in 21-month-old infants.
-In a word recognition task, infants' recognition of a spoken word (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
-Later studies provided electrophysiological evidence of such effect as early as 14 months of age [@friedrich2005lexical].
-
-PHONOLOGY
-Initial lexical representations are also phonologically well-specified [@swingley2000spoken; @swingley2002lexical].
-Overall these results suggest that early lexical representations are systematically organised in the lexicon according to their semantic and phonological properties.
-
-BOTH
-@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
+Building a mental lexicon is a major achievement in the development of an infant.
+By storing representations of how familiar words sound and what they mean, an infant is able to make sense of their linguistic input.
+Infants start forming their first lexical representations before their first year of life [@jusczyk1999; @halle1994; @vihman2004; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
+This initial lexicon consists of only a few items; mainly words for people, interjections, body parts, and food [@tincoff2012six; @tardif2008baby], but it undergoes rapid growth during their second year of life [@ganger2004reexamining; @goldfield1990early; @bloom2002children; @mcmurray2007defusing].
+According to parental reports the average 15-month-old infant already understands more than 100 words, and by two years, they understand more than 400 words [@frank2021variability].
+This accelerated lexical developmental is reflected in infants' trajectories of word recognition: infants recognise familiar words faster and more efficiently as they approach their second birthday [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
+
+Despite being exposed to a more complex linguistic input, bilinguals show equivalent trajectories of word acquisition and word recognition to their monolingual peers' [@vihman2007onset; @vihman2013; @legacy2018vocabulary; @hoff2012; @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes].
+This is a remarkable deed for two reasons.
+First, bilingual infants receive a relative impoverished linguistic input in each of their languages compared to monolinguals [@costa2014does].
+Second, they face a more complex referential context, since they often learn two labels for each referent, one in each language.
+The mechanisms that allow bilingual infants to keep up with monolinguals in their lexical development trajectories are still unclear.
+
+Monolinguals and bilinguals share broadly common word-recognition mechanisms.
+The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal, which results in the activation of lexical representations whose associated phonological forms match the acoustic signal.
+The activated word-forms then compete for selection: the lexical system uses the bottom-up information provided by the auditory input, together with top-down context---provided by grammatical, supra-segmental, and semantic constraints---to select the candidate lexical representation with the best match.
+This sequence of events occurs in a *cascaded* fashion.
+As the recognition system accumulates information about the unfolding acoustic signal, matching phonological representations are activated [@marslen1987functional; @marslen1978processing; @grosjean1980spoken], and in turn activate their associated semantic representations [@neely1977semantic].
+By the time lexical selection occurs, many non-selected phonological and semantic representations have been activated, potentially modulating the dynamics of word recognition.
+
+A considerable amount of evidence for such cascaded account of lexical processing has been provided by studies recording eye movements during word recognition.
+For example, @allopenna1998tracking designed a word-recognition task in which participants were presented, in each trial, with four objects in the screen.
+Participants would then listen to a command like "Pick up the beaker; now put it below the diamond", and perform the action.
+The authors manipulated the phonological relationship between the target object's label (e.g., *casket*), and the label of each of the three distractors.
+Two of the distractors were phonologically related with the target, sharing onset (e.g., *castle*) or offset (e.g., *basket*) with the target word, respectively.
+The other distractor was phonologically unrelated to the target (e.g., *nickel*).
+After hearing the target label, phonological distractors attracted participants' eye fixations more than unrelated distractors.
+Distractors sharing phonological onset did so at an earlier time window than those sharing phonological offset.
+This time course of distractor fixations suggests that the auditory presentation of the target label activated no only its (subsequently selected) phonological form in participants' lexicon, but also that of phonologically related word-forms, leading to competition for selection between the word forms.
+These results converge with cascaded models of auditory word recognition, in which the unfolding acoustic input activates multiple phonological word-forms, which in turn compete for selection, like TRACE [@mcclelland1986trace] and Shortlist [@norris1994shortlist].
+
+The developing mental lexicon also seems to operate in this cascaded fashion.
+Like adults, infants activate non-selected lexical representations.
+This is reflected by the fact that from 21 months of age, infants' lexicon seems to also be systematically organised according to the semantic and phonological properties of its lexical representations.
+Priming paradigms of word recognition have provided a strong body of evidence for the existence of phonological and semantic links between early lexical representations between 18 and 21 months of age [@arias2009lexical; @styles2009infants].
+For instance, using a word recognition task, @arias2009lexical found that infants' spoken word recognition (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
+Other studies have provided electrophysiological evidence of semantic priming at earlier ages [e.g., @rama2013development; @friedrich2005lexical].
+More recent studies have provided evidence for the emergence of such semantic links, even in the absence of visual referents during the experimental task [@willits2013toddlers].
+
+Phonological priming effects have also been reported in the initial lexicon.
+@mani2010infant created an implicit naming task in which each trial started with the *silent* presentation of a prime picture.
+Then, a target-distractor picture pair was presented side-by-side.
+Finally, the target picture's label was presented auditorily.
+The authors manipulated the phonological overlap between the prime label and the target label, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
+Prime and target-distractor pairs were semantically unrelated.
+Interestingly, infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
+This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.The authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
+
+In a follow-up study, @mani2011phonological found the opposite effect in older toddlers.
+After phonologically related primes, 24 month-old toddlers showed weaker target looking preference than after phonologically unrelated primes.
+These results interpreted these outcome as the result of the implicitly generated prime label interfering with the subsequent recognition of the (phonologically related) target word.
+The authors suggested that the shift from facilitation to interference from 18 to 24 months they found in both studies might be the result of a developmental shift in which 18-month-olds' lexicon is not yet organised based on phonological similarity, while 24-month-olds' is.
+This would lead to the former showing a pre-lexical facilitation effect in which such facilitation occurs via the activation of phonological segments, while the latter would show an interference effect due to lateral links between lexical representation having been established.
+
+More recently, @chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
 In each trial, the authors presented participants with four semantically and phonologically pictures.
@@
 The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
-These results support a cascaded activation account of lexical access during the first stages of lexical development.
-@swingley1999continuous
-
-## Cascaded activation in bilingual parallel activation
-
-There is also evidence of cascaded activation in bilinguals.
-A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
-When listening to speech, bilinguals activate all lexical candidates from either language consistent with the speech signal.
-Even more surprising, when speaking, bilinguals activate all potential words consistent with the concepts they want to express.
-This effect has been systematically reported in adults [@marian1999activation; @costa2000cognate; @thierry2007brain; @dunabeitia2009masked].
-
-For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
-This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
-
-A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
-Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
-Cognates are form-similar translation equivalents.
-Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
-
-Also in toddlers [@von2012language; @von2014bilinguals] and school-aged children [@persici2019lexical; @bosma2020cognate].
-Some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
-Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
-Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that Spanish-Catalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
-
-Although recent work has provided strong evidence of parallel activation in early ages, how cognateness shapes that organisation of the early bilingual lexicon, and how this is reflected on the dynamics of lexical access during word comprehension and production is unclear.
-
-Using the experimental paradigm developed by [@arias2009lexical; @arias2013s; @singh2014one] compared within and across language
-priming effects in Chinese-English toddlers.
-@kuipers2015bilingualism compared ERP responses to picture-word pairs in English monolinguals and Welsh-English bilinguals where the words were either semantically related or unrelated to a pictured object.
-Although both studies tested 30-month-olds, the conclusions the authors reached do not fully agree.
-@singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
-
-## Cognate word recogntiion
+These results support a cascaded activation account of lexical access during the first stages of lexical development, paralleling previous findings in adults [@allopenna1998tracking].
+
+Bilinguals provide one of the most interesting pieces of evidence in support of a cascaded account of lexical processing.
+A critical property the bilingual lexicon is that its representations are accessed in a language-non selective way.
+Even during monolingual situations, bilinguals access their lexical representations in both of their languages [e.g.; @thierry2007brain; @dunabeitia2009masked].
+This is reflected in bilinguals' performance in word recognition and production tasks.
+For instance, @marian1999activation presented Russian-English bilinguals with a series of trials that started with an auditory instruction like "Poloji marku nije krestika" ["Put the stamp below the cross"].
+The instruction would be present in Russian (dominant language for most participants).
+The target object (*marku* [*stamp*], in this case) would be present in the screen, together with an object whose English label shared phonological onset with the target label (e.g., *mark*), and two unrelated distractors whose labels in Russian and English did not shared phonological relationship with the target label.
+Converging with @allopenna1998tracking's results in monolingual adults, after hearing the target label bilinguals fixated the cross-language phonological distractor significantly more than the unrelated distractors.
+These findings suggest that participants activated phonologically related word-forms in both Russian *and* English, which affected their overt visual exploration patterns during the task.
+
+Language non-selectivity in the bilingual lexicon has also been shown to affect top-down lexical access during word production.
+@costa2000cognate presented Catalan-Spanish bilinguals with a series of pictures of familiar objects.
+For each object, participants were asked to name it in Catalan (their dominant language).
+Unbeknownst to participants, the authors manipulated the phonological overlap between the pictures' labels in Catalan and their translations in Spanish.
+Participants produced faster words that shared phonological overlap with their Spanish translations (e.g., *gat*-*gat* [*cat*]) than those unrelated to their translation (e.g., *taula*-*mesa* [*table*]).
+Critically, Spanish monolinguals who completed the same task, naming the pictures in Spanish, showed equivalent naming times in both conditions.
+These results reveal that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the activation of its associated phonological forms in both language sin parallel, which influenced the subsequent the dynamics of word production.
+
+Further support for the parallel retrieval of phonological forms during word production is given by implicit naming paradigms.
+Using an adaptation of @mani2010infant's task, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
+The authors presented German-English bilinguals with 120 prime-target pairs.
+Primes were presented as familiar pictures in silence.
+After prime picture offset, target words were presented auditorily.
+Participants' N400 ERP components were recorded from target word onset.
+The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
+When prime and target were phonologically identical (*Affe*-*Affe*, German for *monkey*), or similar (*Fahne*-*Sahne*, German for *flag* and *ice-cream*, respectively) within L1, participants' showed a reduced N400 amplitude, compared to when prime and target were phonologically unrelated (*Messer*-*Seil*, German for *knife* and *rope*).
+Critically, a similar effect was found when prime and target were phonologically related through translation (*Rustsche*-*Kleid*, German for *slide* and *dress*).
+This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
+
+Phonological priming paradigms have also revealed language non-selectivity in the initial bilingual lexicon.
+For instance, @von2012language found evidence of cross-language phonological priming in 21- to 42-months-old children learning German and English.
+At the beginning of each trial, the authors auditorily presented an English prime word embedded in a carrier phrase.
+Then, the target label was auditorily presented in German.
+Finally the target and distractor pictures were presented side-by-side.
+The authors manipulated the phonological overlap between the prime and target labels.
+The novelty in this study lied in the orthogonal manipulation of the phonological overlap between both labels in English and German.
+In some trials, the auditorily presented prime and target labels were phonologically related (e.g., *slide*-*Klide* [*dress*]).
+In some other trials, both labels were phonologically related through translation: the auditorily presented prime label did *not* overlap with the target label (e.g., *leg*-*Stein* [*stone*]), but its translation in German did [*Bein*].
+In the rest of the trials prime and target labels were phonologically unrelated in both languages.
+The authors found a facilitation effect of cross-language priming when both prime and target auditory labels overlapped phonologically, as revealed by a stronger target picture looking preference, as compared to that of unrelated trials.
+Interestingly, participants showed a weaker target preference in priming through translation trials.
+Since participants' target recognition was interfered by the non-presented prime translation, such an inhibitory effect must stem at the lexical level.
+The fact that phonological priming facilitated the recognition of the target words (both labels belong to different languages), and that phonological priming through translation interfered target recognition (translation and target belong to the same language) points to cross-language connections playing an excitatory role, and to within-language connections playing an inhibitory role.
 
@@
 
-Another source of evidence supporting the language non-selective account of lexical access is provided by cross-languistic priming priuming thorught translation paradigms.
-In line with @floccia2020translation, @von2012language found that bilingual toddlers aged 21-to-43-months, and who were learning German and English, showed a stronger target preference in a German word recognition task after being primed with a phonologically related English word, which shared phonological onset with the prime word (e.g., *slide*-*Klide* [German for *dress*]), compared to when prime and target words were phonologically unrelated (e.g., *bottle*-*Ohr* [German for *ear*]).
-Interestingly, they also found evidence of such priming effect when participants were prime with an English word which was *not* phonologically related to the German target word, but rather its German translation was (e.g., *leg* [with German trasnlation *Bein*]-*Stein* [German for *stone*]).
-Altogether, these results indicate that bilingual toddlers activate translation equivalents in parallel during word recognition, and that the phonology of both labels may interact with lexical access in the recognition of subsequet words.
-Importantly, cross-linguitic priming through translation demonstrates that previous findings of a cognateness facilitation in word production and recognition do not result from the mere phonological overlap between auditorily presented and target labels, but also from the phonological overlap between the prime translation (not presented) and the target.
-
-Evidence from cognates.
-Marian and Spivey (1999)
-Costa et al. (2000)
-
-@dijkstra2019multilink
-
-The role of cognates in lexical processing.
-
-Another source of evidence are studies studies involving phonological priming of non-cognates through translation. [SEE REFERENCES FROM VON HOLZEN 2012]
-
-## The rpesent study
-
 The aforementioned studies use priming-though-translation paradigms.
@@
 When prime words are auditorily presented, the task design constraints the naming context to one of the languages.
-The consequence is a potential asymmtry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
-This might lead to a lower strength, and higher lacenty of the activation of the translation.
+The consequence is a potential asymmetry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
+This might lead to a lower strength, and higher latency of the activation of the translation.
+
+Priming through translation paradigms prove the existence of cross-language phonological associations at the lexical level, as suggested by the fact that non-presented prime translations can interfere with subsequent target recognition.
+However, since participants are auditorily presented with a prime label, the contribution of sub-lexical facilitation through acoustic similarity cannot be ruled out.
+For instance, it is possible that the inhibitory priming through translation found by @von2012language is the result
+
+THERE IS NO EVIDENCE OF IMPLICIT NAMING IN BILINGUALS
 
 In the present study, we use an adaptation of an implicit naming paradigm by @mani2010infant, in which participants are primed with a picture, instead of an auditorily presented label.
-@mani2010infant showed that 18 month-old monolinguals implicitly generate the labels of name-known pictures presented in silence.
-In each trial, infants were presented with prime pictures presented in silence, and then with a target and a distractor picture, both presented side-by-side.
-Finally, the target picture's label was presented auditorily.
-The authors manipulated the phonological overlap between the prime label and the target label, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
-Prime and target-distractor pairs were semantically unrelated.
-Interestingly, infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
-This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
+This paradigm prevents infants from activating the prime label in any of their two languages, and therefore makes it more likely that they will activate the prime labels in both languages in parallel.
+Infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
 In particular, the authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
 
-@mani2011phonological used the same paradigm in 24-months-old monolinguals, and also found evidence of implicit naming, but in the opposite direction.
-After phonologically related primes, infants showed weaker target looking preference than after phonologically unrelated primes.
-These results interpreted these outcome as the result of the implicitly generated prime label interfering with the subsequent recognition of the (phonologically related) target word.
-The authors suggested that the shift from facilitation to interference from 18 to 24 months they found in both studies might be the result of a developmental shift in which 18-month-olds' lexicon is not yet organised based on phonological similarity, while 24-month-olds' is.
-This would lead to the former showing a pre-lexical facilitation effect in which such facilitation occurs via the activation of phonological segments, while the latter would show an interference effect due to lateral links between lexical representation having been established.
-Both studies by Mani and Plunkett provide evidence of implicit naming of name-known pictures by 18-month old toddlers and older, and that the resulting labels interact with the dynamics of recognition of subsequently presented word-forms.
-
-Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
-@duta2012erp presented name-known pictures in silence for one second.
-After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
-In some trials the auditory label corresponded to a canonical realisation of the word-form.
-In other trials, the word was mispronounced.
-Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
-A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
-This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
-
-When extended to the bilingual case, this implicit naming task may offer bilingual participants with an uncontrained naming context in whcih the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
-Using an adaptation of @mani2010infant's implicit naming paradigm, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
-The authors presented German-English bilinguals with 120 prime-target pairs.
-Primes were presented as familiar pictures in silence.
-After prime picture offset, target words were presented auditorily.
-Participants' N400 ERP components were recorded from target word onset.
-The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
-When prime and target were phonologically identical (*Affe*-*Affe*, German for *monkey*), or similar (*Fahne*-*Sahne*, German for *flag* and *ice-cream*, respectively) within L1, participants' showed a reduced N400 amplitude, compared to when prime and target were phonologically unrelated (*Messer*-*Seil*, German for *knife* and *rope*).
-Critically, a similar effect was found when prime and target were phonologically related through translation (*Rustsche*-*Kleid*, German for *slide* and *dress*).
-This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
-
-Evidence from cognates.
-
-The role of cognates in lexical processing.
-
-This study also provides a more suitable design for drawing conslusions about developmental change in word recognition trajectories frot wo reasons.
+When extended to the bilingual case, this implicit naming task may offer bilingual participants with an unconstrained naming context in which the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
+
+This study also provides a more suitable design for drawing conclusions about developmental change in word recognition trajectories for two reasons.
 First, it extends the age range of participants, compared to previous studies.
@@
 
-. In order to circumvent the problem of limited vocabulary knowledge
+In order to circumvent the problem of limited vocabulary knowledge
 in the non-dominant language, we propose to test participants only in their dominant language, therefore
@@
 advantages of such approach].
-
-## The present study
 
@@
 Hypothesis 4: if the emergence of within-language or cross-language phonological links is explained better by the growth of cross-language vocabulary size, compared to within-language vocabulary size, a model that incorporates total vocabulary size as a predictor instead of dominant vocabulary size should show better predictive performance.
-If the emergence of such links is explained at all by the growth of vocabulary size, both models incorporating voacbulary size as a predictor should show better predictive performance than a model incorporating participants' age.
-
-# Methods
+If the emergence of such links is explained at all by the growth of vocabulary size, both models incorporating vocabulary size as a predictor should show better predictive performance than a model incorporating participants' age.
+
+# Study 1
+
+## Methods
 
@@
 
-## Participants
+### Participants
 
@@
 #| label: participants-numbers
-n_participants_total <- participants |> 
-	distinct(location, child_id) |> 
-	count(location)
-
-n_participants_sex <- participants |> 
-	distinct(location, sex, child_id) |> 
-	count(location, sex)
-
-n_participants_sessions <- count(participants,
-								 child_id,
-								 name = "n_sessions") |> 
+participants_bcn <- filter(participants, location=="Barcelona")
+
+n_participants_total <- nrow(distinct(participants_bcn, child_id))
+n_sessions_total <- count(participants_bcn)
+
+n_participants_lp <- participants_bcn |> 
+	distinct(lp, child_id) |> 
+	count(lp)
+
+n_participants_lp_sex <- participants_bcn |> 
+	distinct(lp, sex, child_id) |> 
+	count(lp, sex)
+
+n_participants_sessions <- participants_bcn |> 
+	count(child_id, name = "n_sessions") |> 
 	count(n_sessions) |> 
 	group_split(n_sessions) |> 
-	set_names(paste0("session_", 1:3))
-
-n_sessions_total <- count(participants)
-
-n_sessions_lp <- participants |> 
-	summarise(across(age, lst(mean, sd, min, max)),
-			  n = n(),
-			  .by = c(lp)) |> 
+	set_names(paste0("session_", 1:3)) |> 
+	map("n")
+
+n_sessions_lp <- participants_bcn |> 
+	summarise(across(age, lst(mean, sd, min, max)), n = n(), .by = c(lp)) |> 
 	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
 	group_split(lp) |> 
-	set_names(janitor::make_clean_names(unique(participants$lp)))
-
-n_sessions_dominance_lp <- count(participants, lp, test_language) |> 
+	set_names(janitor::make_clean_names(unique(participants_bcn$lp)))
+
+n_sessions_dominance_lp <- count(participants_bcn, lp, test_language) |> 
 	group_split(test_language) |> 
-	set_names(c("catalan", "english", "spanish")) |> 
+	set_names(c("catalan", "spanish")) |> 
 	map(group_split, lp)
 
-n_sessions_lp <- participants |> 
+n_sessions_lp <- participants_bcn |> 
 	count(lp) |> 
 	group_split(lp) |> 
-	set_names(c("monolingual_eng", "monolingual", "bilingual"))
-```
-
-We collected data from `r n_participants_total$n[1]` participants living in the Metropolitan Area of Barcelona (Spain) tested at the Laboratori de recerca en Infància at the Universitat Pompeu Fabra (`r n_participants_sex$n[1]` female, `n_participants_sex$n[2]` male), and `r n_participants_total$n[2]` participants living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford (`r n_participants_sex$n[3]` female, `n_participants_sex$n[4]`, `n_participants_sex$n[5]` not reported).
-Families were recruited from maternity room in private hospitals or from social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r sum(n_participants_total$n)` children that participated, `r n_participants_sessions$session_1$n` participated once, `r n_participants_sessions$session_2$n` participated twice, and `r n_participants_sessions$session_3$n` participated three times.
+	set_names(c("monolingual", "bilingual")) |> 
+	map("n")
+```
+
+We collected data from `r n_participants_total$n[1]` children living in the Metropolitan Area of Barcelona (Spain), tested at the Laboratori de Recerca en Infància at the Universitat Pompeu Fabra.
+Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
+From the `r n_participants_total$n` children that participated, `r n_participants_sessions$session_1` participated once, `r n_participants_sessions$session_2` participated twice, and `r n_participants_sessions$session_3` participated three times.
 Recurrent participants were tested with at least XXX months of difference.
-We gathered a total of `r n_sessions_total$n` testing sessions: `r n_sessions_lp$monolingual_eng$n` from participants in Oxford, and `r n_sessions_lp$monolingual$n + n_sessions_lp$bilingual$n` from participants in Barcelona.
-
-We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
-Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
-The output of this interview is an estimated degree of exposure (*DoE*) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
-According to this estimate, we classified participants as Catalan-, English-, or Spanish-dominant if the language with highest *DoE* was Catalan, English, or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
-From the `r n_sessions_total$n` testing sessions, `r n_sessions_lp$monolingual_eng$n` belonged to English monolinguals,  `r n_sessions_lp$monolingual$n` to Catalan or Spanish monolinguals, and  `r n_sessions_lp$bilingual$n` to Catalan-Spanish bilinguals.
-@tbl-participants shows a detailed description of the linguistic profile of our sample.
+We gathered a total of `r n_sessions_total$n` testing sessions.
+Participants were divided into monolinguals and bilinguals based on their relative degree of exposure to Catalan and Spanish, estimated using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
+We categorised participants as monolingual if exposed to more than 80% or more of the time to their dominant language, and as bilingual otherwise.
+`r Words::English(n_participants_lp$n[1])` of the participants were categorised as monolinguals (`r n_participants_lp_sex[1]` female, `r n_participants_lp_sex[2]` male) and `n_participants_lp$n[2]` as Catalan/Spanish bilinguals (`r n_participants_lp_sex[3]` female, `r n_participants_lp_sex[4]` male) (see @tbl-participants for a detailed summary of participants' age and language profile).
+Participants' vision was normal, none used glasses or any other type of vision corrector.
 
 ```{r tbl-participants}
-#| label: tbl-partiicpants
-#| tbl-cap: "Demographic and linguistic profile of participants."
-participants |> 
+#| label: tbl-participants
+#| tbl-cap: "Demographic and linguistic profile of testing sessions."
+participants_bcn |> 
 	unnest_wider(doe) |> 
 	select(-matches("others")) |> 
-	mutate(lp = case_when(
-		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
-		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
-		.default = lp)) |> 
-	arrange(desc(lp)) |> 
+	arrange(lp, test_language) |> 
 	summarise(n = n(),
+			  n_participants = n_distinct(child_id),
 			  across(age, lst(mean, sd, min, max)),
@@
 	fmt_number(is.numeric, decimals = 1) |> 
-	fmt_integer(n) |> 
+	fmt_integer(c(n, n_participants)) |> 
 	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
@@
 	tab_spanner("Degree of Exposure (%)", matches("doe")) |> 
-	cols_label(n = "N",
+	cols_label(n = "N sessions",
+			   n_participants = "N participants",
 			   age_mean = "M (SD)",
@@
 
-We collected data from `r n_participants_total` monolingual and bilingual participants living in the Metropolitan Area of Barcelona (Spain), who were exposed to at least Catalan and/or Spanish from birth.
-Families were recruited from maternity room in private hospitals in Barcelona, and contacted via phone when the child's age spanned between our age intervals of interest.
-Families were invited to participate at three age points: 21, 25, and 30 months.
-`r n_participants_sessions[[1]]$n` participants were tested at one age point,  `r n_participants_sessions[[2]]$n` at two age points, and `r n_participants_sessions[[3]]$n` at the three age points.
-In total, we gathered data from `r n_sessions_total$n` testing sessions: `r n_sessions_age_group$age_21$n` at 21 months (*Mean* = `r round(n_sessions_age_group$age_21$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_21$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_21$age_min`--`r n_sessions_age_group$age_21$age_max`), `r n_sessions_age_group$age_25$n` at 25 months (*Mean* = `r round(n_sessions_age_group$age_25$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_25$age_min`--`r n_sessions_age_group$age_25$age_max`), and `r n_sessions_age_group$age_30$n` at 30 months (*Mean* = `r round(n_sessions_age_group$age_30$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_30$age_min`--`r n_sessions_age_group$age_30$age_max`).
-
-Participants' vision was normal, none used glasses or any other type of vision corrector.
-
-### Language profile {#sec-lp}
-
-We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
-Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
-The output of this interview is an estimated degree of exposure (DoE) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
-According to this estimate, we classified participants as Catalan- or Spanish-dominant if the language with highest DoE was Catalan or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
-We collected data from `r n_sessions_dominance$catalan$n` Catalan-dominant participants in Catalan (`r n_sessions_dominance_age_group$catalan$age_21$n` at 21 months, `r n_sessions_dominance_age_group$catalan$age_25$n` at 25 months, and `r n_sessions_dominance_age_group$catalan$age_30$n` at 30 months).
-We further classified participants as monolinguals if the DoE to their dominant language exceeded 80% of the total DoE to Catalan and Spanish, and as bilinguals otherwise.
-Participants with DoE to language other than Catalan or Spanish were excluded from analyses.
-This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
-@tbl-participants-lp shows a detailed description of the linguistic profile of our sample.
-
 ### Vocabulary size
@@
 ```{r vocab-values}
-n_imputed <- table(vocabulary$is_imputed)[2]
-prop_imputed <- scales::percent(n_imputed/nrow(vocabulary))
+vocabulary_bcn <- inner_join(vocabulary, 
+							 select(participants_bcn, session_id),
+							 by = join_by(session_id))
+
+n_imputed <- table(vocabulary_bcn$is_imputed)[2]
+prop_imputed <- scales::percent(n_imputed/nrow(vocabulary_bcn))
 n_pool <- nrow(bvq_data$vocabulary)
@@
 Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
-
-We calculated several measures of receptive vocabulary size from each participant's vocabulary: L1 vocabulary size (proportion of words  reported as acquired in the checklist of the dominant language), L2 vocabulary size (proportion of words  reported as acquired in the checklist of the non-dominant language), total vocabulary size (proportion of the words in both checklists reported as acquired), conceptual vocabulary (proportion of concepts for which the participant was reported to have acquired at least one label, in any language), and translation equivalent vocabulary (proportion of concepts for which the participant was reported to have acquired at two labels, one in each language).
+We calculated two measures of receptive vocabulary size for each participant: *L1 vocabulary size* (proportion of words  reported as acquired in the checklist of the dominant language), and *total vocabulary size* (proportion of the words in both checklists reported as acquired) (see @fig-vocabulary).
 
@@
 
-```{r tbl-vocabulary}
-#| label: tbl-vocabulary
-#| tbl-cap: "Participant vocabulary sizes across ages and language profiles.
+```{r fig-vocabulary}
+#| label: fig-vocabulary
+#| fig-cap: "Participant vocabulary sizes across ages and language profiles.
 Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
@@
 #| eval: false
-vocabulary |> 
+#| fig-width: 8
+#| fig-height: 4.5
+vocabulary_bcn |> 
 	inner_join(select(participants, child_id, session_id, age, lp),
@@
 				 names_transform = \(x) gsub("_prop", "", x)) |> 
-	mutate(lp = case_when(
-		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
-		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
-		.default = lp) |> 
-			factor(levels = c("Monolingual (English)",
-							  "Monolingual (Catalan or Spanish)",
-							  "Bilingual (Catalan-Spanish)")),
-		measure = if_else(measure=="l1", 
+	mutate(measure = if_else(measure=="l1", 
 							 "L1 vocabulary", 
@@
 		 y = "Vocabulary size (%)") +
-	theme(panel.grid = element_line(linetype = "dotted",
+	theme(panel.grid.major = element_line(linetype = "dotted",
 										  colour = "grey"),
-		  legend.position = "right",
+		  legend.position = "top",
 		  legend.title = element_blank())
 
-ggsave(file.path("img", "vocabulary.jpeg"),
-	   dpi = 800, height = 8, height = 4)
-```
-
-## Stimuli
+```
+
+### Stimuli
 
@@
 
-### Auditory stimuli
-
-The auditory stimuli were natural exemplars of the selected target words, spoken by Catalan-Spanish proficient bilingual female speaker who was instructed to pronounce each word in a toddler-directed manner.
+#### Auditory stimuli
+
+The auditory stimuli were natural exemplars of the selected target words, spoken by Central Catalan-Spanish proficient bilingual female speaker who was instructed to pronounce each word in a toddler-directed manner.
 Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
-We used the Audacity [@reference] and Praat [@boersma2001speak] to record and edit the audio files.
+We used the Audacity and Praat [@boersma2001speak] software packages to record and edit the audio files.
 The speaker was presented with a list of words in Catalan.
@@
 
-### Visual stimuli
+#### Visual stimuli
 
@@
 
-## Procedure
+### Procedure
 
@@
 Participants sat at approximately 65 cm from the eye-tracker and a XX-in screen of $1929\times1080$ screen resolution.
-We used a custom Matlab XXXX script using the PsychToolbox XXX extension [@brainard] to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
+We used a custom Matlab XXXX script using the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox] to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
 Sampling rate was set at 120 Hz.
@@
 
-## Apparatus
+### Apparatus
 
@@
 
-## Data processing
+### Data processing
 
@@
 
-## Data analysis
+### Data analysis
 
@@
 
-# Results
+## Results
 
@@
 #| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-data_time |> 
+#| fig-width: 11
+#| fig-height: 4
+data_time_bcn |> 
+	drop_na(.prop) |> 
 	summarise(.prop = mean(.prop),
 			  .by = c(lp, timebin, session_id)) |> 
-	ggplot(aes(timebin, .prop, colour = lp)) +
+	ggplot(aes(timebin, .prop)) +
 	facet_wrap(~lp, nrow = 1, scales = "free_x") +
 	geom_line(aes(group = session_id),
-			  # colour = "grey",
+			  colour = "grey",
 			  alpha = 1/10) +
@@
 ```{r tbl-coefs}
-post <- gather_draws(fit_0, `b_.*`, regex = TRUE)
+post <- gather_draws(fit_1, `b_.*`, regex = TRUE)
 
@@
 	facet_wrap(~.variable, scales = "free") +
-	geom_histogram(bins = 15, colour = "white") +
+	geom_histogram(bins = 15, colour = "white",
+				   position = position_nudge(y = 0.1),
+				   fill = "grey80") +
 	geom_errorbar(data = mean_qi(post),
-				  aes(xmin = .lower, xmax = .upper, y = 400),
+				  aes(xmin = .lower, xmax = .upper, y = 0),
 				  width = 1,
@@
 	geom_point(data = mean_qi(post),
-			   aes(x = .value, y = 400),
+			   aes(x = .value, y = 0),
 			   size = 2) +
@@
 
-## Hypothesis 1: within-language phonological priming
-
-## Hypothesis 2: cross-language phonological priming
-
-## Hypothesis 3: emergence of phonological association
-
-## Hypothesis 4: the compating role of age and vocabulary
+### Hypothesis 1: within-language phonological priming
+
+```{r fig-ptlt-recognition-condition}
+#| label: fig-ptlt-recognition-condition
+#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+#| fig-width: 11
+#| fig-height: 4
+data_time_bcn |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(lp, timebin, condition, session_id)) |> 
+	ggplot(aes(timebin, .prop, colour = condition)) +
+	facet_grid(~lp) +
+	# geom_rug(aes(x = timebin[is.na(.prop)])) +
+	# geom_line(aes(group = interaction(condition, session_id)),
+	# 		  alpha = 1/8) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	stat_summary(fun.data = "mean_se",
+				 geom = "errorbar",
+				 width = 0.35,
+				 linewidth = 2/4) +
+	stat_summary(fun = "mean",
+				 geom = "point",
+				 size = 1.2) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 linewidth = 2/4) +
+	labs(x = "Time (ms)",
+		 y = "PTLT",
+		 colour = "Condition") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	scale_y_continuous(labels = scales::percent,
+					   breaks = seq(0, 1, 0.05)) +
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+```
+
+### Hypothesis 2: cross-language phonological priming
 
@@
 						   mean(data_time$timebin),
-						   sd(data_time$timebin))
+						   sd(data_time_bcn$timebin))
 
 age_values <- make_std(c(21, 25, 30),
-					   mean(data_time$age),
-					   sd(data_time$age))
-
-nd <- expand_grid(condition = levels(fit_0$data$condition),
+					   mean(data_time_bcn$age),
+					   sd(data_time_bcn$age))
+
+nd <- expand_grid(condition = levels(fit_3$data$condition),
 				  timebin_std = timebin_values,
@@
 				  # age = c(21, 25, 30),
-				  lp = levels(fit_0$data$lp))
+				  lp = levels(fit_3$data$lp))
 
 epreds <- add_epred_draws(newdata = nd,
-						  object = fit_0,
+						  object = fit_3,
 						  ndraws = NULL,
@@
 						  value = ".value") |> 
+	mutate(.value = plogis(.value)) |> 
 	mean_qi() |> 
@@
 			   fill = condition)) +
-	facet_wrap(lp ~ age_std) +
-	geom_hline(yintercept = 0,
+	facet_grid(lp~age_std) +
+	geom_hline(yintercept = 0.5,
 			   linetype = "dashed") +
@@
 	geom_line(linewidth = 3/4) +
+	# stat_summary(data = data_time_bcn,
+	# 			 aes(y = .elog),
+	# 			 fun = mean,
+	# 			 geom = "point",
+	# 			 size = 2) +
 	labs(x = "Time (ms)",
@@
 		 fill = "Condition") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	scale_x_continuous(breaks = make_std(seq(0, 17, 2),
+										 mean(data_time$timebin),
+										 sd(data_time$timebin)),
+					   labels = \(x) format(seq(0, 17, 2)*100+200, big.mark = ",")) +
 	theme(legend.position = "top",
-		  panel.grid.major = element_line(colour = "grey",
+		  panel.grid.major.y = element_line(colour = "grey",
 		  								linetype = "dotted"))
@@
 ```
+
+### Hypothesis 3: emergence of phonological association
+
+### Hypothesis 4: the compating role of age and vocabulary
+
+In a first analysis, we examined the effect of phonological priming.
+We compared participants' looking preference for the target in related and unrelated trials.
+We first compared the aggregated probability of target looking across time bins in both conditions for each language group.
 
@@
 
-# Discussion
+## Discussion
+
+# Study 2
+
+## Methods
+
+### Participants
+
+```{r}
+#| label: participants-numbers-oxf
+participants_oxf <- filter(participants, location=="Oxford")
+
+n_participants_total <- nrow(distinct(participants_oxf, child_id))
+n_sessions_total <- count(participants_oxf)
+
+n_participants_sex <- participants_oxf |> 
+	distinct(sex, child_id) |> 
+	count(sex)
+
+n_participants_sessions <- participants_oxf |> 
+	count(child_id, name = "n_sessions") |> 
+	count(n_sessions) |> 
+	group_split(n_sessions) |> 
+	set_names(paste0("session_", 1:2)) |> 
+	map("n")
+
+ages <- participants_oxf |> 
+	summarise(n = n(),
+			  n_participants = n_distinct(child_id),
+			  across(age, lst(mean, sd, min, max)),
+			  across(matches("doe_"), lst(mean, sd)),
+			  age_vctr = list(age),
+			  .by = c(lp, test_language))
+
+```
+
+We collected data from `r n_participants_total$n[1]` children (`r n_participants_sex[1]` female, `r n_participants_sex[2]` male, `r n_participants_sex[3]` sex not reported, age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]), living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford.
+Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
+From the `r n_participants_total$n` children that participated, `r n_participants_sessions$session_1` participated once, and `r n_participants_sessions$session_2` participated twice.
+Recurrent participants were tested with at least XXX months of difference.
+We gathered a total of `r n_sessions_total$n` testing sessions.
+All participants were being raised in exclusively British English monolingual homes.
+
+### Vocabulary size
+
+```{r vocab-values}
+vocabulary_oxf <- inner_join(vocabulary, 
+							 select(participants_oxf, session_id),
+							 by = join_by(session_id))
+```
+
+We collected vocabulary data using parental responses to the Oxford Communicative Development Inventory (OCDI) [@hamilton2000infant].
+Families were sent the questionnaire immediately after each experimental session, and were given two weeks to fill it.
+Since all vocabulary sizes of English monolingual infants were only assessed in English, both *L1 vocabulary* and *total vocabulary* sizes were identical (see @fig-vocabulary-oxf).
+
+```{r fig-vocabulary-oxf}
+#| label: fig-vocabulary
+#| fig-cap: "Participant vocabulary sizes across ages and language profiles.
+Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
+Vocabulary size scores from the recurrent participants are shown linked."
+#| eval: false
+#| fig-width: 4
+#| fig-height: 4
+vocabulary_oxf |> 
+	inner_join(select(participants, child_id, session_id, age, lp),
+			   by = join_by(child_id, session_id)) |> 
+	ggplot(aes(age, total_prop)) +
+	geom_line(aes(group = child_id),
+			  alpha = 1/2,
+			  colour = "grey") +
+	geom_point(colour = clrs[1]) +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size (%)") +
+	theme(panel.grid.major = element_line(linetype = "dotted",
+										  colour = "grey"),
+		  legend.position = "top",
+		  legend.title = element_blank())
+```
+
+### Stimuli
+
+New stimuli lists were generated to adapt the experimental procedure to English-learning infants.
+Stimuli lists were created following the same constraints as in Study 1.
+Auditory stimuli were recorded following the same procedure as in Study 1, produced by Southern British English native female speaker in a toddler-directed manner.
+Audio and picture processing were performed following the same workflow as in Study 1.
+
+### Procedure and apparatus
+
+Same as in Study 1.
+The study was run using a custom Matlab script, PresentMate, based on the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox].
+Visual fixations were recorded using a Tobii TX 300 eye-tracker and a 23-in screen of 1920 $\times$ 1080 resolution.
+The Tobii Analytics SDK 3.0 was used to interact with the eye-tracking while the experiment was running.
+Sampling rate was set at 120 Hz.
+A 9-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
+
+### Data processing
+
+Same as in Study 1.
+
+### Data analysis
+
+## Results
+
+# General discussion
+
+IMPLICIT NAMING
+Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
+@duta2012erp presented name-known pictures in silence for one second.
+After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
+In some trials the auditory label corresponded to a canonical realisation of the word-form.
+In other trials, the word was mispronounced.
+Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
+A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
+This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
+
+THE ROLE OF COGNATENESS IN WORD ACQUISITION
+
+For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
+This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
+
+A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
+Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
+Cognates are form-similar translation equivalents.
+Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
+
+Some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
+Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
+Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that Spanish-Catalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
 

### 2023-11-03 manuscript/test.qmd

@@
 ---
-project:
-  render:
-    - manuscript.qmd
-
-format:
-  pdf:
-    keep-tex: true  
-    linenumbers: true
-    doublespacing: false
-    include-in-header: 
-      text: |
-        \usepackage{tipa}
-        \usepackage{booktabs}
-        \hyphenpenalty=100000
-        \exhyphenpenalty=100000
-    knitr:
-      opts_chunk:
-        dev: "cairo_pdf"
-    filters: 
-      - "_extensions/andrewheiss/wordcount/citeproc.lua"
-      - "_extensions/andrewheiss/wordcount/wordcount.lua"
-
-title: "Developmental trajectories of bilingual word recognition"
-short-title: "Developmental trajectories of bilingual word recognition"
-author:
-  - name: Gonzalo Garcia-Castro
-    corresponding: true
-    orcid: 0000-0002-8553-4209
-    email: gonzalo.garciadecastro@upf.edu
-    affiliations:
-      - id: cbc
-        name: Universitat Pompeu Fabra
-        department: Center for Brain and Cognition
-        city: Barcelona, 08005
-  - name: Serene Siow
-    orcid: 0000-0001-6482-2191
-    email: siow.serene@gmail.com
-    affiliations: 
-      - id: oxf
-        name: University of Oxford
-        department: Department of Experimental Psychology
-        city: Oxford, OX2 6GG
-  - name: Nuria Sebastian-Galles
-    orcid: 0000-0001-6938-2498
-    email: nuria.sebastian@upf.edu
-    affiliations: 
-      - ref: cbc
-  - name: Kim Plunkett
-    orcid: 0000-0003-0216-7480
-    email: kim.plunkett@psy.ox.ac.uk
-    affiliations: 
-      - ref: oxf
-keywords:
-  - cognate
-  - word recognition
-  - lexicon
-  - language acquisition
-  - vocabulary
-  - bilingualism
-  - general additive mixed models
-  - bayesian
-csl: "../assets/apa7.csl"
-bibliography: "../assets/references.bib"
-link-citations: true
-editor: source
-lang: en
-freeze: true
-fig-dpi: 1000
 ---
 
-## Quarto
+```{r setup}
+#| label: setup
+#| echo: false
+#| message: false
+#| warning: false
+# load objects
+targets::tar_config_set(store = here::here("_targets"),
+						script = here::here("_targets.R"))
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
+targets::tar_load_globals()
 
-## Running Code
+targets::tar_load(
+	c(participants,
+	  stimuli,
+	  vocabulary,
+	  attrition_trials,
+	  attrition_participants,
+	  bvq_data,
+	  gaze,
+	  data_time,
+	  data_aggr
+	))
 
-When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
+targets::tar_load(
+	c(model_fits_aggr,
+	  model_fits_time,
+	  model_loos_aggr,
+	  model_loos_time
+	))
+
+# prepare data
+attrition <- lst(participants,
+				 attrition_participants,
+				 attrition_trials) |>
+	reduce(inner_join, by = join_by(session_id)) |>
+	unnest_wider(matches("all"), names_sep = "_")
+
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(gt)
+library(patchwork)
+library(english)
+library(gtExtras)
+
+# set ggplot theme and colour palette
+
+my_theme <- theme_minimal() +
+	theme(panel.grid = element_blank(),
+		  axis.line = element_line(colour = "black"),
+		  text = element_text(size = 12, colour = "black"),
+		  axis.text = element_text(colour = "black"))
+
+theme_set(my_theme)
+
+clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
+
+options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
+		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
+		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
+		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
+		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
+		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
+
+set.seed(888)
+
+```
+
+# Introduction
+
+## The early lexicon
+
+Building a mental lexicon is a major achievement in the developmental journey of infants: by accumulating lexical representations of familiar words, infants are later able to recognise them in speech, and to extract meaning from the speech they are exposed to.
+Infants start forming their first lexical representations before their first year of life [@jusczyk1999; @halle1994; @vihman2004].
+When presented with pairs of pictures of familiar objects, 6-months-old infants already direct their gaze towards whichever is named [@bergelson20126; @bergelson2015early].
+This initial lexicon is hardly larger than around fifteen words [@REFERENCE], but it undergoes rapid growth [@REFERENCE] during their second year of life, at the end of which toddlers know an average of XXX words, and by 30 months of age, they know XXX words [@REFERENCE].
+This accelerated lexical developmental during the second year of life is also reflected in infants'  trajectories of word recognition: infants recognise familiar words faster and more efficiently [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
+Bilingual infants' trajectories of lexical acquisition [@hoff2012, @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes] and word recognition [@vihman2007onset; @vihman2013; @legacy2018vocabulary] are equivalent to their monolingual peers'.
+This is a remarkable deed: bilingual infants receive a relative impoverished linguistic input in each of their languages compared to monolinguals [@costa2014does].
+The mechanism that facilitate bilingual lexical development are still unclear.
+
+## (Early) Word recognition is cascaded
+
+Despite their different linguistic input, monolinguals and bilinguals share broadly common word recognition mechanisms.
+The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal.
+This results in the activation of lexical representations whose associated phonological forms matches the acoustic signal to some extent.
+The activated word-forms then compete for selection: the lexical system uses the auditory input, together with top-down context provided by grammatical, supra-segmental, and semantic constraints, to select the candidate lexical representation with the best match.
+There is evidence that spoken word recognition occurs in a *cascaded* fashion.
+The activation and selection of candidate lexical representations overlap in time, relying on partial information that accumulates as the speech signal unfolds [@marslen1987functional; @marslen1978processing; @grosjean1980spoken].
+This cascaded activation triggered by lexical access also results in the activation of the concepts associated to the accesses phonological forms.
+@allopenna1998tracking.
+
+This is also the case of the developing lexicon: like adults, infants activate non-selected lexical representations.
+This is relfected by the fact that from 21 months of age, infants' lexicon seems to be systematically organised accordi to the semantic and phnological properties of the lexical representations.
+
+SEMANTICS
+@arias2009lexical showed evidence of semantic priming in 21-month-old infants.
+In a word recognition task, infants' recognition of a spoken word (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
+Later studies provided electrophysiological evidence of such effect as early as 14 months of age [@friedrich2005lexical].
+
+PHONOLOGY
+Initial lexical representations are also phonologically well-specified [@swingley2000spoken; @swingley2002lexical].
+Overall these results suggest that early lexical representations are systematically organised in the lexicon according to their semantic and phonological properties.
+
+BOTH
+@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
+In each trial, the authors presented participants with four semantically and phonologically pictures.
+Four seconds after pictures onset, a word-form was auditorily presented.
+The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category.
+For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
+Then they would hear the carrier phrase "Look at the **bee**!".
+The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
+These results support a cascaded activation account of lexical access during the first stages of lexical development.
+@swingley1999continuous
+
+## Cascaded activation in bilingual parallel activation
+
+There is also evidence of cascaded activation in bilinguals.
+A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
+When listening to speech, bilinguals activate all lexical candidates from either language consistent with the speech signal.
+Even more surprising, when speaking, bilinguals activate all potential words consistent with the concepts they want to express.
+This effect has been systematically reported in adults [@marian1999activation; @costa2000cognate; @thierry2007brain; @dunabeitia2009masked].
+
+For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
+This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
+
+A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
+Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
+Cognates are form-similar translation equivalents.
+Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
+
+Also in toddlers [@von2012language; @von2014bilinguals] and school-aged children [@persici2019lexical; @bosma2020cognate].
+Some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
+Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
+Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that Spanish-Catalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
+
+Although recent work has provided strong evidence of parallel activation in early ages, how cognateness shapes that organisation of the early bilingual lexicon, and how this is reflected on the dynamics of lexical access during word comprehension and production is unclear.
+
+Using the experimental paradigm developed by [@arias2009lexical; @arias2013s; @singh2014one] compared within and across language
+priming effects in Chinese-English toddlers.
+@kuipers2015bilingualism compared ERP responses to picture-word pairs in English monolinguals and Welsh-English bilinguals where the words were either semantically related or unrelated to a pictured object.
+Although both studies tested 30-month-olds, the conclusions the authors reached do not fully agree.
+@singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
+
+## Cognate word recogntiion
+
+@floccia2020translation tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
+The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, French, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
+A prime word was embedded at the end of a carrier sentence that participants listened to.
+Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
+In Study 1, the target word was the translation equivalent of the prime word (*cheese*-*fromage* for an English-French bilingual).
+In other trials, prime and target words were unrelated (e.g., *sock*-*fromage*).
+There was no phonological overlap at onset between prime and target or distractor labels in either of the two conditions.
+Participants were presented with two blocks of related and unrelated trials.
+In one of the blocks, participants were presented with English prime words and Home Language target words (*sock*-*fromage*), and in the other block they were presented with Additional Language prime words and English target words (*fromage*-*sock*).
+The authors found a cross-linguistic priming effect, in which participants showed a stronger preference for the target picture in the post-naming phase in related trials, as compared to unrelated trials.
+This effect was found regardless of the language of the prime (English or Home Language), or the dominance of the language of the prime (i.e., whether the prime word belonged to the dominant language).
+Target preference exceeded chance level in both conditions.
+In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
+This time, prime and target words were not translation equivalents, but rather words whose referents shared semantic features.
+Results from Study  2 were parallel to those from Study 1.
+The authors found a strong semantic priming effect across languages, regardless of the language of the prime or the dominance of the language of the prime.
+Overall these results suggest that bilinguals recognised target words in both conditions, and benefited from a cross-linguistic facilitation effect from translation equivalents.
+The symmetry of such effect across both languages suggests that participants lexical access occurred in parallel for the two members of translation equivalents.
+As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
+The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
+However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generated by an interaction by the phonological and semantic overlap between cognate primes and targets.
+
+Another source of evidence supporting the language non-selective account of lexical access is provided by cross-languistic priming priuming thorught translation paradigms.
+In line with @floccia2020translation, @von2012language found that bilingual toddlers aged 21-to-43-months, and who were learning German and English, showed a stronger target preference in a German word recognition task after being primed with a phonologically related English word, which shared phonological onset with the prime word (e.g., *slide*-*Klide* [German for *dress*]), compared to when prime and target words were phonologically unrelated (e.g., *bottle*-*Ohr* [German for *ear*]).
+Interestingly, they also found evidence of such priming effect when participants were prime with an English word which was *not* phonologically related to the German target word, but rather its German translation was (e.g., *leg* [with German trasnlation *Bein*]-*Stein* [German for *stone*]).
+Altogether, these results indicate that bilingual toddlers activate translation equivalents in parallel during word recognition, and that the phonology of both labels may interact with lexical access in the recognition of subsequet words.
+Importantly, cross-linguitic priming through translation demonstrates that previous findings of a cognateness facilitation in word production and recognition do not result from the mere phonological overlap between auditorily presented and target labels, but also from the phonological overlap between the prime translation (not presented) and the target.
+
+Evidence from cognates.
+Marian and Spivey (1999)
+Costa et al. (2000)
+
+@dijkstra2019multilink
+
+The role of cognates in lexical processing.
+
+Another source of evidence are studies studies involving phonological priming of non-cognates through translation. [SEE REFERENCES FROM VON HOLZEN 2012]
+
+## The rpesent study
+
+The aforementioned studies use priming-though-translation paradigms.
+In these paradigms, cross-linguistic priming results from activation spreading from the lexical representation of the the (auditorily presented) prime word to the lexical representation of its translation through semantic associations (e.g., translation equivalence).
+When prime words are auditorily presented, the task design constraints the naming context to one of the languages.
+The consequence is a potential asymmtry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
+This might lead to a lower strength, and higher lacenty of the activation of the translation.
+
+In the present study, we use an adaptation of an implicit naming paradigm by @mani2010infant, in which participants are primed with a picture, instead of an auditorily presented label.
+@mani2010infant showed that 18 month-old monolinguals implicitly generate the labels of name-known pictures presented in silence.
+In each trial, infants were presented with prime pictures presented in silence, and then with a target and a distractor picture, both presented side-by-side.
+Finally, the target picture's label was presented auditorily.
+The authors manipulated the phonological overlap between the prime label and the target label, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
+Prime and target-distractor pairs were semantically unrelated.
+Interestingly, infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
+This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
+In particular, the authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
+
+@mani2011phonological used the same paradigm in 24-months-old monolinguals, and also found evidence of implicit naming, but in the opposite direction.
+After phonologically related primes, infants showed weaker target looking preference than after phonologically unrelated primes.
+These results interpreted these outcome as the result of the implicitly generated prime label interfering with the subsequent recognition of the (phonologically related) target word.
+The authors suggested that the shift from facilitation to interference from 18 to 24 months they found in both studies might be the result of a developmental shift in which 18-month-olds' lexicon is not yet organised based on phonological similarity, while 24-month-olds' is.
+This would lead to the former showing a pre-lexical facilitation effect in which such facilitation occurs via the activation of phonological segments, while the latter would show an interference effect due to lateral links between lexical representation having been established.
+Both studies by Mani and Plunkett provide evidence of implicit naming of name-known pictures by 18-month old toddlers and older, and that the resulting labels interact with the dynamics of recognition of subsequently presented word-forms.
+
+Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
+@duta2012erp presented name-known pictures in silence for one second.
+After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
+In some trials the auditory label corresponded to a canonical realisation of the word-form.
+In other trials, the word was mispronounced.
+Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
+A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
+This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
+
+When extended to the bilingual case, this implicit naming task may offer bilingual participants with an uncontrained naming context in whcih the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
+Using an adaptation of @mani2010infant's implicit naming paradigm, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
+The authors presented German-English bilinguals with 120 prime-target pairs.
+Primes were presented as familiar pictures in silence.
+After prime picture offset, target words were presented auditorily.
+Participants' N400 ERP components were recorded from target word onset.
+The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
+When prime and target were phonologically identical (*Affe*-*Affe*, German for *monkey*), or similar (*Fahne*-*Sahne*, German for *flag* and *ice-cream*, respectively) within L1, participants' showed a reduced N400 amplitude, compared to when prime and target were phonologically unrelated (*Messer*-*Seil*, German for *knife* and *rope*).
+Critically, a similar effect was found when prime and target were phonologically related through translation (*Rustsche*-*Kleid*, German for *slide* and *dress*).
+This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
+
+Evidence from cognates.
+
+The role of cognates in lexical processing.
+
+This study also provides a more suitable design for drawing conslusions about developmental change in word recognition trajectories frot wo reasons.
+First, it extends the age range of participants, compared to previous studies.
+Second, participants were tested at three selected age points to ensure a more balanced sample size across ages.
+Third, the partially longitudinal design allows modelling the performance of participants across testing sessions altogether.
+
+. In order to circumvent the problem of limited vocabulary knowledge
+in the non-dominant language, we propose to test participants only in their dominant language, therefore
+directing our research to the question of how possessing a second language affects processing of the
+dominant one in bilingual toddlers [@costa2014does provide a fuller description of the
+advantages of such approach].
+
+## The present study
+
+The present study is aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
+Using an adaptation of [@mani2010infants], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
+We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
+If so, phonological priming effect should be larger when the prime label in  both languages shares phonological overlap with the target words (cognate condition), compared to when only the label of the prime in one language overlaps phonologically with the target (non-cognate condition).
+We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
+
+We compared the explanatory power of three measures of vocabulary size on participants' trajectories of word recognition: L1 vocabulary and total vocabulary.Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary]
+
+# Methods
+
+All materials, data, and reproducible code can be found at the OSF ([https://osf.io/hy984/](https://osf.io/ckydb/)) and GitHub ([https://github.com/gongcastro/cognate-priming](https://github.com/gongcastro/cognate-priming)) repositories.
+This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I.
+Before every testing session, caregivers were asked to read and sign an informed consent form, and were given a token of appreciation at the end of it.
+
+## Participants
 
 ```{r}
-1 + 1
+#| label: participants-numbers
+n_participants_total <- participants |> 
+	distinct(location, child_id) |> 
+	count(location)
+
+n_participants_sex <- participants |> 
+	distinct(location, sex, child_id) |> 
+	count(location, sex)
+
+n_participants_sessions <- count(participants,
+								 child_id,
+								 name = "n_sessions") |> 
+	count(n_sessions) |> 
+	group_split(n_sessions) |> 
+	set_names(paste0("session_", 1:3))
+
+n_sessions_total <- count(participants)
+
+n_sessions_lp <- participants |> 
+	summarise(across(age, lst(mean, sd, min, max)),
+			  n = n(),
+			  .by = c(lp)) |> 
+	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
+	group_split(lp) |> 
+	set_names(janitor::make_clean_names(unique(participants$lp)))
+
+n_sessions_dominance_lp <- count(participants, lp, test_language) |> 
+	group_split(test_language) |> 
+	set_names(c("catalan", "english", "spanish")) |> 
+	map(group_split, lp)
+
+n_sessions_lp <- participants |> 
+	count(lp) |> 
+	group_split(lp) |> 
+	set_names(c("monolingual_eng", "monolingual", "bilingual"))
 ```
 
-You can add options to executable code like this
+We collected data from `r n_participants_total$n[1]` participants living in the Metropolitan Area of Barcelona (Spain) tested at the Laboratori de recerca en Infància at the Universitat Pompeu Fabra (`r n_participants_sex$n[1]` female, `n_participants_sex$n[2]` male), and `r n_participants_total$n[2]` participants living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford (`r n_participants_sex$n[3]` female, `n_participants_sex$n[4]`, `n_participants_sex$n[5]` not reported).
+Families were recruited from maternity room in private hospitals or from social media, and contacted via phone when the child's age spanned between 20 and 32 months.
+From the `r sum(n_participants_total$n)` children that participated, `r n_participants_sessions$session_1$n` participated once, `r n_participants_sessions$session_2$n` participated twice, and `r n_participants_sessions$session_3$n` participated three times.
+Recurrent participants were tested with at least XXX months of difference.
+We gathered a total of `r n_sessions_total$n` testing sessions: `r n_sessions_lp$monolingual_english$n` from participants in Oxford, and `r n_sessions_lp$monolingual$n + n_sessions_lp$bilingual$n` from participants in Barcelona.
 
-```{r}
-#| echo: false
-2 * 2
+We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
+Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
+The output of this interview is an estimated degree of exposure (*DoE*) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
+According to this estimate, we classified participants as Catalan-, English-, or Spanish-dominant if the language with highest *DoE* was Catalan, English, or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
+From the `r n_sessions_total$n` testing sessions, `r n_sessions_lp$monolingual_english$n` belonged to English monolinguals,  `r n_sessions_lp$monolingual$n` to Catalan or Spanish monolinguals, and  `r n_sessions_lp$bilingual$n` to Catalan-Spanish bilinguals.
+@tbl-participants shows a detailed description of the linguistic profile of our sample.
+
+```{r tbl-participants}
+#| label: tbl-partiicpants
+#| tbl-cap: "Demographic and linguistic profile of participants."
+participants |> 
+	unnest_wider(doe) |> 
+	select(-matches("others")) |> 
+	mutate(lp = case_when(
+		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
+		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
+		.default = lp)) |> 
+	arrange(desc(lp)) |> 
+	summarise(n = n(),
+			  across(age, lst(mean, sd, min, max)),
+			  across(matches("doe_"), lst(mean, sd)),
+			  age_vctr = list(age),
+			  .by = c(lp, test_language)) |> 
+	gt(rowname_col = "test_language",
+	   groupname_col = "lp") |> 
+	gt_plt_dist(age_vctr, type = "histogram") |> 
+	fmt_number(is.numeric, decimals = 1) |> 
+	fmt_integer(n) |> 
+	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
+	cols_merge_range(age_min, age_max) |> 
+	cols_merge_uncert(age_mean, age_sd) |> 
+	cols_merge_uncert(doe_catalan_mean, doe_catalan_sd) |> 
+	cols_merge_uncert(doe_english_mean, doe_english_sd) |> 
+	cols_merge_uncert(doe_spanish_mean, doe_spanish_sd) |> 
+	tab_spanner("Age (months)", matches("age")) |> 
+	tab_spanner("Catalan", matches("catalan")) |> 
+	tab_spanner("English", matches("english")) |> 
+	tab_spanner("Spanish", matches("spanish")) |> 
+	tab_spanner("Degree of Exposure (%)", matches("doe")) |> 
+	cols_label(n = "N",
+			   age_mean = "M (SD)",
+			   age_min = "Range",
+			   age_vctr = "Distribution",
+			   doe_catalan_mean = "M (SD)",
+			   doe_english_mean = "M (SD)",
+			   doe_spanish_mean = "M (SD)") |> 
+	tab_style(cell_text(style = "italic"),
+			  cells_column_labels()) |> 
+	tab_style(cell_text(weight = "bold"),
+			  cells_column_spanners())
 ```
 
-The `echo: false` option disables the printing of code (only output is displayed).
+We collected data from `r n_participants_total` monolingual and bilingual participants living in the Metropolitan Area of Barcelona (Spain), who were exposed to at least Catalan and/or Spanish from birth.
+Families were recruited from maternity room in private hospitals in Barcelona, and contacted via phone when the child's age spanned between our age intervals of interest.
+Families were invited to participate at three age points: 21, 25, and 30 months.
+`r n_participants_sessions[[1]]$n` participants were tested at one age point,  `r n_participants_sessions[[2]]$n` at two age points, and `r n_participants_sessions[[3]]$n` at the three age points.
+In total, we gathered data from `r n_sessions_total$n` testing sessions: `r n_sessions_age_group$age_21$n` at 21 months (*Mean* = `r round(n_sessions_age_group$age_21$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_21$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_21$age_min`--`r n_sessions_age_group$age_21$age_max`), `r n_sessions_age_group$age_25$n` at 25 months (*Mean* = `r round(n_sessions_age_group$age_25$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_25$age_min`--`r n_sessions_age_group$age_25$age_max`), and `r n_sessions_age_group$age_30$n` at 30 months (*Mean* = `r round(n_sessions_age_group$age_30$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_30$age_min`--`r n_sessions_age_group$age_30$age_max`).
+
+Participants' vision was normal, none used glasses or any other type of vision corrector.
+
+### Language profile {#sec-lp}
+
+We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
+Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
+The output of this interview is an estimated degree of exposure (DoE) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
+According to this estimate, we classified participants as Catalan- or Spanish-dominant if the language with highest DoE was Catalan or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
+We collected data from `r n_sessions_dominance$catalan$n` Catalan-dominant participants in Catalan (`r n_sessions_dominance_age_group$catalan$age_21$n` at 21 months, `r n_sessions_dominance_age_group$catalan$age_25$n` at 25 months, and `r n_sessions_dominance_age_group$catalan$age_30$n` at 30 months).
+We further classified participants as monolinguals if the DoE to their dominant language exceeded 80% of the total DoE to Catalan and Spanish, and as bilinguals otherwise.
+Participants with DoE to language other than Catalan or Spanish were excluded from analyses.
+This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
+@tbl-participants-lp shows a detailed description of the linguistic profile of our sample.
+
+### Vocabulary size
+
+```{r vocab-values}
+n_imputed <- table(vocabulary$is_imputed)[2]
+prop_imputed <- scales::percent(n_imputed/nrow(vocabulary))
+n_pool <- nrow(bvq_data$vocabulary)
+```
+
+We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability] developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers.
+Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
+
+We calculated several measures of receptive vocabulary size from each participant's vocabulary: L1 vocabulary size (proportion of words  reported as acquired in the checklist of the dominant language), L2 vocabulary size (proportion of words  reported as acquired in the checklist of the non-dominant language), total vocabulary size (proportion of the words in both checklists reported as acquired), conceptual vocabulary (proportion of concepts for which the participant was reported to have acquired at least one label, in any language), and translation equivalent vocabulary (proportion of concepts for which the participant was reported to have acquired at two labels, one in each language).
+
+`r n_imputed` (`r prop_imputed`) Families failed to provide a complete response to the BVQ within the two-week time limit, or did not provide a successful response to the questionnaire.
+For missing questionnaire responses, we imputed the vocabulary size of the participant using single imputation, using the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
+We used participants age in months and their language profile (monolingual/bilingual) as predictors.
+We used the `mice` R package [@van2011mice] to perform imputation using the Bayesian linear regression method.
+
+```{r tbl-vocabulary}
+#| label: tbl-vocabulary
+#| tbl-cap: "Participant vocabulary sizes across ages and language profiles.
+Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
+Vocabulary size scores from the recurrent participants are shown linked."
+#| eval: false
+vocabulary |> 
+	inner_join(select(participants, child_id, session_id, age, lp),
+			   by = join_by(child_id, session_id)) |> 
+	pivot_longer(c(total_prop, l1_prop),
+				 names_to = "measure",
+				 values_to = "prop",
+				 names_transform = \(x) gsub("_prop", "", x)) |> 
+	mutate(lp = case_when(
+		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
+		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
+		.default = lp) |> 
+			factor(levels = c("Monolingual (English)",
+							  "Monolingual (Catalan or Spanish)",
+							  "Bilingual (Catalan-Spanish)")),
+		measure = if_else(measure=="l1", 
+						  "L1 vocabulary", 
+						  "Total vocabulary"),
+		is_imputed = if_else(is_imputed, "Imputed", "Observed") |> 
+			factor(levels = c("Observed", "Imputed"))) |> 
+	ggplot(aes(age, prop, colour = is_imputed)) +
+	facet_grid(measure ~ lp) +
+	geom_line(aes(group = child_id),
+			  alpha = 1/2,
+			  colour = "grey") +
+	geom_point() +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size (%)") +
+	theme(panel.grid = element_line(linetype = "dotted",
+									colour = "grey"),
+		  legend.position = "right",
+		  legend.title = element_blank())
+```
+
+## Stimuli
+
+```{r stimuli-values}
+n_words <- length(unique(with(stimuli, unlist(prime, target, distractor))))
+```
+
+We used `r n_words` distinct words included in the BVQ to create the stimuli lists.
+We created six stimuli lists: three in Catalan, and three in Spanish.
+Each list contained 32 trials, each involving a prime-target-distractor group.
+Each word played a role as either prime, *or* as target and distractor across the three lists in their corresponding language.
+For instance, the Catalan word *cadira* appeared as *prime* in the three lists, but never as *target* or *distractor*; the Catalan word *bici* appeared as *target* and *distractor* across the three lists, but never as a prime.
+Target-distractor pairings were held constant across the three lists in each language.
+For instance, in all Catalan lists the word *bici* was paired with the word *porta*.
+Target-distractor pairings were also yoked, so that each member of the same target-distractor pair appeared once as target and once as distractor in each list.
+For instance, the *bici*-*porta* paired appeared twice in each of the three Catalan lists: once with *bici* as target and *porta* as distractor, and once with *porta* as target and *bici* as distractor.
+This counterbalancing avoided participants encountering looking at the target word guided solely by that word having being named in a previous trial.
+Finally, prime words appeared only once in each list: each target-distractor pair was associated with a different prime word in both appearances.
+In each list, the same prime word was presented alongside a different target-distractor pair.
+For instance, the Catalan prime word *barret* was presented with the *bici*-*porta* target-distractor pair in one list, with the *bici*-*porta* pair in another list, and with *berenar*-*amanida* in the remaining list.
+The order of the trials was randomised across experimental session, so that each time a participant was tested, the order in which the prime-target-distractor was presented was randomised.
+Each participant was randomly assigned to one of the three lists in the corresponding language (their dominant language, see @sec-lp), and always the same list across their experimental sessions in the case of a recurrent participant.
+
+In 16 of the 32 trials of the same list (henceforth *related* trials), the prime and the target words were phonologically related, sharing phonological onset (at least first phoneme).
+In the other 16 trials (*unrelated* trials), prime and target did not share phonological onset.
+8 of the 16 *related* trials included a cognate prime (*cognate* trials), and the other 8 included a non-cognate trials (*non-cognate* trials).
+A prime word was considered cognate if its Catalan and Spanish translation shared phonological onset.
+Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
+Target and distractor word pairs were phonologically unrelated (did not share phonological onset).
+Some of them shared semantic features or a taxonomic relationship.
+This is the case of words associated with especially salient referents such as animals or food.
+To avoid infants guiding their gaze to these objects based on their saliency, we paired animals and food items together.
+The position of the target and distractor pictures (right or left) for each target-distractor pair was alternated, so that in one list the target would appear on the left, in another list it would appear on the right, and so on.
+
+We examined the overall equivalence of the three trial types by comparing them across three variables relating to the target word: lexical frequency, word prevalence, animacy
+@tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
+Lexical frequencies were extracted from the Catalan and Spanish corpora of the CHILDES database [@reference; @reference] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@reference; @reference].
+We defined word prevalence as the proportion of same-aged infants who were reported to understand the word in the BVQ database.
+
+### Auditory stimuli
+
+The auditory stimuli were natural exemplars of the selected target words, spoken by Catalan-Spanish proficient bilingual female speaker who was instructed to pronounce each word in a toddler-directed manner.
+Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
+We used the Audacity [@reference] and Praat [@boersma2001speak] to record and edit the audio files.
+The speaker was presented with a list of words in Catalan.
+The order of the words was pseudo-randomised, and each word was produced three times in a row before moving to the next word in the list.
+After going through all the words in the list, the speaker went through the word list again generating three tokens for each word, now in an inverse order (from bottom of the list to the top).
+We then repeated the same procedure for the list of Spanish words.
+The resulting audios were manually chunked into individual word-forms.
+For each of the six tokens produced for each word, the most adequate was selected for further processing.
+The audios were then transformed to stereo by duplicating them into two channels, denoised, and finally normalised.
+The mean duration of the final audios was `r round(mean(stimuli$duration[stimuli$test_language=="Catalan"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Catalan"]), 2)`) and `r round(mean(stimuli$duration[stimuli$test_language=="Spanish"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Spanish"]), 2)`) seconds for the Catalan and Spanish lists.
+
+To make the pronunciation of the words as familiar as possible to each infant, we generated additional pronunciation variants for some words in Catalan and Spanish.
+Catalan words involving the /\textipa{L}/ phoneme in their Central Catalan variant (e.g., /\textipa{'Lu.n@}) were also recorded with such phoneme replaced by /j/ (e.g., /\textipa{'ju.n@}), a phonological process common in the Metropolitan Area of Barcelona [@reference].
+Spanish words involving the /\textipa{T}/ phoneme were also generated replacing such phoneme with /\textipa{s}/ to better accommodate Latin variants of Spanish.
+Before every experimental session, caregivers were asked to utter three written words involving the /\textipa{L}/ phoneme (in the case of participants tested in Catalan) or the /\textipa{T}/ phoneme (in the case of participants tested in Spanish).
+Each token contained the critical phoneme at onset, inter-vocalic position, and coda.
+The experimenter assigned the participant to the Catalan or Spanish stimuli list involving the closest variant to that of caregivers'.
+
+### Visual stimuli
+
+For each word, we created a picture with a typical referent.
+To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias-trejo2010].
+
+```{r tbl-stimuli}
+#| label: tbl-stimuli
+#| tbl-cap: "Summary of stimuli properties by trial type."
+stimuli |> 
+	summarise(across(c(matches("familiarity_|freq_|animate_"), duration),
+					 tibble::lst(mean, sd, min, max)),
+			  .by = c(test_language, trial_type)) |> 
+	select(-matches("familiarity_se"), -matches("prime"),
+		   -c(is_animate_target_sd,
+		      is_animate_target_min,
+		      is_animate_target_max),
+		   -matches("min"), -matches("max")) |> 
+	gt(groupname_col = "test_language",
+	   rowname_col = "list") |> 
+	fmt_number(is.numeric,
+			   decimals = 1) |> 
+	fmt_number(matches("familiarity|animate"),
+			   scale_by = 100,
+			   decimals = 1) |> 
+	cols_merge(c(freq_target_mean, freq_target_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(familiarity_target_mean, familiarity_target_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(duration_mean, duration_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_label(trial_type = "",
+			   familiarity_target_mean = "Prevalence (%)",
+			   freq_target_mean = "Frequency",
+			   is_animate_target_mean = "Animacy (%)",
+			   duration_mean = "Duration (s)") 
+```
+
+## Procedure
+
+Testing took place in a sound-proof room.
+Participants sat on their caregivers' lap in a dimly lit testing booth while the experimenter conducted the experiment from outside.
+Caregivers were instructed to keep their eyes shut (to avoid recording their gaze, instead of the participant's), to be still, and to avoid interacting with the participant verbally or non-verbally.
+Participants sat at approximately 65 cm from the eye-tracker and a XX-in screen of $1929\times1080$ screen resolution.
+We used a custom Matlab XXXX script using the PsychToolbox XXX extension [@brainard] to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
+Sampling rate was set at 120 Hz.
+A 5-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
+We set a 55% grey background for the calibration and stimuli presentation.
+Auditory stimuli were presented through two loudspeakers located behind the screen, one to each side.
+The experimenter monitored the experimental from outside the room using a centrally located video camera place above the screen.
+After a successful calibration the experimenter triggered the onset of the first trial.
+Trials were presented uninterruptedly and  without intervention of the experimenter until the 32 trials were presented, or the experimental session had to be stopped because of the participant's behaviour.
+
+![Experimental task design with examples in Catalan.
+In each trial, the prime image is presented in silence for 3,000 ms.
+The the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
+In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
+In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
+In unrelated trials (*n* = 32), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){fig-align="center"}
+
+Each trial started with the presentation of an attention getter for 3,000 milliseconds.
+Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
+Fifty milliseconds after the offset of the prime image, an auditory label was played from the loudspeakers and, 700 milliseconds after the onset of the auditory label, the target and distractor pictures were presented side-by-side during 1,000 milliseconds until the end of the trial.
+After this, the attention getter of the next trial was immediately presented.
+Each experimental session took approximately 10 minutes.
+
+## Apparatus
+
+see https://link.springer.com/article/10.3758/s13428-021-01762-8
+
+## Data processing
+
+```{r dataset}
+n_trials <- nrow(attrition)
+n_sessions <- n_distinct(attrition$session_id)
+n_participants <- n_distinct(attrition$child_id)
+n_trials_valid <- nrow(filter(attrition,
+							  is_valid_participant,
+							  is_valid_trial))
+n_sessions_valid <- sum(attrition_participants$is_valid_participant)
+n_participants_valid <- n_distinct(
+	attrition[attrition$is_valid_participant, ]$child_id)
+
+n_exc_prime <- sum(!attrition$is_valid_gaze_all_prime)
+n_exc_test <- sum(!attrition$is_valid_gaze_all_test)
+n_exc_test_each <- sum(!attrition$is_valid_gaze_all_test_each)
+n_exc_vocab <- sum(!attrition$is_valid_vocab)
+n_exc_participants <- sum(!attrition_participants$is_valid_participant)
+
+n_longitudinal <- attrition |>
+	filter(is_valid_participant,
+		   is_valid_trial) |>
+	distinct(child_id, session_n) |> 
+	count(child_id, name = "times") |> 
+	count(times)
+```
+
+We defined a time windows of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
+To avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
+Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
+We excluded trials in which participants failed to provide 50%  valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target-looking *and* distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
+Finally, we excluded trials in which participants did not understand the prime *or* the target word, according to a supplementary vocabulary checklist filled by their caregivers upon experiment completion (*n* = `r format(n_exc_vocab, big.mark = ",")`).
+After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`).
+The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+@tbl-attrition-trials shows a detailed description of the trial attrition.
+
+```{r tbl-attrition}
+#| label: tbl-attrition
+#| tbl-cap: "Participant-level and trial-level sample size after applying inclusion criteria. The number of excluded participants and trials is indicated between parentheses."
+expanded <- expand(attrition, lp, trial_type, is_valid_trial)
+
+n_lp <- attrition |> 
+	distinct(is_valid_participant, lp, session_id) |> 
+	count(is_valid_participant, lp) |> 
+	pivot_wider(names_from = is_valid_participant,
+				values_from = n,
+				names_repair = janitor::make_clean_names) |> 
+	mutate(n_participants_true = true,
+		   n_participants_false = false) |> 
+	select(lp, true, false)
+
+attrition |> 
+	summarise(n_trials_true = sum(is_valid_trial),
+			  n_trials_false = sum(!is_valid_trial),
+			  .by = c(lp, trial_type)) |> 
+	arrange(desc(lp)) |> 
+	# across(n_trials, lst(mean, sd, sum), na.rm = TRUE),
+
+	pivot_wider(id_cols = lp,
+				names_from = c(trial_type),
+				values_from = matches("trials"),
+				names_repair = janitor::make_clean_names) |> 
+	left_join(n_lp, by = join_by(lp)) |> 
+	mutate(lp = case_when(
+		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
+		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
+		.default = lp)) |>
+	select(lp, true, false,
+		   matches("n_trials")) |> 
+	gt(rowname_col = "lp") |> 
+	tab_spanner("Participants", matches("participant")) |> 
+	tab_spanner("Trials", matches("trial")) |> 
+	fmt_integer(everything()) |> 
+	cols_merge(c(true, false),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(n_trials_true_cognate,
+				 n_trials_false_cognate),
+				 pattern = "{1} ({2})") |> 
+	cols_merge(c(n_trials_true_non_cognate,
+				 n_trials_false_non_cognate),
+				 pattern = "{1} ({2})") |> 
+	cols_merge(c(n_trials_true_unrelated, 
+				 n_trials_false_unrelated),
+				 pattern = "{1} ({2})") |> 
+	cols_label(true = "N", 
+			   n_trials_true_cognate = "Cognate",
+			   n_trials_true_non_cognate = "Non-cognate",
+			   n_trials_true_unrelated = "Unrelated") |> 
+	tab_style(cell_text(style = "italic"),
+			  cells_column_labels()) |>
+	grand_summary_rows(fns = list(label = md("*N*")) ~ sum(.),
+					   fmt = ~ fmt_integer(.))
+```
+
+## Data analysis
+
+We conducted two main analyses.
+In the first analysis, we estimated the effect of phonological priming on participants' target looking comparing *related* trials---in which prime and target share phonological onset, and the prime was not a cognate word---with *unrelated* trials---in which prime and target did not share phonological onset, and neither was the prime a cognate word, leaving out *cognate* trials.
+This analysis included all trials on the data set.
+Second, we estimated the effect of cognateness on phonological priming, comparing *cognate* trials---in which prime and target shared phonological onset, and the prime was a cognate word that also shared phonological onset with the target, with *non-cognate* trials---in which prime a target shared phonological onset, and the prime was not a cognate---, leaving out *unrelated* trials.
+
+In both analyses, we modelled the probability of target looking across the time course of the trial.
+For each trial, we chunked the time domain of the target-distractor phase into 20 time bins of 100 ms of duration.
+We then calculated, for each experimental session, time bin, and condition, the number of eye-tracker samples in which the participant was looking to the target and the distractor pictures.
+Finally, we computed the empirical logit of target fixations using @eq-elogit [@barr2008analyzing; @agresti2012categorical], which modelled in our analyses using a Gaussian distribution.
+
+$$
+\eta' = \ln\bigg(\frac{\text{Target} + 0.5}{ \text{Distractor} + 0.5}\bigg)
+$$ {#eq-elogit}
+
+In the first analysis, we included *Relatedness* (`Related` vs.
+`Unrelated`, sum-coded as `-0.5` and `+0.5`), *Group* (`Monolingual` vs.
+`Bilingual`, sum-coded as `-0.5` and `+0.5`), and *Age* (participants' standardised age in months) as fixed, main effects, together with their two- and three-way interactions.
+We used multilevel General Additive Mixed Models (GAMMs) to model the time course of target looking, including cubic regression splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
+For both splines, we specified $k = 10$ basis functions or *knots*--half the number of time bins---for computational convenience.
+Finally, we added by-participant random intercepts, and random slopes for the main effect of *Relatedness* and the main effect of *Age*, both including repeated measures per participant [@pedersen2019hierarchical].
+In the second analysis, we included *Cognateness* (`Cognate` vs.
+`Non-cognate`, sum-coded as `-0.5` and `+0.5`) replacing *Relatedness*.
+@eq-model shows the formal implementation of the model.
+
+To test the contribution of each of the predictors of interest--*Relatedness*/*Cognateness*, and *Group*--, we compared each model ($\mathcal{M_0}$) against a simplified model dropping each of the main effects, *Relatedness*/*Cognateness* ($\mathcal{M}_1$) or *Group* ($\mathcal{M_2}$).
+In both simplified models, the interaction term was dropped.
+We used leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it.
+We then examined the posterior predictions of the best-performing model for interpretation.
+
+$$
+\begin{aligned}
+\textbf{Likelihood:} \\
+y_i &\sim \mathcal{N}(\mu_i, \sigma_i) \\ \\
+\textbf{Linear model:} \\
+\eta'(\mu_i) &= (\beta_0 + u _{0_{i}}) + (\beta_1 + u _{1_{i}}) \cdot \text{[Condition]} +\\
+&\beta_{2} \cdot \text{Group} + \beta_{3} \cdot (\text{[Condition]} \times \text{Group}) +\\
+& (\beta_4 + u_{2_{i}}) \cdot \text{Age} + \sum_{j = 1}^k b_{j_{1}} \cdot \beta_{5_{k}} \cdot \text{Time} + \sum_{j = 1}^k b_{j_{1}} \cdot\beta_{6_{k}} \cdot (\text{Time} \times \text{Group}) \\
+\text{where:} \\
+&\eta'\text{ is the empirical logit of target fixations} \\
+& \text{[Condition] should be replaced with } Relatedness \text{ or } Cognateness \\
+&k \text{ is the number of knots in the spline (10)} \\
+\textbf{Prior:} \\
+\beta_{0-6} &\sim \mathcal{N}(0, 0.5) \\
+u_{0-2} &\sim \mathcal{N}(0, \sigma_{0-2})\\
+b_{0-1} &\sim \text{MVN}(0, \tau_{0-1}) \\
+\sigma_{0-2}, \tau_{0-1} &\sim \text{Exponential}(6)\\
+\rho_{0-2} &\sim LKJCorr(6)\\
+\text{where:}\\
+&\rho_{0-2} \text{ are the correlation parameters for } \sigma_{0-2}
+\end{aligned}
+$$ {#eq-model}
+
+# Results
+
+## Preliminary analyses
+
+```{r fig-ptlt-recognition}
+#| label: fig-ptlt-recognition-aggr
+#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+data_time |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(lp, timebin, session_id)) |> 
+	ggplot(aes(timebin, .prop, colour = lp)) +
+	facet_wrap(~lp, nrow = 1, scales = "free_x") +
+	geom_line(aes(group = session_id),
+			  # colour = "grey",
+			  alpha = 1/10) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	stat_summary(fun.data = "mean_se",
+				 geom = "errorbar",
+				 width = 0.35,
+				 linewidth = 2/4) +
+	stat_summary(fun = "mean",
+				 geom = "point",
+				 size = 1.2) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 linewidth = 2/4) +
+	labs(x = "Time (ms)",
+		 y = "PTLT") +
+	scale_x_continuous(breaks = seq(0, 20, 2),
+					   labels = \(x) format(x*100+300, big.mark = ",")) +
+	scale_y_continuous(labels = scales::percent,
+					   breaks = seq(0, 1, 0.2),
+					   limits = c(0, 1)) +
+	theme(panel.grid.major.y = element_line(colour = "grey",
+											linetype = "dotted"),
+		  legend.position = "none")
+```
+
+```{r fig-ptlt-recognition-age}
+#| label: fig-ptlt-recognition-age
+#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+data_time |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(lp, timebin, age_group, session_id)) |> 
+	ggplot(aes(timebin, .prop, colour = age_group)) +
+	facet_wrap(~lp, nrow = 1, scales = "free_x") +
+	# geom_rug(aes(x = timebin[is.na(.prop)])) +
+	# geom_line(aes(group = session_id),
+	# 		  alpha = 1/8) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	stat_summary(fun.data = "mean_se",
+				 geom = "errorbar",
+				 width = 0.35,
+				 linewidth = 2/4) +
+	stat_summary(fun = "mean",
+				 geom = "point",
+				 size = 1.2) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 linewidth = 2/4) +
+	labs(x = "Time (ms)",
+		 y = "PTLT",
+		 colour = "Age") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	scale_y_continuous(labels = scales::percent,
+					   breaks = seq(0, 1, 0.05)) +
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+```
+
+```{r fig-ptlt-recognition-condition}
+#| label: fig-ptlt-recognition-condition
+#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
+data_time |> 
+	summarise(.prop = mean(.prop),
+			  .by = c(lp, timebin, condition, session_id)) |> 
+	ggplot(aes(timebin, .prop, colour = condition)) +
+	facet_grid(~lp) +
+	# geom_rug(aes(x = timebin[is.na(.prop)])) +
+	# geom_line(aes(group = interaction(condition, session_id)),
+	# 		  alpha = 1/8) +
+	geom_hline(yintercept = 0.5, linetype = "dashed") +
+	stat_summary(fun.data = "mean_se",
+				 geom = "errorbar",
+				 width = 0.35,
+				 linewidth = 2/4) +
+	stat_summary(fun = "mean",
+				 geom = "point",
+				 size = 1.2) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 linewidth = 2/4) +
+	labs(x = "Time (ms)",
+		 y = "PTLT",
+		 colour = "Condition") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	scale_y_continuous(labels = scales::percent,
+					   breaks = seq(0, 1, 0.05)) +
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+```
+
+## Aggregated analysis
+
+In a first analysis, we examined the effect of phonological priming.
+We compared participants' looking preference for the target in related and unrelated trials.
+We first compared the aggregated probability of target looking across time bins in both conditions for each language group.
+
+```{r fig-related-aggregated}
+#| label: fig-related-aggregated
+#| fig-cap: "A) Aggregated probability of target looking for related and unrelated trials.
+Each point represents the mean probability of target looking for one participant in one testing session.
+Lines link observations from the same testing session across conditions.
+Black dots and errorbars indicate the mean and 95% CrI.
+B) Aggregated probability of target looking across ages for related and unrelated trials.
+Lines and error bands indicate the mean and standard error of the mean."
+plot_agg_epreds <- function(newdata, object) {
+
+	epreds <- add_epred_draws(newdata = newdata,
+							  object = object,
+							  re_formula = NA)
+	return(mean_qi(epreds))
+}
+
+voc_values <- c(0.25, 0.5, 0.75, 1.00)
+age_values <- c(21, 25, 30)
+
+nd_0 <- expand(data_aggr, lp, condition, age = age_values)
+nd_1 <- expand(data_aggr, lp, condition, voc_l1 = voc_values)
+nd_2 <- expand(data_aggr, lp, condition, voc_total = voc_values)
+
+epreds <- map2(.x = list(nd_0, nd_1, nd_2),
+			   .y = model_fits_aggr,
+			   .f = plot_agg_epreds) |> 
+	map(\(x) {
+		mutate(x, 
+			   across(matches("voc"),
+			   	   \(x) factor(x = x, 
+			   	   			levels = voc_values,
+			   	   			labels = scales::percent(voc_values))),
+			   across(matches("age"),
+			   	   \(x) factor(x = x,
+			   	   			levels = age_values,
+			   	   			labels = age_values)))
+	}) |> 
+	map(\(x) rename_with(x, \(x) gsub("age|voc_total|voc_l1", "var", x))) |> 
+	set_names(names(model_fits_aggr))
+
+plot_epreds <- function(data, x) {
+	data |> 
+		ggplot(aes(var, .epred, 
+				   colour = condition,
+				   fill = condition)) +
+		facet_wrap(~lp, scales = "free_x") +
+		geom_hline(yintercept = 0,
+				   linetype = "dashed") +
+		geom_errorbar(aes(ymin = .lower,
+						  ymax = .upper),
+					  width = 0.5,
+					  linewidth = 3/4,
+					  position = position_dodge(width = 0.5)) +
+		geom_point(position = position_dodge(width = 0.5),
+				   size = 2)
+}
+
+plot_epreds(epreds$fit_aggr_0) +
+	labs(x = "Age (months)") +
+	plot_epreds(epreds$fit_aggr_1) +
+	labs(x = "L1 vocabulary size") +
+	theme(strip.text = element_blank()) +
+	plot_epreds(epreds$fit_aggr_2) +
+	theme(strip.text = element_blank()) +
+	labs(x = "Total vocabulary size") +
+	plot_layout(ncol = 1, guides = "collect") &
+	labs(y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition") &
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+
+```
+
+## Time course analysis
+
+```{r fig-time}
+#| label: fig-time
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+nd <- expand_grid(condition = levels(model_fits_time$fit_time_2$data$condition),
+				  timebin = seq(0, 17, length.out = 100),
+				  voc_total = mean(model_fits_time$fit_time_2$data$voc_total),
+				  # sesion_id = first(data$session_id),
+				  # age = c(21, 25, 30),
+				  lp = levels(model_fits_time$fit_time_2$data$lp))
+
+epreds <- add_epred_draws(newdata = nd,
+						  object = model_fits_time$fit_time_2,
+						  ndraws = 20,
+						  re_formula = NA,
+						  value = ".value") |> 
+	mean_qi() |> 
+	mutate(lp = factor(lp, 
+					   levels = c("Monolingual (English)",
+					   		   "Monolingual",
+					   		   "Bilingual")))
+
+epreds |> 
+	ggplot(aes(timebin, .value,
+			   colour = condition,
+			   fill = condition)) +
+	facet_wrap(~lp) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	geom_ribbon(aes(ymin = .lower, ymax = .upper),
+				alpha = 0.5,
+				linewidth = 0) +
+	geom_line(linewidth = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	theme(legend.position = "top",
+		  panel.grid.major = element_line(colour = "grey",
+		  								linetype = "dotted"))
+```
+
+```{r fig-time-total}
+#| label: fig-time-total
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+voc_values <- seq(0.25, 1, 0.25)
+
+nd <- expand_grid(condition = levels(model_fits_time$fit_time_2$data$condition),
+				  timebin = seq(0, 17, length.out = 100),
+				  voc_total = voc_values,
+				  # sesion_id = first(data$session_id),
+				  # age = c(21, 25, 30),
+				  lp = levels(model_fits_time$fit_time_2$data$lp))
+
+epreds <- add_epred_draws(newdata = nd,
+						  object = model_fits_time$fit_time_2,
+						  ndraws = 20,
+						  re_formula = NA,
+						  value = ".value") |> 
+	mean_qi() |> 
+	mutate(lp = factor(lp, 
+					   levels = c("Monolingual (English)",
+					   		   "Monolingual",
+					   		   "Bilingual")),
+		   voc_total = factor(x = voc_total, 
+		   				   levels = voc_values,
+		   				   labels = scales::percent(voc_values)))
+
+epreds |> 
+	ggplot(aes(timebin, .value,
+			   colour = condition,
+			   fill = condition)) +
+	facet_grid(lp~voc_total) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	geom_ribbon(aes(ymin = .lower, ymax = .upper),
+				alpha = 0.5,
+				linewidth = 0) +
+	geom_line(linewidth = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	theme(legend.position = "top",
+		  panel.grid.major = element_line(colour = "grey",
+		  								linetype = "dotted"))
+```
+
+{{< pagebreak >}}
+
+# Discussion
+
+## Summary
+
+## Context
+
+## Facilitation vs. inhibition
+
+## Onsets vs. offsets
+
+## Problems and generalisatility
+
+## Future steps
+
+## Conclusions
+
+# References
+
+{{< pagebreak >}}
+
+# Appendix
+
+## Appendix A: imputing voabulary size scores
+
+```{r fig-vocabulary-imputation}
+vocabulary_tmp <- vocabulary |> 
+	left_join(select(participants, child_id, vocab_id, age),
+			  by = join_by(child_id, vocab_id)) |> 
+	relocate(child_id) |> 
+	filter(is_imputed)
+
+bvq_data$vocabulary |> 
+	inner_join(distinct(bvq_data$logs, child_id, response_id, lp, age),
+			   by = join_by(response_id)) |> 
+	mutate(is_imputed = FALSE) |> 
+	bind_rows(vocabulary_tmp) |> 
+	pivot_longer(ends_with("_prop"),
+				 names_to = "measure",
+				 values_to = "prop") |> 
+	drop_na(prop) |> 
+	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"),
+		   measure = factor(measure,
+		   				 levels = c("total_prop",
+		   				 		   "l1_prop",
+		   				 		   "l2_prop",
+		   				 		   "concept_prop",
+		   				 		   "te_prop"),
+		   				 labels = c("Total",
+		   				 		   "L1",
+		   				 		   "L2",
+		   				 		   "Conceptual",
+		   				 		   "TE"))) |> 
+	ggplot(aes(age, prop, 
+			   colour = is_imputed,
+			   fill = is_imputed)) +
+	facet_wrap(~measure) +
+	geom_point(alpha = 1/4, size = 1) +
+	geom_smooth(method = "glm", 
+				formula = "y ~ x",
+				method.args = list(family = "binomial"), 
+				# se = FALSE,
+				size = 1) +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size",
+		 fill = "Imputed",
+		 colour = "Imputed") +
+	theme(legend.position = c(1, 0),
+		  legend.justification = c(1, 0),
+		  legend.title = element_blank())
+
+```
+
+{{< pagebreak >}}
+
+## Appendix B: distribution of prime and target looking times
+
+```{r fig-dist-prime}
+#| label: fig-dist-prime
+#| fig-height: 4
+#| fig-width: 8
+looking_times |> 
+	mutate(prime_time = cut(prime_time, 
+							seq(0, 1.5, 0.1),
+							labels = FALSE,
+							include.lowest = TRUE)) |> 
+	add_count(lp, age_group, name = "n_total") |> 
+	count(lp, age_group, prime_time, n_total) |> 
+	mutate(n = n / n_total) |> 
+	ggplot(aes(prime_time, n)) +
+	facet_grid(lp~age_group) +
+	annotate(geom = "rect",
+			 fill = "orange",
+			 ymin = -Inf,
+			 ymax = Inf,
+			 xmin = 0,
+			 xmax = 0.75*10,
+			 alpha = 1/3,
+			 colour = NA) +
+	# annotate(label = "Excluded trials",
+	# 		 geom = "text",
+	# 		  x = (0.75/2)*10,
+	# 		  y = 1)
+	geom_col(fill = "black") +
+	labs(x = "Prime looking time (s)",
+		 y = "Proportion of trials") +
+	scale_x_continuous(labels = \(x) x/10) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"))
+```
+
+```{r fig-dist-target}
+#| label: fig-dist-target
+#| fig-height: 4
+#| fig-width: 8
+looking_times |> 
+	mutate(target_time = cut(target_time, 
+							 seq(0, 2, 0.1),
+							 labels = FALSE,
+							 include.lowest = TRUE)) |> 
+	add_count(lp, age_group, name = "n_total") |> 
+	count(lp, age_group, target_time, n_total) |> 
+	mutate(n = n / n_total) |> 
+	ggplot(aes(target_time, n)) +
+	facet_grid(lp~age_group) +
+	# annotate(label = "Excluded trials",
+	# 		 geom = "text",
+	# 		  x = (0.75/2)*10,
+	# 		  y = 1)
+	geom_col(fill = "black") +
+	labs(x = "Targets looking time (s)",
+		 y = "Proportion of trials") +
+	scale_x_continuous(labels = \(x) x/10) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"))
+```
+
+{{< pagebreak >}}
+
+## Appendix C: prime and test looking times
+
+```{r fig-looking-times}
+#| label: fig-looking-times
+#| fig-height: 8
+#| fig-width: 8
+#| fig-cap: "Looking time (s) to the prime and target AOI against audio duration. In longer audios, participants are expected to look longer to the prime and target picture."
+
+looking_times |>
+	left_join(select(attrition_trials, 
+					 filename, trial, is_valid_trial),
+			  by = join_by(filename, trial)) |>
+	filter(is_valid_trial) |> 
+	ggplot(aes(duration,
+			   prime_time,
+			   colour = trial_type, 
+			   fill = trial_type,
+			   shape = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_point(alpha = 0.5, 
+			   size = 1) +
+	geom_smooth(method = "lm") +
+	theme(axis.title.x = element_blank()) +
+
+	looking_times |>
+	left_join(select(attrition_trials, 
+					 filename, trial, is_valid_trial),
+			  by = join_by(filename, trial)) |>
+	filter(is_valid_trial) |> 
+	ggplot(aes(duration,
+			   target_time,
+			   colour = trial_type, 
+			   fill = trial_type,
+			   shape = trial_type)) +
+	facet_grid(lp~age_group) +
+	geom_point(alpha = 0.5,
+			   size = 1) +
+	geom_smooth(method = "lm",
+				formula = "y ~ x") +
+	plot_layout(ncol = 1, guides = "collect") &
+	plot_annotation(tag_levels = "A") &
+	labs(x = "Audio duration (s)",
+		 y = "Looking time (1.0-2.0 seconds)",
+		 colour = "Prime type",
+		 fill = "Prime type",
+		 shape = "Prime type") 
+```
+
+## Appendix D: vocabulary checklist validity
+
+```{r fig-validity-target}
+get_data(gaze = gaze,
+		 participants = participants,
+		 stimuli = stimuli,
+		 vocabulary = vocabulary,
+		 attrition_trials = attrition_trials,
+		 attrition_participants = attrition_participants,
+		 time_subset = c(0, 2),
+		 contrast = "related",
+		 is_valid_vocab_all,
+		 clean = FALSE) |> 
+	unnest_wider(is_valid_vocab_all) |>
+	select(session_id, lp, .elog, target) |> 
+	arrange(session_id, target) |> 
+	summarise(.elog_mean = mean(.elog),
+			  .elog_sd = sd(.elog),
+			  n = n(),
+			  .by = c(lp, target)) |> 
+	mutate(target = ifelse(target, "Yes", "No"),
+		   .elog_se = .elog_sd/sqrt(n),
+		   .elog_lower = .elog_mean - .elog_se*1.96,
+		   .elog_upper = .elog_mean + .elog_se*1.96,
+	) |> 
+	ggplot(aes(lp, .elog_mean, 
+			   ymin = .elog_lower,
+			   ymax = .elog_upper,
+			   colour = target)) +
+	facet_wrap(~lp, ncol = 1, scales = "free_x") +
+	geom_errorbar(width = 0.2, linewidth = 3/4, 
+				  position = position_dodge(width = 0.25)) +
+	geom_point(size = 2,
+			   position = position_dodge(width = 0.25)) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	labs(x = "Condition",
+		 y = "P(Target looking)", 
+		 colour = "Knows the target word") +
+	theme(legend.position = "none",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted")) +
+
+	get_data_time(gaze = gaze,
+				  participants = participants,
+				  stimuli = stimuli,
+				  vocabulary = vocabulary,
+				  attrition_trials = attrition_trials,
+				  attrition_participants = attrition_participants,
+				  time_subset = c(0, 2),
+				  contrast = "related",
+				  is_valid_vocab_all,
+				  clean = FALSE) |> 
+	unnest_wider(is_valid_vocab_all) |>
+	select(session_id, age, lp, timebin, .elog, target) |> 
+	arrange(session_id, target) |> 
+	summarise(.elog_mean = mean(.elog),
+			  .elog_sd = sd(.elog),
+			  n = n(),
+			  .by = c(timebin, lp, target)) |> 
+	mutate(target = ifelse(target, "Yes", "No"),
+		   .elog_se = .elog_sd/sqrt(n),
+		   .elog_lower = .elog_mean - .elog_se*1.96,
+		   .elog_upper = .elog_mean + .elog_se*1.96,
+	) |> 
+	ggplot(aes(timebin, .elog_mean,
+			   ymin = .elog_lower,
+			   ymax = .elog_upper,
+			   colour = target,
+			   fill = target)) +
+	facet_wrap(~lp, ncol = 1, scales = "free_x") +
+	geom_line(linewidth = 1/2) +
+	geom_ribbon(alpha = 1/2,
+				colour = NA) +
+	geom_point(size = 2) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	labs(x = "Condition",
+		 y = "P(Target looking)", 
+		 fill = "Knows the target word",
+		 colour = "Knows the target word") +
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"),
+		  axis.title.y = element_blank(),
+		  axis.line.x = element_line()) +
+
+	plot_layout(ncol = 2,
+				widths = c(0.2, 0.8)) &
+	scale_y_continuous(limits = c(-0.5, 1.25))
+```

### 2023-11-03 manuscript/_appendix/_looking-time-distributions.qmd
Add results and exploratory analysis

--- 2023-09-12 manuscript/test.qmd
@@
----
-project:
-  render:
-    - manuscript.qmd
+## Appendix B: distribution of prime and target looking times
 
-format:
-  pdf:
-    keep-tex: true  
-    linenumbers: true
-    doublespacing: false
-    include-in-header: 
-      text: |
-        \usepackage{tipa}
-        \usepackage{booktabs}
-        \hyphenpenalty=100000
-        \exhyphenpenalty=100000
-    knitr:
-      opts_chunk:
-        dev: "cairo_pdf"
-    filters: 
-      - "_extensions/andrewheiss/wordcount/citeproc.lua"
-      - "_extensions/andrewheiss/wordcount/wordcount.lua"
-
-title: "Developmental trajectories of bilingual word recognition"
-short-title: "Developmental trajectories of bilingual word recognition"
-author:
-  - name: Gonzalo Garcia-Castro
-    corresponding: true
-    orcid: 0000-0002-8553-4209
-    email: gonzalo.garciadecastro@upf.edu
-    affiliations:
-      - id: cbc
-        name: Universitat Pompeu Fabra
-        department: Center for Brain and Cognition
-        city: Barcelona, 08005
-  - name: Serene Siow
-    orcid: 0000-0001-6482-2191
-    email: siow.serene@gmail.com
-    affiliations: 
-      - id: oxf
-        name: University of Oxford
-        department: Department of Experimental Psychology
-        city: Oxford, OX2 6GG
-  - name: Nuria Sebastian-Galles
-    orcid: 0000-0001-6938-2498
-    email: nuria.sebastian@upf.edu
-    affiliations: 
-      - ref: cbc
-  - name: Kim Plunkett
-    orcid: 0000-0003-0216-7480
-    email: kim.plunkett@psy.ox.ac.uk
-    affiliations: 
-      - ref: oxf
-keywords:
-  - cognate
-  - word recognition
-  - lexicon
-  - language acquisition
-  - vocabulary
-  - bilingualism
-  - general additive mixed models
-  - bayesian
-csl: "../assets/apa7.csl"
-bibliography: "../assets/references.bib"
-link-citations: true
-editor: source
-lang: en
-freeze: true
-fig-dpi: 1000
----
-
-## Quarto
-
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
-
-## Running Code
-
-When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
-
-```{r}
-1 + 1
+```{r fig-dist-prime}
+#| label: fig-dist-prime
+#| fig-height: 4
+#| fig-width: 8
+looking_times |> 
+	mutate(prime_time = cut(prime_time, 
+							seq(0, 1.5, 0.1),
+							labels = FALSE,
+							include.lowest = TRUE)) |> 
+	add_count(lp, age_group, name = "n_total") |> 
+	count(lp, age_group, prime_time, n_total) |> 
+	mutate(n = n / n_total) |> 
+	ggplot(aes(prime_time, n)) +
+	facet_grid(lp~age_group) +
+	annotate(geom = "rect",
+			 fill = "orange",
+			 ymin = -Inf,
+			 ymax = Inf,
+			 xmin = 0,
+			 xmax = 0.75*10,
+			 alpha = 1/3,
+			 colour = NA) +
+	# annotate(label = "Excluded trials",
+	# 		 geom = "text",
+	# 		  x = (0.75/2)*10,
+	# 		  y = 1)
+	geom_col(fill = "black") +
+	labs(x = "Prime looking time (s)",
+		 y = "Proportion of trials") +
+	scale_x_continuous(labels = \(x) x/10) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"))
 ```
 
-You can add options to executable code like this
-
-```{r}
-#| echo: false
-2 * 2
+```{r fig-dist-target}
+#| label: fig-dist-target
+#| fig-height: 4
+#| fig-width: 8
+looking_times |> 
+	mutate(target_time = cut(target_time, 
+							 seq(0, 2, 0.1),
+							 labels = FALSE,
+							 include.lowest = TRUE)) |> 
+	add_count(lp, age_group, name = "n_total") |> 
+	count(lp, age_group, target_time, n_total) |> 
+	mutate(n = n / n_total) |> 
+	ggplot(aes(target_time, n)) +
+	facet_grid(lp~age_group) +
+	# annotate(label = "Excluded trials",
+	# 		 geom = "text",
+	# 		  x = (0.75/2)*10,
+	# 		  y = 1)
+	geom_col(fill = "black") +
+	labs(x = "Targets looking time (s)",
+		 y = "Proportion of trials") +
+	scale_x_continuous(labels = \(x) x/10) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"))
 ```
 
-The `echo: false` option disables the printing of code (only output is displayed).
+{{< pagebreak >}}

### 2023-11-03 manuscript/_appendix/_vocabulary-validity.qmd
Add results and exploratory analysis

--- 2023-11-01 manuscript/manuscript.qmd
@@
----
----
-
-```{r setup}
-#| label: setup
-#| echo: false
-#| message: false
-#| warning: false
-# load objects
-targets::tar_config_set(store = here::here("_targets"),
-						script = here::here("_targets.R"))
-
-targets::tar_load_globals()
-
-targets::tar_load(
-	c(participants,
-	  stimuli,
-	  vocabulary,
-	  attrition_trials,
-	  attrition_participants,
-	  bvq_data,
-	  gaze,
-	  data_time,
-	  data_aggr
-	))
-
-targets::tar_load(
-	c(model_fits_aggr,
-	  model_fits_time,
-	  model_loos_aggr,
-	  model_loos_time
-	))
-
-# prepare data
-attrition <- lst(participants,
-				 attrition_participants,
-				 attrition_trials) |>
-	reduce(inner_join, by = join_by(session_id)) |>
-	unnest_wider(matches("all"), names_sep = "_") |> 
-	rename_with(\(x) gsub("is_valid_gaze_all_|is_valid_vocab_all", "", x))
-
-library(knitr)
-library(kableExtra)
-library(ggplot2)
-library(gt)
-library(patchwork)
-library(english)
-library(gtExtras)
-
-# set ggplot theme and colour palette
-my_theme <- theme_minimal() +
-	theme(panel.grid = element_blank(),
-		  axis.line = element_line(colour = "black"),
-		  text = element_text(size = 12, colour = "black"),
-		  axis.text = element_text(colour = "black"))
-
-theme_set(my_theme)
-
-clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
-
-options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
-		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
-		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
-		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
-		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
-		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
-
-set.seed(888)
-```
-
-# Introduction
-
-## The early lexicon
-
-Building a mental lexicon is a major achievement in the developmental journey of infants: by accumulating lexical representations of familiar words, infants are later able to recognise them in speech, and to extract meaning from the speech they are exposed to.
-Infants start forming their first lexical representations before their first year of life [@jusczyk1999; @halle1994; @vihman2004].
-When presented with pairs of pictures of familiar objects, 6-months-old infants already direct their gaze towards whichever is named [@bergelson20126; @bergelson2015early].
-This initial lexicon is hardly larger than around fifteen words [@REFERENCE], but it undergoes rapid growth [@REFERENCE] during their second year of life, at the end of which toddlers know an average of XXX words, and by 30 months of age, they know XXX words [@REFERENCE].
-This accelerated lexical developmental during the second year of life is also reflected in infants'  trajectories of word recognition: infants recognise familiar words faster and more efficiently [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
-Bilingual infants' trajectories of lexical acquisition [@hoff2012, @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes] and word recognition [@vihman2007onset; @vihman2013; @legacy2018vocabulary] are equivalent to their monolingual peers'.
-This is a remarkable deed: bilingual infants receive a relative impoverished linguistic input in each of their languages compared to monolinguals [@costa2014does].
-The mechanism that facilitate bilingual lexical development are still unclear.
-
-## (Early) Word recognition is cascaded
-
-Despite their different linguistic input, monolinguals and bilinguals share broadly common word recognition mechanisms.
-The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal.
-This results in the activation of lexical representations whose associated phonological forms matches the acoustic signal to some extent.
-The activated word-forms then compete for selection: the lexical system uses the auditory input, together with top-down context provided by grammatical, supra-segmental, and semantic constraints, to select the candidate lexical representation with the best match.
-There is evidence that spoken word recognition occurs in a *cascaded* fashion.
-The activation and selection of candidate lexical representations overlap in time, relying on partial information that accumulates as the speech signal unfolds [@marslen1987functional; @marslen1978processing; @grosjean1980spoken].
-This cascaded activation triggered by lexical access also results in the activation of the concepts associated to the accesses phonological forms.
-@allopenna1998tracking.
-
-This is also the case of the developing lexicon: like adults, infants activate non-selected lexical representations.
-This is relfected by the fact that from 21 months of age, infants' lexicon seems to be systematically organised accordi to the semantic and phnological properties of the lexical representations.
-
-SEMANTICS
-@arias2009lexical showed evidence of semantic priming in 21-month-old infants.
-In a word recognition task, infants' recognition of a spoken word (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
-Later studies provided electrophysiological evidence of such effect as early as 14 months of age [@friedrich2005lexical].
-
-PHONOLOGY
-Initial lexical representations are also phonologically well-specified [@swingley2000spoken; @swingley2002lexical].
-Overall these results suggest that early lexical representations are systematically organised in the lexicon according to their semantic and phonological properties.
-
-BOTH
-@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
-In each trial, the authors presented participants with four semantically and phonologically pictures.
-Four seconds after pictures onset, a word-form was auditorily presented.
-The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category.
-For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
-Then they would hear the carrier phrase "Look at the **bee**!".
-The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
-These results support a cascaded activation account of lexical access during the first stages of lexical development.
-@swingley1999continuous
-
-## Cascaded activation in bilingual parallel activation
-
-There is also evidence of cascaded activation in bilinguals.
-A critical property of bilingual language processing, both in adults and infants, is that of non-selective access to the lexicon.
-When listening to speech, bilinguals activate all lexical candidates from either language consistent with the speech signal.
-Even more surprising, when speaking, bilinguals activate all potential words consistent with the concepts they want to express.
-This effect has been systematically reported in adults [@marian1999activation; @costa2000cognate; @thierry2007brain; @dunabeitia2009masked].
-
-For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
-This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
-
-A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
-Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
-Cognates are form-similar translation equivalents.
-Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
-
-Also in toddlers [@von2012language; @von2014bilinguals] and school-aged children [@persici2019lexical; @bosma2020cognate].
-Some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
-Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
-Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that Spanish-Catalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
-
-Although recent work has provided strong evidence of parallel activation in early ages, how cognateness shapes that organisation of the early bilingual lexicon, and how this is reflected on the dynamics of lexical access during word comprehension and production is unclear.
-
-Using the experimental paradigm developed by [@arias2009lexical; @arias2013s; @singh2014one] compared within and across language
-priming effects in Chinese-English toddlers.
-@kuipers2015bilingualism compared ERP responses to picture-word pairs in English monolinguals and Welsh-English bilinguals where the words were either semantically related or unrelated to a pictured object.
-Although both studies tested 30-month-olds, the conclusions the authors reached do not fully agree.
-@singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
-
-## Cognate word recogntiion
-
-@floccia2020translation tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
-The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, French, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
-A prime word was embedded at the end of a carrier sentence that participants listened to.
-Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
-In Study 1, the target word was the translation equivalent of the prime word (*cheese*-*fromage* for an English-French bilingual).
-In other trials, prime and target words were unrelated (e.g., *sock*-*fromage*).
-There was no phonological overlap at onset between prime and target or distractor labels in either of the two conditions.
-Participants were presented with two blocks of related and unrelated trials.
-In one of the blocks, participants were presented with English prime words and Home Language target words (*sock*-*fromage*), and in the other block they were presented with Additional Language prime words and English target words (*fromage*-*sock*).
-The authors found a cross-linguistic priming effect, in which participants showed a stronger preference for the target picture in the post-naming phase in related trials, as compared to unrelated trials.
-This effect was found regardless of the language of the prime (English or Home Language), or the dominance of the language of the prime (i.e., whether the prime word belonged to the dominant language).
-Target preference exceeded chance level in both conditions.
-In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
-This time, prime and target words were not translation equivalents, but rather words whose referents shared semantic features.
-Results from Study  2 were parallel to those from Study 1.
-The authors found a strong semantic priming effect across languages, regardless of the language of the prime or the dominance of the language of the prime.
-Overall these results suggest that bilinguals recognised target words in both conditions, and benefited from a cross-linguistic facilitation effect from translation equivalents.
-The symmetry of such effect across both languages suggests that participants lexical access occurred in parallel for the two members of translation equivalents.
-As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
-The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
-However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generated by an interaction by the phonological and semantic overlap between cognate primes and targets.
-
-Another source of evidence supporting the language non-selective account of lexical access is provided by cross-languistic priming priuming thorught translation paradigms.
-In line with @floccia2020translation, @von2012language found that bilingual toddlers aged 21-to-43-months, and who were learning German and English, showed a stronger target preference in a German word recognition task after being primed with a phonologically related English word, which shared phonological onset with the prime word (e.g., *slide*-*Klide* [German for *dress*]), compared to when prime and target words were phonologically unrelated (e.g., *bottle*-*Ohr* [German for *ear*]).
-Interestingly, they also found evidence of such priming effect when participants were prime with an English word which was *not* phonologically related to the German target word, but rather its German translation was (e.g., *leg* [with German trasnlation *Bein*]-*Stein* [German for *stone*]).
-Altogether, these results indicate that bilingual toddlers activate translation equivalents in parallel during word recognition, and that the phonology of both labels may interact with lexical access in the recognition of subsequet words.
-Importantly, cross-linguitic priming through translation demonstrates that previous findings of a cognateness facilitation in word production and recognition do not result from the mere phonological overlap between auditorily presented and target labels, but also from the phonological overlap between the prime translation (not presented) and the target.
-
-Evidence from cognates.
-Marian and Spivey (1999)
-Costa et al. (2000)
-
-@dijkstra2019multilink
-
-The role of cognates in lexical processing.
-
-Another source of evidence are studies studies involving phonological priming of non-cognates through translation. [SEE REFERENCES FROM VON HOLZEN 2012]
-
-## The rpesent study
-
-The aforementioned studies use priming-though-translation paradigms.
-In these paradigms, cross-linguistic priming results from activation spreading from the lexical representation of the the (auditorily presented) prime word to the lexical representation of its translation through semantic associations (e.g., translation equivalence).
-When prime words are auditorily presented, the task design constraints the naming context to one of the languages.
-The consequence is a potential asymmtry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
-This might lead to a lower strength, and higher lacenty of the activation of the translation.
-
-In the present study, we use an adaptation of an implicit naming paradigm by @mani2010infant, in which participants are primed with a picture, instead of an auditorily presented label.
-@mani2010infant showed that 18 month-old monolinguals implicitly generate the labels of name-known pictures presented in silence.
-In each trial, infants were presented with prime pictures presented in silence, and then with a target and a distractor picture, both presented side-by-side.
-Finally, the target picture's label was presented auditorily.
-The authors manipulated the phonological overlap between the prime label and the target label, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
-Prime and target-distractor pairs were semantically unrelated.
-Interestingly, infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
-This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
-In particular, the authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
-
-@mani2011phonological used the same paradigm in 24-months-old monolinguals, and also found evidence of implicit naming, but in the opposite direction.
-After phonologically related primes, infants showed weaker target looking preference than after phonologically unrelated primes.
-These results interpreted these outcome as the result of the implicitly generated prime label interfering with the subsequent recognition of the (phonologically related) target word.
-The authors suggested that the shift from facilitation to interference from 18 to 24 months they found in both studies might be the result of a developmental shift in which 18-month-olds' lexicon is not yet organised based on phonological similarity, while 24-month-olds' is.
-This would lead to the former showing a pre-lexical facilitation effect in which such facilitation occurs via the activation of phonological segments, while the latter would show an interference effect due to lateral links between lexical representation having been established.
-Both studies by Mani and Plunkett provide evidence of implicit naming of name-known pictures by 18-month old toddlers and older, and that the resulting labels interact with the dynamics of recognition of subsequently presented word-forms.
-
-Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
-@duta2012erp presented name-known pictures in silence for one second.
-After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
-In some trials the auditory label corresponded to a canonical realisation of the word-form.
-In other trials, the word was mispronounced.
-Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
-A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
-This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
-
-When extended to the bilingual case, this implicit naming task may offer bilingual participants with an uncontrained naming context in whcih the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
-Using an adaptation of @mani2010infant's implicit naming paradigm, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
-The authors presented German-English bilinguals with 120 prime-target pairs.
-Primes were presented as familiar pictures in silence.
-After prime picture offset, target words were presented auditorily.
-Participants' N400 ERP components were recorded from target word onset.
-The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
-When prime and target were phonologically identical (*Affe*-*Affe*, German for *monkey*), or similar (*Fahne*-*Sahne*, German for *flag* and *ice-cream*, respectively) within L1, participants' showed a reduced N400 amplitude, compared to when prime and target were phonologically unrelated (*Messer*-*Seil*, German for *knife* and *rope*).
-Critically, a similar effect was found when prime and target were phonologically related through translation (*Rustsche*-*Kleid*, German for *slide* and *dress*).
-This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
-
-Evidence from cognates.
-
-The role of cognates in lexical processing.
-
-This study also provides a more suitable design for drawing conslusions about developmental change in word recognition trajectories frot wo reasons.
-First, it extends the age range of participants, compared to previous studies.
-Second, participants were tested at three selected age points to ensure a more balanced sample size across ages.
-Third, the partially longitudinal design allows modelling the performance of participants across testing sessions altogether.
-
-. In order to circumvent the problem of limited vocabulary knowledge
-in the non-dominant language, we propose to test participants only in their dominant language, therefore
-directing our research to the question of how possessing a second language affects processing of the
-dominant one in bilingual toddlers [@costa2014does provide a fuller description of the
-advantages of such approach].
-
-## The present study
-
-The present study is aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
-Using an adaptation of [@mani2010infants], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
-We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
-If so, phonological priming effect should be larger when the prime label in  both languages shares phonological overlap with the target words (cognate condition), compared to when only the label of the prime in one language overlaps phonologically with the target (non-cognate condition).
-We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
-
-We compared the explanatory power of three measures of vocabulary size on participants' trajectories of word recognition: L1 vocabulary and total vocabulary.Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary]
-
-Hypothesis 1: if lexical representations linked through inhibitory links (compete for selection), like in the adult lexicon, target looking should increase faster in *Unrelated* trials compared to *Related* trials.
-If lexical representations are linked through excitatory links, target preference should increase faster in *Related* trials, compared to *Unrelated* trials.
-If lexical representations are sparsely connected, participants should show equivalent patterns of target looking in *Related* and *Unrelated* trials.
-
-Hypothesis 2: if bilinguals' lexical representations linked across languages through inhibitory links (compete for selection), target looking should increase faster in this group in *Related/Non-cognate* trials compared to *Related/Cognate* trials.
-If lexical representations are linked across languages through excitatory links, target preference should increase faster in *Related/Cognate* trials, compared to *Unrelated/Cognate* trials.
-If lexical representations are sparsely connected across languages, bilinguals' patterns of target looking should be equivalent for *Related/Cognate* and *Related/Non-cognate* trials.
-This pattern is also expected for monolingual infants.
-
-Hypothesis 3: if the emergence of within-language or cross-language phonological links is explained (if at all) by the growth of within-language vocabulary size, the difference in target looking between *Related* and *Unrelated*, or between *Related/Cognate* and *Related/Non-cognate* trials should be larger in participants with larger vocabulary sizes in their dominant language, in which they were tested.
-This should be reflected by a $\text{Condition} \times \text{L1 vocabulary}$ two -way interaction, or a $\text{Condition} \times \text{Group} \times \text{Dominant vocabulary}$ three-way interaction.
-
-Hypothesis 4: if the emergence of within-language or cross-language phonological links is explained better by the growth of cross-language vocabulary size, compared to within-language vocabulary size, a model that incorporates total vocabulary size as a predictor instead of dominant vocabulary size should show better predictive performance.
-If the emergence of such links is explained at all by the growth of vocabulary size, both models incorporating voacbulary size as a predictor should show better predictive performance than a model incorporating participants' age.
-
-# Methods
-
-All materials, data, and reproducible code can be found at the OSF ([https://osf.io/hy984/](https://osf.io/ckydb/)) and GitHub ([https://github.com/gongcastro/cognate-priming](https://github.com/gongcastro/cognate-priming)) repositories.
-This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I.
-Before every testing session, caregivers were asked to read and sign an informed consent form, and were given a token of appreciation at the end of it.
-
-## Participants
-
-```{r}
-#| label: participants-numbers
-n_participants_total <- participants |> 
-	distinct(location, child_id) |> 
-	count(location)
-
-n_participants_sex <- participants |> 
-	distinct(location, sex, child_id) |> 
-	count(location, sex)
-
-n_participants_sessions <- count(participants,
-								 child_id,
-								 name = "n_sessions") |> 
-	count(n_sessions) |> 
-	group_split(n_sessions) |> 
-	set_names(paste0("session_", 1:3))
-
-n_sessions_total <- count(participants)
-
-n_sessions_lp <- participants |> 
-	summarise(across(age, lst(mean, sd, min, max)),
-			  n = n(),
-			  .by = c(lp)) |> 
-	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
-	group_split(lp) |> 
-	set_names(janitor::make_clean_names(unique(participants$lp)))
-
-n_sessions_dominance_lp <- count(participants, lp, test_language) |> 
-	group_split(test_language) |> 
-	set_names(c("catalan", "english", "spanish")) |> 
-	map(group_split, lp)
-
-n_sessions_lp <- participants |> 
-	count(lp) |> 
-	group_split(lp) |> 
-	set_names(c("monolingual_eng", "monolingual", "bilingual"))
-```
-
-We collected data from `r n_participants_total$n[1]` participants living in the Metropolitan Area of Barcelona (Spain) tested at the Laboratori de recerca en Infància at the Universitat Pompeu Fabra (`r n_participants_sex$n[1]` female, `n_participants_sex$n[2]` male), and `r n_participants_total$n[2]` participants living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford (`r n_participants_sex$n[3]` female, `n_participants_sex$n[4]`, `n_participants_sex$n[5]` not reported).
-Families were recruited from maternity room in private hospitals or from social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r sum(n_participants_total$n)` children that participated, `r n_participants_sessions$session_1$n` participated once, `r n_participants_sessions$session_2$n` participated twice, and `r n_participants_sessions$session_3$n` participated three times.
-Recurrent participants were tested with at least XXX months of difference.
-We gathered a total of `r n_sessions_total$n` testing sessions: `r n_sessions_lp$monolingual_eng$n` from participants in Oxford, and `r n_sessions_lp$monolingual$n + n_sessions_lp$bilingual$n` from participants in Barcelona.
-
-We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
-Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
-The output of this interview is an estimated degree of exposure (*DoE*) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
-According to this estimate, we classified participants as Catalan-, English-, or Spanish-dominant if the language with highest *DoE* was Catalan, English, or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
-From the `r n_sessions_total$n` testing sessions, `r n_sessions_lp$monolingual_eng$n` belonged to English monolinguals,  `r n_sessions_lp$monolingual$n` to Catalan or Spanish monolinguals, and  `r n_sessions_lp$bilingual$n` to Catalan-Spanish bilinguals.
-@tbl-participants shows a detailed description of the linguistic profile of our sample.
-
-```{r tbl-participants}
-#| label: tbl-partiicpants
-#| tbl-cap: "Demographic and linguistic profile of participants."
-participants |> 
-	unnest_wider(doe) |> 
-	select(-matches("others")) |> 
-	mutate(lp = case_when(
-		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
-		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
-		.default = lp)) |> 
-	arrange(desc(lp)) |> 
-	summarise(n = n(),
-			  across(age, lst(mean, sd, min, max)),
-			  across(matches("doe_"), lst(mean, sd)),
-			  age_vctr = list(age),
-			  .by = c(lp, test_language)) |> 
-	gt(rowname_col = "test_language",
-	   groupname_col = "lp") |> 
-	gt_plt_dist(age_vctr, type = "histogram") |> 
-	fmt_number(is.numeric, decimals = 1) |> 
-	fmt_integer(n) |> 
-	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
-	cols_merge_range(age_min, age_max) |> 
-	cols_merge_uncert(age_mean, age_sd) |> 
-	cols_merge_uncert(doe_catalan_mean, doe_catalan_sd) |> 
-	cols_merge_uncert(doe_english_mean, doe_english_sd) |> 
-	cols_merge_uncert(doe_spanish_mean, doe_spanish_sd) |> 
-	tab_spanner("Age (months)", matches("age")) |> 
-	tab_spanner("Catalan", matches("catalan")) |> 
-	tab_spanner("English", matches("english")) |> 
-	tab_spanner("Spanish", matches("spanish")) |> 
-	tab_spanner("Degree of Exposure (%)", matches("doe")) |> 
-	cols_label(n = "N",
-			   age_mean = "M (SD)",
-			   age_min = "Range",
-			   age_vctr = "Distribution",
-			   doe_catalan_mean = "M (SD)",
-			   doe_english_mean = "M (SD)",
-			   doe_spanish_mean = "M (SD)") |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |> 
-	tab_style(cell_text(weight = "bold"),
-			  cells_column_spanners())
-```
-
-We collected data from `r n_participants_total` monolingual and bilingual participants living in the Metropolitan Area of Barcelona (Spain), who were exposed to at least Catalan and/or Spanish from birth.
-Families were recruited from maternity room in private hospitals in Barcelona, and contacted via phone when the child's age spanned between our age intervals of interest.
-Families were invited to participate at three age points: 21, 25, and 30 months.
-`r n_participants_sessions[[1]]$n` participants were tested at one age point,  `r n_participants_sessions[[2]]$n` at two age points, and `r n_participants_sessions[[3]]$n` at the three age points.
-In total, we gathered data from `r n_sessions_total$n` testing sessions: `r n_sessions_age_group$age_21$n` at 21 months (*Mean* = `r round(n_sessions_age_group$age_21$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_21$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_21$age_min`--`r n_sessions_age_group$age_21$age_max`), `r n_sessions_age_group$age_25$n` at 25 months (*Mean* = `r round(n_sessions_age_group$age_25$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_25$age_min`--`r n_sessions_age_group$age_25$age_max`), and `r n_sessions_age_group$age_30$n` at 30 months (*Mean* = `r round(n_sessions_age_group$age_30$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_30$age_min`--`r n_sessions_age_group$age_30$age_max`).
-
-Participants' vision was normal, none used glasses or any other type of vision corrector.
-
-### Language profile {#sec-lp}
-
-We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
-Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
-The output of this interview is an estimated degree of exposure (DoE) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
-According to this estimate, we classified participants as Catalan- or Spanish-dominant if the language with highest DoE was Catalan or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
-We collected data from `r n_sessions_dominance$catalan$n` Catalan-dominant participants in Catalan (`r n_sessions_dominance_age_group$catalan$age_21$n` at 21 months, `r n_sessions_dominance_age_group$catalan$age_25$n` at 25 months, and `r n_sessions_dominance_age_group$catalan$age_30$n` at 30 months).
-We further classified participants as monolinguals if the DoE to their dominant language exceeded 80% of the total DoE to Catalan and Spanish, and as bilinguals otherwise.
-Participants with DoE to language other than Catalan or Spanish were excluded from analyses.
-This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
-@tbl-participants-lp shows a detailed description of the linguistic profile of our sample.
-
-### Vocabulary size
-
-```{r vocab-values}
-n_imputed <- table(vocabulary$is_imputed)[2]
-prop_imputed <- scales::percent(n_imputed/nrow(vocabulary))
-n_pool <- nrow(bvq_data$vocabulary)
-```
-
-We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability] developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers.
-Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
-
-We calculated several measures of receptive vocabulary size from each participant's vocabulary: L1 vocabulary size (proportion of words  reported as acquired in the checklist of the dominant language), L2 vocabulary size (proportion of words  reported as acquired in the checklist of the non-dominant language), total vocabulary size (proportion of the words in both checklists reported as acquired), conceptual vocabulary (proportion of concepts for which the participant was reported to have acquired at least one label, in any language), and translation equivalent vocabulary (proportion of concepts for which the participant was reported to have acquired at two labels, one in each language).
-
-`r n_imputed` (`r prop_imputed`) Families failed to provide a complete response to the BVQ within the two-week time limit, or did not provide a successful response to the questionnaire.
-For missing questionnaire responses, we imputed the vocabulary size of the participant using single imputation, using the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
-We used participants age in months and their language profile (monolingual/bilingual) as predictors.
-We used the `mice` R package [@van2011mice] to perform imputation using the Bayesian linear regression method.
-
-```{r tbl-vocabulary}
-#| label: tbl-vocabulary
-#| tbl-cap: "Participant vocabulary sizes across ages and language profiles.
-Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
-Vocabulary size scores from the recurrent participants are shown linked."
-#| eval: false
-vocabulary |> 
-	inner_join(select(participants, child_id, session_id, age, lp),
-			   by = join_by(child_id, session_id)) |> 
-	pivot_longer(c(total_prop, l1_prop),
-				 names_to = "measure",
-				 values_to = "prop",
-				 names_transform = \(x) gsub("_prop", "", x)) |> 
-	mutate(lp = case_when(
-		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
-		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
-		.default = lp) |> 
-			factor(levels = c("Monolingual (English)",
-							  "Monolingual (Catalan or Spanish)",
-							  "Bilingual (Catalan-Spanish)")),
-		measure = if_else(measure=="l1", 
-						  "L1 vocabulary", 
-						  "Total vocabulary"),
-		is_imputed = if_else(is_imputed, "Imputed", "Observed") |> 
-			factor(levels = c("Observed", "Imputed"))) |> 
-	ggplot(aes(age, prop, colour = is_imputed)) +
-	facet_grid(measure ~ lp) +
-	geom_line(aes(group = child_id),
-			  alpha = 1/2,
-			  colour = "grey") +
-	geom_point() +
-	labs(x = "Age (months)",
-		 y = "Vocabulary size (%)") +
-	theme(panel.grid = element_line(linetype = "dotted",
-									colour = "grey"),
-		  legend.position = "right",
-		  legend.title = element_blank())
-
-ggsave(file.path("img", "vocabulary.jpeg"),
-	   dpi = 800, height = 8, height = 4)
-```
-
-## Stimuli
-
-```{r stimuli-values}
-n_words <- length(unique(with(stimuli, unlist(prime, target, distractor))))
-```
-
-We used `r n_words` distinct words included in the BVQ to create the stimuli lists.
-We created six stimuli lists: three in Catalan, and three in Spanish.
-Each list contained 32 trials, each involving a prime-target-distractor group.
-Each word played a role as either prime, *or* as target and distractor across the three lists in their corresponding language.
-For instance, the Catalan word *cadira* appeared as *prime* in the three lists, but never as *target* or *distractor*; the Catalan word *bici* appeared as *target* and *distractor* across the three lists, but never as a prime.
-Target-distractor pairings were held constant across the three lists in each language.
-For instance, in all Catalan lists the word *bici* was paired with the word *porta*.
-Target-distractor pairings were also yoked, so that each member of the same target-distractor pair appeared once as target and once as distractor in each list.
-For instance, the *bici*-*porta* paired appeared twice in each of the three Catalan lists: once with *bici* as target and *porta* as distractor, and once with *porta* as target and *bici* as distractor.
-This counterbalancing avoided participants encountering looking at the target word guided solely by that word having being named in a previous trial.
-Finally, prime words appeared only once in each list: each target-distractor pair was associated with a different prime word in both appearances.
-In each list, the same prime word was presented alongside a different target-distractor pair.
-For instance, the Catalan prime word *barret* was presented with the *bici*-*porta* target-distractor pair in one list, with the *bici*-*porta* pair in another list, and with *berenar*-*amanida* in the remaining list.
-The order of the trials was randomised across experimental session, so that each time a participant was tested, the order in which the prime-target-distractor was presented was randomised.
-Each participant was randomly assigned to one of the three lists in the corresponding language (their dominant language, see @sec-lp), and always the same list across their experimental sessions in the case of a recurrent participant.
-
-In 16 of the 32 trials of the same list (henceforth *related* trials), the prime and the target words were phonologically related, sharing phonological onset (at least first phoneme).
-In the other 16 trials (*unrelated* trials), prime and target did not share phonological onset.
-8 of the 16 *related* trials included a cognate prime (*cognate* trials), and the other 8 included a non-cognate trials (*non-cognate* trials).
-A prime word was considered cognate if its Catalan and Spanish translation shared phonological onset.
-Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
-Target and distractor word pairs were phonologically unrelated (did not share phonological onset).
-Some of them shared semantic features or a taxonomic relationship.
-This is the case of words associated with especially salient referents such as animals or food.
-To avoid infants guiding their gaze to these objects based on their saliency, we paired animals and food items together.
-The position of the target and distractor pictures (right or left) for each target-distractor pair was alternated, so that in one list the target would appear on the left, in another list it would appear on the right, and so on.
-
-We examined the overall equivalence of the three trial types by comparing them across three variables relating to the target word: lexical frequency, word prevalence, animacy
-@tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
-Lexical frequencies were extracted from the Catalan and Spanish corpora of the CHILDES database [@reference; @reference] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@reference; @reference].
-We defined word prevalence as the proportion of same-aged infants who were reported to understand the word in the BVQ database.
-
-### Auditory stimuli
-
-The auditory stimuli were natural exemplars of the selected target words, spoken by Catalan-Spanish proficient bilingual female speaker who was instructed to pronounce each word in a toddler-directed manner.
-Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
-We used the Audacity [@reference] and Praat [@boersma2001speak] to record and edit the audio files.
-The speaker was presented with a list of words in Catalan.
-The order of the words was pseudo-randomised, and each word was produced three times in a row before moving to the next word in the list.
-After going through all the words in the list, the speaker went through the word list again generating three tokens for each word, now in an inverse order (from bottom of the list to the top).
-We then repeated the same procedure for the list of Spanish words.
-The resulting audios were manually chunked into individual word-forms.
-For each of the six tokens produced for each word, the most adequate was selected for further processing.
-The audios were then transformed to stereo by duplicating them into two channels, denoised, and finally normalised.
-The mean duration of the final audios was `r round(mean(stimuli$duration[stimuli$test_language=="Catalan"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Catalan"]), 2)`) and `r round(mean(stimuli$duration[stimuli$test_language=="Spanish"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Spanish"]), 2)`) seconds for the Catalan and Spanish lists.
-
-To make the pronunciation of the words as familiar as possible to each infant, we generated additional pronunciation variants for some words in Catalan and Spanish.
-Catalan words involving the /\textipa{L}/ phoneme in their Central Catalan variant (e.g., /\textipa{'Lu.n@}) were also recorded with such phoneme replaced by /j/ (e.g., /\textipa{'ju.n@}), a phonological process common in the Metropolitan Area of Barcelona [@reference].
-Spanish words involving the /\textipa{T}/ phoneme were also generated replacing such phoneme with /\textipa{s}/ to better accommodate Latin variants of Spanish.
-Before every experimental session, caregivers were asked to utter three written words involving the /\textipa{L}/ phoneme (in the case of participants tested in Catalan) or the /\textipa{T}/ phoneme (in the case of participants tested in Spanish).
-Each token contained the critical phoneme at onset, inter-vocalic position, and coda.
-The experimenter assigned the participant to the Catalan or Spanish stimuli list involving the closest variant to that of caregivers'.
-
-### Visual stimuli
-
-For each word, we created a picture with a typical referent.
-To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias-trejo2010].
-
-```{r tbl-stimuli}
-#| label: tbl-stimuli
-#| tbl-cap: "Summary of stimuli properties by trial type."
-stimuli |> 
-	summarise(across(c(matches("familiarity_|freq_|animate_"), duration),
-					 tibble::lst(mean, sd, min, max)),
-			  .by = c(test_language, trial_type)) |> 
-	select(-matches("familiarity_se"), -matches("prime"),
-		   -c(is_animate_target_sd,
-		      is_animate_target_min,
-		      is_animate_target_max),
-		   -matches("min"), -matches("max")) |> 
-	gt(groupname_col = "test_language",
-	   rowname_col = "list") |> 
-	fmt_number(is.numeric,
-			   decimals = 1) |> 
-	fmt_number(matches("familiarity|animate"),
-			   scale_by = 100,
-			   decimals = 1) |> 
-	cols_merge(c(freq_target_mean, freq_target_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(familiarity_target_mean, familiarity_target_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(duration_mean, duration_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_label(trial_type = "",
-			   familiarity_target_mean = "Prevalence (%)",
-			   freq_target_mean = "Frequency",
-			   is_animate_target_mean = "Animacy (%)",
-			   duration_mean = "Duration (s)") 
-```
-
-## Procedure
-
-Testing took place in a sound-proof room.
-Participants sat on their caregivers' lap in a dimly lit testing booth while the experimenter conducted the experiment from outside.
-Caregivers were instructed to keep their eyes shut (to avoid recording their gaze, instead of the participant's), to be still, and to avoid interacting with the participant verbally or non-verbally.
-Participants sat at approximately 65 cm from the eye-tracker and a XX-in screen of $1929\times1080$ screen resolution.
-We used a custom Matlab XXXX script using the PsychToolbox XXX extension [@brainard] to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
-Sampling rate was set at 120 Hz.
-A 5-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
-We set a 55% grey background for the calibration and stimuli presentation.
-Auditory stimuli were presented through two loudspeakers located behind the screen, one to each side.
-The experimenter monitored the experimental from outside the room using a centrally located video camera place above the screen.
-After a successful calibration the experimenter triggered the onset of the first trial.
-Trials were presented uninterruptedly and  without intervention of the experimenter until the 32 trials were presented, or the experimental session had to be stopped because of the participant's behaviour.
-
-![Experimental task design with examples in Catalan.
-In each trial, the prime image is presented in silence for 3,000 ms.
-The the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
-In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
-In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
-In unrelated trials (*n* = 32), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){fig-align="center"}
-
-Each trial started with the presentation of an attention getter for 3,000 milliseconds.
-Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
-Fifty milliseconds after the offset of the prime image, an auditory label was played from the loudspeakers and, 700 milliseconds after the onset of the auditory label, the target and distractor pictures were presented side-by-side during 1,000 milliseconds until the end of the trial.
-After this, the attention getter of the next trial was immediately presented.
-Each experimental session took approximately 10 minutes.
-
-## Apparatus
-
-see https://link.springer.com/article/10.3758/s13428-021-01762-8
-
-## Data processing
-
-```{r dataset}
-n_trials <- nrow(attrition)
-n_sessions <- n_distinct(attrition$session_id)
-n_participants <- n_distinct(attrition$child_id)
-n_trials_valid <- nrow(filter(attrition,
-							  is_valid_participant,
-							  is_valid_trial))
-n_sessions_valid <- sum(attrition_participants$is_valid_participant)
-n_participants_valid <- n_distinct(
-	attrition[attrition$is_valid_participant, ]$child_id)
-
-n_exc_prime <- sum(!attrition$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition$is_valid_gaze_test)
-n_exc_test_any <- sum(!attrition$is_valid_gaze_test_any)
-n_exc_participants <- sum(!attrition_participants$is_valid_participant)
-
-n_longitudinal <- attrition |>
-	filter(is_valid_participant,
-		   is_valid_trial) |>
-	distinct(child_id, session_n) |> 
-	count(child_id, name = "times") |> 
-	count(times)
-```
-
-We defined a time windows of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
-To avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
-Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
-We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_any, big.mark = ",")`) [see @floccia2020translation for a similar approach].
-
-After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`).
-The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition-trials shows a detailed description of the trial attrition.
-
-```{r tbl-attrition}
-#| label: tbl-attrition
-#| tbl-cap: "Participant-level and trial-level sample size after applying inclusion criteria. The number of excluded participants and trials is indicated between parentheses."
-expanded <- expand(attrition, lp, trial_type, is_valid_trial)
-
-n_lp <- attrition |> 
-	distinct(is_valid_participant, lp, session_id) |> 
-	count(is_valid_participant, lp) |> 
-	pivot_wider(names_from = is_valid_participant,
-				values_from = n,
-				names_repair = janitor::make_clean_names) |> 
-	mutate(n_participants_true = true,
-		   n_participants_false = false) |> 
-	select(lp, true, false)
-
-attrition |> 
-	summarise(n_trials_true = sum(is_valid_trial),
-			  n_trials_false = sum(!is_valid_trial),
-			  .by = c(lp, trial_type)) |> 
-	arrange(desc(lp)) |> 
-	# across(n_trials, lst(mean, sd, sum), na.rm = TRUE),
-
-	pivot_wider(id_cols = lp,
-				names_from = c(trial_type),
-				values_from = matches("trials"),
-				names_repair = janitor::make_clean_names) |> 
-	left_join(n_lp, by = join_by(lp)) |> 
-	mutate(lp = case_when(
-		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
-		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
-		.default = lp)) |>
-	select(lp, true, false,
-		   matches("n_trials")) |> 
-	gt(rowname_col = "lp") |> 
-	tab_spanner("Participants", matches("participant")) |> 
-	tab_spanner("Trials", matches("trial")) |> 
-	fmt_integer(everything()) |> 
-	cols_merge(c(true, false),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_cognate,
-				 n_trials_false_cognate),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_non_cognate,
-				 n_trials_false_non_cognate),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_unrelated, 
-				 n_trials_false_unrelated),
-				 pattern = "{1} ({2})") |> 
-	cols_label(true = "N", 
-			   n_trials_true_cognate = "Cognate",
-			   n_trials_true_non_cognate = "Non-cognate",
-			   n_trials_true_unrelated = "Unrelated") |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |>
-	grand_summary_rows(fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~ fmt_integer(.))
-```
-
-## Data analysis
-
-We used multilevel General Additive Models (GAMs) to model our data and test our hypotheses [@pedersen2019hierarchical].
-First, we defined our response variable as the empirical logit of target looking using @eq-elogit across all eye-tracking samples for each each participant in each condition [@barr2008analyzing; @agresti2012categorical].
-We used a Gaussian distribution to model our response variable.
-To test our hypotheses, we then included *Condition*, *Group*, and either *Age* ($\mathcal{M}_0$), *L1 vocabulary* ($\mathcal{M}_1$), or *Total vocabulary* ($\mathcal{M}_2$) as fixed effects in the model.
-We also added all two-way and three-way interactions between the predictors.
-We set two *a priori* contrasts for the *Condition* predictor: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
-We also set two *a priori* contrasts for the *Group* predictor: one comparing *Monolingual (ENG)* with *Monolingual (CAT/SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Bilingual (CAT-SPA)* participants coded as `0`), and another comparing *Monolingual (ENG)* with *Bilingual (CAT-SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Monolingual (CAT/SPA)* participants coded as `0`).
-Before entering the model, the numeric predictors *Age*, *L1 vocabulary*, and *Total vocabulary* were standardised by subtracting from each observation the mean of the predictor, and dividing the result from the standard deviation of the predictor.
-
-$$
-\eta' = \ln\bigg(\frac{\text{Target} + 0.5}{ \text{Distractor} + 0.5}\bigg)
-$$ {#eq-elogit}
-
-We added *Session* as grouping variable, by by-session intercept and *Condition* slopes.
-Each level in the *Session* variable uniquely indexes all observations generated by a participant in a single testing session.
-Testing sessions from the same participant are identified by different indexes.
-For computational limitations, adding both participants and testing sessions as grouping variable in the random effects structure of the model was not possible.
-We instead included testing sessions alone, as observations from the same testing session are more likely to be highly correlated than those from the same participant in different testing sessions (which were recorded at least four months apart).
-To model the time course of target looking across time bins, we included cubic regression splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
-For both splines, we specified $k = 9$ basis functions or *knots*--half the number of time bins---for computational convenience.
-@eq-model shows a formal implementation of the model.
-
-$$
-\begin{aligned}
-\textbf{Likelihood:} \\
-y_i &\sim \mathcal{N}(\mu_i, \sigma_i) \\ \\
-\textbf{Linear model:} \\
-\eta'(\mu_i) &= (\beta_0 + u _{0_{i}}) +
-(\beta_1 + u _{1_{i}}) \cdot \text{Condition} +\\
-&\beta_{2} \cdot \text{Group} +
-\beta_{3} \cdot X + \beta_{4} \cdot (\text{Condition} \times \text{Group}) +\\
-&\beta_{5} \cdot (\text{Condition} \times X) + \beta_{6} \cdot (\text{Group} \times X) +\\
-&\beta_{7} \cdot (\text{Condition} \times \text{Group} \times X) +\\
-& \sum_{j = 1}^k b_{j_{0}} \cdot \beta_{8_{k}} \cdot \text{Time} +
-\sum_{j = 1}^k b_{j_{1}} \cdot\beta_{9_{k}} \cdot (\text{Time} \times \text{Group}) \\
-\text{where:} \\
-&\eta'\text{ is the empirical logit of target fixations} \\
-&X \in \{\text{Age}, \text{L1 vocabulary}, \text{Total vocabulary}\} \\
-&k \text{ is the number of knots in the spline (10)} \\
-\textbf{Prior:} \\
-\beta_{0-9} &\sim \mathcal{N}(0, 0.5) \\
-u_{0-2} &\sim \mathcal{N}(0, \sigma_{0-2})\\
-b_{0-1} &\sim \text{MVN}(0, \tau_{0-1}) \\
-\sigma_{0-2}, \tau_{0-1} &\sim \text{Exponential}(6)\\
-\rho_{0-2} &\sim LKJCorr(6)\\
-\text{where:}\\
-&\rho_{0-2} \text{ are the correlation parameters for } \sigma_{0-2}
-\end{aligned}
-$$ {#eq-model}
-
-The comparison between the three models including *Age*, *L1 vocabulary*, *Total vocabulary* as predictors was performed using leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it [@vehtari2017practical].
-We implemented the model using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
-We ran `r english::words(dim(model_fit$fit_0)[2])` iteration chains using the by-default No U-Turn Sampler algorithm with `r format(niterations(model_fit$fit_0), big.mark = ",")` iterations each and an additional `r format(niterations(model_fits$fit_0), big.mark = ",")` warm-up iterations per chain.
-
-# Results
-
-```{r fig-ptlt-recognition}
-#| label: fig-ptlt-recognition-aggr
-#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-data_time |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(lp, timebin, session_id)) |> 
-	ggplot(aes(timebin, .prop, colour = lp)) +
-	facet_wrap(~lp, nrow = 1, scales = "free_x") +
-	geom_line(aes(group = session_id),
-			  # colour = "grey",
-			  alpha = 1/10) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = "mean_se",
-				 geom = "errorbar",
-				 width = 0.35,
-				 linewidth = 2/4) +
-	stat_summary(fun = "mean",
-				 geom = "point",
-				 size = 1.2) +
-	stat_summary(fun = "mean",
-				 geom = "line",
-				 linewidth = 2/4) +
-	labs(x = "Time (ms)",
-		 y = "PTLT") +
-	scale_x_continuous(breaks = seq(0, 20, 2),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	scale_y_continuous(labels = scales::percent,
-					   breaks = seq(0, 1, 0.2),
-					   limits = c(0, 1)) +
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  legend.position = "none")
-```
-
-```{r tbl-coefs}
-post <- gather_draws(fit_0, `b_.*`, regex = TRUE)
-
-ggplot(post, aes(.value)) +
-	facet_wrap(~.variable, scales = "free") +
-	geom_histogram(bins = 15, colour = "white") +
-	geom_errorbar(data = mean_qi(post),
-				  aes(xmin = .lower, xmax = .upper, y = 400),
-				  width = 1,
-				  linewidth = 3/4) +
-	geom_point(data = mean_qi(post),
-			   aes(x = .value, y = 400),
-			   size = 2) +
-	scale_y_continuous(limits = c(0, 500))
-```
-
-## Hypothesis 1: within-language phonological priming
-
-## Hypothesis 2: cross-language phonological priming
-
-## Hypothesis 3: emergence of phonological association
-
-## Hypothesis 4: the compating role of age and vocabulary
-
-```{r fig-time}
-#| label: fig-time
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-make_std <- function(x, mean, sd) (x - mean) / sd
-
-timebin_values <- make_std(seq(0, 17, length.out = 100),
-						   mean(data_time$timebin),
-						   sd(data_time$timebin))
-
-age_values <- make_std(c(21, 25, 30),
-					   mean(data_time$age),
-					   sd(data_time$age))
-
-nd <- expand_grid(condition = levels(fit_0$data$condition),
-				  timebin_std = timebin_values,
-				  age_std = age_values,
-				  # sesion_id = first(data$session_id),
-				  # age = c(21, 25, 30),
-				  lp = levels(fit_0$data$lp))
-
-epreds <- add_epred_draws(newdata = nd,
-						  object = fit_0,
-						  ndraws = NULL,
-						  re_formula = NA,
-						  value = ".value") |> 
-	mean_qi() |> 
-	mutate(lp = factor(lp, 
-					   levels = c("Monolingual (English)",
-					   		   "Monolingual",
-					   		   "Bilingual")),
-		   age_std = factor(age_std, 
-		   				 levels = age_values,
-		   				 labels = paste0(c(21, 25, 30), " months")))
-
-epreds |> 
-	ggplot(aes(timebin_std, .value,
-			   colour = condition,
-			   fill = condition)) +
-	facet_wrap(lp ~ age_std) +
-	geom_hline(yintercept = 0,
-			   linetype = "dashed") +
-	geom_ribbon(aes(ymin = .lower, ymax = .upper),
-				alpha = 0.5,
-				linewidth = 0) +
-	geom_line(linewidth = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "Logit (Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	theme(legend.position = "top",
-		  panel.grid.major = element_line(colour = "grey",
-		  								linetype = "dotted"))
-
-ggsave(file.path("img", "model-time.jpeg"),
-	   height = 4, width = 10,
-	   dpi = 800)
-```
-
-```{r fig-time-total}
-#| label: fig-time-total
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-voc_values <- seq(0.25, 1, 0.25)
-
-nd <- expand_grid(condition = levels(model_fits_time$fit_time_2$data$condition),
-				  timebin = seq(0, 17, length.out = 100),
-				  voc_total = voc_values,
-				  # sesion_id = first(data$session_id),
-				  # age = c(21, 25, 30),
-				  lp = levels(model_fits_time$fit_time_2$data$lp))
-
-epreds <- add_epred_draws(newdata = nd,
-						  object = model_fits_time$fit_time_2,
-						  ndraws = 20,
-						  re_formula = NA,
-						  value = ".value") |> 
-	mean_qi() |> 
-	mutate(lp = factor(lp, 
-					   levels = c("Monolingual (English)",
-					   		   "Monolingual",
-					   		   "Bilingual")),
-		   voc_total = factor(x = voc_total, 
-		   				   levels = voc_values,
-		   				   labels = scales::percent(voc_values)))
-
-epreds |> 
-	ggplot(aes(timebin, .value,
-			   colour = condition,
-			   fill = condition)) +
-	facet_grid(lp~voc_total) +
-	geom_hline(yintercept = 0,
-			   linetype = "dashed") +
-	geom_ribbon(aes(ymin = .lower, ymax = .upper),
-				alpha = 0.5,
-				linewidth = 0) +
-	geom_line(linewidth = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "Logit (Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	theme(legend.position = "top",
-		  panel.grid.major = element_line(colour = "grey",
-		  								linetype = "dotted"))
-
-ggsave(file.path("img", "model-time-voc-total.jpeg"),
-	   height = 5.5, width = 10,
-	   dpi = 800)
-```
-
-{{< pagebreak >}}
-
-# Discussion
-
-## Summary
-
-## Context
-
-## Facilitation vs. inhibition
-
-## Onsets vs. offsets
-
-## Problems and generalisatility
-
-## Future steps
-
-## Conclusions
-
-# References
-
-{{< pagebreak >}}
-
-# Appendix
-
-## Appendix A: imputing voabulary size scores
-
-```{r fig-vocabulary-imputation}
-vocabulary_tmp <- vocabulary |> 
-	left_join(select(participants, child_id, vocab_id, age),
-			  by = join_by(child_id, vocab_id)) |> 
-	relocate(child_id) |> 
-	filter(is_imputed)
-
-bvq_data$vocabulary |> 
-	inner_join(distinct(bvq_data$logs, child_id, response_id, lp, age),
-			   by = join_by(response_id)) |> 
-	mutate(is_imputed = FALSE) |> 
-	bind_rows(vocabulary_tmp) |> 
-	pivot_longer(ends_with("_prop"),
-				 names_to = "measure",
-				 values_to = "prop") |> 
-	drop_na(prop) |> 
-	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"),
-		   measure = factor(measure,
-		   				 levels = c("total_prop",
-		   				 		   "l1_prop",
-		   				 		   "l2_prop",
-		   				 		   "concept_prop",
-		   				 		   "te_prop"),
-		   				 labels = c("Total",
-		   				 		   "L1",
-		   				 		   "L2",
-		   				 		   "Conceptual",
-		   				 		   "TE"))) |> 
-	ggplot(aes(age, prop, 
-			   colour = is_imputed,
-			   fill = is_imputed)) +
-	facet_wrap(~measure) +
-	geom_point(alpha = 1/4, size = 1) +
-	geom_smooth(method = "glm", 
-				formula = "y ~ x",
-				method.args = list(family = "binomial"), 
-				# se = FALSE,
-				size = 1) +
-	labs(x = "Age (months)",
-		 y = "Vocabulary size",
-		 fill = "Imputed",
-		 colour = "Imputed") +
-	theme(legend.position = c(1, 0),
-		  legend.justification = c(1, 0),
-		  legend.title = element_blank())
-
-```
-
-{{< pagebreak >}}
-
-## Appendix B: distribution of prime and target looking times
-
-```{r fig-dist-prime}
-#| label: fig-dist-prime
-#| fig-height: 4
-#| fig-width: 8
-looking_times |> 
-	mutate(prime_time = cut(prime_time, 
-							seq(0, 1.5, 0.1),
-							labels = FALSE,
-							include.lowest = TRUE)) |> 
-	add_count(lp, age_group, name = "n_total") |> 
-	count(lp, age_group, prime_time, n_total) |> 
-	mutate(n = n / n_total) |> 
-	ggplot(aes(prime_time, n)) +
-	facet_grid(lp~age_group) +
-	annotate(geom = "rect",
-			 fill = "orange",
-			 ymin = -Inf,
-			 ymax = Inf,
-			 xmin = 0,
-			 xmax = 0.75*10,
-			 alpha = 1/3,
-			 colour = NA) +
-	# annotate(label = "Excluded trials",
-	# 		 geom = "text",
-	# 		  x = (0.75/2)*10,
-	# 		  y = 1)
-	geom_col(fill = "black") +
-	labs(x = "Prime looking time (s)",
-		 y = "Proportion of trials") +
-	scale_x_continuous(labels = \(x) x/10) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"))
-```
-
-```{r fig-dist-target}
-#| label: fig-dist-target
-#| fig-height: 4
-#| fig-width: 8
-looking_times |> 
-	mutate(target_time = cut(target_time, 
-							 seq(0, 2, 0.1),
-							 labels = FALSE,
-							 include.lowest = TRUE)) |> 
-	add_count(lp, age_group, name = "n_total") |> 
-	count(lp, age_group, target_time, n_total) |> 
-	mutate(n = n / n_total) |> 
-	ggplot(aes(target_time, n)) +
-	facet_grid(lp~age_group) +
-	# annotate(label = "Excluded trials",
-	# 		 geom = "text",
-	# 		  x = (0.75/2)*10,
-	# 		  y = 1)
-	geom_col(fill = "black") +
-	labs(x = "Targets looking time (s)",
-		 y = "Proportion of trials") +
-	scale_x_continuous(labels = \(x) x/10) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"))
-```
-
-{{< pagebreak >}}
-
-## Appendix C: prime and test looking times
-
-```{r fig-looking-times}
-#| label: fig-looking-times
-#| fig-height: 8
-#| fig-width: 8
-#| fig-cap: "Looking time (s) to the prime and target AOI against audio duration. In longer audios, participants are expected to look longer to the prime and target picture."
-
-looking_times |>
-	left_join(select(attrition_trials, 
-					 filename, trial, is_valid_trial),
-			  by = join_by(filename, trial)) |>
-	filter(is_valid_trial) |> 
-	ggplot(aes(duration,
-			   prime_time,
-			   colour = trial_type, 
-			   fill = trial_type,
-			   shape = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_point(alpha = 0.5, 
-			   size = 1) +
-	geom_smooth(method = "lm") +
-	theme(axis.title.x = element_blank()) +
-
-	looking_times |>
-	left_join(select(attrition_trials, 
-					 filename, trial, is_valid_trial),
-			  by = join_by(filename, trial)) |>
-	filter(is_valid_trial) |> 
-	ggplot(aes(duration,
-			   target_time,
-			   colour = trial_type, 
-			   fill = trial_type,
-			   shape = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_point(alpha = 0.5,
-			   size = 1) +
-	geom_smooth(method = "lm",
-				formula = "y ~ x") +
-	plot_layout(ncol = 1, guides = "collect") &
-	plot_annotation(tag_levels = "A") &
-	labs(x = "Audio duration (s)",
-		 y = "Looking time (1.0-2.0 seconds)",
-		 colour = "Prime type",
-		 fill = "Prime type",
-		 shape = "Prime type") 
-```
-
 ## Appendix D: vocabulary checklist validity
@@
 
-get_data_time(gaze = gaze,
+get_data(gaze = gaze,
 		 participants = participants,

### 2023-11-03 manuscript/manuscript.qmd
Add results and exploratory analysis

@@
 	  gaze,
-	  data_time_bcn
+	  data_bcn
 	))
@@
 By storing representations of how familiar words sound and what they mean, an infant is able to make sense of their linguistic input.
-Infants start forming their first lexical representations before their first year of life [@jusczyk1999; @halle1994; @vihman2004; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
+Infants start forming their first lexical representations before their first year of life [@tincoff1999some; @halle1994emergence; @vihman2004cross; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
 This initial lexicon consists of only a few items; mainly words for people, interjections, body parts, and food [@tincoff2012six; @tardif2008baby], but it undergoes rapid growth during their second year of life [@ganger2004reexamining; @goldfield1990early; @bloom2002children; @mcmurray2007defusing].
@@
 
-Despite being exposed to a more complex linguistic input, bilinguals show equivalent trajectories of word acquisition and word recognition to their monolingual peers' [@vihman2007onset; @vihman2013; @legacy2018vocabulary; @hoff2012; @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes].
+Despite being exposed to a more complex linguistic input, bilinguals show equivalent trajectories of word acquisition and word recognition to their monolingual peers' [@vihman2007onset; @legacy2018vocabulary; @hoff2012dual; @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes].
 This is a remarkable deed for two reasons.
@@
 
-More recently, @chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
+@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
 In each trial, the authors presented participants with four semantically and phonologically pictures.
@@
 For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
-Then they would hear the carrier phrase "Look at the **bee**!".
+Then they would hear the carrier phrase "Look at the *bee*!".
 The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
@@
 
-Bilinguals provide one of the most interesting pieces of evidence in support of a cascaded account of lexical processing.
+One of the most interesting pieces of evidence in support of a cascaded account of lexical processing is provided by bilinguals.
 A critical property the bilingual lexicon is that its representations are accessed in a language-non selective way.
-Even during monolingual situations, bilinguals access their lexical representations in both of their languages [e.g.; @thierry2007brain; @dunabeitia2009masked].
+Even during monolingual situations, bilinguals access their lexical representations in both of their languages [e.g., @thierry2007brain; @dunabeitia2009masked].
 This is reflected in bilinguals' performance in word recognition and production tasks.
@@
 
-Phonological priming paradigms have also revealed language non-selectivity in the initial bilingual lexicon.
+Phonological priming paradigms have also revealed language non-selectivity in the initial bilingual lexicon [@poarch2012cross; @bosma2020cognate; @singh2014one; @jardak2019labels; @von2019impact].
 For instance, @von2012language found evidence of cross-language phonological priming in 21- to 42-months-old children learning German and English.
 At the beginning of each trial, the authors auditorily presented an English prime word embedded in a carrier phrase.
-Then, the target label was auditorily presented in German.
+Then, the target label was also auditorily presented in German.
 Finally the target and distractor pictures were presented side-by-side.
 The authors manipulated the phonological overlap between the prime and target labels.
-The novelty in this study lied in the orthogonal manipulation of the phonological overlap between both labels in English and German.
+The novelty in this study lied in the orthogonal manipulation of the phonological overlap between both English and German labels.
 In some trials, the auditorily presented prime and target labels were phonologically related (e.g., *slide*-*Klide* [*dress*]).
@@
 Interestingly, participants showed a weaker target preference in priming through translation trials.
-Since participants' target recognition was interfered by the non-presented prime translation, such an inhibitory effect must stem at the lexical level.
-The fact that phonological priming facilitated the recognition of the target words (both labels belong to different languages), and that phonological priming through translation interfered target recognition (translation and target belong to the same language) points to cross-language connections playing an excitatory role, and to within-language connections playing an inhibitory role.
-
-@floccia2020translation tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
+
+Using a similar task, @floccia2020translation provided conflicting results to those of @von2012language.
+The authors tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
 The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, French, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
 A prime word was embedded at the end of a carrier sentence that participants listened to.
-Then participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
+Then, participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
 In Study 1, the target word was the translation equivalent of the prime word (*cheese*-*fromage* for an English-French bilingual).
@@
 
-The aforementioned studies use priming-though-translation paradigms.
-In these paradigms, cross-linguistic priming results from activation spreading from the lexical representation of the the (auditorily presented) prime word to the lexical representation of its translation through semantic associations (e.g., translation equivalence).
-When prime words are auditorily presented, the task design constraints the naming context to one of the languages.
+Previous studies had reported similar cross-language priming effects, but as @von2012language note, the conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was not warranted.
+In studies where the auditorily presented prime label was phonologically overlapped with the target label [@REFERENCE], priming effects might be explained by the activation of the phonological segments of the prime label, which facilitated the recognition of the target label, which shared such phonological segments.
+The priming-through-translation results by @von2012language and @floccia2020translation demonstrates that cross-language activation in the developing lexicon occurs at the lexical level.
+Since participants' target recognition was interfered by the non-presented prime translation, such an inhibitory effect must stem at the lexical level.
+The fact that phonological priming facilitated the recognition of the target words (both labels belong to different languages), and that phonological priming through translation interfered target recognition (translation and target belong to the same language) points to cross-language connections playing an excitatory role, and to within-language connections playing an inhibitory role.
+
+Priming-though-translation paradigms, however, come with a cost.
+When prime words are auditorily presented, the task constrains the naming context to one of the languages.
 The consequence is a potential asymmetry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
 This might lead to a lower strength, and higher latency of the activation of the translation.
-
-Priming through translation paradigms prove the existence of cross-language phonological associations at the lexical level, as suggested by the fact that non-presented prime translations can interfere with subsequent target recognition.
-However, since participants are auditorily presented with a prime label, the contribution of sub-lexical facilitation through acoustic similarity cannot be ruled out.
-For instance, it is possible that the inhibitory priming through translation found by @von2012language is the result
-
-THERE IS NO EVIDENCE OF IMPLICIT NAMING IN BILINGUALS
 
@@
 The present study is aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
-Using an adaptation of [@mani2010infants], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
+Using an adaptation of [@mani2010infant], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
 We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
@@
 
-We collected data from `r n_participants_total$n[1]` children living in the Metropolitan Area of Barcelona (Spain), tested at the Laboratori de Recerca en Infància at the Universitat Pompeu Fabra.
+We collected data from `r n_participants_total` children living in the Metropolitan Area of Barcelona (Spain), tested at the Laboratori de Recerca en Infància at the Universitat Pompeu Fabra.
 Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r n_participants_total$n` children that participated, `r n_participants_sessions$session_1` participated once, `r n_participants_sessions$session_2` participated twice, and `r n_participants_sessions$session_3` participated three times.
+From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, `r n_participants_sessions$session_2` participated twice, and `r n_participants_sessions$session_3` participated three times.
 Recurrent participants were tested with at least XXX months of difference.
@@
 We categorised participants as monolingual if exposed to more than 80% or more of the time to their dominant language, and as bilingual otherwise.
-`r Words::English(n_participants_lp$n[1])` of the participants were categorised as monolinguals (`r n_participants_lp_sex[1]` female, `r n_participants_lp_sex[2]` male) and `n_participants_lp$n[2]` as Catalan/Spanish bilinguals (`r n_participants_lp_sex[3]` female, `r n_participants_lp_sex[4]` male) (see @tbl-participants for a detailed summary of participants' age and language profile).
+`r english::Words(n_participants_lp$n[1])` of the participants were categorised as monolinguals (`r n_participants_lp_sex$n[1]` female, `r n_participants_lp_sex$n[2]` male) and `r n_participants_lp$n[2]` as Catalan/Spanish bilinguals (`r n_participants_lp_sex$n[3]` female, `r n_participants_lp_sex$n[4]` male) (see @tbl-participants for a detailed summary of participants' age and language profile).
 Participants' vision was normal, none used glasses or any other type of vision corrector.
@@
 			  across(matches("doe_"), lst(mean, sd)),
-			  age_vctr = list(age),
+			  # age_vctr = list(age),
 			  .by = c(lp, test_language)) |> 
@@
 	   groupname_col = "lp") |> 
-	gt_plt_dist(age_vctr, type = "histogram") |>
+	# gt_plt_dist(age_vctr, type = "histogram") |>
 	fmt_number(is.numeric, decimals = 1) |> 
@@
 	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
-	cols_merge_range(age_min, age_max) |> 
-	cols_merge_uncert(age_mean, age_sd) |> 
-	cols_merge_uncert(doe_catalan_mean, doe_catalan_sd) |> 
-	cols_merge_uncert(doe_english_mean, doe_english_sd) |> 
-	cols_merge_uncert(doe_spanish_mean, doe_spanish_sd) |> 
+	cols_merge(c(age_min, age_max), 
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean, age_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_catalan_mean, doe_catalan_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_english_mean, doe_english_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_spanish_mean, doe_spanish_sd), 
+			   pattern = "{1} ({2})") |> 
 	tab_spanner("Age (months)", matches("age")) |> 
@@
 			   age_min = "Range",
-			   age_vctr = "Distribution",
+			   # age_vctr = "Distribution",
 			   doe_catalan_mean = "M (SD)",
@@
 ```{r vocab-values}
-vocabulary_bcn <- inner_join(vocabulary, 
-							 select(participants_bcn, session_id),
+vocabulary_bcn <- vocabulary |> 
+	inner_join(select(participants_bcn, session_id, lp, age_group),
 			   by = join_by(session_id))
+
+vocab_means <- vocabulary_bcn |> 
+	summarise(across(c(total_prop, l1_prop), lst(mean, sd)),
+			  n = n(),
+			  .by = c(age_group, lp)) %>%
+	mutate(across(matches("prop"), scales::percent)) %>%
+	split(paste0("age_", gsub(" months", "", .$age_group))) |> 
+	map(\(x) split(x, tolower(x$lp)))
 
@@
 Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
-We calculated two measures of receptive vocabulary size for each participant: *L1 vocabulary size* (proportion of words  reported as acquired in the checklist of the dominant language), and *total vocabulary size* (proportion of the words in both checklists reported as acquired) (see @fig-vocabulary).
-
+We calculated two measures of receptive vocabulary size for each participant: *L1 vocabulary size* (proportion of words  reported as acquired in the checklist of the dominant language), and *total vocabulary size* (proportion of the words in both checklists reported as acquired).
 `r n_imputed` (`r prop_imputed`) Families failed to provide a complete response to the BVQ within the two-week time limit, or did not provide a successful response to the questionnaire.
@@
 
+Overall, there was a substantial increase in both total and L1 vocabulary sizes associated to age (see @fig-vocabulary).
+Monolinguals showed overall higher L1 vocabulary sizes than monolinguals: they were reported to understand an average of `r vocab_means$age_21$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$l1_prop_sd`) at 30 months, while bilinguals  were reported to understand an average of `r vocab_means$age_21$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$l1_prop_sd`) at 30 months.
+Total vocabulary sizes showed the opposite pattern, with monolinguals infants being reported to understand `r vocab_means$age_21$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$total_prop_sd`) at 30 months, and bilinguals being reported to understand `r vocab_means$age_21$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$total_prop_sd`) at 30 months.
+
 ```{r fig-vocabulary}
@@
 Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
-Vocabulary size scores from the recurrent participants are shown linked."
-#| eval: false
+Grey lines connect vocabulary size scores from the recurrent participants.
+For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested."
 #| fig-width: 8
@@
 vocabulary_bcn |> 
-	inner_join(select(participants, child_id, session_id, age, lp),
-			   by = join_by(child_id, session_id)) |> 
 	pivot_longer(c(total_prop, l1_prop),
@@
 		   	factor(levels = c("Observed", "Imputed"))) |> 
-	ggplot(aes(age, prop, colour = is_imputed)) +
-	facet_grid(measure ~ lp) +
+	ggplot(aes(age_group, prop,
+			   colour = lp,
+			   fill = lp)) +
+	facet_wrap(~measure) +
 	geom_line(aes(group = child_id),
-			  alpha = 1/2,
-			  colour = "grey") +
-	geom_point() +
+			  colour = "grey",
+			  alpha = 1/4, linewidth = 3/4) +
+	geom_dots(aes(side = if_else(lp=="Monolingual", "left", "right")),
+			  dotsize = 2,
+			  scale = 0.5,
+			  alpha = 3/4) +
+	stat_summary(fun.data = mean_se,
+				 geom = "errorbar",
+				 linewidth = 3/4,
+				 width = 0.15,
+				 colour = "black",
+				 show.legend = FALSE,
+				 position = position_dodge(width = 1.15)) +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 size = 2,
+				 colour = "black",
+				 show.legend = FALSE,
+				 position = position_dodge(width = 1.15)) +
+	# geom_point(alpha = 1) +
 	labs(x = "Age (months)",
-		 y = "Vocabulary size (%)") +
-	theme(panel.grid.major = element_line(linetype = "dotted",
+		 y = "Vocabulary size",
+		 colour = "Group",
+		 fill = "Group") +
+	scale_y_continuous(labels = scales::percent) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
 											colour = "grey"),
@@
 The order of the trials was randomised across experimental session, so that each time a participant was tested, the order in which the prime-target-distractor was presented was randomised.
-Each participant was randomly assigned to one of the three lists in the corresponding language (their dominant language, see @sec-lp), and always the same list across their experimental sessions in the case of a recurrent participant.
+Each participant was randomly assigned to one of the three lists in the corresponding (dominant) language, and always the same list across their experimental sessions in the case of a recurrent participant.
 
@@
 @tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
-Lexical frequencies were extracted from the Catalan and Spanish corpora of the CHILDES database [@reference; @reference] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@reference; @reference].
+Lexical frequencies were extracted from the Catalan and Spanish corpora of the CHILDES database [@macwhinney2000childes; @sanchez2019childes] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@zipf1945meaning; @van2014subtlex].
 We defined word prevalence as the proportion of same-aged infants who were reported to understand the word in the BVQ database.
@@
 To make the pronunciation of the words as familiar as possible to each infant, we generated additional pronunciation variants for some words in Catalan and Spanish.
-Catalan words involving the /\textipa{L}/ phoneme in their Central Catalan variant (e.g., /\textipa{'Lu.n@}) were also recorded with such phoneme replaced by /j/ (e.g., /\textipa{'ju.n@}), a phonological process common in the Metropolitan Area of Barcelona [@reference].
+Catalan words involving the /\textipa{L}/ phoneme in their Central Catalan variant (e.g., /\textipa{'Lu.n@}) were also recorded with such phoneme replaced by /j/ (e.g., /\textipa{'ju.n@}), a phonological process common in the Metropolitan Area of Barcelona.
 Spanish words involving the /\textipa{T}/ phoneme were also generated replacing such phoneme with /\textipa{s}/ to better accommodate Latin variants of Spanish.
@@
 For each word, we created a picture with a typical referent.
-To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias-trejo2010].
+To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias2009lexical].
 
@@
 
-### Data processing
+### Data analysis
+
+#### Data processing
 
@@
 n_exc_test <- sum(!attrition$is_valid_gaze_test)
-n_exc_test_any <- sum(!attrition$is_valid_gaze_test_any)
+n_exc_test_each <- sum(!attrition$is_valid_gaze_test_each)
 n_exc_participants <- sum(!attrition_participants$is_valid_participant)
@@
 We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_any, big.mark = ",")`) [see @floccia2020translation for a similar approach].
+We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
 
@@
 
-### Data analysis
+#### Modelling approach
+
+```{r data-analysis}
+
+r_info <- sessionInfo()
+
+r_version <- glue::glue(r_info$R.version$major,
+						r_info$R.version$minor,
+						.sep = "."
+)
+stan_version <- "2.33.0"
+```
 
@@
 We implemented the model using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
-We ran `r english::words(dim(model_fit$fit_0)[2])` iteration chains using the by-default No U-Turn Sampler algorithm with `r format(niterations(model_fit$fit_0), big.mark = ",")` iterations each and an additional `r format(niterations(model_fits$fit_0), big.mark = ",")` warm-up iterations per chain.
+We ran `r english::words(dim(model_fits_bcn$fit_0$fit)[2])` iteration chains using the by-default No U-Turn Sampler algorithm with `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` iterations each and an additional `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` warm-up iterations per chain.
 
@@
 
-```{r fig-ptlt-recognition}
-#| label: fig-ptlt-recognition-aggr
-#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-#| fig-width: 11
+```{r results-0}
+var_labels <- c("b_Intercept" = "Intercept",
+				"b_age_std" = "Age (+1 SD)",
+				"b_condition1" = "Condition (U vs. RN)",
+				"b_condition1" = "Condition (RN vs. RC)",
+				"b_lp1" = "Group",
+				"sd_child_id__Intercept" = "Intercept",
+				"sd_child_id__age_std" = "Age",
+				"sd_child_id__lpBilingual" = "Group",
+				"sd_child_id:session_id__Intercept" = "Intercept",
+				"sd_child_id:session_id__age_std" = "Age",
+				"sd_child_id:session_id__lpBilingual" = "Group")
+
+get_coefs <- function(model, var_labels, ...) {
+	out <- model |> 
+		gather_draws(...) |> 
+		median_hdci(.width = 0.95) |> 
+		mutate(.variable_name = factor(.variable, 
+									   levels = names(var_labels), 
+									   labels = var_labels),
+			   mdn_label = sprintf("%.3f", .value),
+			   ci_label = sprintf("[%.3f, %.3f]", .lower, .upper)) |> 
+		arrange(.variable) |> 
+		select(.variable:.upper, matches("label")) %>%
+		split(janitor::make_clean_names(.$.variable))
+
+	return(out)
+}
+coefs <- map(model_fits_bcn, 
+			 \(x) get_coefs(model = x, var_labels,
+			 			   `b_.*`, `sd_.*`, regex = TRUE))
+
+get_loos <- function(x, y) {
+	out <- lst(m_0 = x, m_1 = y) |> 
+		loo_compare() |> 
+		as.data.frame() |> 
+		rownames_to_column("model") |>
+		arrange(model) |> 
+		select(model, elpd_diff, se_diff) |> 
+		mutate(diff_label = sprintf("%.3f", elpd_diff),
+			   se_label = sprintf("%.3f", se_diff))
+	return(out)
+}
+
+loos_tbl <- loo_compare(model_loos_bcn[1:5]) |> 
+	as.data.frame() |> 
+	rownames_to_column("model") |> 
+	select(model, matches("diff|elpd"))
+
+```
+
+```{r tbl-loos}
+loos_tbl[1:5] |> 
+	mutate(model = case_when(model=="fit_0" ~ "$\\mathcal{M}_{0}$",
+							 model=="fit_1" ~ "$\\mathcal{M}_{1}$",
+							 model=="fit_2" ~ "$\\mathcal{M}_{2}$",
+							 model=="fit_3" ~ "$\\mathcal{M}_{3}$",
+							 model=="fit_4" ~ "$\\mathcal{M}_{4}$",
+							 model=="fit_5" ~ "$\\mathcal{M}_{5}$")) |>
+	gt() |> 
+	fmt_number(is.numeric) |> 
+	# fmt_markdown(is.character, ) |> 
+	cols_label(elpd_diff = "ELPD (diff.)",
+			   se_diff = "SE ELPD (diff)",
+			   elpd_loo = "ELPD",
+			   se_elpd_loo = "SE ELPD")
+```
+
+@tbl-loos summarises the outputs of the LOO-CV model comparisons.
+Models $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ showed substantially better predicted performance than models $\mathcal{M}_{0}$ and $\mathcal{M}_{1}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
+All $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ models showed equivalent performance, suggesting that adding the two-way and three-way interactions between *Age*, *Group*, and *Condition*, did not improve the the fit of the model.
+We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{4}$.
+We report the median and 95% highest density interval of each fixed regression coefficient.
+
+The outcomes of $\mathcal{M}_{0}$, which only included *Age* and as main effect, revealed successful word recognition across participants.
+Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_0$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$b_intercept$ci_label`).
+The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_0$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_0$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_session_id_intercept$ci_label`).
+The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_0$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_0$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
+
+The 95% HDI of the coefficient of *Group* in $\mathcal{M}_{1}$ included zero ($\beta$ = `r coefs$fit_1$b_lp1$mdn_label`, 95% HDI = `r coefs$fit_1$b_lp1$ci_label`), indicating an equivalent overall target preference in monolinguals and bilinguals.
+The 95% HDI of the first contrast of this predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_2$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition1$ci_label`).
+The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_2$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition2$ci_label`).
+The overall target preference was equivalent across both pairwise condition comparisons.
+The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$fit_3$b_condition1_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1_lp1$ci_label`).
+The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$fit_3$b_condition2_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2_lp1$ci_label`).
+The outcomes of this model indicate that lack of differences in overall target looking time across conditions remained across monolinguals and bilinguals.
+
+Both younger and older participants showed equivalent looking time across conditions, as suggested by the fact that the 95% HDI of the two-way interaction between *Age* and the first *Condition* contrast included zero ($\beta$ = `r coefs$fit_4$b_condition1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_age_std$ci_label`), as well as the interaction between *Age* and the second *Condition* contrast ($\beta$ = `r coefs$fit_4$b_condition2_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_age_std$ci_label`).
+This pattern of results was found in both monolinguals and bilinguals, as the 95% HDI of the three-way interaction between *Age*, *Group*, and *Condition* included zero both the first ($\beta$ = `r coefs$fit_4$b_condition1_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_lp1_age_std$ci_label`) and second ($\beta$ = `r coefs$fit_4$b_condition2_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_lp1_age_std$ci_label`) contrast of *Condition*.
+
+```{r timecourse}
+make_std <- function(x, mean, sd) (x - mean) / sd
+
+timebin_values <- make_std(seq(0, 17, length.out = 100),
+						   mean(data_bcn$timebin),
+						   sd(data_bcn$timebin))
+
+age_values <- make_std(c(20, 30),
+					   mean(data_bcn$age),
+					   sd(data_bcn$age))
+
+nd <- expand_grid(distinct(data_bcn, condition, lp),
+				  timebin_std = timebin_values,
+				  age_std = age_values)
+
+epreds <- add_epred_draws(nd, model_fits_bcn$fit_4, 
+						  re_formula = NA,
+						  ndraws = NULL,
+						  value = ".elog") |> 
+	mutate(age_std = factor(age_std,
+							levels = age_values, 
+							labels = paste0(c(20, 30), " months")))
+
+epreds_chance <- epreds |> 
+	median_hdci() |> 
+	mutate(is_lower_positive = .lower > 0) |> 
+	filter(is_lower_positive) |> 
+	summarise(over_chance = min(timebin_std),
+			  .by = c(lp, condition, age_std)) |> 
+	mutate(over_chance = (over_chance * 
+						  	sd(data_bcn$timebin) +
+						  	mean(data_bcn$timebin))*100+300)
+
+epreds_chance_report <- epreds_chance |> 
+	mutate(over_chance = sprintf("%.2f", over_chance),
+		   age_std = paste0("age_", gsub(" months", "", age_std))) |> 
+	arrange(lp, age_std) %>%
+	split(tolower(.$lp)) |> 
+	map(\(x) split(x, x$age_std)) 
+```
+
+An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
+Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
+
+```{r fig-epreds}
+#| label: fig-epreds
+#| fig-cap: "Posterior mean prdictions of the time course of target fixation in the test phase.
+Lines and intervals indicate the median and 95% credible interval of the posterior predictions, respectively."
+#| fig-width: 8
 #| fig-height: 4
-data_time_bcn |> 
-	drop_na(.prop) |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(lp, timebin, session_id)) |> 
-	ggplot(aes(timebin, .prop)) +
-	facet_wrap(~lp, nrow = 1, scales = "free_x") +
-	geom_line(aes(group = session_id),
-			  colour = "grey",
-			  alpha = 1/10) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = "mean_se",
-				 geom = "errorbar",
-				 width = 0.35,
-				 linewidth = 2/4) +
-	stat_summary(fun = "mean",
-				 geom = "point",
-				 size = 1.2) +
-	stat_summary(fun = "mean",
-				 geom = "line",
-				 linewidth = 2/4) +
-	labs(x = "Time (ms)",
-		 y = "PTLT") +
-	scale_x_continuous(breaks = seq(0, 20, 2),
-					   labels = \(x) format(x*100+300, big.mark = ",")) +
-	scale_y_continuous(labels = scales::percent,
-					   breaks = seq(0, 1, 0.2),
-					   limits = c(0, 1)) +
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  legend.position = "none")
-```
-
-```{r tbl-coefs}
-post <- gather_draws(fit_1, `b_.*`, regex = TRUE)
-
-ggplot(post, aes(.value)) +
-	facet_wrap(~.variable, scales = "free") +
-	geom_histogram(bins = 15, colour = "white",
-				   position = position_nudge(y = 0.1),
-				   fill = "grey80") +
-	geom_errorbar(data = mean_qi(post),
-				  aes(xmin = .lower, xmax = .upper, y = 0),
-				  width = 1,
-				  linewidth = 3/4) +
-	geom_point(data = mean_qi(post),
-			   aes(x = .value, y = 0),
-			   size = 2) +
-	scale_y_continuous(limits = c(0, 500))
-```
-
-### Hypothesis 1: within-language phonological priming
-
-```{r fig-ptlt-recognition-condition}
-#| label: fig-ptlt-recognition-condition
-#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
-#| fig-width: 11
-#| fig-height: 4
-data_time_bcn |> 
-	summarise(.prop = mean(.prop),
-			  .by = c(lp, timebin, condition, session_id)) |> 
-	ggplot(aes(timebin, .prop, colour = condition)) +
-	facet_grid(~lp) +
-	# geom_rug(aes(x = timebin[is.na(.prop)])) +
-	# geom_line(aes(group = interaction(condition, session_id)),
-	# 		  alpha = 1/8) +
-	geom_hline(yintercept = 0.5, linetype = "dashed") +
-	stat_summary(fun.data = "mean_se",
-				 geom = "errorbar",
-				 width = 0.35,
-				 linewidth = 2/4) +
-	stat_summary(fun = "mean",
-				 geom = "point",
-				 size = 1.2) +
-	stat_summary(fun = "mean",
-				 geom = "line",
-				 linewidth = 2/4) +
-	labs(x = "Time (ms)",
-		 y = "PTLT",
-		 colour = "Condition") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	scale_y_continuous(labels = scales::percent,
-					   breaks = seq(0, 1, 0.05)) +
-	theme(legend.position = "top",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-```
-
-### Hypothesis 2: cross-language phonological priming
-
-```{r fig-time}
-#| label: fig-time
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-make_std <- function(x, mean, sd) (x - mean) / sd
-
-timebin_values <- make_std(seq(0, 17, length.out = 100),
-						   mean(data_time$timebin),
-						   sd(data_time_bcn$timebin))
-
-age_values <- make_std(c(21, 25, 30),
-					   mean(data_time_bcn$age),
-					   sd(data_time_bcn$age))
-
-nd <- expand_grid(condition = levels(fit_3$data$condition),
-				  timebin_std = timebin_values,
-				  age_std = age_values,
-				  # sesion_id = first(data$session_id),
-				  # age = c(21, 25, 30),
-				  lp = levels(fit_3$data$lp))
-
-epreds <- add_epred_draws(newdata = nd,
-						  object = fit_3,
-						  ndraws = NULL,
-						  re_formula = NA,
-						  value = ".value") |> 
-	mutate(.value = plogis(.value)) |> 
-	mean_qi() |> 
-	mutate(lp = factor(lp, 
-					   levels = c("Monolingual (English)",
-					   		   "Monolingual",
-					   		   "Bilingual")),
-		   age_std = factor(age_std, 
-		   				 levels = age_values,
-		   				 labels = paste0(c(21, 25, 30), " months")))
-
 epreds |> 
-	ggplot(aes(timebin_std, .value,
+	ggplot(aes(timebin_std, .elog,
 			   colour = condition,
@@
 	facet_grid(lp~age_std) +
-	geom_hline(yintercept = 0.5,
-			   linetype = "dashed") +
-	geom_ribbon(aes(ymin = .lower, ymax = .upper),
-				alpha = 0.5,
-				linewidth = 0) +
-	geom_line(linewidth = 3/4) +
-	# stat_summary(data = data_time_bcn,
-	# 			 aes(y = .elog),
-	# 			 fun = mean,
-	# 			 geom = "point",
-	# 			 size = 2) +
+	geom_hline(yintercept = 0, linetype = "dashed") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
+				 alpha = 1/2,
+				 linewidth = NA) +
+	stat_summary(fun = mean,
+				 geom = "line",
+				 linewidth = 3/4) +
 	labs(x = "Time (ms)",
@@
 		 fill = "Condition") +
-	scale_x_continuous(breaks = make_std(seq(0, 17, 2),
-										 mean(data_time$timebin),
-										 sd(data_time$timebin)),
-					   labels = \(x) format(seq(0, 17, 2)*100+200, big.mark = ",")) +
-	theme(legend.position = "top",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								linetype = "dotted"))
-
-ggsave(file.path("img", "model-time.jpeg"),
-	   height = 4, width = 10,
-	   dpi = 800)
-```
-
-### Hypothesis 3: emergence of phonological association
-
-### Hypothesis 4: the compating role of age and vocabulary
-
-In a first analysis, we examined the effect of phonological priming.
-We compared participants' looking preference for the target in related and unrelated trials.
-We first compared the aggregated probability of target looking across time bins in both conditions for each language group.
-
-```{r fig-time-total}
-#| label: fig-time-total
-#| fig-height: 6
-#| fig-width: 8
-#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
-(A) Mean posterior probability of target looking across the time course of the trial.
-Black lines and intervals indicate the psoterior mean and 95% credible intervals.
-Points indicate the mean probability of target looking across participants.
-(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
-The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
-voc_values <- seq(0.25, 1, 0.25)
-
-nd <- expand_grid(condition = levels(model_fits_time$fit_time_2$data$condition),
-				  timebin = seq(0, 17, length.out = 100),
-				  voc_total = voc_values,
-				  # sesion_id = first(data$session_id),
-				  # age = c(21, 25, 30),
-				  lp = levels(model_fits_time$fit_time_2$data$lp))
-
-epreds <- add_epred_draws(newdata = nd,
-						  object = model_fits_time$fit_time_2,
-						  ndraws = 20,
-						  re_formula = NA,
-						  value = ".value") |> 
-	mean_qi() |> 
-	mutate(lp = factor(lp, 
-					   levels = c("Monolingual (English)",
-					   		   "Monolingual",
-					   		   "Bilingual")),
-		   voc_total = factor(x = voc_total, 
-		   				   levels = voc_values,
-		   				   labels = scales::percent(voc_values)))
-
-epreds |> 
-	ggplot(aes(timebin, .value,
-			   colour = condition,
-			   fill = condition)) +
-	facet_grid(lp~voc_total) +
-	geom_hline(yintercept = 0,
-			   linetype = "dashed") +
-	geom_ribbon(aes(ymin = .lower, ymax = .upper),
-				alpha = 0.5,
-				linewidth = 0) +
-	geom_line(linewidth = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "Logit (Target looking)",
+	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
+										 mean(data_bcn$timebin),
+										 sd(data_bcn$timebin)),
+					   labels = \(x) format(seq(3e2, 2e3, 3e2),
+					   					 big.mark = ",")) &
+	theme(panel.grid.major.y = element_line(colour = "grey",
+											linetype = "dotted"),
+		  legend.position = "top")
+```
+
+In an exploratory analysis, we compared the model-estimated time points at which participants' gaze behaviour showed evidence of target looking above chance level (50%).
+We defined the recognition time of the trial as the earliest time point at which the lower bound of the 95% HDI posterior mean prediction of the target looking excluded zero.
+As expected, the recognition times were on average shorter for older infants than for younger infants.
+Differences between conditions were larger in bilinguals than in monolinguals, especially in the older group.
+The recognition time for monolingual 20-month-olds was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
+In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+
+```{r fig-recognition}
+#| label: fig-recognition
+#| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
+#| fig-width: 7
+#| fig-height: 3
+epreds_chance |> 
+	ggplot(aes(lp, over_chance,
+			   colour = sort(condition),
+			   fill = sort(condition))) + 
+	facet_wrap(~age_std) +
+	geom_point(shape = 16, size = 4) +
+	geom_line(aes(group = condition),
+			  linewidth = 1) +
+	# geom_point(size = 3) +
+	labs(x = "Group",
+		 y = "Recognition time (ms)",
 		 colour = "Condition",
 		 fill = "Condition") +
-	scale_x_continuous(breaks = seq(0, 20, 4),
-					   labels = \(x) format(x*100+200, big.mark = ",")) +
-	theme(legend.position = "top",
-		  panel.grid.major = element_line(colour = "grey",
-		  								linetype = "dotted"))
-
-ggsave(file.path("img", "model-time-voc-total.jpeg"),
-	   height = 5.5, width = 10,
-	   dpi = 800)
-```
-
-{{< pagebreak >}}
-
-## Discussion
-
-# Study 2
-
-## Methods
-
-### Participants
-
-```{r}
-#| label: participants-numbers-oxf
-participants_oxf <- filter(participants, location=="Oxford")
-
-n_participants_total <- nrow(distinct(participants_oxf, child_id))
-n_sessions_total <- count(participants_oxf)
-
-n_participants_sex <- participants_oxf |> 
-	distinct(sex, child_id) |> 
-	count(sex)
-
-n_participants_sessions <- participants_oxf |> 
-	count(child_id, name = "n_sessions") |> 
-	count(n_sessions) |> 
-	group_split(n_sessions) |> 
-	set_names(paste0("session_", 1:2)) |> 
-	map("n")
-
-ages <- participants_oxf |> 
-	summarise(n = n(),
-			  n_participants = n_distinct(child_id),
-			  across(age, lst(mean, sd, min, max)),
-			  across(matches("doe_"), lst(mean, sd)),
-			  age_vctr = list(age),
-			  .by = c(lp, test_language))
-
-```
-
-We collected data from `r n_participants_total$n[1]` children (`r n_participants_sex[1]` female, `r n_participants_sex[2]` male, `r n_participants_sex[3]` sex not reported, age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]), living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford.
-Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r n_participants_total$n` children that participated, `r n_participants_sessions$session_1` participated once, and `r n_participants_sessions$session_2` participated twice.
-Recurrent participants were tested with at least XXX months of difference.
-We gathered a total of `r n_sessions_total$n` testing sessions.
-All participants were being raised in exclusively British English monolingual homes.
-
-### Vocabulary size
-
-```{r vocab-values}
-vocabulary_oxf <- inner_join(vocabulary, 
-							 select(participants_oxf, session_id),
-							 by = join_by(session_id))
-```
-
-We collected vocabulary data using parental responses to the Oxford Communicative Development Inventory (OCDI) [@hamilton2000infant].
-Families were sent the questionnaire immediately after each experimental session, and were given two weeks to fill it.
-Since all vocabulary sizes of English monolingual infants were only assessed in English, both *L1 vocabulary* and *total vocabulary* sizes were identical (see @fig-vocabulary-oxf).
-
-```{r fig-vocabulary-oxf}
-#| label: fig-vocabulary
-#| fig-cap: "Participant vocabulary sizes across ages and language profiles.
-Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
-Vocabulary size scores from the recurrent participants are shown linked."
-#| eval: false
-#| fig-width: 4
-#| fig-height: 4
-vocabulary_oxf |> 
-	inner_join(select(participants, child_id, session_id, age, lp),
-			   by = join_by(child_id, session_id)) |> 
-	ggplot(aes(age, total_prop)) +
-	geom_line(aes(group = child_id),
-			  alpha = 1/2,
-			  colour = "grey") +
-	geom_point(colour = clrs[1]) +
-	labs(x = "Age (months)",
-		 y = "Vocabulary size (%)") +
-	theme(panel.grid.major = element_line(linetype = "dotted",
-										  colour = "grey"),
+	scale_y_continuous(breaks = seq(0, 1e3L, 50)) +
+	theme(panel.grid.major.y = element_line(colour = "grey",
+											linetype = "dotted"),
+		  panel.grid.minor.y = element_line(colour = "grey",
+		  								  linetype = "dotted"),
 		  legend.position = "top",
-		  legend.title = element_blank())
-```
-
-### Stimuli
-
-New stimuli lists were generated to adapt the experimental procedure to English-learning infants.
-Stimuli lists were created following the same constraints as in Study 1.
-Auditory stimuli were recorded following the same procedure as in Study 1, produced by Southern British English native female speaker in a toddler-directed manner.
-Audio and picture processing were performed following the same workflow as in Study 1.
-
-### Procedure and apparatus
-
-Same as in Study 1.
-The study was run using a custom Matlab script, PresentMate, based on the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox].
-Visual fixations were recorded using a Tobii TX 300 eye-tracker and a 23-in screen of 1920 $\times$ 1080 resolution.
-The Tobii Analytics SDK 3.0 was used to interact with the eye-tracking while the experiment was running.
-Sampling rate was set at 120 Hz.
-A 9-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
-
-### Data processing
-
-Same as in Study 1.
-
-### Data analysis
-
-## Results
-
-# General discussion
-
-IMPLICIT NAMING
-Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
-@duta2012erp presented name-known pictures in silence for one second.
-After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
-In some trials the auditory label corresponded to a canonical realisation of the word-form.
-In other trials, the word was mispronounced.
-Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
-A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
-This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
-
-THE ROLE OF COGNATENESS IN WORD ACQUISITION
-
-For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
-This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
-
-A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
-Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
-Cognates are form-similar translation equivalents.
-Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
-
-Some recent studies have investigated the recognition of mispronounced words comparing monolingual and bilingual toddlers.
-Overall, these studies do not find differences between monolinguals and bilinguals [@von2019impact; @wewalaarachchi2017vowels].
-Evidence for differential processing of cognate and non-cognate words is provided by Ramon-Casas and colleagues who observed that Spanish-Catalan 24-month-olds were more prone to accept mispronunciations when the stimuli involved cognate words than when they involved non-cognate words [@ramon2009vowel; @ramon2010non].
-
-## Summary
-
-## Context
-
-## Facilitation vs. inhibition
-
-## Onsets vs. offsets
-
-## Problems and generalisatility
-
-## Future steps
-
-## Conclusions
+		  axis.title.x = element_blank())
+```
 
 # References
-
-{{< pagebreak >}}
-
-# Appendix
-
-## Appendix A: imputing voabulary size scores
-
-```{r fig-vocabulary-imputation}
-vocabulary_tmp <- vocabulary |> 
-	left_join(select(participants, child_id, vocab_id, age),
-			  by = join_by(child_id, vocab_id)) |> 
-	relocate(child_id) |> 
-	filter(is_imputed)
-
-bvq_data$vocabulary |> 
-	inner_join(distinct(bvq_data$logs, child_id, response_id, lp, age),
-			   by = join_by(response_id)) |> 
-	mutate(is_imputed = FALSE) |> 
-	bind_rows(vocabulary_tmp) |> 
-	pivot_longer(ends_with("_prop"),
-				 names_to = "measure",
-				 values_to = "prop") |> 
-	drop_na(prop) |> 
-	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed"),
-		   measure = factor(measure,
-		   				 levels = c("total_prop",
-		   				 		   "l1_prop",
-		   				 		   "l2_prop",
-		   				 		   "concept_prop",
-		   				 		   "te_prop"),
-		   				 labels = c("Total",
-		   				 		   "L1",
-		   				 		   "L2",
-		   				 		   "Conceptual",
-		   				 		   "TE"))) |> 
-	ggplot(aes(age, prop, 
-			   colour = is_imputed,
-			   fill = is_imputed)) +
-	facet_wrap(~measure) +
-	geom_point(alpha = 1/4, size = 1) +
-	geom_smooth(method = "glm", 
-				formula = "y ~ x",
-				method.args = list(family = "binomial"), 
-				# se = FALSE,
-				size = 1) +
-	labs(x = "Age (months)",
-		 y = "Vocabulary size",
-		 fill = "Imputed",
-		 colour = "Imputed") +
-	theme(legend.position = c(1, 0),
-		  legend.justification = c(1, 0),
-		  legend.title = element_blank())
-
-```
-
-{{< pagebreak >}}
-
-## Appendix B: distribution of prime and target looking times
-
-```{r fig-dist-prime}
-#| label: fig-dist-prime
-#| fig-height: 4
-#| fig-width: 8
-looking_times |> 
-	mutate(prime_time = cut(prime_time, 
-							seq(0, 1.5, 0.1),
-							labels = FALSE,
-							include.lowest = TRUE)) |> 
-	add_count(lp, age_group, name = "n_total") |> 
-	count(lp, age_group, prime_time, n_total) |> 
-	mutate(n = n / n_total) |> 
-	ggplot(aes(prime_time, n)) +
-	facet_grid(lp~age_group) +
-	annotate(geom = "rect",
-			 fill = "orange",
-			 ymin = -Inf,
-			 ymax = Inf,
-			 xmin = 0,
-			 xmax = 0.75*10,
-			 alpha = 1/3,
-			 colour = NA) +
-	# annotate(label = "Excluded trials",
-	# 		 geom = "text",
-	# 		  x = (0.75/2)*10,
-	# 		  y = 1)
-	geom_col(fill = "black") +
-	labs(x = "Prime looking time (s)",
-		 y = "Proportion of trials") +
-	scale_x_continuous(labels = \(x) x/10) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"))
-```
-
-```{r fig-dist-target}
-#| label: fig-dist-target
-#| fig-height: 4
-#| fig-width: 8
-looking_times |> 
-	mutate(target_time = cut(target_time, 
-							 seq(0, 2, 0.1),
-							 labels = FALSE,
-							 include.lowest = TRUE)) |> 
-	add_count(lp, age_group, name = "n_total") |> 
-	count(lp, age_group, target_time, n_total) |> 
-	mutate(n = n / n_total) |> 
-	ggplot(aes(target_time, n)) +
-	facet_grid(lp~age_group) +
-	# annotate(label = "Excluded trials",
-	# 		 geom = "text",
-	# 		  x = (0.75/2)*10,
-	# 		  y = 1)
-	geom_col(fill = "black") +
-	labs(x = "Targets looking time (s)",
-		 y = "Proportion of trials") +
-	scale_x_continuous(labels = \(x) x/10) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"))
-```
-
-{{< pagebreak >}}
-
-## Appendix C: prime and test looking times
-
-```{r fig-looking-times}
-#| label: fig-looking-times
-#| fig-height: 8
-#| fig-width: 8
-#| fig-cap: "Looking time (s) to the prime and target AOI against audio duration. In longer audios, participants are expected to look longer to the prime and target picture."
-
-looking_times |>
-	left_join(select(attrition_trials, 
-					 filename, trial, is_valid_trial),
-			  by = join_by(filename, trial)) |>
-	filter(is_valid_trial) |> 
-	ggplot(aes(duration,
-			   prime_time,
-			   colour = trial_type, 
-			   fill = trial_type,
-			   shape = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_point(alpha = 0.5, 
-			   size = 1) +
-	geom_smooth(method = "lm") +
-	theme(axis.title.x = element_blank()) +
-
-	looking_times |>
-	left_join(select(attrition_trials, 
-					 filename, trial, is_valid_trial),
-			  by = join_by(filename, trial)) |>
-	filter(is_valid_trial) |> 
-	ggplot(aes(duration,
-			   target_time,
-			   colour = trial_type, 
-			   fill = trial_type,
-			   shape = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_point(alpha = 0.5,
-			   size = 1) +
-	geom_smooth(method = "lm",
-				formula = "y ~ x") +
-	plot_layout(ncol = 1, guides = "collect") &
-	plot_annotation(tag_levels = "A") &
-	labs(x = "Audio duration (s)",
-		 y = "Looking time (1.0-2.0 seconds)",
-		 colour = "Prime type",
-		 fill = "Prime type",
-		 shape = "Prime type") 
-```
-
-## Appendix D: vocabulary checklist validity
-
-```{r fig-validity-target}
-gaze_tmp <- gaze |> 
-	filter(phase=="Target-Distractor",
-		   between(timestamp, time_subset[1], time_subset[2])) |> 
-	select(session_id, trial, phase, timestamp,
-		   is_gaze_target, is_gaze_distractor, trial_type) |> 
-	mutate(condition = recode_condition(trial_type))
-
-vocabulary_tmp <- rename_with(vocabulary,  
-							  \(x) gsub("_prop", "", paste0("voc_", x)), 
-							  matches("_prop"))
-
-participants_tmp <- participants |> 
-	select(child_id, session_id, age_group, age, lp)
-
-attrition_trials_tmp <- get_attrition_trials(
-	participants = participants,
-	vocabulary = vocabulary,
-	vocabulary_by = c("target"),
-	aoi_coords = aoi_coords,
-	gaze = gaze,
-	min_looking = c(prime = 0.75,
-					test = 1.00,
-					test_each = 0.00,
-					test_any = 0.1)) |> 
-	select(session_id, trial, samples, is_valid_vocab_all) |> 
-	unnest_wider(is_valid_vocab_all) |> 
-	rename_with(\(x) gsub("is_valid_vocab_", "", x))
-
-attrition_participants_tmp <- attrition_participants |> 
-	filter(is_valid_participant) |> 
-	select(session_id)
-
-data <- gaze_tmp |>
-	inner_join(attrition_trials_tmp, by = join_by(session_id, trial)) |> 
-	inner_join(attrition_participants_tmp, by = join_by(session_id)) |> 
-	mutate(condition = recode_condition(trial_type)) |> 
-	select(session_id, trial, condition, is_gaze_target, is_gaze_distractor,
-		   is_valid_vocab_all) |> 
-	# aggregated across trials by participant, time bin and condition
-	# see Chow et al. (2018)
-	summarise(sum_target = sum(is_gaze_target, na.rm = TRUE),
-			  sum_distractor = sum(is_gaze_distractor, na.rm = TRUE),
-			  .nsamples = sum(is_gaze_target | is_gaze_distractor, na.rm = TRUE),
-			  .ntrials = length(unique(trial)),
-			  .by = c(session_id, condition, is_valid_vocab_all)) |> 
-	# empirical logit with adjustment
-	# see Barr et al. (2008)
-	mutate(.nsamples = sum_target + sum_distractor,
-		   .prop = ifelse(.nsamples==0, 0, sum_target / .nsamples),
-		   .elog = log((sum_target + .5)/(sum_distractor + .5))) |> 
-	rename(.sum = sum_target) |> 
-	arrange(desc(session_id), condition) |> 
-	inner_join(participants_tmp, by = join_by(session_id)) |> 
-	inner_join(vocabulary_tmp, by = join_by(child_id, session_id)) |> 
-	mutate(across(c(.nsamples), as.integer),
-		   across(c(child_id, session_id, lp, condition, age_group), as.factor),
-		   across(c(age, voc_l1),
-		   	   \(x) scale(x, scale = TRUE)[, 1],
-		   	   .names = "{.col}_std")) |> 
-	select(child_id, session_id, age_group, age, voc_l1, voc_total, lp,
-		   condition,  .sum, .prop, .elog, .nsamples,
-		   matches("std"), is_valid_vocab_all)
-
-# set a priori contrasts
-contrasts(data$condition) <- cbind(c(-0.5, 0.5, 0),
-								   c(0, -0.5, 0.5))
-contrasts(data$lp) <- cbind(c(-0.5, 0.25, 0.25),
-							c(0, -0.5, 0.5))
-contrasts(data$age_group) <- cbind(c(-0.5, 0.5, 0),
-								   c(0, -0.5, 0.5))
-
-data |> 
-	unnest_wider(is_valid_vocab_all) |>
-	rename_with(\(x) gsub("is_valid_vocab_", "", x)) |> 
-	select(session_id, lp, .elog, target) |> 
-	arrange(session_id, target) |> 
-	summarise(.elog_mean = mean(.elog),
-			  .elog_sd = sd(.elog),
-			  n = n(),
-			  .by = c(lp, target)) |> 
-	mutate(target = ifelse(target, "Yes", "No"),
-		   .elog_se = .elog_sd/sqrt(n),
-		   .elog_lower = .elog_mean - .elog_se*1.96,
-		   .elog_upper = .elog_mean + .elog_se*1.96,
-	) |> 
-	ggplot(aes(lp, .elog_mean, 
-			   ymin = .elog_lower,
-			   ymax = .elog_upper,
-			   colour = target)) +
-	facet_wrap(~lp, ncol = 1, scales = "free_x") +
-	geom_errorbar(width = 0.2, linewidth = 3/4, 
-				  position = position_dodge(width = 0.25)) +
-	geom_point(size = 2,
-			   position = position_dodge(width = 0.25)) +
-	geom_hline(yintercept = 0,
-			   linetype = "dashed") +
-	labs(x = "Condition",
-		 y = "P(Target looking)", 
-		 colour = "Knows the target word") +
-	theme(legend.position = "none",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-
-get_data_time(gaze = gaze,
-			  participants = participants,
-			  stimuli = stimuli,
-			  vocabulary = vocabulary,
-			  attrition_trials = attrition_trials,
-			  attrition_participants = attrition_participants,
-			  time_subset = c(0, 2),
-			  contrast = "related",
-			  is_valid_vocab_all,
-			  clean = FALSE) |> 
-	unnest_wider(is_valid_vocab_all) |>
-	select(session_id, age, lp, timebin, .elog, target) |> 
-	arrange(session_id, target) |> 
-	summarise(.elog_mean = mean(.elog),
-			  .elog_sd = sd(.elog),
-			  n = n(),
-			  .by = c(timebin, lp, target)) |> 
-	mutate(target = ifelse(target, "Yes", "No"),
-		   .elog_se = .elog_sd/sqrt(n),
-		   .elog_lower = .elog_mean - .elog_se*1.96,
-		   .elog_upper = .elog_mean + .elog_se*1.96,
-	) |> 
-	ggplot(aes(timebin, .elog_mean,
-			   ymin = .elog_lower,
-			   ymax = .elog_upper,
-			   colour = target,
-			   fill = target)) +
-	facet_wrap(~lp, ncol = 1, scales = "free_x") +
-	geom_line(linewidth = 1/2) +
-	geom_ribbon(alpha = 1/2,
-				colour = NA) +
-	geom_point(size = 2) +
-	geom_hline(yintercept = 0,
-			   linetype = "dashed") +
-	labs(x = "Condition",
-		 y = "P(Target looking)", 
-		 fill = "Knows the target word",
-		 colour = "Knows the target word") +
-	theme(legend.position = "top",
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"),
-		  axis.title.y = element_blank(),
-		  axis.line.x = element_line()) +
-
-	plot_layout(ncol = 2,
-				widths = c(0.2, 0.8)) &
-	scale_y_continuous(limits = c(-0.5, 1.25))
-```

### 2023-11-03 manuscript/manuscript.qmd

@@
 
-set.seed(888)
+set.seed(1234)
 ```
@@
 		  legend.title = element_blank())
-
 ```
@@
 
+# Study 2
+
+## Methods
+
+### Participants
+
+```{r}
+#| label: participants-numbers-oxf
+participants_oxf <- filter(participants, location=="Oxford")
+
+n_participants_total <- nrow(distinct(participants_oxf, child_id))
+n_sessions_total <- count(participants_oxf)
+
+n_participants_sex <- participants_oxf |> 
+	distinct(sex, child_id) |> 
+	count(sex)
+
+n_participants_sessions <- participants_oxf |> 
+	count(child_id, name = "n_sessions") |> 
+	count(n_sessions) |> 
+	group_split(n_sessions) |> 
+	set_names(paste0("session_", 1:2)) |> 
+	map("n")
+
+ages <- participants_oxf |> 
+	summarise(n = n(),
+			  n_participants = n_distinct(child_id),
+			  across(age, lst(mean, sd, min, max)),
+			  across(matches("doe_"), lst(mean, sd)),
+			  age_vctr = list(age),
+			  .by = c(lp, test_language))
+
+```
+
+We collected data from `r n_participants_total$n[1]` children (`r n_participants_sex[1]` female, `r n_participants_sex[2]` male, `r n_participants_sex[3]` sex not reported, age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]), living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford.
+Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
+From the `r n_participants_total$n` children that participated, `r n_participants_sessions$session_1` participated once, and `r n_participants_sessions$session_2` participated twice.
+Recurrent participants were tested with at least XXX months of difference.
+We gathered a total of `r n_sessions_total$n` testing sessions.
+All participants were being raised in exclusively British English monolingual homes.
+
+### Vocabulary size
+
+```{r vocab-values-oxf}
+vocabulary_oxf <- inner_join(vocabulary, 
+							 select(participants_oxf, session_id),
+							 by = join_by(session_id))
+```
+
+We collected vocabulary data using parental responses to the Oxford Communicative Development Inventory (OCDI) [@hamilton2000infant].
+Families were sent the questionnaire immediately after each experimental session, and were given two weeks to fill it.
+Since all vocabulary sizes of English monolingual infants were only assessed in English, both *L1 vocabulary* and *total vocabulary* sizes were identical (see @fig-vocabulary-oxf).
+
+```{r fig-vocabulary-oxf}
+#| label: fig-vocabulary-oxf
+#| fig-cap: "Participant vocabulary sizes across ages and language profiles.
+Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
+Vocabulary size scores from the recurrent participants are shown linked."
+#| eval: false
+#| fig-width: 4
+#| fig-height: 4
+vocabulary_oxf |> 
+	inner_join(select(participants, child_id, session_id, age_group),
+			   by = join_by(child_id, session_id)) |> 
+	ggplot(aes(age_group, l1_prop)) +
+	geom_line(aes(group = child_id),
+			  colour = "grey",
+			  alpha = 1/4, linewidth = 3/4) +
+	geom_dots(dotsize = 2,
+			  colour = clrs[5],
+			  fill = clrs[5],
+			  scale = 0.5,
+			  side = "both",
+			  alpha = 3/4) +
+	stat_summary(fun.data = mean_se,
+				 geom = "errorbar",
+				 linewidth = 3/4,
+				 width = 0.1,
+				 colour = "black",
+				 show.legend = FALSE) +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 size = 2,
+				 colour = "black",
+				 show.legend = FALSE) +
+	# geom_point(alpha = 1) +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size",
+		 colour = "Group",
+		 fill = "Group") +
+	scale_y_continuous(labels = scales::percent) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"),
+		  legend.position = "top",
+		  legend.title = element_blank())
+```
+
+### Stimuli
+
+New stimuli lists were generated to adapt the experimental procedure to English-learning infants.
+Stimuli lists were created following the same constraints as in Study 1.
+Auditory stimuli were recorded following the same procedure as in Study 1, produced by Southern British English native female speaker in a toddler-directed manner.
+Audio and picture processing were performed following the same workflow as in Study 1.
+
+### Procedure and apparatus
+
+Same as in Study 1.
+The study was run using a custom Matlab script, PresentMate, based on the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox].
+Visual fixations were recorded using a Tobii TX 300 eye-tracker and a 23-in screen of 1920 $\times$ 1080 resolution.
+The Tobii Analytics SDK 3.0 was used to interact with the eye-tracking while the experiment was running.
+Sampling rate was set at 120 Hz.
+A 9-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
+
+### Data analysis
+
+Same as in Study 1, but removing the *Group* predictor from the models, as only monolingual infants were tested.
+
+## Results
+
+```{r results-oxf}
+var_labels <- c("b_Intercept" = "Intercept",
+				"b_age_std" = "Age (+1 SD)",
+				"b_condition1" = "Condition (U vs. RN)",
+				"b_condition1" = "Condition (RN vs. RC)",
+				"sd_child_id__Intercept" = "Intercept",
+				"sd_child_id__age_std" = "Age",
+				"sd_child_id:session_id__Intercept" = "Intercept",
+				"sd_child_id:session_id__age_std" = "Age",
+				"sd_child_id:session_id__lpBilingual" = "Group")
+
+coefs <- map(model_fits_oxf, 
+			 \(x) get_coefs(model = x, var_labels,
+			 			   `b_.*`, `sd_.*`, regex = TRUE))
+
+loos_tbl <- loo_compare(model_loos_oxf) |> 
+	as.data.frame() |> 
+	rownames_to_column("model") |> 
+	select(model, matches("diff|elpd"))
+
+```
+
+```{r tbl-loos-oxf}
+loos_tbl |> 
+	mutate(model = case_when(model=="fit_oxf_0" ~ "$\\mathcal{M}_{0}$",
+							 model=="fit_oxf_1" ~ "$\\mathcal{M}_{1}$",
+							 model=="fit_oxf_2" ~ "$\\mathcal{M}_{2}$",
+							 model=="fit_oxf_3" ~ "$\\mathcal{M}_{3}$")) |>
+	gt() |> 
+	fmt_number(is.numeric) |> 
+	# fmt_markdown(is.character, ) |> 
+	cols_label(elpd_diff = "ELPD (diff.)",
+			   se_diff = "SE ELPD (diff)",
+			   elpd_loo = "ELPD",
+			   se_elpd_loo = "SE ELPD")
+```
+
+@tbl-loos summarises the outputs of the LOO-CV model comparisons.
+Models $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ showed substantially better predicted performance than models $\mathcal{M}_{0}$ and $\mathcal{M}_{1}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
+All $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ models showed equivalent performance, suggesting that adding the two-way and three-way interactions between *Age*, *Group*, and *Condition*, did not improve the the fit of the model.
+We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{4}$.
+We report the median and 95% highest density interval of each fixed regression coefficient.
+
+The outcomes of $\mathcal{M}_{0}$, which only included *Age* and as main effect, revealed successful word recognition across participants.
+Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_0$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$b_intercept$ci_label`).
+The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_0$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_0$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_session_id_intercept$ci_label`).
+The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_0$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_0$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
+
+The 95% HDI of the coefficient of *Group* in $\mathcal{M}_{1}$ included zero ($\beta$ = `r coefs$fit_1$b_lp1$mdn_label`, 95% HDI = `r coefs$fit_1$b_lp1$ci_label`), indicating an equivalent overall target preference in monolinguals and bilinguals.
+The 95% HDI of the first contrast of this predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_2$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition1$ci_label`).
+The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_2$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition2$ci_label`).
+The overall target preference was equivalent across both pairwise condition comparisons.
+The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$fit_3$b_condition1_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1_lp1$ci_label`).
+The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$fit_3$b_condition2_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2_lp1$ci_label`).
+The outcomes of this model indicate that lack of differences in overall target looking time across conditions remained across monolinguals and bilinguals.
+
+Both younger and older participants showed equivalent looking time across conditions, as suggested by the fact that the 95% HDI of the two-way interaction between *Age* and the first *Condition* contrast included zero ($\beta$ = `r coefs$fit_4$b_condition1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_age_std$ci_label`), as well as the interaction between *Age* and the second *Condition* contrast ($\beta$ = `r coefs$fit_4$b_condition2_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_age_std$ci_label`).
+This pattern of results was found in both monolinguals and bilinguals, as the 95% HDI of the three-way interaction between *Age*, *Group*, and *Condition* included zero both the first ($\beta$ = `r coefs$fit_4$b_condition1_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_lp1_age_std$ci_label`) and second ($\beta$ = `r coefs$fit_4$b_condition2_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_lp1_age_std$ci_label`) contrast of *Condition*.
+
+```{r timecourse-oxf}
+timebin_values <- make_std(seq(0, 17, length.out = 100),
+						   mean(data_oxf$timebin),
+						   sd(data_oxf$timebin))
+
+age_values <- make_std(c(20, 30),
+					   mean(data_oxf$age),
+					   sd(data_oxf$age))
+
+nd <- expand_grid(distinct(data_oxf, condition),
+				  timebin_std = timebin_values,
+				  age_std = age_values)
+
+epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_2, 
+						  re_formula = NA,
+						  ndraws = NULL,
+						  value = ".elog") |> 
+	mutate(age_std = factor(age_std,
+							levels = age_values, 
+							labels = paste0(c(20, 30), " months")))
+
+epreds_chance <- epreds |> 
+	median_hdci() |> 
+	mutate(is_lower_positive = .lower > 0) |> 
+	filter(is_lower_positive) |> 
+	summarise(over_chance = min(timebin_std),
+			  .by = c(condition, age_std)) |> 
+	mutate(over_chance = (over_chance * 
+						  	sd(data_oxf$timebin) +
+						  	mean(data_oxf$timebin))*100+300)
+
+epreds_chance_report <- epreds_chance |> 
+	mutate(over_chance = sprintf("%.2f", over_chance),
+		   age_std = paste0("age_", gsub(" months", "", age_std))) |> 
+	arrange(age_std) %>%
+	split(tolower(.$age_std)) 
+```
+
+An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
+Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
+
+```{r fig-epreds-oxf}
+#| label: fig-epreds-oxf
+#| fig-cap: "Posterior mean prdictions of the time course of target fixation in the test phase.
+Lines and intervals indicate the median and 95% credible interval of the posterior predictions, respectively."
+#| fig-width: 8
+#| fig-height: 4
+epreds |> 
+	ggplot(aes(timebin_std, .elog,
+			   colour = condition,
+			   fill = condition)) +
+	facet_wrap(~age_std) +
+	geom_hline(yintercept = 0, linetype = "dashed") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
+				 alpha = 1/2,
+				 linewidth = NA) +
+	stat_summary(fun = mean,
+				 geom = "line",
+				 linewidth = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition") +
+	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
+										 mean(data_bcn$timebin),
+										 sd(data_bcn$timebin)),
+					   labels = \(x) format(seq(3e2, 2e3, 3e2),
+					   					 big.mark = ",")) &
+	theme(panel.grid.major.y = element_line(colour = "grey",
+											linetype = "dotted"),
+		  legend.position = "top")
+```
+
+In an exploratory analysis, we compared the model-estimated time points at which participants' gaze behaviour showed evidence of target looking above chance level (50%).
+We defined the recognition time of the trial as the earliest time point at which the lower bound of the 95% HDI posterior mean prediction of the target looking excluded zero.
+As expected, the recognition times were on average shorter for older infants than for younger infants.
+Differences between conditions were larger in bilinguals than in monolinguals, especially in the older group.
+The recognition time for monolingual 20-month-olds was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
+In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+
+```{r fig-recognition-oxf}
+#| label: fig-recognition-oxf
+#| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
+#| fig-width: 7
+#| fig-height: 3
+epreds_chance |> 
+	ggplot(aes(age_std, over_chance,
+			   colour = sort(condition),
+			   fill = sort(condition))) + 
+	geom_point(shape = 16, size = 4) +
+	geom_line(aes(group = condition),
+			  linewidth = 1) +
+	# geom_point(size = 3) +
+	labs(x = "Group",
+		 y = "Recognition time (ms)",
+		 colour = "Condition",
+		 fill = "Condition") +
+	scale_y_continuous(breaks = seq(0, 1e3L, 25)) +
+	theme(panel.grid.major.y = element_line(colour = "grey",
+											linetype = "dotted"),
+		  panel.grid.minor.y = element_line(colour = "grey",
+		  								  linetype = "dotted"),
+		  legend.position = "top",
+		  axis.title.x = element_blank())
+```
+
+## Discussion
+
+# General discussion
+
 # References

### 2023-11-04 manuscript/manuscript.qmd
Fix Oxford resutls in manuscript

@@
 	  gaze,
-	  data_bcn
+	  data_bcn,
+	  data_oxf
 	))
@@
 	c(model_fits_bcn,
-	  model_loos_bcn
+	  model_loos_bcn,
+	  model_fits_oxf,
+	  model_loos_oxf
 	))
@@
 ```{r dataset}
-n_trials <- nrow(attrition)
-n_sessions <- n_distinct(attrition$session_id)
-n_participants <- n_distinct(attrition$child_id)
-n_trials_valid <- nrow(filter(attrition,
+attrition_bcn <- filter(attrition, location=="Barcelona")
+n_trials <- nrow(attrition_bcn)
+n_sessions <- n_distinct(attrition_bcn$session_id)
+n_participants <- n_distinct(attrition_bcn$child_id)
+n_trials_valid <- nrow(filter(attrition_bcn,
 							  is_valid_participant,
 							  is_valid_trial))
-n_sessions_valid <- sum(attrition_participants$is_valid_participant)
+n_sessions_valid <- sum(distinct(attrition_bcn,
+								 session_id,
+								 .keep_all = TRUE)$is_valid_participant)
 n_participants_valid <- n_distinct(
-	attrition[attrition$is_valid_participant, ]$child_id)
-
-n_exc_prime <- sum(!attrition$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition$is_valid_gaze_test)
-n_exc_test_each <- sum(!attrition$is_valid_gaze_test_each)
-n_exc_participants <- sum(!attrition_participants$is_valid_participant)
-
-n_longitudinal <- attrition |>
+	attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id)
+
+n_exc_prime <- sum(!attrition_bcn$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition_bcn$is_valid_gaze_test)
+n_exc_test_each <- sum(!attrition_bcn$is_valid_gaze_test_each)
+n_exc_participants <- sum(!distinct(attrition_bcn,
+									session_id,
+									.keep_all = TRUE)$is_valid_participant)
+
+n_longitudinal <- attrition_bcn |>
 	filter(is_valid_participant,
@@
 #| tbl-cap: "Participant-level and trial-level sample size after applying inclusion criteria. The number of excluded participants and trials is indicated between parentheses."
-expanded <- expand(attrition, lp, trial_type, is_valid_trial)
-
-n_lp <- attrition |> 
+expanded <- expand(attrition_bcn, lp, trial_type, is_valid_trial)
+
+n_lp <- attrition_bcn |> 
 	distinct(is_valid_participant, lp, session_id) |> 
@@
 
-attrition |> 
+attrition_bcn |> 
 	summarise(n_trials_true = sum(is_valid_trial),
@@
 	left_join(n_lp, by = join_by(lp)) |> 
-	mutate(lp = case_when(
-		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
-		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
-		.default = lp)) |>
 	select(lp, true, false,
@@
 				 pattern = "{1} ({2})") |> 
-	cols_label(true = "N", 
+	cols_label(true = "Participants", 
 			   n_trials_true_cognate = "Cognate",
@@
 
-We collected data from `r n_participants_total$n[1]` children (`r n_participants_sex[1]` female, `r n_participants_sex[2]` male, `r n_participants_sex[3]` sex not reported, age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]), living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford.
+We collected data from `r n_participants_total` children (`r n_participants_sex$n[1]` female, `r n_participants_sex$n[2]` male, `r n_participants_sex$n[3]` sex not reported, age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]), living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford.
 Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r n_participants_total$n` children that participated, `r n_participants_sessions$session_1` participated once, and `r n_participants_sessions$session_2` participated twice.
+From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, and `r n_participants_sessions$session_2` participated twice.
 Recurrent participants were tested with at least XXX months of difference.
@@
 
+```{r dataset_oxf}
+attrition_oxf <- filter(attrition, location=="Oxford")
+n_trials <- nrow(attrition_oxf)
+n_sessions <- n_distinct(attrition_oxf$session_id)
+n_participants <- n_distinct(attrition_oxf$child_id)
+n_trials_valid <- nrow(filter(attrition_oxf,
+							  is_valid_participant,
+							  is_valid_trial))
+n_sessions_valid <- attrition_oxf |> 
+	distinct(child_id, .keep_all = TRUE) |> 
+	pull(is_valid_participant) |> 
+	sum()
+
+n_participants_valid <- n_distinct(
+	attrition_oxf[attrition_oxf$is_valid_participant, ]$child_id)
+
+n_exc_prime <- sum(!attrition_oxf$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition_oxf$is_valid_gaze_test)
+n_exc_test_each <- sum(!attrition_oxf$is_valid_gaze_test_each)
+n_exc_participants <- sum(!attrition_oxf |> 
+	distinct(child_id, .keep_all = TRUE) |> 
+	pull(is_valid_participant))
+
+n_longitudinal <- attrition_oxf |>
+	filter(is_valid_participant,
+		   is_valid_trial) |>
+	distinct(child_id, session_n) |> 
+	count(child_id, name = "times") |> 
+	count(times)
+
+n_trials_condition <- attrition_oxf |> 
+	filter(is_valid_participant) |> 
+	count(trial_type, is_valid_trial) %>%
+	split(janitor::make_clean_names(.$trial_type))
+```
+
+We defined a time windows of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
+To avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
+Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
+We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
+
+After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`).
+The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+From the trials included in the final dataset dataset, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), were `r n_trials_condition$non_cognate_2$n` *Related/Non-cognate* trials(`r n_trials_condition$non_cognate$n` previously excluded), and `r n_trials_condition$cognate_2$n` were *Related/Cognate* trials (`r n_trials_condition$cognate$n` previously excluded).
+
 ## Results

### 2023-11-05 manuscript/manuscript.qmd
General discussion

@@
 A critical property the bilingual lexicon is that its representations are accessed in a language-non selective way.
-Even during monolingual situations, bilinguals access their lexical representations in both of their languages [e.g., @thierry2007brain; @dunabeitia2009masked].
+Even during monolingual situations, bilinguals access their lexical representations in both of their languages [e.g., @thierry2007brain; @dunabeitia2009masked; @HOSHINO; @STROJKERS2010; @dijktra2010baayen].
 This is reflected in bilinguals' performance in word recognition and production tasks.
@@
 Unbeknownst to participants, the authors manipulated the phonological overlap between the pictures' labels in Catalan and their translations in Spanish.
-Participants produced faster words that shared phonological overlap with their Spanish translations (e.g., *gat*-*gat* [*cat*]) than those unrelated to their translation (e.g., *taula*-*mesa* [*table*]).
+In half of the trials, the labels associated to pictures were cognates, that is, phonologically similar translation equivalents in Catalan and Spanish, whereas in the other half of the trials the labels were non-cognates.
+Participants produced faster words in cognate trials (e.g., *gat*-*gat* [*cat*]) than in non-cognate trials (e.g., *taula*-*mesa* [*table*]).
 Critically, Spanish monolinguals who completed the same task, naming the pictures in Spanish, showed equivalent naming times in both conditions.
 These results reveal that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the activation of its associated phonological forms in both language sin parallel, which influenced the subsequent the dynamics of word production.
+the differential processing of cognates has generated a large body of literature providing support for the language-non selective account of lexical access [e.g., @degrootandnas1992; @schwartzkroll2007; @dijkstragrainger1999; @dufourkroll1995; @lemhofferetal2008]
 
@@
 Target preference exceeded chance level in both conditions.
+
 In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
@@
 
-Priming-though-translation paradigms, however, come with a cost.
-When prime words are auditorily presented, the task constrains the naming context to one of the languages.
+Although priming-through-translation studies suggest parallel activation in participants' lexicon in both languages, their design prevents strong interpretations about the extent to which parallel activation is the result of the experimental manipulations of interest.
+The presentation of primes and targets in both languages in the same task---or even within the same trial--- presents participants with a bilingual context that might lead to a higher baseline activation of lexical representations of both languages, compared to monolinguals situations in which parallel activation is claimed to spontaneously take place [@GROSJEAN1997].
+Another limitation of priming-through-translation studies is that, when prime words are auditorily presented, the task constrains the naming context to one of the languages.
 The consequence is a potential asymmetry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
@@
 
-In the present study, we use an adaptation of an implicit naming paradigm by @mani2010infant, in which participants are primed with a picture, instead of an auditorily presented label.
-This paradigm prevents infants from activating the prime label in any of their two languages, and therefore makes it more likely that they will activate the prime labels in both languages in parallel.
-Infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
-In particular, the authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
-
-When extended to the bilingual case, this implicit naming task may offer bilingual participants with an unconstrained naming context in which the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
-
-This study also provides a more suitable design for drawing conclusions about developmental change in word recognition trajectories for two reasons.
-First, it extends the age range of participants, compared to previous studies.
-Second, participants were tested at three selected age points to ensure a more balanced sample size across ages.
-Third, the partially longitudinal design allows modelling the performance of participants across testing sessions altogether.
-
-In order to circumvent the problem of limited vocabulary knowledge
-in the non-dominant language, we propose to test participants only in their dominant language, therefore
-directing our research to the question of how possessing a second language affects processing of the
-dominant one in bilingual toddlers [@costa2014does provide a fuller description of the
-advantages of such approach].
-
-The present study is aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
+In the present study, we aim to put the hypothesis that bilingual infants activate both languages in parallel to a harder test.
+We use an extension of the implicit naming paradigm by @mani2010infant, in which participants are primed with a picture presented in silence.
+This provides participants with an exclusively monolingual context in which they perform the task in only one of their languages.
+If differences in task performance are found associated with covert manipulation of cross-linguistic properties of the stimuli, such differences may be more conclusively linked to the parallel activation of lexical representations in participants' lexicons.
+
+Another advantage of the implicit naming paradigm in the investigation of bilingual lexical processing is the fact that, since participants are not presented with any auditory prime label, the activation of the lexical representation of the prime may occur in both languages as the result of lexical retrieval after visual recognition of the prime picture.
+This contrasts with priming through-translation tasks, in which the prime label in one of the languages is directly activated by auditory word recognition, while the label of its translation is expected to be activated as the result of cascaded activation spreading through their semantic association.
+This may lead to an asymmetry in the time course of the activation of both labels, which might in turn affect the dynamics of phonological priming in subsequent word recognition.
+
+Finally, testing bilingual populations at early ages presents the limitation that the vocabulary size of participants' non-dominant language is relatively small, which substantially constrains the number of items that can be used to as stimuli in the task, as well as the number of trials that can be constructed to generate stimuli lists.
+In order to circumvent the problem of limited vocabulary knowledge in the non-dominant language, tested participants only in their dominant language, therefore directing our research to the question of how possessing a second language affects processing of the dominant one in bilingual toddlers [@costa2014does provide a fuller description of the advantages of such approach].
+
+In summary, the present study was aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
 Using an adaptation of [@mani2010infant], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
 We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
-If so, phonological priming effect should be larger when the prime label in  both languages shares phonological overlap with the target words (cognate condition), compared to when only the label of the prime in one language overlaps phonologically with the target (non-cognate condition).
+If so, phonological priming effect should be larger when the prime label in both languages shares phonological overlap with the target words (*Related/Cognate* condition), compared to when only the label of the prime in one language overlaps phonologically with the target (*Related/Non-cognate*).
 We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
 
-We compared the explanatory power of three measures of vocabulary size on participants' trajectories of word recognition: L1 vocabulary and total vocabulary.Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary]
-
-Hypothesis 1: if lexical representations linked through inhibitory links (compete for selection), like in the adult lexicon, target looking should increase faster in *Unrelated* trials compared to *Related* trials.
-If lexical representations are linked through excitatory links, target preference should increase faster in *Related* trials, compared to *Unrelated* trials.
-If lexical representations are sparsely connected, participants should show equivalent patterns of target looking in *Related* and *Unrelated* trials.
-
-Hypothesis 2: if bilinguals' lexical representations linked across languages through inhibitory links (compete for selection), target looking should increase faster in this group in *Related/Non-cognate* trials compared to *Related/Cognate* trials.
-If lexical representations are linked across languages through excitatory links, target preference should increase faster in *Related/Cognate* trials, compared to *Unrelated/Cognate* trials.
-If lexical representations are sparsely connected across languages, bilinguals' patterns of target looking should be equivalent for *Related/Cognate* and *Related/Non-cognate* trials.
-This pattern is also expected for monolingual infants.
-
-Hypothesis 3: if the emergence of within-language or cross-language phonological links is explained (if at all) by the growth of within-language vocabulary size, the difference in target looking between *Related* and *Unrelated*, or between *Related/Cognate* and *Related/Non-cognate* trials should be larger in participants with larger vocabulary sizes in their dominant language, in which they were tested.
-This should be reflected by a $\text{Condition} \times \text{L1 vocabulary}$ two -way interaction, or a $\text{Condition} \times \text{Group} \times \text{Dominant vocabulary}$ three-way interaction.
-
-Hypothesis 4: if the emergence of within-language or cross-language phonological links is explained better by the growth of cross-language vocabulary size, compared to within-language vocabulary size, a model that incorporates total vocabulary size as a predictor instead of dominant vocabulary size should show better predictive performance.
-If the emergence of such links is explained at all by the growth of vocabulary size, both models incorporating vocabulary size as a predictor should show better predictive performance than a model incorporating participants' age.
+To test cross-language priming effects, we registered participants' time course of target picture looking in the three conditions.
+We predicted within-language priming effects, revealed as differences in target looking between *Unrelated* and *Related/Non-cognate* trials, as previously reported [@von2012, @MANI2001, and @MANI2011].
+We further predicted cross-language priming effects, revealed as differences in target looking between *Related/Non-cognate* and *Related/Cognate* trials.
+This effect should be stronger in bilinguals, if not completely absent in monolinguals, who should be indifferent to the phonological properties of the stimuli in the other language. 
+Following previous studies associating the emergence of phonological links between lexical items to the size of children's vocabulary [@MANI2011], we also compared the explanatory power of two indices of receptive vocabulary size (dominant-language vocabulary size and total vocabulary size) against participants' age.
+We used parental reports of vocabulary checklist to estimate participants' vocabulary size.
+We computed vocabulary size in the dominant language (L1 vocabulary) as the proportion of words in the dominant language reported by their caregivers to be understood by the child in a vocabulary checklist, and the total vocabulary size as the proportion of words reported as understood by the child in *both* languages.
+If within-language or cross-language phonological associations in the lexicon emerge as a function of vocabulary growth, the size of the differences between conditions should larger in participants with larger vocabulary sizes.
+A model including participants' L1 or total vocabulary size as a predictor should then show better performance than a model that instead includes participants age.
+In the case of bilinguals, if the emergence of cross-language priming effects is associated with the growth of their vocabulary is *both* languages, a model including total vocabulary size as a predictor should perform better than a model that includes L1 vocabulary size.
+The opposite pattern would indicate that cross-language priming effects emerge as a function of the growth of L1 vocabulary.
 
@@
 
-```{r results-0}
+```{r results}
 var_labels <- c("b_Intercept" = "Intercept",
@@
 loos_tbl[1:5] |> 
-	mutate(model = case_when(model=="fit_0" ~ "$\\mathcal{M}_{0}$",
-							 model=="fit_1" ~ "$\\mathcal{M}_{1}$",
-							 model=="fit_2" ~ "$\\mathcal{M}_{2}$",
-							 model=="fit_3" ~ "$\\mathcal{M}_{3}$",
-							 model=="fit_4" ~ "$\\mathcal{M}_{4}$",
-							 model=="fit_5" ~ "$\\mathcal{M}_{5}$")) |>
+	mutate(model = gsub("fit_", "", model)) |>
 	gt() |> 
@@
 	# fmt_markdown(is.character, ) |> 
-	cols_label(elpd_diff = "ELPD (diff.)",
+	cols_label(model = "Model",
+			   elpd_diff = "ELPD (diff.)",
 			   se_diff = "SE ELPD (diff)",
@@
 
-The outcomes of $\mathcal{M}_{0}$, which only included *Age* and as main effect, revealed successful word recognition across participants.
-Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_0$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$b_intercept$ci_label`).
-The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_0$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_0$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_session_id_intercept$ci_label`).
-The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_0$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_0$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
-
-The 95% HDI of the coefficient of *Group* in $\mathcal{M}_{1}$ included zero ($\beta$ = `r coefs$fit_1$b_lp1$mdn_label`, 95% HDI = `r coefs$fit_1$b_lp1$ci_label`), indicating an equivalent overall target preference in monolinguals and bilinguals.
-The 95% HDI of the first contrast of this predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_2$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition1$ci_label`).
-The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_2$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition2$ci_label`).
+Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_4$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_4$b_intercept$ci_label`).
+The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_4$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_4$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_4$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_4$sd_child_id_session_id_intercept$ci_label`).
+The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_4$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
+
+The 95% HDI of the coefficient of *Group* in $\mathcal{M}_{1}$ included zero ($\beta$ = `r coefs$fit_4$b_lp1$mdn_label`, 95% HDI = `r coefs$fit_4$b_lp1$ci_label`), indicating an equivalent overall target preference in monolinguals and bilinguals.
+The 95% HDI of the first contrast of this predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_4$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1$ci_label`).
+The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_4$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2$ci_label`).
 The overall target preference was equivalent across both pairwise condition comparisons.
-The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$fit_3$b_condition1_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1_lp1$ci_label`).
-The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$fit_3$b_condition2_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2_lp1$ci_label`).
+The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$fit_4$b_condition1_lp1$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_lp1$ci_label`).
+The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$fit_4$b_condition2_lp1$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_lp1$ci_label`).
 The outcomes of this model indicate that lack of differences in overall target looking time across conditions remained across monolinguals and bilinguals.
@@
 
+## Discussion
+
+In Study 1, we adapted an implicit naming paradigm to investigate the potential role of within- and cross-language phonological priming in 21- to 32-month-old children.
+Overall, participants' performance was equivalent across all priming conditions.
+Both the overall target looking and its course time across the trial suggested strong word recognition, regardless of participants language profile and age.
+An exploratory analyses on word recognition times suggested a complex pattern of results, showing an age effect---in which older participants looked at the target above chance earlier than younger infants---and a weak interaction between priming conditions, age, and language group.
+These results conflict with previous findings in several ways.
+
+First, investigations using implicit naming paradigm had provided strong evidence in favour of infants and toddlers generating internal labels when presented with pictures of familiar objects.
+@mani2010infant and @mani2011phonological reported priming effects in 18 and 24-month-old infants.
+In primed trials, participants' target looking preference was influenced by the previous presentation of a phonologically related referent in silence.
+In control trials---in which prime and target labels were unrelated---no priming effect was found.
+This suggests that infants implicitly named the prime label, and that the resulting internal phonological form was detailed enough to interact with the subsequent auditory recognition of the target word.
+In the present study, we did not find evidence in favour of differences in target looking preference between related and unrelated trials, regardless of the age of participants or their language profile.
+
+```{r doe-exposure}
+doe_mon_exp <- participants_bcn |>
+	filter(lp=="Monolingual")|> 
+	unnest_wider(doe) |> 
+	mutate(doe2 = ifelse(test_language=="Catalan",
+						 doe_spanish, doe_catalan),
+		  is_positive =  doe2 > 0) |> 
+	count(is_positive) 
+```
+Both @mani2010infant and @mani2011phonological, and the present study shared a similar design, but sampled different children populations.
+Participants in Mani and Plunkett's studies were raised in English speaking households in Oxford, while participants in the present study were learning Catalan or Spanish, if not a combination of both.
+We identify two ways in which this might have influenced the results.
+One is that the stimuli lists in Catalan and Spanish might have differed in some critical dimension, which interfered infants' ability to generate implicit labels for prime pictures.
+For example, words in the present study were predominantly bi-syllabic, while those from Mani and Plunkett's studies were mostly monosyllabic, and contained less phonemes on average.
+Longer word-forms might have been more difficult to retrieve in time for a prime effect to take place in target recognition.
+Another possibility is that exposure to a second language might have delayed the developmental trajectories of word production in bilinguals, in such way implicit naming emerges later ages.
+Given that `r scales::percent(doe_mon_exp$n[1] / doe_mon_exp$n[2], accuracy = 0.01)`
+of monolinguals in Barcelona were also exposed to a second language, they might as well been affected by such delay in implicit naming trajectories.
+
+The results from the Study 1 also conflict with previous reports of cross-language priming in toddlers.
+Particularly, @von2012language and @floccia2020translation had provided evidence of phonological priming through translation.
+One critical different between both studies and the present one is the silent or auditory presentation of the prime labels.
+In priming through translation studies, the prime is auditorily presented to participants, and cross-language priming effects take place through the subsequent activation of the prime translation.
+In the present study, the prime label was not named, and participants were expected to generate both the prime label and its translation implicitly.
+It may be the case that infants in the present study faced a more challenging task, having to internally retrieve phonological forms without any auditory prompt like the one provided by priming-through-translation studies.
+
+Finally, another possibility is that participants in the present study did in fact general prime labels, but such labels did not interfere over target recognition.
+This could be because they were not phonologically specified enough.
+This is unlikely, as previous studies have shown strong evidence of fine phonological representations in the early lexicon REFERENCE.
+Instead, it could be the case that the prime labels were activated, but phonological links between lexical representations are still weak or not present, so that priming effects are not possible until later in age.
+To our knowledge, this study is the first one to test bilingual children at this age on implicit naming paradigms, so evidence of priming is not present at the moment.
+
+We found no differences between models including participants' age or any of the two indices of vocabulary size (L1 and total vocabulary size) as predictors.
+Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary].
+
+In summary, the possibly increased difficulty of the task induced by the properties of the stimuli, together with differences in task design and populations might have contributed to the null pattern of results shown in Study 1.
+Given the complexity of the picture drawn by these factors, we conducted a second study with the aim of replicating the original findings by @mani2010infant and @mani2011phonological.
+If phonological priming effects are observed in a same-aged population using the adaptation of the task from Study 1, this would provide evidence in favour of cross-language differences in the developmental trajectories of implicit naming.
+If, on the contrary, a similar patter of null results is found, this would suggest either the existence of finer differences in task implementation compared to the original studies, or point to the effect of interest being less robust than suggested by the literature.
+
 # Study 2
+
+In this study, we conducted a conceptual replication of @mani2010infant and @mani2011phonological.
+Using the same task from Study 1, we tested a same-aged group of monolinguals being exclusively raised in British English speaking homes, the same population tested in the original studies.
+As in Study 1, we manipulated the phonological relationship between the prime and target labels at word onset, as well as the cognate status of the prime label.
+Evidence from implicit naming of prime images would be revealed by differences in target looking or its time course across the trials between *Unrelated* trials, and *Related/Non-cognate* and *Related/Cognate* trials.
+Given that participants in this study are monolinguals---and contrary to the monolinguals in Barcelona, have received no exposure to any other language---we would not expect the cognate status of the prime labels to exert any effect on subsequent target recognition.
 
@@
 loos_tbl |> 
-	mutate(model = case_when(model=="fit_oxf_0" ~ "$\\mathcal{M}_{0}$",
-							 model=="fit_oxf_1" ~ "$\\mathcal{M}_{1}$",
-							 model=="fit_oxf_2" ~ "$\\mathcal{M}_{2}$",
-							 model=="fit_oxf_3" ~ "$\\mathcal{M}_{3}$")) |>
+	mutate(model = gsub("fit_oxf_", "", model)) |>
 	gt() |> 
@@
 
-@tbl-loos summarises the outputs of the LOO-CV model comparisons.
-Models $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ showed substantially better predicted performance than models $\mathcal{M}_{0}$ and $\mathcal{M}_{1}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
-All $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ models showed equivalent performance, suggesting that adding the two-way and three-way interactions between *Age*, *Group*, and *Condition*, did not improve the the fit of the model.
-We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{4}$.
-We report the median and 95% highest density interval of each fixed regression coefficient.
-
-The outcomes of $\mathcal{M}_{0}$, which only included *Age* and as main effect, revealed successful word recognition across participants.
-Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_0$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$b_intercept$ci_label`).
-The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_0$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_0$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_session_id_intercept$ci_label`).
-The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_0$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_0$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
-
-The 95% HDI of the coefficient of *Group* in $\mathcal{M}_{1}$ included zero ($\beta$ = `r coefs$fit_1$b_lp1$mdn_label`, 95% HDI = `r coefs$fit_1$b_lp1$ci_label`), indicating an equivalent overall target preference in monolinguals and bilinguals.
-The 95% HDI of the first contrast of this predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_2$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition1$ci_label`).
-The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_2$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition2$ci_label`).
+@tbl-loos-oxf summarises the outputs of the LOO-CV model comparisons.
+Models $\mathcal{M}_{1}$, $\mathcal{M}_{2}$, and $\mathcal{M}_{3}$ showed substantially better predicted performance than model $\mathcal{M}_{0}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
+All $\mathcal{M}_{1}$, $\mathcal{M}_{2}$, and $\mathcal{M}_{3}$ models showed equivalent performance, suggesting that adding the two-way interaction between *Age* and *Condition* did not improve the the fit of the model.
+We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{3}$.
+
+Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_3$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_3$b_intercept$ci_label`).
+The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_3$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_3$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_3$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_3$sd_child_id_session_id_intercept$ci_label`).
+The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_3$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_0$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
+
+The 95% HDI of the first contrast of the *Condition* predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_3$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1$ci_label`).
+The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_3$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2$ci_label`).
 The overall target preference was equivalent across both pairwise condition comparisons.
@@
 The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$fit_3$b_condition2_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2_lp1$ci_label`).
-The outcomes of this model indicate that lack of differences in overall target looking time across conditions remained across monolinguals and bilinguals.
-
-Both younger and older participants showed equivalent looking time across conditions, as suggested by the fact that the 95% HDI of the two-way interaction between *Age* and the first *Condition* contrast included zero ($\beta$ = `r coefs$fit_4$b_condition1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_age_std$ci_label`), as well as the interaction between *Age* and the second *Condition* contrast ($\beta$ = `r coefs$fit_4$b_condition2_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_age_std$ci_label`).
-This pattern of results was found in both monolinguals and bilinguals, as the 95% HDI of the three-way interaction between *Age*, *Group*, and *Condition* included zero both the first ($\beta$ = `r coefs$fit_4$b_condition1_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_lp1_age_std$ci_label`) and second ($\beta$ = `r coefs$fit_4$b_condition2_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_lp1_age_std$ci_label`) contrast of *Condition*.
+Both younger and older participants showed equivalent looking time across conditions, as suggested by the fact that the 95% HDI of the two-way interaction between *Age* and the first *Condition* contrast included zero ($\beta$ = `r coefs$fit_3$b_condition1_age_std$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1_age_std$ci_label`), as well as the interaction between *Age* and the second *Condition* contrast ($\beta$ = `r coefs$fit_3$b_condition2_age_std$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2_age_std$ci_label`).
 
@@
 	mutate(over_chance = sprintf("%.2f", over_chance),
-		   age_std = paste0("age_", gsub(" months", "", age_std))) |> 
+		   age_std = paste0("age_", 
+		   				 gsub(" months", "", age_std))) |> 
 	arrange(age_std) %>%
@@
 #| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
-#| fig-width: 7
+#| fig-width: 4
 #| fig-height: 3
@@
 
+Study 2 was aimed at investigating whether the phonological priming effects previously reported @mani2010infant and @mani2011phonological could be found using the adaptation of the implicit naming task form Study 1 in a sample with equivalent demographic characteristics to the original studies.
+Results from Study 2 did not provide any evidence in favour of phonological priming.
+English monolingual participants from all ages showed an equivalent pattern of target looking across both related and unrelated trials.
+
+The absence of a phonological priming effect suggest that either English monolinguals did not generate implicit labels for the prime pictures presented in silence, or that if generated, such labels did not interact with the subsequent recognition of the target word.
+Both candidate explanations conflict with both Mani and Plunkett's studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects.
+
+One of the main differences between the implicit naming paradigm used by @mani2010infant and the one in Studies 1 and 2 is the fact that target labels were auditorily presented before target and distractor pictures were presented on screen.
+Given that priming effects are very sensitive to the timing of the activation of the lexical presentation [@REFERENCES], we decided to shorten the time span between prime image naming and target label presentation by removing the pre-naming interval of the test phase, in which both target and distractor pictures are presented form a baseline time interval before the target label is auditorily presented.
+By presenting the auditory target label immediately after the offset of the prime picture, the internally generated prime phonological form would be more likely to affect the activation of the target lexical representation.
+It is possible that this difference in task design might have led to the contrasting outcomes of Mani and Plunkett and the present study.
+Given that participants were not presented with the target and distractor pictures until after the target label was auditorily presented, one possibility is that participants faced the additional task of exploring both pictures to find the target referent, which infants in @mani2010infant did not have to do, because of the pre-naming presentation of target and distractor in the test phase.
+This visual exploration of the screen might have increased the cognitive load of the task, rendering the potential effect of phonological priming to a weaker, undetectable effect.
+
+Another possibility is that the findings in @mani2010infant and @mani2011phonological are less robust than anticipated.
+
+Overall the results from Study 2 support a more methodological explanation of the null pattern of results in Study 1, in which the lack of a phonological priming effect---both within and across languages---might be explained by differences in task design or replicability concerns.
+
 # General discussion
 
+In this paper, we investigated the developmental trajectories of cross-language co-activation in the developing lexicon.
+We tested a longitudinal an cross-sectional sample of 20-to-32 month olds in an implicit naming paradigm, in which we designed three trial types to manipulate the phonological overlap between the prime and target words within and across languages.
+In *Unrelated* trials, prime and target were phonologically unrelated in both languages.
+In *Related/Non-cognate* trials, prime and target labels shared phonological onset only in the dominant language of participants, in which they were tested.
+In *Related/Cognate* trials, the prime label was a cognate: prime and target labels shared phonological onset in both languages.
+In Study 1, we tested a cohort oh monolingual and bilingual infants learning Catalan, Spanish, or both, and found no phonological priming effect in monolinguals or bilinguals.
+In Study 2, we tested a cohort of English monolinguals, and found similar results.
+
+To our knowledge this is the first study investigating cross-language priming using an implicit naming paradigm.
+Such paradigm presents a critical asset for studying bilingual lexical processing.
+Since the prime pictures are presented in silence, the task is exclusively complete in the dominant language of participants.
+This provides a monolingual situation in which differences in performance across experimental conditions that involve cross-linguistic interactions can be more easily associated to the experimental manipulation in a causal way [ @GROSEJAN1997].
+This contrast to other experimental paradigms in which participants are presented with---need to produce---items from both languages.
+Such covert manipulation of the similarity between stimuli from the two languages has allowed previous studies to provide strong support for the language-non selective account of lexical access e.g., [COSTA, 2000; THIERRY 2008, 2011; VON 2014].
+
+Previous studies have provided evidence of English monolingual infants 18-month-old and older being sensitive to phonological priming effects during auditory word recognition.
+@mani2010infant had shown a facilitation effect in word recognition when 18-month-olds were previously presented with a familiar picture whose label shared phonological onset with the target word.
+@mani2011phonological extended these results to 21-month-olds, showing an effect in the opposite direction: phonologically related primes interfered with target word recognition.
+The shift from facilitation to inhibition was interpreted as a shift from sub-lexical facilitation at the phonological level---in which target word recognition is facilitated by the prior activation of an overlapping set of phonological segments---to a lexical interference effect in which the activation of the lexical representation of the phonologically similar prime led to competition dynamics with the subsequently activated representation of the target word.
+The last conclusion was supported by the fact that the size of the interference effect was associated with the increase in participants' vocabulary size, and also with the cohort size of the prime label---primes belonging to a larger neighbourhood of phonologically related words were subject to stronger interference effects during the task
+
+Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
+@duta2012erp presented name-known pictures in silence for one second.
+After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
+In some trials the auditory label corresponded to a canonical realisation of the word-form.
+In other trials, the word was mispronounced.
+Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
+A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
+This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
+In bilinguals, only one study had used an implicit naming paradigm to study cross-language priming.
+@von2014bilinguals adapted @mani2010infant procedure to  test German-English bilinguals.
+The authors manipulated the phonological overlap between the prime label in English (presented in silence) and a German target (auditorily presented) in both German and English.
+Participants' ERPs revealed differences between trials in which the German prime label overlapped phonologically with the English target label, compared to trials in which none of the labels overlapped.
+These results suggest that adult bilinguals implicitly named prime pictures, and that the resulting label interacted with subsequent word recognition.
+
+The results in the present investigation are in strong contrast with the aforementioned studies. Both studies 1 and 2 conflict with implicit naming.
+
+Study 1 conflicts with cross-language studies. singh2014,
+
+@kuipers2015bilingualism compared ERP responses to picture-word pairs in English monolinguals and Welsh-English bilinguals where the words were either semantically related or unrelated to a pictured object.
+Although both studies tested 30-month-olds, the conclusions the authors reached do not fully agree.
+@singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
+
+The present study presents methodological contributions.
+First, the longitudinal design of the data collection provided a more suitable design for drawing conclusions about developmental change in word recognition trajectories, compared to studies that tested participants from a single age group [@FLOCCIA2020], or studies that with an exclusively cross-sectional design [@VON2012].
+Second, the modelling approach in the present study incorporates the double source of repeated measures simultaneously into the random effects structure of the multilevel model.
+The models in Studies 1 and 2 accounts for the time course of target looking across the trials and its associated autocorrelation using Hierarchical General Additive Models [@barr2008; @PEDERSEN].
+The models also incorporate the observations from the same testing session as a nested grouping variable inside participants, so that the test session-level parameters in each model are estimated taking into account the estimations of other testing sessions from the same participants.
+Overall, this approach allowed us to simultaneously model the participant-level variability, the testing session-level variability, and the time series consisting of participants' gaze behaviour during the task.
+Finally, the adoption of a Bayesian approach to implement and estimate the model allowed the incorporation of prior knowledge about the distribution of the parameters to generate stable estimates, despite the complexity of the model.
+
+Why. Auditory presentation, implicit label generation but no priming
+
+rhyme vs onset
+
+word length
+
+The findings in the present investigation have important implications for current models of bilingual lexical development.
+For instance, recent accounts of bilingual words acquisition pointed to a facilitative role of phonological similarity between the two languages.
+A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
+Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
+Cognates are form-similar translation equivalents.
+Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
+In the present study, we failed to observed cross-language effects during word recognition.
+These outcomes are not in line with parallel activation taking place during speech exposure in bilinguals.
+It is possible that the mechanisms involved in the cognate facilitation in bilingual word acquisition are not captured by the task used in the present study.
+Implicit naming might be tapping into lower-level functions, more related to acoustic and phonological processing, while word acquisition and learning might rely on more abstract sources of information that do recruit parallel activation.
+
+recent work uding parental reports of word acquistiion have provided insichc  For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
+This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
+
+One of the limitations of this study lies in the use of cognates as prime words.
+
+Conclusions
+
 # References

### 2023-11-09 manuscript/draft.qmd
Add new comments by NSG

--- 2023-11-04 manuscript/manuscript.qmd
@@
 ---
+format:
+  docx: default
 ---
@@
 
-targets::tar_load(
-	c(model_fits_bcn,
-	  model_loos_bcn,
-	  model_fits_oxf,
-	  model_loos_oxf
-	))
+# targets::tar_load(
+# 	c(model_fits_bcn,
+# 	  model_loos_bcn,
+# 	  model_fits_oxf,
+# 	  model_loos_oxf
+# 	))
 
@@
 
-Building a mental lexicon is a major achievement in the development of an infant.
-By storing representations of how familiar words sound and what they mean, an infant is able to make sense of their linguistic input.
-Infants start forming their first lexical representations before their first year of life [@tincoff1999some; @halle1994emergence; @vihman2004cross; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
-This initial lexicon consists of only a few items; mainly words for people, interjections, body parts, and food [@tincoff2012six; @tardif2008baby], but it undergoes rapid growth during their second year of life [@ganger2004reexamining; @goldfield1990early; @bloom2002children; @mcmurray2007defusing].
-According to parental reports the average 15-month-old infant already understands more than 100 words, and by two years, they understand more than 400 words [@frank2021variability].
+Building a mental lexicon is a major achievement in the development of an infant: by storing representations of how familiar words sound and what they mean, an infant is able to make sense of their linguistic input.
+The foundations of an initial lexicon are in place before their first year of life [@tincoff1999some; @halle1994emergence; @vihman2004cross; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
+This initial lexicon consists of only a few items; mainly words for people, interjections, body parts, and food [@tincoff2012six; @tardif2008baby], but it undergoes rapid growth during the second year of life [@ganger2004reexamining; @goldfield1990early; @bloom2002children; @mcmurray2007defusing].
+According to parental reports, the average 15-month-old infant already understands more than 100 words, and by two years, they understand more than 400 words [@frank2021variability].
 This accelerated lexical developmental is reflected in infants' trajectories of word recognition: infants recognise familiar words faster and more efficiently as they approach their second birthday [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
@@
 Second, they face a more complex referential context, since they often learn two labels for each referent, one in each language.
-The mechanisms that allow bilingual infants to keep up with monolinguals in their lexical development trajectories are still unclear.
+The mechanisms that allow bilingual' trajectories of lexical developmental to keep up with monolinguals' are still unclear.
 
@@
 The authors manipulated the phonological relationship between the target object's label (e.g., *casket*), and the label of each of the three distractors.
-Two of the distractors were phonologically related with the target, sharing onset (e.g., *castle*) or offset (e.g., *basket*) with the target word, respectively.
+Two of the distractors were phonologically related to the target, sharing onset (e.g., *castle*) or offset (e.g., *basket*), respectively.
 The other distractor was phonologically unrelated to the target (e.g., *nickel*).
-After hearing the target label, phonological distractors attracted participants' eye fixations more than unrelated distractors.
+After the onset of the auditory target label, phonological distractors attracted participants' eye fixations more than unrelated distractors.
 Distractors sharing phonological onset did so at an earlier time window than those sharing phonological offset.
@@
 
-The developing mental lexicon also seems to operate in this cascaded fashion.
-Like adults, infants activate non-selected lexical representations.
-This is reflected by the fact that from 21 months of age, infants' lexicon seems to also be systematically organised according to the semantic and phonological properties of its lexical representations.
-Priming paradigms of word recognition have provided a strong body of evidence for the existence of phonological and semantic links between early lexical representations between 18 and 21 months of age [@arias2009lexical; @styles2009infants].
-For instance, using a word recognition task, @arias2009lexical found that infants' spoken word recognition (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
+The developing mental lexicon also seems to operate in this cascaded fashion: like adults, infants activate non-selected lexical representations.
+For instance, priming paradigms of word recognition have provided a strong body of evidence for the existence of phonological and semantic links between early lexical representations between 18 and 21 months of age..
+@arias2009lexical found that infants' spoken word recognition (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
 Other studies have provided electrophysiological evidence of semantic priming at earlier ages [e.g., @rama2013development; @friedrich2005lexical].
 More recent studies have provided evidence for the emergence of such semantic links, even in the absence of visual referents during the experimental task [@willits2013toddlers].
-
 Phonological priming effects have also been reported in the initial lexicon.
-@mani2010infant created an implicit naming task in which each trial started with the *silent* presentation of a prime picture.
+@mani2010infant and @mani2011phonological created an implicit naming task in which each trial started with the *silent* presentation of a prime picture.
 Then, a target-distractor picture pair was presented side-by-side.
@@
 Prime and target-distractor pairs were semantically unrelated.
-Interestingly, infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
-This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.The authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
-
-In a follow-up study, @mani2011phonological found the opposite effect in older toddlers.
-After phonologically related primes, 24 month-old toddlers showed weaker target looking preference than after phonologically unrelated primes.
-These results interpreted these outcome as the result of the implicitly generated prime label interfering with the subsequent recognition of the (phonologically related) target word.
-The authors suggested that the shift from facilitation to interference from 18 to 24 months they found in both studies might be the result of a developmental shift in which 18-month-olds' lexicon is not yet organised based on phonological similarity, while 24-month-olds' is.
-This would lead to the former showing a pre-lexical facilitation effect in which such facilitation occurs via the activation of phonological segments, while the latter would show an interference effect due to lateral links between lexical representation having been established.
-
-@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
+Interestingly, infants showed different target looking preference patterns after phonologically related prime pictures, compared to after phonologically unrelated primes.
+This suggests that infants implicitly named prime pictures---despite such pictures having been presented in silence---and that the phonology of the resulting labels interacted with subsequent target.
+
+@chow2017spoken provided further evidence of semantic *and* phonological links in the early lexicon.
+The authors adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
 In each trial, the authors presented participants with four semantically and phonologically pictures.
@@
 A critical property the bilingual lexicon is that its representations are accessed in a language-non selective way.
-Even during monolingual situations, bilinguals access their lexical representations in both of their languages [e.g., @thierry2007brain; @dunabeitia2009masked].
+Even during monolingual situations, bilinguals access their lexical representations in both of their languages [e.g., @thierry2007brain; @dunabeitia2009masked; @hoshino2008cognate; @strijkers2010tracking; @duyck2007visual].
 This is reflected in bilinguals' performance in word recognition and production tasks.
@@
 The target object (*marku* [*stamp*], in this case) would be present in the screen, together with an object whose English label shared phonological onset with the target label (e.g., *mark*), and two unrelated distractors whose labels in Russian and English did not shared phonological relationship with the target label.
-Converging with @allopenna1998tracking's results in monolingual adults, after hearing the target label bilinguals fixated the cross-language phonological distractor significantly more than the unrelated distractors.
-These findings suggest that participants activated phonologically related word-forms in both Russian *and* English, which affected their overt visual exploration patterns during the task.
+In line with @allopenna1998tracking's results in monolingual adults, bilinguals fixated the cross-language phonological distractor significantly more than the unrelated distractors after hearing the target label.
+These findings suggest that bilinguals activated phonologically related word-forms in both Russian *and* English, which ultimately affected their overt visual exploration patterns during the task.
 
@@
 Unbeknownst to participants, the authors manipulated the phonological overlap between the pictures' labels in Catalan and their translations in Spanish.
-Participants produced faster words that shared phonological overlap with their Spanish translations (e.g., *gat*-*gat* [*cat*]) than those unrelated to their translation (e.g., *taula*-*mesa* [*table*]).
+In half of the trials, the labels associated to the pictures were cognates, that is, phonologically similar translation equivalents (e.g., *gat*-*gat* [*cat*]) in Catalan and Spanish, whereas in the other half of the trials the labels were non-cognates (e.g., *taula*-*mesa* [*table*]).
+Participants named pictures faster in cognate trials than in non-cognate trials.
 Critically, Spanish monolinguals who completed the same task, naming the pictures in Spanish, showed equivalent naming times in both conditions.
-These results reveal that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the activation of its associated phonological forms in both language sin parallel, which influenced the subsequent the dynamics of word production.
-
-Further support for the parallel retrieval of phonological forms during word production is given by implicit naming paradigms.
-Using an adaptation of @mani2010infant's task, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
+These results reveal that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the activation of its associated phonological forms in both languages in parallel, which influenced the subsequent the dynamics of word production.
+This differential processing of cognates and non-cognates has generated a large body of literature providing support for the language-non selective account of lexical access [e.g., @degrootandnas1992; @schwartzkroll2007; @dijkstragrainger1999; @dufour1995matching; @schwartz2007reading; @dijkstra2010cross].
+
+Further evidence in favour of the parallel retrieval of phonological forms during bilingual word production is given by implicit naming paradigms.
+Using an adaptation of @mani2010infant's task, @von2014bilinguals found that bilingual adults generate implicit labels in both labels for visually fixated pictures.
 The authors presented German-English bilinguals with 120 prime-target pairs.
@@
 Then, the target label was also auditorily presented in German.
-Finally the target and distractor pictures were presented side-by-side.
-The authors manipulated the phonological overlap between the prime and target labels.
-The novelty in this study lied in the orthogonal manipulation of the phonological overlap between both English and German labels.
+Finally, the target and distractor pictures were presented side-by-side.
 In some trials, the auditorily presented prime and target labels were phonologically related (e.g., *slide*-*Klide* [*dress*]).
@@
 This effect was found regardless of the language of the prime (English or Home Language), or the dominance of the language of the prime (i.e., whether the prime word belonged to the dominant language).
-Target preference exceeded chance level in both conditions.
-In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
+Target preference exceeded chance level in both conditions, pointing to successful word recognition regardless of the experimental manipulation.
+
+In a second study, @floccia2020translation, the authors tested an equivalent group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
 This time, prime and target words were not translation equivalents, but rather words whose referents shared semantic features.
-Results from Study  2 were parallel to those from Study 1.
+Results paralleled those from their first study.
 The authors found a strong semantic priming effect across languages, regardless of the language of the prime or the dominance of the language of the prime.
-Overall these results suggest that bilinguals recognised target words in both conditions, and benefited from a cross-linguistic facilitation effect from translation equivalents.
+Overall, these results suggest that bilinguals recognised target words in both conditions, and benefited from a cross-linguistic facilitation effect from translation equivalents.
 The symmetry of such effect across both languages suggests that participants lexical access occurred in parallel for the two members of translation equivalents.
-As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
+As the authors noted, the stimuli set of their second study contained multiple cognates due to design constraints, especially in languages with a larger degree of phonological overlap across translation pairs (e.g., English and Dutch).
 The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
-However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generated by an interaction by the phonological and semantic overlap between cognate primes and targets.
-
-Previous studies had reported similar cross-language priming effects, but as @von2012language note, the conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was not warranted.
-In studies where the auditorily presented prime label was phonologically overlapped with the target label [@REFERENCE], priming effects might be explained by the activation of the phonological segments of the prime label, which facilitated the recognition of the target label, which shared such phonological segments.
-The priming-through-translation results by @von2012language and @floccia2020translation demonstrates that cross-language activation in the developing lexicon occurs at the lexical level.
-Since participants' target recognition was interfered by the non-presented prime translation, such an inhibitory effect must stem at the lexical level.
+However, the cross-language effects reported in this second study might still reflect the confounding influence of cognateness, as the resulting effect might have been generated by an interaction by the phonological and semantic overlap between cognate primes and targets.
+
+Previous studies had reported similar cross-language priming effects.
+The conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was nonetheless unwarranted.
+In studies where the auditorily presented prime label was phonologically overlapped with the target label [e.g., @marian1999activation], priming effects might be explained by the activation of the phonological segments of the prime label, which facilitated the recognition of the target label, which shared such phonological segments.
+The priming-through-translation results by @von2012language and @floccia2020translation demonstrate that cross-language activation in the developing lexicon occurs at the lexical level.
+Since participants' target recognition was modulated by the non-presented prime translation, such an inhibitory effect must stem at the lexical level.
 The fact that phonological priming facilitated the recognition of the target words (both labels belong to different languages), and that phonological priming through translation interfered target recognition (translation and target belong to the same language) points to cross-language connections playing an excitatory role, and to within-language connections playing an inhibitory role.
 
-Priming-though-translation paradigms, however, come with a cost.
-When prime words are auditorily presented, the task constrains the naming context to one of the languages.
+The priming-through-translation paradigm provides a convenient framework to investigate parallel activation in the bilingual lexicon, but its design prevents strong interpretations about the extent to which parallel activation is the result of the experimental manipulations of interest.
+The presentation of primes and targets in both languages in the same task---or even within the same trial---presents participants with a bilingual context that might lead to a higher baseline activation of lexical representations of both languages, contrary to a context in which parallel activation results from genuine cross-language activation [@grosjean1997bilingual].
+Another limitation of priming-through-translation studies is that, when prime words are auditorily presented, the task constrains the naming context to one of the languages.
 The consequence is a potential asymmetry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
@@
 
-In the present study, we use an adaptation of an implicit naming paradigm by @mani2010infant, in which participants are primed with a picture, instead of an auditorily presented label.
-This paradigm prevents infants from activating the prime label in any of their two languages, and therefore makes it more likely that they will activate the prime labels in both languages in parallel.
-Infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
-In particular, the authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
-
-When extended to the bilingual case, this implicit naming task may offer bilingual participants with an unconstrained naming context in which the activation of both labels may occur in a truly cascaded fashion for both languages in parallel: the recognition of the prime object depicted activates the (common) semantic representation for both members of the translation equivalent, and this in turn activates the two available phonological word-forms, one in each language.
-
-This study also provides a more suitable design for drawing conclusions about developmental change in word recognition trajectories for two reasons.
-First, it extends the age range of participants, compared to previous studies.
-Second, participants were tested at three selected age points to ensure a more balanced sample size across ages.
-Third, the partially longitudinal design allows modelling the performance of participants across testing sessions altogether.
-
-In order to circumvent the problem of limited vocabulary knowledge
-in the non-dominant language, we propose to test participants only in their dominant language, therefore
-directing our research to the question of how possessing a second language affects processing of the
-dominant one in bilingual toddlers [@costa2014does provide a fuller description of the
-advantages of such approach].
-
-The present study is aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
+In the present study, we put the hypothesis that bilingual infants activate both languages in parallel to a more severe test.
+We used an extension of the implicit naming paradigm by @mani2010infant, in which participants were primed with a picture presented in silence.
+This provides participants with an exclusively monolingual context in which they perform the task in only one of their languages.
+If differences in task performance are found associated with covert manipulation of cross-linguistic properties of the stimuli, such differences may be more conclusively linked to the parallel activation of lexical representations in participants' lexicons.
+By using an implicit naming paradigm, the activation of the lexical representation of the prime may occur in both languages as the result of lexical retrieval after visual recognition of the prime picture, since participants are not presented with any auditory prime label.
+This contrasts with priming through-translation tasks, in which the prime label in one of the languages is directly activated by auditory word recognition, while the label of its translation is expected to be activated as the result of cascaded activation spreading through their semantic association.
+This may lead to an asymmetry in the time course of the activation of both labels, which might in turn affect the dynamics of phonological priming in subsequent word recognition.
+
+In summary, the present study was aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
 Using an adaptation of [@mani2010infant], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
 We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
-If so, phonological priming effect should be larger when the prime label in  both languages shares phonological overlap with the target words (cognate condition), compared to when only the label of the prime in one language overlaps phonologically with the target (non-cognate condition).
+If so, phonological priming effect should be larger when the prime label in both languages shares phonological overlap with the target words (*Related/Cognate* condition), compared to when only the label of the prime in one language overlaps phonologically with the target (*Related/Non-cognate*).
 We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
 
-We compared the explanatory power of three measures of vocabulary size on participants' trajectories of word recognition: L1 vocabulary and total vocabulary.Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary]
-
-Hypothesis 1: if lexical representations linked through inhibitory links (compete for selection), like in the adult lexicon, target looking should increase faster in *Unrelated* trials compared to *Related* trials.
-If lexical representations are linked through excitatory links, target preference should increase faster in *Related* trials, compared to *Unrelated* trials.
-If lexical representations are sparsely connected, participants should show equivalent patterns of target looking in *Related* and *Unrelated* trials.
-
-Hypothesis 2: if bilinguals' lexical representations linked across languages through inhibitory links (compete for selection), target looking should increase faster in this group in *Related/Non-cognate* trials compared to *Related/Cognate* trials.
-If lexical representations are linked across languages through excitatory links, target preference should increase faster in *Related/Cognate* trials, compared to *Unrelated/Cognate* trials.
-If lexical representations are sparsely connected across languages, bilinguals' patterns of target looking should be equivalent for *Related/Cognate* and *Related/Non-cognate* trials.
-This pattern is also expected for monolingual infants.
-
-Hypothesis 3: if the emergence of within-language or cross-language phonological links is explained (if at all) by the growth of within-language vocabulary size, the difference in target looking between *Related* and *Unrelated*, or between *Related/Cognate* and *Related/Non-cognate* trials should be larger in participants with larger vocabulary sizes in their dominant language, in which they were tested.
-This should be reflected by a $\text{Condition} \times \text{L1 vocabulary}$ two -way interaction, or a $\text{Condition} \times \text{Group} \times \text{Dominant vocabulary}$ three-way interaction.
-
-Hypothesis 4: if the emergence of within-language or cross-language phonological links is explained better by the growth of cross-language vocabulary size, compared to within-language vocabulary size, a model that incorporates total vocabulary size as a predictor instead of dominant vocabulary size should show better predictive performance.
-If the emergence of such links is explained at all by the growth of vocabulary size, both models incorporating vocabulary size as a predictor should show better predictive performance than a model incorporating participants' age.
+To test cross-language priming effects, we registered participants' time course of target picture looking in the three conditions.
+We predicted within-language priming effects, revealed as differences in target looking between *Unrelated* and *Related/Non-cognate* trials, as previously reported [@von2012language, @mani2010infant, and @mani2011phonological].
+We further predicted cross-language priming effects, revealed as differences in target looking between *Related/Non-cognate* and *Related/Cognate* trials.
+This effect should be stronger in bilinguals, if not completely absent in monolinguals, who should be indifferent to the phonological properties of the stimuli in the other language.
+
+Following previous studies associating the emergence of phonological links between lexical items to the size of children's vocabulary [@mani2011phonological], we also compared the explanatory power of two indices of receptive vocabulary size (dominant-language vocabulary size and total vocabulary size) against participants' age.
+We used parental reports of vocabulary checklist to estimate participants' vocabulary size.
+We computed vocabulary size in the dominant language (L1 vocabulary) as the proportion of words in the dominant language reported by their caregivers to be understood by the child in a vocabulary checklist, and the total vocabulary size as the proportion of words reported as understood by the child in *both* languages.
+If within-language or cross-language phonological associations in the lexicon emerge as a function of vocabulary growth, the size of the differences between conditions should larger in participants with larger vocabulary sizes.
+A model including participants' L1 or total vocabulary size as a predictor should then show better performance than a model that instead includes participants age.
+In the case of bilinguals, if the emergence of cross-language priming effects is associated with the growth of their vocabulary is *both* languages, a model including total vocabulary size as a predictor should perform better than a model that includes L1 vocabulary size.
+The opposite pattern would indicate that cross-language priming effects emerge as a function of the growth of L1 vocabulary.
+
+Testing bilingual populations at early ages presents the limitation that the vocabulary size of participants' non-dominant language is relatively small, which substantially constrains the number of items that can be used to as stimuli in the task, as well as the number of trials that can be constructed to generate stimuli lists.
+In order to circumvent the problem of limited vocabulary knowledge in the non-dominant language, tested participants only in their dominant language, therefore directing our research to the question of how possessing a second language affects processing of the dominant one in bilingual toddlers [@costa2014does provide a fuller description of the advantages of such approach].
 
@@
 			  cells_column_labels()) |> 
-	tab_style(cell_text(weight = "bold"),
+	tab_style(cell_text(style = "italic"),
 			  cells_column_spanners())
+
+# col_names <- c("Group",
+# 			   "Language",
+# 			   "Sessions", 
+# 			   "Participants",
+# 			   "M (SD)",
+# 			   "Range",
+# 			   "M (SD)",
+# 			   "M (SD)",
+# 			   "M (SD)")
+# participants_bcn |> 
+# 	unnest_wider(doe) |> 
+# 	select(-matches("others")) |> 
+# 	arrange(lp, test_language) |> 
+# 	summarise(n = n(),
+# 			  n_participants = n_distinct(child_id),
+# 			  across(age, lst(mean, sd, min, max)),
+# 			  across(matches("doe_"), lst(mean, sd)),
+# 			  # age_vctr = list(age),
+# 			  .by = c(lp, test_language)) |> 
+# 	mutate(age_mean = sprintf("%.1f (%.1f)", age_mean, age_sd),
+# 		   age_range = sprintf("%.1f-%.1f", age_min, age_max),
+# 		   doe_catalan = sprintf("%.1f (%.1f)", doe_catalan_mean*100, doe_catalan_sd*100),
+# 		   doe_spanish = sprintf("%.1f (%.1f)", doe_spanish_mean*100, doe_spanish_sd*100),
+# 		   doe_english = sprintf("%.1f (%.1f)", doe_english_mean*100, doe_english_sd*100)) |> 
+# 	select(lp:age_mean, age_range, doe_catalan, doe_spanish, doe_english) |> 
+# 	kable(digits = 1, 
+# 		  format = "latex",
+# 		  booktabs = TRUE,
+# 		  col.names = col_names,
+# 		  align = "llrrrrrrrrrrrr"
+# 	) |> 
+# add_header_above(c(
+# 	" " = 4,
+# 	"Age (months)" = 2,
+# 	"Degree of exposure (%)" = 8
+# )) |> 
+# 	row_spec(nrow(tbl_data) - 1,
+# 			 hline_after = TRUE
+# 	) 
+# 	add_footnote("For participants exposed to Catalan and Spanish exclusively, the proportion of Catalan exposure shown in the table is complementary to the degree of exposue to Spanish.
+For participants exposed to a third languages this proportion is not complementary unless one adds the degree of exposed to the third language, which never exceeded 10\\%.
+Participants with 100\\%, 0\\%, and 50\\% Catalan exposure would be traditionaly classified as Catalan monolingual, Spanish monolingual, and Catalan-Spanish bilingual, respectively.", notation = "none", escape = FALSE)
 ```
@@
 Grey lines connect vocabulary size scores from the recurrent participants.
-For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested."
-#| fig-width: 8
-#| fig-height: 4.5
+For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested.
+Only participants included in the final data set are shown."
+#| fig-width: 6
+#| fig-height: 3.5
 vocabulary_bcn |> 
+	inner_join(filter(attrition_participants, is_valid_participant)) |> 
 	pivot_longer(c(total_prop, l1_prop),
@@
 		 fill = "Group") +
-	scale_y_continuous(labels = scales::percent) +
+	scale_y_continuous(labels = scales::percent,
+					   limits = c(0, 1)) +
 	theme(panel.grid.major.y = element_line(linetype = "dotted",
@@
 For instance, the Catalan prime word *barret* was presented with the *bici*-*porta* target-distractor pair in one list, with the *bici*-*porta* pair in another list, and with *berenar*-*amanida* in the remaining list.
+To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias2009lexical].
 The order of the trials was randomised across experimental session, so that each time a participant was tested, the order in which the prime-target-distractor was presented was randomised.
@@
 
-We examined the overall equivalence of the three trial types by comparing them across three variables relating to the target word: lexical frequency, word prevalence, animacy
+We examined the overall equivalence of the three trial types by comparing them across three variables relating to the target word: lexical frequency, word prevalence, animacy.
 @tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
@@
 
-For each word, we created a picture with a typical referent.
-To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias2009lexical].
+Each word was depicted by a realistic phonographic representation of a typical exemplar.
+Image backgrounds were removed from the original pictures using the GNU Image Manipulation Program (GIMP), resized to a rectangle of a maximum of 400 pixels hight or wide, and finally placed in the centre of a 50% grey rectangle square of 500$\times$500 pixels.
+The final stimuli had a resolution of 72 dpi.
+When presented in the eye-tracker screen, the areas of interest (AOI) occupied an area of 13.23$\times$13.23 cm (11.613º visual angle from participants' perspective).
 
@@
 ![Experimental task design with examples in Catalan.
-In each trial, the prime image is presented in silence for 3,000 ms.
+In each trial, the prime image is presented in silence for 1,500 ms.
 The the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
@@
 Each experimental session took approximately 10 minutes.
-
-### Apparatus
-
-see https://link.springer.com/article/10.3758/s13428-021-01762-8
 
@@
 									.keep_all = TRUE)$is_valid_participant) 
+n_exc_participants_vocab <- sum(!distinct(attrition_bcn,
+										  session_id,
+										  .keep_all = TRUE)$is_valid_vocab_size)
 
@@
 
-After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`).
+After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
 The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
@@
 	arrange(desc(lp)) |> 
-	# across(n_trials, lst(mean, sd, sum), na.rm = TRUE),
-
 	pivot_wider(id_cols = lp,
@@
 stan_version <- "2.33.0"
-```
-
-We used multilevel General Additive Models (GAMs) to model our data and test our hypotheses [@pedersen2019hierarchical].
+
+rope_interval <- c(-0.1, +0.1)
+```
+
+We used Bayesian Hierarchical General Additive Models (HGAMs) to model our data and test our hypotheses [@pedersen2019hierarchical].
 First, we defined our response variable as the empirical logit of target looking using @eq-elogit across all eye-tracking samples for each each participant in each condition [@barr2008analyzing; @agresti2012categorical].
@@
 
-We added *Session* as grouping variable, by by-session intercept and *Condition* slopes.
-Each level in the *Session* variable uniquely indexes all observations generated by a participant in a single testing session.
-Testing sessions from the same participant are identified by different indexes.
-For computational limitations, adding both participants and testing sessions as grouping variable in the random effects structure of the model was not possible.
-We instead included testing sessions alone, as observations from the same testing session are more likely to be highly correlated than those from the same participant in different testing sessions (which were recorded at least four months apart).
-To model the time course of target looking across time bins, we included cubic regression splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
-For both splines, we specified $k = 9$ basis functions or *knots*--half the number of time bins---for computational convenience.
+We included *Session*---which indexes individual testing sessions that may belong to the same participant---as grouping variable, nested within *Participant* grouping variable---which indexes a distinct participant.
+This nested random effects structure incorporates the longitudinal design of data collection, in which multiple participants were tested more than once at different ages.
+We added by by-session intercepts and *Condition* slopes, and by-participant intercepts and *Age* slopes.
+To model the time course of target looking across time bins, we included B-splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
+For both splines, we specified $k = 6$ basis functions or *knots*.
 @eq-model shows a formal implementation of the model.
@@
 &X \in \{\text{Age}, \text{L1 vocabulary}, \text{Total vocabulary}\} \\
+&b_{j_{0-1}} \text{ are the basis cubic spline basis functions} \\
 &k \text{ is the number of knots in the spline (10)} \\
@@
 
-The comparison between the three models including *Age*, *L1 vocabulary*, *Total vocabulary* as predictors was performed using leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it [@vehtari2017practical].
+The comparison between the three models including *Age*, *L1 vocabulary*, *Total vocabulary* as predictors was done using leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it [@vehtari2017practical].
 We implemented the model using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
-We ran `r english::words(dim(model_fits_bcn$fit_0$fit)[2])` iteration chains using the by-default No U-Turn Sampler algorithm with `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` iterations each and an additional `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` warm-up iterations per chain.
-
-## Results
-
-```{r results-0}
-var_labels <- c("b_Intercept" = "Intercept",
-				"b_age_std" = "Age (+1 SD)",
-				"b_condition1" = "Condition (U vs. RN)",
-				"b_condition1" = "Condition (RN vs. RC)",
-				"b_lp1" = "Group",
-				"sd_child_id__Intercept" = "Intercept",
-				"sd_child_id__age_std" = "Age",
-				"sd_child_id__lpBilingual" = "Group",
-				"sd_child_id:session_id__Intercept" = "Intercept",
-				"sd_child_id:session_id__age_std" = "Age",
-				"sd_child_id:session_id__lpBilingual" = "Group")
-
-get_coefs <- function(model, var_labels, ...) {
-	out <- model |> 
-		gather_draws(...) |> 
-		median_hdci(.width = 0.95) |> 
-		mutate(.variable_name = factor(.variable, 
-									   levels = names(var_labels), 
-									   labels = var_labels),
-			   mdn_label = sprintf("%.3f", .value),
-			   ci_label = sprintf("[%.3f, %.3f]", .lower, .upper)) |> 
-		arrange(.variable) |> 
-		select(.variable:.upper, matches("label")) %>%
-		split(janitor::make_clean_names(.$.variable))
-
-	return(out)
-}
-coefs <- map(model_fits_bcn, 
-			 \(x) get_coefs(model = x, var_labels,
-			 			   `b_.*`, `sd_.*`, regex = TRUE))
-
-get_loos <- function(x, y) {
-	out <- lst(m_0 = x, m_1 = y) |> 
-		loo_compare() |> 
-		as.data.frame() |> 
-		rownames_to_column("model") |>
-		arrange(model) |> 
-		select(model, elpd_diff, se_diff) |> 
-		mutate(diff_label = sprintf("%.3f", elpd_diff),
-			   se_label = sprintf("%.3f", se_diff))
-	return(out)
-}
-
-loos_tbl <- loo_compare(model_loos_bcn[1:5]) |> 
-	as.data.frame() |> 
-	rownames_to_column("model") |> 
-	select(model, matches("diff|elpd"))
-
-```
-
-```{r tbl-loos}
-loos_tbl[1:5] |> 
-	mutate(model = case_when(model=="fit_0" ~ "$\\mathcal{M}_{0}$",
-							 model=="fit_1" ~ "$\\mathcal{M}_{1}$",
-							 model=="fit_2" ~ "$\\mathcal{M}_{2}$",
-							 model=="fit_3" ~ "$\\mathcal{M}_{3}$",
-							 model=="fit_4" ~ "$\\mathcal{M}_{4}$",
-							 model=="fit_5" ~ "$\\mathcal{M}_{5}$")) |>
-	gt() |> 
-	fmt_number(is.numeric) |> 
-	# fmt_markdown(is.character, ) |> 
-	cols_label(elpd_diff = "ELPD (diff.)",
-			   se_diff = "SE ELPD (diff)",
-			   elpd_loo = "ELPD",
-			   se_elpd_loo = "SE ELPD")
-```
-
-@tbl-loos summarises the outputs of the LOO-CV model comparisons.
-Models $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ showed substantially better predicted performance than models $\mathcal{M}_{0}$ and $\mathcal{M}_{1}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
-All $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ models showed equivalent performance, suggesting that adding the two-way and three-way interactions between *Age*, *Group*, and *Condition*, did not improve the the fit of the model.
-We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{4}$.
-We report the median and 95% highest density interval of each fixed regression coefficient.
-
-The outcomes of $\mathcal{M}_{0}$, which only included *Age* and as main effect, revealed successful word recognition across participants.
-Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_0$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$b_intercept$ci_label`).
-The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_0$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_0$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_session_id_intercept$ci_label`).
-The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_0$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_0$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
-
-The 95% HDI of the coefficient of *Group* in $\mathcal{M}_{1}$ included zero ($\beta$ = `r coefs$fit_1$b_lp1$mdn_label`, 95% HDI = `r coefs$fit_1$b_lp1$ci_label`), indicating an equivalent overall target preference in monolinguals and bilinguals.
-The 95% HDI of the first contrast of this predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_2$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition1$ci_label`).
-The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_2$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition2$ci_label`).
-The overall target preference was equivalent across both pairwise condition comparisons.
-The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$fit_3$b_condition1_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1_lp1$ci_label`).
-The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$fit_3$b_condition2_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2_lp1$ci_label`).
-The outcomes of this model indicate that lack of differences in overall target looking time across conditions remained across monolinguals and bilinguals.
-
-Both younger and older participants showed equivalent looking time across conditions, as suggested by the fact that the 95% HDI of the two-way interaction between *Age* and the first *Condition* contrast included zero ($\beta$ = `r coefs$fit_4$b_condition1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_age_std$ci_label`), as well as the interaction between *Age* and the second *Condition* contrast ($\beta$ = `r coefs$fit_4$b_condition2_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_age_std$ci_label`).
-This pattern of results was found in both monolinguals and bilinguals, as the 95% HDI of the three-way interaction between *Age*, *Group*, and *Condition* included zero both the first ($\beta$ = `r coefs$fit_4$b_condition1_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_lp1_age_std$ci_label`) and second ($\beta$ = `r coefs$fit_4$b_condition2_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_lp1_age_std$ci_label`) contrast of *Condition*.
-
-```{r timecourse}
-make_std <- function(x, mean, sd) (x - mean) / sd
-
-timebin_values <- make_std(seq(0, 17, length.out = 100),
-						   mean(data_bcn$timebin),
-						   sd(data_bcn$timebin))
-
-age_values <- make_std(c(20, 30),
-					   mean(data_bcn$age),
-					   sd(data_bcn$age))
-
-nd <- expand_grid(distinct(data_bcn, condition, lp),
-				  timebin_std = timebin_values,
-				  age_std = age_values)
-
-epreds <- add_epred_draws(nd, model_fits_bcn$fit_4, 
-						  re_formula = NA,
-						  ndraws = NULL,
-						  value = ".elog") |> 
-	mutate(age_std = factor(age_std,
-							levels = age_values, 
-							labels = paste0(c(20, 30), " months")))
-
-epreds_chance <- epreds |> 
-	median_hdci() |> 
-	mutate(is_lower_positive = .lower > 0) |> 
-	filter(is_lower_positive) |> 
-	summarise(over_chance = min(timebin_std),
-			  .by = c(lp, condition, age_std)) |> 
-	mutate(over_chance = (over_chance * 
-						  	sd(data_bcn$timebin) +
-						  	mean(data_bcn$timebin))*100+300)
-
-epreds_chance_report <- epreds_chance |> 
-	mutate(over_chance = sprintf("%.2f", over_chance),
-		   age_std = paste0("age_", gsub(" months", "", age_std))) |> 
-	arrange(lp, age_std) %>%
-	split(tolower(.$lp)) |> 
-	map(\(x) split(x, x$age_std)) 
-```
-
-An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
-Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
-
-```{r fig-epreds}
-#| label: fig-epreds
-#| fig-cap: "Posterior mean prdictions of the time course of target fixation in the test phase.
-Lines and intervals indicate the median and 95% credible interval of the posterior predictions, respectively."
-#| fig-width: 8
-#| fig-height: 4
-epreds |> 
-	ggplot(aes(timebin_std, .elog,
-			   colour = condition,
-			   fill = condition)) +
-	facet_grid(lp~age_std) +
-	geom_hline(yintercept = 0, linetype = "dashed") +
-	stat_summary(fun.data = mean_qi,
-				 geom = "ribbon",
-				 alpha = 1/2,
-				 linewidth = NA) +
-	stat_summary(fun = mean,
-				 geom = "line",
-				 linewidth = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "Logit (Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
-										 mean(data_bcn$timebin),
-										 sd(data_bcn$timebin)),
-					   labels = \(x) format(seq(3e2, 2e3, 3e2),
-					   					 big.mark = ",")) &
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  legend.position = "top")
-```
-
-In an exploratory analysis, we compared the model-estimated time points at which participants' gaze behaviour showed evidence of target looking above chance level (50%).
-We defined the recognition time of the trial as the earliest time point at which the lower bound of the 95% HDI posterior mean prediction of the target looking excluded zero.
-As expected, the recognition times were on average shorter for older infants than for younger infants.
-Differences between conditions were larger in bilinguals than in monolinguals, especially in the older group.
-The recognition time for monolingual 20-month-olds was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-
-```{r fig-recognition}
-#| label: fig-recognition
-#| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
-#| fig-width: 7
-#| fig-height: 3
-epreds_chance |> 
-	ggplot(aes(lp, over_chance,
-			   colour = sort(condition),
-			   fill = sort(condition))) + 
-	facet_wrap(~age_std) +
-	geom_point(shape = 16, size = 4) +
-	geom_line(aes(group = condition),
-			  linewidth = 1) +
-	# geom_point(size = 3) +
-	labs(x = "Group",
-		 y = "Recognition time (ms)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_y_continuous(breaks = seq(0, 1e3L, 50)) +
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  panel.grid.minor.y = element_line(colour = "grey",
-		  								  linetype = "dotted"),
-		  legend.position = "top",
-		  axis.title.x = element_blank())
-```
+We ran four iteration chains using the by-default No U-Turn Sampler algorithm with 1,000 iterations each and an additional 1,000 warm-up iterations per chain.
+
+#### Statistical inference
+
+We assessed the practical relevance of the estimated regression coefficients of the model following @kruschke2018bayesian.
+First, we specified a region of practical equivalence (ROPE) from `r rope_interval["lower"]` to +`r rope_interval["upper"]`, in the probability scale.
+This region indicates the range of values that we considered equivalent to zero.
+We then summarised the posterior distribution of each regression coefficient with the 95% highest density interval (HDI).
+This interval contains the true value of this coefficient with 95% probability, given the data.
+Finally, we calculated the proportion of posterior samples in the 95% HDI that fell into the ROPE, noted as $p(\text{ROPE})$, which indicates the probability that the true value of the regression coefficient falls into the ROPE (and therefore should be considered equivalent to zero).
+For example, $p(\text{ROPE})=.80$ indicates that, given our data, there is a 80% probability that the true value of the coefficient falls within the ROPE, and can therefore be considered equivalent to zero.
 
 # Study 2
+
+In this study, we conducted a conceptual replication of @mani2010infant and @mani2011phonological.
+Using the same task from Study 1, we tested a same-aged group of monolinguals being exclusively raised in British English speaking homes, the same population tested in the original studies.
+As in Study 1, we manipulated the phonological relationship between the prime and target labels at word onset, as well as the cognate status of the prime label.
+Evidence from implicit naming of prime images would be revealed by differences in target looking or its time course across the trials between *Unrelated* trials, and *Related/Non-cognate* and *Related/Cognate* trials.
+Given that participants in this study are monolinguals---and contrary to the monolinguals in Barcelona, have received no exposure to any other language---we would not expect the cognate status of the prime labels to exert any effect on subsequent target recognition.
 
@@
 Vocabulary size scores from the recurrent participants are shown linked."
-#| eval: false
 #| fig-width: 4
@@
 
+n_exc_participants_vocab <- attrition_oxf |> 
+	distinct(child_id, .keep_all = TRUE) |> 
+	mutate(is_valid_vocab_size = !is_valid_vocab_size) |> 
+	pull(is_valid_vocab_size) |> 
+	sum(na.rm = TRUE)
+
 n_longitudinal <- attrition_oxf |>
@@
 From the trials included in the final dataset dataset, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), were `r n_trials_condition$non_cognate_2$n` *Related/Non-cognate* trials(`r n_trials_condition$non_cognate$n` previously excluded), and `r n_trials_condition$cognate_2$n` were *Related/Cognate* trials (`r n_trials_condition$cognate$n` previously excluded).
-
-## Results
-
-```{r results-oxf}
-var_labels <- c("b_Intercept" = "Intercept",
-				"b_age_std" = "Age (+1 SD)",
-				"b_condition1" = "Condition (U vs. RN)",
-				"b_condition1" = "Condition (RN vs. RC)",
-				"sd_child_id__Intercept" = "Intercept",
-				"sd_child_id__age_std" = "Age",
-				"sd_child_id:session_id__Intercept" = "Intercept",
-				"sd_child_id:session_id__age_std" = "Age",
-				"sd_child_id:session_id__lpBilingual" = "Group")
-
-coefs <- map(model_fits_oxf, 
-			 \(x) get_coefs(model = x, var_labels,
-			 			   `b_.*`, `sd_.*`, regex = TRUE))
-
-loos_tbl <- loo_compare(model_loos_oxf) |> 
-	as.data.frame() |> 
-	rownames_to_column("model") |> 
-	select(model, matches("diff|elpd"))
-
-```
-
-```{r tbl-loos-oxf}
-loos_tbl |> 
-	mutate(model = case_when(model=="fit_oxf_0" ~ "$\\mathcal{M}_{0}$",
-							 model=="fit_oxf_1" ~ "$\\mathcal{M}_{1}$",
-							 model=="fit_oxf_2" ~ "$\\mathcal{M}_{2}$",
-							 model=="fit_oxf_3" ~ "$\\mathcal{M}_{3}$")) |>
-	gt() |> 
-	fmt_number(is.numeric) |> 
-	# fmt_markdown(is.character, ) |> 
-	cols_label(elpd_diff = "ELPD (diff.)",
-			   se_diff = "SE ELPD (diff)",
-			   elpd_loo = "ELPD",
-			   se_elpd_loo = "SE ELPD")
-```
-
-@tbl-loos summarises the outputs of the LOO-CV model comparisons.
-Models $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ showed substantially better predicted performance than models $\mathcal{M}_{0}$ and $\mathcal{M}_{1}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
-All $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ models showed equivalent performance, suggesting that adding the two-way and three-way interactions between *Age*, *Group*, and *Condition*, did not improve the the fit of the model.
-We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{4}$.
-We report the median and 95% highest density interval of each fixed regression coefficient.
-
-The outcomes of $\mathcal{M}_{0}$, which only included *Age* and as main effect, revealed successful word recognition across participants.
-Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_0$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$b_intercept$ci_label`).
-The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_0$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_0$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_0$sd_child_id_session_id_intercept$ci_label`).
-The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_0$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_0$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
-
-The 95% HDI of the coefficient of *Group* in $\mathcal{M}_{1}$ included zero ($\beta$ = `r coefs$fit_1$b_lp1$mdn_label`, 95% HDI = `r coefs$fit_1$b_lp1$ci_label`), indicating an equivalent overall target preference in monolinguals and bilinguals.
-The 95% HDI of the first contrast of this predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_2$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition1$ci_label`).
-The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_2$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_2$b_condition2$ci_label`).
-The overall target preference was equivalent across both pairwise condition comparisons.
-The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$fit_3$b_condition1_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1_lp1$ci_label`).
-The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$fit_3$b_condition2_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2_lp1$ci_label`).
-The outcomes of this model indicate that lack of differences in overall target looking time across conditions remained across monolinguals and bilinguals.
-
-Both younger and older participants showed equivalent looking time across conditions, as suggested by the fact that the 95% HDI of the two-way interaction between *Age* and the first *Condition* contrast included zero ($\beta$ = `r coefs$fit_4$b_condition1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_age_std$ci_label`), as well as the interaction between *Age* and the second *Condition* contrast ($\beta$ = `r coefs$fit_4$b_condition2_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_age_std$ci_label`).
-This pattern of results was found in both monolinguals and bilinguals, as the 95% HDI of the three-way interaction between *Age*, *Group*, and *Condition* included zero both the first ($\beta$ = `r coefs$fit_4$b_condition1_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_lp1_age_std$ci_label`) and second ($\beta$ = `r coefs$fit_4$b_condition2_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_lp1_age_std$ci_label`) contrast of *Condition*.
-
-```{r timecourse-oxf}
-timebin_values <- make_std(seq(0, 17, length.out = 100),
-						   mean(data_oxf$timebin),
-						   sd(data_oxf$timebin))
-
-age_values <- make_std(c(20, 30),
-					   mean(data_oxf$age),
-					   sd(data_oxf$age))
-
-nd <- expand_grid(distinct(data_oxf, condition),
-				  timebin_std = timebin_values,
-				  age_std = age_values)
-
-epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_2, 
-						  re_formula = NA,
-						  ndraws = NULL,
-						  value = ".elog") |> 
-	mutate(age_std = factor(age_std,
-							levels = age_values, 
-							labels = paste0(c(20, 30), " months")))
-
-epreds_chance <- epreds |> 
-	median_hdci() |> 
-	mutate(is_lower_positive = .lower > 0) |> 
-	filter(is_lower_positive) |> 
-	summarise(over_chance = min(timebin_std),
-			  .by = c(condition, age_std)) |> 
-	mutate(over_chance = (over_chance * 
-						  	sd(data_oxf$timebin) +
-						  	mean(data_oxf$timebin))*100+300)
-
-epreds_chance_report <- epreds_chance |> 
-	mutate(over_chance = sprintf("%.2f", over_chance),
-		   age_std = paste0("age_", gsub(" months", "", age_std))) |> 
-	arrange(age_std) %>%
-	split(tolower(.$age_std)) 
-```
-
-An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
-Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
-
-```{r fig-epreds-oxf}
-#| label: fig-epreds-oxf
-#| fig-cap: "Posterior mean prdictions of the time course of target fixation in the test phase.
-Lines and intervals indicate the median and 95% credible interval of the posterior predictions, respectively."
-#| fig-width: 8
-#| fig-height: 4
-epreds |> 
-	ggplot(aes(timebin_std, .elog,
-			   colour = condition,
-			   fill = condition)) +
-	facet_wrap(~age_std) +
-	geom_hline(yintercept = 0, linetype = "dashed") +
-	stat_summary(fun.data = mean_qi,
-				 geom = "ribbon",
-				 alpha = 1/2,
-				 linewidth = NA) +
-	stat_summary(fun = mean,
-				 geom = "line",
-				 linewidth = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "Logit (Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
-										 mean(data_bcn$timebin),
-										 sd(data_bcn$timebin)),
-					   labels = \(x) format(seq(3e2, 2e3, 3e2),
-					   					 big.mark = ",")) &
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  legend.position = "top")
-```
-
-In an exploratory analysis, we compared the model-estimated time points at which participants' gaze behaviour showed evidence of target looking above chance level (50%).
-We defined the recognition time of the trial as the earliest time point at which the lower bound of the 95% HDI posterior mean prediction of the target looking excluded zero.
-As expected, the recognition times were on average shorter for older infants than for younger infants.
-Differences between conditions were larger in bilinguals than in monolinguals, especially in the older group.
-The recognition time for monolingual 20-month-olds was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-
-```{r fig-recognition-oxf}
-#| label: fig-recognition-oxf
-#| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
-#| fig-width: 7
-#| fig-height: 3
-epreds_chance |> 
-ggplot(aes(age_std, over_chance,
-colour = sort(condition),
-fill = sort(condition))) + 
-geom_point(shape = 16, size = 4) +
-geom_line(aes(group = condition),
-linewidth = 1) +
-# geom_point(size = 3) +
-labs(x = "Group",
-y = "Recognition time (ms)",
-colour = "Condition",
-fill = "Condition") +
-scale_y_continuous(breaks = seq(0, 1e3L, 25)) +
-theme(panel.grid.major.y = element_line(colour = "grey",
-linetype = "dotted"),
-panel.grid.minor.y = element_line(colour = "grey",
-linetype = "dotted"),
-legend.position = "top",
-axis.title.x = element_blank())
-```
-
-## Discussion
-
-# General discussion
-
-# References

### 2023-11-09 manuscript/manuscript.qmd
Add new comments by NSG

@@
 library(gtExtras)
+library(marginaleffects)
 
@@
 
-Building a mental lexicon is a major achievement in the development of an infant.
-By storing representations of how familiar words sound and what they mean, an infant is able to make sense of their linguistic input.
-Infants start forming their first lexical representations before their first year of life [@tincoff1999some; @halle1994emergence; @vihman2004cross; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
-This initial lexicon consists of only a few items; mainly words for people, interjections, body parts, and food [@tincoff2012six; @tardif2008baby], but it undergoes rapid growth during their second year of life [@ganger2004reexamining; @goldfield1990early; @bloom2002children; @mcmurray2007defusing].
-According to parental reports the average 15-month-old infant already understands more than 100 words, and by two years, they understand more than 400 words [@frank2021variability].
+Building a mental lexicon is a major achievement in the development of an infant: by storing representations of how familiar words sound and what they mean, an infant is able to make sense of their linguistic input.
+The foundations of an initial lexicon are in place before their first year of life [@tincoff1999some; @halle1994emergence; @vihman2004cross; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
+This initial lexicon consists of only a few items; mainly words for people, interjections, body parts, and food [@tincoff2012six; @tardif2008baby], but it undergoes rapid growth during the second year of life [@ganger2004reexamining; @goldfield1990early; @bloom2002children; @mcmurray2007defusing].
+According to parental reports, the average 15-month-old infant already understands more than 100 words, and by two years, they understand more than 400 words [@frank2021variability].
 This accelerated lexical developmental is reflected in infants' trajectories of word recognition: infants recognise familiar words faster and more efficiently as they approach their second birthday [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
-
 Despite being exposed to a more complex linguistic input, bilinguals show equivalent trajectories of word acquisition and word recognition to their monolingual peers' [@vihman2007onset; @legacy2018vocabulary; @hoff2012dual; @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes].
@@
 Second, they face a more complex referential context, since they often learn two labels for each referent, one in each language.
-The mechanisms that allow bilingual infants to keep up with monolinguals in their lexical development trajectories are still unclear.
-
-Monolinguals and bilinguals share broadly common word-recognition mechanisms.
-The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal, which results in the activation of lexical representations whose associated phonological forms match the acoustic signal.
-The activated word-forms then compete for selection: the lexical system uses the bottom-up information provided by the auditory input, together with top-down context---provided by grammatical, supra-segmental, and semantic constraints---to select the candidate lexical representation with the best match.
-This sequence of events occurs in a *cascaded* fashion.
-As the recognition system accumulates information about the unfolding acoustic signal, matching phonological representations are activated [@marslen1987functional; @marslen1978processing; @grosjean1980spoken], and in turn activate their associated semantic representations [@neely1977semantic].
-By the time lexical selection occurs, many non-selected phonological and semantic representations have been activated, potentially modulating the dynamics of word recognition.
-
-A considerable amount of evidence for such cascaded account of lexical processing has been provided by studies recording eye movements during word recognition.
-For example, @allopenna1998tracking designed a word-recognition task in which participants were presented, in each trial, with four objects in the screen.
-Participants would then listen to a command like "Pick up the beaker; now put it below the diamond", and perform the action.
-The authors manipulated the phonological relationship between the target object's label (e.g., *casket*), and the label of each of the three distractors.
-Two of the distractors were phonologically related with the target, sharing onset (e.g., *castle*) or offset (e.g., *basket*) with the target word, respectively.
-The other distractor was phonologically unrelated to the target (e.g., *nickel*).
-After hearing the target label, phonological distractors attracted participants' eye fixations more than unrelated distractors.
-Distractors sharing phonological onset did so at an earlier time window than those sharing phonological offset.
-This time course of distractor fixations suggests that the auditory presentation of the target label activated no only its (subsequently selected) phonological form in participants' lexicon, but also that of phonologically related word-forms, leading to competition for selection between the word forms.
-These results converge with cascaded models of auditory word recognition, in which the unfolding acoustic input activates multiple phonological word-forms, which in turn compete for selection, like TRACE [@mcclelland1986trace] and Shortlist [@norris1994shortlist].
-
-The developing mental lexicon also seems to operate in this cascaded fashion.
-Like adults, infants activate non-selected lexical representations.
-This is reflected by the fact that from 21 months of age, infants' lexicon seems to also be systematically organised according to the semantic and phonological properties of its lexical representations.
-Priming paradigms of word recognition have provided a strong body of evidence for the existence of phonological and semantic links between early lexical representations between 18 and 21 months of age [@arias2009lexical; @styles2009infants].
-For instance, using a word recognition task, @arias2009lexical found that infants' spoken word recognition (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
-Other studies have provided electrophysiological evidence of semantic priming at earlier ages [e.g., @rama2013development; @friedrich2005lexical].
-More recent studies have provided evidence for the emergence of such semantic links, even in the absence of visual referents during the experimental task [@willits2013toddlers].
-
-Phonological priming effects have also been reported in the initial lexicon.
-@mani2010infant created an implicit naming task in which each trial started with the *silent* presentation of a prime picture.
-Then, a target-distractor picture pair was presented side-by-side.
-Finally, the target picture's label was presented auditorily.
-The authors manipulated the phonological overlap between the prime label and the target label, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
-Prime and target-distractor pairs were semantically unrelated.
-Interestingly, infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
-This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.The authors found a facilitation effect: target looking preference was stronger in phonologically related primes, indicating that the activated phonological segments of the generated prime label facilitated the subsequent activation of the phonological representation of the target label during recognition.
-
-In a follow-up study, @mani2011phonological found the opposite effect in older toddlers.
-After phonologically related primes, 24 month-old toddlers showed weaker target looking preference than after phonologically unrelated primes.
-These results interpreted these outcome as the result of the implicitly generated prime label interfering with the subsequent recognition of the (phonologically related) target word.
-The authors suggested that the shift from facilitation to interference from 18 to 24 months they found in both studies might be the result of a developmental shift in which 18-month-olds' lexicon is not yet organised based on phonological similarity, while 24-month-olds' is.
-This would lead to the former showing a pre-lexical facilitation effect in which such facilitation occurs via the activation of phonological segments, while the latter would show an interference effect due to lateral links between lexical representation having been established.
-
-@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
-In each trial, the authors presented participants with four semantically and phonologically pictures.
-Four seconds after pictures onset, a word-form was auditorily presented.
-The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category.
-For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
-Then they would hear the carrier phrase "Look at the *bee*!".
-The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
-These results support a cascaded activation account of lexical access during the first stages of lexical development, paralleling previous findings in adults [@allopenna1998tracking].
-
-One of the most interesting pieces of evidence in support of a cascaded account of lexical processing is provided by bilinguals.
-A critical property the bilingual lexicon is that its representations are accessed in a language-non selective way.
-Even during monolingual situations, bilinguals access their lexical representations in both of their languages [e.g., @thierry2007brain; @dunabeitia2009masked; @HOSHINO; @STROJKERS2010; @dijktra2010baayen].
-This is reflected in bilinguals' performance in word recognition and production tasks.
-For instance, @marian1999activation presented Russian-English bilinguals with a series of trials that started with an auditory instruction like "Poloji marku nije krestika" ["Put the stamp below the cross"].
-The instruction would be present in Russian (dominant language for most participants).
-The target object (*marku* [*stamp*], in this case) would be present in the screen, together with an object whose English label shared phonological onset with the target label (e.g., *mark*), and two unrelated distractors whose labels in Russian and English did not shared phonological relationship with the target label.
-Converging with @allopenna1998tracking's results in monolingual adults, after hearing the target label bilinguals fixated the cross-language phonological distractor significantly more than the unrelated distractors.
-These findings suggest that participants activated phonologically related word-forms in both Russian *and* English, which affected their overt visual exploration patterns during the task.
-
-Language non-selectivity in the bilingual lexicon has also been shown to affect top-down lexical access during word production.
-@costa2000cognate presented Catalan-Spanish bilinguals with a series of pictures of familiar objects.
+The mechanisms that allow bilingual' trajectories of lexical developmental to keep up with monolinguals' are still unclear.
+
+Previous studies have pointed to the interplay between bilingual' languages as a candidate facilitative mechanism behind bilingual lexical acquisition.
+In particular, cross-language similarity at the lexical level has been associated with larger vocabulary sizes.
+@floccia2018introduction collected vocabulary data from a sample of 367 bilingual children living in the United Kingdom, who were learning English and an additional language (out of a diverse pool of 13 languages).
+Using an edit distance-based metric of phonological similarity, the authors computed the average lexical similarity between the translation pairs of the English vocabulary checklist, and of each of the other languages.
+Children's vocabulary sizes in the additional language was positively associated with the amount of language similarity between their two languages.
+For instance, children learning English and Dutch (which share high lexical similarity) showed larger vocabulary sizes than those learning English and Mandarin (which share low lexical similarity).
+The authors suggested that the acquisition of words in the additional language might be facilitated by their cognate status (i.e., being phonologically similar to their translation equivalent).
+Larger vocabulary sizes might then be expected in bilinguals learning two languages sharing a high proportion of cognates.
+Recent studies have reported an earlier acquisition of cognate words [@mitchell2022cognates; @garcia-castro2023cognate], providing further evidence that cross-language similarity at the lexical level might boost vocabulary growth in bilinguals.
+
+The facilitative effect of cross-language similarity is in line with the language non-selective account of bilingual lexical access.
+There is robust evidence suggesting that bilingual adults activate both languages in parallel---even during monolingual situations---which influences their performance in word recognition and production tasks [@marian1999; @groot1992determinants; @schwartz2007reading; @dijkstra1999recognition; @dufour1995matching; @schwartz2007reading; @dijkstra2010cross].
+For instance @costa2000cognate presented Catalan-Spanish bilinguals with a series of pictures of familiar objects.
 For each object, participants were asked to name it in Catalan (their dominant language).
-Unbeknownst to participants, the authors manipulated the phonological overlap between the pictures' labels in Catalan and their translations in Spanish.
-In half of the trials, the labels associated to pictures were cognates, that is, phonologically similar translation equivalents in Catalan and Spanish, whereas in the other half of the trials the labels were non-cognates.
-Participants produced faster words in cognate trials (e.g., *gat*-*gat* [*cat*]) than in non-cognate trials (e.g., *taula*-*mesa* [*table*]).
+Unbeknownst to participants, the authors manipulated the cognate status pictures' labels in Catalan and Spanish.
+In half of the trials, the labels associated to the pictures were cognates (i.e., phonologically similar translation equivalents, e.g., *gat*-*gat* [*cat*]) in Catalan and Spanish, whereas in the other half of the trials the labels were non-cognates (e.g., *taula*-*mesa* [*table*]).
+Participants named pictures faster in cognate trials than in non-cognate trials.
 Critically, Spanish monolinguals who completed the same task, naming the pictures in Spanish, showed equivalent naming times in both conditions.
-These results reveal that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the activation of its associated phonological forms in both language sin parallel, which influenced the subsequent the dynamics of word production.
-the differential processing of cognates has generated a large body of literature providing support for the language-non selective account of lexical access [e.g., @degrootandnas1992; @schwartzkroll2007; @dijkstragrainger1999; @dufourkroll1995; @lemhofferetal2008]
-
-Further support for the parallel retrieval of phonological forms during word production is given by implicit naming paradigms.
-Using an adaptation of @mani2010infant's task, @von2014bilinguals provided evidence that bilingual adults generate implicit labels in both labels for visually fixated pictures.
+These results revealed that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the activation of its associated phonological forms in both languages in parallel, which influenced the subsequent the dynamics of word production.
+
+Parallel activation has also been reported in he developing lexicon [@poarch2012cross; @bosma2020cognate; @singh2014one; @jardak2019labels; @von2019impact; @floccia2020translation].
+For instance, @von2012language found evidence of cross-language phonological priming in twenty 21- to 42-months-old children learning German and English.
+In their experimental task, each trials begun with the auditory presentation of an English prime word embedded in a carrier phrase.
+Then, the target label was auditorily presented in German.
+Finally, the target and a distractor pictures were presented side-by-side.
+The authors created three conditions.
+In the phonological priming condition, the auditorily presented prime and target labels were phonologically related (e.g., *slide*-*Klide* [*dress*]).
+In the priming through translation condition, both labels were phonologically related through translation: the auditorily presented prime label did *not* overlap with the target label (e.g., *leg*-*Stein* [*stone*]), but its translation in German did [*Bein*].
+In the unrelated condition, prime and target labels were phonologically unrelated in both languages.
+Interestingly, participants showed a weaker target preference in priming through translation trials, compared to unrelated trials.
+This was interpreted evidence of the lexical representations of the prime labels being activated in both English and German, leading to interference effects in later target recognition.
+
+Previous studies had reported similar cross-language priming effects.
+The conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was nonetheless unwarranted.
+In studies where the auditorily presented prime label was phonologically overlapped with the target label [e.g., @marian1999activation], priming effects might be explained by the activation of the phonological segments of the prime label, which facilitated the recognition of the target label, which shared such phonological segments.
+This might have been the phonological priming trials in @von2012language, in which prime and target labels shared overt phonological overlap.
+In contrast, the priming through translation results suggest that cross-language activation in the developing lexicon occurs at the lexical level.
+Since participants' target recognition was modulated by the non-presented prime translation, such an inhibitory effect must stem at the lexical level.
+The fact that phonological priming facilitated the recognition of the target words (both labels belong to different languages), and that phonological priming through translation interfered target recognition (translation and target belong to the same language) points to cross-language connections playing an excitatory role, and to within-language connections playing an inhibitory role.
+
+Despite extending the available knowledge on the developing bilingual lexicon, the study by @von2012language has some methodological challenges that prevent strong conclusions about language non-selective access.
+First, participants' received their English input at school, where they heard German and English (between three and four hours each) from a German native speaker.
+Except for four children who also listened to English at home, participants' only exposure to English was 3-4 hours per day, for the time they attended daycare (an average of 12.35 months).
+Assuming that infants are exposed to a daily average of 12 total hours of speech, and they attended daycare only during weekdays, their estimated exposure to English throughout the week represented between `r scales::percent((3*5*4*12.35)/(12*7*4*21), accuracy = 0.01)` and `r scales::percent((4*5*4*12.35)/(12*7*4*21), accuracy = 0.01)` for the 21 month-olds (the youngest in the sample), and between `r scales::percent((3*5*4*12.35)/(12*7*4*43))` and `r scales::percent((4*5*4*12.35)/(12*7*4*43))` for the 43-month-olds.
+Conventionally, children are considered bilingual if exposed to 25% or more of the time to a second language [@byers-heinlein2021multilab; @rocha-hidalgo2023defining].
+Participants in @von2012language might therefore not be generalisable to other populations of bilinguals who received a more balanced dual language input.
+Second, the presence of cognates in the stimuli lists lead to some primes in the phonological priming condition sharing substantial cross-language phonological overlap thought translation with the target words like *fire* /\textipa{faIe}/--*Feuer* /\textipa{fOyeR}/ and *Eier* /\textipa{aIeR}/, or *Moon* /\textipa{mu:n}/--*Mond* /\textipa{mo:nd}/ and *Huhn* /\textipa{hu:n}/.
+Conversely, some trials in the phonological priming through translation shared within-language overlap with the target, such as *Soup* /\text{su:p}/--*Suppe* /\textipa{zupe}/---*Puppe* /\text{pupE}/ and *Puppe* /\textipa{pupE}/.
+Given that the number of total trials in both conditions amounted to six trials, a considerable proportion of the trials presented this methodological limitation.
+Finally, the observed pattern of results was dependent on the inclusion of a single item, *Buch* [*book*, in German].
+When this item was included, monolinguals showed a similar interference effect to bilinguals in the priming through translation condition, in which only bilinguals with knowledge of the translation should show an effect.
+Additionally, given that monolinguals and bilinguals were not directly, it is not possible to conclude that the differences in statistical significance between monolingual and bilingual target looking, compared to chance levels, does not necessarily provide a significant difference between the two groups.
+As a consequence, the conclusion that the interference effects observed in the priming through translation condition is exclusive to bilinguals (which would suggest that the priming effect were not due to the intrinsic properties of the stimuli) in unwarranted.
+
+Additionally, although the priming through translation paradigm provides a convenient framework to investigate parallel activation in the bilingual lexicon, its design prevents strong interpretations about the extent to which parallel activation is the result of the experimental manipulations of interest.
+The presentation of primes and targets in both languages in the same task---or even within the same trial---presents participants with a bilingual context that might lead to a higher baseline activation of lexical representations of both languages, contrary to a context in which parallel activation results from genuine cross-language activation [@grosjean1997bilingual].
+Another limitation of priming through translation studies is that, when prime words are auditorily presented, the task constrains the naming context to one of the languages.
+The consequence is a potential asymmetry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
+This might lead to a lower strength, and higher latency of the activation of the translation.
+In summary, current evidence on the cross-language interplay in the initial lexicon should be considered carefully.
+
+In the present study, we put the hypothesis that bilingual infants activate both languages in parallel to a more severe test.
+We used an extension of the implicit naming task by @mani2010infant, in which participants were primed with a picture presented in silence.
+Previous studies using this paradigm have successfully provided evidence of language non-selectivity.
+In particular, @von2014bilinguals found that bilingual adults generate implicit labels in both labels for visually fixated pictures.
 The authors presented German-English bilinguals with 120 prime-target pairs.
@@
 
-Phonological priming paradigms have also revealed language non-selectivity in the initial bilingual lexicon [@poarch2012cross; @bosma2020cognate; @singh2014one; @jardak2019labels; @von2019impact].
-For instance, @von2012language found evidence of cross-language phonological priming in 21- to 42-months-old children learning German and English.
-At the beginning of each trial, the authors auditorily presented an English prime word embedded in a carrier phrase.
-Then, the target label was also auditorily presented in German.
-Finally the target and distractor pictures were presented side-by-side.
-The authors manipulated the phonological overlap between the prime and target labels.
-The novelty in this study lied in the orthogonal manipulation of the phonological overlap between both English and German labels.
-In some trials, the auditorily presented prime and target labels were phonologically related (e.g., *slide*-*Klide* [*dress*]).
-In some other trials, both labels were phonologically related through translation: the auditorily presented prime label did *not* overlap with the target label (e.g., *leg*-*Stein* [*stone*]), but its translation in German did [*Bein*].
-In the rest of the trials prime and target labels were phonologically unrelated in both languages.
-The authors found a facilitation effect of cross-language priming when both prime and target auditory labels overlapped phonologically, as revealed by a stronger target picture looking preference, as compared to that of unrelated trials.
-Interestingly, participants showed a weaker target preference in priming through translation trials.
-
-Using a similar task, @floccia2020translation provided conflicting results to those of @von2012language.
-The authors tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
-The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, French, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
-A prime word was embedded at the end of a carrier sentence that participants listened to.
-Then, participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
-In Study 1, the target word was the translation equivalent of the prime word (*cheese*-*fromage* for an English-French bilingual).
-In other trials, prime and target words were unrelated (e.g., *sock*-*fromage*).
-There was no phonological overlap at onset between prime and target or distractor labels in either of the two conditions.
-Participants were presented with two blocks of related and unrelated trials.
-In one of the blocks, participants were presented with English prime words and Home Language target words (*sock*-*fromage*), and in the other block they were presented with Additional Language prime words and English target words (*fromage*-*sock*).
-The authors found a cross-linguistic priming effect, in which participants showed a stronger preference for the target picture in the post-naming phase in related trials, as compared to unrelated trials.
-This effect was found regardless of the language of the prime (English or Home Language), or the dominance of the language of the prime (i.e., whether the prime word belonged to the dominant language).
-Target preference exceeded chance level in both conditions.
-
-In Study 2, the authors tested a similar group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
-This time, prime and target words were not translation equivalents, but rather words whose referents shared semantic features.
-Results from Study  2 were parallel to those from Study 1.
-The authors found a strong semantic priming effect across languages, regardless of the language of the prime or the dominance of the language of the prime.
-Overall these results suggest that bilinguals recognised target words in both conditions, and benefited from a cross-linguistic facilitation effect from translation equivalents.
-The symmetry of such effect across both languages suggests that participants lexical access occurred in parallel for the two members of translation equivalents.
-As @floccia2020translation note, the stimuli set of Study 2 contains multiple cognates, especially in languages with a larger degree of phonological overlap across translation pairs, like English and Dutch.
-The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
-However, the cross-language effects reported in Study 2 might still reflect the confounding influence of cognateness, as the resulting effect might have been generated by an interaction by the phonological and semantic overlap between cognate primes and targets.
-
-Previous studies had reported similar cross-language priming effects, but as @von2012language note, the conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was not warranted.
-In studies where the auditorily presented prime label was phonologically overlapped with the target label [@REFERENCE], priming effects might be explained by the activation of the phonological segments of the prime label, which facilitated the recognition of the target label, which shared such phonological segments.
-The priming-through-translation results by @von2012language and @floccia2020translation demonstrates that cross-language activation in the developing lexicon occurs at the lexical level.
-Since participants' target recognition was interfered by the non-presented prime translation, such an inhibitory effect must stem at the lexical level.
-The fact that phonological priming facilitated the recognition of the target words (both labels belong to different languages), and that phonological priming through translation interfered target recognition (translation and target belong to the same language) points to cross-language connections playing an excitatory role, and to within-language connections playing an inhibitory role.
-
-Although priming-through-translation studies suggest parallel activation in participants' lexicon in both languages, their design prevents strong interpretations about the extent to which parallel activation is the result of the experimental manipulations of interest.
-The presentation of primes and targets in both languages in the same task---or even within the same trial--- presents participants with a bilingual context that might lead to a higher baseline activation of lexical representations of both languages, compared to monolinguals situations in which parallel activation is claimed to spontaneously take place [@GROSJEAN1997].
-Another limitation of priming-through-translation studies is that, when prime words are auditorily presented, the task constrains the naming context to one of the languages.
-The consequence is a potential asymmetry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
-This might lead to a lower strength, and higher latency of the activation of the translation.
-
-In the present study, we aim to put the hypothesis that bilingual infants activate both languages in parallel to a harder test.
-We use an extension of the implicit naming paradigm by @mani2010infant, in which participants are primed with a picture presented in silence.
-This provides participants with an exclusively monolingual context in which they perform the task in only one of their languages.
+This paradigm provides participants with an exclusively monolingual context in which they perform the task in only one of their languages.
 If differences in task performance are found associated with covert manipulation of cross-linguistic properties of the stimuli, such differences may be more conclusively linked to the parallel activation of lexical representations in participants' lexicons.
-
-Another advantage of the implicit naming paradigm in the investigation of bilingual lexical processing is the fact that, since participants are not presented with any auditory prime label, the activation of the lexical representation of the prime may occur in both languages as the result of lexical retrieval after visual recognition of the prime picture.
+By using an implicit naming paradigm, the activation of the lexical representation of the prime may occur in both languages as the result of lexical retrieval after visual recognition of the prime picture, since participants are not presented with any auditory prime label.
 This contrasts with priming through-translation tasks, in which the prime label in one of the languages is directly activated by auditory word recognition, while the label of its translation is expected to be activated as the result of cascaded activation spreading through their semantic association.
@@
 
-Finally, testing bilingual populations at early ages presents the limitation that the vocabulary size of participants' non-dominant language is relatively small, which substantially constrains the number of items that can be used to as stimuli in the task, as well as the number of trials that can be constructed to generate stimuli lists.
-In order to circumvent the problem of limited vocabulary knowledge in the non-dominant language, tested participants only in their dominant language, therefore directing our research to the question of how possessing a second language affects processing of the dominant one in bilingual toddlers [@costa2014does provide a fuller description of the advantages of such approach].
-
-In summary, the present study was aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
-Using an adaptation of [@mani2010infant], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
+In the present investigation, we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
 We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
@@
 We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
-
 To test cross-language priming effects, we registered participants' time course of target picture looking in the three conditions.
-We predicted within-language priming effects, revealed as differences in target looking between *Unrelated* and *Related/Non-cognate* trials, as previously reported [@von2012, @MANI2001, and @MANI2011].
+We predicted within-language priming effects, revealed as differences in target looking between *Unrelated* and *Related/Non-cognate* trials, as previously reported [@von2012language, @mani2010infant, and @mani2011phonological].
 We further predicted cross-language priming effects, revealed as differences in target looking between *Related/Non-cognate* and *Related/Cognate* trials.
 This effect should be stronger in bilinguals, if not completely absent in monolinguals, who should be indifferent to the phonological properties of the stimuli in the other language.
-Following previous studies associating the emergence of phonological links between lexical items to the size of children's vocabulary [@MANI2011], we also compared the explanatory power of two indices of receptive vocabulary size (dominant-language vocabulary size and total vocabulary size) against participants' age.
+
+Following previous studies associating the emergence of phonological links between lexical items to the size of children's vocabulary [@mani2011phonological], we also compared the explanatory power of two indices of receptive vocabulary size (dominant-language vocabulary size and total vocabulary size) against participants' age.
 We used parental reports of vocabulary checklist to estimate participants' vocabulary size.
@@
 
+Testing bilingual populations at early ages presents the limitation that the vocabulary size of participants' non-dominant language is relatively small, which substantially constrains the number of items that can be used to as stimuli in the task, as well as the number of trials that can be constructed to generate stimuli lists.
+In order to circumvent the problem of limited vocabulary knowledge in the non-dominant language, tested participants only in their dominant language, therefore directing our research to the question of how possessing a second language affects processing of the dominant one in bilingual toddlers [@costa2014does provide a fuller description of the advantages of such approach].
+
 # Study 1
@@
 	map("n")
+
+suppressWarnings({
+	time_diffs <- participants_bcn |>
+		arrange(child_id, session_id, age) |>
+		mutate(n_session = 1:n()) |>
+		select(child_id, session_id, session_n, age) |> 
+		filter(child_id %in% participants_bcn$child_id[duplicated(participants_bcn$child_id)]) |>
+		pivot_wider(id_cols = child_id, 
+					names_from = session_n, 
+					values_from = age, 
+					names_repair = janitor::make_clean_names) |> 
+		rowwise() |>
+		mutate(diff_1 = x2-x1, diff_2 = x3-x2, 
+			   diff_min = min(diff_1, diff_2, na.rm = TRUE),
+			   diff_max = max(diff_1, diff_2, na.rm = TRUE)) |> 
+		ungroup() |> 
+		summarise(diff_min = min(diff_min, na.rm = TRUE), 
+				  diff_max = max(diff_max, na.rm = TRUE))
+})
 ```
@@
 From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, `r n_participants_sessions$session_2` participated twice, and `r n_participants_sessions$session_3` participated three times.
-Recurrent participants were tested with at least XXX months of difference.
+Recurrent participants were tested with at least `r round(time_diffs$diff_min[1], 2)` months of difference.
 We gathered a total of `r n_sessions_total$n` testing sessions.
@@
 			  cells_column_labels()) |> 
-	tab_style(cell_text(weight = "bold"),
+	tab_style(cell_text(style = "italic"),
 			  cells_column_spanners())
-```
-
-### Vocabulary size
+
+# col_names <- c("Group",
+# 			   "Language",
+# 			   "Sessions", 
+# 			   "Participants",
+# 			   "M (SD)",
+# 			   "Range",
+# 			   "M (SD)",
+# 			   "M (SD)",
+# 			   "M (SD)")
+# participants_bcn |> 
+# 	unnest_wider(doe) |> 
+# 	select(-matches("others")) |> 
+# 	arrange(lp, test_language) |> 
+# 	summarise(n = n(),
+# 			  n_participants = n_distinct(child_id),
+# 			  across(age, lst(mean, sd, min, max)),
+# 			  across(matches("doe_"), lst(mean, sd)),
+# 			  # age_vctr = list(age),
+# 			  .by = c(lp, test_language)) |> 
+# 	mutate(age_mean = sprintf("%.1f (%.1f)", age_mean, age_sd),
+# 		   age_range = sprintf("%.1f-%.1f", age_min, age_max),
+# 		   doe_catalan = sprintf("%.1f (%.1f)", doe_catalan_mean*100, doe_catalan_sd*100),
+# 		   doe_spanish = sprintf("%.1f (%.1f)", doe_spanish_mean*100, doe_spanish_sd*100),
+# 		   doe_english = sprintf("%.1f (%.1f)", doe_english_mean*100, doe_english_sd*100)) |> 
+# 	select(lp:age_mean, age_range, doe_catalan, doe_spanish, doe_english) |> 
+# 	kable(digits = 1, 
+# 		  format = "latex",
+# 		  booktabs = TRUE,
+# 		  col.names = col_names,
+# 		  align = "llrrrrrrrrrrrr"
+# 	)
+# 	add_header_above(c(
+# 		" " = 4,
+# 		"Age (months)" = 2,
+# 		"Degree of exposure (%)" = 8
+# 	)) 
+```
 
@@
 Grey lines connect vocabulary size scores from the recurrent participants.
-For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested."
-#| fig-width: 8
-#| fig-height: 4.5
+For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested.
+Only participants included in the final data set are shown."
+#| fig-width: 6
+#| fig-height: 3.5
 vocabulary_bcn |> 
+	inner_join(filter(attrition_participants, is_valid_participant),
+			   by = join_by(session_id)) |> 
 	pivot_longer(c(total_prop, l1_prop),
@@
 			  dotsize = 2,
+			  stroke = 1/2,
 			  scale = 0.5,
@@
 				 geom = "errorbar",
-				 linewidth = 3/4,
+				 linewidth = 1/2,
 				 width = 0.15,
@@
 				 geom = "point",
-				 size = 2,
+				 size = 1.5,
 				 colour = "black",
@@
 We defined word prevalence as the proportion of same-aged infants who were reported to understand the word in the BVQ database.
-
-#### Auditory stimuli
 
@@
 
-#### Visual stimuli
-
-For each word, we created a picture with a typical referent.
-To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias2009lexical].
+Each word was depicted by a realistic phonographic representation of a typical exemplar.
+Image backgrounds were removed from the original pictures using the GNU Image Manipulation Program (GIMP), resized to a rectangle of a maximum of 400 pixels hight or wide, and finally placed in the centre of a 50% grey rectangle square of 500$\times$500 pixels.
+The final stimuli had a resolution of 72 dpi.
+When presented in the eye-tracker screen, the areas of interest (AOI) occupied an area of 13.23$\times$13.23 cm (11.613º visual angle from participants' perspective).
 
@@
 We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
-
-After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`).
+We also excluded trials in which participants did not provide at least 10% of valid samples (equivalent to 100 ms) of for the target *and* the distractor each (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation; @manidurrantfloccia for a similar approach].
+
+After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
 The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
@@
 
-The comparison between the three models including *Age*, *L1 vocabulary*, *Total vocabulary* as predictors was performed using leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it [@vehtari2017practical].
+The comparison between the three models including *Age*, *L1 vocabulary*, *Total vocabulary* as predictors was done using leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it [@vehtari2017practical].
 We implemented the model using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
@@
 
+#### Statistical inference
+
+We assessed the practical relevance of the estimated regression coefficients of the model following @kruschke2018bayesian.
+First, we specified a region of practical equivalence (ROPE) from `r rope_interval["lower"]` to +`r rope_interval["upper"]`, in the probability scale.
+This region indicates the range of values that we considered equivalent to zero.
+We then summarised the posterior distribution of each regression coefficient with the 95% highest density interval (HDI).
+This interval contains the true value of this coefficient with 95% probability, given the data.
+Finally, we calculated the proportion of posterior samples in the 95% HDI that fell into the ROPE, noted as $p(\text{ROPE})$, which indicates the probability that the true value of the regression coefficient falls into the ROPE (and therefore should be considered equivalent to zero).
+For example, $p(\text{ROPE})=.80$ indicates that, given our data, there is a 80% probability that the true value of the coefficient falls within the ROPE, and can therefore be considered equivalent to zero.
+
+We followed a similar procedure to compare the effect of the predictors of interest on the time course of target looking.
+First, we defined a ROPE from `r rope_interval["lower"]` to +`r rope_interval["upper"]` in the logit scale.
+We then computed the difference between  of the regression coefficient of the continuous predictor *Age*, the difference coefficients *Group*, *Condition*, and *Age* at each time bin, which indicates the marginal effect of the predictor on target looking at that specific
+
 ## Results
 
-```{r results}
-var_labels <- c("b_Intercept" = "Intercept",
-				"b_age_std" = "Age (+1 SD)",
-				"b_condition1" = "Condition (U vs. RN)",
-				"b_condition1" = "Condition (RN vs. RC)",
-				"b_lp1" = "Group",
-				"sd_child_id__Intercept" = "Intercept",
-				"sd_child_id__age_std" = "Age",
-				"sd_child_id__lpBilingual" = "Group",
-				"sd_child_id:session_id__Intercept" = "Intercept",
-				"sd_child_id:session_id__age_std" = "Age",
-				"sd_child_id:session_id__lpBilingual" = "Group")
-
-get_coefs <- function(model, var_labels, ...) {
-	out <- model |> 
-		gather_draws(...) |> 
-		median_hdci(.width = 0.95) |> 
-		mutate(.variable_name = factor(.variable, 
-									   levels = names(var_labels), 
-									   labels = var_labels),
-			   mdn_label = sprintf("%.3f", .value),
-			   ci_label = sprintf("[%.3f, %.3f]", .lower, .upper)) |> 
-		arrange(.variable) |> 
-		select(.variable:.upper, matches("label")) %>%
-		split(janitor::make_clean_names(.$.variable))
-
-	return(out)
-}
-coefs <- map(model_fits_bcn, 
-			 \(x) get_coefs(model = x, var_labels,
-			 			   `b_.*`, `sd_.*`, regex = TRUE))
-
+### Model comparisons
+
+```{r tbl-loos}
+#| label: tbl-loos
+#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of models 0 to 3, and 3 to 6 in Study 1."
 get_loos <- function(x, y) {
@@
 
-loos_tbl <- loo_compare(model_loos_bcn[1:5]) |> 
+loos_03 <- loo_compare(model_loos_bcn[1:4]) |> 
 	as.data.frame() |> 
 	rownames_to_column("model") |> 
-	select(model, matches("diff|elpd"))
-
-```
-
-```{r tbl-loos}
-loos_tbl[1:5] |> 
-	mutate(model = gsub("fit_", "", model)) |>
-	gt() |> 
+	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model))),
+		   across(matches("diff"),
+		   	   \(x) {x[1] <- NA; return(x)}))
+
+loos_36 <- loo_compare(model_loos_bcn[4:7]) |> 
+	as.data.frame() |> 
+	rownames_to_column("model") |> 
+	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model))),
+		   across(matches("diff"),
+		   	   \(x) {x[1] <- NA; return(x)}))
+
+bind_rows("Base models" = loos_03,
+		  "Age and vocabulary size models" = loos_36, 
+		  .id = "type") |> 
+	select(type, model, matches("elpd|diff")) |> 
+	relocate(matches("diff"), .after = matches("loo")) |> 
+	gt(rowname_col = "model", groupname_col = "type") |> 
 	fmt_number(is.numeric) |> 
-	# fmt_markdown(is.character, ) |> 
-	cols_label(model = "Model",
-			   elpd_diff = "ELPD (diff.)",
+	cols_label(elpd_diff = "ELPD (diff.)",
 			   se_diff = "SE ELPD (diff)",
 			   elpd_loo = "ELPD",
-			   se_elpd_loo = "SE ELPD")
+			   se_elpd_loo = "SE ELPD") |> 
+	fmt_missing(missing_text = "---") |> 
+	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new dataset.
+*SE \\(ELPD\\)*: standard error of the *ELPD*, which indictes the uncertainty about the predictive performance for unknown future data.
+*ELPD (diff)*: pairwise difference in *ELPD* for two models.
+The difference is computed relative to the model with highest *ELPD*.
+*SE ELPD (diff.)*: standard error of component-wise differences of *ELPD* between two models.")) |>
+	tab_style(cell_text(style = "italic"), cells_column_labels())
 ```
@@
 @tbl-loos summarises the outputs of the LOO-CV model comparisons.
-Models $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ showed substantially better predicted performance than models $\mathcal{M}_{0}$ and $\mathcal{M}_{1}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
-All $\mathcal{M}_{2}$, $\mathcal{M}_{3}$, and $\mathcal{M}_{4}$ models showed equivalent performance, suggesting that adding the two-way and three-way interactions between *Age*, *Group*, and *Condition*, did not improve the the fit of the model.
-We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{4}$.
-We report the median and 95% highest density interval of each fixed regression coefficient.
-
-Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_4$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_4$b_intercept$ci_label`).
-The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_4$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_4$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_4$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_4$sd_child_id_session_id_intercept$ci_label`).
-The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_4$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
-
-The 95% HDI of the coefficient of *Group* in $\mathcal{M}_{1}$ included zero ($\beta$ = `r coefs$fit_4$b_lp1$mdn_label`, 95% HDI = `r coefs$fit_4$b_lp1$ci_label`), indicating an equivalent overall target preference in monolinguals and bilinguals.
-The 95% HDI of the first contrast of this predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_4$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1$ci_label`).
-The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_4$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2$ci_label`).
+Models $\mathcal{M}_{2}$ and $\mathcal{M}_{3}$, showed substantially better predicted performance than models $\mathcal{M}_{0}$ and $\mathcal{M}_{1}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
+Both $\mathcal{M}_{2}$ and $\mathcal{M}_{3}$ models showed equivalent performance, suggesting that adding the two-way interaction between *Group*, and *Condition*, did not improve the the fit of the model substantially.
+We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{3}$.
+We now report the median and 95% highest density interval of each fixed regression coefficient in $\mathcal{M}_{3}$ (see @tbl-coefs).
+
+### Linear effects
+
+```{r tbl-coefs}
+#| label: tbl-coefs
+#| tbl-cap: "Posterior distribution of regression coefficients.
+Median: median of the posterior distribution in logit scale.
+95\\% HDI: 95\\% highest density interval of the distribution.
+*p*(ROPE): overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero."
+#| echo: false
+#| message: false
+#| warning: false
+#| out-width: 80%
+var_labels <- c("b_Intercept" = "Intercept",
+				"b_age_std" = "Age (+1 SD)",
+				"b_lp1" = "Group",
+				"b_condition1" = "Condition (U vs. RN)",
+				"b_condition2" = "Condition (RN vs. RC)",
+				"b_condition1:lp1" = "Group \U00D7 Condition (U vs. RN)",
+				"b_condition2:lp1" = "Group \U00D7 Condition (RN vs. RC)")
+
+model_summary <- get_posterior_summary(model_fits_bcn$fit_3,
+									   data_bcn,
+									   vars_dict = var_labels,
+									   rope_interval = rope_interval)
+
+coefs <- model_summary |> 
+	mutate(.value = sprintf("%.3f", .value),
+		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
+		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
+	split(janitor::make_clean_names(model_summary$.variable))
+
+# summarise posterior draws
+intercept_label <- paste0("Intercept (at ", round(mean(data_bcn$age), 2), " months)")
+
+tbl_data <- model_summary |>
+	select(.variable_name, .value, .lower, .upper, .rope, .type) |>
+	mutate(.variable_name = gsub("×", "$\\\\times$", .variable_name),
+		   .hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
+		   .rope = case_when(is.na(.rope) ~ "-",
+		   				  .rope > 0.9999 ~ "1",
+		   				  .rope < 0.00001 ~ "0",
+		   				  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope)))) |>
+	select(.variable_name, .value, .lower, .upper, .hdi, .rope)
+
+col_names <- c("", "$\\beta$", "95\\% HDI", "$p(\\text{ROPE})$")
+
+tbl_data |>
+	select(-c(.lower, .upper)) |>
+	kable(
+		format = "latex",
+		escape = FALSE,
+		col.names = col_names,
+		digits = 3,
+		booktabs = TRUE,
+		align = "lclr",
+		linesep = ""
+	) |>
+	kable_styling() |>
+	add_footnote("$\\beta$: median of the posterior distribution in the logit scale.
+95\\% HDI: 95\\% highest density interval of the distribution.
+$p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
+```
+
+Overall, the average participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$b_intercept$.value`, 95% HDI = `r coefs$b_intercept$.ci`), and all of its posterior samples were outside of the ROPE.
+The coefficient of *Age* had a positive sign, but its 95% HDI overlapped completely with the ROPE ($\beta$ = `r coefs$b_age_std$mdn_label`, 95% HDI = `r coefs$b_age_std$.ci`), indicating that participants from all ages showed equivalent overall target word recognition.
+The 95% HDI of the coefficient of *Group* also included zero ($\beta$ = `r coefs$b_lp1$.value`, 95% HDI = `r coefs$b_lp1$.ci`) and completely overlapped with the ROPE, indicating an equivalent overall target preference in monolinguals and bilinguals.
+The 95% HDI of the first contrast of the *Condition* predictor---comparing *Unrelated* and *Related/Non-cognate* trials---included zero ($\beta$ = `r coefs$b_condition1$.value`, 95% HDI = `r coefs$b_condition1$.ci`), and `r coefs$b_condition1$.rope` of its posterior samples overlapped with the ROPE.
+The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$b_condition2$.value`, 95% HDI = `r coefs$b_condition2$.ci`), and `r coefs$b_condition2$.rope` of its posterior samples overlapped with the ROPE.
 The overall target preference was equivalent across both pairwise condition comparisons.
-The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$fit_4$b_condition1_lp1$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_lp1$ci_label`).
-The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$fit_4$b_condition2_lp1$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_lp1$ci_label`).
-The outcomes of this model indicate that lack of differences in overall target looking time across conditions remained across monolinguals and bilinguals.
+The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$b_condition1_lp1$.value`, 95% HDI = `r coefs$b_condition1_lp1$.ci`), with `r coefs$b_condition1_lp1$.rope` of its posterior samples overlapping with the ROPE.
+The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$b_condition2_lp1$.value`, 95% HDI = `r coefs$b_condition2_lp1$.ci`), and  `r coefs$b_condition1$.rope` of its posterior samples fell within the ROPE.
+The outcomes of this model provide strong to moderate evidence against differences in overall target looking time across conditions and across monolinguals and bilinguals.
+
+A comparison between models including *Age* ($\mathcal{M}_{4}$), *L1 vocabulary* ($\mathcal{M}_{5}$), and *Total vocabulary* ($\mathcal{M}_{6}$)---and their three-way and two-way interactions with *Group* and *Condition*---against model $\mathcal{M}_{3}$, which only included *Age* as a covariate is shown in @tbl-loos.
+Overall, all models performed equivalently, with the simplest model $\mathcal{M}_{3}$ showing slightly better performance.
+This suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account *L1 vocabulary*, or *Total vocabulary* sizes.
 
@@
 
+### Time course of target looking
+
 ```{r timecourse}
@@
 
-timebin_values <- make_std(seq(0, 17, length.out = 100),
+timebin_values <- make_std(seq(0, 16, length.out = 100),
 						   mean(data_bcn$timebin),
@@
 
-age_values <- make_std(c(20, 30),
+age_values <- make_std(c(20, 32),
 					   mean(data_bcn$age),
@@
 nd <- expand_grid(distinct(data_bcn, condition, lp),
-				  timebin_std = timebin_values,
-				  age_std = age_values)
-
-epreds <- add_epred_draws(nd, model_fits_bcn$fit_4, 
-						  re_formula = NA,
+				  age_std = 0, timebin_std = timebin_values)
+
+epreds <- add_epred_draws(nd,
+						  model_fits_bcn$fit_3, 
 						  ndraws = NULL,
-						  value = ".elog") |> 
-	mutate(age_std = factor(age_std,
-							levels = age_values, 
-							labels = paste0(c(20, 30), " months")))
+						  re_formula = NA)
+```
+
+An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
+Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
+
+```{r fig-epreds}
+#| label: fig-epreds
+#| fig-cap: "Margin posterior mean predictions.
+A) Posterior mean predictions of the time course of target fixation in the test phase.
+B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
+Lines and intervals indicate the mean and 95% credible interval of the posterior predictions."
+#| fig-width: 8
+#| fig-height: 8
+epreds_summary <- epreds |> 
+	ungroup() |> 
+	summarise(.value = mean_qi(.epred)[[1]],
+			  .lower = mean_qi(.epred)[[2]],
+			  .upper = mean_qi(.epred)[[3]],
+			  .by = c(lp, condition, timebin_std))
+
+plot_epreds <- epreds |> 
+	ggplot(aes(timebin_std, .epred,
+			   colour = condition,
+			   fill = condition,
+			   linetype = condition,
+			   shape = condition)) +
+	facet_wrap(~lp) +
+	# geom_line(aes(group = interaction(lp, condition, .draw)),
+	# 		  alpha = 1/20,
+	# 		  linewidth = 3/4,
+	# 		  linetype = "solid") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
+				 alpha = 1/4,
+				 linewidth = NA) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 # colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0,
+			   colour = "grey") +
+	stat_summary(data = data_bcn,
+				 aes(y = .elog),
+				 fun = "mean",
+				 geom = "point",
+				 size = 2) +
+	labs(x = "Time (ms)",
+		 y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition")
+
+epreds_diff <- epreds |> 
+	pivot_wider(id_cols = c(lp, timebin_std, .draw),
+				names_from = "condition",
+				values_from = ".epred",
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff_1 = related_non_cognate - unrelated,
+		   diff_2 = related_cognate - related_non_cognate) |> 
+	pivot_longer(matches("diff"),
+				 names_to = "diff",
+				 values_to = ".epred",
+				 names_prefix = "diff_") |> 
+	mutate(diff = factor(diff,
+						 levels = c(1, 2),
+						 labels = c("Related/Non-cognate - Unrelated",
+						 		   "Related/Cognate - Related/Non-cognate")))
+
+plot_diffs <- epreds_diff |> 
+	ggplot(aes(timebin_std, .epred)) +
+	facet_wrap(diff~lp, 
+			   labeller = labeller(
+			   	diff = label_value,
+			   	lp = function(x) return(""), 
+			   	.multi_line = FALSE)) +
+	annotate(geom = "rect",
+			 xmin = timebin_values[1],
+			 xmax = timebin_values[length(timebin_values)],
+			 ymin = rope_interval[1],
+			 ymax = rope_interval[2],
+			 fill = "grey",
+			 linewidth = 0,
+			 alpha = 1/2,
+			 linetype = "dotted") +
+	# geom_line(aes(group = interaction(diff, draw)),
+	# 		  alpha = 1/20,
+	# 		  linewidth = 3/4,
+	# 		  colour = "grey",
+	# 		  linetype = "solid") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
+				 fill = clrs[1],
+				 linewidth = NA,
+				 alpha = 1/3) +
+	stat_summary(aes(group = diff),
+				 fun = mean,
+				 geom = "line",
+				 colour = clrs[1],
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0,
+			   colour = "grey") +
+	labs(x = "Time (ms)",
+		 y = "Logit P(Target looking)",
+		 colour = "Comparison",
+		 fill = "Comparison",
+		 linetype = "Comparison")
+
+plot_epreds + plot_diffs +
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") &
+	# scale_y_continuous(limits = c(0.25, 0.75)) +
+	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
+										 mean(data_bcn$timebin),
+										 sd(data_bcn$timebin)),
+					   labels = \(x) format(seq(3e2, 2e3, 3e2),
+					   					 big.mark = ",")) &
+	theme(legend.position = "top",
+		  legend.title = element_blank(),
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+```
+
+```{r recognition}
+nd <- expand_grid(distinct(data_bcn, condition, lp),
+				  age_std = age_values,
+				  timebin_std = timebin_values)
+
+epreds <- add_epred_draws(nd,
+						  model_fits_bcn$fit_3, 
+						  ndraws = NULL,
+						  re_formula = NA)
 
@@
 	mutate(over_chance = sprintf("%.2f", over_chance),
-		   age_std = paste0("age_", gsub(" months", "", age_std))) |> 
+		   age_std = factor(x = age_std,
+		   				 levels = age_values,
+		   				 labels = paste0(c(20, 30), " months"))) |> 
 	arrange(lp, age_std) %>%
 	split(tolower(.$lp)) |> 
-	map(\(x) split(x, x$age_std)) 
-```
-
-An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
-Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
-
-```{r fig-epreds}
-#| label: fig-epreds
-#| fig-cap: "Posterior mean prdictions of the time course of target fixation in the test phase.
-Lines and intervals indicate the median and 95% credible interval of the posterior predictions, respectively."
-#| fig-width: 8
-#| fig-height: 4
-epreds |> 
-	ggplot(aes(timebin_std, .elog,
-			   colour = condition,
-			   fill = condition)) +
-	facet_grid(lp~age_std) +
-	geom_hline(yintercept = 0, linetype = "dashed") +
-	stat_summary(fun.data = mean_qi,
-				 geom = "ribbon",
-				 alpha = 1/2,
-				 linewidth = NA) +
-	stat_summary(fun = mean,
-				 geom = "line",
-				 linewidth = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "Logit (Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
-										 mean(data_bcn$timebin),
-										 sd(data_bcn$timebin)),
-					   labels = \(x) format(seq(3e2, 2e3, 3e2),
-					   					 big.mark = ",")) &
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  legend.position = "top")
+	map(\(x) split(x, paste0("age_", gsub(" months", "", x$age_std))))
 ```
@@
 epreds_chance |> 
+	mutate(age_std = factor(x = age_std,
+							levels = age_values,
+							labels = paste0(c(20, 32), " months"))) |> 
 	ggplot(aes(lp, over_chance,
 			   colour = sort(condition),
+			   shape = sort(condition),
 			   fill = sort(condition))) + 
 	facet_wrap(~age_std) +
-	geom_point(shape = 16, size = 4) +
+	geom_point(size = 3) +
 	geom_line(aes(group = condition),
-			  linewidth = 1) +
-	# geom_point(size = 3) +
+			  linewidth = 1,
+			  alpha = 1/2) +
 	labs(x = "Group",
@@
 		 colour = "Condition",
-		 fill = "Condition") +
+		 fill = "Condition",
+		 shape = "Condition") +
 	scale_y_continuous(breaks = seq(0, 1e3L, 50)) +
@@
 In Study 1, we adapted an implicit naming paradigm to investigate the potential role of within- and cross-language phonological priming in 21- to 32-month-old children.
+Both the overall target looking and its course time across the trial suggested strong word recognition, regardless of priming condition, participant language profile and age.
 Overall, participants' performance was equivalent across all priming conditions.
-Both the overall target looking and its course time across the trial suggested strong word recognition, regardless of participants language profile and age.
 An exploratory analyses on word recognition times suggested a complex pattern of results, showing an age effect---in which older participants looked at the target above chance earlier than younger infants---and a weak interaction between priming conditions, age, and language group.
@@
 
-First, investigations using implicit naming paradigm had provided strong evidence in favour of infants and toddlers generating internal labels when presented with pictures of familiar objects.
+First, previous investigations using implicit naming paradigm had provided strong evidence in favour of infants and toddlers generating internal labels when presented with pictures of familiar objects.
 @mani2010infant and @mani2011phonological reported priming effects in 18 and 24-month-old infants.
@@
 In control trials---in which prime and target labels were unrelated---no priming effect was found.
-This suggests that infants implicitly named the prime label, and that the resulting internal phonological form was detailed enough to interact with the subsequent auditory recognition of the target word.
+This suggested that infants implicitly named the prime label, and that the resulting internal phonological form was detailed enough to interact with the subsequent auditory recognition of the target word.
 In the present study, we did not find evidence in favour of differences in target looking preference between related and unrelated trials, regardless of the age of participants or their language profile.
@@
 ```
-Both @mani2010infant and @mani2011phonological, and the present study shared a similar design, but sampled different children populations.
+
+Both @mani2010infant and @mani2011phonological, and the present study share a similar design, but sampled different children populations.
 Participants in Mani and Plunkett's studies were raised in English speaking households in Oxford, while participants in the present study were learning Catalan or Spanish, if not a combination of both.
@@
 In the present study, the prime label was not named, and participants were expected to generate both the prime label and its translation implicitly.
-It may be the case that infants in the present study faced a more challenging task, having to internally retrieve phonological forms without any auditory prompt like the one provided by priming-through-translation studies.
+It may be the case that infants in the present study faced a more challenging task, having to internally retrieve phonological forms without any auditory prompt like the one provided by priming through translation studies.
 
@@
 Vocabulary size scores from the recurrent participants are shown linked."
-#| eval: false
 #| fig-width: 4
-#| fig-height: 4
+#| fig-height: 2.5
 vocabulary_oxf |> 
+	inner_join(filter(attrition_participants, is_valid_participant),
+			   by = join_by(session_id)) |> 
 	inner_join(select(participants, child_id, session_id, age_group),
@@
 			  fill = clrs[5],
-			  scale = 0.5,
+			  scale = 1,
 			  side = "both",
@@
 				 geom = "errorbar",
-				 linewidth = 3/4,
+				 linewidth = 1/2,
 				 width = 0.1,
@@
 
-```{r results-oxf}
+```{r tbl-loos-oxf}
+#| label: tbl-loos-oxf
+#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 2."
+loos_03 <- loo_compare(model_loos_oxf[1:2]) |> 
+	as.data.frame() |> 
+	rownames_to_column("model") |> 
+	mutate(model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model))),
+		   across(matches("diff"),
+		   	   \(x) {x[1] <- NA; return(x)}))
+
+loos_36 <- loo_compare(model_loos_oxf[2:4]) |> 
+	as.data.frame() |> 
+	rownames_to_column("model") |> 
+	mutate(model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model))),
+		   across(matches("diff"),
+		   	   \(x) {x[1] <- NA; return(x)}))
+
+bind_rows("Base models" = loos_03,
+		  "Age and vocabulary size models" = loos_36, 
+		  .id = "type") |> 
+	select(type, model, matches("elpd|diff")) |> 
+	relocate(matches("diff"), .after = matches("loo")) |> 
+	gt(rowname_col = "model", groupname_col = "type") |> 
+	fmt_number(is.numeric) |> 
+	cols_label(elpd_diff = "ELPD (diff.)",
+			   se_diff = "SE ELPD (diff)",
+			   elpd_loo = "ELPD",
+			   se_elpd_loo = "SE ELPD") |> 
+	fmt_missing(missing_text = "---") |> 
+	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new dataset.
+*SE \\(ELPD\\)*: standard error of the *ELPD*, which indictes the uncertainty about the predictive performance for unknown future data.
+*ELPD (diff)*: pairwise difference in *ELPD* for two models.
+The difference is computed relative to the model with highest *ELPD*.
+*SE ELPD (diff.)*: standard error of component-wise differences of *ELPD* between two models.")) |>
+	tab_style(cell_text(style = "italic"), cells_column_labels())
+```
+
+In line with the results in *Study 1*, including the *Condition* predictor increased the predictive performance of the model substantially, compared to a model including only the main effect of *Age* (see @tbl-loos-oxf).
+We now report the median and 95% highest density interval of each fixed regression coefficient in $\mathcal{M}_{1}$.
+Overall, the average participant' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$b_intercept$.value`, 95% HDI = `r coefs$b_intercept$.ci`) and all of its posterior samples fell outside of the ROPE.
+The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$b_age_std$.value`, 95% HDI = `r coefs$b_age_std$.ci`), and overlapped completely with the ROPE, indicating that participants from all ages showed equivalent overall target word recognition.
+The 95% HDI of the first contrast of the *Condition* predictor---comparing *Unrelated* and *Related/Non-cognate* trials---included zero ($\beta$ = `r coefs$b_condition1$.value`, 95% HDI = `r coefs$b_condition1$.ci`), and `r coefs$b_condition1$.rope` of its posterior samples fell within the ROPE.
+The 95% HDI of the second contrast---comparing *Related/Non-cognate* and *Related/Cognate* trials---also included zero ($\beta$ = `r coefs$b_condition2$.value`, 95% HDI = `r coefs$b_condition2$.ci`), and `r coefs$b_condition2$.rope` of its posterior samples fell within the ROPE.
+The overall target preference was equivalent across both pairwise condition comparisons.
+
+```{r tbl-coefs-oxf}
+#| label: tbl-coefs-oxf
+#| fig-cap: "Margin posterior mean predictions.
+A) Posterior mean predictions of the time course of target fixation in the test phase.
+B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
+Lines and intervals indicate the mean and 95% credible interval of the posterior predictions."
+#| echo: false
+#| message: false
+#| warning: false
+#| out-width: 80%
 var_labels <- c("b_Intercept" = "Intercept",
@@
 				"b_condition1" = "Condition (U vs. RN)",
-				"b_condition1" = "Condition (RN vs. RC)",
-				"sd_child_id__Intercept" = "Intercept",
-				"sd_child_id__age_std" = "Age",
-				"sd_child_id:session_id__Intercept" = "Intercept",
-				"sd_child_id:session_id__age_std" = "Age",
-				"sd_child_id:session_id__lpBilingual" = "Group")
-
-coefs <- map(model_fits_oxf, 
-			 \(x) get_coefs(model = x, var_labels,
-			 			   `b_.*`, `sd_.*`, regex = TRUE))
-
-loos_tbl <- loo_compare(model_loos_oxf) |> 
-	as.data.frame() |> 
-	rownames_to_column("model") |> 
-	select(model, matches("diff|elpd"))
-
-```
-
-```{r tbl-loos-oxf}
-loos_tbl |> 
-	mutate(model = gsub("fit_oxf_", "", model)) |>
-	gt() |> 
-	fmt_number(is.numeric) |> 
-	# fmt_markdown(is.character, ) |> 
-	cols_label(model = "Model",
-			   elpd_diff = "ELPD (diff.)",
-			   se_diff = "SE ELPD (diff)",
-			   elpd_loo = "ELPD",
-			   se_elpd_loo = "SE ELPD")
-```
-
-@tbl-loos-oxf summarises the outputs of the LOO-CV model comparisons.
-Models $\mathcal{M}_{1}$, $\mathcal{M}_{2}$, and $\mathcal{M}_{3}$ showed substantially better predicted performance than model $\mathcal{M}_{0}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
-All $\mathcal{M}_{1}$, $\mathcal{M}_{2}$, and $\mathcal{M}_{3}$ models showed equivalent performance, suggesting that adding the two-way interaction between *Age* and *Condition* did not improve the the fit of the model.
-We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{3}$.
-
-Overall, participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$fit_3$b_intercept$mdn_label`, 95% HDI = `r coefs$fit_3$b_intercept$ci_label`).
-The variability of participants' target preference varied significantly more between participants ($\sigma$ = `r coefs$fit_3$sd_child_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_3$sd_child_id_intercept$ci_label`) than within testing sessions from the same participant ($\sigma$ = `r coefs$fit_3$sd_child_id_session_id_intercept$mdn_label`, 95% HDI = `r coefs$fit_3$sd_child_id_session_id_intercept$ci_label`).
-The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$fit_3$b_age_std$mdn_label`, 95% HDI = `r coefs$fit_0$b_age_std$ci_label`), indicating that participants from all ages showed equivalent overall target word recognition.
-
-The 95% HDI of the first contrast of the *Condition* predictor, comparing *Unrelated* and *Related/Non-cognate* trials, included zero ($\beta$ = `r coefs$fit_3$b_condition1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1$ci_label`).
-The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$fit_3$b_condition2$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2$ci_label`).
-The overall target preference was equivalent across both pairwise condition comparisons.
-The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$fit_3$b_condition1_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1_lp1$ci_label`).
-The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$fit_3$b_condition2_lp1$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2_lp1$ci_label`).
-Both younger and older participants showed equivalent looking time across conditions, as suggested by the fact that the 95% HDI of the two-way interaction between *Age* and the first *Condition* contrast included zero ($\beta$ = `r coefs$fit_3$b_condition1_age_std$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition1_age_std$ci_label`), as well as the interaction between *Age* and the second *Condition* contrast ($\beta$ = `r coefs$fit_3$b_condition2_age_std$mdn_label`, 95% HDI = `r coefs$fit_3$b_condition2_age_std$ci_label`).
+				"b_condition2" = "Condition (RN vs. RC)")
+
+model_summary <- get_posterior_summary(model_fits_oxf$fit_oxf_1,
+									   data_bcn,
+									   vars_dict = var_labels,
+									   rope_interval = rope_interval)
+
+coefs <- model_summary |> 
+	mutate(.value = sprintf("%.3f", .value),
+		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
+		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
+	split(janitor::make_clean_names(model_summary$.variable))
+
+# summarise posterior draws
+intercept_label <- paste0("Intercept (at ", round(mean(data_oxf$age), 2), " months)")
+
+tbl_data <- model_summary |>
+	select(.variable_name, .value, .lower, .upper, .rope, .type) |>
+	mutate(.variable_name = gsub("×", "$\\\\times$", .variable_name),
+		   .hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
+		   .rope = case_when(is.na(.rope) ~ "-",
+		   				  .rope > 0.9999 ~ "1",
+		   				  .rope < 0.00001 ~ "0",
+		   				  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope)))) |>
+	select(.variable_name, .value, .lower, .upper, .hdi, .rope)
+
+col_names <- c("", "$\\beta$", "95\\% HDI", "$p(\\text{ROPE})$")
+
+tbl_data |>
+	select(-c(.lower, .upper)) |>
+	kable(format = "latex",
+		  escape = FALSE,
+		  col.names = col_names,
+		  digits = 3,
+		  booktabs = TRUE,
+		  align = "lclr",
+		  linesep = "") |>
+	kable_styling() |>
+	add_footnote("$\\beta$: median of the posterior distribution in the probability scale.
+95\\% HDI: 95\\% highest density interval of the distribution.
+$p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
+```
+
+@tbl-loos-oxf shows a comparison between models including *Age* ($\mathcal{M}_{2}$), and *L1 vocabulary* ($\mathcal{M}_{3}$)---and their two-way and two-way interaction with *Condition*---against model $\mathcal{M}_{1}$, which only included *Age* as a covariate suggested that all models performed equivalently, with model $\mathcal{M}_{2}$ showing a slightly better performance.
+Overall, this suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account *L1 vocabulary*, or *Total vocabulary* sizes.
 
 ```{r timecourse-oxf}
-timebin_values <- make_std(seq(0, 17, length.out = 100),
-						   mean(data_oxf$timebin),
-						   sd(data_oxf$timebin))
-
-age_values <- make_std(c(20, 30),
-					   mean(data_oxf$age),
-					   sd(data_oxf$age))
-
+nd <- expand_grid(distinct(data_oxf, condition),
+				  timebin_std = timebin_values,
+				  age_std = 0)
+
+epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_1, 
+						  re_formula = NA,
+						  ndraws = NULL,
+						  value = ".epred")
+```
+
+An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
+Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
+
+```{r fig-epreds-oxf}
+#| label: fig-epreds-oxf
+#| fig-cap: "A) Posterior mean predictions of the time course of target fixation in the test phase.
+Thin lines represent 100 individual posterior predictions.
+Thick lines indicate the mean of the posterior predictions.
+B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
+Thin lines represent 100 individual posterior predictions.
+Black lines indicate the mean of the posterior predictions."
+#| fig-width: 6.5
+#| fig-height: 6.5
+epreds_summary <- epreds |> 
+	ungroup() |> 
+	summarise(.value = mean_qi(.epred)[[1]],
+			  .lower = mean_qi(.epred)[[2]],
+			  .upper = mean_qi(.epred)[[3]],
+			  .by = c(condition, timebin_std))
+
+plot_epreds <- epreds |> 
+	ggplot(aes(timebin_std, .epred,
+			   colour = condition,
+			   fill = condition,
+			   linetype = condition,
+			   shape = condition)) +
+	geom_hline(yintercept = 0,
+			   colour = "grey") +
+	# geom_line(aes(group = interaction(condition, .draw)),
+	# 		  alpha = 1/20,
+	# 		  linewidth = 3/4,
+	# 		  linetype = "solid") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
+				 alpha = 1/4,
+				 linewidth = NA) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 # colour = "black",
+				 linewidth = 3/4) +
+	stat_summary(data = data_oxf,
+				 aes(y = .elog),
+				 fun = "mean",
+				 geom = "point",
+				 size = 2) +
+	labs(x = "Time (ms)",
+		 y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition")
+
+epreds_diff <- epreds |> 
+	pivot_wider(id_cols = c(timebin_std, .draw),
+				names_from = "condition",
+				values_from = ".epred",
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff_1 = related_non_cognate - unrelated,
+		   diff_2 = related_cognate - related_non_cognate) |> 
+	pivot_longer(matches("diff"),
+				 names_to = "diff",
+				 values_to = ".epred",
+				 names_prefix = "diff_") |> 
+	mutate(diff = factor(diff,
+						 levels = c(1, 2),
+						 labels = c("Related/Non-cognate - Unrelated",
+						 		   "Related/Cognate - Related/Non-cognate")))
+
+plot_diffs <- epreds_diff |> 
+	ungroup() |> 
+	ggplot(aes(timebin_std, .epred)) +
+	facet_wrap(~diff) +
+	annotate(geom = "rect",
+			 xmin = timebin_values[1],
+			 xmax = timebin_values[length(timebin_values)],
+			 ymin = rope_interval[1],
+			 ymax = rope_interval[2],
+			 fill = "grey",
+			 linewidth = 0,
+			 alpha = 1/2,
+			 linetype = "dotted") +
+	geom_hline(yintercept = 0,
+			   colour = "grey") +
+	# geom_line(aes(group = interaction(diff, draw)),
+	# 		  alpha = 1/20,
+	# 		  linewidth = 3/4,
+	# 		  colour = "grey",
+	# 		  linetype = "solid") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
+				 fill = clrs[1],
+				 linewidth = NA,
+				 alpha = 1/3) +
+	stat_summary(fun = mean,
+				 geom = "line",
+				 colour = clrs[1],
+				 linewidth = 3/4) +
+	geom_hline(yintercept = 0,
+			   colour = "grey") +
+	labs(x = "Time (ms)",
+		 y = "Logit P(Target looking)",
+		 colour = "Comparison",
+		 fill = "Comparison",
+		 linetype = "Comparison")
+
+plot_epreds + plot_diffs +
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") &
+	# scale_y_continuous(limits = c(0.25, 0.75)) +
+	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
+										 mean(data_bcn$timebin),
+										 sd(data_bcn$timebin)),
+					   labels = \(x) format(seq(3e2, 2e3, 3e2),
+					   					 big.mark = ",")) &
+	theme(legend.position = "top",
+		  legend.title = element_blank(),
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+```
+
+```{r recognition-oxf}
 nd <- expand_grid(distinct(data_oxf, condition),
@@
 
-epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_2, 
+epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_1, 
 						  re_formula = NA,
 						  ndraws = NULL,
-						  value = ".elog") |> 
-	mutate(age_std = factor(age_std,
-							levels = age_values, 
-							labels = paste0(c(20, 30), " months")))
+						  value = ".epred")
 
@@
 	mutate(over_chance = (over_chance * 
-						  	sd(data_oxf$timebin) +
-						  	mean(data_oxf$timebin))*100+300)
+						  	sd(data_bcn$timebin) +
+						  	mean(data_bcn$timebin))*100+300)
 
@@
 	mutate(over_chance = sprintf("%.2f", over_chance),
-		   age_std = paste0("age_", 
-		   				 gsub(" months", "", age_std))) |> 
+		   age_std = factor(x = age_std,
+		   				 levels = age_values,
+		   				 labels = paste0(c(20, 30), " months"))) |> 
 	arrange(age_std) %>%
-	split(tolower(.$age_std)) 
-```
-
-An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
-Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
-
-```{r fig-epreds-oxf}
-#| label: fig-epreds-oxf
-#| fig-cap: "Posterior mean prdictions of the time course of target fixation in the test phase.
-Lines and intervals indicate the median and 95% credible interval of the posterior predictions, respectively."
-#| fig-width: 8
-#| fig-height: 4
-epreds |> 
-	ggplot(aes(timebin_std, .elog,
-			   colour = condition,
-			   fill = condition)) +
-	facet_wrap(~age_std) +
-	geom_hline(yintercept = 0, linetype = "dashed") +
-	stat_summary(fun.data = mean_qi,
-				 geom = "ribbon",
-				 alpha = 1/2,
-				 linewidth = NA) +
-	stat_summary(fun = mean,
-				 geom = "line",
-				 linewidth = 3/4) +
-	labs(x = "Time (ms)",
-		 y = "Logit (Target looking)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
-										 mean(data_bcn$timebin),
-										 sd(data_bcn$timebin)),
-					   labels = \(x) format(seq(3e2, 2e3, 3e2),
-					   					 big.mark = ",")) &
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  legend.position = "top")
+	split(paste0("age_", gsub(" months", "", .$age_std)))
 ```
@@
 #| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
-#| fig-width: 4
-#| fig-height: 3
+#| fig-width: 5
+#| fig-height: 3.5
 epreds_chance |> 
+	mutate(age_std = factor(x = age_std,
+							levels = age_values,
+							labels = paste0(c(20, 32), " months"))) |> 
 	ggplot(aes(age_std, over_chance,
@@
 
-Another possibility is that the findings in @mani2010infant and @mani2011phonological are less robust than anticipated.
-
-Overall the results from Study 2 support a more methodological explanation of the null pattern of results in Study 1, in which the lack of a phonological priming effect---both within and across languages---might be explained by differences in task design or replicability concerns.
+Overall, the results from Study 2 support a more methodological explanation of the null pattern of results in Study 1, in which the lack of a phonological priming effect---both within and across languages---might be explained by differences in task design or replicability concerns.
 
@@
 In Study 2, we tested a cohort of English monolinguals, and found similar results.
-
 To our knowledge this is the first study investigating cross-language priming using an implicit naming paradigm.
@@
 Since the prime pictures are presented in silence, the task is exclusively complete in the dominant language of participants.
-This provides a monolingual situation in which differences in performance across experimental conditions that involve cross-linguistic interactions can be more easily associated to the experimental manipulation in a causal way [ @GROSEJAN1997].
+This provides a monolingual situation in which differences in performance across experimental conditions that involve cross-linguistic interactions can be more easily associated to the experimental manipulation in a causal way [@grosjean1997bilingual].
 This contrast to other experimental paradigms in which participants are presented with---need to produce---items from both languages.
-Such covert manipulation of the similarity between stimuli from the two languages has allowed previous studies to provide strong support for the language-non selective account of lexical access e.g., [COSTA, 2000; THIERRY 2008, 2011; VON 2014].
+Such covert manipulation of the similarity between stimuli from the two languages has allowed previous studies to provide strong support for the language-non selective account of lexical access e.g., [@costa2000cognate; @thierry2007brain; @von2014bilinguals].
 
@@
 The present study presents methodological contributions.
-First, the longitudinal design of the data collection provided a more suitable design for drawing conclusions about developmental change in word recognition trajectories, compared to studies that tested participants from a single age group [@FLOCCIA2020], or studies that with an exclusively cross-sectional design [@VON2012].
+First, the longitudinal design of the data collection provided a more suitable design for drawing conclusions about developmental change in word recognition trajectories, compared to studies that tested participants from a single age group [@floccia2020translation], or studies that with an exclusively cross-sectional design [@von2012language].
 Second, the modelling approach in the present study incorporates the double source of repeated measures simultaneously into the random effects structure of the multilevel model.
-The models in Studies 1 and 2 accounts for the time course of target looking across the trials and its associated autocorrelation using Hierarchical General Additive Models [@barr2008; @PEDERSEN].
+The models in Studies 1 and 2 accounts for the time course of target looking across the trials and its associated autocorrelation using Hierarchical General Additive Models [@barr2008analyzing; @pedersen2019hierarchical].
 The models also incorporate the observations from the same testing session as a nested grouping variable inside participants, so that the test session-level parameters in each model are estimated taking into account the estimations of other testing sessions from the same participants.
@@
 
+Another possibility is that the current study lacked the appropriate statistical power to detect the effect sizes of interest.
+Reported differences in looking time associated to priming paradigms in the available literature in children are generally small.
+Despite the relatively larger sample size achieved in the present investigation, participant-level trajectories of target looking are highly variable, which might have increased the uncertainty of the models' estimates.
+
 The findings in the present investigation have important implications for current models of bilingual lexical development.
 For instance, recent accounts of bilingual words acquisition pointed to a facilitative role of phonological similarity between the two languages.
-A monograph by @floccia2018introduction provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
-Later work by @mitchell2022cognate and @garcia-castro@cognate provided evidence for a more direct facilitation effect of cognateness.
+A monograph by @floccia2018vocabulary provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
+Later work by @mitchell2022cognate, @siow2022effect, and @garcia-castro2023cognate provided evidence for a more direct facilitation effect of cognateness.
 Cognates are form-similar translation equivalents.
@@
 
-recent work uding parental reports of word acquistiion have provided insichc  For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
-This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hill2013, @fourtassi2020].
+recent work using parental reports of word acquisition have provided insights.
+For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
+This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hills2009longitudinal, @fourtassi2020growth].
 

### 2023-11-13 manuscript/manuscript.qmd
Finish introduction, fix participant's LP, and finish discussion

@@
 Building a mental lexicon is a major achievement in the development of an infant: by storing representations of how familiar words sound and what they mean, an infant is able to make sense of their linguistic input.
-The foundations of an initial lexicon are in place before their first year of life [@tincoff1999some; @halle1994emergence; @vihman2004cross; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
-This initial lexicon consists of only a few items; mainly words for people, interjections, body parts, and food [@tincoff2012six; @tardif2008baby], but it undergoes rapid growth during the second year of life [@ganger2004reexamining; @goldfield1990early; @bloom2002children; @mcmurray2007defusing].
-According to parental reports, the average 15-month-old infant already understands more than 100 words, and by two years, they understand more than 400 words [@frank2021variability].
+The foundations of an initial lexicon are in place before the end the first year of life [@tincoff1999some; @halle1994emergence; @vihman2004cross; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
+This initial lexicon consists of only a few items; mainly words for people, interjections, body parts, and food [@tincoff2012six; @tardif2008baby], but it undergoes rapid growth during the second year of life [@ganger2004reexamining; @goldfield1990early; @bloom2002children; @mcmurray2007defusing; @bergelson2020comprehension].
+According to parental reports, the average 15-month-old infant already understands more than 100 words, and by two years of age, they understand more than 400 [@frank2021variability].
 This accelerated lexical developmental is reflected in infants' trajectories of word recognition: infants recognise familiar words faster and more efficiently as they approach their second birthday [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
-Despite being exposed to a more complex linguistic input, bilinguals show equivalent trajectories of word acquisition and word recognition to their monolingual peers' [@vihman2007onset; @legacy2018vocabulary; @hoff2012dual; @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes].
+Despite being exposed to a more complex linguistic input, bilinguals show equivalent trajectories of word acquisition and word recognition to their monolingual peers' [@vihman2007onset; @legacy2018vocabulary; @hoff2012dual; @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes; @bialystok2009bilingualism].
 This is a remarkable deed for two reasons.
-First, bilingual infants receive a relative impoverished linguistic input in each of their languages compared to monolinguals [@costa2014does].
-Second, they face a more complex referential context, since they often learn two labels for each referent, one in each language.
+First, bilingual infants receive a relative impoverished quantitative linguistic input in each of their languages, compared to monolinguals [@costa2014does; @cattani2014much; @thordardottir2011relationship].
+Second, they face a more complex referential context, as they often learn two labels for each referent, one in each language [@au1990principle; @tsui2022translation; @bilson2015semantic; @de2006early].
 The mechanisms that allow bilingual' trajectories of lexical developmental to keep up with monolinguals' are still unclear.
 
-Previous studies have pointed to the interplay between bilingual' languages as a candidate facilitative mechanism behind bilingual lexical acquisition.
-In particular, cross-language similarity at the lexical level has been associated with larger vocabulary sizes.
-@floccia2018introduction collected vocabulary data from a sample of 367 bilingual children living in the United Kingdom, who were learning English and an additional language (out of a diverse pool of 13 languages).
-Using an edit distance-based metric of phonological similarity, the authors computed the average lexical similarity between the translation pairs of the English vocabulary checklist, and of each of the other languages.
+Previous studies have pointed to cross-language dynamics as a candidate mechanism boosting lexical acquisition in bilinguals [@floccia2018vocabulary; @blom2020cross; @gampe2021does].
+In particular, lexical similarity between the two languages has been associated with larger vocabulary sizes in bilingual toddlers.
+@floccia2018vocabulary collected parental reports of vocabulary data from a sample of 367 bilingual children living in the United Kingdom, who were learning English and an additional language (out of a diverse pool of 13 languages).
+The authors then used an edit distance-based metric of phonological similarity to compute the average lexical similarity between the translation pairs in English and each of the additional languages.
+English and Dutch shared the highest lexical similarity, while English and Mandarin shared the lowest.
 Children's vocabulary sizes in the additional language was positively associated with the amount of language similarity between their two languages.
-For instance, children learning English and Dutch (which share high lexical similarity) showed larger vocabulary sizes than those learning English and Mandarin (which share low lexical similarity).
+For instance, children learning English and Dutch showed larger vocabulary sizes than those learning English and Mandarin.
 The authors suggested that the acquisition of words in the additional language might be facilitated by their cognate status (i.e., being phonologically similar to their translation equivalent).
-Larger vocabulary sizes might then be expected in bilinguals learning two languages sharing a high proportion of cognates.
-Recent studies have reported an earlier acquisition of cognate words [@mitchell2022cognates; @garcia-castro2023cognate], providing further evidence that cross-language similarity at the lexical level might boost vocabulary growth in bilinguals.
-
-The facilitative effect of cross-language similarity is in line with the language non-selective account of bilingual lexical access.
-There is robust evidence suggesting that bilingual adults activate both languages in parallel---even during monolingual situations---which influences their performance in word recognition and production tasks [@marian1999; @groot1992determinants; @schwartz2007reading; @dijkstra1999recognition; @dufour1995matching; @schwartz2007reading; @dijkstra2010cross].
+If this is the case, larger vocabulary sizes might then be expected in bilinguals learning two languages sharing a high proportion of cognates.
+This would be consistent with available evidence of an earlier acquisition of cognate words [@bosch2014first; @mitchell2022cognates; @garcia2023cognate].
+
+The facilitative effect of cognateness is in line with the language non-selective account of bilingual lexical access.
+This account proposes that bilinguals activate both languages in parallel, even during monolingual situations, as suggested by robust experimental evidence [@marian1999activation; @groot1992determinants; @schwartz2007reading; @dijkstra1999recognition; @dufour1995matching; @dijkstra2010cross].
 For instance @costa2000cognate presented Catalan-Spanish bilinguals with a series of pictures of familiar objects.
-For each object, participants were asked to name it in Catalan (their dominant language).
+Participants were asked to name each picture in Catalan, their dominant language.
 Unbeknownst to participants, the authors manipulated the cognate status pictures' labels in Catalan and Spanish.
@@
 Participants named pictures faster in cognate trials than in non-cognate trials.
-Critically, Spanish monolinguals who completed the same task, naming the pictures in Spanish, showed equivalent naming times in both conditions.
-These results revealed that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the activation of its associated phonological forms in both languages in parallel, which influenced the subsequent the dynamics of word production.
-
-Parallel activation has also been reported in he developing lexicon [@poarch2012cross; @bosma2020cognate; @singh2014one; @jardak2019labels; @von2019impact; @floccia2020translation].
-For instance, @von2012language found evidence of cross-language phonological priming in twenty 21- to 42-months-old children learning German and English.
-In their experimental task, each trials begun with the auditory presentation of an English prime word embedded in a carrier phrase.
-Then, the target label was auditorily presented in German.
-Finally, the target and a distractor pictures were presented side-by-side.
-The authors created three conditions.
-In the phonological priming condition, the auditorily presented prime and target labels were phonologically related (e.g., *slide*-*Klide* [*dress*]).
-In the priming through translation condition, both labels were phonologically related through translation: the auditorily presented prime label did *not* overlap with the target label (e.g., *leg*-*Stein* [*stone*]), but its translation in German did [*Bein*].
-In the unrelated condition, prime and target labels were phonologically unrelated in both languages.
+Critically, Spanish monolinguals---who completed the same task in Spanish---showed equivalent naming times in both conditions.
+These results revealed that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the parallel activation of its associated phonological forms in both languages, which influenced the subsequent dynamics of word production.
+
+Parallel activation has also been reported in the developing lexicon [@poarch2012cross; @bosma2020cognate; @singh2014one; @jardak2019labels; @von2019impact; @floccia2020translation; @bosma2019longitudinal].
+For instance, @von2012language found suggestive evidence of cross-language phonological priming in a sample of 20 German-English bilinguals aged 21 to 43 months.
+In their experimental task, each trial begun with the auditory presentation of an English prime word, followed by a target German label and a pair of target and distractor pictures.
+The authors registered participants' target picture looking (interpreted as a proxy of target word recognition) under three conditions.
+In the *phonological priming* condition, the auditorily presented prime and target labels were phonologically related (e.g., *slide*-*Klide* [*dress*]).
+In the *priming through translation* condition, prime and target were phonologically related through translation: the auditorily presented prime label did *not* overlap with the target label (e.g., *leg*-*Stein* [*stone*]), but its German translation did [*Bein*].
+In the *unrelated* condition, prime and target labels were phonologically unrelated in both languages.
 Interestingly, participants showed a weaker target preference in priming through translation trials, compared to unrelated trials.
 This was interpreted evidence of the lexical representations of the prime labels being activated in both English and German, leading to interference effects in later target recognition.
-
-Previous studies had reported similar cross-language priming effects.
-The conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was nonetheless unwarranted.
-In studies where the auditorily presented prime label was phonologically overlapped with the target label [e.g., @marian1999activation], priming effects might be explained by the activation of the phonological segments of the prime label, which facilitated the recognition of the target label, which shared such phonological segments.
-This might have been the phonological priming trials in @von2012language, in which prime and target labels shared overt phonological overlap.
-In contrast, the priming through translation results suggest that cross-language activation in the developing lexicon occurs at the lexical level.
-Since participants' target recognition was modulated by the non-presented prime translation, such an inhibitory effect must stem at the lexical level.
-The fact that phonological priming facilitated the recognition of the target words (both labels belong to different languages), and that phonological priming through translation interfered target recognition (translation and target belong to the same language) points to cross-language connections playing an excitatory role, and to within-language connections playing an inhibitory role.
-
-Despite extending the available knowledge on the developing bilingual lexicon, the study by @von2012language has some methodological challenges that prevent strong conclusions about language non-selective access.
-First, participants' received their English input at school, where they heard German and English (between three and four hours each) from a German native speaker.
-Except for four children who also listened to English at home, participants' only exposure to English was 3-4 hours per day, for the time they attended daycare (an average of 12.35 months).
-Assuming that infants are exposed to a daily average of 12 total hours of speech, and they attended daycare only during weekdays, their estimated exposure to English throughout the week represented between `r scales::percent((3*5*4*12.35)/(12*7*4*21), accuracy = 0.01)` and `r scales::percent((4*5*4*12.35)/(12*7*4*21), accuracy = 0.01)` for the 21 month-olds (the youngest in the sample), and between `r scales::percent((3*5*4*12.35)/(12*7*4*43))` and `r scales::percent((4*5*4*12.35)/(12*7*4*43))` for the 43-month-olds.
-Conventionally, children are considered bilingual if exposed to 25% or more of the time to a second language [@byers-heinlein2021multilab; @rocha-hidalgo2023defining].
-Participants in @von2012language might therefore not be generalisable to other populations of bilinguals who received a more balanced dual language input.
-Second, the presence of cognates in the stimuli lists lead to some primes in the phonological priming condition sharing substantial cross-language phonological overlap thought translation with the target words like *fire* /\textipa{faIe}/--*Feuer* /\textipa{fOyeR}/ and *Eier* /\textipa{aIeR}/, or *Moon* /\textipa{mu:n}/--*Mond* /\textipa{mo:nd}/ and *Huhn* /\textipa{hu:n}/.
-Conversely, some trials in the phonological priming through translation shared within-language overlap with the target, such as *Soup* /\text{su:p}/--*Suppe* /\textipa{zupe}/---*Puppe* /\text{pupE}/ and *Puppe* /\textipa{pupE}/.
-Given that the number of total trials in both conditions amounted to six trials, a considerable proportion of the trials presented this methodological limitation.
-Finally, the observed pattern of results was dependent on the inclusion of a single item, *Buch* [*book*, in German].
-When this item was included, monolinguals showed a similar interference effect to bilinguals in the priming through translation condition, in which only bilinguals with knowledge of the translation should show an effect.
-Additionally, given that monolinguals and bilinguals were not directly, it is not possible to conclude that the differences in statistical significance between monolingual and bilingual target looking, compared to chance levels, does not necessarily provide a significant difference between the two groups.
-As a consequence, the conclusion that the interference effects observed in the priming through translation condition is exclusive to bilinguals (which would suggest that the priming effect were not due to the intrinsic properties of the stimuli) in unwarranted.
-
-Additionally, although the priming through translation paradigm provides a convenient framework to investigate parallel activation in the bilingual lexicon, its design prevents strong interpretations about the extent to which parallel activation is the result of the experimental manipulations of interest.
-The presentation of primes and targets in both languages in the same task---or even within the same trial---presents participants with a bilingual context that might lead to a higher baseline activation of lexical representations of both languages, contrary to a context in which parallel activation results from genuine cross-language activation [@grosjean1997bilingual].
-Another limitation of priming through translation studies is that, when prime words are auditorily presented, the task constrains the naming context to one of the languages.
-The consequence is a potential asymmetry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
-This might lead to a lower strength, and higher latency of the activation of the translation.
-In summary, current evidence on the cross-language interplay in the initial lexicon should be considered carefully.
-
-In the present study, we put the hypothesis that bilingual infants activate both languages in parallel to a more severe test.
-We used an extension of the implicit naming task by @mani2010infant, in which participants were primed with a picture presented in silence.
-Previous studies using this paradigm have successfully provided evidence of language non-selectivity.
-In particular, @von2014bilinguals found that bilingual adults generate implicit labels in both labels for visually fixated pictures.
+Previous studies had reported similar cross-language priming effects, but the conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was nonetheless unwarranted.
+In studies where the auditorily presented prime label was phonologically overlapped with the target label [e.g., @marian1999activation], priming effects could be explained by sub-lexical facilitation across phonological segments.
+This might explain the facilitation effect found in *phonological priming* trials in @von2012language, in which English prime and German target labels shared overt phonological overlap.
+In contrast, the interference effect found in *priming through translation* trials points to cross-language competition at the lexical level.
+Since participants' target recognition was modulated by the phonology of the German translation of the prime (which participants did *not* hear), cross-language priming can be explained by the lexical co-activation of the English *and* German prime labels.
+
+@von2012language extended the available knowledge on the developing bilingual lexicon, but some methodological challenges prevent drawing strong conclusions from their findings.
+First, bilingual participants' quantitative exposure to English as a second language was lower than what is conventionally considered as bilingualism [20-50% of cumulative exposure, @byers-heinlein2021multilab; @rocha-hidalgo2023defining]^[Except for four participants who were also exposed to English at home, participants in @von2012language received their English input exclusively at school from a German native speaker.
+Participants' exposure to each language ranged between three and four hours per day.
+This implies that participants' exposure to English consisted of an average of 3-4 hours per day, during the time they attended daycare (reported as an average 12.35 months).
+Assuming that infants were exposed to a daily average of 12 total hours of speech, and that they attended daycare five days per week, the estimated cumulative to English in the life of an average child in the sample was between `r scales::percent((3*5*4*12.35)/(12*7*4*21), accuracy = 0.01)` and `r scales::percent((4*5*4*12.35)/(12*7*4*21), accuracy = 0.01)` for the 21 month-olds (the youngest in the sample), and between `r scales::percent((3*5*4*12.35)/(12*7*4*43), accuracy = 0.01)` and `r scales::percent((4*5*4*12.35)/(12*7*4*43), accuracy = 0.01)` for the 43-month-olds.
+These percentages were calculated as:
+$$\frac{\text{Total English input}}{ \text{Total English + German input}} = \frac{3 \text{ or } 4 \text{ hours/day} \times 5 \text{ days/week } \times 4\text{ weeks/month }  \times 21 \text{ or } 43 \text{ months of age}}{12 \text{ hours/day} \times 7 \text{ days/week } \times 4\text{ weeks/month }  \times 21 \text{ or } 43 \text{ months of age}}$$.].
+Results should therefore be taken with caution when generalised to other populations of bilinguals.
+A second consideration is the presence of cognates in a substantial proportion of the trials in the *phonological priming* and *priming thorugh translation* conditions.
+Because of this, some prime labels in *phonological priming* trials shared substantial cross-language phonological overlap thought translation with the target words.
+Conversely, some trials in the *phonological priming through translation* shared within-language overlap with the target.
+Third, the observed pattern of results was dependent on the inclusion of a single item, *Buch* [*book*, in German].
+When this item was included, monolinguals showed a similar interference effect to bilinguals' in the *priming through translation* condition, in which only bilinguals with knowledge of the translation should show an effect.
+Fourth, data from monolinguals and bilinguals were not compared directly (analyses were conducted separately for both groups).
+Differences in statistical significance between monolinguals and bilinguals across conditions do not necessarily guarantee significant differences between the two groups.
+As a consequence, whether the interference effects observed in the *priming through translation* condition is exclusive to bilinguals (which would suggest that the priming effect were not due to the intrinsic properties of the stimuli) or not is unclear.
+In summary, evidence of cross-language activation at the lexical level in infants is, to date, inconclusive.
+
+In the present study, we use an extension of the implicit naming task [@mani2010infant; @mani2011phonological] to put the language non-selectivity in the developing lexicon to a more severe test.
+Previous studies have successfully used this task to investigate priming effects in word recognition in monolingual infants and bilingual adults.
+In the original implementation of the task, @mani2010infant primed infants with a picture presented in silence.
+At test, a target-distractor picture pair were presented side-by-side.
+Finally, the target picture's label was presented auditorily.
+The authors manipulated the phonological overlap between the prime and the target labels, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
+Prime and target-distractor pairs were semantically unrelated.
+Eighteen-month-old infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
+This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
+
+@von2014bilinguals adapted this paradigm to investigate cross-language activation in bilingual adults.
 The authors presented German-English bilinguals with 120 prime-target pairs.
@@
 After prime picture offset, target words were presented auditorily.
-Participants' N400 ERP components were recorded from target word onset.
+Participants' eletrophysiological response was recorded, and N400 evoked potentials to the auditory target label was measured.
 The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
@@
 This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
-
-This paradigm provides participants with an exclusively monolingual context in which they perform the task in only one of their languages.
-If differences in task performance are found associated with covert manipulation of cross-linguistic properties of the stimuli, such differences may be more conclusively linked to the parallel activation of lexical representations in participants' lexicons.
-By using an implicit naming paradigm, the activation of the lexical representation of the prime may occur in both languages as the result of lexical retrieval after visual recognition of the prime picture, since participants are not presented with any auditory prime label.
-This contrasts with priming through-translation tasks, in which the prime label in one of the languages is directly activated by auditory word recognition, while the label of its translation is expected to be activated as the result of cascaded activation spreading through their semantic association.
-This may lead to an asymmetry in the time course of the activation of both labels, which might in turn affect the dynamics of phonological priming in subsequent word recognition.
-
-In the present investigation, we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
-We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
-If so, phonological priming effect should be larger when the prime label in both languages shares phonological overlap with the target words (*Related/Cognate* condition), compared to when only the label of the prime in one language overlaps phonologically with the target (*Related/Non-cognate*).
+In summary, the implicit naming paradigm has been successful used in the past to investigate the emergence of phonological priming effects in monolingual infants, and to investigate cross-language priming effects in bilingual adults.
+
+The implicit naming paradigm provides several advantages over the priming through translation task.
+In the priming through translation task, primes and targets are auditorily presented in both languages in the same trial.
+This presents participants with a bilingual context that might lead to a higher baseline activation of lexical representations of both languages, contrary to a context in which parallel activation results from genuine cross-language activation [@grosjean1997bilingual].
+Also, when prime words are auditorily presented, the task imposes an asymmetry between the activation dynamics of the lexical representation of the prime in each language: while participants hear prime labels in one language, the activation of prime labels in the other must occur via cascaded activation across semantic links with their translations.
+This might lead to a lower strength, and higher latency of the activation of prime labels in one language, compared to the presented labels in the other.
+In contrast, the implicit naming paradigm provides participants with an exclusively monolingual context in which they perform the task in only one of their languages.
+At the same time, the silent presentation of prime pictures allows participants to activate prime labels in both languages in a truly parallel fashion.
+If differences in task performance are found associated with covert manipulation of cross-linguistic properties of prime labels, such differences may be more conclusively linked to the parallel activation of lexical representations in both languages.
+
+In the present investigation, we manipulated both the phonological overlap between the prime word and target word and the cognate status of the prime word, to test the whether bilingual toddlers implicitly name familiar pictures in both languages.
+If this is the case, phonological priming effects should be larger when the prime label in both languages shares phonological overlap with the target words (*Related/Cognate* condition), compared to when only the label of the prime in one language overlaps phonologically with the target (*Related/Non-cognate*).
 We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
-To test cross-language priming effects, we registered participants' time course of target picture looking in the three conditions.
-We predicted within-language priming effects, revealed as differences in target looking between *Unrelated* and *Related/Non-cognate* trials, as previously reported [@von2012language, @mani2010infant, and @mani2011phonological].
+We registered participants' target looking during target-distractor presentation, and that, if within-language priming effects take place, differences in target looking between *Unrelated* and *Related/Non-cognate* trials should be observed, as previously reported [@von2012language, @mani2010infant; @mani2011phonological].
 We further predicted cross-language priming effects, revealed as differences in target looking between *Related/Non-cognate* and *Related/Cognate* trials.
-This effect should be stronger in bilinguals, if not completely absent in monolinguals, who should be indifferent to the phonological properties of the stimuli in the other language.
-
-Following previous studies associating the emergence of phonological links between lexical items to the size of children's vocabulary [@mani2011phonological], we also compared the explanatory power of two indices of receptive vocabulary size (dominant-language vocabulary size and total vocabulary size) against participants' age.
-We used parental reports of vocabulary checklist to estimate participants' vocabulary size.
-We computed vocabulary size in the dominant language (L1 vocabulary) as the proportion of words in the dominant language reported by their caregivers to be understood by the child in a vocabulary checklist, and the total vocabulary size as the proportion of words reported as understood by the child in *both* languages.
+This effect should be stronger in bilinguals than monolinguals, if not completely absent in the latter, who should be indifferent to the phonological properties of the stimuli in the other language.
+
+Following previous studies associating the emergence of phonological links between lexical items to the size of children's vocabulary [@mani2011phonological; @chow2017spoken], we also compared the explanatory power of two indices of receptive vocabulary size against participants' age: dominant-language vocabulary size and total vocabulary size.
 If within-language or cross-language phonological associations in the lexicon emerge as a function of vocabulary growth, the size of the differences between conditions should larger in participants with larger vocabulary sizes.
-A model including participants' L1 or total vocabulary size as a predictor should then show better performance than a model that instead includes participants age.
-In the case of bilinguals, if the emergence of cross-language priming effects is associated with the growth of their vocabulary is *both* languages, a model including total vocabulary size as a predictor should perform better than a model that includes L1 vocabulary size.
-The opposite pattern would indicate that cross-language priming effects emerge as a function of the growth of L1 vocabulary.
+A model including participants' dominant-language or total vocabulary size as a predictor should then show better performance than a model that instead includes participants age.
+In the case of bilinguals, if the emergence of cross-language priming effects is associated with the growth of their vocabulary is *both* languages, a model including total vocabulary size as a predictor should perform better than a model that includes dominant-language vocabulary size.
+The opposite pattern would indicate that cross-language priming effects emerge as a function of the growth of dominant-language vocabulary.
 
@@
 	arrange(lp, test_language) |> 
+	distinct(session_id, child_id, .keep_all = TRUE) |> 
 	summarise(n = n(),
-			  n_participants = n_distinct(child_id),
+			  n_participants = length(unique(child_id)),
 			  across(age, lst(mean, sd, min, max)),
@@
 	   groupname_col = "lp") |> 
+	summary_rows(groups = c("Monolingual", "Bilingual"),
+				 columns = matches("age"),
+				 fns = list(Total ~ mean(.)),
+				 fmt = ~ fmt_number(., decimals = 1, use_seps = FALSE)) |> 
+	summary_rows(groups = c("Monolingual", "Bilingual"),
+				 columns = c(n, n_participants),
+				 fns = list(Total ~ sum(.)),
+				 fmt = ~ fmt_integer(.)) |> 
+	summary_rows(groups = c("Monolingual", "Bilingual"),
+				 columns = matches("doe"),
+				 fns = list(Total ~ mean(.)),
+				 fmt = ~ fmt_number(., decimals = 1, scale_by = 100)) |> 
+	grand_summary_rows(columns = matches("age"),
+					   fns = list(Total ~ mean(.)),
+					   fmt = ~ fmt_number(., decimals = 1)) |> 
+	grand_summary_rows(columns = matches("doe"),
+					   fns = list(Total ~ mean(.)),
+					   fmt = ~ fmt_number(., decimals = 1, scale_by = 100)) |> 
+	grand_summary_rows(columns = c(n, n_participants),
+					   fns = list(Total ~ sum(.)),
+					   fmt = ~ fmt_integer(.)) |> 
 	# gt_plt_dist(age_vctr, type = "histogram") |>
@@
 	cols_merge(c(age_min, age_max), 
-			   pattern = "{1} ({2})") |> 
+			   pattern = "{1}-{2}") |> 
 	cols_merge(c(age_mean, age_sd),
@@
 	tab_spanner("Degree of Exposure (%)", matches("doe")) |> 
-	cols_label(n = "N sessions",
-			   n_participants = "N participants",
+	cols_label(n = "Sessions",
+			   n_participants = "Participants",
 			   age_mean = "M (SD)",
 			   age_min = "Range",
-			   # age_vctr = "Distribution",
 			   doe_catalan_mean = "M (SD)",
@@
 
-We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability] developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers.
+We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers, and inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability].
 Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
 We calculated two measures of receptive vocabulary size for each participant: *L1 vocabulary size* (proportion of words  reported as acquired in the checklist of the dominant language), and *total vocabulary size* (proportion of the words in both checklists reported as acquired).
-`r n_imputed` (`r prop_imputed`) Families failed to provide a complete response to the BVQ within the two-week time limit, or did not provide a successful response to the questionnaire.
-For missing questionnaire responses, we imputed the vocabulary size of the participant using single imputation, using the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
-We used participants age in months and their language profile (monolingual/bilingual) as predictors.
-We used the `mice` R package [@van2011mice] to perform imputation using the Bayesian linear regression method.
+`r english::Words(n_imputed)` (`r prop_imputed`) families failed to provide a complete response to the BVQ within the two-week time limit.
+We imputed missing vocabulary size scores using single imputation, taking the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
+We used participants' age in months and their language profile (monolingual or bilingual) as predictors.
+We used the `mice` R package [@van2011mice] to perform imputation using the Bayesian linear regression method (see Appendix B).
 
 Overall, there was a substantial increase in both total and L1 vocabulary sizes associated to age (see @fig-vocabulary).
-Monolinguals showed overall higher L1 vocabulary sizes than monolinguals: they were reported to understand an average of `r vocab_means$age_21$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$l1_prop_sd`) at 30 months, while bilinguals  were reported to understand an average of `r vocab_means$age_21$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$l1_prop_sd`) at 30 months.
+Monolinguals showed higher L1 vocabulary sizes than monolinguals: they were reported to understand an average of `r vocab_means$age_21$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$l1_prop_sd`) at 30 months, while bilinguals  were reported to understand an average of `r vocab_means$age_21$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$l1_prop_sd`) at 30 months.
 Total vocabulary sizes showed the opposite pattern, with monolinguals infants being reported to understand `r vocab_means$age_21$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$total_prop_sd`) at 30 months, and bilinguals being reported to understand `r vocab_means$age_21$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$total_prop_sd`) at 30 months.
@@
 #| label: fig-vocabulary
-#| fig-cap: "Participant vocabulary sizes across ages and language profiles.
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles.
 Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
@@
 We created six stimuli lists: three in Catalan, and three in Spanish.
-Each list contained 32 trials, each involving a prime-target-distractor group.
-Each word played a role as either prime, *or* as target and distractor across the three lists in their corresponding language.
+Each list contained 32 trials, each involving a prime-target-distractor triplet.
+Words played a role as primes *or* targets/distractors across the three lists in their corresponding language.
 For instance, the Catalan word *cadira* appeared as *prime* in the three lists, but never as *target* or *distractor*; the Catalan word *bici* appeared as *target* and *distractor* across the three lists, but never as a prime.
@@
 Finally, prime words appeared only once in each list: each target-distractor pair was associated with a different prime word in both appearances.
-In each list, the same prime word was presented alongside a different target-distractor pair.
+Across lists, the same prime word was presented alongside a different target-distractor pair.
 For instance, the Catalan prime word *barret* was presented with the *bici*-*porta* target-distractor pair in one list, with the *bici*-*porta* pair in another list, and with *berenar*-*amanida* in the remaining list.
 To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias2009lexical].
-The order of the trials was randomised across experimental session, so that each time a participant was tested, the order in which the prime-target-distractor was presented was randomised.
+The order of the trials was randomised across experimental sessions, so that each time a participant was tested, the order in which the prime-target-distractor was presented was random.
 Each participant was randomly assigned to one of the three lists in the corresponding (dominant) language, and always the same list across their experimental sessions in the case of a recurrent participant.
 
-In 16 of the 32 trials of the same list (henceforth *related* trials), the prime and the target words were phonologically related, sharing phonological onset (at least first phoneme).
-In the other 16 trials (*unrelated* trials), prime and target did not share phonological onset.
-8 of the 16 *related* trials included a cognate prime (*cognate* trials), and the other 8 included a non-cognate trials (*non-cognate* trials).
+In 16 of the 32 trials of the same list (henceforth *Related* trials), the prime and the target words were phonologically related, sharing phonological onset (at least first phoneme).
+In the other 16 trials (*Unrelated* trials), prime and target did not share phonological onset.
+Eight of the 16 *Related* trials included a cognate prime (*Related/Cognate* trials), and the other eight included a non-cognate prime (*Related/Non-cognate* trials).
+Target and distractor word pairs were phonologically unrelated (did not share phonological onset).
 A prime word was considered cognate if its Catalan and Spanish translation shared phonological onset.
 Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
-Target and distractor word pairs were phonologically unrelated (did not share phonological onset).
-Some of them shared semantic features or a taxonomic relationship.
+Some target-distractor pairs shared semantic features or a taxonomic relationship.
 This is the case of words associated with especially salient referents such as animals or food.
@@
 The auditory stimuli were natural exemplars of the selected target words, spoken by Central Catalan-Spanish proficient bilingual female speaker who was instructed to pronounce each word in a toddler-directed manner.
-Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
+Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44,100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
 We used the Audacity and Praat [@boersma2001speak] software packages to record and edit the audio files.
@@
 Each word was depicted by a realistic phonographic representation of a typical exemplar.
-Image backgrounds were removed from the original pictures using the GNU Image Manipulation Program (GIMP), resized to a rectangle of a maximum of 400 pixels hight or wide, and finally placed in the centre of a 50% grey rectangle square of 500$\times$500 pixels.
+Image backgrounds were removed from the original pictures using the GNU Image Manipulation Program (GIMP), resized to a rectangle of a maximum of 400 pixels hight or wide, and finally placed in the centre of a 50% grey rectangle square of 500 $\times$ 500 pixels.
 The final stimuli had a resolution of 72 dpi.
-When presented in the eye-tracker screen, the areas of interest (AOI) occupied an area of 13.23$\times$13.23 cm (11.613º visual angle from participants' perspective).
+When presented in the eye-tracker screen, the areas of interest (AOI) occupied an area of 13.23 $\times$ 13.23 cm (11.613$^{\circ}$ visual angle from participants' perspective).
 
@@
 In each trial, the prime image is presented in silence for 1,500 ms.
-The the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
+Then the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
 In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
 In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
-In unrelated trials (*n* = 32), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){fig-align="center"}
-
-Each trial started with the presentation of an attention getter for 3,000 milliseconds.
+In unrelated trials (*n* = 16), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){fig-align="center"}
+
+Each trial started with the presentation of an attention getter for 3,000 ms.
 Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
@@
 
-We defined a time windows of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
-To avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
+We defined a time window of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
+The first 200 ms of the test phase were discarded to avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
 Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
@@
 We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 10% of valid samples (equivalent to 100 ms) of for the target *and* the distractor each (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation; @manidurrantfloccia for a similar approach].
-
-After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
+We also excluded trials in which participants did not provide at least 10% of valid samples (equivalent to 100 ms) for both the target *and* the distractor (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation; @mani2012activation for a similar approach].
+
+After excluding trials that matched any of the aforementioned criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
 The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
 Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition-trials shows a detailed description of the trial attrition.
+@tbl-attrition shows a detailed description of the trial attrition.
 
@@
 
-We used Bayesian Hierarchical General Additive Models (HGAMs) to model our data and test our hypotheses [@pedersen2019hierarchical].
-First, we defined our response variable as the empirical logit of target looking using @eq-elogit across all eye-tracking samples for each each participant in each condition [@barr2008analyzing; @agresti2012categorical].
-We used a Gaussian distribution to model our response variable.
-To test our hypotheses, we then included *Condition*, *Group*, and either *Age* ($\mathcal{M}_0$), *L1 vocabulary* ($\mathcal{M}_1$), or *Total vocabulary* ($\mathcal{M}_2$) as fixed effects in the model.
-We also added all two-way and three-way interactions between the predictors.
-We set two *a priori* contrasts for the *Condition* predictor: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
+We used Bayesian Hierarchical General Additive Models (HGAMs) to model the data [@pedersen2019hierarchical].
+First, we defined our response variable as the empirical logit of target looking (see @eq-elogit) across all eye-tracking samples for each each participant in each condition [@barr2008analyzing; @agresti2012categorical].
+We used a Gaussian distribution to model this variable.
+To test our hypotheses, we included *Condition*, *Group*, their two-way interaction, and *Age* as fixed effects in the model.
+We set two *a priori* contrasts for the *Condition* predictor [@schad2020capitalize]: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
 We also set two *a priori* contrasts for the *Group* predictor: one comparing *Monolingual (ENG)* with *Monolingual (CAT/SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Bilingual (CAT-SPA)* participants coded as `0`), and another comparing *Monolingual (ENG)* with *Bilingual (CAT-SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Monolingual (CAT/SPA)* participants coded as `0`).
@@
 
-We included *Session*---which indexes individual testing sessions that may belong to the same participant---as grouping variable, nested within *Participant* grouping variable---which indexes a distinct participant.
+We included the variable *Session*---which indexes individual testing sessions that may belong to the same participant---as grouping variable, nested within the *Participant* grouping variable---which indexes a distinct participant.
 This nested random effects structure incorporates the longitudinal design of data collection, in which multiple participants were tested more than once at different ages.
-We added by by-session intercepts and *Condition* slopes, and by-participant intercepts and *Age* slopes.
-To model the time course of target looking across time bins, we included B-splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
-For both splines, we specified $k = 6$ basis functions or *knots*.
+We added by-session intercepts and *Condition* slopes, and by-participant intercepts and *Age* slopes.
+To model the time course of target looking across time bins, we included B-splines for the main effect of *Time*, and one for the interaction between *Group* and *Relatedness* [@wood2017generalized].
+For both splines, we specified $k = 8$ basis functions or *knots*.
 @eq-model shows a formal implementation of the model.
+We implemented the models using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
+We ran `r english::words(dim(model_fits_bcn$fit_0$fit)[2])` iteration chains using the by-default No U-Turn Sampler algorithm with `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` iterations each and an additional `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` warm-up iterations per chain.
 
@@
 \begin{aligned}
-\textbf{Likelihood:} \\
-y_i &\sim \mathcal{N}(\mu_i, \sigma_i) \\ \\
-\textbf{Linear model:} \\
-\eta'(\mu_i) &= (\beta_0 + u _{0_{i}}) +
-(\beta_1 + u _{1_{i}}) \cdot \text{Condition} +\\
+&\textbf{Target looking by participant } i \textbf{ in session } j \\
+y_{ij} &\sim \mathcal{N}(\mu_{ij}, \sigma_{ij}) \\ \\
+&\textbf{Distributional parameters:} \\
+\eta'(\mu_{ij}) &= (\beta_0 + u _{0_{ij}}) +
+(\beta_1 + u _{1_{ij}}) \cdot \text{Condition} +\\
 &\beta_{2} \cdot \text{Group} +
@@
 &\beta_{7} \cdot (\text{Condition} \times \text{Group} \times X) +\\
-& \sum_{j = 1}^k b_{j_{0}} \cdot \beta_{8_{k}} \cdot \text{Time} +
-\sum_{j = 1}^k b_{j_{1}} \cdot\beta_{9_{k}} \cdot (\text{Time} \times \text{Group}) \\
+& \sum_{w = 1}^k b_{w_{0}} \cdot \beta_{8_{k}} \cdot \text{Time} +
+\sum_{w = 1}^k b_{w_{1}} \cdot\beta_{9_{k}} \cdot (\text{Time} \times \text{Group}) \\
 \text{where:} \\
@@
 &X \in \{\text{Age}, \text{L1 vocabulary}, \text{Total vocabulary}\} \\
-&b_{j_{0-1}} \text{ are the basis cubic spline basis functions} \\
+&b_{w_{0-1}} \text{ is the cubic spline of the } w \text{ basis function} \\
 &k \text{ is the number of knots in the spline (10)} \\
-\textbf{Prior:} \\
+&\textbf{Prior:} \\
 \beta_{0-9} &\sim \mathcal{N}(0, 0.5) \\
-u_{0-2} &\sim \mathcal{N}(0, \sigma_{0-2})\\
+u_{0-1_{ij}} &\sim \mathcal{N}(0, \sigma_{0-2})\\
 b_{0-1} &\sim \text{MVN}(0, \tau_{0-1}) \\
@@
 
-The comparison between the three models including *Age*, *L1 vocabulary*, *Total vocabulary* as predictors was done using leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it [@vehtari2017practical].
-We implemented the model using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
-We ran `r english::words(dim(model_fits_bcn$fit_0$fit)[2])` iteration chains using the by-default No U-Turn Sampler algorithm with `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` iterations each and an additional `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` warm-up iterations per chain.
-
 #### Statistical inference
 
-We assessed the practical relevance of the estimated regression coefficients of the model following @kruschke2018bayesian.
-First, we specified a region of practical equivalence (ROPE) from `r rope_interval["lower"]` to +`r rope_interval["upper"]`, in the probability scale.
+We tested the differences between the conditions of interest in two ways.
+First, we examined the posterior distribution of the regression coefficients of the linear predictors in model $\mathcal{M}_0$ (see @eq-model).
+We assessed the practical relevance of the coefficients following @kruschke2018bayesian.
+We specified a region of practical equivalence (ROPE) from `r rope_interval[1]` to +`r rope_interval[2]`, in the logit scale.
 This region indicates the range of values that we considered equivalent to zero.
@@
 For example, $p(\text{ROPE})=.80$ indicates that, given our data, there is a 80% probability that the true value of the coefficient falls within the ROPE, and can therefore be considered equivalent to zero.
-
-We followed a similar procedure to compare the effect of the predictors of interest on the time course of target looking.
-First, we defined a ROPE from `r rope_interval["lower"]` to +`r rope_interval["upper"]` in the logit scale.
-We then computed the difference between  of the regression coefficient of the continuous predictor *Age*, the difference coefficients *Group*, *Condition*, and *Age* at each time bin, which indicates the marginal effect of the predictor on target looking at that specific
+Second, we examined the differences between the priming conditions across the time course of the trial.
+We generated marginal posterior predictions from the model for the three conditions, for monolinguals and monolinguals.
+These predictions included the non-linear relationship between target looking and the time course of the trial.
+We then computed the difference between the marginal posterior predictions for the *Unrelated* and *Related/Non-cognate* conditions, and between those for the *Related/Non-cognate* and *Related/Cognate* conditions, at each time bin.
+Finally, we compared the 95% HDI of the differences against the [-0.1, +0.1] ROPE.
+
+To test our hypotheses regarding the role of age, dominant-language vocabulary size, and total vocabulary size, on the emergence of priming effects, we compared the fit of model $\mathcal{M}_0$ against the fit of other models including the three-way interaction between *Condition*, *Group*, and *Age* ($\mathcal{M}_1$), *L1 vocabulary* ($\mathcal{M}_2$), and *Total vocabulary* ($\mathcal{M}_3$), and all two-way interactions involved.
+We compared the models using one-out cross-validation (LOO-CV) as a benchmark of model performance, using a Pareto-smoothed importance sampling (PSIS) approximation [@vehtari2017practical].
+A better performance by models $\mathcal{M}_1$, $\mathcal{M}_2$, or $\mathcal{M}_3$ over $\mathcal{M}_0$ would point to *Age*, *L1 vocabulary*, or *Total vocabulary*, respectively, playing a substantial role in participants' word-recognition, or on the emergence of priming effects.
 
@@
 
-### Model comparisons
-
-```{r tbl-loos}
-#| label: tbl-loos
-#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of models 0 to 3, and 3 to 6 in Study 1."
-get_loos <- function(x, y) {
-	out <- lst(m_0 = x, m_1 = y) |> 
-		loo_compare() |> 
-		as.data.frame() |> 
-		rownames_to_column("model") |>
-		arrange(model) |> 
-		select(model, elpd_diff, se_diff) |> 
-		mutate(diff_label = sprintf("%.3f", elpd_diff),
-			   se_label = sprintf("%.3f", se_diff))
-	return(out)
-}
-
-loos_03 <- loo_compare(model_loos_bcn[1:4]) |> 
-	as.data.frame() |> 
-	rownames_to_column("model") |> 
-	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model))),
-		   across(matches("diff"),
-		   	   \(x) {x[1] <- NA; return(x)}))
-
-loos_36 <- loo_compare(model_loos_bcn[4:7]) |> 
-	as.data.frame() |> 
-	rownames_to_column("model") |> 
-	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model))),
-		   across(matches("diff"),
-		   	   \(x) {x[1] <- NA; return(x)}))
-
-bind_rows("Base models" = loos_03,
-		  "Age and vocabulary size models" = loos_36, 
-		  .id = "type") |> 
-	select(type, model, matches("elpd|diff")) |> 
-	relocate(matches("diff"), .after = matches("loo")) |> 
-	gt(rowname_col = "model", groupname_col = "type") |> 
-	fmt_number(is.numeric) |> 
-	cols_label(elpd_diff = "ELPD (diff.)",
-			   se_diff = "SE ELPD (diff)",
-			   elpd_loo = "ELPD",
-			   se_elpd_loo = "SE ELPD") |> 
-	fmt_missing(missing_text = "---") |> 
-	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new dataset.
-*SE \\(ELPD\\)*: standard error of the *ELPD*, which indictes the uncertainty about the predictive performance for unknown future data.
-*ELPD (diff)*: pairwise difference in *ELPD* for two models.
-The difference is computed relative to the model with highest *ELPD*.
-*SE ELPD (diff.)*: standard error of component-wise differences of *ELPD* between two models.")) |>
-	tab_style(cell_text(style = "italic"), cells_column_labels())
-```
-
-@tbl-loos summarises the outputs of the LOO-CV model comparisons.
-Models $\mathcal{M}_{2}$ and $\mathcal{M}_{3}$, showed substantially better predicted performance than models $\mathcal{M}_{0}$ and $\mathcal{M}_{1}$, which indicates that adding the *Condition* predictor improves significantly the fit of the models.
-Both $\mathcal{M}_{2}$ and $\mathcal{M}_{3}$ models showed equivalent performance, suggesting that adding the two-way interaction between *Group*, and *Condition*, did not improve the the fit of the model substantially.
-We now report a description of the posterior distribution of the regression coefficients of model $\mathcal{M}_{3}$.
-We now report the median and 95% highest density interval of each fixed regression coefficient in $\mathcal{M}_{3}$ (see @tbl-coefs).
-
-### Linear effects
+### Priming effects
+
+```{r coefs}
+var_labels <- c("b_Intercept" = "Intercept",
+				"b_age_std" = "Age (+1 SD)",
+				"b_lp1" = "Group",
+				"b_condition1" = "Condition (U vs. RN)",
+				"b_condition2" = "Condition (RN vs. RC)",
+				"b_condition1:lp1" = "Group \U00D7 Condition (U vs. RN)",
+				"b_condition2:lp1" = "Group \U00D7 Condition (RN vs. RC)")
+
+model_summary <- get_posterior_summary(model_fits_bcn$fit_3,
+									   data_bcn,
+									   vars_dict = var_labels,
+									   rope_interval = rope_interval)
+
+coefs <- model_summary |> 
+	mutate(.value = sprintf("%.3f", .value),
+		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
+		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
+	split(janitor::make_clean_names(model_summary$.variable))
+```
+
+Overall, the average participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$b_intercept$.value`, 95% HDI = `r coefs$b_intercept$.ci`), and that all of its posterior samples fell outside of the ROPE.
+The coefficient of *Age* had a positive sign, but its 95% HDI overlapped completely with the ROPE ($\beta$ = `r coefs$b_age_std$.value`, 95% HDI = `r coefs$b_age_std$.ci`), indicating that participants from all ages showed equivalent overall target word recognition.
+The 95% HDI of the coefficient of *Group* also included zero ($\beta$ = `r coefs$b_lp1$.value`, 95% HDI = `r coefs$b_lp1$.ci`) and completely overlapped with the ROPE, indicating an equivalent overall target preference in monolinguals and bilinguals.
+The 95% HDI of the first contrast of the *Condition* predictor---comparing *Unrelated* and *Related/Non-cognate* trials---included zero ($\beta$ = `r coefs$b_condition1$.value`, 95% HDI = `r coefs$b_condition1$.ci`), and `r coefs$b_condition1$.rope` of its posterior samples overlapped with the ROPE.
+The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$b_condition2$.value`, 95% HDI = `r coefs$b_condition2$.ci`), and `r coefs$b_condition2$.rope` of its posterior samples overlapped with the ROPE.
+The overall target preference was equivalent across both pairwise condition comparisons.
+The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$b_condition1_lp1$.value`, 95% HDI = `r coefs$b_condition1_lp1$.ci`), with `r coefs$b_condition1_lp1$.rope` of its posterior samples overlapping with the ROPE.
+The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$b_condition2_lp1$.value`, 95% HDI = `r coefs$b_condition2_lp1$.ci`), and  `r coefs$b_condition1$.rope` of its posterior samples fell within the ROPE.
+The outcomes of this model provide strong evidence against differences between monolinguals and monolinguals, and inconclusive evidence for differences in overall target looking time across conditions.
 
@@
 #| message: false
+#| eval: false
 #| warning: false
 #| out-width: 80%
-var_labels <- c("b_Intercept" = "Intercept",
-				"b_age_std" = "Age (+1 SD)",
-				"b_lp1" = "Group",
-				"b_condition1" = "Condition (U vs. RN)",
-				"b_condition2" = "Condition (RN vs. RC)",
-				"b_condition1:lp1" = "Group \U00D7 Condition (U vs. RN)",
-				"b_condition2:lp1" = "Group \U00D7 Condition (RN vs. RC)")
-
-model_summary <- get_posterior_summary(model_fits_bcn$fit_3,
-									   data_bcn,
-									   vars_dict = var_labels,
-									   rope_interval = rope_interval)
-
-coefs <- model_summary |> 
-	mutate(.value = sprintf("%.3f", .value),
-		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
-		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
-	split(janitor::make_clean_names(model_summary$.variable))
-
 # summarise posterior draws
@@
 
-Overall, the average participants' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$b_intercept$.value`, 95% HDI = `r coefs$b_intercept$.ci`), and all of its posterior samples were outside of the ROPE.
-The coefficient of *Age* had a positive sign, but its 95% HDI overlapped completely with the ROPE ($\beta$ = `r coefs$b_age_std$mdn_label`, 95% HDI = `r coefs$b_age_std$.ci`), indicating that participants from all ages showed equivalent overall target word recognition.
-The 95% HDI of the coefficient of *Group* also included zero ($\beta$ = `r coefs$b_lp1$.value`, 95% HDI = `r coefs$b_lp1$.ci`) and completely overlapped with the ROPE, indicating an equivalent overall target preference in monolinguals and bilinguals.
-The 95% HDI of the first contrast of the *Condition* predictor---comparing *Unrelated* and *Related/Non-cognate* trials---included zero ($\beta$ = `r coefs$b_condition1$.value`, 95% HDI = `r coefs$b_condition1$.ci`), and `r coefs$b_condition1$.rope` of its posterior samples overlapped with the ROPE.
-The 95% HDI of the second contrast, comparing *Related/Non-cognate* and *Related/Cognate* trials, also included zero ($\beta$ = `r coefs$b_condition2$.value`, 95% HDI = `r coefs$b_condition2$.ci`), and `r coefs$b_condition2$.rope` of its posterior samples overlapped with the ROPE.
-The overall target preference was equivalent across both pairwise condition comparisons.
-The interaction term between the first *Condition* contrast contained zero ($\beta$ = `r coefs$b_condition1_lp1$.value`, 95% HDI = `r coefs$b_condition1_lp1$.ci`), with `r coefs$b_condition1_lp1$.rope` of its posterior samples overlapping with the ROPE.
-The interaction term between the second *Condition* contrast also contained zero ($\beta$ = `r coefs$b_condition2_lp1$.value`, 95% HDI = `r coefs$b_condition2_lp1$.ci`), and  `r coefs$b_condition1$.rope` of its posterior samples fell within the ROPE.
-The outcomes of this model provide strong to moderate evidence against differences in overall target looking time across conditions and across monolinguals and bilinguals.
-
-A comparison between models including *Age* ($\mathcal{M}_{4}$), *L1 vocabulary* ($\mathcal{M}_{5}$), and *Total vocabulary* ($\mathcal{M}_{6}$)---and their three-way and two-way interactions with *Group* and *Condition*---against model $\mathcal{M}_{3}$, which only included *Age* as a covariate is shown in @tbl-loos.
-Overall, all models performed equivalently, with the simplest model $\mathcal{M}_{3}$ showing slightly better performance.
-This suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account *L1 vocabulary*, or *Total vocabulary* sizes.
-
-Both younger and older participants showed equivalent looking time across conditions, as suggested by the fact that the 95% HDI of the two-way interaction between *Age* and the first *Condition* contrast included zero ($\beta$ = `r coefs$fit_4$b_condition1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_age_std$ci_label`), as well as the interaction between *Age* and the second *Condition* contrast ($\beta$ = `r coefs$fit_4$b_condition2_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_age_std$ci_label`).
-This pattern of results was found in both monolinguals and bilinguals, as the 95% HDI of the three-way interaction between *Age*, *Group*, and *Condition* included zero both the first ($\beta$ = `r coefs$fit_4$b_condition1_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition1_lp1_age_std$ci_label`) and second ($\beta$ = `r coefs$fit_4$b_condition2_lp1_age_std$mdn_label`, 95% HDI = `r coefs$fit_4$b_condition2_lp1_age_std$ci_label`) contrast of *Condition*.
-
-### Time course of target looking
-
 ```{r timecourse}
@@
 #| label: fig-epreds
-#| fig-cap: "Margin posterior mean predictions.
+#| fig-cap: "Marginal posterior mean predictions.
 A) Posterior mean predictions of the time course of target fixation in the test phase.
 B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
-Lines and intervals indicate the mean and 95% credible interval of the posterior predictions."
+Lines and intervals indicate the mean and 95% credible interval of the posterior predictions.
+Red lines indicate the region of practial equivalence (ROPE)."
 #| fig-width: 8
@@
 			   	.multi_line = FALSE)) +
-	annotate(geom = "rect",
-			 xmin = timebin_values[1],
-			 xmax = timebin_values[length(timebin_values)],
-			 ymin = rope_interval[1],
-			 ymax = rope_interval[2],
+	# annotate(geom = "rect",
+	# 		 xmin = timebin_values[1],
+	# 		 xmax = timebin_values[length(timebin_values)],
+	# 		 ymin = rope_interval[1],
+	# 		 ymax = rope_interval[2],
+	# 		 fill = "red",
+	# 		 linewidth = 0,
+	# 		 alpha = 1/2,
+	# 		 linetype = "dotted") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
 				 fill = "grey",
-			 linewidth = 0,
-			 alpha = 1/2,
+				 linewidth = NA,
+				 alpha = 1/3) +
+	stat_summary(aes(group = diff),
+				 fun = mean,
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = rope_interval[1],
+			   colour = "red",
+			   linetype = "dotted") +
+	geom_hline(yintercept = rope_interval[2],
+			   colour = "red",
 			   linetype = "dotted") +
@@
 	# 		  linetype = "solid") +
-	stat_summary(fun.data = mean_qi,
-				 geom = "ribbon",
-				 fill = clrs[1],
-				 linewidth = NA,
-				 alpha = 1/3) +
-	stat_summary(aes(group = diff),
-				 fun = mean,
-				 geom = "line",
-				 colour = clrs[1],
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0,
-			   colour = "grey") +
+
 	labs(x = "Time (ms)",
@@
 
+### The role of age and vocabulary size on priming effects
+
+A comparison between models including *Age* ($\mathcal{M}_{1}$), *L1 vocabulary* ($\mathcal{M}_{2}$), and *Total vocabulary* ($\mathcal{M}_{3}$) against model $\mathcal{M}_{0}$, which only included *Age* as a main effect is shown in @tbl-loos.
+Overall, all models performed equivalently, with the model $\mathcal{M}_{2}$ showing slightly better performance.
+The equivalent performance of all models suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account *L1 vocabulary*, or *Total vocabulary* sizes.
+We now report the median and 95% HDI of the coefficients of $\mathcal{M}_{2}$, the best-fitting model.
+
+```{r tbl-loos}
+#| label: tbl-loos
+#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of models 0 to 3, and 3 to 6 in Study 1."
+get_loos <- function(x, y) {
+	out <- lst(m_0 = x, m_1 = y) |> 
+		loo_compare() |> 
+		as.data.frame() |> 
+		rownames_to_column("model") |>
+		arrange(model) |> 
+		select(model, elpd_diff, se_diff) |> 
+		mutate(diff_label = sprintf("%.3f", elpd_diff),
+			   se_label = sprintf("%.3f", se_diff))
+	return(out)
+}
+
+loo_compare(model_loos_bcn[4:7]) |> 
+	as.data.frame() |> 
+	rownames_to_column("model") |> 
+	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model))-3),
+		   across(matches("diff"),
+		   	   \(x) {x[1] <- NA; return(x)}),
+		   model = case_when(model=="Model 1" ~ "Model 1 (Age)",
+		   				  model=="Model 2" ~ "Model 2 (L1 vocabulary)",
+		   				  model=="Model 3" ~ "Model 3 (Total vocabulary)",
+		   				  .default = model)) |> 
+	select(model, matches("elpd|diff")) |> 
+	relocate(matches("diff"), .after = matches("loo")) |> 
+	gt(rowname_col = "model") |> 
+	fmt_number(is.numeric) |> 
+	cols_label(elpd_diff = "ELPD (diff.)",
+			   se_diff = "SE ELPD (diff)",
+			   elpd_loo = "ELPD",
+			   se_elpd_loo = "SE ELPD") |> 
+	fmt_missing(missing_text = "---") |> 
+	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new dataset.
+*SE \\(ELPD\\)*: standard error of the *ELPD*, which indictes the uncertainty about the predictive performance for unknown future data.
+*ELPD (diff)*: pairwise difference in *ELPD* for two models.
+The difference is computed relative to the model with lowest *ELPD* (best fitting model).
+*SE ELPD (diff.)*: standard error of component-wise differences of *ELPD* between two models.")) |>
+	tab_style(cell_text(style = "italic"), cells_column_labels())
+```
+
+### Word recognition times
+
 ```{r recognition}
@@
 
-In an exploratory analysis, we compared the model-estimated time points at which participants' gaze behaviour showed evidence of target looking above chance level (50%).
+In an exploratory analysis, we compared the model-estimated time points at which participants' gaze behaviour showed evidence of target looking above chance level.
 We defined the recognition time of the trial as the earliest time point at which the lower bound of the 95% HDI posterior mean prediction of the target looking excluded zero.
@@
 
-In Study 1, we adapted an implicit naming paradigm to investigate the potential role of within- and cross-language phonological priming in 21- to 32-month-old children.
-Both the overall target looking and its course time across the trial suggested strong word recognition, regardless of priming condition, participant language profile and age.
+In Study 1, we adapted an implicit naming paradigm to investigate the potential role of within- and cross-language phonological priming in 20- to 32-month-old children.
+Both the overall target looking and its time course across the trial suggested robust word recognition between 550 ms and 700 ms after the onset of the test phase, regardless of priming condition, participant language profile and age.
 Overall, participants' performance was equivalent across all priming conditions.
-An exploratory analyses on word recognition times suggested a complex pattern of results, showing an age effect---in which older participants looked at the target above chance earlier than younger infants---and a weak interaction between priming conditions, age, and language group.
+An exploratory analyses on word recognition times suggested a complex pattern of results, showing an age effect---in which older participants looked at the target above chance earlier than younger infants---and a marginal interaction between priming conditions, age, and language group.
+Overall, we did not find evidence of phonological priming within or across languages.
+
 These results conflict with previous findings in several ways.
-
-First, previous investigations using implicit naming paradigm had provided strong evidence in favour of infants and toddlers generating internal labels when presented with pictures of familiar objects.
+First, previous investigations using implicit naming paradigms had found evidence of infants and toddlers generating internal labels when presented with pictures of familiar objects.
 @mani2010infant and @mani2011phonological reported priming effects in 18 and 24-month-old infants.
-In primed trials, participants' target looking preference was influenced by the previous presentation of a phonologically related referent in silence.
+In primed trials, participants' target looking preference was influenced by the prior presentation of a phonologically related referent in silence.
 In control trials---in which prime and target labels were unrelated---no priming effect was found.
@@
 
-Both @mani2010infant and @mani2011phonological, and the present study share a similar design, but sampled different children populations.
-Participants in Mani and Plunkett's studies were raised in English speaking households in Oxford, while participants in the present study were learning Catalan or Spanish, if not a combination of both.
+Both @mani2010infant and @mani2011phonological, and the present study, share a similar design, but sampled different populations.
+Participants in Mani and Plunkett's studies were raised in English speaking households in Oxford (United Kingdom), while participants in the present study were learning Catalan or Spanish, if not a combination of both in Spain.
 We identify two ways in which this might have influenced the results.
-One is that the stimuli lists in Catalan and Spanish might have differed in some critical dimension, which interfered infants' ability to generate implicit labels for prime pictures.
+One is that the stimuli lists in Catalan and Spanish might have differed in some critical dimension to the English stimuli from Mani and Plunkett.
+This might have interfered infants' ability to generate implicit labels for prime pictures.
 For example, words in the present study were predominantly bi-syllabic, while those from Mani and Plunkett's studies were mostly monosyllabic, and contained less phonemes on average.
@@
 Given that `r scales::percent(doe_mon_exp$n[1] / doe_mon_exp$n[2], accuracy = 0.01)`
-of monolinguals in Barcelona were also exposed to a second language, they might as well been affected by such delay in implicit naming trajectories.
+of monolinguals in Barcelona were exposed to a second language (although less than 20% of the time), they might as well been affected by such delay in implicit naming trajectories.
 
@@
 It may be the case that infants in the present study faced a more challenging task, having to internally retrieve phonological forms without any auditory prompt like the one provided by priming through translation studies.
-
-Finally, another possibility is that participants in the present study did in fact general prime labels, but such labels did not interfere over target recognition.
+Another possibility is that participants in the present study did in fact general prime labels, but such labels did not interfere over target recognition.
 This could be because they were not phonologically specified enough.
-This is unlikely, as previous studies have shown strong evidence of fine phonological representations in the early lexicon REFERENCE.
-Instead, it could be the case that the prime labels were activated, but phonological links between lexical representations are still weak or not present, so that priming effects are not possible until later in age.
-To our knowledge, this study is the first one to test bilingual children at this age on implicit naming paradigms, so evidence of priming is not present at the moment.
-
-We found no differences between models including participants' age or any of the two indices of vocabulary size (L1 and total vocabulary size) as predictors.
-Previous studies suggest that same-language vocabulary size predicts better bilingual infants' performance in word recognition tasks, as compared to cross-language vocabulary size [@marchman2010vocabulary].
-
-In summary, the possibly increased difficulty of the task induced by the properties of the stimuli, together with differences in task design and populations might have contributed to the null pattern of results shown in Study 1.
-Given the complexity of the picture drawn by these factors, we conducted a second study with the aim of replicating the original findings by @mani2010infant and @mani2011phonological.
+This is unlikely in the light of previous work on implicit naming and mispronunciation perception.
+First, @duta2012erp and @styles2015infant had shown electrophysiological evidence of implicit naming in English learning infants as young as 14 months of age.
+Second abundant studies have shown that early lexical representations are encoded in high phonological detail, in both monolinguals and bilinguals [@swingley2000spoken; @bailey2002phonological; @tamasi2016measuring; @tamasi2017pupillometry; @ramon2009vowel].
+It could be the case then, that participants in the present study retrieved prime phonological representations, but phonological links between lexical representations are still weak or not present, so that priming effects are not possible until later in age.
+
+In summary, the possibly higher difficulty of the task induced by the properties of the stimuli, together with differences in task design and populations might have contributed to the null pattern of results shown in Study 1.
+Given the complexity of the picture drawn by these factors, we conducted a second study with the aim of replicating the original findings by @mani2010infant and @mani2011phonological in English monolinguals.
 If phonological priming effects are observed in a same-aged population using the adaptation of the task from Study 1, this would provide evidence in favour of cross-language differences in the developmental trajectories of implicit naming.
@@
 In this study, we conducted a conceptual replication of @mani2010infant and @mani2011phonological.
-Using the same task from Study 1, we tested a same-aged group of monolinguals being exclusively raised in British English speaking homes, the same population tested in the original studies.
-As in Study 1, we manipulated the phonological relationship between the prime and target labels at word onset, as well as the cognate status of the prime label.
-Evidence from implicit naming of prime images would be revealed by differences in target looking or its time course across the trials between *Unrelated* trials, and *Related/Non-cognate* and *Related/Cognate* trials.
-Given that participants in this study are monolinguals---and contrary to the monolinguals in Barcelona, have received no exposure to any other language---we would not expect the cognate status of the prime labels to exert any effect on subsequent target recognition.
+Using the same task from Study 1, we tested a group of monolinguals aged 20 to 32 months being exclusively raised in British English speaking homes, the same population tested in the original studies.
+For consistency with Study 1, we also manipulated the phonological relationship between the prime and target labels at word onset, as well as the cognate status of the prime label.
+Evidence from implicit naming of prime images would be revealed by differences in target looking or its time course across the trials between *Unrelated* trials and *Related/Non-cognate*, and between *Related/Non-cognate* and *Related/Cognate* trials.
+Given that participants in this study are monolinguals---and contrary to the monolinguals in Barcelona, have received no exposure to any other language---we should not find the cognate status of the prime labels to exert any effect on subsequent target recognition.
 
@@
 
-```
-
-We collected data from `r n_participants_total` children (`r n_participants_sex$n[1]` female, `r n_participants_sex$n[2]` male, `r n_participants_sex$n[3]` sex not reported, age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]), living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford.
+suppressWarnings({
+	time_diffs <- participants_oxf |>
+		arrange(child_id, session_id, age) |>
+		mutate(n_session = 1:n()) |>
+		select(child_id, session_id, session_n, age) |> 
+		filter(child_id %in% participants_oxf$child_id[duplicated(participants_oxf$child_id)]) |>
+		pivot_wider(id_cols = child_id, 
+					names_from = session_n, 
+					values_from = age, 
+					names_repair = janitor::make_clean_names) |> 
+		rowwise() |>
+		mutate(diff_min = x2-x1) |> 
+		ungroup() |> 
+		summarise(diff_min = min(diff_min, na.rm = TRUE))
+})
+
+```
+
+We collected data from `r n_participants_total` children (`r n_participants_sex$n[1]` female, `r n_participants_sex$n[2]` male, with `r english::words(n_participants_sex$n[3])` additional participants' sex not being reported; Age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]), living in the Oxfordshire area (United Kingdom).
+Participants were tested at the Oxford BabyLab at the University of Oxford.
 Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
 From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, and `r n_participants_sessions$session_2` participated twice.
-Recurrent participants were tested with at least XXX months of difference.
+Recurrent participants were tested with at least `r round(time_diffs, 2)$diff_min` months of difference.
 We gathered a total of `r n_sessions_total$n` testing sessions.
 All participants were being raised in exclusively British English monolingual homes.
-
-### Vocabulary size
 
@@
 #| label: fig-vocabulary-oxf
-#| fig-cap: "Participant vocabulary sizes across ages and language profiles.
-Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
-Vocabulary size scores from the recurrent participants are shown linked."
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores from the recurrent participants are shown linked."
 #| fig-width: 4
@@
 
-Same as in Study 1, but removing the *Group* predictor from the models, as only monolingual infants were tested.
+Same as in Study 1, but removing the *Group* predictor from the models, given that only monolingual infants were tested.
 
@@
 						  	distinct(child_id, .keep_all = TRUE) |> 
-						  	pull(is_valid_participant))
+						  	pull(is_valid_participant), na.rm = TRUE)
 
@@
 
-We defined a time windows of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
-To avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
-Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
-
 We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
 We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
+We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
 
@@
 
-```{r tbl-loos-oxf}
-#| label: tbl-loos-oxf
-#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 2."
-loos_03 <- loo_compare(model_loos_oxf[1:2]) |> 
-	as.data.frame() |> 
-	rownames_to_column("model") |> 
-	mutate(model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model))),
-		   across(matches("diff"),
-		   	   \(x) {x[1] <- NA; return(x)}))
-
-loos_36 <- loo_compare(model_loos_oxf[2:4]) |> 
-	as.data.frame() |> 
-	rownames_to_column("model") |> 
-	mutate(model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model))),
-		   across(matches("diff"),
-		   	   \(x) {x[1] <- NA; return(x)}))
-
-bind_rows("Base models" = loos_03,
-		  "Age and vocabulary size models" = loos_36, 
-		  .id = "type") |> 
-	select(type, model, matches("elpd|diff")) |> 
-	relocate(matches("diff"), .after = matches("loo")) |> 
-	gt(rowname_col = "model", groupname_col = "type") |> 
-	fmt_number(is.numeric) |> 
-	cols_label(elpd_diff = "ELPD (diff.)",
-			   se_diff = "SE ELPD (diff)",
-			   elpd_loo = "ELPD",
-			   se_elpd_loo = "SE ELPD") |> 
-	fmt_missing(missing_text = "---") |> 
-	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new dataset.
-*SE \\(ELPD\\)*: standard error of the *ELPD*, which indictes the uncertainty about the predictive performance for unknown future data.
-*ELPD (diff)*: pairwise difference in *ELPD* for two models.
-The difference is computed relative to the model with highest *ELPD*.
-*SE ELPD (diff.)*: standard error of component-wise differences of *ELPD* between two models.")) |>
-	tab_style(cell_text(style = "italic"), cells_column_labels())
-```
-
-In line with the results in *Study 1*, including the *Condition* predictor increased the predictive performance of the model substantially, compared to a model including only the main effect of *Age* (see @tbl-loos-oxf).
-We now report the median and 95% highest density interval of each fixed regression coefficient in $\mathcal{M}_{1}$.
-Overall, the average participant' looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$b_intercept$.value`, 95% HDI = `r coefs$b_intercept$.ci`) and all of its posterior samples fell outside of the ROPE.
+### Priming effects
+
+```{r coefs-oxf}
+var_labels <- c("b_Intercept" = "Intercept",
+				"b_age_std" = "Age (+1 SD)",
+				"b_condition1" = "Condition (U vs. RN)",
+				"b_condition2" = "Condition (RN vs. RC)")
+
+model_summary <- get_posterior_summary(model_fits_oxf$fit_oxf_1,
+									   data_bcn,
+									   vars_dict = var_labels,
+									   rope_interval = rope_interval)
+
+coefs <- model_summary |> 
+	mutate(.value = sprintf("%.3f", .value),
+		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
+		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
+	split(janitor::make_clean_names(model_summary$.variable))
+```
+
+Overall, the average participant' target looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$b_intercept$.value`, 95% HDI = `r coefs$b_intercept$.ci`) and all of its posterior samples fell outside of the ROPE.
 The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$b_age_std$.value`, 95% HDI = `r coefs$b_age_std$.ci`), and overlapped completely with the ROPE, indicating that participants from all ages showed equivalent overall target word recognition.
@@
 #| echo: false
+#| eval: false
 #| message: false
@@
 #| out-width: 80%
-var_labels <- c("b_Intercept" = "Intercept",
-				"b_age_std" = "Age (+1 SD)",
-				"b_condition1" = "Condition (U vs. RN)",
-				"b_condition2" = "Condition (RN vs. RC)")
-
-model_summary <- get_posterior_summary(model_fits_oxf$fit_oxf_1,
-									   data_bcn,
-									   vars_dict = var_labels,
-									   rope_interval = rope_interval)
-
-coefs <- model_summary |> 
-	mutate(.value = sprintf("%.3f", .value),
-		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
-		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
-	split(janitor::make_clean_names(model_summary$.variable))
 
@@
 
-@tbl-loos-oxf shows a comparison between models including *Age* ($\mathcal{M}_{2}$), and *L1 vocabulary* ($\mathcal{M}_{3}$)---and their two-way and two-way interaction with *Condition*---against model $\mathcal{M}_{1}$, which only included *Age* as a covariate suggested that all models performed equivalently, with model $\mathcal{M}_{2}$ showing a slightly better performance.
-Overall, this suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account *L1 vocabulary*, or *Total vocabulary* sizes.
-
 ```{r timecourse-oxf}
@@
 
-An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
+An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds-oxf).
 Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
@@
 plot_diffs <- epreds_diff |> 
-	ungroup() |> 
 	ggplot(aes(timebin_std, .epred)) +
 	facet_wrap(~diff) +
-	annotate(geom = "rect",
-			 xmin = timebin_values[1],
-			 xmax = timebin_values[length(timebin_values)],
-			 ymin = rope_interval[1],
-			 ymax = rope_interval[2],
+	# annotate(geom = "rect",
+	# 		 xmin = timebin_values[1],
+	# 		 xmax = timebin_values[length(timebin_values)],
+	# 		 ymin = rope_interval[1],
+	# 		 ymax = rope_interval[2],
+	# 		 fill = "red",
+	# 		 linewidth = 0,
+	# 		 alpha = 1/2,
+	# 		 linetype = "dotted") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
 				 fill = "grey",
-			 linewidth = 0,
-			 alpha = 1/2,
+				 linewidth = NA,
+				 alpha = 1/3) +
+	stat_summary(aes(group = diff),
+				 fun = mean,
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = rope_interval[1],
+			   colour = "red",
 			   linetype = "dotted") +
-	geom_hline(yintercept = 0,
-			   colour = "grey") +
+	geom_hline(yintercept = rope_interval[2],
+			   colour = "red",
+			   linetype = "dotted") +
 	# geom_line(aes(group = interaction(diff, draw)),
@@
 	# 		  linetype = "solid") +
-	stat_summary(fun.data = mean_qi,
-				 geom = "ribbon",
-				 fill = clrs[1],
-				 linewidth = NA,
-				 alpha = 1/3) +
-	stat_summary(fun = mean,
-				 geom = "line",
-				 colour = clrs[1],
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0,
-			   colour = "grey") +
+
 	labs(x = "Time (ms)",
@@
 
+### The role of age and vocabulary size on priming effects
+
+@tbl-loos-oxf shows a comparison between models including *Age* ($\mathcal{M}_{2}$), and *L1 vocabulary* ($\mathcal{M}_{3}$)---and their two-way and two-way interaction with *Condition*---against model $\mathcal{M}_{1}$, which only included *Age* as a covariate suggested that all models performed equivalently, with model $\mathcal{M}_{2}$ showing a slightly better performance.
+Overall, this suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account *L1 vocabulary*, or *Total vocabulary* sizes.
+
+```{r tbl-loos-oxf}
+#| label: tbl-loos-oxf
+#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 2."
+loo_compare(model_loos_oxf[2:4]) |> 
+	as.data.frame() |> 
+	rownames_to_column("model") |> 
+	mutate(model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model))-1),
+		   across(matches("diff"),
+		   	   \(x) {x[1] <- NA; return(x)}),
+		   model = case_when(model=="Model 1" ~ "Model 1 (Age)",
+		   				  model=="Model 2" ~ "Model 2 (L1 vocabulary)",
+		   				  model=="Model 3" ~ "Model 3 (Total vocabulary)",
+		   				  .default = model)) |> 
+	select(model, matches("elpd|diff")) |> 
+	relocate(matches("diff"), .after = matches("loo")) |> 
+	gt(rowname_col = "model") |> 
+	fmt_number(is.numeric) |> 
+	cols_label(elpd_diff = "ELPD (diff.)",
+			   se_diff = "SE ELPD (diff)",
+			   elpd_loo = "ELPD",
+			   se_elpd_loo = "SE ELPD") |> 
+	fmt_missing(missing_text = "---") |> 
+	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new dataset.
+*SE \\(ELPD\\)*: standard error of the *ELPD*, which indictes the uncertainty about the predictive performance for unknown future data.
+*ELPD (diff)*: pairwise difference in *ELPD* for two models.
+The difference is computed relative to the model with lowest *ELPD* (best fitting model).
+*SE ELPD (diff.)*: standard error of component-wise differences of *ELPD* between two models.")) |>
+	tab_style(cell_text(style = "italic"), cells_column_labels())
+```
+
+### Word recognition times
+
 ```{r recognition-oxf}
@@
 
-epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_1, 
+epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_2, 
 						  re_formula = NA,
@@
 	mutate(over_chance = (over_chance * 
-						  	sd(data_bcn$timebin) +
-						  	mean(data_bcn$timebin))*100+300)
+						  	sd(data_oxf$timebin) +
+						  	mean(data_oxf$timebin))*100+300)
 
@@
 
-In an exploratory analysis, we compared the model-estimated time points at which participants' gaze behaviour showed evidence of target looking above chance level (50%).
-We defined the recognition time of the trial as the earliest time point at which the lower bound of the 95% HDI posterior mean prediction of the target looking excluded zero.
 As expected, the recognition times were on average shorter for older infants than for younger infants.
 Differences between conditions were larger in bilinguals than in monolinguals, especially in the older group.
-The recognition time for monolingual 20-month-olds was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+The recognition time for monolingual 20-month-olds was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
+In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
 
@@
 English monolingual participants from all ages showed an equivalent pattern of target looking across both related and unrelated trials.
-
 The absence of a phonological priming effect suggest that either English monolinguals did not generate implicit labels for the prime pictures presented in silence, or that if generated, such labels did not interact with the subsequent recognition of the target word.
-Both candidate explanations conflict with both Mani and Plunkett's studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects.
+Both candidate explanations conflict with both Mani and Plunkett's studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects [@duta2012erp; @styles2015infant].
 
 One of the main differences between the implicit naming paradigm used by @mani2010infant and the one in Studies 1 and 2 is the fact that target labels were auditorily presented before target and distractor pictures were presented on screen.
-Given that priming effects are very sensitive to the timing of the activation of the lexical presentation [@REFERENCES], we decided to shorten the time span between prime image naming and target label presentation by removing the pre-naming interval of the test phase, in which both target and distractor pictures are presented form a baseline time interval before the target label is auditorily presented.
+The rationale behind this decision was to minimise the amount of time elapsed between the presentation of the prime and target labels, in order to facilitate any potential priming effects.
 By presenting the auditory target label immediately after the offset of the prime picture, the internally generated prime phonological form would be more likely to affect the activation of the target lexical representation.
@@
 This visual exploration of the screen might have increased the cognitive load of the task, rendering the potential effect of phonological priming to a weaker, undetectable effect.
-
 Overall, the results from Study 2 support a more methodological explanation of the null pattern of results in Study 1, in which the lack of a phonological priming effect---both within and across languages---might be explained by differences in task design or replicability concerns.
@@
 In this paper, we investigated the developmental trajectories of cross-language co-activation in the developing lexicon.
-We tested a longitudinal an cross-sectional sample of 20-to-32 month olds in an implicit naming paradigm, in which we designed three trial types to manipulate the phonological overlap between the prime and target words within and across languages.
+We tested a large cohort of monolingual and bilingual toddlers in an implicit naming paradigm.
+We designed three experimental conditions to manipulate the phonological overlap between the prime and target words within and across languages.
 In *Unrelated* trials, prime and target were phonologically unrelated in both languages.
@@
 In *Related/Cognate* trials, the prime label was a cognate: prime and target labels shared phonological onset in both languages.
-In Study 1, we tested a cohort oh monolingual and bilingual infants learning Catalan, Spanish, or both, and found no phonological priming effect in monolinguals or bilinguals.
-In Study 2, we tested a cohort of English monolinguals, and found similar results.
+In Study 1, we tested a cohort of monolingual and bilingual infants learning Catalan, Spanish, or both, and found no phonological priming effect in monolinguals or bilinguals.
+In Study 2, we attempted to replicate the original findings by @mani2010infant in a same-aged English monolingual cohort, and found the same null pattern of results.
+
 To our knowledge this is the first study investigating cross-language priming using an implicit naming paradigm.
-Such paradigm presents a critical asset for studying bilingual lexical processing.
-Since the prime pictures are presented in silence, the task is exclusively complete in the dominant language of participants.
-This provides a monolingual situation in which differences in performance across experimental conditions that involve cross-linguistic interactions can be more easily associated to the experimental manipulation in a causal way [@grosjean1997bilingual].
-This contrast to other experimental paradigms in which participants are presented with---need to produce---items from both languages.
-Such covert manipulation of the similarity between stimuli from the two languages has allowed previous studies to provide strong support for the language-non selective account of lexical access e.g., [@costa2000cognate; @thierry2007brain; @von2014bilinguals].
-
-Previous studies have provided evidence of English monolingual infants 18-month-old and older being sensitive to phonological priming effects during auditory word recognition.
+This paradigm presents a critical asset for studying bilingual lexical processing: since the prime pictures are presented in silence, the task can be presented exclusively in the dominant language of participants.
+This provides a monolingual context in which differences in performance across experimental conditions that involve cross-linguistic interactions can be more easily associated to the experimental manipulation in a causal way [@grosjean1997bilingual].
+This contrasts with previously used experimental paradigms in which participants are presented with items from both languages.
+Such covert manipulation of the similarity between stimuli from the two languages has allowed previous studies to provide stronger support for the language-non selective account of lexical access than studies presenting an overtly bilingual task to participants [e.g., @costa2000cognate; @thierry2007brain; @von2014bilinguals].
+
+Previous studies had provided evidence of English monolingual infants 18-month-old and older being sensitive to phonological priming effects during auditory word recognition.
 @mani2010infant had shown a facilitation effect in word recognition when 18-month-olds were previously presented with a familiar picture whose label shared phonological onset with the target word.
@@
 The shift from facilitation to inhibition was interpreted as a shift from sub-lexical facilitation at the phonological level---in which target word recognition is facilitated by the prior activation of an overlapping set of phonological segments---to a lexical interference effect in which the activation of the lexical representation of the phonologically similar prime led to competition dynamics with the subsequently activated representation of the target word.
-The last conclusion was supported by the fact that the size of the interference effect was associated with the increase in participants' vocabulary size, and also with the cohort size of the prime label---primes belonging to a larger neighbourhood of phonologically related words were subject to stronger interference effects during the task
-
-Even earlier evidence of implicit naming was provided through ERP registering at 14 months of age.
+This last conclusion was supported by the fact that the size of the interference effect was associated with the increase in participants' vocabulary size, and also with the cohort size of the prime label---primes belonging to a larger neighbourhood of phonologically related words were subject to stronger interference effects during the task.
+
+Even earlier evidence of implicit naming had been provided through ERP measurements at 14 months of age.
 @duta2012erp presented name-known pictures in silence for one second.
@@
 
-The results in the present investigation are in strong contrast with the aforementioned studies. Both studies 1 and 2 conflict with implicit naming.
-
-Study 1 conflicts with cross-language studies. singh2014,
-
-@kuipers2015bilingualism compared ERP responses to picture-word pairs in English monolinguals and Welsh-English bilinguals where the words were either semantically related or unrelated to a pictured object.
-Although both studies tested 30-month-olds, the conclusions the authors reached do not fully agree.
-@singh2014one concluded that there is a discontinuity between adults and young children in the way the two lexicons interact, while @kuipers2010event and @kuipers2015bilingualism concluded that there are no differences in adults’ and toddlers’ lexical-semantic processing.
-
-The present study presents methodological contributions.
+As mentioned in the Discussion of Study 1, we consider three scenarios under which implicit naming might have occurred, in line with previous literature, but our design failed to capture it.
+First, it might be possible that infants in both Studies 1 and 2 implicitly generated phonological labels for the primes, but such labels lacked the phonological detail to interact with the subsequent recognition of a phonologically related target word.
+This is unlikely, given that both monolinguals and bilinguals have been shown to encode lexical representations with high phonological detail from early ages [@swingley2000spoken; @bailey2002phonological; @tamasi2016measuring; @tamasi2017pupillometry; @ramon2009vowel].
+A second possibility is that participants successfully retrieved the phonological form of the prime labels, but such forms failed to interact with target recognition.
+This would be explained by the lack of strong associations between phonologically related lexical representations at these ages.
+But even if one considers the possibility that participants in Study 1 failed to show priming effects for this reason (for instance, the emergence of phonological associations might follow different trajectories in Catalan-Spanish infants, compared to English infants), the fact that English monolingual infants in Study 2 failed to show such priming effects contradicts previous findings on the same population, reporting priming phonological priming effects in even younger infants [@mani2010infant; @mani2011phonological].
+Finally, it is possible that the adjustments carried out during the adaptation of the task might have reduce the chances of detecting the anticipated effects.
+The most critical difference between the original design of the implicit naming task by Mani and Plunkett and that of the present study is the absence of a pre-naming phase during the test phase.
+Prime and target were presented very close in time.
+The onset of the target occurred 1,550 ms after prime picture onset.
+It is possible that such time interval was too short for participants to retrieve the phonological label of the prime picture, so that the auditory presentation of the target disrupted prime lexical access.
+Further research should investigate the role of prime-target inter-stimulus interval on the time course of lexical access and selection in toddlers.
+
+The present study introduces several methodological contributions.
 First, the longitudinal design of the data collection provided a more suitable design for drawing conclusions about developmental change in word recognition trajectories, compared to studies that tested participants from a single age group [@floccia2020translation], or studies that with an exclusively cross-sectional design [@von2012language].
@@
 
-Why. Auditory presentation, implicit label generation but no priming
-
-rhyme vs onset
-
-word length
-
-Another possibility is that the current study lacked the appropriate statistical power to detect the effect sizes of interest.
-Reported differences in looking time associated to priming paradigms in the available literature in children are generally small.
-Despite the relatively larger sample size achieved in the present investigation, participant-level trajectories of target looking are highly variable, which might have increased the uncertainty of the models' estimates.
-
 The findings in the present investigation have important implications for current models of bilingual lexical development.
-For instance, recent accounts of bilingual words acquisition pointed to a facilitative role of phonological similarity between the two languages.
-A monograph by @floccia2018vocabulary provided evidence of a language distance effect, where bilinguals learning two languages sharing higher lexical similarity knew more words in their less dominant language than those learning two language with lower lexical similarity.
-Later work by @mitchell2022cognate, @siow2022effect, and @garcia-castro2023cognate provided evidence for a more direct facilitation effect of cognateness.
-Cognates are form-similar translation equivalents.
-Cognateness is suggested to facilitate word acquisition through parallel activation: the co-activation of translation equivalents in speech might lead to an faster accumulation of learning instances with words, which ultimately results in an earlier age of acquisition.
-In the present study, we failed to observed cross-language effects during word recognition.
+Recent accounts of bilingual word acquisition pointed to a facilitative role of phonological similarity between the two languages.
+The findings reported by @floccia2018vocabulary pointed to a language distance effect, in which bilinguals learning two lexically similar languages (sharing more cognates) knew more words in their less dominant language than those learning two language with lower lexical similarity.
+Later work by @mitchell2022cognates, @siow2022effect, and @garcia2023cognate provided evidence for a more direct facilitation effect of cognateness.
+The main candidate mechanism behind the cognateness facilitation effect in word acquisition is parallel activation: the co-activation of form-similar translation equivalents during linguistic exposure might lead to a faster accumulation of learning instances for cognate words, which ultimately results in an earlier age of acquisition.
+In the present study, we provide evidence against such cross-language effects during word recognition.
 These outcomes are not in line with parallel activation taking place during speech exposure in bilinguals.
 It is possible that the mechanisms involved in the cognate facilitation in bilingual word acquisition are not captured by the task used in the present study.
-Implicit naming might be tapping into lower-level functions, more related to acoustic and phonological processing, while word acquisition and learning might rely on more abstract sources of information that do recruit parallel activation.
-
-recent work using parental reports of word acquisition have provided insights.
-For instance, previous work on lexical acquisition has provided some insight into how  found that English-Spanish bilinguals' vocabulary in English was influenced by the words they had already acquired in Spanish.
-This is consistent with previous accounts of lexical acquisition in which infants acquire new words through preferential acquisition [@hills2009longitudinal, @fourtassi2020growth].
-
-One of the limitations of this study lies in the use of cognates as prime words.
-
-Conclusions
+The implicit naming task used in the present investigation might be tapping into lower-level functions, related to acoustic and phonological processing, that are related to---but not critical for---word acquisition.
+Future research should contemplate alternative mechanisms for the cognateness facilitation effect on bilingual lexical acquisition.
+
+In summary, we tested the language non-selective hypothesis of lexical access in bilingual toddlers using an implicit naming paradigm.
+In Study 1, we did not find evidence of within-language or cross-language priming effects, suggesting that participants might have not generated covert labels for the prime pictures presented in silence.
+In study 2, we attempted to replicated the original study showing evidence of implicit naming in younger infants, but found no evidence of such effects: monolingual infants did not show evidence of implicit naming.
+Overall, our results allude to more complex state of the investigation about early priming effects than ancitipated from the literature.
 

### 2023-11-13 R/models.R

@@ -150,7 +150,7 @@ fit_single_model <- function(name, formula, data, prior, ...) {
 				   chains = 4L,
 				   cores = 4L,
 				   init = 0.1,
-				   file_refit = "on_change",
+				   file_refit = "never",
 				   file = model_path,
 				   seed = 1234,
 				   control = model_opts,

### 2023-11-17 manuscript/manuscript.qmd
Merge

@@
 stimuli |> 
-	summarise(across(c(matches("familiarity_|freq_|animate_"), duration),
-					 tibble::lst(mean, sd, min, max)),
-			  .by = c(test_language, trial_type)) |> 
-	select(-matches("familiarity_se"), -matches("prime"),
-		   -c(is_animate_target_sd,
-		      is_animate_target_min,
-		      is_animate_target_max),
-		   -matches("min"), -matches("max")) |> 
-	gt(groupname_col = "test_language",
-	   rowname_col = "list") |> 
-	fmt_number(is.numeric,
-			   decimals = 1) |> 
-	fmt_number(matches("familiarity|animate"),
-			   scale_by = 100,
-			   decimals = 1) |> 
+	unnest_wider(c(freq, nphon)) |> 
+	filter(test_language != "English") |> 
+	summarise(across(c(matches("n_phon|freq_|lv_|nphon"), duration),
+					 list(mean = \(x) mean(x, na.rm = TRUE),
+					 	 sd = \(x) sd(x, na.rm = TRUE))),
+			  .by = c(trial_type)) |> 
+	select(-matches("distractor")) |> 
+	gt(rowname_col = "trial_type",
+	   groupname_col = "test_language") |> 
+	# summary_rows(groups = c("Unrelated", "Non-cognate", "Cognate"),
+	# 			 columns = is.numeric,
+	# 			 fns = list(Total ~ mean(.)),
+	# 			 fmt = ~ fmt_number(., decimals = 2)) |> 
+	grand_summary_rows(columns = is.numeric,
+					   fns = list(Total ~ mean(.)),
+					   fmt = ~ fmt_number(., decimals = 2)) |> 
+	tab_spanner("Phonemes", matches("nphon")) |> 
+	tab_spanner("Frequency (Zipf)", matches("freq")) |> 
+	tab_spanner("Phon. similarity [0-1]", matches("lv")) |>
+	fmt_number(is.numeric, decimals = 1) |> 
+	cols_merge(c(freq_prime_mean, freq_prime_sd),
+			   pattern = "{1} ({2})") |> 
 	cols_merge(c(freq_target_mean, freq_target_sd),
 			   pattern = "{1} ({2})") |>
-	cols_merge(c(familiarity_target_mean, familiarity_target_sd),
+	cols_merge(c(nphon_prime_mean, nphon_prime_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(nphon_target_mean, nphon_target_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(lv_pp_mean, lv_pp_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(lv_pt_mean, lv_pt_sd),
 			   pattern = "{1} ({2})") |> 
@@
 	cols_label(trial_type = "",
-			   familiarity_target_mean = "Prevalence (%)",
-			   freq_target_mean = "Frequency",
-			   is_animate_target_mean = "Animacy (%)",
-			   duration_mean = "Duration (s)") 
+			   freq_prime_mean = "Prime",
+			   freq_target_mean = "Target",
+			   lv_pp_mean = "Prime-Prime",
+			   lv_pt_mean = "Prime-Target",
+			   duration_mean = "Audio duration (s)",
+			   nphon_prime_mean = "Prime",
+			   nphon_target_mean = "Target") |> 
+	tab_style(cell_text(style = "italic"),
+			  list(cells_column_labels(),
+			    cells_column_spanners(),
+			    cells_grand_summary()))
 ```
@@
 Audio and picture processing were performed following the same workflow as in Study 1.
+@tbl-stimuli-oxf shows a detailed summary of the properties of the English stimuli in Study 2.
+
+```{r tbl-stimuli-oxf}
+#| label: tbl-stimuli-oxf
+#| tbl-cap: "Summary of stimuli properties by trial type."
+stimuli |> 
+	unnest_wider(c(freq, nphon)) |> 
+	filter(test_language == "English") |> 
+	summarise(across(c(matches("n_phon|freq_|lv_|nphon"), duration),
+					 list(mean = \(x) mean(x, na.rm = TRUE),
+					 	 sd = \(x) sd(x, na.rm = TRUE))),
+			  .by = c(trial_type)) |> 
+	select(-matches("distractor")) |> 
+	gt(rowname_col = "trial_type",
+	   groupname_col = "test_language") |> 
+	# summary_rows(groups = c("Unrelated", "Non-cognate", "Cognate"),
+	# 			 columns = is.numeric,
+	# 			 fns = list(Total ~ mean(.)),
+	# 			 fmt = ~ fmt_number(., decimals = 2)) |> 
+	grand_summary_rows(columns = is.numeric,
+					   fns = list(Total ~ mean(.)),
+					   fmt = ~ fmt_number(., decimals = 2)) |> 
+	tab_spanner("Phonemes", matches("nphon")) |> 
+	tab_spanner("Lexical frequency (Zipf)", matches("freq")) |> 
+	tab_spanner("Phonological similarity [0-1]", matches("lv")) |>
+	fmt_number(is.numeric, decimals = 1) |> 
+	cols_merge(c(freq_prime_mean, freq_prime_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(freq_target_mean, freq_target_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(nphon_prime_mean, nphon_prime_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(nphon_target_mean, nphon_target_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(lv_pp_mean, lv_pp_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(lv_pt_mean, lv_pt_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(duration_mean, duration_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_label(trial_type = "",
+			   freq_prime_mean = "Prime",
+			   freq_target_mean = "Target",
+			   lv_pp_mean = "Prime-Prime",
+			   lv_pt_mean = "Prime-Target",
+			   duration_mean = "Audio duration (s)",
+			   nphon_prime_mean = "Prime",
+			   nphon_target_mean = "Target") |> 
+		tab_style(cell_text(style = "italic"),
+			  list(cells_column_labels(),
+			    cells_column_spanners(),
+			    cells_grand_summary()))
+```
 

### 2023-11-17 R/models.R

@@ -7,9 +7,9 @@
 #' @param attrition_participants Data frame with participants-level inclusion criteria, as generated by [get_attrition_participants].
 #' @param time_subset Numeric vector of length 2 indicating the time window of interest to subset for time course analyses.
 #' 
-get_data <- function(gaze, participants, vocabulary,
+get_data <- function(gaze, participants, stimuli, vocabulary,
 					 attrition_trials, attrition_participants,
-					 time_subset = c(0.00, 2.00)){
+					 time_subset = c(0.00, 2.00)) {
 	
 	if (length(time_subset)!=2 || min(time_subset) < 0 || class(time_subset)!="numeric") {
 		cli_abort("time_subset must be a positive numeric vector of length 2")
@@ -24,11 +24,17 @@ get_data <- function(gaze, participants, vocabulary,
 			   timebin = findInterval(timestamp, seq(time_subset[1], 
 			   									  time_subset[2], 0.1))-1) 
 	
+	d_p <- select(participants, child_id, session_id, age_group, age, lp)
+	
+	d_s <- stimuli |> 
+		unnest_wider(freq) |> 
+		select(trial, test_language, version, list,
+			   trial_type, target, freq = freq_target) 
+		
 	d_v <- rename_with(vocabulary,  
 					   \(x) gsub("_prop", "", paste0("voc_", x)), 
 					   matches("_prop"))
 	
-	d_p <- select(participants, child_id, session_id, age_group, age, lp)
 	
 	d_at <- filter(attrition_trials, is_valid_trial) |> 
 		select(session_id, trial, samples, is_valid_trial) 
@@ -64,7 +70,7 @@ get_data <- function(gaze, participants, vocabulary,
 			   across(c(age, matches("voc_"), timebin),
 			   	   \(x) scale(x, scale = TRUE)[, 1],
 			   	   .names = "{.col}_std")) |> 
-		select(child_id, session_id, age_group, age, voc_l1, voc_total, lp,
+		select(child_id, session_id, age_group, age, lp, voc_l1, voc_total,
 			   condition, timebin, .sum_t, .sum_d, .prop, .elog, .nsamples,
 			   matches("_std")) 
 	
@@ -146,11 +152,11 @@ fit_single_model <- function(name, formula, data, prior, ...) {
 		fit <- brm(formula = formula,
 				   data = data,
 				   prior = prior,
-				   iter = 1e3L,
-				   chains = 4L,
+				   iter = 2e3L,
[…]

### 2023-11-17 R/stimuli.R

@@ -2,7 +2,7 @@
 get_audio_duration <- function(trials) {
 	
 	# get dir paths and validate paths
-	audio.dir <- paste0("stimuli/sounds/sounds_", c("cat", "spa")) 
+	audio.dir <- paste0("stimuli/sounds/sounds_", c("cat", "eng", "spa")) 
 	audio.dir.valid <- dir.exists(audio.dir)
 	
 	if (!all(audio.dir.valid))  {
@@ -17,13 +17,14 @@ get_audio_duration <- function(trials) {
 	durations <- tibble::tibble(audio_path = audio.paths, 
 								duration = durations.vctr)
 	durations$audio <- basename(audio.paths)
-	durations$test_language <- ifelse(grepl("sounds_cat", audio.paths),
-									  "Catalan",
-									  "Spanish")
+	durations$test_language <- case_when(grepl("_cat", audio.paths) ~ "Catalan",
+										 grepl("_spa", audio.paths) ~ "Spanish",
+										 grepl("_eng", audio.paths) ~ "English")
+	durations$duration <- ifelse(durations$test_language=="English",
+								 durations$duration-4, durations$duration)
 	
 	# merge with trials dataset
-	trials_tmp <- distinct(trials[trials$location=="Barcelona", ], 
-						   test_language, version, audio)
+	trials_tmp <- distinct(trials, test_language, version, audio)
 	trials_tmp$audio <- stringi::stri_trans_general(str = trials_tmp$audio, 
 													id = "Latin-ASCII")
 	duration <- inner_join(trials_tmp, durations,
@@ -76,7 +77,7 @@ get_familiarity <- function(
 }
 
 #' Get frequencies from CHILDES
-get_childes_corpora <- function(token, languages = c("cat", "spa")) {
+get_childes_corpora <- function(token, languages = c("eng")) {
 	
 	# if CHILDES exists, load
 	childes.path <- file.path("data-raw", "childes.csv")
@@ -108,7 +109,7 @@ get_childes_corpora <- function(token, languages = c("cat", "spa")) {
 # WARNING: especial characters are not being handled very well
 get_frequency_childes <- function(childes,
 								  token, # word(s) form to look up, e.g. c("table", "mesa")
-								  languages = c("cat", "spa"), # languages in which to look up the word form 
+								  languages = c("eng"), # languages in which to look up the word form 
 								  ... # passed to childesr::get_speaker_statistics)
[…]

### 2023-11-17 R/vocabulary.R

@@ -1,14 +1,11 @@
 #' Get vocabulary data
-get_vocabulary <- function(participants, 
-						   bvq_data, 
+get_vocabulary <- function(participants, bvq_data, 
 						   vocabulary_supp_bcn_file,
 						   vocabulary_file_oxf,
-						   cdi_file_oxf) {
+						   words) {
 	
 	vocab_bcn <- get_vocabulary_bcn(participants, bvq_data, vocabulary_supp_bcn_file)
-	vocab_oxf <- get_vocabulary_oxf(vocabulary_file_oxf,
-									participants,
-									cdi_file_oxf)
+	vocab_oxf <- get_vocabulary_oxf(vocabulary_file_oxf, participants, words)
 	
 	out <- bind_rows(vocab_bcn, vocab_oxf)
 	
@@ -155,16 +152,16 @@ impute_vocabulary <- function(x,
 # Oxford functions -------------------------------------------------------------
 
 #' Import and process vocabulary data
-get_vocabulary_oxf <- function(vocabulary_file,	participants,cdi_file_oxf) {
+get_vocabulary_oxf <- function(vocabulary_file,	participants, words) {
 	
 	participants_tmp <- participants |> 
 		filter(location=="Oxford") |> 
 		select(matches("_id"))
 	
-	stimuli_cdi_oxf <- read_csv(cdi_file_oxf,
-								show_col_types = FALSE,
-								na = c("", NA)) |> 
-		pivot_longer(matches("item"),
+	stimuli_cdi_oxf <- words |> 
+		rename(vocab_item = item,
+			   vocab_item_supp = item_supp) |> 
+		pivot_longer(matches("vocab_item"),
 					 names_to = "version",
 					 values_to = "item_cdi") |> 
 		group_split(version) |> 
@@ -203,7 +200,6 @@ get_vocabulary_oxf <- function(vocabulary_file,	participants,cdi_file_oxf) {
 				  contents = list(item[response]),
 				  .by = c(session_id)) |> 
 		select(session_id, total_prop, contents) 
-	
 	
 	out <- lst(cdi_full, cdi_extended, cdi_supplementary) |> 
 		bind_rows(.id = "version") |> 
@@ -251,9 +247,9 @@ get_cdi_full_oxf <- function(vocabulary_file) {
 						"quantifiers")
 	
 	out <- readxl::read_xlsx(vocabulary_file, 
-								  sheet = "CDI_full",
-								  .name_repair = janitor::make_clean_names,
[…]

### 2023-11-20 manuscript/manuscript.qmd
Remove unncessary files

--- 2023-11-13 manuscript/manuscript.qmd
@@
----
----
-
 ```{r setup}
@@
 library(gtExtras)
-library(marginaleffects)
 
@@
 This is a remarkable deed for two reasons.
-First, bilingual infants receive a relative impoverished quantitative linguistic input in each of their languages, compared to monolinguals [@costa2014does; @cattani2014much; @thordardottir2011relationship].
-Second, they face a more complex referential context, as they often learn two labels for each referent, one in each language [@au1990principle; @tsui2022translation; @bilson2015semantic; @de2006early].
+First, bilingual infants receive a relatively reduced linguistic input in each of their languages, compared to monolinguals [@costa2014does; @cattani2014much; @thordardottir2011relationship].
+Second, they face a more complex referential context: they often learn two labels for each referent (one in each language), which additionally may not be direct translations of each other [@au1990principle; @tsui2022translation; @bilson2015semantic; @de2006early].
 The mechanisms that allow bilingual' trajectories of lexical developmental to keep up with monolinguals' are still unclear.
 
-Previous studies have pointed to cross-language dynamics as a candidate mechanism boosting lexical acquisition in bilinguals [@floccia2018vocabulary; @blom2020cross; @gampe2021does].
-In particular, lexical similarity between the two languages has been associated with larger vocabulary sizes in bilingual toddlers.
-@floccia2018vocabulary collected parental reports of vocabulary data from a sample of 367 bilingual children living in the United Kingdom, who were learning English and an additional language (out of a diverse pool of 13 languages).
-The authors then used an edit distance-based metric of phonological similarity to compute the average lexical similarity between the translation pairs in English and each of the additional languages.
-English and Dutch shared the highest lexical similarity, while English and Mandarin shared the lowest.
-Children's vocabulary sizes in the additional language was positively associated with the amount of language similarity between their two languages.
-For instance, children learning English and Dutch showed larger vocabulary sizes than those learning English and Mandarin.
+Previous studies have pointed to the similarity between the two languages of exposure as a facilitator of lexical acquisition in bilinguals [@floccia2018vocabulary; @blom2020cross; @gampe2021does].
+@floccia2018vocabulary reported larger vocabulary sizes in bilingual toddlers leaning two languages that shared high lexical similarity.
+The authors collected parental reports of vocabulary data from a sample of 367 bilingual children living in the United Kingdom, who were learning English and an additional language (out of a diverse pool of 13 languages).
+The authors then calculated the average phonolexical similarity between English and each of the additional languages.
+English and Dutch shared the highest similarity, while English and Mandarin shared the lowest.
+Overall, children's vocabulary sizes in the additional language was positively associated with the amount of language similarity between their two languages.
+For instance, English-Dutch bilinguals showed larger vocabulary sizes in Dutch than English-Mandarin bilinguals did in Mandarin.
 The authors suggested that the acquisition of words in the additional language might be facilitated by their cognate status (i.e., being phonologically similar to their translation equivalent).
 If this is the case, larger vocabulary sizes might then be expected in bilinguals learning two languages sharing a high proportion of cognates.
-This would be consistent with available evidence of an earlier acquisition of cognate words [@bosch2014first; @mitchell2022cognates; @garcia2023cognate].
-
-The facilitative effect of cognateness is in line with the language non-selective account of bilingual lexical access.
-This account proposes that bilinguals activate both languages in parallel, even during monolingual situations, as suggested by robust experimental evidence [@marian1999activation; @groot1992determinants; @schwartz2007reading; @dijkstra1999recognition; @dufour1995matching; @dijkstra2010cross].
-For instance @costa2000cognate presented Catalan-Spanish bilinguals with a series of pictures of familiar objects.
-Participants were asked to name each picture in Catalan, their dominant language.
+This would be consistent with available evidence of an earlier acquisition of cognate words [@bosch2014first; @mitchell2022cognates; @garcia2023cognate; @schelletter2002effect].
+
+The facilitation effect of cognateness is in line with the language non-selective account of bilingual lexical access.
+This account proposes that bilinguals activate both languages in parallel, even during monolingual situations.
+In adults, there is robust evidence in favour of this language non-selective account of lexical access [@marian1999activation; @groot1992determinants; @schwartz2007reading; @dijkstra1999recognition; @dufour1995matching; @dijkstra2010cross; @spivey1999cross].
+@costa2000cognate presented highly-proficient Catalan-Spanish bilinguals with a series of pictures of familiar objects.
+Participants were asked to name each picture in Spanish.
 Unbeknownst to participants, the authors manipulated the cognate status pictures' labels in Catalan and Spanish.
-In half of the trials, the labels associated to the pictures were cognates (i.e., phonologically similar translation equivalents, e.g., *gat*-*gat* [*cat*]) in Catalan and Spanish, whereas in the other half of the trials the labels were non-cognates (e.g., *taula*-*mesa* [*table*]).
+In half of the trials, the labels associated to the pictures were cognates (e.g., *cat*-*gat* [cat]), whereas in the other half of the trials the labels were non-cognates (e.g., *taula*-*mesa* [table]).
 Participants named pictures faster in cognate trials than in non-cognate trials.
-Critically, Spanish monolinguals---who completed the same task in Spanish---showed equivalent naming times in both conditions.
-These results revealed that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the parallel activation of its associated phonological forms in both languages, which influenced the subsequent dynamics of word production.
+Spanish monolinguals showed equivalent naming times in both conditions.
+These results revealed that bilinguals activated their Catalan phonology, despite performing the naming task exclusively in Spanish: the visual recognition of the presented pictures led to the parallel activation of its associated phonological forms in both languages, which influenced the subsequent dynamics of word production.
 
 Parallel activation has also been reported in the developing lexicon [@poarch2012cross; @bosma2020cognate; @singh2014one; @jardak2019labels; @von2019impact; @floccia2020translation; @bosma2019longitudinal].
-For instance, @von2012language found suggestive evidence of cross-language phonological priming in a sample of 20 German-English bilinguals aged 21 to 43 months.
-In their experimental task, each trial begun with the auditory presentation of an English prime word, followed by a target German label and a pair of target and distractor pictures.
-The authors registered participants' target picture looking (interpreted as a proxy of target word recognition) under three conditions.
-In the *phonological priming* condition, the auditorily presented prime and target labels were phonologically related (e.g., *slide*-*Klide* [*dress*]).
-In the *priming through translation* condition, prime and target were phonologically related through translation: the auditorily presented prime label did *not* overlap with the target label (e.g., *leg*-*Stein* [*stone*]), but its German translation did [*Bein*].
-In the *unrelated* condition, prime and target labels were phonologically unrelated in both languages.
-Interestingly, participants showed a weaker target preference in priming through translation trials, compared to unrelated trials.
-This was interpreted evidence of the lexical representations of the prime labels being activated in both English and German, leading to interference effects in later target recognition.
-Previous studies had reported similar cross-language priming effects, but the conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was nonetheless unwarranted.
-In studies where the auditorily presented prime label was phonologically overlapped with the target label [e.g., @marian1999activation], priming effects could be explained by sub-lexical facilitation across phonological segments.
-This might explain the facilitation effect found in *phonological priming* trials in @von2012language, in which English prime and German target labels shared overt phonological overlap.
-In contrast, the interference effect found in *priming through translation* trials points to cross-language competition at the lexical level.
-Since participants' target recognition was modulated by the phonology of the German translation of the prime (which participants did *not* hear), cross-language priming can be explained by the lexical co-activation of the English *and* German prime labels.
-
-@von2012language extended the available knowledge on the developing bilingual lexicon, but some methodological challenges prevent drawing strong conclusions from their findings.
-First, bilingual participants' quantitative exposure to English as a second language was lower than what is conventionally considered as bilingualism [20-50% of cumulative exposure, @byers-heinlein2021multilab; @rocha-hidalgo2023defining]^[Except for four participants who were also exposed to English at home, participants in @von2012language received their English input exclusively at school from a German native speaker.
-Participants' exposure to each language ranged between three and four hours per day.
-This implies that participants' exposure to English consisted of an average of 3-4 hours per day, during the time they attended daycare (reported as an average 12.35 months).
-Assuming that infants were exposed to a daily average of 12 total hours of speech, and that they attended daycare five days per week, the estimated cumulative to English in the life of an average child in the sample was between `r scales::percent((3*5*4*12.35)/(12*7*4*21), accuracy = 0.01)` and `r scales::percent((4*5*4*12.35)/(12*7*4*21), accuracy = 0.01)` for the 21 month-olds (the youngest in the sample), and between `r scales::percent((3*5*4*12.35)/(12*7*4*43), accuracy = 0.01)` and `r scales::percent((4*5*4*12.35)/(12*7*4*43), accuracy = 0.01)` for the 43-month-olds.
-These percentages were calculated as:
-$$\frac{\text{Total English input}}{ \text{Total English + German input}} = \frac{3 \text{ or } 4 \text{ hours/day} \times 5 \text{ days/week } \times 4\text{ weeks/month }  \times 21 \text{ or } 43 \text{ months of age}}{12 \text{ hours/day} \times 7 \text{ days/week } \times 4\text{ weeks/month }  \times 21 \text{ or } 43 \text{ months of age}}$$.].
-Results should therefore be taken with caution when generalised to other populations of bilinguals.
-A second consideration is the presence of cognates in a substantial proportion of the trials in the *phonological priming* and *priming thorugh translation* conditions.
-Because of this, some prime labels in *phonological priming* trials shared substantial cross-language phonological overlap thought translation with the target words.
-Conversely, some trials in the *phonological priming through translation* shared within-language overlap with the target.
-Third, the observed pattern of results was dependent on the inclusion of a single item, *Buch* [*book*, in German].
-When this item was included, monolinguals showed a similar interference effect to bilinguals' in the *priming through translation* condition, in which only bilinguals with knowledge of the translation should show an effect.
-Fourth, data from monolinguals and bilinguals were not compared directly (analyses were conducted separately for both groups).
-Differences in statistical significance between monolinguals and bilinguals across conditions do not necessarily guarantee significant differences between the two groups.
-As a consequence, whether the interference effects observed in the *priming through translation* condition is exclusive to bilinguals (which would suggest that the priming effect were not due to the intrinsic properties of the stimuli) or not is unclear.
-In summary, evidence of cross-language activation at the lexical level in infants is, to date, inconclusive.
-
-In the present study, we use an extension of the implicit naming task [@mani2010infant; @mani2011phonological] to put the language non-selectivity in the developing lexicon to a more severe test.
-Previous studies have successfully used this task to investigate priming effects in word recognition in monolingual infants and bilingual adults.
-In the original implementation of the task, @mani2010infant primed infants with a picture presented in silence.
-At test, a target-distractor picture pair were presented side-by-side.
-Finally, the target picture's label was presented auditorily.
-The authors manipulated the phonological overlap between the prime and the target labels, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
-Prime and target-distractor pairs were semantically unrelated.
-Eighteen-month-old infants showed a stronger looking preference for the target picture after phonologically related prime pictures, compared to after phonologically unrelated primes.
-This suggests that infants implicitly named prime pictures despite such pictures having been presented in silence, and that the phonology of the resulting label interacted with the subsequent auditory recognition of the target label.
-
-@von2014bilinguals adapted this paradigm to investigate cross-language activation in bilingual adults.
-The authors presented German-English bilinguals with 120 prime-target pairs.
-Primes were presented as familiar pictures in silence.
-After prime picture offset, target words were presented auditorily.
-Participants' eletrophysiological response was recorded, and N400 evoked potentials to the auditory target label was measured.
-The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
-When prime and target were phonologically identical (*Affe*-*Affe*, German for *monkey*), or similar (*Fahne*-*Sahne*, German for *flag* and *ice-cream*, respectively) within L1, participants' showed a reduced N400 amplitude, compared to when prime and target were phonologically unrelated (*Messer*-*Seil*, German for *knife* and *rope*).
-Critically, a similar effect was found when prime and target were phonologically related through translation (*Rustsche*-*Kleid*, German for *slide* and *dress*).
-This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
-In summary, the implicit naming paradigm has been successful used in the past to investigate the emergence of phonological priming effects in monolingual infants, and to investigate cross-language priming effects in bilingual adults.
-
-The implicit naming paradigm provides several advantages over the priming through translation task.
-In the priming through translation task, primes and targets are auditorily presented in both languages in the same trial.
-This presents participants with a bilingual context that might lead to a higher baseline activation of lexical representations of both languages, contrary to a context in which parallel activation results from genuine cross-language activation [@grosjean1997bilingual].
-Also, when prime words are auditorily presented, the task imposes an asymmetry between the activation dynamics of the lexical representation of the prime in each language: while participants hear prime labels in one language, the activation of prime labels in the other must occur via cascaded activation across semantic links with their translations.
-This might lead to a lower strength, and higher latency of the activation of prime labels in one language, compared to the presented labels in the other.
-In contrast, the implicit naming paradigm provides participants with an exclusively monolingual context in which they perform the task in only one of their languages.
-At the same time, the silent presentation of prime pictures allows participants to activate prime labels in both languages in a truly parallel fashion.
-If differences in task performance are found associated with covert manipulation of cross-linguistic properties of prime labels, such differences may be more conclusively linked to the parallel activation of lexical representations in both languages.
-
-In the present investigation, we manipulated both the phonological overlap between the prime word and target word and the cognate status of the prime word, to test the whether bilingual toddlers implicitly name familiar pictures in both languages.
-If this is the case, phonological priming effects should be larger when the prime label in both languages shares phonological overlap with the target words (*Related/Cognate* condition), compared to when only the label of the prime in one language overlaps phonologically with the target (*Related/Non-cognate*).
-We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
-We registered participants' target looking during target-distractor presentation, and that, if within-language priming effects take place, differences in target looking between *Unrelated* and *Related/Non-cognate* trials should be observed, as previously reported [@von2012language, @mani2010infant; @mani2011phonological].
-We further predicted cross-language priming effects, revealed as differences in target looking between *Related/Non-cognate* and *Related/Cognate* trials.
-This effect should be stronger in bilinguals than monolinguals, if not completely absent in the latter, who should be indifferent to the phonological properties of the stimuli in the other language.
-
-Following previous studies associating the emergence of phonological links between lexical items to the size of children's vocabulary [@mani2011phonological; @chow2017spoken], we also compared the explanatory power of two indices of receptive vocabulary size against participants' age: dominant-language vocabulary size and total vocabulary size.
-If within-language or cross-language phonological associations in the lexicon emerge as a function of vocabulary growth, the size of the differences between conditions should larger in participants with larger vocabulary sizes.
-A model including participants' dominant-language or total vocabulary size as a predictor should then show better performance than a model that instead includes participants age.
-In the case of bilinguals, if the emergence of cross-language priming effects is associated with the growth of their vocabulary is *both* languages, a model including total vocabulary size as a predictor should perform better than a model that includes dominant-language vocabulary size.
-The opposite pattern would indicate that cross-language priming effects emerge as a function of the growth of dominant-language vocabulary.
-
-Testing bilingual populations at early ages presents the limitation that the vocabulary size of participants' non-dominant language is relatively small, which substantially constrains the number of items that can be used to as stimuli in the task, as well as the number of trials that can be constructed to generate stimuli lists.
-In order to circumvent the problem of limited vocabulary knowledge in the non-dominant language, tested participants only in their dominant language, therefore directing our research to the question of how possessing a second language affects processing of the dominant one in bilingual toddlers [@costa2014does provide a fuller description of the advantages of such approach].
+@von2012language found evidence of cross-language phonological priming in a sample of 20 German-English bilinguals aged 21 to 43 months.
+In their experimental task, each trial begun with the auditory presentation of an English prime word, followed by a target word in German, and a pair of target and distractor pictures.
+The authors recorded participants' target picture looking as a measure of target word recognition.
+The authors manipulated the cross-linguistic phonological overlap between the prime and the target labels.
+In a *priming through translation* condition, the English prime labels (leg) did not overlap with the German target labels (*Stein* [stone]), but with their German translations (*Bein*) did.
+In the *unrelated* condition, prime and target labels were not phonologically related in either German or English.
+If participants accessed their lexicon in a language non-selective way, the auditory presentation of the prime label in English should lead to the co-activation of its German translation.
+If this is the case, target word recognition should be interfered by the prior activation of a phonologically related German prime label.
+Under this hypothesis, the authors anticipated an delayed target looking in priming through translation trials, compared to unrelated trials.
+The results supported this hypothesis.
+In spite of the relevance of @von2012language study, some methodological issues deserve some consideration.
+First, for most participants, exposure to English (the less prevalent language) was lower than the minimal amount conventionally considered the threshold for bilingual exposure [@byers-heinlein2021multilab; @rocha-hidalgo2023defining].
+Second, some of the prime labels in the priming through translation condition were cognates.
+If both English and German labels overlap phonologically with the German target label, priming effects can be explained by interference between words from the same language, as opposed to cross-language interference.
+Third---and most critically---participants were exposed to both English and German word in a by-trial basis.
+This creates a context in which interference effects may not have arised from the competition between the prime translation and the target words, but between the target word and any other word in the other language.
+Paradigms in which the experimental task is conducted exclusively in one language, while cross-linguistic features are covertly manipulated, offer a methodologically stronger basis for studying language non-selectivity in the developing lexicon [@grosjean1997bilingual].
+
+@mani2010infant designed an implicit naming task, in which primes consisted of pictures presented in silence, instead of auditory labels.
+In each trial, English monolingual infants were first presented with pictures of familiar objects for 1,500 ms.
+Then, a target-distractor picture pair was presented for 2,000 ms, and then the auditory label of the target picture was presented.
+Post-naming target looking was recorded for another 2,000 ms until the end of the trial, as a measure of target word recognition.
+The authors manipulated the phonological overlap between the prime and the target labels, so that in half of the trials both labels were phonologically related, sharing phonological onset (cat-cup), or phonologically unrelated (ball-comb).
+Prime, target and distractor were unrelated otherwise.
+At 18 months of age, participants showed a stronger looking preference for the target pictures after phonologically related prime pictures, compared to after phonologically unrelated primes.
+Since the prime pictures were presented in silence, their results suggested that infants implicitly named the prime pictures, and that the phonology of the resulting word interacted with the subsequent recognition of the auditory target word.
+Later, @mani2011phonological tested 21-month-old infants in the same task.
+This time, priming effects were observed in the opposite direction: when prime and target labels were phonologically related, participants showed significantly weaker target looking preference, compared to unrelated trials.
+The size of this interference effect was associated to participants' vocabulary size, and to the cohort size of the prime label.
+The authors interpreted this finding as indicating a developmental shift.
+At 18 months, participants' word recognition might have experienced a sub-lexical facilitation effect, in which the prior activation of the shared phonological onset between the prime and target labels boosted word recognition.
+In older participants, the lexicon might have reached a critical size at which the recognition of the target was delayed by the activation of its phonological cohort.
+
+The implicit naming paradigm provides an ideal experimental paradigm study the developing bilingual lexicon.
+By covertly manipulating the cross-linguistic relationship between the prime and target labels, parallel activation can be tested while participants are presented with auditory stimuli (target labels) exclusively in one of their languages [see @von2014bilinguals for a similar approach in bilingual adults].
+Capitalizing on the language non-selective account of lexical access, we exploited the implicit naming to investigate the mechanisms behind the emergence of phonological priming effects in the bilingual developing lexicon.
+We tested a cohort of monolingual and bilingual infants learning Catalan and Spanish between 20 and 32 months of age.
+This allowed us to compare the performance of participants with differing vocabulary sizes in the word recognition task.
+In order to circumvent the problem of limited vocabulary knowledge in the non-dominant language, we tested participants only in their dominant language [@costa2014does].
+
+Following @mani2010infants, each trial in the task started with the silent presentation of a prime picture.
+Both monolingual and bilingual infants were expected to implicitly name the prime picture.
+According to the language non-selective hypothesis of lexical access, bilinguals should generate two labels for the prime picture, one in each language.
+To test this prediction, we manipulated the phonological similarity between the prime and the target words in both languages (see @fig-task).
+In *Related/Non-cognate* trials, prime and target labels shared phonological onset in only the language of test.
+For instance an infant tested in Catalan would be presented with a chair as prime picture ($\textbf{c}\text{adira}_{\text{CAT}}/\text{silla}_{\text{SPA}}$) and with $\textbf{c}\text{ullera}_{\text{CAT}}$ [spoon] as target label.
+In line with @mani2011phonological, we anticipated that the phonological overlap between prime and target should modulate target word recognition in both monolinguals and bilinguals.
+This should be reflected in a delayed target looking preference, compared to *Unrelated* trials, in which prime and target did not share phonological onset.
+In *Related/Cognate* trials, the prime shared phonological onset with the target in both languages.
+For instance, the same infants tested in Catalan would be presented with a car as prime picture ($\textbf{c}\text{otxe}_{\text{CAT}}/\textbf{c}\text{oche}_{\text{SPA}}$) and with $\textbf{c}\text{ullera}_{\text{CAT}}$ [spoon] as target label.
+In bilinguals, parallel activation of the prime in both languages should increase the cohort of the target word, leading to stronger interference effects in this condition, compared to *Related/Non-cognate* and *Unrelated* trials.
+
+![Predicted priming effects (or their absence) in the *Related/Cognate*, *Related/Non-cognate*, and *Unrelated* conditions, with examples for a participant tested in Catalan.
+Words represent lexical representations.
+Lexical representations of the task-relevant language (Catalan) are depicted inside grey boxes.
+Solid arrows indicate within-language priming effects, and dashed lines indicate cross-language priming effects.
+In *Related/Cognate* (A) and *Related/Non-cognate* (B) trials, the recognition of the Catalan target word \textipa{kuˈʎe.R@} [spoon] is predicted to be modulated by the prior activation of the prime label in Catalan.
+In *Related/Cognate* trials, the parallel activation of the prime label in Spanish is predicted to increase the strength of the priming effect.](_assets/img/hypotheses.png){fig-align="center"}
+
+In line with previous studies in monolinguals, we further predicted that the strength of the lexical interference effects in the *Related/Non-cognate* and *Related/Cognate* conditions would be associated to participants' vocabulary size.
+Target word recognition should be delayed by the activation of a larger cohort of phonologically related words [@mani2011phonological; @chow2018phonological].
+In the case of bilinguals, two measures of vocabulary size are relevant: *total vocabulary size* and *dominant-language vocabulary size*.
+Total vocabulary size refers to the number of words that a child has acquired, regardless of the language they belong to.
+Dominant-language vocabulary size (L1 vocabulary size, henceforth) refers to the number of acquired words in the dominant language of the child (in which they were tested), the language in which they know more words.
+If the size of interference effects are more tightly associated to bilinguals’ total vocabulary size, it would support the assumption that lexical representations from both languages enter a unique cohort in bilinguals.
+
+Because of the short-lived effects of cross-language activation on lexical processing, and to maximise the probability of detecting priming effects, we introduced a change in the sequence of the trials relative to the original implementation by @mani2010infant.
+We presented target auditory labels inmediately after the offset of the prime picture, and before the onset of the target and distractor pictures.
+By presenting prime pictures and target auditory labels closer in time, implicit naming of the prime picture should be more likely to influence the recognition of the target word.
+To test the effects of this methodological change, we first run a control experiment, Study 1, in which we tested a group of same-aged English monolinguals.
 
@@
 
+In this study, we conducted a conceptual replication of @mani2010infant and @mani2011phonological.
+We tested a group of English monolinguals aged 20 to 32 months, the same population tested in the original studies.
+For consistency with Study 1, we also manipulated the phonological relationship between the prime and target labels at word onset, as well as the cognate status of the prime label.
+Evidence from implicit naming of prime images would be revealed by differences in target looking or its time course across the trials between *Unrelated* trials and *Related/Non-cognate*, and between *Related/Non-cognate* and *Related/Cognate* trials.
+Given that participants in this study are monolinguals---and contrary to the monolinguals in Barcelona, have received no exposure to any other language---we should not find the cognate status of the prime labels to exert any effect on subsequent target recognition.
+
 ## Methods
 
-All materials, data, and reproducible code can be found at the OSF ([https://osf.io/hy984/](https://osf.io/ckydb/)) and GitHub ([https://github.com/gongcastro/cognate-priming](https://github.com/gongcastro/cognate-priming)) repositories.
+All materials, data, and reproducible code can be found at the OSF ([https://osf.io/hy984/](https://osf.io/ckydb/)) and GitHub (<https://github.com/gongcastro/cognate-priming>) repositories.
 This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I.
@@
 ```{r}
-#| label: participants-numbers
-participants_bcn <- filter(participants, location=="Barcelona")
-
-n_participants_total <- nrow(distinct(participants_bcn, child_id))
-n_sessions_total <- count(participants_bcn)
-
-n_participants_lp <- participants_bcn |> 
-	distinct(lp,  child_id) |> 
-	count(lp)
-
-n_participants_lp_sex <- participants_bcn |> 
-	distinct(lp, sex, child_id) |> 
-	count(lp, sex)
-
-n_participants_sessions <- participants_bcn |> 
+#| label: participants-numbers-oxf
+participants_oxf <- filter(participants, location=="Oxford")
+
+n_participants_total <- nrow(distinct(participants_oxf, child_id))
+n_sessions_total <- count(participants_oxf)
+
+n_participants_sex <- participants_oxf |> 
+	distinct(sex, child_id) |> 
+	count(sex)
+
+n_participants_sessions <- participants_oxf |> 
 	count(child_id, name = "n_sessions") |> 
@@
 	group_split(n_sessions) |> 
-	set_names(paste0("session_", 1:3)) |> 
+	set_names(paste0("session_", 1:2)) |> 
 	map("n")
 
-n_sessions_lp <- participants_bcn |> 
-	summarise(across(age, lst(mean, sd, min, max)), n = n(), .by = c(lp)) |> 
-	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
-	group_split(lp) |> 
-	set_names(janitor::make_clean_names(unique(participants_bcn$lp)))
-
-n_sessions_dominance_lp <- count(participants_bcn, lp, test_language) |> 
-	group_split(test_language) |> 
-	set_names(c("catalan", "spanish")) |> 
-	map(group_split, lp)
-
-n_sessions_lp <- participants_bcn |> 
-	count(lp) |> 
-	group_split(lp) |> 
-	set_names(c("monolingual", "bilingual")) |> 
-	map("n")
+ages <- participants_oxf |> 
+	summarise(n = n(),
+			  n_participants = n_distinct(child_id),
+			  across(age, lst(mean, sd, min, max)),
+			  across(matches("doe_"), lst(mean, sd)),
+			  age_vctr = list(age),
+			  .by = c(lp, test_language))
 
 suppressWarnings({
-	time_diffs <- participants_bcn |>
+	time_diffs <- participants_oxf |>
 		arrange(child_id, session_id, age) |>
@@
 		select(child_id, session_id, session_n, age) |> 
-		filter(child_id %in% participants_bcn$child_id[duplicated(participants_bcn$child_id)]) |>
+		filter(child_id %in% participants_oxf$child_id[duplicated(participants_oxf$child_id)]) |>
 		pivot_wider(id_cols = child_id, 
@@
 		rowwise() |>
-		mutate(diff_1 = x2-x1, diff_2 = x3-x2, 
-			   diff_min = min(diff_1, diff_2, na.rm = TRUE),
-			   diff_max = max(diff_1, diff_2, na.rm = TRUE)) |> 
+		mutate(diff_min = x2-x1) |> 
 		ungroup() |> 
-		summarise(diff_min = min(diff_min, na.rm = TRUE), 
-				  diff_max = max(diff_max, na.rm = TRUE))
+		summarise(diff_min = min(diff_min, na.rm = TRUE))
 })
+
 ```
@@
 Participants' vision was normal, none used glasses or any other type of vision corrector.
+
+We collected data from `r n_participants_total` children (`r n_participants_sex$n[1]` female, `r n_participants_sex$n[2]` male, with `r english::words(n_participants_sex$n[3])` additional participants' sex not being reported; Age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = \[`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`\]), living in the Oxfordshire area (United Kingdom).
+Participants were tested at the Oxford BabyLab at the University of Oxford.
+Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
+From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, and `r n_participants_sessions$session_2` participated twice.
+Recurrent participants were tested with at least `r round(time_diffs, 2)$diff_min` months of difference.
+We gathered a total of `r n_sessions_total$n` testing sessions.
+All participants were being raised in exclusively British English monolingual homes.
+
+```{r vocab-values-oxf}
+vocabulary_oxf <- inner_join(vocabulary, 
+							 select(participants_oxf, session_id),
+							 by = join_by(session_id))
+```
+
+We collected vocabulary data using parental responses to the Oxford Communicative Development Inventory (OCDI) [@hamilton2000infant].
+Families were sent the questionnaire immediately after each experimental session, and were given two weeks to fill it.
+Since all vocabulary sizes of English monolingual infants were only assessed in English, both *L1 vocabulary* and *total vocabulary* sizes were identical (see @fig-vocabulary-oxf).
+
+```{r fig-vocabulary-oxf}
+#| label: fig-vocabulary-oxf
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores from the recurrent participants are shown linked."
+#| fig-width: 4
+#| fig-height: 2.5
+vocabulary_oxf |> 
+	inner_join(filter(attrition_participants, is_valid_participant),
+			   by = join_by(session_id)) |> 
+	inner_join(select(participants, child_id, session_id, age_group),
+			   by = join_by(child_id, session_id)) |> 
+	ggplot(aes(age_group, l1_prop)) +
+	geom_line(aes(group = child_id),
+			  colour = "grey",
+			  alpha = 1/4, linewidth = 3/4) +
+	geom_dots(dotsize = 2,
+			  colour = clrs[5],
+			  fill = clrs[5],
+			  scale = 1,
+			  side = "both",
+			  alpha = 3/4) +
+	stat_summary(fun.data = mean_se,
+				 geom = "errorbar",
+				 linewidth = 1/2,
+				 width = 0.1,
+				 colour = "black",
+				 show.legend = FALSE) +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 size = 1.5,
+				 colour = "black",
+				 show.legend = FALSE) +
+	# geom_point(alpha = 1) +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size",
+		 colour = "Group",
+		 fill = "Group") +
+	scale_y_continuous(labels = scales::percent,
+					   limits = c(0, 1)) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"),
+		  legend.position = "top",
+		  legend.title = element_blank())
+```
 
@@
 			  cells_column_spanners())
-
-# col_names <- c("Group",
-# 			   "Language",
-# 			   "Sessions", 
-# 			   "Participants",
-# 			   "M (SD)",
-# 			   "Range",
-# 			   "M (SD)",
-# 			   "M (SD)",
-# 			   "M (SD)")
-# participants_bcn |> 
-# 	unnest_wider(doe) |> 
-# 	select(-matches("others")) |> 
-# 	arrange(lp, test_language) |> 
-# 	summarise(n = n(),
-# 			  n_participants = n_distinct(child_id),
-# 			  across(age, lst(mean, sd, min, max)),
-# 			  across(matches("doe_"), lst(mean, sd)),
-# 			  # age_vctr = list(age),
-# 			  .by = c(lp, test_language)) |> 
-# 	mutate(age_mean = sprintf("%.1f (%.1f)", age_mean, age_sd),
-# 		   age_range = sprintf("%.1f-%.1f", age_min, age_max),
-# 		   doe_catalan = sprintf("%.1f (%.1f)", doe_catalan_mean*100, doe_catalan_sd*100),
-# 		   doe_spanish = sprintf("%.1f (%.1f)", doe_spanish_mean*100, doe_spanish_sd*100),
-# 		   doe_english = sprintf("%.1f (%.1f)", doe_english_mean*100, doe_english_sd*100)) |> 
-# 	select(lp:age_mean, age_range, doe_catalan, doe_spanish, doe_english) |> 
-# 	kable(digits = 1, 
-# 		  format = "latex",
-# 		  booktabs = TRUE,
-# 		  col.names = col_names,
-# 		  align = "llrrrrrrrrrrrr"
-# 	)
-# 	add_header_above(c(
-# 		" " = 4,
-# 		"Age (months)" = 2,
-# 		"Degree of exposure (%)" = 8
-# 	)) 
 ```
@@
 
+New stimuli lists were generated to adapt the experimental procedure to English-learning infants.
+Stimuli lists were created following the same constraints as in Study 1.
+Auditory stimuli were recorded following the same procedure as in Study 1, produced by Southern British English native female speaker in a toddler-directed manner.
+Audio and picture processing were performed following the same workflow as in Study 1.
+
+### Procedure and apparatus
+
+Same as in Study 1.
+The study was run using a custom Matlab script, PresentMate, based on the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox].
+Visual fixations were recorded using a Tobii TX 300 eye-tracker and a 23-in screen of 1920 $\times$ 1080 resolution.
+The Tobii Analytics SDK 3.0 was used to interact with the eye-tracking while the experiment was running.
+Sampling rate was set at 120 Hz.
+A 9-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
+
+### Data analysis
+
+Same as in Study 1, but removing the *Group* predictor from the models, given that only monolingual infants were tested.
+
+```{r dataset_oxf}
+attrition_oxf <- filter(attrition, location=="Oxford")
+n_trials <- nrow(attrition_oxf)
+n_sessions <- n_distinct(attrition_oxf$session_id)
+n_participants <- n_distinct(attrition_oxf$child_id)
+n_trials_valid <- nrow(filter(attrition_oxf,
+							  is_valid_participant,
+							  is_valid_trial))
+n_sessions_valid <- attrition_oxf |> 
+	distinct(child_id, .keep_all = TRUE) |> 
+	pull(is_valid_participant) |> 
+	sum()
+
+n_participants_valid <- n_distinct(
+	attrition_oxf[attrition_oxf$is_valid_participant, ]$child_id)
+
+n_exc_prime <- sum(!attrition_oxf$is_valid_gaze_prime)
+n_exc_test <- sum(!attrition_oxf$is_valid_gaze_test)
+n_exc_test_each <- sum(!attrition_oxf$is_valid_gaze_test_each)
+n_exc_participants <- sum(!attrition_oxf |> 
+						  	distinct(child_id, .keep_all = TRUE) |> 
+						  	pull(is_valid_participant), na.rm = TRUE)
+
+n_exc_participants_vocab <- attrition_oxf |> 
+	distinct(child_id, .keep_all = TRUE) |> 
+	mutate(is_valid_vocab_size = !is_valid_vocab_size) |> 
+	pull(is_valid_vocab_size) |> 
+	sum(na.rm = TRUE)
+
+n_longitudinal <- attrition_oxf |>
+	filter(is_valid_participant,
+		   is_valid_trial) |>
+	distinct(child_id, session_n) |> 
+	count(child_id, name = "times") |> 
+	count(times)
+
+n_trials_condition <- attrition_oxf |> 
+	filter(is_valid_participant) |> 
+	count(trial_type, is_valid_trial) %>%
+	split(janitor::make_clean_names(.$trial_type))
+```
+
+We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
+We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
+We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
+
+After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
+The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+From the trials included in the final dataset dataset, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), were `r n_trials_condition$non_cognate_2$n` *Related/Non-cognate* trials(`r n_trials_condition$non_cognate$n` previously excluded), and `r n_trials_condition$cognate_2$n` were *Related/Cognate* trials (`r n_trials_condition$cognate$n` previously excluded).
+
+## Results
+
+### Priming effects
+
+```{r coefs-oxf}
+var_labels <- c("b_Intercept" = "Intercept",
+				"b_age_std" = "Age (+1 SD)",
+				"b_condition1" = "Condition (U vs. RN)",
+				"b_condition2" = "Condition (RN vs. RC)")
+
+model_summary <- get_posterior_summary(model_fits_oxf$fit_oxf_1,
+									   data_bcn,
+									   vars_dict = var_labels,
+									   rope_interval = rope_interval)
+
+coefs <- model_summary |> 
+	mutate(.value = sprintf("%.3f", .value),
+		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
+		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
+	split(janitor::make_clean_names(model_summary$.variable))
+```
+
+Overall, the average participant' target looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$b_intercept$.value`, 95% HDI = `r coefs$b_intercept$.ci`) and all of its posterior samples fell outside of the ROPE.
+The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$b_age_std$.value`, 95% HDI = `r coefs$b_age_std$.ci`), and overlapped completely with the ROPE, indicating that participants from all ages showed equivalent overall target word recognition.
+The 95% HDI of the first contrast of the *Condition* predictor---comparing *Unrelated* and *Related/Non-cognate* trials---included zero ($\beta$ = `r coefs$b_condition1$.value`, 95% HDI = `r coefs$b_condition1$.ci`), and `r coefs$b_condition1$.rope` of its posterior samples fell within the ROPE.
+The 95% HDI of the second contrast---comparing *Related/Non-cognate* and *Related/Cognate* trials---also included zero ($\beta$ = `r coefs$b_condition2$.value`, 95% HDI = `r coefs$b_condition2$.ci`), and `r coefs$b_condition2$.rope` of its posterior samples fell within the ROPE.
+The overall target preference was equivalent across both pairwise condition comparisons.
+
+```{r tbl-coefs-oxf}
+#| label: tbl-coefs-oxf
+#| fig-cap: "Margin posterior mean predictions.
+A) Posterior mean predictions of the time course of target fixation in the test phase.
+B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
+Lines and intervals indicate the mean and 95% credible interval of the posterior predictions."
+#| echo: false
+#| eval: false
+#| message: false
+#| warning: false
+#| out-width: 80%
+
+# summarise posterior draws
+intercept_label <- paste0("Intercept (at ", round(mean(data_oxf$age), 2), " months)")
+
+tbl_data <- model_summary |>
+	select(.variable_name, .value, .lower, .upper, .rope, .type) |>
+	mutate(.variable_name = gsub("×", "$\\\\times$", .variable_name),
+		   .hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
+		   .rope = case_when(is.na(.rope) ~ "-",
+		   				  .rope > 0.9999 ~ "1",
+		   				  .rope < 0.00001 ~ "0",
+		   				  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope)))) |>
+	select(.variable_name, .value, .lower, .upper, .hdi, .rope)
+
+col_names <- c("", "$\\beta$", "95\\% HDI", "$p(\\text{ROPE})$")
+
+tbl_data |>
+	select(-c(.lower, .upper)) |>
+	kable(format = "latex",
+		  escape = FALSE,
+		  col.names = col_names,
+		  digits = 3,
+		  booktabs = TRUE,
+		  align = "lclr",
+		  linesep = "") |>
+	kable_styling() |>
+	add_footnote("$\\beta$: median of the posterior distribution in the probability scale.
+95\\% HDI: 95\\% highest density interval of the distribution.
+$p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
+```
+
+```{r timecourse-oxf}
+nd <- expand_grid(distinct(data_oxf, condition),
+				  timebin_std = timebin_values,
+				  age_std = 0)
+
+epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_1, 
+						  re_formula = NA,
+						  ndraws = NULL,
+						  value = ".epred")
+```
+
+An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds-oxf).
+Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
+
+```{r fig-epreds-oxf}
+#| label: fig-epreds-oxf
+#| fig-cap: "A) Posterior mean predictions of the time course of target fixation in the test phase.
+Thin lines represent 100 individual posterior predictions.
+Thick lines indicate the mean of the posterior predictions.
+B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
+Thin lines represent 100 individual posterior predictions.
+Black lines indicate the mean of the posterior predictions."
+#| fig-width: 6.5
+#| fig-height: 6.5
+epreds_summary <- epreds |> 
+	ungroup() |> 
+	summarise(.value = mean_qi(.epred)[[1]],
+			  .lower = mean_qi(.epred)[[2]],
+			  .upper = mean_qi(.epred)[[3]],
+			  .by = c(condition, timebin_std))
+
+plot_epreds <- epreds |> 
+	ggplot(aes(timebin_std, .epred,
+			   colour = condition,
+			   fill = condition,
+			   linetype = condition,
+			   shape = condition)) +
+	geom_hline(yintercept = 0,
+			   colour = "grey") +
+	# geom_line(aes(group = interaction(condition, .draw)),
+	# 		  alpha = 1/20,
+	# 		  linewidth = 3/4,
+	# 		  linetype = "solid") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
+				 alpha = 1/4,
+				 linewidth = NA) +
+	stat_summary(fun = "mean",
+				 geom = "line",
+				 # colour = "black",
+				 linewidth = 3/4) +
+	stat_summary(data = data_oxf,
+				 aes(y = .elog),
+				 fun = "mean",
+				 geom = "point",
+				 size = 2) +
+	labs(x = "Time (ms)",
+		 y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition",
+		 linetype = "Condition",
+		 shape = "Condition")
+
+epreds_diff <- epreds |> 
+	pivot_wider(id_cols = c(timebin_std, .draw),
+				names_from = "condition",
+				values_from = ".epred",
+				names_repair = janitor::make_clean_names) |> 
+	mutate(diff_1 = related_non_cognate - unrelated,
+		   diff_2 = related_cognate - related_non_cognate) |> 
+	pivot_longer(matches("diff"),
+				 names_to = "diff",
+				 values_to = ".epred",
+				 names_prefix = "diff_") |> 
+	mutate(diff = factor(diff,
+						 levels = c(1, 2),
+						 labels = c("Related/Non-cognate - Unrelated",
+						 		   "Related/Cognate - Related/Non-cognate")))
+
+plot_diffs <- epreds_diff |> 
+	ggplot(aes(timebin_std, .epred)) +
+	facet_wrap(~diff) +
+	# annotate(geom = "rect",
+	# 		 xmin = timebin_values[1],
+	# 		 xmax = timebin_values[length(timebin_values)],
+	# 		 ymin = rope_interval[1],
+	# 		 ymax = rope_interval[2],
+	# 		 fill = "red",
+	# 		 linewidth = 0,
+	# 		 alpha = 1/2,
+	# 		 linetype = "dotted") +
+	stat_summary(fun.data = mean_qi,
+				 geom = "ribbon",
+				 fill = "grey",
+				 linewidth = NA,
+				 alpha = 1/3) +
+	stat_summary(aes(group = diff),
+				 fun = mean,
+				 geom = "line",
+				 colour = "black",
+				 linewidth = 3/4) +
+	geom_hline(yintercept = rope_interval[1],
+			   colour = "red",
+			   linetype = "dotted") +
+	geom_hline(yintercept = rope_interval[2],
+			   colour = "red",
+			   linetype = "dotted") +
+	# geom_line(aes(group = interaction(diff, draw)),
+	# 		  alpha = 1/20,
+	# 		  linewidth = 3/4,
+	# 		  colour = "grey",
+	# 		  linetype = "solid") +
+
+	labs(x = "Time (ms)",
+		 y = "Logit P(Target looking)",
+		 colour = "Comparison",
+		 fill = "Comparison",
+		 linetype = "Comparison")
+
+plot_epreds + plot_diffs +
+	plot_layout(ncol = 1) &
+	plot_annotation(tag_levels = "A") &
+	# scale_y_continuous(limits = c(0.25, 0.75)) +
+	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
+										 mean(data_bcn$timebin),
+										 sd(data_bcn$timebin)),
+					   labels = \(x) format(seq(3e2, 2e3, 3e2),
+					   					 big.mark = ",")) &
+	theme(legend.position = "top",
+		  legend.title = element_blank(),
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+```
+
+### The role of age and vocabulary size on priming effects
+
+@tbl-loos-oxf shows a comparison between models including *Age* ($\mathcal{M}_{2}$), and *L1 vocabulary* ($\mathcal{M}_{3}$)---and their two-way and two-way interaction with *Condition*---against model $\mathcal{M}_{1}$, which only included *Age* as a covariate suggested that all models performed equivalently, with model $\mathcal{M}_{2}$ showing a slightly better performance.
+Overall, this suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account *L1 vocabulary*, or *Total vocabulary* sizes.
+
+```{r tbl-loos-oxf}
+#| label: tbl-loos-oxf
+#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 2."
+loo_compare(model_loos_oxf[2:4]) |> 
+	as.data.frame() |> 
+	rownames_to_column("model") |> 
+	mutate(model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model))-1),
+		   across(matches("diff"),
+		   	   \(x) {x[1] <- NA; return(x)}),
+		   model = case_when(model=="Model 1" ~ "Model 1 (Age)",
+		   				  model=="Model 2" ~ "Model 2 (L1 vocabulary)",
+		   				  model=="Model 3" ~ "Model 3 (Total vocabulary)",
+		   				  .default = model)) |> 
+	select(model, matches("elpd|diff")) |> 
+	relocate(matches("diff"), .after = matches("loo")) |> 
+	gt(rowname_col = "model") |> 
+	fmt_number(is.numeric) |> 
+	cols_label(elpd_diff = "ELPD (diff.)",
+			   se_diff = "SE ELPD (diff)",
+			   elpd_loo = "ELPD",
+			   se_elpd_loo = "SE ELPD") |> 
+	fmt_missing(missing_text = "---") |> 
+	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new dataset.
+*SE \\(ELPD\\)*: standard error of the *ELPD*, which indictes the uncertainty about the predictive performance for unknown future data.
+*ELPD (diff)*: pairwise difference in *ELPD* for two models.
+The difference is computed relative to the model with lowest *ELPD* (best fitting model).
+*SE ELPD (diff.)*: standard error of component-wise differences of *ELPD* between two models.")) |>
+	tab_style(cell_text(style = "italic"), cells_column_labels())
+```
+
+### Word recognition times
+
+```{r recognition-oxf}
+nd <- expand_grid(distinct(data_oxf, condition),
+				  timebin_std = timebin_values,
+				  age_std = age_values)
+
+epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_2, 
+						  re_formula = NA,
+						  ndraws = NULL,
+						  value = ".epred")
+
+epreds_chance <- epreds |> 
+	median_hdci() |> 
+	mutate(is_lower_positive = .lower > 0) |> 
+	filter(is_lower_positive) |> 
+	summarise(over_chance = min(timebin_std),
+			  .by = c(condition, age_std)) |> 
+	mutate(over_chance = (over_chance * 
+						  	sd(data_oxf$timebin) +
+						  	mean(data_oxf$timebin))*100+300)
+
+epreds_chance_report <- epreds_chance |> 
+	mutate(over_chance = sprintf("%.2f", over_chance),
+		   age_std = factor(x = age_std,
+		   				 levels = age_values,
+		   				 labels = paste0(c(20, 30), " months"))) |> 
+	arrange(age_std) %>%
+	split(paste0("age_", gsub(" months", "", .$age_std)))
+```
+
+As expected, the recognition times were on average shorter for older infants than for younger infants.
+Differences between conditions were larger in bilinguals than in monolinguals, especially in the older group.
+The recognition time for monolingual 20-month-olds was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
+In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
+
+```{r fig-recognition-oxf}
+#| label: fig-recognition-oxf
+#| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
+#| fig-width: 5
+#| fig-height: 3.5
+epreds_chance |> 
+	mutate(age_std = factor(x = age_std,
+							levels = age_values,
+							labels = paste0(c(20, 32), " months"))) |> 
+	ggplot(aes(age_std, over_chance,
+			   colour = sort(condition),
+			   fill = sort(condition))) + 
+	geom_point(shape = 16, size = 4) +
+	geom_line(aes(group = condition),
+			  linewidth = 1) +
+	# geom_point(size = 3) +
+	labs(x = "Group",
+		 y = "Recognition time (ms)",
+		 colour = "Condition",
+		 fill = "Condition") +
+	scale_y_continuous(breaks = seq(0, 1e3L, 25)) +
+	theme(panel.grid.major.y = element_line(colour = "grey",
+											linetype = "dotted"),
+		  panel.grid.minor.y = element_line(colour = "grey",
+		  								  linetype = "dotted"),
+		  legend.position = "top",
+		  axis.title.x = element_blank())
+```
+
+## Discussion
+
+Study 2 was aimed at investigating whether the phonological priming effects previously reported @mani2010infant and @mani2011phonological could be found using the adaptation of the implicit naming task form Study 1 in a sample with equivalent demographic characteristics to the original studies.
+Results from Study 2 did not provide any evidence in favour of phonological priming.
+English monolingual participants from all ages showed an equivalent pattern of target looking across both related and unrelated trials.
+The absence of a phonological priming effect suggest that either English monolinguals did not generate implicit labels for the prime pictures presented in silence, or that if generated, such labels did not interact with the subsequent recognition of the target word.
+Both candidate explanations conflict with both Mani and Plunkett's studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects [@duta2012erp; @styles2015infant].
+
+One of the main differences between the implicit naming paradigm used by @mani2010infant and the one in Studies 1 and 2 is the fact that target labels were auditorily presented before target and distractor pictures were presented on screen.
+The rationale behind this decision was to minimise the amount of time elapsed between the presentation of the prime and target labels, in order to facilitate any potential priming effects.
+By presenting the auditory target label immediately after the offset of the prime picture, the internally generated prime phonological form would be more likely to affect the activation of the target lexical representation.
+It is possible that this difference in task design might have led to the contrasting outcomes of Mani and Plunkett and the present study.
+Given that participants were not presented with the target and distractor pictures until after the target label was auditorily presented, one possibility is that participants faced the additional task of exploring both pictures to find the target referent, which infants in @mani2010infant did not have to do, because of the pre-naming presentation of target and distractor in the test phase.
+This visual exploration of the screen might have increased the cognitive load of the task, rendering the potential effect of phonological priming to a weaker, undetectable effect.
+Overall, the results from Study 2 support a more methodological explanation of the null pattern of results in Study 1, in which the lack of a phonological priming effect---both within and across languages---might be explained by differences in task design or replicability concerns.
+
+# Study 2
+
+## Methods
+
+### Participants
+
+```{r}
+#| label: participants-numbers
+participants_bcn <- filter(participants, location=="Barcelona")
+
+n_participants_total <- nrow(distinct(participants_bcn, child_id))
+n_sessions_total <- count(participants_bcn)
+
+n_participants_lp <- participants_bcn |> 
+	distinct(lp,  child_id) |> 
+	count(lp)
+
+n_participants_lp_sex <- participants_bcn |> 
+	distinct(lp, sex, child_id) |> 
+	count(lp, sex)
+
+n_participants_sessions <- participants_bcn |> 
+	count(child_id, name = "n_sessions") |> 
+	count(n_sessions) |> 
+	group_split(n_sessions) |> 
+	set_names(paste0("session_", 1:3)) |> 
+	map("n")
+
+n_sessions_lp <- participants_bcn |> 
+	summarise(across(age, lst(mean, sd, min, max)), n = n(), .by = c(lp)) |> 
+	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
+	group_split(lp) |> 
+	set_names(janitor::make_clean_names(unique(participants_bcn$lp)))
+
+n_sessions_dominance_lp <- count(participants_bcn, lp, test_language) |> 
+	group_split(test_language) |> 
+	set_names(c("catalan", "spanish")) |> 
+	map(group_split, lp)
+
+n_sessions_lp <- participants_bcn |> 
+	count(lp) |> 
+	group_split(lp) |> 
+	set_names(c("monolingual", "bilingual")) |> 
+	map("n")
+
+suppressWarnings({
+	time_diffs <- participants_bcn |>
+		arrange(child_id, session_id, age) |>
+		mutate(n_session = 1:n()) |>
+		select(child_id, session_id, session_n, age) |> 
+		filter(child_id %in% participants_bcn$child_id[duplicated(participants_bcn$child_id)]) |>
+		pivot_wider(id_cols = child_id, 
+					names_from = session_n, 
+					values_from = age, 
+					names_repair = janitor::make_clean_names) |> 
+		rowwise() |>
+		mutate(diff_1 = x2-x1, diff_2 = x3-x2, 
+			   diff_min = min(diff_1, diff_2, na.rm = TRUE),
+			   diff_max = max(diff_1, diff_2, na.rm = TRUE)) |> 
+		ungroup() |> 
+		summarise(diff_min = min(diff_min, na.rm = TRUE), 
+				  diff_max = max(diff_max, na.rm = TRUE))
+})
+```
+
+We collected data from `r n_participants_total` children living in the Metropolitan Area of Barcelona (Spain), tested at the Laboratori de Recerca en Infància at the Universitat Pompeu Fabra.
+Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
+From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, `r n_participants_sessions$session_2` participated twice, and `r n_participants_sessions$session_3` participated three times.
+Recurrent participants were tested with at least `r round(time_diffs$diff_min[1], 2)` months of difference.
+We gathered a total of `r n_sessions_total$n` testing sessions.
+Participants were divided into monolinguals and bilinguals based on their relative degree of exposure to Catalan and Spanish, estimated using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
+We categorised participants as monolingual if exposed to more than 80% or more of the time to their dominant language, and as bilingual otherwise.
+`r english::Words(n_participants_lp$n[1])` of the participants were categorised as monolinguals (`r n_participants_lp_sex$n[1]` female, `r n_participants_lp_sex$n[2]` male) and `r n_participants_lp$n[2]` as Catalan/Spanish bilinguals (`r n_participants_lp_sex$n[3]` female, `r n_participants_lp_sex$n[4]` male) (see @tbl-participants for a detailed summary of participants' age and language profile).
+Participants' vision was normal, none used glasses or any other type of vision corrector.
+
+```{r tbl-participants}
+#| label: tbl-participants
+#| tbl-cap: "Demographic and linguistic profile of testing sessions."
+participants_bcn |> 
+	unnest_wider(doe) |> 
+	select(-matches("others")) |> 
+	arrange(lp, test_language) |> 
+	distinct(session_id, child_id, .keep_all = TRUE) |> 
+	summarise(n = n(),
+			  n_participants = length(unique(child_id)),
+			  across(age, lst(mean, sd, min, max)),
+			  across(matches("doe_"), lst(mean, sd)),
+			  # age_vctr = list(age),
+			  .by = c(lp, test_language)) |> 
+	gt(rowname_col = "test_language",
+	   groupname_col = "lp") |> 
+	summary_rows(groups = c("Monolingual", "Bilingual"),
+				 columns = matches("age"),
+				 fns = list(Total ~ mean(.)),
+				 fmt = ~ fmt_number(., decimals = 1, use_seps = FALSE)) |> 
+	summary_rows(groups = c("Monolingual", "Bilingual"),
+				 columns = c(n, n_participants),
+				 fns = list(Total ~ sum(.)),
+				 fmt = ~ fmt_integer(.)) |> 
+	summary_rows(groups = c("Monolingual", "Bilingual"),
+				 columns = matches("doe"),
+				 fns = list(Total ~ mean(.)),
+				 fmt = ~ fmt_number(., decimals = 1, scale_by = 100)) |> 
+	grand_summary_rows(columns = matches("age"),
+					   fns = list(Total ~ mean(.)),
+					   fmt = ~ fmt_number(., decimals = 1)) |> 
+	grand_summary_rows(columns = matches("doe"),
+					   fns = list(Total ~ mean(.)),
+					   fmt = ~ fmt_number(., decimals = 1, scale_by = 100)) |> 
+	grand_summary_rows(columns = c(n, n_participants),
+					   fns = list(Total ~ sum(.)),
+					   fmt = ~ fmt_integer(.)) |> 
+	# gt_plt_dist(age_vctr, type = "histogram") |>
+	fmt_number(is.numeric, decimals = 1) |> 
+	fmt_integer(c(n, n_participants)) |> 
+	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
+	cols_merge(c(age_min, age_max), 
+			   pattern = "{1}-{2}") |> 
+	cols_merge(c(age_mean, age_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_catalan_mean, doe_catalan_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_english_mean, doe_english_sd),
+			   pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_spanish_mean, doe_spanish_sd), 
+			   pattern = "{1} ({2})") |> 
+	tab_spanner("Age (months)", matches("age")) |> 
+	tab_spanner("Catalan", matches("catalan")) |> 
+	tab_spanner("English", matches("english")) |> 
+	tab_spanner("Spanish", matches("spanish")) |> 
+	tab_spanner("Degree of Exposure (%)", matches("doe")) |> 
+	cols_label(n = "Sessions",
+			   n_participants = "Participants",
+			   age_mean = "M (SD)",
+			   age_min = "Range",
+			   doe_catalan_mean = "M (SD)",
+			   doe_english_mean = "M (SD)",
+			   doe_spanish_mean = "M (SD)") |> 
+	tab_style(cell_text(style = "italic"),
+			  cells_column_labels()) |> 
+	tab_style(cell_text(style = "italic"),
+			  cells_column_spanners())
+
+# col_names <- c("Group",
+# 			   "Language",
+# 			   "Sessions", 
+# 			   "Participants",
+# 			   "M (SD)",
+# 			   "Range",
+# 			   "M (SD)",
+# 			   "M (SD)",
+# 			   "M (SD)")
+# participants_bcn |> 
+# 	unnest_wider(doe) |> 
+# 	select(-matches("others")) |> 
+# 	arrange(lp, test_language) |> 
+# 	summarise(n = n(),
+# 			  n_participants = n_distinct(child_id),
+# 			  across(age, lst(mean, sd, min, max)),
+# 			  across(matches("doe_"), lst(mean, sd)),
+# 			  # age_vctr = list(age),
+# 			  .by = c(lp, test_language)) |> 
+# 	mutate(age_mean = sprintf("%.1f (%.1f)", age_mean, age_sd),
+# 		   age_range = sprintf("%.1f-%.1f", age_min, age_max),
+# 		   doe_catalan = sprintf("%.1f (%.1f)", doe_catalan_mean*100, doe_catalan_sd*100),
+# 		   doe_spanish = sprintf("%.1f (%.1f)", doe_spanish_mean*100, doe_spanish_sd*100),
+# 		   doe_english = sprintf("%.1f (%.1f)", doe_english_mean*100, doe_english_sd*100)) |> 
+# 	select(lp:age_mean, age_range, doe_catalan, doe_spanish, doe_english) |> 
+# 	kable(digits = 1, 
+# 		  format = "latex",
+# 		  booktabs = TRUE,
+# 		  col.names = col_names,
+# 		  align = "llrrrrrrrrrrrr"
+# 	)
+# 	add_header_above(c(
+# 		" " = 4,
+# 		"Age (months)" = 2,
+# 		"Degree of exposure (%)" = 8
+# 	)) 
+```
+
+```{r vocab-values}
+vocabulary_bcn <- vocabulary |> 
+	inner_join(select(participants_bcn, session_id, lp, age_group),
+			   by = join_by(session_id))
+
+vocab_means <- vocabulary_bcn |> 
+	summarise(across(c(total_prop, l1_prop), lst(mean, sd)),
+			  n = n(),
+			  .by = c(age_group, lp)) %>%
+	mutate(across(matches("prop"), scales::percent)) %>%
+	split(paste0("age_", gsub(" months", "", .$age_group))) |> 
+	map(\(x) split(x, tolower(x$lp)))
+
+n_imputed <- table(vocabulary_bcn$is_imputed)[2]
+prop_imputed <- scales::percent(n_imputed/nrow(vocabulary_bcn))
+n_pool <- nrow(bvq_data$vocabulary)
+```
+
+We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers, and inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability].
+Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
+We calculated two measures of receptive vocabulary size for each participant: *L1 vocabulary size* (proportion of words reported as acquired in the checklist of the dominant language), and *total vocabulary size* (proportion of the words in both checklists reported as acquired).
+`r english::Words(n_imputed)` (`r prop_imputed`) families failed to provide a complete response to the BVQ within the two-week time limit.
+We imputed missing vocabulary size scores using single imputation, taking the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
+We used participants' age in months and their language profile (monolingual or bilingual) as predictors.
+We used the `mice` R package [@van2011mice] to perform imputation using the Bayesian linear regression method (see Appendix B).
+
+Overall, there was a substantial increase in both total and L1 vocabulary sizes associated to age (see @fig-vocabulary).
+Monolinguals showed higher L1 vocabulary sizes than monolinguals: they were reported to understand an average of `r vocab_means$age_21$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$l1_prop_sd`) at 30 months, while bilinguals were reported to understand an average of `r vocab_means$age_21$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$l1_prop_sd`) at 30 months.
+Total vocabulary sizes showed the opposite pattern, with monolinguals infants being reported to understand `r vocab_means$age_21$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$total_prop_sd`) at 30 months, and bilinguals being reported to understand `r vocab_means$age_21$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$total_prop_sd`) at 30 months.
+
+```{r fig-vocabulary}
+#| label: fig-vocabulary
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles.
+Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
+Grey lines connect vocabulary size scores from the recurrent participants.
+For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested.
+Only participants included in the final data set are shown."
+#| fig-width: 6
+#| fig-height: 3.5
+vocabulary_bcn |> 
+	inner_join(filter(attrition_participants, is_valid_participant),
+			   by = join_by(session_id)) |> 
+	pivot_longer(c(total_prop, l1_prop),
+				 names_to = "measure",
+				 values_to = "prop",
+				 names_transform = \(x) gsub("_prop", "", x)) |> 
+	mutate(measure = if_else(measure=="l1", 
+							 "L1 vocabulary", 
+							 "Total vocabulary"),
+		   is_imputed = if_else(is_imputed, "Imputed", "Observed") |> 
+		   	factor(levels = c("Observed", "Imputed"))) |> 
+	ggplot(aes(age_group, prop,
+			   colour = lp,
+			   fill = lp)) +
+	facet_wrap(~measure) +
+	geom_line(aes(group = child_id),
+			  colour = "grey",
+			  alpha = 1/4, linewidth = 3/4) +
+	geom_dots(aes(side = if_else(lp=="Monolingual", "left", "right")),
+			  dotsize = 2,
+			  stroke = 1/2,
+			  scale = 0.5,
+			  alpha = 3/4) +
+	stat_summary(fun.data = mean_se,
+				 geom = "errorbar",
+				 linewidth = 1/2,
+				 width = 0.15,
+				 colour = "black",
+				 show.legend = FALSE,
+				 position = position_dodge(width = 1.15)) +
+	stat_summary(fun = mean,
+				 geom = "point",
+				 size = 1.5,
+				 colour = "black",
+				 show.legend = FALSE,
+				 position = position_dodge(width = 1.15)) +
+	# geom_point(alpha = 1) +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size",
+		 colour = "Group",
+		 fill = "Group") +
+	scale_y_continuous(labels = scales::percent,
+					   limits = c(0, 1)) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"),
+		  legend.position = "top",
+		  legend.title = element_blank())
+```
+
+### Stimuli
+
 ```{r stimuli-values}
@@
 We then computed the difference between the marginal posterior predictions for the *Unrelated* and *Related/Non-cognate* conditions, and between those for the *Related/Non-cognate* and *Related/Cognate* conditions, at each time bin.
-Finally, we compared the 95% HDI of the differences against the [-0.1, +0.1] ROPE.
+Finally, we compared the 95% HDI of the differences against the \[-0.1, +0.1\] ROPE.
 
@@
 Another possibility is that exposure to a second language might have delayed the developmental trajectories of word production in bilinguals, in such way implicit naming emerges later ages.
-Given that `r scales::percent(doe_mon_exp$n[1] / doe_mon_exp$n[2], accuracy = 0.01)`
-of monolinguals in Barcelona were exposed to a second language (although less than 20% of the time), they might as well been affected by such delay in implicit naming trajectories.
+Given that `r scales::percent(doe_mon_exp$n[1] / doe_mon_exp$n[2], accuracy = 0.01)` of monolinguals in Barcelona were exposed to a second language (although less than 20% of the time), they might as well been affected by such delay in implicit naming trajectories.
 
@@
 If, on the contrary, a similar patter of null results is found, this would suggest either the existence of finer differences in task implementation compared to the original studies, or point to the effect of interest being less robust than suggested by the literature.
-
-# Study 2
-
-In this study, we conducted a conceptual replication of @mani2010infant and @mani2011phonological.
-Using the same task from Study 1, we tested a group of monolinguals aged 20 to 32 months being exclusively raised in British English speaking homes, the same population tested in the original studies.
-For consistency with Study 1, we also manipulated the phonological relationship between the prime and target labels at word onset, as well as the cognate status of the prime label.
-Evidence from implicit naming of prime images would be revealed by differences in target looking or its time course across the trials between *Unrelated* trials and *Related/Non-cognate*, and between *Related/Non-cognate* and *Related/Cognate* trials.
-Given that participants in this study are monolinguals---and contrary to the monolinguals in Barcelona, have received no exposure to any other language---we should not find the cognate status of the prime labels to exert any effect on subsequent target recognition.
-
-## Methods
-
-### Participants
-
-```{r}
-#| label: participants-numbers-oxf
-participants_oxf <- filter(participants, location=="Oxford")
-
-n_participants_total <- nrow(distinct(participants_oxf, child_id))
-n_sessions_total <- count(participants_oxf)
-
-n_participants_sex <- participants_oxf |> 
-	distinct(sex, child_id) |> 
-	count(sex)
-
-n_participants_sessions <- participants_oxf |> 
-	count(child_id, name = "n_sessions") |> 
-	count(n_sessions) |> 
-	group_split(n_sessions) |> 
-	set_names(paste0("session_", 1:2)) |> 
-	map("n")
-
-ages <- participants_oxf |> 
-	summarise(n = n(),
-			  n_participants = n_distinct(child_id),
-			  across(age, lst(mean, sd, min, max)),
-			  across(matches("doe_"), lst(mean, sd)),
-			  age_vctr = list(age),
-			  .by = c(lp, test_language))
-
-suppressWarnings({
-	time_diffs <- participants_oxf |>
-		arrange(child_id, session_id, age) |>
-		mutate(n_session = 1:n()) |>
-		select(child_id, session_id, session_n, age) |> 
-		filter(child_id %in% participants_oxf$child_id[duplicated(participants_oxf$child_id)]) |>
-		pivot_wider(id_cols = child_id, 
-					names_from = session_n, 
-					values_from = age, 
-					names_repair = janitor::make_clean_names) |> 
-		rowwise() |>
-		mutate(diff_min = x2-x1) |> 
-		ungroup() |> 
-		summarise(diff_min = min(diff_min, na.rm = TRUE))
-})
-
-```
-
-We collected data from `r n_participants_total` children (`r n_participants_sex$n[1]` female, `r n_participants_sex$n[2]` male, with `r english::words(n_participants_sex$n[3])` additional participants' sex not being reported; Age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]), living in the Oxfordshire area (United Kingdom).
-Participants were tested at the Oxford BabyLab at the University of Oxford.
-Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, and `r n_participants_sessions$session_2` participated twice.
-Recurrent participants were tested with at least `r round(time_diffs, 2)$diff_min` months of difference.
-We gathered a total of `r n_sessions_total$n` testing sessions.
-All participants were being raised in exclusively British English monolingual homes.
-
-```{r vocab-values-oxf}
-vocabulary_oxf <- inner_join(vocabulary, 
-							 select(participants_oxf, session_id),
-							 by = join_by(session_id))
-```
-
-We collected vocabulary data using parental responses to the Oxford Communicative Development Inventory (OCDI) [@hamilton2000infant].
-Families were sent the questionnaire immediately after each experimental session, and were given two weeks to fill it.
-Since all vocabulary sizes of English monolingual infants were only assessed in English, both *L1 vocabulary* and *total vocabulary* sizes were identical (see @fig-vocabulary-oxf).
-
-```{r fig-vocabulary-oxf}
-#| label: fig-vocabulary-oxf
-#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores from the recurrent participants are shown linked."
-#| fig-width: 4
-#| fig-height: 2.5
-vocabulary_oxf |> 
-	inner_join(filter(attrition_participants, is_valid_participant),
-			   by = join_by(session_id)) |> 
-	inner_join(select(participants, child_id, session_id, age_group),
-			   by = join_by(child_id, session_id)) |> 
-	ggplot(aes(age_group, l1_prop)) +
-	geom_line(aes(group = child_id),
-			  colour = "grey",
-			  alpha = 1/4, linewidth = 3/4) +
-	geom_dots(dotsize = 2,
-			  colour = clrs[5],
-			  fill = clrs[5],
-			  scale = 1,
-			  side = "both",
-			  alpha = 3/4) +
-	stat_summary(fun.data = mean_se,
-				 geom = "errorbar",
-				 linewidth = 1/2,
-				 width = 0.1,
-				 colour = "black",
-				 show.legend = FALSE) +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 size = 1.5,
-				 colour = "black",
-				 show.legend = FALSE) +
-	# geom_point(alpha = 1) +
-	labs(x = "Age (months)",
-		 y = "Vocabulary size",
-		 colour = "Group",
-		 fill = "Group") +
-	scale_y_continuous(labels = scales::percent,
-					   limits = c(0, 1)) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"),
-		  legend.position = "top",
-		  legend.title = element_blank())
-```
-
-### Stimuli
-
-New stimuli lists were generated to adapt the experimental procedure to English-learning infants.
-Stimuli lists were created following the same constraints as in Study 1.
-Auditory stimuli were recorded following the same procedure as in Study 1, produced by Southern British English native female speaker in a toddler-directed manner.
-Audio and picture processing were performed following the same workflow as in Study 1.
-
-### Procedure and apparatus
-
-Same as in Study 1.
-The study was run using a custom Matlab script, PresentMate, based on the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox].
-Visual fixations were recorded using a Tobii TX 300 eye-tracker and a 23-in screen of 1920 $\times$ 1080 resolution.
-The Tobii Analytics SDK 3.0 was used to interact with the eye-tracking while the experiment was running.
-Sampling rate was set at 120 Hz.
-A 9-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
-
-### Data analysis
-
-Same as in Study 1, but removing the *Group* predictor from the models, given that only monolingual infants were tested.
-
-```{r dataset_oxf}
-attrition_oxf <- filter(attrition, location=="Oxford")
-n_trials <- nrow(attrition_oxf)
-n_sessions <- n_distinct(attrition_oxf$session_id)
-n_participants <- n_distinct(attrition_oxf$child_id)
-n_trials_valid <- nrow(filter(attrition_oxf,
-							  is_valid_participant,
-							  is_valid_trial))
-n_sessions_valid <- attrition_oxf |> 
-	distinct(child_id, .keep_all = TRUE) |> 
-	pull(is_valid_participant) |> 
-	sum()
-
-n_participants_valid <- n_distinct(
-	attrition_oxf[attrition_oxf$is_valid_participant, ]$child_id)
-
-n_exc_prime <- sum(!attrition_oxf$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition_oxf$is_valid_gaze_test)
-n_exc_test_each <- sum(!attrition_oxf$is_valid_gaze_test_each)
-n_exc_participants <- sum(!attrition_oxf |> 
-						  	distinct(child_id, .keep_all = TRUE) |> 
-						  	pull(is_valid_participant), na.rm = TRUE)
-
-n_exc_participants_vocab <- attrition_oxf |> 
-	distinct(child_id, .keep_all = TRUE) |> 
-	mutate(is_valid_vocab_size = !is_valid_vocab_size) |> 
-	pull(is_valid_vocab_size) |> 
-	sum(na.rm = TRUE)
-
-n_longitudinal <- attrition_oxf |>
-	filter(is_valid_participant,
-		   is_valid_trial) |>
-	distinct(child_id, session_n) |> 
-	count(child_id, name = "times") |> 
-	count(times)
-
-n_trials_condition <- attrition_oxf |> 
-	filter(is_valid_participant) |> 
-	count(trial_type, is_valid_trial) %>%
-	split(janitor::make_clean_names(.$trial_type))
-```
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
-We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
-
-After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
-The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-From the trials included in the final dataset dataset, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), were `r n_trials_condition$non_cognate_2$n` *Related/Non-cognate* trials(`r n_trials_condition$non_cognate$n` previously excluded), and `r n_trials_condition$cognate_2$n` were *Related/Cognate* trials (`r n_trials_condition$cognate$n` previously excluded).
-
-## Results
-
-### Priming effects
-
-```{r coefs-oxf}
-var_labels <- c("b_Intercept" = "Intercept",
-				"b_age_std" = "Age (+1 SD)",
-				"b_condition1" = "Condition (U vs. RN)",
-				"b_condition2" = "Condition (RN vs. RC)")
-
-model_summary <- get_posterior_summary(model_fits_oxf$fit_oxf_1,
-									   data_bcn,
-									   vars_dict = var_labels,
-									   rope_interval = rope_interval)
-
-coefs <- model_summary |> 
-	mutate(.value = sprintf("%.3f", .value),
-		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
-		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
-	split(janitor::make_clean_names(model_summary$.variable))
-```
-
-Overall, the average participant' target looking time exceeded chance levels, as indicated by the fact that the 95% HDI of the intercept term excluded zero ($\beta$ = `r coefs$b_intercept$.value`, 95% HDI = `r coefs$b_intercept$.ci`) and all of its posterior samples fell outside of the ROPE.
-The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$b_age_std$.value`, 95% HDI = `r coefs$b_age_std$.ci`), and overlapped completely with the ROPE, indicating that participants from all ages showed equivalent overall target word recognition.
-The 95% HDI of the first contrast of the *Condition* predictor---comparing *Unrelated* and *Related/Non-cognate* trials---included zero ($\beta$ = `r coefs$b_condition1$.value`, 95% HDI = `r coefs$b_condition1$.ci`), and `r coefs$b_condition1$.rope` of its posterior samples fell within the ROPE.
-The 95% HDI of the second contrast---comparing *Related/Non-cognate* and *Related/Cognate* trials---also included zero ($\beta$ = `r coefs$b_condition2$.value`, 95% HDI = `r coefs$b_condition2$.ci`), and `r coefs$b_condition2$.rope` of its posterior samples fell within the ROPE.
-The overall target preference was equivalent across both pairwise condition comparisons.
-
-```{r tbl-coefs-oxf}
-#| label: tbl-coefs-oxf
-#| fig-cap: "Margin posterior mean predictions.
-A) Posterior mean predictions of the time course of target fixation in the test phase.
-B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
-Lines and intervals indicate the mean and 95% credible interval of the posterior predictions."
-#| echo: false
-#| eval: false
-#| message: false
-#| warning: false
-#| out-width: 80%
-
-# summarise posterior draws
-intercept_label <- paste0("Intercept (at ", round(mean(data_oxf$age), 2), " months)")
-
-tbl_data <- model_summary |>
-	select(.variable_name, .value, .lower, .upper, .rope, .type) |>
-	mutate(.variable_name = gsub("×", "$\\\\times$", .variable_name),
-		   .hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
-		   .rope = case_when(is.na(.rope) ~ "-",
-		   				  .rope > 0.9999 ~ "1",
-		   				  .rope < 0.00001 ~ "0",
-		   				  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope)))) |>
-	select(.variable_name, .value, .lower, .upper, .hdi, .rope)
-
-col_names <- c("", "$\\beta$", "95\\% HDI", "$p(\\text{ROPE})$")
-
-tbl_data |>
-	select(-c(.lower, .upper)) |>
-	kable(format = "latex",
-		  escape = FALSE,
-		  col.names = col_names,
-		  digits = 3,
-		  booktabs = TRUE,
-		  align = "lclr",
-		  linesep = "") |>
-	kable_styling() |>
-	add_footnote("$\\beta$: median of the posterior distribution in the probability scale.
-95\\% HDI: 95\\% highest density interval of the distribution.
-$p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
-```
-
-```{r timecourse-oxf}
-nd <- expand_grid(distinct(data_oxf, condition),
-				  timebin_std = timebin_values,
-				  age_std = 0)
-
-epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_1, 
-						  re_formula = NA,
-						  ndraws = NULL,
-						  value = ".epred")
-```
-
-An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds-oxf).
-Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
-
-```{r fig-epreds-oxf}
-#| label: fig-epreds-oxf
-#| fig-cap: "A) Posterior mean predictions of the time course of target fixation in the test phase.
-Thin lines represent 100 individual posterior predictions.
-Thick lines indicate the mean of the posterior predictions.
-B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
-Thin lines represent 100 individual posterior predictions.
-Black lines indicate the mean of the posterior predictions."
-#| fig-width: 6.5
-#| fig-height: 6.5
-epreds_summary <- epreds |> 
-	ungroup() |> 
-	summarise(.value = mean_qi(.epred)[[1]],
-			  .lower = mean_qi(.epred)[[2]],
-			  .upper = mean_qi(.epred)[[3]],
-			  .by = c(condition, timebin_std))
-
-plot_epreds <- epreds |> 
-	ggplot(aes(timebin_std, .epred,
-			   colour = condition,
-			   fill = condition,
-			   linetype = condition,
-			   shape = condition)) +
-	geom_hline(yintercept = 0,
-			   colour = "grey") +
-	# geom_line(aes(group = interaction(condition, .draw)),
-	# 		  alpha = 1/20,
-	# 		  linewidth = 3/4,
-	# 		  linetype = "solid") +
-	stat_summary(fun.data = mean_qi,
-				 geom = "ribbon",
-				 alpha = 1/4,
-				 linewidth = NA) +
-	stat_summary(fun = "mean",
-				 geom = "line",
-				 # colour = "black",
-				 linewidth = 3/4) +
-	stat_summary(data = data_oxf,
-				 aes(y = .elog),
-				 fun = "mean",
-				 geom = "point",
-				 size = 2) +
-	labs(x = "Time (ms)",
-		 y = "Logit (Target looking)",
-		 colour = "Condition",
-		 fill = "Condition",
-		 linetype = "Condition",
-		 shape = "Condition")
-
-epreds_diff <- epreds |> 
-	pivot_wider(id_cols = c(timebin_std, .draw),
-				names_from = "condition",
-				values_from = ".epred",
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff_1 = related_non_cognate - unrelated,
-		   diff_2 = related_cognate - related_non_cognate) |> 
-	pivot_longer(matches("diff"),
-				 names_to = "diff",
-				 values_to = ".epred",
-				 names_prefix = "diff_") |> 
-	mutate(diff = factor(diff,
-						 levels = c(1, 2),
-						 labels = c("Related/Non-cognate - Unrelated",
-						 		   "Related/Cognate - Related/Non-cognate")))
-
-plot_diffs <- epreds_diff |> 
-	ggplot(aes(timebin_std, .epred)) +
-	facet_wrap(~diff) +
-	# annotate(geom = "rect",
-	# 		 xmin = timebin_values[1],
-	# 		 xmax = timebin_values[length(timebin_values)],
-	# 		 ymin = rope_interval[1],
-	# 		 ymax = rope_interval[2],
-	# 		 fill = "red",
-	# 		 linewidth = 0,
-	# 		 alpha = 1/2,
-	# 		 linetype = "dotted") +
-	stat_summary(fun.data = mean_qi,
-				 geom = "ribbon",
-				 fill = "grey",
-				 linewidth = NA,
-				 alpha = 1/3) +
-	stat_summary(aes(group = diff),
-				 fun = mean,
-				 geom = "line",
-				 colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = rope_interval[1],
-			   colour = "red",
-			   linetype = "dotted") +
-	geom_hline(yintercept = rope_interval[2],
-			   colour = "red",
-			   linetype = "dotted") +
-	# geom_line(aes(group = interaction(diff, draw)),
-	# 		  alpha = 1/20,
-	# 		  linewidth = 3/4,
-	# 		  colour = "grey",
-	# 		  linetype = "solid") +
-
-	labs(x = "Time (ms)",
-		 y = "Logit P(Target looking)",
-		 colour = "Comparison",
-		 fill = "Comparison",
-		 linetype = "Comparison")
-
-plot_epreds + plot_diffs +
-	plot_layout(ncol = 1) &
-	plot_annotation(tag_levels = "A") &
-	# scale_y_continuous(limits = c(0.25, 0.75)) +
-	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
-										 mean(data_bcn$timebin),
-										 sd(data_bcn$timebin)),
-					   labels = \(x) format(seq(3e2, 2e3, 3e2),
-					   					 big.mark = ",")) &
-	theme(legend.position = "top",
-		  legend.title = element_blank(),
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
-```
-
-### The role of age and vocabulary size on priming effects
-
-@tbl-loos-oxf shows a comparison between models including *Age* ($\mathcal{M}_{2}$), and *L1 vocabulary* ($\mathcal{M}_{3}$)---and their two-way and two-way interaction with *Condition*---against model $\mathcal{M}_{1}$, which only included *Age* as a covariate suggested that all models performed equivalently, with model $\mathcal{M}_{2}$ showing a slightly better performance.
-Overall, this suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account *L1 vocabulary*, or *Total vocabulary* sizes.
-
-```{r tbl-loos-oxf}
-#| label: tbl-loos-oxf
-#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 2."
-loo_compare(model_loos_oxf[2:4]) |> 
-	as.data.frame() |> 
-	rownames_to_column("model") |> 
-	mutate(model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model))-1),
-		   across(matches("diff"),
-		   	   \(x) {x[1] <- NA; return(x)}),
-		   model = case_when(model=="Model 1" ~ "Model 1 (Age)",
-		   				  model=="Model 2" ~ "Model 2 (L1 vocabulary)",
-		   				  model=="Model 3" ~ "Model 3 (Total vocabulary)",
-		   				  .default = model)) |> 
-	select(model, matches("elpd|diff")) |> 
-	relocate(matches("diff"), .after = matches("loo")) |> 
-	gt(rowname_col = "model") |> 
-	fmt_number(is.numeric) |> 
-	cols_label(elpd_diff = "ELPD (diff.)",
-			   se_diff = "SE ELPD (diff)",
-			   elpd_loo = "ELPD",
-			   se_elpd_loo = "SE ELPD") |> 
-	fmt_missing(missing_text = "---") |> 
-	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new dataset.
-*SE \\(ELPD\\)*: standard error of the *ELPD*, which indictes the uncertainty about the predictive performance for unknown future data.
-*ELPD (diff)*: pairwise difference in *ELPD* for two models.
-The difference is computed relative to the model with lowest *ELPD* (best fitting model).
-*SE ELPD (diff.)*: standard error of component-wise differences of *ELPD* between two models.")) |>
-	tab_style(cell_text(style = "italic"), cells_column_labels())
-```
-
-### Word recognition times
-
-```{r recognition-oxf}
-nd <- expand_grid(distinct(data_oxf, condition),
-				  timebin_std = timebin_values,
-				  age_std = age_values)
-
-epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_2, 
-						  re_formula = NA,
-						  ndraws = NULL,
-						  value = ".epred")
-
-epreds_chance <- epreds |> 
-	median_hdci() |> 
-	mutate(is_lower_positive = .lower > 0) |> 
-	filter(is_lower_positive) |> 
-	summarise(over_chance = min(timebin_std),
-			  .by = c(condition, age_std)) |> 
-	mutate(over_chance = (over_chance * 
-						  	sd(data_oxf$timebin) +
-						  	mean(data_oxf$timebin))*100+300)
-
-epreds_chance_report <- epreds_chance |> 
-	mutate(over_chance = sprintf("%.2f", over_chance),
-		   age_std = factor(x = age_std,
-		   				 levels = age_values,
-		   				 labels = paste0(c(20, 30), " months"))) |> 
-	arrange(age_std) %>%
-	split(paste0("age_", gsub(" months", "", .$age_std)))
-```
-
-As expected, the recognition times were on average shorter for older infants than for younger infants.
-Differences between conditions were larger in bilinguals than in monolinguals, especially in the older group.
-The recognition time for monolingual 20-month-olds was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-
-```{r fig-recognition-oxf}
-#| label: fig-recognition-oxf
-#| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
-#| fig-width: 5
-#| fig-height: 3.5
-epreds_chance |> 
-	mutate(age_std = factor(x = age_std,
-							levels = age_values,
-							labels = paste0(c(20, 32), " months"))) |> 
-	ggplot(aes(age_std, over_chance,
-			   colour = sort(condition),
-			   fill = sort(condition))) + 
-	geom_point(shape = 16, size = 4) +
-	geom_line(aes(group = condition),
-			  linewidth = 1) +
-	# geom_point(size = 3) +
-	labs(x = "Group",
-		 y = "Recognition time (ms)",
-		 colour = "Condition",
-		 fill = "Condition") +
-	scale_y_continuous(breaks = seq(0, 1e3L, 25)) +
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  panel.grid.minor.y = element_line(colour = "grey",
-		  								  linetype = "dotted"),
-		  legend.position = "top",
-		  axis.title.x = element_blank())
-```
-
-## Discussion
-
-Study 2 was aimed at investigating whether the phonological priming effects previously reported @mani2010infant and @mani2011phonological could be found using the adaptation of the implicit naming task form Study 1 in a sample with equivalent demographic characteristics to the original studies.
-Results from Study 2 did not provide any evidence in favour of phonological priming.
-English monolingual participants from all ages showed an equivalent pattern of target looking across both related and unrelated trials.
-The absence of a phonological priming effect suggest that either English monolinguals did not generate implicit labels for the prime pictures presented in silence, or that if generated, such labels did not interact with the subsequent recognition of the target word.
-Both candidate explanations conflict with both Mani and Plunkett's studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects [@duta2012erp; @styles2015infant].
-
-One of the main differences between the implicit naming paradigm used by @mani2010infant and the one in Studies 1 and 2 is the fact that target labels were auditorily presented before target and distractor pictures were presented on screen.
-The rationale behind this decision was to minimise the amount of time elapsed between the presentation of the prime and target labels, in order to facilitate any potential priming effects.
-By presenting the auditory target label immediately after the offset of the prime picture, the internally generated prime phonological form would be more likely to affect the activation of the target lexical representation.
-It is possible that this difference in task design might have led to the contrasting outcomes of Mani and Plunkett and the present study.
-Given that participants were not presented with the target and distractor pictures until after the target label was auditorily presented, one possibility is that participants faced the additional task of exploring both pictures to find the target referent, which infants in @mani2010infant did not have to do, because of the pre-naming presentation of target and distractor in the test phase.
-This visual exploration of the screen might have increased the cognitive load of the task, rendering the potential effect of phonological priming to a weaker, undetectable effect.
-Overall, the results from Study 2 support a more methodological explanation of the null pattern of results in Study 1, in which the lack of a phonological priming effect---both within and across languages---might be explained by differences in task design or replicability concerns.
 
@@
 
+Previous studies had reported similar cross-language priming effects, but the conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was nonetheless unwarranted.
+In studies where the auditorily presented prime label was phonologically overlapped with the target label [e.g., @marian1999activation], priming effects could be explained by sub-lexical facilitation across phonological segments.
+This might explain the facilitation effect found in *phonological priming* trials in @von2012language, in which English prime and German target labels shared overt phonological overlap.
+In contrast, the interference effect found in *priming through translation* trials points to cross-language competition at the lexical level.
+Since participants' target recognition was modulated by the phonology of the German translation of the prime (which participants did *not* hear), cross-language priming can be explained by the lexical co-activation of the English *and* German prime labels.
+
 # References

### 2023-11-20 manuscript/manuscript.qmd
Merge

--- 2023-11-20 manuscript/manuscript.qmd
@@
 # load objects
-targets::tar_config_set(store = here::here("_targets"),
-						script = here::here("_targets.R"))
+targets::tar_config_set(
+    store = here::here("_targets"),
+    script = here::here("_targets.R")
+)
 
@@
 targets::tar_load(
-	c(participants,
+    c(
+        participants,
         stimuli,
@@
         data_oxf
-	))
+    )
+)
 
 targets::tar_load(
-	c(model_fits_bcn,
+    c(
+        model_fits_bcn,
         model_loos_bcn,
@@
         model_loos_oxf
-	))
+    )
+)
 
 # prepare data
-attrition <- lst(participants,
+attrition <- lst(
+    participants,
     attrition_participants,
-				 attrition_trials) |>
+    attrition_trials
+) |>
     reduce(inner_join, by = join_by(session_id)) |>
@@
 my_theme <- theme_minimal() +
-	theme(panel.grid = element_blank(),
+    theme(
+        panel.grid = element_blank(),
         axis.line = element_line(colour = "black"),
         text = element_text(size = 12, colour = "black"),
-		  axis.text = element_text(colour = "black"))
+        axis.text = element_text(colour = "black")
+    )
 
@@
 
-options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
+options(
+    ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
     ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
@@
     ggplot2.continuous.fill = ggplot2::scale_color_gradient,
-		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
+    ggplot2.continuous.colour = ggplot2::scale_color_gradient
+)
 
@@
 #| label: participants-numbers-oxf
-participants_oxf <- filter(participants, location=="Oxford")
+participants_oxf <- filter(participants, location == "Oxford")
 
@@
 ages <- participants_oxf |>
-	summarise(n = n(),
+    summarise(
+        n = n(),
         n_participants = n_distinct(child_id),
@@
         age_vctr = list(age),
-			  .by = c(lp, test_language))
+        .by = c(lp, test_language)
+    )
 
@@
         filter(child_id %in% participants_oxf$child_id[duplicated(participants_oxf$child_id)]) |>
-		pivot_wider(id_cols = child_id, 
+        pivot_wider(
+            id_cols = child_id,
             names_from = session_n,
             values_from = age,
-					names_repair = janitor::make_clean_names) |> 
+            names_repair = janitor::make_clean_names
+        ) |>
         rowwise() |>
-		mutate(diff_min = x2-x1) |> 
+        mutate(diff_min = x2 - x1) |>
         ungroup() |>
@@
     select(participants_oxf, session_id),
-							 by = join_by(session_id))
+    by = join_by(session_id)
+)
 ```
@@
     inner_join(filter(attrition_participants, is_valid_participant),
-			   by = join_by(session_id)) |> 
+        by = join_by(session_id)
+    ) |>
     inner_join(select(participants, child_id, session_id, age_group),
-			   by = join_by(child_id, session_id)) |> 
+        by = join_by(child_id, session_id)
+    ) |>
     ggplot(aes(age_group, l1_prop)) +
@@
         colour = "grey",
-			  alpha = 1/4, linewidth = 3/4) +
-	geom_dots(dotsize = 2,
+        alpha = 1 / 4, linewidth = 3 / 4
+    ) +
+    geom_dots(
+        dotsize = 2,
         colour = clrs[5],
@@
         side = "both",
-			  alpha = 3/4) +
-	stat_summary(fun.data = mean_se,
+        alpha = 3 / 4
+    ) +
+    stat_summary(
+        fun.data = mean_se,
         geom = "errorbar",
-				 linewidth = 1/2,
+        linewidth = 1 / 2,
         width = 0.1,
         colour = "black",
-				 show.legend = FALSE) +
-	stat_summary(fun = mean,
+        show.legend = FALSE
+    ) +
+    stat_summary(
+        fun = mean,
         geom = "point",
@@
         colour = "black",
-				 show.legend = FALSE) +
+        show.legend = FALSE
+    ) +
     # geom_point(alpha = 1) +
-	labs(x = "Age (months)",
+    labs(
+        x = "Age (months)",
         y = "Vocabulary size",
         colour = "Group",
-		 fill = "Group") +
-	scale_y_continuous(labels = scales::percent,
-					   limits = c(0, 1)) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"),
+        fill = "Group"
+    ) +
+    scale_y_continuous(
+        labels = scales::percent,
+        limits = c(0, 1)
+    ) +
+    theme(
+        panel.grid.major.y = element_line(
+            linetype = "dotted",
+            colour = "grey"
+        ),
         legend.position = "top",
-		  legend.title = element_blank())
+        legend.title = element_blank()
+    )
 ```
@@
     distinct(session_id, child_id, .keep_all = TRUE) |>
-	summarise(n = n(),
+    summarise(
+        n = n(),
         n_participants = length(unique(child_id)),
@@
         # age_vctr = list(age),
-			  .by = c(lp, test_language)) |> 
-	gt(rowname_col = "test_language",
-	   groupname_col = "lp") |> 
-	summary_rows(groups = c("Monolingual", "Bilingual"),
+        .by = c(lp, test_language)
+    ) |>
+    gt(
+        rowname_col = "test_language",
+        groupname_col = "lp"
+    ) |>
+    summary_rows(
+        groups = c("Monolingual", "Bilingual"),
         columns = matches("age"),
         fns = list(Total ~ mean(.)),
-				 fmt = ~ fmt_number(., decimals = 1, use_seps = FALSE)) |> 
-	summary_rows(groups = c("Monolingual", "Bilingual"),
+        fmt = ~ fmt_number(., decimals = 1, use_seps = FALSE)
+    ) |>
+    summary_rows(
+        groups = c("Monolingual", "Bilingual"),
         columns = c(n, n_participants),
         fns = list(Total ~ sum(.)),
-				 fmt = ~ fmt_integer(.)) |> 
-	summary_rows(groups = c("Monolingual", "Bilingual"),
+        fmt = ~ fmt_integer(.)
+    ) |>
+    summary_rows(
+        groups = c("Monolingual", "Bilingual"),
         columns = matches("doe"),
         fns = list(Total ~ mean(.)),
-				 fmt = ~ fmt_number(., decimals = 1, scale_by = 100)) |> 
-	grand_summary_rows(columns = matches("age"),
+        fmt = ~ fmt_number(., decimals = 1, scale_by = 100)
+    ) |>
+    grand_summary_rows(
+        columns = matches("age"),
         fns = list(Total ~ mean(.)),
-					   fmt = ~ fmt_number(., decimals = 1)) |> 
-	grand_summary_rows(columns = matches("doe"),
+        fmt = ~ fmt_number(., decimals = 1)
+    ) |>
+    grand_summary_rows(
+        columns = matches("doe"),
         fns = list(Total ~ mean(.)),
-					   fmt = ~ fmt_number(., decimals = 1, scale_by = 100)) |> 
-	grand_summary_rows(columns = c(n, n_participants),
+        fmt = ~ fmt_number(., decimals = 1, scale_by = 100)
+    ) |>
+    grand_summary_rows(
+        columns = c(n, n_participants),
         fns = list(Total ~ sum(.)),
-					   fmt = ~ fmt_integer(.)) |> 
+        fmt = ~ fmt_integer(.)
+    ) |>
     # gt_plt_dist(age_vctr, type = "histogram") |>
@@
     cols_merge(c(age_min, age_max),
-			   pattern = "{1}-{2}") |> 
+        pattern = "{1}-{2}"
+    ) |>
     cols_merge(c(age_mean, age_sd),
-			   pattern = "{1} ({2})") |> 
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(doe_catalan_mean, doe_catalan_sd),
-			   pattern = "{1} ({2})") |> 
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(doe_english_mean, doe_english_sd),
-			   pattern = "{1} ({2})") |> 
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(doe_spanish_mean, doe_spanish_sd),
-			   pattern = "{1} ({2})") |> 
+        pattern = "{1} ({2})"
+    ) |>
     tab_spanner("Age (months)", matches("age")) |>
@@
     tab_spanner("Degree of Exposure (%)", matches("doe")) |>
-	cols_label(n = "Sessions",
+    cols_label(
+        n = "Sessions",
         n_participants = "Participants",
@@
         doe_english_mean = "M (SD)",
-			   doe_spanish_mean = "M (SD)") |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_spanners())
+        doe_spanish_mean = "M (SD)"
+    ) |>
+    tab_style(
+        cell_text(style = "italic"),
+        cells_column_labels()
+    ) |>
+    tab_style(
+        cell_text(style = "italic"),
+        cells_column_spanners()
+    )
 ```
@@
     inner_join(select(participants_bcn, session_id, lp, age_group),
-			   by = join_by(session_id))
+        by = join_by(session_id)
+    )
 
@@
         n = n(),
-			  .by = c(age_group, lp)) %>%
+        .by = c(age_group, lp)
+    ) %>%
     mutate(across(matches("prop"), scales::percent)) %>%
@@
 n_imputed <- table(vocabulary_bcn$is_imputed)[2]
-prop_imputed <- scales::percent(n_imputed/nrow(vocabulary_bcn))
+prop_imputed <- scales::percent(n_imputed / nrow(vocabulary_bcn))
 n_pool <- nrow(bvq_data$vocabulary)
@@
     inner_join(filter(attrition_participants, is_valid_participant),
-			   by = join_by(session_id)) |> 
+        by = join_by(session_id)
+    ) |>
     pivot_longer(c(total_prop, l1_prop),
@@
         values_to = "prop",
-				 names_transform = \(x) gsub("_prop", "", x)) |> 
-	mutate(measure = if_else(measure=="l1", 
+        names_transform = \(x) gsub("_prop", "", x)
+    ) |>
+    mutate(
+        measure = if_else(measure == "l1",
             "L1 vocabulary",
-							 "Total vocabulary"),
+            "Total vocabulary"
+        ),
         is_imputed = if_else(is_imputed, "Imputed", "Observed") |>
-		   	factor(levels = c("Observed", "Imputed"))) |> 
+            factor(levels = c("Observed", "Imputed"))
+    ) |>
     ggplot(aes(age_group, prop,
         colour = lp,
-			   fill = lp)) +
+        fill = lp
+    )) +
     facet_wrap(~measure) +
@@
         colour = "grey",
-			  alpha = 1/4, linewidth = 3/4) +
-	geom_dots(aes(side = if_else(lp=="Monolingual", "left", "right")),
+        alpha = 1 / 4, linewidth = 3 / 4
+    ) +
+    geom_dots(aes(side = if_else(lp == "Monolingual", "left", "right")),
         dotsize = 2,
-			  stroke = 1/2,
+        stroke = 1 / 2,
         scale = 0.5,
-			  alpha = 3/4) +
-	stat_summary(fun.data = mean_se,
+        alpha = 3 / 4
+    ) +
+    stat_summary(
+        fun.data = mean_se,
         geom = "errorbar",
-				 linewidth = 1/2,
+        linewidth = 1 / 2,
         width = 0.15,
@@
         show.legend = FALSE,
-				 position = position_dodge(width = 1.15)) +
-	stat_summary(fun = mean,
+        position = position_dodge(width = 1.15)
+    ) +
+    stat_summary(
+        fun = mean,
         geom = "point",
@@
         show.legend = FALSE,
-				 position = position_dodge(width = 1.15)) +
+        position = position_dodge(width = 1.15)
+    ) +
     # geom_point(alpha = 1) +
-	labs(x = "Age (months)",
+    labs(
+        x = "Age (months)",
         y = "Vocabulary size",
         colour = "Group",
-		 fill = "Group") +
-	scale_y_continuous(labels = scales::percent,
-					   limits = c(0, 1)) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"),
+        fill = "Group"
+    ) +
+    scale_y_continuous(
+        labels = scales::percent,
+        limits = c(0, 1)
+    ) +
+    theme(
+        panel.grid.major.y = element_line(
+            linetype = "dotted",
+            colour = "grey"
+        ),
         legend.position = "top",
-		  legend.title = element_blank())
+        legend.title = element_blank()
+    )
 ```
@@
 ```{r dataset_oxf}
-attrition_oxf <- filter(attrition, location=="Oxford")
+attrition_oxf <- filter(attrition, location == "Oxford")
 n_trials <- nrow(attrition_oxf)
@@
 n_participants <- n_distinct(attrition_oxf$child_id)
-n_trials_valid <- nrow(filter(attrition_oxf,
+n_trials_valid <- nrow(filter(
+    attrition_oxf,
     is_valid_participant,
-							  is_valid_trial))
+    is_valid_trial
+))
 n_sessions_valid <- attrition_oxf |>
@@
 n_participants_valid <- n_distinct(
-	attrition_oxf[attrition_oxf$is_valid_participant, ]$child_id)
+    attrition_oxf[attrition_oxf$is_valid_participant, ]$child_id
+)
 
@@
 n_longitudinal <- attrition_oxf |>
-	filter(is_valid_participant,
-		   is_valid_trial) |>
+    filter(
+        is_valid_participant,
+        is_valid_trial
+    ) |>
     distinct(child_id, session_n) |>
@@
 ```{r coefs-oxf}
-var_labels <- c("b_Intercept" = "Intercept",
+var_labels <- c(
+    "b_Intercept" = "Intercept",
     "b_age_std" = "Age (+1 SD)",
     "b_condition1" = "Condition (U vs. RN)",
-				"b_condition2" = "Condition (RN vs. RC)")
+    "b_condition2" = "Condition (RN vs. RC)"
+)
 
@@
     vars_dict = var_labels,
-									   rope_interval = rope_interval)
+    rope_interval = rope_interval
+)
 
 coefs <- model_summary |>
-	mutate(.value = sprintf("%.3f", .value),
+    mutate(
+        .value = sprintf("%.3f", .value),
         .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
-		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
+        .rope = scales::percent(.rope, accuracy = 0.01)
+    ) |>
     split(janitor::make_clean_names(model_summary$.variable))
@@
     select(.variable_name, .value, .lower, .upper, .rope, .type) |>
-	mutate(.variable_name = gsub("×", "$\\\\times$", .variable_name),
+    mutate(
+        .variable_name = gsub("×", "$\\\\times$", .variable_name),
         .hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
@@
             .rope < 0.00001 ~ "0",
-		   				  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope)))) |>
+            .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope))
+        )
+    ) |>
     select(.variable_name, .value, .lower, .upper, .hdi, .rope)
@@
     select(-c(.lower, .upper)) |>
-	kable(format = "latex",
+    kable(
+        format = "latex",
         escape = FALSE,
@@
         align = "lclr",
-		  linesep = "") |>
+        linesep = ""
+    ) |>
     kable_styling() |>
@@
     timebin_std = timebin_values,
-				  age_std = 0)
+    age_std = 0
+)
 
@@
     ndraws = NULL,
-						  value = ".epred")
+    value = ".epred"
+)
 ```
@@
     ungroup() |>
-	summarise(.value = mean_qi(.epred)[[1]],
+    summarise(
+        .value = mean_qi(.epred)[[1]],
         .lower = mean_qi(.epred)[[2]],
         .upper = mean_qi(.epred)[[3]],
-			  .by = c(condition, timebin_std))
+        .by = c(condition, timebin_std)
+    )
 
@@
         linetype = condition,
-			   shape = condition)) +
-	geom_hline(yintercept = 0,
-			   colour = "grey") +
+        shape = condition
+    )) +
+    geom_hline(
+        yintercept = 0,
+        colour = "grey"
+    ) +
     # geom_line(aes(group = interaction(condition, .draw)),
@@
     # 		  linetype = "solid") +
-	stat_summary(fun.data = mean_qi,
+    stat_summary(
+        fun.data = mean_qi,
         geom = "ribbon",
-				 alpha = 1/4,
-				 linewidth = NA) +
-	stat_summary(fun = "mean",
+        alpha = 1 / 4,
+        linewidth = NA
+    ) +
+    stat_summary(
+        fun = "mean",
         geom = "line",
         # colour = "black",
-				 linewidth = 3/4) +
-	stat_summary(data = data_oxf,
+        linewidth = 3 / 4
+    ) +
+    stat_summary(
+        data = data_oxf,
         aes(y = .elog),
@@
         geom = "point",
-				 size = 2) +
-	labs(x = "Time (ms)",
+        size = 2
+    ) +
+    labs(
+        x = "Time (ms)",
         y = "Logit (Target looking)",
@@
         linetype = "Condition",
-		 shape = "Condition")
+        shape = "Condition"
+    )
 
 epreds_diff <- epreds |>
-	pivot_wider(id_cols = c(timebin_std, .draw),
+    pivot_wider(
+        id_cols = c(timebin_std, .draw),
         names_from = "condition",
         values_from = ".epred",
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff_1 = related_non_cognate - unrelated,
-		   diff_2 = related_cognate - related_non_cognate) |> 
+        names_repair = janitor::make_clean_names
+    ) |>
+    mutate(
+        diff_1 = related_non_cognate - unrelated,
+        diff_2 = related_cognate - related_non_cognate
+    ) |>
     pivot_longer(matches("diff"),
@@
         values_to = ".epred",
-				 names_prefix = "diff_") |> 
+        names_prefix = "diff_"
+    ) |>
     mutate(diff = factor(diff,
         levels = c(1, 2),
-						 labels = c("Related/Non-cognate - Unrelated",
-						 		   "Related/Cognate - Related/Non-cognate")))
+        labels = c(
+            "Related/Non-cognate - Unrelated",
+            "Related/Cognate - Related/Non-cognate"
+        )
+    ))
 
@@
     # 		 linetype = "dotted") +
-	stat_summary(fun.data = mean_qi,
+    stat_summary(
+        fun.data = mean_qi,
         geom = "ribbon",
@@
         linewidth = NA,
-				 alpha = 1/3) +
+        alpha = 1 / 3
+    ) +
     stat_summary(aes(group = diff),
@@
         colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = rope_interval[1],
+        linewidth = 3 / 4
+    ) +
+    geom_hline(
+        yintercept = rope_interval[1],
         colour = "red",
-			   linetype = "dotted") +
-	geom_hline(yintercept = rope_interval[2],
+        linetype = "dotted"
+    ) +
+    geom_hline(
+        yintercept = rope_interval[2],
         colour = "red",
-			   linetype = "dotted") +
+        linetype = "dotted"
+    ) +
     # geom_line(aes(group = interaction(diff, draw)),
@@
 
-	labs(x = "Time (ms)",
+    labs(
+        x = "Time (ms)",
         y = "Logit P(Target looking)",
@@
         fill = "Comparison",
-		 linetype = "Comparison")
+        linetype = "Comparison"
+    )
 
@@
     # scale_y_continuous(limits = c(0.25, 0.75)) +
-	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
+    scale_x_continuous(
+        breaks = make_std(
+            seq(0, 17, 3),
             mean(data_bcn$timebin),
-										 sd(data_bcn$timebin)),
+            sd(data_bcn$timebin)
+        ),
         labels = \(x) format(seq(3e2, 2e3, 3e2),
-					   					 big.mark = ",")) &
-	theme(legend.position = "top",
+            big.mark = ","
+        )
+    ) &
+    theme(
+        legend.position = "top",
         legend.title = element_blank(),
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
+        panel.grid.major.y = element_line(
+            colour = "grey",
+            linetype = "dotted"
+        )
+    )
 ```
@@
     rownames_to_column("model") |>
-	mutate(model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model))-1),
-		   across(matches("diff"),
-		   	   \(x) {x[1] <- NA; return(x)}),
-		   model = case_when(model=="Model 1" ~ "Model 1 (Age)",
-		   				  model=="Model 2" ~ "Model 2 (L1 vocabulary)",
-		   				  model=="Model 3" ~ "Model 3 (Total vocabulary)",
-		   				  .default = model)) |> 
+    mutate(
+        model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model)) - 1),
+        across(
+            matches("diff"),
+            \(x) {
+                x[1] <- NA
+                return(x)
+            }
+        ),
+        model = case_when(model == "Model 1" ~ "Model 1 (Age)",
+            model == "Model 2" ~ "Model 2 (L1 vocabulary)",
+            model == "Model 3" ~ "Model 3 (Total vocabulary)",
+            .default = model
+        )
+    ) |>
     select(model, matches("elpd|diff")) |>
@@
     fmt_number(is.numeric) |>
-	cols_label(elpd_diff = "ELPD (diff.)",
+    cols_label(
+        elpd_diff = "ELPD (diff.)",
         se_diff = "SE ELPD (diff)",
         elpd_loo = "ELPD",
-			   se_elpd_loo = "SE ELPD") |> 
+        se_elpd_loo = "SE ELPD"
+    ) |>
     fmt_missing(missing_text = "---") |>
@@
     timebin_std = timebin_values,
-				  age_std = age_values)
+    age_std = age_values
+)
 
@@
     ndraws = NULL,
-						  value = ".epred")
+    value = ".epred"
+)
 
@@
     filter(is_lower_positive) |>
-	summarise(over_chance = min(timebin_std),
-			  .by = c(condition, age_std)) |> 
+    summarise(
+        over_chance = min(timebin_std),
+        .by = c(condition, age_std)
+    ) |>
     mutate(over_chance = (over_chance *
         sd(data_oxf$timebin) +
-						  	mean(data_oxf$timebin))*100+300)
+        mean(data_oxf$timebin)) * 100 + 300)
 
 epreds_chance_report <- epreds_chance |>
-	mutate(over_chance = sprintf("%.2f", over_chance),
-		   age_std = factor(x = age_std,
+    mutate(
+        over_chance = sprintf("%.2f", over_chance),
+        age_std = factor(
+            x = age_std,
             levels = age_values,
-		   				 labels = paste0(c(20, 30), " months"))) |> 
+            labels = paste0(c(20, 30), " months")
+        )
+    ) |>
     arrange(age_std) %>%
@@
 epreds_chance |>
-	mutate(age_std = factor(x = age_std,
+    mutate(age_std = factor(
+        x = age_std,
         levels = age_values,
-							labels = paste0(c(20, 32), " months"))) |> 
+        labels = paste0(c(20, 32), " months")
+    )) |>
     ggplot(aes(age_std, over_chance,
         colour = sort(condition),
-			   fill = sort(condition))) + 
+        fill = sort(condition)
+    )) +
     geom_point(shape = 16, size = 4) +
     geom_line(aes(group = condition),
-			  linewidth = 1) +
+        linewidth = 1
+    ) +
     # geom_point(size = 3) +
-	labs(x = "Group",
+    labs(
+        x = "Group",
         y = "Recognition time (ms)",
         colour = "Condition",
-		 fill = "Condition") +
+        fill = "Condition"
+    ) +
     scale_y_continuous(breaks = seq(0, 1e3L, 25)) +
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  panel.grid.minor.y = element_line(colour = "grey",
-		  								  linetype = "dotted"),
+    theme(
+        panel.grid.major.y = element_line(
+            colour = "grey",
+            linetype = "dotted"
+        ),
+        panel.grid.minor.y = element_line(
+            colour = "grey",
+            linetype = "dotted"
+        ),
         legend.position = "top",
-		  axis.title.x = element_blank())
+        axis.title.x = element_blank()
+    )
 ```
@@
 #| label: participants-numbers
-participants_bcn <- filter(participants, location=="Barcelona")
+participants_bcn <- filter(participants, location == "Barcelona")
 
@@
         filter(child_id %in% participants_bcn$child_id[duplicated(participants_bcn$child_id)]) |>
-		pivot_wider(id_cols = child_id, 
+        pivot_wider(
+            id_cols = child_id,
             names_from = session_n,
             values_from = age,
-					names_repair = janitor::make_clean_names) |> 
+            names_repair = janitor::make_clean_names
+        ) |>
         rowwise() |>
-		mutate(diff_1 = x2-x1, diff_2 = x3-x2, 
+        mutate(
+            diff_1 = x2 - x1, diff_2 = x3 - x2,
             diff_min = min(diff_1, diff_2, na.rm = TRUE),
-			   diff_max = max(diff_1, diff_2, na.rm = TRUE)) |> 
+            diff_max = max(diff_1, diff_2, na.rm = TRUE)
+        ) |>
         ungroup() |>
-		summarise(diff_min = min(diff_min, na.rm = TRUE), 
-				  diff_max = max(diff_max, na.rm = TRUE))
+        summarise(
+            diff_min = min(diff_min, na.rm = TRUE),
+            diff_max = max(diff_max, na.rm = TRUE)
+        )
 })
@@
         doe_english_mean = "M (SD)",
-			   doe_spanish_mean = "M (SD)") |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_spanners())
+        doe_spanish_mean = "M (SD)"
+    ) |>
+    tab_style(
+        cell_text(style = "italic"),
+        cells_column_labels()
+    ) |>
+    tab_style(
+        cell_text(style = "italic"),
+        cells_column_spanners()
+    )
 
@@
 stimuli |>
-	summarise(across(c(matches("familiarity_|freq_|animate_"), duration),
-					 tibble::lst(mean, sd, min, max)),
-			  .by = c(test_language, trial_type)) |> 
-	select(-matches("familiarity_se"), -matches("prime"),
-		   -c(is_animate_target_sd,
-		      is_animate_target_min,
-		      is_animate_target_max),
-		   -matches("min"), -matches("max")) |> 
-	gt(groupname_col = "test_language",
-	   rowname_col = "list") |> 
-	fmt_number(is.numeric,
-			   decimals = 1) |> 
-	fmt_number(matches("familiarity|animate"),
-			   scale_by = 100,
-			   decimals = 1) |> 
+    unnest_wider(c(freq, nphon)) |>
+    filter(test_language != "English") |>
+    summarise(
+        across(
+            c(matches("n_phon|freq_|lv_|nphon"), duration),
+            list(
+                mean = \(x) mean(x, na.rm = TRUE),
+                sd = \(x) sd(x, na.rm = TRUE)
+            )
+        ),
+        .by = c(trial_type)
+    ) |>
+    select(-matches("distractor")) |>
+    gt(
+        rowname_col = "trial_type",
+        groupname_col = "test_language"
+    ) |>
+    # summary_rows(groups = c("Unrelated", "Non-cognate", "Cognate"),
+    # 			 columns = is.numeric,
+    # 			 fns = list(Total ~ mean(.)),
+    # 			 fmt = ~ fmt_number(., decimals = 2)) |>
+    grand_summary_rows(
+        columns = is.numeric,
+        fns = list(Total ~ mean(.)),
+        fmt = ~ fmt_number(., decimals = 2)
+    ) |>
+    tab_spanner("Phonemes", matches("nphon")) |>
+    tab_spanner("Frequency (Zipf)", matches("freq")) |>
+    tab_spanner("Phon. similarity [0-1]", matches("lv")) |>
+    fmt_number(is.numeric, decimals = 1) |>
+    cols_merge(c(freq_prime_mean, freq_prime_sd),
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(freq_target_mean, freq_target_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(familiarity_target_mean, familiarity_target_sd),
-			   pattern = "{1} ({2})") |> 
+        pattern = "{1} ({2})"
+    ) |>
+    cols_merge(c(nphon_prime_mean, nphon_prime_sd),
+        pattern = "{1} ({2})"
+    ) |>
+    cols_merge(c(nphon_target_mean, nphon_target_sd),
+        pattern = "{1} ({2})"
+    ) |>
+    cols_merge(c(lv_pp_mean, lv_pp_sd),
+        pattern = "{1} ({2})"
+    ) |>
+    cols_merge(c(lv_pt_mean, lv_pt_sd),
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(duration_mean, duration_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_label(trial_type = "",
-			   familiarity_target_mean = "Prevalence (%)",
-			   freq_target_mean = "Frequency",
-			   is_animate_target_mean = "Animacy (%)",
-			   duration_mean = "Duration (s)") 
+        pattern = "{1} ({2})"
+    ) |>
+    cols_label(
+        trial_type = "",
+        freq_prime_mean = "Prime",
+        freq_target_mean = "Target",
+        lv_pp_mean = "Prime-Prime",
+        lv_pt_mean = "Prime-Target",
+        duration_mean = "Audio duration (s)",
+        nphon_prime_mean = "Prime",
+        nphon_target_mean = "Target"
+    ) |>
+    tab_style(
+        cell_text(style = "italic"),
+        list(
+            cells_column_labels(),
+            cells_column_spanners(),
+            cells_grand_summary()
+        )
+    )
 ```
@@
 ```{r dataset}
-attrition_bcn <- filter(attrition, location=="Barcelona")
+attrition_bcn <- filter(attrition, location == "Barcelona")
 n_trials <- nrow(attrition_bcn)
@@
 n_participants <- n_distinct(attrition_bcn$child_id)
-n_trials_valid <- nrow(filter(attrition_bcn,
+n_trials_valid <- nrow(filter(
+    attrition_bcn,
     is_valid_participant,
-							  is_valid_trial))
+    is_valid_trial
+))
 n_sessions_valid <- sum(distinct(attrition_bcn,
     session_id,
-								 .keep_all = TRUE)$is_valid_participant)
+    .keep_all = TRUE
+)$is_valid_participant)
 n_participants_valid <- n_distinct(
-	attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id)
+    attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id
+)
 
@@
     session_id,
-									.keep_all = TRUE)$is_valid_participant) 
+    .keep_all = TRUE
+)$is_valid_participant)
 n_exc_participants_vocab <- sum(!distinct(attrition_bcn,
     session_id,
-										  .keep_all = TRUE)$is_valid_vocab_size)
+    .keep_all = TRUE
+)$is_valid_vocab_size)
 
 n_longitudinal <- attrition_bcn |>
-	filter(is_valid_participant,
-		   is_valid_trial) |>
+    filter(
+        is_valid_participant,
+        is_valid_trial
+    ) |>
     distinct(child_id, session_n) |>
@@
     count(is_valid_participant, lp) |>
-	pivot_wider(names_from = is_valid_participant,
+    pivot_wider(
+        names_from = is_valid_participant,
         values_from = n,
-				names_repair = janitor::make_clean_names) |> 
-	mutate(n_participants_true = true,
-		   n_participants_false = false) |> 
+        names_repair = janitor::make_clean_names
+    ) |>
+    mutate(
+        n_participants_true = true,
+        n_participants_false = false
+    ) |>
     select(lp, true, false)
@@
 attrition_bcn |>
-	summarise(n_trials_true = sum(is_valid_trial),
+    summarise(
+        n_trials_true = sum(is_valid_trial),
         n_trials_false = sum(!is_valid_trial),
-			  .by = c(lp, trial_type)) |> 
+        .by = c(lp, trial_type)
+    ) |>
     arrange(desc(lp)) |>
-	pivot_wider(id_cols = lp,
+    pivot_wider(
+        id_cols = lp,
         names_from = c(trial_type),
         values_from = matches("trials"),
-				names_repair = janitor::make_clean_names) |> 
+        names_repair = janitor::make_clean_names
+    ) |>
     left_join(n_lp, by = join_by(lp)) |>
-	select(lp, true, false,
-		   matches("n_trials")) |> 
+    select(
+        lp, true, false,
+        matches("n_trials")
+    ) |>
     gt(rowname_col = "lp") |>
@@
     cols_merge(c(true, false),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_cognate,
-				 n_trials_false_cognate),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_non_cognate,
-				 n_trials_false_non_cognate),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_unrelated, 
-				 n_trials_false_unrelated),
-				 pattern = "{1} ({2})") |> 
-	cols_label(true = "Participants", 
+        pattern = "{1} ({2})"
+    ) |>
+    cols_merge(
+        c(
+            n_trials_true_cognate,
+            n_trials_false_cognate
+        ),
+        pattern = "{1} ({2})"
+    ) |>
+    cols_merge(
+        c(
+            n_trials_true_non_cognate,
+            n_trials_false_non_cognate
+        ),
+        pattern = "{1} ({2})"
+    ) |>
+    cols_merge(
+        c(
+            n_trials_true_unrelated,
+            n_trials_false_unrelated
+        ),
+        pattern = "{1} ({2})"
+    ) |>
+    cols_label(
+        true = "Participants",
         n_trials_true_cognate = "Cognate",
         n_trials_true_non_cognate = "Non-cognate",
-			   n_trials_true_unrelated = "Unrelated") |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |>
-	grand_summary_rows(fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~ fmt_integer(.))
+        n_trials_true_unrelated = "Unrelated"
+    ) |>
+    tab_style(
+        cell_text(style = "italic"),
+        cells_column_labels()
+    ) |>
+    grand_summary_rows(
+        fns = list(label = md("*N*")) ~ sum(.),
+        fmt = ~ fmt_integer(.)
+    )
 ```
@@
 ```{r coefs}
-var_labels <- c("b_Intercept" = "Intercept",
+var_labels <- c(
+    "b_Intercept" = "Intercept",
     "b_age_std" = "Age (+1 SD)",
@@
     "b_condition1:lp1" = "Group \U00D7 Condition (U vs. RN)",
-				"b_condition2:lp1" = "Group \U00D7 Condition (RN vs. RC)")
+    "b_condition2:lp1" = "Group \U00D7 Condition (RN vs. RC)"
+)
 
@@
 
-timebin_values <- make_std(seq(0, 16, length.out = 100),
+timebin_values <- make_std(
+    seq(0, 16, length.out = 100),
     mean(data_bcn$timebin),
-						   sd(data_bcn$timebin))
-
-age_values <- make_std(c(20, 32),
+    sd(data_bcn$timebin)
+)
+
+age_values <- make_std(
+    c(20, 32),
     mean(data_bcn$age),
-					   sd(data_bcn$age))
+    sd(data_bcn$age)
+)
 
 nd <- expand_grid(distinct(data_bcn, condition, lp),
-				  age_std = 0, timebin_std = timebin_values)
+    age_std = 0, timebin_std = timebin_values
+)
 
@@
     ndraws = NULL,
-						  re_formula = NA)
+    re_formula = NA
+)
 ```
@@
     ungroup() |>
-	summarise(.value = mean_qi(.epred)[[1]],
+    summarise(
+        .value = mean_qi(.epred)[[1]],
         .lower = mean_qi(.epred)[[2]],
         .upper = mean_qi(.epred)[[3]],
-			  .by = c(lp, condition, timebin_std))
+        .by = c(lp, condition, timebin_std)
+    )
 
@@
         linetype = condition,
-			   shape = condition)) +
+        shape = condition
+    )) +
     facet_wrap(~lp) +
@@
     # 		  linetype = "solid") +
-	stat_summary(fun.data = mean_qi,
+    stat_summary(
+        fun.data = mean_qi,
         geom = "ribbon",
-				 alpha = 1/4,
-				 linewidth = NA) +
-	stat_summary(fun = "mean",
+        alpha = 1 / 4,
+        linewidth = NA
+    ) +
+    stat_summary(
+        fun = "mean",
         geom = "line",
         # colour = "black",
-				 linewidth = 3/4) +
-	geom_hline(yintercept = 0,
-			   colour = "grey") +
-	stat_summary(data = data_bcn,
+        linewidth = 3 / 4
+    ) +
+    geom_hline(
+        yintercept = 0,
+        colour = "grey"
+    ) +
+    stat_summary(
+        data = data_bcn,
         aes(y = .elog),
@@
         linetype = "Condition",
-		 shape = "Condition")
+        shape = "Condition"
+    )
 
 epreds_diff <- epreds |>
-	pivot_wider(id_cols = c(lp, timebin_std, .draw),
+    pivot_wider(
+        id_cols = c(lp, timebin_std, .draw),
         names_from = "condition",
         values_from = ".epred",
-				names_repair = janitor::make_clean_names) |> 
-	mutate(diff_1 = related_non_cognate - unrelated,
-		   diff_2 = related_cognate - related_non_cognate) |> 
+        names_repair = janitor::make_clean_names
+    ) |>
+    mutate(
+        diff_1 = related_non_cognate - unrelated,
+        diff_2 = related_cognate - related_non_cognate
+    ) |>
     pivot_longer(matches("diff"),
@@
     ggplot(aes(timebin_std, .epred)) +
-	facet_wrap(diff~lp, 
+    facet_wrap(diff ~ lp,
         labeller = labeller(
             diff = label_value,
-			   	lp = function(x) return(""), 
-			   	.multi_line = FALSE)) +
+            lp = function(x) {
+                return("")
+            },
+            .multi_line = FALSE
+        )
+    ) +
     # annotate(geom = "rect",
@@
         select(model, elpd_diff, se_diff) |>
-		mutate(diff_label = sprintf("%.3f", elpd_diff),
-			   se_label = sprintf("%.3f", se_diff))
+        mutate(
+            diff_label = sprintf("%.3f", elpd_diff),
+            se_label = sprintf("%.3f", se_diff)
+        )
     return(out)
@@
     rownames_to_column("model") |>
-	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model))-3),
-		   across(matches("diff"),
-		   	   \(x) {x[1] <- NA; return(x)}),
-		   model = case_when(model=="Model 1" ~ "Model 1 (Age)",
-		   				  model=="Model 2" ~ "Model 2 (L1 vocabulary)",
-		   				  model=="Model 3" ~ "Model 3 (Total vocabulary)",
-		   				  .default = model)) |> 
+    mutate(
+        model = paste0("Model ", as.numeric(gsub("fit_", "", model)) - 3),
+        across(
+            matches("diff"),
+            \(x) {
+                x[1] <- NA
+                return(x)
+            }
+        ),
+        model = case_when(model == "Model 1" ~ "Model 1 (Age)",
+            model == "Model 2" ~ "Model 2 (L1 vocabulary)",
+            model == "Model 3" ~ "Model 3 (Total vocabulary)",
+            .default = model
+        )
+    ) |>
     select(model, matches("elpd|diff")) |>
@@
     age_std = age_values,
-				  timebin_std = timebin_values)
+    timebin_std = timebin_values
+)
 
@@
     ndraws = NULL,
-						  re_formula = NA)
+    re_formula = NA
+)
 
@@
     filter(is_lower_positive) |>
-	summarise(over_chance = min(timebin_std),
-			  .by = c(lp, condition, age_std)) |> 
+    summarise(
+        over_chance = min(timebin_std),
+        .by = c(lp, condition, age_std)
+    ) |>
     mutate(over_chance = (over_chance *
         sd(data_bcn$timebin) +
-						  	mean(data_bcn$timebin))*100+300)
+        mean(data_bcn$timebin)) * 100 + 300)
 
 epreds_chance_report <- epreds_chance |>
-	mutate(over_chance = sprintf("%.2f", over_chance),
-		   age_std = factor(x = age_std,
+    mutate(
+        over_chance = sprintf("%.2f", over_chance),
+        age_std = factor(
+            x = age_std,
             levels = age_values,
-		   				 labels = paste0(c(20, 30), " months"))) |> 
+            labels = paste0(c(20, 30), " months")
+        )
+    ) |>
     arrange(lp, age_std) %>%
@@
 epreds_chance |>
-	mutate(age_std = factor(x = age_std,
+    mutate(age_std = factor(
+        x = age_std,
         levels = age_values,
-							labels = paste0(c(20, 32), " months"))) |> 
+        labels = paste0(c(20, 32), " months")
+    )) |>
     ggplot(aes(lp, over_chance,
@@
         shape = sort(condition),
-			   fill = sort(condition))) + 
+        fill = sort(condition)
+    )) +
     facet_wrap(~age_std) +
@@
         linewidth = 1,
-			  alpha = 1/2) +
-	labs(x = "Group",
+        alpha = 1 / 2
+    ) +
+    labs(
+        x = "Group",
         y = "Recognition time (ms)",
@@
         fill = "Condition",
-		 shape = "Condition") +
+        shape = "Condition"
+    ) +
     scale_y_continuous(breaks = seq(0, 1e3L, 50)) +
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"),
-		  panel.grid.minor.y = element_line(colour = "grey",
-		  								  linetype = "dotted"),
+    theme(
+        panel.grid.major.y = element_line(
+            colour = "grey",
+            linetype = "dotted"
+        ),
+        panel.grid.minor.y = element_line(
+            colour = "grey",
+            linetype = "dotted"
+        ),
         legend.position = "top",
-		  axis.title.x = element_blank())
+        axis.title.x = element_blank()
+    )
 ```
@@
 doe_mon_exp <- participants_bcn |>
-	filter(lp=="Monolingual")|> 
+    filter(lp == "Monolingual") |>
     unnest_wider(doe) |>
-	mutate(doe2 = ifelse(test_language=="Catalan",
-						 doe_spanish, doe_catalan),
-		   is_positive =  doe2 > 0) |> 
+    mutate(
+        doe2 = ifelse(test_language == "Catalan",
+            doe_spanish, doe_catalan
+        ),
+        is_positive = doe2 > 0
+    ) |>
     count(is_positive)

### 2023-11-22 manuscript/manuscript.qmd
New version of the interim discussions

@@
 
-Following @mani2010infants, each trial in the task started with the silent presentation of a prime picture.
+Following @mani2010infant, each trial in the task started with the silent presentation of a prime picture.
 Both monolingual and bilingual infants were expected to implicitly name the prime picture.
 According to the language non-selective hypothesis of lexical access, bilinguals should generate two labels for the prime picture, one in each language.
-To test this prediction, we manipulated the phonological similarity between the prime and the target words in both languages (see @fig-task).
+To test this prediction, we manipulated the phonological similarity between the prime and the target words in both languages (see @fig-hypotheses).
 In *Related/Non-cognate* trials, prime and target labels shared phonological onset in only the language of test.
@@
 Solid arrows indicate within-language priming effects, and dashed lines indicate cross-language priming effects.
-In *Related/Cognate* (A) and *Related/Non-cognate* (B) trials, the recognition of the Catalan target word \textipa{kuˈʎe.R@} [spoon] is predicted to be modulated by the prior activation of the prime label in Catalan.
-In *Related/Cognate* trials, the parallel activation of the prime label in Spanish is predicted to increase the strength of the priming effect.](_assets/img/hypotheses.png){fig-align="center"}
+In *Related/Cognate* (A) and *Related/Non-cognate* (B) trials, the recognition of the Catalan target word \textipa{ku"Le.R@} [spoon] is predicted to be modulated by the prior activation of the prime label in Catalan.
+In *Related/Cognate* trials, the parallel activation of the prime label in Spanish is predicted to increase the strength of the priming effect.](_assets/img/hypotheses.png){#fig-hypotheses fig-align="center"}
 
 In line with previous studies in monolinguals, we further predicted that the strength of the lexical interference effects in the *Related/Non-cognate* and *Related/Cognate* conditions would be associated to participants' vocabulary size.
-Target word recognition should be delayed by the activation of a larger cohort of phonologically related words [@mani2011phonological; @chow2018phonological].
+Target word recognition should be delayed by the activation of a larger cohort of phonologically related words [@mani2011phonological; @chow2017spoken].
 In the case of bilinguals, two measures of vocabulary size are relevant: *total vocabulary size* and *dominant-language vocabulary size*.
@@
 Because of the short-lived effects of cross-language activation on lexical processing, and to maximise the probability of detecting priming effects, we introduced a change in the sequence of the trials relative to the original implementation by @mani2010infant.
-We presented target auditory labels inmediately after the offset of the prime picture, and before the onset of the target and distractor pictures.
+We presented target auditory labels immediately after the offset of the prime picture, and before the onset of the target and distractor pictures.
 By presenting prime pictures and target auditory labels closer in time, implicit naming of the prime picture should be more likely to influence the recognition of the target word.
 To test the effects of this methodological change, we first run a control experiment, Study 1, in which we tested a group of same-aged English monolinguals.
+In Study 2, we tested a group of monolinguals and bilinguals learning Catalan and Spanish.
 
@@
 In this study, we conducted a conceptual replication of @mani2010infant and @mani2011phonological.
-We tested a group of English monolinguals aged 20 to 32 months, the same population tested in the original studies.
-For consistency with Study 1, we also manipulated the phonological relationship between the prime and target labels at word onset, as well as the cognate status of the prime label.
-Evidence from implicit naming of prime images would be revealed by differences in target looking or its time course across the trials between *Unrelated* trials and *Related/Non-cognate*, and between *Related/Non-cognate* and *Related/Cognate* trials.
-Given that participants in this study are monolinguals---and contrary to the monolinguals in Barcelona, have received no exposure to any other language---we should not find the cognate status of the prime labels to exert any effect on subsequent target recognition.
+We tested a group of English monolinguals aged 20 to 32 months, living in the Oxfordshire area (United Kingdom).
+As highlighted in the introduction, participants were tested exclusively in English, their dominant language.
+As in the original studies, we manipulated the phonological relationship between the prime and the target label.
+In line with @mani2011phonological, we predicted participants' target looking to change as a function of the phonological relatedness between the prime and target English labels.
+This would reveal that participants implicitly named the prime pictures, generating a phonological label that influenced the subsequent recognition of a phonologically related word.
+To establish a monolingual baseline for all conditions in Study 2, we also manipulated the cognate status of the prime in English and Spanish: in half of the trials the English prime label was phonologically related to its Spanish translation.
+Given participants' lack of familiarity with Spanish (or any language other than English), participants' performance was predicted to be unaffected by the cognate status of the primes.
 
@@
 All materials, data, and reproducible code can be found at the OSF ([https://osf.io/hy984/](https://osf.io/ckydb/)) and GitHub (<https://github.com/gongcastro/cognate-priming>) repositories.
-This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I.
+This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I and the Medical Sciences Research Ethics Board at the University of Oxford, reference R60939/RE009.
 Before every testing session, caregivers were asked to read and sign an informed consent form, and were given a token of appreciation at the end of it.
@@
 
-We collected data from `r n_participants_total` children living in the Metropolitan Area of Barcelona (Spain), tested at the Laboratori de Recerca en Infància at the Universitat Pompeu Fabra.
-Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, `r n_participants_sessions$session_2` participated twice, and `r n_participants_sessions$session_3` participated three times.
-Recurrent participants were tested with at least `r round(time_diffs$diff_min[1], 2)` months of difference.
-We gathered a total of `r n_sessions_total$n` testing sessions.
-Participants were divided into monolinguals and bilinguals based on their relative degree of exposure to Catalan and Spanish, estimated using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
-We categorised participants as monolingual if exposed to more than 80% or more of the time to their dominant language, and as bilingual otherwise.
-`r english::Words(n_participants_lp$n[1])` of the participants were categorised as monolinguals (`r n_participants_lp_sex$n[1]` female, `r n_participants_lp_sex$n[2]` male) and `r n_participants_lp$n[2]` as Catalan/Spanish bilinguals (`r n_participants_lp_sex$n[3]` female, `r n_participants_lp_sex$n[4]` male) (see @tbl-participants for a detailed summary of participants' age and language profile).
-Participants' vision was normal, none used glasses or any other type of vision corrector.
-
-We collected data from `r n_participants_total` children (`r n_participants_sex$n[1]` female, `r n_participants_sex$n[2]` male, with `r english::words(n_participants_sex$n[3])` additional participants' sex not being reported; Age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = \[`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`\]), living in the Oxfordshire area (United Kingdom).
+We collected data from `r n_participants_total` children (`r n_participants_sex$n[1]` female, `r n_participants_sex$n[2]` male, with `r english::words(n_participants_sex$n[3])` additional participants' sex not being reported; Age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]) (see @tbl-participants for a detailed summary of participants' age and language profile), living in the Oxfordshire area (United Kingdom).
 Participants were tested at the Oxford BabyLab at the University of Oxford.
@@
 All participants were being raised in exclusively British English monolingual homes.
-
-```{r vocab-values-oxf}
-vocabulary_oxf <- inner_join(vocabulary,
-    select(participants_oxf, session_id),
-    by = join_by(session_id)
-)
-```
-
-We collected vocabulary data using parental responses to the Oxford Communicative Development Inventory (OCDI) [@hamilton2000infant].
-Families were sent the questionnaire immediately after each experimental session, and were given two weeks to fill it.
-Since all vocabulary sizes of English monolingual infants were only assessed in English, both *L1 vocabulary* and *total vocabulary* sizes were identical (see @fig-vocabulary-oxf).
-
-```{r fig-vocabulary-oxf}
-#| label: fig-vocabulary-oxf
-#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores from the recurrent participants are shown linked."
-#| fig-width: 4
-#| fig-height: 2.5
-vocabulary_oxf |>
-    inner_join(filter(attrition_participants, is_valid_participant),
-        by = join_by(session_id)
-    ) |>
-    inner_join(select(participants, child_id, session_id, age_group),
-        by = join_by(child_id, session_id)
-    ) |>
-    ggplot(aes(age_group, l1_prop)) +
-    geom_line(aes(group = child_id),
-        colour = "grey",
-        alpha = 1 / 4, linewidth = 3 / 4
-    ) +
-    geom_dots(
-        dotsize = 2,
-        colour = clrs[5],
-        fill = clrs[5],
-        scale = 1,
-        side = "both",
-        alpha = 3 / 4
-    ) +
-    stat_summary(
-        fun.data = mean_se,
-        geom = "errorbar",
-        linewidth = 1 / 2,
-        width = 0.1,
-        colour = "black",
-        show.legend = FALSE
-    ) +
-    stat_summary(
-        fun = mean,
-        geom = "point",
-        size = 1.5,
-        colour = "black",
-        show.legend = FALSE
-    ) +
-    # geom_point(alpha = 1) +
-    labs(
-        x = "Age (months)",
-        y = "Vocabulary size",
-        colour = "Group",
-        fill = "Group"
-    ) +
-    scale_y_continuous(
-        labels = scales::percent,
-        limits = c(0, 1)
-    ) +
-    theme(
-        panel.grid.major.y = element_line(
-            linetype = "dotted",
-            colour = "grey"
-        ),
-        legend.position = "top",
-        legend.title = element_blank()
-    )
-```
+Participants' vision was normal, none used glasses or any other type of vision corrector.
 
@@
 #| label: tbl-participants
-#| tbl-cap: "Demographic and linguistic profile of testing sessions."
-participants_bcn |>
+#| tbl-cap: "Demographic and linguistic profile of testing sessions. The number of excluded testing sessions and participants is indicated between parentheses."
+participants |>
 	unnest_wider(doe) |>
@@
 	distinct(session_id, child_id, .keep_all = TRUE) |>
-    summarise(
-        n = n(),
+	mutate(study = if_else(location=="Oxford", 
+						   "Study 1",
+						   "Study 2"),
+		   test_language = paste0(test_language, " dominant"),
+		   lp = gsub(" \\(English\\)", "", lp)) |> 
+	inner_join(attrition_participants,
+			   by = join_by(session_id)) |> 
+	summarise(n = n(),
 			  n_participants = length(unique(child_id)),
@@
 			  # age_vctr = list(age),
-        .by = c(lp, test_language)
-    ) |>
-    gt(
-        rowname_col = "test_language",
-        groupname_col = "lp"
-    ) |>
-    summary_rows(
-        groups = c("Monolingual", "Bilingual"),
-        columns = matches("age"),
+			  .by = c(lp, study, test_language, is_valid_participant)) |> 
+	pivot_wider(id_cols = c(lp, study, test_language),
+				names_from = is_valid_participant,
+				values_from = is.numeric) |> 
+	select(lp, study, test_language, starts_with("n_"), matches("TRUE"),
+		   n_FALSE, n_participants_FALSE) |> 
+	rename_with(\(x) gsub("_TRUE", "", x)) |> 
+	gt(rowname_col = "test_language",
+	   groupname_col = c("study", "lp")) |>
+	grand_summary_rows(columns = matches("age"),
 					   fns = list(Total ~ mean(.)),
-        fmt = ~ fmt_number(., decimals = 1, use_seps = FALSE)
-    ) |>
-    summary_rows(
-        groups = c("Monolingual", "Bilingual"),
-        columns = c(n, n_participants),
+					   fmt = ~ fmt_number(., decimals = 1)) |>
+	grand_summary_rows(columns = c(n, n_participants),
 					   fns = list(Total ~ sum(.)),
-        fmt = ~ fmt_integer(.)
-    ) |>
-    summary_rows(
-        groups = c("Monolingual", "Bilingual"),
-        columns = matches("doe"),
-        fns = list(Total ~ mean(.)),
-        fmt = ~ fmt_number(., decimals = 1, scale_by = 100)
-    ) |>
-    grand_summary_rows(
-        columns = matches("age"),
-        fns = list(Total ~ mean(.)),
-        fmt = ~ fmt_number(., decimals = 1)
-    ) |>
-    grand_summary_rows(
-        columns = matches("doe"),
-        fns = list(Total ~ mean(.)),
-        fmt = ~ fmt_number(., decimals = 1, scale_by = 100)
-    ) |>
-    grand_summary_rows(
-        columns = c(n, n_participants),
-        fns = list(Total ~ sum(.)),
-        fmt = ~ fmt_integer(.)
-    ) |>
+					   fmt = ~ fmt_integer(.)) |>
 	# gt_plt_dist(age_vctr, type = "histogram") |>
 	fmt_number(is.numeric, decimals = 1) |>
-    fmt_integer(c(n, n_participants)) |>
+	fmt_integer(c(n, n_participants, n_FALSE, n_participants_FALSE)) |>
 	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |>
-    cols_merge(c(age_min, age_max),
-        pattern = "{1}-{2}"
-    ) |>
+	cols_merge(c(n, n_FALSE), pattern = "{1} ({2})") |>
+	cols_merge(c(n_participants, n_participants_FALSE),
+			   pattern = "{1} ({2})") |>
+
+	cols_merge(c(age_min, age_max), pattern = "{1}-{2}") |>
 	cols_merge(c(age_mean, age_sd),
-        pattern = "{1} ({2})"
-    ) |>
+			   pattern = "{1} ({2})") |>
 	cols_merge(c(doe_catalan_mean, doe_catalan_sd),
-        pattern = "{1} ({2})"
-    ) |>
+			   pattern = "{1} ({2})") |>
 	cols_merge(c(doe_english_mean, doe_english_sd),
-        pattern = "{1} ({2})"
-    ) |>
+			   pattern = "{1} ({2})") |>
 	cols_merge(c(doe_spanish_mean, doe_spanish_sd),
-        pattern = "{1} ({2})"
-    ) |>
+			   pattern = "{1} ({2})") |>
+	tab_spanner("Sample size", starts_with("n")) |>
 	tab_spanner("Age (months)", matches("age")) |>
@@
 	tab_spanner("Degree of Exposure (%)", matches("doe")) |>
-    cols_label(
-        n = "Sessions",
+	cols_label(n = "Sessions",
 			   n_participants = "Participants",
@@
 			   doe_english_mean = "M (SD)",
-        doe_spanish_mean = "M (SD)"
-    ) |>
-    tab_style(
-        cell_text(style = "italic"),
-        cells_column_labels()
-    ) |>
-    tab_style(
-        cell_text(style = "italic"),
-        cells_column_spanners()
-    )
-```
-
-```{r vocab-values}
-vocabulary_bcn <- vocabulary |>
-    inner_join(select(participants_bcn, session_id, lp, age_group),
-        by = join_by(session_id)
-    )
-
-vocab_means <- vocabulary_bcn |>
-    summarise(across(c(total_prop, l1_prop), lst(mean, sd)),
+			   doe_spanish_mean = "M (SD)") |>
+	tab_style(cell_text(style = "italic"),
+			  cells_column_labels()) |>
+	tab_style(cell_text(style = "italic"),
+			  cells_column_spanners())
+```
+
+```{r vocab-values-oxf}
+vocabulary_oxf <- inner_join(vocabulary,
+							 select(participants_oxf, session_id),
+							 by = join_by(session_id))
+
+vocabulary_oxf_exc <- nrow(participants_oxf) - nrow(vocabulary_oxf)
+```
+
+We collected vocabulary data using parental responses to the Oxford Communicative Development Inventory (OCDI) [@hamilton2000infant].
+Families were sent the questionnaire immediately after each experimental session, and were given two weeks to fill it.
+In the case that a complete response to the OCDI was not provided within the two-week limit, the participants' testing session was excluded from the analyses (*n* = `r vocabulary_oxf_exc`).
+@fig-vocabulary-oxf shows the distribution of participants' vocabulary sizes across ages.
+
+```{r fig-vocabulary}
+#| label: fig-vocabulary-oxf
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles.
+Vocabulary size scores from the recurrent participants are shown linked.
+For visualisation purposes, testing sessions were aggregated at three age points: 21, 25, and 30 months.
+Points and intervals indicate mean and standard deviations, respectively."
+#| fig-width: 6
+#| fig-height: 4
+vocab_plot_data <- vocabulary |>
+	inner_join(filter(attrition_participants, is_valid_participant),
+			   by = join_by(session_id)) |>
+	inner_join(select(participants, location, lp, 
+					  child_id, session_id, age_group),
+			   by = join_by(child_id, session_id)) |>
+	pivot_longer(c(l1_prop, total_prop),
+				 names_to = "type",
+				 values_to = "prop") |> 
+	mutate(location = factor(location, levels = c("Oxford", "Barcelona")),
+		   lp = gsub(" \\(English\\)", "", lp),
+		   side = case_when(location=="Oxford" ~ "both",
+		   				 lp=="Monolingual" ~ "left",
+		   				 lp=="Bilingual" ~ "right"),
+		   type = if_else(type=="l1_prop", 
+		   			   "L1 vocabulary", "Total vocabulary"),
+		   study = if_else(location=="Oxford", 
+		   				"Study 1 (English)", "Study 2 (Catalan/Spanish)"))
+
+vocab_plot_means <- vocab_plot_data |> 
+	summarise(prop_sd = sd(prop, na.rm = TRUE),
+			  prop = mean(prop, na.rm = TRUE),
 			  n = n(),
-        .by = c(age_group, lp)
-    ) %>%
-    mutate(across(matches("prop"), scales::percent)) %>%
-    split(paste0("age_", gsub(" months", "", .$age_group))) |>
-    map(\(x) split(x, tolower(x$lp)))
-
-n_imputed <- table(vocabulary_bcn$is_imputed)[2]
-prop_imputed <- scales::percent(n_imputed / nrow(vocabulary_bcn))
-n_pool <- nrow(bvq_data$vocabulary)
-```
-
-We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers, and inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability].
-Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
-We calculated two measures of receptive vocabulary size for each participant: *L1 vocabulary size* (proportion of words reported as acquired in the checklist of the dominant language), and *total vocabulary size* (proportion of the words in both checklists reported as acquired).
-`r english::Words(n_imputed)` (`r prop_imputed`) families failed to provide a complete response to the BVQ within the two-week time limit.
-We imputed missing vocabulary size scores using single imputation, taking the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
-We used participants' age in months and their language profile (monolingual or bilingual) as predictors.
-We used the `mice` R package [@van2011mice] to perform imputation using the Bayesian linear regression method (see Appendix B).
-
-Overall, there was a substantial increase in both total and L1 vocabulary sizes associated to age (see @fig-vocabulary).
-Monolinguals showed higher L1 vocabulary sizes than monolinguals: they were reported to understand an average of `r vocab_means$age_21$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$l1_prop_sd`) at 30 months, while bilinguals were reported to understand an average of `r vocab_means$age_21$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$l1_prop_sd`) at 30 months.
-Total vocabulary sizes showed the opposite pattern, with monolinguals infants being reported to understand `r vocab_means$age_21$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$total_prop_sd`) at 30 months, and bilinguals being reported to understand `r vocab_means$age_21$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$total_prop_sd`) at 30 months.
-
-```{r fig-vocabulary}
-#| label: fig-vocabulary
-#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles.
-Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
-Grey lines connect vocabulary size scores from the recurrent participants.
-For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested.
-Only participants included in the final data set are shown."
-#| fig-width: 6
-#| fig-height: 3.5
-vocabulary_bcn |>
-    inner_join(filter(attrition_participants, is_valid_participant),
-        by = join_by(session_id)
-    ) |>
-    pivot_longer(c(total_prop, l1_prop),
-        names_to = "measure",
-        values_to = "prop",
-        names_transform = \(x) gsub("_prop", "", x)
-    ) |>
-    mutate(
-        measure = if_else(measure == "l1",
-            "L1 vocabulary",
-            "Total vocabulary"
-        ),
-        is_imputed = if_else(is_imputed, "Imputed", "Observed") |>
-            factor(levels = c("Observed", "Imputed"))
-    ) |>
+			  .by = c(age_group, type, side, lp, type, location)) |> 
+	mutate(.lower = prop - (prop_sd/sqrt(n)),
+		   .upper = prop + (prop_sd/sqrt(n)))
+
+vocab_plot_data |> 
 	ggplot(aes(age_group, prop, 
 			   colour = lp,
-        fill = lp
-    )) +
-    facet_wrap(~measure) +
+			   fill = lp,
+			   side = side)) +
+	facet_grid(type~study) +
 	geom_line(aes(group = child_id),
 			  colour = "grey",
-        alpha = 1 / 4, linewidth = 3 / 4
-    ) +
-    geom_dots(aes(side = if_else(lp == "Monolingual", "left", "right")),
-        dotsize = 2,
-        stroke = 1 / 2,
-        scale = 0.5,
-        alpha = 3 / 4
-    ) +
-    stat_summary(
-        fun.data = mean_se,
-        geom = "errorbar",
-        linewidth = 1 / 2,
-        width = 0.15,
+			  alpha = 1 / 4, linewidth = 3 / 4) +
+	geom_dots(aes(side =),
+			  dotsize = 1.5,
+			  scale = 0.25,
+			  binwidth = 0.025,
+			  alpha = 2 / 4) +
+	geom_errorbar(data = vocab_plot_means,
+				  aes(ymin = .lower,
+				  	ymax = .upper),
 				  colour = "black",
 				  show.legend = FALSE,
-        position = position_dodge(width = 1.15)
-    ) +
-    stat_summary(
-        fun = mean,
-        geom = "point",
-        size = 1.5,
+				  width = 0.15,
+				  linewidth = 1/2,
+				  position = position_dodge(width = 1)) +
+	geom_point(data = vocab_plot_means, 
 			   colour = "black",
 			   show.legend = FALSE,
-        position = position_dodge(width = 1.15)
-    ) +
+			   size = 1.25,
+			   position = position_dodge(width = 1)) +
+	# geom_label(data = vocab_plot_means,
+	# 		   aes(label = sprintf("%.1f%%\n[%.1f, %.1f]",
+	# 		   					prop*100, .lower*100, .upper*100),
+	# 		   	y = 0),
+	# 		   size = 2.5,
+	# 		   fill = "white",
+	# 		   vjust = 0,
+	# 		   show.legend = FALSE,
+	# 		   label.r = unit(0, "lines"),
+	# 		   label.size = 0,
+	# 		   label.padding = unit(0.1, "lines"),
+# 		   position = position_dodge(1),
+# 		   alpha = 1/4) +
 # geom_point(alpha = 1) +
-    labs(
-        x = "Age (months)",
+labs(x = "Age (months)",
 	 y = "Vocabulary size",
 	 colour = "Group",
-        fill = "Group"
-    ) +
-    scale_y_continuous(
-        labels = scales::percent,
-        limits = c(0, 1)
-    ) +
-    theme(
-        panel.grid.major.y = element_line(
-            linetype = "dotted",
-            colour = "grey"
-        ),
+	 fill = "Group") +
+	scale_y_continuous(labels = scales::percent,
+					   limits = c(0, 1)) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"),
 		  legend.position = "top",
-        legend.title = element_blank()
-    )
+		  axis.title.x = element_blank(),
+		  legend.title = element_blank())
 ```
@@
 
-New stimuli lists were generated to adapt the experimental procedure to English-learning infants.
-Stimuli lists were created following the same constraints as in Study 1.
-Auditory stimuli were recorded following the same procedure as in Study 1, produced by Southern British English native female speaker in a toddler-directed manner.
-Audio and picture processing were performed following the same workflow as in Study 1.
+Participants were presented with 32 trials in random order, which belonged to three conditions: *Unrelated* (16 trials), *Related/Non-cognate* (8 trials), and *Related/Cognate* (8 trials).
+In *Unrelated* trials, target was phonologically unrelated with the English and Spanish labels of the prime picture (e.g., $\text{door}_{\text{ENG}}/\text{puerta}_{\text{SPA}}-\text{sock}_{\text{ENG}}$).
+In *Related/Non-cognate* trials, the target shared phonological onset with the English prime label, but not with the Spanish prime label (e.g., $\textbf{t}\text{ree}_{\text{ENG}}/\text{árbol}_{\text{SPA}}-\textbf{t}\text{ruck}_{\text{ENG}}$).
+In *Related/Cognate* trials, the target shared phonological overlap with both English and Spanish prime labels ($\textbf{b}\text{oot}_{\text{ENG}}/\textbf{b}\text{ota}_{\text{SPA}}-\textbf{b}\text{ird}_{\text{ENG}}$).
+Target-distractor pairs were phonologically unrelated, and held constant for all participants.
+Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
+Each target distractor pair was shown twice for each participant, switching roles.
+Distractors were always phonologically unrelated to the prime and target labels in the same trial.
+
+We created fours lists of trials, across which the same target-distractor pair appeared with a different prime, counterbalancing the condition to which it belonged.
+For instance, in list one the *ball*-*trousers* pair was preceded by *bike* (*Related/Cognate*), by *butterfly* (*Related/Non-cognate*) in list two, and by *star* and *nose* (*Unrelated*) in lists three and four.
+@tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
+Lexical frequencies were extracted from the English corpora from the CHILDES database [@macwhinney2000childes; @sanchez2019childes] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@zipf1945meaning; @van2014subtlex].
+
+```{r tbl-stimuli}
+#| label: tbl-stimuli
+#| tbl-cap: "Summary of stimuli properties by trial type."
+stimuli |>
+	unnest_wider(c(freq, nphon)) |>
+	summarise(across(c(matches("n_phon|freq_|lv_|nphon"), duration),
+					 list(	mean = \(x) mean(x, na.rm = TRUE),
+					 	  sd = \(x) sd(x, na.rm = TRUE))),
+			  .by = c(trial_type, test_language)) |>
+	select(-matches("distractor")) |>
+	mutate(test_language = if_else(test_language=="English",
+								   paste0("Study 1: ", test_language),
+								   paste0("Study 2: ", test_language))) |>
+	arrange(test_language) |> 
+	gt(rowname_col = "trial_type",
+	   groupname_col = "test_language") |>
+	# summary_rows(groups = c("Unrelated", "Non-cognate", "Cognate"),
+	# 			 columns = is.numeric,
+	# 			 fns = list(Total ~ mean(.)),
+	# 			 fmt = ~ fmt_number(., decimals = 2)) |>
+	grand_summary_rows(	columns = is.numeric,
+						fns = list(Total ~ mean(.)),
+						fmt = ~ fmt_number(., decimals = 2)) |>
+	tab_spanner("Phonemes", matches("nphon")) |>
+	tab_spanner("Frequency (Zipf)", matches("freq")) |>
+	tab_spanner("Phon. similarity [0-1]", matches("lv")) |>
+	fmt_number(is.numeric, decimals = 1) |>
+	cols_merge(c(freq_prime_mean, freq_prime_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(freq_target_mean, freq_target_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(nphon_prime_mean, nphon_prime_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(nphon_target_mean, nphon_target_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(lv_pp_mean, lv_pp_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(lv_pt_mean, lv_pt_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(duration_mean, duration_sd),
+			   pattern = "{1} ({2})") |>
+	cols_label(trial_type = "",
+			   freq_prime_mean = "Prime",
+			   freq_target_mean = "Target",
+			   lv_pp_mean = "Prime-Prime",
+			   lv_pt_mean = "Prime-Target",
+			   duration_mean = "Duration (s)",
+			   nphon_prime_mean = "Prime",
+			   nphon_target_mean = "Target") |>
+	tab_style(cell_text(style = "italic"),
+			  list(cells_column_labels(),
+			  	 cells_column_spanners(),
+			  	 cells_grand_summary()))
+```
+
+The auditory stimuli were natural exemplars of the selected target words, spoken by a Southern British English female speaker who was instructed to pronounce each word in a toddler-directed manner.
+We used the Audacity and Praat [@boersma2001speak] software packages to trim, denoised, and normalise their amplitude.
+The visual stimuli were realistic photographic representations of a typical exemplars of the prime, target, and distractor words.
+Image backgrounds were removed from the original pictures using the GNU Image Manipulation Program (GIMP), resized to a rectangle of a maximum of 400 pixels hight or wide, and finally placed in the centre of a 50% grey rectangle square of 500 $\times$ 500 pixels.
+The final stimuli had a resolution of 72 dpi.
+When presented in the eye-tracker screen, the areas of interest (AOI) occupied an area of 13.23 $\times$ 13.23 cm (11.613$^{\circ}$ visual angle from participants' perspective).
 
@@
 
-Same as in Study 1.
+Testing took place in a sound-proof room.
+Participants sat on their caregivers' lap in a dimly lit testing booth while the experimenter conducted the experiment from outside.
+Caregivers were instructed to keep their eyes shut (to avoid recording their gaze, instead of the participant's), to be still, and to avoid interacting with the participant verbally or non-verbally.
+Participants sat at approximately 65 cm from the eye-tracker and a XX-in screen of $1929\times1080$ screen resolution.
 The study was run using a custom Matlab script, PresentMate, based on the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox].
@@
 A 9-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
+We set a 55% grey background for the screen during calibration and stimuli presentation.
+Auditory stimuli were presented through two loudspeakers located behind the screen, one to each side.
+The experimenter monitored the experimental from outside the room using a centrally located video camera place above the screen.
+After a successful calibration the experimenter triggered the onset of the first trial.
+Trials were presented uninterruptedly and without intervention of the experimenter until the 32 trials were presented, or the experimental session had to be stopped because of the participant's behaviour.
+
+@fig-task shows a illustrates of the task design.
+Each trial started with the presentation of an attention getter for 3,000 ms.
+Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
+Fifty milliseconds after the offset of the prime image, an auditory label was played from the loudspeakers and, 700 milliseconds after the onset of the auditory label, the target and distractor pictures were presented side-by-side during 1,000 milliseconds until the end of the trial.
+After this, the attention getter of the next trial was immediately presented.
+Each experimental session took approximately 10 minutes.
+
+![Experimental task design with examples in Catalan.
+In each trial, the prime image is presented in silence for 1,500 ms.
+Then the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
+In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
+In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
+In unrelated trials (*n* = 16), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){#fig-task fig-align="center"}
 
@@
 
-Same as in Study 1, but removing the *Group* predictor from the models, given that only monolingual infants were tested.
+#### Data processing
 
@@
 
+We defined a time window of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when both pictures disappeared from screen.
+The first 200 ms of the test phase were discarded to avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
+Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
+Target looking probability was calculated as the empirical logit, using the number of samples inside the time bin in which the participant was looking at the target and distractor AOI (see @eq-elogit) [@barr2008analyzing; @agresti2012categorical].
+This was our response variable.
+
+$$
+\eta' = \ln\bigg(\frac{\text{Target} + 0.5}{ \text{Distractor} + 0.5}\bigg)
+$$ {#eq-elogit}
+
 We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
 We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`).
+We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation; @mani2012activation for a similar approach].
 
@@
 
+```{r tbl-attrition}
+#| label: tbl-attrition
+#| tbl-cap: "Participant-level and trial-level sample size after applying inclusion criteria. The number of excluded participants and trials is indicated between parentheses."
+expanded <- expand(attrition, lp, trial_type, is_valid_trial)
+
+n_lp <- attrition |>
+distinct(is_valid_participant, lp, session_id) |>
+count(is_valid_participant, lp) |>
+pivot_wider(names_from = is_valid_participant,
+values_from = n,
+names_repair = janitor::make_clean_names) |>
+mutate(n_participants_true = true,
+n_participants_false = false) |>
+select(lp, true, false)
+
+attrition |>
+summarise(n_trials_true = sum(is_valid_trial),
+n_trials_false = sum(!is_valid_trial),
+.by = c(lp, trial_type, location)) |>
+arrange(desc(lp)) |>
+pivot_wider(id_cols = c(location, lp),
+names_from = c(trial_type),
+values_from = matches("trials"),
+names_repair = janitor::make_clean_names) |>
+mutate(study = if_else(location=="Oxford", 
+"Study 1: English (Oxford)",
+"Study 2: Catalan/Spanish (Barcelona)")) |> 
+left_join(n_lp, by = join_by(lp)) |>
+select(study, lp, true, false, matches("n_trials")) |>
+gt(rowname_col = "lp",
+groupname_col = "study") |>
+tab_spanner("Participants", matches("participant")) |>
+tab_spanner("Trials", matches("trial")) |>
+fmt_integer(everything()) |>
+cols_merge(c(true, false), pattern = "{1} ({2})") |>
+cols_merge(c(n_trials_true_cognate, n_trials_false_cognate),
+pattern = "{1} ({2})") |>
+cols_merge(c(n_trials_true_non_cognate, n_trials_false_non_cognate),
+pattern = "{1} ({2})") |>
+cols_merge(c(n_trials_true_unrelated, n_trials_false_unrelated),
+pattern = "{1} ({2})") |>
+cols_label(true = "Participants",
+n_trials_true_cognate = "Cognate",
+n_trials_true_non_cognate = "Non-cognate",
+n_trials_true_unrelated = "Unrelated") |>
+tab_style(cell_text(style = "italic"),
+cells_column_labels()) |>
+tab_style(cell_text(align = "left"),
+cells_stub()) |>
+grand_summary_rows(fns = list(label = md("*N*")) ~ sum(.),
+fmt = ~ fmt_integer(.))
+```
+
+#### Modelling approach
+
+```{r data-analysis}
+
+r_info <- sessionInfo()
+
+r_version <- glue::glue(r_info$R.version$major,
+r_info$R.version$minor,
+.sep = "."
+)
+stan_version <- "2.33.0"
+
+rope_interval <- c(-0.1, +0.1)
+```
+
+We used Bayesian Hierarchical General Additive Models (HGAMs) to model the data [@pedersen2019hierarchical], using a Gaussian distribution to model the the logit of target looking.
+First, we fit a model ($\mathcal{M}_0$) that included the main effects of *Condition* and *Age* as fixed effects in the model.
+We set two *a priori* contrasts for the *Condition* predictor [@schad2020capitalize]: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
+Before entering the model, the *Age* predictor was standardised by subtracting from each observation the mean of the predictor, and dividing the result from the standard deviation of the predictor.
+
+We included the variable *Session*---which indexes individual testing sessions that may belong to the same participant---as grouping variable, nested within the *Participant* grouping variable---which indexes a distinct participant.
+This nested random effects structure incorporates the longitudinal design of data collection, in which multiple participants were tested more than once at different ages.
+We added by-session intercepts and *Condition* slopes, and by-participant intercepts and *Age* slopes.
+To model the time course of target looking across time bins, we included B-splines for the main effect of *Time*, and one for the interaction between *Group* and *Relatedness* [@wood2017generalized].
+For both splines, we specified $k = 8$ basis functions or *knots*.
+@eq-model shows a formal implementation of the model.
+
+We implemented this model using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
+We ran `r english::words(dim(model_fits_bcn$fit_0$fit)[2])` iteration chains using the by-default No U-Turn Sampler algorithm with `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` iterations each and an additional `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` warm-up iterations per chain.
+
+$$
+\begin{aligned}
+&\textbf{Target looking by participant } i \textbf{ in session } j \\
+y_{ij} &\sim \mathcal{N}(\mu_{ij}, \sigma_{ij}) \\ \\
+&\textbf{Distributional parameters:} \\
+\eta'(\mu_{ij}) &= (\beta_0 + u _{0_{ij}}) +
+(\beta_1 + u _{1_{ij}}) \text{Condition} + \beta_{2} Age + \\
+& \sum_{w = 1}^k b_{w_{0}} \beta_{3_{k}} \text{Time} +
+\sum_{w = 1}^k b_{w_{1}} \beta_{4_{k}} (\text{Time} \times \text{Group}) \\
+\text{where:} \\
+&\eta'\text{ is the empirical logit of target fixations} \\
+&b_{w_{0-1}} \text{ is the cubic spline of the } w \text{ basis function} \\
+&k \text{ is the number of knots in the spline (10)} \\
+&\textbf{Prior:} \\
+\beta_{0-4} &\sim \mathcal{N}(0, 0.5) \\
+u_{0-1_{ij}} &\sim \mathcal{N}(0, \sigma_{0-2})\\
+b_{0-1} &\sim \text{MVN}(0, \tau_{0-1}) \\
+\sigma_{0-2}, \tau_{0-1} &\sim \text{Exponential}(6)\\
+\rho_{0-2} &\sim LKJCorr(6)\\
+\text{where:}\\
+&\rho_{0-2} \text{ are the correlation parameters for } \sigma_{0-2}
+\end{aligned}
+$$ {#eq-model}
+
 ## Results
@@
 ### Priming effects
+
+We tested the differences between the conditions of interest in two ways.
+First, we examined the posterior distribution of the regression coefficients of the linear predictors in model $\mathcal{M}_0$ (see @eq-model).
+We assessed the practical relevance of the coefficients following @kruschke2018bayesian.
+We specified a region of practical equivalence (ROPE) from `r rope_interval[1]` to +`r rope_interval[2]`, in the logit scale.
+This region indicates the range of values that we considered equivalent to zero.
+We then summarised the posterior distribution of each regression coefficient with the 95% highest density interval (HDI).
+This interval contains the true value of this coefficient with 95% probability, given the data.
+Finally, we calculated the proportion of posterior samples in the 95% HDI that fell into the ROPE, noted as $p(\text{ROPE})$, which indicates the probability that the true value of the regression coefficient falls into the ROPE (and therefore should be considered equivalent to zero).
+For example, $p(\text{ROPE})=.80$ indicates that, given our data, there is a 80% probability that the true value of the coefficient falls within the ROPE, and can therefore be considered equivalent to zero.
 
@@
 
-```{r timecourse-oxf}
-nd <- expand_grid(distinct(data_oxf, condition),
-    timebin_std = timebin_values,
-    age_std = 0
-)
-
-epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_1,
-    re_formula = NA,
-    ndraws = NULL,
-    value = ".epred"
-)
-```
-
-An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds-oxf).
-Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
+Second, we examined the differences between the priming conditions across the time course of the trial, incorporating the smooth functions of the HGAMs to generate marginal posterior predictions for each condition across for each time point.
+@fig-epreds-oxf shows the posterior predictions of the model for each condition, and a summary of the difference between the *Unrelated* and *Related/Non-cognate* conditions, and between those for the *Related/Non-cognate* and *Related/Cognate* conditions, at each time point to test the practical relevance of these differences, were compared their 95% HDI against the [-0.1, +0.1] ROPE.
+This analysis revealed a similar pattern of results to the previously shown: predicted target looking for the three conditions overlaps across the full time course of the trial.
 
@@
 #| fig-height: 6.5
+make_std <- function(x, mean, sd) (x - mean) / sd
+
+timebin_values <- make_std(seq(0, 16, length.out = 100),
+						   mean(data_bcn$timebin),
+						   sd(data_bcn$timebin))
+
+nd <- expand_grid(distinct(data_oxf, condition),
+				  timebin_std = timebin_values,
+				  age_std = 0)
+
+epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_1,
+						  re_formula = NA,
+						  ndraws = NULL,
+						  value = ".epred")
+
 epreds_summary <- epreds |>
@@
 			   linetype = condition,
-        shape = condition
-    )) +
-    geom_hline(
-        yintercept = 0,
-        colour = "grey"
-    ) +
+			   shape = condition)) +
+	geom_hline(yintercept = 0,
+			   colour = "grey") +
 	# geom_line(aes(group = interaction(condition, .draw)),
@@
 	# 		  linetype = "solid") +
-    stat_summary(
-        fun.data = mean_qi,
+	stat_summary(fun.data = mean_qi,
 				 geom = "ribbon",
 				 alpha = 1 / 4,
-        linewidth = NA
-    ) +
-    stat_summary(
-        fun = "mean",
+				 linewidth = NA) +
+	stat_summary(fun = "mean",
 				 geom = "line",
 				 # colour = "black",
-        linewidth = 3 / 4
-    ) +
-    stat_summary(
-        data = data_oxf,
+				 linewidth = 3 / 4) +
+	stat_summary(data = data_oxf,
 				 aes(y = .elog),
@@
 				 geom = "point",
-        size = 2
-    ) +
-    labs(
-        x = "Time (ms)",
+				 size = 2) +
+	labs(x = "Time (ms)",
 		 y = "Logit (Target looking)",
@@
 		 linetype = "Condition",
-        shape = "Condition"
-    )
+		 shape = "Condition")
 
 epreds_diff <- epreds |>
-    pivot_wider(
-        id_cols = c(timebin_std, .draw),
+	pivot_wider(id_cols = c(timebin_std, .draw),
 				names_from = "condition",
 				values_from = ".epred",
-        names_repair = janitor::make_clean_names
-    ) |>
-    mutate(
-        diff_1 = related_non_cognate - unrelated,
-        diff_2 = related_cognate - related_non_cognate
-    ) |>
+				names_repair = janitor::make_clean_names) |>
+	mutate(diff_1 = related_non_cognate - unrelated,
+		   diff_2 = related_cognate - related_non_cognate) |>
 	pivot_longer(matches("diff"),
@@
 				 values_to = ".epred",
-        names_prefix = "diff_"
-    ) |>
+				 names_prefix = "diff_") |>
 	mutate(diff = factor(diff,
@@
 	# 		 linetype = "dotted") +
-    stat_summary(
-        fun.data = mean_qi,
+	stat_summary(fun.data = mean_qi,
 				 geom = "ribbon",
@@
 				 linewidth = NA,
-        alpha = 1 / 3
-    ) +
+				 alpha = 1 / 3) +
 	stat_summary(aes(group = diff),
@@
 				 colour = "black",
-        linewidth = 3 / 4
-    ) +
-    geom_hline(
-        yintercept = rope_interval[1],
+				 linewidth = 3 / 4) +
+	geom_hline(yintercept = rope_interval[1],
 			   colour = "red",
-        linetype = "dotted"
-    ) +
-    geom_hline(
-        yintercept = rope_interval[2],
+			   linetype = "dotted") +
+	geom_hline(yintercept = rope_interval[2],
 			   colour = "red",
-        linetype = "dotted"
-    ) +
+			   linetype = "dotted") +
 	# geom_line(aes(group = interaction(diff, draw)),
@@
 
-    labs(
-        x = "Time (ms)",
+	labs(x = "Time (ms)",
 		 y = "Logit P(Target looking)",
@@
 		 fill = "Comparison",
-        linetype = "Comparison"
-    )
+		 linetype = "Comparison")
 
@@
 	# scale_y_continuous(limits = c(0.25, 0.75)) +
-    scale_x_continuous(
-        breaks = make_std(
-            seq(0, 17, 3),
+	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
 										 mean(data_bcn$timebin),
-            sd(data_bcn$timebin)
-        ),
+										 sd(data_bcn$timebin)),
 					   labels = \(x) format(seq(3e2, 2e3, 3e2),
-            big.mark = ","
-        )
-    ) &
-    theme(
-        legend.position = "top",
+					   					 big.mark = ",")) &
+	theme(legend.position = "top",
 		  legend.title = element_blank(),
-        panel.grid.major.y = element_line(
-            colour = "grey",
-            linetype = "dotted"
-        )
-    )
-```
-
-### The role of age and vocabulary size on priming effects
-
-@tbl-loos-oxf shows a comparison between models including *Age* ($\mathcal{M}_{2}$), and *L1 vocabulary* ($\mathcal{M}_{3}$)---and their two-way and two-way interaction with *Condition*---against model $\mathcal{M}_{1}$, which only included *Age* as a covariate suggested that all models performed equivalently, with model $\mathcal{M}_{2}$ showing a slightly better performance.
-Overall, this suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account *L1 vocabulary*, or *Total vocabulary* sizes.
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+```
+
+### Age and vocabulary size effects
+
+To test our hypotheses regarding the role of age, dominant-language vocabulary size, and total vocabulary size, on the emergence of priming effects, we compared the fit of model $\mathcal{M}_0$ against the fit of other models including the two-way interaction between *Condition* and *Age* ($\mathcal{M}_1$), or the two-way interaction between *Condition* and *L1 vocabulary* ($\mathcal{M}_2$), and all main effects involved.
+We compared the models using one-out cross-validation (LOO-CV) as a benchmark of model performance, using a Pareto-smoothed importance sampling (PSIS) approximation [@vehtari2017practical].
+A better performance by models $\mathcal{M}_1$ or $\mathcal{M}_2$ over $\mathcal{M}_0$ would point to *Age* or *L1 vocabulary*, respectively, playing a substantial role in participants' word-recognition, or on the emergence of priming effects.
+@tbl-loos-oxf shows a summary of the predictive performance of the models, as quantified by the expected log-predictive density (*ELPD*), and its standard error (*SE*, a measure of uncertainty around the *ELPD*).
+Overall, all models, performed equivalently, as shown by the small difference in *ELPD*, relative to the uncertainty of the estimates.
+This suggests that participants' target looking during the test phase can be predicted with relative accuracy without taking into account the age or vocabulary size of the participants.
 
@@
 	rownames_to_column("model") |>
-    mutate(
-        model = paste0("Model ", as.numeric(gsub("fit_oxf_", "", model)) - 1),
-        across(
-            matches("diff"),
+	mutate(model = paste0("Model ",
+						  as.numeric(gsub("fit_oxf_", "", model)) - 1),
+		   across(matches("diff"),
 		   	   \(x) {
@@
 		   	   	return(x)
-            }
-        ),
-        model = case_when(model == "Model 1" ~ "Model 1 (Age)",
+		   	   }),
+		   model = case_when(
+		   	model == "Model 1" ~ "Model 1 (Age)",
 		   	model == "Model 2" ~ "Model 2 (L1 vocabulary)",
@@
 		   	.default = model
-        )
-    ) |>
+		   )) |>
 	select(model, matches("elpd|diff")) |>
@@
 	fmt_number(is.numeric) |>
-    cols_label(
-        elpd_diff = "ELPD (diff.)",
+	cols_label(elpd_diff = "ELPD (diff.)",
 			   se_diff = "SE ELPD (diff)",
 			   elpd_loo = "ELPD",
-        se_elpd_loo = "SE ELPD"
-    ) |>
+			   se_elpd_loo = "SE ELPD") |>
 	fmt_missing(missing_text = "---") |>
@@
 
-### Word recognition times
-
-```{r recognition-oxf}
-nd <- expand_grid(distinct(data_oxf, condition),
-    timebin_std = timebin_values,
-    age_std = age_values
-)
-
-epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_2,
-    re_formula = NA,
-    ndraws = NULL,
-    value = ".epred"
-)
-
-epreds_chance <- epreds |>
-    median_hdci() |>
-    mutate(is_lower_positive = .lower > 0) |>
-    filter(is_lower_positive) |>
-    summarise(
-        over_chance = min(timebin_std),
-        .by = c(condition, age_std)
-    ) |>
-    mutate(over_chance = (over_chance *
-        sd(data_oxf$timebin) +
-        mean(data_oxf$timebin)) * 100 + 300)
-
-epreds_chance_report <- epreds_chance |>
-    mutate(
-        over_chance = sprintf("%.2f", over_chance),
-        age_std = factor(
-            x = age_std,
-            levels = age_values,
-            labels = paste0(c(20, 30), " months")
-        )
-    ) |>
-    arrange(age_std) %>%
-    split(paste0("age_", gsub(" months", "", .$age_std)))
-```
-
-As expected, the recognition times were on average shorter for older infants than for younger infants.
-Differences between conditions were larger in bilinguals than in monolinguals, especially in the older group.
-The recognition time for monolingual 20-month-olds was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-
-```{r fig-recognition-oxf}
-#| label: fig-recognition-oxf
-#| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
-#| fig-width: 5
-#| fig-height: 3.5
-epreds_chance |>
-    mutate(age_std = factor(
-        x = age_std,
-        levels = age_values,
-        labels = paste0(c(20, 32), " months")
-    )) |>
-    ggplot(aes(age_std, over_chance,
-        colour = sort(condition),
-        fill = sort(condition)
-    )) +
-    geom_point(shape = 16, size = 4) +
-    geom_line(aes(group = condition),
-        linewidth = 1
-    ) +
-    # geom_point(size = 3) +
-    labs(
-        x = "Group",
-        y = "Recognition time (ms)",
-        colour = "Condition",
-        fill = "Condition"
-    ) +
-    scale_y_continuous(breaks = seq(0, 1e3L, 25)) +
-    theme(
-        panel.grid.major.y = element_line(
-            colour = "grey",
-            linetype = "dotted"
-        ),
-        panel.grid.minor.y = element_line(
-            colour = "grey",
-            linetype = "dotted"
-        ),
-        legend.position = "top",
-        axis.title.x = element_blank()
-    )
-```
-
 ## Discussion
 
-Study 2 was aimed at investigating whether the phonological priming effects previously reported @mani2010infant and @mani2011phonological could be found using the adaptation of the implicit naming task form Study 1 in a sample with equivalent demographic characteristics to the original studies.
-Results from Study 2 did not provide any evidence in favour of phonological priming.
-English monolingual participants from all ages showed an equivalent pattern of target looking across both related and unrelated trials.
-The absence of a phonological priming effect suggest that either English monolinguals did not generate implicit labels for the prime pictures presented in silence, or that if generated, such labels did not interact with the subsequent recognition of the target word.
+In this study, we attempted to replicate the original study by @mani2010infant and @mani2011phonological, using an extension of the implicit naming paradigm.
+adapted to the bilingual case.
+The main divergence between both implementations was the order in which target labels and target-distractor picture pairs were presented.
+In the original study, participants were presented with the target and distractor pictures immediately after the prime picture and the target auditory label was presented 2,000 ms after the onset of the prime and distractor pictures.
+In our adaptation of the paradigm, we presented the target auditory label immediately after the prime picture, before the target and distractor pictures were displayed in the screen.
+We then presented the target and distractor pictures 700 ms after the onset of the target label.
+The rationale behind this modification was to maximise the probability of observing any priming effects.
+By presenting the prime picture and the auditory target labels closer in time, the prime word might have a higher chance to influence the lexical selection of the target word.
+By testing a sample English monolingual infants with equivalent demographic and linguistic characteristics to the original studies, we expected to set a baseline to later compare bilingual infants in Study 2 against.
+
+Although we found strong evidence of successful word recognition across participants of all ages, results did not provide any evidence in favour of phonological priming.
+English monolingual participants from all ages showed an equivalent pattern of target looking in both related (*Related/Cognate* and *Related/Non-cognate*) and *Unrelated* trials.
+The absence of a phonological priming effect suggest that either English monolinguals did not generate implicit labels for the prime pictures presented in silence, or that, if generated, such labels did not interact with the subsequent recognition of the target word.
 Both candidate explanations conflict with both Mani and Plunkett's studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects [@duta2012erp; @styles2015infant].
 
-One of the main differences between the implicit naming paradigm used by @mani2010infant and the one in Studies 1 and 2 is the fact that target labels were auditorily presented before target and distractor pictures were presented on screen.
-The rationale behind this decision was to minimise the amount of time elapsed between the presentation of the prime and target labels, in order to facilitate any potential priming effects.
-By presenting the auditory target label immediately after the offset of the prime picture, the internally generated prime phonological form would be more likely to affect the activation of the target lexical representation.
-It is possible that this difference in task design might have led to the contrasting outcomes of Mani and Plunkett and the present study.
-Given that participants were not presented with the target and distractor pictures until after the target label was auditorily presented, one possibility is that participants faced the additional task of exploring both pictures to find the target referent, which infants in @mani2010infant did not have to do, because of the pre-naming presentation of target and distractor in the test phase.
-This visual exploration of the screen might have increased the cognitive load of the task, rendering the potential effect of phonological priming to a weaker, undetectable effect.
-Overall, the results from Study 2 support a more methodological explanation of the null pattern of results in Study 1, in which the lack of a phonological priming effect---both within and across languages---might be explained by differences in task design or replicability concerns.
+Adding the predictors *Age* or *Vocabulary size* as predictors in the model, in interaction with *Condition* did not increase the fit of the model.
+This points to neither variable having a substantial influence in participants' target looking behaviour across conditions.
+These results diverge from previous studies reporting an increment in word recognition speed [@fernald1998rapid; @marchman2008speed], and stronger phonological priming effects in children with larger vocabulary sizes [@mani2011phonological; @chow2017spoken].
+Overall, the outcomes of the Study 1 point to the absence of phonological priming effects in English monolingual toddlers, in contrast with previous studies.
+We discuss further candidate explanations for these results, and their implications for the lexical development literature in the General discussion.
 
 # Study 2
+
+Due to time constraints induced by the COVID-19 lockdown between 2020 an 2021, data collection in Study 1 and Study 2 was conducted simultaneously.
+In this study, we present data for monolinguals and bilinguals tested in Barcelona.
 
@@
 #| label: participants-numbers
-participants_bcn <- filter(participants, location == "Barcelona")
+participants_bcn <- filter(participants, location=="Barcelona")
 
@@
 
-```{r tbl-participants}
-#| label: tbl-participants
-#| tbl-cap: "Demographic and linguistic profile of testing sessions."
-participants_bcn |>
-    unnest_wider(doe) |>
-    select(-matches("others")) |>
-    arrange(lp, test_language) |>
-    distinct(session_id, child_id, .keep_all = TRUE) |>
-    summarise(
-        n = n(),
-        n_participants = length(unique(child_id)),
-        across(age, lst(mean, sd, min, max)),
-        across(matches("doe_"), lst(mean, sd)),
-        # age_vctr = list(age),
-        .by = c(lp, test_language)
-    ) |>
-    gt(
-        rowname_col = "test_language",
-        groupname_col = "lp"
-    ) |>
-    summary_rows(
-        groups = c("Monolingual", "Bilingual"),
-        columns = matches("age"),
-        fns = list(Total ~ mean(.)),
-        fmt = ~ fmt_number(., decimals = 1, use_seps = FALSE)
-    ) |>
-    summary_rows(
-        groups = c("Monolingual", "Bilingual"),
-        columns = c(n, n_participants),
-        fns = list(Total ~ sum(.)),
-        fmt = ~ fmt_integer(.)
-    ) |>
-    summary_rows(
-        groups = c("Monolingual", "Bilingual"),
-        columns = matches("doe"),
-        fns = list(Total ~ mean(.)),
-        fmt = ~ fmt_number(., decimals = 1, scale_by = 100)
-    ) |>
-    grand_summary_rows(
-        columns = matches("age"),
-        fns = list(Total ~ mean(.)),
-        fmt = ~ fmt_number(., decimals = 1)
-    ) |>
-    grand_summary_rows(
-        columns = matches("doe"),
-        fns = list(Total ~ mean(.)),
-        fmt = ~ fmt_number(., decimals = 1, scale_by = 100)
-    ) |>
-    grand_summary_rows(
-        columns = c(n, n_participants),
-        fns = list(Total ~ sum(.)),
-        fmt = ~ fmt_integer(.)
-    ) |>
-    # gt_plt_dist(age_vctr, type = "histogram") |>
-    fmt_number(is.numeric, decimals = 1) |>
-    fmt_integer(c(n, n_participants)) |>
-    fmt_number(matches("doe"), decimals = 1, scale_by = 100) |>
-    cols_merge(c(age_min, age_max),
-        pattern = "{1}-{2}"
-    ) |>
-    cols_merge(c(age_mean, age_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(c(doe_catalan_mean, doe_catalan_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(c(doe_english_mean, doe_english_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(c(doe_spanish_mean, doe_spanish_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    tab_spanner("Age (months)", matches("age")) |>
-    tab_spanner("Catalan", matches("catalan")) |>
-    tab_spanner("English", matches("english")) |>
-    tab_spanner("Spanish", matches("spanish")) |>
-    tab_spanner("Degree of Exposure (%)", matches("doe")) |>
-    cols_label(
-        n = "Sessions",
-        n_participants = "Participants",
-        age_mean = "M (SD)",
-        age_min = "Range",
-        doe_catalan_mean = "M (SD)",
-        doe_english_mean = "M (SD)",
-        doe_spanish_mean = "M (SD)"
-    ) |>
-    tab_style(
-        cell_text(style = "italic"),
-        cells_column_labels()
-    ) |>
-    tab_style(
-        cell_text(style = "italic"),
-        cells_column_spanners()
-    )
-
-# col_names <- c("Group",
-# 			   "Language",
-# 			   "Sessions",
-# 			   "Participants",
-# 			   "M (SD)",
-# 			   "Range",
-# 			   "M (SD)",
-# 			   "M (SD)",
-# 			   "M (SD)")
-# participants_bcn |>
-# 	unnest_wider(doe) |>
-# 	select(-matches("others")) |>
-# 	arrange(lp, test_language) |>
-# 	summarise(n = n(),
-# 			  n_participants = n_distinct(child_id),
-# 			  across(age, lst(mean, sd, min, max)),
-# 			  across(matches("doe_"), lst(mean, sd)),
-# 			  # age_vctr = list(age),
-# 			  .by = c(lp, test_language)) |>
-# 	mutate(age_mean = sprintf("%.1f (%.1f)", age_mean, age_sd),
-# 		   age_range = sprintf("%.1f-%.1f", age_min, age_max),
-# 		   doe_catalan = sprintf("%.1f (%.1f)", doe_catalan_mean*100, doe_catalan_sd*100),
-# 		   doe_spanish = sprintf("%.1f (%.1f)", doe_spanish_mean*100, doe_spanish_sd*100),
-# 		   doe_english = sprintf("%.1f (%.1f)", doe_english_mean*100, doe_english_sd*100)) |>
-# 	select(lp:age_mean, age_range, doe_catalan, doe_spanish, doe_english) |>
-# 	kable(digits = 1,
-# 		  format = "latex",
-# 		  booktabs = TRUE,
-# 		  col.names = col_names,
-# 		  align = "llrrrrrrrrrrrr"
-# 	)
-# 	add_header_above(c(
-# 		" " = 4,
-# 		"Age (months)" = 2,
-# 		"Degree of exposure (%)" = 8
-# 	))
-```
-
 ```{r vocab-values}
@@
 inner_join(select(participants_bcn, session_id, lp, age_group),
-        by = join_by(session_id)
-    )
+by = join_by(session_id))
 
@@
 n = n(),
-        .by = c(age_group, lp)
-    ) %>%
+.by = c(age_group, lp)) %>%
 mutate(across(matches("prop"), scales::percent)) %>%
@@
 
-Overall, there was a substantial increase in both total and L1 vocabulary sizes associated to age (see @fig-vocabulary).
-Monolinguals showed higher L1 vocabulary sizes than monolinguals: they were reported to understand an average of `r vocab_means$age_21$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$l1_prop_sd`) at 30 months, while bilinguals were reported to understand an average of `r vocab_means$age_21$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$l1_prop_sd`) at 30 months.
-Total vocabulary sizes showed the opposite pattern, with monolinguals infants being reported to understand `r vocab_means$age_21$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$total_prop_sd`) at 30 months, and bilinguals being reported to understand `r vocab_means$age_21$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$total_prop_sd`) at 30 months.
-
-```{r fig-vocabulary}
-#| label: fig-vocabulary
-#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles.
-Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
-Grey lines connect vocabulary size scores from the recurrent participants.
-For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested.
-Only participants included in the final data set are shown."
-#| fig-width: 6
-#| fig-height: 3.5
-vocabulary_bcn |>
-    inner_join(filter(attrition_participants, is_valid_participant),
-        by = join_by(session_id)
-    ) |>
-    pivot_longer(c(total_prop, l1_prop),
-        names_to = "measure",
-        values_to = "prop",
-        names_transform = \(x) gsub("_prop", "", x)
-    ) |>
-    mutate(
-        measure = if_else(measure == "l1",
-            "L1 vocabulary",
-            "Total vocabulary"
-        ),
-        is_imputed = if_else(is_imputed, "Imputed", "Observed") |>
-            factor(levels = c("Observed", "Imputed"))
-    ) |>
-    ggplot(aes(age_group, prop,
-        colour = lp,
-        fill = lp
-    )) +
-    facet_wrap(~measure) +
-    geom_line(aes(group = child_id),
-        colour = "grey",
-        alpha = 1 / 4, linewidth = 3 / 4
-    ) +
-    geom_dots(aes(side = if_else(lp == "Monolingual", "left", "right")),
-        dotsize = 2,
-        stroke = 1 / 2,
-        scale = 0.5,
-        alpha = 3 / 4
-    ) +
-    stat_summary(
-        fun.data = mean_se,
-        geom = "errorbar",
-        linewidth = 1 / 2,
-        width = 0.15,
-        colour = "black",
-        show.legend = FALSE,
-        position = position_dodge(width = 1.15)
-    ) +
-    stat_summary(
-        fun = mean,
-        geom = "point",
-        size = 1.5,
-        colour = "black",
-        show.legend = FALSE,
-        position = position_dodge(width = 1.15)
-    ) +
-    # geom_point(alpha = 1) +
-    labs(
-        x = "Age (months)",
-        y = "Vocabulary size",
-        colour = "Group",
-        fill = "Group"
-    ) +
-    scale_y_continuous(
-        labels = scales::percent,
-        limits = c(0, 1)
-    ) +
-    theme(
-        panel.grid.major.y = element_line(
-            linetype = "dotted",
-            colour = "grey"
-        ),
-        legend.position = "top",
-        legend.title = element_blank()
-    )
-```
-
 ### Stimuli
@@
 
-We used `r n_words` distinct words included in the BVQ to create the stimuli lists.
-We created six stimuli lists: three in Catalan, and three in Spanish.
-Each list contained 32 trials, each involving a prime-target-distractor triplet.
-Words played a role as primes *or* targets/distractors across the three lists in their corresponding language.
-For instance, the Catalan word *cadira* appeared as *prime* in the three lists, but never as *target* or *distractor*; the Catalan word *bici* appeared as *target* and *distractor* across the three lists, but never as a prime.
-Target-distractor pairings were held constant across the three lists in each language.
-For instance, in all Catalan lists the word *bici* was paired with the word *porta*.
-Target-distractor pairings were also yoked, so that each member of the same target-distractor pair appeared once as target and once as distractor in each list.
-For instance, the *bici*-*porta* paired appeared twice in each of the three Catalan lists: once with *bici* as target and *porta* as distractor, and once with *porta* as target and *bici* as distractor.
-This counterbalancing avoided participants encountering looking at the target word guided solely by that word having being named in a previous trial.
-Finally, prime words appeared only once in each list: each target-distractor pair was associated with a different prime word in both appearances.
-Across lists, the same prime word was presented alongside a different target-distractor pair.
-For instance, the Catalan prime word *barret* was presented with the *bici*-*porta* target-distractor pair in one list, with the *bici*-*porta* pair in another list, and with *berenar*-*amanida* in the remaining list.
-To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias2009lexical].
-The order of the trials was randomised across experimental sessions, so that each time a participant was tested, the order in which the prime-target-distractor was presented was random.
-Each participant was randomly assigned to one of the three lists in the corresponding (dominant) language, and always the same list across their experimental sessions in the case of a recurrent participant.
-
-In 16 of the 32 trials of the same list (henceforth *Related* trials), the prime and the target words were phonologically related, sharing phonological onset (at least first phoneme).
-In the other 16 trials (*Unrelated* trials), prime and target did not share phonological onset.
-Eight of the 16 *Related* trials included a cognate prime (*Related/Cognate* trials), and the other eight included a non-cognate prime (*Related/Non-cognate* trials).
-Target and distractor word pairs were phonologically unrelated (did not share phonological onset).
-A prime word was considered cognate if its Catalan and Spanish translation shared phonological onset.
-Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
-Some target-distractor pairs shared semantic features or a taxonomic relationship.
-This is the case of words associated with especially salient referents such as animals or food.
-To avoid infants guiding their gaze to these objects based on their saliency, we paired animals and food items together.
-The position of the target and distractor pictures (right or left) for each target-distractor pair was alternated, so that in one list the target would appear on the left, in another list it would appear on the right, and so on.
-
-We examined the overall equivalence of the three trial types by comparing them across three variables relating to the target word: lexical frequency, word prevalence, animacy.
-@tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
-Lexical frequencies were extracted from the Catalan and Spanish corpora of the CHILDES database [@macwhinney2000childes; @sanchez2019childes] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@zipf1945meaning; @van2014subtlex].
-We defined word prevalence as the proportion of same-aged infants who were reported to understand the word in the BVQ database.
-
-The auditory stimuli were natural exemplars of the selected target words, spoken by Central Catalan-Spanish proficient bilingual female speaker who was instructed to pronounce each word in a toddler-directed manner.
-Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44,100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
-We used the Audacity and Praat [@boersma2001speak] software packages to record and edit the audio files.
-The speaker was presented with a list of words in Catalan.
-The order of the words was pseudo-randomised, and each word was produced three times in a row before moving to the next word in the list.
-After going through all the words in the list, the speaker went through the word list again generating three tokens for each word, now in an inverse order (from bottom of the list to the top).
-We then repeated the same procedure for the list of Spanish words.
-The resulting audios were manually chunked into individual word-forms.
-For each of the six tokens produced for each word, the most adequate was selected for further processing.
-The audios were then transformed to stereo by duplicating them into two channels, denoised, and finally normalised.
-The mean duration of the final audios was `r round(mean(stimuli$duration[stimuli$test_language=="Catalan"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Catalan"]), 2)`) and `r round(mean(stimuli$duration[stimuli$test_language=="Spanish"]), 2)` (*SD* = `r round(sd(stimuli$duration[stimuli$test_language=="Spanish"]), 2)`) seconds for the Catalan and Spanish lists.
-
-To make the pronunciation of the words as familiar as possible to each infant, we generated additional pronunciation variants for some words in Catalan and Spanish.
-Catalan words involving the /\textipa{L}/ phoneme in their Central Catalan variant (e.g., /\textipa{'Lu.n@}) were also recorded with such phoneme replaced by /j/ (e.g., /\textipa{'ju.n@}), a phonological process common in the Metropolitan Area of Barcelona.
-Spanish words involving the /\textipa{T}/ phoneme were also generated replacing such phoneme with /\textipa{s}/ to better accommodate Latin variants of Spanish.
-Before every experimental session, caregivers were asked to utter three written words involving the /\textipa{L}/ phoneme (in the case of participants tested in Catalan) or the /\textipa{T}/ phoneme (in the case of participants tested in Spanish).
-Each token contained the critical phoneme at onset, inter-vocalic position, and coda.
-The experimenter assigned the participant to the Catalan or Spanish stimuli list involving the closest variant to that of caregivers'.
-
-Each word was depicted by a realistic phonographic representation of a typical exemplar.
-Image backgrounds were removed from the original pictures using the GNU Image Manipulation Program (GIMP), resized to a rectangle of a maximum of 400 pixels hight or wide, and finally placed in the centre of a 50% grey rectangle square of 500 $\times$ 500 pixels.
-The final stimuli had a resolution of 72 dpi.
-When presented in the eye-tracker screen, the areas of interest (AOI) occupied an area of 13.23 $\times$ 13.23 cm (11.613$^{\circ}$ visual angle from participants' perspective).
-
-```{r tbl-stimuli}
-#| label: tbl-stimuli
-#| tbl-cap: "Summary of stimuli properties by trial type."
-stimuli |>
-    unnest_wider(c(freq, nphon)) |>
-    filter(test_language != "English") |>
-    summarise(
-        across(
-            c(matches("n_phon|freq_|lv_|nphon"), duration),
-            list(
-                mean = \(x) mean(x, na.rm = TRUE),
-                sd = \(x) sd(x, na.rm = TRUE)
-            )
-        ),
-        .by = c(trial_type)
-    ) |>
-    select(-matches("distractor")) |>
-    gt(
-        rowname_col = "trial_type",
-        groupname_col = "test_language"
-    ) |>
-    # summary_rows(groups = c("Unrelated", "Non-cognate", "Cognate"),
-    # 			 columns = is.numeric,
-    # 			 fns = list(Total ~ mean(.)),
-    # 			 fmt = ~ fmt_number(., decimals = 2)) |>
-    grand_summary_rows(
-        columns = is.numeric,
-        fns = list(Total ~ mean(.)),
-        fmt = ~ fmt_number(., decimals = 2)
-    ) |>
-    tab_spanner("Phonemes", matches("nphon")) |>
-    tab_spanner("Frequency (Zipf)", matches("freq")) |>
-    tab_spanner("Phon. similarity [0-1]", matches("lv")) |>
-    fmt_number(is.numeric, decimals = 1) |>
-    cols_merge(c(freq_prime_mean, freq_prime_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(c(freq_target_mean, freq_target_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(c(nphon_prime_mean, nphon_prime_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(c(nphon_target_mean, nphon_target_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(c(lv_pp_mean, lv_pp_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(c(lv_pt_mean, lv_pt_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(c(duration_mean, duration_sd),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_label(
-        trial_type = "",
-        freq_prime_mean = "Prime",
-        freq_target_mean = "Target",
-        lv_pp_mean = "Prime-Prime",
-        lv_pt_mean = "Prime-Target",
-        duration_mean = "Audio duration (s)",
-        nphon_prime_mean = "Prime",
-        nphon_target_mean = "Target"
-    ) |>
-    tab_style(
-        cell_text(style = "italic"),
-        list(
-            cells_column_labels(),
-            cells_column_spanners(),
-            cells_grand_summary()
-        )
-    )
-```
+For Study 2, we created six stimuli lists: three in Catalan, and three in Spanish.
+Lists were created following the same constraints as in Study 1,  but now considering the cross-linguistic phonological relationship between Catalan and Spanish, instead of English and Spanish.
+Extracting lexical frequencies from the Catalan and Spanish corpora in the CHILDES database was not possible, given the low number of participants and tokens included in them.
+Instead, we mapped the English lexical frequencies onto their Catalan and Spanish translation equivalents [see @fourtassi2020growth and @garcia2023cognate for similar approaches].
+The auditory stimuli were natural exemplars of the selected target words, spoken by a Southern British English female speaker who was instructed to pronounce each word in a toddler-directed manner.
+New visual stimuli were created to accommodate the words included in the new stimuli lists, and possible cultural differences in the typicality of the exemplars shown in the pictures.
 
@@
 
-Testing took place in a sound-proof room.
-Participants sat on their caregivers' lap in a dimly lit testing booth while the experimenter conducted the experiment from outside.
-Caregivers were instructed to keep their eyes shut (to avoid recording their gaze, instead of the participant's), to be still, and to avoid interacting with the participant verbally or non-verbally.
-Participants sat at approximately 65 cm from the eye-tracker and a XX-in screen of $1929\times1080$ screen resolution.
-We used a custom Matlab XXXX script using the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox] to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
-Sampling rate was set at 120 Hz.
-A 5-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
-We set a 55% grey background for the calibration and stimuli presentation.
-Auditory stimuli were presented through two loudspeakers located behind the screen, one to each side.
-The experimenter monitored the experimental from outside the room using a centrally located video camera place above the screen.
-After a successful calibration the experimenter triggered the onset of the first trial.
-Trials were presented uninterruptedly and without intervention of the experimenter until the 32 trials were presented, or the experimental session had to be stopped because of the participant's behaviour.
-
-![Experimental task design with examples in Catalan.
-In each trial, the prime image is presented in silence for 1,500 ms.
-Then the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
-In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
-In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
-In unrelated trials (*n* = 16), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){fig-align="center"}
-
-Each trial started with the presentation of an attention getter for 3,000 ms.
-Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
-Fifty milliseconds after the offset of the prime image, an auditory label was played from the loudspeakers and, 700 milliseconds after the onset of the auditory label, the target and distractor pictures were presented side-by-side during 1,000 milliseconds until the end of the trial.
-After this, the attention getter of the next trial was immediately presented.
-Each experimental session took approximately 10 minutes.
+Same as in Study 1.
+We used a custom Matlab XXXX script using the PsychToolbox-3 extension to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
 
 ### Data analysis
-
-#### Data processing
 
@@
 
-We defined a time window of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when both pictures disappeared from screen.
-The first 200 ms of the test phase were discarded to avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
-Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
-
 We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
 We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 10% of valid samples (equivalent to 100 ms) for both the target *and* the distractor (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation; @mani2012activation for a similar approach].
+We also excluded trials in which participants did not provide at least 10% of valid samples (equivalent to 100 ms) for both the target *and* the distractor (*n* = `r format(n_exc_test_each, big.mark = ",")`).
 
@@
 
-```{r tbl-attrition}
-#| label: tbl-attrition
-#| tbl-cap: "Participant-level and trial-level sample size after applying inclusion criteria. The number of excluded participants and trials is indicated between parentheses."
-expanded <- expand(attrition_bcn, lp, trial_type, is_valid_trial)
-
-n_lp <- attrition_bcn |>
-    distinct(is_valid_participant, lp, session_id) |>
-    count(is_valid_participant, lp) |>
-    pivot_wider(
-        names_from = is_valid_participant,
-        values_from = n,
-        names_repair = janitor::make_clean_names
-    ) |>
-    mutate(
-        n_participants_true = true,
-        n_participants_false = false
-    ) |>
-    select(lp, true, false)
-
-attrition_bcn |>
-    summarise(
-        n_trials_true = sum(is_valid_trial),
-        n_trials_false = sum(!is_valid_trial),
-        .by = c(lp, trial_type)
-    ) |>
-    arrange(desc(lp)) |>
-    pivot_wider(
-        id_cols = lp,
-        names_from = c(trial_type),
-        values_from = matches("trials"),
-        names_repair = janitor::make_clean_names
-    ) |>
-    left_join(n_lp, by = join_by(lp)) |>
-    select(
-        lp, true, false,
-        matches("n_trials")
-    ) |>
-    gt(rowname_col = "lp") |>
-    tab_spanner("Participants", matches("participant")) |>
-    tab_spanner("Trials", matches("trial")) |>
-    fmt_integer(everything()) |>
-    cols_merge(c(true, false),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(
-        c(
-            n_trials_true_cognate,
-            n_trials_false_cognate
-        ),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(
-        c(
-            n_trials_true_non_cognate,
-            n_trials_false_non_cognate
-        ),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_merge(
-        c(
-            n_trials_true_unrelated,
-            n_trials_false_unrelated
-        ),
-        pattern = "{1} ({2})"
-    ) |>
-    cols_label(
-        true = "Participants",
-        n_trials_true_cognate = "Cognate",
-        n_trials_true_non_cognate = "Non-cognate",
-        n_trials_true_unrelated = "Unrelated"
-    ) |>
-    tab_style(
-        cell_text(style = "italic"),
-        cells_column_labels()
-    ) |>
-    grand_summary_rows(
-        fns = list(label = md("*N*")) ~ sum(.),
-        fmt = ~ fmt_integer(.)
-    )
-```
-
-#### Modelling approach
-
-```{r data-analysis}
-
-r_info <- sessionInfo()
-
-r_version <- glue::glue(r_info$R.version$major,
-    r_info$R.version$minor,
-    .sep = "."
-)
-stan_version <- "2.33.0"
-
-rope_interval <- c(-0.1, +0.1)
-```
-
-We used Bayesian Hierarchical General Additive Models (HGAMs) to model the data [@pedersen2019hierarchical].
-First, we defined our response variable as the empirical logit of target looking (see @eq-elogit) across all eye-tracking samples for each each participant in each condition [@barr2008analyzing; @agresti2012categorical].
-We used a Gaussian distribution to model this variable.
-To test our hypotheses, we included *Condition*, *Group*, their two-way interaction, and *Age* as fixed effects in the model.
-We set two *a priori* contrasts for the *Condition* predictor [@schad2020capitalize]: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
-We also set two *a priori* contrasts for the *Group* predictor: one comparing *Monolingual (ENG)* with *Monolingual (CAT/SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Bilingual (CAT-SPA)* participants coded as `0`), and another comparing *Monolingual (ENG)* with *Bilingual (CAT-SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Monolingual (CAT/SPA)* participants coded as `0`).
-Before entering the model, the numeric predictors *Age*, *L1 vocabulary*, and *Total vocabulary* were standardised by subtracting from each observation the mean of the predictor, and dividing the result from the standard deviation of the predictor.
-
-$$
-\eta' = \ln\bigg(\frac{\text{Target} + 0.5}{ \text{Distractor} + 0.5}\bigg)
-$$ {#eq-elogit}
-
-We included the variable *Session*---which indexes individual testing sessions that may belong to the same participant---as grouping variable, nested within the *Participant* grouping variable---which indexes a distinct participant.
-This nested random effects structure incorporates the longitudinal design of data collection, in which multiple participants were tested more than once at different ages.
-We added by-session intercepts and *Condition* slopes, and by-participant intercepts and *Age* slopes.
-To model the time course of target looking across time bins, we included B-splines for the main effect of *Time*, and one for the interaction between *Group* and *Relatedness* [@wood2017generalized].
-For both splines, we specified $k = 8$ basis functions or *knots*.
-@eq-model shows a formal implementation of the model.
-We implemented the models using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
-We ran `r english::words(dim(model_fits_bcn$fit_0$fit)[2])` iteration chains using the by-default No U-Turn Sampler algorithm with `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` iterations each and an additional `r format(niterations(model_fits_bcn$fit_0), big.mark = ",")` warm-up iterations per chain.
-
-$$
-\begin{aligned}
-&\textbf{Target looking by participant } i \textbf{ in session } j \\
-y_{ij} &\sim \mathcal{N}(\mu_{ij}, \sigma_{ij}) \\ \\
-&\textbf{Distributional parameters:} \\
-\eta'(\mu_{ij}) &= (\beta_0 + u _{0_{ij}}) +
-(\beta_1 + u _{1_{ij}}) \cdot \text{Condition} +\\
-&\beta_{2} \cdot \text{Group} +
-\beta_{3} \cdot X + \beta_{4} \cdot (\text{Condition} \times \text{Group}) +\\
-&\beta_{5} \cdot (\text{Condition} \times X) + \beta_{6} \cdot (\text{Group} \times X) +\\
-&\beta_{7} \cdot (\text{Condition} \times \text{Group} \times X) +\\
-& \sum_{w = 1}^k b_{w_{0}} \cdot \beta_{8_{k}} \cdot \text{Time} +
-\sum_{w = 1}^k b_{w_{1}} \cdot\beta_{9_{k}} \cdot (\text{Time} \times \text{Group}) \\
-\text{where:} \\
-&\eta'\text{ is the empirical logit of target fixations} \\
-&X \in \{\text{Age}, \text{L1 vocabulary}, \text{Total vocabulary}\} \\
-&b_{w_{0-1}} \text{ is the cubic spline of the } w \text{ basis function} \\
-&k \text{ is the number of knots in the spline (10)} \\
-&\textbf{Prior:} \\
-\beta_{0-9} &\sim \mathcal{N}(0, 0.5) \\
-u_{0-1_{ij}} &\sim \mathcal{N}(0, \sigma_{0-2})\\
-b_{0-1} &\sim \text{MVN}(0, \tau_{0-1}) \\
-\sigma_{0-2}, \tau_{0-1} &\sim \text{Exponential}(6)\\
-\rho_{0-2} &\sim LKJCorr(6)\\
-\text{where:}\\
-&\rho_{0-2} \text{ are the correlation parameters for } \sigma_{0-2}
-\end{aligned}
-$$ {#eq-model}
-
-#### Statistical inference
-
-We tested the differences between the conditions of interest in two ways.
-First, we examined the posterior distribution of the regression coefficients of the linear predictors in model $\mathcal{M}_0$ (see @eq-model).
-We assessed the practical relevance of the coefficients following @kruschke2018bayesian.
-We specified a region of practical equivalence (ROPE) from `r rope_interval[1]` to +`r rope_interval[2]`, in the logit scale.
-This region indicates the range of values that we considered equivalent to zero.
-We then summarised the posterior distribution of each regression coefficient with the 95% highest density interval (HDI).
-This interval contains the true value of this coefficient with 95% probability, given the data.
-Finally, we calculated the proportion of posterior samples in the 95% HDI that fell into the ROPE, noted as $p(\text{ROPE})$, which indicates the probability that the true value of the regression coefficient falls into the ROPE (and therefore should be considered equivalent to zero).
-For example, $p(\text{ROPE})=.80$ indicates that, given our data, there is a 80% probability that the true value of the coefficient falls within the ROPE, and can therefore be considered equivalent to zero.
-Second, we examined the differences between the priming conditions across the time course of the trial.
-We generated marginal posterior predictions from the model for the three conditions, for monolinguals and monolinguals.
-These predictions included the non-linear relationship between target looking and the time course of the trial.
-We then computed the difference between the marginal posterior predictions for the *Unrelated* and *Related/Non-cognate* conditions, and between those for the *Related/Non-cognate* and *Related/Cognate* conditions, at each time bin.
-Finally, we compared the 95% HDI of the differences against the \[-0.1, +0.1\] ROPE.
-
-To test our hypotheses regarding the role of age, dominant-language vocabulary size, and total vocabulary size, on the emergence of priming effects, we compared the fit of model $\mathcal{M}_0$ against the fit of other models including the three-way interaction between *Condition*, *Group*, and *Age* ($\mathcal{M}_1$), *L1 vocabulary* ($\mathcal{M}_2$), and *Total vocabulary* ($\mathcal{M}_3$), and all two-way interactions involved.
-We compared the models using one-out cross-validation (LOO-CV) as a benchmark of model performance, using a Pareto-smoothed importance sampling (PSIS) approximation [@vehtari2017practical].
-A better performance by models $\mathcal{M}_1$, $\mathcal{M}_2$, or $\mathcal{M}_3$ over $\mathcal{M}_0$ would point to *Age*, *L1 vocabulary*, or *Total vocabulary*, respectively, playing a substantial role in participants' word-recognition, or on the emergence of priming effects.
+We modelled the data following a similar approach as in Study 1, with the main difference that participants' language profile (*Group*) was now included as a predictor in the model.
+In Study 2, the base model $\mathcal{M}_0$ included the the main effects of *Age*, *Condition*, and *Group*, and the two-way interaction between the *Condition* and  *Group* predictors.
+Contrast coding of the *Condition* predictor was the same as in Study 1.
+We set one *a priori* contrasts for the *Group* predictor, comparing *Monolingual* with *Bilingual* participants (sum-coded as `-0.5` and `+0.5`, respectively).
 
@@
 The coefficient of *Age* had a positive sign, but its 95% HDI overlapped completely with the ROPE ($\beta$ = `r coefs$b_age_std$.value`, 95% HDI = `r coefs$b_age_std$.ci`), indicating that participants from all ages showed equivalent overall target word recognition.
-The 95% HDI of the coefficient of *Group* also included zero ($\beta$ = `r coefs$b_lp1$.value`, 95% HDI = `r coefs$b_lp1$.ci`) and completely overlapped with the ROPE, indicating an equivalent overall target preference in monolinguals and bilinguals.
+The 95% HDI of the coefficient of *Group* also included zero ($\beta$ = `r coefs$b_lp1$.value`, 95% HDI = `r coefs$b_lp1$.ci`) and completely overlapped with the ROPE, indicating an equivalent overall target preference in monolinguals and bilinguals,
+
 The 95% HDI of the first contrast of the *Condition* predictor---comparing *Unrelated* and *Related/Non-cognate* trials---included zero ($\beta$ = `r coefs$b_condition1$.value`, 95% HDI = `r coefs$b_condition1$.ci`), and `r coefs$b_condition1$.rope` of its posterior samples overlapped with the ROPE.
@@
 An analysis of the time course of target looking revealed a similar pattern of results (see @fig-epreds).
-Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups, and also in both extrema of the age range of participants (20 and 32 months).
+Posterior mean prediction for the three conditions overlap across the full time course of the trial in both language groups.
 
@@
 
-### The role of age and vocabulary size on priming effects
+### Age and vocabulary size effects
 
@@
 
-### Word recognition times
-
-```{r recognition}
-nd <- expand_grid(distinct(data_bcn, condition, lp),
-    age_std = age_values,
-    timebin_std = timebin_values
-)
-
-epreds <- add_epred_draws(nd,
-    model_fits_bcn$fit_3,
-    ndraws = NULL,
-    re_formula = NA
-)
-
-epreds_chance <- epreds |>
-    median_hdci() |>
-    mutate(is_lower_positive = .lower > 0) |>
-    filter(is_lower_positive) |>
-    summarise(
-        over_chance = min(timebin_std),
-        .by = c(lp, condition, age_std)
-    ) |>
-    mutate(over_chance = (over_chance *
-        sd(data_bcn$timebin) +
-        mean(data_bcn$timebin)) * 100 + 300)
-
-epreds_chance_report <- epreds_chance |>
-    mutate(
-        over_chance = sprintf("%.2f", over_chance),
-        age_std = factor(
-            x = age_std,
-            levels = age_values,
-            labels = paste0(c(20, 30), " months")
-        )
-    ) |>
-    arrange(lp, age_std) %>%
-    split(tolower(.$lp)) |>
-    map(\(x) split(x, paste0("age_", gsub(" months", "", x$age_std))))
-```
-
-In an exploratory analysis, we compared the model-estimated time points at which participants' gaze behaviour showed evidence of target looking above chance level.
-We defined the recognition time of the trial as the earliest time point at which the lower bound of the 95% HDI posterior mean prediction of the target looking excluded zero.
-As expected, the recognition times were on average shorter for older infants than for younger infants.
-Differences between conditions were larger in bilinguals than in monolinguals, especially in the older group.
-The recognition time for monolingual 20-month-olds was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In monolingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_30$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_30$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_30$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 20 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-In bilingual 30 month-olds, the recognition point was `r epreds_chance_report$monolingual$age_20$over_chance[1]` ms in the *Unrelated* condition, `r epreds_chance_report$monolingual$age_20$over_chance[2]` ms in the *Related/Non-cognate* condition, and `r epreds_chance_report$monolingual$age_20$over_chance[3]` ms in the *Related/Cognate* condition.
-
-```{r fig-recognition}
-#| label: fig-recognition
-#| fig-cap: "Model-predicted recognition times for monlingual and bilinguals at 20 and 30 months of age."
-#| fig-width: 7
-#| fig-height: 3
-epreds_chance |>
-    mutate(age_std = factor(
-        x = age_std,
-        levels = age_values,
-        labels = paste0(c(20, 32), " months")
-    )) |>
-    ggplot(aes(lp, over_chance,
-        colour = sort(condition),
-        shape = sort(condition),
-        fill = sort(condition)
-    )) +
-    facet_wrap(~age_std) +
-    geom_point(size = 3) +
-    geom_line(aes(group = condition),
-        linewidth = 1,
-        alpha = 1 / 2
-    ) +
-    labs(
-        x = "Group",
-        y = "Recognition time (ms)",
-        colour = "Condition",
-        fill = "Condition",
-        shape = "Condition"
-    ) +
-    scale_y_continuous(breaks = seq(0, 1e3L, 50)) +
-    theme(
-        panel.grid.major.y = element_line(
-            colour = "grey",
-            linetype = "dotted"
-        ),
-        panel.grid.minor.y = element_line(
-            colour = "grey",
-            linetype = "dotted"
-        ),
-        legend.position = "top",
-        axis.title.x = element_blank()
-    )
-```
-
 ## Discussion
 
-In Study 1, we adapted an implicit naming paradigm to investigate the potential role of within- and cross-language phonological priming in 20- to 32-month-old children.
-Both the overall target looking and its time course across the trial suggested robust word recognition between 550 ms and 700 ms after the onset of the test phase, regardless of priming condition, participant language profile and age.
-Overall, participants' performance was equivalent across all priming conditions.
-An exploratory analyses on word recognition times suggested a complex pattern of results, showing an age effect---in which older participants looked at the target above chance earlier than younger infants---and a marginal interaction between priming conditions, age, and language group.
-Overall, we did not find evidence of phonological priming within or across languages.
-
+In Study 2, tested a sample of 20-to-32-months-old bilinguals in our adaptation of the implicit naming paradigm to investigate the potential role of within- and cross-language phonological priming.
+We also tested a same aged monolingual control.
+As in Study 1, we within-language priming effects in both *Related/Non-cognate* and *Related/Cognate* trials, as the result of the phonological  similarity between the prime and target labels in the language of test.
+This would suggest that participants lexicalised the prime pictures (presented in silence), and that the resulting word interacted with the auditory recognition of the subsequently presented target label.
+We also predicted bilingual participants to lexicalise the prime picture in both languages in parallel, in line with the language non-selective hypothesis of lexical access.
+If this was the case, participants should show differences in target looking between *Related/Non-cognate* trials---in which the target word shared phonological onset with only the prime label in the test language---and *Related/Cognate* trials---in which the target label also shared phonological overlap with the prime label in the other language.
+
+Paralleling the results from Study 1 participant' looking behaviour suggested robust word recognition, regardless of experimental condition, participant language profile, age, or vocabulary size.
+Overall, participants' performance was equivalent across all priming conditions suggesting that no phonological priming took place within or across languages in either monolinguals or bilinguals.
 These results conflict with previous findings in several ways.
-First, previous investigations using implicit naming paradigms had found evidence of infants and toddlers generating internal labels when presented with pictures of familiar objects.
-@mani2010infant and @mani2011phonological reported priming effects in 18 and 24-month-old infants.
-In primed trials, participants' target looking preference was influenced by the prior presentation of a phonologically related referent in silence.
-In control trials---in which prime and target labels were unrelated---no priming effect was found.
-This suggested that infants implicitly named the prime label, and that the resulting internal phonological form was detailed enough to interact with the subsequent auditory recognition of the target word.
-In the present study, we did not find evidence in favour of differences in target looking preference between related and unrelated trials, regardless of the age of participants or their language profile.
+First, and as discussed in the Discussion section of Study 1, previous investigations using implicit naming paradigms had found evidence of within-language priming effects in same-aged monolinguals learning English (and younger).
+In this study monolingual infants learning Catalan or Spanish did not show evidence of such priming effect, as suggested by their equivalent target looking behaviour in both *Unrelated* and *Related/Non-cognate* trials.
+Given that English monolinguals in Study 1 did not show priming effects either, it cannot be concluded that the diverging results from Study 2 and those available in the literature are due to cross-language differences between Catalan and Spanish, and English.
+
+Second, our results are also in contrast with the non-selective account of lexical access.
+Bilinguals in Study 1 did not show evidence of cross-language priming, as suggested by the lack of differences in target looking between *Related/Non-cognate* and *Related/Cognate* trials.
+Under the non-selective account, we had predicted bilinguals in this study to lexicalise the prime pictures in both languages, which should have exerted a stronger priming effect on target recognition in *Related/Cognate* trials than in *Related/Non-cognate trials*.
+Overall, results in Study 2 did not provide evidence of phonological priming effects in monolingual and bilingual infant learning Catalan and Spanish.
 
@@
 
-Both @mani2010infant and @mani2011phonological, and the present study, share a similar design, but sampled different populations.
-Participants in Mani and Plunkett's studies were raised in English speaking households in Oxford (United Kingdom), while participants in the present study were learning Catalan or Spanish, if not a combination of both in Spain.
-We identify two ways in which this might have influenced the results.
-One is that the stimuli lists in Catalan and Spanish might have differed in some critical dimension to the English stimuli from Mani and Plunkett.
-This might have interfered infants' ability to generate implicit labels for prime pictures.
-For example, words in the present study were predominantly bi-syllabic, while those from Mani and Plunkett's studies were mostly monosyllabic, and contained less phonemes on average.
-Longer word-forms might have been more difficult to retrieve in time for a prime effect to take place in target recognition.
-Another possibility is that exposure to a second language might have delayed the developmental trajectories of word production in bilinguals, in such way implicit naming emerges later ages.
-Given that `r scales::percent(doe_mon_exp$n[1] / doe_mon_exp$n[2], accuracy = 0.01)` of monolinguals in Barcelona were exposed to a second language (although less than 20% of the time), they might as well been affected by such delay in implicit naming trajectories.
-
-The results from the Study 1 also conflict with previous reports of cross-language priming in toddlers.
-Particularly, @von2012language and @floccia2020translation had provided evidence of phonological priming through translation.
-One critical different between both studies and the present one is the silent or auditory presentation of the prime labels.
-In priming through translation studies, the prime is auditorily presented to participants, and cross-language priming effects take place through the subsequent activation of the prime translation.
-In the present study, the prime label was not named, and participants were expected to generate both the prime label and its translation implicitly.
-It may be the case that infants in the present study faced a more challenging task, having to internally retrieve phonological forms without any auditory prompt like the one provided by priming through translation studies.
-Another possibility is that participants in the present study did in fact general prime labels, but such labels did not interfere over target recognition.
-This could be because they were not phonologically specified enough.
-This is unlikely in the light of previous work on implicit naming and mispronunciation perception.
-First, @duta2012erp and @styles2015infant had shown electrophysiological evidence of implicit naming in English learning infants as young as 14 months of age.
-Second abundant studies have shown that early lexical representations are encoded in high phonological detail, in both monolinguals and bilinguals [@swingley2000spoken; @bailey2002phonological; @tamasi2016measuring; @tamasi2017pupillometry; @ramon2009vowel].
-It could be the case then, that participants in the present study retrieved prime phonological representations, but phonological links between lexical representations are still weak or not present, so that priming effects are not possible until later in age.
-
-In summary, the possibly higher difficulty of the task induced by the properties of the stimuli, together with differences in task design and populations might have contributed to the null pattern of results shown in Study 1.
-Given the complexity of the picture drawn by these factors, we conducted a second study with the aim of replicating the original findings by @mani2010infant and @mani2011phonological in English monolinguals.
-If phonological priming effects are observed in a same-aged population using the adaptation of the task from Study 1, this would provide evidence in favour of cross-language differences in the developmental trajectories of implicit naming.
-If, on the contrary, a similar patter of null results is found, this would suggest either the existence of finer differences in task implementation compared to the original studies, or point to the effect of interest being less robust than suggested by the literature.
-
 # General discussion
 
-In this paper, we investigated the developmental trajectories of cross-language co-activation in the developing lexicon.
-We tested a large cohort of monolingual and bilingual toddlers in an implicit naming paradigm.
-We designed three experimental conditions to manipulate the phonological overlap between the prime and target words within and across languages.
+In this paper, we investigated the developmental trajectories of cross-language co-activation in the initial lexicon.
+We tested a large cohort of monolingual and bilingual toddlers in an implicit naming paradigm, in which we designed three experimental conditions to manipulate the phonological overlap between the prime and target words within and across languages.
 In *Unrelated* trials, prime and target were phonologically unrelated in both languages.
@@
 In *Related/Cognate* trials, the prime label was a cognate: prime and target labels shared phonological onset in both languages.
-In Study 1, we tested a cohort of monolingual and bilingual infants learning Catalan, Spanish, or both, and found no phonological priming effect in monolinguals or bilinguals.
-In Study 2, we attempted to replicate the original findings by @mani2010infant in a same-aged English monolingual cohort, and found the same null pattern of results.
-
-To our knowledge this is the first study investigating cross-language priming using an implicit naming paradigm.
-This paradigm presents a critical asset for studying bilingual lexical processing: since the prime pictures are presented in silence, the task can be presented exclusively in the dominant language of participants.
-This provides a monolingual context in which differences in performance across experimental conditions that involve cross-linguistic interactions can be more easily associated to the experimental manipulation in a causal way [@grosjean1997bilingual].
-This contrasts with previously used experimental paradigms in which participants are presented with items from both languages.
-Such covert manipulation of the similarity between stimuli from the two languages has allowed previous studies to provide stronger support for the language-non selective account of lexical access than studies presenting an overtly bilingual task to participants [e.g., @costa2000cognate; @thierry2007brain; @von2014bilinguals].
-
-Previous studies had provided evidence of English monolingual infants 18-month-old and older being sensitive to phonological priming effects during auditory word recognition.
+In Study 1, we attempted to replicate the original findings by @mani2010infant and @mani2011phonological in a same-aged English monolingual cohort.
+We found a null pattern of results in which we did not find any evidence of phonological priming.
+In Study 2, we tested a cohort of monolingual and bilingual infants learning Catalan, Spanish, or both, and found similar results, with no evidence of phonological priming effect in either monolinguals or bilinguals.
+In none neither study was participants' word recognition influenced by their age or vocabulary size.
+
+Previous studies on word recognition had provided evidence phonological priming effects in English monolingual infants 18-month-old and older.
 @mani2010infant had shown a facilitation effect in word recognition when 18-month-olds were previously presented with a familiar picture whose label shared phonological onset with the target word.
 @mani2011phonological extended these results to 21-month-olds, showing an effect in the opposite direction: phonologically related primes interfered with target word recognition.
-The shift from facilitation to inhibition was interpreted as a shift from sub-lexical facilitation at the phonological level---in which target word recognition is facilitated by the prior activation of an overlapping set of phonological segments---to a lexical interference effect in which the activation of the lexical representation of the phonologically similar prime led to competition dynamics with the subsequently activated representation of the target word.
+The results from both studies suggested that participants lexicalised the prime pictures---even if presented in silence---and that the resulting phonological form interacted with subsequent auditory word recognition.
+The shift from facilitation at 18 months to inhibition at 21 months was interpreted as a shift from sub-lexical facilitation at the phonetic level.
+The authors suggested that at 18 months, target word recognition was facilitated by the prior activation of an overlapping set of phonological segments.
+At older ages, participants with larger vocabulary sizes showed an interference effect generated by the increased size of the prime cohort, which led to slower selection of the phonologically related target word.
 This last conclusion was supported by the fact that the size of the interference effect was associated with the increase in participants' vocabulary size, and also with the cohort size of the prime label---primes belonging to a larger neighbourhood of phonologically related words were subject to stronger interference effects during the task.
 
-Even earlier evidence of implicit naming had been provided through ERP measurements at 14 months of age.
+Even earlier evidence of implicit naming had been provided through electrophysiological measurements at 14 months of age.
 @duta2012erp presented name-known pictures in silence for one second.
-After one second, the picture's label was presented auditorily, and the infants' N400 component was registered.
+After one second, the picture's label was auditorily presented, and the infants' N400 component was registered.
 In some trials the auditory label corresponded to a canonical realisation of the word-form.
@@
 This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
-In bilinguals, only one study had used an implicit naming paradigm to study cross-language priming.
-@von2014bilinguals adapted @mani2010infant procedure to test German-English bilinguals.
+Evidence of implicit naming in bilinguals is, however, scarce.
+
+To our knowledge, only one study has used an implicit naming paradigm to study cross-language priming in bilinguals.
+@von2014bilinguals adapted @mani2010infant procedure to test German-English bilingual adults.
 The authors manipulated the phonological overlap between the prime label in English (presented in silence) and a German target (auditorily presented) in both German and English.
-Participants' ERPs revealed differences between trials in which the German prime label overlapped phonologically with the English target label, compared to trials in which none of the labels overlapped.
+Participants' evoked potentials revealed differences between trials in which the German prime label overlapped phonologically with the English target label, compared to trials in which none of the labels overlapped.
 These results suggest that adult bilinguals implicitly named prime pictures, and that the resulting label interacted with subsequent word recognition.
 
-As mentioned in the Discussion of Study 1, we consider three scenarios under which implicit naming might have occurred, in line with previous literature, but our design failed to capture it.
-First, it might be possible that infants in both Studies 1 and 2 implicitly generated phonological labels for the primes, but such labels lacked the phonological detail to interact with the subsequent recognition of a phonologically related target word.
+In contrast with previous studies in monolingual infants, and bilingual adults, we found no evidence of implicit naming was found.
+We consider three scenarios under which implicit naming might have occurred, in line with previous literature, but our design failed to capture it.
+First, it is be possible that infants in both Studies 1 and 2 implicitly generated phonological labels for the primes, but such labels lacked the phonological detail to interact with the subsequent recognition of a phonologically related target word.
 This is unlikely, given that both monolinguals and bilinguals have been shown to encode lexical representations with high phonological detail from early ages [@swingley2000spoken; @bailey2002phonological; @tamasi2016measuring; @tamasi2017pupillometry; @ramon2009vowel].
-A second possibility is that participants successfully retrieved the phonological form of the prime labels, but such forms failed to interact with target recognition.
+
+A second possibility is that participants successfully retrieved a detailed phonological form of the prime labels, but such forms failed to interact with target recognition.
 This would be explained by the lack of strong associations between phonologically related lexical representations at these ages.
 But even if one considers the possibility that participants in Study 1 failed to show priming effects for this reason (for instance, the emergence of phonological associations might follow different trajectories in Catalan-Spanish infants, compared to English infants), the fact that English monolingual infants in Study 2 failed to show such priming effects contradicts previous findings on the same population, reporting priming phonological priming effects in even younger infants [@mani2010infant; @mani2011phonological].
-Finally, it is possible that the adjustments carried out during the adaptation of the task might have reduce the chances of detecting the anticipated effects.
+
+Third, it is possible that the modifications of the implicit naming task in the present investigation might have reduce the chances of detecting the anticipated effects.
 The most critical difference between the original design of the implicit naming task by Mani and Plunkett and that of the present study is the absence of a pre-naming phase during the test phase.
-Prime and target were presented very close in time.
-The onset of the target occurred 1,550 ms after prime picture onset.
-It is possible that such time interval was too short for participants to retrieve the phonological label of the prime picture, so that the auditory presentation of the target disrupted prime lexical access.
+Target auditory labels were presented immediately after the offset of the prime picture.
+It is possible that such time interval was too short for participants to retrieve the phonological label of the prime picture before the target was presented.
 Further research should investigate the role of prime-target inter-stimulus interval on the time course of lexical access and selection in toddlers.
 
-The present study introduces several methodological contributions.
-First, the longitudinal design of the data collection provided a more suitable design for drawing conclusions about developmental change in word recognition trajectories, compared to studies that tested participants from a single age group [@floccia2020translation], or studies that with an exclusively cross-sectional design [@von2012language].
-Second, the modelling approach in the present study incorporates the double source of repeated measures simultaneously into the random effects structure of the multilevel model.
-The models in Studies 1 and 2 accounts for the time course of target looking across the trials and its associated autocorrelation using Hierarchical General Additive Models [@barr2008analyzing; @pedersen2019hierarchical].
-The models also incorporate the observations from the same testing session as a nested grouping variable inside participants, so that the test session-level parameters in each model are estimated taking into account the estimations of other testing sessions from the same participants.
-Overall, this approach allowed us to simultaneously model the participant-level variability, the testing session-level variability, and the time series consisting of participants' gaze behaviour during the task.
-Finally, the adoption of a Bayesian approach to implement and estimate the model allowed the incorporation of prior knowledge about the distribution of the parameters to generate stable estimates, despite the complexity of the model.
-
-The findings in the present investigation have important implications for current models of bilingual lexical development.
+The null pattern of results found in the present investigation would have important implications for current models of bilingual lexical development.
 Recent accounts of bilingual word acquisition pointed to a facilitative role of phonological similarity between the two languages.
@@
 
+The present study introduces several methodological contributions.
+First, this is, to our knowledge, the first study investigating cross-language priming using an implicit naming paradigm in toddlers.
+Second, the longitudinal design of the data collection provided a more suitable design for drawing conclusions about developmental change in word recognition trajectories, compared to studies that tested participants from a single age group [@floccia2020translation], or studies that with an exclusively cross-sectional design [@von2012language].
+Third, the modelling approach in the present study incorporates the double source of repeated measures simultaneously into the random effects structure of the multilevel model.
+The models in Studies 1 and 2 accounts for the time course of target looking across the trials and its associated autocorrelation using Hierarchical General Additive Models [@barr2008analyzing; @pedersen2019hierarchical].
+The models also incorporate the observations from the same testing session as a nested grouping variable inside participants, so that the test session-level parameters in each model are estimated taking into account the estimations of other testing sessions from the same participants.
+Overall, this approach allowed us to simultaneously model the participant-level variability, the testing session-level variability, and the time series consisting of participants' gaze behaviour during the task.
+Finally, the adoption of a Bayesian approach to implement and estimate the model allowed the incorporation of prior knowledge about the distribution of the parameters to generate stable estimates, despite the complexity of the model.
+
 In summary, we tested the language non-selective hypothesis of lexical access in bilingual toddlers using an implicit naming paradigm.
 In Study 1, we did not find evidence of within-language or cross-language priming effects, suggesting that participants might have not generated covert labels for the prime pictures presented in silence.
-In study 2, we attempted to replicated the original study showing evidence of implicit naming in younger infants, but found no evidence of such effects: monolingual infants did not show evidence of implicit naming.
-Overall, our results allude to more complex state of the investigation about early priming effects than ancitipated from the literature.
-
-Previous studies had reported similar cross-language priming effects, but the conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was nonetheless unwarranted.
-In studies where the auditorily presented prime label was phonologically overlapped with the target label [e.g., @marian1999activation], priming effects could be explained by sub-lexical facilitation across phonological segments.
-This might explain the facilitation effect found in *phonological priming* trials in @von2012language, in which English prime and German target labels shared overt phonological overlap.
-In contrast, the interference effect found in *priming through translation* trials points to cross-language competition at the lexical level.
-Since participants' target recognition was modulated by the phonology of the German translation of the prime (which participants did *not* hear), cross-language priming can be explained by the lexical co-activation of the English *and* German prime labels.
+In Study 2, we attempted to replicated the original study showing evidence of implicit naming in younger infants, but found no evidence of such effects: monolingual infants did not show evidence of implicit naming.
+Overall, our results allude to more complex state of the investigation about early priming effects than anticipated from the literature.
 

### 2023-11-22 manuscript/_appendix/_stimuli.qmd
Move stimuli details to appendix

--- 2023-11-09 manuscript/draft.qmd
@@
 ---
-format:
-  docx: default
 ---
 
-```{r setup}
-#| label: setup
-#| echo: false
-#| message: false
-#| warning: false
-# load objects
-targets::tar_config_set(store = here::here("_targets"),
-						script = here::here("_targets.R"))
-
-targets::tar_load_globals()
-
-targets::tar_load(
-	c(participants,
-	  stimuli,
-	  vocabulary,
-	  attrition_trials,
-	  attrition_participants,
-	  bvq_data,
-	  gaze,
-	  data_bcn,
-	  data_oxf
-	))
-
-# targets::tar_load(
-# 	c(model_fits_bcn,
-# 	  model_loos_bcn,
-# 	  model_fits_oxf,
-# 	  model_loos_oxf
-# 	))
-
-# prepare data
-attrition <- lst(participants,
-				 attrition_participants,
-				 attrition_trials) |>
-	reduce(inner_join, by = join_by(session_id)) |>
-	unnest_wider(matches("all"), names_sep = "_") |> 
-	rename_with(\(x) gsub("is_valid_gaze_all_|is_valid_vocab_all", "", x))
-
-library(knitr)
-library(kableExtra)
-library(ggplot2)
-library(gt)
-library(gtExtras)
-library(patchwork)
-library(english)
-library(gtExtras)
-
-# set ggplot theme and colour palette
-my_theme <- theme_minimal() +
-	theme(panel.grid = element_blank(),
-		  axis.line = element_line(colour = "black"),
-		  text = element_text(size = 12, colour = "black"),
-		  axis.text = element_text(colour = "black"))
-
-theme_set(my_theme)
-
-clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
-
-options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
-		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
-		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
-		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
-		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
-		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
-
-set.seed(1234)
+```{r stimuli-values}
+n_words <- stimuli |>
+	filter(test_language=="English") |> 
+	select(prime, target, distractor) |> 
+	unlist() |> 
+	n_distinct()
 ```
 
-# Introduction
-
-Building a mental lexicon is a major achievement in the development of an infant: by storing representations of how familiar words sound and what they mean, an infant is able to make sense of their linguistic input.
-The foundations of an initial lexicon are in place before their first year of life [@tincoff1999some; @halle1994emergence; @vihman2004cross; @parise2012electrophysiological; @bergelson20126; @bergelson2015early].
-This initial lexicon consists of only a few items; mainly words for people, interjections, body parts, and food [@tincoff2012six; @tardif2008baby], but it undergoes rapid growth during the second year of life [@ganger2004reexamining; @goldfield1990early; @bloom2002children; @mcmurray2007defusing].
-According to parental reports, the average 15-month-old infant already understands more than 100 words, and by two years, they understand more than 400 words [@frank2021variability].
-This accelerated lexical developmental is reflected in infants' trajectories of word recognition: infants recognise familiar words faster and more efficiently as they approach their second birthday [@fernald1998rapid; @fernald2001half; @hurtado2007spoken].
-
-Despite being exposed to a more complex linguistic input, bilinguals show equivalent trajectories of word acquisition and word recognition to their monolingual peers' [@vihman2007onset; @legacy2018vocabulary; @hoff2012dual; @de2014bilingual; @pearson1994patterns; @byers-heinlein2023sometimes].
-This is a remarkable deed for two reasons.
-First, bilingual infants receive a relative impoverished linguistic input in each of their languages compared to monolinguals [@costa2014does].
-Second, they face a more complex referential context, since they often learn two labels for each referent, one in each language.
-The mechanisms that allow bilingual' trajectories of lexical developmental to keep up with monolinguals' are still unclear.
-
-Monolinguals and bilinguals share broadly common word-recognition mechanisms.
-The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal, which results in the activation of lexical representations whose associated phonological forms match the acoustic signal.
-The activated word-forms then compete for selection: the lexical system uses the bottom-up information provided by the auditory input, together with top-down context---provided by grammatical, supra-segmental, and semantic constraints---to select the candidate lexical representation with the best match.
-This sequence of events occurs in a *cascaded* fashion.
-As the recognition system accumulates information about the unfolding acoustic signal, matching phonological representations are activated [@marslen1987functional; @marslen1978processing; @grosjean1980spoken], and in turn activate their associated semantic representations [@neely1977semantic].
-By the time lexical selection occurs, many non-selected phonological and semantic representations have been activated, potentially modulating the dynamics of word recognition.
-
-A considerable amount of evidence for such cascaded account of lexical processing has been provided by studies recording eye movements during word recognition.
-For example, @allopenna1998tracking designed a word-recognition task in which participants were presented, in each trial, with four objects in the screen.
-Participants would then listen to a command like "Pick up the beaker; now put it below the diamond", and perform the action.
-The authors manipulated the phonological relationship between the target object's label (e.g., *casket*), and the label of each of the three distractors.
-Two of the distractors were phonologically related to the target, sharing onset (e.g., *castle*) or offset (e.g., *basket*), respectively.
-The other distractor was phonologically unrelated to the target (e.g., *nickel*).
-After the onset of the auditory target label, phonological distractors attracted participants' eye fixations more than unrelated distractors.
-Distractors sharing phonological onset did so at an earlier time window than those sharing phonological offset.
-This time course of distractor fixations suggests that the auditory presentation of the target label activated no only its (subsequently selected) phonological form in participants' lexicon, but also that of phonologically related word-forms, leading to competition for selection between the word forms.
-These results converge with cascaded models of auditory word recognition, in which the unfolding acoustic input activates multiple phonological word-forms, which in turn compete for selection, like TRACE [@mcclelland1986trace] and Shortlist [@norris1994shortlist].
-
-The developing mental lexicon also seems to operate in this cascaded fashion: like adults, infants activate non-selected lexical representations.
-For instance, priming paradigms of word recognition have provided a strong body of evidence for the existence of phonological and semantic links between early lexical representations between 18 and 21 months of age..
-@arias2009lexical found that infants' spoken word recognition (e.g., *dot*) was interfered by the previous presentation of a semantically related word (e.g., *cat*).
-Other studies have provided electrophysiological evidence of semantic priming at earlier ages [e.g., @rama2013development; @friedrich2005lexical].
-More recent studies have provided evidence for the emergence of such semantic links, even in the absence of visual referents during the experimental task [@willits2013toddlers].
-Phonological priming effects have also been reported in the initial lexicon.
-@mani2010infant and @mani2011phonological created an implicit naming task in which each trial started with the *silent* presentation of a prime picture.
-Then, a target-distractor picture pair was presented side-by-side.
-Finally, the target picture's label was presented auditorily.
-The authors manipulated the phonological overlap between the prime label and the target label, so that in half of the trials both labels were phonologically related, sharing phonological onset (*cat*-*cup*), or phonologically unrelated (*ball*-*comb*).
-Prime and target-distractor pairs were semantically unrelated.
-Interestingly, infants showed different target looking preference patterns after phonologically related prime pictures, compared to after phonologically unrelated primes.
-This suggests that infants implicitly named prime pictures---despite such pictures having been presented in silence---and that the phonology of the resulting labels interacted with subsequent target.
-
-@chow2017spoken provided further evidence of semantic *and* phonological links in the early lexicon.
-The authors adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors.
-In each trial, the authors presented participants with four semantically and phonologically pictures.
-Four seconds after pictures onset, a word-form was auditorily presented.
-The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category.
-For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress.
-Then they would hear the carrier phrase "Look at the *bee*!".
-The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial.
-These results support a cascaded activation account of lexical access during the first stages of lexical development, paralleling previous findings in adults [@allopenna1998tracking].
-
-One of the most interesting pieces of evidence in support of a cascaded account of lexical processing is provided by bilinguals.
-A critical property the bilingual lexicon is that its representations are accessed in a language-non selective way.
-Even during monolingual situations, bilinguals access their lexical representations in both of their languages [e.g., @thierry2007brain; @dunabeitia2009masked; @hoshino2008cognate; @strijkers2010tracking; @duyck2007visual].
-This is reflected in bilinguals' performance in word recognition and production tasks.
-For instance, @marian1999activation presented Russian-English bilinguals with a series of trials that started with an auditory instruction like "Poloji marku nije krestika" ["Put the stamp below the cross"].
-The instruction would be present in Russian (dominant language for most participants).
-The target object (*marku* [*stamp*], in this case) would be present in the screen, together with an object whose English label shared phonological onset with the target label (e.g., *mark*), and two unrelated distractors whose labels in Russian and English did not shared phonological relationship with the target label.
-In line with @allopenna1998tracking's results in monolingual adults, bilinguals fixated the cross-language phonological distractor significantly more than the unrelated distractors after hearing the target label.
-These findings suggest that bilinguals activated phonologically related word-forms in both Russian *and* English, which ultimately affected their overt visual exploration patterns during the task.
-
-Language non-selectivity in the bilingual lexicon has also been shown to affect top-down lexical access during word production.
-@costa2000cognate presented Catalan-Spanish bilinguals with a series of pictures of familiar objects.
-For each object, participants were asked to name it in Catalan (their dominant language).
-Unbeknownst to participants, the authors manipulated the phonological overlap between the pictures' labels in Catalan and their translations in Spanish.
-In half of the trials, the labels associated to the pictures were cognates, that is, phonologically similar translation equivalents (e.g., *gat*-*gat* [*cat*]) in Catalan and Spanish, whereas in the other half of the trials the labels were non-cognates (e.g., *taula*-*mesa* [*table*]).
-Participants named pictures faster in cognate trials than in non-cognate trials.
-Critically, Spanish monolinguals who completed the same task, naming the pictures in Spanish, showed equivalent naming times in both conditions.
-These results reveal that bilinguals activated their Spanish phonology, despite performing the naming task exclusively in Catalan: the visual recognition of the presented pictures led to the activation of its associated phonological forms in both languages in parallel, which influenced the subsequent the dynamics of word production.
-This differential processing of cognates and non-cognates has generated a large body of literature providing support for the language-non selective account of lexical access [e.g., @degrootandnas1992; @schwartzkroll2007; @dijkstragrainger1999; @dufour1995matching; @schwartz2007reading; @dijkstra2010cross].
-
-Further evidence in favour of the parallel retrieval of phonological forms during bilingual word production is given by implicit naming paradigms.
-Using an adaptation of @mani2010infant's task, @von2014bilinguals found that bilingual adults generate implicit labels in both labels for visually fixated pictures.
-The authors presented German-English bilinguals with 120 prime-target pairs.
-Primes were presented as familiar pictures in silence.
-After prime picture offset, target words were presented auditorily.
-Participants' N400 ERP components were recorded from target word onset.
-The authors manipulated the phonological relationship between the prime and target word-forms within participants' L1 and across L1 and L2.
-When prime and target were phonologically identical (*Affe*-*Affe*, German for *monkey*), or similar (*Fahne*-*Sahne*, German for *flag* and *ice-cream*, respectively) within L1, participants' showed a reduced N400 amplitude, compared to when prime and target were phonologically unrelated (*Messer*-*Seil*, German for *knife* and *rope*).
-Critically, a similar effect was found when prime and target were phonologically related through translation (*Rustsche*-*Kleid*, German for *slide* and *dress*).
-This suggests that participants activated prime labels in both languages in parallel, and that both labels impacted the dynamics of target words recognition.
-
-Phonological priming paradigms have also revealed language non-selectivity in the initial bilingual lexicon [@poarch2012cross; @bosma2020cognate; @singh2014one; @jardak2019labels; @von2019impact].
-For instance, @von2012language found evidence of cross-language phonological priming in 21- to 42-months-old children learning German and English.
-At the beginning of each trial, the authors auditorily presented an English prime word embedded in a carrier phrase.
-Then, the target label was also auditorily presented in German.
-Finally, the target and distractor pictures were presented side-by-side.
-In some trials, the auditorily presented prime and target labels were phonologically related (e.g., *slide*-*Klide* [*dress*]).
-In some other trials, both labels were phonologically related through translation: the auditorily presented prime label did *not* overlap with the target label (e.g., *leg*-*Stein* [*stone*]), but its translation in German did [*Bein*].
-In the rest of the trials prime and target labels were phonologically unrelated in both languages.
-The authors found a facilitation effect of cross-language priming when both prime and target auditory labels overlapped phonologically, as revealed by a stronger target picture looking preference, as compared to that of unrelated trials.
-Interestingly, participants showed a weaker target preference in priming through translation trials.
-
-Using a similar task, @floccia2020translation provided conflicting results to those of @von2012language.
-The authors tested 27-month-old simultaneous bilinguals in a cross-language priming paradigm.
-The two languages participants were learning were English, and an Additional Language (either Cantonese, Dutch, French, German, Greek, Italian, Mandarin, Polish, Portuguese, or Spanish).
-A prime word was embedded at the end of a carrier sentence that participants listened to.
-Then, participants were presented with the auditory label of the target word, and two pictures were shown side-by-side, the target picture, and a distractor picture.
-In Study 1, the target word was the translation equivalent of the prime word (*cheese*-*fromage* for an English-French bilingual).
-In other trials, prime and target words were unrelated (e.g., *sock*-*fromage*).
-There was no phonological overlap at onset between prime and target or distractor labels in either of the two conditions.
-Participants were presented with two blocks of related and unrelated trials.
-In one of the blocks, participants were presented with English prime words and Home Language target words (*sock*-*fromage*), and in the other block they were presented with Additional Language prime words and English target words (*fromage*-*sock*).
-The authors found a cross-linguistic priming effect, in which participants showed a stronger preference for the target picture in the post-naming phase in related trials, as compared to unrelated trials.
-This effect was found regardless of the language of the prime (English or Home Language), or the dominance of the language of the prime (i.e., whether the prime word belonged to the dominant language).
-Target preference exceeded chance level in both conditions, pointing to successful word recognition regardless of the experimental manipulation.
-
-In a second study, @floccia2020translation, the authors tested an equivalent group of bilinguals in a cross-linguistic semantic priming task, in which participants were primed with words in English, and tested with semantically related words in the Additional Language (or vice versa).
-This time, prime and target words were not translation equivalents, but rather words whose referents shared semantic features.
-Results paralleled those from their first study.
-The authors found a strong semantic priming effect across languages, regardless of the language of the prime or the dominance of the language of the prime.
-Overall, these results suggest that bilinguals recognised target words in both conditions, and benefited from a cross-linguistic facilitation effect from translation equivalents.
-The symmetry of such effect across both languages suggests that participants lexical access occurred in parallel for the two members of translation equivalents.
-As the authors noted, the stimuli set of their second study contained multiple cognates due to design constraints, especially in languages with a larger degree of phonological overlap across translation pairs (e.g., English and Dutch).
-The authors run *post hoc* analyses exploring the effect of cognateness on the cross-language priming effects found, which showed no evidence of a cognateness effect on target preference.
-However, the cross-language effects reported in this second study might still reflect the confounding influence of cognateness, as the resulting effect might have been generated by an interaction by the phonological and semantic overlap between cognate primes and targets.
-
-Previous studies had reported similar cross-language priming effects.
-The conclusion that such effects occurred at the lexical level, as opposed to being the result of mere acoustic similarity, was nonetheless unwarranted.
-In studies where the auditorily presented prime label was phonologically overlapped with the target label [e.g., @marian1999activation], priming effects might be explained by the activation of the phonological segments of the prime label, which facilitated the recognition of the target label, which shared such phonological segments.
-The priming-through-translation results by @von2012language and @floccia2020translation demonstrate that cross-language activation in the developing lexicon occurs at the lexical level.
-Since participants' target recognition was modulated by the non-presented prime translation, such an inhibitory effect must stem at the lexical level.
-The fact that phonological priming facilitated the recognition of the target words (both labels belong to different languages), and that phonological priming through translation interfered target recognition (translation and target belong to the same language) points to cross-language connections playing an excitatory role, and to within-language connections playing an inhibitory role.
-
-The priming-through-translation paradigm provides a convenient framework to investigate parallel activation in the bilingual lexicon, but its design prevents strong interpretations about the extent to which parallel activation is the result of the experimental manipulations of interest.
-The presentation of primes and targets in both languages in the same task---or even within the same trial---presents participants with a bilingual context that might lead to a higher baseline activation of lexical representations of both languages, contrary to a context in which parallel activation results from genuine cross-language activation [@grosjean1997bilingual].
-Another limitation of priming-through-translation studies is that, when prime words are auditorily presented, the task constrains the naming context to one of the languages.
-The consequence is a potential asymmetry between the activation dynamics of the lexical representation of both labels: while the participant has heard one label, the activation of its translation must spread across semantic links.
-This might lead to a lower strength, and higher latency of the activation of the translation.
-
-In the present study, we put the hypothesis that bilingual infants activate both languages in parallel to a more severe test.
-We used an extension of the implicit naming paradigm by @mani2010infant, in which participants were primed with a picture presented in silence.
-This provides participants with an exclusively monolingual context in which they perform the task in only one of their languages.
-If differences in task performance are found associated with covert manipulation of cross-linguistic properties of the stimuli, such differences may be more conclusively linked to the parallel activation of lexical representations in participants' lexicons.
-By using an implicit naming paradigm, the activation of the lexical representation of the prime may occur in both languages as the result of lexical retrieval after visual recognition of the prime picture, since participants are not presented with any auditory prime label.
-This contrasts with priming through-translation tasks, in which the prime label in one of the languages is directly activated by auditory word recognition, while the label of its translation is expected to be activated as the result of cascaded activation spreading through their semantic association.
-This may lead to an asymmetry in the time course of the activation of both labels, which might in turn affect the dynamics of phonological priming in subsequent word recognition.
-
-In summary, the present study was aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them.
-Using an adaptation of [@mani2010infant], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm.
-We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages.
-If so, phonological priming effect should be larger when the prime label in both languages shares phonological overlap with the target words (*Related/Cognate* condition), compared to when only the label of the prime in one language overlaps phonologically with the target (*Related/Non-cognate*).
-We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.
-
-To test cross-language priming effects, we registered participants' time course of target picture looking in the three conditions.
-We predicted within-language priming effects, revealed as differences in target looking between *Unrelated* and *Related/Non-cognate* trials, as previously reported [@von2012language, @mani2010infant, and @mani2011phonological].
-We further predicted cross-language priming effects, revealed as differences in target looking between *Related/Non-cognate* and *Related/Cognate* trials.
-This effect should be stronger in bilinguals, if not completely absent in monolinguals, who should be indifferent to the phonological properties of the stimuli in the other language.
-
-Following previous studies associating the emergence of phonological links between lexical items to the size of children's vocabulary [@mani2011phonological], we also compared the explanatory power of two indices of receptive vocabulary size (dominant-language vocabulary size and total vocabulary size) against participants' age.
-We used parental reports of vocabulary checklist to estimate participants' vocabulary size.
-We computed vocabulary size in the dominant language (L1 vocabulary) as the proportion of words in the dominant language reported by their caregivers to be understood by the child in a vocabulary checklist, and the total vocabulary size as the proportion of words reported as understood by the child in *both* languages.
-If within-language or cross-language phonological associations in the lexicon emerge as a function of vocabulary growth, the size of the differences between conditions should larger in participants with larger vocabulary sizes.
-A model including participants' L1 or total vocabulary size as a predictor should then show better performance than a model that instead includes participants age.
-In the case of bilinguals, if the emergence of cross-language priming effects is associated with the growth of their vocabulary is *both* languages, a model including total vocabulary size as a predictor should perform better than a model that includes L1 vocabulary size.
-The opposite pattern would indicate that cross-language priming effects emerge as a function of the growth of L1 vocabulary.
-
-Testing bilingual populations at early ages presents the limitation that the vocabulary size of participants' non-dominant language is relatively small, which substantially constrains the number of items that can be used to as stimuli in the task, as well as the number of trials that can be constructed to generate stimuli lists.
-In order to circumvent the problem of limited vocabulary knowledge in the non-dominant language, tested participants only in their dominant language, therefore directing our research to the question of how possessing a second language affects processing of the dominant one in bilingual toddlers [@costa2014does provide a fuller description of the advantages of such approach].
-
-# Study 1
-
-## Methods
-
-All materials, data, and reproducible code can be found at the OSF ([https://osf.io/hy984/](https://osf.io/ckydb/)) and GitHub ([https://github.com/gongcastro/cognate-priming](https://github.com/gongcastro/cognate-priming)) repositories.
-This study was conducted according to guidelines laid down in the Declaration of Helsinki, and was approved by the Drug Research Ethical Committee (CEIm) of the IMIM Parc de Salut Mar, reference 2020/9080/I.
-Before every testing session, caregivers were asked to read and sign an informed consent form, and were given a token of appreciation at the end of it.
-
-### Participants
-
-```{r}
-#| label: participants-numbers
-participants_bcn <- filter(participants, location=="Barcelona")
-
-n_participants_total <- nrow(distinct(participants_bcn, child_id))
-n_sessions_total <- count(participants_bcn)
-
-n_participants_lp <- participants_bcn |> 
-	distinct(lp, child_id) |> 
-	count(lp)
-
-n_participants_lp_sex <- participants_bcn |> 
-	distinct(lp, sex, child_id) |> 
-	count(lp, sex)
-
-n_participants_sessions <- participants_bcn |> 
-	count(child_id, name = "n_sessions") |> 
-	count(n_sessions) |> 
-	group_split(n_sessions) |> 
-	set_names(paste0("session_", 1:3)) |> 
-	map("n")
-
-n_sessions_lp <- participants_bcn |> 
-	summarise(across(age, lst(mean, sd, min, max)), n = n(), .by = c(lp)) |> 
-	mutate(across(age_mean:age_max, \(x) round(x, 2))) |> 
-	group_split(lp) |> 
-	set_names(janitor::make_clean_names(unique(participants_bcn$lp)))
-
-n_sessions_dominance_lp <- count(participants_bcn, lp, test_language) |> 
-	group_split(test_language) |> 
-	set_names(c("catalan", "spanish")) |> 
-	map(group_split, lp)
-
-n_sessions_lp <- participants_bcn |> 
-	count(lp) |> 
-	group_split(lp) |> 
-	set_names(c("monolingual", "bilingual")) |> 
-	map("n")
-```
-
-We collected data from `r n_participants_total` children living in the Metropolitan Area of Barcelona (Spain), tested at the Laboratori de Recerca en Infància at the Universitat Pompeu Fabra.
-Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, `r n_participants_sessions$session_2` participated twice, and `r n_participants_sessions$session_3` participated three times.
-Recurrent participants were tested with at least XXX months of difference.
-We gathered a total of `r n_sessions_total$n` testing sessions.
-Participants were divided into monolinguals and bilinguals based on their relative degree of exposure to Catalan and Spanish, estimated using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
-We categorised participants as monolingual if exposed to more than 80% or more of the time to their dominant language, and as bilingual otherwise.
-`r english::Words(n_participants_lp$n[1])` of the participants were categorised as monolinguals (`r n_participants_lp_sex$n[1]` female, `r n_participants_lp_sex$n[2]` male) and `r n_participants_lp$n[2]` as Catalan/Spanish bilinguals (`r n_participants_lp_sex$n[3]` female, `r n_participants_lp_sex$n[4]` male) (see @tbl-participants for a detailed summary of participants' age and language profile).
-Participants' vision was normal, none used glasses or any other type of vision corrector.
-
-```{r tbl-participants}
-#| label: tbl-participants
-#| tbl-cap: "Demographic and linguistic profile of testing sessions."
-participants_bcn |> 
-	unnest_wider(doe) |> 
-	select(-matches("others")) |> 
-	arrange(lp, test_language) |> 
-	summarise(n = n(),
-			  n_participants = n_distinct(child_id),
-			  across(age, lst(mean, sd, min, max)),
-			  across(matches("doe_"), lst(mean, sd)),
-			  # age_vctr = list(age),
-			  .by = c(lp, test_language)) |> 
-	gt(rowname_col = "test_language",
-	   groupname_col = "lp") |> 
-	# gt_plt_dist(age_vctr, type = "histogram") |>
-	fmt_number(is.numeric, decimals = 1) |> 
-	fmt_integer(c(n, n_participants)) |> 
-	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
-	cols_merge(c(age_min, age_max), 
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(age_mean, age_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(doe_catalan_mean, doe_catalan_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(doe_english_mean, doe_english_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(doe_spanish_mean, doe_spanish_sd), 
-			   pattern = "{1} ({2})") |> 
-	tab_spanner("Age (months)", matches("age")) |> 
-	tab_spanner("Catalan", matches("catalan")) |> 
-	tab_spanner("English", matches("english")) |> 
-	tab_spanner("Spanish", matches("spanish")) |> 
-	tab_spanner("Degree of Exposure (%)", matches("doe")) |> 
-	cols_label(n = "N sessions",
-			   n_participants = "N participants",
-			   age_mean = "M (SD)",
-			   age_min = "Range",
-			   # age_vctr = "Distribution",
-			   doe_catalan_mean = "M (SD)",
-			   doe_english_mean = "M (SD)",
-			   doe_spanish_mean = "M (SD)") |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_spanners())
-
-# col_names <- c("Group",
-# 			   "Language",
-# 			   "Sessions", 
-# 			   "Participants",
-# 			   "M (SD)",
-# 			   "Range",
-# 			   "M (SD)",
-# 			   "M (SD)",
-# 			   "M (SD)")
-# participants_bcn |> 
-# 	unnest_wider(doe) |> 
-# 	select(-matches("others")) |> 
-# 	arrange(lp, test_language) |> 
-# 	summarise(n = n(),
-# 			  n_participants = n_distinct(child_id),
-# 			  across(age, lst(mean, sd, min, max)),
-# 			  across(matches("doe_"), lst(mean, sd)),
-# 			  # age_vctr = list(age),
-# 			  .by = c(lp, test_language)) |> 
-# 	mutate(age_mean = sprintf("%.1f (%.1f)", age_mean, age_sd),
-# 		   age_range = sprintf("%.1f-%.1f", age_min, age_max),
-# 		   doe_catalan = sprintf("%.1f (%.1f)", doe_catalan_mean*100, doe_catalan_sd*100),
-# 		   doe_spanish = sprintf("%.1f (%.1f)", doe_spanish_mean*100, doe_spanish_sd*100),
-# 		   doe_english = sprintf("%.1f (%.1f)", doe_english_mean*100, doe_english_sd*100)) |> 
-# 	select(lp:age_mean, age_range, doe_catalan, doe_spanish, doe_english) |> 
-# 	kable(digits = 1, 
-# 		  format = "latex",
-# 		  booktabs = TRUE,
-# 		  col.names = col_names,
-# 		  align = "llrrrrrrrrrrrr"
-# 	) |> 
-# add_header_above(c(
-# 	" " = 4,
-# 	"Age (months)" = 2,
-# 	"Degree of exposure (%)" = 8
-# )) |> 
-# 	row_spec(nrow(tbl_data) - 1,
-# 			 hline_after = TRUE
-# 	) 
-# 	add_footnote("For participants exposed to Catalan and Spanish exclusively, the proportion of Catalan exposure shown in the table is complementary to the degree of exposue to Spanish.
-For participants exposed to a third languages this proportion is not complementary unless one adds the degree of exposed to the third language, which never exceeded 10\\%.
-Participants with 100\\%, 0\\%, and 50\\% Catalan exposure would be traditionaly classified as Catalan monolingual, Spanish monolingual, and Catalan-Spanish bilingual, respectively.", notation = "none", escape = FALSE)
-```
-
-### Vocabulary size
-
-```{r vocab-values}
-vocabulary_bcn <- vocabulary |> 
-	inner_join(select(participants_bcn, session_id, lp, age_group),
-			   by = join_by(session_id))
-
-vocab_means <- vocabulary_bcn |> 
-	summarise(across(c(total_prop, l1_prop), lst(mean, sd)),
-			  n = n(),
-			  .by = c(age_group, lp)) %>%
-	mutate(across(matches("prop"), scales::percent)) %>%
-	split(paste0("age_", gsub(" months", "", .$age_group))) |> 
-	map(\(x) split(x, tolower(x$lp)))
-
-n_imputed <- table(vocabulary_bcn$is_imputed)[2]
-prop_imputed <- scales::percent(n_imputed/nrow(vocabulary_bcn))
-n_pool <- nrow(bvq_data$vocabulary)
-```
-
-We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability] developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers.
-Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
-We calculated two measures of receptive vocabulary size for each participant: *L1 vocabulary size* (proportion of words  reported as acquired in the checklist of the dominant language), and *total vocabulary size* (proportion of the words in both checklists reported as acquired).
-`r n_imputed` (`r prop_imputed`) Families failed to provide a complete response to the BVQ within the two-week time limit, or did not provide a successful response to the questionnaire.
-For missing questionnaire responses, we imputed the vocabulary size of the participant using single imputation, using the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
-We used participants age in months and their language profile (monolingual/bilingual) as predictors.
-We used the `mice` R package [@van2011mice] to perform imputation using the Bayesian linear regression method.
-
-Overall, there was a substantial increase in both total and L1 vocabulary sizes associated to age (see @fig-vocabulary).
-Monolinguals showed overall higher L1 vocabulary sizes than monolinguals: they were reported to understand an average of `r vocab_means$age_21$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$l1_prop_sd`) at 30 months, while bilinguals  were reported to understand an average of `r vocab_means$age_21$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$l1_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$l1_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$l1_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$l1_prop_sd`) at 30 months.
-Total vocabulary sizes showed the opposite pattern, with monolinguals infants being reported to understand `r vocab_means$age_21$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_21$monolingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_25$monolingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$monolingual$total_prop_mean` (*SD* = `r vocab_means$age_30$monolingual$total_prop_sd`) at 30 months, and bilinguals being reported to understand `r vocab_means$age_21$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_21$bilingual$total_prop_sd`) of the words at around 21 months, `r vocab_means$age_25$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_25$bilingual$total_prop_sd`) at 25 months, and `r vocab_means$age_30$bilingual$total_prop_mean` (*SD* = `r vocab_means$age_30$bilingual$total_prop_sd`) at 30 months.
-
-```{r fig-vocabulary}
-#| label: fig-vocabulary
-#| fig-cap: "Participant vocabulary sizes across ages and language profiles.
-Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
-Grey lines connect vocabulary size scores from the recurrent participants.
-For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested.
-Only participants included in the final data set are shown."
-#| fig-width: 6
-#| fig-height: 3.5
-vocabulary_bcn |> 
-	inner_join(filter(attrition_participants, is_valid_participant)) |> 
-	pivot_longer(c(total_prop, l1_prop),
-				 names_to = "measure",
-				 values_to = "prop",
-				 names_transform = \(x) gsub("_prop", "", x)) |> 
-	mutate(measure = if_else(measure=="l1", 
-							 "L1 vocabulary", 
-							 "Total vocabulary"),
-		   is_imputed = if_else(is_imputed, "Imputed", "Observed") |> 
-		   	factor(levels = c("Observed", "Imputed"))) |> 
-	ggplot(aes(age_group, prop,
-			   colour = lp,
-			   fill = lp)) +
-	facet_wrap(~measure) +
-	geom_line(aes(group = child_id),
-			  colour = "grey",
-			  alpha = 1/4, linewidth = 3/4) +
-	geom_dots(aes(side = if_else(lp=="Monolingual", "left", "right")),
-			  dotsize = 2,
-			  scale = 0.5,
-			  alpha = 3/4) +
-	stat_summary(fun.data = mean_se,
-				 geom = "errorbar",
-				 linewidth = 3/4,
-				 width = 0.15,
-				 colour = "black",
-				 show.legend = FALSE,
-				 position = position_dodge(width = 1.15)) +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 size = 2,
-				 colour = "black",
-				 show.legend = FALSE,
-				 position = position_dodge(width = 1.15)) +
-	# geom_point(alpha = 1) +
-	labs(x = "Age (months)",
-		 y = "Vocabulary size",
-		 colour = "Group",
-		 fill = "Group") +
-	scale_y_continuous(labels = scales::percent,
-					   limits = c(0, 1)) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"),
-		  legend.position = "top",
-		  legend.title = element_blank())
-```
-
-### Stimuli
-
-```{r stimuli-values}
-n_words <- length(unique(with(stimuli, unlist(prime, target, distractor))))
-```
-
-We used `r n_words` distinct words included in the BVQ to create the stimuli lists.
-We created six stimuli lists: three in Catalan, and three in Spanish.
-Each list contained 32 trials, each involving a prime-target-distractor group.
-Each word played a role as either prime, *or* as target and distractor across the three lists in their corresponding language.
-For instance, the Catalan word *cadira* appeared as *prime* in the three lists, but never as *target* or *distractor*; the Catalan word *bici* appeared as *target* and *distractor* across the three lists, but never as a prime.
+We used `r n_words` distinct words to create the stimuli lists.
+We created four stimuli lists of 32 trials, each trial involving a prime-target-distractor triplet.
+Words played a role as primes *or* targets/distractors across the three lists in their corresponding language.
+For instance, the word *boot* appeared as *prime* in the three lists, but never as *target* or *distractor*; the word *bird* appeared as *target* and *distractor* across the three lists, but never as a prime.
 Target-distractor pairings were held constant across the three lists in each language.
-For instance, in all Catalan lists the word *bici* was paired with the word *porta*.
+For instance, in all Catalan lists the word *bird* was paired with the word *milk*.
 Target-distractor pairings were also yoked, so that each member of the same target-distractor pair appeared once as target and once as distractor in each list.
-For instance, the *bici*-*porta* paired appeared twice in each of the three Catalan lists: once with *bici* as target and *porta* as distractor, and once with *porta* as target and *bici* as distractor.
+For instance, the *bird*-*milk* pair appeared twice in each of the four lists: once with *bird* as target and *milk* as distractor, and once with *milk* as target and *bird* as distractor.
 This counterbalancing avoided participants encountering looking at the target word guided solely by that word having being named in a previous trial.
 Finally, prime words appeared only once in each list: each target-distractor pair was associated with a different prime word in both appearances.
-In each list, the same prime word was presented alongside a different target-distractor pair.
-For instance, the Catalan prime word *barret* was presented with the *bici*-*porta* target-distractor pair in one list, with the *bici*-*porta* pair in another list, and with *berenar*-*amanida* in the remaining list.
+Across lists, the same prime word was presented alongside a different target-distractor pair.
+For instance, the prime word *boot* was presented with the *bird*-*milk* target-distractor pair in the first list, with the *bucket*-*mouse* pair the second list, with *balloon*-*snail* in the third list, and with *bread*-*fish* in the fourth list.
 To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias2009lexical].
-The order of the trials was randomised across experimental session, so that each time a participant was tested, the order in which the prime-target-distractor was presented was randomised.
+The order of the trials was randomised across experimental sessions, so that each time a participant was tested, the order in which the prime-target-distractor was presented was random.
 Each participant was randomly assigned to one of the three lists in the corresponding (dominant) language, and always the same list across their experimental sessions in the case of a recurrent participant.
-
-In 16 of the 32 trials of the same list (henceforth *related* trials), the prime and the target words were phonologically related, sharing phonological onset (at least first phoneme).
-In the other 16 trials (*unrelated* trials), prime and target did not share phonological onset.
-8 of the 16 *related* trials included a cognate prime (*cognate* trials), and the other 8 included a non-cognate trials (*non-cognate* trials).
-A prime word was considered cognate if its Catalan and Spanish translation shared phonological onset.
-Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
-Target and distractor word pairs were phonologically unrelated (did not share phonological onset).
-Some of them shared semantic features or a taxonomic relationship.
-This is the case of words associated with especially salient referents such as animals or food.
-To avoid infants guiding their gaze to these objects based on their saliency, we paired animals and food items together.
 The position of the target and distractor pictures (right or left) for each target-distractor pair was alternated, so that in one list the target would appear on the left, in another list it would appear on the right, and so on.
 
-We examined the overall equivalence of the three trial types by comparing them across three variables relating to the target word: lexical frequency, word prevalence, animacy.
-@tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
-Lexical frequencies were extracted from the Catalan and Spanish corpora of the CHILDES database [@macwhinney2000childes; @sanchez2019childes] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@zipf1945meaning; @van2014subtlex].
-We defined word prevalence as the proportion of same-aged infants who were reported to understand the word in the BVQ database.
-
-#### Auditory stimuli
-
-The auditory stimuli were natural exemplars of the selected target words, spoken by Central Catalan-Spanish proficient bilingual female speaker who was instructed to pronounce each word in a toddler-directed manner.
-Recordings were made with an Audio-Tecnica 328 microphone (AT2050) at a sampling rate of 44100 Hz, in a soundproof room at the *Laboratori de Recerca en Infancia* at University Pompeu Fabra.
-We used the Audacity and Praat [@boersma2001speak] software packages to record and edit the audio files.
 The speaker was presented with a list of words in Catalan.
@@
 The experimenter assigned the participant to the Catalan or Spanish stimuli list involving the closest variant to that of caregivers'.
-
-#### Visual stimuli
-
-Each word was depicted by a realistic phonographic representation of a typical exemplar.
-Image backgrounds were removed from the original pictures using the GNU Image Manipulation Program (GIMP), resized to a rectangle of a maximum of 400 pixels hight or wide, and finally placed in the centre of a 50% grey rectangle square of 500$\times$500 pixels.
-The final stimuli had a resolution of 72 dpi.
-When presented in the eye-tracker screen, the areas of interest (AOI) occupied an area of 13.23$\times$13.23 cm (11.613º visual angle from participants' perspective).
-
-```{r tbl-stimuli}
-#| label: tbl-stimuli
-#| tbl-cap: "Summary of stimuli properties by trial type."
-stimuli |> 
-	summarise(across(c(matches("familiarity_|freq_|animate_"), duration),
-					 tibble::lst(mean, sd, min, max)),
-			  .by = c(test_language, trial_type)) |> 
-	select(-matches("familiarity_se"), -matches("prime"),
-		   -c(is_animate_target_sd,
-		      is_animate_target_min,
-		      is_animate_target_max),
-		   -matches("min"), -matches("max")) |> 
-	gt(groupname_col = "test_language",
-	   rowname_col = "list") |> 
-	fmt_number(is.numeric,
-			   decimals = 1) |> 
-	fmt_number(matches("familiarity|animate"),
-			   scale_by = 100,
-			   decimals = 1) |> 
-	cols_merge(c(freq_target_mean, freq_target_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(familiarity_target_mean, familiarity_target_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(duration_mean, duration_sd),
-			   pattern = "{1} ({2})") |> 
-	cols_label(trial_type = "",
-			   familiarity_target_mean = "Prevalence (%)",
-			   freq_target_mean = "Frequency",
-			   is_animate_target_mean = "Animacy (%)",
-			   duration_mean = "Duration (s)") 
-```
-
-### Procedure
-
-Testing took place in a sound-proof room.
-Participants sat on their caregivers' lap in a dimly lit testing booth while the experimenter conducted the experiment from outside.
-Caregivers were instructed to keep their eyes shut (to avoid recording their gaze, instead of the participant's), to be still, and to avoid interacting with the participant verbally or non-verbally.
-Participants sat at approximately 65 cm from the eye-tracker and a XX-in screen of $1929\times1080$ screen resolution.
-We used a custom Matlab XXXX script using the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox] to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
-Sampling rate was set at 120 Hz.
-A 5-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
-We set a 55% grey background for the calibration and stimuli presentation.
-Auditory stimuli were presented through two loudspeakers located behind the screen, one to each side.
-The experimenter monitored the experimental from outside the room using a centrally located video camera place above the screen.
-After a successful calibration the experimenter triggered the onset of the first trial.
-Trials were presented uninterruptedly and  without intervention of the experimenter until the 32 trials were presented, or the experimental session had to be stopped because of the participant's behaviour.
-
-![Experimental task design with examples in Catalan.
-In each trial, the prime image is presented in silence for 1,500 ms.
-The the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
-In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
-In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
-In unrelated trials (*n* = 32), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){fig-align="center"}
-
-Each trial started with the presentation of an attention getter for 3,000 milliseconds.
-Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
-Fifty milliseconds after the offset of the prime image, an auditory label was played from the loudspeakers and, 700 milliseconds after the onset of the auditory label, the target and distractor pictures were presented side-by-side during 1,000 milliseconds until the end of the trial.
-After this, the attention getter of the next trial was immediately presented.
-Each experimental session took approximately 10 minutes.
-
-### Data analysis
-
-#### Data processing
-
-```{r dataset}
-attrition_bcn <- filter(attrition, location=="Barcelona")
-n_trials <- nrow(attrition_bcn)
-n_sessions <- n_distinct(attrition_bcn$session_id)
-n_participants <- n_distinct(attrition_bcn$child_id)
-n_trials_valid <- nrow(filter(attrition_bcn,
-							  is_valid_participant,
-							  is_valid_trial))
-n_sessions_valid <- sum(distinct(attrition_bcn,
-								 session_id,
-								 .keep_all = TRUE)$is_valid_participant)
-n_participants_valid <- n_distinct(
-	attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id)
-
-n_exc_prime <- sum(!attrition_bcn$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition_bcn$is_valid_gaze_test)
-n_exc_test_each <- sum(!attrition_bcn$is_valid_gaze_test_each)
-n_exc_participants <- sum(!distinct(attrition_bcn,
-									session_id,
-									.keep_all = TRUE)$is_valid_participant) 
-n_exc_participants_vocab <- sum(!distinct(attrition_bcn,
-										  session_id,
-										  .keep_all = TRUE)$is_valid_vocab_size)
-
-n_longitudinal <- attrition_bcn |>
-	filter(is_valid_participant,
-		   is_valid_trial) |>
-	distinct(child_id, session_n) |> 
-	count(child_id, name = "times") |> 
-	count(times)
-```
-
-We defined a time windows of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
-To avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
-Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
-We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
-
-After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
-The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition-trials shows a detailed description of the trial attrition.
-
-```{r tbl-attrition}
-#| label: tbl-attrition
-#| tbl-cap: "Participant-level and trial-level sample size after applying inclusion criteria. The number of excluded participants and trials is indicated between parentheses."
-expanded <- expand(attrition_bcn, lp, trial_type, is_valid_trial)
-
-n_lp <- attrition_bcn |> 
-	distinct(is_valid_participant, lp, session_id) |> 
-	count(is_valid_participant, lp) |> 
-	pivot_wider(names_from = is_valid_participant,
-				values_from = n,
-				names_repair = janitor::make_clean_names) |> 
-	mutate(n_participants_true = true,
-		   n_participants_false = false) |> 
-	select(lp, true, false)
-
-attrition_bcn |> 
-	summarise(n_trials_true = sum(is_valid_trial),
-			  n_trials_false = sum(!is_valid_trial),
-			  .by = c(lp, trial_type)) |> 
-	arrange(desc(lp)) |> 
-	pivot_wider(id_cols = lp,
-				names_from = c(trial_type),
-				values_from = matches("trials"),
-				names_repair = janitor::make_clean_names) |> 
-	left_join(n_lp, by = join_by(lp)) |> 
-	select(lp, true, false,
-		   matches("n_trials")) |> 
-	gt(rowname_col = "lp") |> 
-	tab_spanner("Participants", matches("participant")) |> 
-	tab_spanner("Trials", matches("trial")) |> 
-	fmt_integer(everything()) |> 
-	cols_merge(c(true, false),
-			   pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_cognate,
-				 n_trials_false_cognate),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_non_cognate,
-				 n_trials_false_non_cognate),
-				 pattern = "{1} ({2})") |> 
-	cols_merge(c(n_trials_true_unrelated, 
-				 n_trials_false_unrelated),
-				 pattern = "{1} ({2})") |> 
-	cols_label(true = "Participants", 
-			   n_trials_true_cognate = "Cognate",
-			   n_trials_true_non_cognate = "Non-cognate",
-			   n_trials_true_unrelated = "Unrelated") |> 
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |>
-	grand_summary_rows(fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~ fmt_integer(.))
-```
-
-#### Modelling approach
-
-```{r data-analysis}
-
-r_info <- sessionInfo()
-
-r_version <- glue::glue(r_info$R.version$major,
-						r_info$R.version$minor,
-						.sep = "."
-)
-stan_version <- "2.33.0"
-
-rope_interval <- c(-0.1, +0.1)
-```
-
-We used Bayesian Hierarchical General Additive Models (HGAMs) to model our data and test our hypotheses [@pedersen2019hierarchical].
-First, we defined our response variable as the empirical logit of target looking using @eq-elogit across all eye-tracking samples for each each participant in each condition [@barr2008analyzing; @agresti2012categorical].
-We used a Gaussian distribution to model our response variable.
-To test our hypotheses, we then included *Condition*, *Group*, and either *Age* ($\mathcal{M}_0$), *L1 vocabulary* ($\mathcal{M}_1$), or *Total vocabulary* ($\mathcal{M}_2$) as fixed effects in the model.
-We also added all two-way and three-way interactions between the predictors.
-We set two *a priori* contrasts for the *Condition* predictor: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
-We also set two *a priori* contrasts for the *Group* predictor: one comparing *Monolingual (ENG)* with *Monolingual (CAT/SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Bilingual (CAT-SPA)* participants coded as `0`), and another comparing *Monolingual (ENG)* with *Bilingual (CAT-SPA)* participants (sum-coded as `-0.5` and `+0.5`, with *Monolingual (CAT/SPA)* participants coded as `0`).
-Before entering the model, the numeric predictors *Age*, *L1 vocabulary*, and *Total vocabulary* were standardised by subtracting from each observation the mean of the predictor, and dividing the result from the standard deviation of the predictor.
-
-$$
-\eta' = \ln\bigg(\frac{\text{Target} + 0.5}{ \text{Distractor} + 0.5}\bigg)
-$$ {#eq-elogit}
-
-We included *Session*---which indexes individual testing sessions that may belong to the same participant---as grouping variable, nested within *Participant* grouping variable---which indexes a distinct participant.
-This nested random effects structure incorporates the longitudinal design of data collection, in which multiple participants were tested more than once at different ages.
-We added by by-session intercepts and *Condition* slopes, and by-participant intercepts and *Age* slopes.
-To model the time course of target looking across time bins, we included B-splines for the main effect of *Time*, and one for an adjustment of the *Time* cubic spline by *Group* and *Relatedness* [@wood2017generalized].
-For both splines, we specified $k = 6$ basis functions or *knots*.
-@eq-model shows a formal implementation of the model.
-
-$$
-\begin{aligned}
-\textbf{Likelihood:} \\
-y_i &\sim \mathcal{N}(\mu_i, \sigma_i) \\ \\
-\textbf{Linear model:} \\
-\eta'(\mu_i) &= (\beta_0 + u _{0_{i}}) +
-(\beta_1 + u _{1_{i}}) \cdot \text{Condition} +\\
-&\beta_{2} \cdot \text{Group} +
-\beta_{3} \cdot X + \beta_{4} \cdot (\text{Condition} \times \text{Group}) +\\
-&\beta_{5} \cdot (\text{Condition} \times X) + \beta_{6} \cdot (\text{Group} \times X) +\\
-&\beta_{7} \cdot (\text{Condition} \times \text{Group} \times X) +\\
-& \sum_{j = 1}^k b_{j_{0}} \cdot \beta_{8_{k}} \cdot \text{Time} +
-\sum_{j = 1}^k b_{j_{1}} \cdot\beta_{9_{k}} \cdot (\text{Time} \times \text{Group}) \\
-\text{where:} \\
-&\eta'\text{ is the empirical logit of target fixations} \\
-&X \in \{\text{Age}, \text{L1 vocabulary}, \text{Total vocabulary}\} \\
-&b_{j_{0-1}} \text{ are the basis cubic spline basis functions} \\
-&k \text{ is the number of knots in the spline (10)} \\
-\textbf{Prior:} \\
-\beta_{0-9} &\sim \mathcal{N}(0, 0.5) \\
-u_{0-2} &\sim \mathcal{N}(0, \sigma_{0-2})\\
-b_{0-1} &\sim \text{MVN}(0, \tau_{0-1}) \\
-\sigma_{0-2}, \tau_{0-1} &\sim \text{Exponential}(6)\\
-\rho_{0-2} &\sim LKJCorr(6)\\
-\text{where:}\\
-&\rho_{0-2} \text{ are the correlation parameters for } \sigma_{0-2}
-\end{aligned}
-$$ {#eq-model}
-
-The comparison between the three models including *Age*, *L1 vocabulary*, *Total vocabulary* as predictors was done using leave-one-out cross-validation (LOO-CV) as a benchmark of model performance, using Pareto-smoothed importance sampling (PSIS) to approximate it [@vehtari2017practical].
-We implemented the model using `brms` [@burkner2017brms], an R interface to the Stan probabilistic language (`r stan_version`) [@carpenter2017stan].
-We ran four iteration chains using the by-default No U-Turn Sampler algorithm with 1,000 iterations each and an additional 1,000 warm-up iterations per chain.
-
-#### Statistical inference
-
-We assessed the practical relevance of the estimated regression coefficients of the model following @kruschke2018bayesian.
-First, we specified a region of practical equivalence (ROPE) from `r rope_interval["lower"]` to +`r rope_interval["upper"]`, in the probability scale.
-This region indicates the range of values that we considered equivalent to zero.
-We then summarised the posterior distribution of each regression coefficient with the 95% highest density interval (HDI).
-This interval contains the true value of this coefficient with 95% probability, given the data.
-Finally, we calculated the proportion of posterior samples in the 95% HDI that fell into the ROPE, noted as $p(\text{ROPE})$, which indicates the probability that the true value of the regression coefficient falls into the ROPE (and therefore should be considered equivalent to zero).
-For example, $p(\text{ROPE})=.80$ indicates that, given our data, there is a 80% probability that the true value of the coefficient falls within the ROPE, and can therefore be considered equivalent to zero.
-
-# Study 2
-
-In this study, we conducted a conceptual replication of @mani2010infant and @mani2011phonological.
-Using the same task from Study 1, we tested a same-aged group of monolinguals being exclusively raised in British English speaking homes, the same population tested in the original studies.
-As in Study 1, we manipulated the phonological relationship between the prime and target labels at word onset, as well as the cognate status of the prime label.
-Evidence from implicit naming of prime images would be revealed by differences in target looking or its time course across the trials between *Unrelated* trials, and *Related/Non-cognate* and *Related/Cognate* trials.
-Given that participants in this study are monolinguals---and contrary to the monolinguals in Barcelona, have received no exposure to any other language---we would not expect the cognate status of the prime labels to exert any effect on subsequent target recognition.
-
-## Methods
-
-### Participants
-
-```{r}
-#| label: participants-numbers-oxf
-participants_oxf <- filter(participants, location=="Oxford")
-
-n_participants_total <- nrow(distinct(participants_oxf, child_id))
-n_sessions_total <- count(participants_oxf)
-
-n_participants_sex <- participants_oxf |> 
-	distinct(sex, child_id) |> 
-	count(sex)
-
-n_participants_sessions <- participants_oxf |> 
-	count(child_id, name = "n_sessions") |> 
-	count(n_sessions) |> 
-	group_split(n_sessions) |> 
-	set_names(paste0("session_", 1:2)) |> 
-	map("n")
-
-ages <- participants_oxf |> 
-	summarise(n = n(),
-			  n_participants = n_distinct(child_id),
-			  across(age, lst(mean, sd, min, max)),
-			  across(matches("doe_"), lst(mean, sd)),
-			  age_vctr = list(age),
-			  .by = c(lp, test_language))
-
-```
-
-We collected data from `r n_participants_total` children (`r n_participants_sex$n[1]` female, `r n_participants_sex$n[2]` male, `r n_participants_sex$n[3]` sex not reported, age: *Mean* = `r round(ages$age_mean, 2)` months, *SD* = `r round(ages$age_sd, 2)`, *Range* = [`r round(ages$age_min, 2)`-`r round(ages$age_max, 2)`]), living in the Oxfordshire area (United Kingdom), tested at the Oxford BabyLab at the University of Oxford.
-Families were recruited from maternity rooms in private hospitals and social media, and contacted via phone when the child's age spanned between 20 and 32 months.
-From the `r n_participants_total` children that participated, `r n_participants_sessions$session_1` participated once, and `r n_participants_sessions$session_2` participated twice.
-Recurrent participants were tested with at least XXX months of difference.
-We gathered a total of `r n_sessions_total$n` testing sessions.
-All participants were being raised in exclusively British English monolingual homes.
-
-### Vocabulary size
-
-```{r vocab-values-oxf}
-vocabulary_oxf <- inner_join(vocabulary, 
-							 select(participants_oxf, session_id),
-							 by = join_by(session_id))
-```
-
-We collected vocabulary data using parental responses to the Oxford Communicative Development Inventory (OCDI) [@hamilton2000infant].
-Families were sent the questionnaire immediately after each experimental session, and were given two weeks to fill it.
-Since all vocabulary sizes of English monolingual infants were only assessed in English, both *L1 vocabulary* and *total vocabulary* sizes were identical (see @fig-vocabulary-oxf).
-
-```{r fig-vocabulary-oxf}
-#| label: fig-vocabulary-oxf
-#| fig-cap: "Participant vocabulary sizes across ages and language profiles.
-Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
-Vocabulary size scores from the recurrent participants are shown linked."
-#| fig-width: 4
-#| fig-height: 4
-vocabulary_oxf |> 
-	inner_join(select(participants, child_id, session_id, age_group),
-			   by = join_by(child_id, session_id)) |> 
-	ggplot(aes(age_group, l1_prop)) +
-	geom_line(aes(group = child_id),
-			  colour = "grey",
-			  alpha = 1/4, linewidth = 3/4) +
-	geom_dots(dotsize = 2,
-			  colour = clrs[5],
-			  fill = clrs[5],
-			  scale = 0.5,
-			  side = "both",
-			  alpha = 3/4) +
-	stat_summary(fun.data = mean_se,
-				 geom = "errorbar",
-				 linewidth = 3/4,
-				 width = 0.1,
-				 colour = "black",
-				 show.legend = FALSE) +
-	stat_summary(fun = mean,
-				 geom = "point",
-				 size = 2,
-				 colour = "black",
-				 show.legend = FALSE) +
-	# geom_point(alpha = 1) +
-	labs(x = "Age (months)",
-		 y = "Vocabulary size",
-		 colour = "Group",
-		 fill = "Group") +
-	scale_y_continuous(labels = scales::percent) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"),
-		  legend.position = "top",
-		  legend.title = element_blank())
-```
-
-### Stimuli
-
-New stimuli lists were generated to adapt the experimental procedure to English-learning infants.
-Stimuli lists were created following the same constraints as in Study 1.
-Auditory stimuli were recorded following the same procedure as in Study 1, produced by Southern British English native female speaker in a toddler-directed manner.
-Audio and picture processing were performed following the same workflow as in Study 1.
-
-### Procedure and apparatus
-
-Same as in Study 1.
-The study was run using a custom Matlab script, PresentMate, based on the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox].
-Visual fixations were recorded using a Tobii TX 300 eye-tracker and a 23-in screen of 1920 $\times$ 1080 resolution.
-The Tobii Analytics SDK 3.0 was used to interact with the eye-tracking while the experiment was running.
-Sampling rate was set at 120 Hz.
-A 9-point calibration was performed before every experimental session, in which the picture of a colourful beach ball was presented.
-
-### Data analysis
-
-Same as in Study 1, but removing the *Group* predictor from the models, as only monolingual infants were tested.
-
-```{r dataset_oxf}
-attrition_oxf <- filter(attrition, location=="Oxford")
-n_trials <- nrow(attrition_oxf)
-n_sessions <- n_distinct(attrition_oxf$session_id)
-n_participants <- n_distinct(attrition_oxf$child_id)
-n_trials_valid <- nrow(filter(attrition_oxf,
-							  is_valid_participant,
-							  is_valid_trial))
-n_sessions_valid <- attrition_oxf |> 
-	distinct(child_id, .keep_all = TRUE) |> 
-	pull(is_valid_participant) |> 
-	sum()
-
-n_participants_valid <- n_distinct(
-	attrition_oxf[attrition_oxf$is_valid_participant, ]$child_id)
-
-n_exc_prime <- sum(!attrition_oxf$is_valid_gaze_prime)
-n_exc_test <- sum(!attrition_oxf$is_valid_gaze_test)
-n_exc_test_each <- sum(!attrition_oxf$is_valid_gaze_test_each)
-n_exc_participants <- sum(!attrition_oxf |> 
-						  	distinct(child_id, .keep_all = TRUE) |> 
-						  	pull(is_valid_participant))
-
-n_exc_participants_vocab <- attrition_oxf |> 
-	distinct(child_id, .keep_all = TRUE) |> 
-	mutate(is_valid_vocab_size = !is_valid_vocab_size) |> 
-	pull(is_valid_vocab_size) |> 
-	sum(na.rm = TRUE)
-
-n_longitudinal <- attrition_oxf |>
-	filter(is_valid_participant,
-		   is_valid_trial) |>
-	distinct(child_id, session_n) |> 
-	count(child_id, name = "times") |> 
-	count(times)
-
-n_trials_condition <- attrition_oxf |> 
-	filter(is_valid_participant) |> 
-	count(trial_type, is_valid_trial) %>%
-	split(janitor::make_clean_names(.$trial_type))
-```
-
-We defined a time windows of interest from 200 ms after target and distractor pictures onset until the end of the trial at 2,000 ms when  both pictures disappeared from screen.
-To avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
-Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
-
-We gathered data from `r format(n_trials, big.mark = ",")` trials from `r n_sessions` testing sessions, generated from `r n_participants` distinct participants.
-We excluded trials in which participants failed to provide 50% valid eye-tracking samples (equivalent to 750 ms) during the prime phase (*n* = `r format(n_exc_prime, big.mark = ",")`) or 50% valid samples (equivalent to 1,000 ms) during the target-distractor phase (*n* = `r format(n_exc_test, big.mark = ",")`).
-We also excluded trials in which participants did not provide at least 5% of valid samples (equivalent to 100 ms) of target or distractor looking in the test phase (*n* = `r format(n_exc_test_each, big.mark = ",")`) [see @floccia2020translation for a similar approach].
-
-After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the  *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
-The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-From the trials included in the final dataset dataset, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), were `r n_trials_condition$non_cognate_2$n` *Related/Non-cognate* trials(`r n_trials_condition$non_cognate$n` previously excluded), and `r n_trials_condition$cognate_2$n` were *Related/Cognate* trials (`r n_trials_condition$cognate$n` previously excluded).

### 2023-11-26 manuscript/manuscript.qmd
Add comments by NSG

@@
 
-targets::tar_load(
-	c(
-		participants,
+targets::tar_load(c(participants,
 					stimuli,
@@
 					data_bcn,
-		data_oxf
-	)
-)
-
-targets::tar_load(
-	c(
-		model_fits_bcn,
+					data_oxf))
+
+targets::tar_load(c(model_fits_bcn,
 					model_loos_bcn,
 					model_fits_oxf,
-		model_loos_oxf
-	)
-)
+					model_loos_oxf))
 
 # prepare data
-attrition <- lst(
-	participants,
+attrition <- lst(participants,
 				 attrition_participants,
-	attrition_trials
-) |>
+				 attrition_trials) |>
 	reduce(inner_join, by = join_by(session_id)) |>
 	unnest_wider(matches("all"), names_sep = "_") |>
-	rename_with(\(x) gsub("is_valid_gaze_all_|is_valid_vocab_all", "", x))
+	rename_with(\(x) gsub("is_valid_gaze_all_|is_valid_vocab_all",
+						  "", x))
 
@@
 my_theme <- theme_minimal() +
-	theme(
-		panel.grid = element_blank(),
+	theme(panel.grid = element_blank(),
 		  axis.line = element_line(colour = "black"),
 		  text = element_text(size = 12, colour = "black"),
-		axis.text = element_text(colour = "black")
-	)
+		  axis.text = element_text(colour = "black"))
 
@@
 
-options(
-	ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
+options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
 		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
@@
 		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
-	ggplot2.continuous.colour = ggplot2::scale_color_gradient
-)
+		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
 
@@
 
-The implicit naming paradigm provides an ideal experimental paradigm study the developing bilingual lexicon.
+The implicit naming paradigm provides an ideal experimental paradigm to study the developing bilingual lexicon.
 By covertly manipulating the cross-linguistic relationship between the prime and target labels, parallel activation can be tested while participants are presented with auditory stimuli (target labels) exclusively in one of their languages [see @von2014bilinguals for a similar approach in bilingual adults].
@@
 We tested a cohort of monolingual and bilingual infants learning Catalan and Spanish between 20 and 32 months of age.
-This allowed us to compare the performance of participants with differing vocabulary sizes in the word recognition task.
+We compared the performance of participants with differing vocabulary sizes in the word recognition task.
 In order to circumvent the problem of limited vocabulary knowledge in the non-dominant language, we tested participants only in their dominant language [@costa2014does].
@@
 In *Related/Non-cognate* trials, prime and target labels shared phonological onset in only the language of test.
-For instance an infant tested in Catalan would be presented with a chair as prime picture ($\textbf{c}\text{adira}_{\text{CAT}}/\text{silla}_{\text{SPA}}$) and with $\textbf{c}\text{ullera}_{\text{CAT}}$ [spoon] as target label.
+For instance an infant tested in Catalan would be presented with a chair as prime picture ($\textbf{c}\text{adira}_{\text{CAT}}/\text{silla}_{\text{SPA}}$ [chair]) and with $\textbf{c}\text{ullera}_{\text{CAT}}$ [spoon] as target label.
 In line with @mani2011phonological, we anticipated that the phonological overlap between prime and target should modulate target word recognition in both monolinguals and bilinguals.
@@
 Target word recognition should be delayed by the activation of a larger cohort of phonologically related words [@mani2011phonological; @chow2017spoken].
-In the case of bilinguals, two measures of vocabulary size are relevant: *total vocabulary size* and *dominant-language vocabulary size*.
-Total vocabulary size refers to the number of words that a child has acquired, regardless of the language they belong to.
-Dominant-language vocabulary size (L1 vocabulary size, henceforth) refers to the number of acquired words in the dominant language of the child (in which they were tested), the language in which they know more words.
-If the size of interference effects are more tightly associated to bilinguals’ total vocabulary size, it would support the assumption that lexical representations from both languages enter a unique cohort in bilinguals.
+We defined vocabulary size as the amount of words participants were reported to understand in their dominant language by their caregivers.
+The choice of the dominant language for calculating vocabulary sizes is due to several reasons.
+First, it allows a more fair comparison between monolinguals (who do not know any language other than their dominant language) and bilinguals (who may know words in a second language).
+Second, since participants were tested exclusively in their dominant language, their vocabulary size in the dominant language is more likely to be associated to participants' performance in the task.
+Third, previous work on word recognition in bilinguals suggests that vocabulary size in the dominant language predicts participants' performance better than total vocabulary (in which vocabulary sizes in both languages are summed together) [@marchman2010vocabulary].
 
@@
 # Study 1
+
+In this study, we conducted a conceptual replication of @mani2010infant and @mani2011phonological.
+We tested a group of English monolinguals aged 20 to 32 months, living in the Oxfordshire area (United Kingdom).
+As just said, participants were tested exclusively in English.
+As in the original studies, we manipulated the phonological relationship between the prime and the target label.
+We expected participants’ target looking to change as a function of the phonological relatedness between the prime and target English labels.
+This would reveal that participants implicitly named the prime pictures, generating a phonological label that influenced the subsequent recognition of a phonologically related word.
+In half of the trials the English prime label was phonologically related to its Spanish translation, that it they were cognates; in the other half they were not phonologically related (non-cognates)^[It was initially planned to collected data from English monolinguals and English-Spanish bilinguals in Oxford, therefore the manipulation of the cognate status of the words in English and Spanish.
+Due to time limitations imposed by the COVD-19 lockdown between 2020 and 2022, collecting data from bilinguals was not possible.
+We report the available data from English monolinguals as a control for Catalan and Spanish monolinguals and bilinguals from Barcelona in Study 2.].
+Given participants’ lack of knowledge of Spanish (or any language other than English), participants’ performance was predicted to be unaffected by the cognate status of the primes.
 
@@
 #| label: participants-numbers-oxf
-participants_oxf <- filter(participants, location == "Oxford")
+participants_oxf <- filter(participants, location=="Oxford")
 
@@
 	tab_spanner("Degree of Exposure (%)", matches("doe")) |>
-	cols_label(n = "Sessions",
+	cols_label(n = "Testing sessions",
 			   n_participants = "Participants",
@@
 We collected vocabulary data using parental responses to the Oxford Communicative Development Inventory (OCDI) [@hamilton2000infant].
+The OCDI is an adaptation of the MacArthur-Bates Communicative Development Inventory [@fenson1994variability] to British English.
+The OCDI includes a vocabulary checklist containing 418 words from 21 semantic-functional categories (e.g., action words, animals, household objects, adverbs, etc.).
+For each word, caregivers are asked to answer if they child is able to *understand*, *understand and say* or does not understand or say the word.
+We calculated participants' receptive vocabulary size scores as the number of words that caregivers marked as *understands* or *understands and says*.
 Families were sent the questionnaire immediately after each experimental session, and were given two weeks to fill it.
@@
 #| label: fig-vocabulary-oxf
-#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles.
-Vocabulary size scores from the recurrent participants are shown linked.
-For visualisation purposes, testing sessions were aggregated at three age points: 21, 25, and 30 months.
-Points and intervals indicate mean and standard deviations, respectively."
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores from the recurrent participants are shown linked. "
 #| fig-width: 6
@@
 			   by = join_by(session_id)) |>
-	inner_join(select(participants, location, lp, 
+	inner_join(select(participants, location, lp, age,
 					  child_id, session_id, age_group),
 			   by = join_by(child_id, session_id)) |> 
-	pivot_longer(c(l1_prop, total_prop),
-				 names_to = "type",
-				 values_to = "prop") |> 
-	mutate(location = factor(location, levels = c("Oxford", "Barcelona")),
+	filter(is_valid_participant) |> 
+	select(child_id, session_id, vocab_id, is_imputed, l1_count,
+		   lp, location, age_group, age) |> 
+	mutate(location = factor(location, 
+							 levels = c("Oxford", "Barcelona")),
 		   lp = gsub(" \\(English\\)", "", lp),
@@
 		   				 lp=="Bilingual" ~ "right"),
-		   type = if_else(type=="l1_prop", 
-		   			   "L1 vocabulary", "Total vocabulary"),
 		   study = if_else(location=="Oxford", 
@@
 vocab_plot_means <- vocab_plot_data |> 
-	summarise(prop_sd = sd(prop, na.rm = TRUE),
-			  prop = mean(prop, na.rm = TRUE),
+	summarise(l1_count_sd = sd(l1_count, na.rm = TRUE),
+			  l1_count = mean(l1_count, na.rm = TRUE),
 			  n = n(),
-			  .by = c(age_group, type, side, lp, type, location)) |> 
-	mutate(.lower = prop - (prop_sd/sqrt(n)),
-		   .upper = prop + (prop_sd/sqrt(n)))
+			  .by = c(age, side, lp, study)) |> 
+	mutate(.lower = l1_count - (l1_count_sd/sqrt(n)),
+		   .upper = l1_count + (l1_count_sd/sqrt(n)))
 
 vocab_plot_data |> 
-	ggplot(aes(age_group, prop, 
-			   colour = lp,
-			   fill = lp,
+	filter(study=="Study 1 (English)") |> 
+	ggplot(aes(age, l1_count, 
 			   side = side)) +
-	facet_grid(type~study) +
-	geom_line(aes(group = child_id),
-			  colour = "grey",
-			  alpha = 1 / 4, linewidth = 3 / 4) +
-	geom_dots(aes(side =),
-			  dotsize = 1.5,
-			  scale = 0.25,
-			  binwidth = 0.025,
-			  alpha = 2 / 4) +
-	geom_errorbar(data = vocab_plot_means,
-				  aes(ymin = .lower,
-				  	ymax = .upper),
-				  colour = "black",
+	geom_point(data = filter(vocab_plot_means, 
+							 study=="Study 1 (English)"), 
+			   colour = clrs[1],
 			   show.legend = FALSE,
-				  width = 0.15,
-				  linewidth = 1/2,
-				  position = position_dodge(width = 1)) +
-	geom_point(data = vocab_plot_means, 
-			   colour = "black",
-			   show.legend = FALSE,
-			   size = 1.25,
-			   position = position_dodge(width = 1)) +
-	# geom_label(data = vocab_plot_means,
-	# 		   aes(label = sprintf("%.1f%%\n[%.1f, %.1f]",
-	# 		   					prop*100, .lower*100, .upper*100),
-	# 		   	y = 0),
-	# 		   size = 2.5,
-	# 		   fill = "white",
-	# 		   vjust = 0,
-	# 		   show.legend = FALSE,
-	# 		   label.r = unit(0, "lines"),
-	# 		   label.size = 0,
-	# 		   label.padding = unit(0.1, "lines"),
-# 		   position = position_dodge(1),
-# 		   alpha = 1/4) +
-# geom_point(alpha = 1) +
+			   size = 2,
+			   shape = 1,
+			   stroke = 1) +
+	geom_smooth(method = "lm", 
+				formula = "y ~ x",
+				colour = clrs[1],
+				fill = clrs[1]) +
 	labs(x = "Age (months)",
@@
 		 fill = "Group") +
-	scale_y_continuous(labels = scales::percent,
-					   limits = c(0, 1)) +
+	scale_y_continuous(limits = c(0, 575),
+					   breaks = seq(0, 1e3, 50)) +
+	scale_x_continuous(breaks = seq(0, 50, 2)) +
 	theme(panel.grid.major.y = element_line(linetype = "dotted",
@@
 
-### Stimuli
+### Design
 
@@
 In *Related/Cognate* trials, the target shared phonological overlap with both English and Spanish prime labels ($\textbf{b}\text{oot}_{\text{ENG}}/\textbf{b}\text{ota}_{\text{SPA}}-\textbf{b}\text{ird}_{\text{ENG}}$).
-Target-distractor pairs were phonologically unrelated, and held constant for all participants.
 Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
-Each target distractor pair was shown twice for each participant, switching roles.
 Distractors were always phonologically unrelated to the prime and target labels in the same trial.
 
-We created fours lists of trials, across which the same target-distractor pair appeared with a different prime, counterbalancing the condition to which it belonged.
-For instance, in list one the *ball*-*trousers* pair was preceded by *bike* (*Related/Cognate*), by *butterfly* (*Related/Non-cognate*) in list two, and by *star* and *nose* (*Unrelated*) in lists three and four.
+@fig-task illustrates the sequence of a trial.
+Each trial started with the presentation of an attention getter for 3,000 ms.
+Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
+Fifty milliseconds after the offset of the prime image, an auditory label was played, 700 milliseconds after the onset of the word, the target and distractor pictures were presented side-by-side during 1,000 milliseconds until the end of the trial.
+After this, the attention getter of the next trial was immediately presented.
+Each experimental session lasted approximately 10 minutes.
+
+![Experimental task design with examples in Catalan.
+In each trial, the prime image is presented in silence for 1,500 ms.
+Then the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
+In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
+In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
+In unrelated trials (*n* = 16), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){#fig-task fig-align="center"}
+
+### Stimuli
+
+We created four stimuli lists, to which participants were randomly allocated.
+Recurrent participants were always allocated to the same list.
+Each list contained a different subset of prime-target-distractor triples.
+Target-distractor pairs were kept constant across lists: all infants, regardless of the list to which they were allocated, were presented with the *ball*-*trousers* target distractor pair.
+Each target-distractor pair was presented twice in their corresponding lists, alternating which word acted as target, and which as distractor.
+For instance, the *ball*-*trousers* pair was presented in all lists twice, once with *ball* as target, and another with *trousers* as target.
+Across lists, the same target-distractor pair appeared with a different prime, counterbalancing the condition to which it belonged.
+For instance, in list one the *ball*-*trousers* pair was preceded by the prime *bike* (*Related/Cognate*), by *butterfly* (*Related/Non-cognate*) in list two, and by *star* and *nose* (*Unrelated*) in lists three and four, respectively.
+
 @tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
+Trials included in each condition had equivalent length (number of phonemes) and lexical frequency.
 Lexical frequencies were extracted from the English corpora from the CHILDES database [@macwhinney2000childes; @sanchez2019childes] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@zipf1945meaning; @van2014subtlex].
+In addition to sharing phonological onset, prime and target shared higher overall phonological similarity---as measured using the Levenshtein distance---between their phonological transcriptions---in the *Related/Cognate* and the *Related/Non-cognate* conditions, compared to the *Unrelated* condition.
+In *Related/Cognate* trials, the prime label in the language of test shared a higher overall phonological similarity with its translation, compared to *Related/Non-cognate* trials.
+Since the number of cognate and non-cognate primes was balanced in *Unrelated* trials, overall phonological similarity between prime labels prime labels in the *Unrelated* condition had an intermediate overall phonological similarity.
+Audio durations were also equivalent across conditions.
 
@@
 						fmt = ~ fmt_number(., decimals = 2)) |>
-	tab_spanner("Phonemes", matches("nphon")) |>
+	tab_spanner("# Phonemes", matches("nphon")) |>
 	tab_spanner("Frequency (Zipf)", matches("freq")) |>
@@
 The auditory stimuli were natural exemplars of the selected target words, spoken by a Southern British English female speaker who was instructed to pronounce each word in a toddler-directed manner.
-We used the Audacity and Praat [@boersma2001speak] software packages to trim, denoised, and normalise their amplitude.
+We used the Audacity and Praat [@boersma2001speak] software packages to trim, denoised, and normalised their amplitude.
 The visual stimuli were realistic photographic representations of a typical exemplars of the prime, target, and distractor words.
-Image backgrounds were removed from the original pictures using the GNU Image Manipulation Program (GIMP), resized to a rectangle of a maximum of 400 pixels hight or wide, and finally placed in the centre of a 50% grey rectangle square of 500 $\times$ 500 pixels.
+Image backgrounds were removed from the original pictures using the GNU Image Manipulation Program (GIMP), resized to a rectangle of a maximum of 400 pixels height or wide, and finally placed in the centre of a 50% grey rectangle square of 500 $\times$ 500 pixels.
 The final stimuli had a resolution of 72 dpi.
@@
 
-### Procedure and apparatus
-
-Testing took place in a sound-proof room.
+### Procedure
+
+Testing took place in a sound-proof room at the BabyLab of the University of Oxford.
 Participants sat on their caregivers' lap in a dimly lit testing booth while the experimenter conducted the experiment from outside.
@@
 
-@fig-task shows a illustrates of the task design.
-Each trial started with the presentation of an attention getter for 3,000 ms.
-Then, the prime picture was presented in silence in the centre of the screen for 1,500 milliseconds.
-Fifty milliseconds after the offset of the prime image, an auditory label was played from the loudspeakers and, 700 milliseconds after the onset of the auditory label, the target and distractor pictures were presented side-by-side during 1,000 milliseconds until the end of the trial.
-After this, the attention getter of the next trial was immediately presented.
-Each experimental session took approximately 10 minutes.
-
-![Experimental task design with examples in Catalan.
-In each trial, the prime image is presented in silence for 1,500 ms.
-Then the auditory target label is presented, and finally the target and distractor pictures are presented side-by-side for 2,000 ms.
-In cognate trials (*n* = 8), Catalan *and* Spanish prime labels shared phonological onset with the target label.
-In non-cognate trials (*n* = 8), only the Catalan prime label shared phonological onset with the target label.
-In unrelated trials (*n* = 16), none of the prime labels shared phonological onset with the target label.](_assets/img/design.png){#fig-task fig-align="center"}
-
 ### Data analysis
@@
 
-```{r dataset_oxf}
+```{r data set_oxf}
 attrition_oxf <- filter(attrition, location == "Oxford")
@@
 Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
-Target looking probability was calculated as the empirical logit, using the number of samples inside the time bin in which the participant was looking at the target and distractor AOI (see @eq-elogit) [@barr2008analyzing; @agresti2012categorical].
-This was our response variable.
+Target looking probability was calculated as the empirical logit, using the number of samples inside the time bin in which the participant was looking at the target and distractor AOI (see @eq-elogit) [@barr2008analyzing; @agresti2012categorical], as follows:
 
@@
 
-After trials that matched any of the aforementioned exclusion criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
-The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
+After trials that matched any of the aforementioned exclusion criteria from the data set, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 42, which corresponds to 10% of the words in the OCDI vocabulary checklist (*n* = `r n_exc_participants_vocab`).
+The final data set included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
 Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-From the trials included in the final dataset dataset, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), were `r n_trials_condition$non_cognate_2$n` *Related/Non-cognate* trials(`r n_trials_condition$non_cognate$n` previously excluded), and `r n_trials_condition$cognate_2$n` were *Related/Cognate* trials (`r n_trials_condition$cognate$n` previously excluded).
+From the trials included in the final data set, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), were `r n_trials_condition$non_cognate_2$n` *Related/Non-cognate* trials(`r n_trials_condition$non_cognate$n` previously excluded), and `r n_trials_condition$cognate_2$n` were *Related/Cognate* trials (`r n_trials_condition$cognate$n` previously excluded).
 
@@
 attrition |>
+	mutate(study = if_else(location=="Oxford", 
+						   "Study 1: English (Oxford)",
+						   "Study 2: Catalan/Spanish (Barcelona)")) |> 	
 	summarise(n_trials_true = sum(is_valid_trial),
 			  n_trials_false = sum(!is_valid_trial),
-.by = c(lp, trial_type, location)) |>
-arrange(desc(lp)) |>
-pivot_wider(id_cols = c(location, lp),
+			  .by = c(lp, trial_type, study)) |>
+	arrange(study, desc(lp)) |>
+	pivot_wider(id_cols = c(study, lp),
 				names_from = c(trial_type),
@@
 				names_repair = janitor::make_clean_names) |>
-mutate(study = if_else(location=="Oxford", 
-"Study 1: English (Oxford)",
-"Study 2: Catalan/Spanish (Barcelona)")) |> 
 	left_join(n_lp, by = join_by(lp)) |>
@@
 First, we fit a model ($\mathcal{M}_0$) that included the main effects of *Condition* and *Age* as fixed effects in the model.
-We set two *a priori* contrasts for the *Condition* predictor [@schad2020capitalize]: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
+Given that the cognate/non-cognate distinction is meaningless for monolinguals, for the following analyses we lumped the *Related/Cognate* and *Related/Non-cognate* into a single level, *Related*.
+We set an *a priori* contrast for the *Condition* predictor [@schad2020capitalize], comparing *Unrelated* and *Related* trials (sum-coded as `-0.5` and `+0.5`.
 Before entering the model, the *Age* predictor was standardised by subtracting from each observation the mean of the predictor, and dividing the result from the standard deviation of the predictor.
@@
 ```{r coefs-oxf}
-var_labels <- c(
-"b_Intercept" = "Intercept",
+var_labels <- c("b_Intercept" = "Intercept",
 				"b_age_std" = "Age (+1 SD)",
-"b_condition1" = "Condition (U vs. RN)",
-"b_condition2" = "Condition (RN vs. RC)"
-)
-
-model_summary <- get_posterior_summary(model_fits_oxf$fit_oxf_1,
+				"b_condition1" = "Condition (U vs. R/NC)",
+				"b_condition2" = "Condition (R/NC vs. R/C)")
+
+model_summary <- get_posterior_summary(model_fits_oxf$fit_oxf_0,
 									   data_bcn,
@@
 coefs <- model_summary |>
-mutate(
-.value = sprintf("%.3f", .value),
+	mutate(.value = sprintf("%.3f", .value),
 		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
-.rope = scales::percent(.rope, accuracy = 0.01)
-) |>
+		   .rope = scales::percent(.rope, accuracy = 0.01)) |>
 	split(janitor::make_clean_names(model_summary$.variable))
@@
 The 95% HDI of the coefficient of *Age* had a positive sign, but did not exclude zero ($\beta$ = `r coefs$b_age_std$.value`, 95% HDI = `r coefs$b_age_std$.ci`), and overlapped completely with the ROPE, indicating that participants from all ages showed equivalent overall target word recognition.
-The 95% HDI of the first contrast of the *Condition* predictor---comparing *Unrelated* and *Related/Non-cognate* trials---included zero ($\beta$ = `r coefs$b_condition1$.value`, 95% HDI = `r coefs$b_condition1$.ci`), and `r coefs$b_condition1$.rope` of its posterior samples fell within the ROPE.
-The 95% HDI of the second contrast---comparing *Related/Non-cognate* and *Related/Cognate* trials---also included zero ($\beta$ = `r coefs$b_condition2$.value`, 95% HDI = `r coefs$b_condition2$.ci`), and `r coefs$b_condition2$.rope` of its posterior samples fell within the ROPE.
-The overall target preference was equivalent across both pairwise condition comparisons.
-
-```{r tbl-coefs-oxf}
-#| label: tbl-coefs-oxf
-#| fig-cap: "Margin posterior mean predictions.
-A) Posterior mean predictions of the time course of target fixation in the test phase.
-B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
-Lines and intervals indicate the mean and 95% credible interval of the posterior predictions."
-#| echo: false
-#| eval: false
-#| message: false
-#| warning: false
-#| out-width: 80%
-
-# summarise posterior draws
-intercept_label <- paste0("Intercept (at ", round(mean(data_oxf$age), 2), " months)")
-
-tbl_data <- model_summary |>
-	select(.variable_name, .value, .lower, .upper, .rope, .type) |>
-	mutate(
-		.variable_name = gsub("×", "$\\\\times$", .variable_name),
-		.hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
-		.rope = case_when(is.na(.rope) ~ "-",
-						  .rope > 0.9999 ~ "1",
-						  .rope < 0.00001 ~ "0",
-						  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope))
-		)
-	) |>
-	select(.variable_name, .value, .lower, .upper, .hdi, .rope)
-
-col_names <- c("", "$\\beta$", "95\\% HDI", "$p(\\text{ROPE})$")
-
-tbl_data |>
-	select(-c(.lower, .upper)) |>
-	kable(
-		format = "latex",
-		escape = FALSE,
-		col.names = col_names,
-		digits = 3,
-		booktabs = TRUE,
-		align = "lclr",
-		linesep = ""
-	) |>
-	kable_styling() |>
-	add_footnote("$\\beta$: median of the posterior distribution in the probability scale.
-95\\% HDI: 95\\% highest density interval of the distribution.
-$p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
-```
-
-Second, we examined the differences between the priming conditions across the time course of the trial, incorporating the smooth functions of the HGAMs to generate marginal posterior predictions for each condition across for each time point.
-@fig-epreds-oxf shows the posterior predictions of the model for each condition, and a summary of the difference between the *Unrelated* and *Related/Non-cognate* conditions, and between those for the *Related/Non-cognate* and *Related/Cognate* conditions, at each time point to test the practical relevance of these differences, were compared their 95% HDI against the [-0.1, +0.1] ROPE.
+The 95% HDI of the contrast of the *Condition* predictor---comparing *Unrelated* and *Related* trials---included zero ($\beta$ = `r coefs$b_condition1$.value`, 95% HDI = `r coefs$b_condition1$.ci`), and `r coefs$b_condition1$.rope` of its posterior samples fell within the ROPE.
+
+Second, we examined the differences between the priming conditions in the time course of the trial, incorporating the smooth functions of the HGAMs to generate marginal posterior predictions for each condition across for each time point.
+@fig-epreds-oxf shows the posterior predictions of the model for each condition, and a summary of the difference between the *Unrelated* and *Related* conditions, at each time point to test the practical relevance of these differences, were compared their 95% HDI against the [-0.1, +0.1] ROPE.
 This analysis revealed a similar pattern of results to the previously shown: predicted target looking for the three conditions overlaps across the full time course of the trial.
@@
 #| fig-cap: "A) Posterior mean predictions of the time course of target fixation in the test phase.
-Thin lines represent 100 individual posterior predictions.
-Thick lines indicate the mean of the posterior predictions.
 B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
-Thin lines represent 100 individual posterior predictions.
-Black lines indicate the mean of the posterior predictions."
+Intervals represent the 95% CrI of the posterior predictions.
+Lines indicate the mean of the posterior predictions."
 #| fig-width: 6.5
@@
 
+obs <- data_oxf |> 
+	summarise(.elog = mean(.elog),
+			  .by = c(timebin_std, condition))
+
 epreds_summary <- epreds |>
 	ungroup() |>
-	summarise(
-		.value = mean_qi(.epred)[[1]],
+	summarise(.value = mean_qi(.epred)[[1]],
 			  .lower = mean_qi(.epred)[[2]],
 			  .upper = mean_qi(.epred)[[3]],
-		.by = c(condition, timebin_std)
-	)
+			  .by = c(condition, timebin_std))
 
@@
 			   colour = "grey") +
-	# geom_line(aes(group = interaction(condition, .draw)),
-	# 		  alpha = 1/20,
-	# 		  linewidth = 3/4,
-	# 		  linetype = "solid") +
 	stat_summary(fun.data = mean_qi,
@@
 				 geom = "line",
-				 # colour = "black",
 				 linewidth = 3 / 4) +
-	stat_summary(data = data_oxf,
+	geom_point(data = obs,
 			   aes(y = .elog),
-				 fun = "mean",
-				 geom = "point",
+			   stroke = 1,
 			   size = 2) +
@@
 		 linetype = "Condition",
-		 shape = "Condition")
+		 shape = "Condition") +
+	scale_y_continuous(limits = c(-0.75, 1.25)) +
+	scale_shape_manual(values = c(1, 2)) +
+	theme(panel.grid.major.y = element_line(colour = "grey",
+											linetype = "dotted"))
 
@@
 				names_repair = janitor::make_clean_names) |>
-	mutate(diff_1 = related_non_cognate - unrelated,
-		   diff_2 = related_cognate - related_non_cognate) |>
-	pivot_longer(matches("diff"),
-				 names_to = "diff",
-				 values_to = ".epred",
-				 names_prefix = "diff_") |>
-	mutate(diff = factor(diff,
-						 levels = c(1, 2),
-						 labels = c(
-						 	"Related/Non-cognate - Unrelated",
-						 	"Related/Cognate - Related/Non-cognate"
-						 )
-	))
+	mutate(.epred = related - unrelated)
 
@@
 	ggplot(aes(timebin_std, .epred)) +
-	facet_wrap(~diff) +
-	# annotate(geom = "rect",
-	# 		 xmin = timebin_values[1],
-	# 		 xmax = timebin_values[length(timebin_values)],
-	# 		 ymin = rope_interval[1],
-	# 		 ymax = rope_interval[2],
-	# 		 fill = "red",
-	# 		 linewidth = 0,
-	# 		 alpha = 1/2,
-	# 		 linetype = "dotted") +
+	annotate(geom = "rect",
+			 alpha = 1/4,
+			 fill = "red",
+			 linewidth = 0,
+			 ymin = rope_interval[1],
+			 ymax = rope_interval[2],
+			 xmin = -Inf,
+			 xmax = Inf) +
 	stat_summary(fun.data = mean_qi,
@@
 				 linewidth = NA,
-				 alpha = 1 / 3) +
-	stat_summary(aes(group = diff),
-				 fun = mean,
+				 alpha = 3/4) +
+	stat_summary(fun = mean,
 				 geom = "line",
@@
 				 linewidth = 3 / 4) +
-	geom_hline(yintercept = rope_interval[1],
-			   colour = "red",
-			   linetype = "dotted") +
-	geom_hline(yintercept = rope_interval[2],
-			   colour = "red",
-			   linetype = "dotted") +
-	# geom_line(aes(group = interaction(diff, draw)),
-	# 		  alpha = 1/20,
-	# 		  linewidth = 3/4,
-	# 		  colour = "grey",
-	# 		  linetype = "solid") +
-
+	# geom_hline(yintercept = rope_interval[1],
+	# 		   colour = "red",
+	# 		   linetype = "dotted") +
+	# geom_hline(yintercept = rope_interval[2],
+	# 		   colour = "red",
+	# 		   linetype = "dotted") +
 	labs(x = "Time (ms)",
@@
 		 fill = "Comparison",
-		 linetype = "Comparison")
+		 linetype = "Comparison") +
+	scale_y_continuous(limits = c(-0.25, 0.5)) +
+	theme(panel.grid.major.y = element_blank())
 
@@
 	theme(legend.position = "top",
-		  legend.title = element_blank(),
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
+		  legend.title = element_blank())
 ```
@@
 
-To test our hypotheses regarding the role of age, dominant-language vocabulary size, and total vocabulary size, on the emergence of priming effects, we compared the fit of model $\mathcal{M}_0$ against the fit of other models including the two-way interaction between *Condition* and *Age* ($\mathcal{M}_1$), or the two-way interaction between *Condition* and *L1 vocabulary* ($\mathcal{M}_2$), and all main effects involved.
+To test our hypotheses regarding the role of age and vocabulary size on the emergence of priming effects, we compared the fit of model $\mathcal{M}_0$ against the fit of other models including the two-way interaction between *Condition* and *Age* ($\mathcal{M}_1$), or the two-way interaction between *Condition* and *Vocabulary* ($\mathcal{M}_2$), and all main effects involved.
+As with *Age*, the *Vocabulary* predictor was standardised before entering the model.
 We compared the models using one-out cross-validation (LOO-CV) as a benchmark of model performance, using a Pareto-smoothed importance sampling (PSIS) approximation [@vehtari2017practical].
-A better performance by models $\mathcal{M}_1$ or $\mathcal{M}_2$ over $\mathcal{M}_0$ would point to *Age* or *L1 vocabulary*, respectively, playing a substantial role in participants' word-recognition, or on the emergence of priming effects.
+A better performance by models $\mathcal{M}_1$ or $\mathcal{M}_2$ over $\mathcal{M}_0$ would point to *Age* or *Vocabulary*, respectively, playing a substantial role in participants' word-recognition, or on the emergence of priming effects.
 @tbl-loos-oxf shows a summary of the predictive performance of the models, as quantified by the expected log-predictive density (*ELPD*), and its standard error (*SE*, a measure of uncertainty around the *ELPD*).
@@
 #| label: tbl-loos-oxf
-#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 2."
-loo_compare(model_loos_oxf[2:4]) |>
+#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 1."
+loo_compare(model_loos_oxf) |>
 	as.data.frame() |>
@@
 	mutate(model = paste0("Model ",
-						  as.numeric(gsub("fit_oxf_", "", model)) - 1),
+						  as.numeric(gsub("fit_oxf_", "", model))),
 		   across(matches("diff"),
@@
 		   model = case_when(
-		   	model == "Model 1" ~ "Model 1 (Age)",
-		   	model == "Model 2" ~ "Model 2 (L1 vocabulary)",
-		   	model == "Model 3" ~ "Model 3 (Total vocabulary)",
+		   	model == "Model 0" ~ "Model 0 (Age as main effect)",
+		   	model == "Model 1" ~ "Model 1 (Age-by-condition)",
+		   	model == "Model 2" ~ "Model 2 (Vocabulary by-condition)",
 		   	.default = model
@@
 	fmt_missing(missing_text = "---") |>
-	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new dataset.
+	tab_footnote(footnote = md("*ELPD*: sum of expected log pointwise predictive density for a new data set.
 *SE \\(ELPD\\)*: standard error of the *ELPD*, which indictes the uncertainty about the predictive performance for unknown future data.
@@
 
-In this study, we attempted to replicate the original study by @mani2010infant and @mani2011phonological, using an extension of the implicit naming paradigm.
-adapted to the bilingual case.
-The main divergence between both implementations was the order in which target labels and target-distractor picture pairs were presented.
-In the original study, participants were presented with the target and distractor pictures immediately after the prime picture and the target auditory label was presented 2,000 ms after the onset of the prime and distractor pictures.
-In our adaptation of the paradigm, we presented the target auditory label immediately after the prime picture, before the target and distractor pictures were displayed in the screen.
-We then presented the target and distractor pictures 700 ms after the onset of the target label.
-The rationale behind this modification was to maximise the probability of observing any priming effects.
-By presenting the prime picture and the auditory target labels closer in time, the prime word might have a higher chance to influence the lexical selection of the target word.
-By testing a sample English monolingual infants with equivalent demographic and linguistic characteristics to the original studies, we expected to set a baseline to later compare bilingual infants in Study 2 against.
-
-Although we found strong evidence of successful word recognition across participants of all ages, results did not provide any evidence in favour of phonological priming.
-English monolingual participants from all ages showed an equivalent pattern of target looking in both related (*Related/Cognate* and *Related/Non-cognate*) and *Unrelated* trials.
+We found strong evidence of successful word recognition across participants of all ages, but we did not observe any evidence of phonological priming.
+English monolingual participants from all ages showed an equivalent pattern of target looking in both Related (Related/Cognate and Related/Non-cognate) and Unrelated trials.
+In conclusion, we failed to replicate the original studies by @mani2010infant and @mani2011phonological.
 The absence of a phonological priming effect suggest that either English monolinguals did not generate implicit labels for the prime pictures presented in silence, or that, if generated, such labels did not interact with the subsequent recognition of the target word.
-Both candidate explanations conflict with both Mani and Plunkett's studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects [@duta2012erp; @styles2015infant].
+Both candidate explanations conflict with both Mani and Plunkett’s studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects (@duta2012erp; @styles2015infant).
 
@@
 These results diverge from previous studies reporting an increment in word recognition speed [@fernald1998rapid; @marchman2008speed], and stronger phonological priming effects in children with larger vocabulary sizes [@mani2011phonological; @chow2017spoken].
-Overall, the outcomes of the Study 1 point to the absence of phonological priming effects in English monolingual toddlers, in contrast with previous studies.
-We discuss further candidate explanations for these results, and their implications for the lexical development literature in the General discussion.
+Overall, this results suggest that our modification of the implicit naming task resulted in the loss of the originally reported effect.
 
@@
 
-Due to time constraints induced by the COVID-19 lockdown between 2020 an 2021, data collection in Study 1 and Study 2 was conducted simultaneously.
-In this study, we present data for monolinguals and bilinguals tested in Barcelona.
+The original planning of the present investigation was to run Study 1 first and once the procedure had been validated to start Study 2.
+However, right at the beginning of data collection, the outbreak of COVID-19 pandemic took place.
+At this point it was decided to run both experiments in parallel.
+Data collection at the Barcelona site proceeded at a faster rate than at Oxford.
+It was not until data collection was well advanced in Barcelona that the results of study 1 were available.
+This is the reason why Study 2 was run with the same procedure as Experiment 1.
 
@@
 We gathered a total of `r n_sessions_total$n` testing sessions.
-Participants were divided into monolinguals and bilinguals based on their relative degree of exposure to Catalan and Spanish, estimated using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
+Participants were divided into monolinguals and bilinguals based on their relative degree of exposure to Catalan and Spanish, estimated using an adaptation of the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
 We categorised participants as monolingual if exposed to more than 80% or more of the time to their dominant language, and as bilingual otherwise.
@@
 n_pool <- nrow(bvq_data$vocabulary)
-```
-
-We collected vocabulary data using parental responses to the Barcelona Vocabulary Inventory [BVQ, @garcia-castro2023bvq], an online vocabulary checklist developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers, and inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability].
+
+n_items <- bvq_data$pool |> 
+	unnest_longer(version) |> 
+	count(language, version) |> 
+	summarise(min = min(n),
+			  max = max(n),
+			  .by = language)
+
+n_categories <- n_distinct(bvq_data$pool$semantic_category)
+```
+
+We collected vocabulary data using parental responses to the Barcelona Vocabulary Questionnaire [BVQ, @garcia-castro2023bvq], an online vocabulary checklist developed to assess the vocabulary size of Catalan-Spanish bilingual toddlers, and inspired in several adaptations of the the Communicative Developmental Inventory [CDI, @fenson1994variability].
+This questionnaire has four versions, each including a different but overlapping subset of words, from a total pool of `r n_pool` words from `r n_categories` functional-semantic categories.
+Each version included a Catalan and a Spanish vocabulary checklist.
+Catalan checklists contained between `r n_items$min[1]` and `r n_items$min[2]` words, and Spanish checklists contained between `r n_items$min[2]` and `r n_items$min[2]` words (see the Methods section of Chapter 1 for a detailed description of the questionnaire..
+Participants were randomly allocated to one of the four versions.
+Recurrent participants were always allocated to the same version.
 Families received a link to the BVQ immediately after each experimental session, and were given two weeks to fill it.
-We calculated two measures of receptive vocabulary size for each participant: *L1 vocabulary size* (proportion of words reported as acquired in the checklist of the dominant language), and *total vocabulary size* (proportion of the words in both checklists reported as acquired).
-`r english::Words(n_imputed)` (`r prop_imputed`) families failed to provide a complete response to the BVQ within the two-week time limit.
+
+Following the same procedure as in Study 1, we calculated participants' vocabulary size as the number of words that caregivers reported their child to *understand* or *understand and say* in the dominant language of the child (i.e., the language of test).
+`r english::Words(n_imputed)` (`r prop_imputed`) families failed to provide a complete response to the vocabulary checklist within the two-week time limit.
 We imputed missing vocabulary size scores using single imputation, taking the vocabulary size scores of a pool of `r n_pool` additional participants for which a successful response for the questionnaire had been gathered.
@@
 
+```{r fig-vocabulary}
+#| label: fig-vocabulary-bcn
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Points and intervals indicate mean and standard deviations, respectively."
+#| fig-width: 6
+#| fig-height: 4
+vocab_plot_data |> 
+	filter(study=="Study 2 (Catalan/Spanish)") |> 
+	ggplot(aes(age, l1_count, 
+			   colour = lp,
+			   fill = lp)) +
+	facet_wrap(~lp) +
+	geom_point(size = 2,
+			   shape = 1,
+			   stroke = 1) +
+	geom_smooth(method = "lm",
+				formula = "y ~ x") +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size",
+		 colour = "Group",
+		 fill = "Group") +
+	scale_color_manual(values = clrs[c(1, 5)]) +
+	scale_fill_manual(values = clrs[c(1, 5)]) +
+	theme(panel.grid.major.y = element_line(linetype = "dotted",
+											colour = "grey"),
+		  legend.position = "top",
+		  axis.title.x = element_blank(),
+		  legend.title = element_blank())
+```
+
 ### Stimuli
@@
 
-For Study 2, we created six stimuli lists: three in Catalan, and three in Spanish.
-Lists were created following the same constraints as in Study 1,  but now considering the cross-linguistic phonological relationship between Catalan and Spanish, instead of English and Spanish.
-Extracting lexical frequencies from the Catalan and Spanish corpora in the CHILDES database was not possible, given the low number of participants and tokens included in them.
-Instead, we mapped the English lexical frequencies onto their Catalan and Spanish translation equivalents [see @fourtassi2020growth and @garcia2023cognate for similar approaches].
-The auditory stimuli were natural exemplars of the selected target words, spoken by a Southern British English female speaker who was instructed to pronounce each word in a toddler-directed manner.
-New visual stimuli were created to accommodate the words included in the new stimuli lists, and possible cultural differences in the typicality of the exemplars shown in the pictures.
+We created six stimuli lists: three in Catalan, and three in Spanish.
+Lists were created following the same constraints as in Study 1,  but now considering the cross-linguistic phonological relationship between Catalan and Spanish.
+Extracting lexical frequencies from the Catalan and Spanish corpora in the CHILDES database was not possible, given the low number of participants and tokens included.
+We mapped the English lexical frequencies onto their Catalan and Spanish translation equivalents [see @fourtassi2020growth and @garcia2023cognate for similar approaches].
+The auditory stimuli were natural exemplars of the selected target words, spoken by a proficient female bilingual speaker of Catalan (Central variety) and Castilian Spanish, who was instructed to pronounce each word in a toddler-directed manner.
+New visual stimuli were created to accommodate the words included in the new stimuli lists, and possible cultural differences in the typicality of the exemplars shown in the pictures (see Appendix A for a detailed description of the stimuli).
 
@@
 
-```{r dataset}
-attrition_bcn <- filter(attrition, location == "Barcelona")
+```{r data set}
+attrition_bcn <- filter(attrition, location=="Barcelona")
 n_trials <- nrow(attrition_bcn)
@@
 
-After excluding trials that matched any of the aforementioned criteria from the dataset, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 10% (*n* = `r n_exc_participants_vocab`).
-The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
+After excluding trials that matched any of the aforementioned criteria from the data set, we excluded participants who did not provide at least two valid trials in each experimental condition (*n* = `r n_exc_participants`), and participants with a dominant-language vocabulary size lower than 10% (which depending on the version of the vocabulary questionnaire they were allocated to, varied from `r floor(min(n_items$min)*0.1)` and `r floor(max(n_items$max)*0.1)`)  (*n* = `r n_exc_participants_vocab`).
+The final data set included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
 Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
@@
 
-We modelled the data following a similar approach as in Study 1, with the main difference that participants' language profile (*Group*) was now included as a predictor in the model.
+We modeled the data following a similar approach as in Study 1, with the main difference that participants' language profile (*Group*) was now included as a predictor in the model, in interaction with the *Condition* predictor.
+We set two *a priori* contrasts for the *Condition* predictor [@schad2020capitalize]: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
 In Study 2, the base model $\mathcal{M}_0$ included the the main effects of *Age*, *Condition*, and *Group*, and the two-way interaction between the *Condition* and  *Group* predictors.
@@
 
-model_summary <- get_posterior_summary(model_fits_bcn$fit_3,
+model_summary <- get_posterior_summary(model_fits_bcn$fit_0,
 									   data_bcn,
@@
 coefs <- model_summary |>
-	mutate(
-		.value = sprintf("%.3f", .value),
+	mutate(.value = sprintf("%.3f", .value),
 		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
-		.rope = scales::percent(.rope, accuracy = 0.01)
-	) |>
+		   .rope = scales::percent(.rope, accuracy = 0.01)) |>
 	split(janitor::make_clean_names(model_summary$.variable))
@@
 
-```{r tbl-coefs}
-#| label: tbl-coefs
-#| tbl-cap: "Posterior distribution of regression coefficients.
-Median: median of the posterior distribution in logit scale.
-95\\% HDI: 95\\% highest density interval of the distribution.
-*p*(ROPE): overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero."
-#| echo: false
-#| message: false
-#| eval: false
-#| warning: false
-#| out-width: 80%
-# summarise posterior draws
-intercept_label <- paste0("Intercept (at ", round(mean(data_bcn$age), 2), " months)")
-
-tbl_data <- model_summary |>
-	select(.variable_name, .value, .lower, .upper, .rope, .type) |>
-	mutate(
-		.variable_name = gsub("×", "$\\\\times$", .variable_name),
-		.hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
-		.rope = case_when(is.na(.rope) ~ "-",
-						  .rope > 0.9999 ~ "1",
-						  .rope < 0.00001 ~ "0",
-						  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope))
-		)
-	) |>
-	select(.variable_name, .value, .lower, .upper, .hdi, .rope)
-
-col_names <- c("", "$\\beta$", "95\\% HDI", "$p(\\text{ROPE})$")
-
-tbl_data |>
-	select(-c(.lower, .upper)) |>
-	kable(
-		format = "latex",
-		escape = FALSE,
-		col.names = col_names,
-		digits = 3,
-		booktabs = TRUE,
-		align = "lclr",
-		linesep = ""
-	) |>
-	kable_styling() |>
-	add_footnote("$\\beta$: median of the posterior distribution in the logit scale.
-95\\% HDI: 95\\% highest density interval of the distribution.
-$p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
-```
-
 ```{r timecourse}
@@
 
-timebin_values <- make_std(
-	seq(0, 16, length.out = 100),
+timebin_values <- make_std(seq(0, 16, length.out = 100),
 						   mean(data_bcn$timebin),
-	sd(data_bcn$timebin)
-)
-
-age_values <- make_std(
-	c(20, 32),
+						   sd(data_bcn$timebin))
+
+age_values <- make_std(c(20, 32),
 					   mean(data_bcn$age),
-	sd(data_bcn$age)
-)
+					   sd(data_bcn$age))
 
 nd <- expand_grid(distinct(data_bcn, condition, lp),
-				  age_std = 0, timebin_std = timebin_values
-)
+				  age_std = 0, timebin_std = timebin_values)
 
 epreds <- add_epred_draws(nd,
-						  model_fits_bcn$fit_3,
+						  model_fits_bcn$fit_0,
 						  ndraws = NULL,
-						  re_formula = NA
-)
+						  re_formula = NA)
 ```
@@
 #| label: fig-epreds
-#| fig-cap: "Marginal posterior mean predictions.
-A) Posterior mean predictions of the time course of target fixation in the test phase.
+#| fig-cap: "A) Posterior mean predictions of the time course of target fixation in the test phase.
 B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
-Lines and intervals indicate the mean and 95% credible interval of the posterior predictions.
-Red lines indicate the region of practial equivalence (ROPE)."
+Intervals represent the 95% CrI of the posterior predictions.
+Lines indicate the mean of the posterior predictions."
 #| fig-width: 8
@@
 	ungroup() |>
-	summarise(
-		.value = mean_qi(.epred)[[1]],
+	summarise(.value = mean_qi(.epred)[[1]],
 			  .lower = mean_qi(.epred)[[2]],
 			  .upper = mean_qi(.epred)[[3]],
-		.by = c(lp, condition, timebin_std)
-	)
-
+			  .by = c(lp, condition, timebin_std))
+
+obs <- data_bcn |> 
+	summarise(.elog = mean(.elog),
+			  .by = c(timebin_std, condition)) 
 plot_epreds <- epreds |>
@@
 			   linetype = condition,
-			   shape = condition
-	)) +
+			   shape = condition)) +
 	facet_wrap(~lp) +
-	# geom_line(aes(group = interaction(lp, condition, .draw)),
-	# 		  alpha = 1/20,
-	# 		  linewidth = 3/4,
-	# 		  linetype = "solid") +
-	stat_summary(
-		fun.data = mean_qi,
+	stat_summary(fun.data = mean_qi,
 				 geom = "ribbon",
 				 alpha = 1 / 4,
-		linewidth = NA
-	) +
-	stat_summary(
-		fun = "mean",
+				 linewidth = NA) +
+	stat_summary(fun = "mean",
 				 geom = "line",
 				 # colour = "black",
-		linewidth = 3 / 4
-	) +
-	geom_hline(
-		yintercept = 0,
-		colour = "grey"
-	) +
-	stat_summary(
-		data = data_bcn,
+				 linewidth = 3 / 4) +
+	geom_hline(yintercept = 0,
+			   colour = "grey") +
+	geom_point(data = obs,
 			   aes(y = .elog),
-		fun = "mean",
-		geom = "point",
-		size = 2
-	) +
-	labs(
-		x = "Time (ms)",
+			   size = 2,
+			   stroke = 1) +
+	labs(x = "Time (ms)",
 		 y = "Logit (Target looking)",
@@
 		 linetype = "Condition",
-		shape = "Condition"
-	)
+		 shape = "Condition") +
+	scale_y_continuous(limits = c(-0.75, 1.25)) +
+	theme(panel.grid.major.y = element_line(colour = "grey",
+											linetype = "dotted"))
 
 epreds_diff <- epreds |>
-	pivot_wider(
-		id_cols = c(lp, timebin_std, .draw),
+	pivot_wider(id_cols = c(lp, timebin_std, .draw),
 				names_from = "condition",
 				values_from = ".epred",
-		names_repair = janitor::make_clean_names
-	) |>
-	mutate(
-		diff_1 = related_non_cognate - unrelated,
-		diff_2 = related_cognate - related_non_cognate
-	) |>
+				names_repair = janitor::make_clean_names) |>
+	mutate(diff_1 = related_non_cognate - unrelated,
+		   diff_2 = related_cognate - related_non_cognate) |>
 	pivot_longer(matches("diff"),
@@
 				 values_to = ".epred",
-				 names_prefix = "diff_"
-	) |>
+				 names_prefix = "diff_") |>
 	mutate(diff = factor(diff,
 						 levels = c(1, 2),
-						 labels = c(
-						 	"Related/Non-cognate - Unrelated",
-						 	"Related/Cognate - Related/Non-cognate"
-						 )
-	))
+						 labels = c("Related/Non-cognate - Unrelated",
+						 		   "Related/Cognate - Related/Non-cognate")))
 
@@
 	facet_wrap(diff ~ lp,
-			   labeller = labeller(
-			   	diff = label_value,
-			   	lp = function(x) {
-			   		return("")
-			   	},
-			   	.multi_line = FALSE
-			   )
-	) +
-	# annotate(geom = "rect",
-	# 		 xmin = timebin_values[1],
-	# 		 xmax = timebin_values[length(timebin_values)],
-	# 		 ymin = rope_interval[1],
-	# 		 ymax = rope_interval[2],
-	# 		 fill = "red",
-	# 		 linewidth = 0,
-	# 		 alpha = 1/2,
-	# 		 linetype = "dotted") +
-	stat_summary(
-		fun.data = mean_qi,
+			   labeller = labeller(diff = label_value,
+			   					lp = \(x) return(""),
+			   					.multi_line = FALSE)) +
+	annotate(geom = "rect",
+			 xmin = -Inf,
+			 xmax = Inf,
+			 ymin = rope_interval[1],
+			 ymax = rope_interval[2],
+			 fill = "red",
+			 linewidth = 0,
+			 alpha = 1/3,
+			 linetype = "dotted") +
+	stat_summary(fun.data = mean_qi,
 				 geom = "ribbon",
@@
 				 linewidth = NA,
-		alpha = 1 / 3
-	) +
-	stat_summary(aes(group = diff),
-				 fun = mean,
+				 alpha = 3/4) +
+	stat_summary(fun = mean,
 				 geom = "line",
 				 colour = "black",
-				 linewidth = 3 / 4
-	) +
-	geom_hline(
-		yintercept = rope_interval[1],
-		colour = "red",
-		linetype = "dotted"
-	) +
-	geom_hline(
-		yintercept = rope_interval[2],
-		colour = "red",
-		linetype = "dotted"
-	) +
-	# geom_line(aes(group = interaction(diff, draw)),
-	# 		  alpha = 1/20,
-	# 		  linewidth = 3/4,
-	# 		  colour = "grey",
-	# 		  linetype = "solid") +
-
-	labs(
-		x = "Time (ms)",
+				 linewidth = 3 / 4) +
+	# geom_hline(yintercept = rope_interval[1],
+	# 		   colour = "red",
+	# 		   linetype = "dotted") +
+	# geom_hline(yintercept = rope_interval[2],
+	# 		   colour = "red",
+	# 		   linetype = "dotted") +
+	labs(x = "Time (ms)",
 		 y = "Logit P(Target looking)",
@@
 		 fill = "Comparison",
-		linetype = "Comparison"
-	)
+		 linetype = "Comparison") +
+	scale_y_continuous(limits = c(-0.25, 0.5))
 
@@
 	# scale_y_continuous(limits = c(0.25, 0.75)) +
-	scale_x_continuous(
-		breaks = make_std(
-			seq(0, 17, 3),
+	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
 										 mean(data_bcn$timebin),
-			sd(data_bcn$timebin)
-		),
+										 sd(data_bcn$timebin)),
 					   labels = \(x) format(seq(3e2, 2e3, 3e2),
-							 big.mark = ","
-		)
-	) &
-	theme(
-		legend.position = "top",
-		legend.title = element_blank(),
-		panel.grid.major.y = element_line(
-			colour = "grey",
-			linetype = "dotted"
-		)
-	)
+					   					 big.mark = ",")) &
+	theme(legend.position = "top",
+		  legend.title = element_blank())
 ```
@@
 
-loo_compare(model_loos_bcn[4:7]) |>
+loo_compare(model_loos_bcn) |>
 	as.data.frame() |>
 	rownames_to_column("model") |>
-	mutate(
-		model = paste0("Model ", as.numeric(gsub("fit_", "", model)) - 3),
-		across(
-			matches("diff"),
+	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model)) - 3),
+		   across(matches("diff"),
 		   	   \(x) {
@@
 		   	   	return(x)
-			}
-		),
-		model = case_when(model == "Model 1" ~ "Model 1 (Age)",
-						  model == "Model 2" ~ "Model 2 (L1 vocabulary)",
-						  model == "Model 3" ~ "Model 3 (Total vocabulary)",
-						  .default = model
-		)
-	) |>
+		   	   }),
+		   model = case_when(model == "Model 1" ~ "Model 0 (Age as main effect)",
+		   				  model == "Model 2" ~ "Model 1 (Age-by-condition)",
+		   				  model == "Model 3" ~ "Model 3 (Vocabulary-by-condition)",
+		   				  .default = model)) |>
 	select(model, matches("elpd|diff")) |>
@@
 ## Discussion
-
-In Study 2, tested a sample of 20-to-32-months-old bilinguals in our adaptation of the implicit naming paradigm to investigate the potential role of within- and cross-language phonological priming.
-We also tested a same aged monolingual control.
-As in Study 1, we within-language priming effects in both *Related/Non-cognate* and *Related/Cognate* trials, as the result of the phonological  similarity between the prime and target labels in the language of test.
-This would suggest that participants lexicalised the prime pictures (presented in silence), and that the resulting word interacted with the auditory recognition of the subsequently presented target label.
-We also predicted bilingual participants to lexicalise the prime picture in both languages in parallel, in line with the language non-selective hypothesis of lexical access.
-If this was the case, participants should show differences in target looking between *Related/Non-cognate* trials---in which the target word shared phonological onset with only the prime label in the test language---and *Related/Cognate* trials---in which the target label also shared phonological overlap with the prime label in the other language.
 

### 2023-11-26 _targets.R

@@ -174,11 +174,19 @@ list(
 			   		 time_subset = c(0.30, 2.00))),
 	
 	tar_target(data_oxf,
-			   get_data(gaze = filter(gaze, location=="Oxford"),
+			   {
+			   	data_oxf <- get_data(gaze = filter(gaze, location=="Oxford"),
 			   		 participants, stimuli, vocabulary,
 			   		 attrition_trials = attrition_trials,
 			   		 attrition_participants = attrition_participants,
-			   		 time_subset = c(0.30, 2.00))),
+			   		 time_subset = c(0.30, 2.00)) |> 
+			   		mutate(condition = as.factor(if_else(condition != "Unrelated",
+			   								   "Related", condition)))
+			   	
+			   	contrasts(data_oxf$condition) <- c(0.5, -0.5)
+			   	
+			   	return(data_oxf)
+			   	}),
 	
 	# Bayesian GAMMs -----------------------------------------------------------
 	
@@ -192,39 +200,20 @@ list(
 	
 	tar_target(model_formulas_bcn,
 			   lst(
-			   	fit_0 = .elog ~ age_std + 
-			   		s(timebin_std, bs = "bs", k = 8) +
-			   		(1 + age_std | child_id) + 
-			   		(1 | child_id:session_id),
-			   	fit_1 = .elog ~ lp + age_std + 
-			   		s(timebin_std, bs = "bs", k = 8) +
-			   		s(timebin_std, by = lp, bs = "bs", k = 8) +
-			   		(1 + age_std | child_id) + 
-			   		(1 | child_id:session_id),
-			   	fit_2 = .elog ~ lp + condition + age_std +
+			   	fit_0 = .elog ~ condition * lp + age_std +
 			   		s(timebin_std, bs = "bs", k = 8) +
 			   		s(timebin_std, by = interaction(condition, lp), bs = "bs", k = 8) +
 			   		(1 + condition + age_std | child_id) +
 			   		(1 + condition | child_id:session_id),
-			   	fit_3 = .elog ~ condition * lp + age_std +
+			   	fit_1 = .elog ~ condition * lp * age_std +
 			   		s(timebin_std, bs = "bs", k = 8) +
 			   		s(timebin_std, by = interaction(condition, lp), bs = "bs", k = 8) +
 			   		(1 + condition + age_std | child_id) +
 			   		(1 + condition | child_id:session_id),
[…]

### 2023-11-27 manuscript/_appendix/_stimuli.qmd
Fix figure

@@
 The experimenter assigned the participant to the Catalan or Spanish stimuli list involving the closest variant to that of caregivers'.
+
+```{r tbl-stimuli}
+#| label: tbl-stimuli
+#| tbl-cap: "Summary of stimuli properties by trial type."
+stimuli |>
+	unnest_wider(c(freq, nphon)) |>
+	summarise(across(c(matches("n_phon|freq_|lv_|nphon"), duration),
+					 list(	mean = \(x) mean(x, na.rm = TRUE),
+					 	  sd = \(x) sd(x, na.rm = TRUE))),
+			  .by = c(trial_type, test_language)) |>
+	select(-matches("distractor")) |>
+	mutate(test_language = if_else(test_language=="English",
+								   paste0("Study 1: ", test_language),
+								   paste0("Study 2: ", test_language))) |>
+	arrange(test_language) |> 
+	gt(rowname_col = "trial_type",
+	   groupname_col = "test_language") |>
+	# summary_rows(groups = c("Unrelated", "Non-cognate", "Cognate"),
+	# 			 columns = is.numeric,
+	# 			 fns = list(Total ~ mean(.)),
+	# 			 fmt = ~ fmt_number(., decimals = 2)) |>
+	grand_summary_rows(	columns = is.numeric,
+						fns = list(Total ~ mean(.)),
+						fmt = ~ fmt_number(., decimals = 2)) |>
+	tab_spanner("Phonemes", matches("nphon")) |>
+	tab_spanner("Frequency (Zipf)", matches("freq")) |>
+	tab_spanner("Phon. similarity [0-1]", matches("lv")) |>
+	fmt_number(is.numeric, decimals = 1) |>
+	cols_merge(c(freq_prime_mean, freq_prime_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(freq_target_mean, freq_target_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(nphon_prime_mean, nphon_prime_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(nphon_target_mean, nphon_target_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(lv_pp_mean, lv_pp_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(lv_pt_mean, lv_pt_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(duration_mean, duration_sd),
+			   pattern = "{1} ({2})") |>
+	cols_label(trial_type = "",
+			   freq_prime_mean = "Prime",
+			   freq_target_mean = "Target",
+			   lv_pp_mean = "Prime-Prime",
+			   lv_pt_mean = "Prime-Target",
+			   duration_mean = "Duration (s)",
+			   nphon_prime_mean = "Prime",
+			   nphon_target_mean = "Target") |>
+	tab_style(cell_text(style = "italic"),
+			  list(cells_column_labels(),
+			  	 cells_column_spanners(),
+			  	 cells_grand_summary()))
+```

### 2023-11-27 manuscript/manuscript.qmd
Fix figure

--- 2023-11-22 manuscript/manuscript.qmd
@@
 # load objects
-targets::tar_config_set(
-	store = here::here("_targets"),
-	script = here::here("_targets.R")
-)
+targets::tar_config_set(store = here::here("_targets"),
+						script = here::here("_targets.R"))
 
@@
 					data_bcn,
-		data_oxf
-	)
-)
-
-targets::tar_load(
-	c(
-		model_fits_bcn,
+					data_oxf))
+
+targets::tar_load(c(model_fits_bcn,
 					model_loos_bcn,
 					model_fits_oxf,
-		model_loos_oxf
-	)
-)
+					model_loos_oxf))
 
 # prepare data
-attrition <- lst(
-	participants,
+attrition <- lst(participants,
 				 attrition_participants,
-	attrition_trials
-) |>
+				 attrition_trials) |>
 	reduce(inner_join, by = join_by(session_id)) |>
@@
 
-library(knitr)
-library(kableExtra)
 library(ggplot2)
 library(gt)
-library(gtExtras)
 library(patchwork)
 library(english)
-library(gtExtras)
 
@@
 
-clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
-
-options(
-	ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
-	ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
-	ggplot2.discrete.fill = clrs[c(1, 4, 5)],
-	ggplot2.discrete.colour = clrs[c(1, 4, 5)],
+clrs <- c("#c8102e", "#1e90ff", "grey50")
+
+options(ggplot2.ordinal.fill = clrs,
+		ggplot2.ordinal.colour = clrs,
+		ggplot2.discrete.fill = clrs,
+		ggplot2.discrete.colour = clrs,
 		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
-	ggplot2.continuous.colour = ggplot2::scale_color_gradient
-)
+		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
 
@@
 	tab_spanner("Degree of Exposure (%)", matches("doe")) |>
-	cols_label(n = "Sessions",
-			   n_participants = "Participants",
-			   age_mean = "M (SD)",
-			   age_min = "Range",
-			   doe_catalan_mean = "M (SD)",
-			   doe_english_mean = "M (SD)",
-			   doe_spanish_mean = "M (SD)") |>
+	cols_label(n = md("*Sessions*"),
+			   n_participants = md("*Participants*"),
+			   age_mean = md("*M (SD)*"),
+			   age_min = md("*Range*"),
+			   doe_catalan_mean = md("*M (SD)*"),
+			   doe_english_mean = md("*M (SD)*"),
+			   doe_spanish_mean = md("*M (SD)*"),) |>
 	tab_style(cell_text(style = "italic"),
@@
 Points and intervals indicate mean and standard deviations, respectively."
-#| fig-width: 6
-#| fig-height: 4
+#| fig-width: 7
+#| fig-height: 5.5
 vocab_plot_data <- vocabulary |>
@@
 		   			   "L1 vocabulary", "Total vocabulary"),
-		   study = if_else(location=="Oxford", 
-		   				"Study 1 (English)", "Study 2 (Catalan/Spanish)"))
+		   study = if_else(location=="Oxford", "Study 1", "Study 2"),
+		   age_group = gsub(" months", "", age_group))
 
@@
 			  n = n(),
-			  .by = c(age_group, type, side, lp, type, location)) |> 
+			  .by = c(age_group, type, side, lp, type, study)) |> 
 	mutate(.lower = prop - (prop_sd/sqrt(n)),
-		   .upper = prop + (prop_sd/sqrt(n)))
+		   .upper = prop + (prop_sd/sqrt(n)),
+		   age_group = gsub(" months", "", age_group))
 
@@
 	geom_line(aes(group = child_id),
-			  colour = "grey",
-			  alpha = 1 / 4, linewidth = 3 / 4) +
-	geom_dots(aes(side =),
-			  dotsize = 1.5,
+			  # colour = "grey",
+			  alpha = 1 / 4,
+			  linewidth = 1 / 2) +
+	geom_dots(dotsize = 1.5,
 			  scale = 0.25,
@@
 			   position = position_dodge(width = 1)) +
-	# geom_label(data = vocab_plot_means,
-	# 		   aes(label = sprintf("%.1f%%\n[%.1f, %.1f]",
-	# 		   					prop*100, .lower*100, .upper*100),
-	# 		   	y = 0),
-	# 		   size = 2.5,
-	# 		   fill = "white",
-	# 		   vjust = 0,
-	# 		   show.legend = FALSE,
-	# 		   label.r = unit(0, "lines"),
-	# 		   label.size = 0,
-	# 		   label.padding = unit(0.1, "lines"),
-# 		   position = position_dodge(1),
-# 		   alpha = 1/4) +
-# geom_point(alpha = 1) +
 	labs(x = "Age (months)",
@@
 		  legend.position = "top",
-		  axis.title.x = element_blank(),
 		  legend.title = element_blank())
@@
 We created fours lists of trials, across which the same target-distractor pair appeared with a different prime, counterbalancing the condition to which it belonged.
-For instance, in list one the *ball*-*trousers* pair was preceded by *bike* (*Related/Cognate*), by *butterfly* (*Related/Non-cognate*) in list two, and by *star* and *nose* (*Unrelated*) in lists three and four.
-@tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
+For instance, in list one the *ball*-*trousers* pair was preceded by *bike* (*Related/Cognate*), by *butterfly* (*Related/Non-cognate*) in list two, and by *star* and *nose* (*Unrelated*) in lists three and four (see Appendix A for a detailed description of the stimuli).
 Lexical frequencies were extracted from the English corpora from the CHILDES database [@macwhinney2000childes; @sanchez2019childes] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@zipf1945meaning; @van2014subtlex].
-
-```{r tbl-stimuli}
-#| label: tbl-stimuli
-#| tbl-cap: "Summary of stimuli properties by trial type."
-stimuli |>
-	unnest_wider(c(freq, nphon)) |>
-	summarise(across(c(matches("n_phon|freq_|lv_|nphon"), duration),
-					 list(	mean = \(x) mean(x, na.rm = TRUE),
-					 	  sd = \(x) sd(x, na.rm = TRUE))),
-			  .by = c(trial_type, test_language)) |>
-	select(-matches("distractor")) |>
-	mutate(test_language = if_else(test_language=="English",
-								   paste0("Study 1: ", test_language),
-								   paste0("Study 2: ", test_language))) |>
-	arrange(test_language) |> 
-	gt(rowname_col = "trial_type",
-	   groupname_col = "test_language") |>
-	# summary_rows(groups = c("Unrelated", "Non-cognate", "Cognate"),
-	# 			 columns = is.numeric,
-	# 			 fns = list(Total ~ mean(.)),
-	# 			 fmt = ~ fmt_number(., decimals = 2)) |>
-	grand_summary_rows(	columns = is.numeric,
-						fns = list(Total ~ mean(.)),
-						fmt = ~ fmt_number(., decimals = 2)) |>
-	tab_spanner("Phonemes", matches("nphon")) |>
-	tab_spanner("Frequency (Zipf)", matches("freq")) |>
-	tab_spanner("Phon. similarity [0-1]", matches("lv")) |>
-	fmt_number(is.numeric, decimals = 1) |>
-	cols_merge(c(freq_prime_mean, freq_prime_sd),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(freq_target_mean, freq_target_sd),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(nphon_prime_mean, nphon_prime_sd),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(nphon_target_mean, nphon_target_sd),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(lv_pp_mean, lv_pp_sd),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(lv_pt_mean, lv_pt_sd),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(duration_mean, duration_sd),
-			   pattern = "{1} ({2})") |>
-	cols_label(trial_type = "",
-			   freq_prime_mean = "Prime",
-			   freq_target_mean = "Target",
-			   lv_pp_mean = "Prime-Prime",
-			   lv_pt_mean = "Prime-Target",
-			   duration_mean = "Duration (s)",
-			   nphon_prime_mean = "Prime",
-			   nphon_target_mean = "Target") |>
-	tab_style(cell_text(style = "italic"),
-			  list(cells_column_labels(),
-			  	 cells_column_spanners(),
-			  	 cells_grand_summary()))
-```
 
@@
 The final dataset included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, and `r n_longitudinal[2, 2]` provided data from two experimental sessions.
 From the trials included in the final dataset dataset, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), were `r n_trials_condition$non_cognate_2$n` *Related/Non-cognate* trials(`r n_trials_condition$non_cognate$n` previously excluded), and `r n_trials_condition$cognate_2$n` were *Related/Cognate* trials (`r n_trials_condition$cognate$n` previously excluded).
-
-```{r tbl-attrition}
-#| label: tbl-attrition
-#| tbl-cap: "Participant-level and trial-level sample size after applying inclusion criteria. The number of excluded participants and trials is indicated between parentheses."
-expanded <- expand(attrition, lp, trial_type, is_valid_trial)
-
-n_lp <- attrition |>
-distinct(is_valid_participant, lp, session_id) |>
-count(is_valid_participant, lp) |>
-pivot_wider(names_from = is_valid_participant,
-values_from = n,
-names_repair = janitor::make_clean_names) |>
-mutate(n_participants_true = true,
-n_participants_false = false) |>
-select(lp, true, false)
-
-attrition |>
-summarise(n_trials_true = sum(is_valid_trial),
-n_trials_false = sum(!is_valid_trial),
-.by = c(lp, trial_type, location)) |>
-arrange(desc(lp)) |>
-pivot_wider(id_cols = c(location, lp),
-names_from = c(trial_type),
-values_from = matches("trials"),
-names_repair = janitor::make_clean_names) |>
-mutate(study = if_else(location=="Oxford", 
-"Study 1: English (Oxford)",
-"Study 2: Catalan/Spanish (Barcelona)")) |> 
-left_join(n_lp, by = join_by(lp)) |>
-select(study, lp, true, false, matches("n_trials")) |>
-gt(rowname_col = "lp",
-groupname_col = "study") |>
-tab_spanner("Participants", matches("participant")) |>
-tab_spanner("Trials", matches("trial")) |>
-fmt_integer(everything()) |>
-cols_merge(c(true, false), pattern = "{1} ({2})") |>
-cols_merge(c(n_trials_true_cognate, n_trials_false_cognate),
-pattern = "{1} ({2})") |>
-cols_merge(c(n_trials_true_non_cognate, n_trials_false_non_cognate),
-pattern = "{1} ({2})") |>
-cols_merge(c(n_trials_true_unrelated, n_trials_false_unrelated),
-pattern = "{1} ({2})") |>
-cols_label(true = "Participants",
-n_trials_true_cognate = "Cognate",
-n_trials_true_non_cognate = "Non-cognate",
-n_trials_true_unrelated = "Unrelated") |>
-tab_style(cell_text(style = "italic"),
-cells_column_labels()) |>
-tab_style(cell_text(align = "left"),
-cells_stub()) |>
-grand_summary_rows(fns = list(label = md("*N*")) ~ sum(.),
-fmt = ~ fmt_integer(.))
-```
 
@@
 ```{r coefs-oxf}
-var_labels <- c(
-"b_Intercept" = "Intercept",
+var_labels <- c("b_Intercept" = "Intercept",
 				"b_age_std" = "Age (+1 SD)",
 				"b_condition1" = "Condition (U vs. RN)",
-"b_condition2" = "Condition (RN vs. RC)"
-)
+				"b_condition2" = "Condition (RN vs. RC)")
 
@@
 									   vars_dict = var_labels,
-rope_interval = rope_interval
-)
+									   rope_interval = rope_interval)
 
 coefs <- model_summary |>
-mutate(
-.value = sprintf("%.3f", .value),
+	mutate(.value = sprintf("%.3f", .value),
 		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
-.rope = scales::percent(.rope, accuracy = 0.01)
-) |>
+		   .rope = scales::percent(.rope, accuracy = 0.01)) |>
 	split(janitor::make_clean_names(model_summary$.variable))
@@
 The overall target preference was equivalent across both pairwise condition comparisons.
-
-```{r tbl-coefs-oxf}
-#| label: tbl-coefs-oxf
-#| fig-cap: "Margin posterior mean predictions.
-A) Posterior mean predictions of the time course of target fixation in the test phase.
-B) Posterior mean prediction of the time course of the differences in target looking time between conditions.
-Lines and intervals indicate the mean and 95% credible interval of the posterior predictions."
-#| echo: false
-#| eval: false
-#| message: false
-#| warning: false
-#| out-width: 80%
-
-# summarise posterior draws
-intercept_label <- paste0("Intercept (at ", round(mean(data_oxf$age), 2), " months)")
-
-tbl_data <- model_summary |>
-	select(.variable_name, .value, .lower, .upper, .rope, .type) |>
-	mutate(
-		.variable_name = gsub("×", "$\\\\times$", .variable_name),
-		.hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
-		.rope = case_when(is.na(.rope) ~ "-",
-						  .rope > 0.9999 ~ "1",
-						  .rope < 0.00001 ~ "0",
-						  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope))
-		)
-	) |>
-	select(.variable_name, .value, .lower, .upper, .hdi, .rope)
-
-col_names <- c("", "$\\beta$", "95\\% HDI", "$p(\\text{ROPE})$")
-
-tbl_data |>
-	select(-c(.lower, .upper)) |>
-	kable(
-		format = "latex",
-		escape = FALSE,
-		col.names = col_names,
-		digits = 3,
-		booktabs = TRUE,
-		align = "lclr",
-		linesep = ""
-	) |>
-	kable_styling() |>
-	add_footnote("$\\beta$: median of the posterior distribution in the probability scale.
-95\\% HDI: 95\\% highest density interval of the distribution.
-$p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
-```
 
@@
 #| label: tbl-loos-oxf
-#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 2."
+#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 1."
 loo_compare(model_loos_oxf[2:4]) |>
@@
 n_participants_valid <- n_distinct(
-	attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id
-)
+	attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id)
 
@@
 									session_id,
-									.keep_all = TRUE
-)$is_valid_participant)
+									.keep_all = TRUE)$is_valid_participant)
 n_exc_participants_vocab <- sum(!distinct(attrition_bcn,
@@
 Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-@tbl-attrition shows a detailed description of the trial attrition.
 
@@
 The outcomes of this model provide strong evidence against differences between monolinguals and monolinguals, and inconclusive evidence for differences in overall target looking time across conditions.
-
-```{r tbl-coefs}
-#| label: tbl-coefs
-#| tbl-cap: "Posterior distribution of regression coefficients.
-Median: median of the posterior distribution in logit scale.
-95\\% HDI: 95\\% highest density interval of the distribution.
-*p*(ROPE): overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero."
-#| echo: false
-#| message: false
-#| eval: false
-#| warning: false
-#| out-width: 80%
-# summarise posterior draws
-intercept_label <- paste0("Intercept (at ", round(mean(data_bcn$age), 2), " months)")
-
-tbl_data <- model_summary |>
-	select(.variable_name, .value, .lower, .upper, .rope, .type) |>
-	mutate(
-		.variable_name = gsub("×", "$\\\\times$", .variable_name),
-		.hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
-		.rope = case_when(is.na(.rope) ~ "-",
-						  .rope > 0.9999 ~ "1",
-						  .rope < 0.00001 ~ "0",
-						  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope))
-		)
-	) |>
-	select(.variable_name, .value, .lower, .upper, .hdi, .rope)
-
-col_names <- c("", "$\\beta$", "95\\% HDI", "$p(\\text{ROPE})$")
-
-tbl_data |>
-	select(-c(.lower, .upper)) |>
-	kable(
-		format = "latex",
-		escape = FALSE,
-		col.names = col_names,
-		digits = 3,
-		booktabs = TRUE,
-		align = "lclr",
-		linesep = ""
-	) |>
-	kable_styling() |>
-	add_footnote("$\\beta$: median of the posterior distribution in the logit scale.
-95\\% HDI: 95\\% highest density interval of the distribution.
-$p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
-```
 
@@
 #| label: tbl-loos
-#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of models 0 to 3, and 3 to 6 in Study 1."
+#| tbl-cap: "Leave-one-out cross validation outcomes, comparing the predictive performance of the models in Study 1."
 get_loos <- function(x, y) {
@@
 	fmt_number(is.numeric) |>
-	cols_label(
-		elpd_diff = "ELPD (diff.)",
+	cols_label(elpd_diff = "ELPD (diff.)",
 			   se_diff = "SE ELPD (diff)",
 			   elpd_loo = "ELPD",
-		se_elpd_loo = "SE ELPD"
-	) |>
+			   se_elpd_loo = "SE ELPD") |>
 	fmt_missing(missing_text = "---") |>

### 2023-11-27 manuscript/manuscript.qmd

--- 2023-11-26 manuscript/manuscript.qmd
@@
 
-library(knitr)
-library(kableExtra)
 library(ggplot2)
+library(ggrepel)
 library(gt)
-library(gtExtras)
 library(patchwork)
 library(english)
-library(gtExtras)
 
@@
 
-clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
-
-options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
-		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
-		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
-		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
+clrs <- c("#004AAD", "#C8102E", "#FF9E1F")
+
+options(ggplot2.ordinal.fill = clrs,
+		ggplot2.ordinal.colour = clrs,
+		ggplot2.discrete.fill = clrs,
+		ggplot2.discrete.colour = clrs,
 		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
@@
 In line with previous studies in monolinguals, we further predicted that the strength of the lexical interference effects in the *Related/Non-cognate* and *Related/Cognate* conditions would be associated to participants' vocabulary size.
-Target word recognition should be delayed by the activation of a larger cohort of phonologically related words [@mani2011phonological; @chow2017spoken].
+Target word recognition should be delayed by the activation of a larger cohort of phonologically related words [@mani2011phonological; @chow2017spoken; @avila2021longitudinal; @mayor2014infant].
 We defined vocabulary size as the amount of words participants were reported to understand in their dominant language by their caregivers.
@@
 	tab_spanner("Degree of Exposure (%)", matches("doe")) |>
-	cols_label(n = "Testing sessions",
+	cols_label(n = "Test sessions",
 			   n_participants = "Participants",
@@
 #| label: fig-vocabulary-oxf
-#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores from the recurrent participants are shown linked. "
-#| fig-width: 6
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles.
+Vocabulary size scores from the recurrent participants are shown linked.
+For visualisation purposes, testing sessions were aggregated at three age points: 21, 25, and 30 months.
+Points and intervals indicate mean and standard deviations, respectively."
+#| fig-width: 5
 #| fig-height: 4
+#| out-width: 70%
 vocab_plot_data <- vocabulary |>
@@
 			   side = side)) +
-	geom_point(data = filter(vocab_plot_means, 
-							 study=="Study 1 (English)"), 
-			   colour = clrs[1],
-			   show.legend = FALSE,
-			   size = 2,
+		geom_point(size = 2,
 			   shape = 1,
+			   colour = "black",
+			   alpha = 1/2,
 			   stroke = 1) +
@@
 				formula = "y ~ x",
-				colour = clrs[1],
-				fill = clrs[1]) +
+				colour = "black",
+				fill = "grey") +
 	labs(x = "Age (months)",
@@
 	scale_y_continuous(limits = c(0, 575),
-					   breaks = seq(0, 1e3, 50)) +
+					   breaks = seq(0, 1e3, 100)) +
 	scale_x_continuous(breaks = seq(0, 50, 2)) +
@@
 
-We created four stimuli lists, to which participants were randomly allocated.
-Recurrent participants were always allocated to the same list.
-Each list contained a different subset of prime-target-distractor triples.
-Target-distractor pairs were kept constant across lists: all infants, regardless of the list to which they were allocated, were presented with the *ball*-*trousers* target distractor pair.
-Each target-distractor pair was presented twice in their corresponding lists, alternating which word acted as target, and which as distractor.
-For instance, the *ball*-*trousers* pair was presented in all lists twice, once with *ball* as target, and another with *trousers* as target.
-Across lists, the same target-distractor pair appeared with a different prime, counterbalancing the condition to which it belonged.
-For instance, in list one the *ball*-*trousers* pair was preceded by the prime *bike* (*Related/Cognate*), by *butterfly* (*Related/Non-cognate*) in list two, and by *star* and *nose* (*Unrelated*) in lists three and four, respectively.
-
+We created four lists of trials, across which the same target-distractor pair appeared with a different prime, counterbalancing the condition to which it belonged.
+For instance, in list one the *ball*-*trousers* pair was preceded by *bike* (*Related/Cognate*), by *butterfly* (*Related/Non-cognate*) in list two, and by *star* and *nose* (*Unrelated*) in lists three and four (see Appendix A for a detailed description of the stimuli).
 @tbl-stimuli shows a detailed summary of the stimuli properties, broken down by trial type and testing language.
@@
 Caregivers were instructed to keep their eyes shut (to avoid recording their gaze, instead of the participant's), to be still, and to avoid interacting with the participant verbally or non-verbally.
-Participants sat at approximately 65 cm from the eye-tracker and a XX-in screen of $1929\times1080$ screen resolution.
-The study was run using a custom Matlab script, PresentMate, based on the PsychToolbox-3 extension [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox].
-Visual fixations were recorded using a Tobii TX 300 eye-tracker and a 23-in screen of 1920 $\times$ 1080 resolution.
+Participants sat at approximately 65 cm from the eye-tracker and a 23-inches screen with $1929\times1080$ resolution.
+The study was run on Windows 7 (64-bit), using a custom Matlab script, PresentMate, based on the PsychToolbox-3 extension (3.0.10, 32 bit) [@kleiner2007s; @brainard1997psychophysics; @pelli1997videotoolbox].
+Visual fixations were recorded using a Tobii TX300 eye-tracker (Tobii Technology, Stockholm, Sweden) and a 23-in screen of 1920 $\times$ 1080 resolution.
 The Tobii Analytics SDK 3.0 was used to interact with the eye-tracking while the experiment was running.
@@
 
-After trials that matched any of the aforementioned exclusion criteria from the data set, we excluded participants who did not provide at least two valid trials in the *Cognate* condition, the *Non-cognate* condition, or the *Unrelated* condition (*n* = `r n_exc_participants`), and participants with a L1 vocabulary size lower than 42, which corresponds to 10% of the words in the OCDI vocabulary checklist (*n* = `r n_exc_participants_vocab`).
+After trials that matched any of the aforementioned exclusion criteria from the data set, we excluded participants who did not provide at least two valid trials in each condition (*n* = `r n_exc_participants`), and participants with a vocabulary size lower than 42, which corresponds to 10% of the words in the OCDI vocabulary checklist (*n* = `r n_exc_participants_vocab`).
 The final data set included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
@@
 						r_info$R.version$minor,
-						.sep = "."
-)
+						.sep = ".")
 stan_version <- "2.33.0"
@@
 									   vars_dict = var_labels,
-									   rope_interval = rope_interval
-)
+									   rope_interval = rope_interval)
 
@@
 #| fig-height: 6.5
+#| out-width: 80%
 make_std <- function(x, mean, sd) (x - mean) / sd
@@
 plot_epreds + plot_diffs +
-	plot_layout(ncol = 1) &
+	plot_layout(ncol = 1, heights = c(0.6, 0.4)) &
 	plot_annotation(tag_levels = "A") &
@@
 The absence of a phonological priming effect suggest that either English monolinguals did not generate implicit labels for the prime pictures presented in silence, or that, if generated, such labels did not interact with the subsequent recognition of the target word.
-Both candidate explanations conflict with both Mani and Plunkett’s studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects (@duta2012erp; @styles2015infant).
+Both candidate explanations conflict with both Mani and Plunkett’s studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects [@duta2012erp; @styles2015infant].
 
@@
 This points to neither variable having a substantial influence in participants' target looking behaviour across conditions.
-These results diverge from previous studies reporting an increment in word recognition speed [@fernald1998rapid; @marchman2008speed], and stronger phonological priming effects in children with larger vocabulary sizes [@mani2011phonological; @chow2017spoken].
+These results diverge from previous studies reporting an increment in word recognition speed [@fernald1998rapid; @marchman2008speed], and stronger phonological priming effects in children with larger vocabulary sizes [@mani2011phonological; @chow2017spoken; @avila2021longitudinal].
 Overall, this results suggest that our modification of the implicit naming task resulted in the loss of the originally reported effect.
@@
 		filter(child_id %in% participants_bcn$child_id[duplicated(participants_bcn$child_id)]) |>
-		pivot_wider(
-			id_cols = child_id,
+		pivot_wider(id_cols = child_id,
 					names_from = session_n,
 					values_from = age,
-			names_repair = janitor::make_clean_names
-		) |>
+					names_repair = janitor::make_clean_names) |>
 		rowwise() |>
-		mutate(
-			diff_1 = x2 - x1, diff_2 = x3 - x2,
+		mutate(diff_1 = x2 - x1, diff_2 = x3 - x2,
 			   diff_min = min(diff_1, diff_2, na.rm = TRUE),
-			diff_max = max(diff_1, diff_2, na.rm = TRUE)
-		) |>
+			   diff_max = max(diff_1, diff_2, na.rm = TRUE)) |>
 		ungroup() |>
-		summarise(
-			diff_min = min(diff_min, na.rm = TRUE),
-			diff_max = max(diff_max, na.rm = TRUE)
-		)
+		summarise(diff_min = min(diff_min, na.rm = TRUE),
+				  diff_max = max(diff_max, na.rm = TRUE))
 })
@@
 Each version included a Catalan and a Spanish vocabulary checklist.
-Catalan checklists contained between `r n_items$min[1]` and `r n_items$min[2]` words, and Spanish checklists contained between `r n_items$min[2]` and `r n_items$min[2]` words (see the Methods section of Chapter 1 for a detailed description of the questionnaire..
+Catalan checklists contained between `r n_items$min[1]` and `r n_items$min[2]` words, and Spanish checklists contained between `r n_items$min[2]` and `r n_items$min[2]` words (see the Methods section of Chapter 1 for a detailed description of the questionnaire.
 Participants were randomly allocated to one of the four versions.
@@
 #| fig-width: 6
-#| fig-height: 4
+#| fig-height: 3
 vocab_plot_data |> 
+	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual"))) |> 
 	filter(study=="Study 2 (Catalan/Spanish)") |> 
-	ggplot(aes(age, l1_count, 
-			   colour = lp,
-			   fill = lp)) +
+	ggplot(aes(age, l1_count)) +
 	facet_wrap(~lp) +
@@
 			   shape = 1,
+			   colour = "black",
+			   alpha = 1/2,
 			   stroke = 1) +
 	geom_smooth(method = "lm", 
-				formula = "y ~ x") +
+				formula = "y ~ x",
+				colour = "black",
+				fill = "grey") +
 	labs(x = "Age (months)",
@@
 		 fill = "Group") +
-	scale_color_manual(values = clrs[c(1, 5)]) +
-	scale_fill_manual(values = clrs[c(1, 5)]) +
+	scale_x_continuous(breaks = seq(0, 40, 2)) +
+	scale_y_continuous(limits = c(0, 575),
+					   breaks = seq(0, 1e3, 100)) +
+	scale_x_continuous(breaks = seq(0, 50, 2)) +
 	theme(panel.grid.major.y = element_line(linetype = "dotted",
 											colour = "grey"),
-		  legend.position = "top",
+		  legend.position = "none",
 		  axis.title.x = element_blank(),
@@
 Same as in Study 1.
-We used a custom Matlab XXXX script using the PsychToolbox-3 extension to present the stimuli, and the Tobii Analytics SDK 3.0 to interact with the eye-tracking while the experiment was running.
+We run the study on Windows 10 64-bit, using custom Matlab (2018a 64-bit) script using the PsychToolbox-3 extension (3.0.15 64-bit) to present the stimuli on a 23-inches screen with $1929\times1080$ resolution, and the Tobii Analytics SDK 3.0 to interact with the eye-tracker (Tobii TX300 and Tobii Pro Sprectrum, Tobii Technology, Stockholm, Sweden) while the experiment was running.
 
@@
 								 session_id,
-								 .keep_all = TRUE
-)$is_valid_participant)
+								 .keep_all = TRUE)$is_valid_participant)
 n_participants_valid <- n_distinct(
-	attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id
-)
+	attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id)
 
@@
 									session_id,
-									.keep_all = TRUE
-)$is_valid_participant)
+									.keep_all = TRUE)$is_valid_participant)
 n_exc_participants_vocab <- sum(!distinct(attrition_bcn,
 										  session_id,
-										  .keep_all = TRUE
-)$is_valid_vocab_size)
+										  .keep_all = TRUE)$is_valid_vocab_size)
 
 n_longitudinal <- attrition_bcn |>
-	filter(
-		is_valid_participant,
-		is_valid_trial
-	) |>
+	filter(is_valid_participant,
+		   is_valid_trial) |>
 	distinct(child_id, session_n) |>
@@
 
-We modeled the data following a similar approach as in Study 1, with the main difference that participants' language profile (*Group*) was now included as a predictor in the model, in interaction with the *Condition* predictor.
+We modelled the data following a similar approach as in Study 1, with the main difference that participants' language profile (*Group*) was now included as a predictor in the model, in interaction with the *Condition* predictor.
 We set two *a priori* contrasts for the *Condition* predictor [@schad2020capitalize]: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
@@
 	"b_condition1:lp1" = "Group \U00D7 Condition (U vs. RN)",
-	"b_condition2:lp1" = "Group \U00D7 Condition (RN vs. RC)"
-)
+	"b_condition2:lp1" = "Group \U00D7 Condition (RN vs. RC)")
 
@@
 		select(model, elpd_diff, se_diff) |>
-		mutate(
-			diff_label = sprintf("%.3f", elpd_diff),
-			se_label = sprintf("%.3f", se_diff)
-		)
+		mutate(diff_label = sprintf("%.3f", elpd_diff),
+			   se_label = sprintf("%.3f", se_diff))
 	return(out)
@@
 	rownames_to_column("model") |>
-	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model)) - 3),
+	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model))),
 		   across(matches("diff"),
@@
 		   	   }),
-		   model = case_when(model == "Model 1" ~ "Model 0 (Age as main effect)",
+		   model = case_when(
+		   	model == "Model 1" ~ "Model 0 (Age as main effect)",
 		   	model == "Model 2" ~ "Model 1 (Age-by-condition)",
@@
 Paralleling the results from Study 1 participant' looking behaviour suggested robust word recognition, regardless of experimental condition, participant language profile, age, or vocabulary size.
-Overall, participants' performance was equivalent across all priming conditions suggesting that no phonological priming took place within or across languages in either monolinguals or bilinguals.
-These results conflict with previous findings in several ways.
-First, and as discussed in the Discussion section of Study 1, previous investigations using implicit naming paradigms had found evidence of within-language priming effects in same-aged monolinguals learning English (and younger).
-In this study monolingual infants learning Catalan or Spanish did not show evidence of such priming effect, as suggested by their equivalent target looking behaviour in both *Unrelated* and *Related/Non-cognate* trials.
-Given that English monolinguals in Study 1 did not show priming effects either, it cannot be concluded that the diverging results from Study 2 and those available in the literature are due to cross-language differences between Catalan and Spanish, and English.
-
-Second, our results are also in contrast with the non-selective account of lexical access.
-Bilinguals in Study 1 did not show evidence of cross-language priming, as suggested by the lack of differences in target looking between *Related/Non-cognate* and *Related/Cognate* trials.
-Under the non-selective account, we had predicted bilinguals in this study to lexicalise the prime pictures in both languages, which should have exerted a stronger priming effect on target recognition in *Related/Cognate* trials than in *Related/Non-cognate trials*.
-Overall, results in Study 2 did not provide evidence of phonological priming effects in monolingual and bilingual infant learning Catalan and Spanish.
+Monolinguals and bilinguals showed equivalent target looking behaviour in *Unrelated*, *Related/Non-cognate*, and *Related/Cognate* trials, suggesting that no phonological priming took place, either within languages or across languages.
+These results contrast with those of previous studies using a similar paradigm, which reported within-language priming effects in same-aged monolinguals [@mani2011phonological; @avila2021longitudinal] and younger [@mani2010infant; @duta2012erp; @styles2015infant], and cross-language priming in adults [@von2014bilinguals].
+
+We anticipated participants' sensitivity to phonological priming to increase with the size of their lexicon, in the light of previous studies in which the maturation of the lexicon was associated with larger phonological interference in word recognition [@mani2011phonological; @chow2017spoken].
+In Study 2, incorporating participants' age as a predictor in the model in interaction with the two contrasts of the *Condition* predictor did not increase the predictive performance of the model.
+Neither did vocabulary size.
+This suggests that the lack of evidence of phonological priming in participants in this study, either within or across languages, did not depend of participants lexical development status.
 
@@
 	unnest_wider(doe) |>
-	mutate(
-		doe2 = ifelse(test_language == "Catalan",
-					  doe_spanish, doe_catalan
-		),
-		is_positive = doe2 > 0
-	) |>
+	mutate(doe2 = ifelse(test_language == "Catalan",
+						 doe_spanish, doe_catalan),
+		   is_positive = doe2 > 0) |>
 	count(is_positive)
@@
 
-In this paper, we investigated the developmental trajectories of cross-language co-activation in the initial lexicon.
+In this chapter, we investigated the developmental trajectories of cross-language co-activation in the initial lexicon.
 We tested a large cohort of monolingual and bilingual toddlers in an implicit naming paradigm, in which we designed three experimental conditions to manipulate the phonological overlap between the prime and target words within and across languages.
-In *Unrelated* trials, prime and target were phonologically unrelated in both languages.
-In *Related/Non-cognate* trials, prime and target labels shared phonological onset only in the dominant language of participants, in which they were tested.
-In *Related/Cognate* trials, the prime label was a cognate: prime and target labels shared phonological onset in both languages.
+In Unrelated trials, prime and target were phonologically unrelated in both languages.
+In Related/Non-cognate trials, prime and target labels shared phonological onset only in the dominant language of participants, in which they were tested.
+In Related/Cognate trials, the prime label was a cognate: prime and target labels shared phonological onset in both languages.
 In Study 1, we attempted to replicate the original findings by @mani2010infant and @mani2011phonological in a same-aged English monolingual cohort.
-We found a null pattern of results in which we did not find any evidence of phonological priming.
+We found a null pattern of results, indicating no evidence of phonological priming.
 In Study 2, we tested a cohort of monolingual and bilingual infants learning Catalan, Spanish, or both, and found similar results, with no evidence of phonological priming effect in either monolinguals or bilinguals.
-In none neither study was participants' word recognition influenced by their age or vocabulary size.
-
-Previous studies on word recognition had provided evidence phonological priming effects in English monolingual infants 18-month-old and older.
-@mani2010infant had shown a facilitation effect in word recognition when 18-month-olds were previously presented with a familiar picture whose label shared phonological onset with the target word.
-@mani2011phonological extended these results to 21-month-olds, showing an effect in the opposite direction: phonologically related primes interfered with target word recognition.
-The results from both studies suggested that participants lexicalised the prime pictures---even if presented in silence---and that the resulting phonological form interacted with subsequent auditory word recognition.
-The shift from facilitation at 18 months to inhibition at 21 months was interpreted as a shift from sub-lexical facilitation at the phonetic level.
-The authors suggested that at 18 months, target word recognition was facilitated by the prior activation of an overlapping set of phonological segments.
-At older ages, participants with larger vocabulary sizes showed an interference effect generated by the increased size of the prime cohort, which led to slower selection of the phonologically related target word.
-This last conclusion was supported by the fact that the size of the interference effect was associated with the increase in participants' vocabulary size, and also with the cohort size of the prime label---primes belonging to a larger neighbourhood of phonologically related words were subject to stronger interference effects during the task.
-
-Even earlier evidence of implicit naming had been provided through electrophysiological measurements at 14 months of age.
-@duta2012erp presented name-known pictures in silence for one second.
-After one second, the picture's label was auditorily presented, and the infants' N400 component was registered.
-In some trials the auditory label corresponded to a canonical realisation of the word-form.
-In other trials, the word was mispronounced.
-Infants ERP signal differed when presented with correct pronunciations or mispronunciations, indicating that infants had generated expectations at the phonological level about the auditory labels of the picture before they were presented with its auditory label.
-A later study by @styles2015infant re-analysed the first 1,000 ms of the trials in the previous study (while the picture was being presented before the auditory label was presented), and found that the ERPs of name-known pictures (according to parental reports of receptive vocabulary) differed from those of name-unknown pictures (which infants would not be able to lexicalise).
-This provides further support to the account that at around 14 months of age, infants already name familiar pictures, even if presented in silence.
-Evidence of implicit naming in bilinguals is, however, scarce.
-
-To our knowledge, only one study has used an implicit naming paradigm to study cross-language priming in bilinguals.
-@von2014bilinguals adapted @mani2010infant procedure to test German-English bilingual adults.
-The authors manipulated the phonological overlap between the prime label in English (presented in silence) and a German target (auditorily presented) in both German and English.
-Participants' evoked potentials revealed differences between trials in which the German prime label overlapped phonologically with the English target label, compared to trials in which none of the labels overlapped.
-These results suggest that adult bilinguals implicitly named prime pictures, and that the resulting label interacted with subsequent word recognition.
-
-In contrast with previous studies in monolingual infants, and bilingual adults, we found no evidence of implicit naming was found.
-We consider three scenarios under which implicit naming might have occurred, in line with previous literature, but our design failed to capture it.
+We did not find any effect of participants' age or vocabulary size.
+
+The null pattern of results in Studies 1 and 2 contrasts with previous findings of within- and cross-language priming using an implicit naming paradigm.
+In their seminal study, @mani2010infant and @mani2011phonological reported within-language priming effects in English monolingual infants.
+In bilinguals, evidence of cross-linguistic priming in a implicit naming paradigm was available in adults [@von2014bilinguals].
+The priming effects shown in these studies reveal that infants and adults retrieve phonologically detailed word-forms when presented with pictures of familiar objects, which later interact with the subsequent auditory recognition of phonologically related words.
+Evidence of such implicit naming is available in infants as young as 14 months.
+Electrophysiological evidence reported by @duta2012erp and @styles2015infant suggests that, at this, age, infants lexicalise name-known pictures presented in silence, and that the generated phonological form is sensitive to subsequent mispronunciations of the word.
+The possibility that infants in the present investigation failed to retrieve phonological word forms is therefore unlikely.
+
+We consider three scenarios under which implicit naming might have occurred in the experiments presented in this chapter, but our design failed to capture it.
 First, it is be possible that infants in both Studies 1 and 2 implicitly generated phonological labels for the primes, but such labels lacked the phonological detail to interact with the subsequent recognition of a phonologically related target word.
-This is unlikely, given that both monolinguals and bilinguals have been shown to encode lexical representations with high phonological detail from early ages [@swingley2000spoken; @bailey2002phonological; @tamasi2016measuring; @tamasi2017pupillometry; @ramon2009vowel].
+This is unlikely, given that both monolinguals [@swingley2000spoken; @bailey2002phonological; @tamasi2017pupillometry] and bilinguals [@ramon2009vowel; @tamasi2016measuring] have been shown to encode lexical representations with high phonological detail from early ages.
 
@@
 
-Third, it is possible that the modifications of the implicit naming task in the present investigation might have reduce the chances of detecting the anticipated effects.
+Third, and most likely, the modifications of the implicit naming task in the present investigation might have reduce the chances of detecting the anticipated effects.
 The most critical difference between the original design of the implicit naming task by Mani and Plunkett and that of the present study is the absence of a pre-naming phase during the test phase.
@@
 It is possible that such time interval was too short for participants to retrieve the phonological label of the prime picture before the target was presented.
-Further research should investigate the role of prime-target inter-stimulus interval on the time course of lexical access and selection in toddlers.
-
-The null pattern of results found in the present investigation would have important implications for current models of bilingual lexical development.
-Recent accounts of bilingual word acquisition pointed to a facilitative role of phonological similarity between the two languages.
-The findings reported by @floccia2018vocabulary pointed to a language distance effect, in which bilinguals learning two lexically similar languages (sharing more cognates) knew more words in their less dominant language than those learning two language with lower lexical similarity.
-Later work by @mitchell2022cognates, @siow2022effect, and @garcia2023cognate provided evidence for a more direct facilitation effect of cognateness.
-The main candidate mechanism behind the cognateness facilitation effect in word acquisition is parallel activation: the co-activation of form-similar translation equivalents during linguistic exposure might lead to a faster accumulation of learning instances for cognate words, which ultimately results in an earlier age of acquisition.
-In the present study, we provide evidence against such cross-language effects during word recognition.
-These outcomes are not in line with parallel activation taking place during speech exposure in bilinguals.
-It is possible that the mechanisms involved in the cognate facilitation in bilingual word acquisition are not captured by the task used in the present study.
-The implicit naming task used in the present investigation might be tapping into lower-level functions, related to acoustic and phonological processing, that are related to---but not critical for---word acquisition.
-Future research should contemplate alternative mechanisms for the cognateness facilitation effect on bilingual lexical acquisition.
-
-The present study introduces several methodological contributions.
-First, this is, to our knowledge, the first study investigating cross-language priming using an implicit naming paradigm in toddlers.
-Second, the longitudinal design of the data collection provided a more suitable design for drawing conclusions about developmental change in word recognition trajectories, compared to studies that tested participants from a single age group [@floccia2020translation], or studies that with an exclusively cross-sectional design [@von2012language].
-Third, the modelling approach in the present study incorporates the double source of repeated measures simultaneously into the random effects structure of the multilevel model.
+Such failure to generate phonological word-forms for prime labels would have prevented participants in Studies 1 and 2 from being affected by phonological priming effects during target word recognition.
+
+```{r fig-mp}
+#| label: fig-mp
+#| fig-cap: "Distribution of lexical frequencies and word familiarity at 18 months for the stimuli in Mani and Plunkett (2010, 2011), and in Study 1.
+A) Lexical frequencies (expressed as Zipf scores) for prime and target words.
+Lexical frequences are shown for related and unrelated primes separately.
+B) Word familiarity scores for prime and target words, calculated as the proportion of participants in the OCDI norms that were reported by their caregivers to understand the word.
+Word familiarity scores are shown for related and unrelated primes separately."
+#| fig-width: 7
+#| fig-height: 3
+mp <- read_csv(file.path("manuscript", "_assets", "data", "mp-stimuli.csv"),
+			   show_col_types = FALSE)
+
+mp_means <- mp |> 
+	filter(role!="distractor") |> 
+	mutate(condition = if_else(role=="target", 
+							   "", condition)) |> 
+	summarise(aoa_sd = sd(aoa, na.rm = TRUE),
+			  aoa = mean(aoa, na.rm = TRUE),
+			  freq_sd = sd(freq),
+			  freq = mean(freq),
+			  .by = c(role, condition, study))
+mp |> 
+	filter(role!="distractor") |> 
+	mutate(condition = if_else(role=="target", 
+							   "", condition)) |> 
+	ggplot(aes(condition, freq, colour = study, fill = study)) +
+	facet_wrap(~role, scales = "free_x") +
+	geom_dots(side = "both",
+			  layout = "swarm",
+			  fill = "white",
+			  stroke = 1,
+			  position = position_dodge(width = 1),
+			  alpha = 1/5) +
+	stat_summary(geom = "errorbar",
+				 fun.data = mean_se,
+				 width = 0.1,
+				 linewidth = 1/2,
+				 position = position_dodge(width = 1)) +
+	stat_summary(geom = "point",
+				 fun = mean,
+				 size = 1.5,
+				 position = position_dodge(width = 1)) +
+	labs(x = "Role", 
+		 y = "Lexical frequency (Zipf)",
+		 colour = "Study",
+		 fill = "Study",
+		 fill = "Study") +
+
+	mp |> 
+	filter(role!="distractor") |> 
+	mutate(condition = if_else(role=="target", 
+							   "", condition)) |> 
+	ggplot(aes(condition, aoa, colour = study, fill = study)) +
+	facet_wrap(~role, scales = "free_x") +
+	geom_dots(side = "both",
+			  layout = "swarm",
+			  fill = "white",
+			  stroke = 1,
+			  position = position_dodge(width = 1),
+			  alpha = 1/5) +
+	stat_summary(geom = "errorbar",
+				 fun.data = mean_se,
+				 width = 0.1,
+				 linewidth = 1/2,
+				 position = position_dodge(width = 1)) +
+	stat_summary(geom = "point",
+				 fun = mean,
+				 size = 1.5,
+				 position = position_dodge(width = 1)) +
+	geom_text_repel(data = summarise(mp, aoa = min(aoa, na.rm = TRUE),
+									 word = word[which.min(aoa)],
+									 .by = c(study, role, condition)),
+					aes(label = word), max.overlaps = 100) |> 
+	labs(x = "Role", 
+		 y = "Familiarity at 18 months",
+		 colour = "Study",
+		 fill = "Study",
+		 fill = "Study") +
+	scale_y_continuous(labels = scales::percent,
+					   limits = c(0, 1)) +
+
+	plot_layout(nrow = 1, guides = "collect") &
+	plot_annotation(tag_levels = "A") &
+	theme(legend.position = "top",
+		  legend.title = element_blank(),
+		  axis.title.x = element_blank(),
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
+```
+
+A difference in the difficulty of the stimuli might have influenced the results in the present study, compared to those of the original studies.
+When designing the stimuli lists, we considered three variables as indices of word difficult during recognition: lexical frequency, age of acquisition, and number of phonemes.
+The distribution of the three variables was equivalent across the three experimental conditions (see @tbl-stimuli), so it is unlikely that such differences cancelled out a possible priming effect.
+However, the stricter limitations under which we build the stimuli lists, might have lead to out stimuli lists including more difficult words than in the original study by @mani2010infant.
+We examined this possibility by comparing the distributions of the English words included in Study 1, with those included in @mani2010infant and @mani2011phonological (stimuli lists are identical in both studies).
+@fig-mp shows a comparison between the stimuli lists of the three studies in lexical frequency and word familiarity at 18 months.
+Overall, words included in Mani and Plunkett and in Study 1 have equivalent lexical frequency, and are know by a similar proportion of English monolinguals infants, according to the OCDI norms.
+This is the case for prime and target words across the related and the unrelated conditions.
+It is therefore unlikely that the lack of priming effects in Study 1 is due to an increased difficulty in the items included.
+
+```{r}
+oxf_vocab <- vocabulary |> 
+	inner_join(filter(attrition_participants,
+					  is_valid_participant),
+			   by = join_by(session_id)) |>
+	inner_join(participants,
+			   by = join_by(child_id, session_id, vocab_id)) |>
+	filter(test_language=="English") |>
+	summarise(l1_count_sd = sd(l1_count), 
+			  l1_count = mean(l1_count),
+			  .by = age_group) |> 
+	arrange(age_group)
+```
+
+Another possibility is that participants in the present study had smaller vocabulary sizes than those of participants in the original studies.
+This hypothesis is not easy to investigate, as quantitative vocabulary sizes were not reported in original studies.
+A more recent study by @avila2021longitudinal, in which phonological priming effects were found associated to participants vocabulary size, did provide summary statistics for participants vocabulary size scores.
+This study tested a cohort of monolingual German infants in a word recognition task, in which participants in which participants were presented with auditory primes and targets, which were phonologically related or unrelated.
+The authors estimated participants' receptive vocabulary sizes using the *Fragebogen zur frühkindlichen Sprachentwicklung* [szagun2009fragebogen], an adaptation of the CDI to German.
+Their cohort of participants showed receptive vocabulary sizes larger than those of participants in the present study.
+Participants in @avila2021longitudinal knew an average of 405.24 (*SD* = 96.29) at 21 months and 501.97	(*SD* = 73.41) at 24 months, which contrast with receptive vocabulary sizes of participants in Study 1: `r round(oxf_vocab$l1_count[1], 2)` at 21 months (*SD* = `r round(oxf_vocab$l1_count_sd[1], 2)`), and `r round(oxf_vocab$l1_count[2], 2)` (*SD* = `r round(oxf_vocab$l1_count_sd[2], 2)`) at 25 months.
+Estimates from both questionnaires should be compared with caution---if at all---given their different lengths.
+It possible that the apparent smaller vocabulary size of English participants in Study 1 is a measurement artefact, resulting from a lower upper bound in the possible number of words that can be marked acquired by caregivers.
+
+Despite the unsuccessful adaptation of the original procedure, the present study introduces several methodological contributions.
+First the longitudinal design of the data collection provided a more suitable design for drawing conclusions about developmental change in word recognition trajectories, compared to studies that tested participants from a single age group [@floccia2020translation], or studies that with an exclusively cross-sectional design [@von2012language].
+Second, the modelling approach in the present study incorporates the double source of repeated measures simultaneously into the random effects structure of the multilevel model.
 The models in Studies 1 and 2 accounts for the time course of target looking across the trials and its associated autocorrelation using Hierarchical General Additive Models [@barr2008analyzing; @pedersen2019hierarchical].
@@
 
-In summary, we tested the language non-selective hypothesis of lexical access in bilingual toddlers using an implicit naming paradigm.
-In Study 1, we did not find evidence of within-language or cross-language priming effects, suggesting that participants might have not generated covert labels for the prime pictures presented in silence.
-In Study 2, we attempted to replicated the original study showing evidence of implicit naming in younger infants, but found no evidence of such effects: monolingual infants did not show evidence of implicit naming.
-Overall, our results allude to more complex state of the investigation about early priming effects than anticipated from the literature.
+In summary, we aimed to test the language non-selective hypothesis of lexical access in bilingual toddlers using an adaptation of the implicit naming paradigm.
+This adaptation involved target auditory labels immediately after the offset of prime pictures, instead of presenting the target labels after a baseline period of 2,000 after the offset of the prime pictures.
+In Study 1, we tested English monolinguals (same population as in the original studies) to establish a baseline to later test bilingual participants.
+We attempted to replicate the previously reported within-language phonological priming effect.
+We did not find evidence of such effect, suggesting that our modification of the original task was unsuccessful.
+Because data collection was conducted simultaneously for Studies 1 and 2, data in Catalan-Spanish monolinguals and bilinguals was available despite the failed replication in Study 1.
+In Study 2, we also found null pattern of results, in which neither monolinguals nor bilinguals showed evidence of within- or cross-language priming effects.
+Overall, our results suggest that the change in the timing of the trial disrupted the dynamics of word recognition in such way that priming effects were no longer detectable in our adaptation of the paradigm.
 

### 2023-11-28 manuscript/_appendix/_stimuli.qmd
Final adjustments to tables and figures

@@
 The experimenter assigned the participant to the Catalan or Spanish stimuli list involving the closest variant to that of caregivers'.
+
+In addition to sharing phonological onset, prime and target shared higher overall phonological similarity---as measured using the Levenshtein distance---between their phonological transcriptions---in the *Related/Cognate* and the *Related/Non-cognate* conditions, compared to the *Unrelated* condition.
+In *Related/Cognate* trials, the prime label in the language of test shared a higher overall phonological similarity with its translation, compared to *Related/Non-cognate* trials.
+Since the number of cognate and non-cognate primes was balanced in *Unrelated* trials, overall phonological similarity between prime labels prime labels in the *Unrelated* condition had an intermediate overall phonological similarity.
 

### 2023-11-28 manuscript/manuscript.qmd
Final adjustments to tables and figures

@@
 ages <- participants_oxf |>
-	summarise(
-		n = n(),
+	summarise(n = n(),
 			  n_participants = n_distinct(child_id),
@@
 			  age_vctr = list(age),
-		.by = c(lp, test_language)
-	)
+			  .by = c(lp, test_language))
 
@@
 		filter(child_id %in% participants_oxf$child_id[duplicated(participants_oxf$child_id)]) |>
-		pivot_wider(
-			id_cols = child_id,
+		pivot_wider(id_cols = child_id,
 					names_from = session_n,
 					values_from = age,
-			names_repair = janitor::make_clean_names
-		) |>
+					names_repair = janitor::make_clean_names) |>
 		rowwise() |>
@@
 			  n_participants = length(unique(child_id)),
-			  across(age, lst(mean, sd, min, max)),
+			  across(age, lst(mean, sd)),
 			  across(matches("doe_"), lst(mean, sd)),
@@
 					   fns = list(Total ~ mean(.)),
-					   fmt = ~ fmt_number(., decimals = 1)) |>
+					   fmt = ~ fmt_number(., decimals = 2)) |>
 	grand_summary_rows(columns = c(n, n_participants),
@@
 	# gt_plt_dist(age_vctr, type = "histogram") |>
-	fmt_number(is.numeric, decimals = 1) |>
+	fmt_number(is.numeric, decimals = 2) |>
 	fmt_integer(c(n, n_participants, n_FALSE, n_participants_FALSE)) |>
-	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |>
+	fmt_number(matches("doe"), decimals = 2, scale_by = 100) |>
 	cols_merge(c(n, n_FALSE), pattern = "{1} ({2})") |>
@@
 			   pattern = "{1} ({2})") |>
-
-	cols_merge(c(age_min, age_max), pattern = "{1}-{2}") |>
 	cols_merge(c(age_mean, age_sd),
@@
 			   age_mean = "M (SD)",
-			   age_min = "Range",
 			   doe_catalan_mean = "M (SD)",
@@
 			   shape = 1,
-			   colour = "black",
-			   alpha = 1/2,
+			   colour = "grey",
+			   alpha = 3/4,
 			   stroke = 1) +
@@
 				colour = "black",
-				fill = "grey") +
+				fill = "black") +
 	labs(x = "Age (months)",
@@
 
+```{r stim-stats}
+durations <- stimuli |>
+	summarise(across(duration, 
+					 lst(mean, sd, min, max)), 
+			  .by = c(test_language)) %>%
+	mutate(across(is.numeric, \(x) format(round(x*1e3, 2), big.mark = ","))) %>%
+	split(janitor::make_clean_names(.$test_language))
+```
+
 We created four lists of trials, across which the same target-distractor pair appeared with a different prime, counterbalancing the condition to which it belonged.
@@
 Lexical frequencies were extracted from the English corpora from the CHILDES database [@macwhinney2000childes; @sanchez2019childes] as counts per million words, and transformed into Zipf scores for easier cross-language comparison [@zipf1945meaning; @van2014subtlex].
-In addition to sharing phonological onset, prime and target shared higher overall phonological similarity---as measured using the Levenshtein distance---between their phonological transcriptions---in the *Related/Cognate* and the *Related/Non-cognate* conditions, compared to the *Unrelated* condition.
-In *Related/Cognate* trials, the prime label in the language of test shared a higher overall phonological similarity with its translation, compared to *Related/Non-cognate* trials.
-Since the number of cognate and non-cognate primes was balanced in *Unrelated* trials, overall phonological similarity between prime labels prime labels in the *Unrelated* condition had an intermediate overall phonological similarity.
-Audio durations were also equivalent across conditions.
+Audios had an average duration of `r durations$english$duration_mean` ms (*SD* = `r durations$english$duration_sd`, *Range* = `r durations$english$duration_min`--`r durations$english$duration_max`).
 
@@
 #| label: tbl-stimuli
-#| tbl-cap: "Summary of stimuli properties by trial type."
+#| tbl-cap: "Summary of stimuli properties by trial type. Values are summarised using the mean and the standard deviation (between parentheses)."
 stimuli |>
-	unnest_wider(c(freq, nphon)) |>
-	summarise(across(c(matches("n_phon|freq_|lv_|nphon"), duration),
+	unnest_wider(c(freq, nphon, familiarity)) |>
+	summarise(across(c(matches("n_phon|freq_|nphon|familiarity")),
 					 list(	mean = \(x) mean(x, na.rm = TRUE),
@@
 	# 			 fmt = ~ fmt_number(., decimals = 2)) |>
-	grand_summary_rows(	columns = is.numeric,
+	grand_summary_rows(columns = matches("phon|freq"),
 					   fns = list(Total ~ mean(.)),
 					   fmt = ~ fmt_number(., decimals = 2)) |>
+		grand_summary_rows(columns = matches("familiarity"),
+					   fns = list(Total ~ mean(.)),
+					   fmt = ~ fmt_number(., decimals = 2, scale_by = 100)) |>
 	tab_spanner("# Phonemes", matches("nphon")) |>
 	tab_spanner("Frequency (Zipf)", matches("freq")) |>
-	tab_spanner("Phon. similarity [0-1]", matches("lv")) |>
-	fmt_number(is.numeric, decimals = 1) |>
+	tab_spanner("Familiarity (%)", matches("familiarity")) |>
+	fmt_number(is.numeric, decimals = 2) |>
+	fmt_number(matches("familiarity"), decimals = 2, scale_by = 100) |> 
 	cols_merge(c(freq_prime_mean, freq_prime_sd),
@@
 	cols_merge(c(freq_target_mean, freq_target_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(familiarity_prime_mean, familiarity_prime_sd),
+			   pattern = "{1} ({2})") |>
+	cols_merge(c(familiarity_target_mean, familiarity_target_sd),
 			   pattern = "{1} ({2})") |>
@@
 			   pattern = "{1} ({2})") |>
-	cols_merge(c(lv_pp_mean, lv_pp_sd),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(lv_pt_mean, lv_pt_sd),
-			   pattern = "{1} ({2})") |>
-	cols_merge(c(duration_mean, duration_sd),
-			   pattern = "{1} ({2})") |>
 	cols_label(trial_type = "",
+			   familiarity_prime_mean = "Prime",
+			   familiarity_target_mean = "Target",
 			   freq_prime_mean = "Prime",
 			   freq_target_mean = "Target",
-			   lv_pp_mean = "Prime-Prime",
-			   lv_pt_mean = "Prime-Target",
-			   duration_mean = "Duration (s)",
 			   nphon_prime_mean = "Prime",
 			   nphon_target_mean = "Target") |>
-	tab_style(cell_text(style = "italic"),
+	tab_style(list(cell_text(style = "italic")), 
 			  list(cells_column_labels(),
@@
 &\textbf{Target looking by participant } i \textbf{ in session } j \\
-y_{ij} &\sim \mathcal{N}(\mu_{ij}, \sigma_{ij}) \\ \\
+y_{ij} &\sim \mathcal{N}(\mu_{ij}, \sigma_{ij}) \\\\
 &\textbf{Distributional parameters:} \\
@@
 					   breaks = seq(0, 1e3, 100)) +
-	scale_x_continuous(breaks = seq(0, 50, 2)) +
 	theme(panel.grid.major.y = element_line(linetype = "dotted",
@@
 The auditory stimuli were natural exemplars of the selected target words, spoken by a proficient female bilingual speaker of Catalan (Central variety) and Castilian Spanish, who was instructed to pronounce each word in a toddler-directed manner.
+Catalan audios had an average duration of `r durations$catalan$duration_mean` ms (*SD* = `r durations$catalan$duration_sd`, *Range* = `r durations$catalan$duration_min`--`r durations$catalan$duration_max`), and Spanish audios had an average duration of  `r durations$spanish$duration_mean` ms (*SD* = `r durations$spanish$duration_sd`, *Range* = `r durations$spanish$duration_min`--`r durations$spanish$duration_max`).
 New visual stimuli were created to accommodate the words included in the new stimuli lists, and possible cultural differences in the typicality of the exemplars shown in the pictures (see Appendix A for a detailed description of the stimuli).
@@
 	mutate(condition = if_else(role=="target", 
-							   "", condition)) |> 
+							   "related/unrelated", condition)) |> 
 	summarise(aoa_sd = sd(aoa, na.rm = TRUE),
@@
 	mutate(condition = if_else(role=="target", 
-							   "", condition)) |> 
+							   "related/unrelated", condition)) |> 
 	ggplot(aes(condition, freq, colour = study, fill = study)) +
@@
 			  position = position_dodge(width = 1),
-			  alpha = 1/5) +
+			  alpha = 1/3) +
 	stat_summary(geom = "errorbar",
@@
 		 colour = "Study",
-		 fill = "Study",
 		 fill = "Study") +
@@
 	mutate(condition = if_else(role=="target", 
-							   "", condition)) |> 
+							   "related/unrelated", condition)) |> 
 	ggplot(aes(condition, aoa, colour = study, fill = study)) +
@@
 This study tested a cohort of monolingual German infants in a word recognition task, in which participants in which participants were presented with auditory primes and targets, which were phonologically related or unrelated.
-The authors estimated participants' receptive vocabulary sizes using the *Fragebogen zur frühkindlichen Sprachentwicklung* [szagun2009fragebogen], an adaptation of the CDI to German.
+The authors estimated participants' receptive vocabulary sizes using the *Fragebogen zur frühkindlichen Sprachentwicklung* [@szagun2009fragebogen], an adaptation of the CDI to German.
 Their cohort of participants showed receptive vocabulary sizes larger than those of participants in the present study.

### 2023-12-13 index.qmd
Built site for gh-pages

@@
----
-title: "Cognate Priming"
-subtitle: "Lab notes"
-date: "Updated: `r format(Sys.Date(), '%Y/%m/%d')`"
-authors:
-  - name: Gonzalo Garcia-Castro
-    orcid: 0000-0002-8553-4209
-    email: gonzalo.garciadecastro@upf.edu
-    corresponding: true
-    affiliations:
-      - name: Universitat Pompeu Fabra
-        department: Center for Brain and Cognition
-        address: Ramon Trias fargas 25-27
-        city: Barcelona
-        state: Spain
-        postal-code: 08005
-abstract: "Previous studies have provided evidence that lexical access is language non-selective in bilinguals: recognising and producing words in one language activates lexical representations of words in the other language (e.g., Costa et al., 2000; Thierry & Wu, 2007).
-It has been suggested that this parallel activation is already present during toddlerhood (Jardak & Byers-Heinlein, 2019; Von Holzen & Mani, 2012), but it is unclear how it impacts the developing lexicon.
-In the present study, we tested Catalan-Spanish and English-Spanish bilinguals in a word recognition task, in which they were presented with words in their dominant language exclusively.
-In each trial, two pictures were presented side-by-side and one of them was named (target picture).
-Participants' visual preference for the named picture was taken as an indicator of word recognition.
-Each pair of pictures was preceded by the presentation of a silent image (prime picture).
-We designed three types of trials: (1) cognate trials in which prime and target labels shared phonological onset and the prime label was a cognate (e.g., flower-flor / fork), (2) non-cognate trials, in which prime and target labels shared phonological onset but the prime label was a non-cognate (e.g., frog-rana / fork), and (3) unrelated trials, in which prime and target labels did not share onset (unrelated trials; car-coche / fork).
-In line with previous studies, we expected participants to generate implicit labels for the prime pictures, which should interfere with target word recognition when both words share phonological onset (e.g., Mani & Plunkett, 2011).
-Additionally, under the hypothesis that bilingual participants would activate labels for the prime pictures in both languages, we predicted that interference would be stronger after cognate primes (labels from both languages share phonological overlap with target word recognition) than after non-cognate primes (only the label in the target language share phonological overlap with target word recognition).
-We tested bilinguals (n = 46) and same-aged monolingual controls, n = 123) at three age points (21, 25, and 30 months) to investigate how any cross-language priming effect emerged or changed across these ages."
-format:
-    html:
-        link-external-newwindow: true
-        number-offset: 0
-        code-fold: true
-        code-overflow: scroll
-        code-line-numbers: true
-        code-copy: hover
-        reference-location: margin
-        execute-dir: "C:/Users/U155880/Documents/trajectories/"
-    pdf: default
-    docx:
-        reference-doc: reference.docx
-fig-dpi: 1000
-warning: false
-echo: false
-toc: true
-colorlinks: true
-number-sections: true
-bibliography: "references.bib"
-csl: "apa7.csl"
----
+```{r setup}
+#| label: setup
+#| echo: false
+#| message: false
+#| warning: false
+# load objects
+# targets::tar_config_set(store = here::here("_targets"),
+# 						script = here::here("_targets.R"))
 
-```{r}
-#| label: setup
-tar_load_globals()
-tar_load_everything()
+targets::tar_load(
+	c(participants,
+	  stimuli,
+	  vocabulary,
+	  attrition_trials,
+	  attrition_participants,
+	  bvq_data,
+	  gaze_aoi,
+	  data_time,
+	  data_aggr
+	))
+
+targets::tar_load(
+	c(model_fits_aggr,
+	  model_fits_time,
+	  model_loos_aggr,
+	  model_loos_time
+	))
+
+# prepare data
+attrition <- lst(participants,
+				 attrition_participants,
+				 attrition_trials) |> 
+	reduce(inner_join, by = join_by(session_id)) |> 
+	unnest_wider(matches("all"), names_sep = "_")
+
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(gt)
+library(patchwork)
+library(english)
+library(gtExtras)
 
 # set ggplot theme and colour palette
-theme_set(theme_custom()) # set custom ggplot theme
+
+my_theme <- theme_minimal() +
+	theme(panel.grid = element_blank(),
+		  axis.line = element_line(colour = "black"),
+		  text = element_text(size = 12, colour = "black"),
+		  axis.text = element_text(colour = "black"))
+
+theme_set(my_theme)
+
 clrs <- c("#003f5c", "#58508d", "#bc5090", "#ff6361", "#ffa600")
 
-options(
-	ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
+options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
 		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
@@
 		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
-	ggplot2.continuous.colour = ggplot2::scale_color_gradient
-)
+		ggplot2.continuous.colour = ggplot2::scale_color_gradient)
 
-# prepare data
-attrition <- attrition %>% 
-	mutate(
-		valid_gaze = valid_gaze_prime & valid_gaze_target,
-		valid_status = case_when(
-			!valid_gaze ~ "Invalid gaze",
-			!valid_participant ~ "Invalid participant",
-			TRUE ~ "Valid"
-		))
-
-participants <- participants %>% 
-	left_join(distinct(attrition, id, age_group, valid_participant)) %>% 
-	drop_na(id) %>% 
-	left_join(vocabulary) %>% 
-	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
+set.seed(888)
 
@@
 
-# Methods
+# Participants
 
-## Participants
-
-```{r}
-#| label: participants-numbers
-n_participants_total <- length(unique(participants$id))
-n_participants_sessions <- count(participants, id, name = "n_sessions") %>% 
-	count(n_sessions) %>% 
-	split(.$n_sessions)
-n_sessions_total <- count(participants)
-n_sessions_age_group <- participants %>% 
-	group_by(age_group) %>% 
-	summarise(across(age, lst(mean, sd, min, max)),
-			  n = n(),
-			  .groups = "drop") %>% 
-	mutate(across(age_mean:age_max, round, 2)) %>% 
-	split(f = .$age_group) %>% 
-	set_names(c("age_21", "age_25", "age_30"))
-n_sessions_dominance <- count(participants, test_language) %>% 
-	split(f = .$test_language) %>% 
-	set_names(c("catalan", "spanish"))
-n_sessions_dominance_age_group <- count(participants, age_group, test_language) %>% 
-	split(f = .$test_language) %>% 
-	set_names(c("catalan", "spanish")) %>% 
-	map(~split(., f = .$age_group) %>% 
-			set_names(c("age_21", "age_25", "age_30")))
-n_sessions_lp <- participants %>% 
-	count(lp) %>% 
-	split(f = .$lp) %>% 
-	set_names(c("monolingual", "bilingual"))
-n_sessions_lp_age_group <- participants %>% 
-	count(lp, age_group) %>% 
-	split(f = .$lp) %>% 
-	set_names(c("monolingual", "bilingual")) %>% 
-	map(~split(., f = .$age_group) %>% 
-			set_names(c("age_21", "age_25", "age_30")))
+```{r tbl-participants}
+#| label: tbl-partiicpants
+#| tbl-cap: "Demographic and linguistic profile of participants."
+participants |> 
+	unnest_wider(doe) |> 
+	select(-matches("others")) |> 
+	mutate(lp = case_when(
+		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
+		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
+		.default = lp)) |> 
+	arrange(desc(lp)) |> 
+	summarise(n = n(),
+			  across(age, lst(mean, sd, min, max)),
+			  across(matches("doe_"), lst(mean, sd)),
+			  age_vctr = list(age),
+			  .by = c(lp, test_language)) |> 
+	gt(rowname_col = "test_language",
+	   groupname_col = "lp") |> 
+	gt_plt_dist(age_vctr, type = "histogram") |> 
+	fmt_number(is.numeric, decimals = 1) |> 
+	fmt_integer(n) |> 
+	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
+	cols_merge_range(age_min, age_max) |> 
+	cols_merge(c(age_mean, age_sd), pattern = "{1} ({2})") |> 
+	cols_merge(c(age_mean, age_sd), pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_catalan_mean, doe_catalan_sd), pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_english_mean, doe_english_sd), pattern = "{1} ({2})") |> 
+	cols_merge(c(doe_spanish_mean, doe_spanish_sd), pattern = "{1} ({2})") |> 
+	tab_spanner("Age (months)", matches("age")) |> 
+	tab_spanner("Catalan", matches("catalan")) |> 
+	tab_spanner("English", matches("english")) |> 
+	tab_spanner("Spanish", matches("spanish")) |> 
+	tab_spanner("Degree of Exposure (%)", matches("doe")) |> 
+	cols_label(n = "N",
+			   age_mean = "M (SD)",
+			   age_min = "Range",
+			   age_vctr = "Distribution",
+			   doe_catalan_mean = "M (SD)",
+			   doe_english_mean = "M (SD)",
+			   doe_spanish_mean = "M (SD)") |> 
+	tab_style(cell_text(style = "italic"),
+			  cells_column_labels()) |> 
+	tab_style(cell_text(weight = "bold"),
+			  cells_column_spanners())
 ```
 
-We collected data from `r n_participants_total` monolingual and bilingual participants living in the Metropolitan Area of Barcelona (Spain), who were exposed to at least Catalan and/or Spanish from birth.
-Families were recruited from maternity room in private hospitals in Barcelona, and contacted via phone when the child's age spanned between our age intervals of interest.
-Families were invited to participate at three age points: 21, 25, and 30 months.
-`r n_participants_sessions[[1]]$n` participants were tested at one age point,  `r n_participants_sessions[[2]]$n` at two age points, and `r n_participants_sessions[[3]]$n` at the three age points.
-In total, we gathered data from `r n_sessions_total$n` testing sessions: `r n_sessions_age_group$age_21$n` at 21 months (*Mean* = `r round(n_sessions_age_group$age_21$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_21$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_21$age_min`--`r n_sessions_age_group$age_21$age_max`), `r n_sessions_age_group$age_25$n` at 25 months (*Mean* = `r round(n_sessions_age_group$age_25$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_25$age_min`--`r n_sessions_age_group$age_25$age_max`), and `r n_sessions_age_group$age_30$n` at 30 months (*Mean* = `r round(n_sessions_age_group$age_30$age_mean, 2)`, *SD* = `r round(n_sessions_age_group$age_25$age_sd, 2)`, *Range* = `r n_sessions_age_group$age_30$age_min`--`r n_sessions_age_group$age_30$age_max`).
+# Vocabulary size
 
-We assessed participants' language profile using the Language Exposure Questionnaire [LEQ, @bosch2001evidence].
-Before each experimental session, the experimenter asked the caretakers to estimate the amount of hours per day they and other people in the infant's social circle have spent speaking to the infant in any language since birth.
-The output of this interview is an estimated degree of exposure (DoE) to each language, indicated by the proportion of time the infant was reported to have listened to each language.
-According to this estimate, we classified participants as Catalan- or Spanish-dominant if the language with highest DoE was Catalan or Spanish, respectively, and tested the participant in the stimuli set that contained words in their native language.
-We collected data from `r n_sessions_dominance$catalan$n` Catalan-dominant participants in Catalan (`r n_sessions_dominance_age_group$catalan$age_21$n` at 21 months, `r n_sessions_dominance_age_group$catalan$age_25$n` at 25 months, and `r n_sessions_dominance_age_group$catalan$age_30$n` at 30 months).
-We further classified participants as monolinguals if the DoE to their dominant language exceeded 80% of the total DoE to Catalan and Spanish, and as bilinguals otherwise.
-Participants with DoE to language other than Catalan or Spanish were excluded from analyses.
-This divided the sample into `r n_sessions_lp$monolingual$n` monolinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$monolinguals$age_25` at 25 months, and `r n_sessions_lp_age_group$monolinguals$age_30` at 30 months), and `r n_sessions_lp$bilingual$n` bilinguals (`r n_sessions_lp_age_group$monolinguals$age_21` at 21 months, `r n_sessions_lp_age_group$bilingual$age_25` at 25 months, and `r n_sessions_lp_age_group$bilingual$age_30` at 30 months).
-tbl-participants-lp summarises the linguistic profile of our sample.
-
-```{r}
-#| label: tbl-participants-lp
-#| tbl-cap: "Description of language profile of participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
-participants %>% 
-	select(id, age_group, age, lp, doe_catalan, doe_spanish, test_language) %>% 
-	mutate(id = paste0(id, " (", age_group, ")")) %>%
-	add_count(lp, name = "n_lp") %>% 
-		add_count(age_group, name = "n_age_group") %>%
-
-	pivot_longer(starts_with("doe_"), names_to = "language", values_to = "doe") %>%
-	add_count(age_group, test_language, name = "n_age_test") %>% 
-	mutate(language = str_remove_all(language, "doe_") %>% 
-		   	str_to_sentence(),
-		   age_group = paste0(age_group, " (N = ", n_age_group, ")"),
-		   test_language = paste0("Tested in ", test_language, " (N = ", n_age_test, ")"),
-		   lp = factor(lp, levels = rev(unique(lp))))  %>% 
-	group_by(age_group, lp, test_language, language) %>% 
-	summarise(across(doe, lst(mean, sd)),
-			  .groups = "drop") %>% 
-	pivot_wider(id_cols = c(age_group, test_language),
-				names_from = c(language, lp),
-				values_from = c(matches("doe"))) %>% 
-	clean_names() %>% 
-	relocate(age_group, test_language,
-			 matches("catalan"),
-			 matches("spanish")) %>% 
-	gt(rowname_col = "test_language", 
-	   groupname_col = "age_group", row_group.sep = ": ") %>% 
-	tab_spanner(md("Monolingual (*N* = 162)"), matches("monolingual")) %>% 
-	tab_spanner(md("Bilingual (*N* = 133)"), matches("bilingual")) %>%
-	fmt_number(matches("doe"), decimals = 1, scale_by = 100) %>% 
-	cols_merge_uncert(col_val = doe_mean_catalan_monolingual,
-					  col_uncert = doe_sd_catalan_monolingual) %>% 
-	cols_merge_uncert(col_val = doe_mean_catalan_bilingual,
-					  col_uncert = doe_sd_catalan_bilingual) %>% 
-	cols_merge_uncert(col_val = doe_mean_spanish_monolingual, 
-					  col_uncert = doe_sd_spanish_monolingual) %>% 
-	cols_merge_uncert(col_val = doe_mean_spanish_bilingual, 
-					  col_uncert = doe_sd_spanish_bilingual) %>%
-
-	cols_label(doe_mean_catalan_monolingual = "Catalan (%)",
-			   doe_mean_catalan_bilingual = "Catalan (%)",
-			   doe_mean_spanish_monolingual = "Spanish (%)",
-			   doe_mean_spanish_bilingual = "Spanish (%)") %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners())) %>% 
-	tab_style(cell_text(size = "small"),
-			  list(cells_body(),
-			  	 cells_stub()))
-```
-
-The research reported in this article was conducted in accordance with the principles expressed in the Declaration of Helsinki and approved by the local ethical committee (the clinical research ethical committee of the Parc de la Salut Mar).
-Before every testing session, caretakers were asked to read and sign an informed consent form, and were given a small gift at the end of it.
-
-## Stimuli
-
-### Animacy
-
-```{r}
-#| label: fig-stimuli-animacy
-#| fig-height: 6
-animacy <- stimuli %>%
-	distinct(test_language, 
-			 target, 
-			 prime, 
-			 .keep_all = TRUE) %>% 
-	pivot_longer(c(is_animate_prime, is_animate_target), 
-				 names_to = "role",
-				 values_to = "is_animate") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "is_animate_"))) %>% 
-	count(test_language,  trial_type, role, is_animate) %>% 
-	drop_na(is_animate) %>% 
-	mutate(is_animate = ifelse(is_animate, "Animate", "Inanimate"))
-
-animacy %>% 
-	# filter(role=="Prime") %>% 
-	ggplot() +
-	aes(x = trial_type, 
-		y = n, 
-		fill = is_animate,
-		colour = is_animate) + 
-	facet_grid(test_language~role) +
-	geom_col(position = position_fill(), colour = "white", size = 0.75) +
-	geom_hline(yintercept = 0.5,  size = 1, colour = "grey") +
-	labs(title = "Prime", 
-		 x = "Trial type", 
-		 y = "# trials",
-		 colour = "Animacy", 
-		 fill = "Animacy") +
-	scale_y_continuous(labels = percent) +
-	coord_flip() + 
-	theme(legend.position = "top",
-		  legend.title = element_blank(),
-		  panel.grid = element_blank(),
-		  axis.title.y = element_blank(),
-		  axis.text = element_text(size = 7),
-		  axis.text.y = element_text(hjust = 1),
-		  strip.text = element_text(size = 11))
-```
-
-### Semantic category
-
-```{r}
-#| label: fig-stimuli-category 
-#| fig-height: 7
-#| fig-width: 12
-stimuli %>% 
-	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
-	pivot_longer(c(semantic_category_prime, semantic_category_target),
-				 names_to = "role",
-				 values_to = "semantic_category") %>% 
-	mutate(role = str_to_sentence(str_remove(role, "semantic_category_"))) %>% 
-	drop_na(trial_type, semantic_category) %>% 
-	count(trial_type, test_language, role, semantic_category, name = "sum") %>% 
-	right_join(expand(., trial_type,  test_language,  role,  semantic_category)) %>%
-	replace_na(list(sum = 0)) %>% 
-	group_by(trial_type, test_language, role) %>% 
-	mutate(n =  sum(sum), prop = sum/n) %>% 
-	ungroup() %>% 
-	ggplot() +
-	aes(x = prop,
-		y = reorder_within(semantic_category, 
-						   desc(prop), 
-						   list(trial_type, role, test_language)),
-		fill = test_language,
-		order = prop) + 
-	facet_wrap(trial_type~role~test_language,
-			   scales = "free_y",
-			   labeller = label_wrap_gen(multi_line = FALSE)) +
-	geom_col(colour = "white",
-			 position = position_dodge(),
-			 width = 1) +
-	labs(x = "% of trials",
-		 y = "Trial type",
-		 colour = "Trial type",
-		 fill = "Trial type") +
-	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
-	scale_y_reordered() +
-	theme(legend.position = "none",
-		  legend.title = element_blank(),
-		  axis.text.y = element_text(size = 9, hjust = 1),
-		  axis.text.x = element_text(size = 8, hjust = 1),
-		  axis.title.y = element_blank(),
-		  axis.ticks.y = element_blank(),
-		  plot.caption = element_text(size = 10, hjust = 0),
-		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
-		  strip.text = element_text(size = 10))
-```
-
-## Vocabulary
-
-We collected vocabulary data from participants.
-In Oxford, participants were sent the online version of the Oxford Communicative Development Inventory [OCDI; @hamilton2000] two weeks before each appointment.
-In Barcelona, participants were sent the online vocabulary inventory [BVQ](https://github.com/gongcastro/bvqdev) immediately after the appointment, and were given two weeks to fill it.
-In Oxford, families filled the vocabulary checklist in the testing language, and when the participant was monolingual, also in the second language.
-In Barcelona, all participants filled the Catalan and the Spanish versions of the vocabulary checklists.
-All checklists included the words involved in the trial lists.
-When filling the vocabulary checklist, families checked each word as being *understood*, *understood and produced* or *none*.
-Each response to either checklist was aggregated to produce several vocabulary measures:
-
-* **Total vocabulary**: total number of words the child knows, summing up both languages.
-For instance, a child who knows 210 words in Catalan and 100 words in Spanish would have a total vocabulary size of 210 words.
-* **L1 vocabulary**: number of words the child knows in the languages of higher exposure (i.e., testing language).
-For instance, for a child exposed to 75% Catalan who knows 210 words in Catalan and 100 words in Spanish, their L1 vocabulary size would be 210 words.
-* **Conceptual vocabulary**: number of lexicalised concepts, that is, the number of concepts for which the child knows a word in at least one of the languages.
-For example, a Catalan-Spanish bilingual that knows *taula* and *mesa* -- Catalan and Spanish translations of *table*-- would have a conceptual vocabulary size of 1.
-
-Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm 1$ month) and language profile (similar exposure to a second language, $\pm 10%$) that completed the same vocabulary checklist previously.
-
-### L1 vocabulary
-
-This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis.
-Results are presented separately for each age group.
-The shape of the violins, represents the distribution of the vocabulary sizes.
-The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values.
-vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure.
-for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.
-
-```{r}
-#| label: fig-vocabulary-l1
-#| fig-cap: "L1 vocabulary. Percentage of words in L1 reported to be understood from the vocabulary checklist."
-#| fig-height: 4
-sample_size <- participants %>% 
-	filter(id %in% fit_0$data$id) %>% 
-	count(age_group)
-
-sample_size_lp <- participants %>% 
-	filter(id %in% fit_0$data$id) %>% 
-	count(age_group, lp) %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		)
-	)
-
-# vocabulary
-participants %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		),
-		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
-							levels = c("Observed", "Imputed"))
-	) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot(aes(lp,  vocab_size_l1, colour = is_imputed, fill = is_imputed)) +
-	facet_wrap(~age_group, scales = "free_x") +
-	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(width = 0.15, size = 1, colour = "black",
-				 fill = "white", outlier.colour = NA,
-				 position = position_nudge(x = 0.3)) +
-	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
-	geom_text(data = sample_size_lp,
-			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
-			  colour = "black", show.legend = FALSE, 
-			  position = position_dodge(width = 2), inherit.aes = FALSE) +
-	labs(y = "Receptive vocabulary", 
-		 colour = "Imputed", 
-		 fill = "Imputed") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(legend.position = "top", 
-		  legend.title = element_blank(),
-		  panel.grid.major.x = element_blank(),
-		  axis.title.x = element_blank(),
-		  axis.text = element_text(size = 9))
-```
-
-### Total vocabulary
-
-```{r}
-#| label: fig-vocabulary-total
-#| fig-cap: "Total vocabulary"
-#| fig-height: 4
-# vocabulary
-participants %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		),
-		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
-							levels = c("Observed", "Imputed"))
-	) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot(aes(lp,  vocab_size_total, colour = is_imputed, fill = is_imputed)) +
-	facet_wrap(~age_group, scales = "free_x") +
-	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(width = 0.15, size = 1, colour = "black",
-				 fill = "white", outlier.colour = NA,
-				 position = position_nudge(x = 0.3)) +
-	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
-	geom_text(data = sample_size_lp,
-			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
-			  colour = "black", show.legend = FALSE, 
-			  position = position_dodge(width = 2), inherit.aes = FALSE) +
-	labs(y = "Receptive vocabulary", 
-		 colour = "Imputed", 
-		 fill = "Imputed") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(legend.position = "top", 
-		  legend.title = element_blank(),
-		  panel.grid.major.x = element_blank(),
-		  axis.title.x = element_blank(),
-		  axis.text = element_text(size = 9))
-```
-
-### Conceptual vocabulary
-
-```{r}
-#| label: fig-vocabulary-conceptual
-#| fig-height: 4
-participants %>% 
-	mutate(
-		age_group = case_when(
-			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
-			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
-			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
-		),
-		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
-							levels = c("Observed", "Imputed"))
-	) %>% 
-	drop_na(lp) %>%
-	filter(valid_participant) %>% 
-	ggplot(aes(lp,  vocab_size_conceptual, colour = is_imputed, fill = is_imputed)) +
-	facet_wrap(~age_group, scales = "free_x") +
-	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
-	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
-			  position = position_nudge(x = 0.3)) +
-	geom_boxplot(width = 0.15, size = 1, colour = "black",
-				 fill = "white", outlier.colour = NA,
-				 position = position_nudge(x = 0.3)) +
-	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
-	geom_text(data = sample_size_lp,
-			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
-			  colour = "black", show.legend = FALSE, 
-			  position = position_dodge(width = 2), inherit.aes = FALSE) +
-	labs(y = "Receptive vocabulary", 
-		 colour = "Imputed", 
-		 fill = "Imputed") +
-	scale_y_continuous(limits = c(0, 1), labels = percent) +
-	theme(legend.position = "top", 
-		  legend.title = element_blank(),
-		  panel.grid.major.x = element_blank(),
-		  axis.title.x = element_blank(),
-		  axis.text = element_text(size = 9))
-```
-
-## Design
-
-## Data analysis
-
-```{r} 
-#| label: tbl-attrition-group
-#| tbl-cap: "Summary of the dataset."
-attrition %>% 
-	left_join(select(participants, age_group, lp, id, date_test)) %>% 
-	add_count(age_group, lp, name = "n_trials") %>% 
-	group_by(id, lp, trial_type, date_test, age_group, valid_participant, n_trials) %>% 
-	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
-			  .groups = "drop") %>% 
-	pivot_wider(names_from = trial_type, values_from = valid_trial_count, values_fill = 0) %>% 
-	clean_names() %>% 
-	add_count(lp, age_group) %>%
-	group_by(lp, age_group, n, n_trials) %>% 
-	summarise(across(cognate:unrelated, lst(sum, mean, sd)),
-			  n_valid = sum(valid_participant),
-			  .groups = "drop") %>%
-	relocate(n_valid, .after = n) %>% 
-	mutate(n_prop = n_valid/n) %>% 
-	arrange(age_group, lp) %>% 
-	relocate(age_group, lp, n_valid, n_prop, matches("cognate"), matches("non_cognate"), matches("unrelated")) %>% 
-	gt(groupname_col = "age_group", rowname_col = "lp")  %>%
-	cols_hide(c(n, n_trials)) %>% 
-	fmt_number(matches("_mean|_sd"), decimals = 1) %>%
-	fmt_percent(matches("_prop"), decimals = 1) %>% 
-	cols_merge_n_pct(col_n = n_valid, col_pct = n_prop, autohide = TRUE)  %>% 
-	tab_spanner("Non-cognate", matches("non_cognate")) %>%
-	tab_spanner("Cognate", starts_with("cognate")) %>%
-	tab_spanner("Unrelated", matches("unrelated")) %>%
-	tab_spanner("Related", matches("cognate")) %>%
-
-	cols_merge_uncert(col_val = cognate_mean, col_uncert = cognate_sd) %>% 
-	cols_merge_uncert(col_val = non_cognate_mean, col_uncert = non_cognate_sd) %>% 
-	cols_merge_uncert(col_val = unrelated_mean, col_uncert = unrelated_sd) %>% 
-	cols_label(age_group = "Age",
-			   n_valid = "Participants (included)",
-			   cognate_sum = "Trials",
-			   cognate_mean = "Mean ± SD",
-			   non_cognate_sum = "Trials",
-			   non_cognate_mean = "Mean ± SD",
-			   unrelated_sum = "Trials",
-			   unrelated_mean = "Mean ± SD") %>% 
-	summary_rows(groups = TRUE,
-				 columns = where(is.integer), 
-				 fns = list("Sum" = ~sum(.)), 
-				 formatter = fmt_number,
-				 decimals = 0) %>% 
-	summary_rows(groups = TRUE,
-				 columns = c(where(is.numeric), -n_valid), 
-				 fns = list("Mean" = ~mean(.)),
-				 formatter = fmt_number,
-				 decimals = 1) %>% 
-	grand_summary_rows(columns = where(is.integer),
-					   fns = list("N" = ~sum(.)),
-					   formatter = fmt_number,
-					   decimals = 0) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary())) 
-```
-
-**Parameters**:
-
-$$
-\begin{align}
-y_{ij} =&~ (\beta_{0} + \beta_{0p} + \beta_{0i}) ~+~ ... \\ 
-& (\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} ~+~ ... \\
-& (\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} ~ + ~ ... \\
-& (\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} ~ + ~ ... \\
-& (\beta_{4} + \beta_{4i}) \times Group_{pi} ~+~ ... \\
-& (\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) ~+~ ... \\
-& (\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) ~+~ ... \\
-& (\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) ~+~ ... \\
-& (\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) ~+~ \\ & \sigma^2_{e}
-\end{align}
-$$
-
-**Priors**:
-
-$$
-\begin{align}
-\beta_0 \sim~ & \mathcal{N}(0, 1) \\
-\beta_{1-8} \sim~ &\mathcal{N}(0, 1) \\
-\sigma_m, ~\sigma^2,~ \sigma^2_p,~ \sigma^2_i \sim~ & exp(2) \\
-\rho \sim ~&  LKJ(2)
-\end{align}
-$$
-
-### Prior expected predicted mean
-
-```{r}
-#| label: fig-prior-epred
-nd <- tibble(time_bin = seq(0, 20, 0.1)) %>% 
-	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)
-
-m <- add_epred_draws(nd, fit_prior, ndraws = 50, re_formula = NA) %>% 
-	mutate(.epred = plogis(.epred))
-
-ggplot(m, aes(time_bin, .epred)) +
-	geom_hline(yintercept = 0.5, colour = "grey", size = 1) +
-	geom_line(aes(group = .draw), colour = clrs[4], size = 1, alpha = 0.5) +
-	labs(x = "Time (ms)",
-		 y = "Proportion of target looking time") +
-	scale_y_continuous(labels = percent) +
-	scale_x_continuous(labels = function(x) format(x*100, big.mark = ","))
+```{r tbl-vocabulary}
+#| label: tbl-vocabulary
+#| tbl-cap: "Participant vocabulary sizes across ages and language profiles.
+Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages).
+Vocabulary size scores from the recurrent participants are shown linked."
+#| eval: false
+vocabulary |> 
+	inner_join(select(participants, child_id, session_id, age, lp),
+			   by = join_by(child_id, session_id)) |> 
+	pivot_longer(c(total_prop, l1_prop),
+				 names_to = "measure",
+				 values_to = "prop",
+				 names_transform = \(x) gsub("_prop", "", x)) |> 
+	mutate(lp = case_when(
+		lp=="Monolingual" ~ "Monolingual (Catalan or Spanish)",
+		lp=="Bilingual" ~ "Bilingual (Catalan-Spanish)",
+		.default = lp) |> 
+			factor(levels = c("Monolingual (English)",
+							  "Monolingual (Catalan or Spanish)",
+							  "Bilingual (Catalan-Spanish)")),
+		measure = if_else(measure=="l1", 
+						  "L1 vocabulary", 
+						  "Total vocabulary"),
+		is_imputed = if_else(is_imputed, "Imputed", "Observed") |> 
+			factor(levels = c("Observed", "Imputed"))) |> 
+	ggplot(aes(age, prop, colour = is_imputed)) +
+	facet_grid(measure ~ lp) +
+	geom_line(aes(group = child_id),
+			  alpha = 1/2,
+			  colour = "grey") +
+	geom_point() +
+	labs(x = "Age (months)",
+		 y = "Vocabulary size (%)") +
+	theme(panel.grid = element_line(linetype = "dotted",
+									colour = "grey"),
+		  legend.position = "right",
+		  legend.title = element_blank())
 ```
@@
 
-## Attrition
+## Observed data
 
-::: {.tabset-panel}
+## Model-based estimates
 
-### By participants
+### Aggregated analyses
 
-```{r}
-#| label: fig-attrition-participants
-#| fig-height: 4
-n_text <- participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(
-		valid_status = case_when(
-			valid_participant & !is_imputed ~ "Valid (observed CDI)",
-			valid_participant & is_imputed ~ "Valid (imputed CDI)",
-			!valid_participant ~ "Excluded"
-		)
-	) %>% 
-	filter(valid_status != "Excluded") %>% 
-	count(lp, age_group) %>% 
-	mutate(n_label = paste0(n, " valid"),
-		   valid_status = "Valid (observed CDI)")
+```{r fig-related-aggregated}
+#| label: fig-related-aggregated
+#| fig-cap: "A) Aggregated probability of target looking for related and unrelated trials.
+Each point represents the mean probability of target looking for one participant in one testing session.
+Lines link observations from the same testing session across conditions.
+Black dots and errorbars indicate the mean and 95% CrI.
+B) Aggregated probability of target looking across ages for related and unrelated trials.
+Lines and error bands indicate the mean and standard error of the mean."
+plot_agg_epreds <- function(newdata, object) {
 
-participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	left_join(vocabulary) %>% 
-	drop_na(valid_participant) %>% 
-	mutate(valid_status = case_when(
-		valid_participant & !is_imputed ~ "valid_cdi_observed",
-		valid_participant & is_imputed ~ "valid_cdi_imputed",
-		!valid_participant ~ "excluded")) %>% 
-	add_count(age_group, lp, name = "n_total") %>% 
-	count(age_group, lp, n_total, valid_status) %>% 
-	pivot_wider(names_from = valid_status, values_from = n, values_fill = 0) %>% 
-	relocate(age_group, lp, n_total, valid_cdi_observed, valid_cdi_imputed, excluded) %>% 
-	mutate(across(matches("valid_|excluded"), ~./n_total, .names = "{.col}_prop")) %>% 
-	gt(rowname_col = "lp", groupname_col = "age_group") %>% 
-	fmt_percent(matches("prop"), decimals = 1) %>% 
-	cols_merge_n_pct(col_n = valid_cdi_observed, col_pct = valid_cdi_observed_prop) %>% 
-	cols_merge_n_pct(col_n = valid_cdi_imputed, col_pct = valid_cdi_imputed_prop) %>% 
-	cols_merge_n_pct(col_n = excluded, col_pct = excluded_prop) %>% 
-	tab_spanner("Included participants", matches("valid")) %>% 
-	tab_spanner("Excluded participants", matches("excluded")) %>% 
-	cols_label(n_total = "N",
-			   valid_cdi_observed = "Collected CDI",
-			   valid_cdi_imputed = "Missing CDI",
-			   excluded = "") %>% 
-	summary_rows(groups = TRUE, columns = where(is.integer), 
-				 fns = list("N" = ~sum(.)),
-				 formatter = fmt_number,
-				 decimals = 0) %>% 
-	grand_summary_rows(columns = where(is.integer), 
-					   fns = list("N" = ~sum(.)),
-					   formatter = fmt_number,
-					   decimals = 0) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary()))
-```
+	epreds <- add_epred_draws(newdata = newdata,
+							  object = object,
+							  re_formula = NA)
+	return(mean_qi(epreds))
+}
 
-### By stimuli properties
+voc_values <- c(0.25, 0.5, 0.75, 1.00)
+age_values <- c(21, 25, 30)
 
-```{r}
-#| label: tbl-attrition-predictors
+nd_0 <- expand(data_aggr, lp, condition, age = age_values)
+nd_1 <- expand(data_aggr, lp, condition, voc_l1 = voc_values)
+nd_2 <- expand(data_aggr, lp, condition, voc_total = voc_values)
 
-attrition %>% 
-	left_join(distinct(stimuli, test_language, list, trial, trial_type,
-					   freq_target, freq_prime, familiarity_prime, familiarity_target)) %>% 
-	mutate(valid_status = ifelse(valid_status != "Valid",  "Excluded", valid_status)) %>% 
-	drop_na() %>% 
-	group_by(trial_type, valid_status, age_group) %>% 
-	summarise(n = n(),
-			  across(matches("freq_|familiarity_"),
-			  	   lst(mean, sd)),
-			  .groups = "drop") %>% 
-	pivot_wider(names_from = valid_status,
-				values_from = c(n, matches("freq_|familiarity_")),
-				values_fill = 0) %>%
-	clean_names() %>% 
-	relocate(age_group, trial_type, n_valid, n_excluded, 
-			 matches("_valid")) %>%
+epreds <- map2(.x = list(nd_0, nd_1, nd_2),
+			   .y = model_fits_aggr,
+			   .f = plot_agg_epreds) |> 
+	map(\(x) {
+		mutate(x, 
+			   across(matches("voc"),
+			   	   \(x) factor(x = x, 
+			   	   			levels = voc_values,
+			   	   			labels = scales::percent(voc_values))),
+			   across(matches("age"),
+			   	   \(x) factor(x = x,
+			   	   			levels = age_values,
+			   	   			labels = age_values)))
+	}) |> 
+	map(\(x) rename_with(x, \(x) gsub("age|voc_total|voc_l1", "var", x))) |> 
+	set_names(names(model_fits_aggr))
 
-	gt(rowname_col = "trial_type", groupname_col = "age_group") %>% 
-	fmt_number(matches("n_"), decimals = 0) %>% 
-	fmt_number(matches("freq_"), decimals = 1) %>% 
-	fmt_percent(matches("familiarity"), decimals = 1) %>% 
-	tab_spanner("N", matches("n_")) %>% 
-	tab_spanner("Prime familiarity", matches("familiarity_?prime_")) %>%
-	tab_spanner("Target familiarity", matches("familiarity_?target_")) %>% 
-	tab_spanner("Prime frequency", matches("freq_?prime_")) %>% 
-	tab_spanner("Target frequency", matches("freq_?target_")) %>%
+plot_epreds <- function(data, x) {
+	data |> 
+		ggplot(aes(var, .epred, 
+				   colour = condition,
+				   fill = condition)) +
+		facet_wrap(~lp, scales = "free_x") +
+		geom_hline(yintercept = 0,
+				   linetype = "dashed") +
+		geom_errorbar(aes(ymin = .lower,
+						  ymax = .upper),
+					  width = 0.5,
+					  linewidth = 3/4,
+					  position = position_dodge(width = 0.5)) +
+		geom_point(position = position_dodge(width = 0.5),
+				   size = 2)
+}
 
-	cols_merge_uncert(col_val = freq_prime_mean_valid, col_uncert = freq_prime_sd_valid) %>% 
-	cols_merge_uncert(col_val = freq_prime_mean_excluded, col_uncert = freq_prime_sd_excluded) %>% 
-	cols_merge_uncert(col_val = freq_target_mean_valid, col_uncert = freq_target_sd_valid) %>% 
-	cols_merge_uncert(col_val = freq_target_mean_excluded, col_uncert = freq_target_sd_excluded) %>%
-
-	cols_merge_uncert(col_val = familiarity_prime_mean_valid, col_uncert = familiarity_prime_sd_valid) %>% 
-	cols_merge_uncert(col_val = familiarity_prime_mean_excluded, col_uncert = familiarity_prime_sd_excluded) %>% 
-	cols_merge_uncert(col_val = familiarity_target_mean_valid, col_uncert = familiarity_target_sd_valid) %>% 
-	cols_merge_uncert(col_val = familiarity_target_mean_excluded, col_uncert = familiarity_target_sd_excluded) %>%
-
-	cols_label(n_excluded = "⨯",
-			   n_valid = "✓",
-			   freq_prime_mean_valid = "✓",
-			   freq_prime_mean_excluded = "⨯",
-			   freq_target_mean_valid = "✓",
-			   freq_target_mean_excluded = "⨯",
-			   familiarity_prime_mean_valid = "✓",
-			   familiarity_prime_mean_excluded = "⨯",
-			   familiarity_target_mean_valid = "✓",
-			   familiarity_target_mean_excluded = "⨯") %>% 
-	summary_rows(groups = TRUE,
-				 columns = matches("freq_") ,
-				 fns = list("Mean" = ~mean(.)), 
-				 formatter = fmt_number,
-				 decimals = 0) %>% 
-	summary_rows(groups = TRUE,
-				 columns = matches("familiarity_"), 
-				 fns = list("Mean" = ~mean(.)),
-				 formatter = fmt_percent,
-				 decimals = 1) %>% 
-	grand_summary_rows(columns = matches("n_"),
-					   fns = list("N" = ~sum(.)),
-					   formatter = fmt_number,
-					   decimals = 0) %>% 
-	tab_style(cell_text(align = "center"),
-			  cells_column_labels()) %>% 
-	tab_style(cell_text(weight = "bold"),
-			  list(cells_column_spanners(),
-			  	 cells_grand_summary(),
-			  	 cells_row_groups(),
-			  	 cells_stub_grand_summary(),
-			  	 cells_stub_summary()))
+plot_epreds(epreds$fit_aggr_0) +
+	labs(x = "Age (months)") +
+	plot_epreds(epreds$fit_aggr_1) +
+	labs(x = "L1 vocabulary size") +
+	theme(strip.text = element_blank()) +
+	plot_epreds(epreds$fit_aggr_2) +
+	theme(strip.text = element_blank()) +
+	labs(x = "Total vocabulary size") +
+	plot_layout(ncol = 1, guides = "collect") &
+	labs(y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition") &
+	theme(legend.position = "top",
+		  panel.grid.major.y = element_line(colour = "grey",
+		  								  linetype = "dotted"))
 
@@
 
-:::
+### Time course analyses
 
-## Descriptive statistics
+```{r fig-time-total}
+#| label: fig-time-total
+#| fig-height: 6
+#| fig-width: 8
+#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1.
+(A) Mean posterior probability of target looking across the time course of the trial.
+Black lines and intervals indicate the psoterior mean and 95% credible intervals.
+Points indicate the mean probability of target looking across participants.
+(B) Difference in posterior probability of target looking between *related* and *unrelated* trials.
+The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
+voc_values <- seq(0.25, 1, 0.25)
 
-### Aggregated target looking
+nd <- expand_grid(condition = levels(model_fits_time$fit_time_2$data$condition),
+				  timebin = seq(0, 17, length.out = 100),
+				  voc_total = voc_values,
+				  # sesion_id = first(data$session_id),
+				  # age = c(21, 25, 30),
+				  lp = levels(model_fits_time$fit_time_2$data$lp))
 
-```{r}
-#| label: fig-descriptives-aggregated
-df %>% 
-	group_by(id, lp, trial_type, age_group) %>%
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	geom_line(aes(group = id), alpha = 0.25) +
-	stat_slab(side = "right", scale = 0.5) +
-	geom_boxplot(width = 0.1, size = 0.75, fill = "white", colour = "black", outlier.colour = NA) +
-	labs(x = "Trial type", y = "Proportion of target looking", colour = "Trial type", fill = "Trial type") +
-	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
-	theme(legend.position = "none")
+epreds <- add_epred_draws(newdata = nd,
+						  object = model_fits_time$fit_time_2,
+						  ndraws = 20,
+						  re_formula = NA,
+						  value = ".value") |> 
+	mean_qi() |> 
+	mutate(lp = factor(lp, 
+					   levels = c("Monolingual (English)",
+					   		   "Monolingual",
+					   		   "Bilingual")),
+		   voc_total = factor(x = voc_total, 
+		   				   levels = voc_values,
+		   				   labels = scales::percent(voc_values)))
+
+epreds |> 
+	ggplot(aes(timebin, .value,
+			   colour = condition,
+			   fill = condition)) +
+	facet_grid(lp~voc_total) +
+	geom_hline(yintercept = 0,
+			   linetype = "dashed") +
+	geom_ribbon(aes(ymin = .lower, ymax = .upper),
+				alpha = 0.5,
+				linewidth = 0) +
+	geom_line(linewidth = 3/4) +
+	labs(x = "Time (ms)",
+		 y = "Logit (Target looking)",
+		 colour = "Condition",
+		 fill = "Condition") +
+	scale_x_continuous(breaks = seq(0, 20, 4),
+					   labels = \(x) format(x*100+200, big.mark = ",")) +
+	theme(legend.position = "top",
+		  panel.grid.major = element_line(colour = "grey",
+		  								linetype = "dotted"))
 ```
-
-### Time-course target looking
-
-```{r}
-#| label: fig-descriptives-time-course
-df %>% 
-	group_by(id, time_bin, lp, trial_type, age_group) %>%
-	summarise(prop = mean(prop), .groups = "drop") %>% 
-	ggplot(aes(time_bin, prop, colour = trial_type, fill = trial_type, shape = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
-	stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
-	stat_summary(fun = mean, geom = "point", size = 2) +
-	stat_summary(fun = mean, geom = "line", size = 0.75) +
-	labs(x = "Time bin (100 ms)", y = "Proportion of target looking",
-		 colour = "Trial type", fill = "Trial type", shape = "Trial type") +
-	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
-	scale_x_continuous(labels = function(x) format(x*100, big.mark = ",")) +
-	theme(legend.position = "top",
-		  panel.grid.major = element_line(colour = "grey", linetype = "dotted"))
-```
-
-## Model outputs
-
-### Model comparison
-
-```{r model-comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-# model_comparison <- waics_l1 %>% 
-# 	map("estimates") %>% 
-# 	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
-# 	bind_rows(.id = "model") %>%
-# 	clean_names() 
-# 	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
-# 	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
-# 	mutate(
-# 		model = c(
-# 			"Intercept",
-# 			"... + Trial type",
-# 			"... + Group \u00d7Trial type\u00d7Group",
-# 			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
-# 			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
-# 		)
-# 	) %>% 
-# 	gt() %>% 
-# 	fmt_number(-model) %>% 
-# 	tab_spanner("WAIC", matches("waic")) %>% 
-# 	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
-# 	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
-# 	cols_label(
-# 		model = "Model",
-# 		estimate_elpd_waic = "Estimate",
-# 		estimate_waic = "Estimate",
-# 		estimate_p_waic = "Estimate",
-# 		se_elpd_waic = md("*SE*"),
-# 		se_waic = md("*SE*"),
-# 		se_p_waic = md("*SE*"),
-# 	) %>% 
-# 	cols_align("right", "model") %>% 
-# 	tab_style(
-# 		cell_text(weight = "bold"),
-# 		cells_column_spanners()
-# 	) %>% 
-# 	tab_style(
-# 		cell_text(style = "italic"),
-# 		cells_column_labels()
-# 	)
-# 
-# gtsave(model_comparison, here("img", "model_comparison.png"))
-# 
-# 
-# as_raw_html(model_comparison)
-
-```
-
-### Fixed effects
-
-```{r}
-#| label: fixed-effects
-#| fig-height: 10
-#| fig-width: 12
-post_draws <- gather_draws(fit_3, `b_.*`, regex = TRUE)
-
-post_draws %>% 
-	median_hdi() %>% 
-	mutate(excludes_zero = (.lower > 0) | (.upper < 0),
-		   excludes_zero = ifelse(excludes_zero, "Yes", "No") %>% 
-		   	factor(levels = c("Yes", "No")),
-		   poly = case_when(str_detect(.variable, "ot1") ~ "Linear",
-		   				 str_detect(.variable, "ot2") ~ "Quadratic",
-		   				 str_detect(.variable, "ot3") ~ "Qubic",
-		   				 TRUE ~ "Main"),
-		   .variable_name = str_remove(.variable, "b_ot1:|b_ot2:|b_ot3:|b_")) %>% 
-	ggplot(aes(x = .value, y = .variable_name, 
-			   xmin = .lower, xmax = .upper, 
-			   colour = excludes_zero)) +
-	facet_wrap(~poly, scales = "free_x") +
-	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
-	geom_pointinterval(size = 5, point_size = 3) +
-	labs(x = "Estimate (Logit scale)", 
-		 y = "Variable", 
-		 fill = "CrI", 
-		 alpha = "CrI",
-		 title = "Main effects",
-		 subtitle = "Mean and 95% credible interval of posterior distribution",
-		 colour = "Interval excludes zero?") +
-	theme(legend.position = "top",
-		  axis.title.y = element_blank(),
-		  axis.text.y = element_text(hjust = 1),
-		  panel.border = element_rect(colour = "black", fill = NA))
-```
-
-### Marginal means
-
-```{r}
-#| label: fig-posterior-epred
-nd <- expand_grid(time_bin = seq(0, 20, 0.1),
-				  age_group = levels(fit_1$data$age_group),
-				  lp = levels(fit_2$data$lp),
-				  trial_type = levels(fit_4$data$trial_type)) %>% 
-	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)
-
-m <- add_epred_draws(nd, fit_3, ndraws = 25, re_formula = NA) %>% 
-	mutate(.epred = plogis(.epred))
-
-m %>% 
-	ggplot(aes(ot1, .epred, colour = trial_type)) +
-	facet_grid(lp~age_group) +
-	geom_line(aes(group = interaction(.draw, trial_type)), alpha = 0.15, size = 1) +
-	stat_summary(fun = median, geom = "line", size = 1) +
-	theme(legend.position = "top")
-```
-
-# Appendix
-
-## Longitudinal participants
-
-We collected data from `r sum(duplicated(participants$participant))` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30).
-Of those, `r sum(duplicated(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r sum(duplicated(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
-
-```{r}
-#| label: fig-participants-longitudinal
-#| fig-height: 10
-#| fig-width: 4
-participants %>% 
-	left_join(distinct(attrition, id, valid_participant)) %>%
-	filter(valid_participant) %>% 
-	add_count(id, lp, name = "n_total") %>% 
-	count(id, age_group, test_language, lp, n_total) %>% 
-	pivot_wider(id_cols = c(id, lp, test_language, n_total),
-				names_from = age_group,
-				values_from = n,
-				values_fill = 0) %>% 
-	pivot_longer(5:7,
-				 names_to = "age_group",
-				 values_to = "n") %>% 
-	mutate(id_reordered = reorder_within(id, by = n_total, within = list(test_language, lp))) %>% 
-	ggplot(aes(age_group, id_reordered, fill = as.factor(n))) + 
-	facet_wrap(test_language~lp, 
-			   scales = "free_y",
-			   labeller = label_wrap_gen(multi_line = FALSE)) +
-	geom_tile(colour = "white") +
-	labs(x = "Age (months)", 
-		 y = "Exposure to 2nd language", 
-		 fill = "Lang. Profile") +
-	scale_fill_manual(values = c("white", clrs[4], "white")) +
-	theme(legend.position = "none",
-		  legend.title = element_blank(),
-		  panel.grid = element_blank(),
-		  axis.text.x = element_text(size = 6),
-		  axis.title.y = element_blank(),
-		  axis.title.x = element_text(size = 6),
-		  axis.text.y = element_blank(),
-		  axis.ticks.y = element_blank(),
-		  strip.text = element_text(size = 6))
-
-```

### 2025-12-09 docs/_appendix/_vocabulary-validity.qmd
Fix code

## Appendix D: vocabulary checklist validity

```{r setup}
library(patchwork)
library(dplyr)
library(tidyr)
```

To test the validity of caregivers' estimates of word comprehension in the vocabulary questionnaires, we compared participants' target looking for target words reported as acquired, compared to those reported as not acquired. If parents' responses are accurate, target looking preference should be stronger in for acquired words. We conducted this analysis by computing the logit of the probability of target looking at during the presentation of the target and the distractor pictures for each participant across conditions, and then across participants. In @fig-validity-target, we report the target looking trends in the three groups tested in Chapter 3: English monolinguals in Study 1, Catalan and Spanish monolinguals in Study 2, and Catalan-Spanish bilinguals in Study 3. Overall,

```{r fig-validity-target}

time_subset <- c(0.3, 2)
gaze_tmp <- gaze |> 
	filter(phase=="Target-Distractor",
		   between(timestamp, time_subset[1], time_subset[2])) |> 
	select(session_id, trial, phase, timestamp,
		   is_gaze_target, is_gaze_distractor, trial_type) |> 
	mutate(condition = recode_condition(trial_type))

vocabulary_tmp <- rename_with(vocabulary,  
							  \(x) gsub("_prop", "", paste0("voc_", x)), 
							  matches("_prop"))

participants_tmp <- participants |> 
	select(child_id, session_id, age_group, age, lp)

attrition_trials_tmp <- get_attrition_trials(
	participants = participants,
	vocabulary = vocabulary,
	vocabulary_by = c("target"),
	aoi_coords = aoi_coords,
	stimuli = stimuli,
	gaze = gaze,
	min_looking = c(prime = 0.75,
					test = 1.00,
					test_each = 0.00,
					test_any = 0.1)) |> 
	select(session_id, trial, samples, is_valid_vocab_all) |> 
	unnest_wider(is_valid_vocab_all) |> 
	rename_with(\(x) gsub("is_valid_vocab_", "", x))

attrition_participants_tmp <- attrition_participants |> 
	filter(is_valid_participant) |> 
	select(session_id)

data <- gaze_tmp |>
	inner_join(attrition_trials_tmp, by = join_by(session_id, trial)) |> 
	inner_join(attrition_participants_tmp, by = join_by(session_id)) |> 
	mutate(condition = recode_condition(trial_type)) |> 
	select(session_id, trial, condition, is_gaze_target, is_gaze_distractor,
		   prime, target, distractor) |> 
	# aggregated across trials by participant, time bin and condition
	# see Chow et al. (2018)
	summarise(sum_target = sum(is_gaze_target, na.rm = TRUE),
			  sum_distractor = sum(is_gaze_distractor, na.rm = TRUE),
			  .nsamples = sum(is_gaze_target | is_gaze_distractor, na.rm = TRUE),
			  .ntrials = length(unique(trial)),
			  .by = c(session_id, condition, prime, target, distractor)) |> 
	# empirical logit with adjustment
	# see Barr et al. (2008)
	mutate(.nsamples = sum_target + sum_distractor,
		   .prop = ifelse(.nsamples==0, 0, sum_target / .nsamples),
		   .elog = log((sum_target + .5)/(sum_distractor + .5))) |> 
	rename(.sum = sum_target) |> 
	arrange(desc(session_id), condition) |> 
	inner_join(participants_tmp, by = join_by(session_id)) |> 
	inner_join(vocabulary_tmp, by = join_by(child_id, session_id)) |> 
	mutate(across(c(.nsamples), as.integer),
		   across(c(child_id, session_id, lp, condition, age_group), as.factor),
		   across(c(age, voc_l1),
		   	   \(x) scale(x, scale = TRUE)[, 1],
		   	   .names = "{.col}_std")) |> 
	select(child_id, session_id, age_group, age, voc_l1, voc_total, lp,
		   condition,  .sum, .prop, .elog, .nsamples,
		   matches("std"), prime, target, distractor)

# set a priori contrasts
contrasts(data$condition) <- cbind(c(-0.5, 0.5, 0),
								   c(0, -0.5, 0.5))
contrasts(data$lp) <- cbind(c(-0.5, 0.25, 0.25),
							c(0, -0.5, 0.5))
contrasts(data$age_group) <- cbind(c(-0.5, 0.5, 0),
								   c(0, -0.5, 0.5))

plot_summary <- data |> 
	select(session_id, lp, .elog, target) |> 
	arrange(session_id, target) |> 
	summarise(.elog_mean = mean(.elog),
			  .elog_sd = sd(.elog),
			  n = n(),
			  .by = c(lp, target)) |> 
	mutate(target = ifelse(target, "Yes", "No"),
		   .elog_se = .elog_sd/sqrt(n),
		   .elog_lower = .elog_mean - .elog_se*1.96,
		   .elog_upper = .elog_mean + .elog_se*1.96) |> 
	ggplot(aes(lp, .elog_mean, 
			   ymin = .elog_lower,
			   ymax = .elog_upper,
			   colour = target)) +
	facet_wrap(~lp, ncol = 1, scales = "free_x") +
	geom_errorbar(width = 0.2, linewidth = 3/4, 
				  position = position_dodge(width = 0.25)) +
	geom_point(size = 2,
			   position = position_dodge(width = 0.25)) +
	geom_hline(yintercept = 0,
			   linetype = "dashed") +
	labs(x = "Condition",
		 y = "P(Target looking)", 
		 colour = "Knows the target word") +
	theme(panel.grid.major.y = element_line(colour = "grey",
											linetype = "dotted"))

data_time <- gaze_tmp |>
	inner_join(attrition_trials_tmp, by = join_by(session_id, trial)) |> 
	inner_join(attrition_participants_tmp, by = join_by(session_id)) |> 
	mutate(condition = recode_condition(trial_type),
		   timebin = cut(timestamp,
		   			  breaks = seq(0.00, 7.00, 0.1),
		   			  labels = FALSE,
		   			  include.lowest = TRUE)) |> 
	select(session_id, trial, timebin, condition, is_gaze_target, is_gaze_distractor,
		   prime, target, distractor) |> 
	# aggregated across trials by participant, time bin and condition
	# see Chow et al. (2018)
	summarise(sum_target = sum(is_gaze_target, na.rm = TRUE),
			  sum_distractor = sum(is_gaze_distractor, na.rm = TRUE),
			  .nsamples = sum(is_gaze_target | is_gaze_distractor, na.rm = TRUE),
			  .ntrials = length(unique(trial)),
			  .by = c(session_id, timebin, condition, prime, target, distractor)) |> 
	# empirical logit with adjustment
	# see Barr et al. (2008)
	mutate(.nsamples = sum_target + sum_distractor,
		   .prop = ifelse(.nsamples==0, 0, sum_target / .nsamples),
		   .elog = log((sum_target + .5)/(sum_distractor + .5))) |> 
	rename(.sum = sum_target) |> 
	arrange(desc(session_id), condition) |> 
	inner_join(participants_tmp, by = join_by(session_id)) |> 
	inner_join(vocabulary_tmp, by = join_by(child_id, session_id)) |> 
	mutate(across(c(.nsamples), as.integer),
		   across(c(child_id, session_id, lp, condition, age_group), as.factor),
		   across(c(age, voc_l1),
		   	   \(x) scale(x, scale = TRUE)[, 1],
		   	   .names = "{.col}_std")) |> 
	select(child_id, session_id, age_group, age, timebin, voc_l1, voc_total, lp,
		   condition,  .sum, .prop, .elog, .nsamples,
		   matches("std"), prime, target, distractor)

plot_time <- data_time |> 
	select(session_id, lp, timebin, .elog, target) |> 
	arrange(session_id, target) |> 
	summarise(.elog_mean = mean(.elog),
			  .elog_sd = sd(.elog),
			  n = n(),
			  .by = c(lp, target, timebin)) |> 
	mutate(target = ifelse(target, "Yes", "No"),
		   .elog_se = .elog_sd/sqrt(n),
		   .elog_lower = .elog_mean - .elog_se*1.96,
		   .elog_upper = .elog_mean + .elog_se*1.96) |> 
	ggplot(aes(timebin, .elog_mean,
			   ymin = .elog_lower,
			   ymax = .elog_upper,
			   colour = target,
			   fill = target)) +
	facet_wrap(~lp, scales = "free_x") +
	geom_line(linewidth = 1/2) +
	geom_ribbon(alpha = 1/2,
				colour = NA) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0,
			   linetype = "dashed") +
	labs(x = "Condition",
		 y = "P(Target looking)", 
		 fill = "Knows the target word",
		 colour = "Knows the target word") +
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted"),
		  axis.title.y = element_blank(),
		  axis.line.x = element_line())

plot_summary | plot_time + 
plot_layout(ncol = 2,
			widths = c(0.2, 0.8)) &
	scale_y_continuous(limits = c(-0.5, 1.25))
```

### 2025-12-09 docs/manuscript.qmd
Fix code

--- 2023-11-28 manuscript/manuscript.qmd
@@
 
-targets::tar_load(c(participants,
+targets::tar_load(c(
+    participants,
     stimuli,
@@
     data_bcn,
-					data_oxf))
-
-targets::tar_load(c(model_fits_bcn,
+    data_oxf
+))
+
+targets::tar_load(c(
+    model_fits_bcn,
     model_loos_bcn,
     model_fits_oxf,
-					model_loos_oxf))
+    model_loos_oxf
+))
 
 # prepare data
-attrition <- lst(participants,
+attrition <- lst(
+    participants,
     attrition_participants,
-				 attrition_trials) |>
+    attrition_trials
+) |>
     reduce(inner_join, by = join_by(session_id)) |>
     unnest_wider(matches("all"), names_sep = "_") |>
-	rename_with(\(x) gsub("is_valid_gaze_all_|is_valid_vocab_all",
-						  "", x))
+    rename_with(\(x) gsub(
+        "is_valid_gaze_all_|is_valid_vocab_all",
+        "", x
+    ))
 
@@
 
-options(ggplot2.ordinal.fill = clrs,
+options(
+    ggplot2.ordinal.fill = clrs,
     ggplot2.ordinal.colour = clrs,
@@
         filter(child_id %in% participants_oxf$child_id[duplicated(participants_oxf$child_id)]) |>
-		pivot_wider(id_cols = child_id,
+        pivot_wider(
+            id_cols = child_id,
             names_from = session_n,
             values_from = age,
-					names_repair = janitor::make_clean_names) |>
+            names_repair = janitor::make_clean_names
+        ) |>
         rowwise() |>
@@
     distinct(session_id, child_id, .keep_all = TRUE) |>
-	mutate(study = if_else(location=="Oxford", 
+    mutate(
+        study = if_else(location == "Oxford",
             "Study 1",
-						   "Study 2"),
+            "Study 2"
+        ),
         test_language = paste0(test_language, " dominant"),
-		   lp = gsub(" \\(English\\)", "", lp)) |> 
+        lp = gsub(" \\(English\\)", "", lp)
+    ) |>
     inner_join(attrition_participants,
-			   by = join_by(session_id)) |> 
-	summarise(n = n(),
+        by = join_by(session_id)
+    ) |>
+    summarise(
+        n = n(),
         n_participants = length(unique(child_id)),
@@
         # age_vctr = list(age),
-			  .by = c(lp, study, test_language, is_valid_participant)) |> 
-	pivot_wider(id_cols = c(lp, study, test_language),
+        .by = c(lp, study, test_language, is_valid_participant)
+    ) |>
+    pivot_wider(
+        id_cols = c(lp, study, test_language),
         names_from = is_valid_participant,
-				values_from = is.numeric) |> 
-	select(lp, study, test_language, starts_with("n_"), matches("TRUE"),
-		   n_FALSE, n_participants_FALSE) |> 
+        values_from = is.numeric
+    ) |>
+    select(
+        lp, study, test_language, starts_with("n_"), matches("TRUE"),
+        n_FALSE, n_participants_FALSE
+    ) |>
     rename_with(\(x) gsub("_TRUE", "", x)) |>
-	gt(rowname_col = "test_language",
-	   groupname_col = c("study", "lp")) |>
-	grand_summary_rows(columns = matches("age"),
+    gt(
+        rowname_col = "test_language",
+        groupname_col = c("study", "lp")
+    ) |>
+    grand_summary_rows(
+        columns = matches("age"),
         fns = list(Total ~ mean(.)),
-					   fmt = ~ fmt_number(., decimals = 2)) |>
-	grand_summary_rows(columns = c(n, n_participants),
+        fmt = ~ fmt_number(., decimals = 2)
+    ) |>
+    grand_summary_rows(
+        columns = c(n, n_participants),
         fns = list(Total ~ sum(.)),
-					   fmt = ~ fmt_integer(.)) |>
+        fmt = ~ fmt_integer(.)
+    ) |>
     # gt_plt_dist(age_vctr, type = "histogram") |>
@@
     cols_merge(c(n_participants, n_participants_FALSE),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(age_mean, age_sd),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(doe_catalan_mean, doe_catalan_sd),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(doe_english_mean, doe_english_sd),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(doe_spanish_mean, doe_spanish_sd),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     tab_spanner("Sample size", starts_with("n")) |>
@@
     tab_spanner("Degree of Exposure (%)", matches("doe")) |>
-	cols_label(n = "Test sessions",
+    cols_label(
+        n = "Test sessions",
         n_participants = "Participants",
@@
         doe_english_mean = "M (SD)",
-			   doe_spanish_mean = "M (SD)") |>
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |>
-	tab_style(cell_text(style = "italic"),
-			  cells_column_spanners())
+        doe_spanish_mean = "M (SD)"
+    ) |>
+    tab_style(
+        cell_text(style = "italic"),
+        cells_column_labels()
+    ) |>
+    tab_style(
+        cell_text(style = "italic"),
+        cells_column_spanners()
+    )
 ```
@@
     select(participants_oxf, session_id),
-							 by = join_by(session_id))
+    by = join_by(session_id)
+)
 
@@
 #| label: fig-vocabulary-oxf
-#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles.
-Vocabulary size scores from the recurrent participants are shown linked.
-For visualisation purposes, testing sessions were aggregated at three age points: 21, 25, and 30 months.
-Points and intervals indicate mean and standard deviations, respectively."
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles."
 #| fig-width: 5
@@
     inner_join(filter(attrition_participants, is_valid_participant),
-			   by = join_by(session_id)) |>
-	inner_join(select(participants, location, lp, age,
-					  child_id, session_id, age_group),
-			   by = join_by(child_id, session_id)) |> 
+        by = join_by(session_id)
+    ) |>
+    inner_join(
+        select(
+            participants, location, lp, age,
+            child_id, session_id, age_group
+        ),
+        by = join_by(child_id, session_id)
+    ) |>
     filter(is_valid_participant) |>
-	select(child_id, session_id, vocab_id, is_imputed, l1_count,
-		   lp, location, age_group, age) |> 
-	mutate(location = factor(location, 
-							 levels = c("Oxford", "Barcelona")),
+    select(
+        child_id, session_id, vocab_id, is_imputed, l1_count,
+        lp, location, age_group, age
+    ) |>
+    mutate(
+        location = factor(location,
+            levels = c("Oxford", "Barcelona")
+        ),
         lp = gsub(" \\(English\\)", "", lp),
-		   side = case_when(location=="Oxford" ~ "both",
-		   				 lp=="Monolingual" ~ "left",
-		   				 lp=="Bilingual" ~ "right"),
-		   study = if_else(location=="Oxford", 
-		   				"Study 1 (English)", "Study 2 (Catalan/Spanish)"))
+        side = case_when(
+            location == "Oxford" ~ "both",
+            lp == "Monolingual" ~ "left",
+            lp == "Bilingual" ~ "right"
+        ),
+        study = if_else(location == "Oxford",
+            "Study 1 (English)", "Study 2 (Catalan/Spanish)"
+        )
+    )
 
 vocab_plot_means <- vocab_plot_data |>
-	summarise(l1_count_sd = sd(l1_count, na.rm = TRUE),
+    summarise(
+        l1_count_sd = sd(l1_count, na.rm = TRUE),
         l1_count = mean(l1_count, na.rm = TRUE),
         n = n(),
-			  .by = c(age, side, lp, study)) |> 
-	mutate(.lower = l1_count - (l1_count_sd/sqrt(n)),
-		   .upper = l1_count + (l1_count_sd/sqrt(n)))
+        .by = c(age, side, lp, study)
+    ) |>
+    mutate(
+        .lower = l1_count - (l1_count_sd / sqrt(n)),
+        .upper = l1_count + (l1_count_sd / sqrt(n))
+    )
 
 vocab_plot_data |>
-	filter(study=="Study 1 (English)") |> 
+    filter(study == "Study 1 (English)") |>
     ggplot(aes(age, l1_count,
-			   side = side)) +
-	geom_point(size = 2,
+        side = side
+    )) +
+    geom_point(
+        size = 2,
         shape = 1,
         colour = "grey",
-			   alpha = 3/4,
-			   stroke = 1) +
-	geom_smooth(method = "lm", 
+        alpha = 3 / 4,
+        stroke = 1
+    ) +
+    geom_smooth(
+        method = "lm",
         formula = "y ~ x",
         colour = "black",
-				fill = "black") +
-	labs(x = "Age (months)",
+        fill = "black"
+    ) +
+    labs(
+        x = "Age (months)",
         y = "Vocabulary size",
         colour = "Group",
-		 fill = "Group") +
-	scale_y_continuous(limits = c(0, 575),
-					   breaks = seq(0, 1e3, 100)) +
+        fill = "Group"
+    ) +
+    scale_y_continuous(
+        limits = c(0, 575),
+        breaks = seq(0, 1e3, 100)
+    ) +
     scale_x_continuous(breaks = seq(0, 50, 2)) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"),
+    theme(
+        panel.grid.major.y = element_line(
+            linetype = "dotted",
+            colour = "grey"
+        ),
         legend.position = "top",
-		  legend.title = element_blank())
+        legend.title = element_blank()
+    )
 ```
@@
 
-Participants were presented with 32 trials in random order, which belonged to three conditions: *Unrelated* (16 trials), *Related/Non-cognate* (8 trials), and *Related/Cognate* (8 trials).
-In *Unrelated* trials, target was phonologically unrelated with the English and Spanish labels of the prime picture (e.g., $\text{door}_{\text{ENG}}/\text{puerta}_{\text{SPA}}-\text{sock}_{\text{ENG}}$).
-In *Related/Non-cognate* trials, the target shared phonological onset with the English prime label, but not with the Spanish prime label (e.g., $\textbf{t}\text{ree}_{\text{ENG}}/\text{árbol}_{\text{SPA}}-\textbf{t}\text{ruck}_{\text{ENG}}$).
-In *Related/Cognate* trials, the target shared phonological overlap with both English and Spanish prime labels ($\textbf{b}\text{oot}_{\text{ENG}}/\textbf{b}\text{ota}_{\text{SPA}}-\textbf{b}\text{ird}_{\text{ENG}}$).
+Participants were presented with 32 trials in random order, which belonged to two conditions: *Related* and *Unrelated* trials.
+In *Related* trials (*n* = 16), the English label of the prime was phonologically related to the target label, sharing phonological onset (e.g., /**\textipa{"t}**\textipa{\*ri:}/$_{\text{ENG}} [\text{tree}]$--/**\textipa{"t}**\textipa{\*r2k}/$_{\text{ENG}} [\text{truck}]$).
+In *Unrelated* trials, the prime and target labels did not share phonological onset (e.g., /\textipa{"dO:}/$_{\text{ENG}} [\text{door}]$--/\textipa{"s6k}/$_{\text{ENG}} [\text{sock}]$).
 Especial attention was paid to avoiding semantic or taxonomic relationships between prime and target words, and between prime and distractor words.
@@
 durations <- stimuli |>
-	summarise(across(duration, 
-					 lst(mean, sd, min, max)), 
-			  .by = c(test_language)) %>%
-	mutate(across(is.numeric, \(x) format(round(x*1e3, 2), big.mark = ","))) %>%
+    summarise(
+        across(
+            duration,
+            lst(mean, sd, min, max)
+        ),
+        .by = c(test_language)
+    ) %>%
+    mutate(across(is.numeric, \(x) format(round(x * 1e3, 2), big.mark = ","))) %>%
     split(janitor::make_clean_names(.$test_language))
@@
     unnest_wider(c(freq, nphon, familiarity)) |>
-	summarise(across(c(matches("n_phon|freq_|nphon|familiarity")),
-					 list(	mean = \(x) mean(x, na.rm = TRUE),
-					 	  sd = \(x) sd(x, na.rm = TRUE))),
-			  .by = c(trial_type, test_language)) |>
+    summarise(
+        across(
+            c(matches("n_phon|freq_|nphon|familiarity")),
+            list(
+                mean = \(x) mean(x, na.rm = TRUE),
+                sd = \(x) sd(x, na.rm = TRUE)
+            )
+        ),
+        .by = c(trial_type, test_language)
+    ) |>
     select(-matches("distractor")) |>
-	mutate(test_language = if_else(test_language=="English",
+    mutate(test_language = if_else(test_language == "English",
         paste0("Study 1: ", test_language),
-								   paste0("Study 2: ", test_language))) |>
+        paste0("Study 2: ", test_language)
+    )) |>
     arrange(test_language) |>
-	gt(rowname_col = "trial_type",
-	   groupname_col = "test_language") |> 
+    gt(
+        rowname_col = "trial_type",
+        groupname_col = "test_language"
+    ) |>
     # summary_rows(groups = c("Unrelated", "Non-cognate", "Cognate"),
@@
     # 			 fmt = ~ fmt_number(., decimals = 2)) |>
-	grand_summary_rows(columns = matches("phon|freq"),
+    grand_summary_rows(
+        columns = matches("phon|freq"),
         fns = list(Total ~ mean(.)),
-					   fmt = ~ fmt_number(., decimals = 2)) |>
-		grand_summary_rows(columns = matches("familiarity"),
+        fmt = ~ fmt_number(., decimals = 2)
+    ) |>
+    grand_summary_rows(
+        columns = matches("familiarity"),
         fns = list(Total ~ mean(.)),
-					   fmt = ~ fmt_number(., decimals = 2, scale_by = 100)) |>
+        fmt = ~ fmt_number(., decimals = 2, scale_by = 100)
+    ) |>
     tab_spanner("# Phonemes", matches("nphon")) |>
@@
     cols_merge(c(freq_prime_mean, freq_prime_sd),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(freq_target_mean, freq_target_sd),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(familiarity_prime_mean, familiarity_prime_sd),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(familiarity_target_mean, familiarity_target_sd),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(nphon_prime_mean, nphon_prime_sd),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(nphon_target_mean, nphon_target_sd),
-			   pattern = "{1} ({2})") |>
-	cols_label(trial_type = "",
+        pattern = "{1} ({2})"
+    ) |>
+    cols_label(
+        trial_type = "",
         familiarity_prime_mean = "Prime",
@@
         nphon_prime_mean = "Prime",
-			   nphon_target_mean = "Target") |>
-	tab_style(list(cell_text(style = "italic")), 
-			  list(cells_column_labels(),
+        nphon_target_mean = "Target"
+    ) |>
+    tab_style(
+        list(cell_text(style = "italic")),
+        list(
+            cells_column_labels(),
             cells_column_spanners(),
-			  	 cells_grand_summary()))
+            cells_grand_summary()
+        )
+    )
 ```
@@
 The first 200 ms of the test phase were discarded to avoid modelling fixations driven by processes other than auditory word recognition [@fernald1998rapid; @fernald2001half].
-Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of 166.67 ms).
+Missing eye-tracker samples were interpolated using the last-observation-carried-forward [see @zettersten2022peekbank for a similar approach], with a maximum of 20 maximum consecutive missing samples being interpolated (an equivalent of `r round(20*1000/120, 2)`).
 Target looking probability was calculated as the empirical logit, using the number of samples inside the time bin in which the participant was looking at the target and distractor AOI (see @eq-elogit) [@barr2008analyzing; @agresti2012categorical], as follows:
@@
 Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
-From the trials included in the final data set, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), were `r n_trials_condition$non_cognate_2$n` *Related/Non-cognate* trials(`r n_trials_condition$non_cognate$n` previously excluded), and `r n_trials_condition$cognate_2$n` were *Related/Cognate* trials (`r n_trials_condition$cognate$n` previously excluded).
+From the trials included in the final data set, `r n_trials_condition$unrelated_2$n` were *Unrelated* trials (`r n_trials_condition$unrelated$n` previously excluded), and `r n_trials_condition$non_cognate_2$n + n_trials_condition$cognate_2$n` were *Related*  trials(`r n_trials_condition$non_cognate$n + n_trials_condition$cognate$n` previously excluded).
 
@@
     count(is_valid_participant, lp) |>
-	pivot_wider(names_from = is_valid_participant,
+    pivot_wider(
+        names_from = is_valid_participant,
         values_from = n,
-				names_repair = janitor::make_clean_names) |>
-	mutate(n_participants_true = true,
-		   n_participants_false = false) |>
+        names_repair = janitor::make_clean_names
+    ) |>
+    mutate(
+        n_participants_true = true,
+        n_participants_false = false
+    ) |>
     select(lp, true, false)
@@
 attrition |>
-	mutate(study = if_else(location=="Oxford", 
+    mutate(study = if_else(location == "Oxford",
         "Study 1: English (Oxford)",
-						   "Study 2: Catalan/Spanish (Barcelona)")) |> 	
-	summarise(n_trials_true = sum(is_valid_trial),
+        "Study 2: Catalan/Spanish (Barcelona)"
+    )) |>
+    summarise(
+        n_trials_true = sum(is_valid_trial),
         n_trials_false = sum(!is_valid_trial),
-			  .by = c(lp, trial_type, study)) |>
+        .by = c(lp, trial_type, study)
+    ) |>
     arrange(study, desc(lp)) |>
-	pivot_wider(id_cols = c(study, lp),
+    pivot_wider(
+        id_cols = c(study, lp),
         names_from = c(trial_type),
         values_from = matches("trials"),
-				names_repair = janitor::make_clean_names) |>
+        names_repair = janitor::make_clean_names
+    ) |>
     left_join(n_lp, by = join_by(lp)) |>
     select(study, lp, true, false, matches("n_trials")) |>
-	gt(rowname_col = "lp",
-	   groupname_col = "study") |>
+    gt(
+        rowname_col = "lp",
+        groupname_col = "study"
+    ) |>
     tab_spanner("Participants", matches("participant")) |>
@@
     cols_merge(c(n_trials_true_cognate, n_trials_false_cognate),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(n_trials_true_non_cognate, n_trials_false_non_cognate),
-			   pattern = "{1} ({2})") |>
+        pattern = "{1} ({2})"
+    ) |>
     cols_merge(c(n_trials_true_unrelated, n_trials_false_unrelated),
-			   pattern = "{1} ({2})") |>
-	cols_label(true = "Participants",
+        pattern = "{1} ({2})"
+    ) |>
+    cols_label(
+        true = "Participants",
         n_trials_true_cognate = "Cognate",
         n_trials_true_non_cognate = "Non-cognate",
-			   n_trials_true_unrelated = "Unrelated") |>
-	tab_style(cell_text(style = "italic"),
-			  cells_column_labels()) |>
-	tab_style(cell_text(align = "left"),
-			  cells_stub()) |>
-	grand_summary_rows(fns = list(label = md("*N*")) ~ sum(.),
-					   fmt = ~ fmt_integer(.))
+        n_trials_true_unrelated = "Unrelated"
+    ) |>
+    tab_style(
+        cell_text(style = "italic"),
+        cells_column_labels()
+    ) |>
+    tab_style(
+        cell_text(align = "left"),
+        cells_stub()
+    ) |>
+    grand_summary_rows(
+        fns = list(label = md("*N*")) ~ sum(.),
+        fmt = ~ fmt_integer(.)
+    )
 ```
@@
     r_info$R.version$minor,
-						.sep = ".")
+    .sep = "."
+)
 stan_version <- "2.33.0"
@@
 First, we fit a model ($\mathcal{M}_0$) that included the main effects of *Condition* and *Age* as fixed effects in the model.
-Given that the cognate/non-cognate distinction is meaningless for monolinguals, for the following analyses we lumped the *Related/Cognate* and *Related/Non-cognate* into a single level, *Related*.
 We set an *a priori* contrast for the *Condition* predictor [@schad2020capitalize], comparing *Unrelated* and *Related* trials (sum-coded as `-0.5` and `+0.5`.
 Before entering the model, the *Age* predictor was standardised by subtracting from each observation the mean of the predictor, and dividing the result from the standard deviation of the predictor.
-
 We included the variable *Session*---which indexes individual testing sessions that may belong to the same participant---as grouping variable, nested within the *Participant* grouping variable---which indexes a distinct participant.
@@
 We added by-session intercepts and *Condition* slopes, and by-participant intercepts and *Age* slopes.
-To model the time course of target looking across time bins, we included B-splines for the main effect of *Time*, and one for the interaction between *Group* and *Relatedness* [@wood2017generalized].
+To model the time course of target looking across time bins, we included B-splines for the main effect of *Time*, and for the *Condition* predictor [@wood2017generalized].
 For both splines, we specified $k = 8$ basis functions or *knots*.
@@
 \eta'(\mu_{ij}) &= (\beta_0 + u _{0_{ij}}) +
-(\beta_1 + u _{1_{ij}}) \text{Condition} + \beta_{2} Age + \\
-& \sum_{w = 1}^k b_{w_{0}} \beta_{3_{k}} \text{Time} +
-\sum_{w = 1}^k b_{w_{1}} \beta_{4_{k}} (\text{Time} \times \text{Group}) \\
+(\beta_1 + u _{1_{ij}}) \text{Condition} + \beta_{2} \text{Age} + \sum_{w = 1}^k b_{w} \beta_{3_{k}} \text{Time} + \\
 \text{where:} \\
 &\eta'\text{ is the empirical logit of target fixations} \\
-&b_{w_{0-1}} \text{ is the cubic spline of the } w \text{ basis function} \\
-&k \text{ is the number of knots in the spline (10)} \\
+&b_{w} \text{ is the cubic spline of the } w \text{ basis function} \\
+&k \text{ is the number of knots in the spline }(k = 8) \\
 &\textbf{Prior:} \\
-\beta_{0-4} &\sim \mathcal{N}(0, 0.5) \\
+\beta_{0-3} &\sim \mathcal{N}(0, 0.5) \\
 u_{0-1_{ij}} &\sim \mathcal{N}(0, \sigma_{0-2})\\
-b_{0-1} &\sim \text{MVN}(0, \tau_{0-1}) \\
-\sigma_{0-2}, \tau_{0-1} &\sim \text{Exponential}(6)\\
-\rho_{0-2} &\sim LKJCorr(6)\\
+b_{w} &\sim \text{MVN}(0, \tau) \\
+\sigma_{0-1}, \tau &\sim \text{Exponential}(6)\\
+\rho_{0-1} &\sim LKJCorr(6)\\
 \text{where:}\\
-&\rho_{0-2} \text{ are the correlation parameters for } \sigma_{0-2}
+&\rho_{0-1} \text{ are the correlation parameters for } \sigma_{0-2}
 \end{aligned}
@@
 ```{r coefs-oxf}
-var_labels <- c("b_Intercept" = "Intercept",
+var_labels <- c(
+    "b_Intercept" = "Intercept",
     "b_age_std" = "Age (+1 SD)",
     "b_condition1" = "Condition (U vs. R/NC)",
-				"b_condition2" = "Condition (R/NC vs. R/C)")
+    "b_condition2" = "Condition (R/NC vs. R/C)"
+)
 
@@
     vars_dict = var_labels,
-									   rope_interval = rope_interval)
+    rope_interval = rope_interval
+)
 
 coefs <- model_summary |>
-	mutate(.value = sprintf("%.3f", .value),
+    mutate(
+        .value = sprintf("%.3f", .value),
         .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
-		   .rope = scales::percent(.rope, accuracy = 0.01)) |>
+        .rope = scales::percent(.rope, accuracy = 0.01)
+    ) |>
     split(janitor::make_clean_names(model_summary$.variable))
@@
 
-timebin_values <- make_std(seq(0, 16, length.out = 100),
+timebin_values <- make_std(
+    seq(0, 16, length.out = 100),
     mean(data_bcn$timebin),
-						   sd(data_bcn$timebin))
+    sd(data_bcn$timebin)
+)
 
@@
     ndraws = NULL,
-						  value = ".epred")
+    value = ".epred"
+)
 
 obs <- data_oxf |>
-	summarise(.elog = mean(.elog),
-			  .by = c(timebin_std, condition))
+    summarise(
+        .elog = mean(.elog),
+        .by = c(timebin_std, condition)
+    )
 
@@
         linetype = condition,
-			   shape = condition)) +
-	geom_hline(yintercept = 0,
-			   colour = "grey") +
-	stat_summary(fun.data = mean_qi,
+        shape = condition
+    )) +
+    geom_hline(
+        yintercept = 0,
+        colour = "grey"
+    ) +
+    stat_summary(
+        fun.data = mean_qi,
         geom = "ribbon",
         alpha = 1 / 4,
-				 linewidth = NA) +
-	stat_summary(fun = "mean",
+        linewidth = NA
+    ) +
+    stat_summary(
+        fun = "mean",
         geom = "line",
-				 linewidth = 3 / 4) +
-	geom_point(data = obs,
+        linewidth = 3 / 4
+    ) +
+    geom_point(
+        data = obs,
         aes(y = .elog),
         stroke = 1,
-			   size = 2) +
-	labs(x = "Time (ms)",
+        size = 2
+    ) +
+    labs(
+        x = "Time (ms)",
         y = "Logit (Target looking)",
@@
         linetype = "Condition",
-		 shape = "Condition") +
+        shape = "Condition"
+    ) +
     scale_y_continuous(limits = c(-0.75, 1.25)) +
     scale_shape_manual(values = c(1, 2)) +
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"))
+    theme(panel.grid.major.y = element_line(
+        colour = "grey",
+        linetype = "dotted"
+    ))
 
 epreds_diff <- epreds |>
-	pivot_wider(id_cols = c(timebin_std, .draw),
+    pivot_wider(
+        id_cols = c(timebin_std, .draw),
         names_from = "condition",
         values_from = ".epred",
-				names_repair = janitor::make_clean_names) |>
+        names_repair = janitor::make_clean_names
+    ) |>
     mutate(.epred = related - unrelated)
@@
     ggplot(aes(timebin_std, .epred)) +
-	annotate(geom = "rect",
-			 alpha = 1/4,
+    annotate(
+        geom = "rect",
+        alpha = 1 / 4,
         fill = "red",
@@
         xmin = -Inf,
-			 xmax = Inf) +
-	stat_summary(fun.data = mean_qi,
+        xmax = Inf
+    ) +
+    stat_summary(
+        fun.data = mean_qi,
         geom = "ribbon",
@@
         linewidth = NA,
-				 alpha = 3/4) +
-	stat_summary(fun = mean,
+        alpha = 3 / 4
+    ) +
+    stat_summary(
+        fun = mean,
         geom = "line",
         colour = "black",
-				 linewidth = 3 / 4) +
+        linewidth = 3 / 4
+    ) +
     # geom_hline(yintercept = rope_interval[1],
@@
     # 		   linetype = "dotted") +
-	labs(x = "Time (ms)",
+    labs(
+        x = "Time (ms)",
         y = "Logit P(Target looking)",
@@
         fill = "Comparison",
-		 linetype = "Comparison") +
+        linetype = "Comparison"
+    ) +
     scale_y_continuous(limits = c(-0.25, 0.5)) +
@@
     # scale_y_continuous(limits = c(0.25, 0.75)) +
-	scale_x_continuous(breaks = make_std(seq(0, 17, 3),
+    scale_x_continuous(
+        breaks = make_std(
+            seq(0, 17, 3),
             mean(data_bcn$timebin),
-										 sd(data_bcn$timebin)),
+            sd(data_bcn$timebin)
+        ),
         labels = \(x) format(seq(3e2, 2e3, 3e2),
-					   					 big.mark = ",")) &
-	theme(legend.position = "top",
-		  legend.title = element_blank())
+            big.mark = ","
+        )
+    ) &
+    theme(
+        legend.position = "top",
+        legend.title = element_blank()
+    )
 ```
@@
     rownames_to_column("model") |>
-	mutate(model = paste0("Model ",
-						  as.numeric(gsub("fit_oxf_", "", model))),
-		   across(matches("diff"),
+    mutate(
+        model = paste0(
+            "Model ",
+            as.numeric(gsub("fit_oxf_", "", model))
+        ),
+        across(
+            matches("diff"),
             \(x) {
@@
                 return(x)
-		   	   }),
+            }
+        ),
         model = case_when(
@@
             .default = model
-		   )) |>
+        )
+    ) |>
     select(model, matches("elpd|diff")) |>
@@
     fmt_number(is.numeric) |>
-	cols_label(elpd_diff = "ELPD (diff.)",
+    cols_label(
+        elpd_diff = "ELPD (diff.)",
         se_diff = "SE ELPD (diff)",
         elpd_loo = "ELPD",
-			   se_elpd_loo = "SE ELPD") |>
+        se_elpd_loo = "SE ELPD"
+    ) |>
     fmt_missing(missing_text = "---") |>
@@
 The absence of a phonological priming effect suggest that either English monolinguals did not generate implicit labels for the prime pictures presented in silence, or that, if generated, such labels did not interact with the subsequent recognition of the target word.
-Both candidate explanations conflict with both Mani and Plunkett’s studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects [@duta2012erp; @styles2015infant].
+Both explanations conflict with both Mani and Plunkett’s studies, and also with previous studies suggesting that infants 12-months and older already generate internal labels when presented with pictures of familiar objects [@duta2012erp; @styles2015infant].
 
@@
         filter(child_id %in% participants_bcn$child_id[duplicated(participants_bcn$child_id)]) |>
-		pivot_wider(id_cols = child_id,
+        pivot_wider(
+            id_cols = child_id,
             names_from = session_n,
             values_from = age,
-					names_repair = janitor::make_clean_names) |>
+            names_repair = janitor::make_clean_names
+        ) |>
         rowwise() |>
-		mutate(diff_1 = x2 - x1, diff_2 = x3 - x2,
+        mutate(
+            diff_1 = x2 - x1, diff_2 = x3 - x2,
             diff_min = min(diff_1, diff_2, na.rm = TRUE),
-			   diff_max = max(diff_1, diff_2, na.rm = TRUE)) |>
+            diff_max = max(diff_1, diff_2, na.rm = TRUE)
+        ) |>
         ungroup() |>
-		summarise(diff_min = min(diff_min, na.rm = TRUE),
-				  diff_max = max(diff_max, na.rm = TRUE))
+        summarise(
+            diff_min = min(diff_min, na.rm = TRUE),
+            diff_max = max(diff_max, na.rm = TRUE)
+        )
 })
@@
     count(language, version) |>
-	summarise(min = min(n),
+    summarise(
+        min = min(n),
         max = max(n),
-			  .by = language)
+        .by = language
+    )
 
@@
 #| label: fig-vocabulary-bcn
-#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Points and intervals indicate mean and standard deviations, respectively."
+#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles."
 #| fig-width: 6
@@
     mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual"))) |>
-	filter(study=="Study 2 (Catalan/Spanish)") |> 
+    filter(study == "Study 2 (Catalan/Spanish)") |>
     ggplot(aes(age, l1_count)) +
     facet_wrap(~lp) +
-	geom_point(size = 2,
+    geom_point(
+        size = 2,
         shape = 1,
         colour = "grey",
-			   alpha = 3/4,
-			   stroke = 1) +
-	geom_smooth(method = "lm", 
+        alpha = 3 / 4,
+        stroke = 1
+    ) +
+    geom_smooth(
+        method = "lm",
         formula = "y ~ x",
         colour = "black",
-				fill = "black") +
-	labs(x = "Age (months)",
+        fill = "black"
+    ) +
+    labs(
+        x = "Age (months)",
         y = "Vocabulary size",
         colour = "Group",
-		 fill = "Group") +
+        fill = "Group"
+    ) +
     scale_x_continuous(breaks = seq(0, 40, 2)) +
-	scale_y_continuous(limits = c(0, 575),
-					   breaks = seq(0, 1e3, 100)) +
-	theme(panel.grid.major.y = element_line(linetype = "dotted",
-											colour = "grey"),
+    scale_y_continuous(
+        limits = c(0, 575),
+        breaks = seq(0, 1e3, 100)
+    ) +
+    theme(
+        panel.grid.major.y = element_line(
+            linetype = "dotted",
+            colour = "grey"
+        ),
         legend.position = "none",
         axis.title.x = element_blank(),
-		  legend.title = element_blank())
-```
+        legend.title = element_blank()
+    )
+```
+
+### Design
+
+Participants were presented with 32 trials in random order, which belonged to three conditions: *Unrelated* trials (*n* = 16), *Related/Non-cognate* (*n* = 8), and *Related/Cognate* (*n* = 8).
+In *Unrelated* trials, the target label shared phonological onset with the Catalan and Spanish labels of the prime picture (e.g., prime: /\textipa{"gos}/$_{\text{CAT}}$--/\textipa{"pe.ro}/$_{\text{SPA}} [\text{dog}]$, target: /\textipa{"ka.za}/$_{\text{CAT}} [\text{house}]$, for a child tested in Catalan).
+In *Related/Non-cognate* trials, the target shared phonological onset with the prime label in the test language, but not with the prime label in the other language (e.g., prime: /**\textipa{m}**\textipa{i"}\textdyoghlig\textipa{o}/$_{\text{CAT}}$ (/\textipa{kal.Te"in}/ $_{\text{SPA}}) [\text{dog}]$, target: /**\textipa{m}**\textipa{u"nE.D@}/$_{\text{CAT}} [\text{coin}]$).
+In *Related/Cognate* trials, the target shared phonological overlap with both English and Spanish prime labels (e.g., prime: /**\textipa{"a}**\textipa{bR@}/$_{\text{CAT}}$--/**\textipa{"a}**\textipa{r.Bol}/ $_{\text{SPA}}) [\text{tree}]$, target: /**\textipa{@}**\textipa{"BE.j@}$/$_{\text{CAT}} [\text{bee}]$).
 
@@
 ```{r data set}
-attrition_bcn <- filter(attrition, location=="Barcelona")
+attrition_bcn <- filter(attrition, location == "Barcelona")
 n_trials <- nrow(attrition_bcn)
@@
     session_id,
-								 .keep_all = TRUE)$is_valid_participant)
+    .keep_all = TRUE
+)$is_valid_participant)
 n_participants_valid <- n_distinct(
-	attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id)
+    attrition_bcn[attrition_bcn$is_valid_participant, ]$child_id
+)
 
@@
     session_id,
-									.keep_all = TRUE)$is_valid_participant)
+    .keep_all = TRUE
+)$is_valid_participant)
 n_exc_participants_vocab <- sum(!distinct(attrition_bcn,
     session_id,
-										  .keep_all = TRUE)$is_valid_vocab_size)
+    .keep_all = TRUE
+)$is_valid_vocab_size)
 
 n_longitudinal <- attrition_bcn |>
-	filter(is_valid_participant,
-		   is_valid_trial) |>
+    filter(
+        is_valid_participant,
+        is_valid_trial
+    ) |>
     distinct(child_id, session_n) |>
@@
 The final data set included `r format(n_trials_valid, big.mark = ",")` trials from `r n_sessions_valid` testing sessions, generated by `r format(n_participants_valid, big.mark = ",")` distinct participants.
-Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, `r n_longitudinal[2, 2]` provided data from two experimental sessions, and `r n_longitudinal[3, 2]` provided data from three experimental sessions.
+Of those participants, `r n_longitudinal[1, 2]` provided data from one experimental session, and `r n_longitudinal[2, 2]` provided data from two experimental sessions.
 @tbl-attrition shows a detailed description of the trial attrition.
@@
 We modelled the data following a similar approach as in Study 1, with the main difference that participants' language profile (*Group*) was now included as a predictor in the model, in interaction with the *Condition* predictor.
-We set two *a priori* contrasts for the *Condition* predictor [@schad2020capitalize]: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
+We set two *a priori* contrasts for the *Condition* predictor: one comparing *Unrelated* and *Related/Non-cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Related/Cognate* trials coded as `0`), and another comparing *Related/Non-cognate* and *Related/Cognate* trials (sum-coded as `-0.5` and `+0.5`, with *Unrelated* trials coded as `0`).
 In Study 2, the base model $\mathcal{M}_0$ included the the main effects of *Age*, *Condition*, and *Group*, and the two-way interaction between the *Condition* and  *Group* predictors.
@@
 We set one *a priori* contrasts for the *Group* predictor, comparing *Monolingual* with *Bilingual* participants (sum-coded as `-0.5` and `+0.5`, respectively).
+To model the time course of target looking, we included B-splines for the main effect of *Time*, and for the two-way interaction between *Condition* and *Group*.
 
@@
     "b_condition1:lp1" = "Group \U00D7 Condition (U vs. RN)",
-	"b_condition2:lp1" = "Group \U00D7 Condition (RN vs. RC)")
+    "b_condition2:lp1" = "Group \U00D7 Condition (RN vs. RC)"
+)
 
@@
     ungroup() |>
-	summarise(.value = mean_qi(.epred)[[1]],
+    summarise(
+        .value = mean_qi(.epred)[[1]],
         .lower = mean_qi(.epred)[[2]],
         .upper = mean_qi(.epred)[[3]],
-			  .by = c(lp, condition, timebin_std))
+        .by = c(lp, condition, timebin_std)
+    )
 
 obs <- data_bcn |>
-	summarise(.elog = mean(.elog),
-			  .by = c(timebin_std, condition)) 
+    summarise(
+        .elog = mean(.elog),
+        .by = c(timebin_std, condition)
+    )
 plot_epreds <- epreds |>
@@
         linetype = condition,
-			   shape = condition)) +
+        shape = condition
+    )) +
     facet_wrap(~lp) +
-	stat_summary(fun.data = mean_qi,
+    stat_summary(
+        fun.data = mean_qi,
         geom = "ribbon",
         alpha = 1 / 4,
-				 linewidth = NA) +
-	stat_summary(fun = "mean",
+        linewidth = NA
+    ) +
+    stat_summary(
+        fun = "mean",
         geom = "line",
         # colour = "black",
-				 linewidth = 3 / 4) +
-	geom_hline(yintercept = 0,
-			   colour = "grey") +
-	geom_point(data = obs,
+        linewidth = 3 / 4
+    ) +
+    geom_hline(
+        yintercept = 0,
+        colour = "grey"
+    ) +
+    geom_point(
+        data = obs,
         aes(y = .elog),
         size = 2,
-			   stroke = 1) +
-	labs(x = "Time (ms)",
+        stroke = 1
+    ) +
+    labs(
+        x = "Time (ms)",
         y = "Logit (Target looking)",
@@
         linetype = "Condition",
-		 shape = "Condition") +
+        shape = "Condition"
+    ) +
     scale_y_continuous(limits = c(-0.75, 1.25)) +
-	theme(panel.grid.major.y = element_line(colour = "grey",
-											linetype = "dotted"))
+    theme(panel.grid.major.y = element_line(
+        colour = "grey",
+        linetype = "dotted"
+    ))
 
 epreds_diff <- epreds |>
-	pivot_wider(id_cols = c(lp, timebin_std, .draw),
+    pivot_wider(
+        id_cols = c(lp, timebin_std, .draw),
         names_from = "condition",
         values_from = ".epred",
-				names_repair = janitor::make_clean_names) |>
-	mutate(diff_1 = related_non_cognate - unrelated,
-		   diff_2 = related_cognate - related_non_cognate) |>
+        names_repair = janitor::make_clean_names
+    ) |>
+    mutate(
+        diff_1 = related_non_cognate - unrelated,
+        diff_2 = related_cognate - related_non_cognate
+    ) |>
     pivot_longer(matches("diff"),
@@
         values_to = ".epred",
-				 names_prefix = "diff_") |>
+        names_prefix = "diff_"
+    ) |>
     mutate(diff = factor(diff,
         levels = c(1, 2),
-						 labels = c("Related/Non-cognate - Unrelated",
-						 		   "Related/Cognate - Related/Non-cognate")))
+        labels = c(
+            "Related/Non-cognate - Unrelated",
+            "Related/Cognate - Related/Non-cognate"
+        )
+    ))
 
@@
     facet_wrap(diff ~ lp,
-			   labeller = labeller(diff = label_value,
+        labeller = labeller(
+            diff = label_value,
             lp = \(x) return(""),
-			   					.multi_line = FALSE)) +
-	annotate(geom = "rect",
+            .multi_line = FALSE
+        )
+    ) +
+    annotate(
+        geom = "rect",
         xmin = -Inf,
@@
         linewidth = 0,
-			 alpha = 1/3,
-			 linetype = "dotted") +
-	stat_summary(fun.data = mean_qi,
+        alpha = 1 / 3,
+        linetype = "dotted"
+    ) +
+    stat_summary(
+        fun.data = mean_qi,
         geom = "ribbon",
@@
         fill = "Comparison",
-		 linetype = "Comparison") +
+        linetype = "Comparison"
+    ) +
     scale_y_continuous(limits = c(-0.25, 0.5))
@@
     rownames_to_column("model") |>
-	mutate(model = paste0("Model ", as.numeric(gsub("fit_", "", model))),
-		   across(matches("diff"),
+    mutate(
+        model = paste0("Model ", as.numeric(gsub("fit_", "", model))),
+        across(
+            matches("diff"),
             \(x) {
@@
             model == "Model 3" ~ "Model 3 (Vocabulary-by-condition)",
-		   	.default = model)) |>
+            .default = model
+        )
+    ) |>
     select(model, matches("elpd|diff")) |>
@@
     unnest_wider(doe) |>
-	mutate(doe2 = ifelse(test_language == "Catalan",
-						 doe_spanish, doe_catalan),
-		   is_positive = doe2 > 0) |>
+    mutate(
+        doe2 = ifelse(test_language == "Catalan",
+            doe_spanish, doe_catalan
+        ),
+        is_positive = doe2 > 0
+    ) |>
     count(is_positive)
@@
 In Study 1, we attempted to replicate the original findings by @mani2010infant and @mani2011phonological in a same-aged English monolingual cohort.
-We found a null pattern of results, indicating no evidence of phonological priming.
+We found no evidence of phonological priming.
 In Study 2, we tested a cohort of monolingual and bilingual infants learning Catalan, Spanish, or both, and found similar results, with no evidence of phonological priming effect in either monolinguals or bilinguals.
@@
 
-The null pattern of results in Studies 1 and 2 contrasts with previous findings of within- and cross-language priming using an implicit naming paradigm.
+The lack of priming effects in Studies 1 and 2 contrasts with previous findings of within- and cross-language priming using an implicit naming paradigm.
 In their seminal study, @mani2010infant and @mani2011phonological reported within-language priming effects in English monolingual infants.
@@
 
-Third, and most likely, the modifications of the implicit naming task in the present investigation might have reduce the chances of detecting the anticipated effects.
+Third, and most likely, the modifications of the implicit naming task in the present investigation might have reduced the chances of detecting the anticipated effects.
 The most critical difference between the original design of the implicit naming task by Mani and Plunkett and that of the present study is the absence of a pre-naming phase during the test phase.
@@
 mp <- read_csv(file.path("manuscript", "_assets", "data", "mp-stimuli.csv"),
-			   show_col_types = FALSE)
+    show_col_types = FALSE
+)
 
 mp_means <- mp |>
-	filter(role!="distractor") |> 
-	mutate(condition = if_else(role=="target", 
-							   "related/unrelated", condition)) |> 
-	summarise(aoa_sd = sd(aoa, na.rm = TRUE),
+    filter(role != "distractor") |>
+    mutate(condition = if_else(role == "target",
+        "related/unrelated", condition
+    )) |>
+    summarise(
+        aoa_sd = sd(aoa, na.rm = TRUE),
         aoa = mean(aoa, na.rm = TRUE),
@@
         freq = mean(freq),
-			  .by = c(role, condition, study))
+        .by = c(role, condition, study)
+    )
 mp |>
-	filter(role!="distractor") |> 
-	mutate(condition = if_else(role=="target", 
-							   "related/unrelated", condition)) |> 
+    filter(role != "distractor") |>
+    mutate(condition = if_else(role == "target",
+        "related/unrelated", condition
+    )) |>
     ggplot(aes(condition, freq, colour = study, fill = study)) +
     facet_wrap(~role, scales = "free_x") +
-	geom_dots(side = "both",
+    geom_dots(
+        side = "both",
         layout = "swarm",
@@
         position = position_dodge(width = 1),
-			  alpha = 1/3) +
-	stat_summary(geom = "errorbar",
+        alpha = 1 / 3
+    ) +
+    stat_summary(
+        geom = "errorbar",
         fun.data = mean_se,
         width = 0.1,
-				 linewidth = 1/2,
-				 position = position_dodge(width = 1)) +
-	stat_summary(geom = "point",
+        linewidth = 1 / 2,
+        position = position_dodge(width = 1)
+    ) +
+    stat_summary(
+        geom = "point",
         fun = mean,
         size = 1.5,
-				 position = position_dodge(width = 1)) +
-	labs(x = "Role", 
+        position = position_dodge(width = 1)
+    ) +
+    labs(
+        x = "Role",
         y = "Lexical frequency (Zipf)",
         colour = "Study",
-		 fill = "Study") +
-
+        fill = "Study"
+    ) +
     mp |>
-	filter(role!="distractor") |> 
-	mutate(condition = if_else(role=="target", 
-							   "related/unrelated", condition)) |> 
+    filter(role != "distractor") |>
+    mutate(condition = if_else(role == "target",
+        "related/unrelated", condition
+    )) |>
     ggplot(aes(condition, aoa, colour = study, fill = study)) +
     facet_wrap(~role, scales = "free_x") +
-	geom_dots(side = "both",
+    geom_dots(
+        side = "both",
         layout = "swarm",
@@
         position = position_dodge(width = 1),
-			  alpha = 1/5) +
-	stat_summary(geom = "errorbar",
+        alpha = 1 / 5
+    ) +
+    stat_summary(
+        geom = "errorbar",
         fun.data = mean_se,
         width = 0.1,
-				 linewidth = 1/2,
-				 position = position_dodge(width = 1)) +
-	stat_summary(geom = "point",
+        linewidth = 1 / 2,
+        position = position_dodge(width = 1)
+    ) +
+    stat_summary(
+        geom = "point",
         fun = mean,
         size = 1.5,
-				 position = position_dodge(width = 1)) +
-	geom_text_repel(data = summarise(mp, aoa = min(aoa, na.rm = TRUE),
+        position = position_dodge(width = 1)
+    ) +
+    geom_text_repel(
+        data = summarise(mp,
+            aoa = min(aoa, na.rm = TRUE),
             word = word[which.min(aoa)],
-									 .by = c(study, role, condition)),
-					aes(label = word), max.overlaps = 100) |> 
-	labs(x = "Role", 
+            .by = c(study, role, condition)
+        ),
+        aes(label = word), max.overlaps = 100
+    ) |>
+    labs(
+        x = "Role",
         y = "Familiarity at 18 months",
         colour = "Study",
-		 fill = "Study") +
-	scale_y_continuous(labels = scales::percent,
-					   limits = c(0, 1)) +
-
+        fill = "Study"
+    ) +
+    scale_y_continuous(
+        labels = scales::percent,
+        limits = c(0, 1)
+    ) +
     plot_layout(nrow = 1, guides = "collect") &
     plot_annotation(tag_levels = "A") &
-	theme(legend.position = "top",
+    theme(
+        legend.position = "top",
         legend.title = element_blank(),
         axis.title.x = element_blank(),
-		  panel.grid.major.y = element_line(colour = "grey",
-		  								  linetype = "dotted"))
+        panel.grid.major.y = element_line(
+            colour = "grey",
+            linetype = "dotted"
+        )
+    )
 ```
@@
 oxf_vocab <- vocabulary |>
-	inner_join(filter(attrition_participants,
-					  is_valid_participant),
-			   by = join_by(session_id)) |>
+    inner_join(
+        filter(
+            attrition_participants,
+            is_valid_participant
+        ),
+        by = join_by(session_id)
+    ) |>
     inner_join(participants,
-			   by = join_by(child_id, session_id, vocab_id)) |>
-	filter(test_language=="English") |>
-	summarise(l1_count_sd = sd(l1_count), 
+        by = join_by(child_id, session_id, vocab_id)
+    ) |>
+    filter(test_language == "English") |>
+    summarise(
+        l1_count_sd = sd(l1_count),
         l1_count = mean(l1_count),
-			  .by = age_group) |> 
+        .by = age_group
+    ) |>
     arrange(age_group)
@@
 Participants in @avila2021longitudinal knew an average of 405.24 (*SD* = 96.29) at 21 months and 501.97	(*SD* = 73.41) at 24 months, which contrast with receptive vocabulary sizes of participants in Study 1: `r round(oxf_vocab$l1_count[1], 2)` at 21 months (*SD* = `r round(oxf_vocab$l1_count_sd[1], 2)`), and `r round(oxf_vocab$l1_count[2], 2)` (*SD* = `r round(oxf_vocab$l1_count_sd[2], 2)`) at 25 months.
-Estimates from both questionnaires should be compared with caution---if at all---given their different lengths.
-It possible that the apparent smaller vocabulary size of English participants in Study 1 is a measurement artefact, resulting from a lower upper bound in the possible number of words that can be marked acquired by caregivers.
 

### 2025-12-09 R/participants.R

@@ -1,97 +1,147 @@
 #' Get participant-level information
 #'
-get_participants <- function(participants_file_bcn,
-							 participants_file_oxf){
-	
-	lp_levels <- c("Monolingual (English)", "Monolingual", "Bilingual")
-	lang_levels <- c("Catalan", "English", "Spanish")
-	sex_levels <- c("f", "m")
-	
-	participants_bcn <- read_csv(participants_file_bcn, 
-								 na = c("NA", ""),
-								 name_repair = janitor::make_clean_names,
-								 show_col_types = FALSE) |> 
-		mutate(across(matches("id"), as.character),
-			   across(starts_with("date_"), dmy),
-			   across(starts_with("doe_"), 
-			   	   \(x) as.numeric(gsub("%", "", x)) * 0.01),
-			   vocab_id_response = vocab_id,
-			   age_group = paste0(age_group, " months"),
-			   valid_participant = as.logical(valid_participant)) |> 
-		filter(!pilot, !is.na(child_id), !is.na(filename), valid_participant) |> 
-		select(child_id, session_id, session_n = session,
-			   vocab_id, vocab_id_response,
-			   date_test, date_birth, lp, age_group, age, sex, version,
-			   matches("doe"), test_language, list, filename) 
-	
-	
-	participants_oxf <- participants_file_oxf |> 
-		read_csv(name_repair = janitor::make_clean_names, 
-				 show_col_types = FALSE,
-				 progress = FALSE) |> 
-		slice(-c(1, 45:50, 84:91, 149:155)) |> 
-		rename(child_id = participant_id,
-			   vocab_id = unique_id_for_cdi_matching,
-			   age_group = test_cohort,
-			   lp = group,
-			   sex = gender,
-			   date_test = dot,
-			   comments = notes,
-			   list = cp_ver) |> 
-		mutate(across(starts_with("date_"), 
-					  \(x) suppressWarnings(dmy(x))),
-			   across(matches("_id"), as.character),
-			   age_group = paste0(age_group, " months"),
-			   age_group = as.factor(age_group),
-			   vocab_id_response = if_else(grepl("^R_", vocab_id),
-			   							vocab_id, NA_character_),
-			   session_id = child_id,
-			   child_id = if_else(!is.na(previous_id_if_applicable),
-			   				   previous_id_if_applicable,
-			   				   child_id),
-			   sex = tolower(substr(sex, 1, 1)),
-			   date_birth = date_test - days(age_days),
-			   age = difftime(date_test, date_test - days(age_days)) |> 
[…]

### 2025-12-09 R/stimuli.R

@@ -28,7 +28,8 @@ get_audio_duration <- function(trials) {
     grepl("-eng", audio.paths) ~ "English"
   )
 
-  durations$duration <- if_else(durations$test_language == "English",
+  durations$duration <- if_else(
+    durations$test_language == "English",
     durations$duration - 4,
     durations$duration
   )
@@ -40,7 +41,9 @@ get_audio_duration <- function(trials) {
     id = "Latin-ASCII"
   )
 
-  duration <- inner_join(trials_tmp, durations,
+  duration <- inner_join(
+    trials_tmp,
+    durations,
     relationship = "many-to-many",
     by = join_by(test_language, audio)
   )
@@ -50,16 +53,23 @@ get_audio_duration <- function(trials) {
 
 #' Get duration of a WAV file
 get_duration <- function(audio_path) {
-  if (!file.exists(audio_path)) cli::cli_abort("{audio_path} does not exist")
+  if (!file.exists(audio_path)) {
+    cli::cli_abort("{audio_path} does not exist")
+  }
   sound <- tuneR::readWave(audio_path) # extract wave
   sound.length <- round(length(sound@left) / sound@samp.rate, 2) # duration
 }
 
 #' Get familiarity data
 #'
-get_familiarity <- function(words, bvq_data, stim_stats_file_oxf,
-                            type = "understands", age = c(17, 19),
-                            .width = 0.95) {
+get_familiarity <- function(
+  words,
+  bvq_data,
+  stim_stats_file_oxf,
+  type = "understands",
+  age = c(17, 19),
+  .width = 0.95
+) {
   fam_oxf <- readxl::read_xlsx(stim_stats_file_oxf) |>
     select(stimulus = item, familiarity = ocdi18_comp) |>
     distinct(stimulus, .keep_all = TRUE) |>
@@ -72,21 +82,18 @@ get_familiarity <- function(words, bvq_data, stim_stats_file_oxf,
     bvq_data$responses,
     age = age,
     .width = .width,
-    lp, language
+    lp,
+    language
   ) |>
     filter(
       item_dominance == "L1",
       type == "understands",
       lp == "Monolingual"
     ) |>
-    summarise(across(c(.sum, .n), sum),
-      .by = c(item, language)
-    ) |>
+    summarise(across(c(.sum, .n), sum), .by = c(item, language)) |>
     mutate(familiarity = .sum / .n) |>
     rename(test_language = language) |>
-    right_join(select(words, stimulus, item),
-      by = join_by(item)
-    ) |>
[…]

### 2025-12-09 _targets.R

@@ -27,11 +27,14 @@ suppressPackageStartupMessages({
 # load functions ---------------------------------------------------------------
 
 invisible({
-  lapply(list.files(
-    path = c("R", "tests/testthat"),
-    full.names = TRUE,
-    pattern = "\\.R$"
-  ), source)
+  lapply(
+    list.files(
+      path = c("R", "tests/testthat"),
+      full.names = TRUE,
+      pattern = "\\.R$"
+    ),
+    source
+  )
 })
 
 # set params -------------------------------------------------------------------
@@ -61,11 +64,11 @@ tar_option_set(
 # it will take shorter after the first time, as it only runs the outdated targets
 
 list(
-
   # get BVQ data -------------------------------------------------------------
 
   # this returns a list with all necessary data
-  tar_target(bvq_data_file,
+  tar_target(
+    bvq_data_file,
     file.path("data-raw", "stimuli", "bvq.rds"),
     format = "file"
   ),
@@ -73,29 +76,40 @@ list(
 
   # stimuli ------------------------------------------------------------------
 
-  tar_target(trials_file, file.path("data-raw", "stimuli", "trials.xlsx"),
+  tar_target(
+    trials_file,
+    file.path("data-raw", "stimuli", "trials.xlsx"),
     format = "file"
   ),
   tar_target(trials, readxl::read_xlsx(trials_file)),
-  tar_target(words_file,
+  tar_target(
+    words_file,
     file.path("data-raw", "stimuli", "words.xlsx"),
     format = "file"
   ),
   tar_target(words, readxl::read_xlsx(words_file)),
-  tar_target(stim_stats_file_oxf, file.path("data-raw", "stimuli", "stim-stats-oxf.xlsx")),
-  tar_target(familiarity, get_familiarity(words, bvq_data, stim_stats_file_oxf)),
+  tar_target(
+    stim_stats_file_oxf,
+    file.path("data-raw", "stimuli", "stim-stats-oxf.xlsx")
+  ),
+  tar_target(
+    familiarity,
+    get_familiarity(words, bvq_data, stim_stats_file_oxf)
+  ),
   tar_target(childes, get_childes_corpora(words$childes_lemma, "eng")),
   tar_target(frequencies, get_frequency_childes(childes, words$childes_lemma)),
-  # tar_target(durations, get_audio_duration(trials)),
+  tar_target(durations, get_audio_duration(trials)),
[…]
